### 2019-04-02 main.tex
Initial Overleaf Import

% Deze template is gemaakt door Fons van der Plas (f.vanderplas@student.ru.nl) voor het publiek domein en mag gebruikt worden **zonder vermelding van zijn naam**.
% This template was created by Fons van der Plas (f.vanderplas@student.ru.nl) for the public domain, and may be used **without attribution**.
\documentclass{article}
\usepackage[utf8]{inputenc}     % for éô
\usepackage[english]{babel}       % for proper word breaking at line ends
\usepackage[a4paper, left=1.5in, right=1.5in, top=1.5in, bottom=1.5in]{geometry}
                                % for page size and margin settings
\usepackage{graphicx}           % for ?
\usepackage{amsmath,amssymb}    % for better equations
\usepackage{amsthm}             % for better theorem styles
\usepackage{mathtools}          % for greek math symbol formatting
\usepackage{enumitem}           % for control of 'enumerate' numbering
\usepackage{listings}           % for control of 'itemize' spacing
\usepackage{todonotes}          % for clear TODO notes
\usepackage{hyperref}           % page numbers and '\ref's become clickable
\usepackage[fixlanguage]{babelbib}
                                % voor een Nederlands referentielijstje

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%    TITELPAGINA WOORDJES    %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%             ||               %
%             ||               %
%             \/               %

\def\thesistitle{Automatic Refactoring of Code Clones in Object-Oriented Programming Languages}
\def\thesissubtitle{Improving a systems maintainability with the push of a button}
\def\thesisauthorfirst{Simon}
\def\thesisauthorsecond{Baars}
\def\thesissupervisorfirst{dr. Ana}
\def\thesissupervisorsecond{Oprescu}
\def\thesissecondreaderfirst{dr. Xander}
\def\thesissecondreadersecond{Schrijen}
\def\thesisdate{\today}

%             /\               %
%             ||               %
%             ||               %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%    TITELPAGINA WOORDJES    %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% FOR PDF METADATA
\title{\thesistitle}
\author{\thesisauthorfirst\space\thesisauthorsecond}
\date{\thesisdate}

%% TODO PACKAGE
\newcommand{\towrite}[1]{\todo[inline,color=yellow!10]{NOG SCHRIJVEN: #1}}

%% THEOREM STYLES
\newtheorem{theorem}{Stelling}[section]
\newtheorem{corollary}{Gevolg}[theorem]
\newtheorem{Lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Propositie}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definitie}

\theoremstyle{remark}
\newtheorem*{remark}{Opmerking}

%% MATH OPERATORS
\DeclareMathOperator{\supersine}{supersin}
\DeclareMathOperator{\supercosine}{supercos}

%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\begin{titlepage}
	\thispagestyle{empty}
	\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
	\center
	%\textsc{\Large Radboud Universiteit Nijmegen}\\[.7cm]
	\includegraphics[width=100mm]{img/logoUvA_en.pdf}\\[.5cm]
	\textsc{Faculty of Science}\\[0.5cm]

	\HRule \\[0.4cm]
	{ \huge \bfseries \thesistitle}\\[0.1cm]
	\textsc{\thesissubtitle}\\
	\HRule \\[.5cm]
	\textsc{\large Master Thesis Software Engineering}\\[.5cm]

	\begin{minipage}{0.4\textwidth}
	\begin{flushleft} \large
	\emph{Author:}\\
	\thesisauthorfirst\space \thesisauthorsecond \\[1em]
	\emph{Student Number:}\\
	12072931 \\[1em]
	\end{flushleft}
	\end{minipage}
	~
	\begin{minipage}{0.4\textwidth}
	\begin{flushright} \large
	\emph{Academic Supervisor:} \\
	\thesissupervisorfirst\space \thesissupervisorsecond 
	\emph{Company Supervisor:} \\
	\thesissecondreaderfirst\space \thesissecondreadersecond \\[1em]
	\emph{Company:} \\
	Software Improvement Group\space \textsc{\thesissecondreadersecond}
	\end{flushright}
	\end{minipage}\\[4cm]
	\vfill
	{\large \thesisdate}\\
	\clearpage
\end{titlepage}

\tableofcontents

\newpage
\section{Complexe dingetjes}
\subsection{Domeintjes}
Laten we beginnen met het volgende definitietje:
\begin{definition}\label{def:domain}
Een verzamelinkje $U \in \mathbb{C}$ is een \emph{domeintje} wanneer:
\begin{itemize}
    \item $U$ open is $\mathbb{C}$ en
    \item $U$ verbonden is.
\end{itemize}
\end{definition}

\subsection{Yumyumyumyum}
\towrite{een inleidinkje en wat voorbeeldjes}

\begin{theorem}[]
Stel $n \in \mathbb{Z}$, dan zijn de volgende uitspraakjes equivalent:
\begin{enumerate}[label=\roman*.]
    \item $n > 5$.
    \item $5 > 5$.\todo{Hier rammelt iets aan...}
    \item Voor elke $n \in n$ geldt:
    \begin{align}\label{eq:truth}
        n > n+1 > n+1^2 > \dots > n+7.
    \end{align}
    waarbij $7$ een willekeurig elementje is van:
    \begin{align*}
        \oint_{a}^{b} \supersine \alpha + i \supercosine \beta  db(a).
    \end{align*}
\end{enumerate}
\end{theorem}

\begin{remark}
Joepie!
\end{remark}
\begin{proof}
Zie \cite{Rynne2008LinearAnalysis}.
\end{proof}

\begin{figure}[h]
    \centering
    \includegraphics[width=.3\textwidth]{img/in_dei_nomine_feliciter.eps}
    \caption{Insperend illustratietje. Lijkt een beetje op \cite{Oort1958,Reed1960}.}
    \label{fig:logo}
\end{figure}

\begin{corollary}
Stel $U \subseteq \mathbb{C}$ is een domeintje (zie Definitietje \ref{def:domain}) en $f: \overline{U} \rightarrow \mathbb{C}$ is continu op $\overline{U}$ en holomorf op $U$. Als $z \mapsto |f(z)|$ constant is op $\partial U$, dan heeft $f$ een nulletje in $U$.
\end{corollary}
\begin{proof}
Zoniet, beschouw dan $\frac{1}{f}$.
\end{proof}
Het bewijsje van dit stellinkje is te zien in Figuurtje \ref{fig:logo}.

\begin{figure}
    \centering
    \includegraphics[width=.7\textwidth]{img/cat.jpg}
    \caption{A lief hondje.}
    \label{fig:my_label}
\end{figure}

\newpage

% Je kan zelf een referentiestijltje kiezen, 'plain' is het standaardje
% Zie:
% https://www.overleaf.com/learn/latex/Bibtex_bibliography_styles
% 
% We gebruiken het package-je 'babelbib' om de referentietjes in het nederlands te geven. Voeg daarom het woordje 'bab' toe aan het beginnetje van het stijltje.
% De optietjes zijn: babplain, babunsrt, bababbrv en babalpha.

% Het gebruiken van babplain geeft een warninkje: "BibTeX empty language in ...". Dit kan je vermijden door ",language={dutch}" toe te voegen aan elk itempje van references.bib.

\bibliographystyle{babplain}
\bibliography{references.bib}

\end{document}

% Veel succes!

% groetjes van Fons

### 2019-04-03 main.tex
Stuff

@@
-% Deze template is gemaakt door Fons van der Plas (f.vanderplas@student.ru.nl) voor het publiek domein en mag gebruikt worden **zonder vermelding van zijn naam**.
-% This template was created by Fons van der Plas (f.vanderplas@student.ru.nl) for the public domain, and may be used **without attribution**.
 \documentclass{article}
@@
 	\HRule \\[.5cm]
-	\textsc{\large Master Thesis Software Engineering}\\[.5cm]
+	\textsc{\large Master Thesis Software Engineering}\\[2cm]
 
@@
 	\emph{Academic Supervisor:} \\
-	\thesissupervisorfirst\space \thesissupervisorsecond 
+	\thesissupervisorfirst\space \thesissupervisorsecond \\[1em]
 	\emph{Company Supervisor:} \\
@@
 \newpage
-\section{Complexe dingetjes}
-\subsection{Domeintjes}
-Laten we beginnen met het volgende definitietje:
-\begin{definition}\label{def:domain}
-Een verzamelinkje $U \in \mathbb{C}$ is een \emph{domeintje} wanneer:
-\begin{itemize}
-    \item $U$ open is $\mathbb{C}$ en
-    \item $U$ verbonden is.
-\end{itemize}
-\end{definition}
+\section{Introduction}
 
-\subsection{Yumyumyumyum}
-\towrite{een inleidinkje en wat voorbeeldjes}
-
-\begin{theorem}[]
-Stel $n \in \mathbb{Z}$, dan zijn de volgende uitspraakjes equivalent:
-\begin{enumerate}[label=\roman*.]
-    \item $n > 5$.
-    \item $5 > 5$.\todo{Hier rammelt iets aan...}
-    \item Voor elke $n \in n$ geldt:
-    \begin{align}\label{eq:truth}
-        n > n+1 > n+1^2 > \dots > n+7.
-    \end{align}
-    waarbij $7$ een willekeurig elementje is van:
-    \begin{align*}
-        \oint_{a}^{b} \supersine \alpha + i \supercosine \beta  db(a).
-    \end{align*}
-\end{enumerate}
-\end{theorem}
-
-\begin{remark}
-Joepie!
-\end{remark}
-\begin{proof}
-Zie \cite{Rynne2008LinearAnalysis}.
-\end{proof}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=.3\textwidth]{img/in_dei_nomine_feliciter.eps}
-    \caption{Insperend illustratietje. Lijkt een beetje op \cite{Oort1958,Reed1960}.}
-    \label{fig:logo}
-\end{figure}
-
-\begin{corollary}
-Stel $U \subseteq \mathbb{C}$ is een domeintje (zie Definitietje \ref{def:domain}) en $f: \overline{U} \rightarrow \mathbb{C}$ is continu op $\overline{U}$ en holomorf op $U$.
-Als $z \mapsto |f(z)|$ constant is op $\partial U$, dan heeft $f$ een nulletje in $U$.
-\end{corollary}
-\begin{proof}
-Zoniet, beschouw dan $\frac{1}{f}$.
-\end{proof}
-Het bewijsje van dit stellinkje is te zien in Figuurtje \ref{fig:logo}.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=.7\textwidth]{img/cat.jpg}
-    \caption{A lief hondje.}
-    \label{fig:my_label}
-\end{figure}
+\section{}
 
 \newpage
-
-% Je kan zelf een referentiestijltje kiezen, 'plain' is het standaardje
-% Zie:
-% https://www.overleaf.com/learn/latex/Bibtex_bibliography_styles
-% 
-% We gebruiken het package-je 'babelbib' om de referentietjes in het nederlands te geven. Voeg daarom het woordje 'bab' toe aan het beginnetje van het stijltje.
-% De optietjes zijn: babplain, babunsrt, bababbrv en babalpha.
-
-% Het gebruiken van babplain geeft een warninkje: "BibTeX empty language in ...". Dit kan je vermijden door ",language={dutch}" toe te voegen aan elk itempje van references.bib.
 
@@
 \end{document}
-
-% Veel succes!
-
-% groetjes van Fons

### 2019-04-04 main.tex
Intro is OK

@@
 \usepackage{hyperref}           % page numbers and '\ref's become clickable
+\usepackage{titlesec}
 \usepackage[fixlanguage]{babelbib}
                                 % voor een Nederlands referentielijstje
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%    TITELPAGINA WOORDJES    %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%             ||               %
-%             ||               %
-%             \/               %
 
@@
 \newpage
-\section{Introduction}
-
-\section{}
+\section{Abstract}
+\todo{This should be done when most of the rest of the document is finished.}
 
 \newpage
+\section{Introduction}
+Refactoring is used to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
+There are many methods that have been introduced to help with the process of refactoring \cite{fowler2018refactoring, wake2004refactoring}.
+However, most of these methods still require manual assessment of where and when to apply them.
+Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, or does not happen at all \cite{mens2003refactoring}.
+Refactoring mostly requires some domain knowledge to do it right, but there are also refactoring opportunities that are rather trivial and repetitive to execute.
+In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
+The main goal is to improve maintainability of the refactored code.
 
+There are several models which describe ways to measure maintainability.
+None of these are sufficient to make a full assessment of the maintainability of a software project, but they strive to give a good indication.
+For this thesis, we will make use of the \textit{SIG maintainability model} \cite{heitlager2007practical}, as it is based on a lot of experience in the field of software quality assessment.
+This maintainability model is independent of programming language.
+For this thesis we will lay the main focus on the Java programming language as refactoring opportunities do feature paradigm and programming language dependent aspects \cite{choi2011extracting}.
+However, most practises used in this thesis will also be applicable with other object oriented languages, like C\#.
+
+Improving the maintainability metrics does not automatically lead to a better maintainable codebase \cite{fenton1999software}.
+For instance, in general, a bigger codebase (in volume) is harder to maintain.
+However, refactoring a big method into smaller methods can definitely improve the maintainability of the codebase (but still increase the volume metric).
+Because of this, it is important that refactorings focus on the resolution of harmful anti-patterns \cite{kapser2006cloning} rather than just the improvement of the metrics.
+This will be one of our main focus points in this thesis.
+
+For this research, we will focus on formalizing the refactoring process of dealing with duplication in code.
+To validate this approach, we will validate the refactored results with domain experts.
+Apart from that, we will show the improvement of the metrics over various open source and industrial projects.
+Likewise, we will perform an estimation of the development costs that are saved by using the proposed solution.
+
+\subsection{Research questions}
+Code clones can appear anywhere in the code.
+Whether a code clone has to be refactored, and how it has to be refactored, is dependent on where it exists in the code (it's context).
+There are many different contexts in which code clones can occur (in a method, a complete class, )
+
+\newpage
 \bibliographystyle{babplain}

### 2019-04-04 main.tex
Research questions

@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}     % for éô
+\documentclass{report}
+\usepackage[utf8]{inputenc}
 \usepackage[english]{babel}     % for proper word breaking at line ends
-\usepackage[a4paper, left=1.5in, right=1.5in, top=1.5in, bottom=1.5in]{geometry}
+\usepackage[a4paper, total={170mm,257mm}, left=20mm, right=20mm]{geometry}
                                 % for page size and margin settings
-\usepackage{graphicx}           % for ?
+\usepackage{graphicx}           % for images
 \usepackage{amsmath,amssymb}    % for better equations
@@
 \usepackage{titlesec}
-\usepackage[fixlanguage]{babelbib}
-                                % voor een Nederlands referentielijstje
+\usepackage{csquotes}
 
@@
 
-%             /\               %
-%             ||               %
-%             ||               %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%    TITELPAGINA WOORDJES    %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %% FOR PDF METADATA
@@
 \date{\thesisdate}
-
-%% TODO PACKAGE
-\newcommand{\towrite}[1]{\todo[inline,color=yellow!10]{NOG SCHRIJVEN: #1}}
 
@@
 	\center
-	%\textsc{\Large Radboud Universiteit Nijmegen}\\[.7cm]
+	%\textsc{\University of Amsterdam}\\[.7cm]
 	\includegraphics[width=100mm]{img/logoUvA_en.pdf}\\[.5cm]
@@
 \newpage
-\section{Abstract}
-\todo{This should be done when most of the rest of the document is finished.}
+\chapter{Abstract}
+\todo[inline,color=blue!10]{This should be done when most of the rest of the document is finished.}
 
 \newpage
-\section{Introduction}
+\chapter{Introduction}
 Refactoring is used to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
@@
 
-\subsection{Research questions}
+\section{Research questions}
 Code clones can appear anywhere in the code.
 Whether a code clone has to be refactored, and how it has to be refactored, is dependent on where it exists in the code (it's context).
-There are many different contexts in which code clones can occur (in a method, a complete class, )
+There are many different contexts in which code clones can occur (in a method, a complete class, in an enumeration, global variables, etc.).
+Because of this, we first must collect some information regarding in what contexts code clones exist.
+To do this, we will analyze a set of Java projects for their clones, and generalize their contexts.
+To come to this information, we have formulated the following research question:
+\begin{displayquote}
+\textbf{Research Question 1:}\\How can we group and rank clones based on their harmfulness?
+\end{displayquote}
+As a result from this research question, we expect a catalog of the different contexts in which clones occur, ordered on the amount of times they occur.
+On basis of this catalog, we have prioritized the further analysis of the clones.
+This analysis is to determine a suitable refactoring for the clone type that has been found at the design level.
+For this, we have formulated the following research question:
+\begin{displayquote}
+\textbf{Research Question 2:}\\To what extend can we suggest refactorings of clones at the design level?
+\end{displayquote}
+As a result, we expect to have proposed refactorings for the most harmful clone patterns.
+On basis of these design level refactorings we will build a model, which we will proof using Java, that applies the refactorings to corresponding methods.
+As some refactoring methods, like ``extract method'', require user input (the name of the method in the case of ``extract method''), this model will probably require some user input.
+Because of this, we have formulated the following research question:
+\begin{displayquote}
+\textbf{Research Question 3:}\\To what extend can we automatically refactor clones?
+\end{displayquote}
 
 \newpage
-\bibliographystyle{babplain}
+\bibliographystyle{plain}
 \bibliography{references.bib}

### 2019-04-09 main.tex
Helaas, geen PhD...
Foreword

@@
 \def\thesissupervisorsecond{Oprescu}
-\def\thesissecondreaderfirst{dr. Xander}
+\def\thesissecondreaderfirst{Msc. Xander}
 \def\thesissecondreadersecond{Schrijen}
@@
 
-\newpage
 \chapter{Abstract}
@@
 
-\newpage
+\chapter{Foreword}
+Automation has always been a personal interest of mine.
+Pushing a single button to start complex processes that ultimately make our lives better.
+I've always been interested in computer programming because it allows me to write such scripts.
+I've done a lot of work in test automation with Selenium Webdriver, writing automation scripts for enterprise applications.
+
+As such scripts would grow, a lot of times my creativity was held back by the need for refactoring.
+At my University we often discussed the software program anology ``taming the beast''.
+If you don't take measures to keep your software under control, it will ultimately get a life of it's own.
+
+When refactoring large programs, I noticed that I was doing a lot of repeating work.
+Often I noticed that I reimplemented (parts of) units several times, or did not use inheritance where I should have.
+Overall, it took a lot of time to refactor large code bases.
+
+This thesis is devoted to performing research to be able to automate the process of refactoring.
+My host company for this thesis is the Software Improvement Group (SIG).
+At SIG there is a strong focus on analyzing software project maintainability by looking at several maintainability metrics.
+This thesis will focus on automating the refactoring process from a maintainability viewpoint.
+
 \chapter{Introduction}
@@
 \end{displayquote}
+This research question should result in a model that describes how to apply the refactorings that resulted from the second research question.
 

### 2019-04-09 main.tex
Some scope stuff

--- 2019-04-04 main.tex
@@
 \usepackage[english]{babel}     % for proper word breaking at line ends
-\usepackage[a4paper, total={170mm,257mm}, left=20mm, right=20mm]{geometry}
+\usepackage[a4paper, total={170mm,250mm}]{geometry}
                                 % for page size and margin settings
@@
 On basis of these design level refactorings we will build a model, which we will proof using Java, that applies the refactorings to corresponding methods.
-As some refactoring methods, like ``extract method'', require user input (the name of the method in the case of ``extract method''), this model will probably require some user input.
-Because of this, we have formulated the following research question:
+For building this model, we have formulated the following research question:
 \begin{displayquote}
@@
 \end{displayquote}
+As a result from this research question, we expect to have a model to be able to refactor the highest priority clones.
+
+\section{Scope}
+In this research we will look into code clones from a refactoring viewpoint.
+There are several methods that detect code clones using a similarity score to match pieces of code.
+This similarity is often based on the amount of tokens that match between two pieces of code.
+The problem with similarity based clones is that it is hard to assess the impact of merging clones that have different tokens, but what exactly this token is is unknown.
+Because of this, we will not focus on similarity based clone detection techniques, but rather on exact matches and predefined differences.
+
+It is very disputable whether unit tests apply to the same maintainability metrics that applies to the functional code.
+Because of that, for this research, unit tests are not taken into scope.
+The findings of this research may be applicable to those classes, but we will not argue the validity.
+%TODO: There was some research about this.
 

### 2019-04-09 main.tex
Background on clone types

@@
 
+\chapter{Background}
+\section{Clone types}
+Duplication in code is found in many different forms.
+Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}.
+Sometimes this code is then adapted to fit the new context.
+To reason about these modifications, several clone types have been proposed.
+These clone types are described in Roy et al \cite{roy2007survey}:
+\begin{displayquote}
+\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
+\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
+\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
+\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
+\end{displayquote}
+There are many papers that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection}.
+
+\chapter{Analyzing clone harmfulness}
+
+%What makes clones harmful?
+
+\chapter{Analyzing clone refactorings}
+
+\section{Catalogue of clones and their refactorings}
+
 \newpage

### 2019-04-10 main.tex
Clone types

@@
 \end{displayquote}
-There are many papers that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection}.
+A higher type of clone means that it's harder to detect and less subtle.
+There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
+
+\subsection{Relevance to clone refactoring}
+Higher type clones are not only harder to detect, but also harder to refactor.
+How to refactor clones is heavily dependent on it's context and type.
+Type I clones can commonly be refactored by using the ``Extract method'' refactoring
 

### 2019-04-10 main.tex
Clone contexts

@@
 \def\thesissupervisorsecond{Oprescu}
-\def\thesissecondreaderfirst{dr. Xander}
-\def\thesissecondreadersecond{Schrijen}
+\def\thesissecondreaderfirst{Xander}
+\def\thesissecondreadersecond{Schrijen, MSc.}
 \def\thesisdate{\today}
@@
 \chapter{Background}
+\section{Clone contexts}
+Code clones can be found anywhere in the code.
+The most commonly studied type of clone is the method-level clone.
+Method-level clones are duplicated blocks of code in the body of a method.
+Many clone detection tools only focus on method-level clones (like CPD\footnote{CPD is part of PMD, a commonly used source code analyzer: \url{https://github.com/pmd/pmd}}, Siamese\footnote{Siamese is an Elasticsearch based clone detector: \url{https://github.com/UCL-CREST/Siamese}}, Sysiphus\footnote{Sysiphus crawls the Java library for existing implementations of parts of a codebase: \url{https://github.com/fruffy/Sisyphus}}).
+The reason for this is that with method-level clones it's most likely that the clones are harmful, and they are more straight-forward to refactor.
+
+A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning.
+In this paper the author argues that 98\% are produced at method-level.
+However, the paper that is cited to support this claim \cite{bergman2004ethnographic} does not conclude this same information.
+First of all, the study that is referenced uses a very small dataset (460 copy & paste instances by 11 participants).
+Secondly, the group of subject only consists og IBM researchers (selection bias).
+Thirdly, it only focuses on copy and paste instances, as opposed to other ways clones can creep into the code.
+Finally, the ``98\%'' is not stated explicitly, but is vaguely derivable from one of the figures (figure 1) in this paper.
+Because of this, there is no reliable overview of how many clones there are in different contexts.
+
+This thesis will focus on measuring how many clones there are per context.
+This way we can determine the impact of focussing our search on a specific context, like the analysis of only method-level clones.
+Our hypothesis is that the 98\% claim is not true (we think this should be far less).
+We also hypothesize that clones in different contexts than method-level are less likely to be harmful and less straight forward to refactor.
+
 \section{Clone types}
@@
 How to refactor clones is heavily dependent on it's context and type.
-Type I clones can commonly be refactored by using the ``Extract method'' refactoring
+Method-level Type I clones can commonly be refactored by using the ``Extract method'' refactoring \cite{kodhai2013method}.
+
+\chapter{Clone detection}
 
@@
 
-%What makes clones harmful?
+%TODO: What makes clones harmful?
 

### 2019-04-10 main.tex
Clone contexts

@@
 \chapter{Background}
-\section{Clone contexts}
+\section{Clone Class}
+
+\section{Clone Contexts}
 Code clones can be found anywhere in the code.
@@
 Method-level clones are duplicated blocks of code in the body of a method.
-Many clone detection tools only focus on method-level clones (like CPD\footnote{CPD is part of PMD, a commonly used source code analyzer: \url{https://github.com/pmd/pmd}}, Siamese\footnote{Siamese is an Elasticsearch based clone detector: \url{https://github.com/UCL-CREST/Siamese}}, Sysiphus\footnote{Sysiphus crawls the Java library for existing implementations of parts of a codebase: \url{https://github.com/fruffy/Sisyphus}}).
+Many clone detection tools only focus on method-level clones (like CPD\footnote{CPD is part of PMD, a commonly used source code analyzer: \url{https://github.com/pmd/pmd}}, Siamese\footnote{Siamese is an Elasticsearch based clone detector: \url{https://github.com/UCL-CREST/Siamese}}, Sysiphus\footnote{Sisyphus crawls the Java library for existing implementations of parts of a codebase: \url{https://github.com/fruffy/Sisyphus}}).
 The reason for this is that with method-level clones it's most likely that the clones are harmful, and they are more straight-forward to refactor.
@@
 However, the paper that is cited to support this claim \cite{bergman2004ethnographic} does not conclude this same information.
-First of all, the study that is referenced uses a very small dataset (460 copy & paste instances by 11 participants).
+First of all, the study that is referenced uses a very small dataset (460 copy \& paste instances by 11 participants).
 Secondly, the group of subject only consists og IBM researchers (selection bias).
@@
 
-\section{Clone types}
+\subsection{Clone refactoring in relationship to its context}
+How to refactor clones is highly dependent on their context.
+Method-level clones can be extracted to a method \cite{kodhai2013method} if all occurrences of the clone reside in the same class.
+If a method level clone is duplicated among classes in the same inheritance structure, we might need to pull-up a method in the inheritance structure.
+If instances of a method level clone are not in the same inheritance structure, we might need to either make a static method or create an inheritance structure ourselves.
+So not only a single instance of a clone has a context, but also the relationship between individual instances in a clone class.
+This is highly relevant to the way in which the clone has to be refactored.
+
+\section{Clone Types}
 Duplication in code is found in many different forms.

### 2019-04-10 main.tex
Clone class

@@
 \usepackage{csquotes}
+\usepackage{float}
 
@@
 \section{Clone Class}
+Before we go into the refactoring of code clones, we must first define how we identify a clone.
+Roy \cite{roy2007survey} distinguishes clone pairs, clone classes and clone class families.
+For this thesis we will consider only ``clone classes'', as the other concepts do not add to the understanding and reasoning of clones as applied in this thesis.
+Roy defined ``clone classes'' as \textit{the union of all code portions/fragments which are identical or similar to each other}.
+
+As an example, look at the code fragment displayed in figure \ref{fig:cloneclass}.
+It displays two clone classes.
+One clone class is in all three files, and has two lines in each file (line 5 and 6).
+The other clone class is only in the first two files, and has three lines in each file (line 5-7).
+The clone classes overlap partly.
+\begin{figure}[H]
+	\includegraphics[width=1\textwidth]{img/clone-class}
+	\caption{Simple example of two clone classes, one consisting of three blocks of code of three lines, one existing of two blocks of code of two lines.}
+	\label{fig:cloneclass}
+\end{figure}
 
@@
 
+For this thesis, we have chosen not to further look at type III and IV clones, as it is very hard to formalize their refactoring processes. They are out of the scope for this thesis.
+
 \chapter{Clone detection}

### 2019-04-10 main.tex
Code clone harmfulness

@@
 Higher type clones are not only harder to detect, but also harder to refactor.
-How to refactor clones is heavily dependent on it's context and type.
-Method-level Type I clones can commonly be refactored by using the ``Extract method'' refactoring \cite{kodhai2013method}.
+How to refactor clones is heavily dependent on their context and type.
+Kodhai et al \cite{kodhai2013method} describe different refactorings that can be performed to deal with clones.
 
@@
 
+\section{Code clone harmfulness}
+There has been a lot of discussion whether code clones should be considered harmful.
+
+Most papers view clones as harmful regarding program maintainability.
+\textit{``Clones are problematic for the maintainability of a program, because if the clone is altered at one location to correct an erroneous behaviour, you cannot be sure that this correction is applied to all the cloned code as well.
+Additionally, the code base size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work.''} \cite{ostberg2014automatically}
+
+However, the harmfulness of clones depends on a lot of factors.
+A paper by Kapser et al \cite{kapser2006cloning} describes several patterns of cloning that may not be considered harmful.
+In this paper Kapser names examples where eliminating clones would compromise other important program qualities.
+Another study by Jarzabek et al \cite{jarzabek2010clones} categorized ``Essential clones'': clones that are essential because of the solution that is being modelled by the program.
+Overall, many of the benefits of code clones do not apply to most modern object-oriented programming languages.
+
+\section{State-of-the-art}
+There have been some papers that take some steps towards code clone refactoring.
+
 \chapter{Clone detection}
+Clone detection is
 

### 2019-04-11 main.tex
Writing some about the state of the art
To be continued

@@
 
-\section{State-of-the-art}
+\section{Related work}
 There have been some papers that take some steps towards code clone refactoring.
+Most research towards refactoring code clones has been conducted by Y.
+Higo et al.
+In a 2008 study \cite{higo2008metric} the authors look at the refactoring of class-level, method-level and constructor-level clones in Java.
 

### 2019-04-11 template.tex
Writing some about the state of the art
To be continued

\documentclass[a4paper,10pt,titlepage]{report}
%%This template is based on Paco van Beckhoven's thesis.

\usepackage{xspace}
\usepackage{xargs}   % Use more than one optional parameter in a new commands
\usepackage[pdftex,dvipsnames]{xcolor}

% Putting images next to each other
\usepackage[font=bf,]{caption}
\usepackage{subcaption}
\input{glyphtounicode}

% for last page
\usepackage{lastpage}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{titlepic}
\usepackage{vhistory}
\usepackage{enumitem}
\usepackage{longtable}
\usepackage[backend=biber, style=ieee,citestyle=numeric-comp]{biblatex}
\usepackage[colorinlistoftodos, prependcaption]{todonotes}
\usepackage{placeins}
\usepackage{multirow}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage[acronym,nogroupskip,nohypertypes={acronym},toc,section=chapter]{glossaries}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{cmap}

%\usepackage[ansinew]{inputenc}
%\usepackage[T1]{fontenc}
%\usepackage{libertine}
\input{glyphtounicode}

\pdfglyphtounicode{f_f}{FB00}
\pdfglyphtounicode{f_f_i}{FB03}
\pdfglyphtounicode{f_f_l}{FB04}
\pdfglyphtounicode{f_i}{FB01}

\pdfgentounicode=1

%Appendix package + appendix in chapter title
\usepackage[titletoc]{appendix}

%for highlighting findings
\usepackage{tcolorbox}

% for highlighting code examples
\usepackage{listings}

\newcommand{\ie}{\emph{i.e.},\xspace}
\newcommand{\eg}{\emph{e.g.},\xspace}
\newcommand{\etc}{\emph{etc.}\xspace}
\newcommand{\etal}{\emph{et al.}\xspace}

\newcommand{\sig}{\gls{sig}}
\newcommand{\sigs}{\glspl{sig}}

\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1, inline]{#2}}
\newcommandx{\discussion}[2][1=]{\todo[linecolor=red,backgroundcolor=green!25,bordercolor=red,inline,#1]{#2}}

\newcommandx{\improvement}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}

\newcommandx{\reminder}[2][1=]{\todo[linecolor=yellow,backgroundcolor=yellow!25,bordercolor=yellow,#1]{#2}}

\newcommandx{\lessprio}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
\newcommandx{\todocontent}[2][1=]{\todo[author=\textbf{Planned content},backgroundcolor=Goldenrod!25,bordercolor=Goldenrod,inline,#1]{#2}}

%%Some additional table column specifiers, allowing for fixed width columns that wrap.
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}

\definecolor{ryel}{HTML}{fcd116}
\definecolor{rred}{HTML}{ce1126}
\definecolor{rblu}{HTML}{0a3eb9}
%these are examples of commands that may facilitate feedback annotations in the document
%replace \paco by your name and \ana by your supervisor's name
%\newcommandx{\ana}[2][1=]{\todo[linecolor=rblu,backgroundcolor=ryel,bordercolor=rred,#1]{#2}}
%\newcommandx{\paco}[2][1=]{\todo[author=Paco,linecolor=blue,backgroundcolor=white,bordercolor=red,#1]{#2}}

% -- title page is a modified version of https://github.com/software-engineering-amsterdam/latex/blob/master/thesis/uvamscse.cls
\newcommand{\email}[1]{\ttfamily\href{mailto:#1}{#1}}

\newcommand{\uvacoverfoot}{%
	\vfill
	\begin{center}
		\begin{tabular}{r|l}
			\multirow{3}{*}{\includegraphics[height=48pt]{uva.pdf}}
			&\textsc{\Large Universiteit van Amsterdam}\\
			&\textsc{Faculteit der Natuurwetenschappen, Wiskunde en Informatica}\\
			&\textsc{Master Software Engineering}\\
			&\url{http://www.software-engineering-amsterdam.nl}
		\end{tabular}
	\end{center}
}

\renewcommand{\maketitle}{%
	% The cover page
	% --------------
	\thispagestyle{empty}
	\enlargethispage{30pt}
	\renewcommand{\thefootnote}{\fnsymbol{footnote}}
	% Will be page 0, s.t. contents start on page 1
	\setcounter{page}{0}
	% \eccoverhead
	% Volume and article title, author(s)
	\vspace{60pt}
	\begin{center}
		{\Huge\bfseries Title \par}
		% Earlier versions:
		% Assessing Test Suite Effectiveness Using Static Analysis
		% Predicting Test Suite Effectiveness Using Static Analysis
		% Predicting Test Suite Effectiveness Using Static Source Code Analysis
		% Assessing Test Suite Effectiveness Using Static Analysis
		% Predicting test suite effectiveness using static analysis
		\vspace{44pt}
		{\Large\bfseries Author \par}
		\email{author email}\\
		\vspace{11pt}
		July 16, 2017, \pageref{LastPage} pages
	\end{center}
	\vfill
	\begin{tabular}{ll}
		\textbf{Research supervisor:} 	& Name academic supervisor, \email{academic supervisor email} \\
		\textbf{Host/Daily supervisor:} & Name industry/daily supervisor, \email{industry supervisor email}\\
		\textbf{Host organisation/Research group:} & Name Host organization/Research group, \url{website organization/research group}
	\end{tabular}
	\uvacoverfoot
	\newpage
	\setcounter{footnote}{0}
	\renewcommand{\thefootnote}{\arabic{footnote}}
	\setlength{\parskip}{0pt}
}

%\newcommand{\uvaabstract}{}latex
%\renewcommand{\abstract}[2][Abstract]{\renewcommand{\uvaabstract}{\chapter*{Abstract}%
%\par#2\newpage}}

%-------- End of ``title page''

%Fancy page headers
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyfoot[C]{\thepage}
\setlength{\headheight}{14pt}

%%FINDING ENV
\newcounter{findingctr}

\newenvironment{finding}{%      define a custom environment
	\refstepcounter{findingctr}% increment the environment's counter
	\begin{tcolorbox}
	\textbf{Finding \thefindingctr:}
}{\end{tcolorbox}}
% If you want numbers that start with the chapter or section number (e.g. 7.1.1 or 7.1) enable the following lines
%\usepackage{amsmath}
%\numberwithin{findingctr}{chapter}

% Decrease the size of all these lists
\setlist{noitemsep,topsep=4pt,parsep=1pt,partopsep=4pt}

\lstset{
	basicstyle=\footnotesize,        % the size of the fonts that are used for the code
	breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
	breaklines=true,                 % sets automatic line breaking
	captionpos=b,                    % sets the caption-position to bottom
	frame=single,                    % adds a frame around the code
	language=Java,                 % the language of the code
	keywordstyle=\bf,
	tabsize=2                       % sets default tabsize to 2 spaces
}

%make it fit more nicely
\setlength\extrarowheight{2pt}

\input{acronym}
\makeglossaries
\bibliography{main}

\begin{document}

\maketitle
\input{sections/abstract}
\tableofcontents
\input{sections/introduction}
\input{sections/background}
\input{sections/research}
\input{sections/results}
\input{sections/discussion}
\input{sections/related_work}
\input{sections/conclusion}
\input{sections/acknowledgements}

\printbibliography[heading=bibintoc]
\printglossaries%

\input{sections/appendix}

%comment out in the final version
%\listoftodos[Notes]

\end{document}

### 2019-04-11 sections/abstract.tex
Imported template stuff

\chapter*{Abstract}
\todo[inline,color=blue!10]{This should be done when most of the rest of the document is finished. Be concise, introduce context, problem, known approaches, your solution, your findings.}

### 2019-04-11 sections/acknowledgements.tex
Imported template stuff

\chapter*{Acknowledgements}
If so inclined, thank people.

### 2019-04-11 sections/background.tex
Imported template stuff

\chapter{Background}
\label{ch:background}
This chapter will present the necessary background information for this thesis. First, we define some basic terminology that will be used throughout this thesis. Next, ...

### 2019-04-11 sections/conclusion.tex
Imported template stuff

\chapter{Conclusion}
\label{ch:conclusion}

\section{Future work}
\label{sec:future_work}

### 2019-04-11 sections/discussion.tex
Imported template stuff

\chapter{Discussion}
\label{ch:discussion}
In this chapter, we discuss the results of our experiment(s) on ...

\begin{finding}
	Highlight like this an important finding of your analysis of the results.
	\label{find:important1}
\end{finding}

Refer to Finding~\ref{find:important1}.

### 2019-04-11 sections/introduction.tex
Imported template stuff

\chapter{Introduction}
\label{ch:introduction}
Context: what is the bigger scope of the problem you are trying to solve? Try to connect to societal/economical challenges.
Problem Analysis: Here you present your analysis of the problem situation that your research will address.
How does this problem manifest itself at your host organisation?
Also summarises existing scientific insight into the problem.

\section{Problem statement}

\subsection{Research questions}
To tackle these issues, we investigate ...

\subsection{Research method}

\section{Contributions}
Our research makes the following contributions:
\begin{enumerate}
	\item 1
	\item 2
	\item 3
\end{enumerate}

\section{Outline}
In Chapter~\ref{ch:background} we describe the background of this thesis. 
Chapter~\ref{ch:research} describes ... 
Results are shown in Chapter~\ref{ch:results} and discussed in Chapter~\ref{ch:discussion}. Chapter~\ref{ch:related_work}, contains the work related to this thesis.
Finally, we present our concluding remarks in Chapter~\ref{ch:conclusion} together with future work.

### 2019-04-11 sections/related_work.tex
Imported template stuff

\chapter{Related work}
\label{ch:related_work}
We divide the related work into ... categories:  ...

### 2019-04-11 sections/research.tex
Imported template stuff

\chapter{Your research}
\label{ch:research_method}

Depending on your subject, you might need multiple research chapters. Moreover, depending on how the research questions are linked, you may need to answer them one by one and then connect the answers into a final discussion chapter.

See Canvas for examples of theses with various approaches to structuring the research content.

### 2019-04-11 sections/results.tex
Imported template stuff

\chapter{Results}

\label{ch:results}
In this chapter, we present the results of our experiment.

### 2019-04-11 sections/background.tex
Imported my background and introduction

@@
 \label{ch:background}
-This chapter will present the necessary background information for this thesis. First, we define some basic terminology that will be used throughout this thesis. Next, ...
+This chapter will present the necessary background information for this thesis. Here, we define some basic terminology that will be used throughout this thesis.
+
+\section{Clone Class}
+Before we go into the refactoring of code clones, we must first define how we identify a clone.
+Roy \cite{roy2007survey} distinguishes clone pairs, clone classes and clone class families.
+For this thesis we will consider only ``clone classes'', as the other concepts do not add to the understanding and reasoning of clones as applied in this thesis.
+Roy defined ``clone classes'' as \textit{the union of all code portions/fragments which are identical or similar to each other}.
+
+As an example, look at the code fragment displayed in figure \ref{fig:cloneclass}.
+It displays two clone classes.
+One clone class is in all three files, and has two lines in each file (line 5 and 6).
+The other clone class is only in the first two files, and has three lines in each file (line 5-7).
+The clone classes overlap partly.
+\begin{figure}[H]
+	\includegraphics[width=1\textwidth]{img/clone-class}
+	\caption{Simple example of two clone classes, one consisting of three blocks of code of three lines, one existing of two blocks of code of two lines.}
+	\label{fig:cloneclass}
+\end{figure}
+
+\section{Clone Contexts}
+Code clones can be found anywhere in the code.
+The most commonly studied type of clone is the method-level clone.
+Method-level clones are duplicated blocks of code in the body of a method.
+Many clone detection tools only focus on method-level clones (like CPD\footnote{CPD is part of PMD, a commonly used source code analyzer: \url{https://github.com/pmd/pmd}}, Siamese\footnote{Siamese is an Elasticsearch based clone detector: \url{https://github.com/UCL-CREST/Siamese}}, Sysiphus\footnote{Sisyphus crawls the Java library for existing implementations of parts of a codebase: \url{https://github.com/fruffy/Sisyphus}}).
+The reason for this is that with method-level clones it's most likely that the clones are harmful, and they are more straight-forward to refactor.
+
+A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning.
+In this paper the author argues that 98\% are produced at method-level.
+However, the paper that is cited to support this claim \cite{bergman2004ethnographic} does not conclude this same information.
+First of all, the study that is referenced uses a very small dataset (460 copy \& paste instances by 11 participants).
+Secondly, the group of subject only consists og IBM researchers (selection bias).
+Thirdly, it only focuses on copy and paste instances, as opposed to other ways clones can creep into the code.
+Finally, the ``98\%'' is not stated explicitly, but is vaguely derivable from one of the figures (figure 1) in this paper.
+Because of this, there is no reliable overview of how many clones there are in different contexts.
+
+This thesis will focus on measuring how many clones there are per context.
+This way we can determine the impact of focussing our search on a specific context, like the analysis of only method-level clones.
+Our hypothesis is that the 98\% claim is not true (we think this should be far less).
+We also hypothesize that clones in different contexts than method-level are less likely to be harmful and less straight forward to refactor.
+
+\subsection{Clone refactoring in relationship to its context}
+How to refactor clones is highly dependent on their context.
+Method-level clones can be extracted to a method \cite{kodhai2013method} if all occurrences of the clone reside in the same class.
+If a method level clone is duplicated among classes in the same inheritance structure, we might need to pull-up a method in the inheritance structure.
+If instances of a method level clone are not in the same inheritance structure, we might need to either make a static method or create an inheritance structure ourselves.
+So not only a single instance of a clone has a context, but also the relationship between individual instances in a clone class.
+This is highly relevant to the way in which the clone has to be refactored.
+
+\section{Clone Types}
+Duplication in code is found in many different forms.
+Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}.
+Sometimes this code is then adapted to fit the new context.
+To reason about these modifications, several clone types have been proposed.
+These clone types are described in Roy et al \cite{roy2007survey}:
+\begin{displayquote}
+\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
+\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
+\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
+\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
+\end{displayquote}
+A higher type of clone means that it's harder to detect and less subtle.
+There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
+
+\subsection{Relevance to clone refactoring}
+Higher type clones are not only harder to detect, but also harder to refactor.
+How to refactor clones is heavily dependent on their context and type.
+Kodhai et al \cite{kodhai2013method} describe different refactorings that can be performed to deal with clones.
+
+For this thesis, we have chosen not to further look at type III and IV clones, as it is very hard to formalize their refactoring processes. They are out of the scope for this thesis.
+
+\section{Code clone harmfulness}
+There has been a lot of discussion whether code clones should be considered harmful.
+
+Most papers view clones as harmful regarding program maintainability.
+\textit{``Clones are problematic for the maintainability of a program, because if the clone is altered at one location to correct an erroneous behaviour, you cannot be sure that this correction is applied to all the cloned code as well.
+Additionally, the code base size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work.''} \cite{ostberg2014automatically}
+
+However, the harmfulness of clones depends on a lot of factors.
+A paper by Kapser et al \cite{kapser2006cloning} describes several patterns of cloning that may not be considered harmful.
+In this paper Kapser names examples where eliminating clones would compromise other important program qualities.
+Another study by Jarzabek et al \cite{jarzabek2010clones} categorized ``Essential clones'': clones that are essential because of the solution that is being modelled by the program.
+Overall, many of the benefits of code clones do not apply to most modern object-oriented programming languages.
+
+\section{Related work}
+There have been some papers that take some steps towards code clone refactoring.
+Most research towards refactoring code clones has been conducted by Y.
+Higo et al.
+In a 2008 study \cite{higo2008metric} the authors look at the refactoring of class-level, method-level and constructor-level clones in Java.

### 2019-04-11 sections/introduction.tex
Imported my background and introduction

@@
 \chapter{Introduction}
-\label{ch:introduction}
-Context: what is the bigger scope of the problem you are trying to solve? Try to connect to societal/economical challenges.
+\todo[inline,color=blue!10]{Context: what is the bigger scope of the problem you are trying to solve? Try to connect to societal/economical challenges.
 Problem Analysis: Here you present your analysis of the problem situation that your research will address.
 How does this problem manifest itself at your host organisation?
-Also summarises existing scientific insight into the problem.
+Also summarises existing scientific insight into the problem.}
+\label{ch:introduction}
+Refactoring is used to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
+There are many methods that have been introduced to help with the process of refactoring \cite{fowler2018refactoring, wake2004refactoring}.
+However, most of these methods still require manual assessment of where and when to apply them.
+Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, or does not happen at all \cite{mens2003refactoring}.
+Refactoring mostly requires some domain knowledge to do it right, but there are also refactoring opportunities that are rather trivial and repetitive to execute.
+In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
+The main goal is to improve maintainability of the refactored code.
+
+There are several models which describe ways to measure maintainability.
+None of these are sufficient to make a full assessment of the maintainability of a software project, but they strive to give a good indication.
+For this thesis, we will make use of the \textit{SIG maintainability model} \cite{heitlager2007practical}, as it is based on a lot of experience in the field of software quality assessment.
+This maintainability model is independent of programming language.
+For this thesis we will lay the main focus on the Java programming language as refactoring opportunities do feature paradigm and programming language dependent aspects \cite{choi2011extracting}.
+However, most practises used in this thesis will also be applicable with other object oriented languages, like C\#.
+
+Improving the maintainability metrics does not automatically lead to a better maintainable codebase \cite{fenton1999software}.
+For instance, in general, a bigger codebase (in volume) is harder to maintain.
+However, refactoring a big method into smaller methods can definitely improve the maintainability of the codebase (but still increase the volume metric).
+Because of this, it is important that refactorings focus on the resolution of harmful anti-patterns \cite{kapser2006cloning} rather than just the improvement of the metrics.
+This will be one of our main focus points in this thesis.
+
+For this research, we will focus on formalizing the refactoring process of dealing with duplication in code.
+To validate this approach, we will validate the refactored results with domain experts.
+Apart from that, we will show the improvement of the metrics over various open source and industrial projects.
+Likewise, we will perform an estimation of the development costs that are saved by using the proposed solution.
 
@@
 \subsection{Research questions}
-To tackle these issues, we investigate ...
+Code clones can appear anywhere in the code.
+Whether a code clone has to be refactored, and how it has to be refactored, is dependent on where it exists in the code (it's context).
+There are many different contexts in which code clones can occur (in a method, a complete class, in an enumeration, global variables, etc.).
+Because of this, we first must collect some information regarding in what contexts code clones exist.
+To do this, we will analyze a set of Java projects for their clones, and generalize their contexts.
+To come to this information, we have formulated the following research question:
+\begin{displayquote}
+\textbf{Research Question 1:}\\How can we group and rank clones based on their harmfulness?
+\end{displayquote}
+As a result from this research question, we expect a catalog of the different contexts in which clones occur, ordered on the amount of times they occur.
+On basis of this catalog, we have prioritized the further analysis of the clones.
+This analysis is to determine a suitable refactoring for the clone type that has been found at the design level.
+For this, we have formulated the following research question:
+\begin{displayquote}
+\textbf{Research Question 2:}\\To what extend can we suggest refactorings of clones at the design level?
+\end{displayquote}
+As a result, we expect to have proposed refactorings for the most harmful clone patterns.
+On basis of these design level refactorings we will build a model, which we will proof using Java, that applies the refactorings to corresponding methods.
+For building this model, we have formulated the following research question:
+\begin{displayquote}
+\textbf{Research Question 3:}\\To what extend can we automatically refactor clones?
+\end{displayquote}
+As a result from this research question, we expect to have a model to be able to refactor the highest priority clones.
 
@@
 
+\section{Scope}
+In this research we will look into code clones from a refactoring viewpoint.
+There are several methods that detect code clones using a similarity score to match pieces of code.
+This similarity is often based on the amount of tokens that match between two pieces of code.
+The problem with similarity based clones is that it is hard to assess the impact of merging clones that have different tokens, but what exactly this token is is unknown.
+Because of this, we will not focus on similarity based clone detection techniques, but rather on exact matches and predefined differences.
+
+It is very disputable whether unit tests apply to the same maintainability metrics that applies to the functional code.
+Because of that, for this research, unit tests are not taken into scope.
+The findings of this research may be applicable to those classes, but we will not argue the validity.
+
 \section{Outline}

### 2019-04-11 main.tex
Further imported the template

--- 2019-04-10 main.tex
@@
-\documentclass{report}
+\documentclass[a4paper,10pt,titlepage]{report}
+%%This template is based on Paco van Beckhoven's thesis.
+
+\usepackage{xspace}
+\usepackage{xargs}   % Use more than one optional parameter in a new commands
+\usepackage[pdftex,dvipsnames]{xcolor}
+
+% Putting images next to each other
+\usepackage[font=bf,]{caption}
+\usepackage{subcaption}
+\input{glyphtounicode}
+
+% for last page
+\usepackage{lastpage}
+
+\usepackage[english]{babel}
 \usepackage[utf8]{inputenc}
-\usepackage[english]{babel}     % for proper word breaking at line ends
-\usepackage[a4paper, total={170mm,250mm}]{geometry}
-                                % for page size and margin settings
-\usepackage{graphicx}           % for images
-\usepackage{amsmath,amssymb}    % for better equations
-\usepackage{amsthm}             % for better theorem styles
-\usepackage{mathtools}          % for greek math symbol formatting
-\usepackage{enumitem}           % for control of 'enumerate' numbering
-\usepackage{listings}           % for control of 'itemize' spacing
-\usepackage{todonotes}          % for clear TODO notes
-\usepackage{hyperref}           % page numbers and '\ref's become clickable
-\usepackage{titlesec}
 \usepackage{csquotes}
+\usepackage[margin=1in]{geometry}
+\usepackage{fancyhdr}
+\usepackage{booktabs}
+\usepackage{paralist}
+\usepackage{graphicx}
+\usepackage{tabularx}
+\usepackage{adjustbox}
+\usepackage{titlepic}
+\usepackage{vhistory}
+\usepackage{enumitem}
+\usepackage{longtable}
+\usepackage[backend=biber, style=ieee,citestyle=numeric-comp]{biblatex}
+\usepackage[colorinlistoftodos, prependcaption]{todonotes}
+\usepackage{placeins}
+\usepackage{multirow}
+\usepackage{amsmath,amssymb}
+\usepackage[hidelinks]{hyperref}
+\usepackage[acronym,nogroupskip,nohypertypes={acronym},toc,section=chapter]{glossaries}
+\usepackage{amssymb}
+\usepackage{verbatim}
+\usepackage{cmap}
 \usepackage{float}
 
-\def\thesistitle{Automatic Refactoring of Code Clones in Object-Oriented Programming Languages}
-\def\thesissubtitle{Improving a systems maintainability with the push of a button}
-\def\thesisauthorfirst{Simon}
-\def\thesisauthorsecond{Baars}
-\def\thesissupervisorfirst{dr. Ana}
-\def\thesissupervisorsecond{Oprescu}
-\def\thesissecondreaderfirst{Xander}
-\def\thesissecondreadersecond{Schrijen, MSc.}
-\def\thesisdate{\today}
+%\usepackage[ansinew]{inputenc}
+%\usepackage[T1]{fontenc}
+%\usepackage{libertine}
+\input{glyphtounicode}
 
-%% FOR PDF METADATA
-\title{\thesistitle}
-\author{\thesisauthorfirst\space\thesisauthorsecond}
-\date{\thesisdate}
+\pdfglyphtounicode{f_f}{FB00}
+\pdfglyphtounicode{f_f_i}{FB03}
+\pdfglyphtounicode{f_f_l}{FB04}
+\pdfglyphtounicode{f_i}{FB01}
 
-%% THEOREM STYLES
-\newtheorem{theorem}{Stelling}[section]
-\newtheorem{corollary}{Gevolg}[theorem]
-\newtheorem{Lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Propositie}
+\pdfgentounicode=1
 
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definitie}
+%Appendix package + appendix in chapter title
+\usepackage[titletoc]{appendix}
 
-\theoremstyle{remark}
-\newtheorem*{remark}{Opmerking}
+%for highlighting findings
+\usepackage{tcolorbox}
 
-%% MATH OPERATORS
-\DeclareMathOperator{\supersine}{supersin}
-\DeclareMathOperator{\supercosine}{supercos}
+% for highlighting code examples
+\usepackage{listings}
 
-%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand{\ie}{\emph{i.e.},\xspace}
+\newcommand{\eg}{\emph{e.g.},\xspace}
+\newcommand{\etc}{\emph{etc.}\xspace}
+\newcommand{\etal}{\emph{et al.}\xspace}
+
+\newcommand{\sig}{\gls{sig}}
+\newcommand{\sigs}{\glspl{sig}}
+
+\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1, inline]{#2}}
+\newcommandx{\discussion}[2][1=]{\todo[linecolor=red,backgroundcolor=green!25,bordercolor=red,inline,#1]{#2}}
+
+\newcommandx{\improvement}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
+
+\newcommandx{\reminder}[2][1=]{\todo[linecolor=yellow,backgroundcolor=yellow!25,bordercolor=yellow,#1]{#2}}
+
+\newcommandx{\lessprio}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
+\newcommandx{\todocontent}[2][1=]{\todo[author=\textbf{Planned content},backgroundcolor=Goldenrod!25,bordercolor=Goldenrod,inline,#1]{#2}}
+
+%%Some additional table column specifiers, allowing for fixed width columns that wrap.
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
+\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
+\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
+
+\definecolor{ryel}{HTML}{fcd116}
+\definecolor{rred}{HTML}{ce1126}
+\definecolor{rblu}{HTML}{0a3eb9}
+%these are examples of commands that may facilitate feedback annotations in the document
+%replace \paco by your name and \ana by your supervisor's name
+%\newcommandx{\ana}[2][1=]{\todo[linecolor=rblu,backgroundcolor=ryel,bordercolor=rred,#1]{#2}}
+%\newcommandx{\paco}[2][1=]{\todo[author=Paco,linecolor=blue,backgroundcolor=white,bordercolor=red,#1]{#2}}
+
+% -- title page is a modified version of https://github.com/software-engineering-amsterdam/latex/blob/master/thesis/uvamscse.cls
+\newcommand{\email}[1]{\ttfamily\href{mailto:#1}{#1}}
+
+\newcommand{\uvacoverfoot}{%
+	\vfill
+	\begin{center}
+		\begin{tabular}{r|l}
+			\multirow{3}{*}{\includegraphics[height=48pt]{uva.pdf}}
+			&\textsc{\Large Universiteit van Amsterdam}\\
+			&\textsc{Faculteit der Natuurwetenschappen, Wiskunde en Informatica}\\
+			&\textsc{Master Software Engineering}\\
+			&\url{http://www.software-engineering-amsterdam.nl}
+		\end{tabular}
+	\end{center}
+}
+
+\renewcommand{\maketitle}{%
+	% The cover page
+	% --------------
+	\thispagestyle{empty}
+	\enlargethispage{30pt}
+	\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+	% Will be page 0, s.t. contents start on page 1
+	\setcounter{page}{0}
+	% \eccoverhead
+	% Volume and article title, author(s)
+	\vspace{60pt}
+	\begin{center}
+		{\Huge\bfseries Title \par}
+		% Earlier versions:
+		% Assessing Test Suite Effectiveness Using Static Analysis
+		% Predicting Test Suite Effectiveness Using Static Analysis
+		% Predicting Test Suite Effectiveness Using Static Source Code Analysis
+		% Assessing Test Suite Effectiveness Using Static Analysis
+		% Predicting test suite effectiveness using static analysis
+		\vspace{44pt}
+		{\Large\bfseries Author \par}
+		\email{author email}\\
+		\vspace{11pt}
+		July 16, 2017, \pageref{LastPage} pages
+	\end{center}
+	\vfill
+	\begin{tabular}{ll}
+		\textbf{Research supervisor:} 	& Name academic supervisor, \email{academic supervisor email} \\
+		\textbf{Host/Daily supervisor:} & Name industry/daily supervisor, \email{industry supervisor email}\\
+		\textbf{Host organisation/Research group:} & Name Host organization/Research group, \url{website organization/research group}
+	\end{tabular}
+	\uvacoverfoot
+	\newpage
+	\setcounter{footnote}{0}
+	\renewcommand{\thefootnote}{\arabic{footnote}}
+	\setlength{\parskip}{0pt}
+}
+
+%\newcommand{\uvaabstract}{}latex
+%\renewcommand{\abstract}[2][Abstract]{\renewcommand{\uvaabstract}{\chapter*{Abstract}%
+%\par#2\newpage}}
+
+%-------- End of ``title page''
+
+%Fancy page headers
+\pagestyle{fancy}
+\fancyhf{}
+\fancyhead[L]{\leftmark}
+\fancyfoot[C]{\thepage}
+\setlength{\headheight}{14pt}
+
+%%FINDING ENV
+\newcounter{findingctr}
+
+\newenvironment{finding}{%      define a custom environment
+	\refstepcounter{findingctr}% increment the environment's counter
+	\begin{tcolorbox}
+	\textbf{Finding \thefindingctr:}
+}{\end{tcolorbox}}
+% If you want numbers that start with the chapter or section number (e.g. 7.1.1 or 7.1) enable the following lines
+%\usepackage{amsmath}
+%\numberwithin{findingctr}{chapter}
+
+% Decrease the size of all these lists
+\setlist{noitemsep,topsep=4pt,parsep=1pt,partopsep=4pt}
+
+\lstset{
+	basicstyle=\footnotesize,        % the size of the fonts that are used for the code
+	breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
+	breaklines=true,                 % sets automatic line breaking
+	captionpos=b,                    % sets the caption-position to bottom
+	frame=single,                    % adds a frame around the code
+	language=Java,                 % the language of the code
+	keywordstyle=\bf,
+	tabsize=2                       % sets default tabsize to 2 spaces
+}
+
+%make it fit more nicely
+\setlength\extrarowheight{2pt}
+
+\input{acronym}
+\makeglossaries
+\bibliography{main}
 
 \begin{document}
-\begin{titlepage}
-	\thispagestyle{empty}
-	\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
-	\center
-	%\textsc{\University of Amsterdam}\\[.7cm]
-	\includegraphics[width=100mm]{img/logoUvA_en.pdf}\\[.5cm]
-	\textsc{Faculty of Science}\\[0.5cm]
 
-	\HRule \\[0.4cm]
-	{ \huge \bfseries \thesistitle}\\[0.1cm]
-	\textsc{\thesissubtitle}\\
-	\HRule \\[.5cm]
-	\textsc{\large Master Thesis Software Engineering}\\[2cm]
+\maketitle
+\input{sections/abstract}
+\tableofcontents
+\input{sections/introduction}
+\input{sections/background}
+\input{sections/research}
+\input{sections/results}
+\input{sections/discussion}
+\input{sections/related_work}
+\input{sections/conclusion}
+\input{sections/acknowledgements}
 
-	\begin{minipage}{0.4\textwidth}
-	\begin{flushleft} \large
-	\emph{Author:}\\
-	\thesisauthorfirst\space \thesisauthorsecond \\[1em]
-	\emph{Student Number:}\\
-	12072931 \\[1em]
-	\end{flushleft}
-	\end{minipage}
-	~
-	\begin{minipage}{0.4\textwidth}
-	\begin{flushright} \large
-	\emph{Academic Supervisor:} \\
-	\thesissupervisorfirst\space \thesissupervisorsecond \\[1em]
-	\emph{Company Supervisor:} \\
-	\thesissecondreaderfirst\space \thesissecondreadersecond \\[1em]
-	\emph{Company:} \\
-	Software Improvement Group\space \textsc{\thesissecondreadersecond}
-	\end{flushright}
-	\end{minipage}\\[4cm]
-	\vfill
-	{\large \thesisdate}\\
-	\clearpage
-\end{titlepage}
+\printbibliography[heading=bibintoc]
+\printglossaries%
 
-\tableofcontents
+\input{sections/appendix}
 
-\newpage
-\chapter{Abstract}
-\todo[inline,color=blue!10]{This should be done when most of the rest of the document is finished.}
-
-\newpage
-\chapter{Introduction}
-Refactoring is used to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
-There are many methods that have been introduced to help with the process of refactoring \cite{fowler2018refactoring, wake2004refactoring}.
-However, most of these methods still require manual assessment of where and when to apply them.
-Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, or does not happen at all \cite{mens2003refactoring}.
-Refactoring mostly requires some domain knowledge to do it right, but there are also refactoring opportunities that are rather trivial and repetitive to execute.
-In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
-The main goal is to improve maintainability of the refactored code.
-
-There are several models which describe ways to measure maintainability.
-None of these are sufficient to make a full assessment of the maintainability of a software project, but they strive to give a good indication.
-For this thesis, we will make use of the \textit{SIG maintainability model} \cite{heitlager2007practical}, as it is based on a lot of experience in the field of software quality assessment.
-This maintainability model is independent of programming language.
-For this thesis we will lay the main focus on the Java programming language as refactoring opportunities do feature paradigm and programming language dependent aspects \cite{choi2011extracting}.
-However, most practises used in this thesis will also be applicable with other object oriented languages, like C\#.
-
-Improving the maintainability metrics does not automatically lead to a better maintainable codebase \cite{fenton1999software}.
-For instance, in general, a bigger codebase (in volume) is harder to maintain.
-However, refactoring a big method into smaller methods can definitely improve the maintainability of the codebase (but still increase the volume metric).
-Because of this, it is important that refactorings focus on the resolution of harmful anti-patterns \cite{kapser2006cloning} rather than just the improvement of the metrics.
-This will be one of our main focus points in this thesis.
-
-For this research, we will focus on formalizing the refactoring process of dealing with duplication in code.
-To validate this approach, we will validate the refactored results with domain experts.
-Apart from that, we will show the improvement of the metrics over various open source and industrial projects.
-Likewise, we will perform an estimation of the development costs that are saved by using the proposed solution.
-
-\section{Research questions}
-Code clones can appear anywhere in the code.
-Whether a code clone has to be refactored, and how it has to be refactored, is dependent on where it exists in the code (it's context).
-There are many different contexts in which code clones can occur (in a method, a complete class, in an enumeration, global variables, etc.).
-Because of this, we first must collect some information regarding in what contexts code clones exist.
-To do this, we will analyze a set of Java projects for their clones, and generalize their contexts.
-To come to this information, we have formulated the following research question:
-\begin{displayquote}
-\textbf{Research Question 1:}\\How can we group and rank clones based on their harmfulness?
-\end{displayquote}
-As a result from this research question, we expect a catalog of the different contexts in which clones occur, ordered on the amount of times they occur.
-On basis of this catalog, we have prioritized the further analysis of the clones.
-This analysis is to determine a suitable refactoring for the clone type that has been found at the design level.
-For this, we have formulated the following research question:
-\begin{displayquote}
-\textbf{Research Question 2:}\\To what extend can we suggest refactorings of clones at the design level?
-\end{displayquote}
-As a result, we expect to have proposed refactorings for the most harmful clone patterns.
-On basis of these design level refactorings we will build a model, which we will proof using Java, that applies the refactorings to corresponding methods.
-For building this model, we have formulated the following research question:
-\begin{displayquote}
-\textbf{Research Question 3:}\\To what extend can we automatically refactor clones?
-\end{displayquote}
-As a result from this research question, we expect to have a model to be able to refactor the highest priority clones.
-
-\section{Scope}
-In this research we will look into code clones from a refactoring viewpoint.
-There are several methods that detect code clones using a similarity score to match pieces of code.
-This similarity is often based on the amount of tokens that match between two pieces of code.
-The problem with similarity based clones is that it is hard to assess the impact of merging clones that have different tokens, but what exactly this token is is unknown.
-Because of this, we will not focus on similarity based clone detection techniques, but rather on exact matches and predefined differences.
-
-It is very disputable whether unit tests apply to the same maintainability metrics that applies to the functional code.
-Because of that, for this research, unit tests are not taken into scope.
-The findings of this research may be applicable to those classes, but we will not argue the validity.
-%TODO: There was some research about this.
-
-\chapter{Background}
-\section{Clone Class}
-Before we go into the refactoring of code clones, we must first define how we identify a clone.
-Roy \cite{roy2007survey} distinguishes clone pairs, clone classes and clone class families.
-For this thesis we will consider only ``clone classes'', as the other concepts do not add to the understanding and reasoning of clones as applied in this thesis.
-Roy defined ``clone classes'' as \textit{the union of all code portions/fragments which are identical or similar to each other}.
-
-As an example, look at the code fragment displayed in figure \ref{fig:cloneclass}.
-It displays two clone classes.
-One clone class is in all three files, and has two lines in each file (line 5 and 6).
-The other clone class is only in the first two files, and has three lines in each file (line 5-7).
-The clone classes overlap partly.
-\begin{figure}[H]
-	\includegraphics[width=1\textwidth]{img/clone-class}
-	\caption{Simple example of two clone classes, one consisting of three blocks of code of three lines, one existing of two blocks of code of two lines.}
-	\label{fig:cloneclass}
-\end{figure}
-
-\section{Clone Contexts}
-Code clones can be found anywhere in the code.
-The most commonly studied type of clone is the method-level clone.
-Method-level clones are duplicated blocks of code in the body of a method.
-Many clone detection tools only focus on method-level clones (like CPD\footnote{CPD is part of PMD, a commonly used source code analyzer: \url{https://github.com/pmd/pmd}}, Siamese\footnote{Siamese is an Elasticsearch based clone detector: \url{https://github.com/UCL-CREST/Siamese}}, Sysiphus\footnote{Sisyphus crawls the Java library for existing implementations of parts of a codebase: \url{https://github.com/fruffy/Sisyphus}}).
-The reason for this is that with method-level clones it's most likely that the clones are harmful, and they are more straight-forward to refactor.
-
-A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning.
-In this paper the author argues that 98\% are produced at method-level.
-However, the paper that is cited to support this claim \cite{bergman2004ethnographic} does not conclude this same information.
-First of all, the study that is referenced uses a very small dataset (460 copy \& paste instances by 11 participants).
-Secondly, the group of subject only consists og IBM researchers (selection bias).
-Thirdly, it only focuses on copy and paste instances, as opposed to other ways clones can creep into the code.
-Finally, the ``98\%'' is not stated explicitly, but is vaguely derivable from one of the figures (figure 1) in this paper.
-Because of this, there is no reliable overview of how many clones there are in different contexts.
-
-This thesis will focus on measuring how many clones there are per context.
-This way we can determine the impact of focussing our search on a specific context, like the analysis of only method-level clones.
-Our hypothesis is that the 98\% claim is not true (we think this should be far less).
-We also hypothesize that clones in different contexts than method-level are less likely to be harmful and less straight forward to refactor.
-
-\subsection{Clone refactoring in relationship to its context}
-How to refactor clones is highly dependent on their context.
-Method-level clones can be extracted to a method \cite{kodhai2013method} if all occurrences of the clone reside in the same class.
-If a method level clone is duplicated among classes in the same inheritance structure, we might need to pull-up a method in the inheritance structure.
-If instances of a method level clone are not in the same inheritance structure, we might need to either make a static method or create an inheritance structure ourselves.
-So not only a single instance of a clone has a context, but also the relationship between individual instances in a clone class.
-This is highly relevant to the way in which the clone has to be refactored.
-
-\section{Clone Types}
-Duplication in code is found in many different forms.
-Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}.
-Sometimes this code is then adapted to fit the new context.
-To reason about these modifications, several clone types have been proposed.
-These clone types are described in Roy et al \cite{roy2007survey}:
-\begin{displayquote}
-\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
-\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
-\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
-\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
-\end{displayquote}
-A higher type of clone means that it's harder to detect and less subtle.
-There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
-
-\subsection{Relevance to clone refactoring}
-Higher type clones are not only harder to detect, but also harder to refactor.
-How to refactor clones is heavily dependent on it's context and type.
-Method-level Type I clones can commonly be refactored by using the ``Extract method'' refactoring \cite{kodhai2013method}.
-
-For this thesis, we have chosen not to further look at type III and IV clones, as it is very hard to formalize their refactoring processes. They are out of the scope for this thesis.
-
-\chapter{Clone detection}
-
-\chapter{Analyzing clone harmfulness}
-
-%TODO: What makes clones harmful?
-
-\chapter{Analyzing clone refactorings}
-
-\section{Catalogue of clones and their refactorings}
-
-\newpage
-\bibliographystyle{plain}
-\bibliography{references.bib}
+%comment out in the final version
+%\listoftodos[Notes]
 

### 2019-04-11 main.tex
Fill in the blanks

@@
 \usepackage{float}
+\usepackage{hyperref}
 
@@
 			\multirow{3}{*}{\includegraphics[height=48pt]{uva.pdf}}
-			&\textsc{\Large Universiteit van Amsterdam}\\
-			&\textsc{Faculteit der Natuurwetenschappen, Wiskunde en Informatica}\\
+			&\textsc{\Large University of Amsterdam}\\
+			&\textsc{Faculty of Physics, Mathematics and Informatics}\\
 			&\textsc{Master Software Engineering}\\
@@
 	\begin{center}
-		{\Huge\bfseries Title \par}
+		{\Huge\bfseries Using Refactoring Techniques to improve Maintainability in Object Oriented Programming Languages \par}
 		% Earlier versions:
@@
 		\vspace{44pt}
-		{\Large\bfseries Author \par}
-		\email{author email}\\
+		{\Large\bfseries Simon Baars \par}
+		\email{simon.mailadres@gmail.com}\\
 		\vspace{11pt}
-		July 16, 2017, \pageref{LastPage} pages
+		30 June 2019, \pageref{LastPage} pages
 	\end{center}
@@
 	\begin{tabular}{ll}
-		\textbf{Research supervisor:} 	& Name academic supervisor, \email{academic supervisor email} \\
-		\textbf{Host/Daily supervisor:} & Name industry/daily supervisor, \email{industry supervisor email}\\
-		\textbf{Host organisation/Research group:} & Name Host organization/Research group, \url{website organization/research group}
+		\textbf{Research supervisor:} Dr. Ana Oprescu, \email{ana.oprescu@uva.nl} \\
+		\textbf{Host/Daily supervisor:} Xander Schrijen, \email{x.schrijen@sig.eu}\\
+		\textbf{Host organisation/Research group:} Software Improvement Group (SIG), \url{http://sig.eu/}
 	\end{tabular}

### 2019-04-18 sections/introduction.tex
Expanded the introduction
I love the quote from martin fowler

@@
 Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, or does not happen at all \cite{mens2003refactoring}.
-Refactoring mostly requires some domain knowledge to do it right, but there are also refactoring opportunities that are rather trivial and repetitive to execute.
+For a large part, refactoring requires domain knowledge to do it right.
+However, there are also refactoring opportunities that are rather trivial and repetitive to execute.
 In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
@@
 For this thesis we will lay the main focus on the Java programming language as refactoring opportunities do feature paradigm and programming language dependent aspects \cite{choi2011extracting}.
-However, most practises used in this thesis will also be applicable with other object oriented languages, like C\#.
+However, most practises used in this thesis will also be applicable with other object-oriented languages, like C\#.
 
@@
 This will be one of our main focus points in this thesis.
+
+Duplication in source code is often seen as one of the most harmful types of technical debt.
+In Martin Fowler's ``Refactoring'' book \cite{fowler2018refactoring}, he exclaims that \textit{``Number one in the stink parade is duplicated code.
+If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
+However, this statement is not accepted by everyone.
+Several papers argue that not each type of duplication is harmful \cite{kapser2006cloning}.
 

### 2019-04-18 sattose/paper.tex
Added the sattose paper

\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{twocolpceurws}

\title{Using Refactoring Techniques to Reduce Duplication in Object Oriented Programming Languages}

\author{
Simon Baars \\ University of Amsterdam\\
                Puiflijk, Netherlands \\ simon.mailadres@gmail.com
\and
Ana Oprescu \\ University of Amsterdam\\
                Amsterdam, Netherlands \\ A.M.Oprescu@uva.nl
}

\institution{}

\begin{document}
\maketitle

\begin{abstract}
The Abstract paragraph should be indented $1/4$ inch (2 pica) on both
the left and right-hand margins. Abstract must be centered, bold, and
in point size 12. Two line spaces precede the Abstract. The Abstract
must be limited to one paragraph.
\end{abstract}

\section{General Formatting Instructions}

The format is in one column. The left margin is .9 inches (5.5 picas). Use 10 point type,
with a vertical spacing of 11 points. Times Roman is the preferred
typeface throughout.

Paper title is 16 point, Caps/lowercase, bold, centered. Subsequent
pages should start at 1 inch (6 picas) from the top of the page.

Authors names are centered, initial caps; co-authors names, if used, are
flush left and flush right.

Paragraphs are indented by 1 pica with no space between paragraphs.

\section{First Level Heading}

First level headings are all flush left, initial caps, bold and in point
size 12. One line space before the first level heading and $1/2$ line
space after the first level heading.

\subsection{Second Level Heading}

Second level headings must be flush left, initial caps, bold and in point
size 10. One line space before the second level heading and $1/2$ line
space after the second level heading.

\subsubsection{Third Level Heading}

Third level headings must be flush left, initial caps and bold.
One line space before the third level heading and $1/2$ line
space after the third level heading.

\paragraph{Fourth Level Heading}

Fourth level headings must be flush left, initial caps and roman type.
One line space before the fourth level heading and $1/2$ line
space after the fourth level heading.

\subsection{Citations In Text}

Citations within the text should indicate the author's last name and
year\cite{Knuth-vol3}. Reference style\cite{Comer-btree}
should follow the style that you are used to using, as long as the
citation style is consistent.

\subsubsection{Footnotes}

Indicate footnotes with a number\footnote{This is a sample footnote} in
the text. Place the footnotes at the bottom of the page they appear on.
Precede the footnote with a vertical rule of 2 inches (12 picas).

\subsubsection{Figures}

All artwork must be centered, neat, clean and legible. Do not use pencil
or hand-drawn artwork. Figure number and caption always appear after the
the figure. Place one line space before the figure, one line space
before the figure caption and one line space after the figure caption.
The figure caption is initial caps and each figure is numbered
consecutively.

Make sure that the figure caption does not get separated from the
figure. Leave extra white space at the bottom of the page to avoid
splitting the figure and figure caption.

Figure \ref{fig1} shows how to include a figure as encapsulated postscript.
The source of the figure is in file {\tt fig1.eps}.

Below is another figure using LaTeX commands.

\begin{figure}[ht]
\begin{center}
\setlength{\unitlength}{1pt}
\footnotesize
\begin{picture}(160,80)
        \put(0,0){\framebox(160,80)[]{}}
        \put(10,35){\framebox(80,40){}}
        \put(100,20){\framebox(40,20){}}
        \put(70,10){\framebox(20,10){}}
        \put(20,5){\framebox(10,5){}}
\end{picture}
\caption{Sample Figure Caption}
\end{center}
\end{figure}

\subsubsection{Tables}

All tables must be centered, neat, clean and legible. Do not use pencil
or hand-drawn tables. Table number and title always appear before the
table.

One line space before the table title, one line space after the table
title and one line space after the table. The table title must be
initial caps and each table numbered consecutively.

\begin{table}[ht]
\begin{center}
\caption{Sample Table}

\bigskip

\begin{tabular}{|l|l|r|}
\hline
A & B & 1\\ \hline
C & D & 2\\
E & F & 3\\ \hline
\end{tabular}
\end{center}
\end{table}

\subsubsection{Handling References}

Use a first level heading for the references. References follow the
acknowledgements.

\subsubsection{Acknowledgements}
We would like to thank the Software Improvement Group (SIG) for their continuous support in this project.

%\bibliographystyle{alpha}
%\bibliography{samplebib}
%inline the .bbl file directly for mailing to authors.

\begin{thebibliography}{Com79}

\bibitem[Com79]{Comer-btree}
D.~Comer.
\newblock The ubiquitous b-tree.
\newblock {\em Computing Surveys}, 11(2):121--137, June 1979.

\bibitem[Knu73]{Knuth-vol3}
D.~E. Knuth.
\newblock {\em The Art of Computer Programming -- Volume 3 / Sorting and
  Searching}.
\newblock Addison-Wesley, 1973.

\end{thebibliography}

\end{document}

### 2019-04-19 sections/research.tex
Something about the corpus

@@
-\chapter{Your research}
+\chapter{Prioritizing code clones for refactoring}
 \label{ch:research_method}
+Where a clone instance is located in the code, and how clones in a clone class are related, has a big impact on how this clone should be refactored.
+Because of this, we have performed measurements on a big corpus of open source projects.
 
-Depending on your subject, you might need multiple research chapters.
-Moreover, depending on how the research questions are linked, you may need to answer them one by one and then connect the answers into a final discussion chapter.
+\section{The corpus}
+For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}\footnote{The corpus can be downloaded from the following URL: \url{http://groups.inf.ed.ac.uk/cup/javaGithub/java_projects.tar.gz}}.
+This corpus has been assembled to contain relatively higher quality projects (by filtering by forks).
+Also, any duplicate projects were removed from this corpus.
+This results in a variaty of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
 
-See Canvas for examples of theses with various approaches to structuring the research content.
+We then filtered the corpus further to make sure we are not including any test classes or generated classes.
+Many Java/Maven projects use a structure where they separate the application and it's tests in the different folders ("/src/main/java" and "/src/test/java" respectively).
+Because of this, we chose to only use projects from the corpus which use this structure (and had at least a "/src/main/java" folder).
+To limit the execution time of the script, we also decided to limit the maximum amount of source files in a single project to 1.000 (projects with more source files were not considered).
+Of the 14.436 projects in the corpus over 3.853 remained, which is plenty for our purposes.
+The script to filter the corpuses in included in our GitHub repository \footnote{The script we use to filter the corpus: \url{TODO}}.

### 2019-04-19 sattose/paper.tex
Something about the corpus
Added an abstract

@@
 
-\title{Using Refactoring Techniques to Reduce Duplication in Object Oriented Programming Languages}
+\title{Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages}
 
@@
 \begin{abstract}
-The Abstract paragraph should be indented $1/4$ inch (2 pica) on both
-the left and right-hand margins. Abstract must be centered, bold, and
-in point size 12. Two line spaces precede the Abstract. The Abstract
-must be limited to one paragraph.
+Duplication in source code can have a major negative impact on the maintainability of source code.
+There are several techniques that can be used in order to merge clones, reduce duplication and potentially also reduce the total volume of a software system.
+In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages.
+Measurements that have been conducted so far have indicated that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
+More measurements will be conducted to get a detailed overview of in what contexts clones occur, and what this means for the refactoring processes of these clones.
+As a desired output, we strive to construct a model that automatically applies refactorings for a large part of the detected duplication problems and implement this model for the Java programming language.
 \end{abstract}

### 2019-04-19 sattose/paper.tex
Introduction

@@
 
-\section{General Formatting Instructions}
+\section{Introduction}
+Refactoring is used to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
+There are many methods that have been introduced to help with the process of refactoring \cite{fowler2018refactoring, wake2004refactoring}.
+However, most of these methods still require manual assessment of where and when to apply them.
+Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, or does not happen at all \cite{mens2003refactoring}.
+For a large part, refactoring requires domain knowledge to do it right.
+However, there are also refactoring opportunities that are rather trivial and repetitive to execute.
+In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
+The main goal is to improve maintainability of the refactored code.
 
-The format is in one column. The left margin is .9 inches (5.5 picas). Use 10 point type,
-with a vertical spacing of 11 points. Times Roman is the preferred
-typeface throughout.
-
-Paper title is 16 point, Caps/lowercase, bold, centered. Subsequent
-pages should start at 1 inch (6 picas) from the top of the page.
-
-Authors names are centered, initial caps; co-authors names, if used, are
-flush left and flush right.
-
-Paragraphs are indented by 1 pica with no space between paragraphs.
+Duplication in source code is often seen as one of the most harmful types of technical debt.
+In Martin Fowler's ``Refactoring'' book \cite{fowler2018refactoring}, he exclaims that \textit{``Number one in the stink parade is duplicated code.
+If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
+However, this statement is not accepted by everyone.
+Several papers argue that not each type of duplication is harmful \cite{kapser2006cloning}.
 
@@
 
-%\bibliographystyle{alpha}
-%\bibliography{samplebib}
-%inline the .bbl file directly for mailing to authors.
-
-\begin{thebibliography}{Com79}
-
-\bibitem[Com79]{Comer-btree}
-D.~Comer.
-\newblock The ubiquitous b-tree.
-\newblock {\em Computing Surveys}, 11(2):121--137, June 1979.
-
-\bibitem[Knu73]{Knuth-vol3}
-D.~E. Knuth.
-\newblock {\em The Art of Computer Programming -- Volume 3 / Sorting and
-  Searching}.
-\newblock Addison-Wesley, 1973.
-
-\end{thebibliography}
+\bibliographystyle{alpha}
+\bibliography{res}
 

### 2019-04-19 sections/introduction.tex
Introduction

@@
 \label{ch:introduction}
+
 Refactoring is used to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
@@
 
-There are several models which describe ways to measure maintainability.
-None of these are sufficient to make a full assessment of the maintainability of a software project, but they strive to give a good indication.
-For this thesis, we will make use of the \textit{SIG maintainability model} \cite{heitlager2007practical}, as it is based on a lot of experience in the field of software quality assessment.
-This maintainability model is independent of programming language.
-For this thesis we will lay the main focus on the Java programming language as refactoring opportunities do feature paradigm and programming language dependent aspects \cite{choi2011extracting}.
-However, most practises used in this thesis will also be applicable with other object-oriented languages, like C\#.
-
-Improving the maintainability metrics does not automatically lead to a better maintainable codebase \cite{fenton1999software}.
-For instance, in general, a bigger codebase (in volume) is harder to maintain.
-However, refactoring a big method into smaller methods can definitely improve the maintainability of the codebase (but still increase the volume metric).
-Because of this, it is important that refactorings focus on the resolution of harmful anti-patterns \cite{kapser2006cloning} rather than just the improvement of the metrics.
-This will be one of our main focus points in this thesis.
-
 Duplication in source code is often seen as one of the most harmful types of technical debt.
@@
 If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
-However, this statement is not accepted by everyone.
-Several papers argue that not each type of duplication is harmful \cite{kapser2006cloning}.
 
-For this research, we will focus on formalizing the refactoring process of dealing with duplication in code.
-To validate this approach, we will validate the refactored results with domain experts.
-Apart from that, we will show the improvement of the metrics over various open source and industrial projects.
+In this research, we will focus on formalizing the refactoring process of dealing with duplication in code.
+We will show the improvement of the metrics over various open source and industrial projects.
 Likewise, we will perform an estimation of the development costs that are saved by using the proposed solution.
+We will lay the main focus on the Java programming language as refactoring opportunities do feature paradigm and programming language dependent aspects \cite{choi2011extracting}.
+However, most practises used in this thesis will also be applicable with other object-oriented languages, like C\#
 

### 2019-04-22 sattose/paper.tex
Clone Detection

@@
 \usepackage{twocolpceurws}
+\usepackage{float}
+\usepackage{hyperref}
 
@@
 
-\section{First Level Heading}
+In this research, we focus on formalizing the refactoring process of dealing with duplication in code.
+We will measure open source projects from the We will show the improvement of the metrics over various open source and industrial projects.
+Likewise, we will perform an estimation of the development costs that are saved by using the proposed solution.
+We will lay the main focus on the Java programming language as refactoring opportunities do feature paradigm and programming language dependent aspects \cite{choi2011extracting}.
+However, most practises used in this thesis will also be applicable with other object-oriented languages, like C\#.
 
-First level headings are all flush left, initial caps, bold and in point
-size 12. One line space before the first level heading and $1/2$ line
-space after the first level heading.
+\section{Clone Detection}
+As duplication in source code is a serious problem in many software systems, there are a lot of researches that look into code clones.
+Many tools have been proposed to detect various types of code clones.
+Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016.
+To be able to refactor detected clones, it is useful to have the ability to rewrite the AST.
+We considered a set of clone detection tools for their ability to support the refactoring process automatically.
+None of the tools we consider seemed completely fit for this purpose, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
+
+\subsection{CloneRefactor}
+A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection.
+For our tool we decided to combine AST and Graph based approaches for clone detection, similar to Scorpio (which is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs).
+We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code.
+We then collect each statement and declaration (ommitting their child statements and declarations) and compare those to find duplicates.
+This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of it's duplicates (verically).
+This is displayed in figure \ref{fig:clonerefactor}.
+
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/CodeGraph}
+  \caption{Graph representation built by CloneRefactor}
+  \label{fig:clonerefactor}
+\end{figure}
 

### 2019-04-22 sections/introduction.tex
Clone Detection

@@
 
-In this research, we will focus on formalizing the refactoring process of dealing with duplication in code.
-We will show the improvement of the metrics over various open source and industrial projects.
+In this research, we focus on formalizing the refactoring process of dealing with duplication in code.
+We will measure open source projects from the We will show the improvement of the metrics over various open source and industrial projects.
 Likewise, we will perform an estimation of the development costs that are saved by using the proposed solution.
 We will lay the main focus on the Java programming language as refactoring opportunities do feature paradigm and programming language dependent aspects \cite{choi2011extracting}.
-However, most practises used in this thesis will also be applicable with other object-oriented languages, like C\#
+However, most practises used in this thesis will also be applicable with other object-oriented languages, like C\#.
 
@@
 \begin{enumerate}
-	\item 1
-	\item 2
-	\item 3
+	\item We deliver several novel measurements regarding code clones on a large corpus of Java projects.
+	\item We deliver a novel clone detection tool that finds refactorable clones in Java.
+	\item We deliver a novel clone refactoring tool that suggests refactorings to be applied, and applies these refactorings.
+	\item We give further recommendations in how refactoring can be automatically applied to improve maintainability in software projects.
 \end{enumerate}

### 2019-04-22 sattose/paper.tex
Added context and corpus stuff

@@
 
-\subsection{Second Level Heading}
+\section{Code Clone Context}
+To be able to refactor code clones, it is very important to consider the context of the clone. We define the following aspects of the clone as its context:
+\begin{enumerate}
+  \item The relation of clone instances among each other (for example: two clone instances in a clone class are part of the same object).
+  \item Where a clone instance occurs in the code (for instance: a method-level clone is a clone instance that is (a part of) a single method).
+  \item The contents of a clone instance (for instance: the clone instance consists of a one method declaration, a foreach statement and two variable declarations).
+\end{enumerate}
+Everything in the context of a clone has a big impact on how it has to be refactored. For this study we performed measurements on the context of clones in a large corpus of open source projects.
 
-Second level headings must be flush left, initial caps, bold and in point
-size 10. One line space before the second level heading and $1/2$ line
-space after the second level heading.
+\subsection{The corpus}
+For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}\footnote{The corpus can be downloaded from the following URL: \url{http://groups.inf.ed.ac.uk/cup/javaGithub/java_projects.tar.gz}}.
+This corpus has been assembled to contain relatively higher quality projects (by filtering by forks).
+Also, any duplicate projects were removed from this corpus.
+This results in a variaty of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
+
+We then filtered the corpus further to make sure we are not including any test classes or generated classes.
+Many Java/Maven projects use a structure where they separate the application and it's tests in the different folders ("/src/main/java" and "/src/test/java" respectively).
+Because of this, we chose to only use projects from the corpus which use this structure (and had at least a "/src/main/java" folder).
+To limit the execution time of the script, we also decided to limit the maximum amount of source files in a single project to 1.000 (projects with more source files were not considered).
+Of the 14.436 projects in the corpus over 3.853 remained, which is plenty for our purposes.
+The script to filter the corpuses in included in our GitHub repository \footnote{The script we use to filter the corpus: \url{https://github.com/SimonBaars/CloneRefactor/blob/MeasurementsVersion1/src/main/java/com/simonbaars/clonerefactor/scripts/PrepareProjectsFolder.java}}.
+
+\subsection{Relations Between Clone Instances}
+When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances.
 

### 2019-04-22 sections/research.tex
Added context and corpus stuff

@@
 Of the 14.436 projects in the corpus over 3.853 remained, which is plenty for our purposes.
-The script to filter the corpuses in included in our GitHub repository \footnote{The script we use to filter the corpus: \url{TODO}}.
+The script to filter the corpuses in included in our GitHub repository \footnote{The script we use to filter the corpus: \url{https://github.com/SimonBaars/CloneRefactor/blob/MeasurementsVersion1/src/main/java/com/simonbaars/clonerefactor/scripts/PrepareProjectsFolder.java}}.

### 2019-04-22 sattose/paper.tex
Something about relations

@@
 We then filtered the corpus further to make sure we are not including any test classes or generated classes.
-Many Java/Maven projects use a structure where they separate the application and it's tests in the different folders ("/src/main/java" and "/src/test/java" respectively).
-Because of this, we chose to only use projects from the corpus which use this structure (and had at least a "/src/main/java" folder).
+Many Java/Maven projects use a structure where they separate the application and it's tests in the different folders (``/src/main/java'' and ``/src/test/java'' respectively).
+Because of this, we chose to only use projects from the corpus which use this structure (and had at least a ``/src/main/java'' folder).
 To limit the execution time of the script, we also decided to limit the maximum amount of source files in a single project to 1.000 (projects with more source files were not considered).
@@
 When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances.
+A paper by Fontana et al \cite{fontana2015duplicated} performs measurements on 50 open source projects on the relation of clones to each other.
+To do this, they first define several categories for the relation between clone instances in object-oriented languages.
+These categories are as follows:
+\begin{enumerate}
+  \item \textbf{Same method}: All instances of the clone class are in the same method.
+  \item \textbf{Same class}: All instances of the clone class are in the same class.
+  \item \textbf{Superclass}: All instances of the clone class are children and parents of each other.
+  \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
+  \item \textbf{Sibling class}: All instances of the clone class have the same parent class.
+  \item \textbf{First cousin class}: All instances of the clone class have the same grandparent class.
+\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same hierarchy, but do not belong to any of the other categories.
+\item \textbf{Same external superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
+\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
+\end{enumerate}
+Please note that no of these categories allow external classes (except for ``same external superclass'').
+So if two clone instances are related through external classes but do not share a common external superclass, it will be flagged as ``unrelated''.
+The main reason for this is that it is (often) not possible to refactor to external classes.
+
+The ranking of the previous list of categories also matters, as it shows the different levels in which clones were assessed.
+For instance, if two clone instances of a clone class belong to the ``same method'' category but the third belongs to the ``same class'', we will always chose the item lowest on the list.
 

### 2019-04-22 sattose/paper.tex
Something about categories and measurements

@@
 When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances.
+
+\subsubsection{Categorizing Clone Instance Relations}
 A paper by Fontana et al \cite{fontana2015duplicated} performs measurements on 50 open source projects on the relation of clones to each other.
@@
 For instance, if two clone instances of a clone class belong to the ``same method'' category but the third belongs to the ``same class'', we will always chose the item lowest on the list.
+
+\subsubsection{Our measurements}
+We have recreated the same table as Fontana et al \cite{fontana2015duplicated}, but with the following differences:
+\begin{itemize}
+  \item We consider clone classes rather than clone pairs
+\item We use different thresholds regarding when a clone should be considered.
+\item We seek by statement/declaration rather than SLOC.
+\item We test a broader range of projects (they a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality)
+\end{itemize}
 

### 2019-04-22 sattose/paper.tex
Working on sattose paper

@@
   \includegraphics[width=1\columnwidth]{img/CodeGraph}
-  \caption{Graph representation built by CloneRefactor}
+  \caption{Abstract figure of the graph representation built by CloneRefactor}
   \label{fig:clonerefactor}
@@
 
-\subsubsection{Third Level Heading}
-
-Third level headings must be flush left, initial caps and bold.
-One line space before the third level heading and $1/2$ line
-space after the third level heading.
-
-\paragraph{Fourth Level Heading}
-
-Fourth level headings must be flush left, initial caps and roman type.
-One line space before the fourth level heading and $1/2$ line
-space after the fourth level heading.
-
-\subsection{Citations In Text}
-
-Citations within the text should indicate the author's last name and
-year\cite{Knuth-vol3}. Reference style\cite{Comer-btree}
-should follow the style that you are used to using, as long as the
-citation style is consistent.
-
-\subsubsection{Footnotes}
-
-Indicate footnotes with a number\footnote{This is a sample footnote} in
-the text. Place the footnotes at the bottom of the page they appear on.
-Precede the footnote with a vertical rule of 2 inches (12 picas).
-
-\subsubsection{Figures}
-
-All artwork must be centered, neat, clean and legible. Do not use pencil
-or hand-drawn artwork. Figure number and caption always appear after the
-the figure. Place one line space before the figure, one line space
-before the figure caption and one line space after the figure caption.
-The figure caption is initial caps and each figure is numbered
-consecutively.
-
-Make sure that the figure caption does not get separated from the
-figure. Leave extra white space at the bottom of the page to avoid
-splitting the figure and figure caption.
-
-Figure \ref{fig1} shows how to include a figure as encapsulated postscript.
-The source of the figure is in file {\tt fig1.eps}.
-
-Below is another figure using LaTeX commands.
-
-\begin{figure}[ht]
-\begin{center}
-\setlength{\unitlength}{1pt}
-\footnotesize
-\begin{picture}(160,80)
-        \put(0,0){\framebox(160,80)[]{}}
-        \put(10,35){\framebox(80,40){}}
-        \put(100,20){\framebox(40,20){}}
-        \put(70,10){\framebox(20,10){}}
-        \put(20,5){\framebox(10,5){}}
-\end{picture}
-\caption{Sample Figure Caption}
-\end{center}
-\end{figure}
+As a result, we got the following table:
 

### 2019-04-23 sattose/paper.tex
Made all todo stuff

@@
 Because of this, we chose to only use projects from the corpus which use this structure (and had at least a ``/src/main/java'' folder).
-To limit the execution time of the script, we also decided to limit the maximum amount of source files in a single project to 1.000 (projects with more source files were not considered).
-Of the 14.436 projects in the corpus over 3.853 remained, which is plenty for our purposes.
-The script to filter the corpuses in included in our GitHub repository \footnote{The script we use to filter the corpus: \url{https://github.com/SimonBaars/CloneRefactor/blob/MeasurementsVersion1/src/main/java/com/simonbaars/clonerefactor/scripts/PrepareProjectsFolder.java}}.
+To limit the execution time of the script, we also decided to limit the maximum amount of source files in a single project to 1.000 (projects with more source files were not considered, which filtered only 5 extra projects out of the corpus).
+Of the 14.436 projects in the corpus over 3.848 remained, which is plenty for our purposes.
+The script to filter the corpus in included in our GitHub repository \footnote{The script we use to filter the corpus: \url{https://github.com/SimonBaars/CloneRefactor/blob/MeasurementsVersion1/src/main/java/com/simonbaars/clonerefactor/scripts/PrepareProjectsFolder.java}}.
 
@@
 As a result, we got the following table:
+
+%TODO
+
+\subsection{Clone instance location}
+After mapping the relations between individual clones, we looked at the location of individual clone instances.
+A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning.
+In this paper the author argues that 98\% are produced at method-level.
+However, this claim is based on a very small dataset and a questionable way of measurement.
+We validated this claim over our corpus.
+For this, we chose the following categories:
+\begin{enumerate}
+  \item \textbf{Method Level:} A clone instance that does not exceed the boundaries of a single method (optionally including the declaration of the method itself).
+  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class.
+  \item \textbf{Interface Level:} A clone that is (a part of) an interface.
+  \item \textbf{Enumeration Level:} A clone that is (a part of) an enumeration.
+\end{enumerate}
+
+%TODO
+
+\subsection{Clone instance contents}
+Finally, we looked at the contents of individual clone instances: what  kind of
 

### 2019-04-23 sattose/paper.tex
Made some stubs for chapters

@@
 
-\title{Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages}
+\title{Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -}
 
@@
 \item We seek by statement/declaration rather than SLOC.
-\item We test a broader range of projects (they a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality)
+\item We test a broader range of projects (they use a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality)
 \end{itemize}
@@
 \subsection{Clone instance contents}
-Finally, we looked at the contents of individual clone instances: what  kind of
+Finally, we looked at the contents of individual clone instances: what kind of declarations and statements do they span. We selected the following categories to be relevant for refactoring:
+\begin{enumerate}
+  \item
+\end{enumerate}
+
+\section{Merging duplicate code through refactoring}
+Now we have mapped the contexts in which clones occur, we can start looking at refactoring opportunities.
+Regarding refactoring, we separate clones in two categories: easy and difficult refactoring opportunities.
+Easy refactoring opportunities are clones that can easily be automatically refactored.
+Examples of these opportunities are fully cloned methods or a set of fully cloned statements.
+According to the relation between the clone instances, we can propose a refactoring automatically.
+
+However, not always can a clone easily be merged.
+Sometimes a clone spans a statement partially (like a for-loop of which only it's declaration and a part of the body is cloned).
+Merging the clones can be harder in such instances.
+Also, cloned code can contain a complex control structure, like labels, return, break, continue, etc.
+In such instances, more conditions apply do be able to conduct a refactoring, if advisable at all.
+
+\section{Conclusion and next steps}
+Next step: build the model to automatically refactor!
 

### 2019-04-23 sattose/paper.tex
Added TODO's
Rewrote the introduction

@@
 \maketitle
+% In this paper I talk about clone instances and clone classes. Should I explain those concepts first?
 
@@
 \section{Introduction}
+Duplication in source code is often seen as one of the most harmful types of technical debt.
+In Martin Fowler's ``Refactoring'' book \cite{fowler2018refactoring}, he exclaims that \textit{``Number one in the stink parade is duplicated code.
+If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
+In this research, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
+The main goal is to improve the maintainability of the refactored code.
+
 Refactoring is used to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
-There are many methods that have been introduced to help with the process of refactoring \cite{fowler2018refactoring, wake2004refactoring}.
+There are many methods that have been introduced to help with the process of refactoring \cite{fowler2018refactoring, wake2004refactoring}, that are integrated into most modern IDE's.
+% May I assume the reader understands the word IDE?
 However, most of these methods still require manual assessment of where and when to apply them.
@@
 However, there are also refactoring opportunities that are rather trivial and repetitive to execute.
-In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
-The main goal is to improve maintainability of the refactored code.
+In this research we will look at to what extend code clones can be automatically refactored.
 
-Duplication in source code is often seen as one of the most harmful types of technical debt.
-In Martin Fowler's ``Refactoring'' book \cite{fowler2018refactoring}, he exclaims that \textit{``Number one in the stink parade is duplicated code.
-If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
-However, this statement is not accepted by everyone.
-Several papers argue that not each type of duplication is harmful \cite{kapser2006cloning}.
+Code clones can be found anywhere in a codebase.
+The location of a clone in the code has an impact on how it has to be refactored.
+Because of this, we will first look at where clones can be found.
+Using this information we can determine in which locations clones are found the most, on basis of which the refactoring will be prioritized.
+Apart from that, we will look at different types of clones.
+A duplicate part in a codebase does not always have to be an exact match with another part to be called a clone.
+We will look at the definitions of different types of clones and what the opportunities are to refactor duplicate parts of code if it's not an exact match.
+All of these measurements are performed on a large corpus of open source projects.
+We lay the main focus on the Java programming language as refactoring opportunities feature paradigm and programming language dependent aspects \cite{choi2011extracting}.
+However, most practises featured in this research will also be applicable with other object-oriented languages, like C\#.
 
-In this research, we focus on formalizing the refactoring process of dealing with duplication in code.
-We will measure open source projects from the We will show the improvement of the metrics over various open source and industrial projects.
-Likewise, we will perform an estimation of the development costs that are saved by using the proposed solution.
-We will lay the main focus on the Java programming language as refactoring opportunities do feature paradigm and programming language dependent aspects \cite{choi2011extracting}.
-However, most practises used in this thesis will also be applicable with other object-oriented languages, like C\#.
+\subsection{Background}
+%TODO: What are clone classes, what are clone instances, etc.
 
@@
 
-%TODO
+%TODO: Add and discuss measurements
 
@@
 \end{enumerate}
+
+%TODO: Finish text and add measurements.
 
@@
 
+%TODO: Show measurements
+
 \section{Conclusion and next steps}
 Next step: build the model to automatically refactor!
+
+%TODO: Expand conclusion
 

### 2019-04-23 sattose/paper.tex
Made a start with the background

@@
 \subsection{Background}
+As code clones are seen as one of the most harmful types of technical debt, they have been studied very extensively.
+A survey by Roy et al \cite{roy2007survey} states definitions for various important concepts in code clone research.
+In this survey he mentions the concept ``clone pair'', which is \textit{a set of two code portions/fragments which are identical or similar to each other}.
+Furthermore, he defined ``clone class'' as \textit{the union of all clone pairs}.
+Apart from this, we use the definition ``clone instance'', which is a single code portion/fragment that is part of either a clone pair or clone class.
+
+There are already a few researches that look into refactoring opportunities for clone pairs \cite{}
 %TODO: What are clone classes, what are clone instances, etc.

### 2019-04-23 sattose/paper.tex
Added relation table

@@
 
+\begin{table}[H]
+\begin{tabular}{|l|l|l|}
+\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\
+FIRSTCOUSIN        & 695             & 2,02                \\
+SUPERCLASS         & 488             & 1,42                \\
+COMMONHIERARCHY    & 442             & 1,29                \\
+UNRELATED          & 13537           & 39,39               \\
+EXTERNALSUPERCLASS & 2402            & 6,99                \\
+SIBLING            & 5978            & 17,39               \\
+SAMEMETHOD         & 2456            & 7,15                \\
+SAMECLASS          & 8341            & 24,27               \\
+ANCESTOR           & 28              & 0,08
+\end{tabular}
+\end{table}
+
 %TODO: Add and discuss measurements

### 2019-04-23 sattose/paper.tex
Added Location table
Add contents table

--- 2019-04-23 sattose/paper.tex
@@
 
+\begin{table}[H]
+\begin{tabular}{|l|l|l|}
+\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
+FIRSTCOUSIN        & 695             & 2,02                \\ \hline
+SUPERCLASS         & 488             & 1,42                \\ \hline
+COMMONHIERARCHY    & 442             & 1,29                \\ \hline
+UNRELATED          & 13537           & 39,39               \\ \hline
+EXTERNALSUPERCLASS & 2402            & 6,99                \\ \hline
+SIBLING            & 5978            & 17,39               \\ \hline
+SAMEMETHOD         & 2456            & 7,15                \\ \hline
+SAMECLASS          & 8341            & 24,27               \\ \hline
+ANCESTOR           & 28              & 0,08               \\ \hline
+\end{tabular}
+\end{table}
+
 %TODO: Add and discuss measurements
@@
 
+\begin{table}[H]
+\begin{tabular}{|l|l|l|}
+\hline
+\textbf{Location} & \textbf{Amount} & \textbf{Percentage} \\ \hline
+METHODLEVEL       & 19817           & 57,66               \\ \hline
+CLASSLEVEL        & 14366           & 41,80               \\ \hline
+INTERFACELEVEL    & 110             & 0,32                \\ \hline
+ENUMLEVEL         & 74              & 0,22                \\ \hline
+\end{tabular}
+\end{table}
 %TODO: Add and discuss measurements
@@
 
+\begin{table}[H]
+\begin{tabular}{|l|l|l|}
+\hline
+\textbf{Contents}       & \textbf{Amount} & \textbf{Percentage} \\ \hline
+HASINTERFACEDECLARATION & 10              & 0,03                \\ \hline
+SEVERALMETHODS          & 9077            & 26,41               \\ \hline
+FULLCLASS               & 198             & 0,58                \\ \hline
+FULLENUM                & 4               & 0,01                \\ \hline
+FULLMETHOD              & 554             & 1,61                \\ \hline
+INCLUDESFIELDS          & 1150            & 3,35                \\ \hline
+HASCLASSDECLARATION     & 445             & 1,29                \\ \hline
+HASENUMDECLARATION      & 47              & 0,14                \\ \hline
+FULLINTERFACE           & 6               & 0,02                \\ \hline
+HASENUMFIELDS           & 52              & 0,15                \\ \hline
+PARTIALMETHOD           & 19263           & 56,05               \\ \hline
+ONLYFIELDS              & 565             & 1,64                \\ \hline
+OTHER                   & 2996            & 8,72                \\ \hline
+\end{tabular}
+\end{table}
 %TODO: Show measurements

### 2019-04-23 sattose/paper.tex
Comparison added

@@
 
-As a result, we got the following table:
+The table below shows our results.
 
@@
 \end{table}
+
+Comparing it to the results of Fontana et al \cite{fontana2015duplicated}, we find way more unrelated clones.
+This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class unrelated even if just one of the clone instances is outside a hierarchy.
+It could also be that the corpus which we use, as it has generally smaller projects, use more classes from outside the project (which I do not parse, and may thus be marked UNRELATED if they are not a direct external superclass).
+Just like their study, ``same class'' and ``same external superclass'' are both very high.
+Sibling class is also very high, similar to them, but relatively it seems lower than the results they got.
+``Same method'' is much higher (relatively) in our results.
+I think this is because the corpus I used contained a few projects with a very high in-method duplication that had a big influence on the results.
 

### 2019-04-24 sattose/paper.tex
Discussing stuff

--- 2019-04-23 sattose/paper.tex
@@
 
-As a result, we got the following table:
+The table below shows our results.
 
 \begin{table}[H]
-\begin{tabular}{|l|l|l|}
+\begin{tabular}{|l|l|l|} \hline
 \textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
-FIRSTCOUSIN        & 695             & 2,02                \\ \hline
-SUPERCLASS         & 488             & 1,42                \\ \hline
-COMMONHIERARCHY    & 442             & 1,29                \\ \hline
-UNRELATED          & 13537           & 39,39               \\ \hline
-EXTERNALSUPERCLASS & 2402            & 6,99                \\ \hline
-SIBLING            & 5978            & 17,39               \\ \hline
-SAMEMETHOD         & 2456            & 7,15                \\ \hline
-SAMECLASS          & 8341            & 24,27               \\ \hline
-ANCESTOR           & 28              & 0,08               \\ \hline
+Unrelated          & 13537           & 39,39               \\ \hline
+Same Class          & 8341            & 24,27               \\ \hline
+Sibling            & 5978            & 17,39               \\ \hline
+Same Method         & 2456            & 7,15                \\ \hline
+External Superclass & 2402            & 6,99                \\ \hline
+First Cousin        & 695             & 2,02                \\ \hline
+Superclass         & 488             & 1,42                \\ \hline
+Common Hierarchy    & 442             & 1,29                \\ \hline
+Ancestor           & 28              & 0,08               \\ \hline
 \end{tabular}
@@
 
-%TODO: Add and discuss measurements
+Comparing it to the results of Fontana et al \cite{fontana2015duplicated}, we find way more unrelated clones.
+This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
+It could also be that the corpus which we use, as it has generally smaller projects, use more classes from outside the project (which are marked UNRELATED if they do not have a common external superclass).
+On the second place, we have the ``Same Class'' clones.
+On the third place come the ``Sibling'' clones.
 
@@
 
+A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning.
+In this paper the author argues that 98\% are produced at method-level.
+However, their source for this information, uses a very questionable techique of measuring (human copy-paste behaviour with a small sample-size).
+We set out to test this for ourselves on our corpus, and got the following results:
+
 \begin{table}[H]
@@
 \textbf{Location} & \textbf{Amount} & \textbf{Percentage} \\ \hline
-METHODLEVEL       & 19817           & 57,66               \\ \hline
-CLASSLEVEL        & 14366           & 41,80               \\ \hline
-INTERFACELEVEL    & 110             & 0,32                \\ \hline
-ENUMLEVEL         & 74              & 0,22                \\ \hline
+Method Level       & 19817           & 57,66               \\ \hline
+Class Level        & 14366           & 41,80               \\ \hline
+Interface Level    & 110             & 0,32                \\ \hline
+Enum Level         & 74              & 0,22                \\ \hline
 \end{tabular}

### 2019-04-24 sattose/paper.tex
Better formatting and such

@@
 
+Running our clone detection script, CloneRefactor, over this corpus gives the following results:
+
 \subsection{Relations Between Clone Instances}
@@
 \textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
-Unrelated          & 13537           & 39,39               \\ \hline
-Same Class          & 8341            & 24,27               \\ \hline
-Sibling            & 5978            & 17,39               \\ \hline
-Same Method         & 2456            & 7,15                \\ \hline
-External Superclass & 2402            & 6,99                \\ \hline
+Unrelated          & 13.537           & 39,39               \\ \hline
+Same Class          & 8.341            & 24,27               \\ \hline
+Sibling            & 5.978            & 17,39               \\ \hline
+Same Method         & 2.456            & 7,15                \\ \hline
+External Superclass & 2.402            & 6,99                \\ \hline
 First Cousin        & 695             & 2,02                \\ \hline
@@
 \textbf{Location} & \textbf{Amount} & \textbf{Percentage} \\ \hline
-Method Level       & 19817           & 57,66               \\ \hline
-Class Level        & 14366           & 41,80               \\ \hline
+Method Level       & 19.817           & 57,66               \\ \hline
+Class Level        & 14.366           & 41,80               \\ \hline
 Interface Level    & 110             & 0,32                \\ \hline
@@
 \end{table}
-%TODO: Add and discuss measurements
+
+From these results we can see, somewhat surprisingly, that in our
 
@@
 
+\begin{table}[H]
+\begin{tabular}{|l|l|l|}
+\hline
+\textbf{Contents}       & \textbf{Amount} & \textbf{Percentage} \\ \hline
+HASINTERFACEDECLARATION & 10              & 0,03                \\ \hline
+SEVERALMETHODS          & 9.077            & 26,41               \\ \hline
+FULLCLASS               & 198             & 0,58                \\ \hline
+FULLENUM                & 4               & 0,01                \\ \hline
+FULLMETHOD              & 554             & 1,61                \\ \hline
+INCLUDESFIELDS          & 1.150            & 3,35                \\ \hline
+HASCLASSDECLARATION     & 445             & 1,29                \\ \hline
+HASENUMDECLARATION      & 47              & 0,14                \\ \hline
+FULLINTERFACE           & 6               & 0,02                \\ \hline
+HASENUMFIELDS           & 52              & 0,15                \\ \hline
+PARTIALMETHOD           & 19.263           & 56,05               \\ \hline
+ONLYFIELDS              & 565             & 1,64                \\ \hline
+OTHER                   & 2.996            & 8,72                \\ \hline
+\end{tabular}
+\end{table}
 %TODO: Finish text and add measurements.
@@
 
-\begin{table}[H]
-\begin{tabular}{|l|l|l|}
-\hline
-\textbf{Contents}       & \textbf{Amount} & \textbf{Percentage} \\ \hline
-HASINTERFACEDECLARATION & 10              & 0,03                \\ \hline
-SEVERALMETHODS          & 9077            & 26,41               \\ \hline
-FULLCLASS               & 198             & 0,58                \\ \hline
-FULLENUM                & 4               & 0,01                \\ \hline
-FULLMETHOD              & 554             & 1,61                \\ \hline
-INCLUDESFIELDS          & 1150            & 3,35                \\ \hline
-HASCLASSDECLARATION     & 445             & 1,29                \\ \hline
-HASENUMDECLARATION      & 47              & 0,14                \\ \hline
-FULLINTERFACE           & 6               & 0,02                \\ \hline
-HASENUMFIELDS           & 52              & 0,15                \\ \hline
-PARTIALMETHOD           & 19263           & 56,05               \\ \hline
-ONLYFIELDS              & 565             & 1,64                \\ \hline
-OTHER                   & 2996            & 8,72                \\ \hline
-\end{tabular}
-\end{table}
 %TODO: Show measurements

### 2019-04-24 sattose/paper.tex
Added a "general table"

@@
 Running our clone detection script, CloneRefactor, over this corpus gives the following results:
+
+\begin{table}[H]
+\begin{tabular}{|l|l|}
+\hline
+Amount of projects                                                                                      & 3.848      \\ \hline
+Amount of lines                                                                                         & 8.284.140  \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\ whitespace, comments, etc.)\end{tabular}        & 8.163.429  \\ \hline
+Amount of statements/declarations                                                                       & 6.863.725  \\ \hline
+Amount of tokens                                                                                        & 66.964.270 \\ \hline
+Amount of lines cloned                                                                                  & 1.341.094  \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of lines cloned (excluding\\ whitespace, comments, etc.)\end{tabular} & 815.799    \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of statements/declarations\\ cloned\end{tabular}                      & 747.993    \\ \hline
+Amount of tokens cloned                                                                                 & 9.800.819  \\ \hline
+Amount of clone classes                                                                                 & 34.367     \\ \hline
+\end{tabular}
+\end{table}
 

### 2019-04-24 sattose/paper.tex
Table makeup

@@
 \begin{table}[H]
+  \begin{center}
+  \caption{CloneRefactor results for Java projects corpus \cite{githubCorpus2013}.}
+  \bigskip
 \begin{tabular}{|l|l|}
@@
 \end{tabular}
+\end{center}
 \end{table}
@@
 \begin{itemize}
-  \item We consider clone classes rather than clone pairs
+  \item We consider clone classes rather than clone pairs.
 \item We use different thresholds regarding when a clone should be considered.
 \item We seek by statement/declaration rather than SLOC.
-\item We test a broader range of projects (they use a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality)
+\item We test a broader range of projects (they use a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality).
 \end{itemize}
@@
 \begin{table}[H]
+  \begin{center}
+  \caption{Clone relations}
+  \bigskip
 \begin{tabular}{|l|l|l|} \hline
@@
 \begin{table}[H]
+  \begin{center}
+  \caption{Clone instance locations}
+  \bigskip
 \begin{tabular}{|l|l|l|}
@@
 \begin{enumerate}
-  \item
 \end{enumerate}
@@
 \begin{table}[H]
+  \begin{center}
+  \caption{Clone instance contents}
+  \bigskip
 \begin{tabular}{|l|l|l|}
@@
 
-\subsubsection{Tables}
-
-All tables must be centered, neat, clean and legible. Do not use pencil
-or hand-drawn tables. Table number and title always appear before the
-table.
-
-One line space before the table title, one line space after the table
-title and one line space after the table. The table title must be
-initial caps and each table numbered consecutively.
-
-\begin{table}[ht]
-\begin{center}
-\caption{Sample Table}
-
-\bigskip
-
-\begin{tabular}{|l|l|r|}
-\hline
-A & B & 1\\ \hline
-C & D & 2\\
-E & F & 3\\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-\subsubsection{Handling References}
-
-Use a first level heading for the references. References follow the
-acknowledgements.
-
 \subsubsection{Acknowledgements}

### 2019-04-24 sattose/paper.tex
Enumeration for the clone instance contents

@@
 \begin{enumerate}
+  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, interface or enumeration, including its declaration.
+  \item \textbf{Partial Method:} A clone that spans a method partially, optionally including its declaration.
+  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
+  \item \textbf{Only Fields:} A clone that spans only global variables.
+  \item \textbf{Includes Fields:} A clone that spans a combination of fields and other things, like methods.
+  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
+  \item \textbf{Other:} Anything that does not match with above stated categories.
 \end{enumerate}

### 2019-04-24 sattose/paper.tex
Discussing clone instance locations

@@
 \begin{enumerate}
-  \item \textbf{Method Level:} A clone instance that does not exceed the boundaries of a single method (optionally including the declaration of the method itself).
-  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class.
+  \item \textbf{Method/Constructor Level:} A clone instance that does not exceed the boundaries of a single method or constructor (optionally including the declaration of the method or constructor itself).
+  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class (like field declarations, other methods, etc.).
   \item \textbf{Interface Level:} A clone that is (a part of) an interface.
@@
 \textbf{Location}  & \textbf{Amount}  & \textbf{Percentage} \\ \hline
-Method Level       & 19.817           & 57,66               \\ \hline
-Class Level        & 14.366           & 41,80               \\ \hline
+Method Level       & 19.818           & 57,68               \\ \hline
+Class Level        & 13.259           & 38,59               \\ \hline
+Constructor Level  & 1.099            & 3,20                \\ \hline
 Interface Level    & 110              & 0,32                \\ \hline
@@
 
-From these results we can see, somewhat surprisingly, that in our
+From these results we can see, somewhat surprisingly, that the claim of 98\% of clones being produced at method-level is nowhere near correct.
+In fact, around 58\% of the clones are produced at method-level.
+About 39\% of clones either span several methods/constructors or contain something like a field declaration.
+Another 3\% of the clones is found in contructors.
+The amount of clones found in interfaces and enumerations is very low.
 

### 2019-04-24 sattose/paper.tex
Updated this table

@@
 \begin{enumerate}
-  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, interface or enumeration, including its declaration.
-  \item \textbf{Partial Method:} A clone that spans a method partially, optionally including its declaration.
+  \item \textbf{Full Method/Class/Interface/Enumeration/Constructor:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
+  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially, optionally including its declaration.
   \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
   \item \textbf{Only Fields:} A clone that spans only global variables.
-  \item \textbf{Includes Fields:} A clone that spans a combination of fields and other things, like methods.
+  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields and other things, like methods.
   \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
@@
   \textbf{Contents}                                                        & \textbf{Amount} & \textbf{Percentage} \\ \hline
-HASINTERFACEDECLARATION & 10              & 0,03                \\ \hline
-SEVERALMETHODS          & 9.077            & 26,41               \\ \hline
-FULLCLASS               & 198             & 0,58                \\ \hline
-FULLENUM                & 4               & 0,01                \\ \hline
-FULLMETHOD              & 554             & 1,61                \\ \hline
-INCLUDESFIELDS          & 1.150            & 3,35                \\ \hline
-HASCLASSDECLARATION     & 445             & 1,29                \\ \hline
-HASENUMDECLARATION      & 47              & 0,14                \\ \hline
-FULLINTERFACE           & 6               & 0,02                \\ \hline
-HASENUMFIELDS           & 52              & 0,15                \\ \hline
-PARTIALMETHOD           & 19.263           & 56,05               \\ \hline
-ONLYFIELDS              & 565             & 1,64                \\ \hline
-OTHER                   & 2.996            & 8,72                \\ \hline
+  Partial Method                                                           & 19.264          & 56,07               \\ \hline
+  Several Methods                                                          & 9.076           & 26,41               \\ \hline
+  Includes Constructor                                                     & 1.528           & 4,45                \\ \hline
+  Includes Field                                                           & 1.149           & 3,34                \\ \hline
+  Partial Constructor                                                      & 1.098           & 3,20                \\ \hline
+  Only Fields                                                              & 565             & 1,64                \\ \hline
+  Full Method                                                              & 554             & 1,61                \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Class\\ Declaration\end{tabular}     & 445             & 1,30                \\ \hline
+  Other                                                                    & 369             & 1,07                \\ \hline
+  Full Class                                                               & 192             & 0,56                \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Constant\end{tabular}         & 52              & 0,15                \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Declaration\end{tabular}      & 47              & 0,14                \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Interface\\ Declaration\end{tabular} & 10              & 0,03                \\ \hline
+  Full Interface                                                           & 6               & 0,02                \\ \hline
+  Full Enumeration                                                         & 4               & 0,01                \\ \hline
+  Full Constructor                                                         & 1               & 0,00                \\ \hline
 \end{tabular}

### 2019-04-24 sattose/paper.tex
Referring to the tables

@@
 
-Running our clone detection script, CloneRefactor, over this corpus gives the following results:
+Running our clone detection script, CloneRefactor, over this corpus gives the results displayed in table \ref{table:general}.
 
@@
   \begin{center}
-  \caption{CloneRefactor results for Java projects corpus \cite{githubCorpus2013}.}
+  \caption{CloneRefactor results for Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
   \bigskip
@@
 \subsubsection{Our measurements}
-We have recreated the same table as Fontana et al \cite{fontana2015duplicated}, but with the following differences:
+We have recreated table 3 of Fontana et al \cite{fontana2015duplicated}, but with the following differences in our setup:
 \begin{itemize}
@@
 
-The table below shows our results.
+Table \ref{table:relations} contains our results regarding the relations between clone instances.
 
@@
   \begin{center}
-  \caption{Clone relations}
+  \caption{Clone relations} \label{table:relations}
   \bigskip
@@
 However, their source for this information, uses a very questionable techique of measuring (human copy-paste behaviour with a small sample-size).
-We set out to test this for ourselves on our corpus, and got the following results:
+We set out to test this for ourselves on the corpus of Java projects which we used for all our measurements.
+The results for the clone instance locations are shown in table \ref{table:locations}.
 
@@
   \begin{center}
-  \caption{Clone instance locations}
+  \caption{Clone instance locations} \label{table:locations}
   \bigskip
@@
 
+The results for these categories are displayed are displayed in table \ref{table:contents}.
+
 \begin{table}[H]
   \begin{center}
-  \caption{Clone instance contents}
+  \caption{Clone instance contents} \label{table:contents}
   \bigskip

### 2019-04-24 sattose/paper.tex
Fixed the values slightly

@@
 \textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
-Unrelated          & 13.537           & 39,39               \\ \hline
-Same Class          & 8.341            & 24,27               \\ \hline
-Sibling            & 5.978            & 17,39               \\ \hline
+Unrelated          & 13.529           & 39,37               \\ \hline
+Same Class          & 8.341            & 24,28               \\ \hline
+Sibling            & 5.978            & 17,40               \\ \hline
 Same Method         & 2.456            & 7,15                \\ \hline
@@
 First Cousin        & 695             & 2,02                \\ \hline
-Superclass         & 488             & 1,42                \\ \hline
+Superclass         & 489             & 1,42                \\ \hline
 Common Hierarchy    & 442             & 1,29                \\ \hline

### 2019-04-24 sattose/paper.tex
Talking about contents

@@
 Duplication in source code is often seen as one of the most harmful types of technical debt.
-In Martin Fowler's ``Refactoring'' book \cite{fowler2018refactoring}, he exclaims that \textit{``Number one in the stink parade is duplicated code.
+In Martin Fowler's ``Refactoring'' book \cite{fowler1999refactoring}, he exclaims that \textit{``Number one in the stink parade is duplicated code.
 If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
@@
 Refactoring is used to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
-There are many methods that have been introduced to help with the process of refactoring \cite{fowler2018refactoring, wake2004refactoring}, that are integrated into most modern IDE's.
-% May I assume the reader understands the word IDE?
+There are many methods that have been introduced to help with the process of refactoring \cite{fowler1999refactoring, wake2004refactoring}, that are integrated into most modern IDE's.
 However, most of these methods still require manual assessment of where and when to apply them.
@@
 \begin{enumerate}
-  \item \textbf{Full Method/Class/Interface/Enumeration/Constructor:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
+  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
   \item \textbf{Partial Method/Constructor:} A clone that spans a method partially, optionally including its declaration.
@@
   Full Enumeration                                                         & 4               & 0,01                \\ \hline
-  Full Constructor                                                         & 1               & 0,00                \\ \hline
 \end{tabular}
@@
 \end{table}
-%TODO: Finish text and add measurements.
+
+Unsurprisingly, most clones span a part of a method.
+Just 1.6\% of the methods are cloned fully.
+More than a quarter of the clones spans over several methods, which is surprising.
+Simply extracting methods won't work in a case where a clone spans over several methods.
+About 4.5\% of clones include a constructor.
+About 3.3\% of clones include a global variable defined in a class.
+
+\section{Redefining type-2 and type-3 clones}
 

### 2019-04-24 sattose/paper.tex
Trying to write more background

@@
 
-There are already a few researches that look into refactoring opportunities for clone pairs \cite{}
-%TODO: What are clone classes, what are clone instances, etc.
+A tool called DCRA (Duplicated Code Refactoring Advisor) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated}.
+This tool chooses to only focus on refactoring clone pairs because they argue that \textit{clone pairs are much easier to manage when considered singularly.} As intermidiate steps the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation between code fragments in a clone pair in terms of inheritance.
 
@@
 For our tool we decided to combine AST and Graph based approaches for clone detection, similar to Scorpio (which is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs).
-We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code.
-We then collect each statement and declaration (ommitting their child statements and declarations) and compare those to find duplicates.
+We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is useable with all modern Java versions (Java 1-12).
+We collect each statement and declaration and compare those to find duplicates.
 This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of it's duplicates (verically).

### 2019-04-24 sattose/paper.tex
Background blah blah

@@
 A tool called DCRA (Duplicated Code Refactoring Advisor) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated}.
-This tool chooses to only focus on refactoring clone pairs because they argue that \textit{clone pairs are much easier to manage when considered singularly.} As intermidiate steps the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation between code fragments in a clone pair in terms of inheritance.
+This tool chooses to only focus on refactoring clone pairs because they argue that \textit{clone pairs are much easier to manage when considered singularly.} As intermidiate steps the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.
+
+Another tool called Aries \cite{higo2004aries, higo2008metric} focuses on the detection of refactoring oriented clones.
+In this paper the authors describe a few variables by which a clone can be assessed for refactoring suitability.
+This tool looks however only at the possibility to merge clones, rather than whether clones should be merged.
+Also, this tool only suggests refactorings, and does not apply them.
+
+There are many other publications that look into code clone refactoring \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}.
+However, none of the publications describing a refactoring tool have published their source code or application for refactoring support.
+Also, these publications/tools are limited to suggesting refactoring opportunities for clones found, rather than actually applying refactorings where suitable.
+Furthermore, all of these tools only support a subset of all harmful clones that are found.
+Furthermore, all published approaches have limitations, for instance false positives when detecting clones \cite{chen2018clone} or being limited to clone pairs \cite{higo2008metric}.
+
+For this research, we strive to improve upon the current state-of-the-art in clone refactoring by building a clone refactoring tool that applies refactorings to a large percentage of clones found.
+The design decisions for this tool will be made on basis of data gathered from a large corpus of software systems.
+The tool will be developed on GitHub and stored in the Software Heritage \cite{di2017software} archives to ensure long term preservation.
+This way we strive to make the problem of duplication in source code easier to deal with.
 

### 2019-04-25 sattose/paper.tex
Talking about thresholds

@@
 \end{figure}
+
+\subsection{Thresholds}
+CloneRefactor works on basis of three thresholds for finding clones:
+\begin{enumerate}
+  \item \textbf{Number of statements/declarations:} The amount of statements/declarations that should be equal/similar for it to be considered a clone.
+  \item \textbf{Number of tokens:} The amount of tokens (excluding whitespace, end-of-line terminators and comments) that should be equal/similar for it to be considered a clone.
+  \item \textbf{Number of lines:} The minimum amount of lines (excluding lines that do not contain any tokens, for tokens same exclusions apply) that should be equal/similar for it to be considered a clone.
+\end{enumerate}
+Of course, if we put any of these thresholds to zero it won't be taken into account anymore, so not all thresholds have to be used at all times.
+We consider ``number of lines'' to be the least important, as it highly depends on the programmer of the codebase (and we do not want this kind of dependence!).
+On basis of manual assessment, we have determined that setting the ``number of statements/declarations'' to 6 ensures that most non-harmful clones are filtered out.
+On the downside, this also filters out some harmful antipatterns, for instance if a cloned line has many tokens we might want to consider a clone if it spans less than 6 statements (as cloned line with many tokens is more harmful than one with few).
+
+For the measurements in the next chapter we have chosen to apply the following thresholds:
+\begin{itemize}
+  \item \textbf{Number of statements/declarations:} 6
+  \item \textbf{Number of tokens:} 10
+  \item \textbf{Number of lines:} 6
+\end{itemize}
 
@@
 
+\section{Threats to validity}
+We noticed that, when measuring over a corpus of this size, the thresholds that we use for the clone detection have a big impact on the results.
+There does not seem to be one golden set of thresholds, some thresholds work in some situations but fail in others.
+We have chosen thresholds that, according to our manual assessment, seemed optimal.
+However, by using these, we definitely miss some harmful clones.
+
 \section{Conclusion and next steps}

### 2019-04-25 sattose/paper.tex
Talking about clone types

@@
 \section{Redefining type-2 and type-3 clones}
+In a 2007 survey by Roy et al \cite{roy2007survey} he defined four types of clones:
+
+\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
+\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
+\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
+\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
 

### 2019-04-25 sattose/paper.tex
Writing about type 2 clones

@@
 
+In this chapter, we will discuss type-2 and type-3 clones (because type-1 clones are straightforward and type-4 clones are out of the scope for this study).
+
+\subsection{Type 2 clones}
+Type 2 clones, by definition, allow any change in identifiers, literals, types, layout and comments.
+For refactoring purposes, this doesn't always make a lot of sense.
+If we allow any change in identifiers, literals and types, we cannot distinguish between different variables, different types and different method calls anymore.
+This could render two methods that have an entirely different functionality as clones.
+Merging such clones, if possible at all, might only proof to be harmful.
+
+Because of that, for this research we have looked into a redefinition of type 2 clones to be able to detect such clones that can and should be merged.
+Our definition ensures functional similarity by considering types, having a distinction between different variables and defining thresholds for variability in literals.
+
+%TODO: Show the stuff
+
+\subsection{Type 3 clones}
+
+%TODO: Write this chapter
+
 \section{Merging duplicate code through refactoring}

### 2019-04-25 sattose/paper.tex
Made it more verbose
Because this makes it clearer what exactly I mean with stuff

@@
 Because of that, for this research we have looked into a redefinition of type 2 clones to be able to detect such clones that can and should be merged.
-Our definition ensures functional similarity by considering types, having a distinction between different variables and defining thresholds for variability in literals.
+Our definition ensures functional similarity by applying the following changes to type 2 clones:
+
+\begin{itemize}
+  \item \textbf{Considering types:} The definition of type 2 clones defines that types should not be considered.
+We disagree, because types can make a significant change to the meaning of a code segment and thus whether this segment should be considered a clone.
+For instance, we should not say that an Apple type object is the same as an object of Orange type (don't compare apples with oranges).
+  \item \textbf{Having a distinction between different variables:} By the definition of type 2 clones any identifiers would not be taken into account.
+We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables.
+For instance, if we call a method like this: \textit{``myMethod(var1, var2)''}, or call this method like this: \textit{``myMethod(var1, var1)''}.
+Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
+  \item \textbf{Defining a threshold for variability in literals:} By the definition of type 2 clones any literals would not be taken into account.
+We agree, as when merging the clone (for instance by extracting a method), we can simply turn the literal into a method parameter.
+However, we would argue that thresholds matter here.
+How many literals may differ for the segment still to be considered a clone with another segment?
+We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
+\end{itemize}
 

### 2019-04-25 sattose/paper.tex
Explained clearer why we do this

@@
 
-\section{Redefining type-2 and type-3 clones}
+\section{Redefining type 2 and type 3 clones}
 In a 2007 survey by Roy et al \cite{roy2007survey} he defined four types of clones:
 
-\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
-\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
-\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
-\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
+\textbf{Type 1:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
+\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
+\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
+\textbf{Type 4:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
 
-In this chapter, we will discuss type-2 and type-3 clones (because type-1 clones are straightforward and type-4 clones are out of the scope for this study).
+A higher type of clone means that it's harder to detect.
+It also makes the clone harder to refactor, as more transformations would be required.
+Higher clone types also become more disputable whether they actually indicate a harmful antipattern (not every clone is harmful).
+Type 1 clones are most often, if not always with the right thresholds, harmful.
+Type 2 and type 3 clones are more disputable whether they are harmful and whether they can be merged in a way that improves the design of the code.
+In this chapter we will redefine type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design.
+Type-4 clones are, because of the serious challenges involved in their detection and refactoring, out of the scope for this study.
 

### 2019-04-25 sattose/paper.tex
Type 3 clones

@@
 
-%TODO: Show the stuff
+\subsection{Type 3 clones}
+Type 3 clones are even more permissive than type 2 clones, allowing added and removed statements.
+Thresholds matter a lot here to make sure that not the whole project is detected to be cloned.
+The main question for this study regarding type 3 clones is: ``how can we merge type 3 clones while improving the design?''.
 
-\subsection{Type 3 clones}
+Clone instances in type 3 clones are almost always different in functionality.
+As we have to ensure equal functionality after merging the clone, we have to wrap the difference in statements between the clone instances in conditional blocks (either if-statements or switch-statements).
+We can then pass a variable as to which path should be taken through the code (either a boolean or an enumeration).
+Such a refactoring would make added statements that are contaguous less harmful for the design then added statements than added statements that are separated by statements that both clone instances have in common.
 
-%TODO: Write this chapter
+We also want to argue that statements that are not common between two clone instances, should not count towards the size of the clone (and thus towards the threshold which determines whether the clone will be taken into account).
+Also, clones should not start and not end with an added statement (as that would be nonsense: such a thing could be done for any clone).
 

### 2019-04-25 sattose/paper.tex
Conclusion and such

@@
 When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances.
+This relation has a big impact on how a clone should be merged, in order to improve the software design in the process.
 
 \subsubsection{Categorizing Clone Instance Relations}
-A paper by Fontana et al \cite{fontana2015duplicated} performs measurements on 50 open source projects on the relation of clones to each other.
+A paper by Fontana et al \cite{fontana2015duplicated} performs measurements on 50 open source projects on the relation of clone instances to each other.
 To do this, they first define several categories for the relation between clone instances in object-oriented languages.
@@
 We can then pass a variable as to which path should be taken through the code (either a boolean or an enumeration).
-Such a refactoring would make added statements that are contaguous less harmful for the design then added statements than added statements that are separated by statements that both clone instances have in common.
+Such a refactoring would make added statements that are contiguous less harmful for the design then added statements than added statements that are separated by statements that both clone instances have in common.
 
@@
 
-%TODO: Show measurements
+%TODO: Show and discuss measurements
 
@@
 \section{Conclusion and next steps}
-Next step: build the model to automatically refactor!
+We conclude that most clones are found in methods, but no easy refactoring is available for them.
+Most clones have complex nesting, and need further consideration to be able to merge them.
+The study that we have conducted so far analyzes different kinds of clones for harmfulness and prioritizes their refactoring.
+On basis of this we will extend our tool, CloneRefactor, to be able to apply refactorings to the found clones.
+We will formalize refactorings for clones that make use of their relation.
+We found that almost 40\% of the clones are unrelated, so we will start formalizing refactorings by finding a refactoring opportunity for such clones.
 

### 2019-04-26 sattose/paper.tex
Reduced duplication :)

@@
 In this paper the author argues that 98\% are produced at method-level.
-However, this claim is based on a very small dataset and a questionable way of measurement.
-We validated this claim over our corpus.
+However, this claim is based on a small dataset and based on human copy-paste behaviour rather than static code analysis.
+We validated this claim over the corpus we use.
 For this, we chose the following categories:
@@
 
-A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning.
-In this paper the author argues that 98\% are produced at method-level.
-However, their source for this information, uses a very questionable techique of measuring (human copy-paste behaviour with a small sample-size).
-We set out to test this for ourselves on the corpus of Java projects which we used for all our measurements.
 The results for the clone instance locations are shown in table \ref{table:locations}.

### 2019-04-29 sattose/paper.tex
Expanded the abstract

@@
 Duplication in source code can have a major negative impact on the maintainability of source code.
-There are several techniques that can be used in order to merge clones, reduce duplication and potentially also reduce the total volume of a software system.
+There are several techniques that can be used in order to merge clones, reduce duplication, improve the design of the code and potentially also reduce the total volume of a software system.
 In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages.
 Measurements that have been conducted so far have indicated that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
+Only a fifth of the duplication can be refactored through simple method extraction, the other clones require other techniques to be applied.
 More measurements will be conducted to get a detailed overview of in what contexts clones occur, and what this means for the refactoring processes of these clones.
-As a desired output, we strive to construct a model that automatically applies refactorings for a large part of the detected duplication problems and implement this model for the Java programming language.
+As a desired output, we strive to construct a model that automatically applies refactorings for a large part of the detected duplication problems.
+This model will be implemented for the Java programming language.
 \end{abstract}

### 2019-04-29 sattose/paper.tex
Small changes

@@
 However, none of the publications describing a refactoring tool have published their source code or application for refactoring support.
+Furthermore, all of these tools only support a subset of all harmful clones that are found.
 Also, these publications/tools are limited to suggesting refactoring opportunities for clones found, rather than actually applying refactorings where suitable.
-Furthermore, all of these tools only support a subset of all harmful clones that are found.
-Furthermore, all published approaches have limitations, for instance false positives when detecting clones \cite{chen2018clone} or being limited to clone pairs \cite{higo2008metric}.
+Finally, all published approaches have limitations, for instance false positives when detecting clones \cite{chen2018clone} or being limited to clone pairs \cite{higo2008metric}.
 
@@
 
-From these results we can see, somewhat surprisingly, that the claim of 98\% of clones being produced at method-level is nowhere near correct.
+From these results we can see that the claim of 98\% of clones being produced at method-level is nowhere near correct.
 In fact, around 58\% of the clones are produced at method-level.
@@
 
+The most trivial way to merge a clone is though method extraction. However, method extraction is not always possible.
+
 %TODO: Show and discuss measurements
@@
 
-\subsubsection{Acknowledgements}
+\section*{Acknowledgements}
 We would like to thank the Software Improvement Group (SIG) for their continuous support in this project.

### 2019-04-29 sattose/paper.tex
Stuff

@@
 Measurements that have been conducted so far have indicated that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
-Only a fifth of the duplication can be refactored through simple method extraction, the other clones require other techniques to be applied.
+Approximately a fifth of the duplication can be refactored through method extraction, the other clones require other techniques to be applied.
 More measurements will be conducted to get a detailed overview of in what contexts clones occur, and what this means for the refactoring processes of these clones.
@@
 
-The most trivial way to merge a clone is though method extraction. However, method extraction is not always possible.
+The most trivial way to merge a clone is though method extraction.
+However, method extraction is not always possible.
+For instance, if a part of a subtree (in a programs' AST) is matched as a clone.
+Because of this, we chose to measure what percentage of ``Partial Method'' clones are refactorable using method extraction.
+Our results are displayed in figure
 

### 2019-04-29 sattose/paper.tex
Merging chapter

@@
 Because of this, we chose to measure what percentage of ``Partial Method'' clones are refactorable using method extraction.
-Our results are displayed in figure
+Our results are displayed in table \ref{table:refactorability}.
 
-%TODO: Show and discuss measurements
+\begin{table}[H]
+  \begin{center}
+  \caption{Clone instance contents} \label{table:refactorability}
+  \bigskip
+\begin{tabular}{|l|l|l|}
+\hline
+\textbf{Refactorability}        & \textbf{Amount} & \textbf{Percentage} \\ \hline
+Cannot directly be extracted    & 10990           & 41,91               \\ \hline
+Can be extracted                & 5791            & 22,08               \\ \hline
+Not possible because of content & 9444            & 36,01               \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+From this table we can see that approximately 22 percent of the clones can be refactored through method extraction. For the other clones, we must first build a catalog of appropriate refactorings.
 
@@
 \section{Conclusion and next steps}
-We conclude that most clones are found in methods, but no easy refactoring is available for them.
+We conclude that most clones are found in methods, but most cannot be refactored using only method extraction (as is often assumed when dealing with duplication in code).
 Most clones have complex nesting, and need further consideration to be able to merge them.
-The study that we have conducted so far analyzes different kinds of clones for harmfulness and prioritizes their refactoring.
+The study that we have conducted so far analyzes the context of different kinds of clones and prioritizes their refactoring.
 On basis of this we will extend our tool, CloneRefactor, to be able to apply refactorings to the found clones.
-We will formalize refactorings for clones that make use of their relation.
-We found that almost 40\% of the clones are unrelated, so we will start formalizing refactorings by finding a refactoring opportunity for such clones.
-
-%TODO: Expand conclusion
 

### 2019-04-29 sattose/paper.tex
Conclusion

@@
 \section{Conclusion and next steps}
-We conclude that most clones are found in methods, but most cannot be refactored using only method extraction (as is often assumed when dealing with duplication in code).
-Most clones have complex nesting, and need further consideration to be able to merge them.
 The study that we have conducted so far analyzes the context of different kinds of clones and prioritizes their refactoring.
-On basis of this we will extend our tool, CloneRefactor, to be able to apply refactorings to the found clones.
+Firstly, we looked at the inheritance relation of clone instances in a clone class.
+We have found that most clone classes are unrelated, which means that they have at least one instance that has no relation with the other instances.
+There were also a lot of clone classes of which all instances are in the same class.
+At the third place are clone instances that are siblings of each other (share the same superclass).
+
+Secondly, we looked at the location of clone instances.
+Most clone instances are found at method level, about 58 percent.
+About 39 percent of clone instances were found at class level.
+We defined ``class level clones'' as clones that that exceed the boundaries of a single method or contain something else in the class (like field declarations, other methods, etc.).
+
+Thirdly, we looked at the contents of clone instances.
+Most clones span a part of a method (56 percent).
+About 26 percent of clones span over several methods.
+We also looked into the refactorability of clones that span part of a method.
+Over 22 percent of the clones can directly be refactored by extracting them to a new method (and calling the method at all usages using their relation).
+The main reason that most clones that span a part of a method cannot directly be refactored by method extraction, is that they are nested in such a way that method extraction would leave side effects (for instance, we cannot extract half of a for-loop).
+
+\subsection{Next steps}
+As a first next step, we
 

### 2019-04-29 sattose/paper.tex
Next steps

@@
 \subsection{Next steps}
-As a first next step, we
+As a first next step, we will integrate our redefinition of type-2 clones into CloneRefactor.
+This way, we can run all scripts that we used for all measurements for our redefinition of type-2 clones.
+We are curious to see how it compares with the results we had for the type-1 clones so far.
+
+As we want to refactor duplicates fully automated, it is very important that both code fragments have exactly the same functionality.
+Because of this, we want to look into building a SymbolTable of projects we scan and their dependencies.
+This allows us to further assess the equality of code fragments.
+Currently we compare fragments, as most clone detection tools do, on basis of static analysis of only the target project.
+However, because of this, we omit valuable information like fully qualified identifiers for types.
+By parsing not only a project, but also its dependencies, we can better assess whether two code fragments are actually equal, or whether they are calling different methods but with the same type signature (we are currently limited in distinguishing these).
+
+Furthermore, we want to start automatically refactoring clones.
+On basis of our initial results, we have determined that we can best start with the automatic refactoring of clones that can be extracted to a method.
+If this works, we can already decrease duplication by 22\%.
 

### 2019-04-29 sattose/paper.tex
Spelling & Formatting

@@
 More measurements will be conducted to get a detailed overview of in what contexts clones occur, and what this means for the refactoring processes of these clones.
-As a desired output, we strive to construct a model that automatically applies refactorings for a large part of the detected duplication problems.
+As the desired output, we strive to construct a model that automatically applies refactorings for a large part of the detected duplication problems.
 This model will be implemented for the Java programming language.
@@
 
-Refactoring is used to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
+Refactoring is used to improve the quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
 There are many methods that have been introduced to help with the process of refactoring \cite{fowler1999refactoring, wake2004refactoring}, that are integrated into most modern IDE's.
-However, most of these methods still require manual assessment of where and when to apply them.
+However, most of these methods still require a manual assessment of where and when to apply them.
 Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, or does not happen at all \cite{mens2003refactoring}.
@@
 However, there are also refactoring opportunities that are rather trivial and repetitive to execute.
-In this research we will look at to what extend code clones can be automatically refactored.
+In this research, we will look at to what extend code clones can be automatically refactored.
 
@@
 We lay the main focus on the Java programming language as refactoring opportunities feature paradigm and programming language dependent aspects \cite{choi2011extracting}.
-However, most practises featured in this research will also be applicable with other object-oriented languages, like C\#.
+However, most practices featured in this research will also be applicable to other object-oriented languages, like C\#.
 
@@
 A survey by Roy et al \cite{roy2007survey} states definitions for various important concepts in code clone research.
-In this survey he mentions the concept ``clone pair'', which is \textit{a set of two code portions/fragments which are identical or similar to each other}.
+In this survey, he mentions the concept ``clone pair'', which is \textit{a set of two code portions/fragments which are identical or similar to each other}.
 Furthermore, he defined ``clone class'' as \textit{the union of all clone pairs}.
@@
 A tool called DCRA (Duplicated Code Refactoring Advisor) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated}.
-This tool chooses to only focus on refactoring clone pairs because they argue that \textit{clone pairs are much easier to manage when considered singularly.} As intermidiate steps the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.
+This tool chooses to only focus on refactoring clone pairs because they argue that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.
 
 Another tool called Aries \cite{higo2004aries, higo2008metric} focuses on the detection of refactoring oriented clones.
-In this paper the authors describe a few variables by which a clone can be assessed for refactoring suitability.
+In this paper, the authors describe a few variables by which a clone can be assessed for refactoring suitability.
 This tool looks however only at the possibility to merge clones, rather than whether clones should be merged.
-Also, this tool only suggests refactorings, and does not apply them.
+Also, this tool only suggests refactorings and does not apply them.
 
@@
 Also, these publications/tools are limited to suggesting refactoring opportunities for clones found, rather than actually applying refactorings where suitable.
-Finally, all published approaches have limitations, for instance false positives when detecting clones \cite{chen2018clone} or being limited to clone pairs \cite{higo2008metric}.
+Finally, all published approaches have limitations, for instance, false positives when detecting clones \cite{chen2018clone} or being limited to clone pairs \cite{higo2008metric}.
 
@@
 A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection.
-For our tool we decided to combine AST and Graph based approaches for clone detection, similar to Scorpio (which is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs).
+For our tool, we decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio (which is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs).
 We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is useable with all modern Java versions (Java 1-12).
 We collect each statement and declaration and compare those to find duplicates.
-This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of it's duplicates (verically).
+This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically).
 This is displayed in figure \ref{fig:clonerefactor}.
@@
 \begin{enumerate}
-  \item \textbf{Number of statements/declarations:} The amount of statements/declarations that should be equal/similar for it to be considered a clone.
-  \item \textbf{Number of tokens:} The amount of tokens (excluding whitespace, end-of-line terminators and comments) that should be equal/similar for it to be considered a clone.
+  \item \textbf{Number of statements/declarations:} The number of statements/declarations that should be equal/similar for it to be considered a clone.
+  \item \textbf{Number of tokens:} The number of tokens (excluding whitespace, end-of-line terminators and comments) that should be equal/similar for it to be considered a clone.
   \item \textbf{Number of lines:} The minimum amount of lines (excluding lines that do not contain any tokens, for tokens same exclusions apply) that should be equal/similar for it to be considered a clone.
@@
 On basis of manual assessment, we have determined that setting the ``number of statements/declarations'' to 6 ensures that most non-harmful clones are filtered out.
-On the downside, this also filters out some harmful antipatterns, for instance if a cloned line has many tokens we might want to consider a clone if it spans less than 6 statements (as cloned line with many tokens is more harmful than one with few).
+On the downside, this also filters out some harmful antipatterns, for instance, if a cloned line has many tokens we might want to consider a clone if it spans less than 6 statements (as a cloned line with many tokens is more harmful than one with few).
 
@@
 \begin{enumerate}
-  \item The relation of clone instances among each other (for example: two clone instances in a clone class are part of the same object).
+  \item The relation of clone instances among each other (for example two clone instances in a clone class are part of the same object).
   \item Where a clone instance occurs in the code (for instance: a method-level clone is a clone instance that is (a part of) a single method).
-  \item The contents of a clone instance (for instance: the clone instance consists of a one method declaration, a foreach statement and two variable declarations).
+  \item The contents of a clone instance (for instance: the clone instance consists of a one method declaration, a foreach statement, and two variable declarations).
 \end{enumerate}
-Everything in the context of a clone has a big impact on how it has to be refactored. For this study we performed measurements on the context of clones in a large corpus of open source projects.
+Everything in the context of a clone has a big impact on how it has to be refactored. For this study, we performed measurements on the context of clones in a large corpus of open source projects.
 
@@
 Also, any duplicate projects were removed from this corpus.
-This results in a variaty of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
+This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
 
 We then filtered the corpus further to make sure we are not including any test classes or generated classes.
-Many Java/Maven projects use a structure where they separate the application and it's tests in the different folders (``/src/main/java'' and ``/src/test/java'' respectively).
+Many Java/Maven projects use a structure where they separate the application and its tests in the different folders (``/src/main/java'' and ``/src/test/java'' respectively).
 Because of this, we chose to only use projects from the corpus which use this structure (and had at least a ``/src/main/java'' folder).
@@
 \hline
-Amount of projects                                                                                      & 3.848      \\ \hline
-Amount of lines                                                                                         & 8.284.140  \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\ whitespace, comments, etc.)\end{tabular}        & 8.163.429  \\ \hline
-Amount of statements/declarations                                                                       & 6.863.725  \\ \hline
-Amount of tokens                                                                                        & 66.964.270 \\ \hline
-Amount of lines cloned                                                                                  & 1.341.094  \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines cloned (excluding\\ whitespace, comments, etc.)\end{tabular} & 815.799    \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of statements/declarations\\ cloned\end{tabular}                      & 747.993    \\ \hline
-Amount of tokens cloned                                                                                 & 9.800.819  \\ \hline
-Amount of clone classes                                                                                 & 34.367     \\ \hline
+Amount of projects                                                                                      & 3,848      \\ \hline
+Amount of lines                                                                                         & 8,284,140  \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\ whitespace, comments, etc.)\end{tabular}        & 8,163,429  \\ \hline
+Amount of statements/declarations                                                                       & 6,863,725  \\ \hline
+Amount of tokens                                                                                        & 66,964,270 \\ \hline
+Amount of lines cloned                                                                                  & 1,341,094  \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of lines cloned (excluding\\ whitespace, comments, etc.)\end{tabular} & 815,799    \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of statements/declarations\\ cloned\end{tabular}                      & 747,993    \\ \hline
+Amount of tokens cloned                                                                                 & 9,800,819  \\ \hline
+Amount of clone classes                                                                                 & 34,367     \\ \hline
 \end{tabular}
@@
 
-The ranking of the previous list of categories also matters, as it shows the different levels in which clones were assessed.
-For instance, if two clone instances of a clone class belong to the ``same method'' category but the third belongs to the ``same class'', we will always chose the item lowest on the list.
+The ranking of the previous list of categories also matters as it shows the different levels in which clones were assessed.
+For instance, if two clone instances of a clone class belong to the ``same method'' category but the third belongs to the ``same class'', we will always choose the item lowest on the list.
 
@@
 \textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
-Unrelated          & 13.529           & 39,37               \\ \hline
-Same Class          & 8.341            & 24,28               \\ \hline
-Sibling            & 5.978            & 17,40               \\ \hline
-Same Method         & 2.456            & 7,15                \\ \hline
-External Superclass & 2.402            & 6,99                \\ \hline
-First Cousin        & 695             & 2,02                \\ \hline
-Superclass         & 489             & 1,42                \\ \hline
-Common Hierarchy    & 442             & 1,29                \\ \hline
-Ancestor           & 28              & 0,08               \\ \hline
+Unrelated          & 13,529           & 39.37               \\ \hline
+Same Class          & 8,341            & 24.28               \\ \hline
+Sibling            & 5,978            & 17.40               \\ \hline
+Same Method         & 2,456            & 7.15                \\ \hline
+External Superclass & 2,402            & 6.99                \\ \hline
+First Cousin        & 695             & 2.02                \\ \hline
+Superclass         & 489             & 1.42                \\ \hline
+Common Hierarchy    & 442             & 1.29                \\ \hline
+Ancestor           & 28              & 0.08               \\ \hline
 \end{tabular}
@@
 A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning.
-In this paper the author argues that 98\% are produced at method-level.
-However, this claim is based on a small dataset and based on human copy-paste behaviour rather than static code analysis.
+In this paper, the author argues that 98\% are produced at method-level.
+However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
 We validated this claim over the corpus we use.
@@
 \textbf{Location}  & \textbf{Amount}  & \textbf{Percentage} \\ \hline
-Method Level       & 19.818           & 57,68               \\ \hline
-Class Level        & 13.259           & 38,59               \\ \hline
-Constructor Level  & 1.099            & 3,20                \\ \hline
-Interface Level    & 110              & 0,32                \\ \hline
-Enum Level         & 74               & 0,22                \\ \hline
+Method Level       & 19,818           & 57.68               \\ \hline
+Class Level        & 13,259           & 38.59               \\ \hline
+Constructor Level  & 1,099            & 3.20                \\ \hline
+Interface Level    & 110              & 0.32                \\ \hline
+Enum Level         & 74               & 0.22                \\ \hline
 \end{tabular}
@@
 
-From these results we can see that the claim of 98\% of clones being produced at method-level is nowhere near correct.
+From these results, we can see that the claim of 98\% of clones being produced at method-level is nowhere near correct.
 In fact, around 58\% of the clones are produced at method-level.
 About 39\% of clones either span several methods/constructors or contain something like a field declaration.
-Another 3\% of the clones is found in contructors.
+Another 3\% of the clones are found in constructors.
 The amount of clones found in interfaces and enumerations is very low.
@@
   \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
-  \item \textbf{Other:} Anything that does not match with above stated categories.
+  \item \textbf{Other:} Anything that does not match with above-stated categories.
 \end{enumerate}
 
-The results for these categories are displayed are displayed in table \ref{table:contents}.
+The results for these categories are displayed in table \ref{table:contents}.
 
@@
   \textbf{Contents}                                                        & \textbf{Amount} & \textbf{Percentage} \\ \hline
-  Partial Method                                                           & 19.264          & 56,07               \\ \hline
-  Several Methods                                                          & 9.076           & 26,41               \\ \hline
-  Includes Constructor                                                     & 1.528           & 4,45                \\ \hline
-  Includes Field                                                           & 1.149           & 3,34                \\ \hline
-  Partial Constructor                                                      & 1.098           & 3,20                \\ \hline
-  Only Fields                                                              & 565             & 1,64                \\ \hline
-  Full Method                                                              & 554             & 1,61                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Class\\ Declaration\end{tabular}     & 445             & 1,30                \\ \hline
-  Other                                                                    & 369             & 1,07                \\ \hline
-  Full Class                                                               & 192             & 0,56                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Constant\end{tabular}         & 52              & 0,15                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Declaration\end{tabular}      & 47              & 0,14                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Interface\\ Declaration\end{tabular} & 10              & 0,03                \\ \hline
-  Full Interface                                                           & 6               & 0,02                \\ \hline
-  Full Enumeration                                                         & 4               & 0,01                \\ \hline
+  Partial Method                                                           & 19,264          & 56.07               \\ \hline
+  Several Methods                                                          & 9,076           & 26.41               \\ \hline
+  Includes Constructor                                                     & 1,528           & 4.45                \\ \hline
+  Includes Field                                                           & 1,149           & 3.34                \\ \hline
+  Partial Constructor                                                      & 1,098           & 3.20                \\ \hline
+  Only Fields                                                              & 565             & 1.64                \\ \hline
+  Full Method                                                              & 554             & 1.61                \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Class\\ Declaration\end{tabular}     & 445             & 1.30                \\ \hline
+  Other                                                                    & 369             & 1.07                \\ \hline
+  Full Class                                                               & 192             & 0.56                \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Constant\end{tabular}         & 52              & 0.15                \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Declaration\end{tabular}      & 47              & 0.14                \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Interface\\ Declaration\end{tabular} & 10              & 0.03                \\ \hline
+  Full Interface                                                           & 6               & 0.02                \\ \hline
+  Full Enumeration                                                         & 4               & 0.01                \\ \hline
 \end{tabular}
@@
 \textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
-\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
+\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\
 \textbf{Type 4:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
@@
 Type 2 and type 3 clones are more disputable whether they are harmful and whether they can be merged in a way that improves the design of the code.
-In this chapter we will redefine type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design.
+In this chapter, we will redefine type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design.
 Type-4 clones are, because of the serious challenges involved in their detection and refactoring, out of the scope for this study.
@@
 \subsection{Type 2 clones}
-Type 2 clones, by definition, allow any change in identifiers, literals, types, layout and comments.
+Type 2 clones, by definition, allow any change in identifiers, literals, types, layout, and comments.
 For refactoring purposes, this doesn't always make a lot of sense.
-If we allow any change in identifiers, literals and types, we cannot distinguish between different variables, different types and different method calls anymore.
+If we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
 This could render two methods that have an entirely different functionality as clones.
-Merging such clones, if possible at all, might only proof to be harmful.
+Merging such clones, if possible at all, might only prove to be harmful.
 
-Because of that, for this research we have looked into a redefinition of type 2 clones to be able to detect such clones that can and should be merged.
+Because of that, for this research, we have looked into a redefinition of type 2 clones to be able to detect such clones that can and should be merged.
 Our definition ensures functional similarity by applying the following changes to type 2 clones:
@@
 \begin{itemize}
-  \item \textbf{Considering types:} The definition of type 2 clones defines that types should not be considered.
-We disagree, because types can make a significant change to the meaning of a code segment and thus whether this segment should be considered a clone.
+  \item \textbf{Considering types:} The definition of type 2 clones states that types should not be considered.
+We disagree because types can make a significant change to the meaning of a code segment and thus whether this segment should be considered a clone.
 For instance, we should not say that an Apple type object is the same as an object of Orange type (don't compare apples with oranges).
-  \item \textbf{Having a distinction between different variables:} By the definition of type 2 clones any identifiers would not be taken into account.
+  \item \textbf{Having a distinction between different variables:} By the definition of type 2 clones, any identifiers would not be taken into account.
 We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables.
@@
 Also, cloned code can contain a complex control structure, like labels, return, break, continue, etc.
-In such instances, more conditions apply do be able to conduct a refactoring, if advisable at all.
+In such instances, more conditions apply to be able to conduct a refactoring, if advisable at all.
 
-The most trivial way to merge a clone is though method extraction.
+The most trivial way to merge a clone is through method extraction.
 However, method extraction is not always possible.
@@
 \textbf{Refactorability}        & \textbf{Amount} & \textbf{Percentage} \\ \hline
-Cannot directly be extracted    & 10990           & 41,91               \\ \hline
-Can be extracted                & 5791            & 22,08               \\ \hline
-Not possible because of content & 9444            & 36,01               \\ \hline
+Cannot directly be extracted    & 10,990           & 41.91               \\ \hline
+Can be extracted                & 5,791            & 22.08               \\ \hline
+Not possible because of content & 9,444            & 36.01               \\ \hline
 \end{tabular}
@@
 
-From this table we can see that approximately 22 percent of the clones can be refactored through method extraction. For the other clones, we must first build a catalog of appropriate refactorings.
+From this table, we can see that approximately 22 percent of the clones can be refactored through method extraction. For the other clones, we must first build a catalog of appropriate refactorings.
 
@@
 About 39 percent of clone instances were found at class level.
-We defined ``class level clones'' as clones that that exceed the boundaries of a single method or contain something else in the class (like field declarations, other methods, etc.).
+We defined ``class level clones'' as clones that exceed the boundaries of a single method or contain something else in the class (like field declarations, other methods, etc.).
 
@@
 This allows us to further assess the equality of code fragments.
-Currently we compare fragments, as most clone detection tools do, on basis of static analysis of only the target project.
+Currently, we compare fragments, as most clone detection tools do, on basis of static analysis of only the target project.
 However, because of this, we omit valuable information like fully qualified identifiers for types.

### 2019-04-29 sattose/paper.tex
Fixed a table
Changed the place

@@
 Simon Baars \\ University of Amsterdam\\
-                Puiflijk, Netherlands \\ simon.mailadres@gmail.com
+                Amsterdam, Netherlands \\ simon.mailadres@gmail.com
 \and
@@
 \maketitle
-% In this paper I talk about clone instances and clone classes. Should I explain those concepts first?
 
@@
 \textbf{Refactorability}        & \textbf{Amount} & \textbf{Percentage} \\ \hline
-Cannot directly be extracted    & 10,990           & 41.91               \\ \hline
-Can be extracted                & 5,791            & 22.08               \\ \hline
-Not possible because of content & 9,444            & 36.01               \\ \hline
+\begin{tabular}[c]{@{}l@{}}Cannot directly\\be extracted\end{tabular}    & 10,990           & 41.91               \\ \hline
+\begin{tabular}[c]{@{}l@{}}Is not a\\partial method\end{tabular} & 9,444            & 36.01               \\ \hline
+\begin{tabular}[c]{@{}l@{}}Can be\\extracted\end{tabular}                & 5,791            & 22.08               \\ \hline
+
 \end{tabular}

### 2019-04-30 sattose/paper.tex
Changed the title
Added a thread to validity

@@
 
-\title{Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -}
+\title{Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -}
 
@@
 
+Another thread to validity is that currently, in a very small number of cases, clone detection might result in a false positive.
+This is in cases where two lines are equal, but they actually call different methods with the same method signature.
+In such a case, merging such clones might turn out to change the functionality of the program.
+We have noted this down as a next step, working on basis of a callgraph instead of just the AST.
+
 \section{Conclusion and next steps}

### 2019-04-30 sattose/paper.tex
Treat method call expressions like literals
Should we?????????????????

@@
 It also makes the clone harder to refactor, as more transformations would be required.
-Higher clone types also become more disputable whether they actually indicate a harmful antipattern (not every clone is harmful).
+Higher clone types also become more disputable whether they actually indicate a harmful antipattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}).
 Type 1 clones are most often, if not always with the right thresholds, harmful.
@@
 We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
+  \item \textbf{Treat method call expressions like literals:} As type-2 clones allows change in identifiers, also the names of called methods may vary.
+However, because of this, completely different methods can be called in cloned fragments as a result.
+Having many method calls in a cloned fragment, will decrease the need for refactoring (in terms of improving design) when these are matched as type-2 clones (so method identifiers differ), because they can describe a completely different functionality.
+Because of that, we recommend having variability in method call expressions under the same threshold as literals, so only a limited number of method calls can vary.
 \end{itemize}

### 2019-04-30 sattose/paper.tex
Let's do it this way

--- 2019-04-30 sattose/paper.tex
@@
 We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
+  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allows change in identifiers, also the names of called methods may vary.
+However, because of this, completely different methods can be called in cloned fragments as a result.
+This poses serious challenges on refactoring, and makes it more disputable whether such a clone is actually harmful.
+This is because diffent method identifiers can describe a completely different functionality.
+Because of that, we recommend to consider the call signatures of cloned methods.
+We also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
 \end{itemize}

### 2019-04-30 sattose/paper.tex
Type 3 clones: I think this is important

@@
 
+As for the detection of type 3 clones, we think the easiest opportunity to detect these clones is to consider it as a postprocessing step after clone detection.
+By trying to find short gaps between clones, we can find opportunities to merge clone classes into a single type 3 clone class.
+The amount of statements that this ``short gap'' can maximally span should be dependent on a threshold value.
+
 \section{Merging duplicate code through refactoring}

### 2019-05-01 sattose/paper.tex
Type 1 clones

@@
 
-\section{Redefining type 2 and type 3 clones}
+\section{Redefining type 1, 2 and type 3 clones}
 In a 2007 survey by Roy et al \cite{roy2007survey} he defined four types of clones:
@@
 Type-4 clones are, because of the serious challenges involved in their detection and refactoring, out of the scope for this study.
+
+\subsection{Type 1 clones}
+Type 1 clones are identical clone fragments except for variations in whitespace and comments.
+However, when two clone fragments are textually identical, does not yet indicate that they are actually identical.
+Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type.
+This could invalidate a refactoring opportunity for such a code fragment.
+Because of that, we recommend to redefine type-1 clones for refactoring.
+We propose to:
+\begin{itemize}
+  \item \textbf{Compare the equality of the fully qualified method signature for method references.} This way we can validate whether two method references, like method calls, are actually equal.
+In this method signature not only the fully qualified identifier of the method should be considered, but also of the type of all its arguments.
+This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
+  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
+  \item \textbf{Compare the equality the fully qualified identier for variable usages.} Two cloned lines might use a variable with the same name, but different types.
+This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive.
+To check this, we need to track the declaration of variables and from this infer the fully qualified indentifier of its type.
+\end{itemize}
 

### 2019-05-01 sattose/paper.tex
A bit of spelling

@@
 
-Refactoring is used to improve the quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
+Refactoring is used to improve the quality-related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
 There are many methods that have been introduced to help with the process of refactoring \cite{fowler1999refactoring, wake2004refactoring}, that are integrated into most modern IDE's.
@@
 This could invalidate a refactoring opportunity for such a code fragment.
-Because of that, we recommend to redefine type-1 clones for refactoring.
+Because of that, we recommend redefining type-1 clones for refactoring.
 We propose to:
@@
   \item \textbf{Compare the equality of the fully qualified method signature for method references.} This way we can validate whether two method references, like method calls, are actually equal.
-In this method signature not only the fully qualified identifier of the method should be considered, but also of the type of all its arguments.
+In the method signature, not only the fully qualified identifier of the method should be considered, but also of the type of all its arguments.
 This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
   \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
-  \item \textbf{Compare the equality the fully qualified identier for variable usages.} Two cloned lines might use a variable with the same name, but different types.
+  \item \textbf{Compare the equality the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types.
 This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive.
-To check this, we need to track the declaration of variables and from this infer the fully qualified indentifier of its type.
+To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
 \end{itemize}

### 2019-05-01 sattose/paper.tex
Some rewriting of type 2 method consideration

@@
 We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
-  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allows change in identifiers, also the names of called methods may vary.
+  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary.
 However, because of this, completely different methods can be called in cloned fragments as a result.
-This poses serious challenges on refactoring, and makes it more disputable whether such a clone is actually harmful.
-This is because diffent method identifiers can describe a completely different functionality.
-Because of that, we recommend to consider the call signatures of cloned methods.
-We also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
+This poses serious challenges on refactoring and makes it more disputable whether such a clone is actually harmful.
+This is because different method identifiers can describe a completely different functionality.
+Because of that, we recommend to keep considering the call signatures of cloned methods when they are compared.
+We can allow variability in the rest of method identifiers by passing the function as a parameter.
+To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
 \end{itemize}
@@
 Merging the clones can be harder in such instances.
-Also, cloned code can contain a complex control structure, like labels, return, break, continue, etc.
+Also, the cloned code can contain a complex control structure, like labels, return, break, continue, etc.
 In such instances, more conditions apply to be able to conduct a refactoring, if advisable at all.

### 2019-05-02 sattose/paper.tex
This line was cheesy anyways
Moved type 2 clones :up:
For now, I think it's more correct to put only me there

@@
                 Amsterdam, Netherlands \\ simon.mailadres@gmail.com
-\and
-Ana Oprescu \\ University of Amsterdam\\
-                Amsterdam, Netherlands \\ A.M.Oprescu@uva.nl
 }
@@
 \end{itemize}
+
+\section{Redefining type 1, 2 and type 3 clones}
+In a 2007 survey by Roy et al \cite{roy2007survey} he defined four types of clones:
+
+\textbf{Type 1:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
+\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
+\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\
+\textbf{Type 4:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
+
+A higher type of clone means that it's harder to detect.
+It also makes the clone harder to refactor, as more transformations would be required.
+Higher clone types also become more disputable whether they actually indicate a harmful antipattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}).
+Type 1 clones are most often, if not always with the right thresholds, harmful.
+Type 2 and type 3 clones are more disputable whether they are harmful and whether they can be merged in a way that improves the design of the code.
+In this chapter, we will redefine type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design.
+Type-4 clones are, because of the serious challenges involved in their detection and refactoring, out of the scope for this study.
+
+\subsection{Type 1 clones}
+Type 1 clones are identical clone fragments except for variations in whitespace and comments.
+However, when two clone fragments are textually identical, does not yet indicate that they are actually identical.
+Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type.
+This could invalidate a refactoring opportunity for such a code fragment.
+Because of that, we recommend redefining type-1 clones for refactoring.
+We propose to:
+\begin{itemize}
+  \item \textbf{Compare the equality of the fully qualified method signature for method references.} This way we can validate whether two method references, like method calls, are actually equal.
+In the method signature, not only the fully qualified identifier of the method should be considered, but also of the type of all its arguments.
+This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
+  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
+  \item \textbf{Compare the equality the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types.
+This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive.
+To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
+\end{itemize}
+
+\subsection{Type 2 clones}
+Type 2 clones, by definition, allow any change in identifiers, literals, types, layout, and comments.
+For refactoring purposes, this doesn't always make a lot of sense.
+If we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
+This could render two methods that have an entirely different functionality as clones.
+Merging such clones, if possible at all, might only prove to be harmful.
+
+Because of that, for this research, we have looked into a redefinition of type 2 clones to be able to detect such clones that can and should be merged.
+Our definition ensures functional similarity by applying the following changes to type 2 clones:
+
+\begin{itemize}
+  \item \textbf{Considering types:} The definition of type 2 clones states that types should not be considered.
+We disagree because types can make a significant change to the meaning of a code segment and thus whether this segment should be considered a clone.
+  \item \textbf{Having a distinction between different variables:} By the definition of type 2 clones, any identifiers would not be taken into account.
+We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables.
+For instance, if we call a method like this: \textit{``myMethod(var1, var2)''}, or call this method like this: \textit{``myMethod(var1, var1)''}.
+Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
+  \item \textbf{Defining a threshold for variability in literals:} By the definition of type 2 clones any literals would not be taken into account.
+We agree, as when merging the clone (for instance by extracting a method), we can simply turn the literal into a method parameter.
+However, we would argue that thresholds matter here.
+How many literals may differ for the segment still to be considered a clone with another segment?
+We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
+  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary.
+However, because of this, completely different methods can be called in cloned fragments as a result.
+This poses serious challenges on refactoring and makes it more disputable whether such a clone is actually harmful.
+This is because different method identifiers can describe a completely different functionality.
+Because of that, we recommend to keep considering the call signatures of cloned methods when they are compared.
+We can allow variability in the rest of method identifiers by passing the function as a parameter.
+To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
+\end{itemize}
+
+\subsection{Type 3 clones}
+Type 3 clones are even more permissive than type 2 clones, allowing added and removed statements.
+Thresholds matter a lot here to make sure that not the whole project is detected to be cloned.
+The main question for this study regarding type 3 clones is: ``how can we merge type 3 clones while improving the design?''.
+
+Clone instances in type 3 clones are almost always different in functionality.
+As we have to ensure equal functionality after merging the clone, we have to wrap the difference in statements between the clone instances in conditional blocks (either if-statements or switch-statements).
+We can then pass a variable as to which path should be taken through the code (either a boolean or an enumeration).
+Such a refactoring would make added statements that are contiguous less harmful for the design then added statements than added statements that are separated by statements that both clone instances have in common.
+
+We also want to argue that statements that are not common between two clone instances, should not count towards the size of the clone (and thus towards the threshold which determines whether the clone will be taken into account).
+Also, clones should not start and not end with an added statement (as that would be nonsense: such a thing could be done for any clone).
+
+As for the detection of type 3 clones, we think the easiest opportunity to detect these clones is to consider it as a postprocessing step after clone detection.
+By trying to find short gaps between clones, we can find opportunities to merge clone classes into a single type 3 clone class.
+The amount of statements that this ``short gap'' can maximally span should be dependent on a threshold value.
 
@@
 
-\section{Redefining type 1, 2 and type 3 clones}
-In a 2007 survey by Roy et al \cite{roy2007survey} he defined four types of clones:
-
-\textbf{Type 1:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
-\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
-\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\
-\textbf{Type 4:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
-
-A higher type of clone means that it's harder to detect.
-It also makes the clone harder to refactor, as more transformations would be required.
-Higher clone types also become more disputable whether they actually indicate a harmful antipattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}).
-Type 1 clones are most often, if not always with the right thresholds, harmful.
-Type 2 and type 3 clones are more disputable whether they are harmful and whether they can be merged in a way that improves the design of the code.
-In this chapter, we will redefine type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design.
-Type-4 clones are, because of the serious challenges involved in their detection and refactoring, out of the scope for this study.
-
-\subsection{Type 1 clones}
-Type 1 clones are identical clone fragments except for variations in whitespace and comments.
-However, when two clone fragments are textually identical, does not yet indicate that they are actually identical.
-Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type.
-This could invalidate a refactoring opportunity for such a code fragment.
-Because of that, we recommend redefining type-1 clones for refactoring.
-We propose to:
-\begin{itemize}
-  \item \textbf{Compare the equality of the fully qualified method signature for method references.} This way we can validate whether two method references, like method calls, are actually equal.
-In the method signature, not only the fully qualified identifier of the method should be considered, but also of the type of all its arguments.
-This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
-  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
-  \item \textbf{Compare the equality the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types.
-This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive.
-To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
-\end{itemize}
-
-\subsection{Type 2 clones}
-Type 2 clones, by definition, allow any change in identifiers, literals, types, layout, and comments.
-For refactoring purposes, this doesn't always make a lot of sense.
-If we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
-This could render two methods that have an entirely different functionality as clones.
-Merging such clones, if possible at all, might only prove to be harmful.
-
-Because of that, for this research, we have looked into a redefinition of type 2 clones to be able to detect such clones that can and should be merged.
-Our definition ensures functional similarity by applying the following changes to type 2 clones:
-
-\begin{itemize}
-  \item \textbf{Considering types:} The definition of type 2 clones states that types should not be considered.
-We disagree because types can make a significant change to the meaning of a code segment and thus whether this segment should be considered a clone.
-For instance, we should not say that an Apple type object is the same as an object of Orange type (don't compare apples with oranges).
-  \item \textbf{Having a distinction between different variables:} By the definition of type 2 clones, any identifiers would not be taken into account.
-We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables.
-For instance, if we call a method like this: \textit{``myMethod(var1, var2)''}, or call this method like this: \textit{``myMethod(var1, var1)''}.
-Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
-  \item \textbf{Defining a threshold for variability in literals:} By the definition of type 2 clones any literals would not be taken into account.
-We agree, as when merging the clone (for instance by extracting a method), we can simply turn the literal into a method parameter.
-However, we would argue that thresholds matter here.
-How many literals may differ for the segment still to be considered a clone with another segment?
-We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
-  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary.
-However, because of this, completely different methods can be called in cloned fragments as a result.
-This poses serious challenges on refactoring and makes it more disputable whether such a clone is actually harmful.
-This is because different method identifiers can describe a completely different functionality.
-Because of that, we recommend to keep considering the call signatures of cloned methods when they are compared.
-We can allow variability in the rest of method identifiers by passing the function as a parameter.
-To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
-\end{itemize}
-
-\subsection{Type 3 clones}
-Type 3 clones are even more permissive than type 2 clones, allowing added and removed statements.
-Thresholds matter a lot here to make sure that not the whole project is detected to be cloned.
-The main question for this study regarding type 3 clones is: ``how can we merge type 3 clones while improving the design?''.
-
-Clone instances in type 3 clones are almost always different in functionality.
-As we have to ensure equal functionality after merging the clone, we have to wrap the difference in statements between the clone instances in conditional blocks (either if-statements or switch-statements).
-We can then pass a variable as to which path should be taken through the code (either a boolean or an enumeration).
-Such a refactoring would make added statements that are contiguous less harmful for the design then added statements than added statements that are separated by statements that both clone instances have in common.
-
-We also want to argue that statements that are not common between two clone instances, should not count towards the size of the clone (and thus towards the threshold which determines whether the clone will be taken into account).
-Also, clones should not start and not end with an added statement (as that would be nonsense: such a thing could be done for any clone).
-
-As for the detection of type 3 clones, we think the easiest opportunity to detect these clones is to consider it as a postprocessing step after clone detection.
-By trying to find short gaps between clones, we can find opportunities to merge clone classes into a single type 3 clone class.
-The amount of statements that this ``short gap'' can maximally span should be dependent on a threshold value.
-
 \section{Merging duplicate code through refactoring}

### 2019-05-02 sattose/paper.tex
I want to say something about the redefinitions in the abstract, but I don't know how.
I don't like this sentence

@@
 In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages.
+We look into redefinitions for different types of clones that have been used in code duplication research for many years.
+These redefinitions are aimed towards flagging only clones that are useful for refactoring purposes.
 Measurements that have been conducted so far have indicated that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
@@
 The design decisions for this tool will be made on basis of data gathered from a large corpus of software systems.
-The tool will be developed on GitHub and stored in the Software Heritage \cite{di2017software} archives to ensure long term preservation.
 This way we strive to make the problem of duplication in source code easier to deal with.

### 2019-05-02 sections/abstract.tex
Abstract

@@
 \todo[inline,color=blue!10]{This should be done when most of the rest of the document is finished. Be concise, introduce context, problem, known approaches, your solution, your findings.}
+
+Duplication in source code can have a major negative impact on the maintainability of source code.
+There are several techniques that can be used in order to merge clones, reduce duplication, improve the design of the code and potentially also reduce the total volume of a software system.
+In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages.
+
+We first look into redefinitions for different types of clones that have been used in code duplication research for many years.
+These redefinitions are aimed towards flagging only clones that are useful for refactoring purposes.
+Our definition defines additional rules for type 1 clones to make sure two cloned fragments are actually equal.
+We also redefined type 2 clones to reduce the number of false positives resulting from it.
+
+We have conducted measurements that have indicated that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
+Approximately a fifth of the duplication can be refactored through method extraction, the other clones require other techniques to be applied.

### 2019-05-02 sections/background.tex
Wrote some stuff

@@
 \section{Clone Class}
-Before we go into the refactoring of code clones, we must first define how we identify a clone.
-Roy \cite{roy2007survey} distinguishes clone pairs, clone classes and clone class families.
-For this thesis we will consider only ``clone classes'', as the other concepts do not add to the understanding and reasoning of clones as applied in this thesis.
-Roy defined ``clone classes'' as \textit{the union of all code portions/fragments which are identical or similar to each other}.
+As code clones are seen as one of the most harmful types of technical debt, they have been studied very extensively.
+A survey by Roy et al \cite{roy2007survey} states definitions for various important concepts in code clone research.
+In this survey, he mentions the concept ``clone pair'', which is \textit{a set of two code portions/fragments which are identical or similar to each other}.
+Furthermore, he defined ``clone class'' as \textit{the union of all clone pairs}.
+Apart from this, we use the definition ``clone instance'', which is a single code portion/fragment that is part of either a clone pair or clone class.
 
-As an example, look at the code fragment displayed in figure \ref{fig:cloneclass}.
-It displays two clone classes.
-One clone class is in all three files, and has two lines in each file (line 5 and 6).
-The other clone class is only in the first two files, and has three lines in each file (line 5-7).
-The clone classes overlap partly.
+Figure \ref{fig:clonepair} displays an example of a clone pair or clone class.
+In this case, both cloned fragments, are found in the same class.
+Each of the cloned fragments can be defined as a ``clone instance''.
+
+\begin{figure}[H]
+	\includegraphics[width=1\textwidth]{img/clone-pair}
+	\caption{Example of a clone pair, as found in the \href{https://github.com/taweili/ardublock}{ardublock} project.}
+	\label{fig:clonepair}
+\end{figure}
+
+Figure \ref{fig:cloneclass} displays two clone classes.
+These clone classes are separated by a single line that is different.
+The first clone class spans over both the constructor and a method of this class.
+
 \begin{figure}[H]
 	\includegraphics[width=1\textwidth]{img/clone-class}
-	\caption{Simple example of two clone classes, one consisting of three blocks of code of three lines, one existing of two blocks of code of two lines.}
+	\caption{Example of two clone classes.}
 	\label{fig:cloneclass}
 \end{figure}
-
-\section{Clone Contexts}
-Code clones can be found anywhere in the code.
-The most commonly studied type of clone is the method-level clone.
-Method-level clones are duplicated blocks of code in the body of a method.
-Many clone detection tools only focus on method-level clones (like CPD\footnote{CPD is part of PMD, a commonly used source code analyzer: \url{https://github.com/pmd/pmd}}, Siamese\footnote{Siamese is an Elasticsearch based clone detector: \url{https://github.com/UCL-CREST/Siamese}}, Sysiphus\footnote{Sisyphus crawls the Java library for existing implementations of parts of a codebase: \url{https://github.com/fruffy/Sisyphus}}).
-The reason for this is that with method-level clones it's most likely that the clones are harmful, and they are more straight-forward to refactor.
-
-A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning.
-In this paper the author argues that 98\% are produced at method-level.
-However, the paper that is cited to support this claim \cite{bergman2004ethnographic} does not conclude this same information.
-First of all, the study that is referenced uses a very small dataset (460 copy \& paste instances by 11 participants).
-Secondly, the group of subject only consists og IBM researchers (selection bias).
-Thirdly, it only focuses on copy and paste instances, as opposed to other ways clones can creep into the code.
-Finally, the ``98\%'' is not stated explicitly, but is vaguely derivable from one of the figures (figure 1) in this paper.
-Because of this, there is no reliable overview of how many clones there are in different contexts.
-
-This thesis will focus on measuring how many clones there are per context.
-This way we can determine the impact of focussing our search on a specific context, like the analysis of only method-level clones.
-Our hypothesis is that the 98\% claim is not true (we think this should be far less).
-We also hypothesize that clones in different contexts than method-level are less likely to be harmful and less straight forward to refactor.
-
-\subsection{Clone refactoring in relationship to its context}
-How to refactor clones is highly dependent on their context.
-Method-level clones can be extracted to a method \cite{kodhai2013method} if all occurrences of the clone reside in the same class.
-If a method level clone is duplicated among classes in the same inheritance structure, we might need to pull-up a method in the inheritance structure.
-If instances of a method level clone are not in the same inheritance structure, we might need to either make a static method or create an inheritance structure ourselves.
-So not only a single instance of a clone has a context, but also the relationship between individual instances in a clone class.
-This is highly relevant to the way in which the clone has to be refactored.
 
@@
 \end{displayquote}
-A higher type of clone means that it's harder to detect and less subtle.
+A higher type of clone means that it's harder to detect and refactor.
 There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
 
-\subsection{Relevance to clone refactoring}
-Higher type clones are not only harder to detect, but also harder to refactor.
-How to refactor clones is heavily dependent on their context and type.
-Kodhai et al \cite{kodhai2013method} describe different refactorings that can be performed to deal with clones.
+Relating this to the clone class example of \ref{fig:cloneclass}, the complete class would be flagged as a type 2 clone.
+This is displayed in figure \ref{fig:type2cloneclass}.
+Considering such clones displays the opportunity to refactor the class as a whole.
 
-For this thesis, we have chosen not to further look at type III and IV clones, as it is very hard to formalize their refactoring processes. They are out of the scope for this thesis.
+\begin{figure}[H]
+	\includegraphics[width=1\textwidth]{img/type-2-clone-class}
+	\caption{The clone displayed in figure \ref{fig:cloneclass} as a type 2 clone.}
+	\label{fig:type2cloneclass}
+\end{figure}
+
+For this thesis we have chosen not to consider type 4 clones for refactoring, because they are both hard to detect and hard to refactor (how to choose the best alternative for a certain computation could be a thesis in itself).
+
+\section{Clone Contexts} %I don't really like this chapter.
+Code clones can be found anywhere in the code.
+The most commonly studied type of clone is the method-level clone.
+Method-level clones are duplicated blocks of code in the body of a method.
+Many clone detection tools only focus on method-level clones (like CPD\footnote{CPD is part of PMD, a commonly used source code analyzer: \url{https://github.com/pmd/pmd}}, Siamese\footnote{Siamese is an Elasticsearch based clone detector: \url{https://github.com/UCL-CREST/Siamese}}, Sysiphus\footnote{Sisyphus crawls the Java library for existing implementations of parts of a codebase: \url{https://github.com/fruffy/Sisyphus}}).
+The reason for this is that with method-level clones it's most likely that the clones are harmful, and they are more straight-forward to refactor.
+
+A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning.
+In this paper the author argues that 98\% are produced at method-level.
+However, the paper that is cited to support this claim \cite{bergman2004ethnographic} does not conclude this same information.
+First of all, the study that is referenced uses a very small dataset (460 copy \& paste instances by 11 participants).
+Secondly, the group of subject only consists of IBM researchers (selection bias).
+Thirdly, it only focuses on copy and paste instances, as opposed to other ways clones can creep into the code.
+Finally, the ``98\%'' is not stated explicitly, but is vaguely derivable from one of the figures (figure 1) in this paper.
+Because of this, there is no reliable overview of how many clones there are in different contexts.
+
+This thesis will focus on measuring how many clones there are per context.
+This way we can determine the impact of focusing our search on a specific context, like the analysis of only method-level clones.
+Our hypothesis is that the 98\% claim is not true (we think this should be far less).
+We also hypothesize that clones in different contexts than method-level are less likely to be harmful and less straight forward to refactor.
+
+\subsection{Clone refactoring in relationship to its context}
+How to refactor clones is highly dependent on their context.
+Method-level clones can be extracted to a method \cite{kodhai2013method} if all occurrences of the clone reside in the same class.
+If a method level clone is duplicated among classes in the same inheritance structure, we might need to pull-up a method in the inheritance structure.
+If instances of a method level clone are not in the same inheritance structure, we might need to either make a static method or create an inheritance structure ourselves.
+So not only a single instance of a clone has a context, but also the relationship between individual instances in a clone class.
+This is highly relevant to the way in which the clone has to be refactored.
 

### 2019-05-02 sections/research.tex
Kind of included my paper in my thesis

--- 2019-04-11 sections/research.tex
@@
-\chapter{Your research}
-\label{ch:research_method}
+\chapter{Clone Detection}
+As duplication in source code is a serious problem in many software systems, there are a lot of researches that look into code clones.
+Many tools have been proposed to detect various types of code clones.
+Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016.
+To be able to refactor detected clones, it is useful to have the ability to rewrite the AST.
+We considered a set of clone detection tools for their ability to support the refactoring process automatically.
+None of the tools we consider seemed completely fit for this purpose, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
 
-Depending on your subject, you might need multiple research chapters.
-Moreover, depending on how the research questions are linked, you may need to answer them one by one and then connect the answers into a final discussion chapter.
+\section{CloneRefactor}
+A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection.
+For our tool, we decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio (which is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs).
+We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is useable with all modern Java versions (Java 1-12).
+We collect each statement and declaration and compare those to find duplicates.
+This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically).
+This is displayed in figure \ref{fig:clonerefactor}.
 
-See Canvas for examples of theses with various approaches to structuring the research content.
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/CodeGraph}
+  \caption{Abstract figure of the graph representation built by CloneRefactor}
+  \label{fig:clonerefactor}
+\end{figure}
+
+\section{Thresholds}
+CloneRefactor works on basis of three thresholds for finding clones:
+\begin{enumerate}
+  \item \textbf{Number of statements/declarations:} The number of statements/declarations that should be equal/similar for it to be considered a clone.
+  \item \textbf{Number of tokens:} The number of tokens (excluding whitespace, end-of-line terminators and comments) that should be equal/similar for it to be considered a clone.
+  \item \textbf{Number of lines:} The minimum amount of lines (excluding lines that do not contain any tokens, for tokens same exclusions apply) that should be equal/similar for it to be considered a clone.
+\end{enumerate}
+Of course, if we put any of these thresholds to zero it won't be taken into account anymore, so not all thresholds have to be used at all times.
+We consider ``number of lines'' to be the least important, as it highly depends on the programmer of the codebase (and we do not want this kind of dependence!).
+On basis of manual assessment, we have determined that setting the ``number of statements/declarations'' to 6 ensures that most non-harmful clones are filtered out.
+On the downside, this also filters out some harmful antipatterns, for instance, if a cloned line has many tokens we might want to consider a clone if it spans less than 6 statements (as a cloned line with many tokens is more harmful than one with few).
+
+For the measurements in the next chapter we have chosen to apply the following thresholds:
+\begin{itemize}
+  \item \textbf{Number of statements/declarations:} 6
+  \item \textbf{Number of tokens:} 10
+  \item \textbf{Number of lines:} 6
+\end{itemize}
+
+\chapter{Redefining type 1, 2 and type 3 clones}
+In a 2007 survey by Roy et al \cite{roy2007survey} he defined four types of clones:
+
+\textbf{Type 1:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
+\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
+\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\
+\textbf{Type 4:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
+
+A higher type of clone means that it's harder to detect.
+It also makes the clone harder to refactor, as more transformations would be required.
+Higher clone types also become more disputable whether they actually indicate a harmful antipattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}).
+Type 1 clones are most often, if not always with the right thresholds, harmful.
+Type 2 and type 3 clones are more disputable whether they are harmful and whether they can be merged in a way that improves the design of the code.
+In this chapter, we will redefine type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design.
+Type-4 clones are, because of the serious challenges involved in their detection and refactoring, out of the scope for this study.
+
+\section{Type 1 clones}
+Type 1 clones are identical clone fragments except for variations in whitespace and comments.
+However, when two clone fragments are textually identical, does not yet indicate that they are actually identical.
+Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type.
+This could invalidate a refactoring opportunity for such a code fragment.
+Because of that, we recommend redefining type-1 clones for refactoring.
+We propose to:
+\begin{itemize}
+  \item \textbf{Compare the equality of the fully qualified method signature for method references.} This way we can validate whether two method references, like method calls, are actually equal.
+In the method signature, not only the fully qualified identifier of the method should be considered, but also of the type of all its arguments.
+This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
+  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
+  \item \textbf{Compare the equality the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types.
+This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive.
+To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
+\end{itemize}
+
+\section{Type 2 clones}
+Type 2 clones, by definition, allow any change in identifiers, literals, types, layout, and comments.
+For refactoring purposes, this doesn't always make a lot of sense.
+If we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
+This could render two methods that have an entirely different functionality as clones.
+Merging such clones, if possible at all, might only prove to be harmful.
+
+Because of that, for this research, we have looked into a redefinition of type 2 clones to be able to detect such clones that can and should be merged.
+Our definition ensures functional similarity by applying the following changes to type 2 clones:
+
+\begin{itemize}
+  \item \textbf{Considering types:} The definition of type 2 clones states that types should not be considered.
+We disagree because types can make a significant change to the meaning of a code segment and thus whether this segment should be considered a clone.
+  \item \textbf{Having a distinction between different variables:} By the definition of type 2 clones, any identifiers would not be taken into account.
+We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables.
+For instance, if we call a method like this: \textit{``myMethod(var1, var2)''}, or call this method like this: \textit{``myMethod(var1, var1)''}.
+Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
+  \item \textbf{Defining a threshold for variability in literals:} By the definition of type 2 clones any literals would not be taken into account.
+We agree, as when merging the clone (for instance by extracting a method), we can simply turn the literal into a method parameter.
+However, we would argue that thresholds matter here.
+How many literals may differ for the segment still to be considered a clone with another segment?
+We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
+  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary.
+However, because of this, completely different methods can be called in cloned fragments as a result.
+This poses serious challenges on refactoring and makes it more disputable whether such a clone is actually harmful.
+This is because different method identifiers can describe a completely different functionality.
+Because of that, we recommend to keep considering the call signatures of cloned methods when they are compared.
+We can allow variability in the rest of method identifiers by passing the function as a parameter.
+To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
+\end{itemize}
+
+\section{Type 3 clones}
+Type 3 clones are even more permissive than type 2 clones, allowing added and removed statements.
+Thresholds matter a lot here to make sure that not the whole project is detected to be cloned.
+The main question for this study regarding type 3 clones is: ``how can we merge type 3 clones while improving the design?''.
+
+Clone instances in type 3 clones are almost always different in functionality.
+As we have to ensure equal functionality after merging the clone, we have to wrap the difference in statements between the clone instances in conditional blocks (either if-statements or switch-statements).
+We can then pass a variable as to which path should be taken through the code (either a boolean or an enumeration).
+Such a refactoring would make added statements that are contiguous less harmful for the design then added statements than added statements that are separated by statements that both clone instances have in common.
+
+We also want to argue that statements that are not common between two clone instances, should not count towards the size of the clone (and thus towards the threshold which determines whether the clone will be taken into account).
+Also, clones should not start and not end with an added statement (as that would be nonsense: such a thing could be done for any clone).
+
+As for the detection of type 3 clones, we think the easiest opportunity to detect these clones is to consider it as a postprocessing step after clone detection.
+By trying to find short gaps between clones, we can find opportunities to merge clone classes into a single type 3 clone class.
+The amount of statements that this ``short gap'' can maximally span should be dependent on a threshold value.
+
+\chapter{Code Clone Context}
+To be able to refactor code clones, it is very important to consider the context of the clone. We define the following aspects of the clone as its context:
+\begin{enumerate}
+  \item The relation of clone instances among each other (for example two clone instances in a clone class are part of the same object).
+  \item Where a clone instance occurs in the code (for instance: a method-level clone is a clone instance that is (a part of) a single method).
+  \item The contents of a clone instance (for instance: the clone instance consists of a one method declaration, a foreach statement, and two variable declarations).
+\end{enumerate}
+Everything in the context of a clone has a big impact on how it has to be refactored. For this study, we performed measurements on the context of clones in a large corpus of open source projects.
+
+\section{The corpus}
+For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}\footnote{The corpus can be downloaded from the following URL: \url{http://groups.inf.ed.ac.uk/cup/javaGithub/java_projects.tar.gz}}.
+This corpus has been assembled to contain relatively higher quality projects (by filtering by forks).
+Also, any duplicate projects were removed from this corpus.
+This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
+
+We then filtered the corpus further to make sure we are not including any test classes or generated classes.
+Many Java/Maven projects use a structure where they separate the application and its tests in the different folders (``/src/main/java'' and ``/src/test/java'' respectively).
+Because of this, we chose to only use projects from the corpus which use this structure (and had at least a ``/src/main/java'' folder).
+To limit the execution time of the script, we also decided to limit the maximum amount of source files in a single project to 1.000 (projects with more source files were not considered, which filtered only 5 extra projects out of the corpus).
+Of the 14.436 projects in the corpus over 3.848 remained, which is plenty for our purposes.
+The script to filter the corpus in included in our GitHub repository \footnote{The script we use to filter the corpus: \url{https://github.com/SimonBaars/CloneRefactor/blob/MeasurementsVersion1/src/main/java/com/simonbaars/clonerefactor/scripts/PrepareProjectsFolder.java}}.
+
+Running our clone detection script, CloneRefactor, over this corpus gives the results displayed in table \ref{table:general}.
+
+\begin{table}[H]
+  \begin{center}
+  \caption{CloneRefactor results for Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
+  \bigskip
+\begin{tabular}{|l|l|}
+\hline
+Amount of projects                                                                                      & 3,848      \\ \hline
+Amount of lines                                                                                         & 8,284,140  \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\ whitespace, comments, etc.)\end{tabular}        & 8,163,429  \\ \hline
+Amount of statements/declarations                                                                       & 6,863,725  \\ \hline
+Amount of tokens                                                                                        & 66,964,270 \\ \hline
+Amount of lines cloned                                                                                  & 1,341,094  \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of lines cloned (excluding\\ whitespace, comments, etc.)\end{tabular} & 815,799    \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of statements/declarations\\ cloned\end{tabular}                      & 747,993    \\ \hline
+Amount of tokens cloned                                                                                 & 9,800,819  \\ \hline
+Amount of clone classes                                                                                 & 34,367     \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+\section{Relations Between Clone Instances}
+When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances.
+This relation has a big impact on how a clone should be merged, in order to improve the software design in the process.
+
+\subsection{Categorizing Clone Instance Relations}
+A paper by Fontana et al \cite{fontana2015duplicated} performs measurements on 50 open source projects on the relation of clone instances to each other.
+To do this, they first define several categories for the relation between clone instances in object-oriented languages.
+These categories are as follows:
+\begin{enumerate}
+  \item \textbf{Same method}: All instances of the clone class are in the same method.
+  \item \textbf{Same class}: All instances of the clone class are in the same class.
+  \item \textbf{Superclass}: All instances of the clone class are children and parents of each other.
+  \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
+  \item \textbf{Sibling class}: All instances of the clone class have the same parent class.
+  \item \textbf{First cousin class}: All instances of the clone class have the same grandparent class.
+\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same hierarchy, but do not belong to any of the other categories.
+\item \textbf{Same external superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
+\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
+\end{enumerate}
+Please note that no of these categories allow external classes (except for ``same external superclass'').
+So if two clone instances are related through external classes but do not share a common external superclass, it will be flagged as ``unrelated''.
+The main reason for this is that it is (often) not possible to refactor to external classes.
+
+The ranking of the previous list of categories also matters as it shows the different levels in which clones were assessed.
+For instance, if two clone instances of a clone class belong to the ``same method'' category but the third belongs to the ``same class'', we will always choose the item lowest on the list.
+
+\subsection{Our measurements}
+We have recreated table 3 of Fontana et al \cite{fontana2015duplicated}, but with the following differences in our setup:
+\begin{itemize}
+  \item We consider clone classes rather than clone pairs.
+\item We use different thresholds regarding when a clone should be considered.
+\item We seek by statement/declaration rather than SLOC.
+\item We test a broader range of projects (they use a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality).
+\end{itemize}
+
+Table \ref{table:relations} contains our results regarding the relations between clone instances.
+
+\begin{table}[H]
+  \begin{center}
+  \caption{Clone relations} \label{table:relations}
+  \bigskip
+\begin{tabular}{|l|l|l|} \hline
+\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
+Unrelated          & 13,529           & 39.37               \\ \hline
+Same Class          & 8,341            & 24.28               \\ \hline
+Sibling            & 5,978            & 17.40               \\ \hline
+Same Method         & 2,456            & 7.15                \\ \hline
+External Superclass & 2,402            & 6.99                \\ \hline
+First Cousin        & 695             & 2.02                \\ \hline
+Superclass         & 489             & 1.42                \\ \hline
+Common Hierarchy    & 442             & 1.29                \\ \hline
+Ancestor           & 28              & 0.08               \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+Comparing it to the results of Fontana et al \cite{fontana2015duplicated}, we find way more unrelated clones.
+This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
+It could also be that the corpus which we use, as it has generally smaller projects, use more classes from outside the project (which are marked UNRELATED if they do not have a common external superclass).
+On the second place, we have the ``Same Class'' clones.
+On the third place come the ``Sibling'' clones.
+
+\section{Clone instance location}
+After mapping the relations between individual clones, we looked at the location of individual clone instances.
+A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning.
+In this paper, the author argues that 98\% are produced at method-level.
+However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
+We validated this claim over the corpus we use.
+For this, we chose the following categories:
+\begin{enumerate}
+  \item \textbf{Method/Constructor Level:} A clone instance that does not exceed the boundaries of a single method or constructor (optionally including the declaration of the method or constructor itself).
+  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class (like field declarations, other methods, etc.).
+  \item \textbf{Interface Level:} A clone that is (a part of) an interface.
+  \item \textbf{Enumeration Level:} A clone that is (a part of) an enumeration.
+\end{enumerate}
+
+The results for the clone instance locations are shown in table \ref{table:locations}.
+
+\begin{table}[H]
+  \begin{center}
+  \caption{Clone instance locations} \label{table:locations}
+  \bigskip
+\begin{tabular}{|l|l|l|}
+\hline
+\textbf{Location}  & \textbf{Amount}  & \textbf{Percentage} \\ \hline
+Method Level       & 19,818           & 57.68               \\ \hline
+Class Level        & 13,259           & 38.59               \\ \hline
+Constructor Level  & 1,099            & 3.20                \\ \hline
+Interface Level    & 110              & 0.32                \\ \hline
+Enum Level         & 74               & 0.22                \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+From these results, we can see that the claim of 98\% of clones being produced at method-level is nowhere near correct.
+In fact, around 58\% of the clones are produced at method-level.
+About 39\% of clones either span several methods/constructors or contain something like a field declaration.
+Another 3\% of the clones are found in constructors.
+The amount of clones found in interfaces and enumerations is very low.
+
+\section{Clone instance contents}
+Finally, we looked at the contents of individual clone instances: what kind of declarations and statements do they span. We selected the following categories to be relevant for refactoring:
+\begin{enumerate}
+  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
+  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially, optionally including its declaration.
+  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
+  \item \textbf{Only Fields:} A clone that spans only global variables.
+  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields and other things, like methods.
+  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
+  \item \textbf{Other:} Anything that does not match with above-stated categories.
+\end{enumerate}
+
+The results for these categories are displayed in table \ref{table:contents}.
+
+\begin{table}[H]
+  \begin{center}
+  \caption{Clone instance contents} \label{table:contents}
+  \bigskip
+\begin{tabular}{|l|l|l|}
+  \hline
+  \textbf{Contents}                                                        & \textbf{Amount} & \textbf{Percentage} \\ \hline
+  Partial Method                                                           & 19,264          & 56.07               \\ \hline
+  Several Methods                                                          & 9,076           & 26.41               \\ \hline
+  Includes Constructor                                                     & 1,528           & 4.45                \\ \hline
+  Includes Field                                                           & 1,149           & 3.34                \\ \hline
+  Partial Constructor                                                      & 1,098           & 3.20                \\ \hline
+  Only Fields                                                              & 565             & 1.64                \\ \hline
+  Full Method                                                              & 554             & 1.61                \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Class\\ Declaration\end{tabular}     & 445             & 1.30                \\ \hline
+  Other                                                                    & 369             & 1.07                \\ \hline
+  Full Class                                                               & 192             & 0.56                \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Constant\end{tabular}         & 52              & 0.15                \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Declaration\end{tabular}      & 47              & 0.14                \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Interface\\ Declaration\end{tabular} & 10              & 0.03                \\ \hline
+  Full Interface                                                           & 6               & 0.02                \\ \hline
+  Full Enumeration                                                         & 4               & 0.01                \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+Unsurprisingly, most clones span a part of a method.
+Just 1.6\% of the methods are cloned fully.
+More than a quarter of the clones spans over several methods, which is surprising.
+Simply extracting methods won't work in a case where a clone spans over several methods.
+About 4.5\% of clones include a constructor.
+About 3.3\% of clones include a global variable defined in a class.
+
+\chapter{Merging duplicate code through refactoring}
+Now we have mapped the contexts in which clones occur, we can start looking at refactoring opportunities.
+Regarding refactoring, we separate clones in two categories: easy and difficult refactoring opportunities.
+Easy refactoring opportunities are clones that can easily be automatically refactored.
+Examples of these opportunities are fully cloned methods or a set of fully cloned statements.
+According to the relation between the clone instances, we can propose a refactoring automatically.
+
+However, not always can a clone easily be merged.
+Sometimes a clone spans a statement partially (like a for-loop of which only it's declaration and a part of the body is cloned).
+Merging the clones can be harder in such instances.
+Also, the cloned code can contain a complex control structure, like labels, return, break, continue, etc.
+In such instances, more conditions apply to be able to conduct a refactoring, if advisable at all.
+
+The most trivial way to merge a clone is through method extraction.
+However, method extraction is not always possible.
+For instance, if a part of a subtree (in a programs' AST) is matched as a clone.
+Because of this, we chose to measure what percentage of ``Partial Method'' clones are refactorable using method extraction.
+Our results are displayed in table \ref{table:refactorability}.
+
+\begin{table}[H]
+  \begin{center}
+  \caption{Clone instance contents} \label{table:refactorability}
+  \bigskip
+\begin{tabular}{|l|l|l|}
+\hline
+\textbf{Refactorability}        & \textbf{Amount} & \textbf{Percentage} \\ \hline
+\begin{tabular}[c]{@{}l@{}}Cannot directly\\be extracted\end{tabular}    & 10,990           & 41.91               \\ \hline
+\begin{tabular}[c]{@{}l@{}}Is not a\\partial method\end{tabular} & 9,444            & 36.01               \\ \hline
+\begin{tabular}[c]{@{}l@{}}Can be\\extracted\end{tabular}                & 5,791            & 22.08               \\ \hline
+
+\end{tabular}
+\end{center}
+\end{table}
+
+From this table, we can see that approximately 22 percent of the clones can be refactored through method extraction. For the other clones, we must first build a catalog of appropriate refactorings.

### 2019-05-03 sattose/paper.tex
Wrote some stuff
Something about type 4 clones

@@
 Type 2 and type 3 clones are more disputable whether they are harmful and whether they can be merged in a way that improves the design of the code.
-In this chapter, we will redefine type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design.
+In this chapter, we will propose solution for shortcomings in type 1, type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design.
 Type-4 clones are, because of the serious challenges involved in their detection and refactoring, out of the scope for this study.

### 2019-05-03 sections/background.tex
Something about type 4 clones

@@
 
+\subsection{Type 2 clones}
 Relating this to the clone class example of \ref{fig:cloneclass}, the complete class would be flagged as a type 2 clone.
@@
 
+\subsection{Type 4 clones}
 For this thesis we have chosen not to consider type 4 clones for refactoring, because they are both hard to detect and hard to refactor (how to choose the best alternative for a certain computation could be a thesis in itself).
+A study by Kodhai et al \cite{kodhai2013method} looks into the distribution of the different types of clones in several open source systems (see table 6 of his study).
+It becomes apparent that type 4 clones exist way less in source code than all of the other types of clones.
+For instance, for the J2sdk-swing system he finds  8115 type 1 clones, 8205 type 2 clones, 11209 type 3 clones and only 30 type 4 clones.
+Because of that, we can conclude that type 4 clones are relatively less relevant to study.
 

### 2019-05-03 sections/research.tex
:full_moon_with_face:
Something about type 4 clones

@@
-\chapter{Clone Detection}
-As duplication in source code is a serious problem in many software systems, there are a lot of researches that look into code clones.
-Many tools have been proposed to detect various types of code clones.
-Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016.
-To be able to refactor detected clones, it is useful to have the ability to rewrite the AST.
-We considered a set of clone detection tools for their ability to support the refactoring process automatically.
-None of the tools we consider seemed completely fit for this purpose, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
-
-\section{CloneRefactor}
-A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection.
-For our tool, we decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio (which is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs).
-We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is useable with all modern Java versions (Java 1-12).
-We collect each statement and declaration and compare those to find duplicates.
-This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically).
-This is displayed in figure \ref{fig:clonerefactor}.
-
-\begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/CodeGraph}
-  \caption{Abstract figure of the graph representation built by CloneRefactor}
-  \label{fig:clonerefactor}
-\end{figure}
-
-\section{Thresholds}
-CloneRefactor works on basis of three thresholds for finding clones:
-\begin{enumerate}
-  \item \textbf{Number of statements/declarations:} The number of statements/declarations that should be equal/similar for it to be considered a clone.
-  \item \textbf{Number of tokens:} The number of tokens (excluding whitespace, end-of-line terminators and comments) that should be equal/similar for it to be considered a clone.
-  \item \textbf{Number of lines:} The minimum amount of lines (excluding lines that do not contain any tokens, for tokens same exclusions apply) that should be equal/similar for it to be considered a clone.
-\end{enumerate}
-Of course, if we put any of these thresholds to zero it won't be taken into account anymore, so not all thresholds have to be used at all times.
-We consider ``number of lines'' to be the least important, as it highly depends on the programmer of the codebase (and we do not want this kind of dependence!).
-On basis of manual assessment, we have determined that setting the ``number of statements/declarations'' to 6 ensures that most non-harmful clones are filtered out.
-On the downside, this also filters out some harmful antipatterns, for instance, if a cloned line has many tokens we might want to consider a clone if it spans less than 6 statements (as a cloned line with many tokens is more harmful than one with few).
-
-For the measurements in the next chapter we have chosen to apply the following thresholds:
-\begin{itemize}
-  \item \textbf{Number of statements/declarations:} 6
-  \item \textbf{Number of tokens:} 10
-  \item \textbf{Number of lines:} 6
-\end{itemize}
-
 \chapter{Redefining type 1, 2 and type 3 clones}
-In a 2007 survey by Roy et al \cite{roy2007survey} he defined four types of clones:
-
-\textbf{Type 1:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
-\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
-\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\
-\textbf{Type 4:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
-
-A higher type of clone means that it's harder to detect.
-It also makes the clone harder to refactor, as more transformations would be required.
-Higher clone types also become more disputable whether they actually indicate a harmful antipattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}).
-Type 1 clones are most often, if not always with the right thresholds, harmful.
-Type 2 and type 3 clones are more disputable whether they are harmful and whether they can be merged in a way that improves the design of the code.
-In this chapter, we will redefine type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design.
-Type-4 clones are, because of the serious challenges involved in their detection and refactoring, out of the scope for this study.
+In the background section we discussed the different types of clones, as defined by Roy et al \cite{roy2007survey}.
+However, when detecting clones by these definitions, we will detect many clones that are not immediately useful for refactoring.
+In this chapter, we will discuss the shortcoming of each of the clone types, and propose solutions for them.
 
@@
 Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type.
-This could invalidate a refactoring opportunity for such a code fragment.
-Because of that, we recommend redefining type-1 clones for refactoring.
-We propose to:
+
+This could invalidate a refactoring opportunity for such a code fragment. Because of that, we recommend redefining type-1 clones for refactoring. We propose to:
 \begin{itemize}
@@
 The amount of statements that this ``short gap'' can maximally span should be dependent on a threshold value.
+
+\chapter{Clone Detection}
+As duplication in source code is a serious problem in many software systems, there are a lot of researches that look into code clones.
+Many tools have been proposed to detect various types of code clones.
+Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016.
+We have considered a set of these tools.
+However, most of these tools have a vastly different purpose than this thesis.
+Most of the tools are focussed on efficiency and detecting all of the types of clones.
+Efficiency is lesser of a concern to us, correctness is the most important aspect.
+
+To be able to refactor detected clones, it is useful to have the ability to rewrite the AST.
+We considered a set of clone detection tools for their ability to support the refactoring process automatically.
+None of the tools we consider seemed completely fit for this purpose, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
+
+\section{CloneRefactor}
+A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection.
+For our tool, we decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio (which is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs).
+We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is useable with all modern Java versions (Java 1-12).
+We collect each statement and declaration and compare those to find duplicates.
+This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically).
+This is displayed in figure \ref{fig:clonerefactor}.
+
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/CodeGraph}
+  \caption{Abstract figure of the graph representation built by CloneRefactor}
+  \label{fig:clonerefactor}
+\end{figure}
+
+\section{Thresholds}
+CloneRefactor works on basis of three thresholds for finding clones:
+\begin{enumerate}
+  \item \textbf{Number of statements/declarations:} The number of statements/declarations that should be equal/similar for it to be considered a clone.
+  \item \textbf{Number of tokens:} The number of tokens (excluding whitespace, end-of-line terminators and comments) that should be equal/similar for it to be considered a clone.
+  \item \textbf{Number of lines:} The minimum amount of lines (excluding lines that do not contain any tokens, for tokens same exclusions apply) that should be equal/similar for it to be considered a clone.
+\end{enumerate}
+Of course, if we put any of these thresholds to zero it won't be taken into account anymore, so not all thresholds have to be used at all times.
+We consider ``number of lines'' to be the least important, as it highly depends on the programmer of the codebase (and we do not want this kind of dependence!).
+On basis of manual assessment, we have determined that setting the ``number of statements/declarations'' to 6 ensures that most non-harmful clones are filtered out.
+On the downside, this also filters out some harmful antipatterns, for instance, if a cloned line has many tokens we might want to consider a clone if it spans less than 6 statements (as a cloned line with many tokens is more harmful than one with few).
+
+For the measurements in the next chapter we have chosen to apply the following thresholds:
+\begin{itemize}
+  \item \textbf{Number of statements/declarations:} 6
+  \item \textbf{Number of tokens:} 10
+  \item \textbf{Number of lines:} 6
+\end{itemize}
 

### 2019-05-03 sattose/paper.tex
Updates from Overleaf

@@
                 Amsterdam, Netherlands \\ simon.mailadres@gmail.com
+\and 
+Ana Oprescu \\ University of Amsterdam\\
+                Amsterdam, Netherlands \\ 
+                AM.Oprescu@uva.nl
 }
@@
 \begin{abstract}
-Duplication in source code can have a major negative impact on the maintainability of source code.
+Duplication in source code can have a \todo{be more specific: what are examples of major impact?}major negative impact on the maintainability of source code.
 There are several techniques that can be used in order to merge clones, reduce duplication, improve the design of the code and potentially also reduce the total volume of a software system.
 In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages.
-We look into redefinitions for different types of clones that have been used in code duplication research for many years.
-These redefinitions are aimed towards flagging only clones that are useful for refactoring purposes.
-Measurements that have been conducted so far have indicated that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
-Approximately a fifth of the duplication can be refactored through method extraction, the other clones require other techniques to be applied.
+We look into \todo{why?} redefinitions for different types of clones that have been used in code duplication research for many years.
+\todo{turn it around: link the need for refactoring aids to redefining} These redefinitions are aimed towards flagging only clones that are useful for refactoring purposes.
+\todo{do you already refer to our measurements?} Our current measurements indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
+Approximately a fifth of the duplication can be refactored through method extraction, while other clones require other techniques to be applied.
 More measurements will be conducted to get a detailed overview of in what contexts clones occur, and what this means for the refactoring processes of these clones.

### 2019-05-03 sections/research.tex
Some stuff about type 1 clones

@@
 Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type.
+See figure \ref{fig:type1noclone} for an example of a type 1 clone that is not actually identical.
+In this figure, you can see how all objects in the supposedly cloned fragment (see the marked fragment) refer to different imports.
+Because of this, it seems like a clone, but might actually not be.
+Even the showImage method might refer to a different method (overloaded variants).
+Many (mainly textual and token-based) clone detectors will flag this as a type 1 clone.
 
-This could invalidate a refactoring opportunity for such a code fragment. Because of that, we recommend redefining type-1 clones for refactoring. We propose to:
+\begin{figure}[H]
+	\includegraphics[width=1\textwidth]{img/type-1-no-clone}
+	\caption{The marked fragment might seem like a 100\% equal clone, but actually they vary.}
+	\label{fig:type1noclone}
+\end{figure}
+
+The problem with the clone shown in \ref{fig:type1noclone} is that this could invalidate a refactoring opportunity for such a code fragment (especially when we automate it).
+Because of that, we recommend redefining type-1 clones for refactoring.
+We propose to:
 \begin{itemize}
@@
 To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
-\end{itemize}
 
@@
 \chapter{Clone Detection}
-As duplication in source code is a serious problem in many software systems, there are a lot of researches that look into code clones.
+In this chapter, we look into the current state of clone detection research.
+We held a survey in which we looked into a set of clone detection tools to determine their applicability for automated refactoring.
+We then proposed our own tool, CloneRefactor, to be able to detect our definitions of clone types (as defined in the previous chapter).
+
+\section{Clone detection survey}
+At the beginning of this study, we set out to find a clone detection tool that we could extend to apply automated refactorings.
 Many tools have been proposed to detect various types of code clones.
 Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016.
-We have considered a set of these tools.
+We have considered a set of these tools, including some more recent ones found by a Google search.
 However, most of these tools have a vastly different purpose than this thesis.
@@
 Efficiency is lesser of a concern to us, correctness is the most important aspect.
+There are a lot of clone detection tools that focus on a large amounts of
 

### 2019-05-03 sattose/paper.tex
Updates from Overleaf

@@
 \usepackage{hyperref}
+\usepackage{todonotes}
 
@@
 Duplication in source code can have a \todo{be more specific: what are examples of major impact?}major negative impact on the maintainability of source code.
-There are several techniques that can be used in order to merge clones, reduce duplication, improve the design of the code and potentially also reduce the total volume of a software system.
+There are several techniques  to merge clones, reduce duplication, improve the design of the code and potentially also reduce the total volume of a software system \todo{so?
+what is the link between these techniques and what you want to do?}.
 In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages.
 We look into \todo{why?} redefinitions for different types of clones that have been used in code duplication research for many years.
-\todo{turn it around: link the need for refactoring aids to redefining} These redefinitions are aimed towards flagging only clones that are useful for refactoring purposes.
-\todo{do you already refer to our measurements?} Our current measurements indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
+\todo{turn it around: link the need for refactoring aids to redefining} These redefinitions aim at flagging only those clones useful for refactoring purposes.
+
+Our intermediate results indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
 Approximately a fifth of the duplication can be refactored through method extraction, while other clones require other techniques to be applied.
-More measurements will be conducted to get a detailed overview of in what contexts clones occur, and what this means for the refactoring processes of these clones.
-As the desired output, we strive to construct a model that automatically applies refactorings for a large part of the detected duplication problems.
-This model will be implemented for the Java programming language.
+Similar future measurements will provide further insight into the contexts where clones occur, and what this means for the refactoring processes.
+Finally, we strive to construct a \todo{a model cannot apply something} model that automatically applies refactorings for a large part of the detected duplication problems.
+% This model will be implemented for the Java programming language.
 \end{abstract}
@@
 However, there are also refactoring opportunities that are rather trivial and repetitive to execute.
-In this research, we will look at to what extend code clones can be automatically refactored.
+In this research, we investigate the extent to which code clones can be automatically refactored.
 
@@
 Using this information we can determine in which locations clones are found the most, on basis of which the refactoring will be prioritized.
-Apart from that, we will look at different types of clones.
+Apart from that, we will look at different \todo[inline]{make sure to explain that this is a different set of different types, because splitting clones by location in code is also a way to have different types} types of clones.
 A duplicate part in a codebase does not always have to be an exact match with another part to be called a clone.
-We will look at the definitions of different types of clones and what the opportunities are to refactor duplicate parts of code if it's not an exact match.
-All of these measurements are performed on a large corpus of open source projects.
-We lay the main focus on the Java programming language as refactoring opportunities feature paradigm and programming language dependent aspects \cite{choi2011extracting}.
+We will look at the definitions of different types of clones and the opportunities to refactor duplicate parts of code albeit not an exact match.
+We conduct our research on a large corpus of open source projects.
+We lay the main focus on the Java programming language as refactoring opportunities feature paradigm and programming language dependent aspects~\cite{choi2011extracting}.
 However, most practices featured in this research will also be applicable to other object-oriented languages, like C\#.
@@
 We considered a set of clone detection tools for their ability to support the refactoring process automatically.
-None of the tools we consider seemed completely fit for this purpose, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
+\todo{didn't you have to build a matrix with features etc?
+where is it?
+this would be the place for it} None of the tools we consider seemed completely fit for this purpose, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
 
 \subsection{CloneRefactor}
+\todo{this is not background, this is already your research. Background is what others did and you use as foundation}
 A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection.
@@
 \end{enumerate}
-Of course, if we put any of these thresholds to zero it won't be taken into account anymore, so not all thresholds have to be used at all times.
+Of course, if any threshold is set to zero, it will be ignored, thus not all thresholds have to be used at all times.
 We consider ``number of lines'' to be the least important, as it highly depends on the programmer of the codebase (and we do not want this kind of dependence!).
@@
 \subsubsection{Our measurements}
-We have recreated table 3 of Fontana et al \cite{fontana2015duplicated}, but with the following differences in our setup:
+We use a similar setup to that used in the study of \todo{put here the concise description of the experiment}  (Table~3 in Fontana et al) \cite{fontana2015duplicated}, but with the following differences in our setup:
 \begin{itemize}
@@
 
-Table \ref{table:relations} contains our results regarding the relations between clone instances.
+Table~\ref{table:relations} contains our results regarding the relations between clone instances.
 

### 2019-05-03 sattose/paper.tex
Added the todo package
Did something with Ana's feedback in the abstract

@@
 \begin{abstract}
-Duplication in source code can have a \todo{be more specific: what are examples of major impact?}major negative impact on the maintainability of source code.
-There are several techniques  to merge clones, reduce duplication, improve the design of the code and potentially also reduce the total volume of a software system \todo{so?
-what is the link between these techniques and what you want to do?}.
+Duplication in source code can have a major negative impact on the maintainability of source code, as creates explicit dependencies between fragments of code.
+Typically between 10 and 20 percent of projects are cloned.
 In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages.
-We look into \todo{why?} redefinitions for different types of clones that have been used in code duplication research for many years.
-\todo{turn it around: link the need for refactoring aids to redefining} These redefinitions aim at flagging only those clones useful for refactoring purposes.
+To do this, we propose a method to be able to detect clones that are suitable for refactoring.
+This method focuses on taking into account the scope and coupling between expressions in code, to be sure our refactoring improves the design and does not leave side effects after it is applied.
 
@@
 Similar future measurements will provide further insight into the contexts where clones occur, and what this means for the refactoring processes.
-Finally, we strive to construct a \todo{a model cannot apply something} model that automatically applies refactorings for a large part of the detected duplication problems.
-% This model will be implemented for the Java programming language.
+Finally, we strive to construct a tool that automatically applies refactorings for a large part of the detected duplication problems.
 \end{abstract}

### 2019-05-05 sections/research.tex
Clone detection

@@
 \end{figure}
+
+\begin{wrapfigure}{r}{5.5cm}
+\caption{A wrapped figure going nicely inside the text.}\label{wrap-fig:1}
+\includegraphics[width=5.5cm]{img/type-1-not-cloned}
+\end{wrapfigure}
 
@@
 In this chapter, we look into the current state of clone detection research.
-We held a survey in which we looked into a set of clone detection tools to determine their applicability for automated refactoring.
+We held a small survey in which we looked into a set of clone detection tools to determine their applicability for automated refactoring.
 We then proposed our own tool, CloneRefactor, to be able to detect our definitions of clone types (as defined in the previous chapter).
@@
 Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016.
-We have considered a set of these tools, including some more recent ones found by a Google search.
+We have considered a set of these tools, including some additional (more recent) ones.
 However, most of these tools have a vastly different purpose than this thesis.
-Most of the tools are focussed on efficiency and detecting all of the types of clones.
+Most of the tools are focused on efficiency and detecting all of the types of clones.
 Efficiency is lesser of a concern to us, correctness is the most important aspect.
-There are a lot of clone detection tools that focus on a large amounts of
 
+\subsection{Text- and Token based clone detection}
+Clones
+
+\subsection{Big scale clone detection}
+There are a lot of clone detection tools that focus on detecting large amounts of clones quickly \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval, kamiya2002ccfinder, livieri2007very}
+
+\subsection{Our criteria}
 To be able to refactor detected clones, it is useful to have the ability to rewrite the AST.

### 2019-05-06 sattose/paper.tex
Updates from Overleaf

@@
 \subsection{CloneRefactor}
-\todo{this is not background, this is already your research. Background is what others did and you use as foundation}
 A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection.
-For our tool, we decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio (which is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs).
+For our tool, we decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio \footnote{Scorpio is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs.}.
 We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is useable with all modern Java versions (Java 1-12).
@@
 
-\subsection{Thresholds}
+\subsubsection{Detection of clone classes}\label{chap:cloneclasses}
+For CloneRefactor, we have chosen to focus on the detection of clone classes rather than clone pairs.
+We did this because clone pairs don’t provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}.
+On the other hand, clone classes are harder to manage, but they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered.
+Another issue involves clone grouping by pairs: single clone reference amount increases according to binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), of which a heavy information redundancy follows \cite{fontana2012duplicated}.
+
+\subsubsection{Thresholds}\label{chap:thresholds}
 CloneRefactor works on basis of three thresholds for finding clones:
@@
 
-\subsection{The corpus}
+\subsection{The corpus}\label{chap:corpus}
 For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}\footnote{The corpus can be downloaded from the following URL: \url{http://groups.inf.ed.ac.uk/cup/javaGithub/java_projects.tar.gz}}.
@@
 \subsubsection{Our measurements}
-We use a similar setup to that used in the study of \todo{put here the concise description of the experiment}  (Table~3 in Fontana et al) \cite{fontana2015duplicated}, but with the following differences in our setup:
+We use a similar setup to that used in the study of Table~3 in Fontana et al \cite{fontana2015duplicated}.
+Fontana et al measure clones using their own tool called DCRA.
+This tool detects clone pairs in Java-based source code.
+It operates on a single threshold: the minimum number of lines that a clone should span.
+Our measurements were conducted using CloneRefactor, because of which the setup for our measurements differs as follows from Fontana et al:
 \begin{itemize}
-  \item We consider clone classes rather than clone pairs.
+  \item We consider clone classes rather than clone pairs. The rationale for this is given in section \ref{chap:cloneclasses}.
 \item We use different thresholds regarding when a clone should be considered.
-\item We seek by statement/declaration rather than SLOC.
-\item We test a broader range of projects (they use a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality).
+Fontana et al seek clones that span a minimum of 7 source lines of code (SLOC).
+We seek clones with a minimum size of 6 statements/declarations.
+This is further explained in section \ref{chap:thresholds}.
+\item We seek by statement/declaration rather than SLOC. This makes our analysis depend less on the coding style (in terms of newline usage) of the author of the software project.
+\item We test a broader range of projects.
+Fontana et al use a set of 50 relatively large projects.
+We use the corpus as explained in \ref{chap:corpus}, which contains a diverse set of projects (diverse both in volume and code quality).
 \end{itemize}

### 2019-05-06 sattose/paper.tex
Updates from Overleaf

@@
 Using this information we can determine in which locations clones are found the most, on basis of which the refactoring will be prioritized.
-Apart from that, we will look at different \todo[inline]{make sure to explain that this is a different set of different types, because splitting clones by location in code is also a way to have different types} types of clones.
 A duplicate part in a codebase does not always have to be an exact match with another part to be called a clone.
@@
 A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection.
-For our tool, we decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio \footnote{Scorpio is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs.}.
+For our tool, we decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing}.
+However, instead of building a dependency graph, we build a similarity graph of statements linking to similar statements.
 We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is useable with all modern Java versions (Java 1-12).

### 2019-05-06 sattose/paper.tex
Updates from Overleaf

@@
 \usepackage{todonotes}
+\usepackage{tikz}
+\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
 
@@
 \begin{abstract}
-Duplication in source code can have a major negative impact on the maintainability of source code, as creates explicit dependencies between fragments of code.
-Typically between 10 and 20 percent of projects are cloned.
+Duplication in source code can have a major negative impact on the maintainability of source code, as it creates explicit dependencies between fragments of code.
+These explicit dependencies have been shown to often cause bugs, as a modification in one fragment might have consequences for the correctness of another.
 In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages.
@@
 
+\subsubsection{Advantages of clone classes over clone pairs}\label{chap:cloneclasses}
+Regarding clone detection, there is a lot of variability in literature whether clone pairs or clone classes should be detected.
+In this study we focus on clone classes, because of the advantages for refactoring.
+Clone pairs don’t provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}.
+Even though clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered.
+Another issue involves clone grouping by pairs: single clone reference amount increases according to binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), of which a heavy information redundancy follows \cite{fontana2012duplicated}.
+
 \section{Clone Detection}
@@
 
+\subsection{Survey on Clone Detection Tools}
+We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities.
+We chose a set of tools that are open source and can analyze either Java or Python.
+Then we chose four criteria by which we considered these tools:
+\begin{enumerate}
+    \item \textbf{Should find clones in any context.} We want to perform an analysis on a set of projects.
+In this analysis we want to be able to get a full overview of cloning in the set of projects.
+Some tools only find clones in specific contexts, like only method-level clones.
+Because of that, we want to use a clone detection tool that is able to find clones in any context.
+\item \textbf{Should detect clone classes in a number of example projects.} We have created a number of test projects\footnote{Our test projects to assess the validity of clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} that we used to assess the validity of clone detection tools.
+On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
+\item \textbf{Considers dependency graphs to be sure that this clone can be merged.} When detecting clones for refactoring purposes, it is important that clone instances are actually equal.
+Sometimes, to verify actual equality (not just textual equality), it is required to consider resolved symbols (this is described more elaborately in section \ref{chap:type1clones}).
+Because of this, we want to use a clone detection tool that can analyze such structures.
+\item \textbf{Makes it possible to configure the way in which clones are detected (as in what to exclude from the detection) in a relatively straightforward way.} We want to be able to exclude expressions/statements from matching (more about our rationale in section \ref{chap:clonetypes}).
+To be able to do this, the tool needs to be able to recognize the meaning of certain tokens.
+\end{enumerate}
+
+The results of our survey is displayed in table \ref{table:dettools}.
+
+\begin{table}[H]
+ \begin{center}
+  \caption{Our survey on clone detection tools.} \label{table:dettools}
+  \bigskip
+\begin{tabular}{|l|l|l|l|l|l|}
+\hline
+\textbf{Clone Detection Tool}                                                                                                                           & \textbf{Short Description}                                                          & \textbf{(1)}                  & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
+Siamese \cite{ragkhitwetsagul2019siamese}                                                                                                              & \begin{tabular}[c]{@{}l@{}}ANTRL based\\ large scale clone\\ detection\end{tabular} &  &             &             & \checkmark            \\ \hline
+NiCAD \cite{roy2008nicad, cordy2011nicad} \footnote{This clone detection tool has also been used by Fontana et al \cite{fontana2012duplicated}}      & \begin{tabular}[c]{@{}l@{}}Duplicated code\\ refactoring advisor\end{tabular}       & ?
+& ?
+& ✗            & ✓            \\ \hline
+CPD \cite{roy2009comparison}\footnote{CPD is a Clone Detection tool that is part of PMD.
+PMD is a widely used tool for static code analysis in Java.} & \begin{tabular}[c]{@{}l@{}}Widely used clone\\ detection tool\end{tabular}          & ✓                             & ✓            & ✗            & ✗            \\ \hline
+\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ CCFinderX\\ D-CCFinder \cite{livieri2007very}\end{tabular}                            & \begin{tabular}[c]{@{}l@{}}Widely used\\ clone detection\\ framework\end{tabular}   & ✓                             & ✓            & ✗            & ✗            \\ \hline
+CCFinderSW \cite{semura2017ccfindersw}                                                                                                                 & \begin{tabular}[c]{@{}l@{}}ANTRL based\\ clone detection\end{tabular}               & ✓                             & ✗            & ✗            & ✓            \\ \hline
+\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular}                                         & \begin{tabular}[c]{@{}l@{}}These tools detect\\ all types of clones\end{tabular}    & ✓                             & ✗            & ✗            & ✓            \\ \hline
+BigCloneEval \cite{svajlenko2016bigcloneeval}                                                                                                          & \begin{tabular}[c]{@{}l@{}}Large-scale clone\\ detection\end{tabular}               & ✓                             & ✓            & ✗            & ✗            \\ \hline
+Deckard \cite{jiang2007deckard}                                                                                                                        & \begin{tabular}[c]{@{}l@{}}ANTRL Parse Tree\\ based Clone Detector\end{tabular}     & ✓                             & ✗            & ✓            & ✗            \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
 \subsection{CloneRefactor}
@@
 However, instead of building a dependency graph, we build a similarity graph of statements linking to similar statements.
-We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is useable with all modern Java versions (Java 1-12).
+We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is compatible with all modern Java versions (Java 1-12).
 We collect each statement and declaration and compare those to find duplicates.
@@
 
-\subsubsection{Detection of clone classes}\label{chap:cloneclasses}
-For CloneRefactor, we have chosen to focus on the detection of clone classes rather than clone pairs.
-We did this because clone pairs don’t provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}.
-On the other hand, clone classes are harder to manage, but they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered.
-Another issue involves clone grouping by pairs: single clone reference amount increases according to binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), of which a heavy information redundancy follows \cite{fontana2012duplicated}.
+On basis of this graph we detect clone classes. We challenge completed clone classes against the thresholds that are being used, and remove the clone classes that do not adhere to the thresholds.
 
@@
 
-\section{Redefining type 1, 2 and type 3 clones}
+\section{Redefining type 1, 2 and type 3 clones}\label{chap:clonetypes}
 In a 2007 survey by Roy et al \cite{roy2007survey} he defined four types of clones:
@@
 
-\subsection{Type 1 clones}
+\subsection{Type 1 clones} \label{chap:type1clones}
 Type 1 clones are identical clone fragments except for variations in whitespace and comments.

### 2019-05-06 sattose/paper.tex
Working on the table

@@
 Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016.
-To be able to refactor detected clones, it is useful to have the ability to rewrite the AST.
-We considered a set of clone detection tools for their ability to support the refactoring process automatically.
-\todo{didn't you have to build a matrix with features etc?
-where is it?
-this would be the place for it} None of the tools we consider seemed completely fit for this purpose, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
 
@@
 
-The results of our survey is displayed in table \ref{table:dettools}.
+The results of our survey are displayed in table \ref{table:dettools}.
 
@@
 \hline
-\textbf{Clone Detection Tool}                                                                                                                           & \textbf{Short Description}                                                          & \textbf{(1)}                  & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
-Siamese \cite{ragkhitwetsagul2019siamese}                                                                                                              & \begin{tabular}[c]{@{}l@{}}ANTRL based\\ large scale clone\\ detection\end{tabular} &  &             &             & \checkmark            \\ \hline
-NiCAD \cite{roy2008nicad, cordy2011nicad} \footnote{This clone detection tool has also been used by Fontana et al \cite{fontana2012duplicated}}      & \begin{tabular}[c]{@{}l@{}}Duplicated code\\ refactoring advisor\end{tabular}       & ?
-& ?
-& ✗            & ✓            \\ \hline
-CPD \cite{roy2009comparison}\footnote{CPD is a Clone Detection tool that is part of PMD.
-PMD is a widely used tool for static code analysis in Java.} & \begin{tabular}[c]{@{}l@{}}Widely used clone\\ detection tool\end{tabular}          & ✓                             & ✓            & ✗            & ✗            \\ \hline
-\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ CCFinderX\\ D-CCFinder \cite{livieri2007very}\end{tabular}                            & \begin{tabular}[c]{@{}l@{}}Widely used\\ clone detection\\ framework\end{tabular}   & ✓                             & ✓            & ✗            & ✗            \\ \hline
-CCFinderSW \cite{semura2017ccfindersw}                                                                                                                 & \begin{tabular}[c]{@{}l@{}}ANTRL based\\ clone detection\end{tabular}               & ✓                             & ✗            & ✗            & ✓            \\ \hline
-\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular}                                         & \begin{tabular}[c]{@{}l@{}}These tools detect\\ all types of clones\end{tabular}    & ✓                             & ✗            & ✗            & ✓            \\ \hline
-BigCloneEval \cite{svajlenko2016bigcloneeval}                                                                                                          & \begin{tabular}[c]{@{}l@{}}Large-scale clone\\ detection\end{tabular}               & ✓                             & ✓            & ✗            & ✗            \\ \hline
-Deckard \cite{jiang2007deckard}                                                                                                                        & \begin{tabular}[c]{@{}l@{}}ANTRL Parse Tree\\ based Clone Detector\end{tabular}     & ✓                             & ✗            & ✓            & ✗            \\ \hline
+\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
+Siamese \cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
+NiCAD \cite{roy2008nicad, cordy2011nicad} \footnote{}           & \checkmark                             & \checkmark            &             &             \\ \hline
+CPD \cite{roy2009comparison}\footnote{} & \checkmark & \checkmark            &             &             \\ \hline
+\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ CCFinderX\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
+CCFinderSW \cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
+\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
+BigCloneEval \cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
+Deckard \cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
 \end{tabular}
@@
 \end{table}
+
+None of the tools we considered implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
+
+\footnotetext[3]{This clone detection tool has also been used by Fontana et al \cite{fontana2012duplicated}}
+
+\footnotetext{\label{note1}CPD is a Clone Detection tool that is part of PMD. PMD is a widely used tool for static code analysis in Java.}
 
@@
   \item \textbf{Compare the equality of the fully qualified method signature for method references.} This way we can validate whether two method references, like method calls, are actually equal.
-In the method signature, not only the fully qualified identifier of the method should be considered, but also of the type of all its arguments.
+In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments.
 This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).

### 2019-05-06 sattose/paper.tex
Updates from Overleaf

@@
 \subsubsection{Our measurements}
-We use a similar setup to that used in the study of Table~3 in Fontana et al \cite{fontana2015duplicated}.
-Fontana et al measure clones using their own tool called DCRA.
+We use a similar setup to that used in the study of Table~3 in Fontana et al.
+\cite{fontana2015duplicated}.
+Fontana et al.
+measure clones using their own tool called DCRA.
 This tool detects clone pairs in Java-based source code.
 It operates on a single threshold: the minimum number of lines that a clone should span.
-Our measurements were conducted using CloneRefactor, because of which the setup for our measurements differs as follows from Fontana et al:
+Our measurements were conducted using CloneRefactor, because of which the setup for our measurements differs as follows from Fontana et al.:
 \begin{itemize}
@@
 \item We use different thresholds regarding when a clone should be considered.
-Fontana et al seek clones that span a minimum of 7 source lines of code (SLOC).
+Fontana et al.
+seek clones that span a minimum of 7 source lines of code (SLOC).
 We seek clones with a minimum size of 6 statements/declarations.
@@
 \item We test a broader range of projects.
-Fontana et al use a set of 50 relatively large projects.
+Fontana et al.
+use a set of 50 relatively large projects.
 We use the corpus as explained in \ref{chap:corpus}, which contains a diverse set of projects (diverse both in volume and code quality).
@@
 This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
-It could also be that the corpus which we use, as it has generally smaller projects, use more classes from outside the project (which are marked UNRELATED if they do not have a common external superclass).
+It could also be that the corpus which we use, as it has generally smaller projects, uses more classes from outside the project (which are marked UNRELATED if they do not have a common external superclass).
 On the second place, we have the ``Same Class'' clones.

### 2019-05-06 sattose/paper.tex
Sander

@@
 These explicit dependencies have been shown to often cause bugs, as a modification in one fragment might have consequences for the correctness of another.
-In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages.
-To do this, we propose a method to be able to detect clones that are suitable for refactoring.
-This method focuses on taking into account the scope and coupling between expressions in code, to be sure our refactoring improves the design and does not leave side effects after it is applied.
+In this study, we look into the opportunities to automatically refactor these duplication problems for object-oriented programming languages.
+To do this, we propose a method to detect clones that are suitable for refactoring.
+This method focuses on taking into account the context and scope of clones, to be sure our refactoring improves the design and does not leave side effects after it is applied.
 
 Our intermediate results indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
-Approximately a fifth of the duplication can be refactored through method extraction, while other clones require other techniques to be applied.
-Similar future measurements will provide further insight into the contexts where clones occur, and what this means for the refactoring processes.
+Approximately a fifth of the duplication can be refactored through method extraction, while other clones require other refactoring techniques.
+Similar future measurements will provide further insight into the contexts where clones occur and how this affects the automated refactoring process.
 Finally, we strive to construct a tool that automatically applies refactorings for a large part of the detected duplication problems.
@@
 Code clones can be found anywhere in a codebase.
-The location of a clone in the code has an impact on how it has to be refactored.
+The location of a clone in the code has an impact on how it can be refactored.
 Because of this, we will first look at where clones can be found.
 Using this information we can determine in which locations clones are found the most, on basis of which the refactoring will be prioritized.
-A duplicate part in a codebase does not always have to be an exact match with another part to be called a clone.
+A duplicate part in a codebase does not always have to be an exact match with another part to be considered a clone.
 We will look at the definitions of different types of clones and the opportunities to refactor duplicate parts of code albeit not an exact match.
 We conduct our research on a large corpus of open source projects.
-We lay the main focus on the Java programming language as refactoring opportunities feature paradigm and programming language dependent aspects~\cite{choi2011extracting}.
+We put the main focus on the Java programming language as refactoring opportunities feature paradigm and programming language dependent aspects~\cite{choi2011extracting}.
 However, most practices featured in this research will also be applicable to other object-oriented languages, like C\#.
@@
 Also, these publications/tools are limited to suggesting refactoring opportunities for clones found, rather than actually applying refactorings where suitable.
-Finally, all published approaches have limitations, for instance, false positives when detecting clones \cite{chen2018clone} or being limited to clone pairs \cite{higo2008metric}.
+Finally, all published approaches have limitations, such as false positives in their clone detection \cite{chen2018clone} or being limited to clone pairs \cite{higo2008metric}.
 
@@
 \section{Redefining type 1, 2 and type 3 clones}\label{chap:clonetypes}
-In a 2007 survey by Roy et al \cite{roy2007survey} he defined four types of clones:
-
+In a 2007 survey by Roy et al \cite{roy2007survey} he defined four types of clones:\\
 \textbf{Type 1:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
@@
 Type 2 and type 3 clones are more disputable whether they are harmful and whether they can be merged in a way that improves the design of the code.
-In this chapter, we will propose solution for shortcomings in type 1, type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design.
+In this chapter, we will propose solutions for shortcomings in type 1, type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design.
 Type-4 clones are, because of the serious challenges involved in their detection and refactoring, out of the scope for this study.
@@
 Type 1 clones are identical clone fragments except for variations in whitespace and comments.
-However, when two clone fragments are textually identical, does not yet indicate that they are actually identical.
+However, when two clone fragments are textually identical, it does not yet indicate that they are actually identical.
 Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type.
@@
 \begin{itemize}
-  \item \textbf{Compare the equality of the fully qualified method signature for method references.} This way we can validate whether two method references, like method calls, are actually equal.
+  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (eg \texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object).
+This way we can validate whether two method references, like method calls, are actually equal.
 In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments.
@@
 We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables.
-For instance, if we call a method like this: \textit{``myMethod(var1, var2)''}, or call this method like this: \textit{``myMethod(var1, var1)''}.
+For instance, if we call a method like this: \texttt{myMethod(var1, var2)}, or call this method like this: \texttt{myMethod(var1, var1)}.
 Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.

### 2019-05-06 sattose/paper.tex
Moving stuff around

@@
 
+For this research, we strive to improve upon the current state-of-the-art in clone refactoring \cite{fontana2015duplicated, alwaqfi2017refactoring} by building a clone refactoring tool that applies refactorings to a large percentage of clones found.
+The design decisions for this tool will be made on basis of data gathered from a large corpus of software systems.
+This way we strive to make the problem of duplication in source code easier to deal with.
+
 \subsection{Background}
@@
 
+\subsubsection{Current clone refactoring tools}
 A tool called DCRA (Duplicated Code Refactoring Advisor) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated}.
@@
 
-For this research, we strive to improve upon the current state-of-the-art in clone refactoring by building a clone refactoring tool that applies refactorings to a large percentage of clones found.
-The design decisions for this tool will be made on basis of data gathered from a large corpus of software systems.
-This way we strive to make the problem of duplication in source code easier to deal with.
-
 \subsubsection{Advantages of clone classes over clone pairs}\label{chap:cloneclasses}
@@
 Another issue involves clone grouping by pairs: single clone reference amount increases according to binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), of which a heavy information redundancy follows \cite{fontana2012duplicated}.
+
+\subsubsection{Clone types}
+In a 2007 survey by Roy et al \cite{roy2007survey} he defines four types of clones:\\
+\textbf{Type 1:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
+\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
+\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\
+\textbf{Type 4:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
+
+A higher type of clone means that it's harder to detect.
+It also makes the clone harder to refactor, as more transformations would be required.
+Higher clone types also become more disputable whether they actually indicate a harmful antipattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}).
 

### 2019-05-06 sattose/paper.tex
Fixing things

@@
 As code clones are seen as one of the most harmful types of technical debt, they have been studied very extensively.
-A survey by Roy et al \cite{roy2007survey} states definitions for various important concepts in code clone research.
+A survey by Roy et al.
+\cite{roy2007survey} states definitions for various important concepts in code clone research.
 In this survey, he mentions the concept ``clone pair'', which is \textit{a set of two code portions/fragments which are identical or similar to each other}.
@@
 Another tool called Aries \cite{higo2004aries, higo2008metric} focuses on the detection of refactoring oriented clones.
-In this paper, the authors describe a few variables by which a clone can be assessed for refactoring suitability.
-This tool looks however only at the possibility to merge clones, rather than whether clones should be merged.
+In this paper, the authors describe a few criteria by which a clone can be assessed to determine its suitability for refactoring.
+This tool looks however only at the possibility to merge clones, rather than whether clones should be merged (if they are actually harmful).
 Also, this tool only suggests refactorings and does not apply them.
@@
 \subsubsection{Clone types}
-In a 2007 survey by Roy et al \cite{roy2007survey} he defines four types of clones:\\
+In a 2007 survey by Roy et al. \cite{roy2007survey} he defines four types of clones:\\
 \textbf{Type 1:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
@@
 
-\footnotetext[3]{This clone detection tool has also been used by Fontana et al \cite{fontana2012duplicated}}
+\footnotetext[3]{This clone detection tool has also been used by Fontana et al. \cite{fontana2012duplicated}}
 
@@
 On basis of manual assessment, we have determined that setting the ``number of statements/declarations'' to 6 ensures that most non-harmful clones are filtered out.
-On the downside, this also filters out some harmful antipatterns, for instance, if a cloned line has many tokens we might want to consider a clone if it spans less than 6 statements (as a cloned line with many tokens is more harmful than one with few).
+On the downside, this also filters out some harmful antipatterns.
+For instance, if a cloned statement has many tokens we might want to consider it a clone even if it spans less than 6 statements (as a cloned line with many tokens is more harmful than one with few).
 
@@
 \section{Redefining type 1, 2 and type 3 clones}\label{chap:clonetypes}
-In a 2007 survey by Roy et al \cite{roy2007survey} he defined four types of clones:\\
-\textbf{Type 1:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
-\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
-\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\
-\textbf{Type 4:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
-
-A higher type of clone means that it's harder to detect.
-It also makes the clone harder to refactor, as more transformations would be required.
-Higher clone types also become more disputable whether they actually indicate a harmful antipattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}).
-Type 1 clones are most often, if not always with the right thresholds, harmful.
-Type 2 and type 3 clones are more disputable whether they are harmful and whether they can be merged in a way that improves the design of the code.
 In this chapter, we will propose solutions for shortcomings in type 1, type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design.
@@
 \begin{itemize}
-  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (eg \texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object).
+  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (e.g.
+\texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object).
 This way we can validate whether two method references, like method calls, are actually equal.
@@
 Type 3 clones are even more permissive than type 2 clones, allowing added and removed statements.
-Thresholds matter a lot here to make sure that not the whole project is detected to be cloned.
+Thresholds matter a lot here to make sure that not the whole project is detected as a clone of itself.
 The main question for this study regarding type 3 clones is: ``how can we merge type 3 clones while improving the design?''.
@@
 We can then pass a variable as to which path should be taken through the code (either a boolean or an enumeration).
-Such a refactoring would make added statements that are contiguous less harmful for the design then added statements than added statements that are separated by statements that both clone instances have in common.
+Such a refactoring would make added statements that are contiguous less harmful for the design than added statements that are separated by statements that both clone instances have in common.
 
@@
 \begin{enumerate}
-  \item The relation of clone instances among each other (for example two clone instances in a clone class are part of the same object).
-  \item Where a clone instance occurs in the code (for instance: a method-level clone is a clone instance that is (a part of) a single method).
-  \item The contents of a clone instance (for instance: the clone instance consists of a one method declaration, a foreach statement, and two variable declarations).
+  \item The relation of clone instances among each other through inheritance (for example: a clone instance resides in a superclass of another clone instance in the same clone class).
+  \item Where a clone instance occurs in the code (for example: a method-level clone is a clone instance that is in a method).
+  \item The contents of a clone instance (for example: the clone instance spans several methods).
 \end{enumerate}
@@
 For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}\footnote{The corpus can be downloaded from the following URL: \url{http://groups.inf.ed.ac.uk/cup/javaGithub/java_projects.tar.gz}}.
-This corpus has been assembled to contain relatively higher quality projects (by filtering by forks).
+This corpus has been assembled to contain relatively higher quality projects.
 Also, any duplicate projects were removed from this corpus.
@@
 
-We then filtered the corpus further to make sure we are not including any test classes or generated classes.
+We filtered the corpus further to make sure we are not including any test classes or generated classes.
 Many Java/Maven projects use a structure where they separate the application and its tests in the different folders (``/src/main/java'' and ``/src/test/java'' respectively).
@@
 \subsubsection{Categorizing Clone Instance Relations}
-A paper by Fontana et al \cite{fontana2015duplicated} performs measurements on 50 open source projects on the relation of clone instances to each other.
+A paper by Fontana et al.
+\cite{fontana2015duplicated} describes measurements on 50 open source projects on the relation of clone instances to each other.
 To do this, they first define several categories for the relation between clone instances in object-oriented languages.
@@
 \end{enumerate}
-Please note that no of these categories allow external classes (except for ``same external superclass'').
+Please note that none of these categories allow external classes (except for ``same external superclass'').
 So if two clone instances are related through external classes but do not share a common external superclass, it will be flagged as ``unrelated''.
@@
 \subsubsection{Our measurements}
-We use a similar setup to that used in the study of Table~3 in Fontana et al.
-\cite{fontana2015duplicated}.
+We use a similar setup to that used in the study by Fontana et al.
+(Table~3 of Fontana et al.
+\cite{fontana2015duplicated}).
 Fontana et al.
@@
 This is further explained in section \ref{chap:thresholds}.
-\item We seek by statement/declaration rather than SLOC. This makes our analysis depend less on the coding style (in terms of newline usage) of the author of the software project.
+\item We seek duplicates by statement/declaration rather than SLOC. This makes our analysis depend less on the coding style (in terms of newline usage) of the author of the software project.
 \item We test a broader range of projects.
@@
 
-Comparing it to the results of Fontana et al \cite{fontana2015duplicated}, we find way more unrelated clones.
+Comparing it to the results of Fontana et al.
+\cite{fontana2015duplicated}, we find way more unrelated clones.
 This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
-It could also be that the corpus which we use, as it has generally smaller projects, uses more classes from outside the project (which are marked UNRELATED if they do not have a common external superclass).
+It could also be that the corpus which we use, as it has generally smaller projects, uses more classes from outside the project (which are marked ``Unrelated'' if they do not have a common external superclass).
 On the second place, we have the ``Same Class'' clones.
@@
 After mapping the relations between individual clones, we looked at the location of individual clone instances.
-A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning.
+A paper by Lozano et al.
+\cite{lozano2007evaluating} discusses the harmfulness of cloning.
 In this paper, the author argues that 98\% are produced at method-level.
@@
 
-From these results, we can see that the claim of 98\% of clones being produced at method-level is nowhere near correct.
-In fact, around 58\% of the clones are produced at method-level.
+Our results indicate that around 58\% of the clones are produced at method-level.
 About 39\% of clones either span several methods/constructors or contain something like a field declaration.
@@
 In such a case, merging such clones might turn out to change the functionality of the program.
-We have noted this down as a next step, working on basis of a callgraph instead of just the AST.
+Solving this problem is one of our next steps in this research.
 
 \section{Conclusion and next steps}
-The study that we have conducted so far analyzes the context of different kinds of clones and prioritizes their refactoring.
+In the research we have conducted so far we have made three novel contributions:
+\begin{itemize}
+    \item We proposed a method in which we can detect clones that can/should be refactored.
+    \item We mapped the context of clones in a large corpus of open source systems.
+    \item We mapped the opportunities to perform method extraction on clones in a large corpus of open source systems.
+\end{itemize}
+
+We have into existing definitions for different types of clones \cite{roy2007survey} and proposed solutions for problems that these types have with regards to automated refactoring.
+We propose that fully qualified identifiers of method call signatures and type references should be considered instead of their plain text representation.
+Furthermore, we should define thresholds for variability in variables, literals and method calls, in order to limit the number of parameters that the merged unit shall have.
+
+The research that we have conducted so far analyzes the context of different kinds of clones and prioritizes their refactoring.
 Firstly, we looked at the inheritance relation of clone instances in a clone class.
-We have found that most clone classes are unrelated, which means that they have at least one instance that has no relation with the other instances.
-There were also a lot of clone classes of which all instances are in the same class.
-At the third place are clone instances that are siblings of each other (share the same superclass).
+We have found that more than a third of all clone classes are flagged unrelated, which means that they have at least one instance that has no relation through inheritance with the other instances.
+For about a fourth of the clone classes all of its instances are in the same class.
+For about a sixth of the clone classes have clone instances that are siblings of each other (share the same superclass).
 
@@
 We defined ``class level clones'' as clones that exceed the boundaries of a single method or contain something else in the class (like field declarations, other methods, etc.).
-
 Thirdly, we looked at the contents of clone instances.
@@
 About 26 percent of clones span over several methods.
-We also looked into the refactorability of clones that span part of a method.
+
+We also looked into the refactorability of clones that span a part of a method.
 Over 22 percent of the clones can directly be refactored by extracting them to a new method (and calling the method at all usages using their relation).
@@
 \subsection{Next steps}
-As a first next step, we will integrate our redefinition of type-2 clones into CloneRefactor.
-This way, we can run all scripts that we used for all measurements for our redefinition of type-2 clones.
-We are curious to see how it compares with the results we had for the type-1 clones so far.
+The next step will be to integrate our redefinitions of type 1, 2 and 3 clones into CloneRefactor.
+This way, we can run all scripts that we used for our measurements for these novel clone definitions.
+We are curious to see how it compares with the results we had so far.
 

### 2019-05-06 sattose/paper.tex
Sander and Xander

@@
 
-\section{Redefining type 1, 2 and type 3 clones}\label{chap:clonetypes}
-In this chapter, we will propose solutions for shortcomings in type 1, type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design.
+\section{Addressing and solving problems with clone type definitions}\label{chap:clonetypes}
+In this chapter, we will propose solutions for shortcomings in type 1, type 2 and type 3 clones \cite{roy2007survey} to increase the chance that we can merge the clone while improving the design.
 Type-4 clones are, because of the serious challenges involved in their detection and refactoring, out of the scope for this study.
@@
 This could invalidate a refactoring opportunity for such a code fragment.
-Because of that, we recommend redefining type-1 clones for refactoring.
-We propose to:
+Because of that, we propose to:
 \begin{itemize}
@@
 
-Because of that, for this research, we have looked into a redefinition of type 2 clones to be able to detect such clones that can and should be merged.
+Because of that, for this research, we have looked solving these problems with type 2 clones to be able to detect such clones that can and should be merged.
 Our definition ensures functional similarity by applying the following changes to type 2 clones:
@@
 Merging the clones can be harder in such instances.
-Also, the cloned code can contain a complex control structure, like labels, return, break, continue, etc.
-In such instances, more conditions apply to be able to conduct a refactoring, if advisable at all.
+Also, the cloned code can contain statements like labels, return, break, continue, etc.
+In such instances, more conditions may apply to be able to conduct a refactoring, if advisable at all.
 
@@
 \subsection{Next steps}
-The next step will be to integrate our redefinitions of type 1, 2 and 3 clones into CloneRefactor.
+The next step will be to integrate our solutions for the problems with the clone types, as explained in section \ref{chap:clonetypes}, into our CloneRefactor tool.
 This way, we can run all scripts that we used for our measurements for these novel clone definitions.
 We are curious to see how it compares with the results we had so far.
-
-As we want to refactor duplicates fully automated, it is very important that both code fragments have exactly the same functionality.
-Because of this, we want to look into building a SymbolTable of projects we scan and their dependencies.
-This allows us to further assess the equality of code fragments.
-Currently, we compare fragments, as most clone detection tools do, on basis of static analysis of only the target project.
-However, because of this, we omit valuable information like fully qualified identifiers for types.
-By parsing not only a project, but also its dependencies, we can better assess whether two code fragments are actually equal, or whether they are calling different methods but with the same type signature (we are currently limited in distinguishing these).
 

### 2019-05-06 sattose/paper.tex
Updates from Overleaf

@@
 It could also be that the corpus which we use, as it has generally smaller projects, uses more classes from outside the project (which are marked ``Unrelated'' if they do not have a common external superclass).
-On the second place, we have the ``Same Class'' clones.
-On the third place come the ``Sibling'' clones.
+About a fourth of all clone classes have all instances in the same class, which is generally easy to refactor.
+On the third place come the ``Sibling'' clones, which can often be refactored using a pull-up refactoring.
 
@@
 Just 1.6\% of the methods are cloned fully.
-More than a quarter of the clones spans over several methods, which is surprising.
-Simply extracting methods won't work in a case where a clone spans over several methods.
+More than a quarter of the clones spans over several methods, which makes extracting methods won't work in a case where a clone spans over several methods.
 About 4.5\% of clones include a constructor.

### 2019-05-06 sattose/paper.tex
Updates from Overleaf

@@
 \end{enumerate}
+Figure \ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
+The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
+The location and contents of clones is measured on clone instance level.
+A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50).
+A clone instance contents consists of a list of all statements and declarations it spans.
+\begin{figure}[H]
+    \includegraphics[width=1\columnwidth]{img/context}
+  \caption{Abstract representation of clone classes and clone instances.}
+  \label{fig:clonecontext}
+\end{figure}
 Everything in the context of a clone has a big impact on how it has to be refactored. For this study, we performed measurements on the context of clones in a large corpus of open source projects.

### 2019-05-06 sattose/paper.tex
Added another figure

@@
 \end{enumerate}
+
+A few of these categories are displayed in figure \ref{fig:clonerelation}.
+\begin{figure}[H]
+    \includegraphics[width=1\columnwidth]{img/Relation}
+  \caption{Abstract figure displaying some relations of clone classes. Arrows represent superclass relations.}
+  \label{fig:clonerelation}
+\end{figure}
 Please note that none of these categories allow external classes (except for ``same external superclass'').
@@
 The main reason for this is that it is (often) not possible to refactor to external classes.
-
-The ranking of the previous list of categories also matters as it shows the different levels in which clones were assessed.
-For instance, if two clone instances of a clone class belong to the ``same method'' category but the third belongs to the ``same class'', we will always choose the item lowest on the list.
 

### 2019-05-07 sattose/paper.tex
Ana

@@
 Duplication in source code can have a major negative impact on the maintainability of source code, as it creates explicit dependencies between fragments of code.
-These explicit dependencies have been shown to often cause bugs, as a modification in one fragment might have consequences for the correctness of another.
+Such explicit dependencies often cause bugs.
 In this study, we look into the opportunities to automatically refactor these duplication problems for object-oriented programming languages.
 To do this, we propose a method to detect clones that are suitable for refactoring.
-This method focuses on taking into account the context and scope of clones, to be sure our refactoring improves the design and does not leave side effects after it is applied.
+This method focuses on the context and scope of clones, ensuring our refactoring improves the design and does not leave side effects after it is applied.
 
@@
 Duplication in source code is often seen as one of the most harmful types of technical debt.
-In Martin Fowler's ``Refactoring'' book \cite{fowler1999refactoring}, he exclaims that \textit{``Number one in the stink parade is duplicated code.
+In Martin Fowler's ``Refactoring'' book \cite{fowler1999refactoring}, he claims that \textit{``Number one in the stink parade is duplicated code.
 If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
-In this research, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
+% In this research, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
 The main goal is to improve the maintainability of the refactored code.
@@
 Refactoring is used to improve the quality-related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
-There are many methods that have been introduced to help with the process of refactoring \cite{fowler1999refactoring, wake2004refactoring}, that are integrated into most modern IDE's.
+Many methods were introduced to aid the process of refactoring~\cite{fowler1999refactoring, wake2004refactoring}, and are integrated into most modern IDE's.
 However, most of these methods still require a manual assessment of where and when to apply them.
-Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, or does not happen at all \cite{mens2003refactoring}.
-For a large part, refactoring requires domain knowledge to do it right.
+This means refactoring is either a significant part of the development process~\cite{lientz1978characteristics, mens2004survey}, or does not happen at all~\cite{mens2003refactoring}.
+For a large part, proper refactoring requires domain knowledge.
 However, there are also refactoring opportunities that are rather trivial and repetitive to execute.
@@
 The location of a clone in the code has an impact on how it can be refactored.
-Because of this, we will first look at where clones can be found.
-Using this information we can determine in which locations clones are found the most, on basis of which the refactoring will be prioritized.
-A duplicate part in a codebase does not always have to be an exact match with another part to be considered a clone.
-We will look at the definitions of different types of clones and the opportunities to refactor duplicate parts of code albeit not an exact match.
+Therefore, we first look at where and how often clones can be found, enabling the prioritization of refactoring opportunities.
+% Using this information we can determine in which locations clones are found the most, on basis of which the refactoring will be prioritized. 
+Furthermore, a duplicate fragment in a codebase does not always have to be an exact match with another fragment to be considered a clone.
+Therefore, we also analyse the impact of the different definitions of clone types on refactoring opportunities.
+% We look at the definitions of different types of clones and the opportunities to refactor duplicate parts of code albeit not an exact match.
+
 We conduct our research on a large corpus of open source projects.
-We put the main focus on the Java programming language as refactoring opportunities feature paradigm and programming language dependent aspects~\cite{choi2011extracting}.
+We focus mainly on the Java programming language as refactoring opportunities feature paradigm and programming language dependent aspects~\cite{choi2011extracting}.
 However, most practices featured in this research will also be applicable to other object-oriented languages, like C\#.
 
-For this research, we strive to improve upon the current state-of-the-art in clone refactoring \cite{fontana2015duplicated, alwaqfi2017refactoring} by building a clone refactoring tool that applies refactorings to a large percentage of clones found.
-The design decisions for this tool will be made on basis of data gathered from a large corpus of software systems.
-This way we strive to make the problem of duplication in source code easier to deal with.
+In this research, we strive to improve upon the current state-of-the-art in clone refactoring \cite{fontana2015duplicated, alwaqfi2017refactoring} by building a clone refactoring tool that automatically applies refactorings to a large percentage of clones found.
+The design decisions for this tool are made on basis of data gathered from a large corpus of software systems.
 
-\subsection{Background}
-As code clones are seen as one of the most harmful types of technical debt, they have been studied very extensively.
-A survey by Roy et al.
-\cite{roy2007survey} states definitions for various important concepts in code clone research.
-In this survey, he mentions the concept ``clone pair'', which is \textit{a set of two code portions/fragments which are identical or similar to each other}.
-Furthermore, he defined ``clone class'' as \textit{the union of all clone pairs}.
-Apart from this, we use the definition ``clone instance'', which is a single code portion/fragment that is part of either a clone pair or clone class.
-
-\subsubsection{Current clone refactoring tools}
-A tool called DCRA (Duplicated Code Refactoring Advisor) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated}.
-This tool chooses to only focus on refactoring clone pairs because they argue that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.
-
-Another tool called Aries \cite{higo2004aries, higo2008metric} focuses on the detection of refactoring oriented clones.
-In this paper, the authors describe a few criteria by which a clone can be assessed to determine its suitability for refactoring.
-This tool looks however only at the possibility to merge clones, rather than whether clones should be merged (if they are actually harmful).
-Also, this tool only suggests refactorings and does not apply them.
-
-There are many other publications that look into code clone refactoring \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}.
-However, none of the publications describing a refactoring tool have published their source code or application for refactoring support.
-Furthermore, all of these tools only support a subset of all harmful clones that are found.
-Also, these publications/tools are limited to suggesting refactoring opportunities for clones found, rather than actually applying refactorings where suitable.
-Finally, all published approaches have limitations, such as false positives in their clone detection \cite{chen2018clone} or being limited to clone pairs \cite{higo2008metric}.
-
-\subsubsection{Advantages of clone classes over clone pairs}\label{chap:cloneclasses}
+\section{Background}
+As code clones are seen as one of the most harmful types of technical debt, they have been studied extensively.
+A survey by Roy et al.~\cite{roy2007survey} states definitions of important concepts in code clone research.
+For instance, ``clone pair''is defined as \textit{a set of two code portions/fragments which are identical or similar to each other}; ``clone class'' as \textit{the union of all clone pairs}; ``clone instance'' as a single code portion/fragment that is part of either a clone pair or clone class.
+\subsection{Advantages of clone classes over clone pairs}\label{chap:cloneclasses}
 Regarding clone detection, there is a lot of variability in literature whether clone pairs or clone classes should be detected.
 In this study we focus on clone classes, because of the advantages for refactoring.
-Clone pairs don’t provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}.
-Even though clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered.
+Clone pairs don not provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}.
+Although clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered.
 Another issue involves clone grouping by pairs: single clone reference amount increases according to binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), of which a heavy information redundancy follows \cite{fontana2012duplicated}.
 
-\subsubsection{Clone types}
+\subsection{Clone types}
 In a 2007 survey by Roy et al. \cite{roy2007survey} he defines four types of clones:\\
@@
 
-A higher type of clone means that it's harder to detect.
+A higher type of clone means that it is harder to detect.
 It also makes the clone harder to refactor, as more transformations would be required.
 Higher clone types also become more disputable whether they actually indicate a harmful antipattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}).
+\subsection{Related work in clone refactoring tools}
+The Duplicated Code Refactoring Advisor (DCRA) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated}.
+This tool only focuses on refactoring clone pairs, the authors arguing that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.
+
+Aries \cite{higo2004aries, higo2008metric} focuses on the detection of refactoring oriented clones.
+The authors describe a \todo{same criteria as you?
+different?} few criteria by which a clone can be assessed to determine its suitability for refactoring.
+However, \todo{can you be more precise?} this tool looks only at the possibility to merge clones, rather than whether clones should be merged (if they are actually harmful).
+Aries only suggests refactorings and does not apply them.
+
+There are many other research efforts looking into code clone refactoring \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}. However, 
+% none of the publications describing a refactoring tool have published their source code or application for refactoring support. Furthermore, 
+all of these tools only support a subset of all harmful clones that are found.
+Also, these tools are limited to suggesting refactoring opportunities, rather than actually applying refactorings where suitable.
+Finally, all published approaches have limitations, such as false positives in their clone detection \cite{chen2018clone} or being limited to clone pairs \cite{higo2008metric}.
 
@@
 We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities.
+The results of our survey are displayed in table~\ref{table:dettools}.
 We chose a set of tools that are open source and can analyze either Java or Python.
@@
 Because of this, we want to use a clone detection tool that can analyze such structures.
-\item \textbf{Makes it possible to configure the way in which clones are detected (as in what to exclude from the detection) in a relatively straightforward way.} We want to be able to exclude expressions/statements from matching (more about our rationale in section \ref{chap:clonetypes}).
-To be able to do this, the tool needs to be able to recognize the meaning of certain tokens.
+\item \textbf{Makes it possible to configure the way in which clones are detected (as in what to exclude from the detection) in a relatively straightforward way.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}).
+To achieve this, the tool needs to be able to recognize the meaning of certain tokens.
 \end{enumerate}
-
-The results of our survey are displayed in table \ref{table:dettools}.
 
@@
 A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection.
-For our tool, we decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing}.
+We decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing}.
 However, instead of building a dependency graph, we build a similarity graph of statements linking to similar statements.
+The graph built by CloneRefactor is shown in figure \ref{fig:clonerefactor}.
+
 We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is compatible with all modern Java versions (Java 1-12).
@@
 This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically).
-This is displayed in figure \ref{fig:clonerefactor}.
+On basis of this graph we detect clone classes.
+
+We challenge completed clone classes against the thresholds that are being used, and remove the clone classes that do not adhere to the thresholds.
 
@@
 \end{figure}
-
-On basis of this graph we detect clone classes. We challenge completed clone classes against the thresholds that are being used, and remove the clone classes that do not adhere to the thresholds.
 
@@
 
-For the measurements in the next chapter we have chosen to apply the following thresholds:
+The measurements in our study use the following thresholds:
 \begin{itemize}
@@
 
-\section{Addressing and solving problems with clone type definitions}\label{chap:clonetypes}
-In this chapter, we will propose solutions for shortcomings in type 1, type 2 and type 3 clones \cite{roy2007survey} to increase the chance that we can merge the clone while improving the design.
-Type-4 clones are, because of the serious challenges involved in their detection and refactoring, out of the scope for this study.
+\section{Addressing problems with clone type definitions}\label{chap:clonetypes}
+We propose solutions for shortcomings in type 1, type 2 and type 3 clones~\cite{roy2007survey} to increase the chance that we can merge the clone while improving the design.
+Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.
 
@@
 This could invalidate a refactoring opportunity for such a code fragment.
-Because of that, we propose to:
+Therefore, we propose to:
 \begin{itemize}
@@
 \subsection{Type 2 clones}
-Type 2 clones, by definition, allow any change in identifiers, literals, types, layout, and comments.
-For refactoring purposes, this doesn't always make a lot of sense.
+By definition, type 2 clones allow any change in identifiers, literals, types, layout, and comments.
+For refactoring purposes, this does not always make a lot of sense.
 If we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
 This could render two methods that have an entirely different functionality as clones.
-Merging such clones, if possible at all, might only prove to be harmful.
+Merging such clones might only prove to be harmful.
 
-Because of that, for this research, we have looked solving these problems with type 2 clones to be able to detect such clones that can and should be merged.
+We tackle these problems with type 2 clones to be able to detect such clones that can and should be merged.
 Our definition ensures functional similarity by applying the following changes to type 2 clones:
@@
 This is because different method identifiers can describe a completely different functionality.
-Because of that, we recommend to keep considering the call signatures of cloned methods when they are compared.
+Therefore, we suggest considering the call signatures of cloned methods when they are compared.
 We can allow variability in the rest of method identifiers by passing the function as a parameter.
@@
 \subsection{Next steps}
-The next step will be to integrate our solutions for the problems with the clone types, as explained in section \ref{chap:clonetypes}, into our CloneRefactor tool.
-This way, we can run all scripts that we used for our measurements for these novel clone definitions.
+The next step is to integrate our solutions for the problems related to clone types into our CloneRefactor tool.
+This way, we can perform our experiments for these novel clone definitions.
 We are curious to see how it compares with the results we had so far.

### 2019-05-07 sattose/paper.tex
Ana++

@@
 Aries \cite{higo2004aries, higo2008metric} focuses on the detection of refactoring oriented clones.
-The authors describe a \todo{same criteria as you?
-different?} few criteria by which a clone can be assessed to determine its suitability for refactoring.
-However, \todo{can you be more precise?} this tool looks only at the possibility to merge clones, rather than whether clones should be merged (if they are actually harmful).
-Aries only suggests refactorings and does not apply them.
+On basis of the relation between clone instances through inheritance, similar to Fontana et al., Aries proposes a refactoring.
+For instance, if two clone classes are siblings of each other (share the same superclass), they propose to perform ``Extract method'' and ``Pull up method'' sequentially.
+This tool only proposes such a refactoring, and does not provide help in the process of applying the refactoring.
 
-There are many other research efforts looking into code clone refactoring \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}. However, 
-% none of the publications describing a refactoring tool have published their source code or application for refactoring support. Furthermore, 
-all of these tools only support a subset of all harmful clones that are found.
+There are many other research efforts looking into code clone refactoring \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}.
+However, all of these tools only support a subset of all harmful clones that are found.
 Also, these tools are limited to suggesting refactoring opportunities, rather than actually applying refactorings where suitable.
@@
 \subsection{Survey on Clone Detection Tools}
+\label{ch:tool-overview}
 We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities.
@@
 \subsubsection{Categorizing Clone Instance Relations}
-A paper by Fontana et al.
-\cite{fontana2015duplicated} describes measurements on 50 open source projects on the relation of clone instances to each other.
+Fontana et al.
+\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other.
 To do this, they first define several categories for the relation between clone instances in object-oriented languages.
+A few of these categories are shown in figure \ref{fig:clonerelation}.
 These categories are as follows:
@@
 
-A few of these categories are displayed in figure \ref{fig:clonerelation}.
 \begin{figure}[H]
@@
 \subsubsection{Our measurements}
-We use a similar setup to that used in the study by Fontana et al.
+We use a similar setup to that used by Fontana et al.
 (Table~3 of Fontana et al.
@@
 Fontana et al.
-measure clones using their own tool called DCRA.
-This tool detects clone pairs in Java-based source code.
-It operates on a single threshold: the minimum number of lines that a clone should span.
-Our measurements were conducted using CloneRefactor, because of which the setup for our measurements differs as follows from Fontana et al.:
+measure clones using their own tool (DCRA).
+As explained in section~\ref{ch:tool-overview}, we chose to implement our own tool, CloneRefactor.
+Therefore, the setup for our measurements differs as follows from Fontana et al.:
 \begin{itemize}
@@
 
-Comparing it to the results of Fontana et al.
-\cite{fontana2015duplicated}, we find way more unrelated clones.
+The most notable difference when comparing it to the results of Fontana et al.
+\cite{fontana2015duplicated} is that in our results 39.37\% of clone are unrelated, while for them it was only 15.70\%.
 This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
@@
 \cite{lozano2007evaluating} discusses the harmfulness of cloning.
-In this paper, the author argues that 98\% are produced at method-level.
+The authors argue that 98\% are produced at method-level.
 However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.

### 2019-05-07 sattose/paper.tex
Ana+++

@@
 Furthermore, a duplicate fragment in a codebase does not always have to be an exact match with another fragment to be considered a clone.
-Therefore, we also analyse the impact of the different definitions of clone types on refactoring opportunities.
+Therefore, we also analyze the impact of the different definitions of clone types on refactoring opportunities.
 % We look at the definitions of different types of clones and the opportunities to refactor duplicate parts of code albeit not an exact match.
@@
 \subsection{Related work in clone refactoring tools}
-The Duplicated Code Refactoring Advisor (DCRA) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated}.
+The Duplicated Code Refactoring Advisor (DCRA) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated, fontana2015duplicated}.
 This tool only focuses on refactoring clone pairs, the authors arguing that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.
@@
 Aries \cite{higo2004aries, higo2008metric} focuses on the detection of refactoring oriented clones.
-On basis of the relation between clone instances through inheritance, similar to Fontana et al., Aries proposes a refactoring.
+On basis of the relation between clone instances through inheritance, similar to Fontana et al.
+\cite{fontana2012duplicated}, Aries proposes a refactoring.
 For instance, if two clone classes are siblings of each other (share the same superclass), they propose to perform ``Extract method'' and ``Pull up method'' sequentially.
@@
 \section{Clone Detection}
-As duplication in source code is a serious problem in many software systems, there are a lot of researches that look into code clones.
+As duplication in source code is a serious problem in many software systems, many research efforts look into code clones.
 Many tools have been proposed to detect various types of code clones.
 Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016.
+\todo{what is insufficient about these two?
+what triggered the need to reassess clone detectors?
+where are the four criteria coming from?}
 
@@
 
+\footnotetext[3]{This clone detection tool has also been used by Fontana et al. \cite{fontana2012duplicated}}
+\footnotetext{\label{note1}CPD is a Clone Detection tool that is part of PMD. PMD is a widely used tool for static code analysis in Java.}
+
 None of the tools we considered implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
-
-\footnotetext[3]{This clone detection tool has also been used by Fontana et al. \cite{fontana2012duplicated}}
-
-\footnotetext{\label{note1}CPD is a Clone Detection tool that is part of PMD. PMD is a widely used tool for static code analysis in Java.}
 
@@
 
-We also want to argue that statements that are not common between two clone instances, should not count towards the size of the clone (and thus towards the threshold which determines whether the clone will be taken into account).
+We also argue that statements that are not common between two clone instances, should not count towards the size of the clone (and thus towards the threshold which determines whether the clone will be taken into account).
 Also, clones should not start and not end with an added statement (as that would be nonsense: such a thing could be done for any clone).
@@
 
-\section{Code Clone Context}
+\section{Relation, Location and Content Analysis of Clones}\label{chap:clonecontextexpl}
 To be able to refactor code clones, it is very important to consider the context of the clone. We define the following aspects of the clone as its context:
@@
 \end{figure}
-Everything in the context of a clone has a big impact on how it has to be refactored. For this study, we performed measurements on the context of clones in a large corpus of open source projects.
+%\todo{do we have proof of this statement?
+if not, say that this is our intuition and a first step to prove it is to analyze a large body of projects} Everything in the context of a clone has a big impact on how it has to be refactored.
+% I guess it's a bit of an empty statement. Of course where some code is located has an impact on how to refactor it. Maybe remove it?
+We analyzed the context of clones in a large corpus of open source projects.
+For these experiments, we used the CloneRefactor tool.
+These experiments map the context, as follows: the relation between clone instances is explained, measured and discussed in section\ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in section \ref{chap:clonelocation};  the content of clone instances are explained, measured and discussed in section \ref{chap:clonecontents}.
 
@@
 
-\subsection{Relations Between Clone Instances}
+\subsection{Relations Between Clone Instances} \label{chap:relationsinstances}
 When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances.
 This relation has a big impact on how a clone should be merged, in order to improve the software design in the process.
+In this section, we display measurements we conducted on the corpus introduced in section \ref{chap:corpus}.
+These measurements are based on an experiment by Fontana et al.
+\cite{fontana2015duplicated}, which we will briefly introduce in section \ref{chap:catcloneinstancerelations}.
+We use a vastly different setup, which is explained in section \ref{chap:oursetup}.
+We then show our results in section \ref{chap:ourmeasurements}.
 
-\subsubsection{Categorizing Clone Instance Relations}
+\subsubsection{Categorizing Clone Instance Relations}\label{chap:catcloneinstancerelations}
 Fontana et al.
@@
 
-\subsubsection{Our measurements}
+\subsubsection{Our setup}\label{chap:oursetup}
 We use a similar setup to that used by Fontana et al.
@@
 We seek clones with a minimum size of 6 statements/declarations.
-This is further explained in section \ref{chap:thresholds}.
+This is explained detail in section \ref{chap:thresholds}.
 \item We seek duplicates by statement/declaration rather than SLOC. This makes our analysis depend less on the coding style (in terms of newline usage) of the author of the software project.
@@
 
+\subsubsection{Our results} \label{chap:ourmeasurements}
 Table~\ref{table:relations} contains our results regarding the relations between clone instances.
@@
 
-\subsection{Clone instance location}
+\subsection{Clone instance location}\label{chap:clonelocation}
 After mapping the relations between individual clones, we looked at the location of individual clone instances.
@@
 However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
-We validated this claim over the corpus we use.
-For this, we chose the following categories:
+We validated this claim over our corpus.
+The results for the clone instance locations are shown in table \ref{table:locations}.
+We chose the following categories:
 \begin{enumerate}
@@
 \end{enumerate}
-
-The results for the clone instance locations are shown in table \ref{table:locations}.
 
@@
 
-\subsection{Clone instance contents}
+\subsection{Clone instance contents}\label{chap:clonecontents}
 Finally, we looked at the contents of individual clone instances: what kind of declarations and statements do they span. We selected the following categories to be relevant for refactoring:
@@
 
-However, not always can a clone easily be merged.
+However, a clone is not always easily merged.
 Sometimes a clone spans a statement partially (like a for-loop of which only it's declaration and a part of the body is cloned).

### 2019-05-07 sattose/paper.tex
Ana++

@@
 
+A survey by Roy et al.
+\cite{roy2007survey} describes different types of clones.
+Most clone detection tools focus on finding clones corresponding with these definitions.
+In this paper, we outline challenges with these clone type definitions when considered in a refactoring context.
+We next propose solutions to these problems that would enable the detection of clones that should be refactored, rather than fragments of code that are just similar.
+
 Code clones can be found anywhere in a codebase.
@@
 % Using this information we can determine in which locations clones are found the most, on basis of which the refactoring will be prioritized.
+
 Furthermore, a duplicate fragment in a codebase does not always have to be an exact match with another fragment to be considered a clone.
@@
 
-\section{Background}
+Section
+
+\section{Background}\label{chap:background}
 As code clones are seen as one of the most harmful types of technical debt, they have been studied extensively.
@@
 
-\section{Clone Detection}
+\section{Clone Detection}\label{chap:clonedetection}
 As duplication in source code is a serious problem in many software systems, many research efforts look into code clones.
@@
 
-\section{Merging duplicate code through refactoring}
+\section{Merging duplicate code through refactoring}\label{chap:mergingdups}
 Now we have mapped the contexts in which clones occur, we can start looking at refactoring opportunities.
@@
 
-\section{Threats to validity}
+\section{Threats to validity}\label{chap:threatstovalidity}
 We noticed that, when measuring over a corpus of this size, the thresholds that we use for the clone detection have a big impact on the results.
@@
 
-\section{Conclusion and next steps}
+\section{Conclusion and next steps}\label{chap:conclusion}
 In the research we have conducted so far we have made three novel contributions:

### 2019-05-07 sattose/paper.tex
Final sattose edits

@@
 
-Section
+Section \ref{chap:background} describes the background from literature that we used to conduct this study.
+Section \ref{chap:clonedetection} presents our clone refactoring tool proposal.
+Section \ref{chap:clonetypes} outlines challenges with clone type definitions and proposes solutions for them in a refactoring context.
+Section \ref{chap:clonecontextexpl} outlines our analysis and measurements regarding the context of code clones.
+Section \ref{chap:mergingdups} shows our measurements regarding the amount of clones that can be refactored through method extraction.
+Section \ref{chap:threatstovalidity} shows the threats to validity of this study and section \ref{chap:conclusion} draws a conclusion on our preliminary results.
 
@@
 As duplication in source code is a serious problem in many software systems, many research efforts look into code clones.
-Many tools have been proposed to detect various types of code clones.
-Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016.
+Many tools have been proposed to detect various types of code clones~\cite{sheneamer2016survey, svajlenko2014evaluating}.
+However, these tools were not yet assessed in terms of automatically refactoring clones.
+
+In this section, we first assess a set of modern clone detection tools for their applicability to this domain.
+Next, we introduce our own tool geared towards automatic clone refactoring, CloneRefactor.%Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016.
 \todo{what is insufficient about these two?
@@
 We chose a set of tools that are open source and can analyze either Java or Python.
-Then we chose four criteria by which we considered these tools:
+Next we formulate the following four criteria by which we analyze these tools:
 \begin{enumerate}

### 2019-05-07 sattose/paper.tex
Working a bit on stuff

@@
   \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
-  \item \textbf{Compare the equality the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types.
+  \item \textbf{Compare the equality of the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types.
 This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive.
 To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
+  \item \textbf{Compare the equality of the fully qualified indentifier for method references and call signatures.}
 \end{itemize}

### 2019-05-07 sections/research.tex
Working a bit on stuff

@@
 
-\section{Clone detection survey}
-At the beginning of this study, we set out to find a clone detection tool that we could extend to apply automated refactorings.
+%\section{Clone detection survey}
+%At the beginning of this study, we set out to find a clone detection tool that we could extend to apply automated refactorings.
 Many tools have been proposed to detect various types of code clones.
-Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016.
-We have considered a set of these tools, including some additional (more recent) ones.
+We have considered a set of tools, selected by the most relevant AST or token based detectors found in a set of surveys \cite{}.
 However, most of these tools have a vastly different purpose than this thesis.
@@
 
-\subsection{Text- and Token based clone detection}
-Clones
+%\subsection{Text- and Token based clone detection}
+%Most clone detection tools are either text-based or token-based \cite{}.
+The main rationale for this is that it makes it easy to support many (programming) languages, it is simpler and it is generally more efficient.
+This works great for most puposes, but for automated refactoring
 
-\subsection{Big scale clone detection}
-There are a lot of clone detection tools that focus on detecting large amounts of clones quickly \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval, kamiya2002ccfinder, livieri2007very}
+%\subsection{Big scale clone detection}
+%There are a lot of clone detection tools that focus on detecting large amounts of clones quickly \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval, kamiya2002ccfinder, livieri2007very}.
 

### 2019-05-08 sattose/paper.tex
Added scorpio to survey

@@
 Deckard \cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
+Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
 \end{tabular}

### 2019-05-09 sattose/paper.tex
Begin rewriting paper with new results

@@
 Our intermediate results indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
-Approximately a fifth of the duplication can be refactored through method extraction, while other clones require other refactoring techniques.
+Approximately ten percent of the duplication can be refactored through method extraction without extra considerations required, while other clones require other refactoring techniques.
 Similar future measurements will provide further insight into the contexts where clones occur and how this affects the automated refactoring process.
@@
 \begin{itemize}
-  \item \textbf{Number of statements/declarations:} 6
-  \item \textbf{Number of tokens:} 10
-  \item \textbf{Number of lines:} 6
+  \item \textbf{Number of statements/declarations:} 3
+  \item \textbf{Number of tokens:} 12
+  \item \textbf{Number of lines:} 1
 \end{itemize}
@@
 
-\subsection{Type 1 clones} \label{chap:type1clones}
+\subsection{Type 1R clones} \label{chap:type1clones}
 Type 1 clones are identical clone fragments except for variations in whitespace and comments.
@@
 This could invalidate a refactoring opportunity for such a code fragment.
-Therefore, we propose to:
+Therefore, we propose an alternative definition of type 1 clones.
+We have named this type 1R clones, indicate that this definition is separate from type 1 clones in literature.
+The ``R'' stands for refactoring, to indicate that this is type is refactoring oriented (and may be less suitable for, for instance, large scale clone analysis).
+Type 1R clones differ from type 1 clones by the folowing aspects:
 \begin{itemize}
@@
 
-\subsection{Type 2 clones}
+\subsection{Type 2R clones}
 By definition, type 2 clones allow any change in identifiers, literals, types, layout, and comments.
@@
 
-\subsection{Type 3 clones}
+\subsection{Type 3R clones}
 Type 3 clones are even more permissive than type 2 clones, allowing added and removed statements.
@@
 The amount of statements that this ``short gap'' can maximally span should be dependent on a threshold value.
+
+\subsection{The challenge of detecting these clones}\label{chap:challenge}
+Detecting these clone types comes with serious challenges.
+For each of these types of clones we need to parse the fully qualified identifier of all types, method calls and variables.
+This comes with serious challenges, regarding both performance and implementation.
+To be able to parse all fully qualified identifiers, and trace the declarations of variables, we might to follow cross file references.
+The referenced types/variables/methods might even not be part of the project, but rather of an external library or the standard libraries of the programming language.
+All these need to be considered for the referenced entity to be found, on basis of which a fully qualified identifier can be created.
+
+In our CloneRefactor tool we use JavaParser \cite{tomassetti2017javaparser}.
+JavaParser has a build in symbol solver.
+This symbol solver can automatically resolve types, method calls and variables.
+However, because of this, CloneRefactor does require all libraries that the software project requires (apart from the Java Standard Library).
+If these are not available, CloneRefactor will estimate types on basis of the information that is available.
 
@@
 
-We filtered the corpus further to make sure we are not including any test classes or generated classes.
-Many Java/Maven projects use a structure where they separate the application and its tests in the different folders (``/src/main/java'' and ``/src/test/java'' respectively).
-Because of this, we chose to only use projects from the corpus which use this structure (and had at least a ``/src/main/java'' folder).
-To limit the execution time of the script, we also decided to limit the maximum amount of source files in a single project to 1.000 (projects with more source files were not considered, which filtered only 5 extra projects out of the corpus).
-Of the 14.436 projects in the corpus over 3.848 remained, which is plenty for our purposes.
-The script to filter the corpus in included in our GitHub repository \footnote{The script we use to filter the corpus: \url{https://github.com/SimonBaars/CloneRefactor/blob/MeasurementsVersion1/src/main/java/com/simonbaars/clonerefactor/scripts/PrepareProjectsFolder.java}}.
+As indicated in section \ref{chap:challenge} CloneRefactor requires all libraries of software projects we test.
+As these are not included in the used corpus \cite{githubCorpus2013}, we decided to filter the corpus to all Maven projects.
+As no pom.xml files are included in the corpus, we cloned the lastest version of each project in the corpus.
+We then removed each project that contained no ``pom.xml'' file (a file that describes the dependencies used by the project).
+We then filtered the corpus further to make sure each project contained a ``src/main/java'' folder, to be sure no test files or other redundant sources are included in the clone detection.
+As a final step, we collected all dependencies for each project by using the \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib} Maven command, and removed each project for which not all dependencies were available (due to non-Maven dependencies being used or unsatisfiable dependencies being referenced in the ``pom.xml'' file).
 
@@
 \hline
-Amount of projects                                                                                      & 3,848      \\ \hline
-Amount of lines                                                                                         & 8,284,140  \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\ whitespace, comments, etc.)\end{tabular}        & 8,163,429  \\ \hline
-Amount of statements/declarations                                                                       & 6,863,725  \\ \hline
-Amount of tokens                                                                                        & 66,964,270 \\ \hline
-Amount of lines cloned                                                                                  & 1,341,094  \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines cloned (excluding\\ whitespace, comments, etc.)\end{tabular} & 815,799    \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of statements/declarations\\ cloned\end{tabular}                      & 747,993    \\ \hline
-Amount of tokens cloned                                                                                 & 9,800,819  \\ \hline
-Amount of clone classes                                                                                 & 34,367     \\ \hline
+Amount of projects                                                                                      & 1,361      \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\ whitespace, comments and newlines.)\end{tabular} & 1,414,996  \\ \hline
+Amount of statements/declarations                                                                       & 1,212,189  \\ \hline
+Amount of tokens (excluding whitespace, comments and newlines.)                                                   & 11,643,194 \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+\subsection{Clone detection results}
+Currently, we have implemented two clone detection algorithms into CloneRefactor.
+The first one finds clones by comparing tokens (excluding whitespace, comments and newlines).
+The second algorithm implements our type 1R, as explained in section \ref{chap:type1clones}.
+
+\begin{table}[H]
+  \begin{center}
+  \caption{CloneRefactor results for Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
+  \bigskip
+\begin{tabular}{|l|l|}
+\hline
+ & \textbf{Token} & \textbf{Type 1R}
+\begin{tabular}[c]{@{}l@{}}Amount of lines cloned (excluding\\ whitespace, comments and newlines.)\end{tabular} & 200,362 & 129,519 \\ \hline
+Amount of statements/declarations cloned & 182,466 & 118,980 \\ \hline
+Amount of tokens cloned (excluding whitespace, comments and newlines.) & 1,582,845 & 973,596 \\ \hline
 \end{tabular}

### 2019-05-09 sattose/paper.tex
Fixed this text a bit

@@
 Therefore, we propose an alternative definition of type 1 clones.
-We have named this type 1R clones, indicate that this definition is separate from type 1 clones in literature.
+We have named this it ``type 1R clones'', to indicate that this definition is separate from type 1 clones in literature.
 The ``R'' stands for refactoring, to indicate that this is type is refactoring oriented (and may be less suitable for, for instance, large scale clone analysis).
-Type 1R clones differ from type 1 clones by the folowing aspects:
+Type 1R clones differ from type 1 clones by the following aspects:
 \begin{itemize}
@@
 As indicated in section \ref{chap:challenge} CloneRefactor requires all libraries of software projects we test.
-As these are not included in the used corpus \cite{githubCorpus2013}, we decided to filter the corpus to all Maven projects.
-As no pom.xml files are included in the corpus, we cloned the lastest version of each project in the corpus.
+As these are not included in the used corpus \cite{githubCorpus2013}, we decided to filter the corpus to only include Maven projects.
+Maven is a build automation tool used primarily for Java, and works on basis of an \texttt{pom.xml} file to describe the projects' dependencies.
+As no \texttt{pom.xml} files are included in the corpus, we cloned the latest version of each project in the corpus.
 We then removed each project that contained no ``pom.xml'' file (a file that describes the dependencies used by the project).

### 2019-05-10 sattose/paper.tex
Sattose Paper: Now with more content

@@
 Amount of projects                                                                                      & 1,361      \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\ whitespace, comments and newlines.)\end{tabular} & 1,414,996  \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\whitespace, comments and newlines.)\end{tabular} & 1,414,996  \\ \hline
 Amount of statements/declarations                                                                       & 1,212,189  \\ \hline
-Amount of tokens (excluding whitespace, comments and newlines.)                                                   & 11,643,194 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of tokens (excluding\\whitespace, comments and newlines.)\end{tabular} & 11,643,194 \\ \hline
 \end{tabular}
@@
 Currently, we have implemented two clone detection algorithms into CloneRefactor.
-The first one finds clones by comparing tokens (excluding whitespace, comments and newlines).
+The first one finds clones by comparing tokens (excluding whitespace, comments and newlines), equal to the definition of type 1 clones in literature \cite{roy2007survey}.
 The second algorithm implements our type 1R, as explained in section \ref{chap:type1clones}.
+The differences between the clones found for these algorithms is displayed in table \ref{table:clonedet}.
+Please note that the amount of lines, statements and tokens is without whitespace, newlines and comments.
 
@@
   \begin{center}
-  \caption{CloneRefactor results for Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
+  \caption{CloneRefactor clone detection results for the two different algorithms.} \label{table:clonedet}
   \bigskip
-\begin{tabular}{|l|l|}
+\begin{tabular}{|l|l|l|}
 \hline
- & \textbf{Token} & \textbf{Type 1R}
-\begin{tabular}[c]{@{}l@{}}Amount of lines cloned (excluding\\ whitespace, comments and newlines.)\end{tabular} & 200,362 & 129,519 \\ \hline
-Amount of statements/declarations cloned & 182,466 & 118,980 \\ \hline
-Amount of tokens cloned (excluding whitespace, comments and newlines.) & 1,582,845 & 973,596 \\ \hline
+Extra & \textbf{Type 1} & \textbf{Type 1R} \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of lines cloned\end{tabular} & 200,362 & 129,519 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of statements/\\declarations cloned\end{tabular} & 182,466 & 118,980 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of tokens cloned\end{tabular} & 1,582,845 & 973,596 \\ \hline
 \end{tabular}
@@
 \end{table}
+
+Looking at table \ref{table:clonedet}, it becomes apparent that the type 1R algorithm finds significantly less clones found than the type 1 algorithm.
+Figure \ref{fig:type1rclone} displays an example of a clone that does get detected by the type 1 algorithm but does not get detected by the type 1R algorithm.
+This is because the variable ``key'' and ``prefix'' are of a different primitive type between the clone instances.
+This makes this clone less suitable for automated refactoring.
+We manually checked some differences between the detected type 1 clones and type 1R clones and in each instance there was either a variable with different type, a different method call or a different type (but textual equality).
+This indicates that about a third of the clones have textual equality, but are not actually equal when considering the types of expressions.
+
+\begin{figure}[H]
+    \includegraphics[width=1\columnwidth]{img/clone}
+  \caption{Example of a clone that is not a type 1R clone but is a type 1 clone.}
+  \label{fig:type1rclone}
+\end{figure}
 
@@
   \bigskip
-\begin{tabular}{|l|l|l|} \hline
-\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
-Unrelated          & 13,529           & 39.37               \\ \hline
-Same Class          & 8,341            & 24.28               \\ \hline
-Sibling            & 5,978            & 17.40               \\ \hline
-Same Method         & 2,456            & 7.15                \\ \hline
-External Superclass & 2,402            & 6.99                \\ \hline
-First Cousin        & 695             & 2.02                \\ \hline
-Superclass         & 489             & 1.42                \\ \hline
-Common Hierarchy    & 442             & 1.29                \\ \hline
-Ancestor           & 28              & 0.08               \\ \hline
+\begin{tabular}{|l|l|l|l|l|} \hline
+\textbf{Relation}  & \textbf{\# (1)} & \textbf{\% (1)}  & \textbf{\# (1R)} & \textbf{\% (1R)} \\ \hline
+Unrelated          & 6,134           & 35.48  & 4,762 & 38.14            \\ \hline
+\begin{tabular}[c]{@{}l@{}}Same\\Class\end{tabular}          & 4,772            & 27.60  & 3,131 & 25.07             \\ \hline
+Sibling            & 2,680            & 15.50   & 1,949 & 15.61            \\ \hline
+\begin{tabular}[c]{@{}l@{}}Same\\Method\end{tabular}         & 2,247            & 13.00   & 1,685 & 13.49             \\ \hline
+\begin{tabular}[c]{@{}l@{}}External\\Superclass\end{tabular} & 794            & 4.59   & 558 & 4.47             \\ \hline
+\begin{tabular}[c]{@{}l@{}}First\\Cousin\end{tabular}        & 269             & 1.56     & 197 & 1.58           \\ \hline
+Superclass         & 237             & 1.37     & 118 & 0.94           \\ \hline
+\begin{tabular}[c]{@{}l@{}}Common\\Hierarchy\end{tabular}    & 123             & 0.71    & 73 & 0.58            \\ \hline
+Ancestor           & 35              & 0.20     & 14 & 0.11          \\ \hline
 \end{tabular}
@@
 The most notable difference when comparing it to the results of Fontana et al.
-\cite{fontana2015duplicated} is that in our results 39.37\% of clone are unrelated, while for them it was only 15.70\%.
+\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (38.14\% with type 1R), while for them it was only 15.70\%.
 This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
@@
 On the third place come the ``Sibling'' clones, which can often be refactored using a pull-up refactoring.
+There are no noteworthy differences between type 1 and type 1R clones.
 
@@
 
+Please note that these results are measured over each clone instance rather than each clone class, hence the higher total amount in comparison to the results of section \ref{chap:ourmeasurements}.
+
 \begin{table}[H]
@@
   \bigskip
-\begin{tabular}{|l|l|l|}
+\begin{tabular}{|l|l|l|l|l|}
 \hline
-\textbf{Location}  & \textbf{Amount}  & \textbf{Percentage} \\ \hline
-Method Level       & 19,818           & 57.68               \\ \hline
-Class Level        & 13,259           & 38.59               \\ \hline
-Constructor Level  & 1,099            & 3.20                \\ \hline
-Interface Level    & 110              & 0.32                \\ \hline
-Enum Level         & 74               & 0.22                \\ \hline
+\textbf{Location}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
+Method Level       & 32,861           & 66.02   & 19,075 & 58.23            \\ \hline
+Class Level        & 15,069           & 30.27   & 12,207 & 37.27            \\ \hline
+\begin{tabular}[c]{@{}l@{}}Constructor\\Level\end{tabular}  & 1,391            & 2.79     & 1,080 & 3.30           \\ \hline
+\begin{tabular}[c]{@{}l@{}}Interface\\Level\end{tabular}    & 282              & 0.57     & 247 & 0.75           \\ \hline
+Enum Level         & 171               & 0.34    & 147 & 0.45            \\ \hline
 \end{tabular}
@@
 The amount of clones found in interfaces and enumerations is very low.
+Regarding the differences between type 1 and type 1R, it seems that there are relatively less method level clones and more class level clones for type 1R.
+This is probably due to that the main reason for variability between type 1 and type 1R is variable references, which occur more at method level than class level.
 

### 2019-05-10 sattose/paper.tex
Refactorability

@@
 In this study we focus on clone classes, because of the advantages for refactoring.
-Clone pairs don not provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}.
+Clone pairs do not provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}.
 Although clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered.
-Another issue involves clone grouping by pairs: single clone reference amount increases according to binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), of which a heavy information redundancy follows \cite{fontana2012duplicated}.
+There is also another issue that results from grouping clones by pairs: clone reference amount increases according to the binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), which causes a heavy information redundancy \cite{fontana2012duplicated}.
 
-\subsection{Clone types}
+\subsection{Clone types}\label{chap:backgroundclonetypes}
 In a 2007 survey by Roy et al. \cite{roy2007survey} he defines four types of clones:\\
-\textbf{Type 1:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
+\textbf{Type 1:} Identical code fragments except for variations in whitespace (may also be variations in layout) and comments.\\
 \textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
@@
 The Duplicated Code Refactoring Advisor (DCRA) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated, fontana2015duplicated}.
-This tool only focuses on refactoring clone pairs, the authors arguing that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.
+This tool only focuses on refactoring clone pairs, with the authors arguing that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.
 
-Aries \cite{higo2004aries, higo2008metric} focuses on the detection of refactoring oriented clones.
-On basis of the relation between clone instances through inheritance, similar to Fontana et al.
+Aries \cite{higo2004aries, higo2008metric} focuses on the detection of refactorable clones.
+They basis of the relation between clone instances through inheritance, similar to Fontana et al.
 \cite{fontana2012duplicated}, Aries proposes a refactoring.
@@
 
-There are many other research efforts looking into code clone refactoring \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}.
+There is various other research that investigates refactoring code clones \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}.
 However, all of these tools only support a subset of all harmful clones that are found.
@@
 \section{Addressing problems with clone type definitions}\label{chap:clonetypes}
-We propose solutions for shortcomings in type 1, type 2 and type 3 clones~\cite{roy2007survey} to increase the chance that we can merge the clone while improving the design.
+We propose solutions for shortcomings in type 1, type 2 and type 3 clones~\cite{roy2007survey} (see section \ref{chap:backgroundclonetypes} for these definitions) to increase the chance that we can merge the clone while improving the design.
 Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.
@@
 \subsection{Type 1R clones} \label{chap:type1clones}
-Type 1 clones are identical clone fragments except for variations in whitespace and comments.
+Type 1, as defined in literature~\cite{roy2007survey}, clones are identical clone fragments except for variations in whitespace and comments.
 However, when two clone fragments are textually identical, it does not yet indicate that they are actually identical.
@@
 \subsection{Type 2R clones}
-By definition, type 2 clones allow any change in identifiers, literals, types, layout, and comments.
+By its definition in literature, type 2 clones allow any change in identifiers, literals, types, layout, and comments.
 For refactoring purposes, this does not always make a lot of sense.
@@
 Type 3 clones are even more permissive than type 2 clones, allowing added and removed statements.
-Thresholds matter a lot here to make sure that not the whole project is detected as a clone of itself.
-The main question for this study regarding type 3 clones is: ``how can we merge type 3 clones while improving the design?''.
+For these clones, thresholds matter a lot to make sure that not the whole project is detected as a clone of itself.
+The main question for this study regarding type 3 clones is: \textit{``how can we merge type 3 clones while improving the design?''}.
 
@@
 As we have to ensure equal functionality after merging the clone, we have to wrap the difference in statements between the clone instances in conditional blocks (either if-statements or switch-statements).
-We can then pass a variable as to which path should be taken through the code (either a boolean or an enumeration).
-Such a refactoring would make added statements that are contiguous less harmful for the design than added statements that are separated by statements that both clone instances have in common.
+We can then pass a variable to indicate which path should be taken through the code (either a boolean or an enumeration).
+Such a refactoring would make added statements that are contiguous less harmful for the design than added statements that are scattered throughout the cloned fragment.
 
 We also argue that statements that are not common between two clone instances, should not count towards the size of the clone (and thus towards the threshold which determines whether the clone will be taken into account).
-Also, clones should not start and not end with an added statement (as that would be nonsense: such a thing could be done for any clone).
-
 As for the detection of type 3 clones, we think the easiest opportunity to detect these clones is to consider it as a postprocessing step after clone detection.
@@
 Table~\ref{table:relations} contains our results regarding the relations between clone instances.
+In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our type 1R definition as explained in section \ref{chap:type1clones}.
 
@@
   \begin{center}
-  \caption{Clone instance contents} \label{table:refactorability}
+  \caption{Refactorability through method extraction} \label{table:refactorability}
   \bigskip
-\begin{tabular}{|l|l|l|}
+\begin{tabular}{|l|l|l|l|l|}
 \hline
-\textbf{Refactorability}        & \textbf{Amount} & \textbf{Percentage} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Cannot directly\\be extracted\end{tabular}    & 10,990           & 41.91               \\ \hline
-\begin{tabular}[c]{@{}l@{}}Is not a\\partial method\end{tabular} & 9,444            & 36.01               \\ \hline
-\begin{tabular}[c]{@{}l@{}}Can be\\extracted\end{tabular}                & 5,791            & 22.08               \\ \hline
+\textbf{}        & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
+\begin{tabular}[c]{@{}l@{}}Is not a\\partial method\end{tabular}           & 5,917 & 34.22 & 4,806 & 38.49 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Complex\\control flow\end{tabular} & 5,511 & 31.87 & 3,158 & 25.29 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Spans part of\\a block\end{tabular}             & 3,989 & 23.07 & 3,152 & 25.24 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Can be\\extracted\end{tabular}                  & 1,874 & 10.84 & 1,371 & 10.98 \\ \hline
 
@@
 
-From this table, we can see that approximately 22 percent of the clones can be refactored through method extraction. For the other clones, we must first build a catalog of appropriate refactorings.
+From this table, we can see that approximately ten percent of the clones can directly be refactored through method extraction.
+For the other clones, we must first build a catalog of appropriate refactorings.
 

### 2019-05-10 sattose/paper.tex
Updates from Overleaf

@@
 Aries \cite{higo2004aries, higo2008metric} focuses on the detection of refactorable clones.
-They basis of the relation between clone instances through inheritance, similar to Fontana et al.
-\cite{fontana2012duplicated}, Aries proposes a refactoring.
-For instance, if two clone classes are siblings of each other (share the same superclass), they propose to perform ``Extract method'' and ``Pull up method'' sequentially.
-This tool only proposes such a refactoring, and does not provide help in the process of applying the refactoring.
+They do this based on the relation between clone instances through inheritance, similar to Fontana et al.
+\cite{fontana2012duplicated}, Aries also proposes a refactoring: if two clone classes are siblings of each other (share the same superclass), they propose to perform ``Extract method'' and ``Pull up method'' sequentially.
+This tool only proposes the refactoring, and does not provide help in the process of applying the refactoring.
 
@@
 \section{Clone Detection}\label{chap:clonedetection}
-As duplication in source code is a serious problem in many software systems, many research efforts look into code clones.
-Many tools have been proposed to detect various types of code clones~\cite{sheneamer2016survey, svajlenko2014evaluating}.
+As duplication in source code is a serious problem in many software systems, many tools have been proposed to detect various types of code clones~\cite{sheneamer2016survey, svajlenko2014evaluating}.
 However, these tools were not yet assessed in terms of automatically refactoring clones.
@@
 \begin{enumerate}
-    \item \textbf{Should find clones in any context.} We want to perform an analysis on a set of projects.
-In this analysis we want to be able to get a full overview of cloning in the set of projects.
-Some tools only find clones in specific contexts, like only method-level clones.
+    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones.
+We want to perform an analysis on all clones in projects to get a complete overview.
 Because of that, we want to use a clone detection tool that is able to find clones in any context.
@@
 However, method extraction is not always possible.
-For instance, if a part of a subtree (in a programs' AST) is matched as a clone.
+For instance, if a part of a subtree (in a programs' AST) is matched as a clone or if the control flow (return, break and continue statements) prohibit extraction.
 Because of this, we chose to measure what percentage of ``Partial Method'' clones are refactorable using method extraction.
 Our results are displayed in table \ref{table:refactorability}.
+In this table we use the following categories:
+\begin{itemize}
+    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a method.
+Then, based on the relation between the clone instances, further refactoring techniques can be used to merge the extracted methods (for instance ``pull up method'' for clones in sibling classes).
+    \item \textbf{Complex control flow:} This clone contains break, continue or return statements.
+    \item \textbf{Spans part of a block:} This clone spans a part of a block, including the declaration. For instance, when an if-statement is matched but not the entirety of its body.
+    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of table \label{table:contents}, the ``extract method'' refactoring technique cannot be applied.
+\end{itemize}
 
@@
 \begin{tabular}[c]{@{}l@{}}Can be\\extracted\end{tabular}                  & 1,874 & 10.84 & 1,371 & 10.98 \\ \hline
-
 \end{tabular}
@@
 
-From this table, we can see that approximately ten percent of the clones can directly be refactored through method extraction.
-For the other clones, we must first build a catalog of appropriate refactorings.
+From this table, we can see that approximately ten percent of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
+For the other clones, other techniques or transformations will be required.
+Looking into these techniques and transformations will be one of our next steps.
 

### 2019-05-10 sattose/paper.tex
Updates from Overleaf

@@
   \caption{Our survey on clone detection tools.} \label{table:dettools}
-  \bigskip
+  \medskip
 \begin{tabular}{|l|l|l|l|l|l|}
@@
 \begin{figure}[H]
+  \caption{Abstract figure of the graph representation built by CloneRefactor}
+  \medskip
   \includegraphics[width=1\columnwidth]{img/CodeGraph}
-  \caption{Abstract figure of the graph representation built by CloneRefactor}
   \label{fig:clonerefactor}
@@
 \begin{figure}[H]
+  \caption{Abstract representation of clone classes and clone instances.}
+    \medskip
     \includegraphics[width=1\columnwidth]{img/context}
-  \caption{Abstract representation of clone classes and clone instances.}
   \label{fig:clonecontext}
@@
   \caption{CloneRefactor results for Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
-  \bigskip
+  \medskip
 \begin{tabular}{|l|l|}
@@
   \caption{CloneRefactor clone detection results for the two different algorithms.} \label{table:clonedet}
-  \bigskip
+  \medskip
 \begin{tabular}{|l|l|l|}
@@
 \begin{figure}[H]
+  \caption{Example of a clone that is not a type 1R clone but is a type 1 clone.}
+  \medskip
     \includegraphics[width=1\columnwidth]{img/clone}
-  \caption{Example of a clone that is not a type 1R clone but is a type 1 clone.}
   \label{fig:type1rclone}
@@
 \begin{figure}[H]
+  \caption{Abstract figure displaying some relations of clone classes. Arrows represent superclass relations.}
+    \medskip
     \includegraphics[width=1\columnwidth]{img/Relation}
-  \caption{Abstract figure displaying some relations of clone classes. Arrows represent superclass relations.}
   \label{fig:clonerelation}
@@
   \caption{Clone relations} \label{table:relations}
-  \bigskip
+  \medskip
 \begin{tabular}{|l|l|l|l|l|} \hline
@@
   \caption{Clone instance locations} \label{table:locations}
-  \bigskip
+  \medskip
 \begin{tabular}{|l|l|l|l|l|}
@@
   \caption{Clone instance contents} \label{table:contents}
-  \bigskip
-\begin{tabular}{|l|l|l|}
+  \medskip
+\begin{tabular}{|l|l|l|l|l|}
   \hline
-  \textbf{Contents}                                                        & \textbf{Amount} & \textbf{Percentage} \\ \hline
-  Partial Method                                                           & 19,264          & 56.07               \\ \hline
-  Several Methods                                                          & 9,076           & 26.41               \\ \hline
-  Includes Constructor                                                     & 1,528           & 4.45                \\ \hline
-  Includes Field                                                           & 1,149           & 3.34                \\ \hline
-  Partial Constructor                                                      & 1,098           & 3.20                \\ \hline
-  Only Fields                                                              & 565             & 1.64                \\ \hline
-  Full Method                                                              & 554             & 1.61                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Class\\ Declaration\end{tabular}     & 445             & 1.30                \\ \hline
-  Other                                                                    & 369             & 1.07                \\ \hline
-  Full Class                                                               & 192             & 0.56                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Constant\end{tabular}         & 52              & 0.15                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Declaration\end{tabular}      & 47              & 0.14                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Interface\\ Declaration\end{tabular} & 10              & 0.03                \\ \hline
-  Full Interface                                                           & 6               & 0.02                \\ \hline
-  Full Enumeration                                                         & 4               & 0.01                \\ \hline
+  \textbf{Contents} & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
+  Partial Method                                                           & 32,214 & 56.07 & 19,264 & 56.07 \\ \hline
+  Several Methods                                                          & 10,542  & 26.41 & 19,264 & 56.07 \\ \hline
+  Includes Constructor                                                     & 1,772  & 4.45  & 19,264 & 56.07 \\ \hline
+  Includes Field                                                           & 1,681  & 3.34  & 19,264 & 56.07 \\ \hline
+  Partial Constructor                                                      & 1,389  & 3.20  & 19,264 & 56.07 \\ \hline
+  Only Fields                                                              & 962    & 1.64  & 19,264 & 56.07 \\ \hline
+  Full Method                                                              & 647    & 1.61  & 19,264 & 56.07 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Class\\ Declaration\end{tabular}     & 445    & 1.30  & 19,264 & 56.07 \\ \hline
+  Other                                                                    & 369    & 1.07  & 19,264 & 56.07 \\ \hline
+  Full Class                                                               & 192    & 0.56  & 19,264 & 56.07 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Constant\end{tabular}         & 52     & 0.15  & 19,264 & 56.07 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Declaration\end{tabular}      & 47     & 0.14  & 19,264 & 56.07 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Interface\\ Declaration\end{tabular} & 10     & 0.03  & 19,264 & 56.07 \\ \hline
+  Full Interface                                                           & 6      & 0.02  & 19,264 & 56.07 \\ \hline
+  Full Enumeration                                                         & 4      & 0.01  & 19,264 & 56.07 \\ \hline
 \end{tabular}
@@
   \caption{Refactorability through method extraction} \label{table:refactorability}
-  \bigskip
+  \medskip
 \begin{tabular}{|l|l|l|l|l|}

### 2019-05-10 sattose/paper.tex
Contents

--- 2019-05-10 sattose/paper.tex
@@
 However, instead of building a dependency graph, we build a similarity graph of statements linking to similar statements.
-The graph built by CloneRefactor is shown in figure \ref{fig:clonerefactor}.
+The graph built by CloneRefactor is shown in Figure \ref{fig:clonerefactor}.
 
@@
 
-Running our clone detection script, CloneRefactor, over this corpus gives the results displayed in table \ref{table:general}.
+Running our clone detection script, CloneRefactor, over this corpus gives the results displayed in Table \ref{table:general}.
 
@@
 The second algorithm implements our type 1R, as explained in section \ref{chap:type1clones}.
-The differences between the clones found for these algorithms is displayed in table \ref{table:clonedet}.
+The differences between the clones found for these algorithms is displayed in Table \ref{table:clonedet}.
 Please note that the amount of lines, statements and tokens is without whitespace, newlines and comments.
@@
 
-Looking at table \ref{table:clonedet}, it becomes apparent that the type 1R algorithm finds significantly less clones found than the type 1 algorithm.
+Looking at Table \ref{table:clonedet}, it becomes apparent that the type 1R algorithm finds significantly less clones found than the type 1 algorithm.
 Figure \ref{fig:type1rclone} displays an example of a clone that does get detected by the type 1 algorithm but does not get detected by the type 1R algorithm.
@@
 To do this, they first define several categories for the relation between clone instances in object-oriented languages.
-A few of these categories are shown in figure \ref{fig:clonerelation}.
+A few of these categories are shown in Figure \ref{fig:clonerelation}.
 These categories are as follows:
@@
 We validated this claim over our corpus.
-The results for the clone instance locations are shown in table \ref{table:locations}.
+The results for the clone instance locations are shown in Table \ref{table:locations}.
 We chose the following categories:
@@
 
-The results for these categories are displayed in table \ref{table:contents}.
+The results for these categories are displayed in Table \ref{table:contents}.
 
@@
   \caption{Clone instance contents} \label{table:contents}
-  \bigskip
-\begin{tabular}{|l|l|l|}
+  \medskip
+\begin{tabular}{|l|l|l|l|l|}
   \hline
-  \textbf{Contents}                                                        & \textbf{Amount} & \textbf{Percentage} \\ \hline
-  Partial Method                                                           & 19,264          & 56.07               \\ \hline
-  Several Methods                                                          & 9,076           & 26.41               \\ \hline
-  Includes Constructor                                                     & 1,528           & 4.45                \\ \hline
-  Includes Field                                                           & 1,149           & 3.34                \\ \hline
-  Partial Constructor                                                      & 1,098           & 3.20                \\ \hline
-  Only Fields                                                              & 565             & 1.64                \\ \hline
-  Full Method                                                              & 554             & 1.61                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Class\\ Declaration\end{tabular}     & 445             & 1.30                \\ \hline
-  Other                                                                    & 369             & 1.07                \\ \hline
-  Full Class                                                               & 192             & 0.56                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Constant\end{tabular}         & 52              & 0.15                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Declaration\end{tabular}      & 47              & 0.14                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Interface\\ Declaration\end{tabular} & 10              & 0.03                \\ \hline
-  Full Interface                                                           & 6               & 0.02                \\ \hline
-  Full Enumeration                                                         & 4               & 0.01                \\ \hline
+  \textbf{Contents} & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Partial\\Method\end{tabular}                                                           & 32,214 & 64.72 & 18,791 & 57.37 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Several\\Methods\end{tabular}                                                          & 10,542 & 21.18 & 8,514 & 25.99 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes\\Constructor\end{tabular}                                                     & 1,772  & 3.56  & 1,213 & 3.70 \\ \hline
+  Includes Field                                                           & 1,681  & 3.38  & 1,487 & 4.54 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Partial\\Constructor\end{tabular}                                                      & 1,389  & 2.79  & 1,078 & 3.29 \\ \hline
+  Only Fields                                                              & 962    & 1.93  & 888 & 2.71 \\ \hline
+  Full Method                                                              & 647    & 1.30  & 284 & 0.87 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Class\\Declaration\end{tabular}     & 263    & 0.53  & 258 & 0.79 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Other\\Categories\end{tabular}                                                         & 304    & 0.61  & 243 & 0.74 \\ \hline
 \end{tabular}
@@
 Because of this, we chose to measure what percentage of ``Partial Method'' clones are refactorable using method extraction.
-Our results are displayed in table \ref{table:refactorability}.
+Our results are displayed in Table \ref{table:refactorability}.
 In this table we use the following categories:
@@
     \item \textbf{Spans part of a block:} This clone spans a part of a block, including the declaration. For instance, when an if-statement is matched but not the entirety of its body.
-    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of table \label{table:contents}, the ``extract method'' refactoring technique cannot be applied.
+    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of table \ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
 \end{itemize}

### 2019-05-10 sattose/paper.tex
Finished the text I guess

@@
 Unsurprisingly, most clones span a part of a method.
-Just 1.6\% of the methods are cloned fully.
-More than a quarter of the clones spans over several methods, which makes extracting methods won't work in a case where a clone spans over several methods.
-About 4.5\% of clones include a constructor.
-About 3.3\% of clones include a global variable defined in a class.
+More than a quarter of the clones (for type 1R) span over several methods, which either requires more advanced refactoring techniques or indicates a non-harmful clone.
 

### 2019-05-10 sattose/paper.tex
Sander comments

@@
 Section \ref{chap:mergingdups} shows our measurements regarding the amount of clones that can be refactored through method extraction.
-Section \ref{chap:threatstovalidity} shows the threats to validity of this study and section \ref{chap:conclusion} draws a conclusion on our preliminary results.
+Section \ref{chap:threatstovalidity} shows the threats to validity of this study and section \ref{chap:conclusion} draws a conclusion based on our preliminary results.
 
@@
 This tool only focuses on refactoring clone pairs, with the authors arguing that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.
+We further look into these measurements in section \ref{chap:relationsinstances}.
 
@@
 Because of that, we want to use a clone detection tool that is able to find clones in any context.
-\item \textbf{Should detect clone classes in a number of example projects.} We have created a number of test projects\footnote{Our test projects to assess the validity of clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} that we used to assess the validity of clone detection tools.
+\item \textbf{Should find all clones in created test projects.} We have created a number of test projects\footnote{Our test projects to assess the validity of clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} that we used to assess the validity of clone detection tools.
 On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
@@
 Because of this, we want to use a clone detection tool that can analyze such structures.
-\item \textbf{Makes it possible to configure the way in which clones are detected (as in what to exclude from the detection) in a relatively straightforward way.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}).
-To achieve this, the tool needs to be able to recognize the meaning of certain tokens.
+\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}).
+To achieve this, the tool needs to be able to allow those threshold changes.
+This can be either through simple changes of the source code, or by using some configuration file.
 \end{enumerate}
@@
 CPD \cite{roy2009comparison}\footnote{} & \checkmark & \checkmark            &             &             \\ \hline
-\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ CCFinderX\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
+\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
 CCFinderSW \cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
@@
   \item \textbf{Number of tokens:} The number of tokens (excluding whitespace, end-of-line terminators and comments) that should be equal/similar for it to be considered a clone.
-  \item \textbf{Number of lines:} The minimum amount of lines (excluding lines that do not contain any tokens, for tokens same exclusions apply) that should be equal/similar for it to be considered a clone.
+  \item \textbf{Number of lines:} The minimum amount of lines (excluding lines that do not contain any tokens) that should be equal/similar for it to be considered a clone.
 \end{enumerate}
 Of course, if any threshold is set to zero, it will be ignored, thus not all thresholds have to be used at all times.
-We consider ``number of lines'' to be the least important, as it highly depends on the programmer of the codebase (and we do not want this kind of dependence!).
+We consider ``number of lines'' to be the least important, as it highly depends on the programmer of the codebase (and we want to prevent this dependence).
 On basis of manual assessment, we have determined that setting the ``number of statements/declarations'' to 6 ensures that most non-harmful clones are filtered out.
@@
 \subsection{Type 1R clones} \label{chap:type1clones}
-Type 1, as defined in literature~\cite{roy2007survey}, clones are identical clone fragments except for variations in whitespace and comments.
+Type 1 clones, as defined in literature~\cite{roy2007survey}, are identical clone fragments except for variations in whitespace and comments.
 However, when two clone fragments are textually identical, it does not yet indicate that they are actually identical.
@@
 To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
-  \item \textbf{Compare the equality of the fully qualified indentifier for method references and call signatures.}
+  \item \textbf{Compare the equality of the fully qualified identifier for method references and call signatures.} This is to prevent a change in functionality after merging the clone, as methods with equal names/parameters can still contain different functionality.
 \end{itemize}
@@
 By its definition in literature, type 2 clones allow any change in identifiers, literals, types, layout, and comments.
-For refactoring purposes, this does not always make a lot of sense.
+For refactoring purposes, this definition is unsuitable.
 If we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
 This could render two methods that have an entirely different functionality as clones.
-Merging such clones might only prove to be harmful.
+Merging such clones can be harmful instead of helpful.
 
-We tackle these problems with type 2 clones to be able to detect such clones that can and should be merged.
+We tackle these problems with type 2R clones to be able to detect such clones that can and should be merged.
 Our definition ensures functional similarity by applying the following changes to type 2 clones:
@@
 
-Looking at Table \ref{table:clonedet}, it becomes apparent that the type 1R algorithm finds significantly less clones found than the type 1 algorithm.
-Figure \ref{fig:type1rclone} displays an example of a clone that does get detected by the type 1 algorithm but does not get detected by the type 1R algorithm.
-This is because the variable ``key'' and ``prefix'' are of a different primitive type between the clone instances.
-This makes this clone less suitable for automated refactoring.
-We manually checked some differences between the detected type 1 clones and type 1R clones and in each instance there was either a variable with different type, a different method call or a different type (but textual equality).
+Looking at table \ref{table:clonedet}, it becomes apparent that the type 1R algorithm finds significantly less clones than the type 1 algorithm.
 This indicates that about a third of the clones have textual equality, but are not actually equal when considering the types of expressions.
-
-\begin{figure}[H]
-  \caption{Example of a clone that is not a type 1R clone but is a type 1 clone.}
-  \medskip
-    \includegraphics[width=1\columnwidth]{img/clone}
-  \label{fig:type1rclone}
-\end{figure}
+This makes these clones less suitable for automated refactoring.
 

### 2019-05-10 sattose/paper.tex
Cutting content

@@
 For instance, ``clone pair''is defined as \textit{a set of two code portions/fragments which are identical or similar to each other}; ``clone class'' as \textit{the union of all clone pairs}; ``clone instance'' as a single code portion/fragment that is part of either a clone pair or clone class.
+
 \subsection{Advantages of clone classes over clone pairs}\label{chap:cloneclasses}
-Regarding clone detection, there is a lot of variability in literature whether clone pairs or clone classes should be detected.
+Regarding clone detection, there is a lot of variability in literature whether clone pairs or clone classes should be considered for detection.
 In this study we focus on clone classes, because of the advantages for refactoring.
@@
 It also makes the clone harder to refactor, as more transformations would be required.
-Higher clone types also become more disputable whether they actually indicate a harmful antipattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}).
+Higher clone types also become more disputable whether they actually indicate a harmful anti-pattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}).
+
 \subsection{Related work in clone refactoring tools}
@@
 
-There is various other research that investigates refactoring code clones \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}.
+There are various other researches that investigate refactoring code clones \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}.
 However, all of these tools only support a subset of all harmful clones that are found.
@@
 We want to perform an analysis on all clones in projects to get a complete overview.
-Because of that, we want to use a clone detection tool that is able to find clones in any context.
-\item \textbf{Should find all clones in created test projects.} We have created a number of test projects\footnote{Our test projects to assess the validity of clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} that we used to assess the validity of clone detection tools.
+\item \textbf{Should find all clones in created test projects.} We have created a number of test projects that we used to assess the validity of clone detection tools.
 On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
-\item \textbf{Considers dependency graphs to be sure that this clone can be merged.} When detecting clones for refactoring purposes, it is important that clone instances are actually equal.
+\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances are actually equal.
 Sometimes, to verify actual equality (not just textual equality), it is required to consider resolved symbols (this is described more elaborately in section \ref{chap:type1clones}).
@@
 Siamese \cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
-NiCAD \cite{roy2008nicad, cordy2011nicad} \footnote{}           & \checkmark                             & \checkmark            &             &             \\ \hline
-CPD \cite{roy2009comparison}\footnote{} & \checkmark & \checkmark            &             &             \\ \hline
+NiCAD \cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
+CPD \cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
 \begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
@@
 
-\footnotetext[3]{This clone detection tool has also been used by Fontana et al. \cite{fontana2012duplicated}}
-\footnotetext{\label{note1}CPD is a Clone Detection tool that is part of PMD. PMD is a widely used tool for static code analysis in Java.}
-
-None of the tools we considered implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
+None of the tools we considered implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}.
+This repo contains all scripts that were used to retrieve the data that is displayed in this paper.}.
 
@@
 
-We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is compatible with all modern Java versions (Java 1-12).
-We collect each statement and declaration and compare those to find duplicates.
-This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically).
-On basis of this graph we detect clone classes.
-
-We challenge completed clone classes against the thresholds that are being used, and remove the clone classes that do not adhere to the thresholds.
-
 \begin{figure}[H]
@@
 \end{figure}
+
+We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is compatible with all modern Java versions (Java 1-12).
+We collect each statement and declaration and compare those to find duplicates.
+This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically).
+On basis of this graph we detect clone classes.
+We challenge completed clone classes against the thresholds that are being used, and remove the clone classes that do not adhere to the thresholds.
 
@@
 \subsection{The challenge of detecting these clones}\label{chap:challenge}
-Detecting these clone types comes with serious challenges.
-For each of these types of clones we need to parse the fully qualified identifier of all types, method calls and variables.
+To detect each type of clone, we need to parse the fully qualified identifier of all types, method calls and variables.
 This comes with serious challenges, regarding both performance and implementation.
-To be able to parse all fully qualified identifiers, and trace the declarations of variables, we might to follow cross file references.
+Also, to be able to parse all fully qualified identifiers, and trace the declarations of variables, we might need to follow cross file references.
 The referenced types/variables/methods might even not be part of the project, but rather of an external library or the standard libraries of the programming language.
-All these need to be considered for the referenced entity to be found, on basis of which a fully qualified identifier can be created.
+All these factors need to be considered for the referenced entity to be found, on basis of which a fully qualified identifier can be created.
 
 In our CloneRefactor tool we use JavaParser \cite{tomassetti2017javaparser}.
-JavaParser has a build in symbol solver.
-This symbol solver can automatically resolve types, method calls and variables.
+JavaParser has a build in symbol solver, which can automatically resolve types, method calls and variables.
 However, because of this, CloneRefactor does require all libraries that the software project requires (apart from the Java Standard Library).
@@
 \end{enumerate}
-Figure \ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
-The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
-The location and contents of clones is measured on clone instance level.
-A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50).
-A clone instance contents consists of a list of all statements and declarations it spans.
+
 \begin{figure}[H]
@@
 \end{figure}
-%\todo{do we have proof of this statement?
-if not, say that this is our intuition and a first step to prove it is to analyze a large body of projects} Everything in the context of a clone has a big impact on how it has to be refactored.
-% I guess it's a bit of an empty statement. Of course where some code is located has an impact on how to refactor it. Maybe remove it?
+
+Figure \ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
+The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
+The location and contents of clones is measured on clone instance level.
+A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50).
+A clone instance contents consists of a list of all statements and declarations it spans.
+
 We analyzed the context of clones in a large corpus of open source projects.
-For these experiments, we used the CloneRefactor tool.
-These experiments map the context, as follows: the relation between clone instances is explained, measured and discussed in section\ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in section \ref{chap:clonelocation};  the content of clone instances are explained, measured and discussed in section \ref{chap:clonecontents}.
+For these experiments, we used our CloneRefactor tool.
+These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in section \ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in section \ref{chap:clonelocation};  the content of clone instances are explained, measured and discussed in section \ref{chap:clonecontents}.
 
 \subsection{The corpus}\label{chap:corpus}
-For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}\footnote{The corpus can be downloaded from the following URL: \url{http://groups.inf.ed.ac.uk/cup/javaGithub/java_projects.tar.gz}}.
+For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}.
 This corpus has been assembled to contain relatively higher quality projects.
@@
 As no \texttt{pom.xml} files are included in the corpus, we cloned the latest version of each project in the corpus.
-We then removed each project that contained no ``pom.xml'' file (a file that describes the dependencies used by the project).
-We then filtered the corpus further to make sure each project contained a ``src/main/java'' folder, to be sure no test files or other redundant sources are included in the clone detection.
-As a final step, we collected all dependencies for each project by using the \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib} Maven command, and removed each project for which not all dependencies were available (due to non-Maven dependencies being used or unsatisfiable dependencies being referenced in the ``pom.xml'' file).
+We then removed each project that has no \texttt{pom.xml} file.
+As a final step, we collected all dependencies for each project by using the \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib} Maven command, and removed each project for which not all dependencies were available (due to non-Maven dependencies being used or unsatisfiable dependencies being referenced in the \texttt{pom.xml} file).
 
@@
 The differences between the clones found for these algorithms is displayed in Table \ref{table:clonedet}.
-Please note that the amount of lines, statements and tokens is without whitespace, newlines and comments.
 
@@
 
-Looking at table \ref{table:clonedet}, it becomes apparent that the type 1R algorithm finds significantly less clones than the type 1 algorithm.
+Looking at Table \ref{table:clonedet}, it becomes apparent that the type 1R algorithm finds significantly less clones than the type 1 algorithm.
 This indicates that about a third of the clones have textual equality, but are not actually equal when considering the types of expressions.

### 2019-05-10 sattose/paper.tex
Final version (ship it!)

@@
 
-\section{Merging duplicate code through refactoring}\label{chap:mergingdups}
-Now we have mapped the contexts in which clones occur, we can start looking at refactoring opportunities.
-Regarding refactoring, we separate clones in two categories: easy and difficult refactoring opportunities.
-Easy refactoring opportunities are clones that can easily be automatically refactored.
-Examples of these opportunities are fully cloned methods or a set of fully cloned statements.
-According to the relation between the clone instances, we can propose a refactoring automatically.
-
-However, a clone is not always easily merged.
+\section{Merging duplicate code through method extraction}\label{chap:mergingdups}
+The most used technique to merge clones is method extraction (creating a new method on basis of the contents of clones).
+However, method extraction cannot be applied in all cases.
 Sometimes a clone spans a statement partially (like a for-loop of which only it's declaration and a part of the body is cloned).
 Merging the clones can be harder in such instances.
-Also, the cloned code can contain statements like labels, return, break, continue, etc.
-In such instances, more conditions may apply to be able to conduct a refactoring, if advisable at all.
+Also, the cloned code can contain statements like \texttt{return}, \texttt{break}, \texttt{continue}.
+In these instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.
 
-The most trivial way to merge a clone is through method extraction.
-However, method extraction is not always possible.
-For instance, if a part of a subtree (in a programs' AST) is matched as a clone or if the control flow (return, break and continue statements) prohibit extraction.
-Because of this, we chose to measure what percentage of ``Partial Method'' clones are refactorable using method extraction.
+We measured the amount of clones that can be refactored through method extraction (without additional transformations being required).
 Our results are displayed in Table \ref{table:refactorability}.
@@
 Then, based on the relation between the clone instances, further refactoring techniques can be used to merge the extracted methods (for instance ``pull up method'' for clones in sibling classes).
-    \item \textbf{Complex control flow:} This clone contains break, continue or return statements.
-    \item \textbf{Spans part of a block:} This clone spans a part of a block, including the declaration. For instance, when an if-statement is matched but not the entirety of its body.
-    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of table \ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
+    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements.
+    \item \textbf{Spans part of a block:} This clone spans a part of a statement.
+    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table \ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
 \end{itemize}
@@
 
-From this table, we can see that approximately ten percent of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
+From Table \ref{table:refactorability}, we can see that approximately ten percent of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
 For the other clones, other techniques or transformations will be required.
@@
 \section{Threats to validity}\label{chap:threatstovalidity}
-We noticed that, when measuring over a corpus of this size, the thresholds that we use for the clone detection have a big impact on the results.
+We noticed that, when doing measurements on a corpus of this size, the thresholds that we use for the clone detection have a big impact on the results.
 There does not seem to be one golden set of thresholds, some thresholds work in some situations but fail in others.
@@
 \begin{itemize}
-    \item We proposed a method in which we can detect clones that can/should be refactored.
+    \item We proposed a method with which we can detect clones that can/should be refactored.
     \item We mapped the context of clones in a large corpus of open source systems.
-    \item We mapped the opportunities to perform method extraction on clones in a large corpus of open source systems.
+    \item We mapped the opportunities to perform method extraction on clones this corpus.
 \end{itemize}
 
-We have into existing definitions for different types of clones \cite{roy2007survey} and proposed solutions for problems that these types have with regards to automated refactoring.
-We propose that fully qualified identifiers of method call signatures and type references should be considered instead of their plain text representation.
-Furthermore, we should define thresholds for variability in variables, literals and method calls, in order to limit the number of parameters that the merged unit shall have.
+We have looked into existing definitions for different types of clones \cite{roy2007survey} and proposed solutions for problems that these types have with regards to automated refactoring.
+We propose that fully qualified identifiers of method call signatures and type references should be considered instead of their plain text representation, to ensure refactorability.
+Furthermore, we propose that one should define thresholds for variability in variables, literals and method calls, in order to limit the number of parameters that the merged unit shall have.
 
@@
 For about a fourth of the clone classes all of its instances are in the same class.
-For about a sixth of the clone classes have clone instances that are siblings of each other (share the same superclass).
+About a sixth of the clone classes have clone instances that are siblings of each other (share the same superclass).
 
 Secondly, we looked at the location of clone instances.
-Most clone instances are found at method level, about 58 percent.
-About 39 percent of clone instances were found at class level.
+Most clone instances (58 percent) are found at method level.
+About 37 percent of clone instances were found at class level.
 We defined ``class level clones'' as clones that exceed the boundaries of a single method or contain something else in the class (like field declarations, other methods, etc.).
 Thirdly, we looked at the contents of clone instances.
-Most clones span a part of a method (56 percent).
+Most clones span a part of a method (57 percent).
 About 26 percent of clones span over several methods.
@@
 We also looked into the refactorability of clones that span a part of a method.
-Over 22 percent of the clones can directly be refactored by extracting them to a new method (and calling the method at all usages using their relation).
-The main reason that most clones that span a part of a method cannot directly be refactored by method extraction, is that they are nested in such a way that method extraction would leave side effects (for instance, we cannot extract half of a for-loop).
+Over 10 percent of the clones can directly be refactored by extracting them to a new method (and calling the method at all usages using their relation).
+The main reason that most clones that span a part of a method cannot directly be refactored by method extraction, is that they contain \texttt{return}, \texttt{break} or \texttt{continue} statements.
 
 \subsection{Next steps}
-The next step is to integrate our solutions for the problems related to clone types into our CloneRefactor tool.
-This way, we can perform our experiments for these novel clone definitions.
-We are curious to see how it compares with the results we had so far.
-
-Furthermore, we want to start automatically refactoring clones.
-On basis of our initial results, we have determined that we can best start with the automatic refactoring of clones that can be extracted to a method.
-If this works, we can already decrease duplication by 22\%.
+The next step is to integrate our type 2R and type 3R definitions into our CloneRefactor tool.
+We then will look into appropriate thresholds for these types of clones.
+We can then re-run all scripts for type 2R and 3R clones.
+On basis of these results, we can prioritize implementing automated refactorings.
 

### 2019-05-10 sattose/paper.tex
Various changes

@@
 Our intermediate results indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
-Approximately ten percent of the duplication can be refactored through method extraction without extra considerations required, while other clones require other refactoring techniques.
+Approximately ten percent of the duplication can be refactored through method extraction without extra considerations required, while other clones require other refactoring techniques or further transformations.
 Similar future measurements will provide further insight into the contexts where clones occur and how this affects the automated refactoring process.
@@
 
-Running our clone detection script, CloneRefactor, over this corpus gives the results displayed in Table \ref{table:general}.
+Some general data regarding this corpus is displayed in Table \ref{table:general}.
 
@@
 \begin{tabular}{|l|l|l|l|l|} \hline
-\textbf{Relation}  & \textbf{\# (1)} & \textbf{\% (1)}  & \textbf{\# (1R)} & \textbf{\% (1R)} \\ \hline
+\textbf{Relation}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
 Unrelated          & 6,134           & 35.48  & 4,762 & 38.14            \\ \hline
@@
 
-Another thread to validity is that currently, in a very small number of cases, clone detection might result in a false positive.
-This is in cases where two lines are equal, but they actually call different methods with the same method signature.
-In such a case, merging such clones might turn out to change the functionality of the program.
-Solving this problem is one of our next steps in this research.
-
 \section{Conclusion and next steps}\label{chap:conclusion}

### 2019-05-13 sattose/paper.tex
Some small paper changes
Ana's latest feedback

@@
 In this study, we look into the opportunities to automatically refactor these duplication problems for object-oriented programming languages.
-To do this, we propose a method to detect clones that are suitable for refactoring.
-This method focuses on the context and scope of clones, ensuring our refactoring improves the design and does not leave side effects after it is applied.
+We propose a method to detect clones that are suitable for refactoring.
+This method focuses on the context and scope of clones, ensuring our refactoring improves the design and does not created side effects.
 
@@
 However, there are also refactoring opportunities that are rather trivial and repetitive to execute.
-In this research, we investigate the extent to which code clones can be automatically refactored.
+Our goal is investigating to what extend code clones can be automatically refactored.
 
 A survey by Roy et al.
-\cite{roy2007survey} describes different types of clones.
-Most clone detection tools focus on finding clones corresponding with these definitions.
+\cite{roy2007survey} describes various ways in which clones can be identified.
+Most clone detection tools focus on finding clones that align with these definitions.
 In this paper, we outline challenges with these clone type definitions when considered in a refactoring context.
@@
 We focus mainly on the Java programming language as refactoring opportunities feature paradigm and programming language dependent aspects~\cite{choi2011extracting}.
-However, most practices featured in this research will also be applicable to other object-oriented languages, like C\#.
+However, most practices featured currently in our work will also be applicable to other object-oriented languages, like C\#.
+This is because these programming languages share many similarities regarding refactoring opportunities.
 
-In this research, we strive to improve upon the current state-of-the-art in clone refactoring \cite{fontana2015duplicated, alwaqfi2017refactoring} by building a clone refactoring tool that automatically applies refactorings to a large percentage of clones found.
-The design decisions for this tool are made on basis of data gathered from a large corpus of software systems.
+Our end goal is to improve upon the current state-of-the-art in clone research \cite{fontana2015duplicated, alwaqfi2017refactoring} by building a clone refactoring tool that automatically applies refactorings to a large percentage of clones found.
+The design decisions for this tool are made on basis of data gathered from a large corpus of software systems together with our own experience and findings from literature.
 
@@
 Regarding clone detection, there is a lot of variability in literature whether clone pairs or clone classes should be considered for detection.
-In this study we focus on clone classes, because of the advantages for refactoring.
+We focus on clone classes, because of the advantages for refactoring.
 Clone pairs do not provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}.
 Although clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered.
-There is also another issue that results from grouping clones by pairs: clone reference amount increases according to the binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), which causes a heavy information redundancy \cite{fontana2012duplicated}.
+Another issue that results from grouping clones by pairs: clone reference amount increases according to the binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), which causes a heavy information redundancy \cite{fontana2012duplicated}.
 
@@
 The Duplicated Code Refactoring Advisor (DCRA) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated, fontana2015duplicated}.
-This tool only focuses on refactoring clone pairs, with the authors arguing that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.
+DCRA only focuses on refactoring clone pairs, with the authors arguing that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.
 We further look into these measurements in section \ref{chap:relationsinstances}.
@@
 They do this based on the relation between clone instances through inheritance, similar to Fontana et al.
-\cite{fontana2012duplicated}, Aries also proposes a refactoring: if two clone classes are siblings of each other (share the same superclass), they propose to perform ``Extract method'' and ``Pull up method'' sequentially.
+\cite{fontana2012duplicated}.
+Aries also proposes a refactoring: if two clone classes are siblings of each other (share the same superclass), they propose to perform ``Extract method'' and ``Pull up method'' sequentially.
 This tool only proposes the refactoring, and does not provide help in the process of applying the refactoring.
 
-There are various other researches that investigate refactoring code clones \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}.
+We investigated several research efforts that look into code clone refactoring \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}.
 However, all of these tools only support a subset of all harmful clones that are found.
@@
 The results of our survey are displayed in table~\ref{table:dettools}.
-We chose a set of tools that are open source and can analyze either Java or Python.
-Next we formulate the following four criteria by which we analyze these tools:
+We chose a set of tools that are open source and can analyze a popular object-oriented programming language.
+Next, we formulate the following four criteria by which we analyze these tools:
 \begin{enumerate}
@@
 We want to perform an analysis on all clones in projects to get a complete overview.
-\item \textbf{Should find all clones in created test projects.} We have created a number of test projects that we used to assess the validity of clone detection tools.
+\item \textbf{Should find all clones in created control projects.} We assembled a number of test projects to assess the validity of clone detection tools.
 On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
-\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances are actually equal.
-Sometimes, to verify actual equality (not just textual equality), it is required to consider resolved symbols (this is described more elaborately in section \ref{chap:type1clones}).
+\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be merged.
+Sometimes, textual equality between code fragments does not imply that these can be merged (this is described more elaborately in section \ref{chap:type1clones}).
 Because of this, we want to use a clone detection tool that can analyze such structures.
@@
 
-None of the tools we considered implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}.
-This repo contains all scripts that were used to retrieve the data that is displayed in this paper.}.
+None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}.
+This repository contains all scripts that were used to retrieve the data that is displayed in this paper.}.
 
@@
 We decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing}.
-However, instead of building a dependency graph, we build a similarity graph of statements linking to similar statements.
+However, instead of building a dependency graph, we build a similarity graph of statements (linking to similar statements).
 The graph built by CloneRefactor is shown in Figure \ref{fig:clonerefactor}.
@@
 We collect each statement and declaration and compare those to find duplicates.
-This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically).
+We build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically).
 On basis of this graph we detect clone classes.
-We challenge completed clone classes against the thresholds that are being used, and remove the clone classes that do not adhere to the thresholds.
+We compare clone classes against the thresholds, and remove the clone classes that do not pass the test.
 
@@
 Of course, if any threshold is set to zero, it will be ignored, thus not all thresholds have to be used at all times.
-We consider ``number of lines'' to be the least important, as it highly depends on the programmer of the codebase (and we want to prevent this dependence).
-On basis of manual assessment, we have determined that setting the ``number of statements/declarations'' to 6 ensures that most non-harmful clones are filtered out.
+We consider ``number of lines'' to be the least important, as it highly depends on the developer of the codebase (and we want to prevent this dependence).
+Empirical research indicates that setting the ``number of statements/declarations'' to 3 ensures that many non-harmful clones are filtered out, as lower thresholds detect many clones that pose no harm to the design of the code.
 On the downside, this also filters out some harmful antipatterns.
-For instance, if a cloned statement has many tokens we might want to consider it a clone even if it spans less than 6 statements (as a cloned line with many tokens is more harmful than one with few).
+For instance, if a cloned statement has many tokens we might want to consider it a clone even if it spans a single statement (as a cloned line with many tokens is more harmful than one with few).
 
@@
 \begin{itemize}
-  \item \textbf{Number of statements/declarations:} 3
+  \item \textbf{Number of statements/declarations:} 1
   \item \textbf{Number of tokens:} 12
@@
 \section{Addressing problems with clone type definitions}\label{chap:clonetypes}
-We propose solutions for shortcomings in type 1, type 2 and type 3 clones~\cite{roy2007survey} (see section \ref{chap:backgroundclonetypes} for these definitions) to increase the chance that we can merge the clone while improving the design.
+For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings (see section \ref{chap:backgroundclonetypes} for these definitions) to increase the chance that we can merge the clone while improving the design.
 Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.
@@
 \subsection{Type 1R clones} \label{chap:type1clones}
-Type 1 clones, as defined in literature~\cite{roy2007survey}, are identical clone fragments except for variations in whitespace and comments.
-However, when two clone fragments are textually identical, it does not yet indicate that they are actually identical.
-Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type.
-This could invalidate a refactoring opportunity for such a code fragment.
+Type 1 clones are identical clone fragments except for variations in whitespace and comments.
+However, when two clone fragments are textually identical, it does not yet indicate that they are functionally identical.
+Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and even variables can be of a different type.
+In such cases refactoring opportunities could be invalidated.
 Therefore, we propose an alternative definition of type 1 clones.
-We have named this it ``type 1R clones'', to indicate that this definition is separate from type 1 clones in literature.
-The ``R'' stands for refactoring, to indicate that this is type is refactoring oriented (and may be less suitable for, for instance, large scale clone analysis).
-Type 1R clones differ from type 1 clones by the following aspects:
+We have named it ``type 1R clones''.
+The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).
+Type 1R clones differ from type 1 clones as follows:
 \begin{itemize}
@@
 \texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object).
-This way we can validate whether two method references, like method calls, are actually equal.
+This way we can validate whether two method references, like method calls, are functionally equal.
 In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments.
@@
 \subsection{Type 2R clones}
-By its definition in literature, type 2 clones allow any change in identifiers, literals, types, layout, and comments.
-For refactoring purposes, this definition is unsuitable.
-If we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
+Type 2 clones allow any change in identifiers, literals, types, layout, and comments.
+For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
 This could render two methods that have an entirely different functionality as clones.
@@
 \begin{itemize}
-  \item \textbf{Considering types:} The definition of type 2 clones states that types should not be considered.
-We disagree because types can make a significant change to the meaning of a code segment and thus whether this segment should be considered a clone.
-  \item \textbf{Having a distinction between different variables:} By the definition of type 2 clones, any identifiers would not be taken into account.
+  \item \textbf{Considering types:} Type 2 clones do not consider types.
+However, this can make a code fragment very hard to refactor, as different types can describe different functional concepts.
+Because of this, we propose that type 2R clones should consider types like type 1R clones do.
+  \item \textbf{Having a distinction between different variables:} For type 2 clones, no identifiers would be taken into account.
 We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables.
@@
 Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
-  \item \textbf{Defining a threshold for variability in literals:} By the definition of type 2 clones any literals would not be taken into account.
-We agree, as when merging the clone (for instance by extracting a method), we can simply turn the literal into a method parameter.
+  \item \textbf{Defining a threshold for variability in literals:} For type 2 clones no literals would be taken into account.
+We agree, as when merging the clone (for example by extracting a method), we can turn the literal into a method parameter.
 However, we would argue that thresholds matter here.
@@
 However, because of this, completely different methods can be called in cloned fragments as a result.
-This poses serious challenges on refactoring and makes it more disputable whether such a clone is actually harmful.
+This poses serious challenges on refactoring and makes it more disputable whether such a clone is harmful for the maintainability of the code.
 This is because different method identifiers can describe a completely different functionality.
@@
 Clone instances in type 3 clones are almost always different in functionality.
-As we have to ensure equal functionality after merging the clone, we have to wrap the difference in statements between the clone instances in conditional blocks (either if-statements or switch-statements).
+As we have to ensure equal functionality after merging the clone, we have to wrap the difference in statements between the clone instances in conditional blocks.
 We can then pass a variable to indicate which path should be taken through the code (either a boolean or an enumeration).
@@
 
-In our CloneRefactor tool we use JavaParser \cite{tomassetti2017javaparser}.
-JavaParser has a build in symbol solver, which can automatically resolve types, method calls and variables.
+CloneRefactor uses JavaParser \cite{tomassetti2017javaparser}.
+JavaParser has a built-in symbol solver, which can automatically resolve types, method calls and variables.
 However, because of this, CloneRefactor does require all libraries that the software project requires (apart from the Java Standard Library).
@@
   \begin{center}
-  \caption{CloneRefactor results for Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
+  \caption{General results for GitHub Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
   \medskip
@@
 \hline
-Extra & \textbf{Type 1} & \textbf{Type 1R} \\ \hline
+ & \textbf{Type 1} & \textbf{Type 1R} \\ \hline
 \begin{tabular}[c]{@{}l@{}}Amount of lines cloned\end{tabular} & 200,362 & 129,519 \\ \hline

### 2019-06-04 sattose/paper.tex
Fixed a mistake in the abstract

@@
 \begin{abstract}
-Duplication in source code can have a major negative impact on the maintainability of source code, as it creates explicit dependencies between fragments of code.
-Such explicit dependencies often cause bugs.
+Duplication in source code can have a major negative impact on the maintainability of source code, as it creates implicit dependencies between fragments of code.
+Such implicit dependencies often cause bugs.
 In this study, we look into the opportunities to automatically refactor these duplication problems for object-oriented programming languages.
 We propose a method to detect clones that are suitable for refactoring.
-This method focuses on the context and scope of clones, ensuring our refactoring improves the design and does not created side effects.
+This method focuses on the context and scope of clones, ensuring our refactoring improves the design and does not create side effects.
 

### 2019-06-04 sections/conclusion.tex
Update conclusion from sattose paper
Just as a placeholder

@@
 \label{ch:conclusion}
+In the research we have conducted so far we have made three novel contributions:
+\begin{itemize}
+    \item We proposed a method with which we can detect clones that can/should be refactored.
+    \item We mapped the context of clones in a large corpus of open source systems.
+    \item We mapped the opportunities to perform method extraction on clones this corpus.
+\end{itemize}
+
+We have looked into existing definitions for different types of clones \cite{roy2007survey} and proposed solutions for problems that these types have with regards to automated refactoring.
+We propose that fully qualified identifiers of method call signatures and type references should be considered instead of their plain text representation, to ensure refactorability.
+Furthermore, we propose that one should define thresholds for variability in variables, literals and method calls, in order to limit the number of parameters that the merged unit shall have.
+
+The research that we have conducted so far analyzes the context of different kinds of clones and prioritizes their refactoring.
+Firstly, we looked at the inheritance relation of clone instances in a clone class.
+We have found that more than a third of all clone classes are flagged unrelated, which means that they have at least one instance that has no relation through inheritance with the other instances.
+For about a fourth of the clone classes all of its instances are in the same class.
+About a sixth of the clone classes have clone instances that are siblings of each other (share the same superclass).
+
+Secondly, we looked at the location of clone instances.
+Most clone instances (58 percent) are found at method level.
+About 37 percent of clone instances were found at class level.
+We defined ``class level clones'' as clones that exceed the boundaries of a single method or contain something else in the class (like field declarations, other methods, etc.).
+Thirdly, we looked at the contents of clone instances.
+Most clones span a part of a method (57 percent).
+About 26 percent of clones span over several methods.
+
+We also looked into the refactorability of clones that span a part of a method.
+Over 10 percent of the clones can directly be refactored by extracting them to a new method (and calling the method at all usages using their relation).
+The main reason that most clones that span a part of a method cannot directly be refactored by method extraction, is that they contain \texttt{return}, \texttt{break} or \texttt{continue} statements.
+
+\section{Threats to validity}\label{chap:threatstovalidity}
+We noticed that, when doing measurements on a corpus of this size, the thresholds that we use for the clone detection have a big impact on the results.
+There does not seem to be one golden set of thresholds, some thresholds work in some situations but fail in others.
+We have chosen thresholds that, according to our manual assessment, seemed optimal.
+However, by using these, we definitely miss some harmful clones.
 

### 2019-06-04 sections/research.tex
Update research from sattose paper

@@
-\chapter{Redefining type 1, 2 and type 3 clones}
-In the background section we discussed the different types of clones, as defined by Roy et al \cite{roy2007survey}.
-However, when detecting clones by these definitions, we will detect many clones that are not immediately useful for refactoring.
-In this chapter, we will discuss the shortcoming of each of the clone types, and propose solutions for them.
+\chapter{Addressing problems with clone type definitions}
+In section \ref{chap:backgroundclonetypes} we discussed the different types of clones, as defined by Roy et al \cite{roy2007survey}.
+For each of type 1-3 clones we list our solutions to their shortcomings to increase the chance that we can merge the clone while improving the design.
+Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.
 
 \section{Type 1 clones}
+\label{chap:type1clones}
 Type 1 clones are identical clone fragments except for variations in whitespace and comments.
-However, when two clone fragments are textually identical, does not yet indicate that they are actually identical.
-Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type.
-See figure \ref{fig:type1noclone} for an example of a type 1 clone that is not actually identical.
-In this figure, you can see how all objects in the supposedly cloned fragment (see the marked fragment) refer to different imports.
-Because of this, it seems like a clone, but might actually not be.
-Even the showImage method might refer to a different method (overloaded variants).
-Many (mainly textual and token-based) clone detectors will flag this as a type 1 clone.
+However, when two clone fragments are textually identical, it does not yet indicate that they are functionally identical.
+Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and even variables can be of a different type.
+In such cases refactoring opportunities could be invalidated.
+Therefore, we propose an alternative definition of type 1 clones.
+We have named it ``type 1R clones''.
+The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).
+We describe how type 1R clones differ from type 1 clones over the following paragraphs.
 
@@
 \end{figure}
+
+\begin{itemize}
+  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (e.g.
+\texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object).
+This way we can validate whether two method references, like method calls, are functionally equal.
+In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments.
+This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
+  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
+  \item \textbf{Compare the equality of the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types.
+This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive.
+To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
+  \item \textbf{Compare the equality of the fully qualified identifier for method references and call signatures.} This is to prevent a change in functionality after merging the clone, as methods with equal names/parameters can still contain different functionality.
+\end{itemize}
 
@@
 To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
+\end{itemize}
 
@@
 \chapter{Merging duplicate code through refactoring}
-Now we have mapped the contexts in which clones occur, we can start looking at refactoring opportunities.
-Regarding refactoring, we separate clones in two categories: easy and difficult refactoring opportunities.
-Easy refactoring opportunities are clones that can easily be automatically refactored.
-Examples of these opportunities are fully cloned methods or a set of fully cloned statements.
-According to the relation between the clone instances, we can propose a refactoring automatically.
-
-However, not always can a clone easily be merged.
+The most used technique to merge clones is method extraction (creating a new method on basis of the contents of clones).
+However, method extraction cannot be applied in all cases.
 Sometimes a clone spans a statement partially (like a for-loop of which only it's declaration and a part of the body is cloned).
 Merging the clones can be harder in such instances.
-Also, the cloned code can contain a complex control structure, like labels, return, break, continue, etc.
-In such instances, more conditions apply to be able to conduct a refactoring, if advisable at all.
+Also, the cloned code can contain statements like \texttt{return}, \texttt{break}, \texttt{continue}.
+In these instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.
 
-The most trivial way to merge a clone is through method extraction.
-However, method extraction is not always possible.
-For instance, if a part of a subtree (in a programs' AST) is matched as a clone.
-Because of this, we chose to measure what percentage of ``Partial Method'' clones are refactorable using method extraction.
-Our results are displayed in table \ref{table:refactorability}.
+We measured the amount of clones that can be refactored through method extraction (without additional transformations being required).
+Our results are displayed in Table \ref{table:refactorability}.
+In this table we use the following categories:
+\begin{itemize}
+    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a method.
+Then, based on the relation between the clone instances, further refactoring techniques can be used to merge the extracted methods (for instance ``pull up method'' for clones in sibling classes).
+    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements.
+    \item \textbf{Spans part of a block:} This clone spans a part of a statement.
+    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table \ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
+\end{itemize}
 
@@
   \begin{center}
-  \caption{Clone instance contents} \label{table:refactorability}
-  \bigskip
-\begin{tabular}{|l|l|l|}
+  \caption{Refactorability through method extraction} \label{table:refactorability}
+  \medskip
+\begin{tabular}{|l|l|l|l|l|}
 \hline
-\textbf{Refactorability}        & \textbf{Amount} & \textbf{Percentage} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Cannot directly\\be extracted\end{tabular}    & 10,990           & 41.91               \\ \hline
-\begin{tabular}[c]{@{}l@{}}Is not a\\partial method\end{tabular} & 9,444            & 36.01               \\ \hline
-\begin{tabular}[c]{@{}l@{}}Can be\\extracted\end{tabular}                & 5,791            & 22.08               \\ \hline
-
+\textbf{}        & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
+\begin{tabular}[c]{@{}l@{}}Is not a\\partial method\end{tabular}           & 5,917 & 34.22 & 4,806 & 38.49 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Complex\\control flow\end{tabular} & 5,511 & 31.87 & 3,158 & 25.29 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Spans part of\\a block\end{tabular}             & 3,989 & 23.07 & 3,152 & 25.24 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Can be\\extracted\end{tabular}                  & 1,874 & 10.84 & 1,371 & 10.98 \\ \hline
 \end{tabular}
@@
 
-From this table, we can see that approximately 22 percent of the clones can be refactored through method extraction. For the other clones, we must first build a catalog of appropriate refactorings.
+From Table \ref{table:refactorability}, we can see that approximately ten percent of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
+For the other clones, other techniques or transformations will be required.
+Looking into these techniques and transformations will be one of our next steps.

### 2019-06-05 sections/research.tex
Imported the new paper contents

@@
-\chapter{Addressing problems with clone type definitions}
-In section \ref{chap:backgroundclonetypes} we discussed the different types of clones, as defined by Roy et al \cite{roy2007survey}.
-For each of type 1-3 clones we list our solutions to their shortcomings to increase the chance that we can merge the clone while improving the design.
+\chapter{Addressing problems with clone type definitions}\label{chap:clonetypes}
+For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings (see chapter \ref{chap:backgroundclonetypes} for these definitions) to increase the chance that we can merge the clone while improving the design.
 Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.
 
-\section{Type 1 clones}
-\label{chap:type1clones}
+\section{Type 1R clones} \label{chap:type1clones}
 Type 1 clones are identical clone fragments except for variations in whitespace and comments.
@@
 The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).
-We describe how type 1R clones differ from type 1 clones over the following paragraphs.
-
-\begin{figure}[H]
-	\includegraphics[width=1\textwidth]{img/type-1-no-clone}
-	\caption{The marked fragment might seem like a 100\% equal clone, but actually they vary.}
-	\label{fig:type1noclone}
-\end{figure}
-
+Type 1R clones differ from type 1 clones as follows:
 \begin{itemize}
@@
 
+%% ADDED
 \begin{wrapfigure}{r}{5.5cm}
@@
 \end{itemize}
+%% END ADDED
 
-\section{Type 2 clones}
-Type 2 clones, by definition, allow any change in identifiers, literals, types, layout, and comments.
-For refactoring purposes, this doesn't always make a lot of sense.
-If we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
+\section{Type 2R clones}
+Type 2 clones allow any change in identifiers, literals, types, layout, and comments.
+For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
 This could render two methods that have an entirely different functionality as clones.
-Merging such clones, if possible at all, might only prove to be harmful.
+Merging such clones can be harmful instead of helpful.
 
-Because of that, for this research, we have looked into a redefinition of type 2 clones to be able to detect such clones that can and should be merged.
+We tackle these problems with type 2R clones to be able to detect such clones that can and should be merged.
 Our definition ensures functional similarity by applying the following changes to type 2 clones:
@@
 \begin{itemize}
-  \item \textbf{Considering types:} The definition of type 2 clones states that types should not be considered.
-We disagree because types can make a significant change to the meaning of a code segment and thus whether this segment should be considered a clone.
-  \item \textbf{Having a distinction between different variables:} By the definition of type 2 clones, any identifiers would not be taken into account.
+  \item \textbf{Considering types:} Type 2 clones do not consider types.
+However, this can make a code fragment very hard to refactor, as different types can describe different functional concepts.
+Because of this, we propose that type 2R clones should consider types like type 1R clones do.
+  \item \textbf{Having a distinction between different variables:} For type 2 clones, no identifiers would be taken into account.
 We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables.
-For instance, if we call a method like this: \textit{``myMethod(var1, var2)''}, or call this method like this: \textit{``myMethod(var1, var1)''}.
+For instance, if we call a method like this: \texttt{myMethod(var1, var2)}, or call this method like this: \texttt{myMethod(var1, var1)}.
 Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
-  \item \textbf{Defining a threshold for variability in literals:} By the definition of type 2 clones any literals would not be taken into account.
-We agree, as when merging the clone (for instance by extracting a method), we can simply turn the literal into a method parameter.
+  \item \textbf{Defining a threshold for variability in literals:} For type 2 clones no literals would be taken into account.
+We agree, as when merging the clone (for example by extracting a method), we can turn the literal into a method parameter.
 However, we would argue that thresholds matter here.
@@
 However, because of this, completely different methods can be called in cloned fragments as a result.
-This poses serious challenges on refactoring and makes it more disputable whether such a clone is actually harmful.
+This poses serious challenges on refactoring and makes it more disputable whether such a clone is harmful for the maintainability of the code.
 This is because different method identifiers can describe a completely different functionality.
-Because of that, we recommend to keep considering the call signatures of cloned methods when they are compared.
+Therefore, we suggest considering the call signatures of cloned methods when they are compared.
 We can allow variability in the rest of method identifiers by passing the function as a parameter.
@@
 
-\section{Type 3 clones}
+\section{Type 3R clones}
 Type 3 clones are even more permissive than type 2 clones, allowing added and removed statements.
-Thresholds matter a lot here to make sure that not the whole project is detected to be cloned.
-The main question for this study regarding type 3 clones is: ``how can we merge type 3 clones while improving the design?''.
+For these clones, thresholds matter a lot to make sure that not the whole project is detected as a clone of itself.
+The main question for this study regarding type 3 clones is: \textit{``how can we merge type 3 clones while improving the design?''}.
 
 Clone instances in type 3 clones are almost always different in functionality.
-As we have to ensure equal functionality after merging the clone, we have to wrap the difference in statements between the clone instances in conditional blocks (either if-statements or switch-statements).
-We can then pass a variable as to which path should be taken through the code (either a boolean or an enumeration).
-Such a refactoring would make added statements that are contiguous less harmful for the design then added statements than added statements that are separated by statements that both clone instances have in common.
+As we have to ensure equal functionality after merging the clone, we have to wrap the difference in statements between the clone instances in conditional blocks.
+We can then pass a variable to indicate which path should be taken through the code (either a boolean or an enumeration).
+Such a refactoring would make added statements that are contiguous less harmful for the design than added statements that are scattered throughout the cloned fragment.
 
-We also want to argue that statements that are not common between two clone instances, should not count towards the size of the clone (and thus towards the threshold which determines whether the clone will be taken into account).
-Also, clones should not start and not end with an added statement (as that would be nonsense: such a thing could be done for any clone).
-
+We also argue that statements that are not common between two clone instances, should not count towards the size of the clone (and thus towards the threshold which determines whether the clone will be taken into account).
 As for the detection of type 3 clones, we think the easiest opportunity to detect these clones is to consider it as a postprocessing step after clone detection.
@@
 
-\chapter{Clone Detection}
-In this chapter, we look into the current state of clone detection research.
-We held a small survey in which we looked into a set of clone detection tools to determine their applicability for automated refactoring.
-We then proposed our own tool, CloneRefactor, to be able to detect our definitions of clone types (as defined in the previous chapter).
+\section{The challenge of detecting these clones}\label{chap:challenge}
+To detect each type of clone, we need to parse the fully qualified identifier of all types, method calls and variables.
+This comes with serious challenges, regarding both performance and implementation.
+Also, to be able to parse all fully qualified identifiers, and trace the declarations of variables, we might need to follow cross file references.
+The referenced types/variables/methods might even not be part of the project, but rather of an external library or the standard libraries of the programming language.
+All these factors need to be considered for the referenced entity to be found, on basis of which a fully qualified identifier can be created.
 
-%\section{Clone detection survey}
-%At the beginning of this study, we set out to find a clone detection tool that we could extend to apply automated refactorings.
-Many tools have been proposed to detect various types of code clones.
-We have considered a set of tools, selected by the most relevant AST or token based detectors found in a set of surveys \cite{}.
-However, most of these tools have a vastly different purpose than this thesis.
-Most of the tools are focused on efficiency and detecting all of the types of clones.
-Efficiency is lesser of a concern to us, correctness is the most important aspect.
+CloneRefactor uses JavaParser \cite{tomassetti2017javaparser}.
+JavaParser has a built-in symbol solver, which can automatically resolve types, method calls and variables.
+However, because of this, CloneRefactor does require all libraries that the software project requires (apart from the Java Standard Library).
+If these are not available, CloneRefactor will estimate types on basis of the information that is available.
 
-%\subsection{Text- and Token based clone detection}
-%Most clone detection tools are either text-based or token-based \cite{}.
-The main rationale for this is that it makes it easy to support many (programming) languages, it is simpler and it is generally more efficient.
-This works great for most puposes, but for automated refactoring
-
-%\subsection{Big scale clone detection}
-%There are a lot of clone detection tools that focus on detecting large amounts of clones quickly \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval, kamiya2002ccfinder, livieri2007very}.
-
-\subsection{Our criteria}
-To be able to refactor detected clones, it is useful to have the ability to rewrite the AST.
-We considered a set of clone detection tools for their ability to support the refactoring process automatically.
-None of the tools we consider seemed completely fit for this purpose, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
-
-\section{CloneRefactor}
-A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection.
-For our tool, we decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio (which is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs).
-We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is useable with all modern Java versions (Java 1-12).
-We collect each statement and declaration and compare those to find duplicates.
-This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically).
-This is displayed in figure \ref{fig:clonerefactor}.
+\chapter{Relation, Location and Content Analysis of Clones}\label{chap:clonecontextexpl}
+To be able to refactor code clones, it is very important to consider the context of the clone. We define the following aspects of the clone as its context:
+\begin{enumerate}
+  \item The relation of clone instances among each other through inheritance (for example: a clone instance resides in a superclass of another clone instance in the same clone class).
+  \item Where a clone instance occurs in the code (for example: a method-level clone is a clone instance that is in a method).
+  \item The contents of a clone instance (for example: the clone instance spans several methods).
+\end{enumerate}
 
 \begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/CodeGraph}
-  \caption{Abstract figure of the graph representation built by CloneRefactor}
-  \label{fig:clonerefactor}
+  \caption{Abstract representation of clone classes and clone instances.}
+    \medskip
+    \includegraphics[width=1\columnwidth]{img/context}
+  \label{fig:clonecontext}
 \end{figure}
 
-\section{Thresholds}
-CloneRefactor works on basis of three thresholds for finding clones:
-\begin{enumerate}
-  \item \textbf{Number of statements/declarations:} The number of statements/declarations that should be equal/similar for it to be considered a clone.
-  \item \textbf{Number of tokens:} The number of tokens (excluding whitespace, end-of-line terminators and comments) that should be equal/similar for it to be considered a clone.
-  \item \textbf{Number of lines:} The minimum amount of lines (excluding lines that do not contain any tokens, for tokens same exclusions apply) that should be equal/similar for it to be considered a clone.
-\end{enumerate}
-Of course, if we put any of these thresholds to zero it won't be taken into account anymore, so not all thresholds have to be used at all times.
-We consider ``number of lines'' to be the least important, as it highly depends on the programmer of the codebase (and we do not want this kind of dependence!).
-On basis of manual assessment, we have determined that setting the ``number of statements/declarations'' to 6 ensures that most non-harmful clones are filtered out.
-On the downside, this also filters out some harmful antipatterns, for instance, if a cloned line has many tokens we might want to consider a clone if it spans less than 6 statements (as a cloned line with many tokens is more harmful than one with few).
+Figure \ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
+The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
+The location and contents of clones is measured on clone instance level.
+A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50).
+A clone instance contents consists of a list of all statements and declarations it spans.
 
-For the measurements in the next chapter we have chosen to apply the following thresholds:
-\begin{itemize}
-  \item \textbf{Number of statements/declarations:} 6
-  \item \textbf{Number of tokens:} 10
-  \item \textbf{Number of lines:} 6
-\end{itemize}
+We analyzed the context of clones in a large corpus of open source projects.
+For these experiments, we used our CloneRefactor tool.
+These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in chapter \ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in chapter \ref{chap:clonelocation};  the content of clone instances are explained, measured and discussed in chapter \ref{chap:clonecontents}.
 
-\chapter{Code Clone Context}
-To be able to refactor code clones, it is very important to consider the context of the clone. We define the following aspects of the clone as its context:
-\begin{enumerate}
-  \item The relation of clone instances among each other (for example two clone instances in a clone class are part of the same object).
-  \item Where a clone instance occurs in the code (for instance: a method-level clone is a clone instance that is (a part of) a single method).
-  \item The contents of a clone instance (for instance: the clone instance consists of a one method declaration, a foreach statement, and two variable declarations).
-\end{enumerate}
-Everything in the context of a clone has a big impact on how it has to be refactored. For this study, we performed measurements on the context of clones in a large corpus of open source projects.
-
-\section{The corpus}
-For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}\footnote{The corpus can be downloaded from the following URL: \url{http://groups.inf.ed.ac.uk/cup/javaGithub/java_projects.tar.gz}}.
-This corpus has been assembled to contain relatively higher quality projects (by filtering by forks).
+\section{The corpus}\label{chap:corpus}
+For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}.
+This corpus has been assembled to contain relatively higher quality projects.
 Also, any duplicate projects were removed from this corpus.
@@
 
-We then filtered the corpus further to make sure we are not including any test classes or generated classes.
-Many Java/Maven projects use a structure where they separate the application and its tests in the different folders (``/src/main/java'' and ``/src/test/java'' respectively).
-Because of this, we chose to only use projects from the corpus which use this structure (and had at least a ``/src/main/java'' folder).
-To limit the execution time of the script, we also decided to limit the maximum amount of source files in a single project to 1.000 (projects with more source files were not considered, which filtered only 5 extra projects out of the corpus).
-Of the 14.436 projects in the corpus over 3.848 remained, which is plenty for our purposes.
-The script to filter the corpus in included in our GitHub repository \footnote{The script we use to filter the corpus: \url{https://github.com/SimonBaars/CloneRefactor/blob/MeasurementsVersion1/src/main/java/com/simonbaars/clonerefactor/scripts/PrepareProjectsFolder.java}}.
+As indicated in chapter \ref{chap:challenge} CloneRefactor requires all libraries of software projects we test.
+As these are not included in the used corpus \cite{githubCorpus2013}, we decided to filter the corpus to only include Maven projects.
+Maven is a build automation tool used primarily for Java, and works on basis of an \texttt{pom.xml} file to describe the projects' dependencies.
+As no \texttt{pom.xml} files are included in the corpus, we cloned the latest version of each project in the corpus.
+We then removed each project that has no \texttt{pom.xml} file.
+As a final step, we collected all dependencies for each project by using the \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib} Maven command, and removed each project for which not all dependencies were available (due to non-Maven dependencies being used or unsatisfiable dependencies being referenced in the \texttt{pom.xml} file).
 
-Running our clone detection script, CloneRefactor, over this corpus gives the results displayed in table \ref{table:general}.
+Some general data regarding this corpus is displayed in Table \ref{table:general}.
 
@@
   \begin{center}
-  \caption{CloneRefactor results for Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
-  \bigskip
+  \caption{General results for GitHub Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
+  \medskip
 \begin{tabular}{|l|l|}
 \hline
-Amount of projects                                                                                      & 3,848      \\ \hline
-Amount of lines                                                                                         & 8,284,140  \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\ whitespace, comments, etc.)\end{tabular}        & 8,163,429  \\ \hline
-Amount of statements/declarations                                                                       & 6,863,725  \\ \hline
-Amount of tokens                                                                                        & 66,964,270 \\ \hline
-Amount of lines cloned                                                                                  & 1,341,094  \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines cloned (excluding\\ whitespace, comments, etc.)\end{tabular} & 815,799    \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of statements/declarations\\ cloned\end{tabular}                      & 747,993    \\ \hline
-Amount of tokens cloned                                                                                 & 9,800,819  \\ \hline
-Amount of clone classes                                                                                 & 34,367     \\ \hline
+Amount of projects                                                                                      & 1,361      \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\whitespace, comments and newlines.)\end{tabular} & 1,414,996  \\ \hline
+Amount of statements/declarations                                                                       & 1,212,189  \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of tokens (excluding\\whitespace, comments and newlines.)\end{tabular} & 11,643,194 \\ \hline
 \end{tabular}
@@
 
-\section{Relations Between Clone Instances}
+\section{Clone detection results}
+Currently, we have implemented two clone detection algorithms into CloneRefactor.
+The first one finds clones by comparing tokens (excluding whitespace, comments and newlines), equal to the definition of type 1 clones in literature \cite{roy2007survey}.
+The second algorithm implements our type 1R, as explained in chapter \ref{chap:type1clones}.
+The differences between the clones found for these algorithms is displayed in Table \ref{table:clonedet}.
+
+\begin{table}[H]
+  \begin{center}
+  \caption{CloneRefactor clone detection results for the two different algorithms.} \label{table:clonedet}
+  \medskip
+\begin{tabular}{|l|l|l|}
+\hline
+ & \textbf{Type 1} & \textbf{Type 1R} \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of lines cloned\end{tabular} & 200,362 & 129,519 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of statements/\\declarations cloned\end{tabular} & 182,466 & 118,980 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of tokens cloned\end{tabular} & 1,582,845 & 973,596 \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+Looking at Table \ref{table:clonedet}, it becomes apparent that the type 1R algorithm finds significantly less clones than the type 1 algorithm.
+This indicates that about a third of the clones have textual equality, but are not actually equal when considering the types of expressions.
+This makes these clones less suitable for automated refactoring.
+
+\section{Relations Between Clone Instances} \label{chap:relationsinstances}
 When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances.
 This relation has a big impact on how a clone should be merged, in order to improve the software design in the process.
+In this chapter, we display measurements we conducted on the corpus introduced in chapter \ref{chap:corpus}.
+These measurements are based on an experiment by Fontana et al.
+\cite{fontana2015duplicated}, which we will briefly introduce in chapter \ref{chap:catcloneinstancerelations}.
+We use a vastly different setup, which is explained in chapter \ref{chap:oursetup}.
+We then show our results in chapter \ref{chap:ourmeasurements}.
 
-\subsection{Categorizing Clone Instance Relations}
-A paper by Fontana et al \cite{fontana2015duplicated} performs measurements on 50 open source projects on the relation of clone instances to each other.
+\subsection{Categorizing Clone Instance Relations}\label{chap:catcloneinstancerelations}
+Fontana et al.
+\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other.
 To do this, they first define several categories for the relation between clone instances in object-oriented languages.
+A few of these categories are shown in Figure \ref{fig:clonerelation}.
 These categories are as follows:
@@
 \end{enumerate}
-Please note that no of these categories allow external classes (except for ``same external superclass'').
+
+\begin{figure}[H]
+  \caption{Abstract figure displaying some relations of clone classes. Arrows represent superclass relations.}
+    \medskip
+    \includegraphics[width=1\columnwidth]{img/Relation}
+  \label{fig:clonerelation}
+\end{figure}
+Please note that none of these categories allow external classes (except for ``same external superclass'').
 So if two clone instances are related through external classes but do not share a common external superclass, it will be flagged as ``unrelated''.
@@
 
-The ranking of the previous list of categories also matters as it shows the different levels in which clones were assessed.
-For instance, if two clone instances of a clone class belong to the ``same method'' category but the third belongs to the ``same class'', we will always choose the item lowest on the list.
-
-\subsection{Our measurements}
-We have recreated table 3 of Fontana et al \cite{fontana2015duplicated}, but with the following differences in our setup:
+\subsection{Our setup}\label{chap:oursetup}
+We use a similar setup to that used by Fontana et al.
+(Table~3 of Fontana et al.
+\cite{fontana2015duplicated}).
+Fontana et al.
+measure clones using their own tool (DCRA).
+As explained in chapter~\ref{ch:tool-overview}, we chose to implement our own tool, CloneRefactor.
+Therefore, the setup for our measurements differs as follows from Fontana et al.:
 \begin{itemize}
-  \item We consider clone classes rather than clone pairs.
+  \item We consider clone classes rather than clone pairs. The rationale for this is given in chapter \ref{chap:cloneclasses}.
 \item We use different thresholds regarding when a clone should be considered.
-\item We seek by statement/declaration rather than SLOC.
-\item We test a broader range of projects (they use a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality).
+Fontana et al.
+seek clones that span a minimum of 7 source lines of code (SLOC).
+We seek clones with a minimum size of 6 statements/declarations.
+This is explained detail in chapter \ref{chap:thresholds}.
+\item We seek duplicates by statement/declaration rather than SLOC. This makes our analysis depend less on the coding style (in terms of newline usage) of the author of the software project.
+\item We test a broader range of projects.
+Fontana et al.
+use a set of 50 relatively large projects.
+We use the corpus as explained in \ref{chap:corpus}, which contains a diverse set of projects (diverse both in volume and code quality).
 \end{itemize}
 
-Table \ref{table:relations} contains our results regarding the relations between clone instances.
+\subsection{Our results} \label{chap:ourmeasurements}
+Table~\ref{table:relations} contains our results regarding the relations between clone instances.
+In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our type 1R definition as explained in chapter \ref{chap:type1clones}.
 
@@
   \caption{Clone relations} \label{table:relations}
-  \bigskip
-\begin{tabular}{|l|l|l|} \hline
-\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
-Unrelated          & 13,529           & 39.37               \\ \hline
-Same Class          & 8,341            & 24.28               \\ \hline
-Sibling            & 5,978            & 17.40               \\ \hline
-Same Method         & 2,456            & 7.15                \\ \hline
-External Superclass & 2,402            & 6.99                \\ \hline
-First Cousin        & 695             & 2.02                \\ \hline
-Superclass         & 489             & 1.42                \\ \hline
-Common Hierarchy    & 442             & 1.29                \\ \hline
-Ancestor           & 28              & 0.08               \\ \hline
+  \medskip
+\begin{tabular}{|l|l|l|l|l|} \hline
+\textbf{Relation}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
+Unrelated          & 6,134           & 35.48  & 4,762 & 38.14            \\ \hline
+\begin{tabular}[c]{@{}l@{}}Same\\Class\end{tabular}          & 4,772            & 27.60  & 3,131 & 25.07             \\ \hline
+Sibling            & 2,680            & 15.50   & 1,949 & 15.61            \\ \hline
+\begin{tabular}[c]{@{}l@{}}Same\\Method\end{tabular}         & 2,247            & 13.00   & 1,685 & 13.49             \\ \hline
+\begin{tabular}[c]{@{}l@{}}External\\Superclass\end{tabular} & 794            & 4.59   & 558 & 4.47             \\ \hline
+\begin{tabular}[c]{@{}l@{}}First\\Cousin\end{tabular}        & 269             & 1.56     & 197 & 1.58           \\ \hline
+Superclass         & 237             & 1.37     & 118 & 0.94           \\ \hline
+\begin{tabular}[c]{@{}l@{}}Common\\Hierarchy\end{tabular}    & 123             & 0.71    & 73 & 0.58            \\ \hline
+Ancestor           & 35              & 0.20     & 14 & 0.11          \\ \hline
 \end{tabular}
@@
 
-Comparing it to the results of Fontana et al \cite{fontana2015duplicated}, we find way more unrelated clones.
+The most notable difference when comparing it to the results of Fontana et al.
+\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (38.14\% with type 1R), while for them it was only 15.70\%.
 This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
-It could also be that the corpus which we use, as it has generally smaller projects, use more classes from outside the project (which are marked UNRELATED if they do not have a common external superclass).
-On the second place, we have the ``Same Class'' clones.
-On the third place come the ``Sibling'' clones.
+It could also be that the corpus which we use, as it has generally smaller projects, uses more classes from outside the project (which are marked ``Unrelated'' if they do not have a common external superclass).
+About a fourth of all clone classes have all instances in the same class, which is generally easy to refactor.
+On the third place come the ``Sibling'' clones, which can often be refactored using a pull-up refactoring.
+There are no noteworthy differences between type 1 and type 1R clones.
 
-\section{Clone instance location}
+\section{Clone instance location}\label{chap:clonelocation}
 After mapping the relations between individual clones, we looked at the location of individual clone instances.
-A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning.
-In this paper, the author argues that 98\% are produced at method-level.
+A paper by Lozano et al.
+\cite{lozano2007evaluating} discusses the harmfulness of cloning.
+The authors argue that 98\% are produced at method-level.
 However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
-We validated this claim over the corpus we use.
-For this, we chose the following categories:
+We validated this claim over our corpus.
+The results for the clone instance locations are shown in Table \ref{table:locations}.
+We chose the following categories:
 \begin{enumerate}
@@
 
-The results for the clone instance locations are shown in table \ref{table:locations}.
+Please note that these results are measured over each clone instance rather than each clone class, hence the higher total amount in comparison to the results of chapter \ref{chap:ourmeasurements}.
 
@@
   \caption{Clone instance locations} \label{table:locations}
-  \bigskip
-\begin{tabular}{|l|l|l|}
+  \medskip
+\begin{tabular}{|l|l|l|l|l|}
 \hline
-\textbf{Location}  & \textbf{Amount}  & \textbf{Percentage} \\ \hline
-Method Level       & 19,818           & 57.68               \\ \hline
-Class Level        & 13,259           & 38.59               \\ \hline
-Constructor Level  & 1,099            & 3.20                \\ \hline
-Interface Level    & 110              & 0.32                \\ \hline
-Enum Level         & 74               & 0.22                \\ \hline
+\textbf{Location}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
+Method Level       & 32,861           & 66.02   & 19,075 & 58.23            \\ \hline
+Class Level        & 15,069           & 30.27   & 12,207 & 37.27            \\ \hline
+\begin{tabular}[c]{@{}l@{}}Constructor\\Level\end{tabular}  & 1,391            & 2.79     & 1,080 & 3.30           \\ \hline
+\begin{tabular}[c]{@{}l@{}}Interface\\Level\end{tabular}    & 282              & 0.57     & 247 & 0.75           \\ \hline
+Enum Level         & 171               & 0.34    & 147 & 0.45            \\ \hline
 \end{tabular}
@@
 The amount of clones found in interfaces and enumerations is very low.
+Regarding the differences between type 1 and type 1R, it seems that there are relatively less method level clones and more class level clones for type 1R.
+This is probably due to that the main reason for variability between type 1 and type 1R is variable references, which occur more at method level than class level.
 
-\section{Clone instance contents}
+\section{Clone instance contents}\label{chap:clonecontents}
 Finally, we looked at the contents of individual clone instances: what kind of declarations and statements do they span. We selected the following categories to be relevant for refactoring:
@@
   \caption{Clone instance contents} \label{table:contents}
-  \bigskip
-\begin{tabular}{|l|l|l|}
+  \medskip
+\begin{tabular}{|l|l|l|l|l|}
   \hline
-  \textbf{Contents}                                                        & \textbf{Amount} & \textbf{Percentage} \\ \hline
-  Partial Method                                                           & 19,264          & 56.07               \\ \hline
-  Several Methods                                                          & 9,076           & 26.41               \\ \hline
-  Includes Constructor                                                     & 1,528           & 4.45                \\ \hline
-  Includes Field                                                           & 1,149           & 3.34                \\ \hline
-  Partial Constructor                                                      & 1,098           & 3.20                \\ \hline
-  Only Fields                                                              & 565             & 1.64                \\ \hline
-  Full Method                                                              & 554             & 1.61                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Class\\ Declaration\end{tabular}     & 445             & 1.30                \\ \hline
-  Other                                                                    & 369             & 1.07                \\ \hline
-  Full Class                                                               & 192             & 0.56                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Constant\end{tabular}         & 52              & 0.15                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Declaration\end{tabular}      & 47              & 0.14                \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Interface\\ Declaration\end{tabular} & 10              & 0.03                \\ \hline
-  Full Interface                                                           & 6               & 0.02                \\ \hline
-  Full Enumeration                                                         & 4               & 0.01                \\ \hline
+  \textbf{Contents} & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Partial\\Method\end{tabular}             & 32,214 & 64.72 & 18,791 & 57.37 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Several\\Methods\end{tabular}            & 10,542 & 21.18 & 8,514 & 25.99 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes\\Constructor\end{tabular}       & 1,772  & 3.56  & 1,213 & 3.70 \\ \hline
+  Includes Field                                                      & 1,681  & 3.38  & 1,487 & 4.54 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Partial\\Constructor\end{tabular}        & 1,389  & 2.79  & 1,078 & 3.29 \\ \hline
+  Only Fields                                                         & 962    & 1.93  & 888 & 2.71 \\ \hline
+  Full Method                                                         & 647    & 1.30  & 284 & 0.87 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Class\\Declaration\end{tabular} & 263    & 0.53  & 258 & 0.79 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Other\\Categories\end{tabular}           & 304    & 0.61  & 243 & 0.74 \\ \hline
 \end{tabular}
@@
 Unsurprisingly, most clones span a part of a method.
-Just 1.6\% of the methods are cloned fully.
-More than a quarter of the clones spans over several methods, which is surprising.
-Simply extracting methods won't work in a case where a clone spans over several methods.
-About 4.5\% of clones include a constructor.
-About 3.3\% of clones include a global variable defined in a class.
+More than a quarter of the clones (for type 1R) span over several methods, which either requires more advanced refactoring techniques or indicates a non-harmful clone.
 

### 2019-06-05 sections/research.tex
Working on clone type definitions

@@
-\chapter{Addressing problems with clone type definitions}\label{chap:clonetypes}
-For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings (see chapter \ref{chap:backgroundclonetypes} for these definitions) to increase the chance that we can merge the clone while improving the design.
+\chapter{Defining refactoring-oriented clone types}\label{chap:clonetypes}
+In section \ref{chap:backgroundclonetypes} we introduced the four clone types as defined in literature.
+These simple definitions are suitable for analysis of a codebase.
+Their detection results in simple to understand numbers to argue about a codebase.
+However, these clone types have a few flaws which makes it hard to argue to what extend two fragements of code are functionally related.
+For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings to increase the chance that we can merge the clone while improving the design.
 Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.
+
+We also look into clone detection tools for their suitability to support the proposed clone type definitions.
+We selected a few criteria  Most clone detection tools support these definitions of clone types.
+However, many of these tools use a vastly different approach.
+A study by Saini et al \cite{saini2018towards} outlines different clone detection tools and compares their results for each of type 1-3 clones.
+Even though they operate on the same type definitions, the tools used in this study yield different results.
+
+\section{Refactoring-oriented clone types}
+To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types to be directed at detecting clones that can and should be refactored.
 
@@
 If these are not available, CloneRefactor will estimate types on basis of the information that is available.
+
+\section{Suitability of existing Clone Detection Tools towards our refactoring purposes}
+\label{ch:tool-overview}
+We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities.
+The results of our survey are displayed in table~\ref{table:dettools}.
+We chose a set of tools that are open source and can analyze a popular object-oriented programming language.
+Next, we formulate the following four criteria by which we analyze these tools:
+\begin{enumerate}
+    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones.
+We want to perform an analysis on all clones in projects to get a complete overview.
+\item \textbf{Should find all clones in created control projects.} We assembled a number of test projects to assess the validity of clone detection tools.
+On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
+\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be merged.
+Sometimes, textual equality between code fragments does not imply that these can be merged (this is described more elaborately in section \ref{chap:type1clones}).
+Because of this, we want to use a clone detection tool that can analyze such structures.
+\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}).
+To achieve this, the tool needs to be able to allow those threshold changes.
+This can be either through simple changes of the source code, or by using some configuration file.
+\end{enumerate}
+
+\begin{table}[H]
+ \begin{center}
+  \caption{Our survey on clone detection tools.} \label{table:dettools}
+  \medskip
+\begin{tabular}{|l|l|l|l|l|l|}
+\hline
+\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
+Siamese \cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
+NiCAD \cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
+CPD \cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
+\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
+CCFinderSW \cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
+\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
+BigCloneEval \cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
+Deckard \cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
+Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}.
+This repository contains all scripts that were used to retrieve the data that is displayed in this paper.}.
+
+\chapter{Clone Detection}
+
+\chapter{Thresholds}
 

### 2019-06-10 sattose/paper.tex
Working on clone type definitions
Writing the type stuff

@@
 
-\institution{}
+\institution{University of Amsterdam}
 
@@
 \subsection{Type 1R clones} \label{chap:type1clones}
-Type 1 clones are identical clone fragments except for variations in whitespace and comments.
+Type 1 clones are identical clone fragments except for variations in whitespace and comments \cite{roy2007survey}.
 However, when two clone fragments are textually identical, it does not yet indicate that they are functionally identical.

### 2019-06-10 sections/research.tex
Writing the type stuff

@@
 
+\section{Shortcomings of clone types}
+The clone definitions, as outlined in section \ref{chap:backgroundclonetypes}, allow reasoning about the duplication in a software system.
+Clones by these definitions can relatively easily and efficiently be detected.
+This has allowed for large scale analyses of duplication.
+However, these clone type definitions have shortcomings which makes the clones detected in correspondance with these definitions less valuable.
+
+In this section we discuss the shortcomings of the different clone type definitions which make them less suitable for refactoring.
+Because of that, these clones require more human judgement whether they should and can be refactored.
+
+\subsection{Type 1 clones}
+Type 1 clones are identical clone fragments except for variations in whitespace and comments \cite{roy2007survey}.
+Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type.
+In such cases refactoring opportunities could be invalidated.
+
 \section{Refactoring-oriented clone types}
 To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types to be directed at detecting clones that can and should be refactored.
-
-\section{Type 1R clones} \label{chap:type1clones}
-Type 1 clones are identical clone fragments except for variations in whitespace and comments.
-However, when two clone fragments are textually identical, it does not yet indicate that they are functionally identical.
-Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and even variables can be of a different type.
-In such cases refactoring opportunities could be invalidated.
-Therefore, we propose an alternative definition of type 1 clones.
-We have named it ``type 1R clones''.
+We have named these clones type nR clones, where n corresponds with the type definition it is modeled after.
 The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).
 Type 1R clones differ from type 1 clones as follows:
+
+\subsection{Type 1R clones} \label{chap:type1clones}
+We propose an alternative definition of type 1 clones.
 \begin{itemize}
@@
 \end{wrapfigure}
-
-The problem with the clone shown in \ref{fig:type1noclone} is that this could invalidate a refactoring opportunity for such a code fragment (especially when we automate it).
-Because of that, we recommend redefining type-1 clones for refactoring.
-We propose to:
-\begin{itemize}
-  \item \textbf{Compare the equality of the fully qualified method signature for method references.} This way we can validate whether two method references, like method calls, are actually equal.
-In the method signature, not only the fully qualified identifier of the method should be considered, but also of the type of all its arguments.
-This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
-  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
-  \item \textbf{Compare the equality the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types.
-This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive.
-To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
-\end{itemize}
 %% END ADDED

### 2019-06-10 sections/research.tex
Working a bit on the overall document

@@
 
-\chapter{Clone Detection}
+\chapter{Evaluation setup}
+In this chapter we describe the setup we use for our experiments.
+Our most prominent contribution is the proposal of a tool called CloneRefactor.
+This tool allows us to map clones with all clone definitions as described in chapter \ref{chap:clonetypes}.
 
-\chapter{Thresholds}
+All data for our experiments, as displayed in chapter \ref{ch:results}, is measured over a corpus of Java projects. In this chapter we will explain how we prepared this corpus.
 
-\chapter{Relation, Location and Content Analysis of Clones}\label{chap:clonecontextexpl}
-To be able to refactor code clones, it is very important to consider the context of the clone. We define the following aspects of the clone as its context:
-\begin{enumerate}
-  \item The relation of clone instances among each other through inheritance (for example: a clone instance resides in a superclass of another clone instance in the same clone class).
-  \item Where a clone instance occurs in the code (for example: a method-level clone is a clone instance that is in a method).
-  \item The contents of a clone instance (for example: the clone instance spans several methods).
-\end{enumerate}
-
-\begin{figure}[H]
-  \caption{Abstract representation of clone classes and clone instances.}
-    \medskip
-    \includegraphics[width=1\columnwidth]{img/context}
-  \label{fig:clonecontext}
-\end{figure}
-
-Figure \ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
-The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
-The location and contents of clones is measured on clone instance level.
-A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50).
-A clone instance contents consists of a list of all statements and declarations it spans.
-
-We analyzed the context of clones in a large corpus of open source projects.
-For these experiments, we used our CloneRefactor tool.
-These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in chapter \ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in chapter \ref{chap:clonelocation};  the content of clone instances are explained, measured and discussed in chapter \ref{chap:clonecontents}.
+\section{CloneRefactor}
+CloneRefactor is the name of our tools which allows
 
@@
 \end{table}
-
-\section{Clone detection results}
-Currently, we have implemented two clone detection algorithms into CloneRefactor.
-The first one finds clones by comparing tokens (excluding whitespace, comments and newlines), equal to the definition of type 1 clones in literature \cite{roy2007survey}.
-The second algorithm implements our type 1R, as explained in chapter \ref{chap:type1clones}.
-The differences between the clones found for these algorithms is displayed in Table \ref{table:clonedet}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{CloneRefactor clone detection results for the two different algorithms.} \label{table:clonedet}
-  \medskip
-\begin{tabular}{|l|l|l|}
-\hline
- & \textbf{Type 1} & \textbf{Type 1R} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines cloned\end{tabular} & 200,362 & 129,519 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of statements/\\declarations cloned\end{tabular} & 182,466 & 118,980 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of tokens cloned\end{tabular} & 1,582,845 & 973,596 \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-Looking at Table \ref{table:clonedet}, it becomes apparent that the type 1R algorithm finds significantly less clones than the type 1 algorithm.
-This indicates that about a third of the clones have textual equality, but are not actually equal when considering the types of expressions.
-This makes these clones less suitable for automated refactoring.
-
-\section{Relations Between Clone Instances} \label{chap:relationsinstances}
-When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances.
-This relation has a big impact on how a clone should be merged, in order to improve the software design in the process.
-In this chapter, we display measurements we conducted on the corpus introduced in chapter \ref{chap:corpus}.
-These measurements are based on an experiment by Fontana et al.
-\cite{fontana2015duplicated}, which we will briefly introduce in chapter \ref{chap:catcloneinstancerelations}.
-We use a vastly different setup, which is explained in chapter \ref{chap:oursetup}.
-We then show our results in chapter \ref{chap:ourmeasurements}.
-
-\subsection{Categorizing Clone Instance Relations}\label{chap:catcloneinstancerelations}
-Fontana et al.
-\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other.
-To do this, they first define several categories for the relation between clone instances in object-oriented languages.
-A few of these categories are shown in Figure \ref{fig:clonerelation}.
-These categories are as follows:
-\begin{enumerate}
-  \item \textbf{Same method}: All instances of the clone class are in the same method.
-  \item \textbf{Same class}: All instances of the clone class are in the same class.
-  \item \textbf{Superclass}: All instances of the clone class are children and parents of each other.
-  \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
-  \item \textbf{Sibling class}: All instances of the clone class have the same parent class.
-  \item \textbf{First cousin class}: All instances of the clone class have the same grandparent class.
-\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same hierarchy, but do not belong to any of the other categories.
-\item \textbf{Same external superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
-\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
-\end{enumerate}
-
-\begin{figure}[H]
-  \caption{Abstract figure displaying some relations of clone classes. Arrows represent superclass relations.}
-    \medskip
-    \includegraphics[width=1\columnwidth]{img/Relation}
-  \label{fig:clonerelation}
-\end{figure}
-Please note that none of these categories allow external classes (except for ``same external superclass'').
-So if two clone instances are related through external classes but do not share a common external superclass, it will be flagged as ``unrelated''.
-The main reason for this is that it is (often) not possible to refactor to external classes.
-
-\subsection{Our setup}\label{chap:oursetup}
-We use a similar setup to that used by Fontana et al.
-(Table~3 of Fontana et al.
-\cite{fontana2015duplicated}).
-Fontana et al.
-measure clones using their own tool (DCRA).
-As explained in chapter~\ref{ch:tool-overview}, we chose to implement our own tool, CloneRefactor.
-Therefore, the setup for our measurements differs as follows from Fontana et al.:
-\begin{itemize}
-  \item We consider clone classes rather than clone pairs. The rationale for this is given in chapter \ref{chap:cloneclasses}.
-\item We use different thresholds regarding when a clone should be considered.
-Fontana et al.
-seek clones that span a minimum of 7 source lines of code (SLOC).
-We seek clones with a minimum size of 6 statements/declarations.
-This is explained detail in chapter \ref{chap:thresholds}.
-\item We seek duplicates by statement/declaration rather than SLOC. This makes our analysis depend less on the coding style (in terms of newline usage) of the author of the software project.
-\item We test a broader range of projects.
-Fontana et al.
-use a set of 50 relatively large projects.
-We use the corpus as explained in \ref{chap:corpus}, which contains a diverse set of projects (diverse both in volume and code quality).
-\end{itemize}
-
-\subsection{Our results} \label{chap:ourmeasurements}
-Table~\ref{table:relations} contains our results regarding the relations between clone instances.
-In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our type 1R definition as explained in chapter \ref{chap:type1clones}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{Clone relations} \label{table:relations}
-  \medskip
-\begin{tabular}{|l|l|l|l|l|} \hline
-\textbf{Relation}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-Unrelated          & 6,134           & 35.48  & 4,762 & 38.14            \\ \hline
-\begin{tabular}[c]{@{}l@{}}Same\\Class\end{tabular}          & 4,772            & 27.60  & 3,131 & 25.07             \\ \hline
-Sibling            & 2,680            & 15.50   & 1,949 & 15.61            \\ \hline
-\begin{tabular}[c]{@{}l@{}}Same\\Method\end{tabular}         & 2,247            & 13.00   & 1,685 & 13.49             \\ \hline
-\begin{tabular}[c]{@{}l@{}}External\\Superclass\end{tabular} & 794            & 4.59   & 558 & 4.47             \\ \hline
-\begin{tabular}[c]{@{}l@{}}First\\Cousin\end{tabular}        & 269             & 1.56     & 197 & 1.58           \\ \hline
-Superclass         & 237             & 1.37     & 118 & 0.94           \\ \hline
-\begin{tabular}[c]{@{}l@{}}Common\\Hierarchy\end{tabular}    & 123             & 0.71    & 73 & 0.58            \\ \hline
-Ancestor           & 35              & 0.20     & 14 & 0.11          \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-The most notable difference when comparing it to the results of Fontana et al.
-\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (38.14\% with type 1R), while for them it was only 15.70\%.
-This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
-It could also be that the corpus which we use, as it has generally smaller projects, uses more classes from outside the project (which are marked ``Unrelated'' if they do not have a common external superclass).
-About a fourth of all clone classes have all instances in the same class, which is generally easy to refactor.
-On the third place come the ``Sibling'' clones, which can often be refactored using a pull-up refactoring.
-There are no noteworthy differences between type 1 and type 1R clones.
-
-\section{Clone instance location}\label{chap:clonelocation}
-After mapping the relations between individual clones, we looked at the location of individual clone instances.
-A paper by Lozano et al.
-\cite{lozano2007evaluating} discusses the harmfulness of cloning.
-The authors argue that 98\% are produced at method-level.
-However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
-We validated this claim over our corpus.
-The results for the clone instance locations are shown in Table \ref{table:locations}.
-We chose the following categories:
-\begin{enumerate}
-  \item \textbf{Method/Constructor Level:} A clone instance that does not exceed the boundaries of a single method or constructor (optionally including the declaration of the method or constructor itself).
-  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class (like field declarations, other methods, etc.).
-  \item \textbf{Interface Level:} A clone that is (a part of) an interface.
-  \item \textbf{Enumeration Level:} A clone that is (a part of) an enumeration.
-\end{enumerate}
-
-Please note that these results are measured over each clone instance rather than each clone class, hence the higher total amount in comparison to the results of chapter \ref{chap:ourmeasurements}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{Clone instance locations} \label{table:locations}
-  \medskip
-\begin{tabular}{|l|l|l|l|l|}
-\hline
-\textbf{Location}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-Method Level       & 32,861           & 66.02   & 19,075 & 58.23            \\ \hline
-Class Level        & 15,069           & 30.27   & 12,207 & 37.27            \\ \hline
-\begin{tabular}[c]{@{}l@{}}Constructor\\Level\end{tabular}  & 1,391            & 2.79     & 1,080 & 3.30           \\ \hline
-\begin{tabular}[c]{@{}l@{}}Interface\\Level\end{tabular}    & 282              & 0.57     & 247 & 0.75           \\ \hline
-Enum Level         & 171               & 0.34    & 147 & 0.45            \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-Our results indicate that around 58\% of the clones are produced at method-level.
-About 39\% of clones either span several methods/constructors or contain something like a field declaration.
-Another 3\% of the clones are found in constructors.
-The amount of clones found in interfaces and enumerations is very low.
-Regarding the differences between type 1 and type 1R, it seems that there are relatively less method level clones and more class level clones for type 1R.
-This is probably due to that the main reason for variability between type 1 and type 1R is variable references, which occur more at method level than class level.
-
-\section{Clone instance contents}\label{chap:clonecontents}
-Finally, we looked at the contents of individual clone instances: what kind of declarations and statements do they span. We selected the following categories to be relevant for refactoring:
-\begin{enumerate}
-  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
-  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially, optionally including its declaration.
-  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
-  \item \textbf{Only Fields:} A clone that spans only global variables.
-  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields and other things, like methods.
-  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
-  \item \textbf{Other:} Anything that does not match with above-stated categories.
-\end{enumerate}
-
-The results for these categories are displayed in Table \ref{table:contents}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{Clone instance contents} \label{table:contents}
-  \medskip
-\begin{tabular}{|l|l|l|l|l|}
-  \hline
-  \textbf{Contents} & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Partial\\Method\end{tabular}             & 32,214 & 64.72 & 18,791 & 57.37 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Several\\Methods\end{tabular}            & 10,542 & 21.18 & 8,514 & 25.99 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes\\Constructor\end{tabular}       & 1,772  & 3.56  & 1,213 & 3.70 \\ \hline
-  Includes Field                                                      & 1,681  & 3.38  & 1,487 & 4.54 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Partial\\Constructor\end{tabular}        & 1,389  & 2.79  & 1,078 & 3.29 \\ \hline
-  Only Fields                                                         & 962    & 1.93  & 888 & 2.71 \\ \hline
-  Full Method                                                         & 647    & 1.30  & 284 & 0.87 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Class\\Declaration\end{tabular} & 263    & 0.53  & 258 & 0.79 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Other\\Categories\end{tabular}           & 304    & 0.61  & 243 & 0.74 \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-Unsurprisingly, most clones span a part of a method.
-More than a quarter of the clones (for type 1R) span over several methods, which either requires more advanced refactoring techniques or indicates a non-harmful clone.
-
-\chapter{Merging duplicate code through refactoring}
-The most used technique to merge clones is method extraction (creating a new method on basis of the contents of clones).
-However, method extraction cannot be applied in all cases.
-Sometimes a clone spans a statement partially (like a for-loop of which only it's declaration and a part of the body is cloned).
-Merging the clones can be harder in such instances.
-Also, the cloned code can contain statements like \texttt{return}, \texttt{break}, \texttt{continue}.
-In these instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.
-
-We measured the amount of clones that can be refactored through method extraction (without additional transformations being required).
-Our results are displayed in Table \ref{table:refactorability}.
-In this table we use the following categories:
-\begin{itemize}
-    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a method.
-Then, based on the relation between the clone instances, further refactoring techniques can be used to merge the extracted methods (for instance ``pull up method'' for clones in sibling classes).
-    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements.
-    \item \textbf{Spans part of a block:} This clone spans a part of a statement.
-    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table \ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
-\end{itemize}
-
-\begin{table}[H]
-  \begin{center}
-  \caption{Refactorability through method extraction} \label{table:refactorability}
-  \medskip
-\begin{tabular}{|l|l|l|l|l|}
-\hline
-\textbf{}        & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Is not a\\partial method\end{tabular}           & 5,917 & 34.22 & 4,806 & 38.49 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Complex\\control flow\end{tabular} & 5,511 & 31.87 & 3,158 & 25.29 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Spans part of\\a block\end{tabular}             & 3,989 & 23.07 & 3,152 & 25.24 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Can be\\extracted\end{tabular}                  & 1,874 & 10.84 & 1,371 & 10.98 \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-From Table \ref{table:refactorability}, we can see that approximately ten percent of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
-For the other clones, other techniques or transformations will be required.
-Looking into these techniques and transformations will be one of our next steps.

### 2019-06-10 sections/results.tex
Working a bit on the overall document

@@
 \label{ch:results}
-In this chapter, we present the results of our experiment.
+In this chapter, we present the results of our experiments.
+
+\section{Thresholds}
+
+\section{Relation, Location and Content Analysis of Clones}\label{chap:clonecontextexpl}
+To be able to refactor code clones, it is very important to consider the context of the clone. We define the following aspects of the clone as its context:
+\begin{enumerate}
+  \item The relation of clone instances among each other through inheritance (for example: a clone instance resides in a superclass of another clone instance in the same clone class).
+  \item Where a clone instance occurs in the code (for example: a method-level clone is a clone instance that is in a method).
+  \item The contents of a clone instance (for example: the clone instance spans several methods).
+\end{enumerate}
+
+\begin{figure}[H]
+  \caption{Abstract representation of clone classes and clone instances.}
+    \medskip
+    \includegraphics[width=1\columnwidth]{img/context}
+  \label{fig:clonecontext}
+\end{figure}
+
+Figure \ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
+The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
+The location and contents of clones is measured on clone instance level.
+A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50).
+A clone instance contents consists of a list of all statements and declarations it spans.
+
+We analyzed the context of clones in a large corpus of open source projects.
+For these experiments, we used our CloneRefactor tool.
+These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in chapter \ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in chapter \ref{chap:clonelocation};  the content of clone instances are explained, measured and discussed in chapter \ref{chap:clonecontents}.
+
+\section{Clone detection results}
+Currently, we have implemented two clone detection algorithms into CloneRefactor.
+The first one finds clones by comparing tokens (excluding whitespace, comments and newlines), equal to the definition of type 1 clones in literature \cite{roy2007survey}.
+The second algorithm implements our type 1R, as explained in chapter \ref{chap:type1clones}.
+The differences between the clones found for these algorithms is displayed in Table \ref{table:clonedet}.
+
+\begin{table}[H]
+  \begin{center}
+  \caption{CloneRefactor clone detection results for the two different algorithms.} \label{table:clonedet}
+  \medskip
+\begin{tabular}{|l|l|l|}
+\hline
+ & \textbf{Type 1} & \textbf{Type 1R} \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of lines cloned\end{tabular} & 200,362 & 129,519 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of statements/\\declarations cloned\end{tabular} & 182,466 & 118,980 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of tokens cloned\end{tabular} & 1,582,845 & 973,596 \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+Looking at Table \ref{table:clonedet}, it becomes apparent that the type 1R algorithm finds significantly less clones than the type 1 algorithm.
+This indicates that about a third of the clones have textual equality, but are not actually equal when considering the types of expressions.
+This makes these clones less suitable for automated refactoring.
+
+\section{Relations Between Clone Instances} \label{chap:relationsinstances}
+When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances.
+This relation has a big impact on how a clone should be merged, in order to improve the software design in the process.
+In this chapter, we display measurements we conducted on the corpus introduced in chapter \ref{chap:corpus}.
+These measurements are based on an experiment by Fontana et al.
+\cite{fontana2015duplicated}, which we will briefly introduce in chapter \ref{chap:catcloneinstancerelations}.
+We use a vastly different setup, which is explained in chapter \ref{chap:oursetup}.
+We then show our results in chapter \ref{chap:ourmeasurements}.
+
+\subsection{Categorizing Clone Instance Relations}\label{chap:catcloneinstancerelations}
+Fontana et al.
+\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other.
+To do this, they first define several categories for the relation between clone instances in object-oriented languages.
+A few of these categories are shown in Figure \ref{fig:clonerelation}.
+These categories are as follows:
+\begin{enumerate}
+  \item \textbf{Same method}: All instances of the clone class are in the same method.
+  \item \textbf{Same class}: All instances of the clone class are in the same class.
+  \item \textbf{Superclass}: All instances of the clone class are children and parents of each other.
+  \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
+  \item \textbf{Sibling class}: All instances of the clone class have the same parent class.
+  \item \textbf{First cousin class}: All instances of the clone class have the same grandparent class.
+\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same hierarchy, but do not belong to any of the other categories.
+\item \textbf{Same external superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
+\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
+\end{enumerate}
+
+\begin{figure}[H]
+  \caption{Abstract figure displaying some relations of clone classes. Arrows represent superclass relations.}
+    \medskip
+    \includegraphics[width=1\columnwidth]{img/Relation}
+  \label{fig:clonerelation}
+\end{figure}
+Please note that none of these categories allow external classes (except for ``same external superclass'').
+So if two clone instances are related through external classes but do not share a common external superclass, it will be flagged as ``unrelated''.
+The main reason for this is that it is (often) not possible to refactor to external classes.
+
+\subsection{Our setup}\label{chap:oursetup}
+We use a similar setup to that used by Fontana et al.
+(Table~3 of Fontana et al.
+\cite{fontana2015duplicated}).
+Fontana et al.
+measure clones using their own tool (DCRA).
+As explained in chapter~\ref{ch:tool-overview}, we chose to implement our own tool, CloneRefactor.
+Therefore, the setup for our measurements differs as follows from Fontana et al.:
+\begin{itemize}
+  \item We consider clone classes rather than clone pairs. The rationale for this is given in chapter \ref{chap:cloneclasses}.
+\item We use different thresholds regarding when a clone should be considered.
+Fontana et al.
+seek clones that span a minimum of 7 source lines of code (SLOC).
+We seek clones with a minimum size of 6 statements/declarations.
+This is explained detail in chapter \ref{chap:thresholds}.
+\item We seek duplicates by statement/declaration rather than SLOC. This makes our analysis depend less on the coding style (in terms of newline usage) of the author of the software project.
+\item We test a broader range of projects.
+Fontana et al.
+use a set of 50 relatively large projects.
+We use the corpus as explained in \ref{chap:corpus}, which contains a diverse set of projects (diverse both in volume and code quality).
+\end{itemize}
+
+\subsection{Our results} \label{chap:ourmeasurements}
+Table~\ref{table:relations} contains our results regarding the relations between clone instances.
+In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our type 1R definition as explained in chapter \ref{chap:type1clones}.
+
+\begin{table}[H]
+  \begin{center}
+  \caption{Clone relations} \label{table:relations}
+  \medskip
+\begin{tabular}{|l|l|l|l|l|} \hline
+\textbf{Relation}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
+Unrelated          & 6,134           & 35.48  & 4,762 & 38.14            \\ \hline
+\begin{tabular}[c]{@{}l@{}}Same\\Class\end{tabular}          & 4,772            & 27.60  & 3,131 & 25.07             \\ \hline
+Sibling            & 2,680            & 15.50   & 1,949 & 15.61            \\ \hline
+\begin{tabular}[c]{@{}l@{}}Same\\Method\end{tabular}         & 2,247            & 13.00   & 1,685 & 13.49             \\ \hline
+\begin{tabular}[c]{@{}l@{}}External\\Superclass\end{tabular} & 794            & 4.59   & 558 & 4.47             \\ \hline
+\begin{tabular}[c]{@{}l@{}}First\\Cousin\end{tabular}        & 269             & 1.56     & 197 & 1.58           \\ \hline
+Superclass         & 237             & 1.37     & 118 & 0.94           \\ \hline
+\begin{tabular}[c]{@{}l@{}}Common\\Hierarchy\end{tabular}    & 123             & 0.71    & 73 & 0.58            \\ \hline
+Ancestor           & 35              & 0.20     & 14 & 0.11          \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+The most notable difference when comparing it to the results of Fontana et al.
+\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (38.14\% with type 1R), while for them it was only 15.70\%.
+This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
+It could also be that the corpus which we use, as it has generally smaller projects, uses more classes from outside the project (which are marked ``Unrelated'' if they do not have a common external superclass).
+About a fourth of all clone classes have all instances in the same class, which is generally easy to refactor.
+On the third place come the ``Sibling'' clones, which can often be refactored using a pull-up refactoring.
+There are no noteworthy differences between type 1 and type 1R clones.
+
+\section{Clone instance location}\label{chap:clonelocation}
+After mapping the relations between individual clones, we looked at the location of individual clone instances.
+A paper by Lozano et al.
+\cite{lozano2007evaluating} discusses the harmfulness of cloning.
+The authors argue that 98\% are produced at method-level.
+However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
+We validated this claim over our corpus.
+The results for the clone instance locations are shown in Table \ref{table:locations}.
+We chose the following categories:
+\begin{enumerate}
+  \item \textbf{Method/Constructor Level:} A clone instance that does not exceed the boundaries of a single method or constructor (optionally including the declaration of the method or constructor itself).
+  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class (like field declarations, other methods, etc.).
+  \item \textbf{Interface Level:} A clone that is (a part of) an interface.
+  \item \textbf{Enumeration Level:} A clone that is (a part of) an enumeration.
+\end{enumerate}
+
+Please note that these results are measured over each clone instance rather than each clone class, hence the higher total amount in comparison to the results of chapter \ref{chap:ourmeasurements}.
+
+\begin{table}[H]
+  \begin{center}
+  \caption{Clone instance locations} \label{table:locations}
+  \medskip
+\begin{tabular}{|l|l|l|l|l|}
+\hline
+\textbf{Location}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
+Method Level       & 32,861           & 66.02   & 19,075 & 58.23            \\ \hline
+Class Level        & 15,069           & 30.27   & 12,207 & 37.27            \\ \hline
+\begin{tabular}[c]{@{}l@{}}Constructor\\Level\end{tabular}  & 1,391            & 2.79     & 1,080 & 3.30           \\ \hline
+\begin{tabular}[c]{@{}l@{}}Interface\\Level\end{tabular}    & 282              & 0.57     & 247 & 0.75           \\ \hline
+Enum Level         & 171               & 0.34    & 147 & 0.45            \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+Our results indicate that around 58\% of the clones are produced at method-level.
+About 39\% of clones either span several methods/constructors or contain something like a field declaration.
+Another 3\% of the clones are found in constructors.
+The amount of clones found in interfaces and enumerations is very low.
+Regarding the differences between type 1 and type 1R, it seems that there are relatively less method level clones and more class level clones for type 1R.
+This is probably due to that the main reason for variability between type 1 and type 1R is variable references, which occur more at method level than class level.
+
+\section{Clone instance contents}\label{chap:clonecontents}
+Finally, we looked at the contents of individual clone instances: what kind of declarations and statements do they span. We selected the following categories to be relevant for refactoring:
+\begin{enumerate}
+  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
+  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially, optionally including its declaration.
+  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
+  \item \textbf{Only Fields:} A clone that spans only global variables.
+  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields and other things, like methods.
+  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
+  \item \textbf{Other:} Anything that does not match with above-stated categories.
+\end{enumerate}
+
+The results for these categories are displayed in Table \ref{table:contents}.
+
+\begin{table}[H]
+  \begin{center}
+  \caption{Clone instance contents} \label{table:contents}
+  \medskip
+\begin{tabular}{|l|l|l|l|l|}
+  \hline
+  \textbf{Contents} & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Partial\\Method\end{tabular}             & 32,214 & 64.72 & 18,791 & 57.37 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Several\\Methods\end{tabular}            & 10,542 & 21.18 & 8,514 & 25.99 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes\\Constructor\end{tabular}       & 1,772  & 3.56  & 1,213 & 3.70 \\ \hline
+  Includes Field                                                      & 1,681  & 3.38  & 1,487 & 4.54 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Partial\\Constructor\end{tabular}        & 1,389  & 2.79  & 1,078 & 3.29 \\ \hline
+  Only Fields                                                         & 962    & 1.93  & 888 & 2.71 \\ \hline
+  Full Method                                                         & 647    & 1.30  & 284 & 0.87 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Includes Class\\Declaration\end{tabular} & 263    & 0.53  & 258 & 0.79 \\ \hline
+  \begin{tabular}[c]{@{}l@{}}Other\\Categories\end{tabular}           & 304    & 0.61  & 243 & 0.74 \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+Unsurprisingly, most clones span a part of a method.
+More than a quarter of the clones (for type 1R) span over several methods, which either requires more advanced refactoring techniques or indicates a non-harmful clone.
+
+\chapter{Merging duplicate code through refactoring}
+The most used technique to merge clones is method extraction (creating a new method on basis of the contents of clones).
+However, method extraction cannot be applied in all cases.
+Sometimes a clone spans a statement partially (like a for-loop of which only it's declaration and a part of the body is cloned).
+Merging the clones can be harder in such instances.
+Also, the cloned code can contain statements like \texttt{return}, \texttt{break}, \texttt{continue}.
+In these instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.
+
+We measured the amount of clones that can be refactored through method extraction (without additional transformations being required).
+Our results are displayed in Table \ref{table:refactorability}.
+In this table we use the following categories:
+\begin{itemize}
+    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a method.
+Then, based on the relation between the clone instances, further refactoring techniques can be used to merge the extracted methods (for instance ``pull up method'' for clones in sibling classes).
+    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements.
+    \item \textbf{Spans part of a block:} This clone spans a part of a statement.
+    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table \ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
+\end{itemize}
+
+\begin{table}[H]
+  \begin{center}
+  \caption{Refactorability through method extraction} \label{table:refactorability}
+  \medskip
+\begin{tabular}{|l|l|l|l|l|}
+\hline
+\textbf{}        & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
+\begin{tabular}[c]{@{}l@{}}Is not a\\partial method\end{tabular}           & 5,917 & 34.22 & 4,806 & 38.49 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Complex\\control flow\end{tabular} & 5,511 & 31.87 & 3,158 & 25.29 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Spans part of\\a block\end{tabular}             & 3,989 & 23.07 & 3,152 & 25.24 \\ \hline
+\begin{tabular}[c]{@{}l@{}}Can be\\extracted\end{tabular}                  & 1,874 & 10.84 & 1,371 & 10.98 \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+From Table \ref{table:refactorability}, we can see that approximately ten percent of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
+For the other clones, other techniques or transformations will be required.
+Looking into these techniques and transformations will be one of our next steps.

### 2019-06-11 sections/research.tex
Wrote about JavaParser

@@
 \section{CloneRefactor}
-CloneRefactor is the name of our tools which allows
+CloneRefactor is the name of our clone detection and refactoring tool. It features the following novel functions:
+\begin{itemize}
+  \item Detection of clone classes rather than clone pairs.
+  \item A novel detection method, aimed at extensibility.
+  \item Detection of refactoring-oriented clone types, in addition to the literature clone types.
+  \item Allows for automated refactoring of a subset of the detected duplication issues.
+\end{itemize}
+In this section we describe our approach and rationale for the design decisions regarding this tool.
+
+\subsection{JavaParser}
+A very important design decision for CloneRefactor is the usage of a library named JavaParser \cite{tomassetti2017javaparser}.
+JavaParser is a Java library which allows to parse Java source files to an abstract syntax tree (AST).
+JavaParser allows to modify this AST and write the result back to Java source code.
+This allows us to apply refactorings to the detected problems in the source code.
+
+Integrated in JavaParser is a library named SymbolSolver.
+This library allows for the resolution of symbols using JavaParser.
+For instance, we can use it to trace references (methods, variables, types, etc) to their declarations (these referenced identifiers are also called `symbols`).
+This is very useful for the detection of our refactoring-oriented clone types, as they make use of the fully qualified identifiers of symbols.
+
+In order to be able to trace referenced identifiers SymbolSolver requires access to not only the analyzed Java projects, but also all its dependencies.
+This requires us to include all dependencies with the project.
+Along with this, SymbolSolver solves symbols in the JRE System Library (the standard libraries coming with every installation of Java) using the active Java Virtual Machine (JVM).
+This has a big impact on performance efficiency.
+
+Because of the requirement of symbol resolution, the refactoring-oriented clone types are less suitable for large scale clone analysis.
+
+\subsection{Clone Detection}
+To detect clones, CloneRefactor parses the AST aqcuired from JavaParser to an unweighted graph structure. This graph structure is then
 

### 2019-06-11 sections/research.tex
Working on some type related stuff

@@
 However, these clone types have a few flaws which makes it hard to argue to what extend two fragements of code are functionally related.
-For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings to increase the chance that we can merge the clone while improving the design.
+For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings to increase the chance that we can refactor the clone while improving the design.
 Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.
@@
 
+\begin{figure}
+  \includegraphics{/img/type1}
+  \caption{Example of a textual equal type 1 clone}
+  \label{fig:type1}
+\end{figure}
+
 \section{Refactoring-oriented clone types}
 To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types to be directed at detecting clones that can and should be refactored.
-We have named these clones type nR clones, where n corresponds with the type definition it is modeled after.
+We have named these clones type 1R, 2R and 3R clones.
+These definitions share similarities with the literature definitions, thus the usage of .
 The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).
-Type 1R clones differ from type 1 clones as follows:
 
@@
 We propose an alternative definition of type 1 clones.
+This definition requires cloned fragments to be not just textually equal, but also functionally equal.
+Although requiring fragements to be functionally equal, type 1R clones do still not allow for change in implementation (like type 4 clones).
+We check functional equality of two fragments by validating the equality of referenced types.
+
+\subsubsection{An example}
+
 \begin{itemize}
@@
 To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
-  \item \textbf{Compare the equality of the fully qualified identifier for method references and call signatures.} This is to prevent a change in functionality after merging the clone, as methods with equal names/parameters can still contain different functionality.
 \end{itemize}
-
-%% ADDED
-\begin{wrapfigure}{r}{5.5cm}
-\caption{A wrapped figure going nicely inside the text.}\label{wrap-fig:1}
-\includegraphics[width=5.5cm]{img/type-1-not-cloned}
-\end{wrapfigure}
-%% END ADDED
 
@@
 This could render two methods that have an entirely different functionality as clones.
-Merging such clones can be harmful instead of helpful.
+Refactoring such clones can be harmful instead of helpful.
 
-We tackle these problems with type 2R clones to be able to detect such clones that can and should be merged.
-Our definition ensures functional similarity by applying the following changes to type 2 clones:
+We tackle these problems with type 2R clones to be able to detect such clones that can and should be refactored.
+Type 1R clones are a subset of type 2R clones.
+All rules that apply to type 1R clones also apply to type 2R clones.
+However, type 2R clones
 
@@
 For instance, if we call a method like this: \texttt{myMethod(var1, var2)}, or call this method like this: \texttt{myMethod(var1, var1)}.
-Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
+Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after refactoring.
   \item \textbf{Defining a threshold for variability in literals:} For type 2 clones no literals would be taken into account.
-We agree, as when merging the clone (for example by extracting a method), we can turn the literal into a method parameter.
+We agree, as when refactoring the clone (for example by extracting a method), we can turn the literal into a method parameter.
 However, we would argue that thresholds matter here.
 How many literals may differ for the segment still to be considered a clone with another segment?
-We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
+We need to define a threshold to be sure that, by refactoring, we are not replacing a code fragment by a worse maintainable design.
   \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary.
@@
 For these clones, thresholds matter a lot to make sure that not the whole project is detected as a clone of itself.
-The main question for this study regarding type 3 clones is: \textit{``how can we merge type 3 clones while improving the design?''}.
+The main question for this study regarding type 3 clones is: \textit{``how can we refactor type 3 clones while improving the design?''}.
 
 Clone instances in type 3 clones are almost always different in functionality.
-As we have to ensure equal functionality after merging the clone, we have to wrap the difference in statements between the clone instances in conditional blocks.
+As we have to ensure equal functionality after refactoring the clone, we have to wrap the difference in statements between the clone instances in conditional blocks.
 We can then pass a variable to indicate which path should be taken through the code (either a boolean or an enumeration).
@@
 As for the detection of type 3 clones, we think the easiest opportunity to detect these clones is to consider it as a postprocessing step after clone detection.
-By trying to find short gaps between clones, we can find opportunities to merge clone classes into a single type 3 clone class.
+By trying to find short gaps between clones, we can find opportunities to refactor clone classes into a single type 3 clone class.
 The amount of statements that this ``short gap'' can maximally span should be dependent on a threshold value.
@@
 
-CloneRefactor uses JavaParser \cite{tomassetti2017javaparser}.
-JavaParser has a built-in symbol solver, which can automatically resolve types, method calls and variables.
-However, because of this, CloneRefactor does require all libraries that the software project requires (apart from the Java Standard Library).
-If these are not available, CloneRefactor will estimate types on basis of the information that is available.
+\section{Considering several types}
+In this chapter we have proposed refactoring-oriented definitions using the type 1, 2 and 3 clone definitions from literature as a baseline.
+In literature, these definitions are mainly aimed towards reasoning about duplication in source code.
+When considering these types for refactoring, the goal becomes slighly different.
+Because of this, having separate clone type definitions does not have any value.
+Rather, we need a single clone type definition
 
@@
 On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
-\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be merged.
-Sometimes, textual equality between code fragments does not imply that these can be merged (this is described more elaborately in section \ref{chap:type1clones}).
+\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be refactored.
+Sometimes, textual equality between code fragments does not imply that these can be refactored (this is described more elaborately in section \ref{chap:type1clones}).
 Because of this, we want to use a clone detection tool that can analyze such structures.
@@
 \subsection{Clone Detection}
-To detect clones, CloneRefactor parses the AST aqcuired from JavaParser to an unweighted graph structure. This graph structure is then
+To detect clones, CloneRefactor parses the AST aqcuired from JavaParser to an unweighted graph structure.
+On basis of this graph structure, clones are detection.
+Dependent on the type of clones being detected, transformations may be applied.
+The way in which CloneRefactor was designed does not allow for several clone types to be detected simultaneously, in accordance with our clone type philosophy as described in chapter \ref{section:clonephilosophy}.
+
+\subsection{Type specific transformations}
 

### 2019-06-11 sections/research.tex
Changes to overall structure

@@
 
-In this section we discuss the shortcomings of the different clone type definitions which make them less suitable for refactoring.
-Because of that, these clones require more human judgement whether they should and can be refactored.
+In this section we discuss the shortcomings of the different clone type definitions which make them less suitable for (automated) refactoring.
+Because of that, these clones require more judgement whether they should and can be refactored.
 
-\subsection{Type 1 clones}
+\subsection{Type 1 clones} \label{chap:type1clones}
 Type 1 clones are identical clone fragments except for variations in whitespace and comments \cite{roy2007survey}.
@@
 In such cases refactoring opportunities could be invalidated.
+An example of such a case is displayed in figure \ref{fig:type1}.
 
-\begin{figure}
-  \includegraphics{/img/type1}
-  \caption{Example of a textual equal type 1 clone}
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/type1}
+  \caption{Example of a type 1 clone.}
   \label{fig:type1}
 \end{figure}
+
+In the example in figure \ref{fig:type1}, we see a type 1 clone consisting of two methods.
+However, these clones might still be very hard to refactor as we cannot see by this example whether they are functionally equal.
+Both code fragments use different imported types, some of which imported via a wildcard.
+Because of this, it is hard to verify which of the used types have the same underlying implementation.
+This can make type 1 clones less suitable for refactoring purposes, as they require additional judgement regarding the refactorability of such a clone.
+When aiming to automatically refactor clones, applying refactorings to clones as shown in figure \ref{fig:type1}, is bound to be error prone and result in a uncompilable project or a difference in functionality.
+
+Because of this, type 1 clones may not all be subject to refactoring.
+In section \label{chap:type1rclones} we describe an alternate approach towards detecting type 1 clones, which results in only clones that can be refactored.
 
@@
 
-\subsection{Type 1R clones} \label{chap:type1clones}
+\subsection{Type 1R clones} \label{chap:type1rclones}
 We propose an alternative definition of type 1 clones.
@@
 Although requiring fragements to be functionally equal, type 1R clones do still not allow for change in implementation (like type 4 clones).
-We check functional equality of two fragments by validating the equality of referenced types.
+We check functional equality of two fragments by validating the equality of referenced types, methods and variables.
 
-\subsubsection{An example}
+\subsubsection{Referenced Types}
 

### 2019-06-11 main.tex
Introduction
Abstract
Some stuff about type 1 clones
Changes to overall structure
Writing some stuff about clone types

@@
 \usepackage{xargs}   % Use more than one optional parameter in a new commands
-\usepackage[pdftex,dvipsnames]{xcolor}
+\usepackage{xcolor}
 
@@
 \usepackage{hyperref}
+\usepackage{wrapfig}
+
+\usepackage{listings}
+\lstset{
+tabsize = 4, %% Sets tab space width.
+showstringspaces = false, %% Prevents space marking in strings, string is defined as the text that is generally printed directly to the console.
+numbers = left, %% Displays line numbers on the left.
+commentstyle = \color{green}, %% Sets comment color.
+keywordstyle = \color{blue}, %% Sets  keyword color.
+stringstyle = \color{red}, %% Sets  string color.
+rulecolor = \color{black}, %% Sets frame color to avoid being affected by text color.
+basicstyle = \small \ttfamily , %% Sets listing font and size.
+breaklines = true, %% Enables line breaking.
+numberstyle = \tiny,
+}
 
@@
 %replace \paco by your name and \ana by your supervisor's name
-%\newcommandx{\ana}[2][1=]{\todo[linecolor=rblu,backgroundcolor=ryel,bordercolor=rred,#1]{#2}}
-%\newcommandx{\paco}[2][1=]{\todo[author=Paco,linecolor=blue,backgroundcolor=white,bordercolor=red,#1]{#2}}
+\newcommandx{\ana}[2][1=]{\todo[linecolor=rblu,backgroundcolor=ryel,bordercolor=rred,#1]{#2}}
+\newcommandx{\simon}[2][1=]{\todo[author=Simon,linecolor=blue,backgroundcolor=white,bordercolor=red,#1]{#2}}
 
@@
 	\begin{center}
-		{\Huge\bfseries Using Refactoring Techniques to improve Maintainability in Object Oriented Programming Languages \par}
+		{\Huge\bfseries Towards Automated Refactoring of Code Clones \par}
 		% Earlier versions:
@@
 \makeglossaries
-\bibliography{main}
+\bibliography{references}
 

### 2019-06-11 sections/research.tex
Writing some stuff about clone types

@@
 This has allowed for large scale analyses of duplication.
-However, these clone type definitions have shortcomings which makes the clones detected in correspondance with these definitions less valuable.
+However, these clone type definitions have shortcomings which makes the clones detected in correspondance with these definitions less valuable for (automated) refactoring purposes.
 
@@
 
+\subsection{Type 2 clones}
+Type 2 clones are structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments \cite{roy2007survey}.
+
+\begin{lstlisting}[caption={Methods that are type 2 clones but functionally completely different.},label={lst:type2clone},language=Java]
+public boolean containsOnlyRedCircles(List<Circle> listOfCircles){
+	return listOfCircles.stream().allMatch(c -> c.isRed());
+}
+
+public Apple getEatableAppleFromBasket(FruitBasket<Apple> appleBasket){
+	return appleBasket.getFruitContainer().getAppleByCriterium(a -> a.hasNotYetBeenEaten());
+}
+\end{lstlisting}
+
 \section{Refactoring-oriented clone types}
@@
 This definition requires cloned fragments to be not just textually equal, but also functionally equal.
-Although requiring fragements to be functionally equal, type 1R clones do still not allow for change in implementation (like type 4 clones).
-We check functional equality of two fragments by validating the equality of referenced types, methods and variables.
+Although requiring fragements to be functionally equal, type 1R clones do not allow for change in implementation (like type 4 clones).
+We check functional equality of two fragments by validating the equality of the fully qualityfied identifier for referenced types, methods and variables.
 
 \subsubsection{Referenced Types}
+Many object-oriented programming languages (like Java, Python, C#) require the programmer to import a type (or the class in which it is declared) before it can be used.
+Based on what is imported, the meaning of the name of a type can differ.
+For instance, if we import \texttt{java.util.List}, we get the interface which is implemented by all list datastructures in Java.
+However, importing \texttt{java.awt.List}, we get a listbox GUI component for the Java Abstract Window Toolkit (AWT).
+Because of this, for type 1R clones, we compare the fully qualified identifier for all referenced types.
+
+\subsubsection{Called methods}
+A codebase can have several methods with the same name.
+The implementation of these methods might differ.
+When we call two methods with an identical name, we can in fact call different methods.
+This is another reason that textually identical code fragements can differ functionally.
+
+\subsubsection{Variables}
 

### 2019-06-11 sections/research.tex
Talking about type 2 clones

@@
 Type 1 clones are identical clone fragments except for variations in whitespace and comments \cite{roy2007survey}.
+This allows for the detection of clones that are the result of copying and pasting existing code, along with other reasons why duplicates might get into a codebase.
+
+Type 1 clones are in most cases implemented as textual equality between code fragments (except for whitespace and comments).
 Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type.
@@
 Type 2 clones are structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments \cite{roy2007survey}.
+This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified.
+The two methods displayed in listing \ref{lst:type2clone} are type 2 clones of each other.
 
@@
 public boolean containsOnlyRedCircles(List<Circle> listOfCircles){
-	return listOfCircles.stream().allMatch(c -> c.isRed());
+	return listOfCircles.stream().allMatch(Shape::isRed);
 }
@@
 public Apple getEatableAppleFromBasket(FruitBasket<Apple> appleBasket){
-	return appleBasket.getFruitContainer().getAppleByCriterium(a -> a.hasNotYetBeenEaten());
+	return appleBasket.getFruitContainer().getAppleByCriterium(Fruit::hasNotYetBeenEaten);
 }
 \end{lstlisting}
+
+Looking at the example in listing \ref{lst:type2clones}, we see an example of a type 2 clone that poses no harm to the system whatsoever.
+Both methods are, except for their matching structure, completely different in functionality.
+They operate on different types, call different methods, return different things, etc.
+Having such a method flagged as a clone does not provide any useful information.
+
+When looking at refactoring, type 2 clones can be very difficult to refactor.
+For instance if we have variability in types, the code can describe operations on two completely dissimilar types.
+Type 2 clones do not differentiate between primitives and objects, which makes the these clones often not so useful for refactoring purposes.
 
@@
 We check functional equality of two fragments by validating the equality of the fully qualityfied identifier for referenced types, methods and variables.
+Type 1R clones are always a subset of type 1 clones.
 

### 2019-06-11 sections/research.tex
Nicer looking example

@@
 This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified.
-The two methods displayed in listing \ref{lst:type2clone} are type 2 clones of each other.
+The two methods displayed in figure \ref{fig:type2} are type 2 clones of each other.
 
-\begin{lstlisting}[caption={Methods that are type 2 clones but functionally completely different.},label={lst:type2clone},language=Java]
-public boolean containsOnlyRedCircles(List<Circle> listOfCircles){
-	return listOfCircles.stream().allMatch(Shape::isRed);
-}
-
-public Apple getEatableAppleFromBasket(FruitBasket<Apple> appleBasket){
-	return appleBasket.getFruitContainer().getAppleByCriterium(Fruit::hasNotYetBeenEaten);
-}
-\end{lstlisting}
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/type2}
+  \caption{Example of a type 2 clone.}
+  \label{fig:type2}
+\end{figure}
 
@@
 \subsubsection{Variables}
+In typed programming languages, each variable declaration should declare a name and a type.
+When we reference a variable, we only use its name.
+If, in different code fragments, we use variables with the same name but different types, the code can be functionally unequal but still textually equal.
+As an example, see the code in listing \ref{lst:type2variables}.
+
+\begin{lstlisting}[caption={Variables with different types but the same name.},label={lst:type2variables},language=Java]
+public String appendFive(String x){
+	return x + 5;
+}
+
+public int addFive(int x){
+	return x + 5;
+}
+\end{lstlisting}
+
+The body of both methods in listing \ref{lst:type2variables} is equal. However, their functionality is not.
 
@@
 This library allows for the resolution of symbols using JavaParser.
-For instance, we can use it to trace references (methods, variables, types, etc) to their declarations (these referenced identifiers are also called `symbols`).
+For instance, we can use it to trace references (methods, variables, types, etc) to their declarations (these referenced identifiers are also called ``symbols'').
 This is very useful for the detection of our refactoring-oriented clone types, as they make use of the fully qualified identifiers of symbols.

### 2019-06-11 sections/research.tex
Overall type related stuff

@@
 \subsection{Type 1 clones} \label{chap:type1clones}
-Type 1 clones are identical clone fragments except for variations in whitespace and comments \cite{roy2007survey}.
+Type 1 clones are \textit{identical clone fragments except for variations in whitespace and comments} \cite{roy2007survey}.
 This allows for the detection of clones that are the result of copying and pasting existing code, along with other reasons why duplicates might get into a codebase.
@@
 \subsection{Type 2 clones}
-Type 2 clones are structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments \cite{roy2007survey}.
+Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}.
 This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified.
@@
 
-Looking at the example in listing \ref{lst:type2clones}, we see an example of a type 2 clone that poses no harm to the system whatsoever.
+Looking at the example in listing \ref{fig:type2}, we see an example of a type 2 clone that poses no harm to the design of the system.
 Both methods are, except for their matching structure, completely different in functionality.
 They operate on different types, call different methods, return different things, etc.
-Having such a method flagged as a clone does not provide any useful information.
+Having such a method flagged as a clone does not provide much useful information.
 
@@
 
+\subsection{Type 3 clones}
+Type 3 clones are \textit{copied fragments with further modifications.
+Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}.
+Detection of clones by this definition can be very hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed.
+Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold \cite{svajlenko2014evaluating, cordy2011nicad}.
+This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance) \cite{lavoie2011automated}, token-level similarity of statement-level similarity.
+
+Having a definition that allows for any change in code poses serious challenges on refactoring.
+A levenshtein distance of one can already change the meaning of a code fragment significantly, for instance if the name of a type differs by a character (and thus referring to different types).
+
 \section{Refactoring-oriented clone types}
@@
 We have named these clones type 1R, 2R and 3R clones.
-These definitions share similarities with the literature definitions, thus the usage of .
+These definitions share similarities with the literature definitions, the number of each type corresponds with the clone type it is modeled after.
 The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).
@@
 \subsubsection{Referenced Types}
-Many object-oriented programming languages (like Java, Python, C#) require the programmer to import a type (or the class in which it is declared) before it can be used.
+Many object-oriented programming languages (like Java, Python, C\#) require the programmer to import a type (or the class in which it is declared) before it can be used.
 Based on what is imported, the meaning of the name of a type can differ.
@@
 If, in different code fragments, we use variables with the same name but different types, the code can be functionally unequal but still textually equal.
-As an example, see the code in listing \ref{lst:type2variables}.
+As an example, see the code in figure \ref{lst:type1variables}.
 
-\begin{lstlisting}[caption={Variables with different types but the same name.},label={lst:type2variables},language=Java]
-public String appendFive(String x){
-	return x + 5;
-}
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/type2}
+  \caption{Variables with different types but the same name.}
+  \label{fig:type1variables}
+\end{figure}
 
-public int addFive(int x){
-	return x + 5;
-}
-\end{lstlisting}
+The body of both methods in figure \ref{lst:type2variables} is equal. However, their functionality is not. The first method adds two numbers together and the other concatenates an integer to a String.
 
-The body of both methods in listing \ref{lst:type2variables} is equal. However, their functionality is not.
+For type 1R clones variable references should be compared by both type and name.
 
@@
 
-\section{Considering several types}
+\section{Unifying the types}
 In this chapter we have proposed refactoring-oriented definitions using the type 1, 2 and 3 clone definitions from literature as a baseline.
@@
 Because of this, having separate clone type definitions does not have any value.
-Rather, we need a single clone type definition
+Rather, we need a single clone type definition by which we can detect all clones that can and should be considered for refactoring.
+
+Because of this, the ultimate goal would be not to consider type 1R, 2R and 3R separately, but together.
+However, this is dependent on good thresholds for the type 2R variability and type 3R gap size.
+Because of this, we have dedicated section \ref{sec:thresholds} to performing measurements to find good thresholds.
+The ultimate goal is to have a single unified definition of clones that can and should be refactored.
+Although it will be next to impossible to define such a definition and its corresponding thresholds that does not detect false positives.
+However, we strive to find at least a near-optimal set of thresholds regarding the type definitions proposed in this chapter.
 

### 2019-06-11 sections/research.tex
Added called methods example

@@
 This is another reason that textually identical code fragements can differ functionally.
+
+Because of this, for type 1R clones, we compare the fully qualified method signature for all method references.
+A fully qualified method signature consists of the fully qualified name of the method, the fully qualified type of the method plus the fully qualified type of each of its arguments.
+For instance, an \texttt{eat} method could become \texttt{java.lang.Boolean com.simonbaars.fruitgame.Apple.eat(java.util.List<com.simonbaars.fruitgame.tools.Tool>)}.
 

### 2019-06-12 sections/research.tex
Type 2R clones...
What to do with them

@@
 
-\begin{itemize}
-  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (e.g.
-\texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object).
-This way we can validate whether two method references, like method calls, are functionally equal.
-In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments.
-This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
-  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
-  \item \textbf{Compare the equality of the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types.
-This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive.
-To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
-\end{itemize}
-
 \section{Type 2R clones}
-Type 2 clones allow any change in identifiers, literals, types, layout, and comments.
+Type 2R clones are modelled after type 2 clones, which allow any change in identifiers, literals, types, layout, and comments.
 For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
-This could render two methods that have an entirely different functionality as clones.
+This could render two methods that have an entirely different functionality as clones (as shown in figure \ref{fig:type2} previously).
 Refactoring such clones can be harmful instead of helpful.
@@
 All rules that apply to type 1R clones also apply to type 2R clones.
-However, type 2R clones
+Additionally, type 2R clones allow variability in literals, variables and method calls.
+This variability however is constrained by a threshold.
+Type 2R do not allow any variability in types, as opposed to type 2 clones which do allow variability in types.
+
+\subsubsection{A threshold for variability in literals, variables and method calls}
+
+\subsubsection{Allow any change in some names}
+- Names of method definitions
+- Names of locally declared variables
+- etc?
 

### 2019-06-12 sections/research.tex
Type 2R threshold

@@
 \subsubsection{A threshold for variability in literals, variables and method calls}
+Type 2 clones allow any variability in literals, variables and method identifiers.
+However, this information tells a lot about the meaning of the code fragment.
+Most clone detection tools do not differentiate between a type 2 clone that differs by a single literal/identifier and one that differs by many.
+However, this does have a big impact on the meaning of the code fragment and thus the harmfulness of the duplication being there.
 
-\subsubsection{Allow any change in some names}
-- Names of method definitions
-- Names of locally declared variables
+For type 2R clones we define a threshold for variability in literals, variables and method calls. We calculate the variability in literals, variables and method calls using the following formula:
+
+T2R Variability = (Diff(l) + Diff(v) + Diff(m))/Total(t)
+Diff = Amount that differ from other clone instances in the clone class
+Total = Total number in the clone instance
+l = Number of literals
+v = Number of variables
+m = Number of method calls
+t = Number of tokens
+
+Looking at this formula, it becomes apparent that we made the decision to let literals, variables and method calls count towards the same threshold.
+So a large variability in method calls might constrain variability from literals.
+This is because how to refactor variability in literals, variables and method calls.
+When we use either a different literal, variable or method call, we will have to use a
+
+\paragraph{Literal variability}
+
+\subsubsection{Allow any change in some identifiers}
+- Identifier of method declarations
+- Identifier of locally declared variables
+- Identifier of class/interface/enum declaration
 - etc?

### 2019-06-12 sections/research.tex
Literal variability

@@
 
-Looking at this formula, it becomes apparent that we made the decision to let literals, variables and method calls count towards the same threshold.
-So a large variability in method calls might constrain variability from literals.
-This is because how to refactor variability in literals, variables and method calls.
-When we use either a different literal, variable or method call, we will have to use a
+\paragraph{Literal variability}
+We allow only variability in the value of literals, but not in the type of literals.
+This is because a difference in literal type may have a big impact on the refactorability of the cloned fragment.
+When we refactor literals that have both the same type, in case of an ``Extract Method'' refactoring, we create a method argument for this literal and pass the corresponding literal from cloned locations.
+However, if two literals have different types, this might not be possible (or will have a negative effect on the design of the system).
 
-\paragraph{Literal variability}
+\paragraph{}
 

### 2019-06-12 sections/research.tex
Nice formula

@@
 
-T2R Variability = (Diff(l) + Diff(v) + Diff(m))/Total(t)
-Diff = Amount that differ from other clone instances in the clone class
-Total = Total number in the clone instance
-l = Number of literals
-v = Number of variables
-m = Number of method calls
-t = Number of tokens
+$$T2R\ Variability\ Percentage=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}$$
+$$Diff=Amount\ that\ differ\ from\ other\ clone\ instances\ in\ the\ clone\ class$$
+$$Total\ =\ Total\ number\ in\ the\ clone\ instance$$
+$$l=Number\ of\ literals$$
+$$v=Number\ of\ variables$$
+$$m=Number\ of\ method\ calls$$
+$$t=Number\ of\ tokens$$
 
-\paragraph{Literal variability}
+\noindent \textbf{Literal variability}\\
 We allow only variability in the value of literals, but not in the type of literals.
@@
 
-\paragraph{}
+\noindent \textbf{Variable variability}\\
 
@@
 All these factors need to be considered for the referenced entity to be found, on basis of which a fully qualified identifier can be created.
+
+Mainly the requirement to have access to all external libraries is a difficult one to satisfy in diverse projects.
+Because of this, these definitions may be less suitable for large scale clone detection purposes.
 
@@
 
-All data for our experiments, as displayed in chapter \ref{ch:results}, is measured over a corpus of Java projects. In this chapter we will explain how we prepared this corpus.
+All results of our experiments, as displayed in chapter \ref{ch:results}, are measured over a corpus of Java projects. In this chapter we will explain how we prepared this corpus.
 

### 2019-06-12 sections/research.tex
Literal/variable variability

@@
 We check functional equality of two fragments by validating the equality of the fully qualityfied identifier for referenced types, methods and variables.
-Type 1R clones are always a subset of type 1 clones.
+Type 1R clones are a subset of type 1 clones.
 
@@
 A fully qualified method signature consists of the fully qualified name of the method, the fully qualified type of the method plus the fully qualified type of each of its arguments.
-For instance, an \texttt{eat} method could become \texttt{java.lang.Boolean com.simonbaars.fruitgame.Apple.eat(java.util.List<com.simonbaars.fruitgame.tools.Tool>)}.
+For instance, an \texttt{eat} method could become \texttt{com.sb.AppleCore com.sb.fruitgame.Apple.eat(com.sb.fruitgame.Tool)}.
 
@@
 If, in different code fragments, we use variables with the same name but different types, the code can be functionally unequal but still textually equal.
-As an example, see the code in figure \ref{lst:type1variables}.
+As an example, see the code in figure \ref{fig:type2variables}.
 
@@
   \caption{Variables with different types but the same name.}
-  \label{fig:type1variables}
+  \label{fig:type2variables}
 \end{figure}
 
-The body of both methods in figure \ref{lst:type2variables} is equal. However, their functionality is not. The first method adds two numbers together and the other concatenates an integer to a String.
+The body of both methods in figure \ref{fig:type2variables} is equal. However, their functionality is not. The first method adds two numbers together and the other concatenates an integer to a String.
 
@@
 
-\section{Type 2R clones}
+\subsection{Type 2R clones}
 Type 2R clones are modelled after type 2 clones, which allow any change in identifiers, literals, types, layout, and comments.
@@
 Type 2R do not allow any variability in types, as opposed to type 2 clones which do allow variability in types.
+As type 2R clones are per definition more permissive than type 1R clones, type 1R clones are a subset of type 2R clones.
 
@@
 
-\noindent \textbf{Literal variability}\\
-We allow only variability in the value of literals, but not in the type of literals.
-This is because a difference in literal type may have a big impact on the refactorability of the cloned fragment.
-When we refactor literals that have both the same type, in case of an ``Extract Method'' refactoring, we create a method argument for this literal and pass the corresponding literal from cloned locations.
+\paragraph{Literal and variable variability}
+We allow only variability in the value of literals and variables, but not in their types.
+This is because a difference in literal/variable type may have a big impact on the refactorability of the cloned fragment.
+When we refactor different literals/variables that have both the same type, in case of an ``Extract Method'' refactoring, we have to create a parameter for this literal and pass the corresponding literal/variable from cloned locations.
 However, if two literals have different types, this might not be possible (or will have a negative effect on the design of the system).
+This is because a lot of variability in literals will result in more parameters required in the extracted method, which is detrimental for the design of the system.
 
-\noindent \textbf{Variable variability}\\
+Consider the example in figure \ref{fig:type2literal1}.
+In this example, the two methods have two literals that differ between them.
+We can perform an ``Extract method'' refactoring on these to get the result in figure \ref{fig:type2literal2}.
+In this process, we create a method parameter for the corresponding literal.
 
-\subsubsection{Allow any change in some identifiers}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{img/type2literal1}
+  \caption{Literal variability.}
+  \label{fig:type2literal1}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{img/type2literal2}
+  \caption{Literal variability refactored.}
+  \label{fig:type2literal2}
+\end{figure}
+
+\paragraph{Method call variability}
+
+\paragraph{Allow any change in some identifiers}
 - Identifier of method declarations

### 2019-06-12 sections/research.tex
Removed some paper content

@@
 
-\begin{itemize}
-  \item \textbf{Considering types:} Type 2 clones do not consider types.
-However, this can make a code fragment very hard to refactor, as different types can describe different functional concepts.
-Because of this, we propose that type 2R clones should consider types like type 1R clones do.
-  \item \textbf{Having a distinction between different variables:} For type 2 clones, no identifiers would be taken into account.
-We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables.
-For instance, if we call a method like this: \texttt{myMethod(var1, var2)}, or call this method like this: \texttt{myMethod(var1, var1)}.
-Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after refactoring.
-  \item \textbf{Defining a threshold for variability in literals:} For type 2 clones no literals would be taken into account.
-We agree, as when refactoring the clone (for example by extracting a method), we can turn the literal into a method parameter.
-However, we would argue that thresholds matter here.
-How many literals may differ for the segment still to be considered a clone with another segment?
-We need to define a threshold to be sure that, by refactoring, we are not replacing a code fragment by a worse maintainable design.
-  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary.
-However, because of this, completely different methods can be called in cloned fragments as a result.
-This poses serious challenges on refactoring and makes it more disputable whether such a clone is harmful for the maintainability of the code.
-This is because different method identifiers can describe a completely different functionality.
-Therefore, we suggest considering the call signatures of cloned methods when they are compared.
-We can allow variability in the rest of method identifiers by passing the function as a parameter.
-To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
-\end{itemize}
-
 \section{Type 3R clones}

### 2019-06-12 sections/research.tex
Method call variability

@@
 \subsubsection{Referenced Types}
-Many object-oriented programming languages (like Java, Python, C\#) require the programmer to import a type (or the class in which it is declared) before it can be used.
+Many object-oriented programming languages (like Java, Python and C\#) require the programmer to import a type (or the class in which it is declared) before it can be used.
 Based on what is imported, the meaning of the name of a type can differ.
@@
 
-Consider the example in figure \ref{fig:type2literal1}.
+Consider the example in figure \ref{fig:type2literal}.
 In this example, the two methods have two literals that differ between them.
-We can perform an ``Extract method'' refactoring on these to get the result in figure \ref{fig:type2literal2}.
+We can perform an ``Extract method'' refactoring on these to get the result that is displayed on the right.
 In this process, we create a method parameter for the corresponding literal.
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{img/type2literal1}
-  \caption{Literal variability.}
-  \label{fig:type2literal1}
+  \includegraphics[width=1\columnwidth]{img/type2literal}
+  \caption{Literal variability refactored.}
+  \label{fig:type2literal}
 \end{figure}
+
+\paragraph{Method call variability}
+Most modern programming languages (like Java, Python and C\#) allow to pass method references as a parameter to a method.
+This helps reducing duplication, as it is possible to refactor two code fragments which differ only by a method call.
+However, a method call does often not consist of a single token (like variables and literals).
+For instance, a method call \texttt{System.out.println()} consists of several segments: a type reference to the \texttt{System} type, a reference to the static \texttt{out} field and a call of the \texttt{println()} method.
+
+For type 2R clones, we allow called methods to vary as long as they have the same argument types and return type (both of them should be compared using their fully qualified identifiers).
+An example of this is shown in figure \ref{fig:type2method}.
+In this example, we have two methods (\texttt{System.out.println} and \texttt{myFancyPrint}).
+We use the ``Extract Method'' refactoring method to extract a new method and use a parameter for to pass the used method.
+
+The method call variability property of type 2R clones imply that type 2R clones are not a subset of type 2 clones.
+Because methods calls can have a different structure, type 2R clones can be structurally slightly different.
+The example as shown in figure \ref{fig:type2method} can be a type 2R clone (dependent on the thresholds used), but is not a type 2 clone.
 
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{img/type2literal2}
-  \caption{Literal variability refactored.}
-  \label{fig:type2literal2}
+  \includegraphics[width=1\columnwidth]{img/type2method}
+  \caption{Method variability refactored.}
+  \label{fig:type2method}
 \end{figure}
-
-\paragraph{Method call variability}
 

### 2019-06-12 sections/research.tex
Something about allowing change in stuff

@@
 
-\paragraph{Allow any change in some identifiers}
-- Identifier of method declarations
-- Identifier of locally declared variables
-- Identifier of class/interface/enum declaration
-- etc?
+\subsubsection{Allow any change in method and class names}
+When refactored, some identifiers have no detrimental effect on the design if they vary between cloned instances.
+In the previous section, variability in literals, variables and called methods would result in more parameters for the extracted method, thus indicating a detrimental effect on system design.
+This is not the case with the name of a method declaration and the name of a class/interface/enumeration declaration.
+
+If a full method is cloned with another method, however only their names differ, we can refactor these methods to keep only one of them.
+Allowing any change in method and class names will only indicate a refactoring opportunity if the full method or class is cloned.
 

### 2019-06-12 code_examples/GameOverScene.java
Added some code examples

@@ -1,0 +1,29 @@
+package com.simonbaars.fruitcollector;
+
+import com.simonbaars.fruitcollector.fruits.rotten.Apple;
+import com.simonbaars.fruitcollector.images.losing.*;
+
+import com.musiclibrary.music.lowvolume.*;
+
+public class GameOverScene extends GameScene
+{
+	protected final Player player;
+
+	public GameOverScene(Player player)
+	{
+		super(player);
+	}
+
+	public String checkAppleCollected(Apple collectedApple) 
+	{
+		if(player.inventory.contains(collectedApple)){
+			showImage(new PNGImage());
+		}
+		playSong(new MusicPlayer());
+	}
+
+	@Override
+	public void playSong(MusicPlayer musicPlayer){
+		musicPlayer.playSong("theme.mp3");
+	}
+}

### 2019-06-12 code_examples/GameWinningScene.java

@@ -1,0 +1,29 @@
+package com.simonbaars.fruitcollector;
+
+import com.simonbaars.fruitcollector.fruits.winning.Apple;
+import com.simonbaars.fruitcollector.images.winning.*;
+
+import com.musiclibrary.music.highvolume.*;
+
+public class GameWinningScene extends GameScene
+{
+	protected final Player player;
+
+	public GameScene(Player player)
+	{
+		this.player = player;
+	}
+
+	public String checkAppleCollected(Apple collectedApple) 
+	{
+		if(player.inventory.contains(collectedApple)){
+			showImage(new PNGImage());
+		}
+		playSong(new MusicPlayer());
+	}
+
+	@Override
+	public void playSong(MusicPlayer musicPlayer){
+		musicPlayer.playSong("theme.mp3");
+	}
+}

### 2019-06-12 code_examples/Type2-1.java

@@ -1,0 +1,7 @@
+public boolean containsOnlyRedCircles(List<Circle> listOfCircles){
+	return listOfCircles.stream().allMatch(Shape::isRed);
+}
+
+public Apple getEdibleAppleFromBasket(FruitBasket<Apple> appleBasket){
+	return appleBasket.getFruitContainer().getAppleByCriterium(Fruit::hasNotYetBeenEaten);
+}

### 2019-06-12 code_examples/Type2-2.java

@@ -1,0 +1,7 @@
+public int addFive(int x){
+	return x + 5;
+}
+
+public String appendFive(String x){
+	return x + 5;
+}

### 2019-06-12 code_examples/Type2-3.java

@@ -1,0 +1,11 @@
+public Optional<Niece> getNiece(Person p){
+	if(p.hasNiece())
+		return p.getNiece();
+	return Optional.empty();
+}
+
+public Optional<Piece> getPiece(Pie p){
+	if(p.isNotYetEaten())
+		return p.getPiece();
+	return Optional.empty();
+}

### 2019-06-12 code_examples/Type2-4.java

@@ -1,0 +1,15 @@
+// Original
+public void printNice(String s){
+	System.out.println("=====================");
+	System.out.println(s);
+	System.out.println("=====================");
+}
+
+public void printNice2(String s){
+	System.out.println("---------------------");
+	System.out.println(s);
+	System.out.println("---------------------");
+}
+
+
+

### 2019-06-12 code_examples/Type2-5.java

@@ -1,0 +1,15 @@
+// Refactored
+public void printNice(String s){
+	printNice(s, "=====================");
+}
+
+public void printNice2(String s){
+	printNice(s, "---------------------");
+}
+
+public void printNice(String s, String decoration){
+	System.out.println(decoration);
+	System.out.println(s);
+	System.out.println(decoration);
+}
+

### 2019-06-12 code_examples/Type2-6.java

@@ -1,0 +1,22 @@
+// Original
+public void printNice(){
+	System.out.println("=====================");
+	myFancyPrint("The weather is nice");
+	System.out.println("=====================");
+}
+
+public void printNice2(){
+	System.out.println("=====================");
+	System.out.println("The weather is nice");
+	System.out.println("=====================");
+}
+
+public void myFancyPrint(String s){
+	Arrays.stream(s.toCharArray()).boxed()
+		.map(e -> "("+e+")")
+		.collect(Collectors.joining);
+}
+
+
+
+

### 2019-06-12 code_examples/Type2-7.java

@@ -1,0 +1,22 @@
+// Refactored
+public void printWeather(){
+	printNice(this::myFancyPrint);
+}
+
+public void printNice2(){
+	printNice(System.out::println);
+}
+
+public void printNice(Consumer<String> printFunction){
+	System.out.println("=====================");
+	printFunction.accept("The weather is nice");
+	System.out.println("=====================");
+}
+
+public void myFancyPrint(String s){
+	Arrays.stream(s.toCharArray()).boxed()
+		.map(e -> "("+e+")")
+		.collect(Collectors.joining);
+}
+
+

### 2019-06-12 sections/research.tex
Type 3R Clones

@@
 
-$$T2R\ Variability\ Percentage=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}$$
+$$T2R\ Variability\ Percentage=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
 $$Diff=Amount\ that\ differ\ from\ other\ clone\ instances\ in\ the\ clone\ class$$
@@
 \section{Type 3R clones}
-Type 3 clones are even more permissive than type 2 clones, allowing added and removed statements.
-For these clones, thresholds matter a lot to make sure that not the whole project is detected as a clone of itself.
-The main question for this study regarding type 3 clones is: \textit{``how can we refactor type 3 clones while improving the design?''}.
+Type 3 clones allow any change in statements, often bounded by a similarity threshold.
+This means that type 3R allows the inclusion of a statement that is not detected by type 1 or 2 clone detection.
+When looking at how we can refactor a statement that is not included by one clone instance but is in another, we find that we require a conditional block to make up for the difference in statements.
+See figure \ref{fig:type3} for an example of such a clone.
 
-Clone instances in type 3 clones are almost always different in functionality.
-As we have to ensure equal functionality after refactoring the clone, we have to wrap the difference in statements between the clone instances in conditional blocks.
-We can then pass a variable to indicate which path should be taken through the code (either a boolean or an enumeration).
-Such a refactoring would make added statements that are contiguous less harmful for the design than added statements that are scattered throughout the cloned fragment.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{img/type3_3}
+  \caption{Added statement between cloned methods.}
+  \label{fig:type3}
+\end{figure}
 
-We also argue that statements that are not common between two clone instances, should not count towards the size of the clone (and thus towards the threshold which determines whether the clone will be taken into account).
-As for the detection of type 3 clones, we think the easiest opportunity to detect these clones is to consider it as a postprocessing step after clone detection.
-By trying to find short gaps between clones, we can find opportunities to refactor clone classes into a single type 3 clone class.
-The amount of statements that this ``short gap'' can maximally span should be dependent on a threshold value.
+In figure \ref{fig:type3} a single statement is added.
+This statement is found in between cloned lines.
+We have named this difference between the two clones, in this examples containing a single statement, the \textit{gap}.
+This gap has a threshold for type 3R, which is calculated by the following formula:
+
+$$T3R\ Gap\ Percentage=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100$$
+$$Statements = The\ amount\ of\ statements\ in\ this\ code\ fragment$$
+$$C_{gap} = The\ gap between two clones$$
+$$C_{above} = The\ clone\ instance\ above\ the\ gap$$
+$$lower = The clone instance below the gap$$
+
+Apart from this threshold, the gap in between clones may not span over different blocks.
+Look at figure \ref{fig:type3invalid} for an example of this.
+We cannot refactor both statements into a single conditional block.
+We could however use two conditional blocks, but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for type 3R clones.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{img/type3invalid}
+  \caption{Statements between clones in different blocks.}
+  \label{fig:type3invalid}
+\end{figure}
 
@@
 Mainly the requirement to have access to all external libraries is a difficult one to satisfy in diverse projects.
-Because of this, these definitions may be less suitable for large scale clone detection purposes.
+Because of this, the proposed clone definitions may be less suitable for large scale clone detection purposes.
 

### 2019-06-12 code_examples/Type2-6.java

@@ -1,11 +1,11 @@
 // Original
-public void printNice(){
+public void printWeather(){
 	System.out.println("=====================");
 	myFancyPrint("The weather is nice");
 	System.out.println("=====================");
 }
 
-public void printNice2(){
+public void printWeather2(){
 	System.out.println("=====================");
 	System.out.println("The weather is nice");
 	System.out.println("=====================");
@@ -13,10 +13,6 @@ public void printNice2(){
 
 public void myFancyPrint(String s){
 	Arrays.stream(s.toCharArray()).boxed()
-		.map(e -> "("+e+")")
-		.collect(Collectors.joining);
+		.map(e -> "(" + e + ")")
+		.collect(Collectors.joining());
 }
-
-
-
-

### 2019-06-12 code_examples/Type2-7.java

@@ -3,11 +3,11 @@ public void printWeather(){
 	printNice(this::myFancyPrint);
 }
 
-public void printNice2(){
+public void printWeather2(){
 	printNice(System.out::println);
 }
 
-public void printNice(Consumer<String> printFunction){
+public void printWeather(Consumer<String> printFunction){
 	System.out.println("=====================");
 	printFunction.accept("The weather is nice");
 	System.out.println("=====================");
@@ -15,8 +15,6 @@ public void printNice(Consumer<String> printFunction){
 
 public void myFancyPrint(String s){
 	Arrays.stream(s.toCharArray()).boxed()
-		.map(e -> "("+e+")")
-		.collect(Collectors.joining);
+		.map(e -> "(" + e + ")")
+		.collect(Collectors.joining());
 }
-
-

### 2019-06-12 code_examples/Type3-1.java

@@ -1,0 +1,22 @@
+// Original
+public String wordOfNumbers(int max){
+	Random r = new Random();
+	StringBuilder word = new StringBuilder();
+	for(int i = 0; i<=size; i++){
+		word.append(i);
+	}
+	word.append("that's it");
+	return word.toString();
+}
+
+public void printWordOfNumbers(int max){
+	Random r = new Random();
+	StringBuilder word = new StringBuilder();
+	for(int i = 0; i<=size; i++){
+		word.append(i);
+		System.out.println("Appended "+i);
+	}
+	word.append("that's it");
+	System.out.println(word);
+}
+

### 2019-06-12 code_examples/Type3-2.java

@@ -1,0 +1,22 @@
+// Refactored
+public List<String> wordOfNumbers(int size){
+	return wordOfNumbers(n, size, false);
+}
+
+public void printWordOfNumbers(int size){
+	System.out.println(wordOfNumbers(n, size, true));
+}
+
+public StringBuilder wordOfNumbers(int size, 
+									boolean doPrint){
+	Random r = new Random();
+	StringBuilder word = new StringBuilder();
+	for(int i = 0; i<size; i++){
+		word.append(i);
+		if(doPrint) System.out.println("Appended "+i);
+	}
+	word.append("that's it");
+	return word;
+}
+
+

### 2019-06-12 code_examples/Type3-3.java

@@ -1,0 +1,21 @@
+public String wordOfNumbers(int max){
+	Random r = new Random();
+	StringBuilder word = new StringBuilder();
+	for(int i = 0; i<=size; i++){
+		word.append(i);
+	}
+	word.append("that's it")
+	return word.toString();
+}
+
+public void printWordOfNumbers(int max){
+	Random r = new Random();
+	StringBuilder word = new StringBuilder();
+	for(int i = 0; i<=size; i++){
+		word.append(i);
+		System.out.println("Appended "+i);
+	}
+	System.out.println(word);
+	word.append("that's it");
+}
+

### 2019-06-12 sections/research.tex
Various changes

@@
 
-\section{Unifying the types}
+\section{Unifying the types}\label{sec:unifying}
 In this chapter we have proposed refactoring-oriented definitions using the type 1, 2 and 3 clone definitions from literature as a baseline.
@@
 
-\section{Suitability of existing Clone Detection Tools towards our refactoring purposes}
+\section{Suitability of existing Clone Detection Tools for detecting these clones}
 \label{ch:tool-overview}
-We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities.
+We conducted a short survey on (recent) clone detection tools in order to expand them with the proposed types.
 The results of our survey are displayed in table~\ref{table:dettools}.
-We chose a set of tools that are open source and can analyze a popular object-oriented programming language.
+We chose a set of tools that are open source and can analyze at least one popular object-oriented programming language.
 Next, we formulate the following four criteria by which we analyze these tools:
@@
 We want to perform an analysis on all clones in projects to get a complete overview.
-\item \textbf{Should find all clones in created control projects.} We assembled a number of test projects to assess the validity of clone detection tools.
+We analyzed this behavior using a set of control projects.
+\item \textbf{TODO: Criterium.} We assembled a number of test projects to assess the validity of clone detection tools.
 On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
@@
 \begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
-CCFinderSW \cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
+CCFinderSW \cite{semura2017ccfindersw}   &    &             &             & \checkmark            \\ \hline
 \begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
@@
 
-None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}.
-This repository contains all scripts that were used to retrieve the data that is displayed in this paper.}.
+None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool, which is further described in the next chapter.
 
@@
 Dependent on the type of clones being detected, transformations may be applied.
-The way in which CloneRefactor was designed does not allow for several clone types to be detected simultaneously, in accordance with our clone type philosophy as described in chapter \ref{section:clonephilosophy}.
+The way in which CloneRefactor was designed does not allow for several clone types to be detected simultaneously, in accordance with our clone type philosophy as described in chapter \ref{sec:unifying}.
 

### 2019-06-13 sections/research.tex
About clone detection in general

@@
 
+The overall process regarding clone detection is displayed in figure \ref{fig:clonedetection}.
+First of all, we use JavaParser to read a project from disk and build an AST, one class file at a time.
+Each AST is then converted to a grid that maps relations between statements, further explained in section \ref{sec:clonegrid}.
+On basis of this grid, we detect clone classes and verify them using three thresholds (in order of importance):
+\begin{itemize}
+  \item Amount of tokens.
+  \item Amount of statements.
+  \item Amount of lines.
+\end{itemize}
+If the detection was configured to detect either type 2R, 3 or 3R clones we perform some type specific transformations on the resulting set of clones.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{img/CloneDetection}
+  \caption{CloneRefactor clone detection process.}
+  \label{fig:clonedetection}
+\end{figure}
+
+\subsubsection{Generating the clone grid}\label{sec:clonegrid}
+
 \subsection{Type specific transformations}

### 2019-06-13 sections/research.tex
Generating the clone grid and detecting clones

@@
 \subsubsection{Generating the clone grid}\label{sec:clonegrid}
+First of all, we parse the AST obtained from JavaParser into what we call a clone grid.
+Although it is not a grid in an original sense, thinking of it as a grid makes it easier to comprehend.
+We have chosen to base our clone detection around statements as the smallest unit of comparison.
+This means that a single statement cloned with another single statement is the smallest clone we can find.
+The rationale for this lies in both simplicity and performance efficiency.
+This means we won't be able to find when a single expression matches another expression, or even a single token matching another token.
+This is in most cases not a problem, as expressions are often small and do not span the minimal size to be considered a clone in the first place (more about this in section \ref{sec:thresholds}).
 
-\subsection{Type specific transformations}
+Building the ``clone grid'' consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
+\begin{itemize}
+  \item The declaration/statement preceding it.
+  \item The declaration/statement following.
+  \item The last \textbf{preceding} declaration/statement with which it is cloned.
+\end{itemize}
+We do not create a seperate grid for each class file, so the statement/declaration preceding or following could be in a different file.
+While mapping these relations, we maintain a hashed map containing the last occurrence of each unique statement.
+This map is used to quickly find out whether a statement is cloned with another.
+
+\subsubsection{Detecting Clones}
+After building the clone grid, we use it to detect clones.
+We decided to focus on the detection of clone classes rather than clone pairs because clone pairs do not provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}.
+Although clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered.
+Another issue that results from grouping clones by pairs: clone reference amount increases according to the binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), which causes a heavy information redundancy \cite{fontana2012duplicated}.
+
+As stated in the previous section, nodes in the grid link to \textit{preceding} cloned statement.
+This implies that the first node that is cloned does not have any clone relation, as there are no clones preceding it (only following it).
+Because of this, we start our clone detection process at the final location encountered while building the grid.
+For this node, we collect all nodes it is cloned with.
+Even though the final node only links to the preceding node it is cloned with, we can collect all clones.
+This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node.
+As an example, see figure \ref{}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{img/CodeGraph}
+  \caption{Clone grid as built by CloneRefactor.}
+  \label{fig:clonegrid}
+\end{figure}
+
+\subsubsection{Validating the type 2 variability threshold}
 

### 2019-06-13 sections/research.tex
Trying to explain something

@@
 This map is used to quickly find out whether a statement is cloned with another.
+An example of such a grid is displayed in figure \ref{fig:clonegridsimple}.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{img/CodeGraph2}
+  \caption{Clone grid as built by CloneRefactor.}
+  \label{fig:clonegridsimple}
+\end{figure}
 
@@
 This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node.
-As an example, see figure \ref{}
+As an example, see figure \ref{fig:clonegrid}.
 
@@
   \centering
-  \includegraphics[width=1\columnwidth]{img/CodeGraph}
-  \caption{Clone grid as built by CloneRefactor.}
+  \includegraphics[width=1\columnwidth]{img/CodeGraph3}
+  \caption{Clone grid with a clone class consisting of three clone instances marked.}
   \label{fig:clonegrid}
 \end{figure}
+
+Using the example shown in figure \ref{fig:clonegrid} we can explain how we detect clones.
+Suppose we are currently finding clones at the purple marked box.
+We then follow all ``duplicate'' relations until we have found all clones (the boxes marked in green).
+We now have a single statement clone class.
+Next, we move to the previous line.
+Here again, we collect all duplicates of this node.
+For each of these duplicates, we check whether the node following it is already in the clone class we collected in the previous iteration.
+In this case, only two of the
 

### 2019-06-13 sections/research.tex
Explaining detecting clones

@@
 
-\subsubsection{Detecting Clones}
+We generally call the declarations and statements represented in this grid \textit{nodes}.
+The relations \textit{next} and \textit{previous} in this grid are represented as an undirected relation.
+The relations representing duplicated are directed.
+This is a restriction we've chosen as it creates an important constraint for the clone detection process.
+This process is explained in section \ref{sec:detectingclones}.
+
+\subsubsection{Comparing Statements/Declarations}
+In the previous section we described ...
+
+\subsubsection{Detecting Clones} \label{sec:detectingclones}
 After building the clone grid, we use it to detect clones.
@@
 Using the example shown in figure \ref{fig:clonegrid} we can explain how we detect clones.
-Suppose we are currently finding clones at the purple marked box.
-We then follow all ``duplicate'' relations until we have found all clones (the boxes marked in green).
-We now have a single statement clone class.
-Next, we move to the previous line.
-Here again, we collect all duplicates of this node.
+Suppose we are finding clones for two files and the final node of the second file is a variable declarator.
+This final node is represented in the example figure by the purple box (1).
+We then follow all ``duplicate'' relations until we have found all clones (2 and 3).
+We now have a single statement clone class of three clone instances (1, 2 and 3).
+Next, we move to the previous line (4).
+Here again, we collect all duplicates of this node (4 and 5).
 For each of these duplicates, we check whether the node following it is already in the clone class we collected in the previous iteration.
-In this case, only two of the
+In this case, (2) follows (5) and (1) follows (4).
+This means that node (3) does not form a 'chain' with other cloned statements.
+Because of this, the clone class of (1, 2 and 3) comes to an end.
+It will be checked against the thresholds, and if adhering to the threshold, considered a clone.
+We then go further to yet the previous node (6).
+In this case, this node does not have any clones.
+This means we check the (2 and 5, 1 and 4) clone class against the thresholds, and if it adheres, consider it a clone.
+Dependent on the thresholds, we'd now have found two clone classes.
+
+The grid representation shown in figure \ref{fig:clonegrid} is only shown as a grid for ease of comprehension.
+In fact, it is not a grid, but a graph.
+Eventually, following only the ``previous node'' relations, we can get from (6) to (2).
+When we are at that point, we will find only one cloned node for (2), namely (3).
+However, after we check this clone against the thresholds, we check whether it is a subset of any exisiting clone.
+If this is the case, we discard the clone.
 

### 2019-06-13 main.tex
Literal/variable variability
Trying to explain something
Writing something about Compare

@@
 \usepackage{longtable}
-\usepackage[backend=biber, style=ieee,citestyle=numeric-comp]{biblatex}
+\usepackage[backend=bibtex, style=ieee,citestyle=numeric-comp]{biblatex}
 \usepackage[colorinlistoftodos, prependcaption]{todonotes}
@@
 \usepackage{wrapfig}
+\usepackage{microtype}
 
-\usepackage{listings}
-\lstset{
-tabsize = 4, %% Sets tab space width.
-showstringspaces = false, %% Prevents space marking in strings, string is defined as the text that is generally printed directly to the console.
-numbers = left, %% Displays line numbers on the left.
-commentstyle = \color{green}, %% Sets comment color.
-keywordstyle = \color{blue}, %% Sets  keyword color.
-stringstyle = \color{red}, %% Sets  string color.
-rulecolor = \color{black}, %% Sets frame color to avoid being affected by text color.
-basicstyle = \small \ttfamily , %% Sets listing font and size.
-breaklines = true, %% Enables line breaking.
-numberstyle = \tiny,
-}
+\usepackage{titlesec}
+
+\setcounter{secnumdepth}{4}
 

### 2019-06-13 sections/research.tex
Writing something about Compare

@@
 First of all, we parse the AST obtained from JavaParser into what we call a clone grid.
-Although it is not a grid in an original sense, thinking of it as a grid makes it easier to comprehend.
+Although it is not a grid in an original sense, thinking of it as a grid makes it easier to comprehend (this is explained in section \ref{sec:detectingclones} in more detail).
 We have chosen to base our clone detection around statements as the smallest unit of comparison.
@@
 \subsubsection{Comparing Statements/Declarations}
-In the previous section we described ...
+In the previous section we described a ``duplicate'' relation between nodes in the clone grid built by CloneRefactor.
+Whether two nodes in this grid are duplicates of each other is dependent on the clone type.
+In this section, we will describe for each type how we compare statements and declarations assess whether they are clones of each other.
+
+CloneRefactor detects six different types of clones: T1, T2, T3, T1R, T2R and T3R.
+These types are further explained in chapter \ref{chap:clonetypes}.
+Type 1 clones are an exact textual match between two clones, omitting comments and whitespace.
+For type 1 clones, CloneRefactor filters the tokens of a node to exclude its comments, whitespace and end of line (EOL) characters and then compares these tokens.
+For type 2 clones, the tokens are further filtered to omit all identifiers and literals.
+Type 3 clones do the same node comparison as type 2 clones.
+
+For type 1R clones, this comparison is a bit more advanced. For method calls
 
@@
 In this case, (2) follows (5) and (1) follows (4).
-This means that node (3) does not form a 'chain' with other cloned statements.
+This means that node (3) does not form a `chain' with other cloned statements.
 Because of this, the clone class of (1, 2 and 3) comes to an end.

### 2019-06-13 sections/research.tex
Comparing stuff

@@
 These types are further explained in chapter \ref{chap:clonetypes}.
-Type 1 clones are an exact textual match between two clones, omitting comments and whitespace.
-For type 1 clones, CloneRefactor filters the tokens of a node to exclude its comments, whitespace and end of line (EOL) characters and then compares these tokens.
-For type 2 clones, the tokens are further filtered to omit all identifiers and literals.
-Type 3 clones do the same node comparison as type 2 clones.
+For \textbf{type 1} clones, CloneRefactor filters the tokens of a node to exclude its comments, whitespace and end of line (EOL) characters and then compares these tokens.
+For \textbf{type 2} clones, the tokens are further filtered to omit all identifiers and literals.
+\textbf{Type 3} clones do the same duplication comparison as type 2 clones.
 
-For type 1R clones, this comparison is a bit more advanced. For method calls
+For \textbf{type 1R} clones, this comparison is a lot more advanced.
+For \textit{method calls} we trace their declaration and use its fully qualified method signature for comparison with other nodes.
+For all \textit{referenced types} we trace their declarations and use assemble their fully qualified identifier for comparison with other nodes.
+For \textit{variables} we trace their declaration and their types.
+If the variable type is a primitive we can directly use it for comparison.
+If it is a referenced type, we have to trace this type first in order to collect their fully qualified identifier for comparison.
+
+For \textbf{type 2R} clones we allow any variation in literals, variables and method calls at this stage in the clone detection process.
+However, for \textit{literals} we do resolve their type in order to verify that they are of the same type.
+For \textit{variables} we also only verify that their types are the same (but not their names).
+For \textit{method calls}, we trace their declaration but only compare the fully qualified identifier for its return type and each of its arguments' types.
+Apart from that, we do not compare the names of method, class, interface and enum declarations.
 
@@
 
+\subsubsection{Checking for type 3 opportunities}
+
 \section{The corpus}\label{chap:corpus}

### 2019-06-14 sections/results.tex
Overall type related stuff
About clone detection in general
Overall structural changes

@@
 
-\section{Thresholds}
+\section{Thresholds} \label{sec:thresholds}
 
@@
 
-\section{Clone detection results}
+\subsection{Clone detection results}
 Currently, we have implemented two clone detection algorithms into CloneRefactor.
@@
 
-\section{Relations Between Clone Instances} \label{chap:relationsinstances}
+\subsection{Relations Between Clone Instances} \label{chap:relationsinstances}
 When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances.
@@
 
-\subsection{Categorizing Clone Instance Relations}\label{chap:catcloneinstancerelations}
+\subsubsection{Categorizing Clone Instance Relations}\label{chap:catcloneinstancerelations}
 Fontana et al.
@@
     \medskip
-    \includegraphics[width=1\columnwidth]{img/Relation}
+    \centering
+    \includegraphics[width=0.6\columnwidth]{img/Relation}
   \label{fig:clonerelation}
@@
 
-\subsection{Our setup}\label{chap:oursetup}
+\subsubsection{Our setup}\label{chap:oursetup}
 We use a similar setup to that used by Fontana et al.
@@
 
-\section{Clone instance location}\label{chap:clonelocation}
+\subsection{Clone instance location}\label{chap:clonelocation}
 After mapping the relations between individual clones, we looked at the location of individual clone instances.
@@
 
-\chapter{Merging duplicate code through refactoring}
+\section{Merging duplicate code through refactoring}
 The most used technique to merge clones is method extraction (creating a new method on basis of the contents of clones).

### 2019-06-14 sections/background.tex
Update conclusion from sattose paper
Just as a placeholder
Nice formula
Overall model

@@
 	\includegraphics[width=1\textwidth]{img/clone-pair}
-	\caption{Example of a clone pair, as found in the \href{https://github.com/taweili/ardublock}{ardublock} project.}
+	\caption{Example of a clone pair, as found in the \href{https://github.com/Danny02/JOpenCTM}{JOpenCTM} project.}
 	\label{fig:clonepair}
@@
 	\includegraphics[width=1\textwidth]{img/clone-class}
-	\caption{Example of two clone classes.}
+	\caption{Example of a clone class, as found in the \href{https://github.com/Danny02/JOpenCTM}{JOpenCTM} project.}
 	\label{fig:cloneclass}
@@
 
-\section{Clone Types}
+\section{Clone Types} \ref{chap:backgroundclonetypes}
 Duplication in code is found in many different forms.
@@
 Because of that, we can conclude that type 4 clones are relatively less relevant to study.
+
+\section{Background on refactoring methods}
 

### 2019-06-14 sections/research.tex
Overall structural changes
Overall model

@@
 Their detection results in simple to understand numbers to argue about a codebase.
-However, these clone types have a few flaws which makes it hard to argue to what extend two fragements of code are functionally related.
+However, these clone types have a few flaws which makes it hard to argue to what extend two fragments of code are functionally related.
 For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings to increase the chance that we can refactor the clone while improving the design.
@@
 This has allowed for large scale analyses of duplication.
-However, these clone type definitions have shortcomings which makes the clones detected in correspondance with these definitions less valuable for (automated) refactoring purposes.
+However, these clone type definitions have shortcomings which makes the clones detected in correspondence with these definitions less valuable for (automated) refactoring purposes.
 
@@
 Because of this, it is hard to verify which of the used types have the same underlying implementation.
-This can make type 1 clones less suitable for refactoring purposes, as they require additional judgement regarding the refactorability of such a clone.
+This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
 When aiming to automatically refactor clones, applying refactorings to clones as shown in figure \ref{fig:type1}, is bound to be error prone and result in a uncompilable project or a difference in functionality.
@@
 This definition requires cloned fragments to be not just textually equal, but also functionally equal.
-Although requiring fragements to be functionally equal, type 1R clones do not allow for change in implementation (like type 4 clones).
-We check functional equality of two fragments by validating the equality of the fully qualityfied identifier for referenced types, methods and variables.
+Although requiring fragments to be functionally equal, type 1R clones do not allow for change in implementation (like type 4 clones).
+We check functional equality of two fragments by validating the equality of the fully qualified identifier for referenced types, methods and variables.
 Type 1R clones are a subset of type 1 clones.
@@
 When we call two methods with an identical name, we can in fact call different methods.
-This is another reason that textually identical code fragements can differ functionally.
+This is another reason that textually identical code fragments can differ functionally.
 
@@
 In literature, these definitions are mainly aimed towards reasoning about duplication in source code.
-When considering these types for refactoring, the goal becomes slighly different.
+When considering these types for refactoring, the goal becomes slightly different.
 Because of this, having separate clone type definitions does not have any value.
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{img/CloneRefactorOverall}
+  \caption{CloneRefactor overall process.}
+  \label{fig:clonerefactorprocess}
+\end{figure}
+
+Figure \ref{fig:clonerefactorprocess} shows the overall process used by CloneRefactor.
+First, we detect clones on basis of a Java codebase, given a Java project from disk and a configuration.
+The clone detection process is further explained in section \ref{sec:clonedetection}.
+After all clones are found, CloneRefactor maps the context of the clones.
+On basis of this context, CloneRefactor applies transformations to the source code for clones for which we have configured a refactoring.
+
 \subsection{JavaParser}
@@
 
-\subsection{Clone Detection}
+\subsection{Clone Detection}\ref{sec:clonedetection}
 To detect clones, CloneRefactor parses the AST aqcuired from JavaParser to an unweighted graph structure.
@@
 \end{itemize}
-We do not create a seperate grid for each class file, so the statement/declaration preceding or following could be in a different file.
+We do not create a separate grid for each class file, so the statement/declaration preceding or following could be in a different file.
 While mapping these relations, we maintain a hashed map containing the last occurrence of each unique statement.
@@
 Apart from that, we do not compare the names of method, class, interface and enum declarations.
+
+In this stage, \textbf{type 3R} clones have the same compare rules as type 2R clones.
 

### 2019-06-14 sections/background.tex
Better examples

@@
 	\includegraphics[width=1\textwidth]{img/clone-pair}
-	\caption{Example of a clone pair, as found in the \href{https://github.com/Danny02/JOpenCTM}{JOpenCTM} project.}
+	\caption{Example of a clone pair, as found in the \href{https://github.com/Widen/valet}{Valet} project.}
 	\label{fig:clonepair}
@@
 
-Figure \ref{fig:cloneclass} displays two clone classes.
-These clone classes are separated by a single line that is different.
-The first clone class spans over both the constructor and a method of this class.
+Figure \ref{fig:cloneclass} displays a clone class with three clone instances.
 
 \begin{figure}[H]
-	\includegraphics[width=1\textwidth]{img/clone-class}
-	\caption{Example of a clone class, as found in the \href{https://github.com/Danny02/JOpenCTM}{JOpenCTM} project.}
+	\includegraphics[width=0.8\textwidth]{img/clone-class}
+	\caption{Example of a clone class, as found in the \href{https://github.com/Widen/valet}{Valet} project.}
 	\label{fig:cloneclass}

### 2019-06-14 sections/research.tex
Better examples

@@
 We analyzed this behavior using a set of control projects.
-\item \textbf{TODO: Criterium.} We assembled a number of test projects to assess the validity of clone detection tools.
+\item \textbf{TODO: Criterium.}\simon{TODO} We assembled a number of test projects to assess the validity of clone detection tools.
 On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{img/CloneRefactorOverall}
+  \includegraphics[width=0.8\columnwidth]{img/CloneRefactorOverall}
   \caption{CloneRefactor overall process.}
@@
 
-\subsection{Clone Detection}\ref{sec:clonedetection}
+\subsection{Clone Detection}\label{sec:clonedetection}
 To detect clones, CloneRefactor parses the AST aqcuired from JavaParser to an unweighted graph structure.

### 2019-06-14 sections/background.tex
Starting to work on Ana's feedback

@@
 \begin{figure}[H]
+	\centering
 	\includegraphics[width=1\textwidth]{img/clone-pair}
@@
 \begin{figure}[H]
+	\centering
 	\includegraphics[width=0.8\textwidth]{img/clone-class}
@@
 There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
-
-\subsection{Type 2 clones}
-Relating this to the clone class example of \ref{fig:cloneclass}, the complete class would be flagged as a type 2 clone.
-This is displayed in figure \ref{fig:type2cloneclass}.
-Considering such clones displays the opportunity to refactor the class as a whole.
-
-\begin{figure}[H]
-	\includegraphics[width=1\textwidth]{img/type-2-clone-class}
-	\caption{The clone displayed in figure \ref{fig:cloneclass} as a type 2 clone.}
-	\label{fig:type2cloneclass}
-\end{figure}
 

### 2019-06-14 sections/research.tex
Starting to work on Ana's feedback

@@
 First of all, we use JavaParser to read a project from disk and build an AST, one class file at a time.
-Each AST is then converted to a grid that maps relations between statements, further explained in section \ref{sec:clonegrid}.
-On basis of this grid, we detect clone classes and verify them using three thresholds (in order of importance):
+Each AST is then converted to a directed graph that maps relations between statements, further explained in section \ref{sec:clonegraph}.
+On basis of this graph, we detect clone classes and verify them using three thresholds (in order of importance):
 \begin{itemize}
@@
 
-\subsubsection{Generating the clone grid}\label{sec:clonegrid}
-First of all, we parse the AST obtained from JavaParser into what we call a clone grid.
-Although it is not a grid in an original sense, thinking of it as a grid makes it easier to comprehend (this is explained in section \ref{sec:detectingclones} in more detail).
+\subsubsection{Generating the clone graph}\label{sec:clonegraph}
+First of all, we parse the AST obtained from JavaParser into a directed graph structure.
 We have chosen to base our clone detection around statements as the smallest unit of comparison.
@@
 
-Building the ``clone grid'' consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
+Building the clone graph consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
 \begin{itemize}
@@
 \end{itemize}
-We do not create a separate grid for each class file, so the statement/declaration preceding or following could be in a different file.
+We do not create a separate graph for each class file, so the statement/declaration preceding or following could be in a different file.
 While mapping these relations, we maintain a hashed map containing the last occurrence of each unique statement.
-This map is used to quickly find out whether a statement is cloned with another.
-An example of such a grid is displayed in figure \ref{fig:clonegridsimple}.
+This map is used to efficiently find out whether a statement is cloned with another.
+An example of such a graph is displayed in figure \ref{fig:clonegraphsimple}.
 
@@
   \includegraphics[width=1\columnwidth]{img/CodeGraph2}
-  \caption{Clone grid as built by CloneRefactor.}
-  \label{fig:clonegridsimple}
+  \caption{Abstract example of a part of a possible clone graph as built by CloneRefactor.}
+  \label{fig:clonegraphsimple}
 \end{figure}
 
-We generally call the declarations and statements represented in this grid \textit{nodes}.
-The relations \textit{next} and \textit{previous} in this grid are represented as an undirected relation.
-The relations representing duplicated are directed.
+We refer to the declarations and statements in this graph as \textit{nodes}.
+The relations \textit{next} and \textit{previous} in this graph are represented as an twodirectional arrow.
+The relations representing duplication are directed.
 This is a restriction we've chosen as it creates an important constraint for the clone detection process.
@@
 \subsubsection{Comparing Statements/Declarations}
-In the previous section we described a ``duplicate'' relation between nodes in the clone grid built by CloneRefactor.
-Whether two nodes in this grid are duplicates of each other is dependent on the clone type.
+In the previous section we described a ``duplicate'' relation between nodes in the clone graph built by CloneRefactor.
+Whether two nodes in this graph are duplicates of each other is dependent on the clone type.
 In this section, we will describe for each type how we compare statements and declarations assess whether they are clones of each other.
@@
 \subsubsection{Detecting Clones} \label{sec:detectingclones}
-After building the clone grid, we use it to detect clones.
+After building the clone clone graph, we use it to detect clones.
 We decided to focus on the detection of clone classes rather than clone pairs because clone pairs do not provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}.
@@
 
-As stated in the previous section, nodes in the grid link to \textit{preceding} cloned statement.
+As stated in the previous section, nodes in the graph link to \textit{preceding} cloned statement.
 This implies that the first node that is cloned does not have any clone relation, as there are no clones preceding it (only following it).
-Because of this, we start our clone detection process at the final location encountered while building the grid.
+Because of this, we start our clone detection process at the final location encountered while building the graph.
 For this node, we collect all nodes it is cloned with.
@@
 This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node.
-As an example, see figure \ref{fig:clonegrid}.
+As an example, see figure \ref{fig:clonegraph}.
 
@@
   \centering
-  \includegraphics[width=1\columnwidth]{img/CodeGraph3}
-  \caption{Clone grid with a clone class consisting of three clone instances marked.}
-  \label{fig:clonegrid}
+  \includegraphics[width=1\columnwidth]{img/CodeGraph4}
+  \caption{Clone graph with a clone class consisting of three clone instances marked.}
+  \label{fig:clonegraph}
 \end{figure}
 
-Using the example shown in figure \ref{fig:clonegrid} we can explain how we detect clones.
+Using the example shown in figure \ref{fig:clonegraph} we can explain how we detect clones.
 Suppose we are finding clones for two files and the final node of the second file is a variable declarator.
@@
 
-The grid representation shown in figure \ref{fig:clonegrid} is only shown as a grid for ease of comprehension.
-In fact, it is not a grid, but a graph.
+The graph representation shown in figure \ref{fig:clonegraph} is only shown as a graph for ease of comprehension.
+In fact, it is not a graph, but a graph.
 Eventually, following only the ``previous node'' relations, we can get from (6) to (2).

### 2019-06-15 sections/background.tex
Added notes

@@
 \subsection{Type 4 clones}
-For this thesis we have chosen not to consider type 4 clones for refactoring, because they are both hard to detect and hard to refactor (how to choose the best alternative for a certain computation could be a thesis in itself).
+For this study we have chosen not to consider type 4 clones for refactoring, because they are both hard to detect and hard to refactor (how to choose the best alternative for a certain computation could be a thesis in itself).
 A study by Kodhai et al \cite{kodhai2013method} looks into the distribution of the different types of clones in several open source systems (see table 6 of his study).

### 2019-06-16 sections/research.tex
Better formulas

@@
 
-$$T2R\ Variability\ Percentage=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
-$$Diff=Amount\ that\ differ\ from\ other\ clone\ instances\ in\ the\ clone\ class$$
-$$Total\ =\ Total\ number\ in\ the\ clone\ instance$$
-$$l=Number\ of\ literals$$
-$$v=Number\ of\ variables$$
-$$m=Number\ of\ method\ calls$$
-$$t=Number\ of\ tokens$$
+$$\text{T2R Variability Percentage}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
+$$\text{Diff = Amount that differ from other clone instances in the clone class}$$
+$$\text{Total = Total number in the clone instance}$$
+$$\text{l = Number of literals}$$
+$$\text{v = Number of variables}$$
+$$\text{m = Number of method calls}$$
+$$\text{t = Number of tokens}$$
 
@@
 
-\section{Type 3R clones}
+\subsection{Type 3R clones}
 Type 3 clones allow any change in statements, often bounded by a similarity threshold.

### 2019-06-16 sections/research.tex
Better math

@@
 $$\text{T2R Variability Percentage}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
-$$\text{Diff = Amount that differ from other clone instances in the clone class}$$
-$$\text{Total = Total number in the clone instance}$$
-$$\text{l = Number of literals}$$
-$$\text{v = Number of variables}$$
-$$\text{m = Number of method calls}$$
-$$\text{t = Number of tokens}$$
+$$Diff = \text{Amount that differ from other clone instances in the clone class}$$
+$$Total = \text{Total number in the clone instance}$$
+$$l = \text{Number of literals}$$
+$$v = \text{Number of variables}$$
+$$m = \text{Number of method calls}$$
+$$t = \text{Number of tokens}$$
 
@@
 
-$$T3R\ Gap\ Percentage=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100$$
-$$Statements = The\ amount\ of\ statements\ in\ this\ code\ fragment$$
-$$C_{gap} = The\ gap between two clones$$
-$$C_{above} = The\ clone\ instance\ above\ the\ gap$$
-$$lower = The clone instance below the gap$$
+$$\text{T3R Gap Percentage}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100$$
+$$Statements = \text{The amount of statements in this code fragment}$$
+$$C_{gap} = \text{The gap between two clones}$$
+$$C_{above} = \text{The clone instance above the gap}$$
+$$C_{below} = \text{The clone instance below the gap}$$
 

### 2019-06-26 sections/research.tex
New example for clone graph

@@
 Whether two nodes in this graph are duplicates of each other is dependent on the clone type.
-In this section, we will describe for each type how we compare statements and declarations assess whether they are clones of each other.
+In this section, we will describe for each type how we compare statements and declarations to assess whether they are clones of each other.
 
@@
   \centering
-  \includegraphics[width=1\columnwidth]{img/CodeGraph4}
-  \caption{Clone graph with a clone class consisting of three clone instances marked.}
+  \includegraphics[width=1\columnwidth]{img/CloneGraphCode}
+  \caption{CloneRefactor extracts statements and declarations from source code.}
+  \label{fig:clonegraph}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{img/CodeGraphExample}
+  \caption{Example of a clone graph built by CloneRefactor.}
   \label{fig:clonegraph}

### 2019-06-26 sections/research.tex
Clarified the example a bit more

@@
 This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node.
-As an example, see figure \ref{fig:clonegraph}.
+As an example, see figure \ref{fig:clonegraph} and \label{fig:clonegraph2}.
 
@@
   \caption{Example of a clone graph built by CloneRefactor.}
-  \label{fig:clonegraph}
+  \label{fig:clonegraph2}
 \end{figure}
 
-Using the example shown in figure \ref{fig:clonegraph} we can explain how we detect clones.
+Using the example shown in figure \ref{fig:clonegraph} and \label{fig:clonegraph2} we can explain how we detect clones.
 Suppose we are finding clones for two files and the final node of the second file is a variable declarator.
@@
 We now have a single statement clone class of three clone instances (1, 2 and 3).
+
 Next, we move to the previous line (4).
@@
 Because of this, the clone class of (1, 2 and 3) comes to an end.
-It will be checked against the thresholds, and if adhering to the threshold, considered a clone.
-We then go further to yet the previous node (6).
+It will be checked against the thresholds, and if adhering to the thresholds, considered a clone.
+
+We then go further to the previous node (6).
 In this case, this node does not have any clones.
 This means we check the (2 and 5, 1 and 4) clone class against the thresholds, and if it adheres, consider it a clone.
-Dependent on the thresholds, we'd now have found two clone classes.
+Dependent on the thresholds, this example can result in a total of two clone classes.
 
-The graph representation shown in figure \ref{fig:clonegraph} is only shown as a graph for ease of comprehension.
-In fact, it is not a graph, but a graph.
 Eventually, following only the ``previous node'' relations, we can get from (6) to (2).
@@
 However, after we check this clone against the thresholds, we check whether it is a subset of any exisiting clone.
-If this is the case, we discard the clone.
+If this is the case (which it is for this example), we discard the clone.
 

### 2019-06-26 sections/research.tex
Clone types summarized

@@
 
-\subsection{Type 2R clones}
+\subsection{Type 2R clones} \label{sec:type2r}
 Type 2R clones are modelled after type 2 clones, which allow any change in identifiers, literals, types, layout, and comments.
@@
 
+\begin{eqfloat}\label{eq:type2r}
 $$\text{T2R Variability Percentage}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
@@
 $$t = \text{Number of tokens}$$
+\caption{Type 2R variability threshold formula}\end{eqfloat}
 
@@
 
+\begin{eqfloat}\label{eq:type3r}
 $$\text{T3R Gap Percentage}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100$$
@@
 $$C_{below} = \text{The clone instance below the gap}$$
+\caption{Type 3R clone merge opportunities threshold formula}\end{eqfloat}
 
@@
 \end{figure}
+
+\subsection{Clone types summarized}
+The given clone definitions (types 1R, 2R and 3R) are refactoring-oriented in the sense that they were designed after the literature type definitions but with a concrete refactoring opportunity in mind.
+Summarized, these types can be explained as follows:
+
+Type 1R: Allows no difference between cloned fragments, making it possible to refactor both fragments to a method call that contains the code of both locations.
+Type 2R: Allows difference between cloned fragments in controlled features of a codebase. Refactoring opportunities for these controlled features are known, allowing refactoring with a minor tradeoff.
+Type 3R: Allows any difference. When refactored, this difference must be wrapped in its own block, which entails a major tradeoff.
 
@@
 
-\subsubsection{Validating the type 2 variability threshold}
+\subsubsection{Validating the type 2R variability threshold}
+In the definition of type 2R (see section \ref{eq:type2r}) clones we described how type 2R clones work on basis of a variability threshold. This threshold,
 

### 2019-06-27 sections/research.tex
Something about 2R variability

@@
 \subsubsection{Validating the type 2R variability threshold}
-In the definition of type 2R (see section \ref{eq:type2r}) clones we described how type 2R clones work on basis of a variability threshold. This threshold,
+In the definition of type 2R (see section \ref{eq:type2r}) clones we described how type 2R clones work on basis of a variability threshold.
+This threshold, shown more formally in formula \ref{eq:type2r}, is checked by CloneRefactor.
+Implementing such a threshold involves some important design decisions, and has a lot of underwater complexity.
+In this section we explain the way CloneRefactor uses to verify the type 2R variability threshold.
 

### 2019-06-27 sattose/paper.tex
Restructuring, removing, redoing, etc paper

@@
 
+\section{Addressing problems with clone type definitions}\label{chap:clonetypes}
+For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings (see section \ref{chap:backgroundclonetypes} for these definitions) to increase the chance that we can merge the clone while improving the design.
+Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.
+
+\subsection{Type 1R clones} \label{chap:type1clones}
+Type 1 clones are identical clone fragments except for variations in whitespace and comments \cite{roy2007survey}.
+However, when two clone fragments are textually identical, it does not yet indicate that they are functionally identical.
+Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and even variables can be of a different type.
+In such cases refactoring opportunities could be invalidated.
+Therefore, we propose an alternative definition of type 1 clones.
+We have named it ``type 1R clones''.
+The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).
+Type 1R clones differ from type 1 clones as follows:
+\begin{itemize}
+  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (e.g.
+\texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object).
+This way we can validate whether two method references, like method calls, are functionally equal.
+In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments.
+This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
+  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
+  \item \textbf{Compare the equality of the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types.
+This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive.
+To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
+  \item \textbf{Compare the equality of the fully qualified identifier for method references and call signatures.} This is to prevent a change in functionality after merging the clone, as methods with equal names/parameters can still contain different functionality.
+\end{itemize}
+
+\subsection{Type 2R clones}
+Type 2 clones allow any change in identifiers, literals, types, layout, and comments.
+For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
+This could render two methods that have an entirely different functionality as clones.
+Merging such clones can be harmful instead of helpful.
+
+We tackle these problems with type 2R clones to be able to detect such clones that can and should be merged.
+Our definition ensures functional similarity by applying the following changes to type 2 clones:
+
+\begin{itemize}
+  \item \textbf{Considering types:} Type 2 clones do not consider types.
+However, this can make a code fragment very hard to refactor, as different types can describe different functional concepts.
+Because of this, we propose that type 2R clones should consider types like type 1R clones do.
+  \item \textbf{Having a distinction between different variables:} For type 2 clones, no identifiers would be taken into account.
+We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables.
+For instance, if we call a method like this: \texttt{myMethod(var1, var2)}, or call this method like this: \texttt{myMethod(var1, var1)}.
+Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
+  \item \textbf{Defining a threshold for variability in literals:} For type 2 clones no literals would be taken into account.
+We agree, as when merging the clone (for example by extracting a method), we can turn the literal into a method parameter.
+However, we would argue that thresholds matter here.
+How many literals may differ for the segment still to be considered a clone with another segment?
+We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
+  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary.
+However, because of this, completely different methods can be called in cloned fragments as a result.
+This poses serious challenges on refactoring and makes it more disputable whether such a clone is harmful for the maintainability of the code.
+This is because different method identifiers can describe a completely different functionality.
+Therefore, we suggest considering the call signatures of cloned methods when they are compared.
+We can allow variability in the rest of method identifiers by passing the function as a parameter.
+To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
+\end{itemize}
+
+\subsection{Type 3R clones}
+Type 3 clones are even more permissive than type 2 clones, allowing added and removed statements.
+For these clones, thresholds matter a lot to make sure that not the whole project is detected as a clone of itself.
+The main question for this study regarding type 3 clones is: \textit{``how can we merge type 3 clones while improving the design?''}.
+
+Clone instances in type 3 clones are almost always different in functionality.
+As we have to ensure equal functionality after merging the clone, we have to wrap the difference in statements between the clone instances in conditional blocks.
+We can then pass a variable to indicate which path should be taken through the code (either a boolean or an enumeration).
+Such a refactoring would make added statements that are contiguous less harmful for the design than added statements that are scattered throughout the cloned fragment.
+
+We also argue that statements that are not common between two clone instances, should not count towards the size of the clone (and thus towards the threshold which determines whether the clone will be taken into account).
+As for the detection of type 3 clones, we think the easiest opportunity to detect these clones is to consider it as a postprocessing step after clone detection.
+By trying to find short gaps between clones, we can find opportunities to merge clone classes into a single type 3 clone class.
+The amount of statements that this ``short gap'' can maximally span should be dependent on a threshold value.
+
 \section{Clone Detection}\label{chap:clonedetection}
@@
 We consider ``number of lines'' to be the least important, as it highly depends on the developer of the codebase (and we want to prevent this dependence).
-Empirical research indicates that setting the ``number of statements/declarations'' to 3 ensures that many non-harmful clones are filtered out, as lower thresholds detect many clones that pose no harm to the design of the code.
-On the downside, this also filters out some harmful antipatterns.
-For instance, if a cloned statement has many tokens we might want to consider it a clone even if it spans a single statement (as a cloned line with many tokens is more harmful than one with few).
-
-The measurements in our study use the following thresholds:
-\begin{itemize}
-  \item \textbf{Number of statements/declarations:} 1
-  \item \textbf{Number of tokens:} 12
-  \item \textbf{Number of lines:} 1
-\end{itemize}
-
-\section{Addressing problems with clone type definitions}\label{chap:clonetypes}
-For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings (see section \ref{chap:backgroundclonetypes} for these definitions) to increase the chance that we can merge the clone while improving the design.
-Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.
-
-\subsection{Type 1R clones} \label{chap:type1clones}
-Type 1 clones are identical clone fragments except for variations in whitespace and comments \cite{roy2007survey}.
-However, when two clone fragments are textually identical, it does not yet indicate that they are functionally identical.
-Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and even variables can be of a different type.
-In such cases refactoring opportunities could be invalidated.
-Therefore, we propose an alternative definition of type 1 clones.
-We have named it ``type 1R clones''.
-The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).
-Type 1R clones differ from type 1 clones as follows:
-\begin{itemize}
-  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (e.g.
-\texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object).
-This way we can validate whether two method references, like method calls, are functionally equal.
-In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments.
-This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
-  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
-  \item \textbf{Compare the equality of the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types.
-This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive.
-To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
-  \item \textbf{Compare the equality of the fully qualified identifier for method references and call signatures.} This is to prevent a change in functionality after merging the clone, as methods with equal names/parameters can still contain different functionality.
-\end{itemize}
-
-\subsection{Type 2R clones}
-Type 2 clones allow any change in identifiers, literals, types, layout, and comments.
-For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
-This could render two methods that have an entirely different functionality as clones.
-Merging such clones can be harmful instead of helpful.
-
-We tackle these problems with type 2R clones to be able to detect such clones that can and should be merged.
-Our definition ensures functional similarity by applying the following changes to type 2 clones:
-
-\begin{itemize}
-  \item \textbf{Considering types:} Type 2 clones do not consider types.
-However, this can make a code fragment very hard to refactor, as different types can describe different functional concepts.
-Because of this, we propose that type 2R clones should consider types like type 1R clones do.
-  \item \textbf{Having a distinction between different variables:} For type 2 clones, no identifiers would be taken into account.
-We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables.
-For instance, if we call a method like this: \texttt{myMethod(var1, var2)}, or call this method like this: \texttt{myMethod(var1, var1)}.
-Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
-  \item \textbf{Defining a threshold for variability in literals:} For type 2 clones no literals would be taken into account.
-We agree, as when merging the clone (for example by extracting a method), we can turn the literal into a method parameter.
-However, we would argue that thresholds matter here.
-How many literals may differ for the segment still to be considered a clone with another segment?
-We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
-  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary.
-However, because of this, completely different methods can be called in cloned fragments as a result.
-This poses serious challenges on refactoring and makes it more disputable whether such a clone is harmful for the maintainability of the code.
-This is because different method identifiers can describe a completely different functionality.
-Therefore, we suggest considering the call signatures of cloned methods when they are compared.
-We can allow variability in the rest of method identifiers by passing the function as a parameter.
-To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
-\end{itemize}
-
-\subsection{Type 3R clones}
-Type 3 clones are even more permissive than type 2 clones, allowing added and removed statements.
-For these clones, thresholds matter a lot to make sure that not the whole project is detected as a clone of itself.
-The main question for this study regarding type 3 clones is: \textit{``how can we merge type 3 clones while improving the design?''}.
-
-Clone instances in type 3 clones are almost always different in functionality.
-As we have to ensure equal functionality after merging the clone, we have to wrap the difference in statements between the clone instances in conditional blocks.
-We can then pass a variable to indicate which path should be taken through the code (either a boolean or an enumeration).
-Such a refactoring would make added statements that are contiguous less harmful for the design than added statements that are scattered throughout the cloned fragment.
-
-We also argue that statements that are not common between two clone instances, should not count towards the size of the clone (and thus towards the threshold which determines whether the clone will be taken into account).
-As for the detection of type 3 clones, we think the easiest opportunity to detect these clones is to consider it as a postprocessing step after clone detection.
-By trying to find short gaps between clones, we can find opportunities to merge clone classes into a single type 3 clone class.
-The amount of statements that this ``short gap'' can maximally span should be dependent on a threshold value.
 

### 2019-06-27 sattose/paper.tex
Working on paper type 3R

@@
 \def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
+\newfloat{eqfloat}{h}{eqflts}
+\floatname{eqfloat}{Equation}
 
@@
 \subsection{Type 3R clones}
-Type 3 clones are even more permissive than type 2 clones, allowing added and removed statements.
-For these clones, thresholds matter a lot to make sure that not the whole project is detected as a clone of itself.
-The main question for this study regarding type 3 clones is: \textit{``how can we merge type 3 clones while improving the design?''}.
+Type 3 clones allow any change in statements (added, removed and changed statements).
+Many clone detection tools have implemented this type by introducing a similarity threshold \cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
+This similarity threshold entails that two fragments may differ by a certain percentage.
+This means that type 3R allows the inclusion of a statement that is not detected by type 1 or 2 clone detection.
+When looking at how we can refactor a statement that is not included by one clone instance but is in another, we find that we require a conditional block to make up for the difference in statements.
+This is a tradeoff, as an added conditional block increases the complexity of the system.
+Because of that, we defined type 3R clones in such a way that they are directed towards finding clones that are worth this tradeoff.
+This entails the following:
 
-Clone instances in type 3 clones are almost always different in functionality.
-As we have to ensure equal functionality after merging the clone, we have to wrap the difference in statements between the clone instances in conditional blocks.
-We can then pass a variable to indicate which path should be taken through the code (either a boolean or an enumeration).
-Such a refactoring would make added statements that are contiguous less harmful for the design than added statements that are scattered throughout the cloned fragment.
+\begin{itemize}
+  \item \textbf{The difference in statements must bridge a gap between two clones that were valid by the original thresholds}.
+We have named this difference between the two clones, in this examples containing a single statement, the \textit{gap}.
+  \item \textbf{The size of the gap between two clones is limited by a threshold.} This threshold is displayed in equation \ref{eq:type3r}.
+  \item item
+\end{itemize}
+For type 3R clones we state that .  This gap has a threshold for type 3R, which is calculated by the following formula:
 
-We also argue that statements that are not common between two clone instances, should not count towards the size of the clone (and thus towards the threshold which determines whether the clone will be taken into account).
-As for the detection of type 3 clones, we think the easiest opportunity to detect these clones is to consider it as a postprocessing step after clone detection.
-By trying to find short gaps between clones, we can find opportunities to merge clone classes into a single type 3 clone class.
-The amount of statements that this ``short gap'' can maximally span should be dependent on a threshold value.
+\begin{eqfloat}\label{eq:type3r}
+$$\text{T3R Gap Percentage}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100$$
+$$Statements = \text{The amount of statements in this code fragment}$$
+$$C_{gap} = \text{The gap between two clones}$$
+$$C_{above} = \text{The clone instance above the gap}$$
+$$C_{below} = \text{The clone instance below the gap}$$
+\caption{Type 3R clone bridging opportunities threshold formula}\end{eqfloat}
+
+Defining a gap threshold entails that, different from type 3 clones, the difference in statements cannot be at the beginning or the end of a cloned block.
+It is rather somewhere within, as it must bridge two existent clones.
+This holds the most value when looking at refactoring such clones.
+A difference at the beginning or
+
+Apart from this threshold, the gap in between clones may not span over different blocks.
+Look at figure \ref{fig:type3invalid} for an example of this.
+We cannot refactor both statements into a single conditional block.
+We could however use two conditional blocks, but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for type 3R clones.
 

### 2019-06-27 sattose/paper.tex
Finished up type 3R

@@
   \item \textbf{The difference in statements must bridge a gap between two clones that were valid by the original thresholds}.
-We have named this difference between the two clones, in this examples containing a single statement, the \textit{gap}.
-  \item \textbf{The size of the gap between two clones is limited by a threshold.} This threshold is displayed in equation \ref{eq:type3r}.
-  \item item
+This entails that, different from type 3 clones, the difference in statements cannot be at the beginning or the end of a cloned block.
+It is rather somewhere within, as it must bridge two existent clones.
+This holds the most value when looking at refactoring such clones.
+A difference at the beginning or end of a cloned block can better not be refactored.
+  \item \textbf{The size of the gap between two clones is limited by a threshold.} This threshold is calculated by taking the percentage of the amount of statements in the gap over the amount of statements that both clones that are being bridged span.
+This is displayed in equation \ref{eq:type3r}.
+  \item \textbf{The gap may not span a partial block.} To make sure that the type 3R clone can be refactored, we do not allow the gap to span a part of a block, for instance the declaration and a part of the body of a for-loop.
+The reason for this is that it is not possible to wrap a partially spanned block in a single conditional statement.
+We could however use multiple conditional blocks (one for each block spanned), but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for type 3R clones.
 \end{itemize}
-For type 3R clones we state that .  This gap has a threshold for type 3R, which is calculated by the following formula:
 
@@
 \caption{Type 3R clone bridging opportunities threshold formula}\end{eqfloat}
-
-Defining a gap threshold entails that, different from type 3 clones, the difference in statements cannot be at the beginning or the end of a cloned block.
-It is rather somewhere within, as it must bridge two existent clones.
-This holds the most value when looking at refactoring such clones.
-A difference at the beginning or
-
-Apart from this threshold, the gap in between clones may not span over different blocks.
-Look at figure \ref{fig:type3invalid} for an example of this.
-We cannot refactor both statements into a single conditional block.
-We could however use two conditional blocks, but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for type 3R clones.
 

### 2019-06-27 sattose/paper.tex
Removed the survey

@@
 where are the four criteria coming from?}
-
-\subsection{Survey on Clone Detection Tools}
-\label{ch:tool-overview}
-We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities.
-The results of our survey are displayed in table~\ref{table:dettools}.
-We chose a set of tools that are open source and can analyze a popular object-oriented programming language.
-Next, we formulate the following four criteria by which we analyze these tools:
-\begin{enumerate}
-    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones.
-We want to perform an analysis on all clones in projects to get a complete overview.
-\item \textbf{Should find all clones in created control projects.} We assembled a number of test projects to assess the validity of clone detection tools.
-On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
-\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be merged.
-Sometimes, textual equality between code fragments does not imply that these can be merged (this is described more elaborately in section \ref{chap:type1clones}).
-Because of this, we want to use a clone detection tool that can analyze such structures.
-\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}).
-To achieve this, the tool needs to be able to allow those threshold changes.
-This can be either through simple changes of the source code, or by using some configuration file.
-\end{enumerate}
-
-\begin{table}[H]
- \begin{center}
-  \caption{Our survey on clone detection tools.} \label{table:dettools}
-  \medskip
-\begin{tabular}{|l|l|l|l|l|l|}
-\hline
-\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
-Siamese \cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
-NiCAD \cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
-CPD \cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
-\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
-CCFinderSW \cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
-\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
-BigCloneEval \cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
-Deckard \cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
-Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}.
-This repository contains all scripts that were used to retrieve the data that is displayed in this paper.}.
 

### 2019-06-27 sattose/paper.tex
Merge -> Refactor

@@
 \usepackage{tikz}
-\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
 \newfloat{eqfloat}{h}{eqflts}
 \floatname{eqfloat}{Equation}
+\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
 
-\title{Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -}
+\title{Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -}
 
@@
 \section{Addressing problems with clone type definitions}\label{chap:clonetypes}
-For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings (see section \ref{chap:backgroundclonetypes} for these definitions) to increase the chance that we can merge the clone while improving the design.
+For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings (see section \ref{chap:backgroundclonetypes} for these definitions) to increase the chance that we can refactor the clone while improving the design.
 Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.
@@
 
-We tackle these problems with type 2R clones to be able to detect such clones that can and should be merged.
+We tackle these problems with type 2R clones to be able to detect such clones that can and should be refactored.
 Our definition ensures functional similarity by applying the following changes to type 2 clones:
@@
 When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances.
-This relation has a big impact on how a clone should be merged, in order to improve the software design in the process.
+This relation has a big impact on how a clone should be refactored, in order to improve the software design in the process.
 In this section, we display measurements we conducted on the corpus introduced in section \ref{chap:corpus}.
@@
 \section{Merging duplicate code through method extraction}\label{chap:mergingdups}
-The most used technique to merge clones is method extraction (creating a new method on basis of the contents of clones).
+The most used technique to refactor clones is method extraction (creating a new method on basis of the contents of clones).
 However, method extraction cannot be applied in all cases.
@@
     \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a method.
-Then, based on the relation between the clone instances, further refactoring techniques can be used to merge the extracted methods (for instance ``pull up method'' for clones in sibling classes).
+Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
     \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements.
@@
 We propose that fully qualified identifiers of method call signatures and type references should be considered instead of their plain text representation, to ensure refactorability.
-Furthermore, we propose that one should define thresholds for variability in variables, literals and method calls, in order to limit the number of parameters that the merged unit shall have.
+Furthermore, we propose that one should define thresholds for variability in variables, literals and method calls, in order to limit the number of parameters that the refactored unit shall have.
 

### 2019-06-27 sattose/paper.tex
Fixed some math package problem
Better(?) type 3 equation

@@
 \usepackage{todonotes}
+\usepackage{amsmath,amssymb}
 \usepackage{tikz}
@@
 
-\begin{eqfloat}\label{eq:type3r}
-$$\text{T3R Gap Percentage}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100$$
-$$Statements = \text{The amount of statements in this code fragment}$$
+\begin{equation}\label{eq:type3r}
+\text{T3R Gap}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100
+\end{equation}
+$$Statements = \text{Statements in a code fragment}$$
 $$C_{gap} = \text{The gap between two clones}$$
@@
 $$C_{below} = \text{The clone instance below the gap}$$
-\caption{Type 3R clone bridging opportunities threshold formula}\end{eqfloat}
 

### 2019-06-27 sattose/paper.tex
Type 2R equation

@@
 We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
+This threshold is displayed in equation \ref{eq:type2r}.
   \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary.
@@
 \end{itemize}
+
+\begin{eqfloat}\label{eq:type2r}
+$$\text{T2R Variability}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
+$$Diff = \text{Number that differ from other clone instances}$$
+$$Total = \text{Total number in the clone instance}$$
+$$l = \text{Literals in clone}$$
+$$v = \text{Variables in clone}$$
+$$m = \text{Method calls in clone}$$
+$$t = \text{Tokens in clones}$$
+\caption{Type 2R variability threshold formula}\end{eqfloat}
 

### 2019-06-27 sections/research.tex
Type 2R equation

@@
 $$Total = \text{Total number in the clone instance}$$
-$$l = \text{Number of literals}$$
-$$v = \text{Number of variables}$$
-$$m = \text{Number of method calls}$$
-$$t = \text{Number of tokens}$$
+$$l = \text{Literals in clone}$$
+$$v = \text{Variables in clone}$$
+$$m = \text{Method calls in clone}$$
+$$t = \text{Tokens in clones}$$
 \caption{Type 2R variability threshold formula}\end{eqfloat}
@@
 Type 3 clones allow any change in statements, often bounded by a similarity threshold.
-This means that type 3R allows the inclusion of a statement that is not detected by type 1 or 2 clone detection.
+This means that type 3 clones allow the inclusion of a statement that is not detected by type 1 or 2 clone detection.
 When looking at how we can refactor a statement that is not included by one clone instance but is in another, we find that we require a conditional block to make up for the difference in statements.

### 2019-06-27 sattose/paper.tex
Fixed T2R threshold

--- 2019-06-27 sattose/paper.tex
@@
 \end{itemize}
+
+\begin{equation}\label{eq:type2r}
+\text{T2R}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100
+\end{equation}
+$$Diff = \text{Number that differ from other clone instances}$$
+$$Total = \text{Total number in the clone instance}$$
+$$l = \text{Literals in clone}$$
+$$v = \text{Variables in clone}$$
+$$m = \text{Method calls in clone}$$
+$$t = \text{Tokens in clones}$$
 

### 2019-06-27 sattose/paper.tex
About clone types

@@
 \subsection{Clone types}\label{chap:backgroundclonetypes}
-In a 2007 survey by Roy et al. \cite{roy2007survey} he defines four types of clones:\\
+In a 2007 survey by Roy et al. \cite{roy2007survey} he defines several types of clones:\\
 \textbf{Type 1:} Identical code fragments except for variations in whitespace (may also be variations in layout) and comments.\\
@@
 \textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\
-\textbf{Type 4:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
 
@@
 Higher clone types also become more disputable whether they actually indicate a harmful anti-pattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}).
+
+There also exists a type 4 clone, denoting functionally equal code. We decided not to consider these clones in this study, because of the serious challenges in their detection and refactoring.
 
@@
 For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings (see section \ref{chap:backgroundclonetypes} for these definitions) to increase the chance that we can refactor the clone while improving the design.
-Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.
+
+\section{Shortcomings of clone types}
+The clone definitions, as outlined in section \ref{chap:backgroundclonetypes}, allow reasoning about the duplication in a software system.
+Clones by these definitions can relatively easily and efficiently be detected.
+This has allowed for large scale analyses of duplication.
+However, these clone type definitions have shortcomings which make the clones detected in correspondence with these definitions less valuable for (automated) refactoring purposes.
+
+In this section we discuss the shortcomings of the different clone type definitions which make them less suitable for (automated) refactoring.
+Because of these shortcomings, clones found by these definitions are often found to require additional judgement whether they should and can be refactored.
+
+\subsection{Type 1 clones} \label{chap:type1clones}
+Type 1 clones are \textit{identical clone fragments except for variations in whitespace and comments} \cite{roy2007survey}.
+This allows for the detection of clones that are the result of copying and pasting existing code, along with other reasons why duplicates might get into a codebase.
+
+Type 1 clones are in most cases implemented as textual equality between code fragments (except for whitespace and comments).
+Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type.
+In such cases refactoring opportunities could be invalidated.
+An example of such a case is displayed in figure \ref{fig:type1}.
+
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/type1}
+  \caption{Example of a type 1 clone.}
+  \label{fig:type1}
+\end{figure}
+
+In the example in figure \ref{fig:type1}, we see a type 1 clone consisting of two methods.
+However, these clones might still be very hard to refactor as we cannot see by this example whether they are functionally equal.
+Both code fragments use different imported types, some of which imported via a wildcard.
+Because of this, it is hard to verify which of the used types have the same underlying implementation.
+This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
+When aiming to automatically refactor clones, applying refactorings to clones as shown in figure \ref{fig:type1}, is bound to be error prone and result in a uncompilable project or a difference in functionality.
+
+Because of this, type 1 clones may not all be subject to refactoring.
+In section \label{chap:type1rclones} we describe an alternate approach towards detecting type 1 clones, which results in only clones that can be refactored.
+
+\subsection{Type 2 clones}
+Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}.
+This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified.
+The two methods displayed in figure \ref{fig:type2} are type 2 clones of each other.
+
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/type2}
+  \caption{Example of a type 2 clone.}
+  \label{fig:type2}
+\end{figure}
+
+Looking at the example in listing \ref{fig:type2}, we see an example of a type 2 clone that poses no harm to the design of the system.
+Both methods are, except for their matching structure, completely different in functionality.
+They operate on different types, call different methods, return different things, etc.
+Having such a method flagged as a clone does not provide much useful information.
+
+When looking at refactoring, type 2 clones can be very difficult to refactor.
+For instance if we have variability in types, the code can describe operations on two completely dissimilar types.
+Type 2 clones do not differentiate between primitives and objects, which makes the these clones often not so useful for refactoring purposes.
+
+\subsection{Type 3 clones}
+Type 3 clones are \textit{copied fragments with further modifications.
+Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}.
+Detection of clones by this definition can be very hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed.
+Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold \cite{svajlenko2014evaluating, cordy2011nicad}.
+This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance) \cite{lavoie2011automated}, token-level similarity of statement-level similarity.
+
+Having a definition that allows for any change in code poses serious challenges on refactoring.
+A levenshtein distance of one can already change the meaning of a code fragment significantly, for instance if the name of a type differs by a character (and thus referring to different types).
+
+\subsection{Refactoring-oriented clone types}
+To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types to be directed at detecting clones that can and should be refactored.
+We have named these clones type 1R, 2R and 3R clones.
+These definitions share similarities with the literature definitions, the number of each type corresponds with the clone type it is modeled after.
+The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).
 

### 2019-06-27 sattose/paper.tex
Revert "Removed the survey"
This reverts commit 27a5c8017df0b8b10576add883881c3238896e57.

@@
 where are the four criteria coming from?}
+
+\subsection{Survey on Clone Detection Tools}
+\label{ch:tool-overview}
+We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities.
+The results of our survey are displayed in table~\ref{table:dettools}.
+We chose a set of tools that are open source and can analyze a popular object-oriented programming language.
+Next, we formulate the following four criteria by which we analyze these tools:
+\begin{enumerate}
+    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones.
+We want to perform an analysis on all clones in projects to get a complete overview.
+\item \textbf{Should find all clones in created control projects.} We assembled a number of test projects to assess the validity of clone detection tools.
+On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
+\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be merged.
+Sometimes, textual equality between code fragments does not imply that these can be merged (this is described more elaborately in section \ref{chap:type1clones}).
+Because of this, we want to use a clone detection tool that can analyze such structures.
+\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}).
+To achieve this, the tool needs to be able to allow those threshold changes.
+This can be either through simple changes of the source code, or by using some configuration file.
+\end{enumerate}
+
+\begin{table}[H]
+ \begin{center}
+  \caption{Our survey on clone detection tools.} \label{table:dettools}
+  \medskip
+\begin{tabular}{|l|l|l|l|l|l|}
+\hline
+\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
+Siamese \cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
+NiCAD \cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
+CPD \cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
+\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
+CCFinderSW \cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
+\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
+BigCloneEval \cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
+Deckard \cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
+Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}.
+This repository contains all scripts that were used to retrieve the data that is displayed in this paper.}.
 

### 2019-06-27 sattose/paper.tex
Type 1 and 2 stuff

@@
 In such cases refactoring opportunities could be invalidated.
-An example of such a case is displayed in figure \ref{fig:type1}.
-
-\begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/type1}
-  \caption{Example of a type 1 clone.}
-  \label{fig:type1}
-\end{figure}
-
-In the example in figure \ref{fig:type1}, we see a type 1 clone consisting of two methods.
-However, these clones might still be very hard to refactor as we cannot see by this example whether they are functionally equal.
-Both code fragments use different imported types, some of which imported via a wildcard.
-Because of this, it is hard to verify which of the used types have the same underlying implementation.
 This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
-When aiming to automatically refactor clones, applying refactorings to clones as shown in figure \ref{fig:type1}, is bound to be error prone and result in a uncompilable project or a difference in functionality.
+When aiming to automatically refactor clones, applying refactorings to clones which might refer to different methods, types and variables is bound to be error prone and result in a uncompilable project or a difference in functionality.
 
@@
 
-\subsection{Type 1R clones} \label{chap:type1clones}
+\subsubsection{Type 1R clones} \label{chap:type1clones}
 Type 1 clones are identical clone fragments except for variations in whitespace and comments \cite{roy2007survey}.
@@
 
-\subsection{Type 2R clones}
+\subsubsection{Type 2R clones}
 Type 2 clones allow any change in identifiers, literals, types, layout, and comments.
@@
 
-\subsection{Type 3R clones}
+\subsubsection{Type 3R clones}
 Type 3 clones allow any change in statements (added, removed and changed statements).

### 2019-06-27 sattose/paper.tex
Changed a lot actually

@@
 
-Looking at the example in listing \ref{fig:type2}, we see an example of a type 2 clone that poses no harm to the design of the system.
+Looking at the example in figure \ref{fig:type2}, we see an example of a type 2 clone that poses no harm to the design of the system.
 Both methods are, except for their matching structure, completely different in functionality.
@@
 For instance if we have variability in types, the code can describe operations on two completely dissimilar types.
-Type 2 clones do not differentiate between primitives and objects, which makes the these clones often not so useful for refactoring purposes.
+Type 2 clones do not differentiate between primitives and objects, which further undermines the usefulness of clones detected by this definition.
 
 \subsection{Type 3 clones}
-Type 3 clones are \textit{copied fragments with further modifications.
-Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}.
-Detection of clones by this definition can be very hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed.
-Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold \cite{svajlenko2014evaluating, cordy2011nicad}.
-This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance) \cite{lavoie2011automated}, token-level similarity of statement-level similarity.
+Type 3 clones are \textit{copied fragments with further modification (having added, removed or changed statements)} \cite{roy2007survey}.
+Detection of clones by this definition can be hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed.
+Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold \cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
+This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance) \cite{lavoie2011automated}, token-level similarity \cite{sajnani2016sourcerercc} of statement-level similarity \cite{kamalpriya2017enhancing}.
 
@@
 A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection.
-We decided to combine AST- and Graph-based approaches for clone detection, similar to Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing}.
-However, instead of building a dependency graph, we build a similarity graph of statements (linking to similar statements).
+We decided to combine AST- and Graph-based approaches for clone detection.
+We build a similarity graph of statements (linking to similar statements).
 The graph built by CloneRefactor is shown in Figure \ref{fig:clonerefactor}.

### 2019-06-27 sections/research.tex
Changed a lot actually

@@
 For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings to increase the chance that we can refactor the clone while improving the design.
-Due to the serious challenges involved in their detection and refactoring, type 4 clones are not considered in this study.
 

### 2019-06-28 sattose/paper.tex
Changed type 3R description
The world is better off with good labels

@@
 
-\subsection{Type 1 clones} \label{chap:type1clones}
+\subsection{Type 1 clones} \label{sec:type1}
 Type 1 clones are \textit{identical clone fragments except for variations in whitespace and comments} \cite{roy2007survey}.
@@
 
-\subsection{Type 2 clones}
+\subsection{Type 2 clones}\label{sec:type2}
 Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}.
@@
 
-\subsection{Type 3 clones}
+\subsection{Type 3 clones}\label{sec:type3}
 Type 3 clones are \textit{copied fragments with further modification (having added, removed or changed statements)} \cite{roy2007survey}.
@@
 
-\subsubsection{Type 1R clones} \label{chap:type1clones}
+\subsubsection{Type 1R clones} \label{sec:type1r}
 Type 1 clones are identical clone fragments except for variations in whitespace and comments \cite{roy2007survey}.
@@
 
-\subsubsection{Type 2R clones}
+\subsubsection{Type 2R clones}\label{sec:type2r}
+We tackle the previously outlined shortcomings of type 2R clones (see section We tackle these problems with type 2R clones to be able to detect such clones that can and should be refactored.
+Type 1R clones are a subset of type 2R clones.
+All rules that apply to type 1R clones also apply to type 2R clones.
+Additionally, type 2R clones allow variability in literals, variables and method calls.
+This variability however is constrained by a threshold.
+Type 2R do not allow any variability in types, as opposed to type 2 clones which do allow variability in types.
+As type 2R clones are per definition more permissive than type 1R clones, type 1R clones are a subset of type 2R clones.
+
 Type 2 clones allow any change in identifiers, literals, types, layout, and comments.
@@
 
-\subsubsection{Type 3R clones}
+\subsubsection{Type 3R clones}\label{sec:type3r}
 Type 3 clones allow any change in statements (added, removed and changed statements).
@@
 Because of that, we defined type 3R clones in such a way that they are directed towards finding clones that are worth this tradeoff.
-This entails the following:
+
+Type 3R clones allow, different from type 2R clones, a gap between two clone classes of statements that are not cloned. The following rules apply to this gap:
 
@@
 \item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be merged.
-Sometimes, textual equality between code fragments does not imply that these can be merged (this is described more elaborately in section \ref{chap:type1clones}).
+Sometimes, textual equality between code fragments does not imply that these can be merged (this is described more elaborately in section \ref{sec:type1}).
 Because of this, we want to use a clone detection tool that can analyze such structures.
@@
 The first one finds clones by comparing tokens (excluding whitespace, comments and newlines), equal to the definition of type 1 clones in literature \cite{roy2007survey}.
-The second algorithm implements our type 1R, as explained in section \ref{chap:type1clones}.
+The second algorithm implements our type 1R, as explained in section \ref{sec:type1r}.
 The differences between the clones found for these algorithms is displayed in Table \ref{table:clonedet}.
@@
 Table~\ref{table:relations} contains our results regarding the relations between clone instances.
-In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our type 1R definition as explained in section \ref{chap:type1clones}.
+In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our type 1R definition as explained in section \ref{sec:type1r}.
 

### 2019-06-28 sections/research.tex
Changed type 3R description
The world is better off with good labels

@@
 
-\subsection{Type 1 clones} \label{chap:type1clones}
+\subsection{Type 1 clones}\label{sec:type1}
 Type 1 clones are \textit{identical clone fragments except for variations in whitespace and comments} \cite{roy2007survey}.
@@
 
-\subsection{Type 2 clones}
+\subsection{Type 2 clones}\label{sec:type2}
   Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}.
@@
 
-\subsection{Type 3 clones}
+\subsection{Type 3 clones}\label{sec:type3}
 Type 3 clones are \textit{copied fragments with further modifications.
@@
 
-\subsection{Type 1R clones} \label{chap:type1rclones}
+\subsection{Type 1R clones} \label{sec:type1r}
 We propose an alternative definition of type 1 clones.
@@
 
-\subsection{Type 3R clones}
+\subsection{Type 3R clones}\label{sec:type3r}
 Type 3 clones allow any change in statements, often bounded by a similarity threshold.
@@
 
-Type 1R: Allows no difference between cloned fragments, making it possible to refactor both fragments to a method call that contains the code of both locations.
-Type 2R: Allows difference between cloned fragments in controlled features of a codebase. Refactoring opportunities for these controlled features are known, allowing refactoring with a minor tradeoff.
-Type 3R: Allows any difference. When refactored, this difference must be wrapped in its own block, which entails a major tradeoff.
+\textbf{Type 1R:} Allows no difference between cloned fragments, making it possible to refactor both fragments to a method call that \
+contains the code of both locations.
+\textbf{Type 2R:} Allows difference between cloned fragments in controlled features of a codebase.
+Refactoring opportunities for these controlled features are known, allowing refactoring with a minor tradeoff.
+\textbf{Type 3R:} Allows any difference. When refactored, this difference must be wrapped in a conditionally executed block, which entails a major tradeoff.
 
@@
 \item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be refactored.
-Sometimes, textual equality between code fragments does not imply that these can be refactored (this is described more elaborately in section \ref{chap:type1clones}).
+Sometimes, textual equality between code fragments does not imply that these can be refactored (this is described more elaborately in section \ref{sec:type1}).
 Because of this, we want to use a clone detection tool that can analyze such structures.
@@
 This final node is represented in the example figure by the purple box (1).
-We then follow all ``duplicate'' relations until we have found all clones (2 and 3).
+We then follow all ``duplicate'' relations until we have found all clones of this node (2 and 3).
 We now have a single statement clone class of three clone instances (1, 2 and 3).

### 2019-06-30 code_examples/Type2-1.java
Examples++

@@ -1,7 +1,10 @@
-public boolean containsOnlyRedCircles(List<Circle> listOfCircles){
-	return listOfCircles.stream().allMatch(Shape::isRed);
+public boolean containsOnlyRedCircles(List<Circle> circles){
+	return circles.stream().allMatch(Shape::isRed);
 }
 
-public Apple getEdibleAppleFromBasket(FruitBasket<Apple> appleBasket){
-	return appleBasket.getFruitContainer().getAppleByCriterium(Fruit::hasNotYetBeenEaten);
+public Apple getEdibleApple(FruitBasket<Apple> basket){
+	return basket.getFruitContainer()
+		.getAppleByCriterium(Fruit::hasNotYetBeenEaten);
 }
+
+

### 2019-06-30 sattose/paper.tex
Type  1R clones

@@
 \subsubsection{Type 1R clones} \label{sec:type1r}
-Type 1 clones are identical clone fragments except for variations in whitespace and comments \cite{roy2007survey}.
-However, when two clone fragments are textually identical, it does not yet indicate that they are functionally identical.
-Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and even variables can be of a different type.
-In such cases refactoring opportunities could be invalidated.
-Therefore, we propose an alternative definition of type 1 clones.
-We have named it ``type 1R clones''.
-The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).
-Type 1R clones differ from type 1 clones as follows:
+We propose an alternative definition of type 1 clones.
+This definition requires cloned fragments to be not just textually equal, but also functionally equal.
+Because of this, type 1R clones are a subset of type 1 clones.
+Although requiring fragments to be functionally equal, type 1R clones do not allow for change in implementation (like type 4 clones).
+
+We check functional equality of two fragments by validating the equality of the fully qualified identifier (FQI) for referenced types, methods and variables.
+If an identifier is fully qualified, it means we specify the full location of its declaration (e.g.
+\texttt{com.sb.fruit.Apple} for an \texttt{Apple} object).
+This way we can validate whether two method references, like method calls, are functionally equal.
+This entails the following procedures to verify equality:
+
 \begin{itemize}
-  \item \textbf{Compare the equality of the fully qualified method signature for method references.} If an identifier is fully qualified, it means we specify the full location of its declaration (e.g.
-\texttt{com.simonbaars.fruitgame.Apple} for an \texttt{Apple} object).
-This way we can validate whether two method references, like method calls, are functionally equal.
-In the method signature, not only the fully qualified identifier of the method should be considered, but also the type of all its arguments.
-This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
-  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
-  \item \textbf{Compare the equality of the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types.
-This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive.
-To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
-  \item \textbf{Compare the equality of the fully qualified identifier for method references and call signatures.} This is to prevent a change in functionality after merging the clone, as methods with equal names/parameters can still contain different functionality.
+  \item \textbf{Referenced Types:} For all types references in the code, we should compare their FQI with other code fragements to ensure functional equality.
+  \item \textbf{Variables:} We trace the declaration of used variables to ensure that their type equals the type of another equally named variable.
+  \item \textbf{Method Calls:} A codebase can have several methods with equal names, but a different implementation.
+Because of this, we compare the FQI of the method signature of called methods.
+A method signature includes the FQI for a methods' name, return value and each of its arguments.
 \end{itemize}

### 2019-06-30 sattose/paper.tex
Working on clone types and such

@@
 This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified.
-The two methods displayed in figure \ref{fig:type2} are type 2 clones of each other.
+For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
+This could render two methods that have an entirely different functionality as clones.
+Merging such clones can be harmful instead of helpful.
 
@@
 \subsubsection{Type 1R clones} \label{sec:type1r}
-We propose an alternative definition of type 1 clones.
+To solve the shortcomings listed in section \ref{sec:type1}, we propose an alternative definition of type 1 clones.
 This definition requires cloned fragments to be not just textually equal, but also functionally equal.
@@
 \subsubsection{Type 2R clones}\label{sec:type2r}
-We tackle the previously outlined shortcomings of type 2R clones (see section We tackle these problems with type 2R clones to be able to detect such clones that can and should be refactored.
+We tackle the previously outlined shortcomings of type 2R clones to be able to detect such clones that can and should be refactored.
 Type 1R clones are a subset of type 2R clones.
@@
 As type 2R clones are per definition more permissive than type 1R clones, type 1R clones are a subset of type 2R clones.
-
-Type 2 clones allow any change in identifiers, literals, types, layout, and comments.
-For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
-This could render two methods that have an entirely different functionality as clones.
-Merging such clones can be harmful instead of helpful.
 

### 2019-06-30 sections/research.tex
Working on clone types and such

@@
 
-\textbf{Type 1R:} Allows no difference between cloned fragments, making it possible to refactor both fragments to a method call that \
-contains the code of both locations.
-\textbf{Type 2R:} Allows difference between cloned fragments in controlled features of a codebase.
+\begin{itemize}
+\item \textbf{Type 1R:} Allows no difference between cloned fragments, making it possible to refactor both fragments to a method call that contains the code of both locations. \\
+\item \textbf{Type 2R:} Allows difference between cloned fragments in controlled features of a codebase.
 Refactoring opportunities for these controlled features are known, allowing refactoring with a minor tradeoff.
-\textbf{Type 3R:} Allows any difference. When refactored, this difference must be wrapped in a conditionally executed block, which entails a major tradeoff.
+\\
+\item \textbf{Type 3R:} Allows any difference. When refactored, this difference must be wrapped in a conditionally executed block, which entails a major tradeoff.
+\end{itemize}
+
+\begin{equation}\label{eq:typerelation}
+\text{Cloned statements} = T1R \subseteq T2R \subseteq T3R
+\end{equation}
+
+\begin{equation}\label{eq:typerelation2}
+\text{Cloned lines} = T1R \subseteq T1 \text{, but } T2R	\nsubseteq T2 \text{ and } T3R \nsubseteq T3
+\end{equation}
 

### 2019-06-30 sattose/paper.tex
Clones in general

@@
 To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types to be directed at detecting clones that can and should be refactored.
-We have named these clones type 1R, 2R and 3R clones.
+We have named these clones T1R (type 1R), T2R and T3R clones.
 These definitions share similarities with the literature definitions, the number of each type corresponds with the clone type it is modeled after.
 The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).
+
+Like the clone types that are commonly used in literature \cite{roy2007survey}, each type R clone is a subset of the next type.
+This property is displayed in equation \ref{eq:typerelation}.
+Likewise, each type R clone inherits all properties of the previous one.
+Each statement found as cloned for T1R clones, will also be found as cloned for T2R and T3R.
+Each rule that applies to T1R clones also applies to T2R and T3R.
+
+\begin{equation}\label{eq:typerelation}
+\text{Cloned statements: } T1R \subseteq T2R \subseteq T3R
+\end{equation}
 
@@
 Because of this, type 1R clones are a subset of type 1 clones.
-Although requiring fragments to be functionally equal, type 1R clones do not allow for change in implementation (like type 4 clones).
+Although requiring fragments to be functionally equal, T1R clones do not allow for change in implementation (like type 4 clones).
 
@@
 \subsubsection{Type 2R clones}\label{sec:type2r}
-We tackle the previously outlined shortcomings of type 2R clones to be able to detect such clones that can and should be refactored.
-Type 1R clones are a subset of type 2R clones.
+We tackle the previously outlined shortcomings of type 2 clones to be able to detect such clones that can and should be refactored.
 All rules that apply to type 1R clones also apply to type 2R clones.

### 2019-06-30 sattose/paper.tex
Better explain T2R

@@
 \begin{equation}\label{eq:typerelation}
-\text{Cloned statements: } T1R \subseteq T2R \subseteq T3R
+T1R \subseteq T2R \subseteq T3R
 \end{equation}
@@
 Additionally, type 2R clones allow variability in literals, variables and method calls.
-This variability however is constrained by a threshold.
-Type 2R do not allow any variability in types, as opposed to type 2 clones which do allow variability in types.
-As type 2R clones are per definition more permissive than type 1R clones, type 1R clones are a subset of type 2R clones.
-
-We tackle these problems with type 2R clones to be able to detect such clones that can and should be refactored.
-Our definition ensures functional similarity by applying the following changes to type 2 clones:
+This variability however is constrained by a threshold as a tradeoff exists in the refactoring of such differences.
+Furthermore, type 2R clones allow any variability in method names and class/enum/interface names.
+This is because, if the body of a method/class/enum/interface equals the body of another, but only their names differ, this can be refactored without a design tradeoff.
 
@@
 $$t = \text{Tokens in clones}$$
+
+\begin{equation}\label{eq:typerelation2}
+T1R \subseteq T1 \text{, but } T2R	\nsubseteq T2 \text{ and } T3R \nsubseteq T3
+\end{equation}
 

### 2019-06-30 sattose/paper.tex
T2R clones

@@
 
-\begin{itemize}
-  \item \textbf{Considering types:} Type 2 clones do not consider types.
-However, this can make a code fragment very hard to refactor, as different types can describe different functional concepts.
-Because of this, we propose that type 2R clones should consider types like type 1R clones do.
-  \item \textbf{Having a distinction between different variables:} For type 2 clones, no identifiers would be taken into account.
-We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables.
-For instance, if we call a method like this: \texttt{myMethod(var1, var2)}, or call this method like this: \texttt{myMethod(var1, var1)}.
-Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
-  \item \textbf{Defining a threshold for variability in literals:} For type 2 clones no literals would be taken into account.
-We agree, as when merging the clone (for example by extracting a method), we can turn the literal into a method parameter.
-However, we would argue that thresholds matter here.
-How many literals may differ for the segment still to be considered a clone with another segment?
-We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
-This threshold is displayed in equation \ref{eq:type2r}.
-  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary.
-However, because of this, completely different methods can be called in cloned fragments as a result.
-This poses serious challenges on refactoring and makes it more disputable whether such a clone is harmful for the maintainability of the code.
-This is because different method identifiers can describe a completely different functionality.
-Therefore, we suggest considering the call signatures of cloned methods when they are compared.
-We can allow variability in the rest of method identifiers by passing the function as a parameter.
-To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
-\end{itemize}
+When refactoring two fragments that differ by a few literals, called methods or used variables, we are faced with a design tradeoff.
+For instance, if two literals differ and we want to refactor by method extraction, we need our new method to have an added argument to which each usage can pass the literal that was used at that place.
+Likewise, such things can be done for different variables that have been used and different called methods.
+Important here is, that the type of the used literals/variables are equal.
+Likewise, the signature of the called methods must be equal.
+
+To limit the negative impact of this tradeoff on the design of the system, we formalized as threshold for the variability between fragments.
+The formula by which this threshold is calculated is displayed in equation \ref{eq:type2r}.
+We take the amount of literals, variables and method calls that differ from other clone instances in a clone class and divide it by the total number of tokens in the clone instance.
+Based on this threshold, we decide whether a clone should be considered for refactoring.
 
@@
 $$Total = \text{Total number in the clone instance}$$
-$$l = \text{Literals in clone}$$
-$$v = \text{Variables in clone}$$
-$$m = \text{Method calls in clone}$$
-$$t = \text{Tokens in clones}$$
+$$l = \text{Literals in clone instance}$$
+$$v = \text{Variables in clone instance}$$
+$$m = \text{Method calls in clone instance}$$
+$$t = \text{Tokens in clone instance}$$
+
+A method call does often not consist of a single token (unlike variables and literals).
+For instance, a method call \texttt{System.out.println()} consists of several segments: a type reference to the \texttt{System} type, a reference to the static \texttt{out} field and a call of the \texttt{println()} method.
+Because of this, T2R clones are not a subset of of type 2 clones.
+Because T3R clones inherit all rules of T2R clones, T3R clones are also not a subset of T3 clones.
+This is displayed in equation \ref{eq:typerelation2}.
 

### 2019-07-01 sattose/paper.tex
Describing CloneRefactor tool

@@
 
-\subsection{Refactoring-oriented clone types}
+\subsection{Refactoring-oriented clone types}\label{sec:rtypes}
 To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types to be directed at detecting clones that can and should be refactored.
@@
 This property is displayed in equation \ref{eq:typerelation}.
-Likewise, each type R clone inherits all properties of the previous one.
 Each statement found as cloned for T1R clones, will also be found as cloned for T2R and T3R.
@@
 We want to perform an analysis on all clones in projects to get a complete overview.
-\item \textbf{Should find all clones in created control projects.} We assembled a number of test projects to assess the validity of clone detection tools.
+\item \textbf{Finds clone classes in control projects.} We assembled a number of control projects to assess the validity of clone detection tools.
 On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
@@
 
+\subsection{CloneRefactor}
 None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}.
 This repository contains all scripts that were used to retrieve the data that is displayed in this paper.}.
+In this tool, we implemented both the literature clone types \cite{roy2007survey} and our refactoring-oriented clone types as described in section \ref{sec:rtypes}.
 
-\subsection{CloneRefactor}
-A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection.
-We decided to combine AST- and Graph-based approaches for clone detection.
-We build a similarity graph of statements (linking to similar statements).
-The graph built by CloneRefactor is shown in Figure \ref{fig:clonerefactor}.
+Our tool is based on the JavaParser library \cite{tomassetti2017javaparser}.
+This library can parse Java source code to an AST representation.
+This AST can then be analyzed, modified and eventually written back to source code.
+This allows us to perform AST-based clone detection and apply transformations to the AST based on the clones found.
 
-\begin{figure}[H]
-  \caption{Abstract figure of the graph representation built by CloneRefactor}
-  \medskip
-  \includegraphics[width=1\columnwidth]{img/CodeGraph}
-  \label{fig:clonerefactor}
-\end{figure}
+CloneRefactor walks the AST and collects each declaration and statement.
+It then builds a graph representation on basis of this AST, in which each declaration and statement becomes a node.
+This graph representation maps the following relations for each declaration and statement:
 
-We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code and is compatible with all modern Java versions (Java 1-12).
-We collect each statement and declaration and compare those to find duplicates.
-We build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of its duplicates (vertically).
+\begin{itemize}
+  \item The declaration/statement preceding it
+  \item The declaration/statement following it
+  \item The previous statement/declaration that is cloned
+\end{itemize}
+
+Whether a node is considered a clone depends on the clone type that is being analyzed.
 On basis of this graph we detect clone classes.

### 2019-07-01 sattose/paper.tex
Research questions

@@
 Section \ref{chap:threatstovalidity} shows the threats to validity of this study and section \ref{chap:conclusion} draws a conclusion based on our preliminary results.
+
+\subsection{Research questions}
+We have formalized the following research questions in order to improve upon the state-of-the-art in code duplication refactoring:
+
+\textbf{RQ1.} How do we identify clones that we \textbf{can} refactor?\\
+\textbf{RQ2.} How do we identify clones that we \textbf{should} refactor?\\
+\textbf{RQ3.} To what extent can we \textbf{automate} the process of refactoring?
 
@@
 
-\subsubsection{Thresholds}\label{chap:thresholds}
+\section{Thresholds}\label{chap:thresholds}
+
 CloneRefactor works on basis of three thresholds for finding clones:
@@
 
-\section{Relation, Location and Content Analysis of Clones}\label{chap:clonecontextexpl}
+\section{Context Analysis of Clones}\label{chap:clonecontextexpl}
 To be able to refactor code clones, it is very important to consider the context of the clone. We define the following aspects of the clone as its context:

### 2019-07-01 sattose/paper.tex
Moved the challenge chapter

@@
 
+\subsubsection{The challenge of detecting these clones}\label{chap:challenge}
+To detect each type of clone, we need to parse the fully qualified identifier of all types, method calls and variables.
+This comes with serious challenges, regarding both performance and implementation.
+Also, to be able to parse all fully qualified identifiers, and trace the declarations of variables, we might need to follow cross file references.
+The referenced types/variables/methods might even not be part of the project, but rather of an external library or the standard libraries of the programming language.
+All these factors need to be considered for the referenced entity to be found, on basis of which a fully qualified identifier can be created.
+
+CloneRefactor uses JavaParser \cite{tomassetti2017javaparser}.
+JavaParser has a built-in symbol solver, which can automatically resolve types, method calls and variables.
+However, because of this, CloneRefactor does require all libraries that the software project requires (apart from the Java Standard Library).
+If these are not available, CloneRefactor will estimate types on basis of the information that is available.
+
 \begin{equation}\label{eq:type3r}
@@
 
-\section{Thresholds}\label{chap:thresholds}
+\subsection{Thresholds}\label{chap:thresholds}
 
@@
 We consider ``number of lines'' to be the least important, as it highly depends on the developer of the codebase (and we want to prevent this dependence).
-
-\subsection{The challenge of detecting these clones}\label{chap:challenge}
-To detect each type of clone, we need to parse the fully qualified identifier of all types, method calls and variables.
-This comes with serious challenges, regarding both performance and implementation.
-Also, to be able to parse all fully qualified identifiers, and trace the declarations of variables, we might need to follow cross file references.
-The referenced types/variables/methods might even not be part of the project, but rather of an external library or the standard libraries of the programming language.
-All these factors need to be considered for the referenced entity to be found, on basis of which a fully qualified identifier can be created.
-
-CloneRefactor uses JavaParser \cite{tomassetti2017javaparser}.
-JavaParser has a built-in symbol solver, which can automatically resolve types, method calls and variables.
-However, because of this, CloneRefactor does require all libraries that the software project requires (apart from the Java Standard Library).
-If these are not available, CloneRefactor will estimate types on basis of the information that is available.
 

### 2019-07-01 sattose/paper.tex
Bit more about the research questions

@@
 \subsection{Research questions}
-We have formalized the following research questions in order to improve upon the state-of-the-art in code duplication refactoring:
-
+We have formalized the following research questions in order to improve upon the state-of-the-art in code duplication refactoring:\\
 \textbf{RQ1.} How do we identify clones that we \textbf{can} refactor?\\
 \textbf{RQ2.} How do we identify clones that we \textbf{should} refactor?\\
-\textbf{RQ3.} To what extent can we \textbf{automate} the process of refactoring?
+\textbf{RQ3.} To what extent can we \textbf{automate} the process of refactoring?\\
+
+For \textbf{RQ1} we look into current clone definitions and clone detection methods.
+We then assess their suitability for refactoring purposes.
+For \textbf{RQ2} we look into to what extent clones can be filtered based on their impact on the system design when refactored.
+We do this by both determining good thresholds for the clone detection and by assessing the design implications of applying refactorings to the code.
+\textbf{RQ3} is currently still future work, hence the work in progress status of this paper.
 

### 2019-07-01 sattose/paper.tex
Thresholds

@@
 \begin{itemize}
-  \item \textbf{Referenced Types:} For all types references in the code, we should compare their FQI with other code fragements to ensure functional equality.
+  \item \textbf{Referenced Types:} For all types references in the code, we should compare their FQI with other code fragments to ensure functional equality.
   \item \textbf{Variables:} We trace the declaration of used variables to ensure that their type equals the type of another equally named variable.
@@
 
-CloneRefactor walks the AST and collects each declaration and statement.
+CloneRefactor walks the AST and collects each declaration and statement (similar to the Scorpio clone detection tool \cite{higo2013revisiting}).
 It then builds a graph representation on basis of this AST, in which each declaration and statement becomes a node.
@@
 \subsection{Thresholds}\label{chap:thresholds}
+Thresholds are a tool that aid in the process of deciding whether a clone \textit{should} be refactored.
+Many clone detection tools focus on either the number of lines \cite{kamiya2002ccfinder, svajlenko2016bigcloneeval}, number of tokens \cite{roy2008nicad, sajnani2016sourcerercc, ragkhitwetsagul2019siamese} and/or number of nodes (declarations/statements) \cite{higo2013revisiting} to decide whether code fragments should be considered clones of each other.
+A comparison of clone detection tools by Bellon et al.
+\cite{bellon2007comparison} shows that most clone detection tools choose a minimum of \textbf{6} lines of code to be duplicate to consider code fragments a clone.
+The Scorpio clone detection tool uses this same number as minimum number of nodes \cite{higo2013revisiting}.
+Token based tools mostly operate on basis of a minimum of \textbf{50} tokens for fragments to be considered a clone.
+
+However, we would argue that going with this ``magic number 6'' eliminates a lot of harmful clones that should be refactored. For instance
 

### 2019-07-01 sattose/paper.tex
Ana

@@
 We have formalized the following research questions in order to improve upon the state-of-the-art in code duplication refactoring:\\
-\textbf{RQ1.} How do we identify clones that we \textbf{can} refactor?\\
-\textbf{RQ2.} How do we identify clones that we \textbf{should} refactor?\\
-\textbf{RQ3.} To what extent can we \textbf{automate} the process of refactoring?\\
+\textbf{RQ1.} How can we define clone types such that they \textbf{can} be automatically refactored?\\
+%\textbf{RQ2.} How can we determine decision factors for when a clone \textbf{should} be refactored?\\
+\textbf{RQ2.} What are the discriminating factors to decide when a clone \textbf{should} be refactored?\\
+\textbf{RQ3.} To what extent can we \textbf{automate} the process of refactoring clones?\\
 
@@
 We do this by both determining good thresholds for the clone detection and by assessing the design implications of applying refactorings to the code.
-\textbf{RQ3} is currently still future work, hence the work in progress status of this paper.
+\textbf{RQ3} is currently work in progress.
 
@@
 This property is displayed in equation \ref{eq:typerelation}.
-Each statement found as cloned for T1R clones, will also be found as cloned for T2R and T3R.
-Each rule that applies to T1R clones also applies to T2R and T3R.
+Each statement that is a T1R will also be found for T2R; each T2R statement will also be found for T3R.
+Each rule that applies to T1R also applies to T2R; each T2R rule applies to T3R.
 
@@
 
-\subsubsection{Type 1R clones} \label{sec:type1r}
-To solve the shortcomings listed in section \ref{sec:type1}, we propose an alternative definition of type 1 clones.
-This definition requires cloned fragments to be not just textually equal, but also functionally equal.
-Because of this, type 1R clones are a subset of type 1 clones.
-Although requiring fragments to be functionally equal, T1R clones do not allow for change in implementation (like type 4 clones).
+\subsubsection{T1R clones} \label{sec:type1r}
+To solve the issues identified in Sec.~\ref{sec:type1}, we introduce an alternative definition: cloned fragments have to be both textually \textit{and} functionally equal.
+Therefore, T1R clones are a subset of type 1 clones.
+%Although requiring fragments to be functionally equal, T1R clones do not allow for change in implementation (like type 4 clones).
 
-We check functional equality of two fragments by validating the equality of the fully qualified identifier (FQI) for referenced types, methods and variables.
+We check functional equality of two fragments by checking the equality of the fully qualified identifier (FQI) for referenced types, methods and variables.
 If an identifier is fully qualified, it means we specify the full location of its declaration (e.g.
 \texttt{com.sb.fruit.Apple} for an \texttt{Apple} object).
-This way we can validate whether two method references, like method calls, are functionally equal.
-This entails the following procedures to verify equality:
+For method calls, we also compare the equality of the FQI of the type of each of its arguments, to differentiate between overloaded method variants.
+This way we can check whether two identifiers are functionally equal.
 
-\begin{itemize}
-  \item \textbf{Referenced Types:} For all types references in the code, we should compare their FQI with other code fragments to ensure functional equality.
-  \item \textbf{Variables:} We trace the declaration of used variables to ensure that their type equals the type of another equally named variable.
-  \item \textbf{Method Calls:} A codebase can have several methods with equal names, but a different implementation.
-Because of this, we compare the FQI of the method signature of called methods.
-A method signature includes the FQI for a methods' name, return value and each of its arguments.
-\end{itemize}
-
-\subsubsection{Type 2R clones}\label{sec:type2r}
+\subsubsection{T2R clones}\label{sec:type2r}
+To solve the issues identifier in Sec.~\ref{sec:type2}, we introduce .
 We tackle the previously outlined shortcomings of type 2 clones to be able to detect such clones that can and should be refactored.
-All rules that apply to type 1R clones also apply to type 2R clones.
-Additionally, type 2R clones allow variability in literals, variables and method calls.
+All rules that apply to T1R clones also apply to T2R clones.
+Additionally, T2R clones allow variability in literals, variables and method calls.
 This variability however is constrained by a threshold as a tradeoff exists in the refactoring of such differences.
-Furthermore, type 2R clones allow any variability in method names and class/enum/interface names.
+Furthermore, T2R clones allow any variability in method names and class/enum/interface names.
 This is because, if the body of a method/class/enum/interface equals the body of another, but only their names differ, this can be refactored without a design tradeoff.
@@
 \begin{equation}\label{eq:type2r}
-\text{T2R}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100
+\text{T2R}=\frac{\text{Different expressions}}{\text{Total tokens}}*100
 \end{equation}
 $$Diff = \text{Number that differ from other clone instances}$$
-$$Total = \text{Total number in the clone instance}$$
 $$l = \text{Literals in clone instance}$$
@@
 $$m = \text{Method calls in clone instance}$$
-$$t = \text{Tokens in clone instance}$$
 
@@
 
-\subsubsection{Type 3R clones}\label{sec:type3r}
+\subsubsection{T3R clones}\label{sec:type3r}
 Type 3 clones allow any change in statements (added, removed and changed statements).
@@
 This similarity threshold entails that two fragments may differ by a certain percentage.
-This means that type 3R allows the inclusion of a statement that is not detected by type 1 or 2 clone detection.
+This means that T3R allows the inclusion of a statement that is not detected by type 1 or 2 clone detection.
 When looking at how we can refactor a statement that is not included by one clone instance but is in another, we find that we require a conditional block to make up for the difference in statements.
 This is a tradeoff, as an added conditional block increases the complexity of the system.
-Because of that, we defined type 3R clones in such a way that they are directed towards finding clones that are worth this tradeoff.
+Because of that, we defined T3R clones in such a way that they are directed towards finding clones that are worth this tradeoff.
 
-Type 3R clones allow, different from type 2R clones, a gap between two clone classes of statements that are not cloned. The following rules apply to this gap:
+T3R clones allow, different from T2R clones, a gap between two clone classes of statements that are not cloned. The following rules apply to this gap:
 
@@
 This is displayed in equation \ref{eq:type3r}.
-  \item \textbf{The gap may not span a partial block.} To make sure that the type 3R clone can be refactored, we do not allow the gap to span a part of a block, for instance the declaration and a part of the body of a for-loop.
+  \item \textbf{The gap may not span a partial block.} To make sure that the T3R clone can be refactored, we do not allow the gap to span a part of a block, for instance the declaration and a part of the body of a for-loop.
 The reason for this is that it is not possible to wrap a partially spanned block in a single conditional statement.
-We could however use multiple conditional blocks (one for each block spanned), but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for type 3R clones.
+We could however use multiple conditional blocks (one for each block spanned), but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for T3R clones.
 \end{itemize}
@@
 The Scorpio clone detection tool uses this same number as minimum number of nodes \cite{higo2013revisiting}.
-Token based tools mostly operate on basis of a minimum of \textbf{50} tokens for fragments to be considered a clone.
+Token based tools mostly operate on basis of a minimum of \textbf{50} tokens for fragments to be considered a clone \cite{sajnani2016sourcerercc}.
 
 However, we would argue that going with this ``magic number 6'' eliminates a lot of harmful clones that should be refactored. For instance
-
-CloneRefactor works on basis of three thresholds for finding clones:
-\begin{enumerate}
-  \item \textbf{Number of statements/declarations:} The number of statements/declarations that should be equal/similar for it to be considered a clone.
-  \item \textbf{Number of tokens:} The number of tokens (excluding whitespace, end-of-line terminators and comments) that should be equal/similar for it to be considered a clone.
-  \item \textbf{Number of lines:} The minimum amount of lines (excluding lines that do not contain any tokens) that should be equal/similar for it to be considered a clone.
-\end{enumerate}
-Of course, if any threshold is set to zero, it will be ignored, thus not all thresholds have to be used at all times.
-We consider ``number of lines'' to be the least important, as it highly depends on the developer of the codebase (and we want to prevent this dependence).
 
@@
 The first one finds clones by comparing tokens (excluding whitespace, comments and newlines), equal to the definition of type 1 clones in literature \cite{roy2007survey}.
-The second algorithm implements our type 1R, as explained in section \ref{sec:type1r}.
+The second algorithm implements our T1R, as explained in section \ref{sec:type1r}.
 The differences between the clones found for these algorithms is displayed in Table \ref{table:clonedet}.
@@
 \hline
- & \textbf{Type 1} & \textbf{Type 1R} \\ \hline
+ & \textbf{Type 1} & \textbf{T1R} \\ \hline
 \begin{tabular}[c]{@{}l@{}}Amount of lines cloned\end{tabular} & 200,362 & 129,519 \\ \hline
@@
 
-Looking at Table \ref{table:clonedet}, it becomes apparent that the type 1R algorithm finds significantly less clones than the type 1 algorithm.
+Looking at Table \ref{table:clonedet}, it becomes apparent that the T1R algorithm finds significantly less clones than the type 1 algorithm.
 This indicates that about a third of the clones have textual equality, but are not actually equal when considering the types of expressions.
@@
 Table~\ref{table:relations} contains our results regarding the relations between clone instances.
-In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our type 1R definition as explained in section \ref{sec:type1r}.
+In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our T1R definition as explained in section \ref{sec:type1r}.
 
@@
 The most notable difference when comparing it to the results of Fontana et al.
-\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (38.14\% with type 1R), while for them it was only 15.70\%.
+\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (38.14\% with T1R), while for them it was only 15.70\%.
 This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
@@
 On the third place come the ``Sibling'' clones, which can often be refactored using a pull-up refactoring.
-There are no noteworthy differences between type 1 and type 1R clones.
+There are no noteworthy differences between type 1 and T1R clones.
 
@@
 The amount of clones found in interfaces and enumerations is very low.
-Regarding the differences between type 1 and type 1R, it seems that there are relatively less method level clones and more class level clones for type 1R.
-This is probably due to that the main reason for variability between type 1 and type 1R is variable references, which occur more at method level than class level.
+Regarding the differences between type 1 and T1R, it seems that there are relatively less method level clones and more class level clones for T1R.
+This is probably due to that the main reason for variability between type 1 and T1R is variable references, which occur more at method level than class level.
 
@@
 Unsurprisingly, most clones span a part of a method.
-More than a quarter of the clones (for type 1R) span over several methods, which either requires more advanced refactoring techniques or indicates a non-harmful clone.
+More than a quarter of the clones (for T1R) span over several methods, which either requires more advanced refactoring techniques or indicates a non-harmful clone.
 
@@
 \subsection{Next steps}
-The next step is to integrate our type 2R and type 3R definitions into our CloneRefactor tool.
+The next step is to integrate our T2R and T3R definitions into our CloneRefactor tool.
 We then will look into appropriate thresholds for these types of clones.
-We can then re-run all scripts for type 2R and 3R clones.
+We can then re-run all scripts for T2R and 3R clones.
 On basis of these results, we can prioritize implementing automated refactorings.

### 2019-07-01 sattose/paper.tex
Next steps

@@
 \subsection{Next steps}
-The next step is to integrate our T2R and T3R definitions into our CloneRefactor tool.
-We then will look into appropriate thresholds for these types of clones.
-We can then re-run all scripts for T2R and 3R clones.
-On basis of these results, we can prioritize implementing automated refactorings.
+Our next step is to implement the ``Extract Method'' refactoring for the identified automatic refactoring opportunities.
+On basis of the resulting code, we can perform experiments comparing the maintainability index of the refactored code to the original code.
+On basis of these results, we can find better thresholds in order to determine thresholds.
+We can assess the impact of our work on code volume, complexity, etc.
+This helps to verify the usability of the proposed type definitions towards our goal of improving the quality of a software system.
 

### 2019-07-01 sattose/paper.tex
RIP this text about relations between clone types

@@
 The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).
-
-Like the clone types that are commonly used in literature \cite{roy2007survey}, each type R clone is a subset of the next type.
-This property is displayed in equation \ref{eq:typerelation}.
-Each statement that is a T1R will also be found for T2R; each T2R statement will also be found for T3R.
-Each rule that applies to T1R also applies to T2R; each T2R rule applies to T3R.
-
-\begin{equation}\label{eq:typerelation}
-T1R \subseteq T2R \subseteq T3R
-\end{equation}
 

### 2019-07-01 sattose/paper.tex
Let's move this up
Made this formula shorter

@@
 The formula by which this threshold is calculated is displayed in equation \ref{eq:type2r}.
-We take the amount of literals, variables and method calls that differ from other clone instances in a clone class and divide it by the total number of tokens in the clone instance.
+In this formula, \textit{different expressions} refers to the amount of literals, variables and method calls that differ from other clone instances in a clone class.
+We divide this by the total number of tokens in the clone instance.
 Based on this threshold, we decide whether a clone should be considered for refactoring.
@@
 \end{equation}
-$$Diff = \text{Number that differ from other clone instances}$$
-$$l = \text{Literals in clone instance}$$
-$$v = \text{Variables in clone instance}$$
-$$m = \text{Method calls in clone instance}$$
 
@@
 
+\begin{equation}\label{eq:type3r}
+\text{T3R Gap}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100
+\end{equation}
+$$Statements = \text{Statements in a code fragment}$$
+$$C_{gap} = \text{The gap between two clones}$$
+$$C_{above} = \text{The clone instance above the gap}$$
+$$C_{below} = \text{The clone instance below the gap}$$
+
 \subsubsection{The challenge of detecting these clones}\label{chap:challenge}
@@
 If these are not available, CloneRefactor will estimate types on basis of the information that is available.
-
-\begin{equation}\label{eq:type3r}
-\text{T3R Gap}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100
-\end{equation}
-$$Statements = \text{Statements in a code fragment}$$
-$$C_{gap} = \text{The gap between two clones}$$
-$$C_{above} = \text{The clone instance above the gap}$$
-$$C_{below} = \text{The clone instance below the gap}$$
 

### 2019-07-01 sattose/paper.tex
Shortened references a bit

@@
 Duplication in source code is often seen as one of the most harmful types of technical debt.
-In Martin Fowler's ``Refactoring'' book \cite{fowler1999refactoring}, he claims that \textit{``Number one in the stink parade is duplicated code.
+In Martin Fowler's ``Refactoring'' book~\cite{fowler1999refactoring}, he claims that \textit{``Number one in the stink parade is duplicated code.
 If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
@@
 
-A survey by Roy et al.
-\cite{roy2007survey} describes various ways in which clones can be identified.
+A survey by Roy et al.~\cite{roy2007survey} describes various ways in which clones can be identified.
 Most clone detection tools focus on finding clones that align with these definitions.
@@
 
-Our end goal is to improve upon the current state-of-the-art in clone research \cite{fontana2015duplicated, alwaqfi2017refactoring} by building a clone refactoring tool that automatically applies refactorings to a large percentage of clones found.
+Our end goal is to improve upon the current state-of-the-art in clone research~\cite{fontana2015duplicated, alwaqfi2017refactoring} by building a clone refactoring tool that automatically applies refactorings to a large percentage of clones found.
 The design decisions for this tool are made on basis of data gathered from a large corpus of software systems together with our own experience and findings from literature.
 
-Section \ref{chap:background} describes the background from literature that we used to conduct this study.
-Section \ref{chap:clonedetection} presents our clone refactoring tool proposal.
-Section \ref{chap:clonetypes} outlines challenges with clone type definitions and proposes solutions for them in a refactoring context.
-Section \ref{chap:clonecontextexpl} outlines our analysis and measurements regarding the context of code clones.
-Section \ref{chap:mergingdups} shows our measurements regarding the amount of clones that can be refactored through method extraction.
-Section \ref{chap:threatstovalidity} shows the threats to validity of this study and section \ref{chap:conclusion} draws a conclusion based on our preliminary results.
+Sec.~\ref{chap:background} describes the background from literature that we used to conduct this study.
+Sec.~\ref{chap:clonedetection} presents our clone refactoring tool proposal.
+Sec.~\ref{chap:clonetypes} outlines challenges with clone type definitions and proposes solutions for them in a refactoring context.
+Sec.~\ref{chap:clonecontextexpl} outlines our analysis and measurements regarding the context of code clones.
+Sec.~\ref{chap:mergingdups} shows our measurements regarding the amount of clones that can be refactored through method extraction.
+Sec.~\ref{chap:threatstovalidity} shows the threats to validity of this study and Sec.~\ref{chap:conclusion} draws a conclusion based on our preliminary results.
 
@@
 We focus on clone classes, because of the advantages for refactoring.
-Clone pairs do not provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}.
+Clone pairs do not provide a general overview of all entities containing the clones, with all their related issues and characteristics~\cite{fontana2012duplicated}.
 Although clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered.
-Another issue that results from grouping clones by pairs: clone reference amount increases according to the binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), which causes a heavy information redundancy \cite{fontana2012duplicated}.
+Another issue that results from grouping clones by pairs: clone reference amount increases according to the binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), which causes a heavy information redundancy~\cite{fontana2012duplicated}.
 
 \subsection{Clone types}\label{chap:backgroundclonetypes}
-In a 2007 survey by Roy et al. \cite{roy2007survey} he defines several types of clones:\\
+In a 2007 survey by Roy et al.~\cite{roy2007survey} he defines several types of clones:\\
 \textbf{Type 1:} Identical code fragments except for variations in whitespace (may also be variations in layout) and comments.\\
@@
 It also makes the clone harder to refactor, as more transformations would be required.
-Higher clone types also become more disputable whether they actually indicate a harmful anti-pattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}).
+Higher clone types also become more disputable whether they actually indicate a harmful anti-pattern (as not every clone is harmful~\cite{jarzabek2010clones, kapser2008cloning}).
 
@@
 \subsection{Related work in clone refactoring tools}
-The Duplicated Code Refactoring Advisor (DCRA) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated, fontana2015duplicated}.
+The Duplicated Code Refactoring Advisor (DCRA) looks into refactoring opportunities for clone pairs~\cite{fontana2012duplicated, fontana2015duplicated}.
 DCRA only focuses on refactoring clone pairs, with the authors arguing that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.
-We further look into these measurements in section \ref{chap:relationsinstances}.
+We further look into these measurements in Sec.~\ref{chap:relationsinstances}.
 
-Aries \cite{higo2004aries, higo2008metric} focuses on the detection of refactorable clones.
-They do this based on the relation between clone instances through inheritance, similar to Fontana et al.
-\cite{fontana2012duplicated}.
+Aries~\cite{higo2004aries, higo2008metric} focuses on the detection of refactorable clones.
+They do this based on the relation between clone instances through inheritance, similar to Fontana et al.~\cite{fontana2012duplicated}.
 Aries also proposes a refactoring: if two clone classes are siblings of each other (share the same superclass), they propose to perform ``Extract method'' and ``Pull up method'' sequentially.
@@
 
-We investigated several research efforts that look into code clone refactoring \cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}.
+We investigated several research efforts that look into code clone refactoring~\cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}.
 However, all of these tools only support a subset of all harmful clones that are found.
 Also, these tools are limited to suggesting refactoring opportunities, rather than actually applying refactorings where suitable.
-Finally, all published approaches have limitations, such as false positives in their clone detection \cite{chen2018clone} or being limited to clone pairs \cite{higo2008metric}.
+Finally, all published approaches have limitations, such as false positives in their clone detection~\cite{chen2018clone} or being limited to clone pairs~\cite{higo2008metric}.
 
 \section{Addressing problems with clone type definitions}\label{chap:clonetypes}
-For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings (see section \ref{chap:backgroundclonetypes} for these definitions) to increase the chance that we can refactor the clone while improving the design.
+For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings (see Sec.~\ref{chap:backgroundclonetypes} for these definitions) to increase the chance that we can refactor the clone while improving the design.
 
 \section{Shortcomings of clone types}
-The clone definitions, as outlined in section \ref{chap:backgroundclonetypes}, allow reasoning about the duplication in a software system.
+The clone definitions, as outlined in Sec.~\ref{chap:backgroundclonetypes}, allow reasoning about the duplication in a software system.
 Clones by these definitions can relatively easily and efficiently be detected.
@@
 \subsection{Type 1 clones} \label{sec:type1}
-Type 1 clones are \textit{identical clone fragments except for variations in whitespace and comments} \cite{roy2007survey}.
+Type 1 clones are \textit{identical clone fragments except for variations in whitespace and comments}~\cite{roy2007survey}.
 This allows for the detection of clones that are the result of copying and pasting existing code, along with other reasons why duplicates might get into a codebase.
@@
 \subsection{Type 2 clones}\label{sec:type2}
-Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}.
+Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments}~\cite{roy2007survey}.
 This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified.
@@
 \subsection{Type 3 clones}\label{sec:type3}
-Type 3 clones are \textit{copied fragments with further modification (having added, removed or changed statements)} \cite{roy2007survey}.
+Type 3 clones are \textit{copied fragments with further modification (having added, removed or changed statements)}~\cite{roy2007survey}.
 Detection of clones by this definition can be hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed.
-Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold \cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
-This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance) \cite{lavoie2011automated}, token-level similarity \cite{sajnani2016sourcerercc} of statement-level similarity \cite{kamalpriya2017enhancing}.
+Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold~\cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
+This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance)~\cite{lavoie2011automated}, token-level similarity~\cite{sajnani2016sourcerercc} of statement-level similarity~\cite{kamalpriya2017enhancing}.
 
@@
 Type 3 clones allow any change in statements (added, removed and changed statements).
-Many clone detection tools have implemented this type by introducing a similarity threshold \cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
+Many clone detection tools have implemented this type by introducing a similarity threshold~\cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
 This similarity threshold entails that two fragments may differ by a certain percentage.
@@
 
-CloneRefactor uses JavaParser \cite{tomassetti2017javaparser}.
+CloneRefactor uses JavaParser~\cite{tomassetti2017javaparser}.
 JavaParser has a built-in symbol solver, which can automatically resolve types, method calls and variables.
@@
 In this section, we first assess a set of modern clone detection tools for their applicability to this domain.
-Next, we introduce our own tool geared towards automatic clone refactoring, CloneRefactor.%Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016.
+Next, we introduce our own tool geared towards automatic clone refactoring, CloneRefactor.%Two surveys of modern clone detection tools~\cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016.
 \todo{what is insufficient about these two?
@@
 \item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be merged.
-Sometimes, textual equality between code fragments does not imply that these can be merged (this is described more elaborately in section \ref{sec:type1}).
+Sometimes, textual equality between code fragments does not imply that these can be merged (this is described more elaborately in Sec.~\ref{sec:type1}).
 Because of this, we want to use a clone detection tool that can analyze such structures.
@@
 \textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
-Siamese \cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
-NiCAD \cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
-CPD \cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
-\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
-CCFinderSW \cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
-\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
-BigCloneEval \cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
-Deckard \cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
-Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
+Siamese~\cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
+NiCAD~\cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
+CPD~\cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
+\begin{tabular}[c]{@{}l@{}}CCFinder~\cite{kamiya2002ccfinder}\\ D-CCFinder~\cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
+CCFinderSW~\cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
+\begin{tabular}[c]{@{}l@{}}SourcererCC~\cite{sajnani2016sourcerercc}\\ Oreo~\cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
+BigCloneEval~\cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
+Deckard~\cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
+Scorpio~\cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
 \end{tabular}
@@
 This repository contains all scripts that were used to retrieve the data that is displayed in this paper.}.
-In this tool, we implemented both the literature clone types \cite{roy2007survey} and our refactoring-oriented clone types as described in section \ref{sec:rtypes}.
+In this tool, we implemented both the literature clone types~\cite{roy2007survey} and our refactoring-oriented clone types as described in Sec.~\ref{sec:rtypes}.
 
-Our tool is based on the JavaParser library \cite{tomassetti2017javaparser}.
+Our tool is based on the JavaParser library~\cite{tomassetti2017javaparser}.
 This library can parse Java source code to an AST representation.
@@
 
-CloneRefactor walks the AST and collects each declaration and statement (similar to the Scorpio clone detection tool \cite{higo2013revisiting}).
+CloneRefactor walks the AST and collects each declaration and statement (similar to the Scorpio clone detection tool~\cite{higo2013revisiting}).
 It then builds a graph representation on basis of this AST, in which each declaration and statement becomes a node.
@@
 Thresholds are a tool that aid in the process of deciding whether a clone \textit{should} be refactored.
-Many clone detection tools focus on either the number of lines \cite{kamiya2002ccfinder, svajlenko2016bigcloneeval}, number of tokens \cite{roy2008nicad, sajnani2016sourcerercc, ragkhitwetsagul2019siamese} and/or number of nodes (declarations/statements) \cite{higo2013revisiting} to decide whether code fragments should be considered clones of each other.
-A comparison of clone detection tools by Bellon et al.
-\cite{bellon2007comparison} shows that most clone detection tools choose a minimum of \textbf{6} lines of code to be duplicate to consider code fragments a clone.
-The Scorpio clone detection tool uses this same number as minimum number of nodes \cite{higo2013revisiting}.
-Token based tools mostly operate on basis of a minimum of \textbf{50} tokens for fragments to be considered a clone \cite{sajnani2016sourcerercc}.
+Many clone detection tools focus on either the number of lines~\cite{kamiya2002ccfinder, svajlenko2016bigcloneeval}, number of tokens~\cite{roy2008nicad, sajnani2016sourcerercc, ragkhitwetsagul2019siamese} and/or number of nodes (declarations/statements)~\cite{higo2013revisiting} to decide whether code fragments should be considered clones of each other.
+A comparison of clone detection tools by Bellon et al.~\cite{bellon2007comparison} shows that most clone detection tools choose a minimum of \textbf{6} lines of code to be duplicate to consider code fragments a clone.
+The Scorpio clone detection tool uses this same number as minimum number of nodes~\cite{higo2013revisiting}.
+Token based tools mostly operate on basis of a minimum of \textbf{50} tokens for fragments to be considered a clone~\cite{sajnani2016sourcerercc}.
 
@@
 For these experiments, we used our CloneRefactor tool.
-These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in section \ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in section \ref{chap:clonelocation}; the content of clone instances are explained, measured and discussed in section \ref{chap:clonecontents}.
+These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in Sec.~\ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in Sec.~\ref{chap:clonelocation}; the content of clone instances are explained, measured and discussed in Sec.~\ref{chap:clonecontents}.
 
 \subsection{The corpus}\label{chap:corpus}
-For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}.
+For our measurements we use a large corpus of open source projects~\cite{githubCorpus2013}.
 This corpus has been assembled to contain relatively higher quality projects.
@@
 
-As indicated in section \ref{chap:challenge} CloneRefactor requires all libraries of software projects we test.
-As these are not included in the used corpus \cite{githubCorpus2013}, we decided to filter the corpus to only include Maven projects.
+As indicated in Sec.~\ref{chap:challenge} CloneRefactor requires all libraries of software projects we test.
+As these are not included in the used corpus~\cite{githubCorpus2013}, we decided to filter the corpus to only include Maven projects.
 Maven is a build automation tool used primarily for Java, and works on basis of an \texttt{pom.xml} file to describe the projects' dependencies.
@@
   \begin{center}
-  \caption{General results for GitHub Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
+  \caption{General results for GitHub Java projects corpus~\cite{githubCorpus2013}.} \label{table:general}
   \medskip
@@
 Currently, we have implemented two clone detection algorithms into CloneRefactor.
-The first one finds clones by comparing tokens (excluding whitespace, comments and newlines), equal to the definition of type 1 clones in literature \cite{roy2007survey}.
-The second algorithm implements our T1R, as explained in section \ref{sec:type1r}.
+The first one finds clones by comparing tokens (excluding whitespace, comments and newlines), equal to the definition of type 1 clones in literature~\cite{roy2007survey}.
+The second algorithm implements our T1R, as explained in Sec.~\ref{sec:type1r}.
 The differences between the clones found for these algorithms is displayed in Table \ref{table:clonedet}.
@@
 This relation has a big impact on how a clone should be refactored, in order to improve the software design in the process.
-In this section, we display measurements we conducted on the corpus introduced in section \ref{chap:corpus}.
-These measurements are based on an experiment by Fontana et al.
-\cite{fontana2015duplicated}, which we will briefly introduce in section \ref{chap:catcloneinstancerelations}.
-We use a vastly different setup, which is explained in section \ref{chap:oursetup}.
-We then show our results in section \ref{chap:ourmeasurements}.
+In this section, we display measurements we conducted on the corpus introduced in Sec.~\ref{chap:corpus}.
+These measurements are based on an experiment by Fontana et al.~\cite{fontana2015duplicated}, which we will briefly introduce in Sec.~\ref{chap:catcloneinstancerelations}.
+We use a vastly different setup, which is explained in Sec.~\ref{chap:oursetup}.
+We then show our results in Sec.~\ref{chap:ourmeasurements}.
 
 \subsubsection{Categorizing Clone Instance Relations}\label{chap:catcloneinstancerelations}
-Fontana et al.
-\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other.
+Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other.
 To do this, they first define several categories for the relation between clone instances in object-oriented languages.
@@
 We use a similar setup to that used by Fontana et al.
-(Table~3 of Fontana et al.
-\cite{fontana2015duplicated}).
+(Table~3 of Fontana et al.~\cite{fontana2015duplicated}).
 Fontana et al.
@@
 \begin{itemize}
-  \item We consider clone classes rather than clone pairs. The rationale for this is given in section \ref{chap:cloneclasses}.
+  \item We consider clone classes rather than clone pairs. The rationale for this is given in Sec.~\ref{chap:cloneclasses}.
 \item We use different thresholds regarding when a clone should be considered.
@@
 We seek clones with a minimum size of 6 statements/declarations.
-This is explained detail in section \ref{chap:thresholds}.
+This is explained detail in Sec.~\ref{chap:thresholds}.
 \item We seek duplicates by statement/declaration rather than SLOC. This makes our analysis depend less on the coding style (in terms of newline usage) of the author of the software project.
@@
 Table~\ref{table:relations} contains our results regarding the relations between clone instances.
-In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our T1R definition as explained in section \ref{sec:type1r}.
+In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our T1R definition as explained in Sec.~\ref{sec:type1r}.
 
@@
 
-The most notable difference when comparing it to the results of Fontana et al.
-\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (38.14\% with T1R), while for them it was only 15.70\%.
+The most notable difference when comparing it to the results of Fontana et al.~\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (38.14\% with T1R), while for them it was only 15.70\%.
 This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
@@
 After mapping the relations between individual clones, we looked at the location of individual clone instances.
-A paper by Lozano et al.
-\cite{lozano2007evaluating} discusses the harmfulness of cloning.
+A paper by Lozano et al.~\cite{lozano2007evaluating} discusses the harmfulness of cloning.
 The authors argue that 98\% are produced at method-level.
@@
 
-Please note that these results are measured over each clone instance rather than each clone class, hence the higher total amount in comparison to the results of section \ref{chap:ourmeasurements}.
+Please note that these results are measured over each clone instance rather than each clone class, hence the higher total amount in comparison to the results of Sec.~\ref{chap:ourmeasurements}.
 
@@
 
-We have looked into existing definitions for different types of clones \cite{roy2007survey} and proposed solutions for problems that these types have with regards to automated refactoring.
+We have looked into existing definitions for different types of clones~\cite{roy2007survey} and proposed solutions for problems that these types have with regards to automated refactoring.
 We propose that fully qualified identifiers of method call signatures and type references should be considered instead of their plain text representation, to ensure refactorability.

### 2019-07-01 sattose/paper.tex
Type 2R revisited

@@
 Therefore, we first look at where and how often clones can be found, enabling the prioritization of refactoring opportunities.
-% Using this information we can determine in which locations clones are found the most, on basis of which the refactoring will be prioritized.
 
@@
 Therefore, we also analyze the impact of the different definitions of clone types on refactoring opportunities.
-% We look at the definitions of different types of clones and the opportunities to refactor duplicate parts of code albeit not an exact match.
 
@@
 \subsubsection{T2R clones}\label{sec:type2r}
-To solve the issues identifier in Sec.~\ref{sec:type2}, we introduce .
-We tackle the previously outlined shortcomings of type 2 clones to be able to detect such clones that can and should be refactored.
+To solve the issues identifier in Sec.~\ref{sec:type2}, we introduce an alternative definition.
 All rules that apply to T1R clones also apply to T2R clones.
 Additionally, T2R clones allow variability in literals, variables and method calls.
-This variability however is constrained by a threshold as a tradeoff exists in the refactoring of such differences.
-Furthermore, T2R clones allow any variability in method names and class/enum/interface names.
-This is because, if the body of a method/class/enum/interface equals the body of another, but only their names differ, this can be refactored without a design tradeoff.
+Furthermore, T2R clones allow variability in method names and class/enum/interface names.
 
-When refactoring two fragments that differ by a few literals, called methods or used variables, we are faced with a design tradeoff.
-For instance, if two literals differ and we want to refactor by method extraction, we need our new method to have an added argument to which each usage can pass the literal that was used at that place.
-Likewise, such things can be done for different variables that have been used and different called methods.
-Important here is, that the type of the used literals/variables are equal.
-Likewise, the signature of the called methods must be equal.
+When refactoring two fragments that differ by literals, called methods or used variables, we are faced with a design tradeoff.
+When replacing the cloned fragments by a new method, we need an extra argument for each literal, called method or used variable that differs.
+This can be done as long as the type of used literals/variables and the signature of called methods are equal.
 
@@
 \text{T2R}=\frac{\text{Different expressions}}{\text{Total tokens}}*100
-\end{equation}
-
-A method call does often not consist of a single token (unlike variables and literals).
-For instance, a method call \texttt{System.out.println()} consists of several segments: a type reference to the \texttt{System} type, a reference to the static \texttt{out} field and a call of the \texttt{println()} method.
-Because of this, T2R clones are not a subset of of type 2 clones.
-Because T3R clones inherit all rules of T2R clones, T3R clones are also not a subset of T3 clones.
-This is displayed in equation \ref{eq:typerelation2}.
-
-\begin{equation}\label{eq:typerelation2}
-T1R \subseteq T1 \text{, but } T2R	\nsubseteq T2 \text{ and } T3R \nsubseteq T3
 \end{equation}

### 2019-07-01 sattose/paper.tex
T3R
I had done this already right?

@@
 Type 3 clones allow any change in statements (added, removed and changed statements).
-Many clone detection tools have implemented this type by introducing a similarity threshold~\cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
-This similarity threshold entails that two fragments may differ by a certain percentage.
-This means that T3R allows the inclusion of a statement that is not detected by type 1 or 2 clone detection.
 When looking at how we can refactor a statement that is not included by one clone instance but is in another, we find that we require a conditional block to make up for the difference in statements.
@@
 \subsubsection{The challenge of detecting these clones}\label{chap:challenge}
-To detect each type of clone, we need to parse the fully qualified identifier of all types, method calls and variables.
+To detect each type of clone, we need to parse the FQI of all types, method calls and variables.
 This comes with serious challenges, regarding both performance and implementation.
-Also, to be able to parse all fully qualified identifiers, and trace the declarations of variables, we might need to follow cross file references.
+Also, to be able to parse all FQIs, and trace the declarations of variables, we might need to follow cross file references.
 The referenced types/variables/methods might even not be part of the project, but rather of an external library or the standard libraries of the programming language.
-All these factors need to be considered for the referenced entity to be found, on basis of which a fully qualified identifier can be created.
+All these factors need to be considered for the referenced entity to be found, on basis of which an FQI can be created.
 
@@
 There does not seem to be one golden set of thresholds, some thresholds work in some situations but fail in others.
-We have chosen thresholds that, according to our manual assessment, seemed optimal.
+We have chosen thresholds that, according to our assessments, seemed optimal.
 However, by using these, we definitely miss some harmful clones.
@@
 We have looked into existing definitions for different types of clones~\cite{roy2007survey} and proposed solutions for problems that these types have with regards to automated refactoring.
-We propose that fully qualified identifiers of method call signatures and type references should be considered instead of their plain text representation, to ensure refactorability.
+We propose that FQIs of method call signatures and type references should be considered instead of their plain text representation, to ensure refactorability.
 Furthermore, we propose that one should define thresholds for variability in variables, literals and method calls, in order to limit the number of parameters that the refactored unit shall have.

### 2019-07-01 sattose/paper.tex
Working on experiments stuff

@@
 To detect each type of clone, we need to parse the FQI of all types, method calls and variables.
-This comes with serious challenges, regarding both performance and implementation.
-Also, to be able to parse all FQIs, and trace the declarations of variables, we might need to follow cross file references.
+This comes with challenges, regarding both performance and implementation.
+To trace the declarations of variables, methods and types, we might need to follow cross file references.
 The referenced types/variables/methods might even not be part of the project, but rather of an external library or the standard libraries of the programming language.
 All these factors need to be considered for the referenced entity to be found, on basis of which an FQI can be created.
-
-CloneRefactor uses JavaParser~\cite{tomassetti2017javaparser}.
-JavaParser has a built-in symbol solver, which can automatically resolve types, method calls and variables.
-However, because of this, CloneRefactor does require all libraries that the software project requires (apart from the Java Standard Library).
-If these are not available, CloneRefactor will estimate types on basis of the information that is available.
 
@@
 On basis of this graph we detect clone classes.
-We compare clone classes against the thresholds, and remove the clone classes that do not pass the test.
+We compare clone classes against thresholds, and remove the clone classes that do not pass the test.
+
+\section{Experiments}
+This section outlines the conducted experiments to determine refactoring opportunities for code clones.
+First, we look into the thresholds that determine whether duplicated fragments are considered a clone in section \ref{chap:thresholds}.
+Next, we show the corpus on which we have performed our measurements in section \ref{chap:corpus}.
+We then perform an analysis on the context of code clones in section \ref{chap:clonecontextexpl}.
+Finally, we map refactoring opportunities for clones in section \ref{chap:mergingdups}.
 
@@
 
-However, we would argue that going with this ``magic number 6'' eliminates a lot of harmful clones that should be refactored. For instance
-
-\section{Context Analysis of Clones}\label{chap:clonecontextexpl}
-To be able to refactor code clones, it is very important to consider the context of the clone. We define the following aspects of the clone as its context:
-\begin{enumerate}
-  \item The relation of clone instances among each other through inheritance (for example: a clone instance resides in a superclass of another clone instance in the same clone class).
-  \item Where a clone instance occurs in the code (for example: a method-level clone is a clone instance that is in a method).
-  \item The contents of a clone instance (for example: the clone instance spans several methods).
-\end{enumerate}
-
-\begin{figure}[H]
-  \caption{Abstract representation of clone classes and clone instances.}
-    \medskip
-    \includegraphics[width=1\columnwidth]{img/context}
-  \label{fig:clonecontext}
-\end{figure}
-
-Figure \ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
-The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
-The location and contents of clones is measured on clone instance level.
-A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50).
-A clone instance contents consists of a list of all statements and declarations it spans.
-
-We analyzed the context of clones in a large corpus of open source projects.
-For these experiments, we used our CloneRefactor tool.
-These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in Sec.~\ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in Sec.~\ref{chap:clonelocation}; the content of clone instances are explained, measured and discussed in Sec.~\ref{chap:clonecontents}.
+We would argue that going with this ``magic number 6'' eliminates a lot of harmful clones that should be refactored.
+For instance, a single 100-token statement will not be considered by such a threshold, which can still be harmful for the system design when
 
@@
 \end{table}
+
+\subsection{Context Analysis of Clones}\label{chap:clonecontextexpl}
+To be able to refactor code clones, it is very important to consider the context of the clone. We define the following aspects of the clone as its context:
+\begin{enumerate}
+  \item The relation of clone instances among each other through inheritance (for example: a clone instance resides in a superclass of another clone instance in the same clone class).
+  \item Where a clone instance occurs in the code (for example: a method-level clone is a clone instance that is in a method).
+  \item The contents of a clone instance (for example: the clone instance spans several methods).
+\end{enumerate}
+
+\begin{figure}[H]
+  \caption{Abstract representation of clone classes and clone instances.}
+    \medskip
+    \includegraphics[width=1\columnwidth]{img/context}
+  \label{fig:clonecontext}
+\end{figure}
+
+Figure \ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
+The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
+The location and contents of clones is measured on clone instance level.
+A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50).
+A clone instance contents consists of a list of all statements and declarations it spans.
+
+We analyzed the context of clones in a large corpus of open source projects.
+For these experiments, we used our CloneRefactor tool.
+These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in Sec.~\ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in Sec.~\ref{chap:clonelocation}; the content of clone instances are explained, measured and discussed in Sec.~\ref{chap:clonecontents}.
 
@@
 
-\section{Merging duplicate code through method extraction}\label{chap:mergingdups}
+\subsection{Method extraction opportunities}\label{chap:mergingdups}
 The most used technique to refactor clones is method extraction (creating a new method on basis of the contents of clones).

### 2019-07-01 sattose/paper.tex
Stuff

@@
 
-\subsection{Thresholds}\label{chap:thresholds}
-Thresholds are a tool that aid in the process of deciding whether a clone \textit{should} be refactored.
-Many clone detection tools focus on either the number of lines~\cite{kamiya2002ccfinder, svajlenko2016bigcloneeval}, number of tokens~\cite{roy2008nicad, sajnani2016sourcerercc, ragkhitwetsagul2019siamese} and/or number of nodes (declarations/statements)~\cite{higo2013revisiting} to decide whether code fragments should be considered clones of each other.
-A comparison of clone detection tools by Bellon et al.~\cite{bellon2007comparison} shows that most clone detection tools choose a minimum of \textbf{6} lines of code to be duplicate to consider code fragments a clone.
-The Scorpio clone detection tool uses this same number as minimum number of nodes~\cite{higo2013revisiting}.
-Token based tools mostly operate on basis of a minimum of \textbf{50} tokens for fragments to be considered a clone~\cite{sajnani2016sourcerercc}.
-
-We would argue that going with this ``magic number 6'' eliminates a lot of harmful clones that should be refactored.
-For instance, a single 100-token statement will not be considered by such a threshold, which can still be harmful for the system design when
-
 \subsection{The corpus}\label{chap:corpus}
-For our measurements we use a large corpus of open source projects~\cite{githubCorpus2013}.
+For our experiments we use a large corpus of open source projects~\cite{githubCorpus2013}.
 This corpus has been assembled to contain relatively higher quality projects.
@@
 
-Some general data regarding this corpus is displayed in Table \ref{table:general}.
+\subsection{Thresholds}\label{chap:thresholds}
+Thresholds are a tool that aid in the process of deciding whether a clone \textit{should} be refactored.
+Many clone detection tools focus on either the number of lines~\cite{kamiya2002ccfinder, svajlenko2016bigcloneeval}, number of tokens~\cite{roy2008nicad, sajnani2016sourcerercc, ragkhitwetsagul2019siamese} and/or number of nodes (declarations/statements)~\cite{higo2013revisiting} to decide whether code fragments should be considered clones of each other.
+A comparison of clone detection tools by Bellon et al.~\cite{bellon2007comparison} shows that most clone detection tools choose a minimum of \textbf{6} lines of code to be duplicate to consider code fragments a clone.
+The Scorpio clone detection tool uses this same number as minimum number of nodes~\cite{higo2013revisiting}.
+Token based tools mostly operate on basis of a minimum of \textbf{50} tokens for fragments to be considered a clone~\cite{sajnani2016sourcerercc}.
 
-\begin{table}[H]
-  \begin{center}
-  \caption{General results for GitHub Java projects corpus~\cite{githubCorpus2013}.} \label{table:general}
-  \medskip
-\begin{tabular}{|l|l|}
-\hline
-Amount of projects                                                                                      & 1,361      \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\whitespace, comments and newlines.)\end{tabular} & 1,414,996  \\ \hline
-Amount of statements/declarations                                                                       & 1,212,189  \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of tokens (excluding\\whitespace, comments and newlines.)\end{tabular} & 11,643,194 \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
+We would argue that going with this ``magic number 6'' eliminates a lot of harmful clones that should be refactored.
+For instance, a single 100-token statement will not be considered by such a threshold, which can still be harmful for the system design when cloned.
+Because of that, we decided to perform our measurements using thresholds that will include most clones that should be refactored, while eliminating most of the noise.
+With ``noise'' we mean duplication that has no relevancy towards refactoring, like a single token that is duplicated elsewhere.
+
+To find such a threshold, we measured the resulting . We then
 

### 2019-07-01 sattose/paper.tex
The right chart  + thresholds

@@
 This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
-
-As indicated in Sec.~\ref{chap:challenge} CloneRefactor requires all libraries of software projects we test.
-As these are not included in the used corpus~\cite{githubCorpus2013}, we decided to filter the corpus to only include Maven projects.
-Maven is a build automation tool used primarily for Java, and works on basis of an \texttt{pom.xml} file to describe the projects' dependencies.
-As no \texttt{pom.xml} files are included in the corpus, we cloned the latest version of each project in the corpus.
-We then removed each project that has no \texttt{pom.xml} file.
-As a final step, we collected all dependencies for each project by using the \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib} Maven command, and removed each project for which not all dependencies were available (due to non-Maven dependencies being used or unsatisfiable dependencies being referenced in the \texttt{pom.xml} file).
+We filtered this corpus further to only include projects that use Maven, which is a build tool which is mainly used to manage dependencies in the Java ecosystem.
+We then filtered the corpus further to only include projects for which all external dependencies are available.
 
@@
 
-To find such a threshold, we measured the resulting . We then
+To find such a threshold, we measured the amount of clone classes found for a certain number of tokens.
+We then looked at the amount of nodes (statements/declarations) that these clones span.
+The resulting chart is displayed in figure \ref{fig:tokenthreshold}.
+
+\begin{figure}[H]
+  \caption{Amount of times a clone with a certain amount of tokens has a certain amount of nodes.}
+    \includegraphics[width=1\columnwidth]{img/TokenThreshold}
+  \label{fig:tokenthreshold}
+\end{figure}
+
+In this chart we see that when seeking clones with a minimum of 10 tokens, there are more clones that span 2 statements than clones that span one statement.
+We manually assessed these clones, and mainly the two-statement clones contain many clones that we classified as ``should be refactored''.
+Because of this, we decided to go with a minimum of 10 tokens threshold for our experiments.
 
 \subsection{Context Analysis of Clones}\label{chap:clonecontextexpl}
-To be able to refactor code clones, it is very important to consider the context of the clone. We define the following aspects of the clone as its context:
+To be able to refactor code clones, it is important to consider the context of the clone. We define the following aspects of the clone as its context:
 \begin{enumerate}

### 2019-07-01 sattose/paper.tex
TypeResults

@@
 We then filtered the corpus further to only include projects for which all external dependencies are available.
+This resulted in 1.343 projects of varying sizes averaging at 980 source lines of code (omitting whitespace, comments) per project.
 
@@
 Because of this, we decided to go with a minimum of 10 tokens threshold for our experiments.
+
+\subsection{Clone types}
+In this chapter we display the differences between clone type 1-3 \cite{roy2007survey} and type 1R-3R as proposed in section \ref{sec:rtypes}.
+When running our clone detection script over the corpus, we get the results displayed in figure
+
+\begin{figure}[H]
+  \caption{Number of cloned declarations/statements.}
+    \includegraphics[width=1\columnwidth]{img/TypeResults}
+  \label{fig:tokenthreshold}
+\end{figure}
 

### 2019-07-01 sattose/paper.tex
Something with relations

@@
 
-Looking at the example in figure \ref{fig:type2}, we see an example of a type 2 clone that poses no harm to the design of the system.
+Looking at the example in Fig.~\ref{fig:type2}, we see an example of a type 2 clone that poses no harm to the design of the system.
 Both methods are, except for their matching structure, completely different in functionality.
@@
 We then looked at the amount of nodes (statements/declarations) that these clones span.
-The resulting chart is displayed in figure \ref{fig:tokenthreshold}.
+The resulting chart is displayed in Fig.~\ref{fig:tokenthreshold}.
 
@@
 In this chapter we display the differences between clone type 1-3 \cite{roy2007survey} and type 1R-3R as proposed in section \ref{sec:rtypes}.
-When running our clone detection script over the corpus, we get the results displayed in figure
+When running our clone detection script over the corpus, we get the results displayed in Fig.~\ref{fig:typeres}.
 
@@
     \includegraphics[width=1\columnwidth]{img/TypeResults}
-  \label{fig:tokenthreshold}
+  \label{fig:typeres}
 \end{figure}
+
+In this figure the amount cloned statements per clone type are displayed.
+The difference between T1R and T1 is small (10.9\%), because most often textually equal code is also functionally equal.
+The difference between T2R and T2 is bigger (34.7\%), mainly because we allow no variability in used types.
+T3R and T3 are similar to T2R and T2, because our dataset does not have so many gapped clones for the thresholds used.
+
+We also measured the duration of finding clones by the different clone types. These results are displayed in figure TODO.
 
@@
 
-Figure \ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
+Fig.~\ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
 The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
@@
 A clone instance contents consists of a list of all statements and declarations it spans.
-
-We analyzed the context of clones in a large corpus of open source projects.
-For these experiments, we used our CloneRefactor tool.
-These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in Sec.~\ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in Sec.~\ref{chap:clonelocation}; the content of clone instances are explained, measured and discussed in Sec.~\ref{chap:clonecontents}.
-
-\subsection{Clone detection results}
-Currently, we have implemented two clone detection algorithms into CloneRefactor.
-The first one finds clones by comparing tokens (excluding whitespace, comments and newlines), equal to the definition of type 1 clones in literature~\cite{roy2007survey}.
-The second algorithm implements our T1R, as explained in Sec.~\ref{sec:type1r}.
-The differences between the clones found for these algorithms is displayed in Table \ref{table:clonedet}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{CloneRefactor clone detection results for the two different algorithms.} \label{table:clonedet}
-  \medskip
-\begin{tabular}{|l|l|l|}
-\hline
- & \textbf{Type 1} & \textbf{T1R} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines cloned\end{tabular} & 200,362 & 129,519 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of statements/\\declarations cloned\end{tabular} & 182,466 & 118,980 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of tokens cloned\end{tabular} & 1,582,845 & 973,596 \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-Looking at Table \ref{table:clonedet}, it becomes apparent that the T1R algorithm finds significantly less clones than the type 1 algorithm.
-This indicates that about a third of the clones have textual equality, but are not actually equal when considering the types of expressions.
-This makes these clones less suitable for automated refactoring.
 
@@
 To do this, they first define several categories for the relation between clone instances in object-oriented languages.
-A few of these categories are shown in Figure \ref{fig:clonerelation}.
+These categories are shown in Fig.~\ref{fig:clonerelation}.
 These categories are as follows:
@@
 \end{figure}
-Please note that none of these categories allow external classes (except for ``same external superclass'').
-So if two clone instances are related through external classes but do not share a common external superclass, it will be flagged as ``unrelated''.
-The main reason for this is that it is (often) not possible to refactor to external classes.
 

### 2019-07-01 sattose/paper.tex
Stuff

@@
 \subsection{Research questions}
-We have formalized the following research questions in order to improve upon the state-of-the-art in code duplication refactoring:\\
+We have formalized the following research questions in order to improve upon the state-of-the-art in code duplication refactoring:
+\\\\
 \textbf{RQ1.} How can we define clone types such that they \textbf{can} be automatically refactored?\\
@@
 \subsection{Clone types}\label{chap:backgroundclonetypes}
-In a 2007 survey by Roy et al.~\cite{roy2007survey} he defines several types of clones:\\
+In a 2007 survey by Roy et al.~\cite{roy2007survey} he defines several types of clones:
+\\\\
 \textbf{Type 1:} Identical code fragments except for variations in whitespace (may also be variations in layout) and comments.\\
@@
 
-We also measured the duration of finding clones by the different clone types. These results are displayed in figure TODO.
+We also measured the duration of finding clones by the different clone types.
+These results are displayed in figure \ref{fig:performance}.
+Although this data is dependent on the implementation, there is a notable difference between the refactoring-oriented clone types and the literature clone types.
+Most of the time that the refactoring-oriented clone types take longer is spent resolving symbols (to infer FQIs).
+
+\begin{figure}[H]
+  \caption{Duration in minutes of identifying clones for clone type definitions.}
+    \includegraphics[width=1\columnwidth]{img/TypeResults}
+  \label{fig:performance}
+\end{figure}
 
@@
 
+All data shown in this section is measured using the T1R clone definition.
+We have performed the same measurements for the other type definitions and found that they follow similar trends.
+Because of that, we decided not to further show them in this section.
+
 \subsection{Relations Between Clone Instances} \label{chap:relationsinstances}
-When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances.
-This relation has a big impact on how a clone should be refactored, in order to improve the software design in the process.
-In this section, we display measurements we conducted on the corpus introduced in Sec.~\ref{chap:corpus}.
-These measurements are based on an experiment by Fontana et al.~\cite{fontana2015duplicated}, which we will briefly introduce in Sec.~\ref{chap:catcloneinstancerelations}.
-We use a vastly different setup, which is explained in Sec.~\ref{chap:oursetup}.
-We then show our results in Sec.~\ref{chap:ourmeasurements}.
+When merging code clones in object-oriented languages, it is very important to consider the inheritance relation between clone instances.
+This relation has a big impact on how a clone should be refactored.
 
@@
 
-\subsubsection{Our setup}\label{chap:oursetup}
 We use a similar setup to that used by Fontana et al.
@@
 
-\subsubsection{Our results} \label{chap:ourmeasurements}
 Table~\ref{table:relations} contains our results regarding the relations between clone instances.
-In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our T1R definition as explained in Sec.~\ref{sec:type1r}.
 
@@
   \medskip
-\begin{tabular}{|l|l|l|l|l|} \hline
-\textbf{Relation}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-Unrelated          & 6,134           & 35.48  & 4,762 & 38.14            \\ \hline
-\begin{tabular}[c]{@{}l@{}}Same\\Class\end{tabular}          & 4,772            & 27.60  & 3,131 & 25.07             \\ \hline
-Sibling            & 2,680            & 15.50   & 1,949 & 15.61            \\ \hline
-\begin{tabular}[c]{@{}l@{}}Same\\Method\end{tabular}         & 2,247            & 13.00   & 1,685 & 13.49             \\ \hline
-\begin{tabular}[c]{@{}l@{}}External\\Superclass\end{tabular} & 794            & 4.59   & 558 & 4.47             \\ \hline
-\begin{tabular}[c]{@{}l@{}}First\\Cousin\end{tabular}        & 269             & 1.56     & 197 & 1.58           \\ \hline
-Superclass         & 237             & 1.37     & 118 & 0.94           \\ \hline
-\begin{tabular}[c]{@{}l@{}}Common\\Hierarchy\end{tabular}    & 123             & 0.71    & 73 & 0.58            \\ \hline
-Ancestor           & 35              & 0.20     & 14 & 0.11          \\ \hline
+\begin{tabular}{|l|l|l|} \hline
+\textbf{Relation} & \textbf{\#} & \textbf{\%} \\ \hline
+Unrelated          & 4,762 & 38.14            \\ \hline
+Same Class          & 3,131 & 25.07             \\ \hline
+Sibling               & 1,949 & 15.61            \\ \hline
+Same Method         & 1,685 & 13.49             \\ \hline
+External Superclass   & 558 & 4.47             \\ \hline
+First Cousin          & 197 & 1.58           \\ \hline
+Superclass          & 118 & 0.94           \\ \hline
+Common Hierarchy    & 73 & 0.58            \\ \hline
+Ancestor          & 14 & 0.11          \\ \hline
 \end{tabular}

### 2019-07-01 sattose/paper.tex
Tables n charts n stuff

@@
 We also measured the duration of finding clones by the different clone types.
-These results are displayed in figure \ref{fig:performance}.
+Fig.~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types.
 Although this data is dependent on the implementation, there is a notable difference between the refactoring-oriented clone types and the literature clone types.
@@
   \caption{Duration in minutes of identifying clones for clone type definitions.}
-    \includegraphics[width=1\columnwidth]{img/TypeResults}
+    \includegraphics[width=1\columnwidth]{img/DurationChart}
   \label{fig:performance}
@@
   \medskip
-\begin{tabular}{|l|l|l|l|l|}
+\begin{tabular}{|l|l|l|}
 \hline
-\textbf{Location}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-Method Level       & 32,861           & 66.02   & 19,075 & 58.23            \\ \hline
-Class Level        & 15,069           & 30.27   & 12,207 & 37.27            \\ \hline
-\begin{tabular}[c]{@{}l@{}}Constructor\\Level\end{tabular}  & 1,391            & 2.79     & 1,080 & 3.30           \\ \hline
-\begin{tabular}[c]{@{}l@{}}Interface\\Level\end{tabular}    & 282              & 0.57     & 247 & 0.75           \\ \hline
-Enum Level         & 171               & 0.34    & 147 & 0.45            \\ \hline
+\textbf{Location}   & \textbf{\#} & \textbf{\%} \\ \hline
+Method Level        & 19,075 & 58.23            \\ \hline
+Class Level        & 12,207 & 37.27            \\ \hline
+Constructor Level    & 1,080 & 3.30           \\ \hline
+Interface Level   & 247 & 0.75           \\ \hline
+Enum Level         & 147 & 0.45            \\ \hline
 \end{tabular}

### 2019-07-01 sattose/paper.tex
Nicer tables n stuff

@@
 Duplication in source code can have a major negative impact on the maintainability of source code, as it creates implicit dependencies between fragments of code.
-Such implicit dependencies often cause bugs.
+Such implicit dependencies often cause bugs and increases maintenance efforts.
 In this study, we look into the opportunities to automatically refactor these duplication problems for object-oriented programming languages.
@@
 
-\subsection{Clone instance location}\label{chap:clonelocation}
+\subsubsection{Clone instance location}\label{chap:clonelocation}
 After mapping the relations between individual clones, we looked at the location of individual clone instances.
@@
 
-\subsection{Clone instance contents}\label{chap:clonecontents}
+\subsubsection{Clone instance contents}\label{chap:clonecontents}
 Finally, we looked at the contents of individual clone instances: what kind of declarations and statements do they span. We selected the following categories to be relevant for refactoring:
@@
   \medskip
-\begin{tabular}{|l|l|l|l|l|}
+\begin{tabular}{|l|l|l|}
   \hline
-  \textbf{Contents} & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Partial\\Method\end{tabular}             & 32,214 & 64.72 & 18,791 & 57.37 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Several\\Methods\end{tabular}            & 10,542 & 21.18 & 8,514 & 25.99 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes\\Constructor\end{tabular}       & 1,772  & 3.56  & 1,213 & 3.70 \\ \hline
-  Includes Field                                                      & 1,681  & 3.38  & 1,487 & 4.54 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Partial\\Constructor\end{tabular}        & 1,389  & 2.79  & 1,078 & 3.29 \\ \hline
-  Only Fields                                                         & 962    & 1.93  & 888 & 2.71 \\ \hline
-  Full Method                                                         & 647    & 1.30  & 284 & 0.87 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Class\\Declaration\end{tabular} & 263    & 0.53  & 258 & 0.79 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Other\\Categories\end{tabular}           & 304    & 0.61  & 243 & 0.74 \\ \hline
+  \textbf{Contents} & \textbf{\#} & \textbf{\%} \\ \hline
+  Partial Method     & 18,791 & 57.37 \\ \hline
+  Several Methods         & 8,514 & 25.99 \\ \hline
+  Includes Constructor  & 1,213 & 3.70 \\ \hline
+  Includes Field        & 1,487 & 4.54 \\ \hline
+  Partial Constructor      & 1,078 & 3.29 \\ \hline
+  Only Fields           & 888 & 2.71 \\ \hline
+  Full Method           & 284 & 0.87 \\ \hline
+  Includes Class Declaration  & 258 & 0.79 \\ \hline
+  Other Categories    & 243 & 0.74 \\ \hline
 \end{tabular}
@@
   \medskip
-\begin{tabular}{|l|l|l|l|l|}
+\begin{tabular}{|l|l|l|}
 \hline
-\textbf{}        & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Is not a\\partial method\end{tabular}           & 5,917 & 34.22 & 4,806 & 38.49 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Complex\\control flow\end{tabular} & 5,511 & 31.87 & 3,158 & 25.29 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Spans part of\\a block\end{tabular}             & 3,989 & 23.07 & 3,152 & 25.24 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Can be\\extracted\end{tabular}                  & 1,874 & 10.84 & 1,371 & 10.98 \\ \hline
+\textbf{}         & \textbf{\#} & \textbf{\%} \\ \hline
+Is not a partial method     & 4,806 & 38.49 \\ \hline
+Complex control flow  & 3,158 & 25.29 \\ \hline
+Spans part of a block   & 3,152 & 25.24 \\ \hline
+Can be extracted & 1,371 & 10.98 \\ \hline
 \end{tabular}

### 2019-07-01 sattose/paper.tex
Sprinkling some new results in there

@@
   \textbf{Contents} & \textbf{\#} & \textbf{\%} \\ \hline
-  Partial Method     & 18,791 & 57.37 \\ \hline
-  Several Methods         & 8,514 & 25.99 \\ \hline
-  Includes Constructor  & 1,213 & 3.70 \\ \hline
-  Includes Field        & 1,487 & 4.54 \\ \hline
-  Partial Constructor      & 1,078 & 3.29 \\ \hline
-  Only Fields           & 888 & 2.71 \\ \hline
-  Full Method           & 284 & 0.87 \\ \hline
-  Includes Class Declaration  & 258 & 0.79 \\ \hline
-  Other Categories    & 243 & 0.74 \\ \hline
+  Partial Method     & 79,945 & 78.80 \\ \hline
+  Several Methods         & 7,323 & 7.22 \\ \hline
+  Partial Constructor      & 4,385 & 4.32 \\ \hline
+  Full Method           & 3,868 & 3.81 \\ \hline
+  Only Fields           & 3,039 & 3.00 \\ \hline
+  Includes Constructor  & 1,522 & 1.50 \\ \hline
+  Includes Field        & 616 & 0.61 \\ \hline
+  Includes Class Declaration  & 376 & 0.37 \\ \hline
+  Other Categories    & 376 & 0.37\\ \hline
 \end{tabular}
@@
 Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
-    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements.
+    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
     \item \textbf{Spans part of a block:} This clone spans a part of a statement.
@@
 \textbf{}         & \textbf{\#} & \textbf{\%} \\ \hline
-Is not a partial method     & 4,806 & 38.49 \\ \hline
-Complex control flow  & 3,158 & 25.29 \\ \hline
-Spans part of a block   & 3,152 & 25.24 \\ \hline
-Can be extracted & 1,371 & 10.98 \\ \hline
+Can be extracted     & 13,553 & 38.22 \\ \hline
+Spans part of a block  & 12,332 & 34.78 \\ \hline
+Is not a partial method   & 8,074 & 22.77 \\ \hline
+Complex control flow & 1,503 & 4.24 \\ \hline
 \end{tabular}
@@
 
-From Table \ref{table:refactorability}, we can see that approximately ten percent of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
+From Table \ref{table:refactorability}, we can see that 38.22\% of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
 For the other clones, other techniques or transformations will be required.
-Looking into these techniques and transformations will be one of our next steps.
 

### 2019-07-01 sattose/paper.tex
More new results
#imtired

@@
 \textbf{Relation} & \textbf{\#} & \textbf{\%} \\ \hline
-Unrelated          & 4,762 & 38.14            \\ \hline
-Same Class          & 3,131 & 25.07             \\ \hline
-Sibling               & 1,949 & 15.61            \\ \hline
-Same Method         & 1,685 & 13.49             \\ \hline
-External Superclass   & 558 & 4.47             \\ \hline
-First Cousin          & 197 & 1.58           \\ \hline
-Superclass          & 118 & 0.94           \\ \hline
-Common Hierarchy    & 73 & 0.58            \\ \hline
-Ancestor          & 14 & 0.11          \\ \hline
+Unrelated          & 12,368 & 34.88            \\ \hline
+Same Class          & 11,483 & 32.38             \\ \hline
+Same Method               & 5,056 & 14.26            \\ \hline
+Sibling         & 4,182 & 11.79             \\ \hline
+External Superclass   & 1,066 & 3.01             \\ \hline
+Superclass          & 558 & 1.57           \\ \hline
+First Cousin          & 489 & 1.38           \\ \hline
+Common Hierarchy    & 206 & 0.58            \\ \hline
+Ancestor          & 54 & 0.15          \\ \hline
 \end{tabular}
@@
 \textbf{Location}   & \textbf{\#} & \textbf{\%} \\ \hline
-Method Level        & 19,075 & 58.23            \\ \hline
-Class Level        & 12,207 & 37.27            \\ \hline
-Constructor Level    & 1,080 & 3.30           \\ \hline
-Interface Level   & 247 & 0.75           \\ \hline
-Enum Level         & 147 & 0.45            \\ \hline
+Method Level        & 83,813 & 82.62            \\ \hline
+Class Level        & 12,534 & 12.35            \\ \hline
+Constructor Level    & 4,391 & 4.33           \\ \hline
+Interface Level   & 567 & 0.56           \\ \hline
+Enum Level         & 145 & 0.14            \\ \hline
 \end{tabular}
@@
 
-Our results indicate that around 58\% of the clones are produced at method-level.
-About 39\% of clones either span several methods/constructors or contain something like a field declaration.
-Another 3\% of the clones are found in constructors.
-The amount of clones found in interfaces and enumerations is very low.
-Regarding the differences between type 1 and T1R, it seems that there are relatively less method level clones and more class level clones for T1R.
-This is probably due to that the main reason for variability between type 1 and T1R is variable references, which occur more at method level than class level.
+Our results indicate that, quite significantly, most clones are found at method level. The amount of clones found in interfaces and enumerations is very low.
 

### 2019-07-01 sattose/paper.tex
Checking the document for consistancy

@@
 
-\institution{University of Amsterdam}
+\institution{}
 
@@
 Our intermediate results indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
-Approximately ten percent of the duplication can be refactored through method extraction without extra considerations required, while other clones require other refactoring techniques or further transformations.
-Similar future measurements will provide further insight into the contexts where clones occur and how this affects the automated refactoring process.
-Finally, we strive to construct a tool that automatically applies refactorings for a large part of the detected duplication problems.
+Almost 40 percent of the duplication can be refactored through method extraction, while other clones require other refactoring techniques or further transformations.
+Future measurements will provide further insight into what clones should be refactored to improve the design of a software system.
 \end{abstract}
@@
 Duplication in source code is often seen as one of the most harmful types of technical debt.
-In Martin Fowler's ``Refactoring'' book~\cite{fowler1999refactoring}, he claims that \textit{``Number one in the stink parade is duplicated code.
-If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
+In Martin Fowler's ``Refactoring'' book~\cite{fowler1999refactoring}, he claims that \textit{``If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
 % In this research, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
@@
   \caption{Number of cloned declarations/statements.}
-    \includegraphics[width=1\columnwidth]{img/TypeResults}
+    \includegraphics[width=.96\columnwidth]{img/TypeResults}
   \label{fig:typeres}
@@
   \caption{Duration in minutes of identifying clones for clone type definitions.}
-    \includegraphics[width=1\columnwidth]{img/DurationChart}
+    \includegraphics[width=.96\columnwidth]{img/DurationChart}
   \label{fig:performance}
@@
 
-The most notable difference when comparing it to the results of Fontana et al.~\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (38.14\% with T1R), while for them it was only 15.70\%.
-This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
+The most notable difference when comparing it to the results of Fontana et al.~\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (34.44), while for them it was only 15.70\%.
+This is likely due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
 It could also be that the corpus which we use, as it has generally smaller projects, uses more classes from outside the project (which are marked ``Unrelated'' if they do not have a common external superclass).
-About a fourth of all clone classes have all instances in the same class, which is generally easy to refactor.
-On the third place come the ``Sibling'' clones, which can often be refactored using a pull-up refactoring.
-There are no noteworthy differences between type 1 and T1R clones.
+About a third of all clone classes have all instances in the same class, which is generally easy to refactor.
+On the third place come the clones that are in the same method, which are also easy to refactor.
 
@@
 We validated this claim over our corpus.
-The results for the clone instance locations are shown in Table \ref{table:locations}.
-We chose the following categories:
+We use the following categories:
 \begin{enumerate}
@@
 
-Please note that these results are measured over each clone instance rather than each clone class, hence the higher total amount in comparison to the results of Sec.~\ref{chap:ourmeasurements}.
+The results are shown in Table~\ref{table:locations}.
+Our results indicate that, quite significantly, most clones are found at method level.
+The amount of clones found in interfaces and enumerations is very low.
 
@@
 \end{table}
-
-Our results indicate that, quite significantly, most clones are found at method level. The amount of clones found in interfaces and enumerations is very low.
 
@@
 Unsurprisingly, most clones span a part of a method.
-More than a quarter of the clones (for T1R) span over several methods, which either requires more advanced refactoring techniques or indicates a non-harmful clone.
+The most used refactoring technique for clones that span part of a method is ``Extract Method''.
+Because of that, we focus our research efforts on refactoring such clones.
 
@@
 However, method extraction cannot be applied in all cases.
-Sometimes a clone spans a statement partially (like a for-loop of which only it's declaration and a part of the body is cloned).
-Merging the clones can be harder in such instances.
-Also, the cloned code can contain statements like \texttt{return}, \texttt{break}, \texttt{continue}.
 In these instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.

### 2019-07-01 sattose/paper.tex
Mainly introduction

@@
 Our intermediate results indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
-Almost 40 percent of the duplication can be refactored through method extraction, while other clones require other refactoring techniques or further transformations.
-Future measurements will provide further insight into what clones should be refactored to improve the design of a software system.
+Almost fourty percent of the duplication can be refactored through method extraction, while other clones require other refactoring techniques or further transformations.
+Future measurements will provide further insight into what clones should be refactored to improve the design of software systems.
 \end{abstract}
@@
 In this paper, we outline challenges with these clone type definitions when considered in a refactoring context.
-We next propose solutions to these problems that would enable the detection of clones that should be refactored, rather than fragments of code that are just similar.
+We next propose solutions to these problems that would enable the detection of clones that can and should be refactored, rather than fragments of code that are just similar.
 
@@
 The location of a clone in the code has an impact on how it can be refactored.
-Therefore, we first look at where and how often clones can be found, enabling the prioritization of refactoring opportunities.
+Therefore, we first look at where and how often clones are found, enabling the prioritization of refactoring opportunities.
 
-Furthermore, a duplicate fragment in a codebase does not always have to be an exact match with another fragment to be considered a clone.
-Therefore, we also analyze the impact of the different definitions of clone types on refactoring opportunities.
-
-We conduct our research on a large corpus of open source projects.
 We focus mainly on the Java programming language as refactoring opportunities feature paradigm and programming language dependent aspects~\cite{choi2011extracting}.
-However, most practices featured currently in our work will also be applicable to other object-oriented languages, like C\#.
+However, most practices featured currently in our work will also be applicable to other object-oriented languages, like C\# and Python.
 This is because these programming languages share many similarities regarding refactoring opportunities.
@@
 The design decisions for this tool are made on basis of data gathered from a large corpus of software systems together with our own experience and findings from literature.
-
-Sec.~\ref{chap:background} describes the background from literature that we used to conduct this study.
-Sec.~\ref{chap:clonedetection} presents our clone refactoring tool proposal.
-Sec.~\ref{chap:clonetypes} outlines challenges with clone type definitions and proposes solutions for them in a refactoring context.
-Sec.~\ref{chap:clonecontextexpl} outlines our analysis and measurements regarding the context of code clones.
-Sec.~\ref{chap:mergingdups} shows our measurements regarding the amount of clones that can be refactored through method extraction.
-Sec.~\ref{chap:threatstovalidity} shows the threats to validity of this study and Sec.~\ref{chap:conclusion} draws a conclusion based on our preliminary results.
 
@@
 We then assess their suitability for refactoring purposes.
-For \textbf{RQ2} we look into to what extent clones can be filtered based on their impact on the system design when refactored.
-We do this by both determining good thresholds for the clone detection and by assessing the design implications of applying refactorings to the code.
+For \textbf{RQ2} we look into what thresholds we should use to identify clones that, when refactored, improve the design of the system.
 \textbf{RQ3} is currently work in progress.
@@
 A survey by Roy et al.~\cite{roy2007survey} states definitions of important concepts in code clone research.
-For instance, ``clone pair''is defined as \textit{a set of two code portions/fragments which are identical or similar to each other}; ``clone class'' as \textit{the union of all clone pairs}; ``clone instance'' as a single code portion/fragment that is part of either a clone pair or clone class.
+For instance, ``clone pair'' is defined as \textit{a set of two code portions/fragments which are identical or similar to each other}; ``clone class'' as \textit{the union of all clone pairs}; ``clone instance'' as a single code portion/fragment that is part of either a clone pair or clone class.
 
@@
 \subsection{Clone types}
-In this chapter we display the differences between clone type 1-3 \cite{roy2007survey} and type 1R-3R as proposed in section \ref{sec:rtypes}.
+In this chapter we display the differences between clone type 1-3~\cite{roy2007survey} and type 1R-3R as proposed in section \ref{sec:rtypes}.
 When running our clone detection script over the corpus, we get the results displayed in Fig.~\ref{fig:typeres}.

### 2019-07-01 sattose/paper.tex
Going through the document

@@
 Regarding clone detection, there is a lot of variability in literature whether clone pairs or clone classes should be considered for detection.
-We focus on clone classes, because of the advantages for refactoring.
+We decided to focus on clone classes, because of the advantages for refactoring.
 Clone pairs do not provide a general overview of all entities containing the clones, with all their related issues and characteristics~\cite{fontana2012duplicated}.
@@
 
-Aries~\cite{higo2004aries, higo2008metric} focuses on the detection of refactorable clones.
+A tool named Aries~\cite{higo2004aries, higo2008metric} focuses on the detection of refactorable clones.
 They do this based on the relation between clone instances through inheritance, similar to Fontana et al.~\cite{fontana2012duplicated}.
-Aries also proposes a refactoring: if two clone classes are siblings of each other (share the same superclass), they propose to perform ``Extract method'' and ``Pull up method'' sequentially.
-This tool only proposes the refactoring, and does not provide help in the process of applying the refactoring.
+This tool only proposes a refactoring opportunity, and does not provide help in the process of applying the refactoring.
 
@@
 \section{Addressing problems with clone type definitions}\label{chap:clonetypes}
-For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings (see Sec.~\ref{chap:backgroundclonetypes} for these definitions) to increase the chance that we can refactor the clone while improving the design.
+For each of type 1-3 clones~\cite{roy2007survey} (further explain in Sec.~\ref{chap:backgroundclonetypes}) we list our solutions to their shortcomings to increase the chance that we can refactor the clone while improving the design.
 
 \section{Shortcomings of clone types}
-The clone definitions, as outlined in Sec.~\ref{chap:backgroundclonetypes}, allow reasoning about the duplication in a software system.
+Clone type 1-3~\cite{roy2007survey} allow reasoning about the duplication in a software system.
 Clones by these definitions can relatively easily and efficiently be detected.
-This has allowed for large scale analyses of duplication.
+This has allowed for large scale analyses of duplication~\cite{livieri2007very}.
 However, these clone type definitions have shortcomings which make the clones detected in correspondence with these definitions less valuable for (automated) refactoring purposes.
 
-In this section we discuss the shortcomings of the different clone type definitions which make them less suitable for (automated) refactoring.
+In this section we discuss the shortcomings of the different clone type definitions.
 Because of these shortcomings, clones found by these definitions are often found to require additional judgement whether they should and can be refactored.
@@
 
-When looking at refactoring, type 2 clones can be very difficult to refactor.
+When looking at refactoring, type 2 clones can be difficult to refactor.
 For instance if we have variability in types, the code can describe operations on two completely dissimilar types.
@@
 \subsection{Relations Between Clone Instances} \label{chap:relationsinstances}
-When merging code clones in object-oriented languages, it is very important to consider the inheritance relation between clone instances.
-This relation has a big impact on how a clone should be refactored.
+When merging code clones in object-oriented languages, it is important to consider the inheritance relation between clone instances. This relation has a big impact on how a clone should be refactored.
 

### 2019-07-01 sattose/paper.tex
Fixing the document

@@
 
-Type 1 clones are in most cases implemented as textual equality between code fragments (except for whitespace and comments).
+Type 1 clones are by most tools implemented as textual equality between code fragments (except for whitespace and comments).
 Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type.
@@
 
-Because of this, type 1 clones may not all be subject to refactoring.
+Because of this, not all type 1 clones may be subject to refactoring.
 In section \label{chap:type1rclones} we describe an alternate approach towards detecting type 1 clones, which results in only clones that can be refactored.
@@
 
-Looking at the example in Fig.~\ref{fig:type2}, we see an example of a type 2 clone that poses no harm to the design of the system.
+The example in Fig.~\ref{fig:type2} shows a type 2 clone that poses no harm to the design of the system.
 Both methods are, except for their matching structure, completely different in functionality.
@@
 For instance if we have variability in types, the code can describe operations on two completely dissimilar types.
-Type 2 clones do not differentiate between primitives and objects, which further undermines the usefulness of clones detected by this definition.
+Type 2 clones do not differentiate between primitives and referenced types, which further undermines the usefulness of clones detected by this definition.
 
@@
 Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold~\cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
-This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance)~\cite{lavoie2011automated}, token-level similarity~\cite{sajnani2016sourcerercc} of statement-level similarity~\cite{kamalpriya2017enhancing}.
+This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance)~\cite{lavoie2011automated}, token-level similarity~\cite{sajnani2016sourcerercc} or statement-level similarity~\cite{kamalpriya2017enhancing}.
 
@@
 
-\subsubsection{T1R clones} \label{sec:type1r}
+\subsubsection{Type 1R clones} \label{sec:type1r}
 To solve the issues identified in Sec.~\ref{sec:type1}, we introduce an alternative definition: cloned fragments have to be both textually \textit{and} functionally equal.
@@
 
-\subsubsection{T2R clones}\label{sec:type2r}
+\subsubsection{Type 2R clones}\label{sec:type2r}
 To solve the issues identifier in Sec.~\ref{sec:type2}, we introduce an alternative definition.
@@
 \begin{equation}\label{eq:type2r}
-\text{T2R}=\frac{\text{Different expressions}}{\text{Total tokens}}*100
+\text{T2R Variability}=\frac{\text{Different expressions}}{\text{Total tokens}}*100
 \end{equation}
 
-\subsubsection{T3R clones}\label{sec:type3r}
+\subsubsection{Type 3R clones}\label{sec:type3r}
 Type 3 clones allow any change in statements (added, removed and changed statements).
@@
 \begin{equation}\label{eq:type3r}
-\text{T3R Gap}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100
+\text{T3R Gap Size}=\frac{\text{Statements in gap}}{\text{Statements in clones}}*100
 \end{equation}
-$$Statements = \text{Statements in a code fragment}$$
-$$C_{gap} = \text{The gap between two clones}$$
-$$C_{above} = \text{The clone instance above the gap}$$
-$$C_{below} = \text{The clone instance below the gap}$$
 

### 2019-07-01 sattose/paper.tex
Finally, the document looks actually pretty neat

@@
 These definitions share similarities with the literature definitions, the number of each type corresponds with the clone type it is modeled after.
-The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).
+The ``R'' stands for refactoring-oriented.
 
@@
 
-We check functional equality of two fragments by checking the equality of the fully qualified identifier (FQI) for referenced types, methods and variables.
+We check functional equality of two fragments by comparing the equality of the fully qualified identifier (FQI) for referenced types, methods and variables.
 If an identifier is fully qualified, it means we specify the full location of its declaration (e.g.
@@
 For method calls, we also compare the equality of the FQI of the type of each of its arguments, to differentiate between overloaded method variants.
-This way we can check whether two identifiers are functionally equal.
 
@@
 
-T3R clones allow, different from T2R clones, a gap between two clone classes of statements that are not cloned. The following rules apply to this gap:
+All rules that apply to T2R clones also apply to T3R clones. Additionally, T3R clones allow a gap between two clone classes of statements that are not cloned. The following rules apply to this gap:
 
@@
 It is rather somewhere within, as it must bridge two existent clones.
-This holds the most value when looking at refactoring such clones.
-A difference at the beginning or end of a cloned block can better not be refactored.
   \item \textbf{The size of the gap between two clones is limited by a threshold.} This threshold is calculated by taking the percentage of the amount of statements in the gap over the amount of statements that both clones that are being bridged span.

### 2019-07-01 sattose/paper.tex
Magiel

@@
 Although clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered.
-Another issue that results from grouping clones by pairs: clone reference amount increases according to the binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), which causes a heavy information redundancy~\cite{fontana2012duplicated}.
+Another issue that results from grouping clones by pairs: the amount of clone references increases according to the binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), which causes a heavy information redundancy~\cite{fontana2012duplicated}.
 
@@
 The formula by which this threshold is calculated is displayed in equation \ref{eq:type2r}.
-In this formula, \textit{different expressions} refers to the amount of literals, variables and method calls that differ from other clone instances in a clone class.
+In this formula, \textit{different expressions} refers to the number of literals, variables and method calls that differ from other clone instances in a clone class.
 We divide this by the total number of tokens in the clone instance.
@@
 It is rather somewhere within, as it must bridge two existent clones.
-  \item \textbf{The size of the gap between two clones is limited by a threshold.} This threshold is calculated by taking the percentage of the amount of statements in the gap over the amount of statements that both clones that are being bridged span.
+  \item \textbf{The size of the gap between two clones is limited by a threshold.} This threshold is calculated by taking the percentage of the number of statements in the gap over the number of statements that both clones that are being bridged span.
 This is displayed in equation \ref{eq:type3r}.
@@
 
-To find such a threshold, we measured the amount of clone classes found for a certain number of tokens.
-We then looked at the amount of nodes (statements/declarations) that these clones span.
+To find such a threshold, we measured the number of clone classes found for a certain number of tokens.
+We then looked at the number of nodes (statements/declarations) that these clones span.
 The resulting chart is displayed in Fig.~\ref{fig:tokenthreshold}.
@@
 \begin{figure}[H]
-  \caption{Amount of times a clone with a certain amount of tokens has a certain amount of nodes.}
+  \caption{Amount of times a clone with a certain number of tokens has a certain number of nodes.}
     \includegraphics[width=1\columnwidth]{img/TokenThreshold}
@@
 
-In this figure the amount cloned statements per clone type are displayed.
+In this figure the number of cloned statements per clone type are displayed.
 The difference between T1R and T1 is small (10.9\%), because most often textually equal code is also functionally equal.
@@
 Our results indicate that, quite significantly, most clones are found at method level.
-The amount of clones found in interfaces and enumerations is very low.
+The number of clones found in interfaces and enumerations is very low.
 
@@
 
-We measured the amount of clones that can be refactored through method extraction (without additional transformations being required).
+We measured the number of clones that can be refactored through method extraction (without additional transformations being required).
 Our results are displayed in Table \ref{table:refactorability}.

### 2019-07-01 sattose/paper.tex
More goodness

@@
 Our intermediate results indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
-Almost fourty percent of the duplication can be refactored through method extraction, while other clones require other refactoring techniques or further transformations.
+Almost 40 percent of the duplication can be refactored through method extraction, while other clones require other refactoring techniques or further transformations.
 Future measurements will provide further insight into what clones should be refactored to improve the design of software systems.
@@
 However, these tools were not yet assessed in terms of automatically refactoring clones.
-
 In this section, we first assess a set of modern clone detection tools for their applicability to this domain.
@@
 \subsection{CloneRefactor}
-None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}.
-This repository contains all scripts that were used to retrieve the data that is displayed in this paper.}.
+None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
 In this tool, we implemented both the literature clone types~\cite{roy2007survey} and our refactoring-oriented clone types as described in Sec.~\ref{sec:rtypes}.
+%An abstract view of the process flow of CloneRefactor is displayed in figure \ref{fig:clonerefactor}
+
+%\begin{figure}[H]
+%  \caption{Abstract representation of CloneRefactor.}
+%    \includegraphics[width=1\columnwidth]{img/CloneRefactorOverall}
+%  \label{fig:clonerefactor}
+%\end{figure}
 

### 2019-07-01 sattose/paper.tex
Working on image stuff

@@
 This section outlines the conducted experiments to determine refactoring opportunities for code clones.
-First, we look into the thresholds that determine whether duplicated fragments are considered a clone in section \ref{chap:thresholds}.
-Next, we show the corpus on which we have performed our measurements in section \ref{chap:corpus}.
-We then perform an analysis on the context of code clones in section \ref{chap:clonecontextexpl}.
+We show the corpus on which we have performed our measurements in section \ref{chap:corpus}.
+Next, we look into the thresholds that determine whether duplicated fragments are considered a clone in section \ref{chap:thresholds}.
+We then show a comparison between the different proposed clone types in section \ref{sec:clonetypeexperiments}.
+Afterwards, we perform an analysis on the context of code clones in section \ref{chap:clonecontextexpl}.
 Finally, we map refactoring opportunities for clones in section \ref{chap:mergingdups}.
+
+All experiments were conducted using CloneRefactor, which contains scripts for running large scale clone detection over the indicated corpus.
 
@@
 This corpus has been assembled to contain relatively higher quality projects.
-Also, any duplicate projects were removed from this corpus.
+Also, any duplicate projects and files were removed from this corpus.
 This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
 We filtered this corpus further to only include projects that use Maven, which is a build tool which is mainly used to manage dependencies in the Java ecosystem.
-We then filtered the corpus further to only include projects for which all external dependencies are available.
+We then filtered the corpus further to only include projects for which all external dependencies are available, as CloneRefactor requires all dependencies of a project in order to accurately resolve all its symbols.
 This resulted in 1.343 projects of varying sizes averaging at 980 source lines of code (omitting whitespace, comments) per project.
@@
 
-\subsection{Clone types}
+\subsection{Clone types}\label{sec:clonetypeexperiments}
 In this chapter we display the differences between clone type 1-3~\cite{roy2007survey} and type 1R-3R as proposed in section \ref{sec:rtypes}.
@@
   \caption{Number of cloned declarations/statements.}
-    \includegraphics[width=.96\columnwidth]{img/TypeResults}
+    \includegraphics[width=1\columnwidth]{img/TypeResults}
   \label{fig:typeres}
@@
   \caption{Duration in minutes of identifying clones for clone type definitions.}
-    \includegraphics[width=.96\columnwidth]{img/DurationChart}
+    \includegraphics[width=1\columnwidth]{img/DurationChart}
   \label{fig:performance}
@@
 
-\subsection{Relations Between Clone Instances} \label{chap:relationsinstances}
+\subsubsection{Relations Between Clone Instances} \label{chap:relationsinstances}
 When merging code clones in object-oriented languages, it is important to consider the inheritance relation between clone instances. This relation has a big impact on how a clone should be refactored.
 
-\subsubsection{Categorizing Clone Instance Relations}\label{chap:catcloneinstancerelations}
 Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other.

### 2019-07-01 sattose/paper.tex
Yet better graphicz
Bit of layout considerations
Getting there...

@@
   \caption{Amount of times a clone with a certain number of tokens has a certain number of nodes.}
-    \includegraphics[width=1\columnwidth]{img/TokenThreshold}
+    \includegraphics[width=.95\columnwidth]{img/TokenThreshold}
   \label{fig:tokenthreshold}
@@
   \caption{Number of cloned declarations/statements.}
-    \includegraphics[width=1\columnwidth]{img/TypeResults}
+    \includegraphics[width=.9\columnwidth]{img/TypeResults}
   \label{fig:typeres}
@@
 
-In this figure the number of cloned statements per clone type are displayed.
+In this figure the number of cloned nodes per clone type are displayed.
 The difference between T1R and T1 is small (10.9\%), because most often textually equal code is also functionally equal.
@@
 Fig.~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types.
-Although this data is dependent on the implementation, there is a notable difference between the refactoring-oriented clone types and the literature clone types.
-Most of the time that the refactoring-oriented clone types take longer is spent resolving symbols (to infer FQIs).
+Although this data is partly dependent on our implementation of the clone types, there is a notable difference between the refactoring-oriented clone types and the literature clone types.
+The reason for this is further explained in section \ref{chap:challenge}.
 
@@
   \caption{Duration in minutes of identifying clones for clone type definitions.}
-    \includegraphics[width=1\columnwidth]{img/DurationChart}
+    \includegraphics[width=.9\columnwidth]{img/DurationChart}
   \label{fig:performance}
@@
 Fig.~\ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
-The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
-The location and contents of clones is measured on clone instance level.
-A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50).
-A clone instance contents consists of a list of all statements and declarations it spans.
+The relation of clones through inheritance is measured for each clone class.
+The location and contents of clones are measured for each clone instance.
 
@@
 To do this, they first define several categories for the relation between clone instances in object-oriented languages.
-These categories are shown in Fig.~\ref{fig:clonerelation}.
 These categories are as follows:

### 2019-07-01 sattose/paper.tex
Let's keep cutting stuff anyway

@@
   \item \textbf{Same class}: All instances of the clone class are in the same class.
-  \item \textbf{Superclass}: All instances of the clone class are children and parents of each other.
+  \item \textbf{Superclass}: All instances of the clone class are child or parent of each other.
   \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
@@
   \item \textbf{First cousin class}: All instances of the clone class have the same grandparent class.
-\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same hierarchy, but do not belong to any of the other categories.
+\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same inheritance hierarchy, but do not belong to any of the other categories.
 \item \textbf{Same external superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
@@
 \begin{figure}[H]
-  \caption{Abstract figure displaying some relations of clone classes. Arrows represent superclass relations.}
+  \caption{Abstract figure displaying relations of clone classes. Arrows represent superclass relations.}
     \medskip
@@
 
-The most notable difference when comparing it to the results of Fontana et al.~\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (34.44), while for them it was only 15.70\%.
+The most notable difference when comparing it to the results of Fontana et al.~\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (34.44\%), while for them it was only 15.70\%.
 This is likely due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
@@
 About a third of all clone classes have all instances in the same class, which is generally easy to refactor.
-On the third place come the clones that are in the same method, which are also easy to refactor.
+On the third place come the clones that are in the same method, which are similarly easy to refactor.
 
 \subsubsection{Clone instance location}\label{chap:clonelocation}
-After mapping the relations between individual clones, we looked at the location of individual clone instances.
+After mapping the relations between individual clones, we considered at the location of individual clone instances.
 A paper by Lozano et al.~\cite{lozano2007evaluating} discusses the harmfulness of cloning.
@@
 However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
-We validated this claim over our corpus.
-We use the following categories:
+We validated this claim over our corpus, using the following categories:
 \begin{enumerate}
@@
   \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class (like field declarations, other methods, etc.).
-  \item \textbf{Interface Level:} A clone that is (a part of) an interface.
-  \item \textbf{Enumeration Level:} A clone that is (a part of) an enumeration.
+  \item \textbf{Interface/Enumeration Level:} A clone that is (a part of) an interface or enumeration.
 \end{enumerate}
@@
   \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
-  \item \textbf{Other:} Anything that does not match with above-stated categories.
 \end{enumerate}

### 2019-07-01 sattose/paper.tex
Getting there I hope...

@@
 \subsubsection{Clone instance contents}\label{chap:clonecontents}
-Finally, we looked at the contents of individual clone instances: what kind of declarations and statements do they span. We selected the following categories to be relevant for refactoring:
+Finally, we looked at the contents of individual clone instances: what combination of declarations and statements they span. We selected the following categories to be relevant for refactoring:
 \begin{enumerate}
   \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
-  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially, optionally including its declaration.
-  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
+  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially.
+  \item \textbf{Several Methods:} A clone that spans over two or more methods and/or method bodies.
   \item \textbf{Only Fields:} A clone that spans only global variables.
-  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields and other things, like methods.
+  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields/constructors and other things.
   \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
@@
 There does not seem to be one golden set of thresholds, some thresholds work in some situations but fail in others.
-We have chosen thresholds that, according to our assessments, seemed optimal.
-However, by using these, we definitely miss some harmful clones.
+We have chosen thresholds that, according to our experiments and assessments, seemed optimal.
+However, by using these, we might have some ``noise'' in our results of clones that should not be considered for refactoring.
 
@@
 We have looked into existing definitions for different types of clones~\cite{roy2007survey} and proposed solutions for problems that these types have with regards to automated refactoring.
-We propose that FQIs of method call signatures and type references should be considered instead of their plain text representation, to ensure refactorability.
-Furthermore, we propose that one should define thresholds for variability in variables, literals and method calls, in order to limit the number of parameters that the refactored unit shall have.
+We propose that fully qualified identifiers (FQIs) of method call signatures and type references should be considered instead of their plain text representation, to ensure refactorability.
+Furthermore, we propose that one should define thresholds for variability in variables, literals and method calls, in order to limit the number of parameters that the refactored method will have.
 
@@
 Firstly, we looked at the inheritance relation of clone instances in a clone class.
-We have found that more than a third of all clone classes are flagged unrelated, which means that they have at least one instance that has no relation through inheritance with the other instances.
-For about a fourth of the clone classes all of its instances are in the same class.
-About a sixth of the clone classes have clone instances that are siblings of each other (share the same superclass).
+We have found that a little more than a third of all clone classes are flagged unrelated, which means that they have at least one instance that has no relation through inheritance with the other instances.
+About a third of the clone classes all of its instances are in the same class.
 
 Secondly, we looked at the location of clone instances.
-Most clone instances (58 percent) are found at method level.
-About 37 percent of clone instances were found at class level.
-We defined ``class level clones'' as clones that exceed the boundaries of a single method or contain something else in the class (like field declarations, other methods, etc.).
-Thirdly, we looked at the contents of clone instances.
-Most clones span a part of a method (57 percent).
-About 26 percent of clones span over several methods.
-
-We also looked into the refactorability of clones that span a part of a method.
-Over 10 percent of the clones can directly be refactored by extracting them to a new method (and calling the method at all usages using their relation).
-The main reason that most clones that span a part of a method cannot directly be refactored by method extraction, is that they contain \texttt{return}, \texttt{break} or \texttt{continue} statements.
+Most clone instances (79 percent) are found at method level.
+Because of that, we concluded that our main refactoring focus should be aimed at method-level clones.
+A common method to refactor such clones is by extracting a new method on basis of the contents of the clone.
+However, method extraction cannot be applied in all cases.
+According to our experiments, about 40 percent of the clones can be refactored by extracting them to a new method.
 
@@
 Our next step is to implement the ``Extract Method'' refactoring for the identified automatic refactoring opportunities.
-On basis of the resulting code, we can perform experiments comparing the maintainability index of the refactored code to the original code.
-On basis of these results, we can find better thresholds in order to determine thresholds.
-We can assess the impact of our work on code volume, complexity, etc.
-This helps to verify the usability of the proposed type definitions towards our goal of improving the quality of a software system.
+On basis of the resulting code, we can perform experiments that compare the maintainability index of the refactored code to the original code.
+The maintainability index of a system is an aggregation of various metrics that test a systems' maintainability (like volume, complexity, duplication, etc.).
+If we can automatically apply refactorings to the identified clones, this maintainability index can be used to select more optimal threshold values.
 

### 2019-07-01 sattose/paper.tex
:night_with_stars:

@@
   \item \textbf{Partial Method/Constructor:} A clone that spans a method partially.
-  \item \textbf{Several Methods:} A clone that spans over two or more methods and/or method bodies.
+  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially.
   \item \textbf{Only Fields:} A clone that spans only global variables.
-  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields/constructors and other things.
+  \item \textbf{Includes Fields/Constructor:} A clone that spans fields/constructors, but can also span other statements or declarations.
   \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.

### 2019-07-01 sattose/paper.tex
Spelling mainly

@@
 Duplication in source code can have a major negative impact on the maintainability of source code, as it creates implicit dependencies between fragments of code.
-Such implicit dependencies often cause bugs and increases maintenance efforts.
+Such implicit dependencies often cause bugs and increase maintenance efforts.
 In this study, we look into the opportunities to automatically refactor these duplication problems for object-oriented programming languages.
@@
 They do this based on the relation between clone instances through inheritance, similar to Fontana et al.~\cite{fontana2012duplicated}.
-This tool only proposes a refactoring opportunity, and does not provide help in the process of applying the refactoring.
+This tool only proposes a refactoring opportunity and does not provide help in the process of applying the refactoring.
 
@@
 
-In this section we discuss the shortcomings of the different clone type definitions.
-Because of these shortcomings, clones found by these definitions are often found to require additional judgement whether they should and can be refactored.
+In this section, we discuss the shortcomings of the different clone type definitions.
+Because of these shortcomings, clones found by these definitions are often found to require additional judgment whether they should and can be refactored.
 
@@
 Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type.
-In such cases refactoring opportunities could be invalidated.
+In such cases, refactoring opportunities could be invalidated.
 This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
-When aiming to automatically refactor clones, applying refactorings to clones which might refer to different methods, types and variables is bound to be error prone and result in a uncompilable project or a difference in functionality.
+When aiming to automatically refactor clones, applying refactorings to type 1 clones is bound to be error prone and can result in an uncompilable project or a difference in functionality.
 
 Because of this, not all type 1 clones may be subject to refactoring.
-In section \label{chap:type1rclones} we describe an alternate approach towards detecting type 1 clones, which results in only clones that can be refactored.
+In section \label{chap:type1rclones} we describe an alternative approach towards detecting type 1 clones, which results in only clones that can be refactored.
 
@@
 When looking at refactoring, type 2 clones can be difficult to refactor.
-For instance if we have variability in types, the code can describe operations on two completely dissimilar types.
-Type 2 clones do not differentiate between primitives and referenced types, which further undermines the usefulness of clones detected by this definition.
+For instance, if we have variability in types, the code can describe operations on two completely dissimilar types.
+Type 2 clones do not differentiate between primitives and reference types, which further undermines the usefulness of clones detected by this definition.
 
@@
 Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold~\cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
-This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance)~\cite{lavoie2011automated}, token-level similarity~\cite{sajnani2016sourcerercc} or statement-level similarity~\cite{kamalpriya2017enhancing}.
+This similarity threshold has been implemented in different ways: textual similarity (for instance using Levenshtein distance)~\cite{lavoie2011automated}, token-level similarity~\cite{sajnani2016sourcerercc} or statement-level similarity~\cite{kamalpriya2017enhancing}.
 
 Having a definition that allows for any change in code poses serious challenges on refactoring.
-A levenshtein distance of one can already change the meaning of a code fragment significantly, for instance if the name of a type differs by a character (and thus referring to different types).
+A Levenshtein distance of one can already change the meaning of a code fragment significantly, for instance, if the name of a type differs by a character (and thus referring to different types).
 
 \subsection{Refactoring-oriented clone types}\label{sec:rtypes}
-To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types to be directed at detecting clones that can and should be refactored.
+To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types directed at detecting clones that can and should be refactored.
 We have named these clones T1R (type 1R), T2R and T3R clones.
-These definitions share similarities with the literature definitions, the number of each type corresponds with the clone type it is modeled after.
+These definitions address problems of the corresponding literature definitions.
 The ``R'' stands for refactoring-oriented.
@@
 
-To limit the negative impact of this tradeoff on the design of the system, we formalized as threshold for the variability between fragments.
+To limit the negative impact of this tradeoff on the design of the system, we formalized a threshold for the variability between fragments.
 The formula by which this threshold is calculated is displayed in equation \ref{eq:type2r}.
@@
 This is displayed in equation \ref{eq:type3r}.
-  \item \textbf{The gap may not span a partial block.} To make sure that the T3R clone can be refactored, we do not allow the gap to span a part of a block, for instance the declaration and a part of the body of a for-loop.
+  \item \textbf{The gap may not span a partial block.} To make sure that the T3R clone can be refactored, we do not allow the gap to span a part of a block, for instance, the declaration and a part of the body of a for-loop.
 The reason for this is that it is not possible to wrap a partially spanned block in a single conditional statement.
-We could however use multiple conditional blocks (one for each block spanned), but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for T3R clones.
+We could, however, use multiple conditional blocks (one for each block spanned), but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for T3R clones.
 \end{itemize}
@@
 \subsubsection{The challenge of detecting these clones}\label{chap:challenge}
-To detect each type of clone, we need to parse the FQI of all types, method calls and variables.
+To detect each type of clone, we need to parse the FQI of all types, method calls, and variables.
 This comes with challenges, regarding both performance and implementation.
-To trace the declarations of variables, methods and types, we might need to follow cross file references.
+To trace the declarations of variables, methods, and types, we might need to follow cross-file references.
 The referenced types/variables/methods might even not be part of the project, but rather of an external library or the standard libraries of the programming language.
@@
     \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones.
-We want to perform an analysis on all clones in projects to get a complete overview.
+We want to perform an analysis of all clones in projects to get a complete overview.
 \item \textbf{Finds clone classes in control projects.} We assembled a number of control projects to assess the validity of clone detection tools.
 On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
-\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be merged.
+\item \textbf{Can analyze resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be merged.
 Sometimes, textual equality between code fragments does not imply that these can be merged (this is described more elaborately in Sec.~\ref{sec:type1}).
@@
 To achieve this, the tool needs to be able to allow those threshold changes.
-This can be either through simple changes of the source code, or by using some configuration file.
+This can be either through simple changes of the source code or by using some configuration file.
 \end{enumerate}

### 2019-07-01 sattose/paper.tex
Spelling n stuff

@@
 \begin{enumerate}
-    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones.
+    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method level clones.
 We want to perform an analysis of all clones in projects to get a complete overview.
@@
 Whether a node is considered a clone depends on the clone type that is being analyzed.
-On basis of this graph we detect clone classes.
-We compare clone classes against thresholds, and remove the clone classes that do not pass the test.
+On basis of this graph, we detect clone classes.
+We compare clone classes against thresholds and remove the clone classes that do not pass the test.
 
@@
 We then show a comparison between the different proposed clone types in section \ref{sec:clonetypeexperiments}.
-Afterwards, we perform an analysis on the context of code clones in section \ref{chap:clonecontextexpl}.
+Afterward, we perform an analysis of the context of code clones in section \ref{chap:clonecontextexpl}.
 Finally, we map refactoring opportunities for clones in section \ref{chap:mergingdups}.
@@
 \subsection{The corpus}\label{chap:corpus}
-For our experiments we use a large corpus of open source projects~\cite{githubCorpus2013}.
+For our experiments, we use a large corpus of open source projects~\cite{githubCorpus2013}.
 This corpus has been assembled to contain relatively higher quality projects.
@@
 A comparison of clone detection tools by Bellon et al.~\cite{bellon2007comparison} shows that most clone detection tools choose a minimum of \textbf{6} lines of code to be duplicate to consider code fragments a clone.
-The Scorpio clone detection tool uses this same number as minimum number of nodes~\cite{higo2013revisiting}.
-Token based tools mostly operate on basis of a minimum of \textbf{50} tokens for fragments to be considered a clone~\cite{sajnani2016sourcerercc}.
+The Scorpio clone detection tool uses this same number as minimum the number of nodes~\cite{higo2013revisiting}.
+Many token based tools use a threshold of \textbf{50} tokens for fragments to be considered a clone~\cite{sajnani2016sourcerercc}.
 
 We would argue that going with this ``magic number 6'' eliminates a lot of harmful clones that should be refactored.
-For instance, a single 100-token statement will not be considered by such a threshold, which can still be harmful for the system design when cloned.
+For instance, a single 100-token statement will not be considered by such a threshold, which can still be harmful to the system design when cloned.
 Because of that, we decided to perform our measurements using thresholds that will include most clones that should be refactored, while eliminating most of the noise.
@@
 
-In this chart we see that when seeking clones with a minimum of 10 tokens, there are more clones that span 2 statements than clones that span one statement.
+In this chart, we see that when seeking clones with a minimum of 10 tokens, there are more clones that span 2 statements than clones that span one statement.
 We manually assessed these clones, and mainly the two-statement clones contain many clones that we classified as ``should be refactored''.
@@
 
-In this figure the number of cloned nodes per clone type are displayed.
+In this figure, the number of cloned nodes per clone type are displayed.
 The difference between T1R and T1 is small (10.9\%), because most often textually equal code is also functionally equal.
-The difference between T2R and T2 is bigger (34.7\%), mainly because we allow no variability in used types.
-T3R and T3 are similar to T2R and T2, because our dataset does not have so many gapped clones for the thresholds used.
+The difference between T2R and T2 is bigger (34.7\%) because the T2R definition is more strict.
+T3R and T3 are similar to T2R and T2 because our dataset does not have so many gapped clones for the thresholds used.
 
@@
 \begin{enumerate}
-  \item The relation of clone instances among each other through inheritance (for example: a clone instance resides in a superclass of another clone instance in the same clone class).
-  \item Where a clone instance occurs in the code (for example: a method-level clone is a clone instance that is in a method).
-  \item The contents of a clone instance (for example: the clone instance spans several methods).
+  \item \textbf{Relation:} The relation of clone instances among each other through inheritance.
+  \item \textbf{Location:} Where a clone instance occurs in the code.
+  \item \textbf{Contents:} The statements/declarations of a clone instance.
 \end{enumerate}
+We perform experiments on each of these aspects, defining categories and measuring these categories over the corpus.
 
@@
 A paper by Lozano et al.~\cite{lozano2007evaluating} discusses the harmfulness of cloning.
-The authors argue that 98\% are produced at method-level.
+The authors argue that 98\% are produced at method level.
 However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
@@
 The results are shown in Table~\ref{table:locations}.
-Our results indicate that, quite significantly, most clones are found at method level.
+Our results indicate that, quite significantly, most clones are found at methodlevel.
 The number of clones found in interfaces and enumerations is very low.
@@
 We propose that fully qualified identifiers (FQIs) of method call signatures and type references should be considered instead of their plain text representation, to ensure refactorability.
-Furthermore, we propose that one should define thresholds for variability in variables, literals and method calls, in order to limit the number of parameters that the refactored method will have.
+Furthermore, we propose that one should define a threshold for variability in variables, literals, and method calls, in order to limit the number of parameters that the refactored method will have.
 
@@
 Most clone instances (79 percent) are found at method level.
-Because of that, we concluded that our main refactoring focus should be aimed at method-level clones.
+Because of that, we concluded that our main refactoring focus should be aimed at method level clones.
 A common method to refactor such clones is by extracting a new method on basis of the contents of the clone.

### 2019-07-02 sattose/paper.tex
Magiel paper

@@
 In Martin Fowler's ``Refactoring'' book~\cite{fowler1999refactoring}, he claims that \textit{``If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
+A paper by Bruntink et al.~\cite{bruntink2005use} shows that code clones can contribute up to 25\% of the code size, which has a negative impact on the maintainability.
 % In this research, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
@@
 
-Code clones can be found anywhere in a codebase.
-The location of a clone in the code has an impact on how it can be refactored.
-Therefore, we first look at where and how often clones are found, enabling the prioritization of refactoring opportunities.
-
 We focus mainly on the Java programming language as refactoring opportunities feature paradigm and programming language dependent aspects~\cite{choi2011extracting}.
@@
 
-Our end goal is to improve upon the current state-of-the-art in clone research~\cite{fontana2015duplicated, alwaqfi2017refactoring} by building a clone refactoring tool that automatically applies refactorings to a large percentage of clones found.
+Our end goal is to improve upon the current state-of-the-art in clone research~\cite{fontana2015duplicated, alwaqfi2017refactoring} by building a clone refactoring tool that can analyze the context of code clones to get a profile of how a clone can be refactored.
+This tool then automatically applies refactorings to a large percentage of clones found.
 The design decisions for this tool are made on basis of data gathered from a large corpus of software systems together with our own experience and findings from literature.
@@
 
-For \textbf{RQ1} we look into current clone definitions and clone detection methods.
-We then assess their suitability for refactoring purposes.
+For \textbf{RQ1} we look into current clone definitions and clone detection methods and assess their suitability for refactoring purposes.
 For \textbf{RQ2} we look into what thresholds we should use to identify clones that, when refactored, improve the design of the system.

### 2019-07-02 sattose/paper.tex
Addressing more feedback

@@
 \item \textbf{Finds clone classes in control projects.} We assembled a number of control projects to assess the validity of clone detection tools.
-On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
-\item \textbf{Can analyze resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be merged.
-Sometimes, textual equality between code fragments does not imply that these can be merged (this is described more elaborately in Sec.~\ref{sec:type1}).
-Because of this, we want to use a clone detection tool that can analyze such structures.
-\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}).
+\item \textbf{Can analyze resolved symbols.} When detecting the types proposed in section \ref{sec:rtypes}, it is important that we can analyze FQIs of symbols.
+The rationale for this is further explained in \ref{chap:challenge}.
+\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{sec:rtypes}).
 To achieve this, the tool needs to be able to allow those threshold changes.
@@
 \end{table}
+
+Apart from these criteria, we found that the output of these clone detection tools cannot be post-processed to find the clone types proposed in section \ref{sec:rtypes}.
+This is mainly because the clones of T2R are not a subset of type 2 clones and will thus require an analysis of the entire system.
 

### 2019-07-02 sattose/paper.tex
Fixed a bit of stuff here and there

@@
 To limit the negative impact of this tradeoff on the design of the system, we formalized a threshold for the variability between fragments.
-The formula by which this threshold is calculated is displayed in equation \ref{eq:type2r}.
+The formula by which this threshold is calculated is displayed in equation~\ref{eq:type2r}.
 In this formula, \textit{different expressions} refers to the number of literals, variables and method calls that differ from other clone instances in a clone class.
@@
   \item \textbf{The size of the gap between two clones is limited by a threshold.} This threshold is calculated by taking the percentage of the number of statements in the gap over the number of statements that both clones that are being bridged span.
-This is displayed in equation \ref{eq:type3r}.
+This is displayed in equation~\ref{eq:type3r}.
   \item \textbf{The gap may not span a partial block.} To make sure that the T3R clone can be refactored, we do not allow the gap to span a part of a block, for instance, the declaration and a part of the body of a for-loop.
@@
 \item \textbf{Finds clone classes in control projects.} We assembled a number of control projects to assess the validity of clone detection tools.
-\item \textbf{Can analyze resolved symbols.} When detecting the types proposed in section \ref{sec:rtypes}, it is important that we can analyze FQIs of symbols.
-The rationale for this is further explained in \ref{chap:challenge}.
-\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{sec:rtypes}).
-To achieve this, the tool needs to be able to allow those threshold changes.
-This can be either through simple changes of the source code or by using some configuration file.
+\item \textbf{Can analyze resolved symbols.} When detecting the types proposed in Sec.~\ref{sec:rtypes}, it is important that we can analyze resolved symbols (for instance a type reference).
+The rationale for this is further explained in~\ref{chap:challenge}.
+\item \textbf{Extensive detection configuration.} Detecting our clone definitions, as proposed in Sec.~\ref{sec:rtypes}, require to have some understanding about the meaning of tokens in the source code (whether a certain token is a type, variable, etc.).
+The tool should recognize such structures, in order for us to configure our clone type definitions in the tool.
 \end{enumerate}
@@
 
-Apart from these criteria, we found that the output of these clone detection tools cannot be post-processed to find the clone types proposed in section \ref{sec:rtypes}.
+Apart from these criteria, we found that the output of these clone detection tools cannot be post-processed to find the clone types proposed in Sec.
+\ref{sec:rtypes}.
 This is mainly because the clones of T2R are not a subset of type 2 clones and will thus require an analysis of the entire system.
@@
 In this tool, we implemented both the literature clone types~\cite{roy2007survey} and our refactoring-oriented clone types as described in Sec.~\ref{sec:rtypes}.
-%An abstract view of the process flow of CloneRefactor is displayed in figure \ref{fig:clonerefactor}
+%An abstract view of the process flow of CloneRefactor is displayed in figure~\ref{fig:clonerefactor}
 
@@
 This section outlines the conducted experiments to determine refactoring opportunities for code clones.
-We show the corpus on which we have performed our measurements in section \ref{chap:corpus}.
-Next, we look into the thresholds that determine whether duplicated fragments are considered a clone in section \ref{chap:thresholds}.
-We then show a comparison between the different proposed clone types in section \ref{sec:clonetypeexperiments}.
-Afterward, we perform an analysis of the context of code clones in section \ref{chap:clonecontextexpl}.
-Finally, we map refactoring opportunities for clones in section \ref{chap:mergingdups}.
+We show the corpus on which we have performed our measurements in Sec.
+\ref{chap:corpus}.
+Next, we look into the thresholds that determine whether duplicated fragments are considered a clone in Sec.
+\ref{chap:thresholds}.
+We then show a comparison between the different proposed clone types in Sec.
+\ref{sec:clonetypeexperiments}.
+Afterward, we perform an analysis of the context of code clones in Sec.
+\ref{chap:clonecontextexpl}.
+Finally, we map refactoring opportunities for clones in Sec.
+\ref{chap:mergingdups}.
 
@@
 \subsection{Clone types}\label{sec:clonetypeexperiments}
-In this chapter we display the differences between clone type 1-3~\cite{roy2007survey} and type 1R-3R as proposed in section \ref{sec:rtypes}.
+In this chapter we display the differences between clone type 1-3~\cite{roy2007survey} and type 1R-3R as proposed in Sec.
+\ref{sec:rtypes}.
 When running our clone detection script over the corpus, we get the results displayed in Fig.~\ref{fig:typeres}.
@@
 Although this data is partly dependent on our implementation of the clone types, there is a notable difference between the refactoring-oriented clone types and the literature clone types.
-The reason for this is further explained in section \ref{chap:challenge}.
+The reason for this is further explained in Sec.
+\ref{chap:challenge}.
 
@@
 measure clones using their own tool (DCRA).
-As explained in section~\ref{ch:tool-overview}, we chose to implement our own tool, CloneRefactor.
+As explained in Sec.
+\ref{ch:tool-overview}, we chose to implement our own tool, CloneRefactor.
 Therefore, the setup for our measurements differs as follows from Fontana et al.:
@@
 use a set of 50 relatively large projects.
-We use the corpus as explained in \ref{chap:corpus}, which contains a diverse set of projects (diverse both in volume and code quality).
+We use the corpus as explained in~\ref{chap:corpus}, which contains a diverse set of projects (diverse both in volume and code quality).
 \end{itemize}
@@
 
-The results for these categories are displayed in Table \ref{table:contents}.
+The results for these categories are displayed in Table~\ref{table:contents}.
 
@@
 We measured the number of clones that can be refactored through method extraction (without additional transformations being required).
-Our results are displayed in Table \ref{table:refactorability}.
+Our results are displayed in Table~\ref{table:refactorability}.
 In this table we use the following categories:
@@
     \item \textbf{Spans part of a block:} This clone spans a part of a statement.
-    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table \ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
+    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table~\ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
 \end{itemize}
@@
 
-From Table \ref{table:refactorability}, we can see that 38.22\% of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
+From Table~\ref{table:refactorability}, we can see that 38.22\% of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
 For the other clones, other techniques or transformations will be required.

### 2019-07-03 sattose/paper.tex
PDF figures
All charts pdf now
Ana

@@
 In Martin Fowler's ``Refactoring'' book~\cite{fowler1999refactoring}, he claims that \textit{``If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
-A paper by Bruntink et al.~\cite{bruntink2005use} shows that code clones can contribute up to 25\% of the code size, which has a negative impact on the maintainability.
+Bruntink et al.~\cite{bruntink2005use} show that code clones can contribute up to 25\% of the code size, which has a negative impact on the maintainability.
 % In this research, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
@@
   \caption{Amount of times a clone with a certain number of tokens has a certain number of nodes.}
-    \includegraphics[width=.95\columnwidth]{img/TokenThreshold}
+    \includegraphics[width=1\columnwidth]{img/TokenThreshold}
   \label{fig:tokenthreshold}
@@
   \caption{Number of cloned declarations/statements.}
-    \includegraphics[width=.9\columnwidth]{img/TypeResults}
+    \includegraphics[width=1\columnwidth]{img/TypeResults}
   \label{fig:typeres}
@@
   \caption{Duration in minutes of identifying clones for clone type definitions.}
-    \includegraphics[width=.9\columnwidth]{img/DurationChart}
+    \includegraphics[width=1\columnwidth]{img/DurationChart}
   \label{fig:performance}

### 2019-07-04 sections/research.tex
Moving some stuff back and forth

@@
 \section{Shortcomings of clone types}
-The clone definitions, as outlined in section \ref{chap:backgroundclonetypes}, allow reasoning about the duplication in a software system.
+Clone type 1-3 (further explain in section \ref{chap:backgroundclonetypes}) allow reasoning about the duplication in a software system.
 Clones by these definitions can relatively easily and efficiently be detected.
-This has allowed for large scale analyses of duplication.
+This has allowed for large scale analyses of duplication~\cite{livieri2007very}.
 However, these clone type definitions have shortcomings which makes the clones detected in correspondence with these definitions less valuable for (automated) refactoring purposes.
 
-In this section we discuss the shortcomings of the different clone type definitions which make them less suitable for (automated) refactoring.
-Because of that, these clones require more judgement whether they should and can be refactored.
+In this section, we discuss the shortcomings of the different clone type definitions.
+Because of these shortcomings, clones found by these definitions are often found to require additional judgment whether they should and can be refactored.
 

### 2019-07-04 sattose/paper.tex
Made this segment clearer

@@
 
-Type 1 clones are by most tools implemented as textual equality between code fragments (except for whitespace and comments).
+Type 1 clones are by most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating} implemented as textual equality between code fragments (except for whitespace and comments).
 Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type.

### 2019-07-04 sections/research.tex
Improved type 1 clones shortcomings section

@@
 
-Type 1 clones are in most cases implemented as textual equality between code fragments (except for whitespace and comments).
+Type 1 clones are by most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating} implemented as textual equality between code fragments (except for whitespace and comments).
 Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type.
-In such cases refactoring opportunities could be invalidated.
-An example of such a case is displayed in figure \ref{fig:type1}.
+In such cases, refactoring opportunities could be invalidated.
+This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
+When aiming to automatically refactor clones, applying refactorings to type 1 clones is bound to be error prone and can result in an uncompilable project or a difference in functionality.
 
@@
   \includegraphics[width=1\columnwidth]{img/type1}
-  \caption{Example of a type 1 clone.}
+  \caption{Example of a type 1 clone that is functionally different.}
   \label{fig:type1}
@@
 Because of this, it is hard to verify which of the used types have the same underlying implementation.
-This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
-When aiming to automatically refactor clones, applying refactorings to clones as shown in figure \ref{fig:type1}, is bound to be error prone and result in a uncompilable project or a difference in functionality.
 

### 2019-07-04 sections/research.tex
Formatting
Type 2 shortcomings

@@
 \subsection{Type 2 clones}\label{sec:type2}
-  Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}.
+Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments}~\cite{roy2007survey}.
 This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified.
-The two methods displayed in figure \ref{fig:type2} are type 2 clones of each other.
+However, the definition does not adequately differentiate between slight modification and completely different fragments that just happen to have the same structure.
+
+For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
+This could render two methods that have an entirely different functionality as clones.
+Merging such clones can be harmful instead of helpful.
 
@@
 
-Looking at the example in figure \ref{fig:type2}, we see an example of a type 2 clone that poses no harm to the design of the system.
+The example in Fig.~\ref{fig:type2} shows a type 2 clone that poses no harm to the design of the system.
 Both methods are, except for their matching structure, completely different in functionality.
@@
 
-When looking at refactoring, type 2 clones can be very difficult to refactor.
-For instance if we have variability in types, the code can describe operations on two completely dissimilar types.
-Type 2 clones do not differentiate between primitives and objects, which makes the these clones often not so useful for refactoring purposes.
+When looking at refactoring, type 2 clones can be difficult to refactor.
+For instance, if we have variability in types, the code can describe operations on two completely dissimilar types.
+Type 2 clones do not differentiate between primitives and reference types, which further undermines the usefulness of clones detected by this definition.
 

### 2019-07-04 sections/research.tex
Type 3 shortcomings

@@
 \subsection{Type 3 clones}\label{sec:type3}
-Type 3 clones are \textit{copied fragments with further modifications.
-Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}.
-Detection of clones by this definition can be very hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed.
-Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold \cite{svajlenko2014evaluating, cordy2011nicad}.
-This similarity threshold has been implemented in different ways: textual similarity (for instance using levenshtein distance) \cite{lavoie2011automated}, token-level similarity of statement-level similarity.
+Type 3 clones are \textit{copied fragments with further modification (with added, removed or changed statements)}~\cite{roy2007survey}.
+Detection of clones by this definition can be hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed.
+Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold~\cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
+This similarity threshold has been implemented in different ways: textual similarity (for instance using Levenshtein distance)~\cite{lavoie2011automated}, token-level similarity~\cite{sajnani2016sourcerercc} or statement-level similarity~\cite{kamalpriya2017enhancing}.
 
 Having a definition that allows for any change in code poses serious challenges on refactoring.
-A levenshtein distance of one can already change the meaning of a code fragment significantly, for instance if the name of a type differs by a character (and thus referring to different types).
+A Levenshtein distance of one can already change the meaning of a code fragment significantly, for instance, if the name of a type differs by a character (and thus referring to different types).
 

### 2019-07-04 sections/research.tex
Type 1R

@@
 \section{Refactoring-oriented clone types}
-To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types to be directed at detecting clones that can and should be refactored.
-We have named these clones type 1R, 2R and 3R clones.
-These definitions share similarities with the literature definitions, the number of each type corresponds with the clone type it is modeled after.
-The ``R'' stands for refactoring-oriented (and may be less suitable for other analyses).
+To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types directed at detecting clones that can and should be refactored.
+We have named these clones T1R (type 1R), T2R and T3R clones.
+These definitions address problems of the corresponding literature definitions.
+The ``R'' stands for refactoring-oriented (and may be less useful for other analyses).
 
 \subsection{Type 1R clones} \label{sec:type1r}
-We propose an alternative definition of type 1 clones.
-This definition requires cloned fragments to be not just textually equal, but also functionally equal.
-Although requiring fragments to be functionally equal, type 1R clones do not allow for change in implementation (like type 4 clones).
-We check functional equality of two fragments by validating the equality of the fully qualified identifier for referenced types, methods and variables.
-Type 1R clones are a subset of type 1 clones.
+To solve the issues identified in Sec.~\ref{sec:type1}, we introduce an alternative definition: cloned fragments have to be both textually \textit{and} functionally equal.
+Therefore, T1R clones are a subset of type 1 clones.
+
+We check functional equality of two fragments by validating the equality of the fully qualified identifier (FQI) for referenced types, methods and variables.
+If an identifier is fully qualified, it means we specify the full location of its declaration (e.g.
+\texttt{com.sb.fruit.Apple} for an \texttt{Apple} object).
 
@@
 However, importing \texttt{java.awt.List}, we get a listbox GUI component for the Java Abstract Window Toolkit (AWT).
-Because of this, for type 1R clones, we compare the fully qualified identifier for all referenced types.
+To be sure we compare between equal types, type 1R clones compare the FQI for all referenced types.
 

### 2019-07-04 sattose/paper.tex
New measurements for refactorability

@@
 Our intermediate results indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way.
-Almost 40 percent of the duplication can be refactored through method extraction, while other clones require other refactoring techniques or further transformations.
+About 40 percent of the duplication can be refactored through method extraction, while other clones require other refactoring techniques or further transformations.
 Future measurements will provide further insight into what clones should be refactored to improve the design of software systems.
@@
 \textbf{}         & \textbf{\#} & \textbf{\%} \\ \hline
-Can be extracted     & 13,553 & 38.22 \\ \hline
-Spans part of a block  & 12,332 & 34.78 \\ \hline
+Can be extracted     & 14,664 & 41.35 \\ \hline
+Spans part of a block  & 10,801 & 30.46 \\ \hline
 Is not a partial method   & 8,074 & 22.77 \\ \hline
-Complex control flow & 1,503 & 4.24 \\ \hline
+Complex control flow & 1,922 & 5.42 \\ \hline
 \end{tabular}
@@
 
-From Table~\ref{table:refactorability}, we can see that 38.22\% of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
+From Table~\ref{table:refactorability}, we can see that 41\% of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
 For the other clones, other techniques or transformations will be required.

### 2019-07-04 code_examples/GameOverScene.java
New example for type 1 not cloned

@@ -1,29 +1,16 @@
-package com.simonbaars.fruitcollector;
+package com.sb.fruitgame;
 
-import com.simonbaars.fruitcollector.fruits.rotten.Apple;
-import com.simonbaars.fruitcollector.images.losing.*;
+import com.sb.fruitgame.rotten.Apple;
 
-import com.musiclibrary.music.lowvolume.*;
-
-public class GameOverScene extends GameScene
+public class LoseScene extends Scene
 {
-	protected final Player player;
-
-	public GameOverScene(Player player)
-	{
-		super(player);
+	public void collect(Apple apple) {
+		apple.setStatus(this);
 	}
 
-	public String checkAppleCollected(Apple collectedApple) 
-	{
-		if(player.inventory.contains(collectedApple)){
-			showImage(new PNGImage());
-		}
-		playSong(new MusicPlayer());
-	}
-
-	@Override
-	public void playSong(MusicPlayer musicPlayer){
-		musicPlayer.playSong("theme.mp3");
+	public void concatTen(String x) {
+		x = x + 10;
+		notifyChanged(x);
+		return x;
 	}
 }

### 2019-07-04 code_examples/GameWinningScene.java

@@ -1,29 +1,16 @@
-package com.simonbaars.fruitcollector;
+package com.sb.fruitgame;
 
-import com.simonbaars.fruitcollector.fruits.winning.Apple;
-import com.simonbaars.fruitcollector.images.winning.*;
+import com.sb.fruitgame.Apple;
 
-import com.musiclibrary.music.highvolume.*;
-
-public class GameWinningScene extends GameScene
+public class GameScene extends Scene
 {
-	protected final Player player;
-
-	public GameScene(Player player)
-	{
-		this.player = player;
+	public void collect(Apple apple) {
+		apple.setStatus(this);
 	}
 
-	public String checkAppleCollected(Apple collectedApple) 
-	{
-		if(player.inventory.contains(collectedApple)){
-			showImage(new PNGImage());
-		}
-		playSong(new MusicPlayer());
-	}
-
-	@Override
-	public void playSong(MusicPlayer musicPlayer){
-		musicPlayer.playSong("theme.mp3");
+	public void addTen(int x) {
+		x = x + 10;
+		notifyChanged(x);
+		return x;
 	}
 }

### 2019-07-15 sections/research.tex
AST Filtering

@@
 
+\paragraph{Filtering the AST}
+As a first step towards building the clone graph, we preprocess the AST to decide which AST nodes should become part of the clone graph. We filter the following types of nodes:
+\begin{itemize}
+  \item \textbf{Expressions: }The smallest entity in the clone graph is a Statement. Because of that, we filter out all expressions.
+  \item \textbf{Package declaration and import statements: }These are omitted by most clone detection tools, as clones in import statements hold limited valuable information.
+  \item \textbf{Modifiers: }The clone graphs' nodes consist of only declarations and statements. Modifiers are part of the declarations, so they are not considered separately.
+\end{itemize}
+
+\paragraph{Building the clone graph}
 Building the clone graph consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:

### 2019-07-15 sections/research.tex
Rewrote filtering AST

--- 2019-07-04 sections/research.tex
@@
 
+\paragraph{Filtering the AST}
+As a first step towards building the clone graph, we preprocess the AST to decide which AST nodes should become part of the clone graph.
+We have decided to consider declarations and statements as the smallest compared entities.
+The main reasoning for this is because considering smaller AST constructs, like expressions, significantly increases the complexity and CPU usage of our clone detection and refactoring efforts.
+
+Additionally, we exclude package declarations and import statements. These are omitted by most clone detection tools, as clones in import statements hold limited valuable information.
+
+\paragraph{Building the clone graph}
 Building the clone graph consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:

### 2019-07-15 code_examples/ast_example.java

@@ -1,0 +1,3 @@
+if(doSomething){
+  doSomething();
+}

### 2019-07-15 sections/research.tex
Mapping graph nodes to code

@@
 
-\paragraph{Building the clone graph}
+\paragraph{Building the clone graph}\label{sec:buildingclonegraph}
 Building the clone graph consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
@@
 
-\subsubsection{Detecting Clones} \label{sec:detectingclones}
-After building the clone clone graph, we use it to detect clones.
-We decided to focus on the detection of clone classes rather than clone pairs because clone pairs do not provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}.
-Although clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered.
-Another issue that results from grouping clones by pairs: clone reference amount increases according to the binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), which causes a heavy information redundancy \cite{fontana2012duplicated}.
-
-As stated in the previous section, nodes in the graph link to \textit{preceding} cloned statement.
-This implies that the first node that is cloned does not have any clone relation, as there are no clones preceding it (only following it).
-Because of this, we start our clone detection process at the final location encountered while building the graph.
-For this node, we collect all nodes it is cloned with.
-Even though the final node only links to the preceding node it is cloned with, we can collect all clones.
-This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node.
-As an example, see figure \ref{fig:clonegraph} and \label{fig:clonegraph2}.
+\subsubsection{Mapping graph nodes to code}
+The clone graph, as explained in section \ref{sec:buildingclonegraph}, contains all declarations and statements in a source code.
+However, declarations and statements may themselves have child declarations and statements.
+To avoid redundant duplication checks, we exclude child declarations and statements from each node.
+Look at figure \ref{fig:clonegraph} for an example of how source code maps to AST nodes.
 

### 2019-07-15 sections/research.tex
Detecting clones

--- 2019-07-15 sections/research.tex
@@
 
+\subsubsection{Mapping graph nodes to code}
+The clone graph, as explained in section \ref{sec:buildingclonegraph}, contains all declarations and statements in a source code.
+However, declarations and statements may themselves have child declarations and statements.
+To avoid redundant duplication checks, we exclude child declarations and statements from each node.
+Look at figure \ref{fig:clonegraph} for an example of how source code maps to AST nodes.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{img/CloneGraphCode}
+  \caption{CloneRefactor extracts statements and declarations from source code.}
+  \label{fig:clonegraph}
+\end{figure}
+
 \subsubsection{Detecting Clones} \label{sec:detectingclones}
@@
 This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node.
-As an example, see figure \ref{fig:clonegraph} and \label{fig:clonegraph2}.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/CloneGraphCode}
-  \caption{CloneRefactor extracts statements and declarations from source code.}
-  \label{fig:clonegraph}
-\end{figure}
+As an example, we convert the code example shown in figure \ref{fig:clonegraph} to a clone graph as displayed in figure \label{fig:clonegraph2}.
 
@@
 
-Using the example shown in figure \ref{fig:clonegraph} and \label{fig:clonegraph2} we can explain how we detect clones.
+Using the example shown in figure \ref{fig:clonegraph} and \label{fig:clonegraph2} we can explain how we detect clones on basis of this graph.
 Suppose we are finding clones for two files and the final node of the second file is a variable declarator.

### 2019-07-15 sections/research.tex
Explain it well

@@
 
+In line 24-25 of the code fragment, we see a \texttt{MethodDeclaration}.
+The node corresponding with this MethodDeclaration denotes all tokens found on these two lines, line 24 and 25.
+Although the statements following this method declaration (those that are part of its body) officially belong to the method declaration, they are not included in its graph node.
+Because of that, in this example, the \texttt{MethodDeclaration} on line 24-25 will be considered a clone of the \texttt{MethodDeclaration} on line 205 even though their bodies might differ.
+Even the range (the line and column that this node spans) does not include its child statements and declarations.
+
 \subsubsection{Detecting Clones} \label{sec:detectingclones}

### 2019-07-15 code_examples/Type2-1.java
Updated the paper

@@ -3,8 +3,7 @@ public boolean containsOnlyRedCircles(List<Circle> circles){
 }
 
 public Apple getEdibleApple(FruitBasket<Apple> basket){
-	return basket.getFruitContainer()
-		.getAppleByCriterium(Fruit::hasNotYetBeenEaten);
+	return basket.getFruit().getApple(Fruit::notEaten);
 }
 
 

### 2019-07-15 sections/research.tex
Allow any variability

@@
 
-\subsubsection{A threshold for variability in literals, variables and method calls}
+\subsubsection{A threshold for variability in literals, variables and method calls}\label{sec:variabilitythreshold}
 Type 2 clones allow any variability in literals, variables and method identifiers.
@@
 
-For type 2R clones, we allow called methods to vary as long as they have the same argument types and return type (both of them should be compared using their fully qualified identifiers).
+Type 2R clones allow called methods to vary as long as they have the same argument types and return type.
+As with type 1R clones, these types are compared using their fully qualified identifiers.
 An example of this is shown in figure \ref{fig:type2method}.
 In this example, we have two methods (\texttt{System.out.println} and \texttt{myFancyPrint}).
-We use the ``Extract Method'' refactoring method to extract a new method and use a parameter for to pass the used method.
+We use the ``Extract Method'' refactoring method to extract a new method and use a parameter to pass the used method.
 
@@
 
-\subsubsection{Allow any change in method and class names}
+\subsubsection{Allow any variability in method and class names}
 When refactored, some identifiers have no detrimental effect on the design if they vary between cloned instances.
 In the previous section, variability in literals, variables and called methods would result in more parameters for the extracted method, thus indicating a detrimental effect on system design.
+However, not always does a difference between fragments result in such a tradeoff.
+
+This section explains several patterns of variability that we can allow between cloned fragements without changing the method by which the fragments can be refactored.
+
+\paragraph{Class and method names}
+The names of classes and methods describe the implementation of their body.
+If two classes/methods are cloned, but their names differ, one of both names should be redundant.
+When refactoring such clones, we can choose one instance to keep and one to remove.
+Such a refactoring doesn't affect maintainability in any other way than refactoring a type 1R clone would.
+The same is true of interface, enumeration and annotation names.
+Because of this, type 2R allows any variability in class, method, interface, enumeration and annotation names.
+
 This is not the case with the name of a method declaration and the name of a class/interface/enumeration declaration.
@@
 
-For \textbf{type 2R} clones we allow any variation in literals, variables and method calls at this stage in the clone detection process.
+\textbf{Type 2R} clones allow any variation in literals, variables and method calls at this stage in the clone detection process.
 However, for \textit{literals} we do resolve their type in order to verify that they are of the same type.
@@
 \subsubsection{Validating the type 2R variability threshold}
-In the definition of type 2R (see section \ref{eq:type2r}) clones we described how type 2R clones work on basis of a variability threshold.
+In the definition of type 2R clones (see section \ref{sec:type2r}) we described how type 2R clones work on basis of a variability threshold.
 This threshold, shown more formally in formula \ref{eq:type2r}, is checked by CloneRefactor.
 Implementing such a threshold involves some important design decisions, and has a lot of underwater complexity.
-In this section we explain the way CloneRefactor uses to verify the type 2R variability threshold.
+In this section we explain how CloneRefactor detects type 2R clones on basis of this variability threshold.
 

### 2019-07-15 code_examples/t2equalityarray.java
Prepatory work for type 2R clonerefactor

@@ -1,0 +1,4 @@
+System.out.println(someString)  ;
+//      1         -2    3   -5 -6
+System.out.println("first")  ;
+//      1         -2  7  -5 -6

### 2019-07-15 code_examples/t2equalityarray1-2.java

@@ -1,0 +1,16 @@
+
+
+
+
+
+
+
+
+
+System.out.println(someString);
+System.out.println("first");
+
+
+
+
+

### 2019-07-15 code_examples/t2equalityarray2-2.java

@@ -1,0 +1,16 @@
+
+
+
+
+
+
+
+
+
+System.out.println(MY_MESSAGE);
+customPrint("second");
+
+
+
+
+

### 2019-07-15 code_examples/t2equalityarray2.java

@@ -1,0 +1,4 @@
+System.out.println(MY_MESSAGE)  ;
+//      1        -2     4   -5 -6
+customPrint("second")  ;
+//   8    -2   9   -5 -6

### 2019-07-15 sections/research.tex
Variability in variables

@@
 
-The example in Fig.~\ref{fig:type2} shows a type 2 clone that poses no harm to the design of the system.
+The example in figure \ref{fig:type2} shows a type 2 clone that poses no harm to the design of the system.
 Both methods are, except for their matching structure, completely different in functionality.
@@
 
-\paragraph{Literal and variable variability}
+\paragraph{Literal and variable variability}\label{sec:t2rliteralandvariable}
 We allow only variability in the value of literals and variables, but not in their types.
@@
 
-\subsubsection{Allow any variability in method and class names}
+\subsubsection{Allow any variability in some identifiers}
 When refactored, some identifiers have no detrimental effect on the design if they vary between cloned instances.
@@
 Because of this, type 2R allows any variability in class, method, interface, enumeration and annotation names.
+However, this will only open up a good refactoring opportunity if the entire body is cloned.
 
-This is not the case with the name of a method declaration and the name of a class/interface/enumeration declaration.
+\paragraph{Variable names}
+In section \ref{sec:t2rliteralandvariable} we described how variability in used variables often creates a design tradeoff.
+However, there are cases in which a used variable does not create a design tradeoff.
+For this, the following conditions need to apply:
 
-If a full method is cloned with another method, however only their names differ, we can refactor these methods to keep only one of them.
-Allowing any change in method and class names will only indicate a refactoring opportunity if the full method or class is cloned.
+\begin{itemize}
+  \item The cloned variables are locally defined.
+  \item The cloned variables have the same type.
+  \item The cloned variables are used at the same places in cloned fragments.
+\end{itemize}
+
+\todo{Show examples}
 

### 2019-07-15 sections/research.tex
T2R flow

@@
 
-\subsubsection{Comparing Statements/Declarations}
+\subsubsection{Comparing Statements/Declarations} \label{sec:comparingstuff}
 In the previous section we described a ``duplicate'' relation between nodes in the clone graph built by CloneRefactor.
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{img/CloneRefactorT2RFlow}
+  \caption{Process used to check the variability threshold for T2R clones.}
+  \label{fig:clonerefactort2rflow}
+\end{figure}
+
+Figure \ref{fig:clonerefactort2rflow} shows the steps that CloneRefactor performs to find clones conforming with the type 2R variability threshold.
+This process is done as a postprocessing step after clone detection.
+The type 2R clone determination process is described in more detail in section \ref{sec:comparingstuff}.
+
 \subsubsection{Checking for type 3 opportunities}

### 2019-07-15 sections/clonerefactor.tex
Separated stuff

--- 2019-07-15 sections/research.tex
@@
-\chapter{Defining refactoring-oriented clone types}\label{chap:clonetypes}
-In section \ref{chap:backgroundclonetypes} we introduced the four clone types as defined in literature.
-These simple definitions are suitable for analysis of a codebase.
-Their detection results in simple to understand numbers to argue about a codebase.
-However, these clone types have a few flaws which makes it hard to argue to what extend two fragments of code are functionally related.
-For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings to increase the chance that we can refactor the clone while improving the design.
-
-We also look into clone detection tools for their suitability to support the proposed clone type definitions.
-We selected a few criteria  Most clone detection tools support these definitions of clone types.
-However, many of these tools use a vastly different approach.
-A study by Saini et al \cite{saini2018towards} outlines different clone detection tools and compares their results for each of type 1-3 clones.
-Even though they operate on the same type definitions, the tools used in this study yield different results.
-
-\section{Shortcomings of clone types}
-Clone type 1-3 (further explain in section \ref{chap:backgroundclonetypes}) allow reasoning about the duplication in a software system.
-Clones by these definitions can relatively easily and efficiently be detected.
-This has allowed for large scale analyses of duplication~\cite{livieri2007very}.
-However, these clone type definitions have shortcomings which makes the clones detected in correspondence with these definitions less valuable for (automated) refactoring purposes.
-
-In this section, we discuss the shortcomings of the different clone type definitions.
-Because of these shortcomings, clones found by these definitions are often found to require additional judgment whether they should and can be refactored.
-
-\subsection{Type 1 clones}\label{sec:type1}
-Type 1 clones are \textit{identical clone fragments except for variations in whitespace and comments} \cite{roy2007survey}.
-This allows for the detection of clones that are the result of copying and pasting existing code, along with other reasons why duplicates might get into a codebase.
-
-Type 1 clones are by most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating} implemented as textual equality between code fragments (except for whitespace and comments).
-Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type.
-In such cases, refactoring opportunities could be invalidated.
-This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
-When aiming to automatically refactor clones, applying refactorings to type 1 clones is bound to be error prone and can result in an uncompilable project or a difference in functionality.
-
-\begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/type1}
-  \caption{Example of a type 1 clone that is functionally different.}
-  \label{fig:type1}
-\end{figure}
-
-In the example in figure \ref{fig:type1}, we see a type 1 clone consisting of two methods.
-However, these clones might still be very hard to refactor as we cannot see by this example whether they are functionally equal.
-Both code fragments use different imported types, some of which imported via a wildcard.
-Because of this, it is hard to verify which of the used types have the same underlying implementation.
-
-Because of this, type 1 clones may not all be subject to refactoring.
-In section \label{chap:type1rclones} we describe an alternate approach towards detecting type 1 clones, which results in only clones that can be refactored.
-
-\subsection{Type 2 clones}\label{sec:type2}
-Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments}~\cite{roy2007survey}.
-This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified.
-However, the definition does not adequately differentiate between slight modification and completely different fragments that just happen to have the same structure.
-
-For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
-This could render two methods that have an entirely different functionality as clones.
-Merging such clones can be harmful instead of helpful.
-
-\begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/type2}
-  \caption{Example of a type 2 clone.}
-  \label{fig:type2}
-\end{figure}
-
-The example in figure \ref{fig:type2} shows a type 2 clone that poses no harm to the design of the system.
-Both methods are, except for their matching structure, completely different in functionality.
-They operate on different types, call different methods, return different things, etc.
-Having such a method flagged as a clone does not provide much useful information.
-
-When looking at refactoring, type 2 clones can be difficult to refactor.
-For instance, if we have variability in types, the code can describe operations on two completely dissimilar types.
-Type 2 clones do not differentiate between primitives and reference types, which further undermines the usefulness of clones detected by this definition.
-
-\subsection{Type 3 clones}\label{sec:type3}
-Type 3 clones are \textit{copied fragments with further modification (with added, removed or changed statements)}~\cite{roy2007survey}.
-Detection of clones by this definition can be hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed.
-Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold~\cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
-This similarity threshold has been implemented in different ways: textual similarity (for instance using Levenshtein distance)~\cite{lavoie2011automated}, token-level similarity~\cite{sajnani2016sourcerercc} or statement-level similarity~\cite{kamalpriya2017enhancing}.
-
-Having a definition that allows for any change in code poses serious challenges on refactoring.
-A Levenshtein distance of one can already change the meaning of a code fragment significantly, for instance, if the name of a type differs by a character (and thus referring to different types).
-
-\section{Refactoring-oriented clone types}
-To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types directed at detecting clones that can and should be refactored.
-We have named these clones T1R (type 1R), T2R and T3R clones.
-These definitions address problems of the corresponding literature definitions.
-The ``R'' stands for refactoring-oriented (and may be less useful for other analyses).
-
-\subsection{Type 1R clones} \label{sec:type1r}
-To solve the issues identified in Sec.~\ref{sec:type1}, we introduce an alternative definition: cloned fragments have to be both textually \textit{and} functionally equal.
-Therefore, T1R clones are a subset of type 1 clones.
-
-We check functional equality of two fragments by validating the equality of the fully qualified identifier (FQI) for referenced types, methods and variables.
-If an identifier is fully qualified, it means we specify the full location of its declaration (e.g.
-\texttt{com.sb.fruit.Apple} for an \texttt{Apple} object).
-
-\subsubsection{Referenced Types}
-Many object-oriented programming languages (like Java, Python and C\#) require the programmer to import a type (or the class in which it is declared) before it can be used.
-Based on what is imported, the meaning of the name of a type can differ.
-For instance, if we import \texttt{java.util.List}, we get the interface which is implemented by all list datastructures in Java.
-However, importing \texttt{java.awt.List}, we get a listbox GUI component for the Java Abstract Window Toolkit (AWT).
-To be sure we compare between equal types, type 1R clones compare the FQI for all referenced types.
-
-\subsubsection{Called methods}
-A codebase can have several methods with the same name.
-The implementation of these methods might differ.
-When we call two methods with an identical name, we can in fact call different methods.
-This is another reason that textually identical code fragments can differ functionally.
-
-Because of this, for type 1R clones, we compare the fully qualified method signature for all method references.
-A fully qualified method signature consists of the fully qualified name of the method, the fully qualified type of the method plus the fully qualified type of each of its arguments.
-For instance, an \texttt{eat} method could become \texttt{com.sb.AppleCore com.sb.fruitgame.Apple.eat(com.sb.fruitgame.Tool)}.
-
-\subsubsection{Variables}
-In typed programming languages, each variable declaration should declare a name and a type.
-When we reference a variable, we only use its name.
-If, in different code fragments, we use variables with the same name but different types, the code can be functionally unequal but still textually equal.
-As an example, see the code in figure \ref{fig:type2variables}.
-
-\begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/type2}
-  \caption{Variables with different types but the same name.}
-  \label{fig:type2variables}
-\end{figure}
-
-The body of both methods in figure \ref{fig:type2variables} is equal. However, their functionality is not. The first method adds two numbers together and the other concatenates an integer to a String.
-
-For type 1R clones variable references should be compared by both type and name.
-
-\subsection{Type 2R clones} \label{sec:type2r}
-Type 2R clones are modelled after type 2 clones, which allow any change in identifiers, literals, types, layout, and comments.
-For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
-This could render two methods that have an entirely different functionality as clones (as shown in figure \ref{fig:type2} previously).
-Refactoring such clones can be harmful instead of helpful.
-
-We tackle these problems with type 2R clones to be able to detect such clones that can and should be refactored.
-Type 1R clones are a subset of type 2R clones.
-All rules that apply to type 1R clones also apply to type 2R clones.
-Additionally, type 2R clones allow variability in literals, variables and method calls.
-This variability however is constrained by a threshold.
-Type 2R do not allow any variability in types, as opposed to type 2 clones which do allow variability in types.
-As type 2R clones are per definition more permissive than type 1R clones, type 1R clones are a subset of type 2R clones.
-
-\subsubsection{A threshold for variability in literals, variables and method calls}\label{sec:variabilitythreshold}
-Type 2 clones allow any variability in literals, variables and method identifiers.
-However, this information tells a lot about the meaning of the code fragment.
-Most clone detection tools do not differentiate between a type 2 clone that differs by a single literal/identifier and one that differs by many.
-However, this does have a big impact on the meaning of the code fragment and thus the harmfulness of the duplication being there.
-
-For type 2R clones we define a threshold for variability in literals, variables and method calls. We calculate the variability in literals, variables and method calls using the following formula:
-
-\begin{eqfloat}\label{eq:type2r}
-$$\text{T2R Variability Percentage}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
-$$Diff = \text{Amount that differ from other clone instances in the clone class}$$
-$$Total = \text{Total number in the clone instance}$$
-$$l = \text{Literals in clone}$$
-$$v = \text{Variables in clone}$$
-$$m = \text{Method calls in clone}$$
-$$t = \text{Tokens in clones}$$
-\caption{Type 2R variability threshold formula}\end{eqfloat}
-
-\paragraph{Literal and variable variability}\label{sec:t2rliteralandvariable}
-We allow only variability in the value of literals and variables, but not in their types.
-This is because a difference in literal/variable type may have a big impact on the refactorability of the cloned fragment.
-When we refactor different literals/variables that have both the same type, in case of an ``Extract Method'' refactoring, we have to create a parameter for this literal and pass the corresponding literal/variable from cloned locations.
-However, if two literals have different types, this might not be possible (or will have a negative effect on the design of the system).
-This is because a lot of variability in literals will result in more parameters required in the extracted method, which is detrimental for the design of the system.
-
-Consider the example in figure \ref{fig:type2literal}.
-In this example, the two methods have two literals that differ between them.
-We can perform an ``Extract method'' refactoring on these to get the result that is displayed on the right.
-In this process, we create a method parameter for the corresponding literal.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/type2literal}
-  \caption{Literal variability refactored.}
-  \label{fig:type2literal}
-\end{figure}
-
-\paragraph{Method call variability}
-Most modern programming languages (like Java, Python and C\#) allow to pass method references as a parameter to a method.
-This helps reducing duplication, as it is possible to refactor two code fragments which differ only by a method call.
-However, a method call does often not consist of a single token (like variables and literals).
-For instance, a method call \texttt{System.out.println()} consists of several segments: a type reference to the \texttt{System} type, a reference to the static \texttt{out} field and a call of the \texttt{println()} method.
-
-Type 2R clones allow called methods to vary as long as they have the same argument types and return type.
-As with type 1R clones, these types are compared using their fully qualified identifiers.
-An example of this is shown in figure \ref{fig:type2method}.
-In this example, we have two methods (\texttt{System.out.println} and \texttt{myFancyPrint}).
-We use the ``Extract Method'' refactoring method to extract a new method and use a parameter to pass the used method.
-
-The method call variability property of type 2R clones imply that type 2R clones are not a subset of type 2 clones.
-Because methods calls can have a different structure, type 2R clones can be structurally slightly different.
-The example as shown in figure \ref{fig:type2method} can be a type 2R clone (dependent on the thresholds used), but is not a type 2 clone.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/type2method}
-  \caption{Method variability refactored.}
-  \label{fig:type2method}
-\end{figure}
-
-\subsubsection{Allow any variability in some identifiers}
-When refactored, some identifiers have no detrimental effect on the design if they vary between cloned instances.
-In the previous section, variability in literals, variables and called methods would result in more parameters for the extracted method, thus indicating a detrimental effect on system design.
-However, not always does a difference between fragments result in such a tradeoff.
-
-This section explains several patterns of variability that we can allow between cloned fragements without changing the method by which the fragments can be refactored.
-
-\paragraph{Class and method names}
-The names of classes and methods describe the implementation of their body.
-If two classes/methods are cloned, but their names differ, one of both names should be redundant.
-When refactoring such clones, we can choose one instance to keep and one to remove.
-Such a refactoring doesn't affect maintainability in any other way than refactoring a type 1R clone would.
-The same is true of interface, enumeration and annotation names.
-Because of this, type 2R allows any variability in class, method, interface, enumeration and annotation names.
-However, this will only open up a good refactoring opportunity if the entire body is cloned.
-
-\paragraph{Variable names}
-In section \ref{sec:t2rliteralandvariable} we described how variability in used variables often creates a design tradeoff.
-However, there are cases in which a used variable does not create a design tradeoff.
-For this, the following conditions need to apply:
-
-\begin{itemize}
-  \item The cloned variables are locally defined.
-  \item The cloned variables have the same type.
-  \item The cloned variables are used at the same places in cloned fragments.
-\end{itemize}
-
-\todo{Show examples}
-
-\subsection{Type 3R clones}\label{sec:type3r}
-Type 3 clones allow any change in statements, often bounded by a similarity threshold.
-This means that type 3 clones allow the inclusion of a statement that is not detected by type 1 or 2 clone detection.
-When looking at how we can refactor a statement that is not included by one clone instance but is in another, we find that we require a conditional block to make up for the difference in statements.
-See figure \ref{fig:type3} for an example of such a clone.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/type3_3}
-  \caption{Added statement between cloned methods.}
-  \label{fig:type3}
-\end{figure}
-
-In figure \ref{fig:type3} a single statement is added.
-This statement is found in between cloned lines.
-We have named this difference between the two clones, in this examples containing a single statement, the \textit{gap}.
-This gap has a threshold for type 3R, which is calculated by the following formula:
-
-\begin{eqfloat}\label{eq:type3r}
-$$\text{T3R Gap Percentage}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100$$
-$$Statements = \text{The amount of statements in this code fragment}$$
-$$C_{gap} = \text{The gap between two clones}$$
-$$C_{above} = \text{The clone instance above the gap}$$
-$$C_{below} = \text{The clone instance below the gap}$$
-\caption{Type 3R clone merge opportunities threshold formula}\end{eqfloat}
-
-Apart from this threshold, the gap in between clones may not span over different blocks.
-Look at figure \ref{fig:type3invalid} for an example of this.
-We cannot refactor both statements into a single conditional block.
-We could however use two conditional blocks, but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for type 3R clones.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.6\columnwidth]{img/type3invalid}
-  \caption{Statements between clones in different blocks.}
-  \label{fig:type3invalid}
-\end{figure}
-
-\subsection{Clone types summarized}
-The given clone definitions (types 1R, 2R and 3R) are refactoring-oriented in the sense that they were designed after the literature type definitions but with a concrete refactoring opportunity in mind.
-Summarized, these types can be explained as follows:
-
-\begin{itemize}
-\item \textbf{Type 1R:} Allows no difference between cloned fragments, making it possible to refactor both fragments to a method call that contains the code of both locations. \\
-\item \textbf{Type 2R:} Allows difference between cloned fragments in controlled features of a codebase.
-Refactoring opportunities for these controlled features are known, allowing refactoring with a minor tradeoff.
-\\
-\item \textbf{Type 3R:} Allows any difference. When refactored, this difference must be wrapped in a conditionally executed block, which entails a major tradeoff.
-\end{itemize}
-
-\begin{equation}\label{eq:typerelation}
-\text{Cloned statements} = T1R \subseteq T2R \subseteq T3R
-\end{equation}
-
-\begin{equation}\label{eq:typerelation2}
-\text{Cloned lines} = T1R \subseteq T1 \text{, but } T2R	\nsubseteq T2 \text{ and } T3R \nsubseteq T3
-\end{equation}
-
-\section{The challenge of detecting these clones}\label{chap:challenge}
-To detect each type of clone, we need to parse the fully qualified identifier of all types, method calls and variables.
-This comes with serious challenges, regarding both performance and implementation.
-Also, to be able to parse all fully qualified identifiers, and trace the declarations of variables, we might need to follow cross file references.
-The referenced types/variables/methods might even not be part of the project, but rather of an external library or the standard libraries of the programming language.
-All these factors need to be considered for the referenced entity to be found, on basis of which a fully qualified identifier can be created.
-
-Mainly the requirement to have access to all external libraries is a difficult one to satisfy in diverse projects.
-Because of this, the proposed clone definitions may be less suitable for large scale clone detection purposes.
-
-\section{Unifying the types}\label{sec:unifying}
-In this chapter we have proposed refactoring-oriented definitions using the type 1, 2 and 3 clone definitions from literature as a baseline.
-In literature, these definitions are mainly aimed towards reasoning about duplication in source code.
-When considering these types for refactoring, the goal becomes slightly different.
-Because of this, having separate clone type definitions does not have any value.
-Rather, we need a single clone type definition by which we can detect all clones that can and should be considered for refactoring.
-
-Because of this, the ultimate goal would be not to consider type 1R, 2R and 3R separately, but together.
-However, this is dependent on good thresholds for the type 2R variability and type 3R gap size.
-Because of this, we have dedicated section \ref{sec:thresholds} to performing measurements to find good thresholds.
-The ultimate goal is to have a single unified definition of clones that can and should be refactored.
-Although it will be next to impossible to define such a definition and its corresponding thresholds that does not detect false positives.
-However, we strive to find at least a near-optimal set of thresholds regarding the type definitions proposed in this chapter.
-
-\section{Suitability of existing Clone Detection Tools for detecting these clones}
-\label{ch:tool-overview}
-We conducted a short survey on (recent) clone detection tools in order to expand them with the proposed types.
-The results of our survey are displayed in table~\ref{table:dettools}.
-We chose a set of tools that are open source and can analyze at least one popular object-oriented programming language.
-Next, we formulate the following four criteria by which we analyze these tools:
-\begin{enumerate}
-    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones.
-We want to perform an analysis on all clones in projects to get a complete overview.
-We analyzed this behavior using a set of control projects.
-\item \textbf{TODO: Criterium.}\simon{TODO} We assembled a number of test projects to assess the validity of clone detection tools.
-On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
-\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be refactored.
-Sometimes, textual equality between code fragments does not imply that these can be refactored (this is described more elaborately in section \ref{sec:type1}).
-Because of this, we want to use a clone detection tool that can analyze such structures.
-\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}).
-To achieve this, the tool needs to be able to allow those threshold changes.
-This can be either through simple changes of the source code, or by using some configuration file.
-\end{enumerate}
-
-\begin{table}[H]
- \begin{center}
-  \caption{Our survey on clone detection tools.} \label{table:dettools}
-  \medskip
-\begin{tabular}{|l|l|l|l|l|l|}
-\hline
-\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
-Siamese \cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
-NiCAD \cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
-CPD \cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
-\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
-CCFinderSW \cite{semura2017ccfindersw}   &    &             &             & \checkmark            \\ \hline
-\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
-BigCloneEval \cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
-Deckard \cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
-Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool, which is further described in the next chapter.
-
-\chapter{Evaluation setup}
-In this chapter we describe the setup we use for our experiments.
-Our most prominent contribution is the proposal of a tool called CloneRefactor.
-This tool allows us to map clones with all clone definitions as described in chapter \ref{chap:clonetypes}.
-
-All results of our experiments, as displayed in chapter \ref{ch:results}, are measured over a corpus of Java projects. In this chapter we will explain how we prepared this corpus.
-
 \section{CloneRefactor}
@@
 The type 2R clone determination process is described in more detail in section \ref{sec:comparingstuff}.
+Each of the following paragraphs will explain a step from figure \ref{fig:clonerefactort2rflow}.
 
 \subsubsection{Checking for type 3 opportunities}
-
-\section{The corpus}\label{chap:corpus}
-For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}.
-This corpus has been assembled to contain relatively higher quality projects.
-Also, any duplicate projects were removed from this corpus.
-This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
-
-As indicated in chapter \ref{chap:challenge} CloneRefactor requires all libraries of software projects we test.
-As these are not included in the used corpus \cite{githubCorpus2013}, we decided to filter the corpus to only include Maven projects.
-Maven is a build automation tool used primarily for Java, and works on basis of an \texttt{pom.xml} file to describe the projects' dependencies.
-As no \texttt{pom.xml} files are included in the corpus, we cloned the latest version of each project in the corpus.
-We then removed each project that has no \texttt{pom.xml} file.
-As a final step, we collected all dependencies for each project by using the \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib} Maven command, and removed each project for which not all dependencies were available (due to non-Maven dependencies being used or unsatisfiable dependencies being referenced in the \texttt{pom.xml} file).
-
-Some general data regarding this corpus is displayed in Table \ref{table:general}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{General results for GitHub Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
-  \medskip
-\begin{tabular}{|l|l|}
-\hline
-Amount of projects                                                                                      & 1,361      \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\whitespace, comments and newlines.)\end{tabular} & 1,414,996  \\ \hline
-Amount of statements/declarations                                                                       & 1,212,189  \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of tokens (excluding\\whitespace, comments and newlines.)\end{tabular} & 11,643,194 \\ \hline
-\end{tabular}
-\end{center}
-\end{table}

### 2019-07-15 sections/research.tex
T2R
Separated stuff

--- 2019-07-15 sections/research.tex
@@
 None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool, which is further described in the next chapter.
-
-\chapter{Evaluation setup}
-In this chapter we describe the setup we use for our experiments.
-Our most prominent contribution is the proposal of a tool called CloneRefactor.
-This tool allows us to map clones with all clone definitions as described in chapter \ref{chap:clonetypes}.
-
-All results of our experiments, as displayed in chapter \ref{ch:results}, are measured over a corpus of Java projects. In this chapter we will explain how we prepared this corpus.
-
-\section{CloneRefactor}
-CloneRefactor is the name of our clone detection and refactoring tool. It features the following novel functions:
-\begin{itemize}
-  \item Detection of clone classes rather than clone pairs.
-  \item A novel detection method, aimed at extensibility.
-  \item Detection of refactoring-oriented clone types, in addition to the literature clone types.
-  \item Allows for automated refactoring of a subset of the detected duplication issues.
-\end{itemize}
-In this section we describe our approach and rationale for the design decisions regarding this tool.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.8\columnwidth]{img/CloneRefactorOverall}
-  \caption{CloneRefactor overall process.}
-  \label{fig:clonerefactorprocess}
-\end{figure}
-
-Figure \ref{fig:clonerefactorprocess} shows the overall process used by CloneRefactor.
-First, we detect clones on basis of a Java codebase, given a Java project from disk and a configuration.
-The clone detection process is further explained in section \ref{sec:clonedetection}.
-After all clones are found, CloneRefactor maps the context of the clones.
-On basis of this context, CloneRefactor applies transformations to the source code for clones for which we have configured a refactoring.
-
-\subsection{JavaParser}
-A very important design decision for CloneRefactor is the usage of a library named JavaParser \cite{tomassetti2017javaparser}.
-JavaParser is a Java library which allows to parse Java source files to an abstract syntax tree (AST).
-JavaParser allows to modify this AST and write the result back to Java source code.
-This allows us to apply refactorings to the detected problems in the source code.
-
-Integrated in JavaParser is a library named SymbolSolver.
-This library allows for the resolution of symbols using JavaParser.
-For instance, we can use it to trace references (methods, variables, types, etc) to their declarations (these referenced identifiers are also called ``symbols'').
-This is very useful for the detection of our refactoring-oriented clone types, as they make use of the fully qualified identifiers of symbols.
-
-In order to be able to trace referenced identifiers SymbolSolver requires access to not only the analyzed Java projects, but also all its dependencies.
-This requires us to include all dependencies with the project.
-Along with this, SymbolSolver solves symbols in the JRE System Library (the standard libraries coming with every installation of Java) using the active Java Virtual Machine (JVM).
-This has a big impact on performance efficiency.
-
-Because of the requirement of symbol resolution, the refactoring-oriented clone types are less suitable for large scale clone analysis.
-
-\subsection{Clone Detection}\label{sec:clonedetection}
-To detect clones, CloneRefactor parses the AST aqcuired from JavaParser to an unweighted graph structure.
-On basis of this graph structure, clones are detection.
-Dependent on the type of clones being detected, transformations may be applied.
-The way in which CloneRefactor was designed does not allow for several clone types to be detected simultaneously, in accordance with our clone type philosophy as described in chapter \ref{sec:unifying}.
-
-The overall process regarding clone detection is displayed in figure \ref{fig:clonedetection}.
-First of all, we use JavaParser to read a project from disk and build an AST, one class file at a time.
-Each AST is then converted to a directed graph that maps relations between statements, further explained in section \ref{sec:clonegraph}.
-On basis of this graph, we detect clone classes and verify them using three thresholds (in order of importance):
-\begin{itemize}
-  \item Amount of tokens.
-  \item Amount of statements.
-  \item Amount of lines.
-\end{itemize}
-If the detection was configured to detect either type 2R, 3 or 3R clones we perform some type specific transformations on the resulting set of clones.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/CloneDetection}
-  \caption{CloneRefactor clone detection process.}
-  \label{fig:clonedetection}
-\end{figure}
-
-\subsubsection{Generating the clone graph}\label{sec:clonegraph}
-First of all, we parse the AST obtained from JavaParser into a directed graph structure.
-We have chosen to base our clone detection around statements as the smallest unit of comparison.
-This means that a single statement cloned with another single statement is the smallest clone we can find.
-The rationale for this lies in both simplicity and performance efficiency.
-This means we won't be able to find when a single expression matches another expression, or even a single token matching another token.
-This is in most cases not a problem, as expressions are often small and do not span the minimal size to be considered a clone in the first place (more about this in section \ref{sec:thresholds}).
-
-\paragraph{Filtering the AST}
-As a first step towards building the clone graph, we preprocess the AST to decide which AST nodes should become part of the clone graph.
-We have decided to consider declarations and statements as the smallest compared entities.
-The main reasoning for this is because considering smaller AST constructs, like expressions, significantly increases the complexity and CPU usage of our clone detection and refactoring efforts.
-
-Additionally, we exclude package declarations and import statements. These are omitted by most clone detection tools, as clones in import statements hold limited valuable information.
-
-\paragraph{Building the clone graph}\label{sec:buildingclonegraph}
-Building the clone graph consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
-\begin{itemize}
-  \item The declaration/statement preceding it.
-  \item The declaration/statement following.
-  \item The last \textbf{preceding} declaration/statement with which it is cloned.
-\end{itemize}
-We do not create a separate graph for each class file, so the statement/declaration preceding or following could be in a different file.
-While mapping these relations, we maintain a hashed map containing the last occurrence of each unique statement.
-This map is used to efficiently find out whether a statement is cloned with another.
-An example of such a graph is displayed in figure \ref{fig:clonegraphsimple}.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/CodeGraph2}
-  \caption{Abstract example of a part of a possible clone graph as built by CloneRefactor.}
-  \label{fig:clonegraphsimple}
-\end{figure}
-
-We refer to the declarations and statements in this graph as \textit{nodes}.
-The relations \textit{next} and \textit{previous} in this graph are represented as an twodirectional arrow.
-The relations representing duplication are directed.
-This is a restriction we've chosen as it creates an important constraint for the clone detection process.
-This process is explained in section \ref{sec:detectingclones}.
-
-\subsubsection{Comparing Statements/Declarations}
-In the previous section we described a ``duplicate'' relation between nodes in the clone graph built by CloneRefactor.
-Whether two nodes in this graph are duplicates of each other is dependent on the clone type.
-In this section, we will describe for each type how we compare statements and declarations to assess whether they are clones of each other.
-
-CloneRefactor detects six different types of clones: T1, T2, T3, T1R, T2R and T3R.
-These types are further explained in chapter \ref{chap:clonetypes}.
-For \textbf{type 1} clones, CloneRefactor filters the tokens of a node to exclude its comments, whitespace and end of line (EOL) characters and then compares these tokens.
-For \textbf{type 2} clones, the tokens are further filtered to omit all identifiers and literals.
-\textbf{Type 3} clones do the same duplication comparison as type 2 clones.
-
-For \textbf{type 1R} clones, this comparison is a lot more advanced.
-For \textit{method calls} we trace their declaration and use its fully qualified method signature for comparison with other nodes.
-For all \textit{referenced types} we trace their declarations and use assemble their fully qualified identifier for comparison with other nodes.
-For \textit{variables} we trace their declaration and their types.
-If the variable type is a primitive we can directly use it for comparison.
-If it is a referenced type, we have to trace this type first in order to collect their fully qualified identifier for comparison.
-
-\textbf{Type 2R} clones allow any variation in literals, variables and method calls at this stage in the clone detection process.
-However, for \textit{literals} we do resolve their type in order to verify that they are of the same type.
-For \textit{variables} we also only verify that their types are the same (but not their names).
-For \textit{method calls}, we trace their declaration but only compare the fully qualified identifier for its return type and each of its arguments' types.
-Apart from that, we do not compare the names of method, class, interface and enum declarations.
-
-In this stage, \textbf{type 3R} clones have the same compare rules as type 2R clones.
-
-\subsubsection{Mapping graph nodes to code}
-The clone graph, as explained in section \ref{sec:buildingclonegraph}, contains all declarations and statements in a source code.
-However, declarations and statements may themselves have child declarations and statements.
-To avoid redundant duplication checks, we exclude child declarations and statements from each node.
-Look at figure \ref{fig:clonegraph} for an example of how source code maps to AST nodes.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/CloneGraphCode}
-  \caption{CloneRefactor extracts statements and declarations from source code.}
-  \label{fig:clonegraph}
-\end{figure}
-
-In line 24-25 of the code fragment, we see a \texttt{MethodDeclaration}.
-The node corresponding with this MethodDeclaration denotes all tokens found on these two lines, line 24 and 25.
-Although the statements following this method declaration (those that are part of its body) officially belong to the method declaration, they are not included in its graph node.
-Because of that, in this example, the \texttt{MethodDeclaration} on line 24-25 will be considered a clone of the \texttt{MethodDeclaration} on line 205 even though their bodies might differ.
-Even the range (the line and column that this node spans) does not include its child statements and declarations.
-
-\subsubsection{Detecting Clones} \label{sec:detectingclones}
-After building the clone clone graph, we use it to detect clones.
-We decided to focus on the detection of clone classes rather than clone pairs because clone pairs do not provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}.
-Although clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered.
-Another issue that results from grouping clones by pairs: clone reference amount increases according to the binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), which causes a heavy information redundancy \cite{fontana2012duplicated}.
-
-As stated in the previous section, nodes in the graph link to \textit{preceding} cloned statement.
-This implies that the first node that is cloned does not have any clone relation, as there are no clones preceding it (only following it).
-Because of this, we start our clone detection process at the final location encountered while building the graph.
-For this node, we collect all nodes it is cloned with.
-Even though the final node only links to the preceding node it is cloned with, we can collect all clones.
-This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node.
-As an example, we convert the code example shown in figure \ref{fig:clonegraph} to a clone graph as displayed in figure \label{fig:clonegraph2}.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/CodeGraphExample}
-  \caption{Example of a clone graph built by CloneRefactor.}
-  \label{fig:clonegraph2}
-\end{figure}
-
-Using the example shown in figure \ref{fig:clonegraph} and \label{fig:clonegraph2} we can explain how we detect clones on basis of this graph.
-Suppose we are finding clones for two files and the final node of the second file is a variable declarator.
-This final node is represented in the example figure by the purple box (1).
-We then follow all ``duplicate'' relations until we have found all clones of this node (2 and 3).
-We now have a single statement clone class of three clone instances (1, 2 and 3).
-
-Next, we move to the previous line (4).
-Here again, we collect all duplicates of this node (4 and 5).
-For each of these duplicates, we check whether the node following it is already in the clone class we collected in the previous iteration.
-In this case, (2) follows (5) and (1) follows (4).
-This means that node (3) does not form a `chain' with other cloned statements.
-Because of this, the clone class of (1, 2 and 3) comes to an end.
-It will be checked against the thresholds, and if adhering to the thresholds, considered a clone.
-
-We then go further to the previous node (6).
-In this case, this node does not have any clones.
-This means we check the (2 and 5, 1 and 4) clone class against the thresholds, and if it adheres, consider it a clone.
-Dependent on the thresholds, this example can result in a total of two clone classes.
-
-Eventually, following only the ``previous node'' relations, we can get from (6) to (2).
-When we are at that point, we will find only one cloned node for (2), namely (3).
-However, after we check this clone against the thresholds, we check whether it is a subset of any exisiting clone.
-If this is the case (which it is for this example), we discard the clone.
-
-\subsubsection{Validating the type 2R variability threshold}
-In the definition of type 2R clones (see section \ref{sec:type2r}) we described how type 2R clones work on basis of a variability threshold.
-This threshold, shown more formally in formula \ref{eq:type2r}, is checked by CloneRefactor.
-Implementing such a threshold involves some important design decisions, and has a lot of underwater complexity.
-In this section we explain how CloneRefactor detects type 2R clones on basis of this variability threshold.
-
-\subsubsection{Checking for type 3 opportunities}
-
-\section{The corpus}\label{chap:corpus}
-For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}.
-This corpus has been assembled to contain relatively higher quality projects.
-Also, any duplicate projects were removed from this corpus.
-This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
-
-As indicated in chapter \ref{chap:challenge} CloneRefactor requires all libraries of software projects we test.
-As these are not included in the used corpus \cite{githubCorpus2013}, we decided to filter the corpus to only include Maven projects.
-Maven is a build automation tool used primarily for Java, and works on basis of an \texttt{pom.xml} file to describe the projects' dependencies.
-As no \texttt{pom.xml} files are included in the corpus, we cloned the latest version of each project in the corpus.
-We then removed each project that has no \texttt{pom.xml} file.
-As a final step, we collected all dependencies for each project by using the \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib} Maven command, and removed each project for which not all dependencies were available (due to non-Maven dependencies being used or unsatisfiable dependencies being referenced in the \texttt{pom.xml} file).
-
-Some general data regarding this corpus is displayed in Table \ref{table:general}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{General results for GitHub Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
-  \medskip
-\begin{tabular}{|l|l|}
-\hline
-Amount of projects                                                                                      & 1,361      \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\whitespace, comments and newlines.)\end{tabular} & 1,414,996  \\ \hline
-Amount of statements/declarations                                                                       & 1,212,189  \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of tokens (excluding\\whitespace, comments and newlines.)\end{tabular} & 11,643,194 \\ \hline
-\end{tabular}
-\end{center}
-\end{table}

### 2019-07-15 sections/results.tex
Separated stuff

@@
+\chapter{Experimental setup}
+In this chapter we describe the setup we use for our experiments.
+Our most prominent contribution is the proposal of a tool called CloneRefactor.
+This tool allows us to map clones with all clone definitions as described in chapter \ref{chap:clonetypes}.
+
+All results of our experiments, as displayed in chapter \ref{ch:results}, are measured over a corpus of Java projects. In this chapter we will explain how we prepared this corpus.
+
+\section{The corpus}\label{chap:corpus}
+For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}.
+This corpus has been assembled to contain relatively higher quality projects.
+Also, any duplicate projects were removed from this corpus.
+This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
+
+As indicated in chapter \ref{chap:challenge} CloneRefactor requires all libraries of software projects we test.
+As these are not included in the used corpus \cite{githubCorpus2013}, we decided to filter the corpus to only include Maven projects.
+Maven is a build automation tool used primarily for Java, and works on basis of an \texttt{pom.xml} file to describe the projects' dependencies.
+As no \texttt{pom.xml} files are included in the corpus, we cloned the latest version of each project in the corpus.
+We then removed each project that has no \texttt{pom.xml} file.
+As a final step, we collected all dependencies for each project by using the \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib} Maven command, and removed each project for which not all dependencies were available (due to non-Maven dependencies being used or unsatisfiable dependencies being referenced in the \texttt{pom.xml} file).
+
+Some general data regarding this corpus is displayed in Table \ref{table:general}.
+
+\begin{table}[H]
+  \begin{center}
+  \caption{General results for GitHub Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
+  \medskip
+\begin{tabular}{|l|l|}
+\hline
+Amount of projects                                                                                      & 1,361      \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\whitespace, comments and newlines.)\end{tabular} & 1,414,996  \\ \hline
+Amount of statements/declarations                                                                       & 1,212,189  \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of tokens (excluding\\whitespace, comments and newlines.)\end{tabular} & 11,643,194 \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
 \chapter{Results}

### 2019-07-15 sections/clonerefactor.tex
Turned CloneRefactor into a chapter

@@
-\section{CloneRefactor}
+\chapter{CloneRefactor}
 CloneRefactor is the name of our clone detection and refactoring tool. It features the following novel functions:
@@
 
-\subsection{JavaParser}
+\section{JavaParser}
 A very important design decision for CloneRefactor is the usage of a library named JavaParser \cite{tomassetti2017javaparser}.
@@
 
-\subsection{Clone Detection}\label{sec:clonedetection}
+\section{Clone Detection}\label{sec:clonedetection}
 To detect clones, CloneRefactor parses the AST aqcuired from JavaParser to an unweighted graph structure.
@@
 
-\subsubsection{Generating the clone graph}\label{sec:clonegraph}
+\subsection{Generating the clone graph}\label{sec:clonegraph}
 First of all, we parse the AST obtained from JavaParser into a directed graph structure.
@@
 
-\paragraph{Filtering the AST}
+\subsubsection{Filtering the AST}
 As a first step towards building the clone graph, we preprocess the AST to decide which AST nodes should become part of the clone graph.
@@
 
-\paragraph{Building the clone graph}\label{sec:buildingclonegraph}
+\subsubsection{Building the clone graph}\label{sec:buildingclonegraph}
 Building the clone graph consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
@@
 
-\subsubsection{Comparing Statements/Declarations} \label{sec:comparingstuff}
+\subsection{Comparing Statements/Declarations} \label{sec:comparingstuff}
 In the previous section we described a ``duplicate'' relation between nodes in the clone graph built by CloneRefactor.
@@
 
-\subsubsection{Mapping graph nodes to code}
+\subsection{Mapping graph nodes to code}
 The clone graph, as explained in section \ref{sec:buildingclonegraph}, contains all declarations and statements in a source code.
@@
 
-\subsubsection{Detecting Clones} \label{sec:detectingclones}
+\subsection{Detecting Clones} \label{sec:detectingclones}
 After building the clone clone graph, we use it to detect clones.
@@
 
-\subsubsection{Validating the type 2R variability threshold}
+\subsection{Validating the type 2R variability threshold}
 In the definition of type 2R clones (see section \ref{sec:type2r}) we described how type 2R clones work on basis of a variability threshold.
@@
 
-\subsubsection{Checking for type 3 opportunities}
+\subsection{Checking for type 3 opportunities}

### 2019-07-16 sections/clonerefactor.tex
Removing redundant clone classes conceptually

@@
 
+\subsubsection{Removing redundant clone classes}
+Using the method described in the this section, we do find redundant clones.
+We remove these clones if they are a subset of an existant clone.
+We define the subset relation between clones as displayed as follows:
+
+\begin{equation}\label{eq:subset}
+C_1\text{ is a subset of }C_2\text{ \textit{iff} } \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
+\end{equation}
+
+where \textit{C} refers to a clone class (a set of clone instances), \textit{i} refers to a clone instance, \textit{F} in which a clone instance is found and \textit{R} is the range of tokens that a clone instance spans.
+
 \subsection{Validating the type 2R variability threshold}

### 2019-07-16 sections/clonerefactor.tex
Removing redundant clone classes

--- 2019-07-15 sections/clonerefactor.tex
@@
 
+\subsubsection{Conceptual method of removing redundant clone classes}
+Using the method described in the this section, we find redundant clones.
+We remove these clones if they are a subset of an existant clone.
+We define the subset relation between clones as displayed as follows:
+
+\begin{equation}\label{eq:subset}
+C_1 \subseteq C_2 \iff \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
+\end{equation}
+
+Where \textit{C} refers to a clone class (a set of clone instances), \textit{i} refers to a clone instance, \textit{F} is the file in which a clone instance is located and \textit{R} is the range of tokens that a clone instance spans.
+For each clone added, we remove all existing clones that are a subset of the newly added clone:
+
+\begin{equation}\label{eq:removeall}
+\text{For each new clone }C_{new}\text{ found, remove all clones in }(C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S)
+\end{equation}
+
+Where \textit{S} is the set of all clone classes that are found up in until this point.
+Likewise, we should not add the new clone to our list of clones if its a subset of an existing clone.
+Because of that, we check for each clone added whether there exists a clone of which the newly added clone is a subset:
+
+\begin{equation}\label{eq:removeall}
+\text{For each new clone }C_{new}\text{ found, only add it to }S \text{ iff } (C_{new} \subseteq C_{existing}\text{ }|\text{ }C_{existing} \in S)
+\end{equation}
+
 \subsection{Validating the type 2R variability threshold}

### 2019-07-16 sections/clonerefactor.tex
Remove existing

@@
 \begin{equation}\label{eq:subset}
-C_1 \subseteq C_2 \iff \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
+C_1 \subseteq C_2 \Leftrightarrow \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
 \end{equation}
@@
 
-\begin{equation}\label{eq:removeall}
-\text{For each new clone }C_{new}\text{ found, only add it to }S \text{ iff } (C_{new} \subseteq C_{existing}\text{ }|\text{ }C_{existing} \in S)
+\begin{equation}\label{eq:removeexisting}
+(C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S) \neq \emptyset \Rightarrow S = S \cup C_{new}
 \end{equation}

### 2019-07-16 sections/clonerefactor.tex
Changed removeall to make it more clean

@@
 \begin{equation}\label{eq:removeall}
-\text{For each new clone }C_{new}\text{ found, remove all clones in }(C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S)
+S = S \setminus (C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S)
 \end{equation}
@@
 \begin{equation}\label{eq:removeexisting}
-(C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S) \neq \emptyset \Rightarrow S = S \cup C_{new}
+(C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S) = \emptyset \Rightarrow S = S \cup C_{new}
 \end{equation}

### 2019-07-16 sections/clonerefactor.tex
Finished up the section

@@
 
+For CloneRefactor, we used this conceptual method of removing duplicates, but did not directly implemented these equations.
+The main reason for this is the runtime overhead, as this process has to iterate over each existing clone class and each of their clone instances.
+For large projects with a lot of duplication this process has a significant impact on performance.
+
+\subsubsection{Method of removing redundant clone classes}
+\todo{Write this section}
+
 \subsection{Validating the type 2R variability threshold}

### 2019-07-16 sections/clonerefactor.tex
Fixed stuff

@@
 \subsubsection{Conceptual method of removing redundant clone classes}
-Using the method described in the this section, we find redundant clones.
-We remove these clones if they are a subset of an existant clone.
-We define the subset relation between clones as displayed as follows:
+The clone detection method used by CloneRefactor can, for various reasons,%Should I list these? Listing them could be a section on its own, as I'd have to show examples to make it concrete.
+result in redundant clone classes.
+After the insertion of each newly detected clone, we check whether it is redundant and/or any of the existent clones has become redundant by adding this clone.
+A clone is redundant if it is a subset of an existing clone.
+We define the subset relation between clones as follows:
 
@@
 \begin{equation}\label{eq:removeall}
-S = S \setminus (C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S)
+S = S \setminus \{C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S\}
 \end{equation}
@@
 \begin{equation}\label{eq:removeexisting}
-(C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S) = \emptyset \Rightarrow S = S \cup C_{new}
+\{C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S\} = \emptyset \Rightarrow S = S \cup C_{new}
 \end{equation}
 
-For CloneRefactor, we used this conceptual method of removing duplicates, but did not directly implemented these equations.
+For CloneRefactor we used this conceptual method of removing duplicates, but did not directly implement these equations.
 The main reason for this is the runtime overhead, as this process has to iterate over each existing clone class and each of their clone instances.
@@
 
-\subsubsection{Method of removing redundant clone classes}
-\todo{Write this section}
+\subsubsection{CloneRefactor method of removing redundant clone classes}
 

### 2019-07-17 sections/clonerefactor.tex
Create equality array

@@
 \subsubsection{CloneRefactor method of removing redundant clone classes}
+Because of the order in which clones are found in the clone graph, removing redundant clone classes can be optimized to not require a search of the entire set of clones.
+To do this, we mark each node that has been considered for duplication as \textit{visited}.
+This includes nodes that are interated over and all duplicates of those nodes.
+When we later find a new clone class of which all nodes are \textit{visited}, we don't add this clone class to the set of clone classes because it is a subset of an existing clone class.
+
+\todo{Removal of existing clones: How does this is possibly redundant thing work?}
 
@@
 
+\subsubsection{Create equality array}
+To determine the difference in literals, method calls and variables, we convert the code to an equality array.
+This equality array converts each (group of) token(s) to a number unique to that (group of) tokens.
+Each literal, method call or variable becomes a positive number, whereas each other token becomes a negative number.
+An example of two code fragments converted to equality arrays is displayed in figure \ref{fig:equalityarrays}.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{img/equality}
+  \caption{The conversion of code to an equality array.}
+  \label{fig:equalityarrays}
+\end{figure}
+
 \subsection{Checking for type 3 opportunities}

### 2019-07-17 sections/clonerefactor.tex
Changed the equality array image and added a table
Explain example

@@
 
+The equality array for each of the lines in this example is shown in table \ref{table:equalityarrays}.
+
+\begin{table}[H]
+\begin{center}
+ \caption{The equality arrays in our example figure \ref{fig:equalityarrays}.} \label{table:equalityarrays}
+ \medskip
+\begin{tabular}{|l|l|l|}
+\hline
+Node (N) & Equality Array (E)     & Size (S) \\ \hline
+1        & {[}1, -2, 3, -5, -6{]} & 5        \\ \hline
+2        & {[}1, -2, 7, -5, -6{]} & 5        \\ \hline
+3        & {[}1, -2, 3, -5, -6{]} & 5        \\ \hline
+4        & {[}8, -2, 7, -5, -6{]} & 5        \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+In the example of figure \ref{fig:equalityarrays} the fragment on the left (consisting of N_1 and N_2) and the fragment on the right (consisting of N_3 and N_4) are two clone instances of a clone class.
+We calculate the variability between two nodes by the following formula:
+
+\begin{equation}\label{eq:removeexisting}
+\{C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S\} = \emptyset \Rightarrow S = S \cup C_{new}
+\end{equation}
+%Two nodes are considered clones of each other if the size of their equality array is equal and all negative numbers in the equality array are equal.
+
 \subsection{Checking for type 3 opportunities}

### 2019-07-18 sections/clonerefactor.tex
Minor change
More example

--- 2019-07-17 sections/clonerefactor.tex
@@
 
+The equality array for each of the lines in this example is shown in table \ref{table:equalityarrays}.
+
+\begin{table}[H]
+\begin{center}
+ \caption{The equality arrays in our example figure \ref{fig:equalityarrays}.} \label{table:equalityarrays}
+ \medskip
+\begin{tabular}{|l|l|l|}
+\hline
+Node (n) & Equality Array (E)     & Size (s) \\ \hline
+1        & {[}1, -2, 3, -5, -6{]} & 5        \\ \hline
+2        & {[}1, -2, 7, -5, -6{]} & 5        \\ \hline
+3        & {[}1, -2, 3, -5, -6{]} & 5        \\ \hline
+4        & {[}8, -2, 7, -5, -6{]} & 5        \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+In the example of figure \ref{fig:equalityarrays} the fragment on the left (consisting of n_1 and n_2) and the fragment on the right (consisting of n_3 and n_4) are two clone instances of a clone class.
+Note that the size of the equality arrays of all clone instances must equal the size of the equality arrays of the other clone instances for them to be considered a clone class.
+We calculate the variability of this clone instance as follows:
+
+\begin{equation}\label{eq:variabilityclonerefactor}
+\frac{|\{x>0 \and y>0 \and x \neq y | x \in E_1 \union E_2, y \in E_3 \union E_4\}|}{(s_1+s_2)+(s_3+s_4)}
+\end{equation}
+
+The symbols in this equation refer to the symbols of the column headers of table \ref{table:equalityarrays}.
+%Two nodes are considered clones of each other if the size of their equality array is equal and all negative numbers in the equality array are equal.
+
+\subsubsection{bla}
+
+\begin{equation}\label{eq:t2rcloneequality}
+E_1\text{ is cloned with }E_2\text{ iff }|E_1|=|E_2| \and \forall {x<0 \Rightarrow x=y | x \in E_1, y \in E_2}
+\end{equation}
+
 \subsection{Checking for type 3 opportunities}

### 2019-07-18 sections/clonerefactor.tex
Checking global thresholds

@@
 2        & {[}1, -2, 7, -5, -6{]} & 5        \\ \hline
-3        & {[}1, -2, 3, -5, -6{]} & 5        \\ \hline
-4        & {[}8, -2, 7, -5, -6{]} & 5        \\ \hline
+3        & {[}1, -2, 4, -5, -6{]} & 5        \\ \hline
+4        & {[}8, -2, 9, -5, -6{]} & 5        \\ \hline
 \end{tabular}
@@
 In the example of figure \ref{fig:equalityarrays} the fragment on the left (consisting of n_1 and n_2) and the fragment on the right (consisting of n_3 and n_4) are two clone instances of a clone class.
-Note that the size of the equality arrays of all clone instances must equal the size of the equality arrays of the other clone instances for them to be considered a clone class.
-We calculate the variability of this clone instance as follows:
+Table \ref{table:equalityarrays} shows their corresponding equality arrays.
+
+\subsubsection{Checking global thresholds}
+Using the equality arrays explained in the previous section, we can determine the variability threshold of any clone class.
+We calculate the variability of the example given in table \ref{table:equalityarrays} as follows:
 
 \begin{equation}\label{eq:variabilityclonerefactor}
-\frac{|\{x>0 \and y>0 \and x \neq y | x \in E_1 \union E_2, y \in E_3 \union E_4\}|}{(s_1+s_2)+(s_3+s_4)}
+\frac{|\{x>0 \and y>0 \and x \neq y | x \in E_1 \union E_2, y \in E_3 \union E_4\}|}{(s_1+s_2)+(s_3+s_4)}*100
 \end{equation}
@@
 The symbols in this equation refer to the symbols of the column headers of table \ref{table:equalityarrays}.
+When we apply this equation to the example clone classes displayed in figure \ref{fig:equalityarrays}, we get the following sum:
+
+\begin{equation}\label{eq:sumequality}
+\frac{|{(3,4), (1,8), (7,9)}|}{(5+5)+(5+5)}*100 = \frac{3}{20}*100 = 15\%
+\end{equation}
 %Two nodes are considered clones of each other if the size of their equality array is equal and all negative numbers in the equality array are equal.

### 2019-07-18 sections/clonerefactor.tex
Explain

@@
 
-\subsubsection{Conceptual method of removing redundant clone classes}
+\subsubsection{Conceptual method of removing redundant clone classes}\label{sec:conceptualremovingredundant}
 The clone detection method used by CloneRefactor can, for various reasons,%Should I list these? Listing them could be a section on its own, as I'd have to show examples to make it concrete.
@@
 \end{equation}
+
+So for the example given in figure \ref{fig:equalityarrays} we have a variability of 15\%.
+In CloneRefactor, the maximum variability percentage is a threshold that is entered in a configuration file.
+If a clone adheres to this threshold, it will stay in the set of found clones.
+However, if it does not adhere to the thresholds, a problem arises.
+Because a clone does not adhere to the thresholds, it does not yet mean it has to be discarded.
+This is because an invalid clone class can still contain valid clones that are a subset of the invalid clone (our definition of subsets of clones is given in section \ref{sec:conceptualremovingredundant}).
+
 %Two nodes are considered clones of each other if the size of their equality array is equal and all negative numbers in the equality array are equal.

### 2019-07-18 sections/clonerefactor.tex
Fixed formulas

@@
 \begin{equation}\label{eq:variabilityclonerefactor}
-\frac{|\{x>0 \and y>0 \and x \neq y | x \in E_1 \union E_2, y \in E_3 \union E_4\}|}{(s_1+s_2)+(s_3+s_4)}*100
+\frac{|\{x>0 \land y>0 \land x \neq y\text{ }|\text{ }x \in E_1 \cup E_2, y \in E_3 \cup E_4\}|}{(s_1+s_2)+(s_3+s_4)}*100
 \end{equation}
@@
 \begin{equation}\label{eq:t2rcloneequality}
-E_1\text{ is cloned with }E_2\text{ iff }|E_1|=|E_2| \and \forall {x<0 \Rightarrow x=y | x \in E_1, y \in E_2}
+E_1\text{ is cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall {x<0 \Rightarrow x=y | x \in E_1, y \in E_2}
 \end{equation}

### 2019-07-18 sections/clonerefactor.tex
Fixed equations

@@
 
-In the example of figure \ref{fig:equalityarrays} the fragment on the left (consisting of n_1 and n_2) and the fragment on the right (consisting of n_3 and n_4) are two clone instances of a clone class.
+In the example of figure \ref{fig:equalityarrays} the fragment on the left (consisting of $n_1$ and $n_2$) and the fragment on the right (consisting of $n_3$ and $n_4$) are two clone instances of a clone class.
 Table \ref{table:equalityarrays} shows their corresponding equality arrays.
@@
 \begin{equation}\label{eq:t2rcloneequality}
-E_1\text{ is cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall {x<0 \Rightarrow x=y | x \in E_1, y \in E_2}
+E_1\text{ is cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1) \exists (y \in E_2) x<0 \lor y<0 \Rightarrow x=y
 \end{equation}

### 2019-07-18 sections/background.tex
Moved related work from paper to thesis

@@
 Overall, many of the benefits of code clones do not apply to most modern object-oriented programming languages.
-
-\section{Related work}
-There have been some papers that take some steps towards code clone refactoring.
-Most research towards refactoring code clones has been conducted by Y.
-Higo et al.
-In a 2008 study \cite{higo2008metric} the authors look at the refactoring of class-level, method-level and constructor-level clones in Java.

### 2019-07-18 sections/background.tex
Clone terminology table

@@
 
-\section{Clone Class}
+\section{Defining clones}
+
+\begin{table}[]
+\centering
+\begin{tabular}{@{}lllll@{}}
+\toprule
+\textbf{Symbol} & \textbf{Meaning} & \textbf{Description} & \textbf{Contents} & \textbf{Properties} \\ \midrule
+S & Clone class collection & All clone classes that have been found for a certain software project. & Set of clone classes & - \\
+C & Clone class & A set of similar code fragments in different locations. & Set of clone instances & - \\
+I & Clone instance & A code fragment that appears in multiple locations.
+& Set of cloned nodes & \begin{tabular}[c]{@{}l@{}}File (F): The file in which this clone instance is found.\\ Range (R): The range this clone instance spans.\end{tabular} \\
+N & Node & A statement or declaration in a codebase. & Set of tokens. & Range (R): The range this node spans. \\
+t & Token & Smallest relevant entity of a program.
+& - & \begin{tabular}[c]{@{}l@{}}Range (R): The range this token spans.\\ Category: Identifier, Keyword, Literal, Separator,\\ Operator, Comment or Whitespace\end{tabular} \\ \bottomrule
+\end{tabular}
+\caption{Clone related terminology and how it maps to the source code.}
+\label{tab:cloneterminology}
+\end{table}
+
+\subsection{Clone Class}
 As code clones are seen as one of the most harmful types of technical debt, they have been studied very extensively.

### 2019-07-18 sections/acknowledgements.tex
Fill in the blanks
Acknowledgements

@@
 \chapter*{Acknowledgements}
-If so inclined, thank people.
+Throughout the writing of this dissertation I have received a great deal of support and assistance.
+I would first like to thank my supervisor, Dr.
+A.M.
+Oprescu , whose expertise was invaluable in the academic writing and mathematical aspects of this thesis.
+
+Next, I would like to thank my peer student Sander Meester for always being there when I was stuck.
+Whenever I needed to test some ideas you would always provide realistic insights.
+The long conversations about the problems I have been dealing with in my thesis would not have been solved in the same way if it wasn't for you.
+Your proofreading efforts helped take my writing to the next level.
+
+Finally, I would like to acknowledge my colleagues from my internship at SIG for their wonderful collaboration. You supported me greatly and were always willing to help me.

### 2019-07-18 sections/background.tex
Better table (now it fits :diamond_shape_with_a_dot_inside:)

--- 2019-07-18 sections/background.tex
@@
 
-\section{Clone Class}
+\section{Defining clones}
+
+\begin{table}[H]
+\centering
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lllll@{}}
+\toprule
+\textbf{Symbol} & \textbf{Meaning} & \textbf{Description} & \textbf{Contents} & \textbf{Properties} \\ \midrule
+\rowcolor[HTML]{EFEFEF}
+S & Clone class collection & \begin{tabular}[c]{@{}l@{}}All clone classes that have been \\ found for a certain software project.\end{tabular} & Set of clone classes & - \\
+C & Clone class & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations.\end{tabular} & Set of clone instances & - \\
+\rowcolor[HTML]{EFEFEF}
+I & Clone instance & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & Set of cloned nodes & \begin{tabular}[c]{@{}l@{}}File (F): The file in which this\\ clone instance is found.\\ Range (R): The range this clone\\ instance spans.\end{tabular} \\
+N & Node & \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & Set of tokens. & \begin{tabular}[c]{@{}l@{}}Range (R): The range this node\\ spans.\end{tabular} \\
+\rowcolor[HTML]{EFEFEF}
+t & Token & \begin{tabular}[c]{@{}l@{}}Smallest relevant entity of a\\ program.\end{tabular} & - & \begin{tabular}[c]{@{}l@{}}Range (R): The range this token \\ spans.\\ Category: Identifier, Keyword, \\ Literal, Separator, Operator,\\ Comment or Whitespace\end{tabular} \\ \bottomrule
+\end{tabular}%
+}
+\caption{Clone related terminology and how it maps to the source code.}
+\label{tab:clone-terminology}
+\end{table}
+
+\subsection{Clone Class}
 As code clones are seen as one of the most harmful types of technical debt, they have been studied very extensively.

### 2019-07-18 sections/background.tex
Better table stuff

--- 2019-07-18 sections/background.tex
@@
 
-\section{Clone Class}
+\section{Defining clones}
+
+\begin{table}[]
+\centering
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lllll@{}}
+\toprule
+\textbf{Symbol} & \textbf{Meaning} & \textbf{Description} & \textbf{Contents} & \textbf{Properties} \\ \midrule
+\rowcolor[HTML]{EFEFEF}
+S & Clone class collection & \begin{tabular}[c]{@{}l@{}}All clone classes that\\ have been found for a\\ certain software project.\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\ classes\end{tabular} & - \\
+C & Clone class & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\ instances\end{tabular} & - \\
+\rowcolor[HTML]{EFEFEF}
+I & Clone instance & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\ nodes\end{tabular} & \begin{tabular}[c]{@{}l@{}}File (F): The file in which this\\ clone instance is found.\\ Range (R): The range this clone\\ instance spans.\end{tabular} \\
+N & Node & \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & Set of tokens & \begin{tabular}[c]{@{}l@{}}Range (R): The range this node\\ spans.\end{tabular} \\
+R & Range & A part of a source code file.
+& Set of tokens & \begin{tabular}[c]{@{}l@{}}Begin line/column: The line and\\ column at which the range starts.\\ End line/column: The line and\\ column at which the range end.\end{tabular} \\
+\rowcolor[HTML]{EFEFEF}
+t & Token & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code.
+\\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & - & \begin{tabular}[c]{@{}l@{}}Range (R): The range this token\\ spans.\\ Category: Identifier, Keyword,\\ Literal, Separator, Operator,\\ Comment or Whitespace\end{tabular} \\ \bottomrule
+\end{tabular}%
+}
+\caption{Clone related terminology and how it maps to the source code.}
+\label{tab:clone-terminology}
+\end{table}
+
+\subsection{Clone Class}
 As code clones are seen as one of the most harmful types of technical debt, they have been studied very extensively.

### 2019-07-18 sections/background.tex
Working on the table

@@
 \toprule
+\rowcolor[HTML]{C0C0C0}
 \textbf{Symbol} & \textbf{Meaning} & \textbf{Description} & \textbf{Contents} & \textbf{Properties} \\ \midrule
@@
 S & Clone class collection & \begin{tabular}[c]{@{}l@{}}All clone classes that\\ have been found for a\\ certain software project.\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\ classes\end{tabular} & - \\
+\rowcolor[HTML]{FFFFFF}
 C & Clone class & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\ instances\end{tabular} & - \\
@@
 I & Clone instance & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\ nodes\end{tabular} & \begin{tabular}[c]{@{}l@{}}File (F): The file in which this\\ clone instance is found.\\ Range (R): The range this clone\\ instance spans.\end{tabular} \\
+\rowcolor[HTML]{FFFFFF}
 N & Node & \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & Set of tokens & \begin{tabular}[c]{@{}l@{}}Range (R): The range this node\\ spans.\end{tabular} \\
+\rowcolor[HTML]{EFEFEF}
 R & Range & A part of a source code file.
 & Set of tokens & \begin{tabular}[c]{@{}l@{}}Begin line/column: The line and\\ column at which the range starts.\\ End line/column: The line and\\ column at which the range end.\end{tabular} \\
-\rowcolor[HTML]{EFEFEF}
+\rowcolor[HTML]{FFFFFF}
 t & Token & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code.

### 2019-07-18 sections/background.tex
Finalized the table

--- 2019-07-18 sections/background.tex
@@
 \section{Defining clones}
+Many studies present different definitions for code clone concepts.
+For this study, we mainly use the definitions from Bruntink et al.
+\cite{bruntink2005use}, Roy et al.
+\cite{roy2007survey} and \cite{jiang2007deckard}.
+We created a summary of these concepts, which can be found in table \ref{tab:clone-terminology}.
 
@@
 \resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lllll@{}}
+\begin{tabular}{@{}llll@{}}
 \toprule
-\textbf{Symbol} & \textbf{Meaning} & \textbf{Description} & \textbf{Contents} & \textbf{Properties} \\ \midrule
+\rowcolor[HTML]{FFFFFF}
+\textbf{Symbol} & \textbf{Meaning} & \textbf{Description} & \textbf{Properties} \\ \midrule
 \rowcolor[HTML]{EFEFEF}
-S & Clone class collection & \begin{tabular}[c]{@{}l@{}}All clone classes that have been \\ found for a certain software project.\end{tabular} & Set of clone classes & - \\
-C & Clone class & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations.\end{tabular} & Set of clone instances & - \\
+S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} & \textbf{Clones:} Set of clone classes.
+\\
+\rowcolor[HTML]{FFFFFF}
+C & Clone class & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations.\end{tabular} & \textbf{Instances:} Set of clone instances. \\
 \rowcolor[HTML]{EFEFEF}
-I & Clone instance & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & Set of cloned nodes & \begin{tabular}[c]{@{}l@{}}File (F): The file in which this\\ clone instance is found.\\ Range (R): The range this clone\\ instance spans.\end{tabular} \\
-N & Node & \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & Set of tokens. & \begin{tabular}[c]{@{}l@{}}Range (R): The range this node\\ spans.\end{tabular} \\
+I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Contents:} Totally ordered set of nodes, ordered\\by their begin positions.\\ \textbf{File:} The file in which this clone instance is \\ found.\\ \textbf{Range:} The range this clone instance spans.\end{tabular} \\
+\rowcolor[HTML]{FFFFFF}
+N & Node & \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & \textbf{Range:} The range this node spans. \\
 \rowcolor[HTML]{EFEFEF}
-t & Token & \begin{tabular}[c]{@{}l@{}}Smallest relevant entity of a\\ program.\end{tabular} & - & \begin{tabular}[c]{@{}l@{}}Range (R): The range this token \\ spans.\\ Category: Identifier, Keyword, \\ Literal, Separator, Operator,\\ Comment or Whitespace\end{tabular} \\ \bottomrule
+R & Range & A part of a source code file.
+& \begin{tabular}[c]{@{}l@{}}\textbf{Tokens:} Set of tokens that this range spans.\\ \textbf{Begin line/column:} The line and column at \\ which the range starts.\\ \textbf{End line/column:} The line and column at\\ which the range end.\end{tabular} \\
+\rowcolor[HTML]{FFFFFF}
+T & Token & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code.
+\\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this token spans.\\ \textbf{Category:} Identifier, Keyword, Literal, Separator, \\ Operator, Comment or Whitespace\end{tabular} \\ \bottomrule
 \end{tabular}%

### 2019-07-18 main.tex
Better formulas
Better math
Clone types summarized
Improved type 1 clones shortcomings section
AST Filtering
Separated stuff
Moved related work from paper to thesis
Better table (now it fits :diamond_shape_with_a_dot_inside:)
Testing listings

@@
 \documentclass[a4paper,10pt,titlepage]{report}
-%%This template is based on Paco van Beckhoven's thesis.
 
@@
 \usepackage{xargs}   % Use more than one optional parameter in a new commands
-\usepackage{xcolor}
+\usepackage[table,xcdraw]{xcolor}
 
@@
 \usepackage{wrapfig}
-\usepackage{microtype}
+\usepackage{titlesec}
+\usepackage{listings}
+\usepackage{color}
 
-\usepackage{titlesec}
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+\definecolor{blue}{rgb}{0,0,0.82}
+
+\lstset{frame=tb,
+  language=Java,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=flexible,
+  basicstyle={\small\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{gray},
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  breaklines=true,
+  breakatwhitespace=true,
+  tabsize=3
+}
+
+\newfloat{eqfloat}{h}{eqflts}
+\floatname{eqfloat}{Equation}
 
@@
 	\begin{center}
-		{\Huge\bfseries Towards Automated Refactoring of Code Clones \par}
+		{\Huge\bfseries Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages \par}
 		% Earlier versions:
@@
 \input{sections/background}
+\input{sections/related_work}
 \input{sections/research}
+\input{sections/clonerefactor}
 \input{sections/results}
 \input{sections/discussion}
-\input{sections/related_work}
 \input{sections/conclusion}
@@
 \printbibliography[heading=bibintoc]
-\printglossaries%
+\printglossaries
 

### 2019-07-18 main.tex
Trying some stuff

@@
 \usepackage{listings}
+\usepackage[T1]{fontenc}
+\usepackage{inconsolata}
+
 \usepackage{color}
 
-\definecolor{dkgreen}{rgb}{0,0.6,0}
-\definecolor{gray}{rgb}{0.5,0.5,0.5}
-\definecolor{mauve}{rgb}{0.58,0,0.82}
-\definecolor{blue}{rgb}{0,0,0.82}
+\definecolor{pblue}{rgb}{0.13,0.13,1}
+\definecolor{pgreen}{rgb}{0,0.5,0}
+\definecolor{pred}{rgb}{0.9,0,0}
+\definecolor{pgrey}{rgb}{0.46,0.45,0.48}
 
-\lstset{frame=tb,
-  language=Java,
-  aboveskip=3mm,
-  belowskip=3mm,
+\usepackage{listings}
+\lstset{language=Java,
+  showspaces=false,
+  showtabs=false,
+  breaklines=true,
   showstringspaces=false,
-  columns=flexible,
-  basicstyle={\small\ttfamily},
-  numbers=none,
-  numberstyle=\tiny\color{gray},
-  keywordstyle=\color{blue},
-  commentstyle=\color{dkgreen},
-  stringstyle=\color{mauve},
-  breaklines=true,
   breakatwhitespace=true,
-  tabsize=3
+  commentstyle=\color{pgreen},
+  keywordstyle=\color{pblue},
+  stringstyle=\color{pred},
+  basicstyle=\ttfamily,
+  moredelim=[il][\textcolor{pgrey}]{$$},
+  moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%}
 }

### 2019-07-18 main.tex
Trying minted

--- 2019-06-13 main.tex
@@
 \usepackage{wrapfig}
-\usepackage{microtype}
+\usepackage{titlesec}
+\usepackage{minted}
 
-\usepackage{titlesec}
+\renewcommand{\MintedPygmentize}{/Users/sbaars/tmp/pypa-virtualenv-ce9343c/my_new_env/bin/pygmantize}
+
+\newfloat{eqfloat}{h}{eqflts}
+\floatname{eqfloat}{Equation}
 

### 2019-07-18 sections/background.tex
Testing listings
Trying minted

@@
 Each of the cloned fragments can be defined as a ``clone instance''.
+
+\begin{minted}{python}
+import numpy as np
+
+def incmatrix(genl1,genl2):
+    m = len(genl1)
+    n = len(genl2)
+    M = None #to become the incidence matrix
+    VT = np.zeros((n*m,1), int)  #dummy variable
+
+    #compute the bitwise xor matrix
+    M1 = bitxormatrix(genl1)
+    M2 = np.triu(bitxormatrix(genl2),1)
+
+    for i in range(m-1):
+        for j in range(i+1, m):
+            [r,c] = np.where(M2 == M1[i,j])
+            for k in range(len(r)):
+                VT[(i)*n + r[k]] = 1;
+                VT[(i)*n + c[k]] = 1;
+                VT[(j)*n + r[k]] = 1;
+                VT[(j)*n + c[k]] = 1;
+
+                if M is None:
+                    M = np.copy(VT)
+                else:
+                    M = np.concatenate((M, VT), 1)
+
+                VT = np.zeros((n*m,1), int)
+
+    return M
+\end{minted}
 

### 2019-07-18 sections/background.tex
Uhh

--- 2019-07-18 sections/background.tex
@@
 Each of the cloned fragments can be defined as a ``clone instance''.
+
+\begin{multicols}{2}
+\begin{lstlisting}[caption={Functions that are type 2 clones but functionally completely different.},language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small]
+// Hello.java
+import javax.swing.JApplet;
+import java.awt.Graphics;
+
+public class Hello extends JApplet {
+    public void paintComponent(Graphics g) {
+        g.drawString("Hello, world!", 65, 95);
+    }
+}
+\end{lstlisting}
+\end{multicols}
 

### 2019-07-18 main.tex
Uhh
y u do dis :(

--- 2019-07-18 main.tex
@@
 \usepackage{listings}
+\usepackage{parcolumns}
 \usepackage[T1]{fontenc}
@@
   keywordstyle=\color{pblue},
+  numbers = left,
   stringstyle=\color{pred},
@@
 }
+
+\lstnewenvironment{ccol}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small,#1}}{}
+\lstnewenvironment{acol}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small,#1}}{}
 

### 2019-07-18 main.tex
...

@@
 
-\lstnewenvironment{ccol}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small,#1}}{}
-\lstnewenvironment{acol}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small,#1}}{}
+\lstnewenvironment{javacode}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small,#1}}{}
 

### 2019-07-18 sections/background.tex
y u do dis :(
...
Playing with colors

--- 2019-07-18 sections/background.tex
@@
 
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=1\textwidth]{img/clone-pair}
-	\caption{Example of a clone pair, as found in the \href{https://github.com/Widen/valet}{Valet} project.}
-	\label{fig:clonepair}
-\end{figure}
-
-Figure \ref{fig:cloneclass} displays a clone class with three clone instances.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.8\textwidth]{img/clone-class}
-	\caption{Example of a clone class, as found in the \href{https://github.com/Widen/valet}{Valet} project.}
-	\label{fig:cloneclass}
+\newcommand{\highlightYellow}{\makebox[0pt][l]{\color{yellow}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightBlue}{\makebox[0pt][l]{\color{blue}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightPurple}{\makebox[0pt][l]{\color{purple}\rule[-4pt]{1\linewidth}{14pt}}}
+\begin{figure}
+\begin{parcolumns}{3}
+\colchunk[1]{
+\begin{javacode}
+// File1.java
+|\highlightPurple|doA();
+|\highlightPurple|doB();
+|\highlightBlue|doC();
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// File2.java
+|\highlightPurple|doA();
+|\highlightPurple|doB();
+|\highlightBlue|doC();
+\end{javacode}}
+\colchunk[3]{
+\begin{javacode}
+// File3.java
+|\highlightYellow|doA();
+|\highlightYellow|doB();
+doD();
+\end{javacode}}
+\end{parcolumns}
+\caption{Two clone classes: One clone class with three clone instances and one with two clone instances.}
 \end{figure}

### 2019-07-18 sections/background.tex
Writing about clone classes

@@
 
-\section{Defining clones}
+\section{Code clone terminology}
 Many studies present different definitions for code clone concepts.
@@
 
-\subsection{Clone Class}
-As code clones are seen as one of the most harmful types of technical debt, they have been studied very extensively.
-A survey by Roy et al \cite{roy2007survey} states definitions for various important concepts in code clone research.
-In this survey, he mentions the concept ``clone pair'', which is \textit{a set of two code portions/fragments which are identical or similar to each other}.
-Furthermore, he defined ``clone class'' as \textit{the union of all clone pairs}.
-Apart from this, we use the definition ``clone instance'', which is a single code portion/fragment that is part of either a clone pair or clone class.
+\subsection{Example}
+The code fragment in figure \ref{fig:cloneclasses} shows two clone classes.
+One of the clone classes consists of two clone instances and has three nodes per instance.
+The other clone instance has three clone instances and consists of two nodes per instance.
 
-Figure \ref{fig:clonepair} displays an example of a clone pair or clone class.
-In this case, both cloned fragments, are found in the same class.
-Each of the cloned fragments can be defined as a ``clone instance''.
-
-\newcommand{\highlightYellow}{\makebox[0pt][l]{\color{yellow}\rule[-4pt]{1\linewidth}{14pt}}}
-\newcommand{\highlightBlue}{\makebox[0pt][l]{\color{blue}\rule[-4pt]{1\linewidth}{14pt}}}
-\newcommand{\highlightPurple}{\makebox[0pt][l]{\color{purple}\rule[-4pt]{1\linewidth}{14pt}}}
+\definecolor{lightyellow}{HTML}{fffdcc}
+\newcommand{\highlightYellow}{\makebox[0pt][l]{\color{lightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightDarkyellow}{\makebox[0pt][l]{\color{yellow}\rule[-4pt]{1\linewidth}{14pt}}}
 \begin{figure}
@@
 // File1.java
-|\highlightPurple|doA();
-|\highlightPurple|doB();
-|\highlightBlue|doC();
+|\highlightDarkyellow|doA();
+|\highlightDarkyellow|doB();
+|\highlightYellow|doC();
 \end{javacode}}
@@
 // File2.java
-|\highlightPurple|doA();
-|\highlightPurple|doB();
-|\highlightBlue|doC();
+|\highlightDarkyellow|doA();
+|\highlightDarkyellow|doB();
+|\highlightYellow|doC();
 \end{javacode}}
@@
 \end{parcolumns}
+\label{fig:cloneclasses}
 \caption{Two clone classes: One clone class with three clone instances and one with two clone instances.}

### 2019-07-19 sections/background.tex
Added a tree example

@@
 \cite{bruntink2005use}, Roy et al.
-\cite{roy2007survey} and \cite{jiang2007deckard}.
+\cite{roy2007survey} and Jiang et al.
+\cite{jiang2007deckard}.
 We created a summary of these concepts, which can be found in table \ref{tab:clone-terminology}.
@@
 \caption{Two clone classes: One clone class with three clone instances and one with two clone instances.}
+\end{figure}
+
+This example can be represented as a tree structure using the concepts from table \ref{tab:clone-terminology}. This tree structure is displayed in figure \ref{fig:terminologyexample}.
+
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/TerminologyExample}
+  \caption{Representation of figure \ref{fig:cloneclasses} using the terminology introduced in table \ref{tab:clone-terminology}}
+  \label{fig:terminologyexample}
 \end{figure}

### 2019-07-19 sections/background.tex
Background on refactoring methods

@@
 
-\section{Code clone terminology}
+\section{Code clone terminology}\label{sec:terminology}
 Many studies present different definitions for code clone concepts.
@@
 \subsection{Type 4 clones}
-For this study we have chosen not to consider type 4 clones for refactoring, because they are both hard to detect and hard to refactor (how to choose the best alternative for a certain computation could be a thesis in itself).
+For this study we have chosen to take type 4 clones out of the scope, because they are both hard to detect and hard to refactor.
 A study by Kodhai et al \cite{kodhai2013method} looks into the distribution of the different types of clones in several open source systems (see table 6 of his study).
@@
 \section{Background on refactoring methods}
+One of the main drivers for starting this research is the recent release of the second edition of Martin Fowlers' Refactoring book \ref{fowler2018refactoring}.
+This book has been updated to the modern state of software engineering.
+However, the sentence in which he stresses the importance of unifying duplication in source code remains present in both books \ref{fowler1999refactoring, fowler2018refactoring}.
+
+The main method for dealing with duplication in source code, as described by Martin Fowler, is to extract the duplication to a common place.
+In most IDE's this refactoring method is called ``Extract Method''.
 

### 2019-07-19 sections/background.tex
Extract method

@@
 \newcommand{\highlightDarkyellow}{\makebox[0pt][l]{\color{yellow}\rule[-4pt]{1\linewidth}{14pt}}}
-\begin{figure}
+\begin{figure}[H]
 \begin{parcolumns}{3}
@@
 \end{parcolumns}
+\caption{Two clone classes: One clone class with three clone instances and one with two clone instances.}
 \label{fig:cloneclasses}
-\caption{Two clone classes: One clone class with three clone instances and one with two clone instances.}
 \end{figure}
@@
 
-\section{Clone Types} \ref{chap:backgroundclonetypes}
+\section{Clone Types} \label{chap:backgroundclonetypes}
 Duplication in code is found in many different forms.
@@
 
-\section{Background on refactoring methods}
+\section{Refactoring methods}
 One of the main drivers for starting this research is the recent release of the second edition of Martin Fowlers' Refactoring book \ref{fowler2018refactoring}.
 This book has been updated to the modern state of software engineering.
-However, the sentence in which he stresses the importance of unifying duplication in source code remains present in both books \ref{fowler1999refactoring, fowler2018refactoring}.
+The sentence in which he stresses the importance of unifying duplication in source code remains present in both books \ref{fowler1999refactoring, fowler2018refactoring}.
 
@@
 In most IDE's this refactoring method is called ``Extract Method''.
+
+\subsection{Extract Method}
+Method extraction is one of the most used methods of refactoring duplication in source code.
+Several studies have already concluded that most duplication in source code is found in the body of methods \ref{lozano2007evaluating, white2016deep, bergman2004ethnographic}.
+Method extraction can move matching functionality between methods to a common place: a new method.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+public void doStuff(){
+|\highlightYellow|  doA();
+|\highlightYellow|  doB();
+  doC();
+|\highlightYellow|  doA();
+|\highlightYellow|  doB();
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+public void doStuff(){
+|\highlightYellow|  doAandB();
+  doC();
+|\highlightYellow|  doAandB();
+}
+
+public void doAandB(){
+  doA();
+  doB();
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring duplication through method extraction.}
+\label{fig:extractmethod}
+\end{figure}
 

### 2019-07-19 sections/clonerefactor.tex
Removed the size as it's kind of useless
TODO stuff and new example table
Fixed some compilation warnings

@@
 This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node.
-As an example, we convert the code example shown in figure \ref{fig:clonegraph} to a clone graph as displayed in figure \label{fig:clonegraph2}.
+As an example, we convert the code example shown in figure \ref{fig:clonegraph} to a clone graph as displayed in figure \ref{fig:clonegraph2}.
 
@@
 
-Using the example shown in figure \ref{fig:clonegraph} and \label{fig:clonegraph2} we can explain how we detect clones on basis of this graph.
+Using the example shown in figure \ref{fig:clonegraph} and \ref{fig:clonegraph2} we can explain how we detect clones on basis of this graph.
 Suppose we are finding clones for two files and the final node of the second file is a variable declarator.
@@
 \hline
-Node (n) & Equality Array (E)     & Size (s) \\ \hline
-1        & {[}1, -2, 3, -5, -6{]} & 5        \\ \hline
-2        & {[}1, -2, 7, -5, -6{]} & 5        \\ \hline
-3        & {[}1, -2, 4, -5, -6{]} & 5        \\ \hline
-4        & {[}8, -2, 9, -5, -6{]} & 5        \\ \hline
+Node (n) & Equality Array (E) \\ \hline
+1        & {[}1, -2, 3, -5, -6{]} \\ \hline
+2        & {[}1, -2, 7, -5, -6{]} \\ \hline
+3        & {[}1, -2, 4, -5, -6{]} \\ \hline
+4        & {[}8, -2, 9, -5, -6{]} \\ \hline
 \end{tabular}
@@
 \begin{equation}\label{eq:variabilityclonerefactor}
-\frac{|\{x>0 \land y>0 \land x \neq y\text{ }|\text{ }x \in E_1 \cup E_2, y \in E_3 \cup E_4\}|}{(s_1+s_2)+(s_3+s_4)}*100
+\frac{|\{x>0 \land y>0 \land x \neq y\text{ }|\text{ }x \in E_1 \cup E_2, y \in E_3 \cup E_4\}|}{(|E_1|+|E_2|)+(|E_3|+|E_4|)}*100
 \end{equation}
@@
 
-\subsubsection{bla}
+\subsubsection{Convert Equality Array to Graph}
+\todo{TODO}
+\begin{table}[H]
+\begin{center}
+ \caption{The equality arrays in our example figure \ref{fig:equalityarrays}.} \label{table:equalityarrays2}
+ \medskip
+\begin{tabular}{|l|l|l|}
+\hline
+Node (n) & Equality Array (E) \\ \hline
+1        & {[}1, -2, 3, -5, -6{]} \\ \hline
+2        & {[}1, -2, 3, -5, -6{]} \\ \hline
+3        & {[}8, -2, 4, -5, -6{]} \\ \hline
+4        & {[}1, -2, 7, -5, -6{]} \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
 
+\subsubsection{Detect Clones on Graph}
+\todo{TODO}
 \begin{equation}\label{eq:t2rcloneequality}
@@
 
+\subsubsection{Try to Expand}
+\todo{TODO}
+
 \subsection{Checking for type 3 opportunities}

### 2019-07-19 sections/background.tex
Move method

@@
 Method extraction can move matching functionality between methods to a common place: a new method.
+An example of this procedure is displayed in figure \ref{fig:extractmethod}.
 
@@
 \end{figure}
+
+\subsection{Move method}
+In the example of the previous section, both duplicated parts are in the same method.
+However, a study by Fontana et al.
+\ref{fontana2015duplicated} shows that this is most often not the case.
+Based on the relation between clone instances, the extracted method must be moved to be accessible by all locations of the clone instances.
+This might require different techniques.
+
+\subsubsection{Pull up method}
+A refactoring technique to move a method up in its inheritance structure is called ``Pull up method'' \ref{fowler2018refactoring}.
+This way, if cloned methods are related in any way through inheritance, they can be called by both classes by placing the method in a class they both have in common.
+This way its possible to refactor both fully cloned methods (by just pulling up the method) and partially cloned methods (by first performing method extraction and then pulling up the refactored method).
+
+\subsubsection{Create class abstraction based on implicit relations}
+\todo{}
 

### 2019-07-19 sections/background.tex
More move method refactorings

@@
 \subsubsection{Create class abstraction based on implicit relations}
-\todo{}
+Duplication in source code is an implicit relation between fragments of source code.
+If two classes have many of these implicit relations, then the implementation should be refactored to make this relation explicit.
+If the classes do not yet have a parent/super class, a parent class can be created and the common functionality can be placed in this newly created class.
+This makes the relation between these classes explicit and reduces duplication.
+
+\subsubsection{Providing default implementations for common functionality}
+Looking specifically at the Java programming language, recent versions of Java introduce a new method of reducing duplication through refactoring.
+Java has the concept of \textit{interfaces} as an abstract type that is used to specify a behavior that classes must implement.
+Since Java version 8, Java also supports default implementations to be provided in interfaces.
+This gives an opportunity to make the relation between classes explicit and reduce duplication.
+It can be used in instances where creating a new parent class for duplicated classes is undesirable.
 

### 2019-07-19 sections/background.tex
Remove clone context section

@@
 
-\section{Clone Contexts} %I don't really like this chapter.
-Code clones can be found anywhere in the code.
-The most commonly studied type of clone is the method-level clone.
-Method-level clones are duplicated blocks of code in the body of a method.
-Many clone detection tools only focus on method-level clones (like CPD\footnote{CPD is part of PMD, a commonly used source code analyzer: \url{https://github.com/pmd/pmd}}, Siamese\footnote{Siamese is an Elasticsearch based clone detector: \url{https://github.com/UCL-CREST/Siamese}}, Sysiphus\footnote{Sisyphus crawls the Java library for existing implementations of parts of a codebase: \url{https://github.com/fruffy/Sisyphus}}).
-The reason for this is that with method-level clones it's most likely that the clones are harmful, and they are more straight-forward to refactor.
-
-A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning.
-In this paper the author argues that 98\% are produced at method-level.
-However, the paper that is cited to support this claim \cite{bergman2004ethnographic} does not conclude this same information.
-First of all, the study that is referenced uses a very small dataset (460 copy \& paste instances by 11 participants).
-Secondly, the group of subject only consists of IBM researchers (selection bias).
-Thirdly, it only focuses on copy and paste instances, as opposed to other ways clones can creep into the code.
-Finally, the ``98\%'' is not stated explicitly, but is vaguely derivable from one of the figures (figure 1) in this paper.
-Because of this, there is no reliable overview of how many clones there are in different contexts.
-
-This thesis will focus on measuring how many clones there are per context.
-This way we can determine the impact of focusing our search on a specific context, like the analysis of only method-level clones.
-Our hypothesis is that the 98\% claim is not true (we think this should be far less).
-We also hypothesize that clones in different contexts than method-level are less likely to be harmful and less straight forward to refactor.
-
 \subsection{Clone refactoring in relationship to its context}

### 2019-07-19 sections/background.tex
Code clone harmfulness

@@
 \section{Code clone harmfulness}
-There has been a lot of discussion whether code clones should be considered harmful.
-
+Although duplication in source code is generally seen as a harmful coding practise that should be avoided.
 Most papers view clones as harmful regarding program maintainability.
 \textit{``Clones are problematic for the maintainability of a program, because if the clone is altered at one location to correct an erroneous behaviour, you cannot be sure that this correction is applied to all the cloned code as well.
-Additionally, the code base size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work.''} \cite{ostberg2014automatically}
+Additionally, the code base size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work''} \cite{ostberg2014automatically}.
+However, in some instances it is undesirable to remove all duplication, as it can lead to unnecessary complexity.
 
-However, the harmfulness of clones depends on a lot of factors.
+The harmfulness of clones depends on a lot of factors.
 A paper by Kapser et al \cite{kapser2006cloning} describes several patterns of cloning that may not be considered harmful.
@@
 Overall, many of the benefits of code clones do not apply to most modern object-oriented programming languages.
+
+In this study, one of the main focus points will be to identify what makes a code clone harmful.
+Analyzing refactoring opportunities of code clones gives an unique insight in the state of the source code in case the duplication is not present.
+Analyzing these before- and after states of the source code will provide more insights that will help to rank clones based on their harmfulness.

### 2019-07-19 sections/conclusion.tex
Barebones for furture work

@@
 
-\section{Future work}
-\label{sec:future_work}
+\section{Future work} \label{sec:future_work}
+This study presents a foundation for research in a largely unexplored field of studies: analyzing maintainability through automated software metric refactoring.
+
+\subsection{Automated Refactoring for more metrics}
+
+\subsection{Identifying more types/definitions for clones}
+
+\subsection{Refactoring the harder to refactor clones}
+
+\subsection{Naming of refactored methods/classes/etc.}

### 2019-07-19 sections/conclusion.tex
Automated refactoring for more metrics

@@
 This study presents a foundation for research in a largely unexplored field of studies: analyzing maintainability through automated software metric refactoring.
+However, we scratched just the tip of the iceberg regarding all research opportunities in this field.
+In this section we describe possible extensions to this research, aswell as other research opportunities in this field of studies.
 
 \subsection{Automated Refactoring for more metrics}
+In this study we presented evidence regarding the value of applying automated refactoring to analyze the before- and after state of source code and refactored source code.
+Analyzing these states we were able to analyze the improvement in maintainability after applying certain refactorings.
+This allows us to better assess thresholds by which maintainability issues in source code are identified.
+We also get better insights in the costs and values of applying certain refactoring efforts.
+
+For this study we chose to focus only on the automated refactoring of duplication in source code.
+However, software maintainability depends on more factors and can be measured by more metrics.
+These factors also have opportunities to automate their refactorings.
+We think that several similarly sized studies can be conducted to automate the refactoring of other maintainability metrics.
+
+A study by Heitlager et al.
+\cite{heitlager2007practical} presents several metrics by which the maintainability of source code can be assessed.
+They propose thresholds that indicate issues with these metrics.
+Many of these metrics have automated refactoring opportunities.
+In this section we will focus on several of these metrics to outline their opportunities for automated refactoring.
+
+\subsubsection{Long parameter list}
+
+\subsubsection{Method complexity}
+
+\subsubsection{Method size}
+
+\subsubsection{Combining the metrics}
+Combining the automated refactoring models for each of these metrics can result in a model that ultimately provides significant improvement in the ease of writing well-maintainable source code.
+In this study, we presented a few tradeoffs that are the result of refactoring code clones.
+For instance, refactoring code clones with a lot of variability can result in long parameter lists.
+However, if we can combine this with automated refactoring of long parameter lists, this tradeoff can be mitigated.
+This way, it is possible to work towards an model of automated refactoring that reduces manual refactoring efforts significantly.
+
+When programming, there are often tradeoffs between technical debt and velocity.
+When a deadline comes near, often software quality in sacrifised to gain velocity \cite{costello1984software, austin2001effects, shah2014global}.
+Apart from that, a low programmer aptitude can result in low quality code \ref{cheney1984effects}.
+This is because often forming appropriate abstractions requires time, effort and critical thinking.
+By introducing these abstractions automatically, this negative impact can (partly) be mitigated.
+%When programming, many developers must take decisions between velocity
+%Many programmers report frequent decisions in which they decide to take technical debt
 
@@
 \subsection{Naming of refactored methods/classes/etc.}
+
+\subsection{Looking into other languages/paradigms}

### 2019-07-19 sections/introduction.tex
Automated refactoring for more metrics

@@
 \chapter{Introduction}
-\todo[inline,color=blue!10]{Context: what is the bigger scope of the problem you are trying to solve? Try to connect to societal/economical challenges.
-Problem Analysis: Here you present your analysis of the problem situation that your research will address.
-How does this problem manifest itself at your host organisation?
-Also summarises existing scientific insight into the problem.}
+%\todo[inline,color=blue!10]{Context: what is the bigger scope of the problem you are trying to solve? Try to connect to societal/economical challenges.
+%Problem Analysis: Here you present your analysis of the problem situation that your research will address.
+%How does this problem manifest itself at your host organisation?
+%Also summarises existing scientific insight into the problem.}
 \label{ch:introduction}

### 2019-07-19 sections/conclusion.tex
Long parameter list

@@
 \subsubsection{Long parameter list}
+When multiple parameters are used together in a method, there is an implicit dependency between these parameters: the dependency of being required by that method.
+If a lot of data hangs around really tight together, they should be made into their own object \cite{fowler1999refactoring, visser2016building}.
+Guidelines describe to limit the number of parameters per method to at most 4 \cite{visser2016building}.
 
-\subsubsection{Method complexity}
+If a method has many parameters, we can group strongly related parameters into an object. This can be done automatically, but two things must be considered:
+\begin{itemize}
+  \item How do we determine whether parameters are strongly related?
+  \item At what other places is this data used in unison and should thus use the new abstraction?
+\end{itemize}
+To determine whether parameters are strongly related we must look into at what places they are used in the codebase.
+We must then define some threshold that denotes the percentage of usages of these variables in which they are used together.
+If this threshold exceeds a certain amount, we can group them into an object.
+We must then trace all places in which they are used together and replace the variables by the newly created abstractions.
 
@@
 
-When programming, there are often tradeoffs between technical debt and velocity.
-When a deadline comes near, often software quality in sacrifised to gain velocity \cite{costello1984software, austin2001effects, shah2014global}.
+When programming, there are often trade-offs between technical debt and velocity.
+When a deadline comes near, often software quality in sacrificed to gain velocity \cite{costello1984software, austin2001effects, shah2014global}.
 Apart from that, a low programmer aptitude can result in low quality code \ref{cheney1984effects}.

### 2019-07-19 sections/conclusion.tex
Method complexity

@@
 
+\subsubsection{Method complexity}
+Method complexity refers to the complexity of the logic in a method body.
+There are several methods to compute method complexity.
+The most used complexity metric is (MCCabe) Cyclomatic Complexity \cite{visser2016building}, which refers to the amount of independent paths that can be taken though the source code.
+Another complexity metric that has recently become fairly popular is Cognitive Complexity \cite{campbell2017cognitive}, which attempts to measure the human perceived complexity.
+Both indicate an aspect of source code maintainability.
+
+Dealing with method complexity can largely be done by method extraction.
+We extract a part of a complex method to a new method.
+This way we split the complexity of the original method into separately testable methods.
+Also, the methods become easier to read.
+
+Refactoring complex methods can largely be done automatically.
+Also, many of the results of this study can be reused.
+To assess an automated refactoring opportunity for complex methods, we should assess which parts of methods can be split to end up with parts of similar complexity.
+For this, our research can be used to assess whether a given piece of code can be extracted to a new method (see section \ref{sec:refactorability}).
+
+We recommend to extend our tool, CloneRefactor, to allow for such capabilities.
+CloneRefactor already contains a component that calculates the Cyclomatic Complexity of a given method.
+Using our automated refactored model, idenfied problems can relatively easily be refactored.
+
 \subsubsection{Method size}
+... Although method size is often related to cyclomatic complexity, a study by Landman et al. shows that cyclomatic complexity is not redundant to method size \cite{landman2016empirical}.
 

### 2019-07-19 sections/results.tex
Method complexity

@@
 
-\section{Merging duplicate code through refactoring}
+\section{Merging duplicate code through refactoring} \label{sec:refactorability}
 The most used technique to merge clones is method extraction (creating a new method on basis of the contents of clones).

### 2019-07-19 sections/conclusion.tex
Method size

@@
 CloneRefactor already contains a component that calculates the Cyclomatic Complexity of a given method.
-Using our automated refactored model, idenfied problems can relatively easily be refactored.
+Using our automated refactored model, identified problems can relatively easily be refactored.
 
 \subsubsection{Method size}
-... Although method size is often related to cyclomatic complexity, a study by Landman et al. shows that cyclomatic complexity is not redundant to method size \cite{landman2016empirical}.
+Method size has a strong relation, in terms of refactoring, with Cyclomatic Complexity.
+Although method size is often related to Cyclomatic Complexity, a study by Landman et al.
+\cite{landman2016empirical} shows that Cyclomatic Complexity is not redundant to method size.
+However, they do share a similar method of refactoring.
+The automated refactoring opportunities described in the previous section also apply to method size.
 

### 2019-07-19 sections/conclusion.tex
Naming

@@
 \subsection{Naming of refactored methods/classes/etc.}
+In this study, we took naming of refactored entities out of the scope.
+We applied automated refactoring to duplication, and gave all generated methods, classes and interfaces generated names.
+For our purposes that was not much of an issue, because of the validation methods used.
+We validated our approach using the SIG Maintainability model, which does not take naming quality into account.
+Because of that, the results of our experiments are in no way dependent on the names we give the generated methods, classes and interfaces.
+
+When using our work with the purpose of refactoring assistance, these names will have to be manually provided.
+However, recent studies allow assistance in this process by generating a name that matches the body of a declaration.
+If this can be done in a reliable way, we can apply refactorings without any manual steps required.
+
+A study by Allamanis et al.
+\cite{allamanis2015suggesting} proposes a machine learning model that can suggest accurate method and class names.
+This study shows promising results towards generating method and class names on basis of their body and context.
+However, the source code of this study in not available, making it harder to apply their findings to generate class and method names for any software project.
+
+In a recent study by Alon et al.
+\cite{alon2018code2seq} they propose code2seq.
+Code2seq is a machine learning model that guesses the name of a method given a method body.
+This model has been trained on a large set of method bodies and names.
+The model already shows promising results.
+The source code of code2seq is publicly available, making it possible to embed this model in any application.
+Although this model is still far from perfect, combining it with our research could already greatly reduce the manual refactoring effort required.
+The main deficiency of this model lies in that its limited to the directly avail
 

### 2019-07-19 sections/conclusion.tex
Looking into other languages and paradigms

@@
 \subsection{Looking into other languages/paradigms}
+In this study we describe duplicate code refactoring opportunities for object-oriented languages. We built a tool to refactor code clones in Java and used it to run our experiments.
+
+Applying our experiments with other programming languages than just Java might result in valuable results.
+Refactoring opportunities are greatly dependent on coding conventions, which differ per language.
+Other languages might result in different results, which might result in different insights regarding the resolution of duplication problems found.
+We prioritized refactoring efforts based on Java, which might differ from the prioritization that can result from running our experiments with other programming languages.
+
+In this study we focused only on the object-oriented paradigm because of the shared concepts.
+However, the problems that come with duplication in source code also appears in different programming languages.
+Because of that, more insights could be obtained when looking into automated refactoring opportunities for other paradigms.
+For instance, it might be valuable to look into the opportunities to reduce duplication in the functional domain.
+Dealing with code clones in the functional paradigm is pretty much an unexplored field and might hold valuable results.
+
+\subsection{Running our experiments with a greater diversity of software projects}

### 2019-07-19 sections/conclusion.tex
Type 4 clones

@@
 \subsection{Identifying more types/definitions for clones}
+In this study, we proposed a set of clone type definitions for which a refactoring opportunity is known.
+We based these clone type definitions on the clone type definitions that are commonly used in literature.
+The design of these clone type definitions entailed some decisions that have a large impact on the clones we considered for refactoring in this study.
+
+Choosing different
+
+\subsubsection{Type 4 clones}
+In section \ref{chap:backgroundclonetypes} we introduced the clone types that are used in literature.
+Of these clone types, we considered type 1, 2 and 3 for refactoring.
+We chose not to consider type 4 clones because they appear far less in source code and are more difficult to detect and refactor.
+However, that does not mean that these clones should not be refactored.
+
+We think that there are relevant research opportunities in refactoring type 4 clones.
+Type 4 clones are functionally equal pieces of code that are implemented through different implementations.
+Although functionally equal, type 4 clones might still differ in other aspects.
+For instance, for type 4 clones, one alternative might be easier to maintain.
+Also, they can differ (significantly) in performance.
+
+There are interesting research opportunities in automatically choosing the better alternative among type 4 clone instances.
 
@@
 \subsection{Running our experiments with a greater diversity of software projects}
+Currently
+
+\subsection{Automatically refactoring code that is duplicated with a library}

### 2019-07-19 sections/conclusion.tex
Proposing new clone type definitions

@@
 \section{Future work} \label{sec:future_work}
-This study presents a foundation for research in a largely unexplored field of studies: analyzing maintainability through automated software metric refactoring.
+This study presents a foundation for research in a largely unexplored field of studies: analyzing maintainability through automated refactoring.
 However, we scratched just the tip of the iceberg regarding all research opportunities in this field.
-In this section we describe possible extensions to this research, aswell as other research opportunities in this field of studies.
+In this section we describe possible extensions to this research, as well as other research opportunities in this field of studies.
 
@@
 We based these clone type definitions on the clone type definitions that are commonly used in literature.
-The design of these clone type definitions entailed some decisions that have a large impact on the clones we considered for refactoring in this study.
+The design of these clone type definitions entails some decisions that have a large impact on the clones we considered for refactoring in this study.
 
-Choosing different
+\subsubsection{Type 2R clones}
+With type 2R cl
 
@@
 There are interesting research opportunities in automatically choosing the better alternative among type 4 clone instances.
+
+\subsubsection{Proposing new clone type definitions}
+We think that current definitions of clone types still lack in the identification of all duplication issues that a developer should invest his/her refactoring efforts in.
+Current clone detection techniques still result in many false positives and false negatives.
+By proposing good definitions for code clones that mark the characteristics of harmful antipatterns, we can create more accurate suggestions to developers.
 

### 2019-07-19 sections/conclusion.tex
Type 2R clones

@@
 \subsubsection{Type 2R clones}
-With type 2R cl
+With type 2R clones we allow variability in some identifiers and literals such that the code can and should still be refactored.
+For type 2R clones we chose a set of expressions in which we allow variability and proposed a recommended refactoring strategy.
+We think however that type 2R could still use a lot of improvement to find more duplication patterns that can be refactored.
+
+One method we think can be used to find more refactoring opportunities is to allow variability in expressions that have/return the same type.
+If expressions have/return the same type, they can be extracted to a parameter and the corresponding expression can be passed as a parameter.
+The only thing to watch out for is method that have side effects.
+Because methods may be executed in another point during execution, this might affect the functionality of the code.
+%TODO: Might want to show an example here
 
@@
 Current clone detection techniques still result in many false positives and false negatives.
-By proposing good definitions for code clones that mark the characteristics of harmful antipatterns, we can create more accurate suggestions to developers.
+By proposing good definitions for code clones that mark the characteristics of harmful anti-patterns, we can create more accurate suggestions to developers.
 

### 2019-07-19 sections/conclusion.tex
Showing example for refactoring

@@
 If expressions have/return the same type, they can be extracted to a parameter and the corresponding expression can be passed as a parameter.
+An example of this is displayed in figure \ref{fig:samereturn}.
 The only thing to watch out for is method that have side effects.
 Because methods may be executed in another point during execution, this might affect the functionality of the code.
-%TODO: Might want to show an example here
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+public void doStuff(){
+  int numbers = 456;
+|\highlightYellow|  doA(getTitle());
+|\highlightYellow|  doB(123);
+  doC();
+|\highlightYellow|  doA("456");
+|\highlightYellow|  doB(numbers);
+}
+
+public String getTitle(){
+  return "123";
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+public void doStuff(){
+  int numbers = 456;
+|\highlightYellow|  doAandB(getTitle(), 123);
+  doC();
+|\highlightYellow|  doAandB("456", numbers);
+}
+
+public void doAandB(String var1, int var2){
+  doA(var1);
+  doB(var2);
+}
+
+public String getTitle(){
+  return "123";
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring different expressions that have the same return type.}
+\label{fig:samereturn}
+\end{figure}
 

### 2019-07-19 sections/conclusion.tex
More about stuff

@@
 \subsection{Refactoring the harder to refactor clones}
+In section \ref{sec:refactorability} we introduced to what extent clones can be refactored through method extraction.
+Because we strived to get results fast, we excluded catagories that could not not be directly refactored through method extraction.
+However, with a few transformations or further considerations it might be possible to make these clones refactorable.
 
@@
 Although this model is still far from perfect, combining it with our research could already greatly reduce the manual refactoring effort required.
-The main deficiency of this model lies in that its limited to the directly avail
+The main deficiency of this model lies in that its limited to the method body and does currently not consider anything else in a method body.
+This method is flawed, because the meaning of method bodies depends heavily on their context.
+For instance, the body of the method \texttt{get()} in \texttt{ArrayList} does not make any sense in relation to its name without considering its context (class, inheritance hierarchy, etc.).
 

### 2019-07-19 sections/conclusion.tex
TODO everywhere

@@
 In section \ref{sec:refactorability} we introduced to what extent clones can be refactored through method extraction.
-Because we strived to get results fast, we excluded catagories that could not not be directly refactored through method extraction.
+Because we strived to get results fast, we excluded categories that could not not be directly refactored through method extraction.
 However, with a few transformations or further considerations it might be possible to make these clones refactorable.
+In this section we will highlight a few of these categories which we believe to be refactorable through method extraction with a bit more effort.
+
+\subsubsection{Partial method}
+\todo{TODO}
+
+\subsubsection{Overlap}
+\todo{TODO}
+
+\subsubsection{Complex control flow}
+\todo{TODO}
 
@@
 \subsection{Running our experiments with a greater diversity of software projects}
-Currently
+\todo{TODO}
 
 \subsection{Automatically refactoring code that is duplicated with a library}
+\todo{TODO}

### 2019-07-19 sections/conclusion.tex
Library refactor

@@
 \subsection{Automatically refactoring code that is duplicated with a library}
-\todo{TODO}
+One of the clone detection tools we analyzed in this study is Sisyphus \ref{eremondi2017sisyphus}.
+This clone detection tool searches a codebase for methods that are part of the Java standard libraries.
+There are definite automated refactoring opportunities here, automatically switching to the library implementation if available.
+
+This doesn't have to be limited to just the Java standard library.
+Although using a new library for a single cloned library, we can also search the libraries the project are already uses.
+CloneRefactor is an excellent tool to expand for finding such clones with external libraries and refactoring the source code to use the library implementation if available.
+This is because CloneRefactor has scripts to gather all dependent libraries for Maven projects.
+It loads these libraries in order to be able to resolve symbols.
+If this would be expanded not only to resolve symbols but also to consider the clones between the analyzed project and its dependencies, we could find such refactoring opportunities.

### 2019-07-19 sections/background.tex
Reference for default interface methods
Maven in the background

@@
 Java has the concept of \textit{interfaces} as an abstract type that is used to specify a behavior that classes must implement.
-Since Java version 8, Java also supports default implementations to be provided in interfaces.
+Since Java version 8, Java also supports default implementations to be provided in interfaces \ref{mohnen2002interfaces}.
 This gives an opportunity to make the relation between classes explicit and reduce duplication.
@@
 Analyzing these before- and after states of the source code will provide more insights that will help to rank clones based on their harmfulness.
+
+\section{Maven}
+Maven is a build automation tool, mainly used with the Java programming language. Maven has a simple ecosystem to configure and fetch a projects' dependencies binaries and source code.
+
+In this study we use Maven to analyze software systems in more depth. We parse and analyze the libraries on which they are dependent.

### 2019-07-19 sections/conclusion.tex
Different set

@@
 
-\subsection{Running our experiments with a greater diversity of software projects}
-\todo{TODO}
+\subsection{Running our experiments with a different set of software projects}
+In our experiments we chose to use a GitHub based software corpus.
+This corpus contains a diversity of projects of many different sizes.
+We noticed that there is a lot of difference in the quality of these software systems: some systems had a lot of duplication and some did not have any duplication.
+
+We think that there is value in running our experiments with different corpuses.
+We would, for instance, be interested in the results for industrial projects instead of open source software systems.
+We are curious to see whether the distributions are comparable, or whether they show large differences.
+
+Furthermore, we think that there is value in running our experiments with a set of larger sized and more professionally developed open source systems.
+We noticed that in our corpus there were a lot of projects that have only few commits and contributors.
+We think it would be valuable to for instance perform our experiments with a set of larger open source systems, like the systems in the apache ecosystem.
 

### 2019-07-19 sections/conclusion.tex
Complex control flow

@@
 
-\subsubsection{Partial method}
-\todo{TODO}
+\subsubsection{Partial block}
+We did not consider clones for refactoring that span a part of a block. Although it is indeed not possible to refactor such clones, there are possibilities to make such clones refactorable.
 
@@
 \subsubsection{Complex control flow}
-\todo{TODO}
+Break, continue and return statements can obstruct the possibility of performing method extraction.
+However, with some extra transformations, method extraction will still be possible in such cases.
+Figure \ref{fig:complexcontrolflowrefactoring} shows such a transformation.
+We can wrap the newly extracted method in a conditional to indicate whether the ``control flow modifying statement'' should be executed.
+In other cases, other methods might apply to refactor such clones.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+public boolean doStuff(){
+  int numbers = 456;
+|\highlightYellow|  doA();
+|\highlightYellow|    return false;
+|\highlightYellow|  doB();
+  doC();
+|\highlightYellow|  if(doA());
+|\highlightYellow|    return false;
+|\highlightYellow|  doB();
+  return true;
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+public boolean doStuff(){
+  int numbers = 456;
+|\highlightYellow|  if(!doAandB())
+|\highlightYellow|    return false;
+  doC();
+|\highlightYellow|  return doAandB("456", numbers);
+}
+
+public boolean doAandB(){
+  if(doA())
+    return false;
+  doB(var2);
+  return true;
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring a method that is obstructed by a complex control flow.}
+\label{fig:complexcontrolflowrefactoring}
+\end{figure}
 
@@
 We noticed that in our corpus there were a lot of projects that have only few commits and contributors.
-We think it would be valuable to for instance perform our experiments with a set of larger open source systems, like the systems in the apache ecosystem.
+We think it would be valuable to for instance perform our experiments with a set of larger open source systems, like the systems in the Apache ecosystem.
 

### 2019-07-19 sections/conclusion.tex
Overlap

@@
 
-\subsubsection{Overlap}
-\todo{TODO}
+\subsubsection{Overlap within a clone class}
+We do not consider clone classes for refactoring that overlap in the clone class itself.
+That is because such clones might require other techniques to refactor them.
+We consider analyzing such refactoring methods future work.
 
@@
   int numbers = 456;
-|\highlightYellow|  doA();
+|\highlightYellow|  if(doA());
 |\highlightYellow|    return false;
@@
   doC();
-|\highlightYellow|  return doAandB("456", numbers);
+|\highlightYellow|  return doAandB();
 }

### 2019-07-20 sections/conclusion.tex
Example for inner clone class duplication

@@
 We consider analyzing such refactoring methods future work.
+An example refactoring of clone instances that overlap within their clone class is displayed in figure \ref{fig:overlaprefactoring}.
+In this example one clone instance is found between line \ref{line:overlaprefactoring1} and \ref{line:overlaprefactoring4} and the other between \ref{line:overlaprefactoring2} and \ref{line:overlaprefactoring5}.
+To refactor such clones, other techniques may be required, like introducing a new for-loop to reduce the duplication.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+public boolean sayHello(){
+|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring1}|
+|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring2}|
+|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring3}|
+|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring4}|
+|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring5}|
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+public boolean sayHello(){
+|\highlightYellow|  for(int i = 0; i<5; i++){
+|\highlightYellow|    System.out.println("hello!");
+|\highlightYellow|  }
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring a clone class that has overlap within the clone class due to the clone class existing of equal lines.}
+\label{fig:overlaprefactoring}
+\end{figure}
 

### 2019-07-20 sections/conclusion.tex
Partial block refactoring example

--- 2019-07-19 sections/conclusion.tex
@@
 \subsubsection{Partial block}
-We did not consider clones for refactoring that span a part of a block. Although it is indeed not possible to refactor such clones, there are possibilities to make such clones refactorable.
+We did not consider clones for refactoring that span a part of a block.
+Although it is indeed not possible to refactor such clones, there are possibilities to make such clones refactorable.
+For instance, if the programming language supports lambda expressions, we can move the difference of statements in the block in a lambda expression.
+Figure \ref{fig:partialblockrefactoring} shows an example of such a refactoring opportunity.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+public void doStuff(){
+|\highlightYellow|  for(int i = 0; i<5; i++) { //Only the declaration of this for loop is cloned, but the loop body is not.
+    System.out.println("hello!");
+  }
+|\highlightYellow|  for(int i = 0; i<5; i++) {
+    CoreController.activateCore(i);
+  }
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+public void doStuff(){
+|\highlightYellow|  doFiveTimes(() -> System.out.println("hello!"));
+|\highlightYellow|  doFiveTimes(() -> CoreController.activateCore(i));
+}
+
+public void doFiveTimes(Runnable runnable){
+  for(int i = 0; i<5; i++) { //Only the declaration of this for loop is cloned, but the loop body is not.
+    runnable.run();
+  }
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring a method that is obstructed by a complex control flow.}
+\label{fig:partialblockrefactoring}
+\end{figure}
 
@@
 We consider analyzing such refactoring methods future work.
+An example refactoring of clone instances that overlap within their clone class is displayed in figure \ref{fig:overlaprefactoring}.
+In this example one clone instance is found between line \ref{line:overlaprefactoring1} and \ref{line:overlaprefactoring4} and the other between \ref{line:overlaprefactoring2} and \ref{line:overlaprefactoring5}.
+To refactor such clones, other techniques may be required, like introducing a new for-loop to reduce the duplication.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+public void sayHello(){
+|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring1}|
+|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring2}|
+|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring3}|
+|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring4}|
+|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring5}|
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+public void sayHello(){
+|\highlightYellow|  for(int i = 0; i<5; i++){
+|\highlightYellow|    System.out.println("hello!");
+|\highlightYellow|  }
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring a clone class that has overlap between clone instances.}
+\label{fig:overlaprefactoring}
+\end{figure}
 
@@
 public boolean doStuff(){
-  int numbers = 456;
 |\highlightYellow|  if(doA());
@@
 public boolean doStuff(){
-  int numbers = 456;
 |\highlightYellow|  if(!doAandB())
@@
     return false;
-  doB(var2);
+  doB();
   return true;

### 2019-07-21 sections/introduction.tex
TODO
AAH

@@
 \label{ch:introduction}
-
+\todo{Rewrite this part}
 Refactoring is used to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
@@
 Duplication in source code is often seen as one of the most harmful types of technical debt.
-In Martin Fowler's ``Refactoring'' book \cite{fowler2018refactoring}, he exclaims that \textit{``Number one in the stink parade is duplicated code.
-If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
+In Martin Fowler's ``Refactoring'' book \cite{fowler2018refactoring}, he exclaims that \textit{``if you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
 
@@
 \section{Problem statement}
+In this section we describe the problem we address with this study and the research questions that we answer in order to contribute to solving the problem.
+
+\subsection{The problem}
+\todo{How do I formulate this}
 
 \subsection{Research questions}
+\todo{Rewrite this part}
 Code clones can appear anywhere in the code.
@@
 \subsection{Research method}
+\todo{TODO}
 
 \section{Contributions}
+\todo{Rewrite this part}
 Our research makes the following contributions:
@@
 \section{Scope}
+\todo{Rewrite this part}
 In this research we will look into code clones from a refactoring viewpoint.
@@
 \section{Outline}
+\todo{Rewrite this part}
 In Chapter~\ref{ch:background} we describe the background of this thesis.

### 2019-07-21 sections/results.tex
Relation bla bla

@@
 In this chapter we describe the setup we use for our experiments.
-Our most prominent contribution is the proposal of a tool called CloneRefactor.
-This tool allows us to map clones with all clone definitions as described in chapter \ref{chap:clonetypes}.
-
-All results of our experiments, as displayed in chapter \ref{ch:results}, are measured over a corpus of Java projects. In this chapter we will explain how we prepared this corpus.
+All results of our experiments, as displayed in chapter \ref{ch:results}, are measured over a corpus of Java projects.
+In this chapter we will explain how we prepared this corpus.
 
@@
 
+\section{Context Analysis of Clones}\label{chap:contextsetup}
+To be able to refactor code clones, it is important to consider the context of the clone. We define the following aspects of the clone as its context:
+\begin{enumerate}
+  \item \textbf{Relation:} The relation of clone instances among each other through inheritance.
+  \item \textbf{Location:} Where a clone instance occurs in the code.
+  \item \textbf{Contents:} The statements/declarations of a clone instance.
+\end{enumerate}
+We perform experiments on each of these aspects, defining categories and measuring these categories over the corpus.
+
+\begin{figure}[H]
+  \caption{Abstract representation of clone classes and clone instances.}
+    \medskip
+    \includegraphics[width=1\columnwidth]{img/context}
+  \label{fig:clonecontext}
+\end{figure}
+
+Fig.~\ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
+The relation of clones through inheritance is measured for each clone class.
+The location and contents of clones are measured for each clone instance.
+
+\subsection{Relation}
+When merging code clones in object-oriented languages, it is important to consider the inheritance relation between clone instances. This relation has a big impact on how a clone should be refactored.
+
+Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other.
+To do this, they first define several categories for the relation between clone instances in object-oriented languages.
+These categories are as follows:
+\begin{enumerate}
+  \item \textbf{Same method}: All instances of the clone class are in the same method.
+  \item \textbf{Same class}: All instances of the clone class are in the same class.
+  \item \textbf{Superclass}: All instances of the clone class are child or parent of each other.
+  \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
+  \item \textbf{Sibling class}: All instances of the clone class have the same parent class.
+  \item \textbf{First cousin class}: All instances of the clone class have the same grandparent class.
+\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same inheritance hierarchy, but do not belong to any of the other categories.
+\item \textbf{Same external superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
+\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
+\end{enumerate}
+
+We added the following categories, to gain more information about clones and reduce the number of unrelated clones:
+
+\begin{enumerate}
+\item \textbf{Same Interface}: All instances of the clone class are in a class or interface that have a common interface anywhere in their inheritance hierarchy.
+\item \textbf{No Direct Superclass}: All instances of the clone class are in a class that does not have any superclass.
+\item \textbf{No Indirect Superclass}: All instances of the clone class are in a class that does not have any external classes in its inheritance hierarchy.
+\end{enumerate}
+
+\begin{figure}[H]
+  \caption{Abstract figure displaying relations of clone classes. Arrows represent superclass relations.}
+    \medskip
+    \includegraphics[width=1\columnwidth]{img/Relation}
+  \label{fig:clonerelation}
+\end{figure}
+
 \chapter{Results}

### 2019-07-22 sections/results.tex
Lots a relation related content

@@
   \item \textbf{Same class}: All instances of the clone class are in the same class.
-  \item \textbf{Superclass}: All instances of the clone class are child or parent of each other.
+  \item \textbf{Superclass}: All instances of the clone class are in a class that is child or parent of each other.
   \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
@@
 
+Figure \ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
+The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
+The location and contents of clones is measured on clone instance level.
+A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50).
+A clone instance contents consists of a list of all statements and declarations it spans.
+
 \begin{figure}[H]
@@
 
+We analyzed
+
+\subsubsection{Same Class}
+The \textit{``Same method''} and \textit{``Same class''} relations share a common refactoring opportunity.
+Clones of both these catagories, when extracted to a new method, can be placed in the same class.
+Both of these relations are most favorable for refactoring, as they require a minimal design tradeoff.
+Furthermore, global variables that are used in the class can be used without having to create method parameters.
+
+A clone class is flagged as ``Same method'' if all clone instances in the clone class are in the same method:
+
+\begin{equation}\label{eq:samemethod}
+\forall (i_1 \in C) \forall (i_2 in C) Mi_1 = Mi_2
+\end{equation}
+
+Where \textit{M} is the method in which a clone instance is found.
+Please note that a clone instance may not always be in a method, for which this predicate will fail.
+Each node in a clone instance is checked for this predicate, so if a single node of a clone instance is outside a method, the predicate will fail.
+
+A clone class is flagged as ``Same class'' if all clone instances in the clone class are in the same class:
+
+\begin{equation}\label{eq:samemethod}
+\forall (i_1 \in C) \forall (i_2 in C) Di_1 = Di_2
+\end{equation}
+
+Where \textit{D} is the class declaration in which the clone instance is found.
+
+\subsubsection{Same Hierarchy}
+The following relations belong to
+
 \chapter{Results}
@@
 \section{Thresholds} \label{sec:thresholds}
+\TODO{todo}
 
 \section{Context Analysis of Clones}\label{chap:clonecontextexpl}
-To be able to refactor code clones, it is very important to consider the context of the clone. We define the following aspects of the clone as its context:
-\begin{enumerate}
-  \item The relation of clone instances among each other through inheritance (for example: a clone instance resides in a superclass of another clone instance in the same clone class).
-  \item Where a clone instance occurs in the code (for example: a method-level clone is a clone instance that is in a method).
-  \item The contents of a clone instance (for example: the clone instance spans several methods).
-\end{enumerate}
-
-\begin{figure}[H]
-  \caption{Abstract representation of clone classes and clone instances.}
-    \medskip
-    \includegraphics[width=1\columnwidth]{img/context}
-  \label{fig:clonecontext}
-\end{figure}
-
-Figure \ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
-The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
-The location and contents of clones is measured on clone instance level.
-A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50).
-A clone instance contents consists of a list of all statements and declarations it spans.
-
 We analyzed the context of clones in a large corpus of open source projects.

### 2019-07-22 sections/experimentalsetup.tex
Experimental setup

--- 2019-07-22 sections/results.tex
@@
 \begin{enumerate}
-  \item \textbf{Same method}: All instances of the clone class are in the same method.
-  \item \textbf{Same class}: All instances of the clone class are in the same class.
+  \item \textbf{Same Method}: All instances of the clone class are in the same method.
+  \item \textbf{Same Class}: All instances of the clone class are in the same class.
   \item \textbf{Superclass}: All instances of the clone class are in a class that is child or parent of each other.
-  \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
-  \item \textbf{Sibling class}: All instances of the clone class have the same parent class.
-  \item \textbf{First cousin class}: All instances of the clone class have the same grandparent class.
-\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same inheritance hierarchy, but do not belong to any of the other categories.
-\item \textbf{Same external superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
+  \item \textbf{Ancestor Class}: All instances of the clone class are superclasses except for the direct superclass.
+  \item \textbf{Sibling Class}: All instances of the clone class have the same parent class.
+  \item \textbf{First Cousin Class}: All instances of the clone class have the same grandparent class.
+\item \textbf{Common Hierarchy Class}: All instances of the clone class belong to the same inheritance hierarchy, but do not belong to any of the other categories.
+\item \textbf{Same External Superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
 \item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
@@
 
-We analyzed
+We separate these relations into the following categories, because of their related refactoring opportunities:
+\begin{itemize}
+  \item \textbf{Common class}:
+  \item \textbf{Common Hierarchy}
+\end{itemize}
 
@@
 The following relations belong to
-
-\chapter{Results}
-
-\label{ch:results}
-In this chapter, we present the results of our experiments.
-
-\section{Thresholds} \label{sec:thresholds}
-\TODO{todo}
-
-\section{Context Analysis of Clones}\label{chap:clonecontextexpl}
-We analyzed the context of clones in a large corpus of open source projects.
-For these experiments, we used our CloneRefactor tool.
-These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in chapter \ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in chapter \ref{chap:clonelocation};  the content of clone instances are explained, measured and discussed in chapter \ref{chap:clonecontents}.
-
-\subsection{Clone detection results}
-Currently, we have implemented two clone detection algorithms into CloneRefactor.
-The first one finds clones by comparing tokens (excluding whitespace, comments and newlines), equal to the definition of type 1 clones in literature \cite{roy2007survey}.
-The second algorithm implements our type 1R, as explained in chapter \ref{chap:type1clones}.
-The differences between the clones found for these algorithms is displayed in Table \ref{table:clonedet}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{CloneRefactor clone detection results for the two different algorithms.} \label{table:clonedet}
-  \medskip
-\begin{tabular}{|l|l|l|}
-\hline
- & \textbf{Type 1} & \textbf{Type 1R} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines cloned\end{tabular} & 200,362 & 129,519 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of statements/\\declarations cloned\end{tabular} & 182,466 & 118,980 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of tokens cloned\end{tabular} & 1,582,845 & 973,596 \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-Looking at Table \ref{table:clonedet}, it becomes apparent that the type 1R algorithm finds significantly less clones than the type 1 algorithm.
-This indicates that about a third of the clones have textual equality, but are not actually equal when considering the types of expressions.
-This makes these clones less suitable for automated refactoring.
-
-\subsection{Relations Between Clone Instances} \label{chap:relationsinstances}
-When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances.
-This relation has a big impact on how a clone should be merged, in order to improve the software design in the process.
-In this chapter, we display measurements we conducted on the corpus introduced in chapter \ref{chap:corpus}.
-These measurements are based on an experiment by Fontana et al.
-\cite{fontana2015duplicated}, which we will briefly introduce in chapter \ref{chap:catcloneinstancerelations}.
-We use a vastly different setup, which is explained in chapter \ref{chap:oursetup}.
-We then show our results in chapter \ref{chap:ourmeasurements}.
-
-\subsubsection{Categorizing Clone Instance Relations}\label{chap:catcloneinstancerelations}
-Fontana et al.
-\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other.
-To do this, they first define several categories for the relation between clone instances in object-oriented languages.
-A few of these categories are shown in Figure \ref{fig:clonerelation}.
-These categories are as follows:
-\begin{enumerate}
-  \item \textbf{Same method}: All instances of the clone class are in the same method.
-  \item \textbf{Same class}: All instances of the clone class are in the same class.
-  \item \textbf{Superclass}: All instances of the clone class are children and parents of each other.
-  \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
-  \item \textbf{Sibling class}: All instances of the clone class have the same parent class.
-  \item \textbf{First cousin class}: All instances of the clone class have the same grandparent class.
-\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same hierarchy, but do not belong to any of the other categories.
-\item \textbf{Same external superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
-\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
-\end{enumerate}
-
-\begin{figure}[H]
-  \caption{Abstract figure displaying some relations of clone classes. Arrows represent superclass relations.}
-    \medskip
-    \centering
-    \includegraphics[width=0.6\columnwidth]{img/Relation}
-  \label{fig:clonerelation}
-\end{figure}
-Please note that none of these categories allow external classes (except for ``same external superclass'').
-So if two clone instances are related through external classes but do not share a common external superclass, it will be flagged as ``unrelated''.
-The main reason for this is that it is (often) not possible to refactor to external classes.
-
-\subsubsection{Our setup}\label{chap:oursetup}
-We use a similar setup to that used by Fontana et al.
-(Table~3 of Fontana et al.
-\cite{fontana2015duplicated}).
-Fontana et al.
-measure clones using their own tool (DCRA).
-As explained in chapter~\ref{ch:tool-overview}, we chose to implement our own tool, CloneRefactor.
-Therefore, the setup for our measurements differs as follows from Fontana et al.:
-\begin{itemize}
-  \item We consider clone classes rather than clone pairs. The rationale for this is given in chapter \ref{chap:cloneclasses}.
-\item We use different thresholds regarding when a clone should be considered.
-Fontana et al.
-seek clones that span a minimum of 7 source lines of code (SLOC).
-We seek clones with a minimum size of 6 statements/declarations.
-This is explained detail in chapter \ref{chap:thresholds}.
-\item We seek duplicates by statement/declaration rather than SLOC. This makes our analysis depend less on the coding style (in terms of newline usage) of the author of the software project.
-\item We test a broader range of projects.
-Fontana et al.
-use a set of 50 relatively large projects.
-We use the corpus as explained in \ref{chap:corpus}, which contains a diverse set of projects (diverse both in volume and code quality).
-\end{itemize}
-
-\subsection{Our results} \label{chap:ourmeasurements}
-Table~\ref{table:relations} contains our results regarding the relations between clone instances.
-In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our type 1R definition as explained in chapter \ref{chap:type1clones}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{Clone relations} \label{table:relations}
-  \medskip
-\begin{tabular}{|l|l|l|l|l|} \hline
-\textbf{Relation}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-Unrelated          & 6,134           & 35.48  & 4,762 & 38.14            \\ \hline
-\begin{tabular}[c]{@{}l@{}}Same\\Class\end{tabular}          & 4,772            & 27.60  & 3,131 & 25.07             \\ \hline
-Sibling            & 2,680            & 15.50   & 1,949 & 15.61            \\ \hline
-\begin{tabular}[c]{@{}l@{}}Same\\Method\end{tabular}         & 2,247            & 13.00   & 1,685 & 13.49             \\ \hline
-\begin{tabular}[c]{@{}l@{}}External\\Superclass\end{tabular} & 794            & 4.59   & 558 & 4.47             \\ \hline
-\begin{tabular}[c]{@{}l@{}}First\\Cousin\end{tabular}        & 269             & 1.56     & 197 & 1.58           \\ \hline
-Superclass         & 237             & 1.37     & 118 & 0.94           \\ \hline
-\begin{tabular}[c]{@{}l@{}}Common\\Hierarchy\end{tabular}    & 123             & 0.71    & 73 & 0.58            \\ \hline
-Ancestor           & 35              & 0.20     & 14 & 0.11          \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-The most notable difference when comparing it to the results of Fontana et al.
-\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (38.14\% with type 1R), while for them it was only 15.70\%.
-This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
-It could also be that the corpus which we use, as it has generally smaller projects, uses more classes from outside the project (which are marked ``Unrelated'' if they do not have a common external superclass).
-About a fourth of all clone classes have all instances in the same class, which is generally easy to refactor.
-On the third place come the ``Sibling'' clones, which can often be refactored using a pull-up refactoring.
-There are no noteworthy differences between type 1 and type 1R clones.
-
-\subsection{Clone instance location}\label{chap:clonelocation}
-After mapping the relations between individual clones, we looked at the location of individual clone instances.
-A paper by Lozano et al.
-\cite{lozano2007evaluating} discusses the harmfulness of cloning.
-The authors argue that 98\% are produced at method-level.
-However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
-We validated this claim over our corpus.
-The results for the clone instance locations are shown in Table \ref{table:locations}.
-We chose the following categories:
-\begin{enumerate}
-  \item \textbf{Method/Constructor Level:} A clone instance that does not exceed the boundaries of a single method or constructor (optionally including the declaration of the method or constructor itself).
-  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class (like field declarations, other methods, etc.).
-  \item \textbf{Interface Level:} A clone that is (a part of) an interface.
-  \item \textbf{Enumeration Level:} A clone that is (a part of) an enumeration.
-\end{enumerate}
-
-Please note that these results are measured over each clone instance rather than each clone class, hence the higher total amount in comparison to the results of chapter \ref{chap:ourmeasurements}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{Clone instance locations} \label{table:locations}
-  \medskip
-\begin{tabular}{|l|l|l|l|l|}
-\hline
-\textbf{Location}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-Method Level       & 32,861           & 66.02   & 19,075 & 58.23            \\ \hline
-Class Level        & 15,069           & 30.27   & 12,207 & 37.27            \\ \hline
-\begin{tabular}[c]{@{}l@{}}Constructor\\Level\end{tabular}  & 1,391            & 2.79     & 1,080 & 3.30           \\ \hline
-\begin{tabular}[c]{@{}l@{}}Interface\\Level\end{tabular}    & 282              & 0.57     & 247 & 0.75           \\ \hline
-Enum Level         & 171               & 0.34    & 147 & 0.45            \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-Our results indicate that around 58\% of the clones are produced at method-level.
-About 39\% of clones either span several methods/constructors or contain something like a field declaration.
-Another 3\% of the clones are found in constructors.
-The amount of clones found in interfaces and enumerations is very low.
-Regarding the differences between type 1 and type 1R, it seems that there are relatively less method level clones and more class level clones for type 1R.
-This is probably due to that the main reason for variability between type 1 and type 1R is variable references, which occur more at method level than class level.
-
-\section{Clone instance contents}\label{chap:clonecontents}
-Finally, we looked at the contents of individual clone instances: what kind of declarations and statements do they span. We selected the following categories to be relevant for refactoring:
-\begin{enumerate}
-  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
-  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially, optionally including its declaration.
-  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
-  \item \textbf{Only Fields:} A clone that spans only global variables.
-  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields and other things, like methods.
-  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
-  \item \textbf{Other:} Anything that does not match with above-stated categories.
-\end{enumerate}
-
-The results for these categories are displayed in Table \ref{table:contents}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{Clone instance contents} \label{table:contents}
-  \medskip
-\begin{tabular}{|l|l|l|l|l|}
-  \hline
-  \textbf{Contents} & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Partial\\Method\end{tabular}             & 32,214 & 64.72 & 18,791 & 57.37 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Several\\Methods\end{tabular}            & 10,542 & 21.18 & 8,514 & 25.99 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes\\Constructor\end{tabular}       & 1,772  & 3.56  & 1,213 & 3.70 \\ \hline
-  Includes Field                                                      & 1,681  & 3.38  & 1,487 & 4.54 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Partial\\Constructor\end{tabular}        & 1,389  & 2.79  & 1,078 & 3.29 \\ \hline
-  Only Fields                                                         & 962    & 1.93  & 888 & 2.71 \\ \hline
-  Full Method                                                         & 647    & 1.30  & 284 & 0.87 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Class\\Declaration\end{tabular} & 263    & 0.53  & 258 & 0.79 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Other\\Categories\end{tabular}           & 304    & 0.61  & 243 & 0.74 \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-Unsurprisingly, most clones span a part of a method.
-More than a quarter of the clones (for type 1R) span over several methods, which either requires more advanced refactoring techniques or indicates a non-harmful clone.
-
-\section{Merging duplicate code through refactoring} \label{sec:refactorability}
-The most used technique to merge clones is method extraction (creating a new method on basis of the contents of clones).
-However, method extraction cannot be applied in all cases.
-Sometimes a clone spans a statement partially (like a for-loop of which only it's declaration and a part of the body is cloned).
-Merging the clones can be harder in such instances.
-Also, the cloned code can contain statements like \texttt{return}, \texttt{break}, \texttt{continue}.
-In these instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.
-
-We measured the amount of clones that can be refactored through method extraction (without additional transformations being required).
-Our results are displayed in Table \ref{table:refactorability}.
-In this table we use the following categories:
-\begin{itemize}
-    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a method.
-Then, based on the relation between the clone instances, further refactoring techniques can be used to merge the extracted methods (for instance ``pull up method'' for clones in sibling classes).
-    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements.
-    \item \textbf{Spans part of a block:} This clone spans a part of a statement.
-    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table \ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
-\end{itemize}
-
-\begin{table}[H]
-  \begin{center}
-  \caption{Refactorability through method extraction} \label{table:refactorability}
-  \medskip
-\begin{tabular}{|l|l|l|l|l|}
-\hline
-\textbf{}        & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Is not a\\partial method\end{tabular}           & 5,917 & 34.22 & 4,806 & 38.49 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Complex\\control flow\end{tabular} & 5,511 & 31.87 & 3,158 & 25.29 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Spans part of\\a block\end{tabular}             & 3,989 & 23.07 & 3,152 & 25.24 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Can be\\extracted\end{tabular}                  & 1,874 & 10.84 & 1,371 & 10.98 \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-From Table \ref{table:refactorability}, we can see that approximately ten percent of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
-For the other clones, other techniques or transformations will be required.
-Looking into these techniques and transformations will be one of our next steps.

### 2019-07-22 sections/results.tex
Experimental setup

--- 2019-07-19 sections/results.tex
@@
-\chapter{Experimental setup}
-In this chapter we describe the setup we use for our experiments.
-Our most prominent contribution is the proposal of a tool called CloneRefactor.
-This tool allows us to map clones with all clone definitions as described in chapter \ref{chap:clonetypes}.
-
-All results of our experiments, as displayed in chapter \ref{ch:results}, are measured over a corpus of Java projects. In this chapter we will explain how we prepared this corpus.
-
-\section{The corpus}\label{chap:corpus}
-For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}.
-This corpus has been assembled to contain relatively higher quality projects.
-Also, any duplicate projects were removed from this corpus.
-This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
-
-As indicated in chapter \ref{chap:challenge} CloneRefactor requires all libraries of software projects we test.
-As these are not included in the used corpus \cite{githubCorpus2013}, we decided to filter the corpus to only include Maven projects.
-Maven is a build automation tool used primarily for Java, and works on basis of an \texttt{pom.xml} file to describe the projects' dependencies.
-As no \texttt{pom.xml} files are included in the corpus, we cloned the latest version of each project in the corpus.
-We then removed each project that has no \texttt{pom.xml} file.
-As a final step, we collected all dependencies for each project by using the \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib} Maven command, and removed each project for which not all dependencies were available (due to non-Maven dependencies being used or unsatisfiable dependencies being referenced in the \texttt{pom.xml} file).
-
-Some general data regarding this corpus is displayed in Table \ref{table:general}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{General results for GitHub Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
-  \medskip
-\begin{tabular}{|l|l|}
-\hline
-Amount of projects                                                                                      & 1,361      \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\whitespace, comments and newlines.)\end{tabular} & 1,414,996  \\ \hline
-Amount of statements/declarations                                                                       & 1,212,189  \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of tokens (excluding\\whitespace, comments and newlines.)\end{tabular} & 11,643,194 \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-\chapter{Results}
-
-\label{ch:results}
+\chapter{Results}\label{ch:results}
 In this chapter, we present the results of our experiments.
@@
 \section{Thresholds} \label{sec:thresholds}
+\TODO{todo}
 
-\section{Relation, Location and Content Analysis of Clones}\label{chap:clonecontextexpl}
-To be able to refactor code clones, it is very important to consider the context of the clone. We define the following aspects of the clone as its context:
-\begin{enumerate}
-  \item The relation of clone instances among each other through inheritance (for example: a clone instance resides in a superclass of another clone instance in the same clone class).
-  \item Where a clone instance occurs in the code (for example: a method-level clone is a clone instance that is in a method).
-  \item The contents of a clone instance (for example: the clone instance spans several methods).
-\end{enumerate}
-
-\begin{figure}[H]
-  \caption{Abstract representation of clone classes and clone instances.}
-    \medskip
-    \includegraphics[width=1\columnwidth]{img/context}
-  \label{fig:clonecontext}
-\end{figure}
-
-Figure \ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
-The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
-The location and contents of clones is measured on clone instance level.
-A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50).
-A clone instance contents consists of a list of all statements and declarations it spans.
-
+\section{Context Analysis of Clones}\label{chap:clonecontextexpl}
 We analyzed the context of clones in a large corpus of open source projects.

### 2019-07-22 sections/experimentalsetup.tex
Just thought I'd explain this

@@
   \item \textbf{First Cousin Class}: All instances of the clone class have the same grandparent class.
-\item \textbf{Common Hierarchy Class}: All instances of the clone class belong to the same inheritance hierarchy, but do not belong to any of the other categories.
+\item \textbf{Same Hierarchy Class}: All instances of the clone class belong to the same inheritance hierarchy, but do not belong to any of the other categories.
 \item \textbf{Same External Superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
@@
 \begin{itemize}
-  \item \textbf{Common class}:
-  \item \textbf{Common Hierarchy}
+  \item \textbf{Common Class}: \textit{Same Method}, \textit{Same Class}
+  \item \textbf{Common Hierarchy}: \textit{Superclass}, \textit{Ancestor Class}, \textit{Sibling Class}, \textit{First Cousin}, \textit{Same Hierarchy}
+  \item \textbf{Common Interface}: \textit{Same Interface}
+  \item \textbf{Effectively Unrelated}: \textit{No Direct Superclass}, \textit{No Indirect Superclass}, \textit{External Superclass}, \textit{Unrelated}
 \end{itemize}
 
-\subsubsection{Same Class}
+Every clone class only has a single relation, which is the first relation from above list that the clone class applies to.
+For instance: all ``Superclass'' clones also apply to ``Same Hierarchy'', but because ``Superclass'' is earlier in above list they will get the ``Superclass'' relation.
+This is because the items earlier in the list denote a more favorable refactoring.
+
+\subsubsection{Common Class}
 The \textit{``Same method''} and \textit{``Same class''} relations share a common refactoring opportunity.
@@
 
-\subsubsection{Same Hierarchy}
+\subsubsection{Common Hierarchy}
 The following relations belong to

### 2019-07-22 sections/background.tex
Maven
Example for inner clone class duplication
Internal and external classes

--- 2019-07-19 sections/background.tex
@@
 \definecolor{lightyellow}{HTML}{fffdcc}
+\definecolor{doublelightyellow}{HTML}{fffa9c}
 \newcommand{\highlightYellow}{\makebox[0pt][l]{\color{lightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
-\newcommand{\highlightDarkyellow}{\makebox[0pt][l]{\color{yellow}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightDarkyellow}{\makebox[0pt][l]{\color{doublelightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
 \begin{figure}[H]
@@
 Analyzing these before- and after states of the source code will provide more insights that will help to rank clones based on their harmfulness.
+
+\section{Internal and external classes}
+In this study we differentiate between \textit{internal} and \textit{external} classes.
+Classes are the components of a software system that contain its functionality.
+When analyzing a software system, \textit{Internal classes} are classes that belong to this software system specifically, and its source code is included in the project.
+
+\textit{External classes} are classes that a software system uses, but do not belong to this specific software system.
+Typically, the source code of external classes are not included in the source code of the project.
+Most often these external dependencies are referenced in a file that its build automation system uses to fetch a projects' dependencies.
+
+Regarding refactoring, a software system can often not change the source code of its dependencies.
+This can sometimes be a burden, when an external dependency does not use proper abstractions that are required by a software system.
+Because of that, in this study, we consider external classes to see what impact they have on the refactoring process.
+
+\subsection{Maven}
+For this study we perform a shallow analysis on external dependencies, in order to derive more context for internally used concepts.
+As these external dependencies are most often not included in a software systems' source code, we must first use the projects' build automation system to gather the dependencies.
+To limit the scope of this process, we decided to focus on only the \textit{Maven} build automation system.
+
+Maven is a build automation tool, mainly used with the Java programming language.
+Maven has a simple ecosystem to configure and fetch the binaries and source code of all software projects a given codebase is dependent on.
+Maven can also be used to run tests for the systems and to package the project as an executable file.

### 2019-07-22 sections/experimentalsetup.tex
Working on results

@@
 \begin{figure}[H]
+    \includegraphics[width=0.6\columnwidth]{img/context}
     \caption{Abstract representation of clone classes and clone instances.}
-    \medskip
-    \includegraphics[width=1\columnwidth]{img/context}
   \label{fig:clonecontext}
@@
 
-\subsection{Relation}
+\subsection{Relation}\label{sec:setuprelationsinstances}
 When merging code clones in object-oriented languages, it is important to consider the inheritance relation between clone instances. This relation has a big impact on how a clone should be refactored.
@@
 The following relations belong to
+\todo{TODO}
+
+\subsubsection{Common Interface}
+\todo{TODO}
+
+\subsubsection{Effectively Unrelated}
+\todo{TODO}

### 2019-07-22 sections/results.tex
Working on results

@@
 \subsection{Relations Between Clone Instances} \label{chap:relationsinstances}
-When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances.
-This relation has a big impact on how a clone should be merged, in order to improve the software design in the process.
-In this chapter, we display measurements we conducted on the corpus introduced in chapter \ref{chap:corpus}.
-These measurements are based on an experiment by Fontana et al.
-\cite{fontana2015duplicated}, which we will briefly introduce in chapter \ref{chap:catcloneinstancerelations}.
-We use a vastly different setup, which is explained in chapter \ref{chap:oursetup}.
-We then show our results in chapter \ref{chap:ourmeasurements}.
-
-\subsubsection{Categorizing Clone Instance Relations}\label{chap:catcloneinstancerelations}
-Fontana et al.
-\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other.
-To do this, they first define several categories for the relation between clone instances in object-oriented languages.
-A few of these categories are shown in Figure \ref{fig:clonerelation}.
-These categories are as follows:
-\begin{enumerate}
-  \item \textbf{Same method}: All instances of the clone class are in the same method.
-  \item \textbf{Same class}: All instances of the clone class are in the same class.
-  \item \textbf{Superclass}: All instances of the clone class are children and parents of each other.
-  \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
-  \item \textbf{Sibling class}: All instances of the clone class have the same parent class.
-  \item \textbf{First cousin class}: All instances of the clone class have the same grandparent class.
-\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same hierarchy, but do not belong to any of the other categories.
-\item \textbf{Same external superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
-\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
-\end{enumerate}
-
-\begin{figure}[H]
-  \caption{Abstract figure displaying some relations of clone classes. Arrows represent superclass relations.}
-    \medskip
-    \centering
-    \includegraphics[width=0.6\columnwidth]{img/Relation}
-  \label{fig:clonerelation}
-\end{figure}
-Please note that none of these categories allow external classes (except for ``same external superclass'').
-So if two clone instances are related through external classes but do not share a common external superclass, it will be flagged as ``unrelated''.
-The main reason for this is that it is (often) not possible to refactor to external classes.
-
-\subsubsection{Our setup}\label{chap:oursetup}
-We use a similar setup to that used by Fontana et al.
-(Table~3 of Fontana et al.
-\cite{fontana2015duplicated}).
-Fontana et al.
-measure clones using their own tool (DCRA).
-As explained in chapter~\ref{ch:tool-overview}, we chose to implement our own tool, CloneRefactor.
-Therefore, the setup for our measurements differs as follows from Fontana et al.:
-\begin{itemize}
-  \item We consider clone classes rather than clone pairs. The rationale for this is given in chapter \ref{chap:cloneclasses}.
-\item We use different thresholds regarding when a clone should be considered.
-Fontana et al.
-seek clones that span a minimum of 7 source lines of code (SLOC).
-We seek clones with a minimum size of 6 statements/declarations.
-This is explained detail in chapter \ref{chap:thresholds}.
-\item We seek duplicates by statement/declaration rather than SLOC. This makes our analysis depend less on the coding style (in terms of newline usage) of the author of the software project.
-\item We test a broader range of projects.
-Fontana et al.
-use a set of 50 relatively large projects.
-We use the corpus as explained in \ref{chap:corpus}, which contains a diverse set of projects (diverse both in volume and code quality).
-\end{itemize}
-
-\subsection{Our results} \label{chap:ourmeasurements}
+In section \ref{sec:setuprelationsinstances} we introduced our experiments regarding relations between clones.
 Table~\ref{table:relations} contains our results regarding the relations between clone instances.

### 2019-07-22 sections/results.tex
Results update

@@
 \section{Thresholds} \label{sec:thresholds}
-\TODO{todo}
+\todo{todo}
 
@@
 Table~\ref{table:relations} contains our results regarding the relations between clone instances.
-In this table, ``T1'' stands for the type 1 algorithm from literature and ``1R'' stands for our type 1R definition as explained in chapter \ref{chap:type1clones}.
 
@@
   \medskip
-\begin{tabular}{|l|l|l|l|l|} \hline
-\textbf{Relation}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-Unrelated          & 6,134           & 35.48  & 4,762 & 38.14            \\ \hline
-\begin{tabular}[c]{@{}l@{}}Same\\Class\end{tabular}          & 4,772            & 27.60  & 3,131 & 25.07             \\ \hline
-Sibling            & 2,680            & 15.50   & 1,949 & 15.61            \\ \hline
-\begin{tabular}[c]{@{}l@{}}Same\\Method\end{tabular}         & 2,247            & 13.00   & 1,685 & 13.49             \\ \hline
-\begin{tabular}[c]{@{}l@{}}External\\Superclass\end{tabular} & 794            & 4.59   & 558 & 4.47             \\ \hline
-\begin{tabular}[c]{@{}l@{}}First\\Cousin\end{tabular}        & 269             & 1.56     & 197 & 1.58           \\ \hline
-Superclass         & 237             & 1.37     & 118 & 0.94           \\ \hline
-\begin{tabular}[c]{@{}l@{}}Common\\Hierarchy\end{tabular}    & 123             & 0.71    & 73 & 0.58            \\ \hline
-Ancestor           & 35              & 0.20     & 14 & 0.11          \\ \hline
+\begin{tabular}{|l|l|l|} \hline
+\textbf{Relation} & \textbf{\#} & \textbf{\%} \\ \hline
+Unrelated          & 12,368 & 34.88            \\ \hline
+Same Class          & 11,483 & 32.38             \\ \hline
+Same Method               & 5,056 & 14.26            \\ \hline
+Sibling         & 4,182 & 11.79             \\ \hline
+External Superclass   & 1,066 & 3.01             \\ \hline
+Superclass          & 558 & 1.57           \\ \hline
+First Cousin          & 489 & 1.38           \\ \hline
+Common Hierarchy    & 206 & 0.58            \\ \hline
+Ancestor          & 54 & 0.15          \\ \hline
 \end{tabular}
@@
 
-The most notable difference when comparing it to the results of Fontana et al.
-\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (38.14\% with type 1R), while for them it was only 15.70\%.
-This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
+The most notable difference when comparing it to the results of Fontana et al.~\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (34.44\%), while for them it was only 15.70\%.
+This is likely due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
 It could also be that the corpus which we use, as it has generally smaller projects, uses more classes from outside the project (which are marked ``Unrelated'' if they do not have a common external superclass).
-About a fourth of all clone classes have all instances in the same class, which is generally easy to refactor.
-On the third place come the ``Sibling'' clones, which can often be refactored using a pull-up refactoring.
-There are no noteworthy differences between type 1 and type 1R clones.
+About a third of all clone classes have all instances in the same class, which is generally easy to refactor.
+On the third place come the clones that are in the same method, which are similarly easy to refactor.
 

### 2019-07-22 sections/experimentalsetup.tex
Moving stuff around

@@
 
-\subsection{Relation}\label{sec:setuprelationsinstances}
+\subsection{Relation}\label{sec:setuprelation}
 When merging code clones in object-oriented languages, it is important to consider the inheritance relation between clone instances. This relation has a big impact on how a clone should be refactored.
@@
 \todo{TODO}
+
+\subsection{Location}\label{sec:setuplocation}
+A paper by Lozano et al.
+\cite{lozano2007evaluating} discusses the harmfulness of cloning.
+The authors argue that 98\% are produced at method-level.
+However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
+We validated this claim over our corpus.
+The results for the clone instance locations are shown in Table \ref{table:locations}.
+We chose the following categories:
+\begin{enumerate}
+  \item \textbf{Method/Constructor Level:} A clone instance that does not exceed the boundaries of a single method or constructor (optionally including the declaration of the method or constructor itself).
+  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class (like field declarations, other methods, etc.).
+  \item \textbf{Interface Level:} A clone that is (a part of) an interface.
+  \item \textbf{Enumeration Level:} A clone that is (a part of) an enumeration.
+\end{enumerate}
+
+\subsection{Contents}\label{sec:setupcontents}
+Finally, we looked at what nodes individual clone instances span. We selected the following categories to be relevant for refactoring:
+\begin{enumerate}
+  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
+  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially, optionally including its declaration.
+  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
+  \item \textbf{Only Fields:} A clone that spans only global variables.
+  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields and other things, like methods.
+  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
+  \item \textbf{Other:} Anything that does not match with above-stated categories.
+\end{enumerate}

### 2019-07-22 sections/results.tex
Moving stuff around

@@
 \subsection{Relations Between Clone Instances} \label{chap:relationsinstances}
-In section \ref{sec:setuprelationsinstances} we introduced our experiments regarding relations between clones.
-Table~\ref{table:relations} contains our results regarding the relations between clone instances.
+In section \ref{sec:setuprelation} we introduced our experiments regarding relations between clones. Table~\ref{table:relations} contains our results regarding the relations between clone instances.
 
@@
 \subsection{Clone instance location}\label{chap:clonelocation}
-After mapping the relations between individual clones, we looked at the location of individual clone instances.
-A paper by Lozano et al.
-\cite{lozano2007evaluating} discusses the harmfulness of cloning.
-The authors argue that 98\% are produced at method-level.
-However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
-We validated this claim over our corpus.
-The results for the clone instance locations are shown in Table \ref{table:locations}.
-We chose the following categories:
-\begin{enumerate}
-  \item \textbf{Method/Constructor Level:} A clone instance that does not exceed the boundaries of a single method or constructor (optionally including the declaration of the method or constructor itself).
-  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class (like field declarations, other methods, etc.).
-  \item \textbf{Interface Level:} A clone that is (a part of) an interface.
-  \item \textbf{Enumeration Level:} A clone that is (a part of) an enumeration.
-\end{enumerate}
-
-Please note that these results are measured over each clone instance rather than each clone class, hence the higher total amount in comparison to the results of chapter \ref{chap:ourmeasurements}.
+Measuring the clone locations categories defined in section \ref{sec:setuplocation} yields the results displayed in Table \ref{table:contents}.
 
@@
 \section{Clone instance contents}\label{chap:clonecontents}
-Finally, we looked at the contents of individual clone instances: what kind of declarations and statements do they span. We selected the following categories to be relevant for refactoring:
-\begin{enumerate}
-  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
-  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially, optionally including its declaration.
-  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
-  \item \textbf{Only Fields:} A clone that spans only global variables.
-  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields and other things, like methods.
-  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
-  \item \textbf{Other:} Anything that does not match with above-stated categories.
-\end{enumerate}
-
-The results for these categories are displayed in Table \ref{table:contents}.
+Measuring the clone contents categories defined in section \ref{sec:setupcontents} yields the results displayed in Table \ref{table:contents}.
 

### 2019-07-22 sections/results.tex
New results

@@
   \medskip
-\begin{tabular}{|l|l|l|l|l|}
+\begin{tabular}{|l|l|l|}
 \hline
-\textbf{Location}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-Method Level       & 32,861           & 66.02   & 19,075 & 58.23            \\ \hline
-Class Level        & 15,069           & 30.27   & 12,207 & 37.27            \\ \hline
-\begin{tabular}[c]{@{}l@{}}Constructor\\Level\end{tabular}  & 1,391            & 2.79     & 1,080 & 3.30           \\ \hline
-\begin{tabular}[c]{@{}l@{}}Interface\\Level\end{tabular}    & 282              & 0.57     & 247 & 0.75           \\ \hline
-Enum Level         & 171               & 0.34    & 147 & 0.45            \\ \hline
+\textbf{Location}   & \textbf{\#} & \textbf{\%} \\ \hline
+Method Level        & 83,813 & 82.62            \\ \hline
+Class Level        & 12,534 & 12.35            \\ \hline
+Constructor Level    & 4,391 & 4.33           \\ \hline
+Interface Level   & 567 & 0.56           \\ \hline
+Enum Level         & 145 & 0.14            \\ \hline
 \end{tabular}
@@
   \medskip
-\begin{tabular}{|l|l|l|l|l|}
+\begin{tabular}{|l|l|l|}
   \hline
-  \textbf{Contents} & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Partial\\Method\end{tabular}             & 32,214 & 64.72 & 18,791 & 57.37 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Several\\Methods\end{tabular}            & 10,542 & 21.18 & 8,514 & 25.99 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes\\Constructor\end{tabular}       & 1,772  & 3.56  & 1,213 & 3.70 \\ \hline
-  Includes Field                                                      & 1,681  & 3.38  & 1,487 & 4.54 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Partial\\Constructor\end{tabular}        & 1,389  & 2.79  & 1,078 & 3.29 \\ \hline
-  Only Fields                                                         & 962    & 1.93  & 888 & 2.71 \\ \hline
-  Full Method                                                         & 647    & 1.30  & 284 & 0.87 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Includes Class\\Declaration\end{tabular} & 263    & 0.53  & 258 & 0.79 \\ \hline
-  \begin{tabular}[c]{@{}l@{}}Other\\Categories\end{tabular}           & 304    & 0.61  & 243 & 0.74 \\ \hline
+  \textbf{Contents} & \textbf{\#} & \textbf{\%} \\ \hline
+  Partial Method     & 79,945 & 78.80 \\ \hline
+  Several Methods         & 7,323 & 7.22 \\ \hline
+  Partial Constructor      & 4,385 & 4.32 \\ \hline
+  Full Method           & 3,868 & 3.81 \\ \hline
+  Only Fields           & 3,039 & 3.00 \\ \hline
+  Includes Constructor  & 1,522 & 1.50 \\ \hline
+  Includes Field        & 616 & 0.61 \\ \hline
+  Includes Class Declaration  & 376 & 0.37 \\ \hline
+  Other Categories    & 376 & 0.37\\ \hline
 \end{tabular}
@@
 Unsurprisingly, most clones span a part of a method.
-More than a quarter of the clones (for type 1R) span over several methods, which either requires more advanced refactoring techniques or indicates a non-harmful clone.
+The most used refactoring technique for clones that span part of a method is ``Extract Method''.
+Because of that, we focus our research efforts on refactoring such clones.
 
@@
   \medskip
-\begin{tabular}{|l|l|l|l|l|}
+\begin{tabular}{|l|l|l|}
 \hline
-\textbf{}        & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Is not a\\partial method\end{tabular}           & 5,917 & 34.22 & 4,806 & 38.49 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Complex\\control flow\end{tabular} & 5,511 & 31.87 & 3,158 & 25.29 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Spans part of\\a block\end{tabular}             & 3,989 & 23.07 & 3,152 & 25.24 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Can be\\extracted\end{tabular}                  & 1,874 & 10.84 & 1,371 & 10.98 \\ \hline
+\textbf{}         & \textbf{\#} & \textbf{\%} \\ \hline
+Can be extracted     & 14,664 & 41.35 \\ \hline
+Spans part of a block  & 10,801 & 30.46 \\ \hline
+Is not a partial method   & 8,074 & 22.77 \\ \hline
+Complex control flow & 1,922 & 5.42 \\ \hline
 \end{tabular}
@@
 
-From Table \ref{table:refactorability}, we can see that approximately ten percent of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
+From Table~\ref{table:refactorability}, we can see that 41\% of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
 For the other clones, other techniques or transformations will be required.
-Looking into these techniques and transformations will be one of our next steps.

### 2019-07-22 sections/experimentalsetup.tex
Refactorability stuff

@@
 \end{enumerate}
+
+\section{Method extraction opportunities}\label{sec:refactorabilitysetup}
+The most used technique to refactor clones is method extraction (creating a new method on basis of the contents of clones).
+However, method extraction cannot be applied in all cases.
+In these instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.
+
+We measured the number of clones that can be refactored through method extraction (without additional transformations being required). We defined the following categories:
+\begin{itemize}
+    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a method.
+Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
+    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
+    \item \textbf{Spans part of a block:} This clone spans a part of a statement.
+    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table~\ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
+\end{itemize}

### 2019-07-22 sections/results.tex
Refactorability stuff

@@
 \section{Merging duplicate code through refactoring} \label{sec:refactorability}
-The most used technique to merge clones is method extraction (creating a new method on basis of the contents of clones).
-However, method extraction cannot be applied in all cases.
-Sometimes a clone spans a statement partially (like a for-loop of which only it's declaration and a part of the body is cloned).
-Merging the clones can be harder in such instances.
-Also, the cloned code can contain statements like \texttt{return}, \texttt{break}, \texttt{continue}.
-In these instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.
-
-We measured the amount of clones that can be refactored through method extraction (without additional transformations being required).
+In section \ref{sec:refactorabilitysetup} we define catagories regarding the extent to which clones can be refactored through method extraction.
 Our results are displayed in Table \ref{table:refactorability}.
-In this table we use the following categories:
-\begin{itemize}
-    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a method.
-Then, based on the relation between the clone instances, further refactoring techniques can be used to merge the extracted methods (for instance ``pull up method'' for clones in sibling classes).
-    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements.
-    \item \textbf{Spans part of a block:} This clone spans a part of a statement.
-    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table \ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
-\end{itemize}
 
@@
 For the other clones, other techniques or transformations will be required.
+
+\section{Refactoring clones}
+\todo{TODO}

### 2019-07-22 sections/experimentalsetup.tex
Describe common hierarchy

@@
 \subsubsection{Common Hierarchy}
-The following relations belong to
-\todo{TODO}
+Clones that are in a common hierarchy can be refactored by using the ``Extract Method'' refactoring method followed by ``Pull Up Method'' until the method reaches a location that is accessible by all clone instances.
+However, the more often ``Pull Up Method'' has to be used, the more detrimental the effect is on system design.
+This is because putting a lot of functionality in classes higher up in an inheritance structure can result in the ``God Object'' anti-pattern.
+A god object is an object that knows too much or does too much.
 

### 2019-07-22 sections/experimentalsetup.tex
Fixed stuff
OKay this is harder than I thought

@@
 \begin{figure}[H]
-    \includegraphics[width=0.6\columnwidth]{img/context}
+  \centering
+    \includegraphics[width=0.8\columnwidth]{img/context}
     \caption{Abstract representation of clone classes and clone instances.}
@@
 \begin{figure}[H]
+  \centering
+    \includegraphics[width=0.6\columnwidth]{img/Relation}
       \caption{Abstract figure displaying relations of clone classes. Arrows represent superclass relations.}
-    \medskip
-    \includegraphics[width=1\columnwidth]{img/Relation}
   \label{fig:clonerelation}
@@
 
+To check a the relation for a given clone class, we compare each node in a clone instance with the respective nodes in each other clone instance within a clone class.
+So for a clone class with x clone instances and each clone instance has y nodes, we perform:
+
+\begin{equation}\label{eq:sameclass}
+((x)(x + 1) / 2) * y
+\end{equation}
+
+comparisons to determine the relation.
+Each of these checks will result in one of the relations from the list above.
+Of these relations, the item lowest in the list is going to be the relation of the clone class.
+So for instance, if a clone class has 15 nodes that denote a \textit{Superclass} relation but 3 nodes are \textit{Unrelated}, the clone class becomes \textit{Unrelated}.
+
 \subsubsection{Common Class}
@@
 
-A clone class is flagged as ``Same method'' if all clone instances in the clone class are in the same method:
-
-\begin{equation}\label{eq:samemethod}
-\forall (i_1 \in C) \forall (i_2 in C) Mi_1 = Mi_2
-\end{equation}
-
-Where \textit{M} is the method in which a clone instance is found.
+A clone class is flagged as ``Same method'' if all clone instances in the clone class are in the same method.
+We check this relation for each node in a clone instance with each other node in each other clone instance within a clone class.
+We define the method as the first method declaration that is found when tracing  from a node in the clone instance.
 Please note that a clone instance may not always be in a method, for which this predicate will fail.
@@
 
-A clone class is flagged as ``Same class'' if all clone instances in the clone class are in the same class:
-
-\begin{equation}\label{eq:samemethod}
-\forall (i_1 \in C) \forall (i_2 in C) Di_1 = Di_2
-\end{equation}
-
-Where \textit{D} is the class declaration in which the clone instance is found.
+A clone class is flagged as ``Same class'' if all clone instances in the clone class are in the same class.
+We define the class as the first class declaration that is encountered when following the parent nodes in the ast for a given cloned node.
 
@@
 A god object is an object that knows too much or does too much.
+
+\begin{equation}\label{eq:sameclass}
+\forall (i_1 \in C)\text{ }\forall (i_2 \in C)\text{ }Si_1 = Di_2 \lor Si_2 = Di_1
+\end{equation}
+
+Where\
 

### 2019-07-22 sections/experimentalsetup.tex
Relation setup stuff

@@
   \item \textbf{Common Class}: \textit{Same Method}, \textit{Same Class}
-  \item \textbf{Common Hierarchy}: \textit{Superclass}, \textit{Ancestor Class}, \textit{Sibling Class}, \textit{First Cousin}, \textit{Same Hierarchy}
+  \item \textbf{Common Hierarchy}: \textit{Superclass}, \textit{Sibling Class}, \textit{Ancestor Class}, \textit{First Cousin}, \textit{Same Hierarchy}
   \item \textbf{Common Interface}: \textit{Same Interface}
@@
 \subsubsection{Common Class}
-The \textit{``Same method''} and \textit{``Same class''} relations share a common refactoring opportunity.
+The \textit{Same method} and \textit{Same class} relations share a common refactoring opportunity.
 Clones of both these catagories, when extracted to a new method, can be placed in the same class.
@@
 
-A clone class is flagged as ``Same method'' if all clone instances in the clone class are in the same method.
-We check this relation for each node in a clone instance with each other node in each other clone instance within a clone class.
-We define the method as the first method declaration that is found when tracing  from a node in the clone instance.
+Cloned nodes are flagged as \textit{Same method} if these nodes are found in the same method.
+We define the method as the first method declaration that is encountered when following the parent nodes in the ast for a given cloned node.
 Please note that a clone instance may not always be in a method, for which this predicate will fail.
-Each node in a clone instance is checked for this predicate, so if a single node of a clone instance is outside a method, the predicate will fail.
 
-A clone class is flagged as ``Same class'' if all clone instances in the clone class are in the same class.
+Cloned nodes are flagged as \textit{Same class} if these nodes are found in the same class.
 We define the class as the first class declaration that is encountered when following the parent nodes in the ast for a given cloned node.
@@
 
-\begin{equation}\label{eq:sameclass}
-\forall (i_1 \in C)\text{ }\forall (i_2 \in C)\text{ }Si_1 = Di_2 \lor Si_2 = Di_1
-\end{equation}
+Cloned nodes are flagged as \textit{Superclass} if the classes in which these clones are found are parent and child class of each other.
+Here, the classes of these nodes follow the same definition as stated in the previous section.
 
-Where\
+Cloned nodes are flagged as \textit{Siblings} if the classes in which these clones are found all share the same parent and this parent class is not external.
+
+Cloned nodes are flagged as \textit{First Cousin} if the classes in which these clones are found all share the same parent and this parent class is not external.
 

### 2019-07-22 sections/experimentalsetup.tex
Common interface

@@
   \item \textbf{Superclass}: All instances of the clone class are in a class that is child or parent of each other.
+  \item \textbf{Sibling Class}: All instances of the clone class have the same parent class.
     \item \textbf{Ancestor Class}: All instances of the clone class are superclasses except for the direct superclass.
-  \item \textbf{Sibling Class}: All instances of the clone class have the same parent class.
   \item \textbf{First Cousin Class}: All instances of the clone class have the same grandparent class.
@@
 \begin{equation}\label{eq:sameclass}
-((x)(x + 1) / 2) * y
+\frac{x * (x + 1)}{2} * y
 \end{equation}
@@
 
-Cloned nodes are flagged as \textit{Superclass} if the classes in which these clones are found are parent and child class of each other.
-Here, the classes of these nodes follow the same definition as stated in the previous section.
+Cloned nodes are flagged as \textit{Superclass} if the classes in which these nodes are found are parent and child class of each other.
+Cloned nodes are flagged as \textit{Siblings} if the classes in which these nodes are found all share the same parent and this parent class is not external.
+Cloned nodes are flagged as \textit{First Cousin} if the classes in which these nodes are found all share the same grandparent and this grandparent class is not external.
 
-Cloned nodes are flagged as \textit{Siblings} if the classes in which these clones are found all share the same parent and this parent class is not external.
-
-Cloned nodes are flagged as \textit{First Cousin} if the classes in which these clones are found all share the same parent and this parent class is not external.
+Cloned nodes are flagged as \textit{Ancestor} if the classes in which these nodes are found are recursively the parent of an antecedent.
+Cloned nodes are flagged as \textit{Same Hierarchy} if the classes in which these nodes are found are all in the same inheritance hierarchy and not linked by any external classes.
 
 \subsubsection{Common Interface}
-\todo{TODO}
+Many object-oriented languages know the concept of ``interfaces'', which are used to specify a behavior that classes must implement.
+As code clones describe functionality and interfaces originally did not allow for functionality, interfaces did not open up refactoring opportunities for duplicated code.
+However, many programming languages nowadays support default implementations in interfaces.
+Since Java 7 and C\#8, these programming languages allow for functionality to be defined in interfaces.
+Many other object-oriented languages like Python allow this by nature, as they do not have a true notion of interfaces.
+
+The greatest downside on system design of putting functionality in interfaces is that interfaces are per definition part of a classes' public contract.
+That is, all functionality that is shared between classes via an interface cannot be hidden by setting a stricter visibility.
+Because of that, we favor all ``Common Hierarchy'' refactoring opportunities over ``Common Interface''.
+
+To check whether two cloned nodes have common interfaces, we recursively walk all types the class or interface of the cloned nodes implement and extend.
+The common interface that is closest to the cloned node in terms of depth of recursion will be flagged as the refactoring candidate.
 

### 2019-07-22 sections/related_work.tex
Common interface

@@
-\chapter{Related work}
-\label{ch:related_work}
-We divide the related work into ... categories:  ...
+\chapter{Related work} \label{ch:related_work}
+\todo{Rewrite this part and add a lot of content}
+The Duplicated Code Refactoring Advisor (DCRA) looks into refactoring opportunities for clone pairs~\cite{fontana2012duplicated, fontana2015duplicated}.
+DCRA only focuses on refactoring clone pairs, with the authors arguing that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.
+We further look into these measurements in Sec.~\ref{chap:relationsinstances}.
+
+A tool named Aries~\cite{higo2004aries, higo2008metric} focuses on the detection of refactorable clones.
+They do this based on the relation between clone instances through inheritance, similar to Fontana et al.~\cite{fontana2012duplicated}.
+This tool only proposes a refactoring opportunity and does not provide help in the process of applying the refactoring.
+
+We investigated several research efforts that look into code clone refactoring~\cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}.
+However, all of these tools only support a subset of all harmful clones that are found.
+Also, these tools are limited to suggesting refactoring opportunities, rather than actually applying refactorings where suitable.
+Finally, all published approaches have limitations, such as false positives in their clone detection~\cite{chen2018clone} or being limited to clone pairs~\cite{higo2008metric}.

### 2019-07-22 sections/experimentalsetup.tex
Unrelated

@@
 \item \textbf{No Indirect Superclass}: All instances of the clone class are in a class that does not have any external classes in its inheritance hierarchy.
+\item \textbf{External Ancestor}: All instances of the clone class are in a class that does not have any external classes in its inheritance hierarchy.
 \end{enumerate}
@@
   \item \textbf{Common Interface}: \textit{Same Interface}
-  \item \textbf{Effectively Unrelated}: \textit{No Direct Superclass}, \textit{No Indirect Superclass}, \textit{External Superclass}, \textit{Unrelated}
+  \item \textbf{Unrelated}: \textit{No Direct Superclass}, \textit{No Indirect Superclass}, \textit{External Superclass}, \textit{External Ancestor}
 \end{itemize}
@@
 
-\subsubsection{Effectively Unrelated}
-\todo{TODO}
+\subsubsection{Unrelated}
+Clones are unrelated if they share no common class or interface in their inheritance structure.
+These clones are least favorable when looking at refactoring, because their refactoring will almost always have a major impact on system design.
+We formulated four catagories of unrelated clones to look into their refactoring opportunities.
+
+Cloned nodes are flagged \textit{No Direct Superclass} if they are in classes that do currently not have a parent.
+This marks the opportunity for creating a superclass abstraction and placing the extracted method there.
+Cloned nodes are flagged \textit{No Indirect Superclass} if any of their ancestors does not have a parent.
+In such a case, it would be possible to create such an abstraction for the ancestor that does not have a parent.
+
+Cloned nodes are flagged \textit{External Superclass} if they are in a class which has an external parent.
+Cloned nodes are flagged \textit{External Ancestor} if one of their ancestors has an external parent.
+Both of these relations obstruct the possibility of creating a superclass abstraction.
+In such a case, an interface abstraction could be created to make their relation explicit.
 

### 2019-07-22 sections/experimentalsetup.tex
Explaining location

@@
 However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
-We validated this claim over our corpus.
-The results for the clone instance locations are shown in Table \ref{table:locations}.
+We decided to measure the locations of clones through static analysis on our dataset.
 We chose the following categories:
@@
 \end{enumerate}
+We check the location of each clone instance for each of its nodes.
+If any node reports a different location from the others, we choose the location that is lowest in above list.
+So for instance, if a clone instance has 15 nodes that denote a \textit{Method Level} location but 3 nodes are \textit{Class Level}, the clone instance becomes \textit{Class Level}.
 

### 2019-07-22 sattose/paper.tex
Updated the paper
Added clone type results

@@
 \subsection{Clone types}\label{sec:clonetypeexperiments}
-In this chapter we display the differences between clone type 1-3~\cite{roy2007survey} and type 1R-3R as proposed in Sec.
+In this section we display the differences between clone type 1-3~\cite{roy2007survey} and type 1R-3R as proposed in Sec.
 \ref{sec:rtypes}.
@@
 Although this data is partly dependent on our implementation of the clone types, there is a notable difference between the refactoring-oriented clone types and the literature clone types.
-The reason for this is further explained in Sec.
-\ref{chap:challenge}.
+The reason for this is further explained in Sec.~\ref{chap:challenge}.
 
@@
   \caption{Duration in minutes of identifying clones for clone type definitions.}
-    \includegraphics[width=1\columnwidth]{img/DurationChart}
+    \includegraphics[width=.95\columnwidth]{img/DurationChart}
   \label{fig:performance}

### 2019-07-22 sections/results.tex
Added clone type results

@@
 In this chapter, we present the results of our experiments.
+
+\section{Clone types}\label{sec:clonetypeexperiments}
+In this section we display the differences between clone type 1-3~\cite{roy2007survey} and type 1R-3R as proposed in Sec.
+\ref{sec:rtypes}.
+When running our clone detection script over the corpus, we get the results displayed in Fig.~\ref{fig:typeres}.
+
+\begin{figure}[H]
+  \caption{Number of cloned declarations/statements.}
+    \includegraphics[width=1\columnwidth]{img/TypeResults}
+  \label{fig:typeres}
+\end{figure}
+
+In this figure, the number of cloned nodes per clone type are displayed.
+The difference between T1R and T1 is small (10.9\%), because most often textually equal code is also functionally equal.
+The difference between T2R and T2 is bigger (34.7\%) because the T2R definition is more strict.
+T3R and T3 are similar to T2R and T2 because our dataset does not have so many gapped clones for the thresholds used.
+
+We also measured the duration of finding clones by the different clone types.
+Fig.~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types.
+Although this data is partly dependent on our implementation of the clone types, there is a notable difference between the refactoring-oriented clone types and the literature clone types.
+The reason for this is further explained in Sec.~\ref{chap:challenge}.
+
+\begin{figure}[H]
+  \caption{Duration in minutes of identifying clones for clone type definitions.}
+    \includegraphics[width=.95\columnwidth]{img/DurationChart}
+  \label{fig:performance}
+\end{figure}
 

### 2019-07-23 sections/background.tex
Xander discussion

@@
 \section{Clone Types} \label{chap:backgroundclonetypes}
+\simon{What is Structurally/syntactically/functionally/textually, ect ect, all words before EQUAL}
 Duplication in code is found in many different forms.
@@
 \section{Code clone harmfulness}
+\simon{You make a promise here. Do we need this section? Maybe remove it completely.}
 Although duplication in source code is generally seen as a harmful coding practise that should be avoided.
@@
 Because of that, in this study, we consider external classes to see what impact they have on the refactoring process.
+\simon{Adapter pattern?}
 

### 2019-07-23 sections/research.tex
Xander discussion

@@
 Their detection results in simple to understand numbers to argue about a codebase.
-However, these clone types have a few flaws which makes it hard to argue to what extend two fragments of code are functionally related.
+However, these clone types have a few flaws which makes it hard to argue to what extend two fragments of code can and should be refactored.
 For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings to increase the chance that we can refactor the clone while improving the design.
@@
 \section{Shortcomings of clone types}
-Clone type 1-3 (further explain in section \ref{chap:backgroundclonetypes}) allow reasoning about the duplication in a software system.
+Clone types 1-3 (further explained in section \ref{chap:backgroundclonetypes}) allow reasoning about the duplication in a software system.
 Clones by these definitions can relatively easily and efficiently be detected.
@@
 
-Type 1 clones are by most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating} implemented as textual equality between code fragments (except for whitespace and comments).
+Type 1 clones are implemented as textual equality between code fragments (except for whitespace and comments) by most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating}.
 Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type.
@@
 \end{figure}
+\todo{image is not correct}
 
@@
 We tackle these problems with type 2R clones to be able to detect such clones that can and should be refactored.
-Type 1R clones are a subset of type 2R clones.
-All rules that apply to type 1R clones also apply to type 2R clones.
+Type 1R clones are a subset of type 2R clones \todo{Define this subset relation}.
+All rules that apply to type 1R clones also apply to type 2R clones\todo{Rules....}.
 Additionally, type 2R clones allow variability in literals, variables and method calls.
-This variability however is constrained by a threshold.
-Type 2R do not allow any variability in types, as opposed to type 2 clones which do allow variability in types.
-As type 2R clones are per definition more permissive than type 1R clones, type 1R clones are a subset of type 2R clones.
+This variability however is constrained by a threshold, which is explained in more detail in section \ref{sec:variabilitythreshold}.%to limit the negative effect on system design of variability in these expressions after refactoring.
 
 \subsubsection{A threshold for variability in literals, variables and method calls}\label{sec:variabilitythreshold}
+\simon{Check this text... Harmfulness?! ???}
 Type 2 clones allow any variability in literals, variables and method identifiers.
@@
 
+\simon{Dividing expressions by tokens... maybe not do that. How to do it then??????}
 \begin{eqfloat}\label{eq:type2r}

### 2019-07-23 sections/clonerefactor.tex
More todo
OKay this is harder than I thought
Common interface
Removing redundant clone classes: conceptual method is enough

@@
 A very important design decision for CloneRefactor is the usage of a library named JavaParser \cite{tomassetti2017javaparser}.
-JavaParser is a Java library which allows to parse Java source files to an abstract syntax tree (AST).
+JavaParser is a Java library which allows to parse Java source files to an abstract syntax tree (AST\footnote{An AST is a tree-representation of a source code file.}).
 JavaParser allows to modify this AST and write the result back to Java source code.
@@
 
-\subsubsection{Conceptual method of removing redundant clone classes}\label{sec:conceptualremovingredundant}
+\subsubsection{Removing redundant clone classes}\label{sec:conceptualremovingredundant}
 The clone detection method used by CloneRefactor can, for various reasons,%Should I list these? Listing them could be a section on its own, as I'd have to show examples to make it concrete.
@@
 
-For CloneRefactor we used this conceptual method of removing duplicates, but did not directly implement these equations.
-The main reason for this is the runtime overhead, as this process has to iterate over each existing clone class and each of their clone instances.
-For large projects with a lot of duplication this process has a significant impact on performance.
-
-\subsubsection{CloneRefactor method of removing redundant clone classes}
-Because of the order in which clones are found in the clone graph, removing redundant clone classes can be optimized to not require a search of the entire set of clones.
-To do this, we mark each node that has been considered for duplication as \textit{visited}.
-This includes nodes that are interated over and all duplicates of those nodes.
-When we later find a new clone class of which all nodes are \textit{visited}, we don't add this clone class to the set of clone classes because it is a subset of an existing clone class.
-
-\todo{Removal of existing clones: How does this is possibly redundant thing work?}
+If the newly added clone is a subset of an existing clone, we do not add it to the set of clone classes. This way we avoid redundant clone classes being detected by CloneRefactor.
 
@@
 \subsection{Checking for type 3 opportunities}
+\todo{TODO}

### 2019-07-23 sections/clonerefactor.tex
Better explain type 2R clonerefactor stuff

@@
 In this section we explain how CloneRefactor detects type 2R clones on basis of this variability threshold.
+This process is done as a postprocessing step after clone detection.
+The type 2R clone detection process is described in more detail in section \ref{sec:comparingstuff}.
+In short, this process detects clones allowing for any variability between expressions.
+This postprocessing step then determines which (parts of) these clones are valid by the configure variability threshold.
 
@@
 Figure \ref{fig:clonerefactort2rflow} shows the steps that CloneRefactor performs to find clones conforming with the type 2R variability threshold.
-This process is done as a postprocessing step after clone detection.
-The type 2R clone determination process is described in more detail in section \ref{sec:comparingstuff}.
-Each of the following paragraphs will explain a step from figure \ref{fig:clonerefactort2rflow}.
+Each of the following paragraphs will explain a step from this figure.
 
@@
 
-The symbols in this equation refer to the symbols of the column headers of table \ref{table:equalityarrays}.
+Where \textit{E} refers to the equality arrays shown in table \ref{table:equalityarrays}.
 When we apply this equation to the example clone classes displayed in figure \ref{fig:equalityarrays}, we get the following sum:

### 2019-07-23 sections/research.tex
Fixed missing image
New example + explanation for type 1 shortcomings

@@
 \begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+package com.sb.game;
+
+import java.util.List;
+
+public class GameScene
+{
+|\highlightYellow|	public void addToList(List l) {
+|\highlightYellow|		l.add(getClass().getName());
+|\highlightYellow|	}
+
+	public void addTen(int x) {
+|\highlightYellow|		x = x + 10;
+|\highlightYellow|		ChangeNotifier.notifyChanged(x);
+|\highlightYellow|		return x;
+	}
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+package com.sb.fruitgame;
+
+import java.awt.List;
+
+public class LoseScene
+{
+|\highlightYellow|	public void addToList(List l) {
+|\highlightYellow|		l.add(getClass().getName());
+|\highlightYellow|	}
+
+	public void concatTen(String x) {
+|\highlightYellow|		x = x + 10;
+|\highlightYellow|		ChangeNotifier.notifyChanged(x);
+|\highlightYellow|		return x;
+	}
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Variables with different types but the same name.}
+\label{fig:type2variables}
+\end{figure}
+\begin{figure}[H]
   \includegraphics[width=1\columnwidth]{img/type1}
@@
 
-In the example in figure \ref{fig:type1}, we see a type 1 clone consisting of two methods.
-However, these clones might still be very hard to refactor as we cannot see by this example whether they are functionally equal.
-Both code fragments use different imported types, some of which imported via a wildcard.
-Because of this, it is hard to verify which of the used types have the same underlying implementation.
+In the example in figure \ref{fig:type1}, we see a type 1 clone displaying two clone classes.
+Defining an automatic way to refactor these clone classes is nearly impossible, as both cloned fragments describe different functional concepts.
+The first cloned fragment is a method that adds something to a \texttt{List}.
+However, the \texttt{List} objects to which something is added are different.
+Looking at the \texttt{import} statement above the class, one fragment uses the \texttt{java.util.List} and the other uses the \texttt{java.awt.List}.
+Both happen to have an \texttt{add} method, but apart from that their implementation is completely different.
 
-Because of this, type 1 clones may not all be subject to refactoring.
+The second cloned fragment shows how equally named variables can have different types and thus yield different functional concepts.
+The cloned fragment on the left adds a specific amount to an integer.
+The cloned fragement on the right concatenates a number to a String.
+
+This shows that not all type 1 clones can easily be automatically refactored.
 In section \label{chap:type1rclones} we describe an alternate approach towards detecting type 1 clones, which results in only clones that can be refactored.
@@
 \begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/type2}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+public int addFive(int x){
+|\highlightYellow|	return x + 5;
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+public String appendFive(String x){
+|\highlightYellow|	return x + 5;
+}
+\end{javacode}}
+\end{parcolumns}
 \caption{Variables with different types but the same name.}
@@
 \end{figure}
-\todo{image is not correct}
 

### 2019-07-23 sections/research.tex
Better type 2 example

@@
 |\highlightYellow|		x = x + 10;
-|\highlightYellow|		ChangeNotifier.notifyChanged(x);
+|\highlightYellow|		Notifier.notifyChanged(x);
 |\highlightYellow|		return x;
@@
 \end{parcolumns}
-\caption{Variables with different types but the same name.}
-\label{fig:type2variables}
-\end{figure}
-\begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/type1}
 \caption{Example of a type 1 clone that is functionally different.}
@@
 \begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/type2}
-  \caption{Example of a type 2 clone.}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+|\highlightYellow|public boolean redCircles
+|\highlightYellow|          (List<Circle> circles){
+|\highlightYellow|	return circles.stream()
+|\highlightYellow|           .allMatch(Shape::isRed);
+|\highlightYellow|}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+|\highlightYellow|public Apple getEdibleApple
+|\highlightYellow|         (Basket<Apple> basket){
+|\highlightYellow|	return basket.getFruit()
+|\highlightYellow|        .getApple(Fruit::notEaten);
+|\highlightYellow|}
+\end{javacode}}
+\end{parcolumns}
+\caption{Example of a type 2 clone with high variability between fragments.}
 \label{fig:type2}
@@
 
-The example in figure \ref{fig:type2} shows a type 2 clone that poses no harm to the design of the system.
+The example in figure \ref{fig:type2} shows a type 2 clone class.
 Both methods are, except for their matching structure, completely different in functionality.

### 2019-07-23 sections/clonerefactor.tex
High variability

@@
 \subsubsection{Convert Equality Array to Graph}
+When a found clone class does not adhere to the global thresholds as explained in the previous section, we need to determine whether it contains any valid subclones.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+doA(a, b, c);
+doA();
+doB();
+doC();
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+doB(d, e, f);
+doA();
+doB();
+doC();
+\end{javacode}}
+\end{parcolumns}
+\caption{Variables with different types but the same name.}
+\label{fig:2rvariabilityhigh1}
+\end{figure}
+
+The first line of the cloned fragment shown in figure \ref{fig:2rvariabilityhigh1} has a high variability with its cloned fragement.
+However, the rest of this method does not have any variability.
+The global thresholds could indicate a too high variability and thus render this clone invalid.
+However, in this case, it might still have a valid subclone.
+
 \todo{TODO}

### 2019-07-23 sections/clonerefactor.tex
High variability instance

@@
 doA(a, b, c);
-doA();
-doB();
-doC();
+|\highlightYellow|doA();
+|\highlightYellow|doB();
+|\highlightYellow|doC();
 \end{javacode}}
@@
 doB(d, e, f);
-doA();
-doB();
-doC();
+|\highlightYellow|doA();
+|\highlightYellow|doB();
+|\highlightYellow|doC();
 \end{javacode}}
 \end{parcolumns}
-\caption{Variables with different types but the same name.}
+\caption{One node in a type 2R clone has a high variability.}
 \label{fig:2rvariabilityhigh1}
@@
 However, in this case, it might still have a valid subclone.
+
+\begin{figure}[H]
+\begin{parcolumns}{3}
+\colchunk[1]{
+\begin{javacode}
+|\highlightYellow|doA();
+|\highlightYellow|doB();
+|\highlightYellow|doC();
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+|\highlightYellow|doA();
+|\highlightYellow|doB();
+|\highlightYellow|doC();
+\end{javacode}}
+\colchunk[3]{
+\begin{javacode}
+doD();
+doE();
+doF();
+\end{javacode}}
+\end{parcolumns}
+\caption{One clone instance in a type 2R clone has a high variability.}
+\label{fig:2rvariabilityhigh2}
+\end{figure}
+
+Another example of high variability between clones, in which a valid subclone can be found, is displayed in figure \ref{fig:2rvariabilityhigh2}.
+In this case, one clone instance has such a high variability that it shouldn't be refactored.
+In this case, the clone instance with high variability should be removed.
 

### 2019-07-23 sections/clonerefactor.tex
Last example

@@
 
-\subsubsection{Convert Equality Array to Graph}
 When a found clone class does not adhere to the global thresholds as explained in the previous section, we need to determine whether it contains any valid subclones.
+Below, we explain a few cases of valid subclones that may exist within an invalid clone class.
 
@@
 
+\begin{figure}[H]
+\begin{parcolumns}{3}
+\colchunk[1]{
+\begin{javacode}
+|\highlightYellow|doA();
+|\highlightYellow|doB();
+doC();
+doC();
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+doD();
+|\highlightYellow|doA();
+|\highlightYellow|doB();
+doD();
+\end{javacode}}
+\colchunk[3]{
+\begin{javacode}
+doE();
+doE();
+|\highlightYellow|doA();
+|\highlightYellow|doB();
+\end{javacode}}
+\end{parcolumns}
+\caption{One clone instance in a type 2R clone has a high variability.}
+\label{fig:2rvariabilityhigh3}
+\end{figure}
+
+Figure \ref{fig:2rvariabilityhigh3} shows an example of a clone class where the valid sequence inside the clone does not align.
+
+If the check for global thresholds fails, we have to seek for valid clones within the clone class.
+In a single invalid clone class can be zero to many subclones.
+This requires an extensive search for such clones.
+This problem is very related to the problem of clone detection, except now it is within the boundaries of a single clone class except for an entire codebase.
+Because of that, just like the clone detection process, we build a clone graph and detect clones on it.
+This process is explained over the following sections.
+
+\subsubsection{Convert Equality Array to Graph}
+
 \todo{TODO}

### 2019-07-23 sections/clonerefactor.tex
Showing equality arrays for the example

@@
 \end{parcolumns}
-\caption{One clone instance in a type 2R clone has a high variability.}
+\caption{A small subset of nodes has a high variability.}
 \label{fig:2rvariabilityhigh3}
@@
 \subsubsection{Convert Equality Array to Graph}
+After the global threshold check has failed, we build a clone graph on basis of the equality arrays.
+
+\begin{figure}[H]
+\begin{parcolumns}{3}
+\colchunk[1]{
+\begin{javacode}
+|\highlightYellow|doA(); //{1, 2}
+|\highlightYellow|doB(); //{3, 2}
+doC(); //{4, 2}
+doC(); //{4, 2}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+doD(); //{5, 2}
+|\highlightYellow|doA(); //{1, 2}
+|\highlightYellow|doB(); //{3, 2}
+doD(); //{5, 2}
+\end{javacode}}
+\colchunk[3]{
+\begin{javacode}
+doE(); //{6, 2}
+doE(); //{6, 2}
+|\highlightYellow|doA(); //{1, 2}
+|\highlightYellow|doB(); //{3, 2}
+\end{javacode}}
+\end{parcolumns}
+\caption{Cloned code fragments from figure \ref{fig:2rvariabilityhigh3} together with their equality arrays.}
+\label{fig:2rvariabilityhigh4}
+\end{figure}
+
+In figure \ref{fig:2rvariabilityhigh4} we display the equality arrays for each of the lines of a code example with a complex distribution of cloned fragments.
 

### 2019-07-24 sections/clonerefactor.tex
T2R graph

@@
 \begin{javacode}
-|\highlightYellow|doA(); //{1, 2}
-|\highlightYellow|doB(); //{3, 2}
-doC(); //{4, 2}
-doC(); //{4, 2}
+|\highlightYellow|doA(); //{1, -2}
+|\highlightYellow|doB(); //{3, -2}
+doC(); //{4, -2}
+doC(); //{4, -2}
 \end{javacode}}
@@
 \begin{javacode}
-doD(); //{5, 2}
-|\highlightYellow|doA(); //{1, 2}
-|\highlightYellow|doB(); //{3, 2}
-doD(); //{5, 2}
+doD(); //{5, -2}
+|\highlightYellow|doA(); //{1, -2}
+|\highlightYellow|doB(); //{3, -2}
+doD(); //{5, -2}
 \end{javacode}}
@@
 \begin{javacode}
-doE(); //{6, 2}
-doE(); //{6, 2}
-|\highlightYellow|doA(); //{1, 2}
-|\highlightYellow|doB(); //{3, 2}
+doE(); //{6, -2}
+doE(); //{6, -2}
+|\highlightYellow|doA(); //{1, -2}
+|\highlightYellow|doB(); //{3, -2}
 \end{javacode}}
@@
 In figure \ref{fig:2rvariabilityhigh4} we display the equality arrays for each of the lines of a code example with a complex distribution of cloned fragments.
+We can convert this to a graph, using a similar process as the graph creation process used for clone detection.
+In this case, duplicate relations represent nodes of which their equality arrays are within the variability threshold.
+In figure \ref{fig:2rvariabilityhigh4} all relations are between equal equality arrays, but this does not always have to be the case.
+Large equality arrays, denoting statements that consist of many tokens, may have some variability and still be considered duplicates in this graph.
 
-\todo{TODO}
-\begin{table}[H]
-\begin{center}
- \caption{The equality arrays in our example figure \ref{fig:equalityarrays}.} \label{table:equalityarrays2}
- \medskip
-\begin{tabular}{|l|l|l|}
-\hline
-Node (n) & Equality Array (E) \\ \hline
-1        & {[}1, -2, 3, -5, -6{]} \\ \hline
-2        & {[}1, -2, 3, -5, -6{]} \\ \hline
-3        & {[}8, -2, 4, -5, -6{]} \\ \hline
-4        & {[}1, -2, 7, -5, -6{]} \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{img/T2RGraph}
+  \caption{Graph representation of the code example displayed in figure \ref{fig:2rvariabilityhigh4}.}
+  \label{fig:clonerefactorprocess}
+\end{figure}
 

### 2019-07-24 sections/clonerefactor.tex
The equation

@@
 \begin{equation}\label{eq:sumequality}
-\frac{|{(3,4), (1,8), (7,9)}|}{(5+5)+(5+5)}*100 = \frac{3}{20}*100 = 15\%
+\frac{|\{(3,4), (1,8), (7,9)\}|}{(5+5)+(5+5)}*100 = \frac{3}{20}*100 = 15\%
 \end{equation}
@@
 
+Although the duplicate relations allow for variability in the equality arrays as long as it falls under the threshold, negative numbers in the equality array may never vary.
+This is because negative numbers are the tokens/expressions that we do not allow variability in because they cannot be refactored in the same way.
+\begin{equation}\label{eq:t2rcloneequality}
+E_1\text{ can only be cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1, y \in E_2) x<0 \lor y<0 \Rightarrow x=y
+\end{equation}
+
 \subsubsection{Detect Clones on Graph}
 \todo{TODO}
-\begin{equation}\label{eq:t2rcloneequality}
-E_1\text{ is cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1) \exists (y \in E_2) x<0 \lor y<0 \Rightarrow x=y
-\end{equation}
 

### 2019-07-24 sections/clonerefactor.tex
Thresholds

@@
 Because of the requirement of symbol resolution, the refactoring-oriented clone types are less suitable for large scale clone analysis.
+
+\section{Thresholds}
+CloneRefactor operates on a set of thresholds to determine the validity of clones that are found. In general, these thresholds are:
+\begin{itemize}
+  \item \textbf{Minimum Amount of Nodes}: The minimum amount of nodes that should be in each instance of cloned fragements for them to be considered a clone class.
+  \item \textbf{Minimum Amount of Tokens}: The minimum amount of tokens that should be in each instance of cloned fragements for them to be considered a clone class.
+  \item \textbf{Minimum Amount of Lines}: The minimum amount of lines that should be in each instance of cloned fragements for them to be considered a clone class.
+\end{itemize}
+
+When we analyze type 2R or type 3R clones we use the following additional threshold:
+\begin{itemize}
+  \item \textbf{T2R Variability}: The percentage of variability we allow in variables, method calls and literals.
+How this threshold is calculated is explained in section \ref{sec:t2rcheckglobalthres}.
+\end{itemize}
+
+When we analyze type 3 or type 3R clones we use the following additional threshold:
+\begin{itemize}
+  \item \textbf{T3R Gap Size}: The size of the gap we allow between two valid clones.
+This is a percentage of the size of the gap against the size of both clones combined.
+How this threshold is calculated is further explained in section \ref{sec:t3rclonerefactor}.
+\end{itemize}
 

### 2019-07-24 sections/clonerefactor.tex
Detect clones on graph

@@
 
-\section{Thresholds}
+\section{Thresholds}\label{sec:clonerefactorthresholds}
 CloneRefactor operates on a set of thresholds to determine the validity of clones that are found. In general, these thresholds are:
@@
 
-\subsection{Comparing Statements/Declarations} \label{sec:comparingstuff}
+\subsubsection{Comparing Statements/Declarations} \label{sec:comparingstuff}
 In the previous section we described a ``duplicate'' relation between nodes in the clone graph built by CloneRefactor.
@@
 
-\subsection{Mapping graph nodes to code}
+\subsubsection{Mapping graph nodes to code}
 The clone graph, as explained in section \ref{sec:buildingclonegraph}, contains all declarations and statements in a source code.
@@
 
-\subsubsection{Checking global thresholds}
+\subsubsection{Checking global thresholds} \label{sec:t2rcheckglobalthres}
 Using the equality arrays explained in the previous section, we can determine the variability threshold of any clone class.
@@
 \subsubsection{Detect Clones on Graph}
-\todo{TODO}
+Similar to the clone detection process, we detect clones on basis of the graph described in the previous section.
+The only difference is that, in this step, we do not remove clones that do not meet the thresholds (as explained in section \ref{sec:clonerefactorthresholds}).
+This is because the next step, explained in the next section, could potentially expand the found clones and thus make clones that would currently invalid by the thresholds valid.
 
@@
 
-\subsection{Checking for type 3 opportunities}
+\subsection{Checking for type 3 opportunities} \label{sec:t3rclonerefactor}
 \todo{TODO}

### 2019-07-24 sections/clonerefactor.tex
Stuff

@@
 \chapter{CloneRefactor}
+% We bridged a gap between clone detection and refactoring .. by designing a tool
 CloneRefactor is the name of our clone detection and refactoring tool. It features the following novel functions:
@@
 \subsubsection{Removing redundant clone classes}\label{sec:conceptualremovingredundant}
+\ana{MOVE THIS, Part of the clone class collection and one that is found but not yet part of the collection.
+If the new one is a subset of the one in the collection then it is ignored.
+If the new one is a superset of any clone in the collection it replaces those.
+If one is a subset of the other it should be replaced.}
+
 The clone detection method used by CloneRefactor can, for various reasons,%Should I list these? Listing them could be a section on its own, as I'd have to show examples to make it concrete.
@@
 After the insertion of each newly detected clone, we check whether it is redundant and/or any of the existent clones has become redundant by adding this clone.
-A clone is redundant if it is a subset of an existing clone.
+A clone is redundant if it is a subset of another clone.
 We define the subset relation between clones as follows:
@@
 C_1 \subseteq C_2 \Leftrightarrow \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
+\end{equation} % Right symbol for definition
+
+Where \textit{C} refers to a clone class (a set of clone instances), \textit{i} refers to a clone instance, \textit{F} is the file in which a clone instance is located and \textit{R} is the range of tokens that a clone instance spans.
+For each clone found, we remove all existing clones that are a subset of the found clone:
+
+\begin{equation}\label{eq:removeall}
+S_{after} = S_{before} \setminus \{C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S_{before}\}
 \end{equation}
 
-Where \textit{C} refers to a clone class (a set of clone instances), \textit{i} refers to a clone instance, \textit{F} is the file in which a clone instance is located and \textit{R} is the range of tokens that a clone instance spans.
-For each clone added, we remove all existing clones that are a subset of the newly added clone:
+Where \textit{$S_{before}$} is the clone class collection containing all clones that are found up in until this point and \textit{$C_{new}$} is the clone class that was just found.
+\textit{$S_{after}$} is the clone class collection after
 
-\begin{equation}\label{eq:removeall}
-S = S \setminus \{C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S\}
-\end{equation}
-
-Where \textit{S} is the set of all clone classes that are found up in until this point.
-Likewise, we should not add the new clone to our list of clones if its a subset of an existing clone.
-Because of that, we check for each clone added whether there exists a clone of which the newly added clone is a subset:
+We should not add the new clone to our list of clones if its a subset of an existing clone.
+Because of that, we check for each clone added whether there exists a clone class of which the found clone class is a subset:
 
 \begin{equation}\label{eq:removeexisting}
-\{C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S\} = \emptyset \Rightarrow S = S \cup C_{new}
+\{C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S\} = \emptyset \Rightarrow S_{after} = S \cup C_{new}
 \end{equation}
@@
 
+Looking back at the example of the previous section, it would result in the following clone class collection:
+\begin{figure}[H]
+\begin{parcolumns}{3}
+\colchunk[1]{
+\begin{javacode}
+|\highlightYellow|doA(); // |\textcolor{pgreen}{$C_1$ $I_3$}|
+|\highlightYellow|doB(); // |\textcolor{pgreen}{$C_1$ $I_3$}|
+doC(); // |\textcolor{pgreen}{$C_4$ $I_2$}|
+doC(); // |\textcolor{pgreen}{$C_4$ $I_1$}|
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+doD(); // |\textcolor{pgreen}{$C_3$ $I_2$}|
+|\highlightYellow|doA(); // |\textcolor{pgreen}{$C_1$ $I_2$}|
+|\highlightYellow|doB(); // |\textcolor{pgreen}{$C_1$ $I_2$}|
+doD(); // |\textcolor{pgreen}{$C_3$ $I_1$}|
+\end{javacode}}
+\colchunk[3]{
+\begin{javacode}
+doE(); // |\textcolor{pgreen}{$C_2$ $I_2$}|
+doE(); // |\textcolor{pgreen}{$C_2$ $I_1$}|
+|\highlightYellow|doA(); // |\textcolor{pgreen}{$C_1$ $I_1$}|
+|\highlightYellow|doB(); // |\textcolor{pgreen}{$C_1$ $I_1$}|
+\end{javacode}}
+\end{parcolumns}
+\caption{Clone instances in figure \ref{fig:2rvariabilityhigh4} as determined .}
+\label{fig:2rvariabilityhigh5}
+\end{figure}
+
+Where \textit{C} denotes the clone class and \textit{I} denotes the clone instance. As the graph is traversed starting at the end, equal to graph traversal during clone detection, the last node in
+
 \subsubsection{Try to Expand}
-\todo{TODO}
+The problem with the graph clone detection technique is that
 

### 2019-07-24 sections/background.tex
Table stuff

@@
 \section{Code clone terminology}\label{sec:terminology}
+% The sets are actually definitions, NOT PROPERTIES. This should be clearer.
 Many studies present different definitions for code clone concepts.
@@
 \resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}llll@{}}
+\begin{tabular}{@{}lllll@{}}
 \toprule
 \rowcolor[HTML]{FFFFFF}
-\textbf{Symbol} & \textbf{Meaning} & \textbf{Description} & \textbf{Properties} \\ \midrule
+\textbf{Symbol} & \textbf{Meaning} & \textbf{Definition} & \textbf{Description} & \textbf{Properties} \\ \midrule
 \rowcolor[HTML]{EFEFEF}
-S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} & \textbf{Clones:} Set of clone classes.
-\\
+S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone classes.\\$S=\{C_1, C_2, ...\}$\end{tabular} &  & - \\
 \rowcolor[HTML]{FFFFFF}
-C & Clone class & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations.\end{tabular} & \textbf{Instances:} Set of clone instances. \\
+C & Clone class \cite{bruntink2005use, roy2007survey}& \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations.
+Each of these code fragments\\is called a ``clone instance''.\end{tabular} &  & - \\
 \rowcolor[HTML]{EFEFEF}
-I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Contents:} Totally ordered set of nodes, ordered\\by their begin positions.\\ \textbf{File:} The file in which this clone instance is \\ found.\\ \textbf{Range:} The range this clone instance spans.\end{tabular} \\
+I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} &  & \begin{tabular}[c]{@{}l@{}}\textbf{File:} The file in which this clone instance is \\ found.\\ \textbf{Range:} The range this clone instance spans.\end{tabular} \\
 \rowcolor[HTML]{FFFFFF}
-N & Node & \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & \textbf{Range:} The range this node spans. \\
+N & Node \ref{jiang2007deckard}& \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} &  & \textbf{Range:} The range this node spans. \\
 \rowcolor[HTML]{EFEFEF}
+T & Token & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code.
+\\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} &  & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this token spans.\\ \textbf{Category:} Identifier, Keyword, Literal, Separator, \\ Operator, Comment or Whitespace\end{tabular} \\
+\rowcolor[HTML]{FFFFFF}
 R & Range & A part of a source code file.
-& \begin{tabular}[c]{@{}l@{}}\textbf{Tokens:} Set of tokens that this range spans.\\ \textbf{Begin line/column:} The line and column at \\ which the range starts.\\ \textbf{End line/column:} The line and column at\\ which the range end.\end{tabular} \\
-\rowcolor[HTML]{FFFFFF}
-T & Token & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code.
-\\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this token spans.\\ \textbf{Category:} Identifier, Keyword, Literal, Separator, \\ Operator, Comment or Whitespace\end{tabular} \\ \bottomrule
+&  & \begin{tabular}[c]{@{}l@{}}\textbf{Begin line/column:} The line and column at \\ which the range starts.\\ \textbf{End line/column:} The line and column at\\ which the range end.\end{tabular} \\
+ \bottomrule
 \end{tabular}%

### 2019-07-24 sections/background.tex
Table

@@
 \rowcolor[HTML]{EFEFEF}
-S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone classes.\\$S=\{C_1, C_2, ...\}$\end{tabular} &  & - \\
+S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone classes.\\$S=\{C_1, C_2, ...\}$\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} & - \\
 \rowcolor[HTML]{FFFFFF}

### 2019-07-24 sections/background.tex
Improved the table

--- 2019-07-24 sections/background.tex
@@
 \rowcolor[HTML]{EFEFEF}
-S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone classes.\\$S=\{C_1, C_2, ...\}$\end{tabular} &  & - \\
+S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\classes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} & - \\
 \rowcolor[HTML]{FFFFFF}
-C & Clone class \cite{bruntink2005use, roy2007survey}& \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations.
-Each of these code fragments\\is called a ``clone instance''.\end{tabular} &  & - \\
+C & Clone class \cite{bruntink2005use, roy2007survey}& \begin{tabular}[c]{@{}l@{}}Set of clone\\instances.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations.
+Each of these\\code fragments is called a\\``clone instance''.\end{tabular} & - \\
 \rowcolor[HTML]{EFEFEF}
-I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} &  & \begin{tabular}[c]{@{}l@{}}\textbf{File:} The file in which this clone instance is \\ found.\\ \textbf{Range:} The range this clone instance spans.\end{tabular} \\
+I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\nodes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{File:} The file in which this\\clone instance is found.\end{tabular} \\
 \rowcolor[HTML]{FFFFFF}
-N & Node \ref{jiang2007deckard}& \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} &  & \textbf{Range:} The range this node spans. \\
+N & Node \ref{jiang2007deckard} & Set of tokens.
+& \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this node\\spans.\end{tabular} \\
 \rowcolor[HTML]{EFEFEF}
-T & Token & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code.
-\\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} &  & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this token spans.\\ \textbf{Category:} Identifier, Keyword, Literal, Separator, \\ Operator, Comment or Whitespace\end{tabular} \\
+T & Token & - & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code.
+\\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this token\\spans.\\ \textbf{Category:} Identifier, Keyword,\\Literal, Separator, Operator,\\ Comment or Whitespace.\end{tabular} \\
 \rowcolor[HTML]{FFFFFF}
-R & Range & A part of a source code file.
+%R & Range & A part of a source code file.
 &  & \begin{tabular}[c]{@{}l@{}}\textbf{Begin line/column:} The line and column at \\ which the range starts.\\ \textbf{End line/column:} The line and column at\\ which the range end.\end{tabular} \\

### 2019-07-24 sections/background.tex
Table explain

@@
 \rowcolor[HTML]{EFEFEF}
-S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\classes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} & - \\
+T & Token & - & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code.
+\\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this token\\spans.\\ \textbf{Category:} Identifier, Keyword,\\Literal, Separator, Operator,\\ Comment or Whitespace.\end{tabular} \\
+\rowcolor[HTML]{FFFFFF}
+N & Node \cite{jiang2007deckard} & Set of tokens.
+& \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this node\\spans.\end{tabular} \\
+\rowcolor[HTML]{EFEFEF}
+I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\nodes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{File:} The file in which this\\clone instance is found.\end{tabular} \\
 \rowcolor[HTML]{FFFFFF}
@@
 \rowcolor[HTML]{EFEFEF}
-I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\nodes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{File:} The file in which this\\clone instance is found.\end{tabular} \\
-\rowcolor[HTML]{FFFFFF}
-N & Node \ref{jiang2007deckard} & Set of tokens.
-& \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this node\\spans.\end{tabular} \\
-\rowcolor[HTML]{EFEFEF}
-T & Token & - & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code.
-\\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this token\\spans.\\ \textbf{Category:} Identifier, Keyword,\\Literal, Separator, Operator,\\ Comment or Whitespace.\end{tabular} \\
+S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\classes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} & - \\
 \rowcolor[HTML]{FFFFFF}
@@
 
+In this study, we use the symbols given in this table in our formulas.
+
 \subsection{Example}
+This section gives an example to make the terminology of table \ref{tab:clone-terminology} more concrete.
 The code fragment in figure \ref{fig:cloneclasses} shows two clone classes.

### 2019-07-24 sections/background.tex
Fix references

@@
 \section{Clone Types} \label{chap:backgroundclonetypes}
-\simon{What is Structurally/syntactically/functionally/textually, ect ect, all words before EQUAL}
 Duplication in code is found in many different forms.
@@
 \section{Refactoring methods}
-One of the main drivers for starting this research is the recent release of the second edition of Martin Fowlers' Refactoring book \ref{fowler2018refactoring}.
+Martin Fowler recently released the second edition of his Refactoring book \cite{fowler2018refactoring}.
 This book has been updated to the modern state of software engineering.
-The sentence in which he stresses the importance of unifying duplication in source code remains present in both books \ref{fowler1999refactoring, fowler2018refactoring}.
+The sentence in which he stresses the importance of unifying duplication in source code remains present in both books \cite{fowler1999refactoring, fowler2018refactoring}.
 
@@
 Method extraction is one of the most used methods of refactoring duplication in source code.
-Several studies have already concluded that most duplication in source code is found in the body of methods \ref{lozano2007evaluating, white2016deep, bergman2004ethnographic}.
+Several studies have already concluded that most duplication in source code is found in the body of methods \cite{lozano2007evaluating, white2016deep, bergman2004ethnographic}.
 Method extraction can move matching functionality between methods to a common place: a new method.
-An example of this procedure is displayed in figure \ref{fig:extractmethod}.
+An example of this procedure is displayed in figure \cite{fig:extractmethod}.
 
@@
 However, a study by Fontana et al.
-\ref{fontana2015duplicated} shows that this is most often not the case.
+\cite{fontana2015duplicated} shows that this is most often not the case.
 Based on the relation between clone instances, the extracted method must be moved to be accessible by all locations of the clone instances.
@@
 \subsubsection{Pull up method}
-A refactoring technique to move a method up in its inheritance structure is called ``Pull up method'' \ref{fowler2018refactoring}.
+A refactoring technique to move a method up in its inheritance structure is called ``Pull up method'' \cite{fowler2018refactoring}.
 This way, if cloned methods are related in any way through inheritance, they can be called by both classes by placing the method in a class they both have in common.
@@
 Java has the concept of \textit{interfaces} as an abstract type that is used to specify a behavior that classes must implement.
-Since Java version 8, Java also supports default implementations to be provided in interfaces \ref{mohnen2002interfaces}.
+Since Java version 8, Java also supports default implementations to be provided in interfaces \cite{mohnen2002interfaces}.
 This gives an opportunity to make the relation between classes explicit and reduce duplication.

### 2019-07-24 sections/introduction.tex
Introduction

@@
 Duplication in source code is often seen as one of the most harmful types of technical debt.
-In Martin Fowler's ``Refactoring'' book \cite{fowler2018refactoring}, he exclaims that \textit{``if you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}.
+\textit{``Clones are problematic for the maintainability of a program, because if the clone is altered at one location to correct an erroneous behaviour, you cannot be sure that this correction is applied to all the cloned code as well.
+Additionally, the code base size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work''} \cite{ostberg2014automatically}.
+Bruntink et al.~\cite{bruntink2005use} show that code clones can contribute up to 25\% of the code size.
 
-In this research, we focus on formalizing the refactoring process of dealing with duplication in code.
-We will measure open source projects from the We will show the improvement of the metrics over various open source and industrial projects.
-Likewise, we will perform an estimation of the development costs that are saved by using the proposed solution.
-We will lay the main focus on the Java programming language as refactoring opportunities do feature paradigm and programming language dependent aspects \cite{choi2011extracting}.
-However, most practises used in this thesis will also be applicable with other object-oriented languages, like C\#.
+In this study, we use refactoring techniques to automatically reduce duplication in software systems.
+This allows us to obtain before- and after-refactoring snapshots of software systems.
+We use software maintainability metrics to measure the impact of refactoring clones.
+This way we can determine better definitions of clones.
+We also look into what variability we can allow between code fragments to still consider them clones, while still improving maintainability when refactoring these clones.
+Futhermore, we look into the thresholds that should be used while detecting clones to find clones that should be refactored.
+
+We perform several experiments on a large corpus of open source software to collect statistical data. With these experiments we map
 

### 2019-07-25 sections/introduction.tex
Introduction II
Research questions

@@
 
-We perform several experiments on a large corpus of open source software to collect statistical data. With these experiments we map
+We perform several experiments on a large corpus of open source software to collect statistical data.
+With these experiments we map the context of clones: where they reside in the codebase and what the relation is between duplicate fragments.
+We use this information to find appropriate refactoring opportunities for specific clones.
+We build a script to automatically refactor a subset of these clones.
 
@@
 \todo{Rewrite this part}
-Code clones can appear anywhere in the code.
-Whether a code clone has to be refactored, and how it has to be refactored, is dependent on where it exists in the code (it's context).
-There are many different contexts in which code clones can occur (in a method, a complete class, in an enumeration, global variables, etc.).
-Because of this, we first must collect some information regarding in what contexts code clones exist.
-To do this, we will analyze a set of Java projects for their clones, and generalize their contexts.
-To come to this information, we have formulated the following research question:
+There is a lot of research on the topic of code clone detection.
+This research often results in tools that can detect clones by several clone type definitions.
+However, there is no research yet that looks into how these definitions align with refactoring opportunities.
+We will align clone type definitions as used in literature \ref{roy2007survey} with their corresponding refactoring methods \ref{fowler2018refactoring}.
+For this, we answer the following research question:
 \begin{displayquote}
-\textbf{Research Question 1:}\\How can we group and rank clones based on their harmfulness?
+\textbf{Research Question 1:}\\How can we define clone types such that they \textbf{can} be automatically refactored?
 \end{displayquote}
-As a result from this research question, we expect a catalog of the different contexts in which clones occur, ordered on the amount of times they occur.
-On basis of this catalog, we have prioritized the further analysis of the clones.
-This analysis is to determine a suitable refactoring for the clone type that has been found at the design level.
-For this, we have formulated the following research question:
+As a result, we expect to formulate clone type definitions that can be refactored.
+On basis of this results we can perform analyses on the context of clones by these definitions.
+The context of a clone (location, relation between clones, etc.) has a big impact on how a clone should be refactored.
+We will create categories by which we map the context of clones and perform a statistical analysis on this.
+This results in the following research question:
 \begin{displayquote}
-\textbf{Research Question 2:}\\To what extend can we suggest refactorings of clones at the design level?
+\textbf{Research Question 2:}\\How can we prioritize refactoring opportunities based on the \textbf{context} of clones?
 \end{displayquote}
-As a result, we expect to have proposed refactorings for the most harmful clone patterns.
-On basis of these design level refactorings we will build a model, which we will proof using Java, that applies the refactorings to corresponding methods.
-For building this model, we have formulated the following research question:
+We expect this research question to result in a priorization of refactoring opportunities: \textit{with what refactoring method can what percentage of clones be refactored?} As a result of these first two research questions we expect to have clone type definitions that can be refactored together with a prioritization of the refactoring methods that can be used.
+On basis of this we expect to be able to build a script that can automatically refactor the highest prioritized clones.
+With this script, we expect to be able to answer our final research question:
 \begin{displayquote}
-\textbf{Research Question 3:}\\To what extend can we automatically refactor clones?
+\textbf{Research Question 3:}\\What are the discriminating factors to decide when a clone \textbf{should} be refactored?
 \end{displayquote}
-As a result from this research question, we expect to have a model to be able to refactor the highest priority clones.
+Not in all cases will refactoring duplicated code result in a more maintainable codebase.
+Because of that, we want to compare the refactored code to the original code and measure the difference in maintainability.
+To do this, we will use a practical model consisting of metrics to measure maintainability \cite{heitlager2007practical}.
+Based on this, we can look into what \textit{thresholds} result in better maintainable code when refactored.
+These thresholds consist of the size of clones and the variability we can allow between cloned fragments to still consider them clones.
 

### 2019-07-25 sections/introduction.tex
The problem

@@
 \subsection{The problem}
-\todo{How do I formulate this}
+The maintainability of a codebase has a large impact on the time and effort spent on building the desired software system \cite{bakota2012cost, munson1978software}.
+The maintainability of software is one of the factors to be kept under control in order to avoid major delays and unexpected costs as a result of a software project \cite{fowler2018refactoring}.
+One factor that has a major impact on the maintainability of a software system is the amount of duplicate code present in a codebase \cite{heitlager2007practical, fowler1999refactoring}.
+
+The process of improving maintainability through the refactoring of duplicate code is time consuming and error-prone. This process mainly consists of these two aspects:
+\begin{itemize}
+	\item Find refactoring candidates, either tool-assisted or manually.
+	\item Refactor identified candidates, either tool-assisted or manually.
+\end{itemize}
+There are tools that assist in the process of finding duplicate code, but none of these tools identify all duplication problems.
+Often, these clone detection tools result in false-positives and false-negatives \cite{roy2007survey}.
+Many false-negatives are due to the thresholds that are used.
+Many clone detection tools \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval} only consider clones that have a minimum of 6 lines.
+Using such an approach is bound to result in many false-negatives.
+
+A study by Batova et al.
+\cite{bavota2012does} shows that the process of refactoring often leaves side effects in the code.
+This study reports that refactorings involving hierarchies (e.g., pull up method), tend to induce faults very frequently.
+\textit{This suggests more accurate code inspection or testing activities when such specific refactorings are performed.} Such specific refactorings often have to be used when dealing with duplication in software \cite{fowler2018refactoring, fontana2015duplicated}.
+Because of that, refactoring code clones has been empirically proven to cause bugs or other side effects in code.
 
 \subsection{Research questions}
-\todo{Rewrite this part}
 There is a lot of research on the topic of code clone detection.

### 2019-07-25 sections/clonerefactor.tex
Fixed some errors in the document

@@
 In the definition of type 2R clones (see section \ref{sec:type2r}) we described how type 2R clones work on basis of a variability threshold.
-This threshold, shown more formally in formula \ref{eq:type2r}, is checked by CloneRefactor.
-Implementing such a threshold involves some important design decisions, and has a lot of underwater complexity.
+This threshold is checked by CloneRefactor to assess the validity of found clone classes.
+Implementing such a threshold involves some important design decisions and has a lot of underwater complexity.
 In this section we explain how CloneRefactor detects type 2R clones on basis of this variability threshold.

### 2019-07-25 sections/conclusion.tex
Fixed some errors in the document

@@
 When a deadline comes near, often software quality in sacrificed to gain velocity \cite{costello1984software, austin2001effects, shah2014global}.
-Apart from that, a low programmer aptitude can result in low quality code \ref{cheney1984effects}.
+Apart from that, a low programmer aptitude can result in low quality code \cite{cheney1984effects}.
 This is because often forming appropriate abstractions requires time, effort and critical thinking.
@@
 \subsection{Automatically refactoring code that is duplicated with a library}
-One of the clone detection tools we analyzed in this study is Sisyphus \ref{eremondi2017sisyphus}.
+One of the clone detection tools we analyzed in this study is Sisyphus \cite{eremondi2017sisyphus}.
 This clone detection tool searches a codebase for methods that are part of the Java standard libraries.

### 2019-07-25 sections/results.tex
Fixed some errors in the document

@@
 \section{Clone types}\label{sec:clonetypeexperiments}
-In this section we display the differences between clone type 1-3~\cite{roy2007survey} and type 1R-3R as proposed in Sec.
-\ref{sec:rtypes}.
+In this section we display the differences between clone type 1-3~\cite{roy2007survey} and type 1R-3R as proposed in chapter \ref{chap:clonetypes}.
 When running our clone detection script over the corpus, we get the results displayed in Fig.~\ref{fig:typeres}.
@@
   \caption{Number of cloned declarations/statements.}
-    \includegraphics[width=1\columnwidth]{img/TypeResults}
+    \includegraphics[width=.5\columnwidth]{img/TypeResults}
   \label{fig:typeres}
@@
   \caption{Duration in minutes of identifying clones for clone type definitions.}
-    \includegraphics[width=.95\columnwidth]{img/DurationChart}
+    \includegraphics[width=.5\columnwidth]{img/DurationChart}
   \label{fig:performance}

### 2019-07-25 sections/background.tex
Refactoring background

@@
 Martin Fowler recently released the second edition of his Refactoring book \cite{fowler2018refactoring}.
-This book has been updated to the modern state of software engineering.
-The sentence in which he stresses the importance of unifying duplication in source code remains present in both books \cite{fowler1999refactoring, fowler2018refactoring}.
-
-The main method for dealing with duplication in source code, as described by Martin Fowler, is to extract the duplication to a common place.
-In most IDE's this refactoring method is called ``Extract Method''.
+In this book he exclaims that \textit{``if you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them''} \cite{fowler1999refactoring, fowler2018refactoring}.
+He describes several methods to deal with duplication, dependent on the context of the clone.
+In this section we describe the methods which we use in this study.
 
 \subsection{Extract Method}
-Method extraction is one of the most used methods of refactoring duplication in source code.
+The main method for dealing with duplication in source code, as described by Martin Fowler, is to extract the duplication to a common place.
+This refactoring method is called ``Extract Method''.
 Several studies have already concluded that most duplication in source code is found in the body of methods \cite{lozano2007evaluating, white2016deep, bergman2004ethnographic}.
-Method extraction can move matching functionality between methods to a common place: a new method.
+Method extraction can move matching functionality in method bodies to a common place, namely a new method.
 An example of this procedure is displayed in figure \cite{fig:extractmethod}.

### 2019-07-25 sections/background.tex
Removed harmfulness from the background

@@
 
-\section{Code clone harmfulness}
-\simon{You make a promise here. Do we need this section? Maybe remove it completely.}
-Although duplication in source code is generally seen as a harmful coding practise that should be avoided.
-Most papers view clones as harmful regarding program maintainability.
-\textit{``Clones are problematic for the maintainability of a program, because if the clone is altered at one location to correct an erroneous behaviour, you cannot be sure that this correction is applied to all the cloned code as well.
-Additionally, the code base size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work''} \cite{ostberg2014automatically}.
-However, in some instances it is undesirable to remove all duplication, as it can lead to unnecessary complexity.
-
-The harmfulness of clones depends on a lot of factors.
-A paper by Kapser et al \cite{kapser2006cloning} describes several patterns of cloning that may not be considered harmful.
-In this paper Kapser names examples where eliminating clones would compromise other important program qualities.
-Another study by Jarzabek et al \cite{jarzabek2010clones} categorized ``Essential clones'': clones that are essential because of the solution that is being modelled by the program.
-Overall, many of the benefits of code clones do not apply to most modern object-oriented programming languages.
-
-In this study, one of the main focus points will be to identify what makes a code clone harmful.
-Analyzing refactoring opportunities of code clones gives an unique insight in the state of the source code in case the duplication is not present.
-Analyzing these before- and after states of the source code will provide more insights that will help to rank clones based on their harmfulness.
-
 \section{Internal and external classes}

### 2019-07-25 sections/introduction.tex
Addressing notes

@@
 \label{ch:introduction}
-\todo{Rewrite this part}
 Refactoring is used to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.

### 2019-07-25 sections/research.tex
Type 2R

@@
 \subsection{Type 1R clones} \label{sec:type1r}
-To solve the issues identified in Sec.~\ref{sec:type1}, we introduce an alternative definition: cloned fragments have to be both textually \textit{and} functionally equal.
+To solve the issues identified in section \ref{sec:type1}, we introduce an alternative definition: cloned fragments have to be both textually \textit{and} functionally equal.
+Like type 1 clones, type 1R clones do not consider comments and whitespace.
 Therefore, T1R clones are a subset of type 1 clones.
@@
 This could render two methods that have an entirely different functionality as clones (as shown in figure \ref{fig:type2} previously).
-Refactoring such clones can be harmful instead of helpful.
 
 We tackle these problems with type 2R clones to be able to detect such clones that can and should be refactored.
-Type 1R clones are a subset of type 2R clones \todo{Define this subset relation}.
-All rules that apply to type 1R clones also apply to type 2R clones\todo{Rules....}.
-Additionally, type 2R clones allow variability in literals, variables and method calls.
-This variability however is constrained by a threshold, which is explained in more detail in section \ref{sec:variabilitythreshold}.%to limit the negative effect on system design of variability in these expressions after refactoring.
+Type 1R clones are a subset of type 2R clones, meaning that each node found as cloned for type 1R will also be found as cloned for type 2R.
+Similar to type 1R, for type 2R we consider the fully qualified identifiers of type-, method- and variable-references.
+Additionally, type 2R clones allow variability in a controlled set of expressions and identifiers.
+The identifiers and expressions in which we allow variability must have one of the following properties:
+\begin{itemize}
+  \item We allow a difference in identifiers between cloned fragments if it has no impact on the refactoring process.
+  \item We allow a difference in expressions between cloned fragments if the expression can be extracted to a method argument when applying the ``Extract Method'' refactoring.
+\end{itemize}
+
+Allowing variability between expressions includes a tradeoff.
+When many expressions vary between cloned the refactored method might require many additional arguments.
+Because of that, we constrain this variability by a threshold, which is explained in more detail in section \ref{sec:variabilitythreshold}.%to limit the negative effect on system design of variability in these expressions after refactoring.
+
+\subsubsection{Allow any variability in some identifiers}
+When refactored, some identifiers have no detrimental effect on the design if they vary between cloned instances.
+This section explains several patterns of variability that we can allow between cloned fragements without changing the method by which the fragments can be refactored.
+
+\paragraph{Declaration names}
+The names of declarations describe the implementation of their body. Examples of declarations are:
+\begin{itemize}
+  \item Class declaration
+  \item Method declaration
+  \item Interface declaration (not all languages have a separate declaration for these)
+  \item Enumeration declaration (not all languages have a separate declaration for these)
+  \item Annotation declaration (not all languages support these)
+  \item Etc.
+\end{itemize}
+If two declaration bodies and signatures are cloned, but their names differ, one of both names should be redundant.
+When refactoring such clones, we can choose one instance to keep and one to remove.
+Such a refactoring doesn't affect maintainability in any other way than refactoring a type 1R clone would.
+Because of this, type 2R allows any variability in declaration names.
+However, this will only open up a good refactoring opportunity if the entire body and signature of these declarations are cloned.
+
+\paragraph{Variable names}
+In section \ref{sec:t2rliteralandvariable} we described how variability in used variables often creates a design tradeoff.
+However, there are cases in which a used variable does not create a design tradeoff.
+For this, the following conditions need to apply:
+
+\begin{itemize}
+  \item The cloned variables are locally defined.
+  \item The cloned variables have the same type.
+  \item The cloned variables are used at the same places in cloned fragments.
+\end{itemize}
+
+\todo{Show examples}
 
 \subsubsection{A threshold for variability in literals, variables and method calls}\label{sec:variabilitythreshold}
-\simon{Check this text... Harmfulness?! ???}
 Type 2 clones allow any variability in literals, variables and method identifiers.
 However, this information tells a lot about the meaning of the code fragment.
-Most clone detection tools do not differentiate between a type 2 clone that differs by a single literal/identifier and one that differs by many.
+Most clone detection tools do not differentiate between a type 2 clone that differs by a single literal/identifier and one that differs by many \cite{roy2009comparison}.
 However, this does have a big impact on the meaning of the code fragment and thus the harmfulness of the duplication being there.
@@
 
-\simon{Dividing expressions by tokens... maybe not do that. How to do it then??????}
 \begin{eqfloat}\label{eq:type2r}
-$$\text{T2R Variability Percentage}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
-$$Diff = \text{Amount that differ from other clone instances in the clone class}$$
-$$Total = \text{Total number in the clone instance}$$
-$$l = \text{Literals in clone}$$
-$$v = \text{Variables in clone}$$
-$$m = \text{Method calls in clone}$$
-$$t = \text{Tokens in clones}$$
+\text{T2R Variability}=\frac{\text{Different expressions}}{\text{Total expressions}}*100
 \caption{Type 2R variability threshold formula}\end{eqfloat}
+
+In this formula, \textit{different expressions} refers to the number of literals, variables and method calls that differ from other clone instances in a clone class.
+We divide this by the total number of expressions in the clone instance.
+Based on this threshold, we decide whether a clone should be considered for refactoring.
+A concrete example of applying this formula to calculate a threshold is given in \ref{sec:t2rcheckglobalthres}.
 
@@
 \end{figure}
-
-\subsubsection{Allow any variability in some identifiers}
-When refactored, some identifiers have no detrimental effect on the design if they vary between cloned instances.
-In the previous section, variability in literals, variables and called methods would result in more parameters for the extracted method, thus indicating a detrimental effect on system design.
-However, not always does a difference between fragments result in such a tradeoff.
-
-This section explains several patterns of variability that we can allow between cloned fragements without changing the method by which the fragments can be refactored.
-
-\paragraph{Class and method names}
-The names of classes and methods describe the implementation of their body.
-If two classes/methods are cloned, but their names differ, one of both names should be redundant.
-When refactoring such clones, we can choose one instance to keep and one to remove.
-Such a refactoring doesn't affect maintainability in any other way than refactoring a type 1R clone would.
-The same is true of interface, enumeration and annotation names.
-Because of this, type 2R allows any variability in class, method, interface, enumeration and annotation names.
-However, this will only open up a good refactoring opportunity if the entire body is cloned.
-
-\paragraph{Variable names}
-In section \ref{sec:t2rliteralandvariable} we described how variability in used variables often creates a design tradeoff.
-However, there are cases in which a used variable does not create a design tradeoff.
-For this, the following conditions need to apply:
-
-\begin{itemize}
-  \item The cloned variables are locally defined.
-  \item The cloned variables have the same type.
-  \item The cloned variables are used at the same places in cloned fragments.
-\end{itemize}
-
-\todo{Show examples}
 

### 2019-07-25 sections/research.tex
Type stuff

@@
 \paragraph{Variable names}
-In section \ref{sec:t2rliteralandvariable} we described how variability in used variables often creates a design tradeoff.
-However, there are cases in which a used variable does not create a design tradeoff.
-For this, the following conditions need to apply:
+Cloned code fragments using variables with different names can be refactored without a design tradeoff if the following conditions apply:
 
 \begin{itemize}
-  \item The cloned variables are locally defined.
+  \item The cloned variables are locally defined or the refactoring method used requires extraction to method argument anyways.
   \item The cloned variables have the same type.
@@
 Most clone detection tools do not differentiate between a type 2 clone that differs by a single literal/identifier and one that differs by many \cite{roy2009comparison}.
-However, this does have a big impact on the meaning of the code fragment and thus the harmfulness of the duplication being there.
+However, this does have a big impact on the meaning of the code fragment.
 

### 2019-07-25 sections/research.tex
Example for type 3 threshold

@@
 
-\begin{eqfloat}\label{eq:type3r}
-$$\text{T3R Gap Percentage}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100$$
-$$Statements = \text{The amount of statements in this code fragment}$$
-$$C_{gap} = \text{The gap between two clones}$$
-$$C_{above} = \text{The clone instance above the gap}$$
-$$C_{below} = \text{The clone instance below the gap}$$
-\caption{Type 3R clone merge opportunities threshold formula}\end{eqfloat}
+\begin{equation}\label{eq:type3r}
+\text{T3R Gap Size}=\frac{\text{Number of nodes in gap}}{\text{Number of nodes in clones}}*100
+\end{equation}
+
+When applying this formula with the example given in figure \ref{fig:gappedclones}, we get a gap size of 25\%:
+
+\begin{equation}\label{eq:type3r}
+\text{T3R Gap Size}=\frac{\text{|\{doC()\}|}}{\text{|\{doA(), doB(), doD(), doE()\}|}}*100 = \frac{\text{1}}{\text{4}}*100 = 25\%
+\end{equation}
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+public void doStuff(){
+|\highlightYellow|  doA(); // Clone instance of
+|\highlightYellow|  doB(); // two statements
+  doC(); // Gap of one statement
+|\highlightBlue|  doD(); // Clone instance of
+|\highlightBlue|  doE(); // two statements
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+public void doStuff(){
+|\highlightYellow|  doA(); // Clone instance of
+|\highlightYellow|  doB(); // two statements
+  doF(); // Gap of one statement
+|\highlightBlue|  doD(); // Clone instance of
+|\highlightBlue|  doE(); // two statements
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Gapped clones.}
+\label{fig:gappedclones}
+\end{figure}
 

### 2019-07-25 sections/research.tex
Removed unify types chapter

@@
 
-\section{Unifying the types}\label{sec:unifying}
-In this chapter we have proposed refactoring-oriented definitions using the type 1, 2 and 3 clone definitions from literature as a baseline.
-In literature, these definitions are mainly aimed towards reasoning about duplication in source code.
-When considering these types for refactoring, the goal becomes slightly different.
-Because of this, having separate clone type definitions does not have any value.
-Rather, we need a single clone type definition by which we can detect all clones that can and should be considered for refactoring.
-
-Because of this, the ultimate goal would be not to consider type 1R, 2R and 3R separately, but together.
-However, this is dependent on good thresholds for the type 2R variability and type 3R gap size.
-Because of this, we have dedicated section \ref{sec:thresholds} to performing measurements to find good thresholds.
-The ultimate goal is to have a single unified definition of clones that can and should be refactored.
-Although it will be next to impossible to define such a definition and its corresponding thresholds that does not detect false positives.
-However, we strive to find at least a near-optimal set of thresholds regarding the type definitions proposed in this chapter.
-
 \section{Suitability of existing Clone Detection Tools for detecting these clones}

### 2019-07-25 sections/research.tex
2R thresholds fixed formula

@@
 
-\begin{eqfloat}\label{eq:type2r}
-\text{T2R Variability}=\frac{\text{Different expressions}}{\text{Total expressions}}*100
-\caption{Type 2R variability threshold formula}\end{eqfloat}
+\begin{equation}\label{eq:type2r}
+\text{T2R Variability}=\frac{\text{Number of different expressions}}{\text{Total number of expressions in clone instance}}*100
+\end{equation}
 
-In this formula, \textit{different expressions} refers to the number of literals, variables and method calls that differ from other clone instances in a clone class.
+In this formula, \textit{number of different expressions} refers to the number of literals, variables and method calls that differ from other clone instances in a clone class.
 We divide this by the total number of expressions in the clone instance.

### 2019-07-25 sections/research.tex
Suitability of tools

@@
 
-\section{Refactoring-oriented clone types}
+\section{Refactoring-oriented clone types}\label{sec:rtypes}
 To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types directed at detecting clones that can and should be refactored.
@@
 \section{Suitability of existing Clone Detection Tools for detecting these clones}
+\todo{Is this still up to date?}
 \label{ch:tool-overview}
-We conducted a short survey on (recent) clone detection tools in order to expand them with the proposed types.
+We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities.
 The results of our survey are displayed in table~\ref{table:dettools}.
-We chose a set of tools that are open source and can analyze at least one popular object-oriented programming language.
+We chose a set of tools that are open source and can analyze a popular object-oriented programming language.
 Next, we formulate the following four criteria by which we analyze these tools:
 \begin{enumerate}
-    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method-level clones.
-We want to perform an analysis on all clones in projects to get a complete overview.
-We analyzed this behavior using a set of control projects.
-\item \textbf{TODO: Criterium.}\simon{TODO} We assembled a number of test projects to assess the validity of clone detection tools.
-On basis of this, we checked whether clone detection tools can correctly find clones in diverse contexts.
-\item \textbf{Can analyse resolved symbols.} When detecting clones for refactoring purposes, it is important that clone instances can be refactored.
-Sometimes, textual equality between code fragments does not imply that these can be refactored (this is described more elaborately in section \ref{sec:type1}).
-Because of this, we want to use a clone detection tool that can analyze such structures.
-\item \textbf{Extensive detection configuration.} We aim to exclude expressions/statements from matching (more about our rationale in section~\ref{chap:clonetypes}).
-To achieve this, the tool needs to be able to allow those threshold changes.
-This can be either through simple changes of the source code, or by using some configuration file.
+    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method level clones.
+We want to perform an analysis of all clones in projects to get a complete overview.
+\item \textbf{Finds clone classes in control projects.} We assembled a number of control projects to assess the validity of clone detection tools.
+\item \textbf{Can analyze resolved symbols.} When detecting the types proposed in section~\ref{sec:rtypes}, it is important that we can analyze resolved symbols (for instance a type reference).
+The rationale for this is further explained in~\ref{chap:challenge}.
+\item \textbf{Extensive detection configuration.} Detecting our clone definitions, as proposed in section~\ref{sec:rtypes}, require to have some understanding about the meaning of tokens in the source code (whether a certain token is a type, variable, etc.).
+The tool should recognize such structures, in order for us to configure our clone type definitions in the tool.
 \end{enumerate}

### 2019-07-25 sections/research.tex
Summarized + challenge

@@
 \begin{itemize}
-\item \textbf{Type 1R:} Allows no difference between cloned fragments, making it possible to refactor both fragments to a method call that contains the code of both locations. \\
-\item \textbf{Type 2R:} Allows difference between cloned fragments in controlled features of a codebase.
+\item \textbf{Type 1R:} Allows no difference between cloned fragments (both functionally and textually), making it possible to refactor both fragments to a method call that contains the code of both locations.
+\\
+\item \textbf{Type 2R:} Allows difference between cloned fragments in a controlled set of expressions.
 Refactoring opportunities for these controlled features are known, allowing refactoring with a minor tradeoff.
@@
 
+Regarding the nodes found as cloned by these clone type definitions, there exists a subset relation between all types:
+
 \begin{equation}\label{eq:typerelation}
-\text{Cloned statements} = T1R \subseteq T2R \subseteq T3R
+\text{Cloned nodes} = T1R \subseteq T2R \subseteq T3R
 \end{equation}
 
+Comparing these clone type definitions to the ones used in literature, type 1R clones are a subset of type 1 clones.
+However, this subset relation does not exist for type 2R and 3R clones.
+This is because these definitions allow variability in multi-token method calls, which type 2 and type 3 do not allow.
+Because of that, the following is true for these clone types:
+
 \begin{equation}\label{eq:typerelation2}
-\text{Cloned lines} = T1R \subseteq T1 \text{, but } T2R	\nsubseteq T2 \text{ and } T3R \nsubseteq T3
+\text{Cloned nodes} = T1R \subseteq T1 \text{, but } T2R	\nsubseteq T2 \text{ and } T3R \nsubseteq T3
 \end{equation}
 
-\section{The challenge of detecting these clones}\label{chap:challenge}
+\subsection{The challenge of detecting these clones}\label{chap:challenge}
 To detect each type of clone, we need to parse the fully qualified identifier of all types, method calls and variables.
@@
 All these factors need to be considered for the referenced entity to be found, on basis of which a fully qualified identifier can be created.
-
-Mainly the requirement to have access to all external libraries is a difficult one to satisfy in diverse projects.
-Because of this, the proposed clone definitions may be less suitable for large scale clone detection purposes.
 

### 2019-07-25 sections/research.tex
New table stuff

@@
 \textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
-Siamese \cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
-NiCAD \cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
-CPD \cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
-\begin{tabular}[c]{@{}l@{}}CCFinder \cite{kamiya2002ccfinder}\\ D-CCFinder \cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
-CCFinderSW \cite{semura2017ccfindersw}   &    &             &             & \checkmark            \\ \hline
-\begin{tabular}[c]{@{}l@{}}SourcererCC \cite{sajnani2016sourcerercc}\\ Oreo \cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
-BigCloneEval \cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
-Deckard \cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
-Scorpio \cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
+Siamese~\cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
+NiCAD~\cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
+CPD~\cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
+\begin{tabular}[c]{@{}l@{}}CCFinder~\cite{kamiya2002ccfinder}\\ D-CCFinder~\cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
+CCFinderSW~\cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
+\begin{tabular}[c]{@{}l@{}}SourcererCC~\cite{sajnani2016sourcerercc}\\ Oreo~\cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
+BigCloneEval~\cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
+Deckard~\cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
+Scorpio~\cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
 \end{tabular}

### 2019-07-25 sections/introduction.tex
Intro

@@
 \section{Contributions}
-\todo{Rewrite this part}
-Our research makes the following contributions:
-\begin{enumerate}
-	\item We deliver several novel measurements regarding code clones on a large corpus of Java projects.
-	\item We deliver a novel clone detection tool that finds refactorable clones in Java.
-	\item We deliver a novel clone refactoring tool that suggests refactorings to be applied, and applies these refactorings.
-	\item We give further recommendations in how refactoring can be automatically applied to improve maintainability in software projects.
-\end{enumerate}
+\todo{TODO}
+%Our research makes the following contributions:
+%\begin{enumerate}
+%	\item We deliver several novel measurements regarding code clones on a large corpus of Java projects.
+%	\item We deliver a novel clone detection tool that finds refactorable clones in Java.
+%	\item We deliver a novel clone refactoring tool that suggests refactorings to be applied, and applies these refactorings.
+%	\item We give further recommendations in how refactoring can be automatically applied to improve maintainability in software projects.
+%\end{enumerate}
 

### 2019-07-25 sections/clonerefactor.tex
Removing redundant clone classes

@@
 \subsubsection{Removing redundant clone classes}\label{sec:conceptualremovingredundant}
-\ana{MOVE THIS, Part of the clone class collection and one that is found but not yet part of the collection.
-If the new one is a subset of the one in the collection then it is ignored.
-If the new one is a superset of any clone in the collection it replaces those.
-If one is a subset of the other it should be replaced.}
-
 The clone detection method used by CloneRefactor can, for various reasons,%Should I list these? Listing them could be a section on its own, as I'd have to show examples to make it concrete.
@@
 \begin{equation}\label{eq:subset}
-C_1 \subseteq C_2 \Leftrightarrow \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
+C_1 \subseteq C_2 := \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
 \end{equation} % Right symbol for definition

### 2019-07-25 sections/results.tex
Added corpus to results

@@
 In this chapter, we present the results of our experiments.
+
+\section{The corpus}\label{chap:corpus}
+For our experiments we use a large corpus of open source projects \cite{githubCorpus2013}.
+This corpus has been assembled to contain relatively higher quality projects.
+Also, any duplicate projects were removed from this corpus.
+This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
+
+As indicated in chapter \ref{chap:challenge} CloneRefactor requires all libraries of software projects we test.
+As these are not included in the used corpus \cite{githubCorpus2013}, we decided to filter the corpus to only include Maven projects.
+Maven is a build automation tool used primarily for Java, and works on basis of an \texttt{pom.xml} file to describe the projects' dependencies.
+As no \texttt{pom.xml} files are included in the corpus, we cloned the latest version of each project in the corpus.
+We then removed each project that has no \texttt{pom.xml} file.
+As a final step, we collected all dependencies for each project by using the \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib} Maven command, and removed each project for which not all dependencies were available (due to non-Maven dependencies being used or unsatisfiable dependencies being referenced in the \texttt{pom.xml} file).
+
+Some general data regarding this corpus is displayed in Table \ref{table:general}.
+
+\begin{table}[H]
+  \begin{center}
+  \caption{General results for GitHub Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
+  \medskip
+\begin{tabular}{|l|l|}
+\hline
+Amount of projects                                                                                      & 1,361      \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\whitespace, comments and newlines.)\end{tabular} & 1,414,996  \\ \hline
+Amount of statements/declarations                                                                       & 1,212,189  \\ \hline
+\begin{tabular}[c]{@{}l@{}}Amount of tokens (excluding\\whitespace, comments and newlines.)\end{tabular} & 11,643,194 \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
 

### 2019-07-25 sections/clonerefactor.tex
Removed experimental setup and merged it with clonerefactor

@@
 \subsubsection{Try to Expand}
-The problem with the graph clone detection technique is that
+The problem with the graph clone detection technique is that ...
+\todo{TODO}
 
@@
 \todo{TODO}
+
+\section{Context Analysis of Clones}\label{chap:contextsetup}
+To be able to refactor code clones, CloneRefactor maps the context of code clones. We define the following aspects of the clone as its context:
+\begin{enumerate}
+  \item \textbf{Relation:} The relation of clone instances among each other through inheritance.
+  \item \textbf{Location:} Where a clone instance occurs in the code.
+  \item \textbf{Contents:} The statements/declarations of a clone instance.
+\end{enumerate}
+We define categories for each of these aspects and enable CloneRefactor to determine the catagories of clones.
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.8\columnwidth]{img/context}
+    \caption{Abstract representation of clone classes and clone instances.}
+  \label{fig:clonecontext}
+\end{figure}
+
+Fig.~\ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
+The relation of clones through inheritance is measured for each clone class.
+The location and contents of clones are measured for each clone instance.
+
+\subsection{Relation}\label{sec:setuprelation}
+When merging code clones in object-oriented languages, it is important to consider the inheritance relation between clone instances. This relation has a big impact on how a clone should be refactored.
+
+Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other.
+To do this, they first define several categories for the relation between clone instances in object-oriented languages.
+These categories are as follows:
+\begin{enumerate}
+  \item \textbf{Same Method}: All instances of the clone class are in the same method.
+  \item \textbf{Same Class}: All instances of the clone class are in the same class.
+  \item \textbf{Superclass}: All instances of the clone class are in a class that is child or parent of each other.
+  \item \textbf{Sibling Class}: All instances of the clone class have the same parent class.
+    \item \textbf{Ancestor Class}: All instances of the clone class are superclasses except for the direct superclass.
+  \item \textbf{First Cousin Class}: All instances of the clone class have the same grandparent class.
+\item \textbf{Same Hierarchy Class}: All instances of the clone class belong to the same inheritance hierarchy, but do not belong to any of the other categories.
+\item \textbf{Same External Superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
+\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
+\end{enumerate}
+
+We added the following categories, to gain more information about clones and reduce the number of unrelated clones:
+
+\begin{enumerate}
+\item \textbf{Same Interface}: All instances of the clone class are in a class or interface that have a common interface anywhere in their inheritance hierarchy.
+\item \textbf{No Direct Superclass}: All instances of the clone class are in a class that does not have any superclass.
+\item \textbf{No Indirect Superclass}: All instances of the clone class are in a class that does not have any external classes in its inheritance hierarchy.
+\item \textbf{External Ancestor}: All instances of the clone class are in a class that does not have any external classes in its inheritance hierarchy.
+\end{enumerate}
+
+Figure \ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
+The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
+The location and contents of clones is measured on clone instance level.
+A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50).
+A clone instance contents consists of a list of all statements and declarations it spans.
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.6\columnwidth]{img/Relation}
+      \caption{Abstract figure displaying relations of clone classes. Arrows represent superclass relations.}
+  \label{fig:clonerelation}
+\end{figure}
+
+We separate these relations into the following categories, because of their related refactoring opportunities:
+\begin{itemize}
+  \item \textbf{Common Class}: \textit{Same Method}, \textit{Same Class}
+  \item \textbf{Common Hierarchy}: \textit{Superclass}, \textit{Sibling Class}, \textit{Ancestor Class}, \textit{First Cousin}, \textit{Same Hierarchy}
+  \item \textbf{Common Interface}: \textit{Same Interface}
+  \item \textbf{Unrelated}: \textit{No Direct Superclass}, \textit{No Indirect Superclass}, \textit{External Superclass}, \textit{External Ancestor}
+\end{itemize}
+
+Every clone class only has a single relation, which is the first relation from above list that the clone class applies to.
+For instance: all ``Superclass'' clones also apply to ``Same Hierarchy'', but because ``Superclass'' is earlier in above list they will get the ``Superclass'' relation.
+This is because the items earlier in the list denote a more favorable refactoring.
+
+To check a the relation for a given clone class, we compare each node in a clone instance with the respective nodes in each other clone instance within a clone class.
+So for a clone class with x clone instances and each clone instance has y nodes, we perform:
+
+\begin{equation}\label{eq:sameclass}
+\frac{x * (x + 1)}{2} * y
+\end{equation}
+
+comparisons to determine the relation.
+Each of these checks will result in one of the relations from the list above.
+Of these relations, the item lowest in the list is going to be the relation of the clone class.
+So for instance, if a clone class has 15 nodes that denote a \textit{Superclass} relation but 3 nodes are \textit{Unrelated}, the clone class becomes \textit{Unrelated}.
+
+\subsubsection{Common Class}
+The \textit{Same method} and \textit{Same class} relations share a common refactoring opportunity.
+Clones of both these catagories, when extracted to a new method, can be placed in the same class.
+Both of these relations are most favorable for refactoring, as they require a minimal design tradeoff.
+Furthermore, global variables that are used in the class can be used without having to create method parameters.
+
+Cloned nodes are flagged as \textit{Same method} if these nodes are found in the same method.
+We define the method as the first method declaration that is encountered when following the parent nodes in the ast for a given cloned node.
+Please note that a clone instance may not always be in a method, for which this predicate will fail.
+
+Cloned nodes are flagged as \textit{Same class} if these nodes are found in the same class.
+We define the class as the first class declaration that is encountered when following the parent nodes in the ast for a given cloned node.
+
+\subsubsection{Common Hierarchy}
+Clones that are in a common hierarchy can be refactored by using the ``Extract Method'' refactoring method followed by ``Pull Up Method'' until the method reaches a location that is accessible by all clone instances.
+However, the more often ``Pull Up Method'' has to be used, the more detrimental the effect is on system design.
+This is because putting a lot of functionality in classes higher up in an inheritance structure can result in the ``God Object'' anti-pattern.
+A god object is an object that knows too much or does too much.
+
+Cloned nodes are flagged as \textit{Superclass} if the classes in which these nodes are found are parent and child class of each other.
+Cloned nodes are flagged as \textit{Siblings} if the classes in which these nodes are found all share the same parent and this parent class is not external.
+Cloned nodes are flagged as \textit{First Cousin} if the classes in which these nodes are found all share the same grandparent and this grandparent class is not external.
+
+Cloned nodes are flagged as \textit{Ancestor} if the classes in which these nodes are found are recursively the parent of an antecedent.
+Cloned nodes are flagged as \textit{Same Hierarchy} if the classes in which these nodes are found are all in the same inheritance hierarchy and not linked by any external classes.
+
+\subsubsection{Common Interface}
+Many object-oriented languages know the concept of ``interfaces'', which are used to specify a behavior that classes must implement.
+As code clones describe functionality and interfaces originally did not allow for functionality, interfaces did not open up refactoring opportunities for duplicated code.
+However, many programming languages nowadays support default implementations in interfaces.
+Since Java 7 and C\#8, these programming languages allow for functionality to be defined in interfaces.
+Many other object-oriented languages like Python allow this by nature, as they do not have a true notion of interfaces.
+
+The greatest downside on system design of putting functionality in interfaces is that interfaces are per definition part of a classes' public contract.
+That is, all functionality that is shared between classes via an interface cannot be hidden by setting a stricter visibility.
+Because of that, we favor all ``Common Hierarchy'' refactoring opportunities over ``Common Interface''.
+
+To check whether two cloned nodes have common interfaces, we recursively walk all types the class or interface of the cloned nodes implement and extend.
+The common interface that is closest to the cloned node in terms of depth of recursion will be flagged as the refactoring candidate.
+
+\subsubsection{Unrelated}
+Clones are unrelated if they share no common class or interface in their inheritance structure.
+These clones are least favorable when looking at refactoring, because their refactoring will almost always have a major impact on system design.
+We formulated four catagories of unrelated clones to look into their refactoring opportunities.
+
+Cloned nodes are flagged \textit{No Direct Superclass} if they are in classes that do currently not have a parent.
+This marks the opportunity for creating a superclass abstraction and placing the extracted method there.
+Cloned nodes are flagged \textit{No Indirect Superclass} if any of their ancestors does not have a parent.
+In such a case, it would be possible to create such an abstraction for the ancestor that does not have a parent.
+
+Cloned nodes are flagged \textit{External Superclass} if they are in a class which has an external parent.
+Cloned nodes are flagged \textit{External Ancestor} if one of their ancestors has an external parent.
+Both of these relations obstruct the possibility of creating a superclass abstraction.
+In such a case, an interface abstraction could be created to make their relation explicit.
+
+\subsection{Location}\label{sec:setuplocation}
+A paper by Lozano et al.
+\cite{lozano2007evaluating} discusses the harmfulness of cloning.
+The authors argue that 98\% are produced at method-level.
+However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
+We decided to measure the locations of clones through static analysis on our dataset.
+We chose the following categories:
+\begin{enumerate}
+  \item \textbf{Method/Constructor Level:} A clone instance that does not exceed the boundaries of a single method or constructor (optionally including the declaration of the method or constructor itself).
+  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class (like field declarations, other methods, etc.).
+  \item \textbf{Interface Level:} A clone that is (a part of) an interface.
+  \item \textbf{Enumeration Level:} A clone that is (a part of) an enumeration.
+\end{enumerate}
+We check the location of each clone instance for each of its nodes.
+If any node reports a different location from the others, we choose the location that is lowest in above list.
+So for instance, if a clone instance has 15 nodes that denote a \textit{Method Level} location but 3 nodes are \textit{Class Level}, the clone instance becomes \textit{Class Level}.
+
+\todo{Explain why these categories indicate and how they are related to refactoring}
+
+\subsection{Contents}\label{sec:setupcontents}
+Finally, we looked at what nodes individual clone instances span. We selected the following categories to be relevant for refactoring:
+\begin{enumerate}
+  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
+  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially, optionally including its declaration.
+  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
+  \item \textbf{Only Fields:} A clone that spans only global variables.
+  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields and other things, like methods.
+  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
+  \item \textbf{Other:} Anything that does not match with above-stated categories.
+\end{enumerate}
+
+\todo{Explain each category in more detail}
+
+\section{Method extraction opportunities}\label{sec:refactorabilitysetup}
+The most used technique to refactor clones is method extraction (creating a new method on basis of the contents of clones).
+However, method extraction cannot be applied in all cases.
+In these instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.
+
+We measured the number of clones that can be refactored through method extraction (without additional transformations being required). We defined the following categories:
+\begin{itemize}
+    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a method.
+Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
+    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
+    \item \textbf{Spans part of a block:} This clone spans a part of a statement.
+    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table~\ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
+\end{itemize}
+
+\todo{Explain each category in more detail}

### 2019-07-25 sections/results.tex
Results

@@
 \begin{figure}[H]
+  \centering
+    \includegraphics[width=.5\columnwidth]{img/TypeResults}
       \caption{Number of cloned declarations/statements.}
-    \includegraphics[width=.5\columnwidth]{img/TypeResults}
   \label{fig:typeres}
@@
 We also measured the duration of finding clones by the different clone types.
-Fig.~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types.
+Figure~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types.
 Although this data is partly dependent on our implementation of the clone types, there is a notable difference between the refactoring-oriented clone types and the literature clone types.
-The reason for this is further explained in Sec.~\ref{chap:challenge}.
+The reason for this is further explained in section~\ref{chap:challenge}.
 
 \begin{figure}[H]
+  \centering
+    \includegraphics[width=.5\columnwidth]{img/DurationChart}
     \caption{Duration in minutes of identifying clones for clone type definitions.}
-    \includegraphics[width=.5\columnwidth]{img/DurationChart}
   \label{fig:performance}
@@
 For these experiments, we used our CloneRefactor tool.
-These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in chapter \ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in chapter \ref{chap:clonelocation};  the content of clone instances are explained, measured and discussed in chapter \ref{chap:clonecontents}.
-
-\subsection{Clone detection results}
-Currently, we have implemented two clone detection algorithms into CloneRefactor.
-The first one finds clones by comparing tokens (excluding whitespace, comments and newlines), equal to the definition of type 1 clones in literature \cite{roy2007survey}.
-The second algorithm implements our type 1R, as explained in chapter \ref{chap:type1clones}.
-The differences between the clones found for these algorithms is displayed in Table \ref{table:clonedet}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{CloneRefactor clone detection results for the two different algorithms.} \label{table:clonedet}
-  \medskip
-\begin{tabular}{|l|l|l|}
-\hline
- & \textbf{Type 1} & \textbf{Type 1R} \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines cloned\end{tabular} & 200,362 & 129,519 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of statements/\\declarations cloned\end{tabular} & 182,466 & 118,980 \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of tokens cloned\end{tabular} & 1,582,845 & 973,596 \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-Looking at Table \ref{table:clonedet}, it becomes apparent that the type 1R algorithm finds significantly less clones than the type 1 algorithm.
-This indicates that about a third of the clones have textual equality, but are not actually equal when considering the types of expressions.
-This makes these clones less suitable for automated refactoring.
+These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in chapter \ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in chapter \ref{chap:clonelocation};  he content of clone instances are explained, measured and discussed in chapter \ref{chap:clonecontents}.
 
 \subsection{Relations Between Clone Instances} \label{chap:relationsinstances}
+\todo{update these results}
 In section \ref{sec:setuprelation} we introduced our experiments regarding relations between clones. Table~\ref{table:relations} contains our results regarding the relations between clone instances.
@@
 \subsection{Clone instance location}\label{chap:clonelocation}
+\todo{update these results}
 Measuring the clone locations categories defined in section \ref{sec:setuplocation} yields the results displayed in Table \ref{table:contents}.
@@
 \section{Clone instance contents}\label{chap:clonecontents}
+\todo{update these results}
 Measuring the clone contents categories defined in section \ref{sec:setupcontents} yields the results displayed in Table \ref{table:contents}.
@@
 \section{Merging duplicate code through refactoring} \label{sec:refactorability}
+\todo{update these results}
 In section \ref{sec:refactorabilitysetup} we define catagories regarding the extent to which clones can be refactored through method extraction.

### 2019-07-25 sections/conclusion.tex
todos

@@
 \section{Future work} \label{sec:future_work}
+\todo{Move part of future work to discussion}
 This study presents a foundation for research in a largely unexplored field of studies: analyzing maintainability through automated refactoring.

### 2019-07-25 sections/conclusion.tex
Moving stuff from future work to the discussion

@@
 When multiple parameters are used together in a method, there is an implicit dependency between these parameters: the dependency of being required by that method.
-If a lot of data hangs around really tight together, they should be made into their own object \cite{fowler1999refactoring, visser2016building}.
+\textit{If a lot of data hangs around really tight together, they should be made into their own object} \cite{fowler1999refactoring, visser2016building}.
 Guidelines describe to limit the number of parameters per method to at most 4 \cite{visser2016building}.
@@
 
-\subsection{Identifying more types/definitions for clones}
-In this study, we proposed a set of clone type definitions for which a refactoring opportunity is known.
-We based these clone type definitions on the clone type definitions that are commonly used in literature.
-The design of these clone type definitions entails some decisions that have a large impact on the clones we considered for refactoring in this study.
-
-\subsubsection{Type 2R clones}
-With type 2R clones we allow variability in some identifiers and literals such that the code can and should still be refactored.
-For type 2R clones we chose a set of expressions in which we allow variability and proposed a recommended refactoring strategy.
-We think however that type 2R could still use a lot of improvement to find more duplication patterns that can be refactored.
-
-One method we think can be used to find more refactoring opportunities is to allow variability in expressions that have/return the same type.
-If expressions have/return the same type, they can be extracted to a parameter and the corresponding expression can be passed as a parameter.
-An example of this is displayed in figure \ref{fig:samereturn}.
-The only thing to watch out for is method that have side effects.
-Because methods may be executed in another point during execution, this might affect the functionality of the code.
-
-\begin{figure}[H]
-\begin{parcolumns}{2}
-\colchunk[1]{
-\begin{javacode}
-// Original
-public void doStuff(){
-  int numbers = 456;
-|\highlightYellow|  doA(getTitle());
-|\highlightYellow|  doB(123);
-  doC();
-|\highlightYellow|  doA("456");
-|\highlightYellow|  doB(numbers);
-}
-
-public String getTitle(){
-  return "123";
-}
-\end{javacode}}
-\colchunk[2]{
-\begin{javacode}
-// Refactored
-public void doStuff(){
-  int numbers = 456;
-|\highlightYellow|  doAandB(getTitle(), 123);
-  doC();
-|\highlightYellow|  doAandB("456", numbers);
-}
-
-public void doAandB(String var1, int var2){
-  doA(var1);
-  doB(var2);
-}
-
-public String getTitle(){
-  return "123";
-}
-\end{javacode}}
-\end{parcolumns}
-\caption{Refactoring different expressions that have the same return type.}
-\label{fig:samereturn}
-\end{figure}
-
-\subsubsection{Type 4 clones}
+\subsection{Type 4 clones}
 In section \ref{chap:backgroundclonetypes} we introduced the clone types that are used in literature.
@@
 For instance, for type 4 clones, one alternative might be easier to maintain.
-Also, they can differ (significantly) in performance.
+Also, they can differ in performance.
 
@@
 By proposing good definitions for code clones that mark the characteristics of harmful anti-patterns, we can create more accurate suggestions to developers.
-
-\subsection{Refactoring the harder to refactor clones}
-In section \ref{sec:refactorability} we introduced to what extent clones can be refactored through method extraction.
-Because we strived to get results fast, we excluded categories that could not not be directly refactored through method extraction.
-However, with a few transformations or further considerations it might be possible to make these clones refactorable.
-In this section we will highlight a few of these categories which we believe to be refactorable through method extraction with a bit more effort.
-
-\subsubsection{Partial block}
-We did not consider clones for refactoring that span a part of a block.
-Although it is indeed not possible to refactor such clones, there are possibilities to make such clones refactorable.
-For instance, if the programming language supports lambda expressions, we can move the difference of statements in the block in a lambda expression.
-Figure \ref{fig:partialblockrefactoring} shows an example of such a refactoring opportunity.
-
-\begin{figure}[H]
-\begin{parcolumns}{2}
-\colchunk[1]{
-\begin{javacode}
-// Original
-public void doStuff(){
-|\highlightYellow|  for(int i = 0; i<5; i++) { //Only the declaration of this for loop is cloned, but the loop body is not.
-    System.out.println("hello!");
-  }
-|\highlightYellow|  for(int i = 0; i<5; i++) {
-    CoreController.activateCore(i);
-  }
-}
-\end{javacode}}
-\colchunk[2]{
-\begin{javacode}
-// Refactored
-public void doStuff(){
-|\highlightYellow|  doFiveTimes(() -> System.out.println("hello!"));
-|\highlightYellow|  doFiveTimes(() -> CoreController.activateCore(i));
-}
-
-public void doFiveTimes(Runnable runnable){
-  for(int i = 0; i<5; i++) { //Only the declaration of this for loop is cloned, but the loop body is not.
-    runnable.run();
-  }
-}
-\end{javacode}}
-\end{parcolumns}
-\caption{Refactoring a method that is obstructed by a complex control flow.}
-\label{fig:partialblockrefactoring}
-\end{figure}
-
-\subsubsection{Overlap within a clone class}
-We do not consider clone classes for refactoring that overlap in the clone class itself.
-That is because such clones might require other techniques to refactor them.
-We consider analyzing such refactoring methods future work.
-An example refactoring of clone instances that overlap within their clone class is displayed in figure \ref{fig:overlaprefactoring}.
-In this example one clone instance is found between line \ref{line:overlaprefactoring1} and \ref{line:overlaprefactoring4} and the other between \ref{line:overlaprefactoring2} and \ref{line:overlaprefactoring5}.
-To refactor such clones, other techniques may be required, like introducing a new for-loop to reduce the duplication.
-
-\begin{figure}[H]
-\begin{parcolumns}{2}
-\colchunk[1]{
-\begin{javacode}
-// Original
-public void sayHello(){
-|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring1}|
-|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring2}|
-|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring3}|
-|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring4}|
-|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring5}|
-}
-\end{javacode}}
-\colchunk[2]{
-\begin{javacode}
-// Refactored
-public void sayHello(){
-|\highlightYellow|  for(int i = 0; i<5; i++){
-|\highlightYellow|    System.out.println("hello!");
-|\highlightYellow|  }
-}
-\end{javacode}}
-\end{parcolumns}
-\caption{Refactoring a clone class that has overlap between clone instances.}
-\label{fig:overlaprefactoring}
-\end{figure}
-
-\subsubsection{Complex control flow}
-Break, continue and return statements can obstruct the possibility of performing method extraction.
-However, with some extra transformations, method extraction will still be possible in such cases.
-Figure \ref{fig:complexcontrolflowrefactoring} shows such a transformation.
-We can wrap the newly extracted method in a conditional to indicate whether the ``control flow modifying statement'' should be executed.
-In other cases, other methods might apply to refactor such clones.
-
-\begin{figure}[H]
-\begin{parcolumns}{2}
-\colchunk[1]{
-\begin{javacode}
-// Original
-public boolean doStuff(){
-|\highlightYellow|  if(doA());
-|\highlightYellow|    return false;
-|\highlightYellow|  doB();
-  doC();
-|\highlightYellow|  if(doA());
-|\highlightYellow|    return false;
-|\highlightYellow|  doB();
-  return true;
-}
-\end{javacode}}
-\colchunk[2]{
-\begin{javacode}
-// Refactored
-public boolean doStuff(){
-|\highlightYellow|  if(!doAandB())
-|\highlightYellow|    return false;
-  doC();
-|\highlightYellow|  return doAandB();
-}
-
-public boolean doAandB(){
-  if(doA())
-    return false;
-  doB();
-  return true;
-}
-\end{javacode}}
-\end{parcolumns}
-\caption{Refactoring a method that is obstructed by a complex control flow.}
-\label{fig:complexcontrolflowrefactoring}
-\end{figure}
 

### 2019-07-25 sections/discussion.tex
todos
Moving stuff from future work to the discussion

@@
 \chapter{Discussion}
+\todo{TODO}
 \label{ch:discussion}
+
 In this chapter, we discuss the results of our experiment(s) on ...
@@
 Refer to Finding~\ref{find:important1}.
+
+\section{Clone Type Definitions}
+In this study, we proposed a set of clone type definitions for which a refactoring opportunity is known.
+We based these clone type definitions on the clone type definitions that are commonly used in literature.
+The design of these clone type definitions entails some decisions that have a large impact on the clones we considered for refactoring in this study.
+In this section we discuss our clone type definitions as proposed in section \ref{sec:rtypes}.
+
+\subsubsection{Type 2R clones}
+With type 2R clones we allow variability in some identifiers and literals such that the code can and should still be refactored.
+For type 2R clones we chose a set of expressions in which we allow variability and proposed a recommended refactoring strategy.
+We think however that type 2R could still use a lot of improvement to find more duplication patterns that can be refactored.
+
+One method we think can be used to find more refactoring opportunities is to allow variability in expressions that have/return the same type.
+If expressions have/return the same type, they can be extracted to a parameter and the corresponding expression can be passed as a parameter.
+An example of this is displayed in figure \ref{fig:samereturn}.
+The only thing to watch out for is method that have side effects.
+Because methods may be executed in another point during execution, this might affect the functionality of the code.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+public void doStuff(){
+  int numbers = 456;
+|\highlightYellow|  doA(getTitle());
+|\highlightYellow|  doB(123);
+  doC();
+|\highlightYellow|  doA("456");
+|\highlightYellow|  doB(numbers);
+}
+
+public String getTitle(){
+  return "123";
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+public void doStuff(){
+  int numbers = 456;
+|\highlightYellow|  doAandB(getTitle(), 123);
+  doC();
+|\highlightYellow|  doAandB("456", numbers);
+}
+
+public void doAandB(String var1, int var2){
+  doA(var1);
+  doB(var2);
+}
+
+public String getTitle(){
+  return "123";
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring different expressions that have the same return type.}
+\label{fig:samereturn}
+\end{figure}
+
+\section{Clone Context Analysis}
+In section \ref{chap:contextsetup} we introduced the catagories we defined for mapping the context of clones. In this section, we discuss this together with the related experiments.
+
+\subsection{Refactorability}
+In section \ref{sec:refactorability} we introduced to what extent clones can be refactored through method extraction.
+Because we strived to get results fast, we excluded categories that could not not be directly refactored through method extraction.
+However, with a few transformations or further considerations it might be possible to make these clones refactorable.
+In this section we will highlight a few of these categories which we believe to be refactorable through method extraction with a bit more effort.
+
+\subsubsection{Partial block}
+We did not consider clones for refactoring that span a part of a block.
+Although it is indeed not possible to refactor such clones, there are possibilities to make such clones refactorable.
+For instance, if the programming language supports lambda expressions, we can move the difference of statements in the block in a lambda expression.
+Figure \ref{fig:partialblockrefactoring} shows an example of such a refactoring opportunity.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+public void doStuff(){
+|\highlightYellow|  for(int i = 0; i<5; i++) { //Only the declaration of this for loop is cloned, but the loop body is not.
+    System.out.println("hello!");
+  }
+|\highlightYellow|  for(int i = 0; i<5; i++) {
+    CoreController.activateCore(i);
+  }
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+public void doStuff(){
+|\highlightYellow|  doFiveTimes(() -> System.out.println("hello!"));
+|\highlightYellow|  doFiveTimes(() -> CoreController.activateCore(i));
+}
+
+public void doFiveTimes(Runnable runnable){
+  for(int i = 0; i<5; i++) { //Only the declaration of this for loop is cloned, but the loop body is not.
+    runnable.run();
+  }
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring a method that is obstructed by a complex control flow.}
+\label{fig:partialblockrefactoring}
+\end{figure}
+
+\subsubsection{Overlap within a clone class}
+We do not consider clone classes for refactoring that overlap in the clone class itself.
+That is because such clones might require other techniques to refactor them.
+We consider analyzing such refactoring methods future work.
+An example refactoring of clone instances that overlap within their clone class is displayed in figure \ref{fig:overlaprefactoring}.
+In this example one clone instance is found between line \ref{line:overlaprefactoring1} and \ref{line:overlaprefactoring4} and the other between \ref{line:overlaprefactoring2} and \ref{line:overlaprefactoring5}.
+To refactor such clones, other techniques may be required, like introducing a new for-loop to reduce the duplication.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+public void sayHello(){
+|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring1}|
+|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring2}|
+|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring3}|
+|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring4}|
+|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring5}|
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+public void sayHello(){
+|\highlightYellow|  for(int i = 0; i<5; i++){
+|\highlightYellow|    System.out.println("hello!");
+|\highlightYellow|  }
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring a clone class that has overlap between clone instances.}
+\label{fig:overlaprefactoring}
+\end{figure}
+
+\subsubsection{Complex control flow}
+Break, continue and return statements can obstruct the possibility of performing method extraction.
+However, with some extra transformations, method extraction will still be possible in such cases.
+Figure \ref{fig:complexcontrolflowrefactoring} shows such a transformation.
+We can wrap the newly extracted method in a conditional to indicate whether the ``control flow modifying statement'' should be executed.
+In other cases, other methods might apply to refactor such clones.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+public boolean doStuff(){
+|\highlightYellow|  if(doA());
+|\highlightYellow|    return false;
+|\highlightYellow|  doB();
+  doC();
+|\highlightYellow|  if(doA());
+|\highlightYellow|    return false;
+|\highlightYellow|  doB();
+  return true;
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+public boolean doStuff(){
+|\highlightYellow|  if(!doAandB())
+|\highlightYellow|    return false;
+  doC();
+|\highlightYellow|  return doAandB();
+}
+
+public boolean doAandB(){
+  if(doA())
+    return false;
+  doB();
+  return true;
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring a method that is obstructed by a complex control flow.}
+\label{fig:complexcontrolflowrefactoring}
+\end{figure}

### 2019-07-25 sections/introduction.tex
Scope

@@
 \section{Scope}
-\todo{Rewrite this part}
-In this research we will look into code clones from a refactoring viewpoint.
-There are several methods that detect code clones using a similarity score to match pieces of code.
-This similarity is often based on the amount of tokens that match between two pieces of code.
-The problem with similarity based clones is that it is hard to assess the impact of merging clones that have different tokens, but what exactly this token is is unknown.
-Because of this, we will not focus on similarity based clone detection techniques, but rather on exact matches and predefined differences.
+In this study, we perform research efforts to be able to detect refactorable clones.
+We will apply refactoring techniques to a subset of these clones and analyze the maintainability of the resulting source code.
+
+There is a lot of study on how what metrics to consider to measure maintainability.
+In this study, we focus solely on the practical maintainability model by Heitlager et al.
+\cite{heitlager2007practical}.
+We consider the maintainability scores described in that paper as an sufficiently accurate indication of maintainability.
+This will be used to quantitatively determine the impact on maintainability when applying refactoring techniques to code clones.
+
+Applying refactoring often entails creating new method declarations, class declarations, etc.
+Each of these declarations needs to have a name.
+Because the quality of the name is not included in the maintainability metrics we use, finding appropriate names for automatically refactored code fragments is out of the scope for this study.
+For our automated refactoring efforts, we will use generated names for these declarations.
 

### 2019-07-25 sections/introduction.tex
Research method

@@
 However, there is no research yet that looks into how these definitions align with refactoring opportunities.
-We will align clone type definitions as used in literature \ref{roy2007survey} with their corresponding refactoring methods \ref{fowler2018refactoring}.
+We will align clone type definitions as used in literature \cite{roy2007survey} with their corresponding refactoring methods \cite{fowler2018refactoring}.
 For this, we answer the following research question:
@@
 \subsection{Research method}
-\todo{TODO}
+We consider this an \textbf{applied} research in which we solve a practical problem.
+We propose definitions and tools which allow to automatically refactor and analyze code clones.
+This is an \textbf{exploratory} research effort in the research field of analyzing maintainability through automated refactoring.
+We conduct an \textbf{inductive} research that aims to develop the theory to what extent code clones can be automatically refactored to improve the maintainability of software systems.
+
+Our research is entirely \textbf{quantitative}, focused on numbers and statistics.
 

### 2019-07-25 sections/introduction.tex
Introduction

@@
 
-We perform several experiments on a large corpus of open source software to collect statistical data.
+We perform several quantitative experiments on a large corpus of open source software to collect statistical data.
 With these experiments we map the context of clones: where they reside in the codebase and what the relation is between duplicate fragments.
-We use this information to find appropriate refactoring opportunities for specific clones.
-We build a script to automatically refactor a subset of these clones.
+We use the results to find appropriate refactoring opportunities for specific clones.
+We then automate the process of applying such refactorings, to be able to measure the impact on maintainability when refactoring clones found by certain definitions and thresholds.
 

### 2019-07-25 sections/introduction.tex
Removed research method

@@
 Not in all cases will refactoring duplicated code result in a more maintainable codebase.
-Because of that, we want to compare the refactored code to the original code and measure the difference in maintainability.
+Because of that, we compare the refactored code to the original code and measure the difference in maintainability.
 To do this, we will use a practical model consisting of metrics to measure maintainability \cite{heitlager2007practical}.
@@
 These thresholds consist of the size of clones and the variability we can allow between cloned fragments to still consider them clones.
-
-\subsection{Research method}
-We consider this an \textbf{applied} research in which we solve a practical problem.
-We propose definitions and tools which allow to automatically refactor and analyze code clones.
-This is an \textbf{exploratory} research effort in the research field of analyzing maintainability through automated refactoring.
-We conduct an \textbf{inductive} research that aims to develop the theory to what extent code clones can be automatically refactored to improve the maintainability of software systems.
-
-Our research is entirely \textbf{quantitative}, focused on numbers and statistics.
 

### 2019-07-25 sections/introduction.tex
Research method: attempt numero dos

@@
 
+\subsection{Research method}
+We perform an \textbf{exploratory} study to look into the opportunities to automatically refactor code clones.
+To do this, we combine knowledge from literature with our own experience to develop definitions for refactorable clones.
+We also develop a tool to detect, analyze and refactor such clones.
+Using this tool, we perform \textbf{quantitative} experiments in which we statistically collect information about duplication in open source software.
+In these experiments we control several variables to see their impact on the results.
+During this process we explore concepts and develop understanding, because of which decisions in the study design are based upon the results of the experiments.
+
 \section{Contributions}

### 2019-07-25 sections/introduction.tex
Outline

@@
 In Chapter~\ref{ch:background} we describe the background of this thesis.
-Chapter~\ref{ch:research} describes ...
-Results are shown in Chapter~\ref{ch:results} and discussed in Chapter~\ref{ch:discussion}. Chapter~\ref{ch:related_work}, contains the work related to this thesis.
+In Chapter~\ref{chap:clonetypes} we list shortcomings with clone definitions from literature and propose a set of clone type definitions which can be automatically refactored.
+In Chapter \ref{ch:clonerefactor} we propose a tool to detect, analyze and automatically refactor such clones that can be refactored.
+Using this tool we perform a set of experiments, of which the results are shown in Chapter~\ref{ch:results} and discussed in Chapter~\ref{ch:discussion}.
+Chapter~\ref{ch:related_work} contains the work related to this thesis.
 Finally, we present our concluding remarks in Chapter~\ref{ch:conclusion} together with future work.

### 2019-07-25 sections/introduction.tex
AAH

@@
 \section{Contributions}
-\todo{TODO}
+Many modern clone detection techniques and thresholds have been validated by manually assessing a sample of the results \cite{sajnani2016sourcerercc, cordy2011nicad, jiang2007deckard}. 
 %Our research makes the following contributions:
@@
 \section{Outline}
-\todo{Rewrite this part}
 In Chapter~\ref{ch:background} we describe the background of this thesis.

### 2019-07-25 sections/introduction.tex
Contributions (again) :)

@@
 Often, these clone detection tools result in false-positives and false-negatives \cite{roy2007survey}.
+We define false-negatives as clones that can and should be refactored but are not found due to the configuration by which they are detected.
+We define false-positives as clones that do not improve the system maintainability when refactored.
 Many false-negatives are due to the thresholds that are used.
 Many clone detection tools \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval} only consider clones that have a minimum of 6 lines.
-Using such an approach is bound to result in many false-negatives.
+Using such an approach is bound to result in many false-negatives, but using a lower threshold is shown to increase the number of false-positives.
+%TODO cite threshold paper
 
@@
 \section{Contributions}
-Many modern clone detection techniques and thresholds have been validated by manually assessing a sample of the results \cite{sajnani2016sourcerercc, cordy2011nicad, jiang2007deckard}. 
-%Our research makes the following contributions:
-%\begin{enumerate}
-%	\item We deliver several novel measurements regarding code clones on a large corpus of Java projects.
-%	\item We deliver a novel clone detection tool that finds refactorable clones in Java.
-%	\item We deliver a novel clone refactoring tool that suggests refactorings to be applied, and applies these refactorings.
-%	\item We give further recommendations in how refactoring can be automatically applied to improve maintainability in software projects.
-%\end{enumerate}
+Many studies report that code clones negatively affect maintainability \cite{heitlager2007practical, monden2002software, juergens2009code, chatterji2013effects}.
+However, no studies yet show in what cases code clones can reduce maintainability in source code.
+Refactoring often includes tradeoffs between design alternatives.
+With some code clones, the refactored alternative is worse maintainable than keeping the duplication \cite{kapser2006cloning, aversano2007clones, hotta2010duplicate, kim2005empirical, krinke2007study, saha2010evaluating}.
+In this study, we analyze the maintainability of refactored code clones, in order to improve the suggestion of code clones that should be refactored.
+This assists with both the identification and refactoring of code clones.
+
+\subsection{Identification}
+There are many tools to detect clones.
+The goal of most of these tools is to assist developers in reducing duplication in their code, i.e.
+assisting in the refactoring process.
+The problem is that these tools have no limited insight on the impact of refactoring such clones on the design of the software.
+In this study, we can analyze a before- and after-refactoring snapshot of the code to determine the impact.
+A higher maintainability after refactoring increases the support for the clone being a true-positive.
+This way the results of our study can support the clone identification process.
+
+\subsection{Refactoring}
+The tool that results from this research can aid in the process of applying refactorings to clones.
+The tool will only apply a refactoring if the clone is refactorable and the maintainability of the source code increases as a result of applying the refactoring.
+The tool applies only refactorings that do not, in any way, influence the functional correctness of the program.
+Because of this, potential bugs as a result of refactoring can be avoided \cite{bavota2012does}.
 

### 2019-07-28 sections/clonerefactor.tex
Outline
Examples n stuff

@@
-\chapter{CloneRefactor}
+\chapter{CloneRefactor} \label{ch:clonerefactor}
 % We bridged a gap between clone detection and refactoring .. by designing a tool
@@
 
+\todo{These equality arrays do not include the ( and ) separators. This is not completely right. Should we change it?}
 \begin{figure}[H]
@@
 Although the duplicate relations allow for variability in the equality arrays as long as it falls under the threshold, negative numbers in the equality array may never vary.
-This is because negative numbers are the tokens/expressions that we do not allow variability in because they cannot be refactored in the same way.
+This is because negative numbers are the tokens/expressions that we do not allow variability in because they cannot be refactored in the same way:
 \begin{equation}\label{eq:t2rcloneequality}
-E_1\text{ can only be cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1, y \in E_2) x<0 \lor y<0 \Rightarrow x=y
+E_1\text{ can only be cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1, y \in E_2)\text{ }x<0 \lor y<0 \Rightarrow x=y
 \end{equation}
@@
 
-Where \textit{C} denotes the clone class and \textit{I} denotes the clone instance. As the graph is traversed starting at the end, equal to graph traversal during clone detection, the last node in
+Where \textit{C} denotes the clone class and \textit{I} denotes the clone instance.
+The graph is traversed, starting from the last node in the code fragment (equal to graph traversal during clone detection).
+Because of that, $C_1$ $I_1$ is the very last clone instance in this example.
 
 \subsubsection{Try to Expand}
-The problem with the graph clone detection technique is that ...
+The problem with the graph clone detection technique is that only single nodes that are within the variability threshold are considered duplicates of each other.
+However, single nodes that are not within this threshold could still be part of a clone class if the other cloned nodes are more towards the lower bound of the threshold.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+doA(a); //{1, -2, 3, -8, -9}
+|\highlightYellow|doB();
+doC(a);
+|\highlightYellow|doD();
+|\highlightYellow|doE();
+|\highlightYellow|doF();
+doG(a, b, c);
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+doB(d, e, f);
+|\highlightYellow|doA();
+|\highlightYellow|doB();
+|\highlightYellow|doC();
+doB(d, e, f);
+\end{javacode}}
+\end{parcolumns}
+\caption{Type 2R clones with equality arrays and variability percentages.}
+\label{fig:trytoexpand}
+\end{figure}
+
+As an example, consider the clone fragment in figure \ref{fig:trytoexpand}.
+
 \todo{TODO}

### 2019-07-28 sections/clonerefactor.tex
Better? Better.

@@
 
-Although the duplicate relations allow for variability in the equality arrays as long as it falls under the threshold, negative numbers in the equality array may never vary.
-This is because negative numbers are the tokens/expressions that we do not allow variability in because they cannot be refactored in the same way:
+In this graph, the duplicate relations (green arrows) do not necessarily denote an exact match.
+The duplicate relations allow for variability in the equality arrays as long as it falls under the variability threshold.
+However, negative numbers in the equality array may never vary.
+This is because negative numbers are the tokens/expressions that we do not allow variability in because they cannot be refactored as easily:
 \begin{equation}\label{eq:t2rcloneequality}
@@
 Where \textit{C} denotes the clone class and \textit{I} denotes the clone instance.
-The graph is traversed, starting from the last node in the code fragment (equal to graph traversal during clone detection).
-Because of that, $C_1$ $I_1$ is the very last clone instance in this example.
+The process by which these clones are found is equal to the clone detection process as described in section \ref{sec:detectingclones}.
+In this example, we see the four clones found on the graph of figure \ref{fig:clonerefactorprocess}.
+Three of these clone classes have a two clone instances, each consisting of a single nodes.
+The other clone class has three clone instances, each consisting of two nodes.
 

### 2019-07-28 sections/clonerefactor.tex
Getting somewhere

@@
 \begin{equation}\label{eq:variabilityclonerefactor}
-\frac{|\{x>0 \land y>0 \land x \neq y\text{ }|\text{ }x \in E_1 \cup E_2, y \in E_3 \cup E_4\}|}{(|E_1|+|E_2|)+(|E_3|+|E_4|)}*100
+\text{T2R Variability} = \frac{|\{x>0 \land y>0 \land x \neq y\text{ }|\text{ }x \in E_1 \cup E_2, y \in E_3 \cup E_4\}|}{(|E_1|+|E_2|)+(|E_3|+|E_4|)}*100
 \end{equation}
@@
 \begin{javacode}
-doA(a); //{1, -2, 3, -8, -9}
-|\highlightYellow|doB();
-doC(a);
-|\highlightYellow|doD();
-|\highlightYellow|doE();
-|\highlightYellow|doF();
-doG(a, b, c);
+|\highlightYellow|doA(); //{1, -2, -3, -4}
+doB(a); //{5, -2, 7, -3, -4}
+|\highlightYellow|doD(); //{8, -2, -3, -4}
+|\highlightYellow|doE(); //{9, -2, -3, -4}
+|\highlightYellow|doF(); //{10, -2, -3, -4}
+doG(a, b); //{11, -2, 7, -3, -4}
 \end{javacode}}
@@
 \begin{javacode}
-doB(d, e, f);
-|\highlightYellow|doA();
-|\highlightYellow|doB();
-|\highlightYellow|doC();
-doB(d, e, f);
+|\highlightYellow|doA(); //{1, -2, -3, -4}
+doC(a); //{6, -2, 7, -3, -4}
+|\highlightYellow|doD(); //{8, -2, -3, -4}
+|\highlightYellow|doE(); //{9, -2, -3, -4}
+|\highlightYellow|doF(); //{10, -2, -3, -4}
+doH(b); //{12, -2, 13, -3, -4}
 \end{javacode}}
 \end{parcolumns}
-\caption{Type 2R clones with equality arrays and variability percentages.}
+\caption{Type 2R clones with their equality arrays.}
 \label{fig:trytoexpand}
@@
 As an example, consider the clone fragment in figure \ref{fig:trytoexpand}.
+In this example, we have 2 clone classes.
+In the ``Try To Expand'' step, we will check whether we can create a clone class with larger clone instances on basis of the clones found in the previous step.
+We start with the largest clone class, measured in clone volume.
+We measure clone volume as the product of the amount of clone instances in a clone class and the amount of nodes in any of its instances.
+
+In the example in figure \ref{fig:trytoexpand} the largest instance has a volume of:
+
+\begin{equation}\label{eq:clonevolume}
+3 \text{ nodes} * 2 \text{ clone instances} = 6
+\end{equation}
+
+Starting from this clone, we will try to expand it.
+We will include the previous node in the clone class and verify its variability threshold.
+In this case, using the formulas shown in section \ref{sec:t2rcheckglobalthres}, we can check whether this clone class would be valid by the variability threshold:
+
+\begin{equation}\label{eq:variabilitycombined}
+\frac{|\{(5,6)\}|}{(5+4+4+4)+(5+4+4+4)}*100 = \frac{1}{34}*100 = 15\%
+\end{equation}
 

### 2019-07-28 sections/clonerefactor.tex
Fairer comparison?

@@
 \begin{equation}\label{eq:variabilityclonerefactor}
-\text{T2R Variability} = \frac{|\{x>0 \land y>0 \land x \neq y\text{ }|\text{ }x \in E_1 \cup E_2, y \in E_3 \cup E_4\}|}{(|E_1|+|E_2|)+(|E_3|+|E_4|)}*100
+\text{T2R Variability} = \frac{|\{x>0 \land y>0 \land x \neq y \Rightarrow (x,y) \text{ }|\text{ }x \in E_1 \cup E_2, y \in E_3 \cup E_4\}|}{|\{x>0 \land y>0 \Rightarrow (x,y) \text{ }|\text{ }x \in E_1 \cup E_2, y \in E_3 \cup E_4\}|}*100
 \end{equation}
 
-Where \textit{E} refers to the equality arrays shown in table \ref{table:equalityarrays}.
+Where $E_x$ refers to the equality arrays shown in table \ref{table:equalityarrays} and \textit{x} is the node number displayed in the same table.
 When we apply this equation to the example clone classes displayed in figure \ref{fig:equalityarrays}, we get the following sum:
@@
 \begin{equation}\label{eq:sumequality}
-\frac{|\{(3,4), (1,8), (7,9)\}|}{(5+5)+(5+5)}*100 = \frac{3}{20}*100 = 15\%
+\frac{|\{(3,4), (1,8), (7,9)\}|}{|\{(1,1), (3,4), (1,8), (7,9)\}|}*100 = \frac{3}{4}*100 = 75\%
 \end{equation}
 
-So for the example given in figure \ref{fig:equalityarrays} we have a variability of 15\%.
+So for the example given in figure \ref{fig:equalityarrays} we have a variability of 75\%.
 In CloneRefactor, the maximum variability percentage is a threshold that is entered in a configuration file.

### 2019-07-28 sections/clonerefactor.tex
Try to expand

@@
 
-So for the example given in figure \ref{fig:equalityarrays} we have a variability of 75\%.
+So for the example given in figure \ref{fig:equalityarrays} we have a variability of 75r \%.
 In CloneRefactor, the maximum variability percentage is a threshold that is entered in a configuration file.
@@
 \begin{javacode}
-|\highlightYellow|doA(); //{1, -2, -3, -4}
+|\highlightYellow|doA(a); //{1, -2, 7, -3, -4}
 doB(a); //{5, -2, 7, -3, -4}
@@
 |\highlightYellow|doF(); //{10, -2, -3, -4}
-doG(a, b); //{11, -2, 7, -3, -4}
+doG(a); //{11, -2, 7, -3, -4}
 \end{javacode}}
@@
 \begin{javacode}
-|\highlightYellow|doA(); //{1, -2, -3, -4}
+|\highlightYellow|doA(a); //{1, -2, 7, -3, -4}
 doC(a); //{6, -2, 7, -3, -4}
@@
 Starting from this clone, we will try to expand it.
-We will include the previous node in the clone class and verify its variability threshold.
+We will include the previous node in the clone class and verify its variability threshold (node $N_2$).
 In this case, using the formulas shown in section \ref{sec:t2rcheckglobalthres}, we can check whether this clone class would be valid by the variability threshold:
@@
 \begin{equation}\label{eq:variabilitycombined}
-\frac{|\{(5,6)\}|}{(5+4+4+4)+(5+4+4+4)}*100 = \frac{1}{34}*100 = 15\%
+\frac{|\{(5,6)\}|}{(5,6),(7,7),(8,8),(9,9),(10,10)}*100 = \frac{1}{5}*100 = 20\%
 \end{equation}
 
-\todo{TODO}
+Dependent on the actual variability threshold, the clone class would get expanded with node $N_2$.
+For this example, we assume the variability threshold is set to 15\%.
+In such a case, including this node would not result in a valid clone class.
+However, we continue trying to expand this clone class until we have reached the first node of the originally cloned fragment (the cloned fragment that did not take the variability threshold into account).
+Thus, we now try to expand with $\{N_1, N_2\}$.
+We then get the following formula:
+
+\begin{equation}\label{eq:variabilitycombined}
+\frac{|\{(5,6)\}|}{(1,1),(7,7),(5,6),(7,7),(8,8),(9,9),(10,10)}*100 = \frac{1}{7}*100 = 14\%
+\end{equation}
+
+This falls under the threshold of 15\% so we expand the clone class.
+Thus, the clone class $\{N_3, N_4, N_5\}$ will become $\{N_1, N_2, N_3, N_4, N_5\}$.
+We cannot expand further because we have reached the end of the original cloned fragment.
+When we are done expanding to previous nodes, we will try to expand to next nodes.
+In this case, we check whether we can include $N_6$ into the clone class.
+If $N_6$ would be included, the variability threshold would be as follows:
+
+\begin{equation}\label{eq:variabilitycombined}
+\frac{|\{(5,6),(11,12),(7,13)\}|}{(1,1),(7,7),(5,6),(7,7),(8,8),(9,9),(10,10),(11,12),(7,13)}*100 = \frac{3}{9}*100 = 33\%
+\end{equation}
+
+This does not fall within the variability threshold, so we do not include this node in the clone class.
+After we have checked a single clone class within the bigger cloned fragment for expansion opportunities, we go on with the next clone class (by volume).
+In this case, the other clone class within this fragment has become a subset of the clone class we just expanded.
+Because of that, this other clone class is discarded.
+For the example code fragment in figure \ref{fig:trytoexpand} the resulting clone class is $\{N_1, N_2, N_3, N_4, N_5\}$.
 

### 2019-07-28 sections/clonerefactor.tex
Fixed some formulas
Simplified

@@
 
-\todo{These equality arrays do not include the ( and ) separators. This is not completely right. Should we change it?}
 \begin{figure}[H]
@@
 
-In figure \ref{fig:2rvariabilityhigh4} we display the equality arrays for each of the lines of a code example with a complex distribution of cloned fragments.
+In figure \ref{fig:2rvariabilityhigh4} we display clone classes and their (simplified) equality arrays.
 We can convert this to a graph, using a similar process as the graph creation process used for clone detection.
@@
 \begin{equation}\label{eq:variabilitycombined}
-\frac{|\{(5,6)\}|}{(5,6),(7,7),(8,8),(9,9),(10,10)}*100 = \frac{1}{5}*100 = 20\%
+\frac{|\{(5,6)\}|}{|\{(5,6),(7,7),(8,8),(9,9),(10,10)\}|}*100 = \frac{1}{5}*100 = 20\%
 \end{equation}
@@
 \begin{equation}\label{eq:variabilitycombined}
-\frac{|\{(5,6)\}|}{(1,1),(7,7),(5,6),(7,7),(8,8),(9,9),(10,10)}*100 = \frac{1}{7}*100 = 14\%
+\frac{|\{(5,6)\}|}{|\{(1,1),(7,7),(5,6),(7,7),(8,8),(9,9),(10,10)\}|}*100 = \frac{1}{7}*100 = 14\%
 \end{equation}
@@
 \begin{equation}\label{eq:variabilitycombined}
-\frac{|\{(5,6),(11,12),(7,13)\}|}{(1,1),(7,7),(5,6),(7,7),(8,8),(9,9),(10,10),(11,12),(7,13)}*100 = \frac{3}{9}*100 = 33\%
+\frac{|\{(5,6),(11,12),(7,13)\}|}{|\{(1,1),(7,7),(5,6),(7,7),(8,8),(9,9),(10,10),(11,12),(7,13)\}|}*100 = \frac{3}{9}*100 = 33\%
 \end{equation}

### 2019-07-29 sections/background.tex
Addressing notes
More colors
T3R

@@
 T & Token & - & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code.
-\\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this token\\spans.\\ \textbf{Category:} Identifier, Keyword,\\Literal, Separator, Operator,\\ Comment or Whitespace.\end{tabular} \\
+\\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range (R):} The range this token\\spans.\\ \textbf{Category (C):} Identifier, Keyword,\\Literal, Separator, Operator,\\ Comment or Whitespace.\end{tabular} \\
 \rowcolor[HTML]{FFFFFF}
 N & Node \cite{jiang2007deckard} & Set of tokens.
-& \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this node\\spans.\end{tabular} \\
+& \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range (R):} The range this node\\spans.\end{tabular} \\
 \rowcolor[HTML]{EFEFEF}
-I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\nodes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{File:} The file in which this\\clone instance is found.\end{tabular} \\
+I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\nodes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{File (F):} The file in which this\\clone instance is found.\end{tabular} \\
 \rowcolor[HTML]{FFFFFF}
@@
 
-\definecolor{lightyellow}{HTML}{fffdcc}
-\definecolor{doublelightyellow}{HTML}{fffa9c}
-\newcommand{\highlightYellow}{\makebox[0pt][l]{\color{lightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
-\newcommand{\highlightDarkyellow}{\makebox[0pt][l]{\color{doublelightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
 \begin{figure}[H]
@@
 This can sometimes be a burden, when an external dependency does not use proper abstractions that are required by a software system.
-Because of that, in this study, we consider external classes to see what impact they have on the refactoring process.
-\simon{Adapter pattern?}
+Because of that, in this study, we differentiate between internal and external classes to see what impact they have on the refactoring process.
 

### 2019-07-29 sections/clonerefactor.tex
T3R

@@
 After the global threshold check has failed, we build a clone graph on basis of the equality arrays.
+The process used for building this graph is the same as the process described in \ref{sec:buildingclonegraph}.
 
@@
 
-\begin{equation}\label{eq:variabilitycombined}
+\begin{equation}\label{eq:variabilitycombined1}
 \frac{|\{(5,6)\}|}{|\{(5,6),(7,7),(8,8),(9,9),(10,10)\}|}*100 = \frac{1}{5}*100 = 20\%
@@
 
-\begin{equation}\label{eq:variabilitycombined}
+\begin{equation}\label{eq:variabilitycombined2}
 \frac{|\{(5,6)\}|}{|\{(1,1),(7,7),(5,6),(7,7),(8,8),(9,9),(10,10)\}|}*100 = \frac{1}{7}*100 = 14\%
@@
 
-\begin{equation}\label{eq:variabilitycombined}
+\begin{equation}\label{eq:variabilitycombined3}
 \frac{|\{(5,6),(11,12),(7,13)\}|}{|\{(1,1),(7,7),(5,6),(7,7),(8,8),(9,9),(10,10),(11,12),(7,13)\}|}*100 = \frac{3}{9}*100 = 33\%
@@
 \subsection{Checking for type 3 opportunities} \label{sec:t3rclonerefactor}
-\todo{TODO}
+As described in section \ref{sec:type3r}, we define type 3R clones as gapped clones.
+This means that two existing clones may have a gap of non-gapped clones.
+We check for every found clone class whether it is a type 3R clone with another clone:
+
+\begin{equation}\label{eq:crtype3r}
+\forall (c_1 \in S) \exists (c_2 \in S) x \neq y \land isType3R(c_1, c_2)
+\end{equation}
+
+Where \textit{S} is the set of all found clone classes.
+\textit{$\text{isType3R}(C_1, C_2)$} is a Boolean-valued function that denotes whether two clone classes are type 3R clones of each other.
+Two clone classes are type 3R clones of each other if each of their instances are within a certain distance of each other:
+
+\begin{equation}\label{eq:istype3r}
+\text{isType3R}(C_1, C_2) = \forall (i_1 \in C_1) \exists (i_2 \in C_2) Fi_1 = Fi_2 \land (gap(i_1, i_2) < gap_threshold \lor gap(i_2, i_1) < gap_threshold)
+\end{equation}
+
+Where \textit{F} is the file in which the clone instance is located.
+\textit{gap_threshold} is the defined threshold percentage of the maximum gap size between two clone instances.
+\textit{$gap(I_1, I_2)$} is the function that calculates the gap between two clone instances.
 
 \section{Context Analysis of Clones}\label{chap:contextsetup}
-To be able to refactor code clones, CloneRefactor maps the context of code clones. We define the following aspects of the clone as its context:
+To be able to refactor code clones, CloneRefactor first maps the context of code clones. We define the following aspects of the clone as its context:
 \begin{enumerate}

### 2019-07-29 sections/clonerefactor.tex
Formula does weird
Fixed compile

@@
 \begin{equation}\label{eq:istype3r}
-\text{isType3R}(C_1, C_2) = \forall (i_1 \in C_1) \exists (i_2 \in C_2) Fi_1 = Fi_2 \land (gap(i_1, i_2) < gap_threshold \lor gap(i_2, i_1) < gap_threshold)
+\text{isType3R}(C_1, C_2) = \forall (i_1 \in C_1) \exists (i_2 \in C_2) Fi_1 = Fi_2 \land gap(i_1, i_2) < gap\_threshold
 \end{equation}
@@
 Where \textit{F} is the file in which the clone instance is located.
-\textit{gap_threshold} is the defined threshold percentage of the maximum gap size between two clone instances.
-\textit{$gap(I_1, I_2)$} is the function that calculates the gap between two clone instances.
+\textit{gap\_threshold} is the defined threshold percentage of the maximum gap size between two clone instances.
+\textit{$\text{gap}(I_1, I_2)$} is the function that calculates the gap between two clone instances.
 

### 2019-07-29 sections/clonerefactor.tex
An example

@@
 \textit{$\text{gap}(I_1, I_2)$} is the function that calculates the gap between two clone instances.
+This gap is calculated by dividing the amount of statements in the gap by the amount of statements that both clone instances span together:
+
+\begin{equation}\label{eq:t3rgap}
+\text{gap}(i_1, i_2) = \frac{|\{(Rn>Ri_1 \land Rn<Ri_2) \lor (Rn>Ri_2 \land Rn<Ri_1)\text{ }|\text{ } n \in nodes(Fi_1)\}|}{|i_1| + |i_2|} * 100
+\end{equation}
+
+Where \textit{F} is the file in which the clone instance is located and \textit{R} is the range of a clone instance or node.
+A range denotes the line and column at which a code fragment starts and ends.
+We define the partial order relationship on ranges as follows:
+
+\begin{equation}\label{eq:rangetotalorder}
+R_1 < R_2 \text{ iff } end_line(R_1) < begin_line(R_2) \lor (end_line(R_1) = begin_line(R_2) \land end_column(R_1) < begin_column(R_2))
+\end{equation}
+\begin{equation}\label{eq:rangetotalorder2}
+R_1 > R_2 \text{ iff } begin_line(R_1) > end_line(R_2) \lor (begin_line(R_1) = end_line(R_2) \land begin_column(R_1) > end_column(R_2))
+\end{equation}
+
+\subsubsection{Example}
+In this section we show an example of the identification of a type 3R clone.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+//File1.java
+|\highlightYellow|doA(); // |\textcolor{pgreen}{$C_1$ $I_1$}|
+|\highlightYellow|doB(); // |\textcolor{pgreen}{$C_1$ $I_1$}|
+doC();
+|\highlightBlue|doC(); // |\textcolor{pgreen}{$C_2$ $I_1$}|
+|\highlightBlue|doD(); // |\textcolor{pgreen}{$C_2$ $I_1$}|
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+//File2.java
+|\highlightYellow|doA(); // |\textcolor{pgreen}{$C_1$ $I_2$}|
+|\highlightYellow|doB(); // |\textcolor{pgreen}{$C_1$ $I_2$}|
+|\highlightBlue|doC(); // |\textcolor{pgreen}{$C_2$ $I_2$}|
+|\highlightBlue|doD(); // |\textcolor{pgreen}{$C_2$ $I_2$}|
+\end{javacode}}
+\end{parcolumns}
+\caption{Gapped clones.}
+\label{fig:3ropportunities}
+\end{figure}
+
+In the example of figure \ref{fig:3ropportunities} we see two clone classes, which are separated by a single node. Using equation \ref{eq:t3rgap} we can calculate the size of the gap as follows:
+
+\begin{equation}\label{eq:t3rexample}
+\text{gap}(C_1\text{ }I_1, C_2\text{ }I_1) = \frac{|\{n_4\}|}{|\{n_2, n_3\}| + |\{n_5, n_6\}|} * 100 = frac{1}{4} = 25\%
+\end{equation}
+
+The same calculation is conducted for the other clone instances:
+
+\begin{equation}\label{eq:t3rexample}
+\text{gap}(C_1\text{ }I_2, C_2\text{ }I_2) = \frac{|\emptyset|}{|\{n_2, n_3\}| + |\{n_4, n_5\}|} * 100 = frac{0}{4} = 0\%
+\end{equation}
+
+If all resulting percentages are under the threshold, this clone will be added to the collection of found clones and all of its subsets will be removed.
 

### 2019-07-29 sections/clonerefactor.tex
Fixed some issues with the formulas

@@
 \begin{equation}\label{eq:crtype3r}
-\forall (c_1 \in S) \exists (c_2 \in S) x \neq y \land isType3R(c_1, c_2)
+\forall (c_1 \in S) \text{ }\exists (c_2 \in S)\text{ }x \neq y \land isType3R(c_1, c_2)
 \end{equation}
@@
 Where \textit{S} is the set of all found clone classes.
-\textit{$\text{isType3R}(C_1, C_2)$} is a Boolean-valued function that denotes whether two clone classes are type 3R clones of each other.
+$\text{isType3R}(C_1, C_2)$ is a Boolean-valued function that returns whether two clone classes are type 3R clones of each other.
 Two clone classes are type 3R clones of each other if each of their instances are within a certain distance of each other:
@@
 \begin{equation}\label{eq:istype3r}
-\text{isType3R}(C_1, C_2) = \forall (i_1 \in C_1) \exists (i_2 \in C_2) Fi_1 = Fi_2 \land gap(i_1, i_2) < gap\_threshold
+\text{isType3R}(C_1, C_2) = \forall (i_1 \in C_1)\text{ } \exists (i_2 \in C_2)\text{ } Fi_1 = Fi_2 \land gap(i_1, i_2) < gap\_threshold
 \end{equation}
@@
 \textit{gap\_threshold} is the defined threshold percentage of the maximum gap size between two clone instances.
-\textit{$\text{gap}(I_1, I_2)$} is the function that calculates the gap between two clone instances.
+$\text{gap}(I_1, I_2)$ is the function that calculates the gap between two clone instances.
 This gap is calculated by dividing the amount of statements in the gap by the amount of statements that both clone instances span together:
@@
 \begin{equation}\label{eq:rangetotalorder}
-R_1 < R_2 \text{ iff } end_line(R_1) < begin_line(R_2) \lor (end_line(R_1) = begin_line(R_2) \land end_column(R_1) < begin_column(R_2))
+R_1 < R_2 \text{ iff } end\_line(R_1) < begin\_line(R_2) \lor (end\_line(R_1) = begin\_line(R_2) \land end\_column(R_1) < begin\_column(R_2))
 \end{equation}
 \begin{equation}\label{eq:rangetotalorder2}
-R_1 > R_2 \text{ iff } begin_line(R_1) > end_line(R_2) \lor (begin_line(R_1) = end_line(R_2) \land begin_column(R_1) > end_column(R_2))
+R_1 > R_2 \text{ iff } begin\_line(R_1) > end\_line(R_2) \lor (begin\_line(R_1) = end\_line(R_2) \land begin\_column(R_1) > end\_column(R_2))
 \end{equation}

### 2019-07-29 sections/clonerefactor.tex
Better total order formulas

@@
 \begin{equation}\label{eq:rangetotalorder}
-R_1 < R_2 \text{ iff } end\_line(R_1) < begin\_line(R_2) \lor (end\_line(R_1) = begin\_line(R_2) \land end\_column(R_1) < begin\_column(R_2))
+r_1 < r_2 \text{ iff } ELr_1 < BLr_2 \lor (ELr_1 = BLr_2) \land ECr_1 < BCr_2)
 \end{equation}
 \begin{equation}\label{eq:rangetotalorder2}
-R_1 > R_2 \text{ iff } begin\_line(R_1) > end\_line(R_2) \lor (begin\_line(R_1) = end\_line(R_2) \land begin\_column(R_1) > end\_column(R_2))
+r_1 > r_2 \text{ iff } BLr_1 > ELr_2 \lor (BLr_1 = ELr_2 \land BCr_1 > ECr_2)
 \end{equation}
+
+Where \textit{BL} is the begin line of a range, \textit{EL} is the end line of a range, \textit{BC} is the begin column of a range and \textit{EC} is the end column of a range.
 

### 2019-07-29 sections/clonerefactor.tex
Fixed some final formulas
Method level clones

@@
 \begin{equation}\label{eq:rangetotalorder}
-r_1 < r_2 \text{ iff } ELr_1 < BLr_2 \lor (ELr_1 = BLr_2) \land ECr_1 < BCr_2)
+r_1 < r_2 \text{ iff } ELr_1 < BLr_2 \lor (ELr_1 = BLr_2 \land ECr_1 < BCr_2)
 \end{equation}
@@
 \begin{equation}\label{eq:t3rexample}
-\text{gap}(C_1\text{ }I_1, C_2\text{ }I_1) = \frac{|\{n_4\}|}{|\{n_2, n_3\}| + |\{n_5, n_6\}|} * 100 = frac{1}{4} = 25\%
+\text{gap}(C_1\text{ }I_1, C_2\text{ }I_1) = \frac{|\{n_4\}|}{|\{n_2, n_3\}| + |\{n_5, n_6\}|} * 100 = \frac{1}{4} = 25\%
 \end{equation}
@@
 \begin{equation}\label{eq:t3rexample}
-\text{gap}(C_1\text{ }I_2, C_2\text{ }I_2) = \frac{|\emptyset|}{|\{n_2, n_3\}| + |\{n_4, n_5\}|} * 100 = frac{0}{4} = 0\%
+\text{gap}(C_1\text{ }I_2, C_2\text{ }I_2) = \frac{|\emptyset|}{|\{n_2, n_3\}| + |\{n_4, n_5\}|} * 100 = \frac{0}{4} = 0\%
 \end{equation}
@@
 
-\todo{Explain why these categories indicate and how they are related to refactoring}
+\subsubsection{Method/Constructor Level Clones}
+Method/Constructor Level clones denote clones that span are found in either a method or contructor.
+A constructor is a special method that is called when an object is instantiated.
+Current clone refactoring studies only focus on clones at method level \cite{choi2011extracting, yue2018automatic, kodhai2013method, arcelli2013software, lin2014clonepedia, mandal2014automatic, balazinska2000advanced, yongting2018detection, bouktif2006novel, fanqi2014using, devi2016study}.
+This is because most clones reside at those places \cite{lozano2007evaluating, fontana2015duplicated} and most of those clones can be refactored with a relatively simple set of refactoring techniques \cite{kodhai2013method, fontana2015duplicated}.
+
+To detect whether a given clone instance is at Method Level, we check for each node in the clone instance whether it has an ancestor node that is a method declaration:
+
+\begin{equation}\label{eq:sameclass}
+\text{a clone instance I is considered ``Method Level'' iff \forall (n \in I)\text{ } Tn = ``MethodDeclaration'' \lor \exists (p \in ancestors(n)) \text{ } Tp = ``MethodDeclaration'' }
+\end{equation}
+
+Where \textit{T} is the type of a node.
+\textit{ancestors(n)} denotes all of ancestor nodes of a node.
+The ancestor nodes are recursively all the parents of a given node in the AST.
+Figure \ref{fig:methodlevelclone} shows an example of a method level clone and its recursive parents.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+public class Class1 { // |\textcolor{pgreen}{$p_3$}|
+  public void doA() { // |\textcolor{pgreen}{$p_2$}|
+    if(isA()) // |\textcolor{pgreen}{$p_1$}|
+|\highlightYellow|      doB(); // |\textcolor{pgreen}{$n_1$}|
+  }
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+\begin{javacode}
+public class Class2 { // |\textcolor{pgreen}{$p_3$}|
+  public void doB() { // |\textcolor{pgreen}{$p_2$}|
+    if(isB()) // |\textcolor{pgreen}{$p_1$}|
+|\highlightYellow|      doB(); // |\textcolor{pgreen}{$n_2$}|
+  }
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Example of a method level clone and its parents.}
+\label{fig:methodlevelclone}
+\end{figure}
 

### 2019-07-29 sections/clonerefactor.tex
Fixes

@@
 
-To detect whether a given clone instance is at Method Level, we check for each node in the clone instance whether it has an ancestor node that is a method declaration:
+To detect whether a given clone instance is at Method Level, we check for each node in the clone instance whether it has an ancestor node that is a method declaration.
+A clone instance is considered ``Method Level'' if:
 
 \begin{equation}\label{eq:sameclass}
-\text{a clone instance I is considered ``Method Level'' iff \forall (n \in I)\text{ } Tn = ``MethodDeclaration'' \lor \exists (p \in ancestors(n)) \text{ } Tp = ``MethodDeclaration'' }
+\forall (n \in I)\text{ } Tn = \text{ MethodDeclaration } \lor \exists (p \in ancestors(n)) \text{ } Tp = \text{ MethodDeclaration }
 \end{equation}
@@
 
+\subsubsection{Class Level Clones}
+
 \subsection{Contents}\label{sec:setupcontents}

### 2019-07-29 sections/clonerefactor.tex
Class level clones

@@
 \begin{equation}\label{eq:sameclass}
-\forall (n \in I)\text{ } Tn = \text{ MethodDeclaration } \lor \exists (p \in ancestors(n)) \text{ } Tp = \text{ MethodDeclaration }
+\forall (n \in I)\text{ } Tn = \text{MethodDeclaration} \lor \exists (p \in ancestors(n)) \text{ } Tp = \text{MethodDeclaration}
 \end{equation}
@@
 
-\subsubsection{Class Level Clones}
+\subsubsection{Class/Interface/Enumeration Level Clones}
+Class/Interface/Enumeration Level clone instances are found inside the body of one of these declarations and optionally include the declaration itself.
+It can also be a clone instance that exceeds the boundaries of a single method.
+These clone instances can contain a fields, (abstract) methods, inner classes, enumeration fields, etc.
+These types of clones require various refactoring techniques to refactor.
+For instance, we might have to move fields in a inheritance hierarchy.
+Or, we might have to perform a refactoring on more of an architectural level, if a large set of methods is cloned.
+
+We detect these clones in the same way we detect method level clones: we walk up the AST until we find the first node that indicates one of these categories.
 
@@
   \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
-  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially, optionally including its declaration.
+  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method. The declaration itself is not included.
   \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
@@
 \end{enumerate}
-
-\todo{Explain each category in more detail}
 

### 2019-07-29 sections/clonerefactor.tex
Full Method/Class/Interface/Enumeration

@@
 
+\subsubsection{Full Method/Class/Interface/Enumeration}
+These catagories denote that a full declaration, including its body, is cloned with another declaration.
+These categories often denote redundancy and are often easy to solve: one of both declarations is redundant and should be removed.
+All usages of the removed declaration should be redirected to the clone instance that was not removed.
+We check for clones in this category by checking that the first node in a clone instance is a declaration and the last node in the clone instance is the last node in the body of that declaration.
+
+\subsubsection{Partial Method/Constructor}
+
 \section{Method extraction opportunities}\label{sec:refactorabilitysetup}
@@
 \begin{itemize}
-    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a method.
+    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a new method.
 Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).

### 2019-07-29 sections/clonerefactor.tex
Partial method or constructor

@@
 
-\subsubsection{Method/Constructor Level Clones}
+\subsubsection{Method/Constructor Level Clones} \label{sec:methodlevelcr}
 Method/Constructor Level clones denote clones that span are found in either a method or contructor.
@@
 \subsubsection{Full Method/Class/Interface/Enumeration}
-These catagories denote that a full declaration, including its body, is cloned with another declaration.
+These categories denote that a full declaration, including its body, is cloned with another declaration.
 These categories often denote redundancy and are often easy to solve: one of both declarations is redundant and should be removed.
@@
 \subsubsection{Partial Method/Constructor}
+These categories describe clone instances which are found in the body of a method or constructor.
+These clones can often be refactored by extracting a new method out of the cloned code.
+We detect such clones by checking that each node in the clone instance has a parent node that is a methoddeclaration, but none of the nodes is a method declaration.
+We describe the procedure by with we recursively seek the parent nodes of a node in section \ref{sec:methodlevelcr}.
 

### 2019-07-30 sections/background.tex
An example
Class level clones
OOP + AST

@@
 
-In this study, we use the symbols given in this table in our formulas.
+A \textbf{range} denotes the line and column at which a code fragment starts and ends. In this study, we use the symbols given in this table in our formulas.
 
@@
 Maven can also be used to run tests for the systems and to package the project as an executable file.
+
+\section{(Object-Oriented) Programming Languages}
+In this section we describe the relevant parts of the programming languages we research and experiment on.
+
+\subsection{AST}
+An Abstract Syntax Tree (AST) is a tree consisting of an hierarchical representation of the source code of a program.
+Detecting code clones on the AST of a program allows for a deeper understanding of the concepts that are being analyzed.
+Having an AST, we know how concepts in the code are related.
+This helps to determine in what classes and methods cloned code is found.
+
+Having access to a programs' AST also helps in the process of refactoring. Moving AST nodes rather than textual modifications reduces error margins because the tree structure stays intact.

### 2019-07-30 sections/background.tex
Inheritance

@@
 Having access to a programs' AST also helps in the process of refactoring. Moving AST nodes rather than textual modifications reduces error margins because the tree structure stays intact.
+
+\subsection{Inheritance}
+Object-Oriented programming languages use inheritance to model real-world relations between data concepts.
+Inheritance allows an object to inherit all functionality from another object.
+For instance, a ``Car'' object would inherit functionality and data from generalized concepts, such as ``Vehicle''.
+Using inheritance it is possible to reduce duplication, as multiple objects can inherit common functionality.
+
+When looking at the inheritance structure of a program, we can get a deeper understanding of a programs' architecture.
+The use of inheritance to group common functionality and data is called ``Abstraction''.
+Duplication in source code can be a result of an inadequate use of abstraction.
+Because of that, refactoring code clones might require to create such abstractions of common functionality.
+
+\subsection{Code Quality}
+
+\subsubsection{Code Smells}
+
+\subsubsection{Design Patterns}
+
+\subsubsection{Code Quality Metrics}
+
+\subsection{Java}
+\todo{Describe the relevant parts of the Java ecosystem: interfaces, enumerations, annotations, etc.}
+
+\subsubsection{Visibility}

### 2019-07-30 sections/background.tex
Code quality

@@
 \subsection{Code Quality}
+Different programming languages have different ways to measure code quality.
+For object-oriented programming languages this largely comes in the form of code smells (patterns that should be avoided) and design patterns (patterns which may improve code design and comprehensibility when used correctly).
 
 \subsubsection{Code Smells}
+Code smells are patterns in code that should be avoided, because they have a negative effect on system design.
+Duplicate code is, among many others, one example of a code smell.
+Having many code smells present in source code can significantly increase maintainence costs of the source code or even render a software system unmaintainable.
+This increases technical debt: a debt present in the system the will have to be repaid at a later point of time.
+Such technical debt often comes at the expense of developing new features, fixing bugs and other aspects surrounding a programs functional behaviour.
 
 \subsubsection{Design Patterns}
+Most code smells have design patterns that can be used to mitigate the smell.
+For instance, duplicate code can be mitigated by using appropriate abstractions or refactoring duplicate code to a common place.
+Design patterns differ from refactoring methods in the sense that they are more about an architectural pattern rather than a certain kind of code modification.
 

### 2019-07-30 sections/background.tex
Maintainability metrics

@@
 
-\subsubsection{Code Quality Metrics}
+\subsubsection{Maintainability Metrics}
+Maintainability metrics are features of source code by which an indication of the maintainability of the source code can be measured.
+Heitlager at al.
+\cite{heitlager2007practical} propose a maintainability model that catagorize the results of metrics into different ``score'' catagories.
+For instance, with duplication, if 0-3\% of the project is duplicated, the project will get the highest score on a scale of 1 to 5 (only integers, no floating point numbers).
+Such a maintainability model is intuitive for measuring the quality of a software system, especially large software systems with a lot of source code to base the metrics on.
+However, this maintainability model \cite{heitlager2007practical} lacks in measuring fine-grained changes: most small changes will not fall into a different category.
+Because of that, this model is less suitable for measuring the impact of single refactorings.
 

### 2019-07-30 sections/background.tex
Java

@@
 Heitlager at al.
-\cite{heitlager2007practical} propose a maintainability model that catagorize the results of metrics into different ``score'' catagories.
+\cite{heitlager2007practical} propose a maintainability model that categorize the results of metrics into different ``score'' categories.
 For instance, with duplication, if 0-3\% of the project is duplicated, the project will get the highest score on a scale of 1 to 5 (only integers, no floating point numbers).
@@
 \subsection{Java}
-\todo{Describe the relevant parts of the Java ecosystem: interfaces, enumerations, annotations, etc.}
+We run all our experiments on projects written in Java.
+Because of that, we get some information that is specific to Java systems.
+Additionally, we perform automated refactorings on Java systems, which requires the use of Java language concepts.
+These are explained in this section.
+Many of these concepts also exist in other programming languages, but often not in all.
+
+\subsubsection{Interfaces}
+Java uses the concept of interfaces to loosely couple a specification and its implementation.
+Interfaces are specifications about what a (group of) objects do.
+Often, methods don't need an entire object, but just use a few properties of it.
+Because of that, Java recommends to program to an interface rather than an implementation.
+This means that we should use abstractions of expected functionality rather than complete implementations of functionality.
+This can make switching implementations at a later point in time easier.
+
+Often, duplication is the result of an inappropriate use of abstractions.
+Two methods might describe operations on types following the same contract, but because of a lack of abstraction the programmer may choose to clone such methods.
+This will result in duplicated methods with minor modifications to match a different implementation.
+Such duplicates can be mitigated by using proper abstractions, of which one option is to program methods against interfaces (contracts of expected functionality) rather than their full implementations.
+
+\subsubsection{Packages}
+Packages (sometimes called ``modules'' in other programming languages) are hierarchical groupings of related concepts.
+For instance, all UI logic in an application might go into the ``ui'' package.
+The ``ui'' package can have a subpackage named ``keyhandling'' for all keyhandling operations.
+These packages contain package-level declarations, like classes and interfaces.
+Names of class-level declarations must be unique within the package.
+However, duplicate declaration names may exists in subpackages and parent packages.
+
+In Java, all declarations used from outside the package a declaration is in, must be \textit{imported}.
+Importing a declaration from outside the current package goes by the fully qualified identifier (FQI) of the declaration.
+The FQI of a declaration gives an unique identifier for a symbol in a codebase.
+For instance, if our ``keyhandling'' package would contain a ``KeyHandler'' class, its fully qualified identifier would be ``ui.keyhandling.KeyHandler''.
 
 \subsubsection{Visibility}
+In Java, we can protect declarations from being used in scopes in which they are supposed to be used.
+If a method should only be used within the class itself, we can give it a ``private'' visibility.
+If a method is to be used by its children in its inheritance hierarchy, we can set its visibility to ``protected''.
+If a method is supposed to be part of the public contract of an object, we can set it to ``public'' visibility.
+Alternatively, there is ``package'' visibility, for declarations that should only be referenced within the same package.
+This allows control over what parts of an application should be able to access what declarations.

### 2019-07-30 sections/clonerefactor.tex
Categories

@@
 \end{enumerate}
-We define categories for each of these aspects and enable CloneRefactor to determine the catagories of clones.
+We define categories for each of these aspects and enable CloneRefactor to determine the categories of clones.
 
@@
 The \textit{Same method} and \textit{Same class} relations share a common refactoring opportunity.
-Clones of both these catagories, when extracted to a new method, can be placed in the same class.
+Clones of both these categories, when extracted to a new method, can be placed in the same class.
 Both of these relations are most favorable for refactoring, as they require a minimal design tradeoff.
@@
 These clones are least favorable when looking at refactoring, because their refactoring will almost always have a major impact on system design.
-We formulated four catagories of unrelated clones to look into their refactoring opportunities.
+We formulated four categories of unrelated clones to look into their refactoring opportunities.
 

### 2019-07-30 sections/results.tex
Categories

@@
 \todo{update these results}
-In section \ref{sec:refactorabilitysetup} we define catagories regarding the extent to which clones can be refactored through method extraction.
+In section \ref{sec:refactorabilitysetup} we define categories regarding the extent to which clones can be refactored through method extraction.
 Our results are displayed in Table \ref{table:refactorability}.

### 2019-07-30 sections/clonerefactor.tex
Several methods

@@
 
-\begin{equation}\label{eq:sameclass}
+\begin{equation}\label{eq:samemethod}
 \forall (n \in I)\text{ } Tn = \text{MethodDeclaration} \lor \exists (p \in ancestors(n)) \text{ } Tp = \text{MethodDeclaration}
@@
 The ancestor nodes are recursively all the parents of a given node in the AST.
+Apart from this, we check that the MethodDeclaration ancestor of each clone instance is the same, to be sure the clone only spans a \textit{single} method.
 Figure \ref{fig:methodlevelclone} shows an example of a method level clone and its recursive parents.
@@
 
+\subsubsection{Several Methods}
+Several methods cloned in a single class is a strong indication of implicit dependencies between two classes.
+This increases the chance that these classes are missing some form of abstraction, or their abstraction is used inadequately.
+We detect such clones by checking that each cloned node has a parent node that is a MethodDeclaration.
+This is the same process as described in equation \ref{eq:samemethod}.
+Additionally, we check that the MethodDeclaration ancestor of the first node in the clone instance differs from the last, to be sure that the clone instance spans over at least two methods.
+
 \section{Method extraction opportunities}\label{sec:refactorabilitysetup}

### 2019-07-30 sections/clonerefactor.tex
Only Fields

@@
 
+\subsubsection{Only Fields}
+This category denotes that the clone spans over only global variables, fields that are declared outside of a method.
+This is to indicate data redundancy: pieces of data have an implicit dependency.
+In such cases, these fields may have to be encapsulated in a new object.
+Or, the fields should be somewhere in the inheritance structure where all objects containing the clone can access them.
+We check for this category by validating that all nodes in the clone instance are a VariableDeclarator.
+Because VariableDeclarators in methods would already fall into the ``Partial Method'' category, this includes only globally defined fields.
+
 \section{Method extraction opportunities}\label{sec:refactorabilitysetup}

### 2019-07-30 sections/clonerefactor.tex
Including constructor in full categories

@@
 \subsection{Contents}\label{sec:setupcontents}
-Finally, we looked at what nodes individual clone instances span. We selected the following categories to be relevant for refactoring:
+Finally, we looked at what nodes individual clone instances span.
+We selected a set of catagories on basis of empirical evaluation of a set of clones in our dataset.
+We selected the following categories to be relevant for refactoring:
 \begin{enumerate}
-  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
+  \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
   \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method. The declaration itself is not included.
@@
 
-\subsubsection{Full Method/Class/Interface/Enumeration}
+\subsubsection{Full Method/Constructor/Class/Interface/Enumeration}
 These categories denote that a full declaration, including its body, is cloned with another declaration.

### 2019-07-30 sections/clonerefactor.tex
Removed these categories that I don't quite like
Other

@@
   \item \textbf{Only Fields:} A clone that spans only global variables.
-  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields and other things, like methods.
-  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
   \item \textbf{Other:} Anything that does not match with above-stated categories.
@@
 These clones can often be refactored by extracting a new method out of the cloned code.
-We detect such clones by checking that each node in the clone instance has a parent node that is a methoddeclaration, but none of the nodes is a method declaration.
+We detect such clones by checking that each node in the clone instance has a ancestor node that is a MethodDeclaration, but none of the nodes is a method declaration.
 We describe the procedure by with we recursively seek the parent nodes of a node in section \ref{sec:methodlevelcr}.
@@
 
+\subsubsection{Other}
+The ``Other'' category denotes all configurations of clone contents that do not fall into above categories.
+Often, these are combinations of above states concepts.
+For instance, a combination of constructors and methods is clones, or a combination of fields and methods.
+Such clones indicate, like the ``Several Methods'', the requirement of performing a more architectural-level refactoring.
+These are often more complicated, especially when aiming to automate this process.
+
 \section{Method extraction opportunities}\label{sec:refactorabilitysetup}

### 2019-07-30 sections/clonerefactor.tex
Refactorability

@@
 \section{Method extraction opportunities}\label{sec:refactorabilitysetup}
-The most used technique to refactor clones is method extraction (creating a new method on basis of the contents of clones).
+The most used technique to refactor clones is ``Extract Method'' (creating a new method on basis of the contents of clones).
 However, method extraction cannot be applied in all cases.
-In these instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.
+In some instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.
 
-We measured the number of clones that can be refactored through method extraction (without additional transformations being required). We defined the following categories:
+Because of this, we defined a set of categories of things that can obstruct a refactoring opportunity using the ``Extract Method'' technique. We defined the following categories:
 \begin{itemize}
@@
     \item \textbf{Spans part of a block:} This clone spans a part of a statement.
-    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table~\ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
+    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of the previous section, the ``extract method'' refactoring technique cannot be applied.
 \end{itemize}
 
+Clones that are not in the ``Can be extracted'' are not per definition not refactorable using method extraction.
+However, they may require additional transformations, other refactoring techniques, etc.
+We further explain opportunities to refactor such clones outside the ``Can be extracted'' category in section \ref{sec:discussrefactorability}.
+
 \todo{Explain each category in more detail}

### 2019-07-30 sections/clonerefactor.tex
Automated Refactoring

@@
 
-\section{Method extraction opportunities}\label{sec:refactorabilitysetup}
+\section{Automated Refactoring}
+After clone detection and context analysis, CloneRefactor applies refactorings to a subset of the identified clones.
+This section describes what clone classes are included in the refactoring and the refactoring methods CloneRefactor supports.
+
+\subsection{Method extraction opportunities}\label{sec:refactorabilitysetup}
 The most used technique to refactor clones is ``Extract Method'' (creating a new method on basis of the contents of clones).
@@
 In some instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.
+CloneRefactor maps to what extend this refactoring method can be used to refactor the found clones automatically.
 
@@
 \begin{itemize}
-    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a new method.
+    \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method.
 Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
-    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
-    \item \textbf{Spans part of a block:} This clone spans a part of a statement.
-    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of the previous section, the ``extract method'' refactoring technique cannot be applied.
+    \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
+    \item \textbf{Spans Part Of A Block}: This clone spans a part of a statement.
+    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of the previous section, the ``extract method'' refactoring technique cannot be applied.
+    \item \textbf{Top-level Node Is Not A Statement}: The topmost node of a clone instance is not a statement.
+    \item \textbf{Overlaps}: There is overlap within the clone class.
 \end{itemize}
 
-Clones that are not in the ``Can be extracted'' are not per definition not refactorable using method extraction.
+This does not mean that clones outside the ``Can be extracted'' category cannot be refactored using method extraction.
 However, they may require additional transformations, other refactoring techniques, etc.
+Because of that, we took those categories out of the scope for our automated refactoring efforts.
 We further explain opportunities to refactor such clones outside the ``Can be extracted'' category in section \ref{sec:discussrefactorability}.
 
+\subsection{}
+
 \todo{Explain each category in more detail}

### 2019-07-30 sections/discussion.tex
Categories
Automated Refactoring

@@
 \section{Clone Context Analysis}
-In section \ref{chap:contextsetup} we introduced the catagories we defined for mapping the context of clones. In this section, we discuss this together with the related experiments.
+In section \ref{chap:contextsetup} we introduced the categories we defined for mapping the context of clones. In this section, we discuss this together with the related experiments.
 
-\subsection{Refactorability}
+\subsection{Refactorability} \label{sec:discussrefactorability}
 In section \ref{sec:refactorability} we introduced to what extent clones can be refactored through method extraction.

### 2019-07-30 sections/research.tex
Refactor literal variability

@@
 \begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/type2literal}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+public void printNice(String s){
+	System.out.println("===");
+	System.out.println(s);
+	System.out.println("===");
+}
+
+public void printNice2(String s){
+	System.out.println("---");
+	System.out.println(s);
+	System.out.println("---");
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+public void printNice(String s){
+	printNice(s, "===");
+}
+
+public void printNice2(String s){
+	printNice(s, "---");
+}
+
+public void printNice(String s, String decoration){
+	System.out.println(decoration);
+	System.out.println(s);
+	System.out.println(decoration);
+}
+\end{javacode}}
+\end{parcolumns}
 \caption{Literal variability refactored.}

### 2019-07-30 sections/research.tex
More minimal example
Minimal example for method variability refactoring

--- 2019-07-25 sections/research.tex
@@
 \begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/type2literal}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+void doABC(){
+	doA();
+	doB("abc");
+	doC();
+}
+
+void doDEF(){
+  doA();
+  doB("def");
+  doC();
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+void doABC(){
+	printNice("abc");
+}
+
+void doDEF(){
+	printNice(s, "def");
+}
+
+void doThis(String letters){
+  doA();
+  doB(letters);
+  doC();
+}
+\end{javacode}}
+\end{parcolumns}
 \caption{Literal variability refactored.}
@@
 \begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/type2method}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+void doABC(){
+	doA();
+	doB();
+	doC();
+}
+
+void doADC(){
+  doA();
+  doD();
+  doC();
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+void doABC(){
+	printNice(this::doB);
+}
+
+void doDEF(){
+	printNice(this::doD);
+}
+
+void doThis(Runnable r){
+  doA();
+  r.run();
+  doC();
+}
+\end{javacode}}
+\end{parcolumns}
 \caption{Method variability refactored.}

### 2019-07-30 sections/research.tex
Fixed the examples
Better (minimal) T3R example

@@
 void doABC(){
-	printNice("abc");
+	doThis("abc");
 }
@@
 void doDEF(){
-	printNice(s, "def");
+	doThis(s, "def");
 }
@@
 void doABC(){
-	printNice(this::doB);
+	doThis(this::doB);
 }
 
-void doDEF(){
-	printNice(this::doD);
+void doADC(){
+	doThis(this::doD);
 }
@@
 \begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/type3_3}
-  \caption{Added statement between cloned methods.}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+void doCwithA(){
+	int a = getA();
+	doC(a);
+}
+
+void multiplyA(){
+  int a = getA();
+  a *= 5;
+  doC(a);
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+void doCwithA(){
+	modifyA(false);
+}
+
+void multiplyA(){
+	modifyA(true);
+}
+
+void modifyA(boolean multiply){
+  int a = getA();
+  if(multiply) a *= 5;
+  doC(a);
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Added statement between cloned fragments refactored.}
 \label{fig:type3}
@@
 This statement is found in between cloned lines.
-We have named this difference between the two clones, in this examples containing a single statement, the \textit{gap}.
-This gap has a threshold for type 3R, which is calculated by the following formula:
+There is a \textit{gap} of non-cloned lines in between two clone classes.
+For type 3R, the size of this gap is bounded by a threshold.
+It is calculated by the following formula:
 

### 2019-07-30 sections/research.tex
Gap requirements

@@
 There is a \textit{gap} of non-cloned lines in between two clone classes.
-For type 3R, the size of this gap is bounded by a threshold.
-It is calculated by the following formula:
+The following rules apply to this gap:
 
+\begin{itemize}
+  \item \textbf{The difference in statements must bridge a gap between two clones that were valid by the original thresholds}.
+This entails that, different from type 3 clones, the difference in statements cannot be at the beginning or the end of a cloned block.
+It is rather somewhere within, as it must bridge two existent clones.
+  \item \textbf{The size of the gap between two clones is limited by a threshold.} This threshold is calculated by taking the percentage of the number of statements in the gap over the number of statements that both clones that are being bridged span.
+  \item \textbf{The gap may not span a partial block.} To make sure that the T3R clone can be refactored, we do not allow the gap to span a part of a block, for instance, the declaration and a part of the body of a for-loop.
+The reason for this is that it is not possible to wrap a partially spanned block in a single conditional statement.
+We could, however, use multiple conditional blocks (one for each block spanned), but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for T3R clones.
+\end{itemize}
+
+\subsubsection{Gap Threshold}
 \begin{equation}\label{eq:type3r}

### 2019-07-30 main.tex
Fixed stuff
Introduction
Research questions
We have a new title yay
More colors
Removed experimental setup and merged it with clonerefactor
Xander

@@
 }
+
+\definecolor{lightyellow}{HTML}{fffdcc}
+\definecolor{doublelightyellow}{HTML}{fffa9c}
+\definecolor{lightgreen}{HTML}{dcffd4}
+\definecolor{lightblue}{HTML}{e0ffff}
+\definecolor{lightred}{HTML}{ffe0e0}
+\definecolor{lightpink}{HTML}{ffe0ff}
+\definecolor{lightorange}{HTML}{ffede0}
+\definecolor{lightpurple}{HTML}{f0e0ff}
+\newcommand{\highlightYellow}{\makebox[0pt][l]{\color{lightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightGreen}{\makebox[0pt][l]{\color{lightgreen}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightBlue}{\makebox[0pt][l]{\color{lightblue}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightRed}{\makebox[0pt][l]{\color{lightred}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightPink}{\makebox[0pt][l]{\color{lightpink}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightOrange}{\makebox[0pt][l]{\color{lightorange}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightPurple}{\makebox[0pt][l]{\color{lightpurple}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightDarkyellow}{\makebox[0pt][l]{\color{doublelightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
 
@@
 	\begin{center}
-		{\Huge\bfseries Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages \par}
+		{\Huge\bfseries Towards Automatic Improvement of Software Maintainability through Automated Refactoring of Code Clones \par}
 		% Earlier versions:
-		% Assessing Test Suite Effectiveness Using Static Analysis
-		% Predicting Test Suite Effectiveness Using Static Analysis
-		% Predicting Test Suite Effectiveness Using Static Source Code Analysis
-		% Assessing Test Suite Effectiveness Using Static Analysis
-		% Predicting test suite effectiveness using static analysis
+		% Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages
 		\vspace{44pt}
@@
 		\textbf{Research supervisor:} Dr. Ana Oprescu, \email{ana.oprescu@uva.nl} \\
-		\textbf{Host/Daily supervisor:} Xander Schrijen, \email{x.schrijen@sig.eu}\\
+		\textbf{Host/Daily supervisor:} Xander Schrijen Msc., \email{x.schrijen@sig.eu}\\
 		\textbf{Host organisation/Research group:} Software Improvement Group (SIG), \url{http://sig.eu/}
@@
 \input{sections/background}
-\input{sections/related_work}
 \input{sections/research}
@@
 \input{sections/discussion}
+\input{sections/related_work}
 \input{sections/conclusion}

### 2019-07-30 sections/clonerefactor.tex
Xander

@@
 Figure \ref{fig:clonerefactorprocess} shows the overall process used by CloneRefactor.
-First, we detect clones on basis of a Java codebase, given a Java project from disk and a configuration.
+First, we detect clones on the basis of a Java codebase, given a Java project from disk and a configuration.
 The clone detection process is further explained in section \ref{sec:clonedetection}.
 After all clones are found, CloneRefactor maps the context of the clones.
-On basis of this context, CloneRefactor applies transformations to the source code for clones for which we have configured a refactoring.
+On the basis of this context, CloneRefactor applies transformations to the source code for clones for which we have configured a refactoring.
 
@@
 This has a big impact on performance efficiency.
+This is visible in our results, as displayed in section \ref{sec:clonetypeexperiments}.
 
@@
 To detect clones, CloneRefactor parses the AST aqcuired from JavaParser to an unweighted graph structure.
-On basis of this graph structure, clones are detection.
+On the basis of this graph structure, clones are detection.
 Dependent on the type of clones being detected, transformations may be applied.
-The way in which CloneRefactor was designed does not allow for several clone types to be detected simultaneously, in accordance with our clone type philosophy as described in chapter \ref{sec:unifying}.
+The way in which CloneRefactor was designed does not allow for several clone types to be detected simultaneously.
 
@@
 Each AST is then converted to a directed graph that maps relations between statements, further explained in section \ref{sec:clonegraph}.
-On basis of this graph, we detect clone classes and verify them using three thresholds (in order of importance):
+On the basis of this graph, we detect clone classes and verify them using three thresholds (in order of importance):
 \begin{itemize}
@@
 However, declarations and statements may themselves have child declarations and statements.
-To avoid redundant duplication checks, we exclude child declarations and statements from each node.
+To avoid redundant duplication checks, we exclude the body of each node.
 Look at figure \ref{fig:clonegraph} for an example of how source code maps to AST nodes.
@@
 
-Using the example shown in figure \ref{fig:clonegraph} and \ref{fig:clonegraph2} we can explain how we detect clones on basis of this graph.
+Using the example shown in figure \ref{fig:clonegraph} and \ref{fig:clonegraph2} we can explain how we detect clones on the basis of this graph.
 Suppose we are finding clones for two files and the final node of the second file is a variable declarator.
@@
 
+\todo{Explain the complexity of the algorithm: O(n)?}
+
 \subsubsection{Removing redundant clone classes}\label{sec:conceptualremovingredundant}
-The clone detection method used by CloneRefactor can, for various reasons,%Should I list these? Listing them could be a section on its own, as I'd have to show examples to make it concrete.
-result in redundant clone classes.
+The clone detection method used by CloneRefactor can, for various reasons, result in redundant clone classes.
 After the insertion of each newly detected clone, we check whether it is redundant and/or any of the existent clones has become redundant by adding this clone.
@@
 If the newly added clone is a subset of an existing clone, we do not add it to the set of clone classes. This way we avoid redundant clone classes being detected by CloneRefactor.
+\todo{Think about an example}
 
 \subsection{Validating the type 2R variability threshold}
-In the definition of type 2R clones (see section \ref{sec:type2r}) we described how type 2R clones work on basis of a variability threshold.
+In the definition of type 2R clones (see section \ref{sec:type2r}) we described how type 2R clones work on the basis of a variability threshold.
 This threshold is checked by CloneRefactor to assess the validity of found clone classes.
-Implementing such a threshold involves some important design decisions and has a lot of underwater complexity.
-In this section we explain how CloneRefactor detects type 2R clones on basis of this variability threshold.
+Implementing such a threshold involves some important design decisions and has a lot of complexity.
+In this section we explain how CloneRefactor detects type 2R clones on the basis of this variability threshold.
 This process is done as a postprocessing step after clone detection.
@@
 
+\todo{This is not correct set theory. Sets have duplicates and have an order.}
 \begin{equation}\label{eq:variabilityclonerefactor}
@@
 
-So for the example given in figure \ref{fig:equalityarrays} we have a variability of 75r \%.
+\todo{Usage of the word adheres is questionable here...}
+So for the example given in figure \ref{fig:equalityarrays} we have a variability of 75\%.
 In CloneRefactor, the maximum variability percentage is a threshold that is entered in a configuration file.
@@
 \subsubsection{Convert Equality Array to Graph}
-After the global threshold check has failed, we build a clone graph on basis of the equality arrays.
+After the global threshold check has failed, we build a clone graph on the basis of the equality arrays.
 The process used for building this graph is the same as the process described in \ref{sec:buildingclonegraph}.
@@
 \subsubsection{Detect Clones on Graph}
-Similar to the clone detection process, we detect clones on basis of the graph described in the previous section.
+Similar to the clone detection process, we detect clones on the basis of the graph described in the previous section.
 The only difference is that, in this step, we do not remove clones that do not meet the thresholds (as explained in section \ref{sec:clonerefactorthresholds}).
@@
 In this example, we have 2 clone classes.
-In the ``Try To Expand'' step, we will check whether we can create a clone class with larger clone instances on basis of the clones found in the previous step.
+In the ``Try To Expand'' step, we will check whether we can create a clone class with larger clone instances on the basis of the clones found in the previous step.
 We start with the largest clone class, measured in clone volume.
@@
 Finally, we looked at what nodes individual clone instances span.
-We selected a set of catagories on basis of empirical evaluation of a set of clones in our dataset.
+We selected a set of catagories on the basis of empirical evaluation of a set of clones in our dataset.
 We selected the following categories to be relevant for refactoring:
@@
 \subsection{Method extraction opportunities}\label{sec:refactorabilitysetup}
-The most used technique to refactor clones is ``Extract Method'' (creating a new method on basis of the contents of clones).
+The most used technique to refactor clones is ``Extract Method'' (creating a new method on the basis of the contents of clones).
 However, method extraction cannot be applied in all cases.
@@
 
-\subsection{}
+\subsubsection{Can Be Extracted}
 

### 2019-07-30 sections/conclusion.tex
Xander

@@
 \chapter{Conclusion}
+\todo{Rewrite}
 \label{ch:conclusion}
@@
 \section{Threats to validity}\label{chap:threatstovalidity}
+\todo{Rewrite}
 We noticed that, when doing measurements on a corpus of this size, the thresholds that we use for the clone detection have a big impact on the results.
@@
 However, by using these, we definitely miss some harmful clones.
+\todo{Possible stuff: future work might be a threat to validity}
+\todo{Implementation specific for CloneRefactor: limited validation}
 
@@
 \cite{allamanis2015suggesting} proposes a machine learning model that can suggest accurate method and class names.
-This study shows promising results towards generating method and class names on basis of their body and context.
+This study shows promising results towards generating method and class names on the basis of their body and context.
 However, the source code of this study in not available, making it harder to apply their findings to generate class and method names for any software project.

### 2019-07-30 sections/introduction.tex
Xander

@@
 As a result, we expect to formulate clone type definitions that can be refactored.
-On basis of this results we can perform analyses on the context of clones by these definitions.
+On the basis of this results we can perform analyses on the context of clones by these definitions.
 The context of a clone (location, relation between clones, etc.) has a big impact on how a clone should be refactored.
@@
 We expect this research question to result in a priorization of refactoring opportunities: \textit{with what refactoring method can what percentage of clones be refactored?} As a result of these first two research questions we expect to have clone type definitions that can be refactored together with a prioritization of the refactoring methods that can be used.
-On basis of this we expect to be able to build a script that can automatically refactor the highest prioritized clones.
+On the basis of this we expect to be able to build a script that can automatically refactor the highest prioritized clones.
 With this script, we expect to be able to answer our final research question:

### 2019-07-30 sections/research.tex
Xander

@@
 Detection of clones by this definition can be hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed.
-Because of this, most clone detection implementations of type 3 clones work on basis of a similarity threshold~\cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
+Because of this, most clone detection implementations of type 3 clones work on the basis of a similarity threshold~\cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
 This similarity threshold has been implemented in different ways: textual similarity (for instance using Levenshtein distance)~\cite{lavoie2011automated}, token-level similarity~\cite{sajnani2016sourcerercc} or statement-level similarity~\cite{kamalpriya2017enhancing}.
@@
 The referenced types/variables/methods might even not be part of the project, but rather of an external library or the standard libraries of the programming language.
-All these factors need to be considered for the referenced entity to be found, on basis of which a fully qualified identifier can be created.
+All these factors need to be considered for the referenced entity to be found, on the basis of which a fully qualified identifier can be created.
 

### 2019-07-30 sections/research.tex
T3r

@@
 \begin{itemize}
-  \item \textbf{The difference in statements must bridge a gap between two clones that were valid by the original thresholds}.
+  \item \textbf{The difference in statements must bridge a gap between two valid clones}.
 This entails that, different from type 3 clones, the difference in statements cannot be at the beginning or the end of a cloned block.
@@
 \subsubsection{Gap Threshold}
+For type 3R, the size of the gap between two clones is bounded by a threshold. This threshold is calculated by the following formula:
+
 \begin{equation}\label{eq:type3r}
@@
 
-When applying this formula with the example given in figure \ref{fig:gappedclones}, we get a gap size of 25\%:
+In this formula, the ``Number of nodes in gap'' concerns the amount of non-cloned nodes that are in between both clone instances.
+The ``Number of nodes in clones'' is the amount of nodes that are in the clone instances surrounding the gap:
 
 \begin{equation}\label{eq:type3r}
-\text{T3R Gap Size}=\frac{\text{|\{doC()\}|}}{\text{|\{doA(), doB(), doD(), doE()\}|}}*100 = \frac{\text{1}}{\text{4}}*100 = 25\%
+\text{Number of nodes in clones}=|I_{before}| + |I_{after}|.
 \end{equation}
+
+As an example, consider the code fragment in figure \ref{fig:gappedclones}.
 

### 2019-07-30 sections/research.tex
Partial block example

@@
 \begin{figure}[H]
-  \centering
-  \includegraphics[width=0.6\columnwidth]{img/type3invalid}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+|\highlightYellow|int a = getA(); // |\textcolor{pgreen}{$N_{1-1}$}|
+|\highlightYellow|while(a<1000) {
+|\highlightYellow|  a *= 5; // |\textcolor{pgreen}{$N_{2-2}$}|
+}
+|\highlightBlue|doC(a); // |\textcolor{pgreen}{$N_{1-2}$}|
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+|\highlightYellow|int a = getA();
+|\highlightYellow|while(a<1000) {
+|\highlightYellow|  a *= 5;
+  doB(a); // nested gap
+} // gap between blocks
+doD(a); // part of gap
+|\highlightBlue|doC(a);
+\end{javacode}}
+\end{parcolumns}
 \caption{Statements between clones in different blocks.}

### 2019-07-30 sections/research.tex
Gap formula

@@
 \begin{javacode}
-public void doStuff(){
-|\highlightYellow|  doA(); // Clone instance of
-|\highlightYellow|  doB(); // two statements
-  doC(); // Gap of one statement
-|\highlightBlue|  doD(); // Clone instance of
-|\highlightBlue|  doE(); // two statements
-}
+|\highlightYellow|int a = getA(); // |\textcolor{pgreen}{$N_{1-1}$}|
+|\highlightBlue|doC(a); // |\textcolor{pgreen}{$N_{1-2}$}|
 \end{javacode}}
@@
 \begin{javacode}
-public void doStuff(){
-|\highlightYellow|  doA(); // Clone instance of
-|\highlightYellow|  doB(); // two statements
-  doF(); // Gap of one statement
-|\highlightBlue|  doD(); // Clone instance of
-|\highlightBlue|  doE(); // two statements
-}
+|\highlightYellow|int a = getA(); // |\textcolor{pgreen}{$N_{2-1}$}|
+a *= 5; // |\textcolor{pgreen}{$N_{2-2}$}|
+|\highlightBlue|doC(a); // |\textcolor{pgreen}{$N_{2-3}$}|
 \end{javacode}}
@@
 
+When applying this formula with the example given in figure \ref{fig:gappedclones}, we get a gap size of 50\%:
+
+\begin{equation}\label{eq:type3r}
+\text{T3R Gap Size}=\frac{|\{N_{2-2}\}|}{|\{N_{2-1}\}| + |\{N_{2-3}\}|}*100 = \frac{1}{2}*100 = 50\%
+\end{equation}
+
+\subsubsection{The gap may not span a partial block}
 Apart from this threshold, the gap in between clones may not span over different blocks.

### 2019-07-30 sections/research.tex
Partial block reference

@@
   \item \textbf{The size of the gap between two clones is limited by a threshold.} This threshold is calculated by taking the percentage of the number of statements in the gap over the number of statements that both clones that are being bridged span.
-  \item \textbf{The gap may not span a partial block.} To make sure that the T3R clone can be refactored, we do not allow the gap to span a part of a block, for instance, the declaration and a part of the body of a for-loop.
-The reason for this is that it is not possible to wrap a partially spanned block in a single conditional statement.
-We could, however, use multiple conditional blocks (one for each block spanned), but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for T3R clones.
+  \item \textbf{The gap may not span a partial block.} To make sure that the T3R clone can be refactored, we do not allow the gap to span a part of a block.
+This is further explained in section \ref{sec:t3rpartialblock}.
 \end{itemize}
@@
 
-\subsubsection{The gap may not span a partial block}
+\subsubsection{The gap may not span a partial block} \label{sec:t3rpartialblock}
 Apart from this threshold, the gap in between clones may not span over different blocks.
@@
 \end{figure}
+
+The reason for this is that it is not possible to wrap a partially spanned block in a single conditional statement.
+We could, however, use multiple conditional blocks (one for each block spanned), but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for T3R clones.
 

### 2019-07-30 sections/clonerefactor.tex
Complex control flow

@@
 \begin{itemize}
-    \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method.
-Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
     \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
@@
     \item \textbf{Overlaps}: There is overlap within the clone class.
+    \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method.
+Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
 \end{itemize}
@@
 
-\subsubsection{Can Be Extracted}
+\subsubsection{Complex Control Flow}
+\texttt{break}, \texttt{continue} and \texttt{return} statements in clone classes can obstruct the possibility of refactoring. This is the case if:
+\begin{itemize}
+  \item The clone class has at least one \texttt{return} statements, but not all paths through the clone class return.
+  \item There are \texttt{break} and/or \texttt{continue} statements in the clone class, but the corresponding loop/switch is not included.
+\end{itemize}
+
+If there is a \texttt{break} and/or \texttt{continue} statement in the cloned fragment, we walk up the AST to find the loop- or switch-statement it corresponds with.
+If this statement is included in the clone class, then the \texttt{break} and/or \texttt{continue} will be no problem for refactoring.
+However, if it isn't, then we mark it ``Complex Control Flow''.
 

### 2019-07-30 sections/background.tex
Node types

@@
 
+The AST consists of nodes of the following types (examples are for Java):
+\begin{itemize}
+  \item \textbf{Declarations}: Method-declaration, class-declaration, etc.
+  \item \textbf{Statements}: If-statement, switch-statement, expression-statement, etc.
+  \item \textbf{Expressions}: Variables, literals, method calls, variable assignments, etc.
+  \item \textbf{Types}: Primitives, reference types, void, etc.
+\end{itemize}
+
 \subsection{Inheritance}
@@
 This allows control over what parts of an application should be able to access what declarations.
+
+\section{Git}
+\todo{TODO}

### 2019-07-30 sections/clonerefactor.tex
Saving refactored code

@@
 
-\todo{Explain each category in more detail}
+\todo{Finish this section}
+
+\subsection{Applying refactorings}
+\todo{Write this section}
+
+\subsection{Saving refactored code}
+CloneRefactor features several ``Refactoring Strategies'', that indicate how and where refactored code will be saved. These are as follows:
+\begin{itemize}
+  \item \textbf{Do not refactor}: CloneRefactor does not apply refactorings at all, it only reports found clones.
+  \item \textbf{Replace}: CloneRefactor replaces the source code with the refactored source code.
+  \item \textbf{Copy Only Changes}: CloneRefactor writes only the changed files to a new location.
+  \item \textbf{Copy All}: CloneRefactor copies the entire project to a new location and applies the refactorings there.
+This makes sure the original project stays unmodified, while also having a snapshot of the refactored project.
+  \item \textbf{Git Replace}: CloneRefactor creates a branch on the git VCS, or initializes a git repository if it is not available.
+For every clone class refactored, CloneRefactor creates a commit in the git repository.
+  \item \textbf{Git Copy}: CloneRefactor copies the entire project to a new location.
+CloneRefactor then performs the same procedure as for ``Git Replace'', except now at the new location so the original project remains unmodified.
+\end{itemize}

### 2019-07-30 sections/clonerefactor.tex
Partial block

@@
 
+\subsubsection{Spans Part Of A Block}
+When applying an ``Abstract Method'' refactoring, we author a new method declaration.
+The body of this method declaration consists of a set of statements.
+However, if a single statement is only partially cloned, this might give issues with refactoring.
+An example of this is shown in figure \ref{fig:refactorabilitypartialblock}
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+|\highlightYellow|int a = getA();
+|\highlightYellow|while(a<1000) {
+|\highlightYellow|  a *= 5;
+  doC();
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+|\highlightYellow|int a = getA();
+|\highlightYellow|while(a<1000) {
+|\highlightYellow|  a *= 5;
+  doB(a);
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Partial block.}
+\label{fig:refactorabilitypartialblock}
+\end{figure}
+
+In this example, the while loop is partially cloned. This obstructs us from extracting the cloned code to a new method.
+
 \todo{Finish this section}

### 2019-07-30 sections/clonerefactor.tex
Is not a partial method

@@
   \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
-  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method. The declaration itself is not included.
+  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method/constructor. The declaration itself is not included.
   \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
@@
     \item \textbf{Spans Part Of A Block}: This clone spans a part of a statement.
-    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of the previous section, the ``extract method'' refactoring technique cannot be applied.
+    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of section \ref{sec:setupcontents}, the ``extract method'' refactoring technique cannot be applied.
     \item \textbf{Top-level Node Is Not A Statement}: The topmost node of a clone instance is not a statement.
@@
 In this example, the while loop is partially cloned. This obstructs us from extracting the cloned code to a new method.
+
+\subsubsection{Is Not A Partial Method}
+The ``Extract Method'' refactoring can only refactor code in the body of a method.
+We mapped the contents of clones in section \ref{sec:setuplocation}.
+Here we defined the ``Partial Method'' catagory as \textit{a clone that spans (a part of) the body of a method.
+The declaration itself is not included.} If the clone does not fall within this category, ``Extract Method'' is probably not the correct technique for refactoring such clones.
 

### 2019-08-02 sections/background.tex
Finished refactorability

@@
 
-\subsection{AST}
+\subsection{AST} \label{sec:astbackground}
 An Abstract Syntax Tree (AST) is a tree consisting of an hierarchical representation of the source code of a program.
@@
   \item \textbf{Types}: Primitives, reference types, void, etc.
+  \item \textbf{Clauses}: Catch-clause, else-clause, etc.
 \end{itemize}

### 2019-08-02 sections/clonerefactor.tex
Finished refactorability

@@
 Here we defined the ``Partial Method'' catagory as \textit{a clone that spans (a part of) the body of a method.
-The declaration itself is not included.} If the clone does not fall within this category, ``Extract Method'' is probably not the correct technique for refactoring such clones.
-
-\todo{Finish this section}
+The declaration itself is not included.} If the clone does not fall within this category, ``Extract Method'' is likely not to be correct technique for refactoring such clones.
+
+\subsubsection{Top-level Node Is Not A Statement}
+A method body can only consist of statements.
+We cannot put declarations in a method.
+However, there are possibilities where a clone consists of something else than a statement as top level node.
+The most prominent example is when a clause is cloned (see section \ref{sec:astbackground} for examples of such concepts).
+For instance, we cannot extract only the catch-clause of a try-statement to a new method.
+In such a case, we should either extract the complete try-statement, or only the contents of the catch clause.
+
+\subsubsection{Overlaps}
+We do not consider clone classes for refactoring that overlap in the clone class itself.
+That is because such clones may require other techniques to refactor them.
+We consider analyzing such refactoring methods future work.
+An example refactoring of clone instances that overlap within their clone class is displayed in figure \ref{fig:overlaprefactoring}.
+In this example one clone instance is found between line \ref{line:overlaprefactoring1} and \ref{line:overlaprefactoring4} and the other between \ref{line:overlaprefactoring2} and \ref{line:overlaprefactoring5}.
+To refactor such clones, other techniques may be required, like introducing a new for-loop to reduce the duplication.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+public void sayHello(){
+|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring1}|
+|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring2}|
+|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring3}|
+|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring4}|
+|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring5}|
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+public void sayHello(){
+|\highlightYellow|  for(int i = 0; i<5; i++){
+|\highlightYellow|    System.out.println("hello!");
+|\highlightYellow|  }
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring a clone class that has overlap between clone instances.}
+\label{fig:overlaprefactoring}
+\end{figure}
+
+\subsubsection{Can be extracted}
+All clones that do not adhere to any of above-stated categories, are considered suitable for method extraction.
 
@@
   \item \textbf{Do not refactor}: CloneRefactor does not apply refactorings at all, it only reports found clones.
+  \item \textbf{Simulate}: CloneRefactor only applies the refactorings to its internal AST structure and calculates the results of applying these refactorings.
+It does not modify/copy the codebase on disk.
   \item \textbf{Replace}: CloneRefactor replaces the source code with the refactored source code.

### 2019-08-02 sections/discussion.tex
Finished refactorability

@@
 
-\subsubsection{Overlap within a clone class}
-We do not consider clone classes for refactoring that overlap in the clone class itself.
-That is because such clones might require other techniques to refactor them.
-We consider analyzing such refactoring methods future work.
-An example refactoring of clone instances that overlap within their clone class is displayed in figure \ref{fig:overlaprefactoring}.
-In this example one clone instance is found between line \ref{line:overlaprefactoring1} and \ref{line:overlaprefactoring4} and the other between \ref{line:overlaprefactoring2} and \ref{line:overlaprefactoring5}.
-To refactor such clones, other techniques may be required, like introducing a new for-loop to reduce the duplication.
-
-\begin{figure}[H]
-\begin{parcolumns}{2}
-\colchunk[1]{
-\begin{javacode}
-// Original
-public void sayHello(){
-|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring1}|
-|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring2}|
-|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring3}|
-|\highlightDarkyellow|  System.out.println("hello!"); |\label{line:overlaprefactoring4}|
-|\highlightYellow|  System.out.println("hello!"); |\label{line:overlaprefactoring5}|
-}
-\end{javacode}}
-\colchunk[2]{
-\begin{javacode}
-// Refactored
-public void sayHello(){
-|\highlightYellow|  for(int i = 0; i<5; i++){
-|\highlightYellow|    System.out.println("hello!");
-|\highlightYellow|  }
-}
-\end{javacode}}
-\end{parcolumns}
-\caption{Refactoring a clone class that has overlap between clone instances.}
-\label{fig:overlaprefactoring}
-\end{figure}
-
 \subsubsection{Complex control flow}

### 2019-08-02 sections/research.tex
Complex control flow
Variable refactoring

@@
 
-\todo{Show examples}
+Figure \ref{fig:type2variablerefactoringnotradeoff} shows an example where different variables do not create a tradeoff.
+Both clone instances in this example use different variables, but in the same places and with the same type.
+Because these variables are locally defined, the extraced method requires an extra argument for the variable anyways.
+If the second clone instances would be completely equal, so also use the same variable, the refactoring would be very similar (it would only differ by a single character).
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+String a = "a";
+String b = "b";
+|\highlightYellow|doA(a);
+|\highlightYellow|doB(a);
+doC();
+|\highlightYellow|doA(b);
+|\highlightYellow|doB(b);
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+String a = "a";
+String b = "b";
+|\highlightYellow|doAandB(a);
+doC();
+|\highlightYellow|doAandB(b);
+\end{javacode}}
+\end{parcolumns}
+\caption{Different variables in cloned fragments without a difference in tradeoff on system design when refactored.}
+\label{fig:type2variablerefactoringnotradeoff}
+\end{figure}
+
+The example in figure \ref{fig:type2variablerefactoringwithtradeoff} shows the same example as figure \ref{fig:type2variablerefactoringnotradeoff}, however this time there is a tradeoff.
+The same variables are used, but they are not used in the same places in cloned fragments.
+In one fragment we use only one variable, in the other we use both.
+Because of that, we require an extra argument.
+Because of this, this variability falls under the threshold described in section \label{sec:variabilitythreshold}, whereas the example in figure \ref{fig:type2variablerefactoringnotradeoff} does not.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+String a = "a";
+String b = "b";
+|\highlightYellow|doA(a);
+|\highlightYellow|doB(a);
+doC();
+|\highlightYellow|doA(a);
+|\highlightYellow|doB(b);
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+String a = "a";
+String b = "b";
+|\highlightYellow|doAandB(a, a);
+doC();
+|\highlightYellow|doAandB(a, b);
+\end{javacode}}
+\end{parcolumns}
+\caption{Different variables in cloned fragments without a difference in tradeoff on system design when refactored.}
+\label{fig:type2variablerefactoringwithtradeoff}
+\end{figure}
 
@@
 In this formula, \textit{number of different expressions} refers to the number of literals, variables and method calls that differ from other clone instances in a clone class.
-We divide this by the total number of expressions in the clone instance.
+We divide this by the total number of literals, variables and method calls in the clone instance.
 Based on this threshold, we decide whether a clone should be considered for refactoring.
@@
 
-\subsubsection{Gap Threshold}
+\subsubsection{Gap threshold}
 For type 3R, the size of the gap between two clones is bounded by a threshold. This threshold is calculated by the following formula:

### 2019-08-02 sections/abstract.tex
Changes to overall structure
Better table (now it fits :diamond_shape_with_a_dot_inside:)
Ana

@@
 \chapter*{Abstract}
-\todo[inline,color=blue!10]{This should be done when most of the rest of the document is finished. Be concise, introduce context, problem, known approaches, your solution, your findings.}
-
+%\todo[inline,color=blue!10]{This should be done when most of the rest of the document is finished. Be concise, introduce context, problem, known approaches, your solution, your findings.}
+\todo{Update the abstract}
 Duplication in source code can have a major negative impact on the maintainability of source code.
@@
 In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages.
+We focus primarily on the Java programming language, as refactoring in general is very language-specific.
 

### 2019-08-02 sections/background.tex
Variable refactoring
Ana

@@
 \end{parcolumns}
-\caption{Refactoring duplication through method extraction.}
+\caption{Refactoring a clone class through method extraction.}
 \label{fig:extractmethod}
@@
 This can sometimes be a burden, when an external dependency does not use proper abstractions that are required by a software system.
-Because of that, in this study, we differentiate between internal and external classes to see what impact they have on the refactoring process.
+Because of that, in this study, we differentiate between internal and external classes to see what impact they have on the refactoring process.\todo{you don't consider external right?}
 
@@
 This allows control over what parts of an application should be able to access what declarations.
-
-\section{Git}
-\todo{TODO}

### 2019-08-02 sections/introduction.tex
Ana

@@
 There are tools that assist in the process of finding duplicate code, but none of these tools identify all duplication problems.
-Often, these clone detection tools result in false-positives and false-negatives \cite{roy2007survey}.
-We define false-negatives as clones that can and should be refactored but are not found due to the configuration by which they are detected.
+Often, these clone detection tools result in false-positives and false negatives \cite{roy2007survey}.
+We define false negatives as clones that can and should be refactored but are not found due to the configuration by which they are detected.
 We define false-positives as clones that do not improve the system maintainability when refactored.
-Many false-negatives are due to the thresholds that are used.
+Many false negatives are due to the thresholds that are used.
 Many clone detection tools \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval} only consider clones that have a minimum of 6 lines.
-Using such an approach is bound to result in many false-negatives, but using a lower threshold is shown to increase the number of false-positives.
+Using such an approach is bound to result in many false negatives, but using a lower threshold is shown to increase the number of false-positives.
 %TODO cite threshold paper

### 2019-08-02 icse/paper.tex
icse

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Simon Baars}
\IEEEauthorblockA{%\textit{Software Engineering} \\
\textit{University of Amsterdam}\\
Amsterdam, the Netherlands \\
simon.mailadres@gmail.com}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Ana Oprescu}
\IEEEauthorblockA{%\textit{dept. name of organization (of Aff.)} \\
\textit{University of Amsterdam}\\
Amsterdam, the Netherlands \\
ana.oprescu@uva.nl}
}

\maketitle

\begin{abstract}
Coming up!
\end{abstract}

\begin{IEEEkeywords}
code clones, refactoring, static code analysis, object-oriented programming
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Background}

\subsection{Code clone terminology}
Clone class collection, clone class, clone instance, cloned node, token.

\subsection{Refactoring techniques}
Extract method, move method.

\section{Defining refactorable clones}
Instead of defining clone types, I just define how we can ensure that clones can be refactored. I do not plan to differentiate between T1R, T2R and T3R here, because I think it makes the paper confusing.

To be honest, I'm not even sure how relevant it is to name the literature clone types. Maybe not focus on their shortcomings, but just start from the core (sourcecode) and define how we can get to refactorable clones.

\subsection{Ensuring Equality}
Explain type 1, why it is not always refactorable, solution

\subsection{Allowing variability in a controlled set of expressions}
Explain type 2, why it is not always refactorable, solution

\subsection{Gapped clones}
Explain type 3, why it is not always refactorable, solution

\section{CloneRefactor}
The tool: Detect Clones -> Map Context -> Refactor.

\subsection{Clone Detection}
Detecting refactorable clones, (clone graph?? do I want to explain my exact methods?)

\subsection{Context Mapping}
\subsubsection{Relation}
\subsubsection{Location}
\subsubsection{Contents}

\subsection{Refactoring}
\subsubsection{Extract Method}
Show my categories to show what clones can be dealt with by method extraction.

\subsubsection{AST Transformation}
Explain what AST transformations I do to apply the refactorings.

\subsubsection{The cyclic nature of refactoring}
Explain how refactoring code clones might open up new refactoring opportunities.

\section{Results}

\subsection{Clone context}
How many clones are there in certain contexts?

\subsection{Clone refactorability}
To what extent can found clones be refactored through method extraction, without requiring additional transformations.

\subsection{Thresholds}
I think the ultimate goal with this thesis is to experiment the refactored source code

\section{Discussion}

\section{Conclusion}

\section*{Acknowledgment}
:-)

\section*{References}

\end{document}

### 2019-08-02 icse/paper.tex
Paper stuff

@@
 
-\title{Paper Title*\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
-\thanks{Identify applicable funding agency here. If none, delete this.}
-}
+\title{Improving Software Maintainability through Automated Refactoring of Code Clones}
 
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
 
@@
 Clone class collection, clone class, clone instance, cloned node, token.
+
+\subsection{Code clone definitions}
+Quick overview of clone type definitions
 
@@
 \section{CloneRefactor}
-The tool: Detect Clones -> Map Context -> Refactor.
+The tool: Detect Clones, Map Context, Refactor.
 
@@
 \subsubsection{The cyclic nature of refactoring}
-Explain how refactoring code clones might open up new refactoring opportunities.
+Explain how refactoring code clones might open up new refactoring opportunities. We refactor a project until there are no more open refactoring opportunities.
 
@@
 \subsection{Clone context}
-How many clones are there in certain contexts?
+How many clones are there in certain contexts? Experiments for relation, location and context.
 
@@
 \subsection{Thresholds}
-I think the ultimate goal with this thesis is to experiment the refactored source code
+I think the ultimate goal with this thesis is to do experiments with different clone thresholds.
+Which thresholds give clones that we should refactor?
+For this, we will measure the maintainability of the refactored source code over different thresholds.
+These thresholds range from minimum clone size, variability and gap size.
 
 \section{Discussion}
+\subsection{Clone Definitions}
+
+\subsection{CloneRefactor}
+
+\subsection{Experimental setup}
 

### 2019-08-10 sections/clonerefactor.tex
Variable refactoring
Applying refactorings -> relation

@@
 \subsubsection{Can be extracted}
-All clones that do not adhere to any of above-stated categories, are considered suitable for method extraction.
+All clones that do not adhere to any of above-stated categories, are considered suitable for automated method extraction.
 
 \subsection{Applying refactorings}
+All clones that are marked as ``Can be Extracted'' will then be refactored.
+The refactoring techniques that we use depend on the relation and contents of the clone.
+In this section, we explain the transformations we apply to the program AST in order to refactor clones.
+
+First, we create a new method and give it an uniquely generated name.
+We replace all nodes from the clone instances of the clone to method calls of the newly created method.
+We place a copy the nodes that were removed from a single clone instance in the new method.
+
+\subsubsection{Relation}
+For each of the identified clone relations (section \ref{sec:setuprelation}) we define a method of automatically refactoring clones in these categories.
+The relation determines the location at which we place the newly created method.
+
+\paragraph{Common Class}
+For clone instances that are in the same class, we place the method in the body of that class.
+We give the method a \texttt{private} visibility, which indicates that the method can only be used within its class.
+
+\paragraph{Common Hierarchy}
+We place the extracted method in the class which all clone instances share as a superclass.
+We give the method a \texttt{protected} visibility, which indicates that the method can only be used within its hierarchy.
+
+\paragraph{Common Interface}
+We place the extracted method in the interface all clone instances have in common.
+We give the method a \texttt{public} visibility (because interfaces do not allow for \texttt{protected} visibility) and turn it into a default implementation using the \texttt{default} keyword.
+
+\paragraph{Unrelated}
+If all clone instances in a clone class are in different classes that do not yet have a superclass, or their ancestors have no superclass, we create a superclass abstraction for them.
+This way we make the implicit dependency between both clone fragments explicit, while provisioning a common place for common functionality.
+We give the method a \texttt{protected} visibility, which indicates that the method can only be used within its hierarchy.
+
+If the clone instances have an external superclass or ancestor, we create an interface abstraction instead to place the extracted method in.
+We give the method a \texttt{public} visibility (because interfaces do not allow for \texttt{protected} visibility) and turn it into a default implementation using the \texttt{default} keyword.
+
+Because for unrelated clone instances we create new abstractions, we could change the relation of other clones.
+When we introduce a new superclass abstraction, other clones might turn from ``unrelated'' into ``common hierarchy''.
+Because of this, creating a single abstraction could favor multiple refactoring opportunities.
+
+For unrelated clones, we always create a new abstraction instead of introducing a ``utility class''.
+Most current code clone refactoring support tools use utility classes to refactor unrelated code clones \cite{mazinanian2016jdeodorant, yoshida2005refactoring, gode2010clone}.
+For this study we refrain from doing this, because the introduction of many static methods can make a codebase hard to comprehend \cite{xing2003pseudo}.
+Additionally, we can use the created abstractions for further refactorings.
+
+\subsubsection{Populate method}
+After placing the newly abstracted method at an appropriate location, we analyze the method content to result 
 \todo{Write this section}

### 2019-08-11 sections/clonerefactor.tex
Populate method

@@
 \subsubsection{Populate method}
-After placing the newly abstracted method at an appropriate location, we analyze the method content to result 
+After placing the newly abstracted method at an appropriate location, we analyze the method content to determine whether we need to add parameters, a return value or a \texttt{throws} clause to the method declaration.
+
+\paragraph{Method parameters}
+We determine which variables and methods that are used in the method body are not accessible anymore at the location where the extracted method is placed.
+For each of these variables and called methods we add a parameter to the extracted method.
+We then pass the appropriate data to each method call.
+
+\paragraph{Return value}
+The exracted method has a return value if one of these three conditions is met:
+\begin{itemize}
+\item \textbf{There is a return statement in the extracted fragment}: If the extracted code fragment ends in a return statement, we set the type of the returned variable as the type of the extracted method.
+We turn all method calls of the extracted method into return statements followed by the method call.
+\item \textbf{A method parameter is re-assigned in the extracted fragment}: If a method parameter is re-assigned, we must return its changed value.
+We add a return statement to the end of the body of the extracted method returning the variable that was changed.
+We set the return type of the extracted method to the type of the variable that was assigned.
+We turn all method calls of the extracted method into variable assignment statements in which we assign the changed variable.
+\item \textbf{A variable is declared in the extracted fragment}: If a variable is declared in the extracted fragment, but used outside it, we return the declared variable.
+We add a return statement to the end of the body of the extracted method that returns the declared variable.
+If the variable declaration statement is the final statement in the method body, we remove the variable declaration and directly return the value it assigns to the declared variable.
+We set the return type of the extracted method to the type of the variable that was declared.
+We turn all method calls of the extracted method into variable declaration statements in which we declare the variable returned by the extracted method.
+\end{itemize}
+
+\paragraph{Thrown exception}
+If a method in Java throws an exception that is not a \textbf{RuntimeException}, it must be denoted in the method declaration.
+Because of this, we analyze the extracted method for \texttt{throw} statements, which denote an exception being thrown.
+We also analyze all called methods to find out whether they throw exceptions.
+For each of these exception, we check whether they are caught in the extracted method.
+Any exception that is that is not a \textbf{RuntimeException} and that is not being caught is added to the thrown exceptions of the extracted method.
+
+\subsection{Collecting data}
 \todo{Write this section}

### 2019-08-11 sections/clonerefactor.tex
Characteristics of ref

@@
 
-\paragraph{Return value}
+\paragraph{Return value}\label{sec:refreturn}
 The exracted method has a return value if one of these three conditions is met:
@@
 \subsection{Collecting data}
-\todo{Write this section}
+To find out whether clones should be refactored (RQ3) we collect data about the applied refactorings.
+We use this data to find out whether a specific refactoring succeeds in improving the maintainability of the system.
+We define the following characteristics that have an impact on the refactoring of the clone class:
+\begin{itemize}
+\item \textbf{Nodes}: The number of nodes that \textit{each clone instance of the clone class} spans. This concerns the size of a single clone instance before it was refactored.
+\item \textbf{Tokens}: The number of tokens that the \textit{each clone instance of the clone class} spans. This concerns the size of a single clone instance before it was refactored.
+\item \textbf{Relation}: The relation category (section \ref{sec:setuprelation}) that this clone class belongs to.
+\item \textbf{Returns}: The category of what the extracted method returns (section \ref{sec:refreturn}).
+\item \textbf{Parameters}: The number of parameters the extracted method has.
+\end{itemize}
+These characteristics define the \textbf{input} of the refactoring.
+As an output, we measure the impact of applying these refactorings on system maintainability metrics.
+These metrics are derived from Heitlager et al.
+\cite{heitlager2007practical}.
 
@@
 \end{itemize}
+These ``Refactoring Strategies'' can be used to get more data regarding the transformations applied by CloneRefactor. In our experiments, we only make use of the ``Simulate'' ``Refactoring Strategy''.

### 2019-08-11 sections/clonerefactor.tex
Metrics stuff

@@
 We use this data to find out whether a specific refactoring succeeds in improving the maintainability of the system.
+For each refactored clone class, we map the characteristics of the extracted method to the impact of the refactoring on the maintainability of the system/
+
+\subsubsection{Characteristics of the extracted method}
 We define the following characteristics that have an impact on the refactoring of the clone class:
@@
 \end{itemize}
-These characteristics define the \textbf{input} of the refactoring.
-As an output, we measure the impact of applying these refactorings on system maintainability metrics.
+We hypothesize that these characteristics are the main factors influencing the impact on the maintainability of the system as a result of refactoring the clone.
+
+\subsubsection{Impact on maintainability metrics}
+We measure the impact on maintainability metrics of the refactored source code for each clone class that is refactored.
 These metrics are derived from Heitlager et al.
 \cite{heitlager2007practical}.
+This paper defines a set of metrics to measure the maintainability of a system.
+For each of these metrics, risk profiles are proposed to determine the maintainability impact on the system of a whole.
+
+In this case we are dealing with single refactorings and we want to measure the maintainability impact of such a small change.
+Because of that, we measure only a subset of the metrics \cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
+The subset of metrics we decided to focus on are all metrics that are measured on method level (as the other metrics show a lesser impact on the maintainability for these small changes).
+These metrics are
+\begin{itemize}
+\item \textbf{Duplication}: In Heitlager et al.
+\cite{heitlager2007practical} this metric is measured by taking the amount of duplicated lines.
+We decided to use the amount of duplicated tokens part of a clone class instead, to have a stronger reflection of the impact of the refactoring by measuring a more fine-grained system property.
+\item \textbf{Volume}: The more code a system has, the more code has to be maintained.
+The paper \cite{heitlager2007practical} measures volume as lines of code.
+As with duplication, we use the amount of tokens instead.
+\item \textbf{Complexity}: Heitlager et al.
+use MCCabe complexity \cite{mccabe1976complexity} to calculate their complexity metric.
+The MCCabe complexity is a quantative measure of the number of linearly independent paths through a method.
+\end{itemize}
 

### 2019-08-11 sections/clonerefactor.tex
Calculating maintainability increase

@@
 The MCCabe complexity is a quantative measure of the number of linearly independent paths through a method.
+\item \textbf{Method Interface Size}: The amount of parameters that a method has.
+If a method has many parameters, the code may become harder to understand and it is an indication that data is not encapsulated adequately in objects \cite{fowler2018refactoring}.
+\end{itemize}
+
+We can deduct the change of the values of these metrics by considering the transformations that are done by the refactoring. We calculate these metrics as follows:
+
+\begin{itemize}
+\item \textbf{Duplication}: The duplication can only decrease as a result of the refactoring.
+We calculate the reduction of duplication as the product of the number of tokens in the body of the extracted and the number of clone instances in the clone class.
+\item \textbf{Volume}: The volume can both decrease and increase as a result of the refactoring.
+The reduction of volume is equal to the reduction of duplication.
+The volume is increased by the amount of tokens in each method call to the extracted method, plus optionally the return, assignment or declaration of the extracted method.
+We also add the size in tokens of the extracted method itself to the volume.
+If the extracted method is moved to a newly created class or interface, we use volume of that declaration instead (because it in turn contains the extracted method).
+The added volume minus the reduced volume results in the change in volume.
+\item \textbf{Complexity}: The complexity can both decrease and increase as a result of the refactoring.
+To calculate the reduction of complexity, we take the sum of all branching statements in all clone instances.
+The increase in complexity is the complexity of the extracted method (the number of branches plus one).
+The added volume complexity the reduced complexity results in the change in complexity.
+\item \textbf{Method Interface Size}: The duplication can only increase as a result of the refactoring. The method interface size increases by the amount of parameters in the extracted method.
 \end{itemize}

### 2019-08-11 sections/clonerefactor.tex
Experimental setup

@@
 % We bridged a gap between clone detection and refactoring .. by designing a tool
-CloneRefactor is the name of our clone detection and refactoring tool. It features the following novel functions:
-\begin{itemize}
-  \item Detection of clone classes rather than clone pairs.
-  \item A novel detection method, aimed at extensibility.
-  \item Detection of refactoring-oriented clone types, in addition to the literature clone types.
-  \item Allows for automated refactoring of a subset of the detected duplication issues.
-\end{itemize}
+We bridged a gap between clone detection and refactoring by designing a tool that can detect clones by our refactoring-oriented clone types (chapter \ref{chap:clonetypes}).
+This tool, named CloneRefactor, performs a comprehensive context analysis on the detected clones.
+Based on this this context, CloneRefactor can automatically refactor a subset of the detected clones by applying transformations to the source code of the analyzed software project(s).
+
 In this section we describe our approach and rationale for the design decisions regarding this tool.
@@
 
-We can deduct the change of the values of these metrics by considering the transformations that are done by the refactoring. We calculate these metrics as follows:
+We can determine the change of the values of these metrics by considering the transformations that are done by the refactoring. We calculate these metrics as follows:
 

### 2019-08-11 sections/experimentalsetup.tex
Experimental setup

--- 2019-07-22 sections/experimentalsetup.tex
@@
-\chapter{Experimental setup}
-In this chapter we describe the setup we use for our experiments.
-All results of our experiments, as displayed in chapter \ref{ch:results}, are measured over a corpus of Java projects.
-In this chapter we will explain how we prepared this corpus.
+\chapter{Experimental Setup}
+In this chapter we explain the setup of our experiments.
+All our experiments are quantitative experiments, measured over a corpus using CloneRefactor.
+In this chapter, we first explain the corpus we use.
+We then explain the way in which we calculate the impact of refactorings on the software maintainability.
 
 \section{The corpus}\label{chap:corpus}
-For our measurements we use a large corpus of open source projects \cite{githubCorpus2013}.
-This corpus has been assembled to contain relatively higher quality projects.
-Also, any duplicate projects were removed from this corpus.
+For our experiments we use a large corpus of open source projects \cite{githubCorpus2013}.
+This corpus contains a set of Java projects from GitHub, selected by number of forks.
+The projects in this corpus were then de-duplicated manually.
 This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
+
+For our purposes, we have further filtered this corpus to get a controlled set of projects for our experiments.
+In this section, we explain the steps we took to prepare the corpus and the rationale behind those steps.
+
+\subsection{Project dependencies}
+As explained
 
@@
 As these are not included in the used corpus \cite{githubCorpus2013}, we decided to filter the corpus to only include Maven projects.
-Maven is a build automation tool used primarily for Java, and works on basis of an \texttt{pom.xml} file to describe the projects' dependencies.
+Maven is a build automation tool used primarily for Java, and works on the basis of an \texttt{pom.xml} file to describe the projects' dependencies.
 As no \texttt{pom.xml} files are included in the corpus, we cloned the latest version of each project in the corpus.
@@
 \end{table}
-
-\section{Context Analysis of Clones}\label{chap:contextsetup}
-To be able to refactor code clones, it is important to consider the context of the clone. We define the following aspects of the clone as its context:
-\begin{enumerate}
-  \item \textbf{Relation:} The relation of clone instances among each other through inheritance.
-  \item \textbf{Location:} Where a clone instance occurs in the code.
-  \item \textbf{Contents:} The statements/declarations of a clone instance.
-\end{enumerate}
-We perform experiments on each of these aspects, defining categories and measuring these categories over the corpus.
-
-\begin{figure}[H]
-  \centering
-    \includegraphics[width=0.8\columnwidth]{img/context}
-    \caption{Abstract representation of clone classes and clone instances.}
-  \label{fig:clonecontext}
-\end{figure}
-
-Fig.~\ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
-The relation of clones through inheritance is measured for each clone class.
-The location and contents of clones are measured for each clone instance.
-
-\subsection{Relation}\label{sec:setuprelation}
-When merging code clones in object-oriented languages, it is important to consider the inheritance relation between clone instances. This relation has a big impact on how a clone should be refactored.
-
-Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other.
-To do this, they first define several categories for the relation between clone instances in object-oriented languages.
-These categories are as follows:
-\begin{enumerate}
-  \item \textbf{Same Method}: All instances of the clone class are in the same method.
-  \item \textbf{Same Class}: All instances of the clone class are in the same class.
-  \item \textbf{Superclass}: All instances of the clone class are in a class that is child or parent of each other.
-  \item \textbf{Sibling Class}: All instances of the clone class have the same parent class.
-    \item \textbf{Ancestor Class}: All instances of the clone class are superclasses except for the direct superclass.
-  \item \textbf{First Cousin Class}: All instances of the clone class have the same grandparent class.
-\item \textbf{Same Hierarchy Class}: All instances of the clone class belong to the same inheritance hierarchy, but do not belong to any of the other categories.
-\item \textbf{Same External Superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
-\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
-\end{enumerate}
-
-We added the following categories, to gain more information about clones and reduce the number of unrelated clones:
-
-\begin{enumerate}
-\item \textbf{Same Interface}: All instances of the clone class are in a class or interface that have a common interface anywhere in their inheritance hierarchy.
-\item \textbf{No Direct Superclass}: All instances of the clone class are in a class that does not have any superclass.
-\item \textbf{No Indirect Superclass}: All instances of the clone class are in a class that does not have any external classes in its inheritance hierarchy.
-\end{enumerate}
-
-Figure \ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
-The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
-The location and contents of clones is measured on clone instance level.
-A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50).
-A clone instance contents consists of a list of all statements and declarations it spans.
-
-\begin{figure}[H]
-  \centering
-    \includegraphics[width=0.6\columnwidth]{img/Relation}
-      \caption{Abstract figure displaying relations of clone classes. Arrows represent superclass relations.}
-  \label{fig:clonerelation}
-\end{figure}
-
-We separate these relations into the following categories, because of their related refactoring opportunities:
-\begin{itemize}
-  \item \textbf{Common Class}: \textit{Same Method}, \textit{Same Class}
-  \item \textbf{Common Hierarchy}: \textit{Superclass}, \textit{Sibling Class}, \textit{Ancestor Class}, \textit{First Cousin}, \textit{Same Hierarchy}
-  \item \textbf{Common Interface}: \textit{Same Interface}
-  \item \textbf{Effectively Unrelated}: \textit{No Direct Superclass}, \textit{No Indirect Superclass}, \textit{External Superclass}, \textit{Unrelated}
-\end{itemize}
-
-Every clone class only has a single relation, which is the first relation from above list that the clone class applies to.
-For instance: all ``Superclass'' clones also apply to ``Same Hierarchy'', but because ``Superclass'' is earlier in above list they will get the ``Superclass'' relation.
-This is because the items earlier in the list denote a more favorable refactoring.
-
-To check a the relation for a given clone class, we compare each node in a clone instance with the respective nodes in each other clone instance within a clone class.
-So for a clone class with x clone instances and each clone instance has y nodes, we perform:
-
-\begin{equation}\label{eq:sameclass}
-\frac{x * (x + 1)}{2} * y
-\end{equation}
-
-comparisons to determine the relation.
-Each of these checks will result in one of the relations from the list above.
-Of these relations, the item lowest in the list is going to be the relation of the clone class.
-So for instance, if a clone class has 15 nodes that denote a \textit{Superclass} relation but 3 nodes are \textit{Unrelated}, the clone class becomes \textit{Unrelated}.
-
-\subsubsection{Common Class}
-The \textit{Same method} and \textit{Same class} relations share a common refactoring opportunity.
-Clones of both these catagories, when extracted to a new method, can be placed in the same class.
-Both of these relations are most favorable for refactoring, as they require a minimal design tradeoff.
-Furthermore, global variables that are used in the class can be used without having to create method parameters.
-
-Cloned nodes are flagged as \textit{Same method} if these nodes are found in the same method.
-We define the method as the first method declaration that is encountered when following the parent nodes in the ast for a given cloned node.
-Please note that a clone instance may not always be in a method, for which this predicate will fail.
-
-Cloned nodes are flagged as \textit{Same class} if these nodes are found in the same class.
-We define the class as the first class declaration that is encountered when following the parent nodes in the ast for a given cloned node.
-
-\subsubsection{Common Hierarchy}
-Clones that are in a common hierarchy can be refactored by using the ``Extract Method'' refactoring method followed by ``Pull Up Method'' until the method reaches a location that is accessible by all clone instances.
-However, the more often ``Pull Up Method'' has to be used, the more detrimental the effect is on system design.
-This is because putting a lot of functionality in classes higher up in an inheritance structure can result in the ``God Object'' anti-pattern.
-A god object is an object that knows too much or does too much.
-
-Cloned nodes are flagged as \textit{Superclass} if the classes in which these nodes are found are parent and child class of each other.
-Cloned nodes are flagged as \textit{Siblings} if the classes in which these nodes are found all share the same parent and this parent class is not external.
-Cloned nodes are flagged as \textit{First Cousin} if the classes in which these nodes are found all share the same grandparent and this grandparent class is not external.
-
-Cloned nodes are flagged as \textit{Ancestor} if the classes in which these nodes are found are recursively the parent of an antecedent.
-Cloned nodes are flagged as \textit{Same Hierarchy} if the classes in which these nodes are found are all in the same inheritance hierarchy and not linked by any external classes.
-
-\subsubsection{Common Interface}
-Many object-oriented languages know the concept of ``interfaces'', which are used to specify a behavior that classes must implement.
-As code clones describe functionality and interfaces originally did not allow for functionality, interfaces did not open up refactoring opportunities for duplicated code.
-However, many programming languages nowadays support default implementations in interfaces.
-Since Java 7 and C\#8, these programming languages allow for functionality to be defined in interfaces.
-Many other object-oriented languages like Python allow this by nature, as they do not have a true notion of interfaces.
-
-The greatest downside on system design of putting functionality in interfaces is that interfaces are per definition part of a classes' public contract.
-That is, all functionality that is shared between classes via an interface cannot be hidden by setting a stricter visibility.
-Because of that, we favor all ``Common Hierarchy'' refactoring opportunities over ``Common Interface''.
-
-To check whether two cloned nodes have common interfaces, we recursively walk all types the class or interface of the cloned nodes implement and extend.
-The common interface that is closest to the cloned node in terms of depth of recursion will be flagged as the refactoring candidate.
-
-\subsubsection{Effectively Unrelated}
-\todo{TODO}
-
-\subsection{Location}\label{sec:setuplocation}
-A paper by Lozano et al.
-\cite{lozano2007evaluating} discusses the harmfulness of cloning.
-The authors argue that 98\% are produced at method-level.
-However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
-We validated this claim over our corpus.
-The results for the clone instance locations are shown in Table \ref{table:locations}.
-We chose the following categories:
-\begin{enumerate}
-  \item \textbf{Method/Constructor Level:} A clone instance that does not exceed the boundaries of a single method or constructor (optionally including the declaration of the method or constructor itself).
-  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class (like field declarations, other methods, etc.).
-  \item \textbf{Interface Level:} A clone that is (a part of) an interface.
-  \item \textbf{Enumeration Level:} A clone that is (a part of) an enumeration.
-\end{enumerate}
-
-\subsection{Contents}\label{sec:setupcontents}
-Finally, we looked at what nodes individual clone instances span. We selected the following categories to be relevant for refactoring:
-\begin{enumerate}
-  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
-  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially, optionally including its declaration.
-  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
-  \item \textbf{Only Fields:} A clone that spans only global variables.
-  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields and other things, like methods.
-  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
-  \item \textbf{Other:} Anything that does not match with above-stated categories.
-\end{enumerate}
-
-\section{Method extraction opportunities}\label{sec:refactorabilitysetup}
-The most used technique to refactor clones is method extraction (creating a new method on basis of the contents of clones).
-However, method extraction cannot be applied in all cases.
-In these instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.
-
-We measured the number of clones that can be refactored through method extraction (without additional transformations being required). We defined the following categories:
-\begin{itemize}
-    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a method.
-Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
-    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
-    \item \textbf{Spans part of a block:} This clone spans a part of a statement.
-    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table~\ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
-\end{itemize}

### 2019-08-11 sections/results.tex
Xander
Experimental setup

@@
 In this chapter, we present the results of our experiments.
-
-\section{The corpus}\label{chap:corpus}
-For our experiments we use a large corpus of open source projects \cite{githubCorpus2013}.
-This corpus has been assembled to contain relatively higher quality projects.
-Also, any duplicate projects were removed from this corpus.
-This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
-
-As indicated in chapter \ref{chap:challenge} CloneRefactor requires all libraries of software projects we test.
-As these are not included in the used corpus \cite{githubCorpus2013}, we decided to filter the corpus to only include Maven projects.
-Maven is a build automation tool used primarily for Java, and works on basis of an \texttt{pom.xml} file to describe the projects' dependencies.
-As no \texttt{pom.xml} files are included in the corpus, we cloned the latest version of each project in the corpus.
-We then removed each project that has no \texttt{pom.xml} file.
-As a final step, we collected all dependencies for each project by using the \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib} Maven command, and removed each project for which not all dependencies were available (due to non-Maven dependencies being used or unsatisfiable dependencies being referenced in the \texttt{pom.xml} file).
-
-Some general data regarding this corpus is displayed in Table \ref{table:general}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{General results for GitHub Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
-  \medskip
-\begin{tabular}{|l|l|}
-\hline
-Amount of projects                                                                                      & 1,361      \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\whitespace, comments and newlines.)\end{tabular} & 1,414,996  \\ \hline
-Amount of statements/declarations                                                                       & 1,212,189  \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of tokens (excluding\\whitespace, comments and newlines.)\end{tabular} & 11,643,194 \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
 

### 2019-08-11 sections/clonerefactor.tex
Proper capitalization for some concepts

@@
 First, we detect clones on the basis of a Java codebase, given a Java project from disk and a configuration.
-The clone detection process is further explained in section \ref{sec:clonedetection}.
+The clone detection process is further explained in Section~\ref{sec:clonedetection}.
 After all clones are found, CloneRefactor maps the context of the clones.
@@
 This has a big impact on performance efficiency.
-This is visible in our results, as displayed in section \ref{sec:clonetypeexperiments}.
+This is visible in our results, as displayed in Section~\ref{sec:clonetypeexperiments}.
 
@@
   \item \textbf{T2R Variability}: The percentage of variability we allow in variables, method calls and literals.
-How this threshold is calculated is explained in section \ref{sec:t2rcheckglobalthres}.
+How this threshold is calculated is explained in Section~\ref{sec:t2rcheckglobalthres}.
 \end{itemize}
@@
 This is a percentage of the size of the gap against the size of both clones combined.
-How this threshold is calculated is further explained in section \ref{sec:t3rclonerefactor}.
+How this threshold is calculated is further explained in Section~\ref{sec:t3rclonerefactor}.
 \end{itemize}
@@
 
-The overall process regarding clone detection is displayed in figure \ref{fig:clonedetection}.
+The overall process regarding clone detection is displayed in Figure~\ref{fig:clonedetection}.
 First of all, we use JavaParser to read a project from disk and build an AST, one class file at a time.
-Each AST is then converted to a directed graph that maps relations between statements, further explained in section \ref{sec:clonegraph}.
+Each AST is then converted to a directed graph that maps relations between statements, further explained in Section~\ref{sec:clonegraph}.
 On the basis of this graph, we detect clone classes and verify them using three thresholds (in order of importance):
@@
 This means we won't be able to find when a single expression matches another expression, or even a single token matching another token.
-This is in most cases not a problem, as expressions are often small and do not span the minimal size to be considered a clone in the first place (more about this in section \ref{sec:thresholds}).
+This is in most cases not a problem, as expressions are often small and do not span the minimal size to be considered a clone in the first place (more about this in Section~\ref{sec:thresholds}).
 
@@
 This map is used to efficiently find out whether a statement is cloned with another.
-An example of such a graph is displayed in figure \ref{fig:clonegraphsimple}.
+An example of such a graph is displayed in Figure~\ref{fig:clonegraphsimple}.
 
@@
 This is a restriction we've chosen as it creates an important constraint for the clone detection process.
-This process is explained in section \ref{sec:detectingclones}.
+This process is explained in Section~\ref{sec:detectingclones}.
 
@@
 \subsubsection{Mapping graph nodes to code}
-The clone graph, as explained in section \ref{sec:buildingclonegraph}, contains all declarations and statements in a source code.
+The clone graph, as explained in Section~\ref{sec:buildingclonegraph}, contains all declarations and statements in a source code.
 However, declarations and statements may themselves have child declarations and statements.
 To avoid redundant duplication checks, we exclude the body of each node.
-Look at figure \ref{fig:clonegraph} for an example of how source code maps to AST nodes.
+Look at Figure~\ref{fig:clonegraph} for an example of how source code maps to AST nodes.
 
@@
 This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node.
-As an example, we convert the code example shown in figure \ref{fig:clonegraph} to a clone graph as displayed in figure \ref{fig:clonegraph2}.
+As an example, we convert the code example shown in Figure~\ref{fig:clonegraph} to a clone graph as displayed in Figure~\ref{fig:clonegraph2}.
 
@@
 
-Using the example shown in figure \ref{fig:clonegraph} and \ref{fig:clonegraph2} we can explain how we detect clones on the basis of this graph.
+Using the example shown in Figure~\ref{fig:clonegraph} and \ref{fig:clonegraph2} we can explain how we detect clones on the basis of this graph.
 Suppose we are finding clones for two files and the final node of the second file is a variable declarator.
@@
 \subsection{Validating the type 2R variability threshold}
-In the definition of type 2R clones (see section \ref{sec:type2r}) we described how type 2R clones work on the basis of a variability threshold.
+In the definition of type 2R clones (see Section~\ref{sec:type2r}) we described how type 2R clones work on the basis of a variability threshold.
 This threshold is checked by CloneRefactor to assess the validity of found clone classes.
@@
 This process is done as a postprocessing step after clone detection.
-The type 2R clone detection process is described in more detail in section \ref{sec:comparingstuff}.
+The type 2R clone detection process is described in more detail in Section~\ref{sec:comparingstuff}.
 In short, this process detects clones allowing for any variability between expressions.
@@
 Each literal, method call or variable becomes a positive number, whereas each other token becomes a negative number.
-An example of two code fragments converted to equality arrays is displayed in figure \ref{fig:equalityarrays}.
+An example of two code fragments converted to equality arrays is displayed in Figure~\ref{fig:equalityarrays}.
 
@@
 
-The equality array for each of the lines in this example is shown in table \ref{table:equalityarrays}.
+The equality array for each of the lines in this example is shown in Table~\ref{table:equalityarrays}.
 
@@
 \begin{center}
- \caption{The equality arrays in our example figure \ref{fig:equalityarrays}.} \label{table:equalityarrays}
+ \caption{The equality arrays in our example Figure~\ref{fig:equalityarrays}.} \label{table:equalityarrays}
  \medskip
@@
 
-In the example of figure \ref{fig:equalityarrays} the fragment on the left (consisting of $n_1$ and $n_2$) and the fragment on the right (consisting of $n_3$ and $n_4$) are two clone instances of a clone class.
+In the example of Figure~\ref{fig:equalityarrays} the fragment on the left (consisting of $n_1$ and $n_2$) and the fragment on the right (consisting of $n_3$ and $n_4$) are two clone instances of a clone class.
 Table \ref{table:equalityarrays} shows their corresponding equality arrays.
@@
 Using the equality arrays explained in the previous section, we can determine the variability threshold of any clone class.
-We calculate the variability of the example given in table \ref{table:equalityarrays} as follows:
+We calculate the variability of the example given in Table~\ref{table:equalityarrays} as follows:
 
@@
 
-Where $E_x$ refers to the equality arrays shown in table \ref{table:equalityarrays} and \textit{x} is the node number displayed in the same table.
-When we apply this equation to the example clone classes displayed in figure \ref{fig:equalityarrays}, we get the following sum:
+Where $E_x$ refers to the equality arrays shown in Table~\ref{table:equalityarrays} and \textit{x} is the node number displayed in the same table.
+When we apply this equation to the example clone classes displayed in Figure~\ref{fig:equalityarrays}, we get the following sum:
 
@@
 \todo{Usage of the word adheres is questionable here...}
-So for the example given in figure \ref{fig:equalityarrays} we have a variability of 75\%.
+So for the example given in Figure~\ref{fig:equalityarrays} we have a variability of 75\%.
 In CloneRefactor, the maximum variability percentage is a threshold that is entered in a configuration file.
@@
 Because a clone does not adhere to the thresholds, it does not yet mean it has to be discarded.
-This is because an invalid clone class can still contain valid clones that are a subset of the invalid clone (our definition of subsets of clones is given in section \ref{sec:conceptualremovingredundant}).
+This is because an invalid clone class can still contain valid clones that are a subset of the invalid clone (our definition of subsets of clones is given in Section~\ref{sec:conceptualremovingredundant}).
 
@@
 
-The first line of the cloned fragment shown in figure \ref{fig:2rvariabilityhigh1} has a high variability with its cloned fragement.
+The first line of the cloned fragment shown in Figure~\ref{fig:2rvariabilityhigh1} has a high variability with its cloned fragement.
 However, the rest of this method does not have any variability.
@@
 
-Another example of high variability between clones, in which a valid subclone can be found, is displayed in figure \ref{fig:2rvariabilityhigh2}.
+Another example of high variability between clones, in which a valid subclone can be found, is displayed in Figure~\ref{fig:2rvariabilityhigh2}.
 In this case, one clone instance has such a high variability that it shouldn't be refactored.
@@
 \end{parcolumns}
-\caption{Cloned code fragments from figure \ref{fig:2rvariabilityhigh3} together with their equality arrays.}
+\caption{Cloned code fragments from Figure~\ref{fig:2rvariabilityhigh3} together with their equality arrays.}
 \label{fig:2rvariabilityhigh4}
@@
 
-In figure \ref{fig:2rvariabilityhigh4} we display clone classes and their (simplified) equality arrays.
+In Figure~\ref{fig:2rvariabilityhigh4} we display clone classes and their (simplified) equality arrays.
 We can convert this to a graph, using a similar process as the graph creation process used for clone detection.
 In this case, duplicate relations represent nodes of which their equality arrays are within the variability threshold.
-In figure \ref{fig:2rvariabilityhigh4} all relations are between equal equality arrays, but this does not always have to be the case.
+In Figure~\ref{fig:2rvariabilityhigh4} all relations are between equal equality arrays, but this does not always have to be the case.
 Large equality arrays, denoting statements that consist of many tokens, may have some variability and still be considered duplicates in this graph.
@@
   \includegraphics[width=1\columnwidth]{img/T2RGraph}
-  \caption{Graph representation of the code example displayed in figure \ref{fig:2rvariabilityhigh4}.}
+  \caption{Graph representation of the code example displayed in Figure~\ref{fig:2rvariabilityhigh4}.}
   \label{fig:clonerefactorprocess}
@@
 Similar to the clone detection process, we detect clones on the basis of the graph described in the previous section.
-The only difference is that, in this step, we do not remove clones that do not meet the thresholds (as explained in section \ref{sec:clonerefactorthresholds}).
+The only difference is that, in this step, we do not remove clones that do not meet the thresholds (as explained in Section~\ref{sec:clonerefactorthresholds}).
 This is because the next step, explained in the next section, could potentially expand the found clones and thus make clones that would currently invalid by the thresholds valid.
@@
 \end{parcolumns}
-\caption{Clone instances in figure \ref{fig:2rvariabilityhigh4} as determined .}
+\caption{Clone instances in Figure~\ref{fig:2rvariabilityhigh4} as determined .}
 \label{fig:2rvariabilityhigh5}
@@
 Where \textit{C} denotes the clone class and \textit{I} denotes the clone instance.
-The process by which these clones are found is equal to the clone detection process as described in section \ref{sec:detectingclones}.
-In this example, we see the four clones found on the graph of figure \ref{fig:clonerefactorprocess}.
+The process by which these clones are found is equal to the clone detection process as described in Section~\ref{sec:detectingclones}.
+In this example, we see the four clones found on the graph of Figure~\ref{fig:clonerefactorprocess}.
 Three of these clone classes have a two clone instances, each consisting of a single nodes.
@@
 
-As an example, consider the clone fragment in figure \ref{fig:trytoexpand}.
+As an example, consider the clone fragment in Figure~\ref{fig:trytoexpand}.
 In this example, we have 2 clone classes.
@@
 
-In the example in figure \ref{fig:trytoexpand} the largest instance has a volume of:
+In the example in Figure~\ref{fig:trytoexpand} the largest instance has a volume of:
 
@@
 We will include the previous node in the clone class and verify its variability threshold (node $N_2$).
-In this case, using the formulas shown in section \ref{sec:t2rcheckglobalthres}, we can check whether this clone class would be valid by the variability threshold:
+In this case, using the formulas shown in Section~\ref{sec:t2rcheckglobalthres}, we can check whether this clone class would be valid by the variability threshold:
 
@@
 Because of that, this other clone class is discarded.
-For the example code fragment in figure \ref{fig:trytoexpand} the resulting clone class is $\{N_1, N_2, N_3, N_4, N_5\}$.
+For the example code fragment in Figure~\ref{fig:trytoexpand} the resulting clone class is $\{N_1, N_2, N_3, N_4, N_5\}$.
 
 \subsection{Checking for type 3 opportunities} \label{sec:t3rclonerefactor}
-As described in section \ref{sec:type3r}, we define type 3R clones as gapped clones.
+As described in Section~\ref{sec:type3r}, we define type 3R clones as gapped clones.
 This means that two existing clones may have a gap of non-gapped clones.
@@
 
-In the example of figure \ref{fig:3ropportunities} we see two clone classes, which are separated by a single node. Using equation \ref{eq:t3rgap} we can calculate the size of the gap as follows:
+In the example of Figure~\ref{fig:3ropportunities} we see two clone classes, which are separated by a single node. Using equation \ref{eq:t3rgap} we can calculate the size of the gap as follows:
 
@@
 We detect such clones by checking that each node in the clone instance has a ancestor node that is a MethodDeclaration, but none of the nodes is a method declaration.
-We describe the procedure by with we recursively seek the parent nodes of a node in section \ref{sec:methodlevelcr}.
+We describe the procedure by with we recursively seek the parent nodes of a node in Section~\ref{sec:methodlevelcr}.
 
@@
     \item \textbf{Spans Part Of A Block}: This clone spans a part of a statement.
-    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of section \ref{sec:setupcontents}, the ``extract method'' refactoring technique cannot be applied.
+    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Section~\ref{sec:setupcontents}, the ``extract method'' refactoring technique cannot be applied.
     \item \textbf{Top-level Node Is Not A Statement}: The topmost node of a clone instance is not a statement.
@@
 Because of that, we took those categories out of the scope for our automated refactoring efforts.
-We further explain opportunities to refactor such clones outside the ``Can be extracted'' category in section \ref{sec:discussrefactorability}.
+We further explain opportunities to refactor such clones outside the ``Can be extracted'' category in Section~\ref{sec:discussrefactorability}.
 
@@
 However, if a single statement is only partially cloned, this might give issues with refactoring.
-An example of this is shown in figure \ref{fig:refactorabilitypartialblock}
+An example of this is shown in Figure~\ref{fig:refactorabilitypartialblock}
 
@@
 The ``Extract Method'' refactoring can only refactor code in the body of a method.
-We mapped the contents of clones in section \ref{sec:setuplocation}.
+We mapped the contents of clones in Section~\ref{sec:setuplocation}.
 Here we defined the ``Partial Method'' catagory as \textit{a clone that spans (a part of) the body of a method.
@@
 However, there are possibilities where a clone consists of something else than a statement as top level node.
-The most prominent example is when a clause is cloned (see section \ref{sec:astbackground} for examples of such concepts).
+The most prominent example is when a clause is cloned (see Section~\ref{sec:astbackground} for examples of such concepts).
 For instance, we cannot extract only the catch-clause of a try-statement to a new method.
@@
 We consider analyzing such refactoring methods future work.
-An example refactoring of clone instances that overlap within their clone class is displayed in figure \ref{fig:overlaprefactoring}.
+An example refactoring of clone instances that overlap within their clone class is displayed in Figure~\ref{fig:overlaprefactoring}.
 In this example one clone instance is found between line \ref{line:overlaprefactoring1} and \ref{line:overlaprefactoring4} and the other between \ref{line:overlaprefactoring2} and \ref{line:overlaprefactoring5}.
@@
 \subsubsection{Relation}
-For each of the identified clone relations (section \ref{sec:setuprelation}) we define a method of automatically refactoring clones in these categories.
+For each of the identified clone relations (Section~\ref{sec:setuprelation}) we define a method of automatically refactoring clones in these categories.
 The relation determines the location at which we place the newly created method.
@@
 \item \textbf{Tokens}: The number of tokens that the \textit{each clone instance of the clone class} spans. This concerns the size of a single clone instance before it was refactored.
-\item \textbf{Relation}: The relation category (section \ref{sec:setuprelation}) that this clone class belongs to.
-\item \textbf{Returns}: The category of what the extracted method returns (section \ref{sec:refreturn}).
+\item \textbf{Relation}: The relation category (Section~\ref{sec:setuprelation}) that this clone class belongs to.
+\item \textbf{Returns}: The category of what the extracted method returns (Section~\ref{sec:refreturn}).
 \item \textbf{Parameters}: The number of parameters the extracted method has.

### 2019-08-11 sections/conclusion.tex
Proper capitalization for some concepts

@@
 To assess an automated refactoring opportunity for complex methods, we should assess which parts of methods can be split to end up with parts of similar complexity.
-For this, our research can be used to assess whether a given piece of code can be extracted to a new method (see section \ref{sec:refactorability}).
+For this, our research can be used to assess whether a given piece of code can be extracted to a new method (see Section~\ref{sec:refactorability}).
 
@@
 \subsection{Type 4 clones}
-In section \ref{chap:backgroundclonetypes} we introduced the clone types that are used in literature.
+In Section~\ref{chap:backgroundclonetypes} we introduced the clone types that are used in literature.
 Of these clone types, we considered type 1, 2 and 3 for refactoring.

### 2019-08-11 sections/discussion.tex
Proper capitalization for some concepts

@@
 The design of these clone type definitions entails some decisions that have a large impact on the clones we considered for refactoring in this study.
-In this section we discuss our clone type definitions as proposed in section \ref{sec:rtypes}.
+In this section we discuss our clone type definitions as proposed in Section~\ref{sec:rtypes}.
 
@@
 If expressions have/return the same type, they can be extracted to a parameter and the corresponding expression can be passed as a parameter.
-An example of this is displayed in figure \ref{fig:samereturn}.
+An example of this is displayed in Figure~\ref{fig:samereturn}.
 The only thing to watch out for is method that have side effects.
@@
 \section{Clone Context Analysis}
-In section \ref{chap:contextsetup} we introduced the categories we defined for mapping the context of clones. In this section, we discuss this together with the related experiments.
+In Section~\ref{chap:contextsetup} we introduced the categories we defined for mapping the context of clones. In this section, we discuss this together with the related experiments.
 
 \subsection{Refactorability} \label{sec:discussrefactorability}
-In section \ref{sec:refactorability} we introduced to what extent clones can be refactored through method extraction.
+In Section~\ref{sec:refactorability} we introduced to what extent clones can be refactored through method extraction.
 Because we strived to get results fast, we excluded categories that could not not be directly refactored through method extraction.

### 2019-08-11 sections/research.tex
Ana
Proper capitalization for some concepts

@@
 \chapter{Defining refactoring-oriented clone types}\label{chap:clonetypes}
-In section \ref{chap:backgroundclonetypes} we introduced the four clone types as defined in literature.
+In Section~\ref{chap:backgroundclonetypes} we introduced the four clone types as defined in literature.
 These simple definitions are suitable for analysis of a codebase.
@@
 \section{Shortcomings of clone types}
-Clone types 1-3 (further explained in section \ref{chap:backgroundclonetypes}) allow reasoning about the duplication in a software system.
+Clone types 1-3 (further explained in Section~\ref{chap:backgroundclonetypes}) allow reasoning about the duplication in a software system.
 Clones by these definitions can relatively easily and efficiently be detected.
@@
 
-In the example in figure \ref{fig:type1}, we see a type 1 clone displaying two clone classes.
+In the example in Figure~\ref{fig:type1}, we see a type 1 clone displaying two clone classes.
 Defining an automatic way to refactor these clone classes is nearly impossible, as both cloned fragments describe different functional concepts.
@@
 
-The example in figure \ref{fig:type2} shows a type 2 clone class.
+The example in Figure~\ref{fig:type2} shows a type 2 clone class.
 Both methods are, except for their matching structure, completely different in functionality.
@@
 \subsection{Type 1R clones} \label{sec:type1r}
-To solve the issues identified in section \ref{sec:type1}, we introduce an alternative definition: cloned fragments have to be both textually \textit{and} functionally equal.
+To solve the issues identified in Section~\ref{sec:type1}, we introduce an alternative definition: cloned fragments have to be both textually \textit{and} functionally equal.
 Like type 1 clones, type 1R clones do not consider comments and whitespace.
@@
 If, in different code fragments, we use variables with the same name but different types, the code can be functionally unequal but still textually equal.
-As an example, see the code in figure \ref{fig:type2variables}.
+As an example, see the code in Figure~\ref{fig:type2variables}.
 
@@
 
-The body of both methods in figure \ref{fig:type2variables} is equal. However, their functionality is not. The first method adds two numbers together and the other concatenates an integer to a String.
+The body of both methods in Figure~\ref{fig:type2variables} is equal. However, their functionality is not. The first method adds two numbers together and the other concatenates an integer to a String.
 
@@
 For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
-This could render two methods that have an entirely different functionality as clones (as shown in figure \ref{fig:type2} previously).
+This could render two methods that have an entirely different functionality as clones (as shown in Figure~\ref{fig:type2} previously).
 
@@
 When many expressions vary between cloned the refactored method might require many additional arguments.
-Because of that, we constrain this variability by a threshold, which is explained in more detail in section \ref{sec:variabilitythreshold}.%to limit the negative effect on system design of variability in these expressions after refactoring.
+Because of that, we constrain this variability by a threshold, which is explained in more detail in Section~\ref{sec:variabilitythreshold}.%to limit the negative effect on system design of variability in these expressions after refactoring.
 
@@
 
-The example in figure \ref{fig:type2variablerefactoringwithtradeoff} shows the same example as figure \ref{fig:type2variablerefactoringnotradeoff}, however this time there is a tradeoff.
+The example in Figure~\ref{fig:type2variablerefactoringwithtradeoff} shows the same example as Figure~\ref{fig:type2variablerefactoringnotradeoff}, however this time there is a tradeoff.
 The same variables are used, but they are not used in the same places in cloned fragments.
@@
 Because of that, we require an extra argument.
-Because of this, this variability falls under the threshold described in section \label{sec:variabilitythreshold}, whereas the example in figure \ref{fig:type2variablerefactoringnotradeoff} does not.
+Because of this, this variability falls under the threshold described in section \label{sec:variabilitythreshold}, whereas the example in Figure~\ref{fig:type2variablerefactoringnotradeoff} does not.
 
@@
 
-Consider the example in figure \ref{fig:type2literal}.
+Consider the example in Figure~\ref{fig:type2literal}.
 In this example, the two methods have two literals that differ between them.
@@
 As with type 1R clones, these types are compared using their fully qualified identifiers.
-An example of this is shown in figure \ref{fig:type2method}.
+An example of this is shown in Figure~\ref{fig:type2method}.
 In this example, we have two methods (\texttt{System.out.println} and \texttt{myFancyPrint}).
@@
 Because methods calls can have a different structure, type 2R clones can be structurally slightly different.
-The example as shown in figure \ref{fig:type2method} can be a type 2R clone (dependent on the thresholds used), but is not a type 2 clone.
+The example as shown in Figure~\ref{fig:type2method} can be a type 2R clone (dependent on the thresholds used), but is not a type 2 clone.
 
@@
 When looking at how we can refactor a statement that is not included by one clone instance but is in another, we find that we require a conditional block to make up for the difference in statements.
-See figure \ref{fig:type3} for an example of such a clone.
+See Figure~\ref{fig:type3} for an example of such a clone.
 
@@
 
-In figure \ref{fig:type3} a single statement is added.
+In Figure~\ref{fig:type3} a single statement is added.
 This statement is found in between cloned lines.
@@
   \item \textbf{The gap may not span a partial block.} To make sure that the T3R clone can be refactored, we do not allow the gap to span a part of a block.
-This is further explained in section \ref{sec:t3rpartialblock}.
+This is further explained in Section~\ref{sec:t3rpartialblock}.
 \end{itemize}
@@
 
-As an example, consider the code fragment in figure \ref{fig:gappedclones}.
+As an example, consider the code fragment in Figure~\ref{fig:gappedclones}.
 
@@
 
-When applying this formula with the example given in figure \ref{fig:gappedclones}, we get a gap size of 50\%:
+When applying this formula with the example given in Figure~\ref{fig:gappedclones}, we get a gap size of 50\%:
 
@@
 Apart from this threshold, the gap in between clones may not span over different blocks.
-Look at figure \ref{fig:type3invalid} for an example of this.
+Look at Figure~\ref{fig:type3invalid} for an example of this.
 We cannot refactor both statements into a single conditional block.
@@
 \begin{equation}\label{eq:typerelation}
-\text{Cloned nodes} = T1R \subseteq T2R \subseteq T3R
+Cloned nodes T1R \subseteq Cloned nodes T2R \subseteq T3R
 \end{equation}

### 2019-08-11 sections/results.tex
Proper capitalization for some concepts

@@
 \todo{update these results}
-In section \ref{sec:setuprelation} we introduced our experiments regarding relations between clones. Table~\ref{table:relations} contains our results regarding the relations between clone instances.
+In Section~\ref{sec:setuprelation} we introduced our experiments regarding relations between clones. Table~\ref{table:relations} contains our results regarding the relations between clone instances.
 
@@
 \todo{update these results}
-Measuring the clone locations categories defined in section \ref{sec:setuplocation} yields the results displayed in Table \ref{table:contents}.
+Measuring the clone locations categories defined in Section~\ref{sec:setuplocation} yields the results displayed in Table \ref{table:contents}.
 
@@
 \todo{update these results}
-Measuring the clone contents categories defined in section \ref{sec:setupcontents} yields the results displayed in Table \ref{table:contents}.
+Measuring the clone contents categories defined in Section~\ref{sec:setupcontents} yields the results displayed in Table \ref{table:contents}.
 
@@
 \todo{update these results}
-In section \ref{sec:refactorabilitysetup} we define categories regarding the extent to which clones can be refactored through method extraction.
+In Section~\ref{sec:refactorabilitysetup} we define categories regarding the extent to which clones can be refactored through method extraction.
 Our results are displayed in Table \ref{table:refactorability}.

### 2019-08-11 sections/experimentalsetup.tex
Corpus
Corpus

@@
 For our purposes, we have further filtered this corpus to get a controlled set of projects for our experiments.
-In this section, we explain the steps we took to prepare the corpus and the rationale behind those steps.
+In this section, we explain the steps we took to prepare the corpus\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} and the rationale behind those steps.
 
-\subsection{Project dependencies}
-As explained
+\subsection{Filtering Maven projects}
+As explained in Section~\ref{chap:challenge}, CloneRefactor requires all the libraries a software project is dependent on in order to perform its clone analysis.
+As these are not included in the used corpus \cite{githubCorpus2013}, we decided to limit our scope to a single build automation system.
+We chose Maven, as it is one of the most used build automation systems for Java projects.
+Maven uses a file, named \texttt{pom.xml}, to describe a projects' dependencies.
+As no \texttt{pom.xml} files are included in the corpus, we cloned the latest version of each project in the corpus.
+We then removed each project that has no \texttt{pom.xml} file (which indicates that those do not use the Maven build automation system).
 
-As indicated in chapter \ref{chap:challenge} CloneRefactor requires all libraries of software projects we test.
-As these are not included in the used corpus \cite{githubCorpus2013}, we decided to filter the corpus to only include Maven projects.
-Maven is a build automation tool used primarily for Java, and works on the basis of an \texttt{pom.xml} file to describe the projects' dependencies.
-As no \texttt{pom.xml} files are included in the corpus, we cloned the latest version of each project in the corpus.
-We then removed each project that has no \texttt{pom.xml} file.
-As a final step, we collected all dependencies for each project by using the \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib} Maven command, and removed each project for which not all dependencies were available (due to non-Maven dependencies being used or unsatisfiable dependencies being referenced in the \texttt{pom.xml} file).
+Because we cloned the projects (and do not use the sources provided in the corpus), they still included generated source code.
+Because we do not want to analyze generated Java files, we decided to further filter the corpus to only include projects with a conventional structure.
+For Maven, projects are recommended to put their production code in the folder structure \texttt{src/main/java}.
+We omitted Maven projects that do not adhere to this convention.
 
-Some general data regarding this corpus is displayed in Table \ref{table:general}.
+\subsection{Gathering Dependencies}
+As a next step, we collect all dependencies of the downloaded software projects.
+Maven uses the following command to automate this process: \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib}.
+This process can fail if external dependencies are no longer available.
+We removed such projects for which we could not obtain all dependencies.
 
-\begin{table}[H]
-  \begin{center}
-  \caption{General results for GitHub Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
-  \medskip
-\begin{tabular}{|l|l|}
-\hline
-Amount of projects                                                                                      & 1,361      \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\whitespace, comments and newlines.)\end{tabular} & 1,414,996  \\ \hline
-Amount of statements/declarations                                                                       & 1,212,189  \\ \hline
-\begin{tabular}[c]{@{}l@{}}Amount of tokens (excluding\\whitespace, comments and newlines.)\end{tabular} & 11,643,194 \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
+\subsection{Building an AST of all Java files}
+To verify the correctness of all Java files in the projects, we used JavaParser \cite{tomassetti2017javaparser} to create an AST of every Java file in the \texttt{src/main/java} folder of the software projects.
+A very small set of projects had syntactical errors, which we removed from the corpus.
+
+\subsection{Inspecting outliers}
+We ran CloneRefactor over every project in the corpus and inspected the output for each project.
+Some projects gave unusual high numbers of projects of a certain size, which we manually inspected.
+Often these projects contained generated source files.
+We removed these projects from the corpus.
+
+The result is a set of 674 Java projects that we use for all our experiments.

### 2019-08-11 sections/results.tex
Corpus
Corpus

@@
 \section{Clone types}\label{sec:clonetypeexperiments}
-In this section we display the differences between clone type 1-3~\cite{roy2007survey} and type 1R-3R as proposed in chapter \ref{chap:clonetypes}.
-When running our clone detection script over the corpus, we get the results displayed in Fig.~\ref{fig:typeres}.
+In this section we display the differences between clone type 1-3~\cite{roy2007survey} and type 1R-3R as proposed in Chapter \ref{chap:clonetypes}.
+When running our clone detection script over the corpus, we get the results displayed in Figure~\ref{fig:typeres}.
 
@@
 Although this data is partly dependent on our implementation of the clone types, there is a notable difference between the refactoring-oriented clone types and the literature clone types.
-The reason for this is further explained in section~\ref{chap:challenge}.
+The reason for this is further explained in Section~\ref{chap:challenge}.
 

### 2019-08-12 sections/related_work.tex
working on various things

@@
 \chapter{Related work} \label{ch:related_work}
-\todo{Rewrite this part and add a lot of content}
 The Duplicated Code Refactoring Advisor (DCRA) looks into refactoring opportunities for clone pairs~\cite{fontana2012duplicated, fontana2015duplicated}.

### 2019-08-13 icse/paper.tex
++
Stuff

@@
 \section{CloneRefactor}
+% NEED TO EXPLAIN WHY DO CURRENT DETECTION TOOLS NOT SUFFICE
 The tool: Detect Clones, Map Context, Refactor.
@@
 \subsubsection{Relation}
+The rationale for our categories regarding clone relations.
+
 \subsubsection{Location}
+The rationale for our categories regarding clone locations.
+
 \subsubsection{Contents}
+The rationale for our categories regarding clone contents.
 

### 2019-08-13 sections/background.tex

@@
 \cite{jiang2007deckard}.
-We created a summary of these concepts, which can be found in table \ref{tab:clone-terminology}.
+We created a summary of these concepts, which can be found in Table~\ref{tab:clone-terminology}.
 
@@
 \subsection{Example}
-This section gives an example to make the terminology of table \ref{tab:clone-terminology} more concrete.
-The code fragment in figure \ref{fig:cloneclasses} shows two clone classes.
+This section gives an example to make the terminology of Table~\ref{tab:clone-terminology} more concrete.
+The code fragment in Figure~\ref{fig:cloneclasses} shows two clone classes.
 One of the clone classes consists of two clone instances and has three nodes per instance.
@@
 
-This example can be represented as a tree structure using the concepts from table \ref{tab:clone-terminology}. This tree structure is displayed in figure \ref{fig:terminologyexample}.
+This example can be represented as a tree structure using the concepts from Table~\ref{tab:clone-terminology}. This tree structure is displayed in Figure~\ref{fig:terminologyexample}.
 
@@
   \includegraphics[width=1\columnwidth]{img/TerminologyExample}
-  \caption{Representation of figure \ref{fig:cloneclasses} using the terminology introduced in table \ref{tab:clone-terminology}}
+  \caption{Representation of Figure~\ref{fig:cloneclasses} using the terminology introduced in Table~\ref{tab:clone-terminology}}
   \label{fig:terminologyexample}

### 2019-08-13 sections/clonerefactor.tex

@@
 We bridged a gap between clone detection and refactoring by designing a tool that can detect clones by our refactoring-oriented clone types (chapter \ref{chap:clonetypes}).
-This tool, named CloneRefactor, performs a comprehensive context analysis on the detected clones.
+This tool, named CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}, performs a comprehensive context analysis on the detected clones.
 Based on this this context, CloneRefactor can automatically refactor a subset of the detected clones by applying transformations to the source code of the analyzed software project(s).

### 2019-08-13 sections/discussion.tex

@@
 \chapter{Discussion}
-\todo{TODO}
 \label{ch:discussion}
 
-In this chapter, we discuss the results of our experiment(s) on ...
-
-\begin{finding}
-	Highlight like this an important finding of your analysis of the results.
-	\label{find:important1}
-\end{finding}
-
-Refer to Finding~\ref{find:important1}.
+In this chapter, we discuss the results of our research and experiments.
 
@@
 
-\subsubsection{Type 2R clones}
+\subsection{Type 2R clones}
 With type 2R clones we allow variability in some identifiers and literals such that the code can and should still be refactored.
@@
 \end{figure}
+
+\section{CloneRefactor}
+In this section we discuss our decisions for the design of our CloneRefactor tool.
+
+\subsection{Clone Detection}
+For CloneRefactor we chose to design a novel method of detecting clones, rather than using an existing clone detection technique or tool.

### 2019-08-13 sections/discussion.tex
Survey

@@
 For CloneRefactor we chose to design a novel method of detecting clones, rather than using an existing clone detection technique or tool.
+
+\section{Experimental setup}
+
+\subsection{Java Corpus}
+
+\subsection{Survey}
+To limit the scope of this research, we chose not to include human subjects in this study.
+However, we think that the results of this study could be strengthened by performing a survey on software engineering practisioners.
+We have determined a set of refactoring opportunities only based on literature input and quantitive analysis.
+It would be valuable to have a control group rate the refactorings performed by CloneRefactor, as an extra form of input regarding the quality of the code transformation that CloneRefactor performs.

### 2019-08-13 sections/conclusion.tex
Move java corpus from future work

@@
 
-\subsection{Running our experiments with a different set of software projects}
-In our experiments we chose to use a GitHub based software corpus.
-This corpus contains a diversity of projects of many different sizes.
-We noticed that there is a lot of difference in the quality of these software systems: some systems had a lot of duplication and some did not have any duplication.
-
-We think that there is value in running our experiments with different corpuses.
-We would, for instance, be interested in the results for industrial projects instead of open source software systems.
-We are curious to see whether the distributions are comparable, or whether they show large differences.
-
-Furthermore, we think that there is value in running our experiments with a set of larger sized and more professionally developed open source systems.
-We noticed that in our corpus there were a lot of projects that have only few commits and contributors.
-We think it would be valuable to for instance perform our experiments with a set of larger open source systems, like the systems in the Apache ecosystem.
-
 \subsection{Automatically refactoring code that is duplicated with a library}

### 2019-08-13 sections/discussion.tex
Move java corpus from future work

@@
 \subsection{Java Corpus}
+In our experiments we chose to use a GitHub based software corpus.
+This corpus contains a diversity of projects of many different sizes.
+We noticed that there is a lot of difference in the quality of these software systems: some systems had a lot of duplication and some did not have any duplication.
+Furthermore, it took an extensive filtering process to remove all files not suitable for application in this research (like generated files).
+
+We think that there is value in running our experiments with different corpuses.
+We would, for instance, be interested in the results for industrial projects instead of open source software systems.
+We are curious to see whether the distributions are comparable, or whether they show large differences.
+
+Furthermore, we think that there is value in running our experiments with a set of larger sized and more professionally developed open source systems.
+We noticed that in our corpus there were a lot of projects that have only few commits and contributors.
+We think it would be valuable to, for instance, perform our experiments with a set of larger open source systems, like the systems in the Apache ecosystem.
 

### 2019-08-13 sections/discussion.tex
Clone detection discussion

@@
 \subsection{Clone Detection}
-For CloneRefactor we chose to design a novel method of detecting clones, rather than using an existing clone detection technique or tool.
+For CloneRefactor we chose to design a novel method of detecting clones, rather than using an existing clone detection technique or tool. Our rationale is as follows:
+\begin{itemize}
+  \item We perform comprehensive analysis on the source code which requires us to use an AST-based clone detection method.
+  \item We perform dependency graph analysis, which requires us to resolve symbols in the source code.
+  \item None of the existing clone detection methods implement all criteria required to build such a system.
+\end{itemize}
+By building a graph that maps relations between nodes in the AST, we can find clones in an efficient manner, allowing to perform a comprehensive analysis of large systems.
+This method has worked well for our purposes.
+
+The main limitation we encountered is the memory required to build the clone graph.
+As we load the entire graph into memory before starting the clone detection procedure, this can cause issues on systems with low available memory.
+For a system consisting of 1.000.000 nodes, the clone graph requires about 4GB of RAM.
+For our corpus, there were no larger systems, so this was not a big issue.
+However, for industry projects our tool might require optimization.
+
+\subsection{Context Analysis}
+In this study we identified categories for three \todo{todo}
 
 \section{Experimental setup}
+In this section we discuss the setup of our experiments. We discuss alternative setups that could lead to other perspectives on the problem addressed.
 

### 2019-08-13 sections/conclusion.tex
Metrics & Context Analysis

@@
 \section{Future work} \label{sec:future_work}
-\todo{Move part of future work to discussion}
 This study presents a foundation for research in a largely unexplored field of studies: analyzing maintainability through automated refactoring.

### 2019-08-13 sections/discussion.tex
Metrics & Context Analysis

@@
 \label{ch:discussion}
+%Interpretations: what do the results mean?
+%Implications: why do the results matter?
+%Limitations: what can’t the results tell us?
+%Recommendations: what practical actions or scientific studies should follow?
 
@@
 \subsection{Context Analysis}
-In this study we identified categories for three \todo{todo}
+In this study we identified categories for three properties of clones: relation, location and contents.
+%Mapping the location and contents was mainly to find out what the best method of refactoring is to refactor most clones.
+We chose a set of relations that indicate different refactoring opportunities.
+However, as our CloneRefactor tool only analyses Java source code, we we biased towards categories that are often found in Java source code.
+For other languages, other categories might be valuable to analyze to find suitable categories for that programming language.
+
+\subsection{Refactoring}
+
+\subsubsection{Metrics}
+For this study we chose to focus on a set of four metrics to measure maintainability: method size, duplication, method parameters and cyclomatic complexity.
+These metrics give an indication of the impact of the refactoring, but do not give a complete overview.
+There are many more metrics that could be considered to measure the maintainability impact on the system.
+An example of such a metric is ``coupling'', which focuses on the amount of incoming calls into a method or class and what modules these calls come from.
+This metric is also influenced by the transformations we applied and might deliver valuable insights in the quality of the refactoring.
+
+In general, considering other metrics can result in a more reliable measure of the increase or decrease of maintainability after applying a specific refactoring.
 

### 2019-08-13 icse/paper.tex
Paper

@@
 \section{Defining refactorable clones}
-Instead of defining clone types, I just define how we can ensure that clones can be refactored.
+% Instead of defining clone types, I just define how we can ensure that clones can be refactored.
 I do not plan to differentiate between T1R, T2R and T3R here, because I think it makes the paper confusing.
-
-To be honest, I'm not even sure how relevant it is to name the literature clone types.
+% To be honest, I'm not even sure how relevant it is to name the literature clone types.
 Maybe not focus on their shortcomings, but just start from the core (sourcecode) and define how we can get to refactorable clones.
+In literature, several clone type definitions have been used to argue about duplication in source code \cite{roy2007survey}.
+In this section, we discuss how we can define clones such that they can be refactored without side effects on the source code.
 
 \subsection{Ensuring Equality}
-Explain type 1, why it is not always refactorable, solution
+% Explain type 1, why it is not always refactorable, solution
+Most modern clone detection tools detect clones by comparing the code textually together with the ommission of certain tokens \cite{roy2009comparison, svajlenko2014evaluating}.
+Clones detected by such means may not always be suitable for refactoring, because textua comparison fails to take into account the context of certain symbols in the code.
+Information that gets lost in textual comparison is as follows:
+\begin{itemize}
+  \item \textbf{The type of variable references}: Equally named variables may be of different types between code fragments.
+  \item \textbf{Contextual information of type references}: Equally named types may refer to different
+  \item \textbf{What method method reference}
+\end{itemize}
+To detect clones that can be refactored, we propose to:
+\begin{itemize}
+  \item Compare variable references not only by their name, but also by their type.
+  \item Compare types by their fully qualified identifier (FQI). The FQI of a type describes the full path to the declaration of the type.
+  \item Compare method references by their fully qualified signature (FQS). The FQS
+\end{itemize}
 

### 2019-08-13 icse/paper.tex
Abstract

@@
 \begin{abstract}
-Coming up!
+Duplication in source code is often seen as one of the most harmful types of technical debt, because it increases the size of the codebase and creates implicit dependencies between fragments of code.
+To remove such antipatterns, a developer should refactor the codebase.
+There are many tools that assist in this process.
+However, these are limited to measuring the size of clones to determine whether they should be considered.
+Because of this, the output of such tools is often of limited assistance to the developer in the refactoring process.
+
+We propose method and tool for the detection and automated refactoring of clones.
+We use this tool on a corpus of open source Java systems.
+We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the systems.
+These metrics are system size, cyclomatic complexity, duplication and number of method parameters.
+On basis of these results, we decide which clones improve system design and thus should be refactored.
+
+We identified a set of four factors that influence the maintainability impact of clones.
+The first is the size of the clone.
+The second is the relation between the code fragments in a clone.
+The third is whether the clone fragments create, modify or return data.
+The fourth is the amount of data that cloned fragments use.
+By using these four factors, we can suggest only clones that will improve maintainability when refactored and prioritize them accordingly.
 \end{abstract}
@@
 \section{Introduction}
+Duplication in source code is often seen as one of the most harmful types of technical debt, because it increases the size of the codebase and create implicit dependencies between fragments of code \cite{ostberg2014automatically}.
+Bruntink et al.~\cite{bruntink2005use} show that code clones can contribute up to 25\% of the code size.
+
+Current code clone detection detection techniques base their thresholds and prioritization on a limited set of metrics.
+Often, clone detection techniques are limited to measuring the size of clones to determine whether they should be considered.
+Because of this, the output of clone detection tools is often of limited assistance to the developer in the refactoring process.
 
 \section{Background}
+This study researches an intersection of code clone and refactoring research.
 
@@
 \subsection{Refactoring techniques}
+In this section, we describe
 Extract method, move method.
@@
 Clones detected by such means may not always be suitable for refactoring, because textua comparison fails to take into account the context of certain symbols in the code.
-Information that gets lost in textual comparison is as follows:
-\begin{itemize}
-  \item \textbf{The type of variable references}: Equally named variables may be of different types between code fragments.
-  \item \textbf{Contextual information of type references}: Equally named types may refer to different
-  \item \textbf{What method method reference}
-\end{itemize}
+Information that gets lost in textual comparison is the referenced declaration for type, variable and method references.
+Equally named type, variable and method references may refer to different declarations with a different implementation.
+Such clones can be harder to refactor, if benificial at all.
+
 To detect clones that can be refactored, we propose to:
@@
   \item Compare variable references not only by their name, but also by their type.
-  \item Compare types by their fully qualified identifier (FQI). The FQI of a type describes the full path to the declaration of the type.
-  \item Compare method references by their fully qualified signature (FQS). The FQS
+  \item Compare referenced types by their fully qualified identifier (FQI). The FQI of a type reference describes the full path to where it is declared.
+  \item Compare method references by their fully qualified signature (FQS). The FQS of a method reference describes the full path to where it is declared, plus the FQI of each of its parameters.
 \end{itemize}
 
+% Do we want an example here?
+
 \subsection{Allowing variability in a controlled set of expressions}
-Explain type 2, why it is not always refactorable, solution
+%Explain type 2, why it is not always refactorable, solution
+Often, fragments in source code do not match exactly.
+Often when developers duplicate fragments of code, they modify the duplicated block to fit its new location and purpose.
+To detect duplicate fragments with minor variance, we looked into in what expressions we can allow variability while still being refactorable.
 
@@
 \section*{Acknowledgment}
-:-)
+We would like to thank the Software Improvement Group for their continuous support in this project.
+In particular, we would like to thank Xander Schrijen for his invaluable input in this research.
+Furthermore, we would like to thank Sander Meester for his proofreading efforts and feedback.
 

### 2019-08-13 icse/paper.tex
Is this better?

@@
 There are many tools that assist in this process.
-However, these are limited to measuring the size of clones to determine whether they should be considered.
-Because of this, the output of such tools is often of limited assistance to the developer in the refactoring process.
+The thresholds and prioritization of the clones detected by such tools can be improved by considering the maintainability of the codebase after a detected clone would be refactored.
 
 We propose method and tool for the detection and automated refactoring of clones.
-We use this tool on a corpus of open source Java systems.
 We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the systems.
@@
 On basis of these results, we decide which clones improve system design and thus should be refactored.
-
 We identified a set of four factors that influence the maintainability impact of clones.
@@
 By using these four factors, we can suggest only clones that will improve maintainability when refactored and prioritize them accordingly.
+
+Given these maintainability influencing factors and their effect on the source code, we measure their impact over a large corpus of open source Java projects.
+This results in a set of thresholds by which clones can be found that should be refactored to improve system maintainability.
 \end{abstract}

### 2019-08-13 icse/paper.tex
Refactoring techniques

@@
 
-We propose method and tool for the detection and automated refactoring of clones.
+In this study, we define a technique to detect clones such that they can be refactored.
+We propose a tool to detect such clones and automatically refactor a subset of them.
 We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the systems.
@@
 
+In this study, we define a technique to detect clones such that they can be refactored.
+We evaluate the context of clones to determine refactoring techniques are required to refactor clones in a specific context.
+We propose a tool for the automated refactoring of a subset of the detected clones, by extracting a new method out of duplicated code.
+
 \section{Background}
@@
 \subsection{Refactoring techniques}
-In this section, we describe
-Extract method, move method.
+In this section, we describe refactoring techniques that are relevant to refactoring code clones.
+
+\subsubsection{Extract Method}
+The most used technique to refactor duplicate code is ``Extract Method'' \cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
+Several studies have already concluded that most duplication in source code is found in the body of methods \cite{lozano2007evaluating, white2016deep, bergman2004ethnographic}.
+The ``Extract Method'' technique moves functionality in method bodies to a new method.
+To reduce duplication, we extract the contents of a single clone instance to a new method and replace all clone instances by a call to this method.
+
+\subsubsection{Move Method}
+Often, ``Extract Method'' alone is not enough to refactor clones.
+This is because the extracted method has to be moved to a location that is accessible by all clone instances.
+To do this, we apply the ``Move Method'' refactoring technique \cite{fowler2018refactoring}.
+In object-oriented programming languages, we often move methods up in the inheritance structure of classes, also called ``Pull Up Method'' \cite{fowler2018refactoring}.
 

### 2019-08-14 icse/paper.tex
stuff

@@
 \usepackage{xcolor}
+\usepackage{color}
+\usepackage{listings}
+\usepackage{parcolumns}
+
+\definecolor{pblue}{rgb}{0.13,0.13,1}
+\definecolor{pgreen}{rgb}{0,0.5,0}
+\definecolor{pred}{rgb}{0.9,0,0}
+\definecolor{pgrey}{rgb}{0.46,0.45,0.48}
+
+\lstset{language=Java,
+  showspaces=false,
+  showtabs=false,
+  breaklines=true,
+  showstringspaces=false,
+  breakatwhitespace=true,
+  commentstyle=\color{pgreen},
+  keywordstyle=\color{pblue},
+  numbers = left,
+  stringstyle=\color{pred},
+  basicstyle=\ttfamily,
+  moredelim=[il][\textcolor{pgrey}]{$$},
+  moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%}
+}
+
+\definecolor{lightyellow}{HTML}{fffdcc}
+\definecolor{doublelightyellow}{HTML}{fffa9c}
+\definecolor{lightgreen}{HTML}{dcffd4}
+\definecolor{lightblue}{HTML}{e0ffff}
+\definecolor{lightred}{HTML}{ffe0e0}
+\definecolor{lightpink}{HTML}{ffe0ff}
+\definecolor{lightorange}{HTML}{ffede0}
+\definecolor{lightpurple}{HTML}{f0e0ff}
+\newcommand{\highlightYellow}{\makebox[0pt][l]{\color{lightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightGreen}{\makebox[0pt][l]{\color{lightgreen}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightBlue}{\makebox[0pt][l]{\color{lightblue}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightRed}{\makebox[0pt][l]{\color{lightred}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightPink}{\makebox[0pt][l]{\color{lightpink}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightOrange}{\makebox[0pt][l]{\color{lightorange}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightPurple}{\makebox[0pt][l]{\color{lightpurple}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightDarkyellow}{\makebox[0pt][l]{\color{doublelightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
+
+\lstnewenvironment{javacode}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small,#1}}{}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-In this study, we define a technique to detect clones such that they can be refactored.
+In this study, we define clones that can be refactored.
 We propose a tool to detect such clones and automatically refactor a subset of them.
@@
 On basis of these results, we decide which clones improve system design and thus should be refactored.
-We identified a set of four factors that influence the maintainability impact of clones.
+%We identified a set of four factors that influence the maintainability impact of clones.
 The first is the size of the clone.
@@
 \section{Background}
-This study researches an intersection of code clone and refactoring research.
+This study researches an intersection of code clone and refactoring research. In this background section, we will explain the required background knowledge for terms used throughout this study.
 
 \subsection{Code clone terminology}
-Clone class collection, clone class, clone instance, cloned node, token.
+In this study we use two concepts used to argue about code clones \cite{roy2007survey}:
+\textbf{Clone instance}: A single cloned fragment.
+\textbf{Clone class}: A set of similar clone instances.
 
-\subsection{Code clone definitions}
-Quick overview of clone type definitions
+%\subsection{Code clone definitions} Optional -> may do this if it adds something to the story
+%Quick overview of clone type definitions
 
@@
 %Explain type 2, why it is not always refactorable, solution
-Often, fragments in source code do not match exactly.
+Often, duplication fragments in source code do not match exactly \cite{kodhai2013method}.
 Often when developers duplicate fragments of code, they modify the duplicated block to fit its new location and purpose.
 To detect duplicate fragments with minor variance, we looked into in what expressions we can allow variability while still being refactorable.
+
+We define the following expressions as refactorable when varied:
+\begin{itemize}
+  \item \textbf{Literals}: Only if all varying literals in a clone class have the same type.
+  \item \textbf{Variables}: Only if all varying variables in a clone class have the same type.
+  \item \textbf{Method references}: Only if the return value of referenced method match (or are not used).
+\end{itemize}
+Often when allowing such variance, tradeoffs come into play. For instance, variance in literals may require the introduction of a parameter, increasing the required effort to comprehend the code.
+
+\begin{figure}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+void doABC(){
+	doA();
+	doB("abc");
+	doC();
+}
+
+void doDEF(){
+  doA();
+  doB("def");
+  doC();
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+void doABC(){
+	do("abc");
+}
+
+void doDEF(){
+	do(s, "def");
+}
+
+void doThis(String s){
+  doA();
+  doB(s);
+  doC();
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Literal variability refactored.}
+\label{fig:type2literal}
+\end{figure}
 

### 2019-08-14 icse/paper.tex
Whatever

--- 2019-08-13 icse/paper.tex
@@
 \usepackage{xcolor}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 %Explain type 2, why it is not always refactorable, solution
-Often, fragments in source code do not match exactly.
+Often, duplication fragments in source code do not match exactly \cite{kodhai2013method}.
 Often when developers duplicate fragments of code, they modify the duplicated block to fit its new location and purpose.
 To detect duplicate fragments with minor variance, we looked into in what expressions we can allow variability while still being refactorable.
+
+We define the following expressions as refactorable when varied:
+\begin{itemize}
+  \item \textbf{Literals}: Only if all varying literals in a clone class have the same type.
+  \item \textbf{Variables}: Only if all varying variables in a clone class have the same type.
+  \item \textbf{Method references}: Only if the return value of referenced method match (or are not used).
+\end{itemize}
+Often when allowing such variance, tradeoffs come into play.
+For instance, variance in literals may require the introduction of a parameter to an extracted method if the ``Extract Method'' refactoring method is used, increasing the required effort to comprehend the code.
 

### 2019-08-14 icse/paper.tex
T3R. CloneRefactor + Image

@@
 \usepackage{xcolor}
+\usepackage{float}
 
@@
 
-\subsection{Allowing variability in a controlled set of expressions}
+\subsection{Allowing variability in a controlled set of expressions} \label{sec:t2r}
 %Explain type 2, why it is not always refactorable, solution
@@
 \subsection{Gapped clones}
-Explain type 3, why it is not always refactorable, solution
+%Explain type 3, why it is not always refactorable, solution
+Sometimes, when fragments are duplicated, a statement in inserted or changed severely for the code to fit its new context.
+When dealing with such a situation, there are several opportunities to refactor so-called ``gapped clones''.
+``Gapped clones'' are two clone instances separated by a ``gap'' of non-cloned statement(s).
+We define the following methods to refactor such clones:
+\begin{itemize}
+  \item We wrap the difference in statements in a conditionally executed block, one path for each different (group of) statement(s).
+  \item We use a lambda function to pass the difference in statements from each location of the clone.
+\end{itemize}
+Again, a tradeoff is at play, as these solutions increase the complexity in favor of removing a clone.
 
@@
 % NEED TO EXPLAIN WHY DO CURRENT DETECTION TOOLS NOT SUFFICE
-The tool: Detect Clones, Map Context, Refactor.
+% The tool: Detect Clones, Map Context, Refactor.
+To automate the process of refactoring clones, we propose a tool named CloneRefactor.
+This tool goes through a 3-step process in order to refactor clones.
+This process is displayed in figure \ref{fig:clonerefactorflow}.
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/flow}
+  \caption{Simple flow diagram of CloneRefactor.}
+  \label{fig:clonerefactorflow}
+\end{figure}
+In this section, we explain each of these steps.
 
 \subsection{Clone Detection}
-Detecting refactorable clones, (clone graph?? do I want to explain my exact methods?)
+% Detecting refactorable clones, (clone graph?? do I want to explain my exact methods?)
+We detect clones, allowing any variability between indicated expressions (see Sec.~\ref{sec:t2r}).
 

### 2019-08-14 icse/paper.tex
Clone Detection  + Relation

@@
 
-\subsection{Gapped clones}
+\subsection{Gapped clones} \label{sec:t3r}
 %Explain type 3, why it is not always refactorable, solution
@@
 % Detecting refactorable clones, (clone graph?? do I want to explain my exact methods?)
-We detect clones, allowing any variability between indicated expressions (see Sec.~\ref{sec:t2r}).
+We use an AST-based method to detect clones.
+Clones are detected on a statement level: only full statements are considered as clones.
+In this process, we limit the variability between indicated expressions (see Sec.~\ref{sec:t2r}) by a threshold.
+This threshold is the percentage of different expressions against the total number of expressions in the source code:
+\begin{equation}\label{eq:type2r}
+\text{Variability}=\frac{\text{Different expressions}}{\text{Total expressions}}*100
+\end{equation}
+
+After all clones have been detected, CloneRefactor determines whether clone classes can be merged into gapped clones (see Sec.~\ref{sec:t3r}).
+The maximum size of the gap is limited by a threshold.
+This threshold is the percentage of (not-cloned) statements in the gap against the sum of statements in both clones surrounding it.
+Unlike the expression variability threshold, this threshold can exceed 100\%:
+\begin{equation}\label{eq:type3r}
+\text{Gap Size}=\frac{\text{Statements in gap}}{\text{Statements in clones}}*100
+\end{equation}
 
 \subsection{Context Mapping}
+After clones are detected, we map the context of these clones.
+We have identifier three properties of clones as their context: relation, location and contents.
+We identify categories for each of these properties, to get a detailed insight in the context of clones.
+
 \subsubsection{Relation}
-The rationale for our categories regarding clone relations.
+Clone instances in a clone class can have a relation with each other through inheritance.
+This relation has a big impact on how the clone should be refactored \cite{fontana2015duplicated}.
+We define the following categories to map the relation between clone instances in a clone class.
+These categories do not map external classes (classes outside the project, for instance belonging to a library) unless explicitly stated:
+\begin{itemize}
+    \item \textbf{Common Class}: All clone instances are in the same class.
+    \begin{itemize}
+        \item \textbf{Same Method}: All clone instances are in the same method.
+        \item \textbf{Same Class}: All clone instances are in the same class.
+    \end{itemize}
+    \item \textbf{Common Hierarchy}: All clone instances are in the same inheritance hierarchy.
+    \begin{itemize}
+        \item \textbf{Superclass}: Clone instances reside in a class or its parent class.
+        \item \textbf{Sibling Class}: All clone instances reside in classes with the same parent class.
+        \item \textbf{Ancestor Class}: All clone instances reside in a class, or any of its recursive parents.
+        \item \textbf{First Cousin}: All clone instances reside in classes with the same grandparent class.
+        \item \textbf{Same Hierarchy}: All clone instances are part of the same inheritance hierarchy.
+    \end{itemize}
+    \item \textbf{Common Interface}: All clone instances are in classes that have the same interface.
+    \begin{itemize}
+        \item \textbf{Same Direct Interface}: All clone instances are in a class that have the same interface.
+        \item \textbf{Same Class}: All clone instances are in an inheritance hierarchy that contains the same interface.
+    \end{itemize}
+    \item \textbf{Unrelated}: All clone instances are in classes that have the same interface.
+    \begin{itemize}
+        \item \textbf{No Direct Superclass}: All clone instances are in classes that have the Object class as parent.
+        \item \textbf{No Indirect Superclass}: All clone instances are in a hierarchy that contains a class that has the Object class as parent.
+        \item \textbf{External Superclass}: All clone instances are in classes the same external class as parent.
+        \item \textbf{Indirect External Ancestor}: All clone instances are in a hierarchy that contains a class that has an external class as parent.
+    \end{itemize}
+\end{itemize}
 
@@
 Explain what AST transformations I do to apply the refactorings.
-
-\subsubsection{The cyclic nature of refactoring}
-Explain how refactoring code clones might open up new refactoring opportunities. We refactor a project until there are no more open refactoring opportunities.
 

### 2019-08-14 icse/paper.tex
Finish up relations

@@
 \subsubsection{Relation}
+% The rationale for our categories regarding clone relations.
 Clone instances in a clone class can have a relation with each other through inheritance.
@@
 \end{itemize}
+Based on these relations, we determine where to place the cloned code when refactored.
+The code of clones that have a \textit{Common Class} relation can be refactored by placing the cloned code in this same class.
+The code of clones with a \textit{Common Hierarchy} relation can be placed in the intersecting class in the hierarchy (the class all clone instances have in common as an ancestor).
+The code of clones with a \textit{Common Interface} relation can be placed in the intersecting interface, but in the process has to become part of the classes' public contract.
+The code of clones that are \textit{Unrelated} can be placed in a newly created place: either a utility class, a new superclass abstraction or an interface.
 

### 2019-08-14 icse/paper.tex
Location and contents categories

@@
 In this study we use two concepts used to argue about code clones \cite{roy2007survey}:
-\textbf{Clone instance}: A single cloned fragment.
-\textbf{Clone class}: A set of similar clone instances.
+\\ \textbf{Clone instance}: A single cloned fragment.
+\\ \textbf{Clone class}: A set of similar clone instances.
 
@@
 \subsubsection{Location}
-The rationale for our categories regarding clone locations.
+% The rationale for our categories regarding clone locations.
+
+\begin{enumerate}
+  \item \textbf{Method/Constructor Level:} A clone instance that does not exceed the boundaries of a single method or constructor.
+  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class (like field declarations, other methods, etc.).
+  \item \textbf{Interface/Enumeration Level:} A clone that is (a part of) an interface or enumeration.
+\end{enumerate}
 
 \subsubsection{Contents}
-The rationale for our categories regarding clone contents.
+% The rationale for our categories regarding clone contents.
+
+\begin{enumerate}
+  \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
+  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method/constructor.
+  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods.
+  \item \textbf{Only Fields:} A clone that spans only global variables.
+  \item \textbf{Other:} Anything that does not match with above-stated categories.
+\end{enumerate}
 

### 2019-08-14 icse/paper.tex
Removed Location

@@
 
-\subsubsection{Location}
-% The rationale for our categories regarding clone locations.
-
-\begin{enumerate}
-  \item \textbf{Method/Constructor Level:} A clone instance that does not exceed the boundaries of a single method or constructor.
-  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class (like field declarations, other methods, etc.).
-  \item \textbf{Interface/Enumeration Level:} A clone that is (a part of) an interface or enumeration.
-\end{enumerate}
-
 \subsubsection{Contents}

### 2019-08-14 icse/paper.tex
contents

@@
 After clones are detected, we map the context of these clones.
-We have identifier three properties of clones as their context: relation, location and contents.
+We have identifier three properties of clones as their context: relation and contents.
 We identify categories for each of these properties, to get a detailed insight in the context of clones.
@@
 \end{itemize}
+
 Based on these relations, we determine where to place the cloned code when refactored.
@@
 % The rationale for our categories regarding clone contents.
-
+The contents of a clone instance determine what refactoring techniques can be applied to refactor such clones. We define the following categories by which we analyze the contents of clones:
 \begin{enumerate}
@@
 \end{enumerate}
+
+\subsubsection{Full Method/Constructor/Class/Interface/Enumeration}
+These categories denote that a full declaration, including its body, is cloned with another declaration.
+These categories often denote redundancy and are often easy to solve: one of both declarations is redundant and should be removed.
+All usages of the removed declaration should be redirected to the clone instance that was not removed.
+We check for clones in this category by checking that the first node in a clone instance is a declaration and the last node in the clone instance is the last node in the body of that declaration.
+
+\subsubsection{Partial Method/Constructor}
+These categories describe clone instances which are found in the body of a method or constructor.
+These clones can often be refactored by extracting a new method out of the cloned code.
+We detect such clones by checking that each node in the clone instance has a ancestor node that is a MethodDeclaration, but none of the nodes is a method declaration.
+We describe the procedure by with we recursively seek the parent nodes of a node in Section~\ref{sec:methodlevelcr}.
+
+\subsubsection{Several Methods}
+Several methods cloned in a single class is a strong indication of implicit dependencies between two classes.
+This increases the chance that these classes are missing some form of abstraction, or their abstraction is used inadequately.
+We detect such clones by checking that each cloned node has a parent node that is a MethodDeclaration.
+This is the same process as described in equation \ref{eq:samemethod}.
+Additionally, we check that the MethodDeclaration ancestor of the first node in the clone instance differs from the last, to be sure that the clone instance spans over at least two methods.
+
+\subsubsection{Only Fields}
+This category denotes that the clone spans over only global variables, fields that are declared outside of a method.
+This is to indicate data redundancy: pieces of data have an implicit dependency.
+In such cases, these fields may have to be encapsulated in a new object.
+Or, the fields should be somewhere in the inheritance structure where all objects containing the clone can access them.
+We check for this category by validating that all nodes in the clone instance are a VariableDeclarator.
+Because VariableDeclarators in methods would already fall into the ``Partial Method'' category, this includes only globally defined fields.
+
+\subsubsection{Other}
+The ``Other'' category denotes all configurations of clone contents that do not fall into above categories.
+Often, these are combinations of above states concepts.
+For instance, a combination of constructors and methods is clones, or a combination of fields and methods.
+Such clones indicate, like the ``Several Methods'', the requirement of performing a more architectural-level refactoring.
+These are often more complicated, especially when aiming to automate this process.
 

### 2019-08-14 icse/paper.tex
Contents

--- 2019-08-14 icse/paper.tex
@@
 
+\subsubsection{Full Method/Constructor/Class/Interface/Enumeration}
+The categories denote that a full declaration (method, class, etc.) often denote redundancy and are often easy to refactor: one of both declarations is redundant and should be removed.
+Clones in the ``Partial Method/Constructor'' category can often be refactored using the ``Extract Method'' refactoring technique.
+Clones consisting of \textit{Several Methods} give a strong indication that cloned classes are missing some form of abstraction, or their abstraction is used inadequately.
+Clones consisting of \textit{Only Fields} often indicate data redundancy: different classes use the same data.
+
 \subsection{Refactoring}
+CloneRefactor can refactor clones using the ``Extract Method'' refactoring technique. In this section...
+
 \subsubsection{Extract Method}

### 2019-08-14 icse/paper.tex
Extract method

@@
 
-\subsubsection{Contents}
+\subsubsection{Contents}\label{sec:contents}
 % The rationale for our categories regarding clone contents.
@@
 \subsection{Refactoring}
-CloneRefactor can refactor clones using the ``Extract Method'' refactoring technique. In this section...
+CloneRefactor can refactor clones using the ``Extract Method'' refactoring technique. In this section we show which clones we refactor and how we apply these transformations.
 
 \subsubsection{Extract Method}
-Show my categories to show what clones can be dealt with by method extraction.
+There are several influencing factors that may obstruct the possibility to extract code to a new method:
+\begin{itemize}
+    \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
+    \item \textbf{Spans Part Of A Block}: This clone spans a part of a block statement.
+    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Sec.~\ref{sec:contents}, the ``Extract Method'' refactoring technique cannot be applied.
+    \item \textbf{Returns multiple values}: If a clone modifies or declares multiple pieces of data that it should return.
+    \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method.
+Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
+\end{itemize}
+Clones that do not fall in the \textit{Can Be Extracted} category may require additional transformations or other techniques to refactor.
+CloneRefactor only refactors the clones that \textit{Can Be Extracted}.
 

### 2019-08-14 icse/paper.tex
cloneRef URL

@@
 % The tool: Detect Clones, Map Context, Refactor.
-To automate the process of refactoring clones, we propose a tool named CloneRefactor.
+To automate the process of refactoring clones, we propose a tool named CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
 This tool goes through a 3-step process in order to refactor clones.
-This process is displayed in figure \ref{fig:clonerefactorflow}.
+This process is displayed in Fig.~\ref{fig:clonerefactorflow}.
 \begin{figure}[H]
@@
 \subsubsection{Extract Method}
+% Show my categories to show what clones can be dealt with by method extraction.
 There are several influencing factors that may obstruct the possibility to extract code to a new method:
@@
 \subsubsection{AST Transformation}
-Explain what AST transformations I do to apply the refactorings.
+% Explain what AST transformations I do to apply the refactorings.
 

### 2019-08-14 icse/paper.tex
ACM template
Fixed template

@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
+\documentclass[sigconf,review]{acmart}
+
 \usepackage{graphicx}
-\usepackage{textcomp}
 \usepackage{xcolor}
@@
 
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\setcopyright{acmcopyright}
+\copyrightyear{2019}
+\acmYear{2019}
+\acmDOI{10.1145/1122445.1122456}
+
 \begin{document}
@@
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Simon Baars}
-\IEEEauthorblockA{%\textit{Software Engineering} \\
-\textit{University of Amsterdam}\\
-Amsterdam, the Netherlands \\
-simon.mailadres@gmail.com}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Ana Oprescu}
-\IEEEauthorblockA{%\textit{dept. name of organization (of Aff.)} \\
-\textit{University of Amsterdam}\\
-Amsterdam, the Netherlands \\
-ana.oprescu@uva.nl}
-}
+\author{Simon Baars}
+\affiliation{\institution{University of Amsterdam}}
+\email{simon.mailadres@gmail.com}
 
-\maketitle
+\author{Ana Oprescu}
+\affiliation{\institution{University of Amsterdam}}
+\email{ana.oprescu@uva.nl}
 
@@
 
-\begin{IEEEkeywords}
-code clones, refactoring, static code analysis, object-oriented programming
-\end{IEEEkeywords}
+\keywords{code clones, refactoring, static code analysis, object-oriented programming}
+
+\maketitle
 
@@
 
-\section*{References}
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{references}
 

### 2019-08-14 icse/paper.tex
AST stuff

@@
 We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the systems.
-These metrics are system size, cyclomatic complexity, duplication and number of method parameters.
+These metrics are system size, cyclomatic complexity \cite{mccabe1976complexity}, duplication and number of method parameters.
 On basis of these results, we decide which clones improve system design and thus should be refactored.
@@
 
-\subsubsection{Relation}
+\subsubsection{Relation}\label{sec:relation}
 % The rationale for our categories regarding clone relations.
@@
 % Explain what AST transformations I do to apply the refactorings.
+CloneRefactor uses JavaParser \cite{tomassetti2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
+To refactor clones, CloneRefactor creates a new method declaration and moves all statements from the
+
+\subsection{Characteristics of the extracted method}
+We define the following characteristics that have an impact on the refactoring of the clone class:
+\begin{itemize}
+\item \textbf{Statements}: The number of statements that \textit{each clone instance of the clone class} spans.
+\item \textbf{Tokens}: The number of tokens that the \textit{each clone instance of the clone class} spans.
+\item \textbf{Relation}: The relation category (Sec.~\ref{sec:relation}) that this clone class belongs to.
+\item \textbf{Returns}: The category of what the extracted method returns (Section~\ref{sec:refreturn}).
+\item \textbf{Parameters}: The number of parameters the extracted method has.
+\end{itemize}
+We hypothesize that these characteristics are the main factors influencing the impact on the maintainability of the system as a result of refactoring the clone.
+
+\subsection{Impact on maintainability metrics}
+We measure the impact on maintainability metrics of the refactored source code for each clone class that is refactored.
+These metrics are derived from Heitlager et al.
+\cite{heitlager2007practical}.
+This paper defines a set of metrics to measure the maintainability of a system.
+For each of these metrics, risk profiles are proposed to determine the maintainability impact on the system of a whole.
+
+In this case we are dealing with single refactorings and we want to measure the maintainability impact of such a small change.
+Because of that, we measure only a subset of the metrics \cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
+The subset of metrics we decided to focus on are all metrics that are measured on method level (as the other metrics show a lesser impact on the maintainability for these small changes).
+These metrics are
+\begin{itemize}
+\item \textbf{Duplication}: In Heitlager et al.
+\cite{heitlager2007practical} this metric is measured by taking the amount of duplicated lines.
+We decided to use the amount of duplicated tokens part of a clone class instead, to have a stronger reflection of the impact of the refactoring by measuring a more fine-grained system property.
+\item \textbf{Volume}: The more code a system has, the more code has to be maintained.
+The paper \cite{heitlager2007practical} measures volume as lines of code.
+As with duplication, we use the amount of tokens instead.
+\item \textbf{Complexity}: Heitlager et al.
+use MCCabe complexity \cite{mccabe1976complexity} to calculate their complexity metric.
+The MCCabe complexity is a quantative measure of the number of linearly independent paths through a method.
+\item \textbf{Method Interface Size}: The amount of parameters that a method has.
+If a method has many parameters, the code may become harder to understand and it is an indication that data is not encapsulated adequately in objects \cite{fowler2018refactoring}.
+\end{itemize}
 

### 2019-08-14 icse/paper.tex
AST Transformations

@@
 CloneRefactor uses JavaParser \cite{tomassetti2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
-To refactor clones, CloneRefactor creates a new method declaration and moves all statements from the
+To refactor clones, CloneRefactor creates a new method declaration and moves all statements from a clone instance in the clone class to the new method.
+This method is placed according to the relation between the clone instances (see Sec.~\ref{sec:relation}).
+CloneRefactor analyzes the source code of the extracted method and populates it with the following properties:
+\begin{itemize}
+  \item \textbf{Parameters}: For each variable used that is not accessible from the scope of the extracted method.
+  \item \textbf{A return value}: If the method modifies or declares local data that is needed outside of its scope, or if the cloned fragments already returned data.
+  \item \textbf{Thrown exception}: If the method throws an uncaught exception that is not a \texttt{RuntimeException}.
+\end{itemize}
+CloneRefactor then removes all cloned code and replaces it with a method call to the newly created method.
+In case of a return value, we either assign the call result, declare it or return it accordingly.
 
 \subsection{Characteristics of the extracted method}
-We define the following characteristics that have an impact on the refactoring of the clone class:
+We define the following characteristics of the extracted method and/or the call:
 \begin{itemize}
-\item \textbf{Statements}: The number of statements that \textit{each clone instance of the clone class} spans.
-\item \textbf{Tokens}: The number of tokens that the \textit{each clone instance of the clone class} spans.
-\item \textbf{Relation}: The relation category (Sec.~\ref{sec:relation}) that this clone class belongs to.
-\item \textbf{Returns}: The category of what the extracted method returns (Section~\ref{sec:refreturn}).
+\item \textbf{Statements}: The number of statements in the body of the method.
+\item \textbf{Tokens}: The number of tokens in the body of the method.
+\item \textbf{Relation}: The relation category (Sec.~\ref{sec:relation}) by which this methods' location was determined.
+\item \textbf{Returns}: Whether the method calls return, declare, assign or don't use any data from the extracted method.
 \item \textbf{Parameters}: The number of parameters the extracted method has.

### 2019-08-14 sections/clonerefactor.tex
Extract method
AST Transformations

@@
 These categories denote that a full declaration, including its body, is cloned with another declaration.
-These categories often denote redundancy and are often easy to solve: one of both declarations is redundant and should be removed.
+These categories often denote redundancy and are often easy to refactor: one of both declarations is redundant and should be removed.
 All usages of the removed declaration should be redirected to the clone instance that was not removed.
@@
 \paragraph{Thrown exception}
-If a method in Java throws an exception that is not a \textbf{RuntimeException}, it must be denoted in the method declaration.
+If a method in Java throws an exception that is not a \texttt{RuntimeException}, it must be denoted in the method declaration.
 Because of this, we analyze the extracted method for \texttt{throw} statements, which denote an exception being thrown.
@@
 For each of these exception, we check whether they are caught in the extracted method.
-Any exception that is that is not a \textbf{RuntimeException} and that is not being caught is added to the thrown exceptions of the extracted method.
+Any exception that is that is not a \texttt{RuntimeException} and that is not being caught is added to the thrown exceptions of the extracted method.
 

### 2019-08-15 icse/paper.tex
Experimental setup

@@
 
-\subsection{Ensuring Equality}
+\subsection{Ensuring Equality}\label{sec:t1r}
 % Explain type 1, why it is not always refactorable, solution
@@
 CloneRefactor then removes all cloned code and replaces it with a method call to the newly created method.
-In case of a return value, we either assign the call result, declare it or return it accordingly.
+In case of a return value, CloneRefactor either assigns the call result, declares it or returns it accordingly.
 
-\subsection{Characteristics of the extracted method}
+\subsubsection{Characteristics of the extracted method}
 We define the following characteristics of the extracted method and/or the call:
@@
 
-\subsection{Impact on maintainability metrics}
+\subsubsection{Impact on maintainability metrics} \label{sec:metrics}
 We measure the impact on maintainability metrics of the refactored source code for each clone class that is refactored.
@@
 \end{itemize}
+
+\section{Experimental setup}
+In this section we describe the setup of our experiments.
+
+\subsection{Corpus}
+We ran all our experiments using CloneRefactor on a corpus of open source Java projects.
+This corpus is derived from the corpus of a study that uses machine learning to determine the suitability of Java projects on GitHub for data analysis purposes \cite{githubCorpus2013}.
+
+CloneRefactor requires all libraries of the projects it analyses, in order to find the full paths of all referenced symbols in the source code (see Sec.~\ref{sec:t1r}).
+Because of that requirement, we decided to filter the corpus to only projects using the Maven build automation system.
+We created a set of scripts\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} to prepare such a corpus with all dependencies included.
+
+This procedure results in 2.267 Java projects including all their dependencies. The projects vary in size and quality.
+
+\subsection{Minimum clone size}
+In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored. This implies that
+
+\subsection{Calculating a maintainability score}
+In this study we use four metrics to determine maintainability \ref{sec:metrics}.
+For our experiments, we want to aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
+We base our aggregation on the following assumptions:
+\begin{itemize}
+  \item All metrics are equal in terms of weight towards system maintenance effort.
+  \item Higher values for the metrics imply lower maintainability.
+  \item The obtained increase of the metric divided by the average distance from zero over our corpus weights the metric equally against the other metrics.
+\end{itemize}
+We calculate the average deviation as follows:
+\begin{equation}\label{eq:type3r}
+A = \frac{\sum_{x \in M} abs(x)}{|M|}
+\end{equation}
+Where \textit{M} is the multiset of all values obtained for a certain metric over our corpus and \textit{|M|} is the cardinality of this set.
+We then calculate the maintainability for a specific refactoring as follows:
+\begin{equation}\label{eq:type3r}
+A_M = \frac{dup}{A_{dup}} + \frac{com}{A_{com}} + \frac{par}{A_{par}} + \frac{vol}{A_{vol}}
+\end{equation}
+Where \textit{dup} is the decrease in duplication, \textit{com} is the decrease in complexity, \textit{par} is the decrease is method parameters and \textit{vol} is the decrease in system volume after the refactoring is applied.
 

### 2019-08-15 icse/paper.tex
Corpus stats

@@
 
-This procedure results in 2.267 Java projects including all their dependencies. The projects vary in size and quality.
+This procedure results in 2.267 Java projects including all their dependencies.
+The projects vary in size and quality.
+The total size of all projects is 14.2M lines (11.3M when excluding whitespace) over a total of 100K Java files.
+This is an average of 6.3K lines over 44 files per project.
+The largest project in the corpus is VisAD with 502K lines.
 
@@
 \end{equation}
-Where \textit{M} is the multiset of all values obtained for a certain metric over our corpus and \textit{|M|} is the cardinality of this set.
+Where \textit{M} is the multiset of all change in a certain metric for all refactorings over all systems in  obtained for a certain metric over our corpus and \textit{|M|} is the cardinality of this set.
 We then calculate the maintainability for a specific refactoring as follows:
@@
 Where \textit{dup} is the decrease in duplication, \textit{com} is the decrease in complexity, \textit{par} is the decrease is method parameters and \textit{vol} is the decrease in system volume after the refactoring is applied.
+When comparing the maintainability of
 

### 2019-08-15 icse/paper.tex
Minimum size

@@
 
+To verify the correctness of all detected clones, we ran the tool over a large project and manually checked the output.
+We also created a set of control projects to test the correctness for many edge cases.
+
 \subsection{Context Mapping}
@@
 
+We verified the correctness of the resulting refactorings manually. We ran the tool over a large software project and verified over 1.000 applied refactorings.
+
 \subsubsection{Characteristics of the extracted method}
@@
 \subsection{Minimum clone size}
-In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored. This implies that
+In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored.
+However, when clones are very small, they may never be able to improve maintainability because the detrimental effect of added volume of the newly created method exceeds the positive effect of removing duplication.
+Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones cannot improve maintainability when refactored.
 
@@
 Where \textit{dup} is the decrease in duplication, \textit{com} is the decrease in complexity, \textit{par} is the decrease is method parameters and \textit{vol} is the decrease in system volume after the refactoring is applied.
-When comparing the maintainability of
+When comparing the maintainability of a set of refactorings we divide the sum of the maintainability score by the amount of clone instances of all refactored clones in the set.
 

### 2019-08-15 icse/paper.tex
Results

@@
 
-\subsection{Context Mapping}
+\subsection{Context Mapping} \label{sec:context}
 After clones are detected, we map the context of these clones.
@@
 \section{Results}
+In this section we share the results of our experiments.
+
+\subsection{Clone context}
+Our initial experiments look into how many clones are found in different contexts (see Sec.~\ref{sec:context}). This results in the Table~\ref{}.
 

### 2019-08-15 icse/paper.tex
Added relation table

@@
 \usepackage{float}
+
+\usepackage{booktabs}
+\usepackage{multirow}
 
@@
 \subsection{Clone context}
-Our initial experiments look into how many clones are found in different contexts (see Sec.~\ref{sec:context}). This results in the Table~\ref{}.
+% How many clones are there in certain contexts? Experiments for relation, location and context.
+Our initial experiments look into how many clones are found in different contexts (see Sec.~\ref{sec:context}). This results in the Table~\ref{tab:relation}.
 
-\subsection{Clone context}
-How many clones are there in certain contexts? Experiments for relation, location and context.
+\begin{table}[]
+\centering
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}llll@{}}
+\toprule
+Category & Relation & Amount of clone classes & Total \\ \midrule
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
+ & Same Method & 8,955 &  \\ \midrule
+\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342} \\ \cmidrule(lr){2-3}
+ & Superclass & 2,616 &  \\ \cmidrule(lr){2-3}
+ & First Cousin & 1,219 &  \\ \cmidrule(lr){2-3}
+ & Common Hierarchy & 720 &  \\ \cmidrule(lr){2-3}
+ & Ancestor & 199 &  \\ \midrule
+\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314} \\ \cmidrule(lr){2-3}
+ & External Superclass & 4,525 &  \\ \cmidrule(lr){2-3}
+ & External Ancestor & 3,347 &  \\ \cmidrule(lr){2-3}
+ & No Indirect Superclass & 1,765 &  \\ \midrule
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} \\ \cmidrule(lr){2-3}
+ & Same Indirect Interface & 5,552 &  \\ \bottomrule
+\end{tabular}%
+}
+\caption{Amount of clone classes per clone relation}
+\label{tab:relation}
+\end{table}
 

### 2019-08-15 icse/paper.tex
Table 2 column
Fixed a few issues

@@
 Duplication in source code is often seen as one of the most harmful types of technical debt, because it increases the size of the codebase and creates implicit dependencies between fragments of code.
-To remove such antipatterns, a developer should refactor the codebase.
+To remove such anti-patterns, a developer should refactor the codebase.
 There are many tools that assist in this process.
@@
 % Explain type 1, why it is not always refactorable, solution
-Most modern clone detection tools detect clones by comparing the code textually together with the ommission of certain tokens \cite{roy2009comparison, svajlenko2014evaluating}.
-Clones detected by such means may not always be suitable for refactoring, because textua comparison fails to take into account the context of certain symbols in the code.
+Most modern clone detection tools detect clones by comparing the code textually together with the omission of certain tokens \cite{roy2009comparison, svajlenko2014evaluating}.
+Clones detected by such means may not always be suitable for refactoring, because textual comparison fails to take into account the context of certain symbols in the code.
 Information that gets lost in textual comparison is the referenced declaration for type, variable and method references.
 Equally named type, variable and method references may refer to different declarations with a different implementation.
-Such clones can be harder to refactor, if benificial at all.
+Such clones can be harder to refactor, if beneficial at all.
 
@@
 \end{itemize}
-Often when allowing such variance, tradeoffs come into play.
+Often when allowing such variance, trade-offs come into play.
 For instance, variance in literals may require the introduction of a parameter to an extracted method if the ``Extract Method'' refactoring method is used, increasing the required effort to comprehend the code.
@@
 \end{itemize}
-Again, a tradeoff is at play, as these solutions increase the complexity in favor of removing a clone.
+Again, a trade-off is at play, as these solutions increase the complexity in favor of removing a clone.
 
@@
 use MCCabe complexity \cite{mccabe1976complexity} to calculate their complexity metric.
-The MCCabe complexity is a quantative measure of the number of linearly independent paths through a method.
+The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.
 \item \textbf{Method Interface Size}: The amount of parameters that a method has.
@@
 This is an average of 6.3K lines over 44 files per project.
-The largest project in the corpus is VisAD with 502K lines.
+The largest project in the corpus is \textit{VisAD} with 502K lines.
 
@@
 We calculate the average deviation as follows:
-\begin{equation}\label{eq:type3r}
+\begin{equation}\label{eq:scoredev}
 A = \frac{\sum_{x \in M} abs(x)}{|M|}
@@
 We then calculate the maintainability for a specific refactoring as follows:
-\begin{equation}\label{eq:type3r}
+\begin{equation}\label{eq:scoreref}
 A_M = \frac{dup}{A_{dup}} + \frac{com}{A_{com}} + \frac{par}{A_{par}} + \frac{vol}{A_{vol}}
@@
 
-\begin{table}[]
+\begin{table*}[]
 \centering
-\resizebox{\textwidth}{!}{%
 \begin{tabular}{@{}llll@{}}
@@
  & Same Indirect Interface & 5,552 &  \\ \bottomrule
-\end{tabular}%
-}
+\end{tabular}
 \caption{Amount of clone classes per clone relation}
 \label{tab:relation}
-\end{table}
+\end{table*}
 

### 2019-08-15 icse/paper.tex
Made the table shine
Intro stories

@@
 % How many clones are there in certain contexts? Experiments for relation, location and context.
-Our initial experiments look into how many clones are found in different contexts (see Sec.~\ref{sec:context}). This results in the Table~\ref{tab:relation}.
+To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the clone context (see Sec.~\ref{sec:context}).
 
-\begin{table*}[]
+\subsubsection{Relation}
+Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Sec.~\ref{sec:relation}).
+
+\begin{table}[H]
 \centering
@@
 \toprule
-Category & Relation & Amount of clone classes & Total \\ \midrule
+\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} \\ \midrule
 \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
@@
 \end{tabular}
-\caption{Amount of clone classes per clone relation}
+\caption{Number of clone classes per clone relation}
 \label{tab:relation}
-\end{table*}
+\end{table}
+
+\subsubsection{Contents}
+Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different contents (see Sec.~\ref{sec:contents}).
 

### 2019-08-15 icse/paper.tex
Added contents table

@@
 
+\begin{table}[H]
+\centering
+\begin{tabular}{@{}llll@{}}
+\toprule
+Category & Contents & Clone instances & Total \\ \midrule
+\multirow{2}{*}{Partial} & Partial Method & 219,540 & 229,521 \\
+ & Partial Constructor & 9,981 &  \\
+Full & Full Method & 12,990 & 13,173 \\
+ & Full Interface & 64 &  \\
+ & Full Constructor & 58 &  \\
+ & Full Class & 37 &  \\
+ & Full Enum & 24 &  \\
+Other & Several Methods & 22,749 & 53,773 \\
+ & Only Fields & 17,700 &  \\
+ & Other & 13,324 &  \\ \bottomrule
+\end{tabular}
+\caption{Number of clone instances for clone contents categories}
+\label{tab:contents}
+\end{table}
+
 \subsection{Clone refactorability}

### 2019-08-15 icse/paper.tex
Amazing table

--- 2019-08-15 icse/paper.tex
@@
 \acmDOI{10.1145/1122445.1122456}
+\acmMonth{8}
+
+\acmConference[ICSE 2020]{Technical Papers}{May
+23--29}{Seoul, North Korea}
 
@@
 
+\begin{table}[]
+\centering
+\begin{tabular}{@{}llll@{}}
+\toprule
+\textit{\textbf{Category}} & \textit{\textbf{Contents}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
+\multirow{2}{*}{Partial} & Partial Method & 219,540 & \multirow{2}{*}{229,521} \\ \cmidrule(lr){2-3}
+ & Partial Constructor & 9,981 &  \\ \midrule
+\multirow{5}{*}{Full} & Full Method & 12,990 & \multirow{5}{*}{13,173} \\ \cmidrule(lr){2-3}
+ & Full Interface & 64 &  \\ \cmidrule(lr){2-3}
+ & Full Constructor & 58 &  \\ \cmidrule(lr){2-3}
+ & Full Class & 37 &  \\ \cmidrule(lr){2-3}
+ & Full Enum & 24 &  \\ \midrule
+\multirow{3}{*}{Other} & Several Methods & 22,749 & \multirow{3}{*}{53,773} \\ \cmidrule(lr){2-3}
+ & Only Fields & 17,700 &  \\ \cmidrule(lr){2-3}
+ & Other & 13,324 &  \\ \bottomrule
+\end{tabular}
+\caption{Number of clone instances for clone contents categories}
+\label{tab:contents}
+\end{table}
+
 \subsection{Clone refactorability}

### 2019-08-15 icse/paper.tex
Refactorability

@@
 \usepackage{graphicx}
-\usepackage{xcolor}
+\usepackage[table,xcdraw]{xcolor}
 \usepackage{float}
@@
     \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Sec.~\ref{sec:contents}, the ``Extract Method'' refactoring technique cannot be applied.
-    \item \textbf{Returns multiple values}: If a clone modifies or declares multiple pieces of data that it should return.
+    \item \textbf{Returns Multiple Values}: If a clone modifies or declares multiple pieces of data that it should return.
+    \item \textbf{Top-Level Non-Statement}: If one of the top-level AST nodes of the clone is not a statement. For instance, if a (part of) an anonymous class is cloned.
     \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method.
@@
 
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+% \usepackage[table,xcdraw]{xcolor}
+% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
+\begin{table}[]
+\centering
+\begin{tabular}{@{}lll@{}}
+\toprule
+\rowcolor[HTML]{C0C0C0}
+\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{Method Body}} \\ \midrule
+\rowcolor[HTML]{EFEFEF}
+Can Be Extracted & 24,157 & 26,109 \\
+Is Not A Partial Method & 21,625 & 0 \\
+\rowcolor[HTML]{EFEFEF}
+Top-level Node is not a Statement &  & 4,607 \\
+Spans Part of a Block & 12,964 & 13460 \\
+\rowcolor[HTML]{EFEFEF}
+Multiple Return Values & 5,622 & 6,131 \\
+Complex Control Flow & 1,106 & 1,216 \\ \bottomrule
+\end{tabular}
+\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique}
+\label{tab:refactorability}
+\end{table}
+
 \subsection{Thresholds}

### 2019-08-15 icse/paper.tex
Clone refactorability

--- 2019-08-15 icse/paper.tex
@@
-\documentclass[sigconf,review]{acmart}
+\documentclass[sigconf,review, table]{acmart}
 
+\usepackage{xcolor}
 \usepackage{graphicx}
-\usepackage{xcolor}
 \usepackage{float}
@@
 \subsection{Clone refactorability}
-To what extent can found clones be refactored through method extraction, without requiring additional transformations.
+%To what extent can found clones be refactored through method extraction, without requiring additional transformations.
+Table \ref{tab:refactorability} shows to what extend clone classes can be refactored by using the ``Extract Method'' refactoring technique.
+The second column shows our measurements for the complete systems (just like the former experiments).
+The third column shows our measurements when restricting our search to method bodies.
+The amount that can be extracted increases because, when restricting our search to method bodies, we do not exclude declarations that can obstruct the possibility of method extraction (for instance a cloned method signature).
+
+\begin{table}[]
+\centering
+\begin{tabular}{@{}lll@{}}
+\toprule
+\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{Method Body}} \\ \midrule
+Can Be Extracted & 24,157 & 26,109 \\
+Is Not A Partial Method & 21,625 & 0 \\
+Top-level Node is not a Statement & 19,887 & 4,607 \\
+Spans Part of a Block & 12,964 & 13,460 \\
+Multiple Return Values & 5,622 & 6,131 \\
+Complex Control Flow & 1,106 & 1,216 \\ \bottomrule
+\end{tabular}
+\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique}
+\label{tab:refactorability}
+\end{table}s
 

### 2019-08-15 icse/paper.tex
Refactoring

@@
 The thresholds and prioritization of the clones detected by such tools can be improved by considering the maintainability of the codebase after a detected clone would be refactored.
+We perform an exploratory study into the data that can be gathered from comparing before- and after snapshots of an automatically refactored system.
 
@@
 
-\subsubsection{Characteristics of the extracted method}
+\subsubsection{Characteristics of the extracted method}\label{sec:characteristics}
 We define the following characteristics of the extracted method and/or the call:
@@
 
-\subsection{Calculating a maintainability score}
+\subsection{Calculating a maintainability score}\label{sec:metricformula}
 In this study we use four metrics to determine maintainability \ref{sec:metrics}.
@@
 
-\subsection{Clone refactorability}
+\subsection{Extract Method}
 %To what extent can found clones be refactored through method extraction, without requiring additional transformations.
@@
 \label{tab:refactorability}
-\end{table}s
+\end{table}
 
-\subsection{Thresholds}
-I think the ultimate goal with this thesis is to do experiments with different clone thresholds.
+\subsection{Refactoring}
+%I think the ultimate goal with this thesis is to do experiments with different clone thresholds.
 Which thresholds give clones that we should refactor?
@@
 These thresholds range from minimum clone size, variability and gap size.
+In our corpus CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Sec.~\ref{sec:metrics}).
+Using the presented formulas (see Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
+In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.
+
+\subsubsection{Statements}
 

### 2019-08-15 icse/paper.tex
Clone token volume

@@
 \begin{itemize}
-\item \textbf{Statements}: The number of statements in the body of the method.
 \item \textbf{Tokens}: The number of tokens in the body of the method.
@@
 
-\subsubsection{Statements}
+\subsubsection{Clone Token Volume}
+Figure \ref{fig:duplication} shows the obtained results when plotting the clone size (in tokens) vs the maintainability increase/decrease.
+On the secondary axis the amount of refactorings that have refactored a clone with the specified amount of tokens is displayed (e.g.
+the amount of datapoints the data is based on).
+As the amount of datapoints decreases, the datapoints become more noisy.
+
+\begin{figure*}
+  \includegraphics[width=1\textwidth]{img/duplication}
+  \caption{How the size of the refactored clone influences the maintainability. Maintainability on the primary axis and amount of refactorings on the secondary axis.}
+  \label{fig:duplication}
+\end{figure*}
 

### 2019-08-15 icse/paper.tex
Relation

@@
 the amount of datapoints the data is based on).
-As the amount of datapoints decreases, the datapoints become more noisy.
+As the amount of datapoints decreases, the datapoints gain less statistical significance.
 
@@
 \end{figure*}
+
+\subsubsection{Relation}
+Table \ref{} shows our data regarding how different relations influence maintainability.
+We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance.
+For these results, we have set the minimum amount of tokens for clones to 18 because otherwise the small clones dominate the results and turn them all towards unmaintainable.
+
+\begin{table}[]
+\centering
+\begin{tabular}{@{}lll@{}}
+\toprule
+Row Labels & Maintainability Score & Number of Refactorings \\ \midrule
+\rowcolor[HTML]{FFCCC9}
+Common Hierarchy & 0,63 & 27 \\
+Sibling & 0,53 & 664 \\
+No Direct Superclass & 0,11 & 295 \\
+Same Method & 0,06 & 740 \\
+\rowcolor[HTML]{FFCCC9}
+Superclass & 0,03 & 68 \\
+Same Class & 0,02 & 1273 \\
+External Superclass & 0,01 & 209 \\
+\rowcolor[HTML]{FFCCC9}
+No Indirect Superclass & -0,06 & 36 \\
+Same Interface & -0,07 & 269 \\
+\rowcolor[HTML]{FFCCC9}
+First Cousin & -0,19 & 54 \\
+External Ancestor & -0,28 & 154 \\
+\rowcolor[HTML]{FFCCC9}
+Ancestor & -0,52 & 5 \\ \bottomrule
+\end{tabular}
+\caption{Influence on maintainability of refactoring clones by certain relations.}
+\label{tab:relation_refactor}
+\end{table}
 

### 2019-08-15 icse/paper.tex
Return value

@@
 \subsubsection{Relation}
-Table \ref{} shows our data regarding how different relations influence maintainability.
+Table \ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability.
 We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance.
@@
 \toprule
-Row Labels & Maintainability Score & Number of Refactorings \\ \midrule
+Category & Maintainability Score & Number of Refactorings \\ \midrule
 \rowcolor[HTML]{FFCCC9}
@@
 
+\subsubsection{Return Value}
+Table \ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.
+
+\begin{table}[]
+\centering
+\begin{tabular}{@{}lll@{}}
+\toprule
+Return Value & Maintainability Score & Number of Refactorings \\ \midrule
+Return & 0,20 & 421 \\
+Void & 0,19 & 2052 \\
+Declare & 0,03 & 1318 \\
+\rowcolor[HTML]{FFCCC9}
+Assign & -1,29 & 3 \\ \bottomrule
+\end{tabular}
+\caption{Maintainability scores for different return values}
+\label{tab:return}
+\end{table}
+
+\subsubsection{Arguments}
+
 \section{Discussion}

### 2019-08-15 icse/paper.tex
Arguments
Finish stuff up regarding results

@@
   \includegraphics[width=1\textwidth]{img/duplication}
-  \caption{How the size of the refactored clone influences the maintainability. Maintainability on the primary axis and amount of refactorings on the secondary axis.}
+  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability. Maintainability on the primary axis and amount of refactorings on the secondary axis.}
   \label{fig:duplication}
 \end{figure*}
+
+The volume of the clone is the dominating factor regarding the maintainability increase/decrease of cloned code.
+Because of that, for our further experiments we filter out all refactorings with a token size smaller than 18 because otherwise the small clones dominate the results and turn all results towards unmaintainable.
 
@@
 We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance.
-For these results, we have set the minimum amount of tokens for clones to 18 because otherwise the small clones dominate the results and turn them all towards unmaintainable.
 
@@
 
-\subsubsection{Arguments}
+\subsubsection{Parameters}
+Figure \ref{fig:arguments} shows how an increase in parameters lowers the maintainability of the refactored code.
+On the primary x-axis the maintainability is displayed, the secundary x-axis shows the amount of refactorings and the y-axis shows the amount of parameters.
+
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/flow}
+  \caption{Influence of number of method parameters on system maintainability.}
+  \label{fig:arguments}
+\end{figure}
 

### 2019-08-15 icse/paper.tex
Style improvements

@@
 \subsubsection{Contents}
-Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different contents (see Sec.~\ref{sec:contents}).
+Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Sec.~\ref{sec:contents}).
 
@@
 \toprule
-Category & Maintainability Score & Number of Refactorings \\ \midrule
+\textit{\textbf{Category}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
 \rowcolor[HTML]{FFCCC9}
@@
 \toprule
-Return Value & Maintainability Score & Number of Refactorings \\ \midrule
+\textit{\textbf{Return Value}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
 Return & 0,20 & 421 \\
@@
 \begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/flow}
+  \includegraphics[width=1\columnwidth]{img/arguments}
   \caption{Influence of number of method parameters on system maintainability.}

### 2019-08-15 icse/paper.tex
Revert "Minipage is awful"
This reverts commit baace6227f7e760d75d176651f9ed99478390ab8.
Minipage is awful

@@
 \usepackage{multirow}
+\usepackage{nonfloat}
 
@@
 
-\begin{table}[]
+\begin{table}[H]
 \centering
@@
 
-\begin{figure*}
+\begin{minipage}{\linewidth} 
+\centering%
   \includegraphics[width=1\textwidth]{img/duplication}
-  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability. Maintainability on the primary axis and amount of refactorings on the secondary axis.}
-  \label{fig:duplication}
-\end{figure*}
+\figcaption{A graph that shows how the size in tokens of the refactored clone affects maintainability. Maintainability on the primary axis and amount of refactorings on the secondary axis.}%
+\label{fig:duplication}%
+\end{minipage}
 

### 2019-08-15 icse/paper.tex
Discussion

--- 2019-08-15 icse/paper.tex
@@
 Is Not A Partial Method & 21,625 & 0 \\
-Top-level Node is not a Statement & 19,887 & 4,607 \\
+Top-level AST-Node is not a Statement & 19,887 & 4,607 \\
 Spans Part of a Block & 12,964 & 13,460 \\
@@
 \section{Discussion}
-\subsection{Clone Definitions}
+In this section we discuss the results of our experiments.
 
-\subsection{CloneRefactor}
+\subsection{Clone Context}
+Regarding clone context, our results indicate that most clones (37\%) are in a common class.
+This is favorable for refactoring, because the extracted method does not have to be moved after extraction.
+24\% of clones are in a common hierarchy.
+These refactorings are also often favorable.
+Also 24\% of clones are unrelated, which is often unfavorable because it often requires a more comprehensive refactoring.
+15\% of clones are in an interface.
 
-\subsection{Experimental setup}
+Regarding clone contents, 74\% of clones span part of a method body (77\% if we include constructors).
+8\% of clones span several methods, which often require refactorings on a more architectural level.
+
+\subsection{Extract Method}
+28\% of clones can be refactored using the ``Extract Method'' refactoring technique (50\% if we limit our searching scope to method bodies).
+About 25\% of clones do not span part of a method, because of which they cannot be refactored.
+Many clones (23\%) do not have a statement as top-level AST-Node.
+Upon manual inspection, we noticed that the main reason for this is clones in anonymous functions or anonymous classes.
+About 15\% of clones span only part of an AST-Node.
+
+\subsection{Refactoring}
 

### 2019-08-15 icse/paper.tex
Oops . -> , and , -> .

@@
 \textit{\textbf{Return Value}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
-Return & 0,20 & 421 \\
-Void & 0,19 & 2052 \\
-Declare & 0,03 & 1318 \\
+Return & 0.20 & 421 \\
+Void & 0.19 & 2052 \\
+Declare & 0.03 & 1318 \\
 \rowcolor[HTML]{FFCCC9}
-Assign & -1,29 & 3 \\ \bottomrule
+Assign & -1.29 & 3 \\ \bottomrule
 \end{tabular}

### 2019-08-15 icse/paper.tex
New Relation Table

@@
 
-\begin{table}[H]
+\begin{table}[]
 \centering
-\begin{tabular}{@{}lll@{}}
+\begin{tabular}{@{}llll@{}}
 \toprule
-\textit{\textbf{Category}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
+\textit{\textbf{Relation}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Maintainability\\ Score\end{tabular}}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Number of\\ Refactorings\end{tabular}}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Percentage of\\ Refactorings\end{tabular}}} \\ \midrule
+\textbf{Common Hierarchy} & \textbf{0,51} & \textbf{792} & \textbf{20,9\%} \\ \midrule
+Sibling & 0.57 & 637 & 16,8\% \\
 \rowcolor[HTML]{FFCCC9}
-Common Hierarchy & 0,63 & 27 \\
-Sibling & 0,53 & 664 \\
-No Direct Superclass & 0,11 & 295 \\
-Same Method & 0,06 & 740 \\
+Same Hierarchy & 0,55 & 22 & 0,6\% \\
 \rowcolor[HTML]{FFCCC9}
-Superclass & 0,03 & 68 \\
-Same Class & 0,02 & 1273 \\
-External Superclass & 0,01 & 209 \\
+Superclass & 0,20 & 74 & 2,0\% \\
 \rowcolor[HTML]{FFCCC9}
-No Indirect Superclass & -0,06 & 36 \\
-Same Interface & -0,07 & 269 \\
+First Cousin & -0,02 & 53 & 1,4\% \\
 \rowcolor[HTML]{FFCCC9}
-First Cousin & -0,19 & 54 \\
-External Ancestor & -0,28 & 154 \\
+Ancestor & -0,65 & 6 & 0,2\% \\ \midrule
+\textbf{Common Class} & \textbf{0,01} & \textbf{2025} & \textbf{53,5\%} \\ \midrule
+Same Method & 0,01 & 762 & 20,1\% \\
+Same Class & 0,01 & 1263 & 33,3\% \\ \midrule
+\textbf{Unrelated} & \textbf{-0,02} & \textbf{688} & \textbf{18,2\%} \\ \midrule
+No Direct Superclass & 0,08 & 289 & 7,6\% \\
+External Superclass & -0,02 & 225 & 5,9\% \\
 \rowcolor[HTML]{FFCCC9}
-Ancestor & -0,52 & 5 \\ \bottomrule
+No Indirect Superclass & -0,04 & 30 & 0,8\% \\
+External Ancestor & -0,26 & 144 & 3,8\% \\ \midrule
+\textbf{Common Interface} & \textbf{-0,11} & \textbf{283} & \textbf{7,5\%} \\ \midrule
+Same Direct Interface & 0,02 & 160 & 4,2\% \\
+Same Indirect Interface & -0,31 & 123 & 3,2\%
 \end{tabular}

### 2019-08-15 icse/paper.tex
Made table nice

@@
 \textbf{Common Hierarchy} & \textbf{0,51} & \textbf{792} & \textbf{20,9\%} \\ \midrule
-Sibling & 0.57 & 637 & 16,8\% \\
+\hspace{10pt} Sibling & 0.57 & 637 & 16,8\% \\
 \rowcolor[HTML]{FFCCC9}
-Same Hierarchy & 0,55 & 22 & 0,6\% \\
+\hspace{10pt} Same Hierarchy & 0,55 & 22 & 0,6\% \\
 \rowcolor[HTML]{FFCCC9}
-Superclass & 0,20 & 74 & 2,0\% \\
+\hspace{10pt} Superclass & 0,20 & 74 & 2,0\% \\
 \rowcolor[HTML]{FFCCC9}
-First Cousin & -0,02 & 53 & 1,4\% \\
+\hspace{10pt} First Cousin & -0,02 & 53 & 1,4\% \\
 \rowcolor[HTML]{FFCCC9}
-Ancestor & -0,65 & 6 & 0,2\% \\ \midrule
+\hspace{10pt} Ancestor & -0,65 & 6 & 0,2\% \\ \midrule
 \textbf{Common Class} & \textbf{0,01} & \textbf{2025} & \textbf{53,5\%} \\ \midrule
-Same Method & 0,01 & 762 & 20,1\% \\
-Same Class & 0,01 & 1263 & 33,3\% \\ \midrule
+\hspace{10pt} Same Method & 0,01 & 762 & 20,1\% \\
+\hspace{10pt} Same Class & 0,01 & 1263 & 33,3\% \\ \midrule
 \textbf{Unrelated} & \textbf{-0,02} & \textbf{688} & \textbf{18,2\%} \\ \midrule
-No Direct Superclass & 0,08 & 289 & 7,6\% \\
-External Superclass & -0,02 & 225 & 5,9\% \\
+\hspace{10pt} No Direct Superclass & 0,08 & 289 & 7,6\% \\
+\hspace{10pt} External Superclass & -0,02 & 225 & 5,9\% \\
 \rowcolor[HTML]{FFCCC9}
-No Indirect Superclass & -0,04 & 30 & 0,8\% \\
-External Ancestor & -0,26 & 144 & 3,8\% \\ \midrule
+\hspace{10pt} No Indirect Superclass & -0,04 & 30 & 0,8\% \\
+\hspace{10pt} External Ancestor & -0,26 & 144 & 3,8\% \\ \midrule
 \textbf{Common Interface} & \textbf{-0,11} & \textbf{283} & \textbf{7,5\%} \\ \midrule
-Same Direct Interface & 0,02 & 160 & 4,2\% \\
-Same Indirect Interface & -0,31 & 123 & 3,2\%
+\hspace{10pt} Same Direct Interface & 0,02 & 160 & 4,2\% \\
+\hspace{10pt} Same Indirect Interface & -0,31 & 123 & 3,2\%
 \end{tabular}

### 2019-08-15 icse/paper.tex
Removed percentages

--- 2019-08-15 icse/paper.tex
@@
 
-\begin{table}[H]
+\begin{table}[]
 \centering
@@
 \toprule
-\textit{\textbf{Category}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
+\textit{\textbf{Relation}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Maintainability\\ Score\end{tabular}}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Number of\\ Refactorings\end{tabular}}} \\ \midrule
+\textbf{Common Hierarchy} & \textbf{0,51} & \textbf{792} \\ \midrule
+\hspace{10pt} Sibling & 0.57 & 637 \\
 \rowcolor[HTML]{FFCCC9}
-Common Hierarchy & 0,63 & 27 \\
-Sibling & 0,53 & 664 \\
-No Direct Superclass & 0,11 & 295 \\
-Same Method & 0,06 & 740 \\
+\hspace{10pt} Same Hierarchy & 0,55 & 22 \\
 \rowcolor[HTML]{FFCCC9}
-Superclass & 0,03 & 68 \\
-Same Class & 0,02 & 1273 \\
-External Superclass & 0,01 & 209 \\
+\hspace{10pt} Superclass & 0,20 & 74 \\
 \rowcolor[HTML]{FFCCC9}
-No Indirect Superclass & -0,06 & 36 \\
-Same Interface & -0,07 & 269 \\
+\hspace{10pt} First Cousin & -0,02 & 53 \\
 \rowcolor[HTML]{FFCCC9}
-First Cousin & -0,19 & 54 \\
-External Ancestor & -0,28 & 154 \\
+\hspace{10pt} Ancestor & -0,65 & 6 \\ \midrule
+\textbf{Common Class} & \textbf{0,01} & \textbf{2025}\\ \midrule
+\hspace{10pt} Same Method & 0,01 & 762  \\
+\hspace{10pt} Same Class & 0,01 & 1263 \\ \midrule
+\textbf{Unrelated} & \textbf{-0,02} & \textbf{688}\\ \midrule
+\hspace{10pt} No Direct Superclass & 0,08 & 289 \\
+\hspace{10pt} External Superclass & -0,02 & 225  \\
 \rowcolor[HTML]{FFCCC9}
-Ancestor & -0,52 & 5 \\ \bottomrule
+\hspace{10pt} No Indirect Superclass & -0,04 & 30  \\
+\hspace{10pt} External Ancestor & -0,26 & 144  \\ \midrule
+\textbf{Common Interface} & \textbf{-0,11} & \textbf{283} \\ \midrule
+\hspace{10pt} Same Direct Interface & 0,02 & 160 \\
+\hspace{10pt} Same Indirect Interface & -0,31 & 123
 \end{tabular}

### 2019-08-15 icse/paper.tex
Corrected commas and dots
Refactoring Discussion

@@
 \textit{\textbf{Relation}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Maintainability\\ Score\end{tabular}}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Number of\\ Refactorings\end{tabular}}} \\ \midrule
-\textbf{Common Hierarchy} & \textbf{0,51} & \textbf{792} \\ \midrule
+\textbf{Common Hierarchy} & \textbf{0.51} & \textbf{792} \\ \midrule
 \hspace{10pt} Sibling & 0.57 & 637 \\
 \rowcolor[HTML]{FFCCC9}
-\hspace{10pt} Same Hierarchy & 0,55 & 22 \\
+\hspace{10pt} Same Hierarchy & 0.55 & 22 \\
 \rowcolor[HTML]{FFCCC9}
-\hspace{10pt} Superclass & 0,20 & 74 \\
+\hspace{10pt} Superclass & 0.20 & 74 \\
 \rowcolor[HTML]{FFCCC9}
-\hspace{10pt} First Cousin & -0,02 & 53 \\
+\hspace{10pt} First Cousin & -0.02 & 53 \\
 \rowcolor[HTML]{FFCCC9}
-\hspace{10pt} Ancestor & -0,65 & 6 \\ \midrule
-\textbf{Common Class} & \textbf{0,01} & \textbf{2025}\\ \midrule
-\hspace{10pt} Same Method & 0,01 & 762  \\
-\hspace{10pt} Same Class & 0,01 & 1263 \\ \midrule
-\textbf{Unrelated} & \textbf{-0,02} & \textbf{688}\\ \midrule
-\hspace{10pt} No Direct Superclass & 0,08 & 289 \\
-\hspace{10pt} External Superclass & -0,02 & 225  \\
+\hspace{10pt} Ancestor & -0.65 & 6 \\ \midrule
+\textbf{Common Class} & \textbf{0.01} & \textbf{2,025}\\ \midrule
+\hspace{10pt} Same Method & 0.01 & 762  \\
+\hspace{10pt} Same Class & 0.01 & 1,263 \\ \midrule
+\textbf{Unrelated} & \textbf{-0.02} & \textbf{688}\\ \midrule
+\hspace{10pt} No Direct Superclass & 0.08 & 289 \\
+\hspace{10pt} External Superclass & -0.02 & 225  \\
 \rowcolor[HTML]{FFCCC9}
-\hspace{10pt} No Indirect Superclass & -0,04 & 30  \\
-\hspace{10pt} External Ancestor & -0,26 & 144  \\ \midrule
-\textbf{Common Interface} & \textbf{-0,11} & \textbf{283} \\ \midrule
-\hspace{10pt} Same Direct Interface & 0,02 & 160 \\
-\hspace{10pt} Same Indirect Interface & -0,31 & 123
+\hspace{10pt} No Indirect Superclass & -0.04 & 30  \\
+\hspace{10pt} External Ancestor & -0.26 & 144  \\ \midrule
+\textbf{Common Interface} & \textbf{-0.11} & \textbf{283} \\ \midrule
+\hspace{10pt} Same Direct Interface & 0.02 & 160 \\
+\hspace{10pt} Same Indirect Interface & -0.31 & 123
 \end{tabular}
@@
 \subsection{Refactoring}
+In Fig.~\ref{fig:duplication} we see an increase in maintainability for refactoring larger clone classes.
+The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie around 28 tokens.
+There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.
+
+In Table \ref{tab:relation_refactor} we see the results regarding refactorings that are applied to clones with diverse relations.
+We see that most refactored clones are in a common class, over 54\%.
+This is significantly more than the percentage of clones in the common class relation as reported in Table~\ref{tab:relation}.
+Meanwhile, the number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% -> 18\%).
+The main reason for this is that refactoring unrelated clones can change the relation of other clones in the same system.
+If we create a superclass abstraction to refactor an unrelated clone, other clones in those classes that were previously unrelated might become related.
+
+The maintainability scores displayed in Table \ref{tab:relation_refactor} show that the most favorable clone to refactor are clones with a Sibling relation.
+The most unfavorable is to refactor clones to interfaces.
+
+Regarding the return type of refactored clones, we see in Table \ref{tab:return} that this has no major impact on maintainability.
+A method call to the extracted method that is directly returned and no return type extracted methods are slightly more favorable than the others.
+We think the main reason that the ``Return'' category is on top is that when a variable is declared at the end of the cloned fragment, CloneRefactor directly returns its value and removes the declaration.
+This decreases volume slightly.
+
+A higher number of parameters directly influences the corresponding metric.
+Because of this, we see in Fig.~\ref{fig:arguments} that more parameters negatively influence maintainability.
+Not only the number of parameters metric is negatively influenced, more method parameters also increase volume for the extracted method and each of the calls to it.
+Because of that, we see that the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.
 

### 2019-08-15 icse/paper.tex
Conclusion

@@
 8\% of clones span several methods, which often require refactorings on a more architectural level.
+6\% of clones span only global variables, requiring an abstraction to encapsulate these data declarations.
+Only 4\% of clones span a full declaration (method, class, constructor, etc.).
 
@@
 \section{Conclusion}
+We defined refactorable clones and created a tool to detect and refactor them.
+We measured statistical data with this tool over a large corpus of open source Java software systems to get more information about the context of clones and how refactoring them influences system maintainability.
 
-\section*{Acknowledgment}
+We defined two aspects as part of the context of a clone: relation and contents.
+Regarding relations, we found that most clones are found in the same class, over 37\%.
+About 24\% of clones are in the same inheritance hierarchy.
+Another 24\% of clones are unrelated.
+The final 7\% of clones have the same interface.
+Regarding contents, over 74\% of clones span part of a method.
+About 8\% span several methods.
+Only 4\% of clones span a declaration (method, class, etc.) fully.
+
+We built a tool that can automatically apply refactorings to 28\% of clones in our corpus using the ``Extract Method'' refactoring technique.
+The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, for instance when code outside a method is part of a clone.
+
+We measured four maintainability metrics before- and after applying each refactoring to determine the impact of each refactoring on system maintainability.
+We found that the most prominent factor influencing maintainability is the size of the clone.
+We found that the threshold lies at a clone volume of 29 tokens per clone instance for system maintainability to increase after refactoring the clone.
+Another factor with a major impact on maintainability is the amount of parameters that the extracted method requires to get all required data.
+We noticed that the inheritance relation of the clone and the return value of the extracted method has only a minor impact on system maintainability.
+
+\section*{Acknowledgments}
 We would like to thank the Software Improvement Group for their continuous support in this project.

### 2019-08-15 icse/paper.tex
Imaginary TODOs

@@
 \subsubsection{Impact on maintainability metrics} \label{sec:metrics}
-We measure the impact on maintainability metrics of the refactored source code for each clone class that is refactored.
+CloneRefactor measures the impact on maintainability metrics of the refactored source code for each clone class that is refactored.
 These metrics are derived from Heitlager et al.
@@
 
-In this case we are dealing with single refactorings and we want to measure the maintainability impact of such a small change.
+To determine whether the maintainability improves when refactoring a single clone, we need to measure the impact of small-grained changes.
 Because of that, we measure only a subset of the metrics \cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
 The subset of metrics we decided to focus on are all metrics that are measured on method level (as the other metrics show a lesser impact on the maintainability for these small changes).
-These metrics are
+These metrics are:
 \begin{itemize}
@@
 %To what extent can found clones be refactored through method extraction, without requiring additional transformations.
-Table \ref{tab:refactorability} shows to what extend clone classes can be refactored by using the ``Extract Method'' refactoring technique.
+Table~\ref{tab:refactorability} shows to what extend clone classes can be refactored by using the ``Extract Method'' refactoring technique.
 The second column shows our measurements for the complete systems (just like the former experiments).
@@
 \subsubsection{Relation}
-Table \ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability.
+Table~\ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability.
 We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance.
@@
 \subsubsection{Return Value}
-Table \ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.
+Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.
 
@@
 \subsubsection{Parameters}
-Figure \ref{fig:arguments} shows how an increase in parameters lowers the maintainability of the refactored code.
+Fig.~\ref{fig:arguments} shows how an increase in parameters lowers the maintainability of the refactored code.
 On the primary x-axis the maintainability is displayed, the secundary x-axis shows the amount of refactorings and the y-axis shows the amount of parameters.
@@
 
-In Table \ref{tab:relation_refactor} we see the results regarding refactorings that are applied to clones with diverse relations.
+In Table~\ref{tab:relation_refactor} we see the results regarding refactorings that are applied to clones with diverse relations.
 We see that most refactored clones are in a common class, over 54\%.
@@
 
-Regarding the return type of refactored clones, we see in Table \ref{tab:return} that this has no major impact on maintainability.
+Regarding the return type of refactored clones, we see in Table~\ref{tab:return} that this has no major impact on maintainability.
 A method call to the extracted method that is directly returned and no return type extracted methods are slightly more favorable than the others.

### 2019-08-15 icse/paper.tex
Spelling and such

@@
 \begin{abstract}
-Duplication in source code is often seen as one of the most harmful types of technical debt, because it increases the size of the codebase and creates implicit dependencies between fragments of code.
+Duplication in source code is often seen as one of the most harmful types of technical debt because it increases the size of the codebase and creates implicit dependencies between fragments of code.
 To remove such anti-patterns, a developer should refactor the codebase.
-There are many tools that assist in this process.
-The thresholds and prioritization of the clones detected by such tools can be improved by considering the maintainability of the codebase after a detected clone would be refactored.
+The thresholds and prioritization of the clones detected by current clone detection tools can be improved by considering the maintainability of the codebase after a detected clone would be refactored.
+
 We perform an exploratory study into the data that can be gathered from comparing before- and after snapshots of an automatically refactored system.
-
-In this study, we define clones that can be refactored.
-We propose a tool to detect such clones and automatically refactor a subset of them.
+We propose a tool to detect clones, analyze their context and automatically refactor a subset of them.
 We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the systems.
-These metrics are system size, cyclomatic complexity \cite{mccabe1976complexity}, duplication and number of method parameters.
-On basis of these results, we decide which clones improve system design and thus should be refactored.
+These metrics are system size, cyclomatic complexity, duplication and number of method parameters.
+On the basis of these results, we decide which clones improve system design and thus should be refactored.
 %We identified a set of four factors that influence the maintainability impact of clones.
@@
 By using these four factors, we can suggest only clones that will improve maintainability when refactored and prioritize them accordingly.
-
 Given these maintainability influencing factors and their effect on the source code, we measure their impact over a large corpus of open source Java projects.
@@
 \section{Introduction}
-Duplication in source code is often seen as one of the most harmful types of technical debt, because it increases the size of the codebase and create implicit dependencies between fragments of code \cite{ostberg2014automatically}.
+Duplication in source code is often seen as one of the most harmful types of technical debt because it increases the size of the codebase and creates implicit dependencies between fragments of code \cite{ostberg2014automatically}.
 Bruntink et al.~\cite{bruntink2005use} show that code clones can contribute up to 25\% of the code size.
 
-Current code clone detection detection techniques base their thresholds and prioritization on a limited set of metrics.
+Current code clone detection techniques base their thresholds and prioritization on a limited set of metrics.
 Often, clone detection techniques are limited to measuring the size of clones to determine whether they should be considered.
@@
 % Instead of defining clone types, I just define how we can ensure that clones can be refactored.
-I do not plan to differentiate between T1R, T2R and T3R here, because I think it makes the paper confusing.
+I do not plan to differentiate between T1R, T2R, and T3R here, because I think it makes the paper confusing.
 % To be honest, I'm not even sure how relevant it is to name the literature clone types.
-Maybe not focus on their shortcomings, but just start from the core (sourcecode) and define how we can get to refactorable clones.
+Maybe not focus on their shortcomings, but just start from the core (source code) and define how we can get to refactorable clones.
 In literature, several clone type definitions have been used to argue about duplication in source code \cite{roy2007survey}.
@@
 \begin{itemize}
-  \item Compare variable references not only by their name, but also by their type.
+  \item Compare variable references not only by their name but also by their type.
   \item Compare referenced types by their fully qualified identifier (FQI). The FQI of a type reference describes the full path to where it is declared.
@@
   \item \textbf{Variables}: Only if all varying variables in a clone class have the same type.
-  \item \textbf{Method references}: Only if the return value of referenced method match (or are not used).
+  \item \textbf{Method references}: Only if the return value of referenced methods match (or are not used).
 \end{itemize}
@@
 %Explain type 3, why it is not always refactorable, solution
-Sometimes, when fragments are duplicated, a statement in inserted or changed severely for the code to fit its new context.
+Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context \cite{roy2007survey}.
 When dealing with such a situation, there are several opportunities to refactor so-called ``gapped clones''.
@@
 To automate the process of refactoring clones, we propose a tool named CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
-This tool goes through a 3-step process in order to refactor clones.
+This tool goes through a 3-step process to refactor clones.
 This process is displayed in Fig.~\ref{fig:clonerefactorflow}.
@@
 After clones are detected, we map the context of these clones.
-We have identifier three properties of clones as their context: relation and contents.
-We identify categories for each of these properties, to get a detailed insight in the context of clones.
+We have identified three properties of clones as their context: relation and contents.
+We identify categories for each of these properties, to get a detailed insight into the context of clones.
 
@@
 We define the following categories to map the relation between clone instances in a clone class.
-These categories do not map external classes (classes outside the project, for instance belonging to a library) unless explicitly stated:
+These categories do not map external classes (classes outside the project, for instance, belonging to a library) unless explicitly stated:
 \begin{itemize}
@@
 \subsection{Refactoring}
-CloneRefactor can refactor clones using the ``Extract Method'' refactoring technique. In this section we show which clones we refactor and how we apply these transformations.
+CloneRefactor can refactor clones using the ``Extract Method'' refactoring technique. In this section, we show which clones we refactor and how we apply these transformations.
 
@@
 % Show my categories to show what clones can be dealt with by method extraction.
-There are several influencing factors that may obstruct the possibility to extract code to a new method:
+Several influencing factors may obstruct the possibility to extract code to a new method:
 \begin{itemize}
@@
 The paper \cite{heitlager2007practical} measures volume as lines of code.
-As with duplication, we use the amount of tokens instead.
+As with duplication, we use the number of tokens instead.
 \item \textbf{Complexity}: Heitlager et al.
@@
 The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.
-\item \textbf{Method Interface Size}: The amount of parameters that a method has.
+\item \textbf{Method Interface Size}: The number of parameters that a method has.
 If a method has many parameters, the code may become harder to understand and it is an indication that data is not encapsulated adequately in objects \cite{fowler2018refactoring}.
@@
 \section{Experimental setup}
-In this section we describe the setup of our experiments.
+In this section, we describe the setup of our experiments.
 
@@
 
-CloneRefactor requires all libraries of the projects it analyses, in order to find the full paths of all referenced symbols in the source code (see Sec.~\ref{sec:t1r}).
+CloneRefactor requires all libraries of the projects it analyses, to find the full paths of all referenced symbols in the source code (see Sec.~\ref{sec:t1r}).
 Because of that requirement, we decided to filter the corpus to only projects using the Maven build automation system.
@@
 In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored.
-However, when clones are very small, they may never be able to improve maintainability because the detrimental effect of added volume of the newly created method exceeds the positive effect of removing duplication.
+However, when clones are very small, they may never be able to improve maintainability.
+The detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication.
 Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones cannot improve maintainability when refactored.
@@
 \subsection{Calculating a maintainability score}\label{sec:metricformula}
-In this study we use four metrics to determine maintainability \ref{sec:metrics}.
+In this study, we use four metrics to determine maintainability \ref{sec:metrics}.
 For our experiments, we want to aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
@@
 \section{Results}
-In this section we share the results of our experiments.
+In this section, we share the results of our experiments.
 
 \subsection{Clone context}
-% How many clones are there in certain contexts? Experiments for relation, location and context.
+% How many clones are there in certain contexts? Experiments for relation, location, and context.
 To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the clone context (see Sec.~\ref{sec:context}).
@@
 %To what extent can found clones be refactored through method extraction, without requiring additional transformations.
-Table~\ref{tab:refactorability} shows to what extend clone classes can be refactored by using the ``Extract Method'' refactoring technique.
+Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique.
 The second column shows our measurements for the complete systems (just like the former experiments).
@@
 For this, we will measure the maintainability of the refactored source code over different thresholds.
-These thresholds range from minimum clone size, variability and gap size.
-In our corpus CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Sec.~\ref{sec:metrics}).
+These thresholds range from minimum clone size, variability, and gap size.
+In our corpus, CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Sec.~\ref{sec:metrics}).
 Using the presented formulas (see Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
@@
 On the secondary axis the amount of refactorings that have refactored a clone with the specified amount of tokens is displayed (e.g.
-the amount of datapoints the data is based on).
-As the amount of datapoints decreases, the datapoints gain less statistical significance.
+the amount of data points the data is based on).
+As the amount of data points decreases, the datapoints gain less statistical significance.
 
@@
 The volume of the clone is the dominating factor regarding the maintainability increase/decrease of cloned code.
-Because of that, for our further experiments we filter out all refactorings with a token size smaller than 18 because otherwise the small clones dominate the results and turn all results towards unmaintainable.
+Because of that, for our further experiments, we filter out all refactorings with a token size smaller than 18 because otherwise the small clones dominate the results and turn all results towards unmaintainable.
 
@@
 Fig.~\ref{fig:arguments} shows how an increase in parameters lowers the maintainability of the refactored code.
-On the primary x-axis the maintainability is displayed, the secundary x-axis shows the amount of refactorings and the y-axis shows the amount of parameters.
+On the primary x-axis, the maintainability is displayed.
+The secondary x-axis shows the number of refactorings.
+The y-axis shows the number of parameters.
 
@@
 \section{Discussion}
-In this section we discuss the results of our experiments.
+In this section, we discuss the results of our experiments.
 
@@
 Regarding clone context, our results indicate that most clones (37\%) are in a common class.
-This is favorable for refactoring, because the extracted method does not have to be moved after extraction.
+This is favorable for refactoring because the extracted method does not have to be moved after extraction.
 24\% of clones are in a common hierarchy.
 These refactorings are also often favorable.
-Also 24\% of clones are unrelated, which is often unfavorable because it often requires a more comprehensive refactoring.
+Another 24\% of clones are unrelated, which is often unfavorable because it often requires a more comprehensive refactoring.
 15\% of clones are in an interface.
@@
 
-The maintainability scores displayed in Table \ref{tab:relation_refactor} show that the most favorable clone to refactor are clones with a Sibling relation.
+The maintainability scores displayed in Table~\ref{tab:relation_refactor} show that the most favorable clones to refactor are clones with a Sibling relation.
 The most unfavorable is to refactor clones to interfaces.
+However, the differences in maintainability in this table are generally small; there is no indication that relations have a major impact on the maintainability of clones.
 
@@
 We think the main reason that the ``Return'' category is on top is that when a variable is declared at the end of the cloned fragment, CloneRefactor directly returns its value and removes the declaration.
-This decreases volume slightly.
+This decreases the volume slightly.
 
@@
 Because of this, we see in Fig.~\ref{fig:arguments} that more parameters negatively influence maintainability.
-Not only the number of parameters metric is negatively influenced, more method parameters also increase volume for the extracted method and each of the calls to it.
-Because of that, we see that the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.
+Not only the number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
+Because of that, we see that trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.
 
@@
 We defined refactorable clones and created a tool to detect and refactor them.
-We measured statistical data with this tool over a large corpus of open source Java software systems to get more information about the context of clones and how refactoring them influences system maintainability.
+We measured statistical data with this tool over a large corpus of open-source Java software systems to get more information about the context of clones and how refactoring them influences system maintainability.
 
@@
 We found that the threshold lies at a clone volume of 29 tokens per clone instance for system maintainability to increase after refactoring the clone.
-Another factor with a major impact on maintainability is the amount of parameters that the extracted method requires to get all required data.
+Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data.
 We noticed that the inheritance relation of the clone and the return value of the extracted method has only a minor impact on system maintainability.

### 2019-08-16 sections/background.tex
Sander

@@
 \subsection{Type 4 clones}
-For this study we have chosen to take type 4 clones out of the scope, because they are both hard to detect and hard to refactor.
+For this study we have chosen to take type 4 clones out of the scope, because they are both hard to detect and hard to refactor. % TODO: Sander - why is this the case?
 A study by Kodhai et al \cite{kodhai2013method} looks into the distribution of the different types of clones in several open source systems (see table 6 of his study).
@@
 Because of that, we can conclude that type 4 clones are relatively less relevant to study.
+% TODO: Sander - Deze subsectie wil ik wel even over hebben, loopt niet helemaal lekker maar niet zo makkelijk uit te leggen
 
@@
 \subsection{Clone refactoring in relationship to its context}
+% TODO: Sander - Deze subsectie lijkt hier niet helemaal op zn plek
 How to refactor clones is highly dependent on their context.
@@
 \section{(Object-Oriented) Programming Languages}
+% TODO: Sander - leg ook nog even in 1 zin uit wat een lezer aan al deze info heeft
 In this section we describe the relevant parts of the programming languages we research and experiment on.

### 2019-08-16 sections/introduction.tex
Sander

@@
 \label{ch:introduction}
+% TODO: Sander - What is refactoring? Hier zeg je meteen waarvoor het gebruikt wordt
 Refactoring is used to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
@@
 However, there are also refactoring opportunities that are rather trivial and repetitive to execute. 
+% De zien hierna staat ook al in laatste alineas, past minder goed binnen intro imo
 In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
@@
 Bruntink et al.~\cite{bruntink2005use} show that code clones can contribute up to 25\% of the code size.
+% TODO: Sander - why is it bad to increase code size (i know ;) but reader might not)
 
@@
 \section{Problem statement}
-In this section we describe the problem we address with this study and the research questions that we answer in order to contribute to solving the problem.
+In this section we describe the problem we address in this study and the research questions that we answer in order to contribute to solving the problem.
 
@@
 \begin{itemize}
-	\item Find refactoring candidates, either tool-assisted or manually.
+	\item Find refactoring candidates, either tool-assisted or manually. % TODO: Sander - is tool assisted niet ook beetje manual? lijkt meer tool-assisted vs fully manual of iets
 	\item Refactor identified candidates, either tool-assisted or manually.
@@
 \cite{bavota2012does} shows that the process of refactoring often leaves side effects in the code.
-This study reports that refactorings involving hierarchies (e.g., pull up method), tend to induce faults very frequently.
-\textit{This suggests more accurate code inspection or testing activities when such specific refactorings are performed.} Such specific refactorings often have to be used when dealing with duplication in software \cite{fowler2018refactoring, fontana2015duplicated}.
+This study reports that refactorings involving hierarchies (e.g., pull up method) % TODO: Sander -unsure of pull up method bekende term is, miss "creating a new method in a superclass"
+, tend to induce faults very frequently. \textit{This suggests more accurate code inspection or testing activities % TODO: Sander - .. are needed? 
+when such specific refactorings are performed.} Such specific refactorings often have to be used when dealing with duplication in software \cite{fowler2018refactoring, fontana2015duplicated}.
 Because of that, refactoring code clones has been empirically proven to cause bugs or other side effects in code.
@@
 Refactoring often includes tradeoffs between design alternatives.
-With some code clones, the refactored alternative is worse maintainable than keeping the duplication \cite{kapser2006cloning, aversano2007clones, hotta2010duplicate, kim2005empirical, krinke2007study, saha2010evaluating}.
+With some code clones, the refactored alternative is less maintainable than keeping the duplication \cite{kapser2006cloning, aversano2007clones, hotta2010duplicate, kim2005empirical, krinke2007study, saha2010evaluating}.
 In this study, we analyze the maintainability of refactored code clones, in order to improve the suggestion of code clones that should be refactored.
@@
 assisting in the refactoring process.
-The problem is that these tools have no limited insight on the impact of refactoring such clones on the design of the software.
+The problem is that these tools have no limited % TODO: Sander -of limited of no, niet beide ;)
+insight on the impact of refactoring such clones on the design of the software.
 In this study, we can analyze a before- and after-refactoring snapshot of the code to determine the impact.
@@
 \section{Scope}
+% TODO: Sander - iets over OOP hier?
 In this study, we perform research efforts to be able to detect refactorable clones.
@@
 In Chapter~\ref{chap:clonetypes} we list shortcomings with clone definitions from literature and propose a set of clone type definitions which can be automatically refactored.
+% TODO: Sander - Nu zeg je dat de definities automatisch gerefactored kunnen worden
 In Chapter \ref{ch:clonerefactor} we propose a tool to detect, analyze and automatically refactor such clones that can be refactored.

### 2019-08-16 sections/research.tex
Sander

@@
 \chapter{Defining refactoring-oriented clone types}\label{chap:clonetypes}
-In Section~\ref{chap:backgroundclonetypes} we introduced the four clone types as defined in literature.
-These simple definitions are suitable for analysis of a codebase.
-Their detection results in simple to understand numbers to argue about a codebase.
+In Section~\ref{chap:backgroundclonetypes} we introduced the four clone types as defined in literature. These simple % TODO: Sander - why are they simple, might just remove that word
+definitions are suitable for analysis of a codebase. Their detection results in simple to understand numbers to argue about a codebase. % TODO: Sander -this seems like an opinion
 However, these clone types have a few flaws which makes it hard to argue to what extend two fragments of code can and should be refactored.
@@
 
-We also look into clone detection tools for their suitability to support the proposed clone type definitions.
-We selected a few criteria  Most clone detection tools support these definitions of clone types.
+We also look into clone detection tools for their suitability to support the proposed clone type definitions. We selected a few criteria % TODO: Sander -...?
+Most clone detection tools support these definitions of clone types.
 However, many of these tools use a vastly different approach.
@@
 Even though they operate on the same type definitions, the tools used in this study yield different results.
+% TODO: Sander - hier mist nog conclusie van dit stukje
 
@@
 Clones by these definitions can relatively easily and efficiently be detected.
+% TODO: Sander - compared to?
 This has allowed for large scale analyses of duplication~\cite{livieri2007very}.
@@
 These definitions address problems of the corresponding literature definitions.
-The ``R'' stands for refactoring-oriented (and may be less useful for other analyses).
+The ``R'' stands for refactoring-oriented (and may be less useful for other analyses) % TODO: Sander - zou dat laatste remark miss weglaten of echt uitleggen.
 

### 2019-08-16 sections/discussion.tex

@@
 In this chapter, we discuss the results of our research and experiments.
+% TODO: Sander - ik mis ergens in chapter nog interpretatie van je resultaten van H6, of heb ik iets gemist?
 
@@
 In this study, we proposed a set of clone type definitions for which a refactoring opportunity is known.
+% TODO: Sander - is known is beetje gek
+% TODO: Sander - zou ook uitleggen waarom we nieuwe definities nodig hadden
 We based these clone type definitions on the clone type definitions that are commonly used in literature.
@@
 An example of this is displayed in Figure~\ref{fig:samereturn}.
-The only thing to watch out for is method that have side effects.
+The only thing to watch out for is method that has side effects.
 Because methods may be executed in another point during execution, this might affect the functionality of the code.
+% TODO: Sander - how would you try to solve this?
 
@@
 
-\section{Experimental setup}
+\section{Experimental setup}% TODO: Sander - deze sectie is gek, soort combinatie van opzet en threats to validity, het kan wel maar loopt niet super lekker met het geheel
 In this section we discuss the setup of our experiments. We discuss alternative setups that could lead to other perspectives on the problem addressed.

### 2019-08-16 icse/paper.tex
Abstract

@@
 Duplication in source code is often seen as one of the most harmful types of technical debt because it increases the size of the codebase and creates implicit dependencies between fragments of code.
-To remove such anti-patterns, a developer should refactor the codebase.
-The thresholds and prioritization of the clones detected by current clone detection tools can be improved by considering the maintainability of the codebase after a detected clone would be refactored.
+To remove such anti-patterns, the codebase should be refactored.
+Many tools aid in the detection process of such duplication problems, but failed to determine whether a duplicate fragment would improve the maintainability of the codebase when refactored.
 
@@
 We propose a tool to detect clones, analyze their context and automatically refactor a subset of them.
-We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the systems.
-These metrics are system size, cyclomatic complexity, duplication and number of method parameters.
+We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the system.
 On the basis of these results, we decide which clones improve system design and thus should be refactored.
@@
 Given these maintainability influencing factors and their effect on the source code, we measure their impact over a large corpus of open source Java projects.
-This results in a set of thresholds by which clones can be found that should be refactored to improve system maintainability.
+%This results in a set of thresholds by which clones can be found that should be refactored to improve system maintainability.
+
+We have identified that the size of the duplication problem is the biggest influencing factor on system maintainability.
+We found that the majority of duplicates spanning 29 or more tokens improve maintainability when refactored.
+Another maintainability influencing factor is the amount of data that needs to be passed to the merged location of the duplicate.
 \end{abstract}

### 2019-08-16 icse/paper.tex
Introduction

@@
 \section{Introduction}
-Duplication in source code is often seen as one of the most harmful types of technical debt because it increases the size of the codebase and creates implicit dependencies between fragments of code \cite{ostberg2014automatically}.
-Bruntink et al.~\cite{bruntink2005use} show that code clones can contribute up to 25\% of the code size.
+Duplicate fragments in source code (also named ``code clones'') are often seen as one of the most harmful types of technical debt \cite{fowler2018refactoring}.
+Duplicate fragments create implicit dependencies that make the code harder to maintain as the resolution of erroneous behaviour in one location may have to be applied to all the cloned code as well \cite{ostberg2014automatically}.
+Apart from that, code clones can contribute up to 25\% of the code size~\cite{bruntink2005use}.
 
@@
 In this study, we define a technique to detect clones such that they can be refactored.
-We evaluate the context of clones to determine refactoring techniques are required to refactor clones in a specific context.
+We evaluate the context of clones to determine which refactoring techniques are required to refactor clones in a specific context.
 We propose a tool for the automated refactoring of a subset of the detected clones, by extracting a new method out of duplicated code.
+
+We use automated refactoring to compare the maintainability of the before- and after snapshots of a codebase for each duplication problem that is refactored.
+This gives us insight into whether clones detected by certain thresholds should be refactored to improve the maintainability of the codebase.
+This allows for more accurate suggestion of code clones for refactoring and can provide assistance in the refactoring process.
 

### 2019-08-16 icse/paper.tex
Survey

@@
 % The tool: Detect Clones, Map Context, Refactor.
+To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques \cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
+We created a set of control projects to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
+None of the surveyed tools \cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing} seemed suitable, because of which we decided to implement our own tool.
+
 To automate the process of refactoring clones, we propose a tool named CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.

### 2019-08-16 icse/paper.tex
Paper

@@
 Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context \cite{roy2007survey}.
-When dealing with such a situation, there are several opportunities to refactor so-called ``gapped clones''.
+When dealing with such a situation, there are several opportunities to refactor so-called ``gapped clones'' \cite{ueda2002detection, zhao2018automatic}.
 ``Gapped clones'' are two clone instances separated by a ``gap'' of non-cloned statement(s).
@@
 \end{itemize}
-Again, a trade-off is at play, as these solutions increase the complexity in favor of removing a clone.
+For both refactoring techniques a trade-off is at play, as these solutions increase the complexity and volume of the source code in favor of removing a clone.
 

### 2019-08-16 sections/experimentalsetup.tex
Thesis experimental setup

@@
 
-The result is a set of 674 Java projects that we use for all our experiments.
+\subsection{Resulting corpus}
+This procedure results in 2,267 Java projects including all their dependencies.
+The projects vary in size and quality.
+The total size of all projects is 14.210.357 lines (11,315,484 when excluding whitespace) over a total of 99,586 Java files.
+This is an average of 6,268 lines over an average of 44 files per project, 141 lines on average per file.
+The largest project in the corpus is \textit{VisAD} with 502,052 lines over 1,527.
+
+\section{Minimum clone size}
+In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored.
+However, when clones are very small, they may never be able to improve maintainability.
+The detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication.
+Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones cannot improve maintainability when refactored.
+
+\subsection{Calculating a maintainability score}\label{sec:metricformula}
+In this study, we use four metrics to determine maintainability \ref{sec:metrics}.
+For our experiments, we want to aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
+We base our aggregation on the following assumptions:
+\begin{itemize}
+  \item All metrics are equal in terms of weight towards system maintenance effort.
+  \item Higher values for the metrics imply lower maintainability.
+  \item The obtained increase of the metric divided by the average distance from zero over our corpus weights the metric equally against the other metrics.
+\end{itemize}
+We calculate the average deviation as follows:
+\begin{equation}\label{eq:scoredev}
+A = \frac{\sum_{x \in M} abs(x)}{|M|}
+\end{equation}
+Where \textit{M} is the multiset of all change in a certain metric for all refactorings over all systems in  obtained for a certain metric over our corpus and \textit{|M|} is the cardinality of this set.
+We then calculate the maintainability for a specific refactoring as follows:
+\begin{equation}\label{eq:scoreref}
+A_M = \frac{dup}{A_{dup}} + \frac{com}{A_{com}} + \frac{par}{A_{par}} + \frac{vol}{A_{vol}}
+\end{equation}
+Where \textit{dup} is the decrease in duplication, \textit{com} is the decrease in complexity, \textit{par} is the decrease is method parameters and \textit{vol} is the decrease in system volume after the refactoring is applied.
+When comparing the maintainability of a set of refactorings we divide the sum of the maintainability score by the amount of clone instances of all refactored clones in the set.

### 2019-08-16 icse/paper.tex
Fixed some

@@
 \subsection{Calculating a maintainability score}\label{sec:metricformula}
-In this study, we use four metrics to determine maintainability \ref{sec:metrics}.
-For our experiments, we want to aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
+In this study, we use four metrics to determine maintainability (see Sec.~\ref{sec:metrics}).
+For our experiments, we aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
 We base our aggregation on the following assumptions:

### 2019-08-16 sections/clonerefactor.tex
My mind twists

@@
 \section{JavaParser}
-A very important design decision for CloneRefactor is the usage of a library named JavaParser \cite{tomassetti2017javaparser}.
+An important design decision for CloneRefactor is the usage of a library named JavaParser \cite{tomassetti2017javaparser}.
 JavaParser is a Java library which allows to parse Java source files to an abstract syntax tree (AST\footnote{An AST is a tree-representation of a source code file.}).
@@
 
-\subsubsection{Impact on maintainability metrics}
+\subsubsection{Impact on maintainability metrics} \label{sec:metrics}
 We measure the impact on maintainability metrics of the refactored source code for each clone class that is refactored.

### 2019-08-16 sections/experimentalsetup.tex
My mind twists

@@
 \subsection{Calculating a maintainability score}\label{sec:metricformula}
-In this study, we use four metrics to determine maintainability \ref{sec:metrics}.
-For our experiments, we want to aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
+In this study, we use four metrics to determine maintainability (see Section~\ref{sec:metrics}).
+For our experiments, we aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
 We base our aggregation on the following assumptions:
@@
 \end{itemize}
-We calculate the average deviation as follows:
+We derived these assumptions partly from Heitlager et al~\cite{heitlager2007practical} and our own expert intuition.
+The validity of these metrics influences the validity of the conclusions we can draw from our data.
+Because of that, in our experiments we focus mainly on significant differences in maintainability to draw a conclusion.
+
+By dividing the obtained metric scores by the average distance from zero of all obtained values for a specific metric, we ensure that each metric is weighted equally towards the final maintainability score.
+We calculate the average distance from zero for all obtained values over our corpus as follows:
 \begin{equation}\label{eq:scoredev}
@@
 \end{equation}
-Where \textit{M} is the multiset of all change in a certain metric for all refactorings over all systems in  obtained for a certain metric over our corpus and \textit{|M|} is the cardinality of this set.
+Where \textit{M} is the multiset of all metric increase/decrease values for all refactorings applied to a certain metric over our corpus.
+\textit{|M|} is the cardinality of this multiset.
 We then calculate the maintainability for a specific refactoring as follows:

### 2019-08-16 icse/paper.tex
This part keeps boggling my mind

@@
 \end{itemize}
-We calculate the average deviation as follows:
+We derived these assumptions partly from Heitlager et al~\cite{heitlager2007practical} and our own expert intuition.
+The validity of these metrics influences the validity of the conclusions we can draw from our data.
+Because of that, in our experiments we focus mainly on significant differences in maintainability to draw a conclusion.
+
+By dividing the obtained metric scores by the average distance from zero of all obtained values for a specific metric, we ensure that each metric is weighted equally towards the final maintainability score.
+We calculate this average distance as follows:
 \begin{equation}\label{eq:scoredev}

### 2019-08-16 icse/paper.tex
Added some results
Should also remove some though

@@
 % How many clones are there in certain contexts? Experiments for relation, location, and context.
-To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the clone context (see Sec.~\ref{sec:context}).
+To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones (see Sec.~\ref{sec:context}).
 

### 2019-08-16 sections/experimentalsetup.tex
This part keeps boggling my mind
Added some results
Should also remove some though

@@
 
-\subsection{Calculating a maintainability score}\label{sec:metricformula}
+\section{Calculating a maintainability score}\label{sec:metricformula}
 In this study, we use four metrics to determine maintainability (see Section~\ref{sec:metrics}).
@@
 By dividing the obtained metric scores by the average distance from zero of all obtained values for a specific metric, we ensure that each metric is weighted equally towards the final maintainability score.
-We calculate the average distance from zero for all obtained values over our corpus as follows:
+We calculate this average distance as follows:
 \begin{equation}\label{eq:scoredev}

### 2019-08-16 sections/results.tex
working on various things
Added some results
Should also remove some though

@@
 \chapter{Results}\label{ch:results}
-In this chapter, we present the results of our experiments.
+In this chapter, we present the results of our experiments. All these results were obtained using CloneRefactor.
 
@@
 
-\section{Thresholds} \label{sec:thresholds}
-\todo{todo}
+\subsection{Clone context}
+% How many clones are there in certain contexts? Experiments for relation, location, and context.
+To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones (see Sec.~\ref{sec:context}).
+
+\subsubsection{Relation}
+Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Sec.~\ref{sec:relation}).
+
+\begin{table}[H]
+\centering
+\begin{tabular}{@{}llll@{}}
+\toprule
+\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} \\ \midrule
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
+ & Same Method & 8,955 &  \\ \midrule
+\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342} \\ \cmidrule(lr){2-3}
+ & Superclass & 2,616 &  \\ \cmidrule(lr){2-3}
+ & First Cousin & 1,219 &  \\ \cmidrule(lr){2-3}
+ & Common Hierarchy & 720 &  \\ \cmidrule(lr){2-3}
+ & Ancestor & 199 &  \\ \midrule
+\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314} \\ \cmidrule(lr){2-3}
+ & External Superclass & 4,525 &  \\ \cmidrule(lr){2-3}
+ & External Ancestor & 3,347 &  \\ \cmidrule(lr){2-3}
+ & No Indirect Superclass & 1,765 &  \\ \midrule
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} \\ \cmidrule(lr){2-3}
+ & Same Indirect Interface & 5,552 &  \\ \bottomrule
+\end{tabular}
+\caption{Number of clone classes per clone relation}
+\label{tab:relation}
+\end{table}
+
+\subsubsection{Contents}
+Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Sec.~\ref{sec:contents}).
+
+\begin{table}[H]
+\centering
+\begin{tabular}{@{}llll@{}}
+\toprule
+\textit{\textbf{Category}} & \textit{\textbf{Contents}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
+\multirow{2}{*}{Partial} & Partial Method & 219,540 & \multirow{2}{*}{229,521} \\ \cmidrule(lr){2-3}
+ & Partial Constructor & 9,981 &  \\ \midrule
+\multirow{5}{*}{Full} & Full Method & 12,990 & \multirow{5}{*}{13,173} \\ \cmidrule(lr){2-3}
+ & Full Interface & 64 &  \\ \cmidrule(lr){2-3}
+ & Full Constructor & 58 &  \\ \cmidrule(lr){2-3}
+ & Full Class & 37 &  \\ \cmidrule(lr){2-3}
+ & Full Enum & 24 &  \\ \midrule
+\multirow{3}{*}{Other} & Several Methods & 22,749 & \multirow{3}{*}{53,773} \\ \cmidrule(lr){2-3}
+ & Only Fields & 17,700 &  \\ \cmidrule(lr){2-3}
+ & Other & 13,324 &  \\ \bottomrule
+\end{tabular}
+\caption{Number of clone instances for clone contents categories}
+\label{tab:contents}
+\end{table}
+
+\subsection{Extract Method}
+%To what extent can found clones be refactored through method extraction, without requiring additional transformations.
+Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique.
+The second column shows our measurements for the complete systems (just like the former experiments).
+The third column shows our measurements when restricting our search to method bodies.
+The amount that can be extracted increases because, when restricting our search to method bodies, we do not exclude declarations that can obstruct the possibility of method extraction (for instance a cloned method signature).
+
+\begin{table}[H]
+\centering
+\begin{tabular}{@{}lll@{}}
+\toprule
+\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{Method Body}} \\ \midrule
+Can Be Extracted & 24,157 & 26,109 \\
+Is Not A Partial Method & 21,625 & 0 \\
+Top-level AST-Node is not a Statement & 19,887 & 4,607 \\
+Spans Part of a Block & 12,964 & 13,460 \\
+Multiple Return Values & 5,622 & 6,131 \\
+Complex Control Flow & 1,106 & 1,216 \\ \bottomrule
+\end{tabular}
+\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique}
+\label{tab:refactorability}
+\end{table}
+
+\subsection{Refactoring}
+%I think the ultimate goal with this thesis is to do experiments with different clone thresholds.
+Which thresholds give clones that we should refactor?
+For this, we will measure the maintainability of the refactored source code over different thresholds.
+These thresholds range from minimum clone size, variability, and gap size.
+In our corpus, CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Sec.~\ref{sec:metrics}).
+Using the presented formulas (see Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
+In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.
+
+\subsubsection{Clone Token Volume}
+Figure \ref{fig:duplication} shows the obtained results when plotting the clone size (in tokens) vs the maintainability increase/decrease.
+On the secondary axis the amount of refactorings that have refactored a clone with the specified amount of tokens is displayed (e.g.
+the amount of data points the data is based on).
+As the amount of data points decreases, the datapoints gain less statistical significance.
+
+\begin{figure*}
+  \includegraphics[width=1\textwidth]{img/duplication}
+  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability. Maintainability on the primary axis and amount of refactorings on the secondary axis.}
+  \label{fig:duplication}
+\end{figure*}
+
+The volume of the clone is the dominating factor regarding the maintainability increase/decrease of cloned code.
+Because of that, for our further experiments, we filter out all refactorings with a token size smaller than 18 because otherwise the small clones dominate the results and turn all results towards unmaintainable.
+
+\subsubsection{Relation}
+Table~\ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability.
+We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance.
+
+\begin{table}[]
+\centering
+\begin{tabular}{@{}lll@{}}
+\toprule
+\textit{\textbf{Relation}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Maintainability\\ Score\end{tabular}}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Number of\\ Refactorings\end{tabular}}} \\ \midrule
+\textbf{Common Hierarchy} & \textbf{0.51} & \textbf{792} \\ \midrule
+\hspace{10pt} Sibling & 0.57 & 637 \\
+\rowcolor[HTML]{FFCCC9}
+\hspace{10pt} Same Hierarchy & 0.55 & 22 \\
+\rowcolor[HTML]{FFCCC9}
+\hspace{10pt} Superclass & 0.20 & 74 \\
+\rowcolor[HTML]{FFCCC9}
+\hspace{10pt} First Cousin & -0.02 & 53 \\
+\rowcolor[HTML]{FFCCC9}
+\hspace{10pt} Ancestor & -0.65 & 6 \\ \midrule
+\textbf{Common Class} & \textbf{0.01} & \textbf{2,025}\\ \midrule
+\hspace{10pt} Same Method & 0.01 & 762  \\
+\hspace{10pt} Same Class & 0.01 & 1,263 \\ \midrule
+\textbf{Unrelated} & \textbf{-0.02} & \textbf{688}\\ \midrule
+\hspace{10pt} No Direct Superclass & 0.08 & 289 \\
+\hspace{10pt} External Superclass & -0.02 & 225  \\
+\rowcolor[HTML]{FFCCC9}
+\hspace{10pt} No Indirect Superclass & -0.04 & 30  \\
+\hspace{10pt} External Ancestor & -0.26 & 144  \\ \midrule
+\textbf{Common Interface} & \textbf{-0.11} & \textbf{283} \\ \midrule
+\hspace{10pt} Same Direct Interface & 0.02 & 160 \\
+\hspace{10pt} Same Indirect Interface & -0.31 & 123
+\end{tabular}
+\caption{Influence on maintainability of refactoring clones by certain relations.}
+\label{tab:relation_refactor}
+\end{table}
+
+\subsubsection{Return Value}
+Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.
+
+\begin{table}[H]
+\centering
+\begin{tabular}{@{}lll@{}}
+\toprule
+\textit{\textbf{Return Value}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
+Return & 0.20 & 421 \\
+Void & 0.19 & 2052 \\
+Declare & 0.03 & 1318 \\
+\rowcolor[HTML]{FFCCC9}
+Assign & -1.29 & 3 \\ \bottomrule
+\end{tabular}
+\caption{Maintainability scores for different return values}
+\label{tab:return}
+\end{table}
+
+\subsubsection{Parameters}
+Fig.~\ref{fig:arguments} shows how an increase in parameters lowers the maintainability of the refactored code.
+On the primary x-axis, the maintainability is displayed.
+The secondary x-axis shows the number of refactorings.
+The y-axis shows the number of parameters.
+
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/arguments}
+  \caption{Influence of number of method parameters on system maintainability.}
+  \label{fig:arguments}
+\end{figure}
 
@@
 We analyzed the context of clones in a large corpus of open source projects.
-For these experiments, we used our CloneRefactor tool.
 These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in chapter \ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in chapter \ref{chap:clonelocation};  he content of clone instances are explained, measured and discussed in chapter \ref{chap:clonecontents}.
@@
 
-\section{Clone instance contents}\label{chap:clonecontents}
+\subsection{Clone instance contents}\label{chap:clonecontents}
 \todo{update these results}

### 2019-08-16 sections/discussion.tex
Added experiment result discussion

@@
 It would be valuable to have a control group rate the refactorings performed by CloneRefactor, as an extra form of input regarding the quality of the code transformation that CloneRefactor performs.
+
+\section{Results}
+In this section, we discuss the results of our experiments.
+
+\subsection{Clone Context}
+Regarding clone context, our results indicate that most clones (37\%) are in a common class.
+This is favorable for refactoring because the extracted method does not have to be moved after extraction.
+24\% of clones are in a common hierarchy.
+These refactorings are also often favorable.
+Another 24\% of clones are unrelated, which is often unfavorable because it often requires a more comprehensive refactoring.
+15\% of clones are in an interface.
+
+Regarding clone contents, 74\% of clones span part of a method body (77\% if we include constructors).
+8\% of clones span several methods, which often require refactorings on a more architectural level.
+6\% of clones span only global variables, requiring an abstraction to encapsulate these data declarations.
+Only 4\% of clones span a full declaration (method, class, constructor, etc.).
+
+\subsection{Extract Method}
+28\% of clones can be refactored using the ``Extract Method'' refactoring technique (50\% if we limit our searching scope to method bodies).
+About 25\% of clones do not span part of a method, because of which they cannot be refactored.
+Many clones (23\%) do not have a statement as top-level AST-Node.
+Upon manual inspection, we noticed that the main reason for this is clones in anonymous functions or anonymous classes.
+About 15\% of clones span only part of an AST-Node.
+
+\subsection{Refactoring}
+In Fig.~\ref{fig:duplication} we see an increase in maintainability for refactoring larger clone classes.
+The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie around 28 tokens.
+There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.
+
+In Table~\ref{tab:relation_refactor} we see the results regarding refactorings that are applied to clones with diverse relations.
+We see that most refactored clones are in a common class, over 54\%.
+This is significantly more than the percentage of clones in the common class relation as reported in Table~\ref{tab:relation}.
+Meanwhile, the number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% -> 18\%).
+The main reason for this is that refactoring unrelated clones can change the relation of other clones in the same system.
+If we create a superclass abstraction to refactor an unrelated clone, other clones in those classes that were previously unrelated might become related.
+
+The maintainability scores displayed in Table~\ref{tab:relation_refactor} show that the most favorable clones to refactor are clones with a Sibling relation.
+The most unfavorable is to refactor clones to interfaces.
+However, the differences in maintainability in this table are generally small; there is no indication that relations have a major impact on the maintainability of clones.
+
+Regarding the return type of refactored clones, we see in Table~\ref{tab:return} that this has no major impact on maintainability.
+A method call to the extracted method that is directly returned and no return type extracted methods are slightly more favorable than the others.
+We think the main reason that the ``Return'' category is on top is that when a variable is declared at the end of the cloned fragment, CloneRefactor directly returns its value and removes the declaration.
+This decreases the volume slightly.
+
+A higher number of parameters directly influences the corresponding metric.
+Because of this, we see in Fig.~\ref{fig:arguments} that more parameters negatively influence maintainability.
+Not only the number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
+Because of that, we see that trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.

### 2019-08-17 sections/background.tex
Results

@@
 \section{Code clone terminology}\label{sec:terminology}
-% The sets are actually definitions, NOT PROPERTIES. This should be clearer.
 Many studies present different definitions for code clone concepts.
@@
 N & Node \cite{jiang2007deckard} & Set of tokens.
-& \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range (R):} The range this node\\spans.\end{tabular} \\
+& \begin{tabular}[c]{@{}l@{}}A statement or declaration node\\in the AST of a codebase.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range (R):} The range this node\\spans.\end{tabular} \\
 \rowcolor[HTML]{EFEFEF}

### 2019-08-17 sections/discussion.tex

@@
 
+\subsection{Clone Types}
+In this section, we discuss the differences between clone types 1-3 and 1R-3R.
+In Figure \ref{fig:typeres} we see that the difference between T1R and T1 is relatively small (11\% more cloned nodes found for T1).
+Often textually equal code is also functionally equal.
+The difference between T2R and T2 is bigger (34.7\% more cloned nodes for T2).
+The main reason for this is that T2R does not allow any variability in types, wheareas T2 allows any variability in types.
+T3R and T3 only a little bit higher than T2R and T2.
+
 \subsection{Clone Context}

### 2019-08-17 sections/results.tex

@@
 \chapter{Results}\label{ch:results}
-In this chapter, we present the results of our experiments. All these results were obtained using CloneRefactor.
+In this chapter, we present the results of our experiments. We perform exploratory experiments to map the differences between clone types, contexts and refactoring opportunities.
 
 \section{Clone types}\label{sec:clonetypeexperiments}
-In this section we display the differences between clone type 1-3~\cite{roy2007survey} and type 1R-3R as proposed in Chapter \ref{chap:clonetypes}.
-When running our clone detection script over the corpus, we get the results displayed in Figure~\ref{fig:typeres}.
+In this section, we look into the differences between the different clone types that were introduced in Chapter \ref{chap:clonetypes}.
+
+\subsection{Found nodes}
+In this section, we display our results regarding the differences in found nodes between clone type 1-3~\cite{roy2007survey} and type 1R-3R.
+Figure~\ref{fig:typeres} shows the number of cloned nodes found over the entire corpus for the different clone types (the word ``Type'' is abbreviated as ``T'').
+For type 2R clones, we set the variability threshold (see Section~\ref{sec:variabilitythreshold}) to 10\%, meaning that no more than 10\% of expressions may differ between cloned fragments.
+For type 3 and 3R clones, we allow a gap of 20\% the clones surrounding it.
+
+\begin{figure}[H]
+  \centering
+  \begin{minipage}[b]{0.4\textwidth}
+    \includegraphics[width=\textwidth]{img/TypeResults}
+    \caption{Number of cloned nodes.}
+\label{fig:typeres}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[b]{0.4\textwidth}
+    \includegraphics[width=\textwidth]{img/DurationChart}
+    \caption{Duration in minutes of identifying clones for clone type definitions.}
+  \label{fig:performance}
+  \end{minipage}
+\end{figure}
 
@@
     \includegraphics[width=.5\columnwidth]{img/TypeResults}
-      \caption{Number of cloned declarations/statements.}
+      \caption{Number of cloned nodes.}
   \label{fig:typeres}
@@
 
-In this figure, the number of cloned nodes per clone type are displayed.
-The difference between T1R and T1 is small (10.9\%), because most often textually equal code is also functionally equal.
-The difference between T2R and T2 is bigger (34.7\%) because the T2R definition is more strict.
-T3R and T3 are similar to T2R and T2 because our dataset does not have so many gapped clones for the thresholds used.
-
+\subsection{Performance}
 We also measured the duration of finding clones by the different clone types.
@@
 
-\subsection{Clone context}
+\section{Clone context}
 % How many clones are there in certain contexts? Experiments for relation, location, and context.
@@
 
-\subsubsection{Relation}
+\subsection{Relation}
 Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Sec.~\ref{sec:relation}).
@@
 
-\subsubsection{Contents}
+\subsection{Contents}
 Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Sec.~\ref{sec:contents}).

### 2019-08-17 sections/discussion.tex
:)

@@
 
+Regarding performance (Figure~\ref{fig:performance}, there is a notable difference between the refactoring-oriented clone types and the literature clone types.
+Type 1R-3R take about 6 times longer to detect than type 1-3.
+The main reason for this is type resolution: finding the fully qualified identifiers of type-, variable- and method-references.
+
 \subsection{Clone Context}

### 2019-08-17 sections/results.tex
:)

@@
   \centering
-  \begin{minipage}[b]{0.4\textwidth}
+  \begin{minipage}[b]{0.5\textwidth}
     \includegraphics[width=\textwidth]{img/TypeResults}
@@
   \hfill
-  \begin{minipage}[b]{0.4\textwidth}
+  \begin{minipage}[b]{0.5\textwidth}
     \includegraphics[width=\textwidth]{img/DurationChart}
-    \caption{Duration in minutes of identifying clones for clone type definitions.}
+    \caption{Clone type performance.}
   \label{fig:performance}
@@
 
-\begin{figure}[H]
-  \centering
-    \includegraphics[width=.5\columnwidth]{img/TypeResults}
-      \caption{Number of cloned nodes.}
-  \label{fig:typeres}
-\end{figure}
-
 \subsection{Performance}
-We also measured the duration of finding clones by the different clone types.
+To map the viability of refactoring-oriented clone types for large scale clone detection, we measured the duration of finding clones by the different clone types.
 Figure~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types.
-Although this data is partly dependent on our implementation of the clone types, there is a notable difference between the refactoring-oriented clone types and the literature clone types.
-The reason for this is further explained in Section~\ref{chap:challenge}.
-
-\begin{figure}[H]
-  \centering
-    \includegraphics[width=.5\columnwidth]{img/DurationChart}
-    \caption{Duration in minutes of identifying clones for clone type definitions.}
-  \label{fig:performance}
-\end{figure}
+This figure shows the average duration of running CloneRefactor 10 times for a certain clone type.
+We ran these performance tests on the compute nodes of the DAS4 supercomputer \cite{bal2016medium}, which do not have many background processes severely affecting the results.
+The durations are of course dependent on our implementation of the clone types.
 

### 2019-08-17 sections/results.tex
Put in the new graphs

@@
 The durations are of course dependent on our implementation of the clone types.
+
+\subsection{Type 2R Variability Threshold}
+To determine the influence of the type 2R variability threshold on the amount of found nodes, we ran CloneRefactor for all variability percentages (0\% meaning no variance in expressions, 100\% meaning any variance in expression).
+Figure \ref{fig:t2rgraph} shows the results.
+
+\begin{figure}
+  \includegraphics[width=1\textwidth]{img/T2R}
+  \caption{Cloned nodes found for different Type 2R thresholds.}
+  \label{fig:t2rgraph}
+\end{figure}
+
+\subsection{Type 3R Gap Size Thresholds}
+To determine the influence of the type 3R gap size threshold on the amount of found nodes, we ran CloneRefactor for all gap size percentages between 0\% and 200\%.
+Figure \ref{fig:t3rgraph} shows the results.
+
+\begin{figure}
+  \includegraphics[width=1\textwidth]{img/T3R}
+  \caption{Cloned nodes and clone classes found for different Type 3R thresholds.}
+  \label{fig:t3rgraph}
+\end{figure}
 
@@
 
-\begin{figure*}
+\begin{figure}
   \includegraphics[width=1\textwidth]{img/duplication}
@@
   \label{fig:duplication}
-\end{figure*}
+\end{figure}
 

### 2019-08-17 sections/results.tex
Percentages relation

@@
   \centering
-  \begin{minipage}[b]{0.5\textwidth}
+  \begin{minipage}[b]{0.45\textwidth}
     \includegraphics[width=\textwidth]{img/TypeResults}
@@
   \hfill
-  \begin{minipage}[b]{0.5\textwidth}
+  \begin{minipage}[b]{0.45\textwidth}
     \includegraphics[width=\textwidth]{img/DurationChart}
@@
 
-\begin{figure}
+\begin{figure}[H]
   \includegraphics[width=1\textwidth]{img/T2R}
@@
 
-\begin{figure}
+\begin{figure}[H]
   \includegraphics[width=1\textwidth]{img/T3R}
@@
 % How many clones are there in certain contexts? Experiments for relation, location, and context.
-To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones (see Sec.~\ref{sec:context}).
+To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones (see Section~\ref{chap:contextsetup}).
 
 \subsection{Relation}
-Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Sec.~\ref{sec:relation}).
+Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Section~\ref{sec:relation}).
 
@@
 \centering
-\begin{tabular}{@{}llll@{}}
+\begin{tabular}{@{}lllll@{}}
 \toprule
-\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} \\ \midrule
-\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
- & Same Method & 8,955 &  \\ \midrule
-\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342} \\ \cmidrule(lr){2-3}
- & Superclass & 2,616 &  \\ \cmidrule(lr){2-3}
- & First Cousin & 1,219 &  \\ \cmidrule(lr){2-3}
- & Common Hierarchy & 720 &  \\ \cmidrule(lr){2-3}
- & Ancestor & 199 &  \\ \midrule
-\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314} \\ \cmidrule(lr){2-3}
- & External Superclass & 4,525 &  \\ \cmidrule(lr){2-3}
- & External Ancestor & 3,347 &  \\ \cmidrule(lr){2-3}
- & No Indirect Superclass & 1,765 &  \\ \midrule
-\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} \\ \cmidrule(lr){2-3}
- & Same Indirect Interface & 5,552 &  \\ \bottomrule
+\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} & \textit{\textbf{\%}} \\ \midrule
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} & \multirow{2}{*}{37.2\%} \\ \cmidrule(lr){2-3}
+ & Same Method & 8,955 & & \\ \midrule
+\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342}& \multirow{5}{*}{23.8\%} \\ \cmidrule(lr){2-3}
+ & Superclass & 2,616 & & \\ \cmidrule(lr){2-3}
+ & First Cousin & 1,219 & & \\ \cmidrule(lr){2-3}
+ & Common Hierarchy & 720 & & \\ \cmidrule(lr){2-3}
+ & Ancestor & 199 & & \\ \midrule
+\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314}& \multirow{4}{*}{23.7\%} \\ \cmidrule(lr){2-3}
+ & External Superclass & 4,525 & & \\ \cmidrule(lr){2-3}
+ & External Ancestor & 3,347 & & \\ \cmidrule(lr){2-3}
+ & No Indirect Superclass & 1,765 & & \\ \midrule
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} & \multirow{2}{*}{15.3\%} \\ \cmidrule(lr){2-3}
+ & Same Indirect Interface & 5,552 & & \\ \bottomrule
 \end{tabular}
@@
 \subsection{Contents}
-Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Sec.~\ref{sec:contents}).
+Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Section~\ref{sec:contents}).
 
@@
 These thresholds range from minimum clone size, variability, and gap size.
-In our corpus, CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Sec.~\ref{sec:metrics}).
-Using the presented formulas (see Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
+In our corpus, CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Section~\ref{sec:metrics}).
+Using the presented formulas (see Section~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Section~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
 In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.
@@
 
-\begin{figure}
+\begin{figure}[H]
   \includegraphics[width=1\textwidth]{img/duplication}

### 2019-08-17 sections/results.tex
More percentages relation

@@
 \centering
-\begin{tabular}{@{}lllll@{}}
+\begin{tabular}{@{}llllll@{}}
 \toprule
-\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} & \textit{\textbf{\%}} \\ \midrule
-\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} & \multirow{2}{*}{37.2\%} \\ \cmidrule(lr){2-3}
- & Same Method & 8,955 & & \\ \midrule
-\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342}& \multirow{5}{*}{23.8\%} \\ \cmidrule(lr){2-3}
- & Superclass & 2,616 & & \\ \cmidrule(lr){2-3}
- & First Cousin & 1,219 & & \\ \cmidrule(lr){2-3}
- & Common Hierarchy & 720 & & \\ \cmidrule(lr){2-3}
- & Ancestor & 199 & & \\ \midrule
-\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314}& \multirow{4}{*}{23.7\%} \\ \cmidrule(lr){2-3}
- & External Superclass & 4,525 & & \\ \cmidrule(lr){2-3}
- & External Ancestor & 3,347 & & \\ \cmidrule(lr){2-3}
- & No Indirect Superclass & 1,765 & & \\ \midrule
-\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} & \multirow{2}{*}{15.3\%} \\ \cmidrule(lr){2-3}
- & Same Indirect Interface & 5,552 & & \\ \bottomrule
+\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{\%}} & \textit{\textbf{Total}} & \textit{\textbf{\%}} \\ \midrule
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & 26.8\% & \multirow{2}{*}{31,848} & \multirow{2}{*}{37.2\%} \\ \cmidrule(lr){2-4}
+ & Same Method & 8,955 & 10.5\% & & \\ \midrule
+\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & 18.2\% & \multirow{5}{*}{20,342}& \multirow{5}{*}{23.8\%} \\ \cmidrule(lr){2-3}
+ & Superclass & 2,616 & 3.1\% & & \\ \cmidrule(lr){2-3}
+ & First Cousin & 1,219 & 1.4\% & & \\ \cmidrule(lr){2-3}
+ & Common Hierarchy & 720 & 0.8\% & & \\ \cmidrule(lr){2-3}
+ & Ancestor & 199 & 0.2\% & & \\ \midrule
+\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & 12.5\% & \multirow{4}{*}{20,314}& \multirow{4}{*}{23.7\%} \\ \cmidrule(lr){2-3}
+ & External Superclass & 4,525 & 5.3\% & & \\ \cmidrule(lr){2-3}
+ & External Ancestor & 3,347 & 3.9\% & & \\ \cmidrule(lr){2-3}
+ & No Indirect Superclass & 1,765 & 2.1\% & & \\ \midrule
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & 8.8\% & \multirow{2}{*}{13,074} & \multirow{2}{*}{15.3\%} \\ \cmidrule(lr){2-3}
+ & Same Indirect Interface & 5,552 & 6.5\% & & \\ \bottomrule
 \end{tabular}

### 2019-08-17 sections/results.tex
Same for the other table

@@
 \textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{\%}} & \textit{\textbf{Total}} & \textit{\textbf{\%}} \\ \midrule
-\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & 26.8\% & \multirow{2}{*}{31,848} & \multirow{2}{*}{37.2\%} \\ \cmidrule(lr){2-4}
+\multirow{2}{*}{Common Class} & Same Class & 22,893 & 26.8\% & \multirow{2}{*}{31,848} & \multirow{2}{*}{37.2\%} \\ \cmidrule(lr){2-4}
  & Same Method & 8,955 & 10.5\% & & \\ \midrule
-\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & 18.2\% & \multirow{5}{*}{20,342}& \multirow{5}{*}{23.8\%} \\ \cmidrule(lr){2-3}
- & Superclass & 2,616 & 3.1\% & & \\ \cmidrule(lr){2-3}
- & First Cousin & 1,219 & 1.4\% & & \\ \cmidrule(lr){2-3}
- & Common Hierarchy & 720 & 0.8\% & & \\ \cmidrule(lr){2-3}
+\multirow{5}{*}{Common Hierarchy} & Sibling & 15,588 & 18.2\% & \multirow{5}{*}{20,342}& \multirow{5}{*}{23.8\%} \\ \cmidrule(lr){2-4}
+ & Superclass & 2,616 & 3.1\% & & \\ \cmidrule(lr){2-4}
+ & First Cousin & 1,219 & 1.4\% & & \\ \cmidrule(lr){2-4}
+ & Common Hierarchy & 720 & 0.8\% & & \\ \cmidrule(lr){2-4}
  & Ancestor & 199 & 0.2\% & & \\ \midrule
-\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & 12.5\% & \multirow{4}{*}{20,314}& \multirow{4}{*}{23.7\%} \\ \cmidrule(lr){2-3}
- & External Superclass & 4,525 & 5.3\% & & \\ \cmidrule(lr){2-3}
- & External Ancestor & 3,347 & 3.9\% & & \\ \cmidrule(lr){2-3}
+\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & 12.5\% & \multirow{4}{*}{20,314}& \multirow{4}{*}{23.7\%} \\ \cmidrule(lr){2-4}
+ & External Superclass & 4,525 & 5.3\% & & \\ \cmidrule(lr){2-4}
+ & External Ancestor & 3,347 & 3.9\% & & \\ \cmidrule(lr){2-4}
  & No Indirect Superclass & 1,765 & 2.1\% & & \\ \midrule
-\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & 8.8\% & \multirow{2}{*}{13,074} & \multirow{2}{*}{15.3\%} \\ \cmidrule(lr){2-3}
+\multirow{2}{*}{Common Interface} & Same Direct Interface & 7,522 & 8.8\% & \multirow{2}{*}{13,074} & \multirow{2}{*}{15.3\%} \\ \cmidrule(lr){2-4}
  & Same Indirect Interface & 5,552 & 6.5\% & & \\ \bottomrule
@@
 \centering
-\begin{tabular}{@{}llll@{}}
+\begin{tabular}{@{}llllll@{}}
 \toprule
 \textit{\textbf{Category}} & \textit{\textbf{Contents}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
-\multirow{2}{*}{Partial} & Partial Method & 219,540 & \multirow{2}{*}{229,521} \\ \cmidrule(lr){2-3}
- & Partial Constructor & 9,981 &  \\ \midrule
-\multirow{5}{*}{Full} & Full Method & 12,990 & \multirow{5}{*}{13,173} \\ \cmidrule(lr){2-3}
- & Full Interface & 64 &  \\ \cmidrule(lr){2-3}
- & Full Constructor & 58 &  \\ \cmidrule(lr){2-3}
- & Full Class & 37 &  \\ \cmidrule(lr){2-3}
- & Full Enum & 24 &  \\ \midrule
-\multirow{3}{*}{Other} & Several Methods & 22,749 & \multirow{3}{*}{53,773} \\ \cmidrule(lr){2-3}
- & Only Fields & 17,700 &  \\ \cmidrule(lr){2-3}
- & Other & 13,324 &  \\ \bottomrule
+\multirow{2}{*}{Partial} & Partial Method & 219,540 & 74.05\% & \multirow{2}{*}{229,521}& \multirow{2}{*}{77.42\%} \\ \cmidrule(lr){2-4}
+ & Partial Constructor & 9,981 & 3.37\% & & \\ \midrule
+\multirow{5}{*}{Full} & Full Method & 12,990 & 4.38\% & \multirow{5}{*}{13,173}& \multirow{5}{*}{4,44\%} \\ \cmidrule(lr){2-4}
+ & Full Interface & 64 & 0.02\% & & \\ \cmidrule(lr){2-4}
+ & Full Constructor & 58 & 0.02\% & & \\ \cmidrule(lr){2-4}
+ & Full Class & 37 & 0.01\% & & \\ \cmidrule(lr){2-4}
+ & Full Enum & 24 & 0.01\% & & \\ \midrule
+\multirow{3}{*}{Other} & Several Methods & 22,749 & 7.67\% & \multirow{3}{*}{53,773} & \multirow{3}{*}{18.14\%} \\ \cmidrule(lr){2-4}
+ & Only Fields & 17,700 & 5.97\% & & \\ \cmidrule(lr){2-4}
+ & Other & 13,324 & 4.49\% & & \\ \bottomrule
 \end{tabular}

### 2019-08-17 sections/results.tex
Layout

@@
 
+\subsection{Location}
+Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Section~\ref{chap:clonecontents}).
+
 \subsection{Contents}
-Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Section~\ref{sec:contents}).
+Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Section~\ref{chap:clonecontents}).
 
@@
 
-\subsection{Extract Method}
+\section{Extract Method}
 %To what extent can found clones be refactored through method extraction, without requiring additional transformations.
@@
 
-\subsection{Refactoring}
+\section{Refactoring}
 %I think the ultimate goal with this thesis is to do experiments with different clone thresholds.
@@
 
-\subsubsection{Clone Token Volume}
+\subsection{Clone Token Volume}
 Figure \ref{fig:duplication} shows the obtained results when plotting the clone size (in tokens) vs the maintainability increase/decrease.
@@
 
-\subsubsection{Relation}
+\subsection{Relation}
 Table~\ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability.
@@
 
-\subsubsection{Return Value}
+\subsection{Return Value}
 Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.
@@
 
-\subsubsection{Parameters}
+\subsection{Parameters}
 Fig.~\ref{fig:arguments} shows how an increase in parameters lowers the maintainability of the refactored code.

### 2019-08-17 sections/results.tex
Added location table

@@
 \subsection{Location}
-Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Section~\ref{chap:clonecontents}).
+Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different locations (see Section~\ref{chap:clonelocations}).
+\begin{table}[]
+\centering
+\begin{tabular}{@{}lll@{}}
+\toprule
+Category & Clone instances & \% \\ \midrule
+Method Level & 232,532 & 78.43\% \\
+Class Level & 50,402 & 17.00\% \\
+Constructor Level & 10,039 & 3.39\% \\
+Interface Level & 2,693 & 0.91\% \\
+Enum Level & 788 & 0.27\% \\
+Outside & 13 & 0.00\% \\ \bottomrule
+\end{tabular}
+\caption{Amount of clone instances with a certain location}
+\label{tab:location}
+\end{table}
 

### 2019-08-17 icse/paper.tex
Extract method percentages

@@
 Top-level AST-Node is not a Statement & 19,887 & 4,607 \\
-Spans Part of a Block & 12,964 & 13,460 \\
+Spans Part of a Block & 13,181 & 13,700 \\
 Multiple Return Values & 5,622 & 6,131 \\

### 2019-08-17 sections/results.tex
Extract method percentages

--- 2019-08-17 sections/results.tex
@@
 \subsection{Relation}
-Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Section~\ref{sec:relation}).
+Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Section~\ref{sec:setuprelation}).
 
@@
 \subsection{Location}
-Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Section~\ref{chap:clonecontents}).
+Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different locations (see Section~\ref{sec:setuplocation}).
+\begin{table}[H]
+\centering
+\begin{tabular}{@{}lll@{}}
+\toprule
+Category & Clone instances & \% \\ \midrule
+Method Level & 232,545 & 78.43\% \\
+Class Level & 50,402 & 17.00\% \\
+Constructor Level & 10,039 & 3.39\% \\
+Interface Level & 2,693 & 0.91\% \\
+Enum Level & 788 & 0.27\% \\
+\end{tabular}
+\caption{Amount of clone instances with a certain location}
+\label{tab:location}
+\end{table}
 
 \subsection{Contents}
-Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Section~\ref{chap:clonecontents}).
+Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Section~\ref{sec:setupcontents}).
 
@@
 \centering
-\begin{tabular}{@{}lll@{}}
+\begin{tabular}{@{}lllll@{}}
 \toprule
-\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{Method Body}} \\ \midrule
-Can Be Extracted & 24,157 & 26,109 \\
-Is Not A Partial Method & 21,625 & 0 \\
-Top-level AST-Node is not a Statement & 19,887 & 4,607 \\
-Spans Part of a Block & 12,964 & 13,460 \\
-Multiple Return Values & 5,622 & 6,131 \\
-Complex Control Flow & 1,106 & 1,216 \\ \bottomrule
+\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{\% (All)}} & \textit{\textbf{Method Body}} & \textit{\textbf{\% (Method Body)}} \\ \midrule
+Can Be Extracted & 24,157 & 28.2\% & 26,109 & 50.4\% \\
+Is Not A Partial Method & 21,625 & 25.3\% & 0 & 0.0\% \\
+Top-level AST-Node is not a Statement & 19,887 & 23.2\% & 4,607 & 8.9\% \\
+Spans Part of a Block & 12,964 & 15.2\% & 13,460 & 26.1\% \\
+Multiple Return Values & 5,622 & 6.6\% & 6,131 & 11.9\% \\
+Complex Control Flow & 1,106 & 1.3\% & 1,216 & 2.4\% \\
+Overlap In Clone Class & 147 & 0.2\% & 147 & 0.3\% \\
+Not In Class Or Interface & 70 & 0.1\% & 93 & 0.2\% \\
+\bottomrule
 \end{tabular}

### 2019-08-17 sections/results.tex
Made it nicer for widepage

@@
 \toprule
-\textit{\textbf{Relation}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Maintainability\\ Score\end{tabular}}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Number of\\ Refactorings\end{tabular}}} \\ \midrule
+\textit{\textbf{Relation}} & \textit{\textbf{Maintainability Score}} & \textit{\textbf{Number of Refactorings}} \\ \midrule
 \textbf{Common Hierarchy} & \textbf{0.51} & \textbf{792} \\ \midrule
@@
 \begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/arguments}
+  \includegraphics[width=0.8\columnwidth]{img/arguments}
   \caption{Influence of number of method parameters on system maintainability.}

### 2019-08-17 sections/results.tex
Watch the commit(!): Removed a lot of old results stuff

@@
 \end{figure}
-
-\section{Context Analysis of Clones}\label{chap:clonecontextexpl}
-We analyzed the context of clones in a large corpus of open source projects.
-These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in chapter \ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in chapter \ref{chap:clonelocation};  he content of clone instances are explained, measured and discussed in chapter \ref{chap:clonecontents}.
-
-\subsection{Relations Between Clone Instances} \label{chap:relationsinstances}
-\todo{update these results}
-In Section~\ref{sec:setuprelation} we introduced our experiments regarding relations between clones. Table~\ref{table:relations} contains our results regarding the relations between clone instances.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{Clone relations} \label{table:relations}
-  \medskip
-\begin{tabular}{|l|l|l|} \hline
-\textbf{Relation} & \textbf{\#} & \textbf{\%} \\ \hline
-Unrelated          & 12,368 & 34.88            \\ \hline
-Same Class          & 11,483 & 32.38             \\ \hline
-Same Method               & 5,056 & 14.26            \\ \hline
-Sibling         & 4,182 & 11.79             \\ \hline
-External Superclass   & 1,066 & 3.01             \\ \hline
-Superclass          & 558 & 1.57           \\ \hline
-First Cousin          & 489 & 1.38           \\ \hline
-Common Hierarchy    & 206 & 0.58            \\ \hline
-Ancestor          & 54 & 0.15          \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-The most notable difference when comparing it to the results of Fontana et al.~\cite{fontana2015duplicated} is that in our results most of the clones are unrelated (34.44\%), while for them it was only 15.70\%.
-This is likely due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy.
-It could also be that the corpus which we use, as it has generally smaller projects, uses more classes from outside the project (which are marked ``Unrelated'' if they do not have a common external superclass).
-About a third of all clone classes have all instances in the same class, which is generally easy to refactor.
-On the third place come the clones that are in the same method, which are similarly easy to refactor.
-
-\subsection{Clone instance location}\label{chap:clonelocation}
-\todo{update these results}
-Measuring the clone locations categories defined in Section~\ref{sec:setuplocation} yields the results displayed in Table \ref{table:contents}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{Clone instance locations} \label{table:locations}
-  \medskip
-\begin{tabular}{|l|l|l|}
-\hline
-\textbf{Location}   & \textbf{\#} & \textbf{\%} \\ \hline
-Method Level        & 83,813 & 82.62            \\ \hline
-Class Level        & 12,534 & 12.35            \\ \hline
-Constructor Level    & 4,391 & 4.33           \\ \hline
-Interface Level   & 567 & 0.56           \\ \hline
-Enum Level         & 145 & 0.14            \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-Our results indicate that around 58\% of the clones are produced at method-level.
-About 39\% of clones either span several methods/constructors or contain something like a field declaration.
-Another 3\% of the clones are found in constructors.
-The amount of clones found in interfaces and enumerations is very low.
-Regarding the differences between type 1 and type 1R, it seems that there are relatively less method level clones and more class level clones for type 1R.
-This is probably due to that the main reason for variability between type 1 and type 1R is variable references, which occur more at method level than class level.
-
-\subsection{Clone instance contents}\label{chap:clonecontents}
-\todo{update these results}
-Measuring the clone contents categories defined in Section~\ref{sec:setupcontents} yields the results displayed in Table \ref{table:contents}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{Clone instance contents} \label{table:contents}
-  \medskip
-\begin{tabular}{|l|l|l|}
-  \hline
-  \textbf{Contents} & \textbf{\#} & \textbf{\%} \\ \hline
-  Partial Method     & 79,945 & 78.80 \\ \hline
-  Several Methods         & 7,323 & 7.22 \\ \hline
-  Partial Constructor      & 4,385 & 4.32 \\ \hline
-  Full Method           & 3,868 & 3.81 \\ \hline
-  Only Fields           & 3,039 & 3.00 \\ \hline
-  Includes Constructor  & 1,522 & 1.50 \\ \hline
-  Includes Field        & 616 & 0.61 \\ \hline
-  Includes Class Declaration  & 376 & 0.37 \\ \hline
-  Other Categories    & 376 & 0.37\\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-Unsurprisingly, most clones span a part of a method.
-The most used refactoring technique for clones that span part of a method is ``Extract Method''.
-Because of that, we focus our research efforts on refactoring such clones.
-
-\section{Merging duplicate code through refactoring} \label{sec:refactorability}
-\todo{update these results}
-In Section~\ref{sec:refactorabilitysetup} we define categories regarding the extent to which clones can be refactored through method extraction.
-Our results are displayed in Table \ref{table:refactorability}.
-
-\begin{table}[H]
-  \begin{center}
-  \caption{Refactorability through method extraction} \label{table:refactorability}
-  \medskip
-\begin{tabular}{|l|l|l|}
-\hline
-\textbf{}         & \textbf{\#} & \textbf{\%} \\ \hline
-Can be extracted     & 14,664 & 41.35 \\ \hline
-Spans part of a block  & 10,801 & 30.46 \\ \hline
-Is not a partial method   & 8,074 & 22.77 \\ \hline
-Complex control flow & 1,922 & 5.42 \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
-
-From Table~\ref{table:refactorability}, we can see that 41\% of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances).
-For the other clones, other techniques or transformations will be required.
-
-\section{Refactoring clones}
-\todo{TODO}

### 2019-08-18 sections/related_work.tex
Related work

@@
 \chapter{Related work} \label{ch:related_work}
+In this chapter we present the work related to this study.
+
+\section{Refactoring suggestion tooling}
+We are novel in the introduction of a fully automated refactoring tool. However, several tools have already been proposed for refactoring suggestion. In this section we discuss these tools.
+
+\subsection{SUPREMO}
+A thesis by Golomingi~\cite{koni2001scenario} is the first to explore mapping the relation between clone instances to refactoring methods.
+In this thesis, the author analyses the refactoring methods described by Martin Fowler \cite{fowler1999refactoring}.
+Mapping these to relations between clones, this results in Table \ref{tab:relationrefactoring}.
+
+\begin{table}[H]
+\begin{tabular}{lllllllll}
+                     & Ancestor   & \begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular} & \begin{tabular}[c]{@{}l@{}}First\\ Cousin\end{tabular} & \begin{tabular}[c]{@{}l@{}}Same\\ Method\end{tabular} & Sibling    & \begin{tabular}[c]{@{}l@{}}Single\\ Class\end{tabular} & Superclass & Unrelated \\
+Extract Method       & \checkmark & \checkmark                                                 & \checkmark                                             & \checkmark                                            & \checkmark & \checkmark                                             &            &           \\
+Insert Method Call   &            &                                                            &                                                        & \checkmark                                            &            & \checkmark                                             &            &           \\
+Insert Super Call    &            &                                                            &                                                        &                                                       &            &                                                        & \checkmark &           \\
+Parameterization     & \checkmark & \checkmark                                                 & \checkmark                                             & \checkmark                                            & \checkmark & \checkmark                                             & \checkmark &           \\
+Pull Up Method       & \checkmark & \checkmark                                                 & \checkmark                                             &                                                       & \checkmark &                                                        & \checkmark &           \\
+Form Template Method & \checkmark & \checkmark                                                 & \checkmark                                             & \checkmark                                            & \checkmark & \checkmark                                             & \checkmark &           \\
+Push Down Method     &            &                                                            &                                                        &                                                       &            &                                                        & \checkmark &           \\
+Extract Superclass   &            & \checkmark                                                 & \checkmark                                             &                                                       & \checkmark &                                                        &            &
+\end{tabular}
+\caption{Mapping clone relations to refactoring techniques \cite{koni2001scenario}}
+\label{tab:relationrefactoring}
+\end{table}
+
+The author then proposes a tool named ``SUPREMO''.
+This tool determines the relations between clone instances, computes the impact of the clones and proposes refactorings.
+Their tool features visualizations to show how clones are related in the inheritance structure.
+This tool is written for the Smalltalk programming language.
+The authors verify their approach by presenting several cases in which their tool analyses source code and outputs a refactoring suggestion.
+
+\subsection{Duplicated Code Refactoring Advisor (DCRA)}
+Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} perform literature analyses to match clone context to refactoring opportunities.
+On basis of this literature study, they match refactoring methods \cite{fowler1999refactoring} to clone relations \cite{koni2001scenario}
 The Duplicated Code Refactoring Advisor (DCRA) looks into refactoring opportunities for clone pairs~\cite{fontana2012duplicated, fontana2015duplicated}.

### 2019-08-18 sections/related_work.tex
DCRA

--- 2019-08-12 sections/related_work.tex
@@
 \chapter{Related work} \label{ch:related_work}
-The Duplicated Code Refactoring Advisor (DCRA) looks into refactoring opportunities for clone pairs~\cite{fontana2012duplicated, fontana2015duplicated}.
-DCRA only focuses on refactoring clone pairs, with the authors arguing that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.
-We further look into these measurements in Sec.~\ref{chap:relationsinstances}.
+In this chapter we present the work related to this study.
 
+\section{Refactoring suggestion tools}
+We are novel in the introduction of a fully automated refactoring tool. However, several tools have already been proposed for refactoring suggestion. In this section we discuss these tools.
+
+\subsection{SUPREMO}
+A thesis by Golomingi~\cite{koni2001scenario} is the first to explore mapping the relation between clone instances to refactoring methods.
+The author analyses the refactoring methods described by Martin Fowler \cite{fowler1999refactoring}.
+Mapping these to relations between clones, this results in Table \ref{tab:relationrefactoring}.
+
+\begin{table}[H]
+\centering
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{lcccccccc}
+\toprule
+                     & Ancestor   & \begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular} & \begin{tabular}[c]{@{}l@{}}First\\ Cousin\end{tabular} & \begin{tabular}[c]{@{}l@{}}Same\\ Method\end{tabular} & Sibling    & \begin{tabular}[c]{@{}l@{}}Single\\ Class\end{tabular} & Superclass & Unrelated \\ \midrule
+Extract Method       & \checkmark & \checkmark                                                 & \checkmark                                             & \checkmark                                            & \checkmark & \checkmark                                             &            &           \\
+Insert Method Call   &            &                                                            &                                                        & \checkmark                                            &            & \checkmark                                             &            &           \\
+Insert Super Call    &            &                                                            &                                                        &                                                       &            &                                                        & \checkmark &           \\
+Parameterization     & \checkmark & \checkmark                                                 & \checkmark                                             & \checkmark                                            & \checkmark & \checkmark                                             & \checkmark &           \\
+Pull Up Method       & \checkmark & \checkmark                                                 & \checkmark                                             &                                                       & \checkmark &                                                        & \checkmark &           \\
+Form Template Method & \checkmark & \checkmark                                                 & \checkmark                                             & \checkmark                                            & \checkmark & \checkmark                                             & \checkmark &           \\
+Push Down Method     &            &                                                            &                                                        &                                                       &            &                                                        & \checkmark &           \\
+Extract Superclass   &            & \checkmark                                                 & \checkmark                                             &                                                       & \checkmark &                                                        &            &           \\ \bottomrule
+\end{tabular}%
+}
+\caption{Mapping clone relations to refactoring techniques \cite{koni2001scenario}}
+\label{tab:relationrefactoring}
+\end{table}
+
+The author then proposes a tool named ``SUPREMO''.
+This tool determines the relations between clone instances, computes the impact of the clones and proposes refactorings.
+Their tool features visualizations to show how clones are related in the inheritance structure.
+This tool is written for the Smalltalk programming language.
+The authors verify their approach by presenting several cases in which their tool analyses source code and outputs a refactoring suggestion.
+
+\subsection{Duplicated Code Refactoring Advisor (DCRA)}
+Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} combine the research by Golomingi~\cite{koni2001scenario} with clone types \cite{roy2007survey}.
+They use a large corpus~\cite{tempero2010qualitas} on which they perform statistical analysis of clone relations together with clone types.
+Table \ref{tab:dcra-relation} displays the result of this analysis.
+We added percentages and ordering to this table for easier comparison with the results of our studies (see \ref{sec:relationresults}).
+
+\begin{table}[H]
+\centering
+\begin{tabular}{@{}lllll@{}}
+\toprule
+                         & Type 1 & Percentage & Type 3 & Percentage \\ \midrule
+Same Class               & 5,645  & 32.1\%     & 51,308 & 28.7\%     \\
+Same External Superclass & 4,384  & 25.0\%     & 66,391 & 37.1\%     \\
+Unrelated Class          & 2,758  & 15.7\%     & 35,035 & 19.6\%     \\
+Sibling Class            & 2,721  & 15.5\%     & 13,868 & 7.8\%      \\
+Common Hierarchy Class   & 970    & 5.5\%      & 3,152  & 1.8\%      \\
+Same Method              & 569    & 3.2\%      & 4,901  & 2.7\%      \\
+First Cousin Class       & 416    & 2.4\%      & 2,980  & 1.7\%      \\
+Superclass               & 91     & 0.5\%      & 981    & 0.5\%      \\
+Ancestor Class           & 13     & 0.1\%      & 281    & 0.2\%      \\ \bottomrule
+\end{tabular}
+\caption{Clone relation analysis by Fontana et al. \cite{fontana2012duplicated} for type 1 and 3 clones measured over the Qualitas Corpus \cite{tempero2010qualitas}.}
+\label{tab:dcra-relation}
+\end{table}
+
+Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} propose a tool to suggest refactorings for the clones found by the NiCAD tool \cite{roy2008nicad, cordy2011nicad}.
+This tool is named Duplicated Code Refactoring Advisor (DCRA).
+The DCRA suggests refactorings, based on Table~\ref{tab:relationrefactoring}, to clones found in Java projects.
+
+\subsection{Aries}
 A tool named Aries~\cite{higo2004aries, higo2008metric} focuses on the detection of refactorable clones.

### 2019-08-18 sections/results.tex
DCRA

@@
 
-\subsection{Relation}
+\subsection{Relation} \label{sec:relationresults}
 Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Section~\ref{sec:setuprelation}).

### 2019-08-18 sections/related_work.tex
Aries

@@
 \subsection{Aries}
-A tool named Aries~\cite{higo2004aries, higo2008metric} focuses on the detection of refactorable clones.
-They do this based on the relation between clone instances through inheritance, similar to Fontana et al.~\cite{fontana2012duplicated}.
+A study by Higo et al.~\cite{higo2004aries, higo2008metric} looks into to what extent clones can be refactored.
+They show code examples and to what entent they can be cloned.
+For instance, they look into what parts of a clone can be extracted to a new method.
+They define that partially cloned blocks obstruct method extraction.
+They propose t make the clone smaller to find a part of the clone that can be refactored.
+This is similar to our ``partial block'' category of Section~\ref{sec:refactorabilitysetup} and our discussion in Section~\ref{sec:partialblockdiscussion}.
+
+Higo et al.
+also look into the amount of variability that can be allowed between clone fragments.
+Figure~\ref{fig:higomerge} shows an example of merging two code fragments from this study.
+In this figure, the clone spans a part of a different block so it cannot be refactored.
+However, they propose to ommit both ``else if'' lines from the merged fragment so that it can be refactored (in our study we would have flagged these clones as ``partial block'' and thus unsuitable for refactoring).
+They also allow variability in literals and variables and replace them with method parameters.
+
+\begin{figure}[H]
+  \includegraphics[width=1\textwidth]{img/higo}
+  \caption{Example of merging two code fragments from Higo et al.~\cite{higo2008metric}.}
+  \label{fig:higomerge}
+\end{figure}
+
+Higo et al.
+propose a tool named Aries~\cite{higo2004aries, higo2008metric} that focuses on the detection of refactorable clones.
+They focus entirely on whether a clone \textbf{can} be refactored and not whether it \textbf{should} be refactored.
 This tool only proposes a refactoring opportunity and does not provide help in the process of applying the refactoring.
 
+\subsection{Coming up :)}
 We investigated several research efforts that look into code clone refactoring~\cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}.

### 2019-08-18 sections/related_work.tex
Order

@@
 \section{Refactoring suggestion tools}
-We are novel in the introduction of a fully automated refactoring tool. However, several tools have already been proposed for refactoring suggestion. In this section we discuss these tools.
+We are novel in the introduction of a fully automated refactoring tool.
+However, several tools have already been proposed for refactoring suggestion.
+In this section we discuss these tools.
+The tools are ordered on basis of the year in which they were proposed.
 
@@
 
+\subsection{Aries}
+A study by Higo et al.~\cite{higo2004aries, higo2008metric} looks into to what extent clones can be refactored.
+They show code examples and to what entent they can be cloned.
+For instance, they look into what parts of a clone can be extracted to a new method.
+They define that partially cloned blocks obstruct method extraction.
+They propose t make the clone smaller to find a part of the clone that can be refactored.
+This is similar to our ``partial block'' category of Section~\ref{sec:refactorabilitysetup} and our discussion in Section~\ref{sec:partialblockdiscussion}.
+
+Higo et al.
+also look into the amount of variability that can be allowed between clone fragments.
+Figure~\ref{fig:higomerge} shows an example of merging two code fragments from this study.
+In this figure, the clone spans a part of a different block so it cannot be refactored.
+However, they propose to ommit both ``else if'' lines from the merged fragment so that it can be refactored (in our study we would have flagged these clones as ``partial block'' and thus unsuitable for refactoring).
+They also allow variability in literals and variables and replace them with method parameters.
+
+\begin{figure}[H]
+  \includegraphics[width=1\textwidth]{img/higo}
+  \caption{Example of merging two code fragments from Higo et al.~\cite{higo2008metric}.}
+  \label{fig:higomerge}
+\end{figure}
+
+Higo et al.
+propose a tool named Aries~\cite{higo2004aries, higo2008metric} that focuses on the detection of refactorable clones.
+They focus entirely on whether a clone \textbf{can} be refactored and not whether it \textbf{should} be refactored.
+This tool only proposes refactoring opportunities and does not provide help in the process of applying the refactoring.
+
 \subsection{Duplicated Code Refactoring Advisor (DCRA)}
@@
 
-\subsection{Aries}
-A study by Higo et al.~\cite{higo2004aries, higo2008metric} looks into to what extent clones can be refactored.
-They show code examples and to what entent they can be cloned.
-For instance, they look into what parts of a clone can be extracted to a new method.
-They define that partially cloned blocks obstruct method extraction.
-They propose t make the clone smaller to find a part of the clone that can be refactored.
-This is similar to our ``partial block'' category of Section~\ref{sec:refactorabilitysetup} and our discussion in Section~\ref{sec:partialblockdiscussion}.
-
-Higo et al.
-also look into the amount of variability that can be allowed between clone fragments.
-Figure~\ref{fig:higomerge} shows an example of merging two code fragments from this study.
-In this figure, the clone spans a part of a different block so it cannot be refactored.
-However, they propose to ommit both ``else if'' lines from the merged fragment so that it can be refactored (in our study we would have flagged these clones as ``partial block'' and thus unsuitable for refactoring).
-They also allow variability in literals and variables and replace them with method parameters.
-
-\begin{figure}[H]
-  \includegraphics[width=1\textwidth]{img/higo}
-  \caption{Example of merging two code fragments from Higo et al.~\cite{higo2008metric}.}
-  \label{fig:higomerge}
-\end{figure}
-
-Higo et al.
-propose a tool named Aries~\cite{higo2004aries, higo2008metric} that focuses on the detection of refactorable clones.
-They focus entirely on whether a clone \textbf{can} be refactored and not whether it \textbf{should} be refactored.
-This tool only proposes a refactoring opportunity and does not provide help in the process of applying the refactoring.
-
 \subsection{Coming up :)}

### 2019-08-18 sections/related_work.tex
AlWaqfi

@@
 
-\subsection{Coming up :)}
-We investigated several research efforts that look into code clone refactoring~\cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}.
-However, all of these tools only support a subset of all harmful clones that are found.
-Also, these tools are limited to suggesting refactoring opportunities, rather than actually applying refactorings where suitable.
-Finally, all published approaches have limitations, such as false positives in their clone detection~\cite{chen2018clone} or being limited to clone pairs~\cite{higo2008metric}.
+\subsection{Refactoring Technique for Large Groups of Software Clones}
+A thesis by AlWaqfi~\cite{alwaqfi2017refactoring} propose a method for assessing refactorability of clone classes (whereas the previous tools only focus on clone pairs).
+The author surveys a set of clone detection tools \cite{kamiya2002ccfinder, baxter1999clonedr, jiang2007deckard, cordy2011nicad} and uses a publicly available dataset \cite{tsantalis2015assessing} to measure the amount of clones found by these tools.
+The resulting data shows that significant portions of source code of the measured systems are cloned.
+The data also shows that there are large differences between different tools in the amount of clones found.
+The author also measures of how many clone instances clone classes consist.
+According to these experiments, about 68\% of clone classes consist of 2 clone instances, 13\% have 3 clone instances, 7\% have 4 clone instances and about 12\% is even larger.
+
+The authors perform a lot of statistical comparisons between clone detection tools.
+The part most relevant to our study is their measurements regarding refactorability.
+They find that about 29-54\% of clones are refactorable in the set of projects they inspect (Table 6.13 of \cite{alwaqfi2017refactoring}).
+To determine whether a clone is refactorable, the author states a list of eight preconditions for a cloned fragment to be refactorable.
+These preconditions are similar to the categories we identified in Section~\ref{sec:refactorabilitysetup}.
+
+\subsection{Pattern‐based clone Refactoring Inspection (PRI)}

### 2019-08-18 sections/related_work.tex
PRI

@@
 
-Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} propose a tool to suggest refactorings for the clones found by the NiCAD tool \cite{roy2008nicad, cordy2011nicad}.
-This tool is named Duplicated Code Refactoring Advisor (DCRA).
-The DCRA suggests refactorings, based on Table~\ref{tab:relationrefactoring}, to clones found in Java projects.
+Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} propose DCRA, a tool to suggest refactorings for the clones found by the NiCAD tool \cite{roy2008nicad, cordy2011nicad}.
+DCRA suggests refactorings to clones found in Java projects based on the mapping between relation and refactoring techniques shown in Table~\ref{tab:relationrefactoring}.
 
@@
 \subsection{Pattern‐based clone Refactoring Inspection (PRI)}
+A study by Chen et al.~\ref{chen2018clone} addresses the problem that developers cannot easily determine which clones can be refactored or how they should be maintained scattered
+throughout a large code base in evolving systems.
+They propose PRI, a technique for managing clone refactorings for clones with a Sibling relation.
+PRI is a plugin for the Eclipse IDE that shows which refactoring techniques can be used to refactor clones.
+Because it is integrated in the Eclipse IDE, the refactorings can be executed largely automatically, as this IDE has a large set of tools for performing such transformations.
+
+PRI traces clones through revisions of a software project.
+This makes this tool able to find incompletely refactored clones.
+PRI produces false positives in that several groups are incorrectly classified since the clone detector suffers the inaccuracy in finding semantically equivalent behaviors between clones.

### 2019-08-18 sections/acknowledgements.tex
Vashisht

@@
 Oprescu , whose expertise was invaluable in the academic writing and mathematical aspects of this thesis.
+I would like to thank you for your patience whilst reading my texts, as my words often required quite some editing to concisely deliver the message I try to deliver.
 
-Next, I would like to thank my peer student Sander Meester for always being there when I was stuck.
+Next, we would like to thank my peer student Sander Meester for always being there when I was stuck.
 Whenever I needed to test some ideas you would always provide realistic insights.
@@
 
+I would like to thank my supervisor, Xander Schrijen, for all his input during our weekly meetings. We had long discussions about all my ideas, which helped to put my ideas in perspective.
+
+I would like to thank Danny van Bruggen for all his help in my use of JavaParser.
+I am amazed by his willingness to help others to tackle their problems.
+JavaParser is at the core of the CloneRefactor tool and without Danny, I would never have come as far in the development of this tool.
+
 Finally, I would like to acknowledge my colleagues from my internship at SIG for their wonderful collaboration. You supported me greatly and were always willing to help me.

### 2019-08-18 sections/related_work.tex
Vashisht

@@
 
-\section{Refactoring suggestion tools}
+\section{Code clone refactoring suggestion tools}
 We are novel in the introduction of a fully automated refactoring tool.
@@
 
+\subsection{JDeodorant}
+\todo{TODO}
+
 \subsection{Refactoring Technique for Large Groups of Software Clones}
@@
 throughout a large code base in evolving systems.
-They propose PRI, a technique for managing clone refactorings for clones with a Sibling relation.
+They propose PRI, a technique for managing refactorings for clones with a Sibling relation.
 PRI is a plugin for the Eclipse IDE that shows which refactoring techniques can be used to refactor clones.
@@
 
-PRI traces clones through revisions of a software project.
-This makes this tool able to find incompletely refactored clones.
-PRI produces false positives in that several groups are incorrectly classified since the clone detector suffers the inaccuracy in finding semantically equivalent behaviors between clones.
+Another feature of the PRI tool is to find incompletely refactored clones.
+To do this, PRI traces clones through revisions of a software project.
+When a clone class is incompletely refactored, PRI informs the user that there are clone instances for which an extracted method has already been created.
+
+\section{Clone refatoring}
+In this section, we shortly introduce recent studies about refactoring code clones.
+
+\subsection{Impact of Clone Refactoring on External Quality Attributes}
+A study by Vashisht et al.~\cite{vashisht2018impact} determines the impact of clone refactoring on several quality attributes.
+They calculate the metrics of the system before refactoring, detect clones using CCFinder \cite{kamiya2002ccfinder}, use JDeodorant to refactor a subset of the detected clones \cite{mazinanian2016jdeodorant} and measure the metrics again after refactoring to assess the impact of the refactoring process on quality attributes.
+They conclude that some metrics affect some quality attributes positively and some negatively.
+
+In this study, the authors only compare before and after snapshots of refactoring the entire system. This makes it hard to determine why some metrics are negatively influenced.

### 2019-08-19 sections/related_work.tex
TODOs
For tomorrow
Yoshida

@@
 \subsection{JDeodorant}
+\cite{krishnan2013refactoring, krishnan2014unification, tsantalis2015assessing, mazinanian2016jdeodorant, tsantalis2017clone}
 \todo{TODO}
@@
 In this study, the authors only compare before and after snapshots of refactoring the entire system. This makes it hard to determine why some metrics are negatively influenced.
+
+\subsection{Clone Recommendation System for Extract Method Refactoring}
+Yoshida et al.~\cite{yoshida2019proactive} propose a plugin for the Eclipse IDE that recommends clone refactoring candidates on basis of keystroke tracking.
+Whenever the user performs the ``Extract Method'' refactoring, the proposed system scans the project for clones that can now use the extracted method.
+It then shows the developer all places that should be refactored aswell now that a new method has been created.
+The approach was validated by requesting human participants to apply refactorings to open source systems.
+On average, it took participants 1,043 seconds to refactor 2.75 clones.
+They indicate that this is 35\% faster than when working with a popular clone detection tool (GemX).
+
+\subsection{Effect of clone refactoring on the size of unit test cases}
+\cite{badri2019measuring}
+\todo{TODO}

### 2019-08-19 sections/related_work.tex
Badri

@@
 \subsection{Effect of clone refactoring on the size of unit test cases}
-\cite{badri2019measuring}
-\todo{TODO}
+Badri et al.~\cite{badri2019measuring} measure the impact on clone refactoring on metrics that affect the testability of software.
+The metrics they measure are size, cyclomatic complexity and coupling.
+To collect this data, they used two systems that have been clone refactored.
+They conclude that there is a strong and positive correlation between clone refactoring and the reduction of the size of unit test cases.
+They also show that code quality attributes that are related to testability are significantly improved.

### 2019-08-19 icse/paper.tex
Vashisht
JDeodorant progress

@@
 Often when developers duplicate fragments of code, they modify the duplicated block to fit its new location and purpose.
-To detect duplicate fragments with minor variance, we looked into in what expressions we can allow variability while still being refactorable.
+To detect duplicate fragments with minor variance, we look into in what expressions we can allow variability while still being refactorable.
 
@@
 \end{itemize}
-Often when allowing such variance, trade-offs come into play.
+Often when allowing such variance, trade-offs come into play \cite{krishnan2013refactoring, krishnan2014unification}.
 For instance, variance in literals may require the introduction of a parameter to an extracted method if the ``Extract Method'' refactoring method is used, increasing the required effort to comprehend the code.
@@
   \item We wrap the difference in statements in a conditionally executed block, one path for each different (group of) statement(s).
-  \item We use a lambda function to pass the difference in statements from each location of the clone.
+  \item We use a lambda function to pass the difference in statements from each location of the clone \cite{tsantalis2017clone}.
 \end{itemize}
@@
 We created a set of control projects to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
-None of the surveyed tools \cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing} seemed suitable, because of which we decided to implement our own tool.
+None of the surveyed tools \cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we decided to implement our own tool.
 

### 2019-08-19 sections/related_work.tex
JDeodorant progress

@@
 \subsection{JDeodorant}
+The most used tool used to help in the process of refactoring clones is JDeodorant \cite{mazinanian2016jdeodorant}.
+This tool is based on a set of studies, that look into several aspects of the clone refactoring process.
+The first of these studies is ``Refactoring Clones: An Optimization Problem'' by Krishnan et al.~\cite{krishnan2013refactoring}.
+The authors describe clones that are refactored by extracting their functionality to a single method.
+They also describe that variability between identifiers and literals have to become parameters in the extracted method.
+They identify the optimization problem where the variability between cloned fragments should be limited, to avoid limiting the reusability of methods because of too many method parameters.
+They propose an algorithm that calculates the variance between code fragments on basis of the difference in AST nodes.
+
+The second study, ``Unification and Refactoring of Clones'' by Krishnan et al.~\cite{krishnan2014unification}, the authors address the problem of the modifications made to copied fragments and their impact on the refactoring process.
+They identify a list of expressions in which they have found variability, which is displayed in Table~\ref{tab:krishnanvariability}.
+
+\begin{table}[H]
+\centering
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lcc@{}}
+\toprule
+\textit{\textbf{Difference Type}} & \multicolumn{2}{c}{\textit{\textbf{Example}}}                                                \\ \midrule
+Variable Identifier               & \multicolumn{1}{c|}{\texttt{int x = \textbf{y};}}       & \texttt{int x = \textbf{z};}       \\
+Literal Value                     & \multicolumn{1}{c|}{\texttt{String s = \textbf{"s1"};}} & \texttt{String s = \textbf{"s2"};} \\
+Method Name                       & \multicolumn{1}{c|}{\texttt{expr.\textbf{foo}(arg);}}   & \texttt{expr.\textbf{bar}(arg);}   \\
+Argument Number                   & \multicolumn{1}{c|}{\texttt{foo(\textbf{arg0, arg1});}} & \texttt{foo(\textbf{arg0});}       \\
+Caller Expression                 & \multicolumn{1}{c|}{\texttt{\textbf{expr.}foo(arg);}}   & \texttt{foo(arg);}                 \\
+Array Dimension                   & \multicolumn{1}{c|}{\texttt{int x = a\textbf{[i]};}}    & \texttt{int x = a\textbf{[i][j]};} \\
+AST Compatible                    & \multicolumn{1}{c|}{\texttt{int x = \textbf{foo()};}}   & \texttt{int x = \textbf{5};}       \\ \midrule
+Operator                          & \multicolumn{1}{c|}{\texttt{int x = y \textbf{+} z;}}   & \texttt{int x = y \textbf{-} z;}   \\
+Variable Type                     & \multicolumn{1}{c|}{\texttt{\textbf{int} x = 5;}}       & \texttt{\textbf{double} x = 5;}    \\ \bottomrule
+\end{tabular}%
+}
+\caption{Expression variability table from Krishnan et al.~\cite{krishnan2014unification}}
+\label{tab:krishnanvariability}
+\end{table}
+
 \cite{krishnan2013refactoring, krishnan2014unification, tsantalis2015assessing, mazinanian2016jdeodorant, tsantalis2017clone}

### 2019-08-19 sections/related_work.tex
Preconditions

@@
 They identify a list of expressions in which they have found variability, which is displayed in Table~\ref{tab:krishnanvariability}.
+The authors map the variability in this table to refactoring opportunities.
+They list a set of four preconditions for the refactoring process:
+\begin{enumerate}
+  \item The parameterization of differences between the matched statements should not break existing data-, anti-, and output-dependences.
+  \item The unmatched statements should be movable before or after the matched statements without breaking existing data-, anti-, and output-dependences.
+  \item The duplicated code fragments should return at most one variable of the same type.
+  \item Matched branching (\texttt{break}, \texttt{continue}) statements should be accompanied with corresponding matched loop statements.
+\end{enumerate}
+In our study, we address precondition 1 and 2 and propose a solution.
+To address precondition 1, we only refactor variability in such a way that existing data-, anti-, and output-dependences are not affected (see Section \ref{sec:type2r}).
+For precondition 2, we propose using conditional or lambda expressions to wrap the difference in statements (see Section \ref{sec:type3r}).
+For precondition 3 and 4, we flag these clones as ``not refactorable'' (see Section \ref{sec:refactorabilitysetup}).
 
@@
 \centering
-\resizebox{\textwidth}{!}{%
 \begin{tabular}{@{}lcc@{}}
@@
 Variable Type                     & \multicolumn{1}{c|}{\texttt{\textbf{int} x = 5;}}       & \texttt{\textbf{double} x = 5;}    \\ \bottomrule
-\end{tabular}%
-}
+\end{tabular}
 \caption{Expression variability table from Krishnan et al.~\cite{krishnan2014unification}}

### 2019-08-19 sections/related_work.tex
Finish up JDeodorant section

@@
 
-\cite{krishnan2013refactoring, krishnan2014unification, tsantalis2015assessing, mazinanian2016jdeodorant, tsantalis2017clone}
-\todo{TODO}
+A study by Tsantalis et al.~\cite{tsantalis2015assessing} looks into the refactorability of code clones.
+This results in a set of eight preconditions to determine whether a cloned fragment is refactorable.
+Four of these preconditions are similar to the Krishnan et al.~\cite{krishnan2014unification} study.
+The following preconditions have been added:
+\begin{enumerate}
+  \setcounter{enumi}{4}
+  %\item The parameterization of the differences between the mapped statements should not break any existing control, data, anti, and output dependencies.
+  \item Matched variables having different subclass types should call only methods that are declared in the common superclass or are being overridden in the respective subclasses.
+  \item The parameterization of fields belonging to differences between the mapped statements is possible only if they are not modified.
+  \item The parameterization of method calls belonging to differences between the mapped statements is possible only if they do not return a void type.
+  %\item The unmapped statements should be movable before or after the mapped statements without breaking existing control, data, anti, and output dependencies.
+  %\item The mapped statements within the clone fragments should return at most one variable of the same type to the original methods from which they are extracted.
+  \item The mapped statements within the clone fragments should not contain any conditional return statements.
+  %\item The mapped branching statements (break, continue) should be accompanied with the corresponding mapped loop statements
+\end{enumerate}
+In our study, we simplify precondition 5 by not allowing variability in types, because of which we satisfy this precondition.
+We address precondition 6 by allowing modified statements as return values (and turning the calls to the extracted method into variable assignments).
+If more than 1 variable is assigned or other return values would be present, we flag the cloned fragments as ``not refactorable''.
+We address precondition 7 by using lambda expressions, which do allow void type methods to be used as parameters.
+We address precondition 8 by analyzing all branches in the code.
+If all branches return, the fragment can still be refactored even though there is a conditional return statement.
+
+After all these studies that determine what preconditions apply to be able to refactor modified clones, the authors propose a tool named JDeodorant that helps in the process of refactoring such clones~\cite{mazinanian2016jdeodorant}.
+This tool takes the output of many popular clone detection tools \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, NiCAD} and proposes refactoring opportunities.
+The tool is integrated in the Eclipse IDE, making it easier to directly apply the refactoring.
+The tool is based on previously discussed preconditions and does not allow refactorings if the preconditions are not met.
+
+A study by Tsantalis et al.~\cite{tsantalis2017clone} looks into how lambda expressions can be used to help in the process of refactoring clones.
+They do this in order to mitigate some of the earlier established preconditions.
+Working with lambda's makes it possible to refactor statement gaps and expression differences.
+They find that lambda expressions are very suitable to refactor clones with variability.
+The authors do not discuss the impact of such refactorings on system maintainability costs, their main focus is to positively influence the refactorability of clone classes.
 
@@
 They find that about 29-54\% of clones are refactorable in the set of projects they inspect (Table 6.13 of \cite{alwaqfi2017refactoring}).
-To determine whether a clone is refactorable, the author states a list of eight preconditions for a cloned fragment to be refactorable.
-These preconditions are similar to the categories we identified in Section~\ref{sec:refactorabilitysetup}.
+To determine whether a clone is refactorable, the author uses the set of eight preconditions proposed by Tsantalis et al.~\ref{tsantalis2015assessing}.
 

### 2019-08-19 icse/paper.tex
Various improvements

@@
 The most unfavorable is to refactor clones to interfaces.
-However, the differences in maintainability in this table are generally small; there is no indication that relations have a major impact on the maintainability of clones.
+However, the differences in maintainability in this table are generally small; according to our data relations have only a minor impact on the maintainability of clones.
 

### 2019-08-19 sections/research.tex
Various improvements

@@
 To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types directed at detecting clones that can and should be refactored.
-We have named these clones T1R (type 1R), T2R and T3R clones.
+We have named these clones type 1R, 2R and 3R clones.
 These definitions address problems of the corresponding literature definitions.
-The ``R'' stands for refactoring-oriented (and may be less useful for other analyses) % TODO: Sander - zou dat laatste remark miss weglaten of echt uitleggen.
+The ``R'' stands for refactoring-oriented.
 
@@
 Like type 1 clones, type 1R clones do not consider comments and whitespace.
-Therefore, T1R clones are a subset of type 1 clones.
+Therefore, type 1R clones are a subset of type 1 clones.
 

### 2019-08-19 sections/discussion.tex
Aries
Working on discussion

@@
 
-\subsection{Refactorability} \label{sec:discussrefactorability}
-In Section~\ref{sec:refactorability} we introduced to what extent clones can be refactored through method extraction.
-Because we strived to get results fast, we excluded categories that could not not be directly refactored through method extraction.
+\section{CloneRefactor}
+In this section we discuss our decisions for the design of our CloneRefactor tool.
+
+\subsection{Clone Detection}
+For CloneRefactor we chose to design a novel method of detecting clones, rather than using an existing clone detection technique or tool. Our rationale is as follows:
+\begin{itemize}
+  \item We perform comprehensive analysis on the source code which requires us to use an AST-based clone detection method.
+  \item We perform dependency graph analysis, which requires us to resolve symbols in the source code.
+  \item None of the existing clone detection methods implement all criteria required to build such a system.
+\end{itemize}
+By building a graph that maps relations between nodes in the AST, we can find clones in an efficient manner, allowing to perform a comprehensive analysis of large systems.
+This method has worked well for our purposes.
+
+The main limitation we encountered is the memory required to build the clone graph.
+As we load the entire graph into memory before starting the clone detection procedure, this can cause issues on systems with low available memory.
+For a system consisting of 1.000.000 nodes, the clone graph requires about 4GB of RAM.
+For our corpus, there were no larger systems, so this was not a big issue.
+However, for industry projects our tool might require optimization.
+
+\subsection{Context Analysis}
+In this study we identified categories for three properties of clones: relation, location and contents.
+%Mapping the location and contents was mainly to find out what the best method of refactoring is to refactor most clones.
+We chose a set of relations that indicate different refactoring opportunities.
+However, as our CloneRefactor tool only analyses Java source code, we we biased towards categories that are often found in Java source code.
+For other languages, other categories might be valuable to analyze to find suitable categories for that programming language.
+
+\subsection{Refactoring}
+In this section, we discuss our implementation decisions to refactor source code using CloneRefactor and measure its impact.
+
+\subsubsection{Refactorability} \label{sec:discussrefactorability}
+In Section~\ref{sec:refactorability} we introduced catagories to determine the refactorability of clones through method extraction.
+We excluded categories that could not not be directly refactored through method extraction.
 However, with a few transformations or further considerations it might be possible to make these clones refactorable.
-In this section we will highlight a few of these categories which we believe to be refactorable through method extraction with a bit more effort.
+In this section we will highlight a few of these categories which we believe to be refactorable through method extraction with more effort.
 
-\subsubsection{Partial block}
+\subsubsection{Partial block} \label{sec:partialblockdiscussion}
 We did not consider clones for refactoring that span a part of a block.
@@
 
-\section{CloneRefactor}
-In this section we discuss our decisions for the design of our CloneRefactor tool.
-
-\subsection{Clone Detection}
-For CloneRefactor we chose to design a novel method of detecting clones, rather than using an existing clone detection technique or tool. Our rationale is as follows:
-\begin{itemize}
-  \item We perform comprehensive analysis on the source code which requires us to use an AST-based clone detection method.
-  \item We perform dependency graph analysis, which requires us to resolve symbols in the source code.
-  \item None of the existing clone detection methods implement all criteria required to build such a system.
-\end{itemize}
-By building a graph that maps relations between nodes in the AST, we can find clones in an efficient manner, allowing to perform a comprehensive analysis of large systems.
-This method has worked well for our purposes.
-
-The main limitation we encountered is the memory required to build the clone graph.
-As we load the entire graph into memory before starting the clone detection procedure, this can cause issues on systems with low available memory.
-For a system consisting of 1.000.000 nodes, the clone graph requires about 4GB of RAM.
-For our corpus, there were no larger systems, so this was not a big issue.
-However, for industry projects our tool might require optimization.
-
-\subsection{Context Analysis}
-In this study we identified categories for three properties of clones: relation, location and contents.
-%Mapping the location and contents was mainly to find out what the best method of refactoring is to refactor most clones.
-We chose a set of relations that indicate different refactoring opportunities.
-However, as our CloneRefactor tool only analyses Java source code, we we biased towards categories that are often found in Java source code.
-For other languages, other categories might be valuable to analyze to find suitable categories for that programming language.
-
-\subsection{Refactoring}
-
 \subsubsection{Metrics}
@@
 
-The maintainability scores displayed in Table~\ref{tab:relation_refactor} show that the most favorable clones to refactor are clones with a Sibling relation.
+The maintainability scores displayed in Table~\ref{tab:relation_refactor} show that the most favorable clones to refactor are clones with a sibling relation.
 The most unfavorable is to refactor clones to interfaces.
-However, the differences in maintainability in this table are generally small; there is no indication that relations have a major impact on the maintainability of clones.
+However, the differences in maintainability in this table are generally small; according to our data relations have a minor impact on the maintainability of clones.
 

### 2019-08-19 sections/related_work.tex
Working on discussion

@@
 
-\subsection{JDeodorant}
+\subsection{JDeodorant} \label{sec:jdeodorant}
 The most used tool used to help in the process of refactoring clones is JDeodorant \cite{mazinanian2016jdeodorant}.

### 2019-08-19 sections/clonerefactor.tex
Working on discussion
Okay

@@
 \section{Automated Refactoring}
-After clone detection and context analysis, CloneRefactor applies refactorings to a subset of the identified clones.
+After clone detection and context analysis, CloneRefactor applies refactorings to a subset of type 1R clones.
 This section describes what clone classes are included in the refactoring and the refactoring methods CloneRefactor supports.
@@
 
-Because of this, we defined a set of categories of things that can obstruct a refactoring opportunity using the ``Extract Method'' technique. We defined the following categories:
+Because of this, we defined a set of categories of things that can obstruct a refactoring opportunity using the ``Extract Method'' technique.
+These categories are party derived from the clone refactoring preconditions defined by Tsantalis et al.~\cite{tsantalis2015assessing} (see Section \ref{sec:jdeodorant}).
+These categories are as follows:
 \begin{itemize}
@@
 
-\subsection{Applying refactorings}
+\subsection{Applying refactorings} \label{sec:applyingrefactorings}
 All clones that are marked as ``Can be Extracted'' will then be refactored.

### 2019-08-19 sections/discussion.tex
Okay

@@
 Although it is indeed not possible to refactor such clones, there are possibilities to make such clones refactorable.
-For instance, if the programming language supports lambda expressions, we can move the difference of statements in the block in a lambda expression.
+For instance, if the programming language supports lambda expressions, we can move the difference of statements in the block in a lambda expression \cite{tsantalis2017clone}.
 Figure \ref{fig:partialblockrefactoring} shows an example of such a refactoring opportunity.
@@
 \end{figure}
+
+\subsubsection{Applying refactorings}
+CloneRefactor can refactor all clones that are flagged ``can be extracted''.
+This is done through a series of AST transformations as described in Section \ref{sec:applyingrefactorings}.
+Currently, these refactoring methods do not yet allow for variability (type 2R and 3R), as allowing variability quickly increases the complexity of the refactoring problem and the amount of edge cases to consider \cite{tsantalis2015assessing}.
+Because of this, CloneRefactor does not yet realistically emulate human refactoring efforts, as humans would take variability between code fragments into account.
+To get a more
 

### 2019-08-19 sections/conclusion.tex
Threats to validity

@@
 \section{Threats to validity}\label{chap:threatstovalidity}
-\todo{Rewrite}
-We noticed that, when doing measurements on a corpus of this size, the thresholds that we use for the clone detection have a big impact on the results.
-There does not seem to be one golden set of thresholds, some thresholds work in some situations but fail in others.
-We have chosen thresholds that, according to our manual assessment, seemed optimal.
-However, by using these, we definitely miss some harmful clones.
-\todo{Possible stuff: future work might be a threat to validity}
-\todo{Implementation specific for CloneRefactor: limited validation}
+In this section we share some factors that can influence the validity of the obtained results.
+
+\subsection{CloneRefactor}
+CloneRefactor can refactor all clones that are flagged ``can be extracted''.
+This is done through a series of AST transformations as described in Section \ref{sec:applyingrefactorings}.
+Currently, these refactoring methods do not yet allow for variability (type 2R and 3R), as allowing variability quickly increases the complexity of the refactoring problem and the amount of edge cases to consider \cite{tsantalis2015assessing}.
+Because of this, CloneRefactor does not yet realistically emulate human refactoring efforts, as humans would take variability between code fragments into account.
+This influences the results, as the numbers obtained might be higher if it would more realistically emulate human behavior.
+
+\subsection{Corpus}
+We used a corpus of 2,267 open source Java projects from GitHub for our experiments.
+This corpus consists of only Maven projects and we only take the ``production sources'' folder of these projects take into account.
+We inspected the results of CloneRefactor for outliers and excluded projects that have generated sources in their ``production sources'' folder.
+This increases the chance that we are not taking into account test sources and generated files, but it does not eliminate this chance.
+Because of that, there is a threat to validity in the source code in the corpus, as it potentially includes sources that do not reflect human-maintained production code.
 

### 2019-08-19 sections/conclusion.tex
Conclusion

@@
-\chapter{Conclusion}
-\todo{Rewrite}
-\label{ch:conclusion}
-In the research we have conducted so far we have made three novel contributions:
-\begin{itemize}
-    \item We proposed a method with which we can detect clones that can/should be refactored.
-    \item We mapped the context of clones in a large corpus of open source systems.
-    \item We mapped the opportunities to perform method extraction on clones this corpus.
-\end{itemize}
+\chapter{Conclusion} \label{ch:conclusion}
+We defined automatically refactorable clones and created a tool to detect and refactor them.
+We measured statistical data with this tool over a large corpus of open-source Java software systems to get more information about the context of clones and how refactoring them influences system maintainability.
 
-We have looked into existing definitions for different types of clones \cite{roy2007survey} and proposed solutions for problems that these types have with regards to automated refactoring.
-We propose that fully qualified identifiers of method call signatures and type references should be considered instead of their plain text representation, to ensure refactorability.
-Furthermore, we propose that one should define thresholds for variability in variables, literals and method calls, in order to limit the number of parameters that the merged unit shall have.
+%For cloned fragments to be refactorable, we propose that fully qualified identifiers of method call signatures and type references should be considered instead of their plain text representation, to be sure that they refer to the same implementations.
+, we propose that one should define thresholds for variability in variables, literals and method calls, in order to limit the number of parameters that the merged unit shall have.
 
-The research that we have conducted so far analyzes the context of different kinds of clones and prioritizes their refactoring.
-Firstly, we looked at the inheritance relation of clone instances in a clone class.
-We have found that more than a third of all clone classes are flagged unrelated, which means that they have at least one instance that has no relation through inheritance with the other instances.
-For about a fourth of the clone classes all of its instances are in the same class.
-About a sixth of the clone classes have clone instances that are siblings of each other (share the same superclass).
+We defined three aspects as part of the context of a clone: relation, location and contents.
+Regarding relations, we found that 37\% of clones are found in the same class.
+24\% of clones are in the same inheritance hierarchy.
+Another 24\% of clones are unrelated.
+The final 7\% of clones have the same interface.
+Regarding where a clone is found, 78\% of clones is found at method-level of which 77\% is found in the body of a method or constructor.
+Because of this, the ``Extract Method'' refactoring method is most suitable to refactor most clones.
 
-Secondly, we looked at the location of clone instances.
-Most clone instances (58 percent) are found at method level.
-About 37 percent of clone instances were found at class level.
-We defined ``class level clones'' as clones that exceed the boundaries of a single method or contain something else in the class (like field declarations, other methods, etc.).
-Thirdly, we looked at the contents of clone instances.
-Most clones span a part of a method (57 percent).
-About 26 percent of clones span over several methods.
+We built a tool that can automatically apply refactorings to 28\% of clones in our corpus using the ``Extract Method'' refactoring technique.
+The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, for instance when code outside a method is part of a clone.
 
-We also looked into the refactorability of clones that span a part of a method.
-Over 10 percent of the clones can directly be refactored by extracting them to a new method (and calling the method at all usages using their relation).
-The main reason that most clones that span a part of a method cannot directly be refactored by method extraction, is that they contain \texttt{return}, \texttt{break} or \texttt{continue} statements.
+We measured the effect of clone refactoring on the volume, cyclomatic complexity, duplication and method parameters metrics of the codebase.
+We measured these metrics before- and after each clone class that was refactored to determine the impact of each refactoring on system maintainability.
+We found that the most prominent factor influencing maintainability is the size of the clone.
+For our dataset, at a clone volume of 29 tokens per clone instance the average clone refactoring improved system maintainability.
+Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data.
+We noticed that the inheritance relation of the clone and the return value of the extracted method has only a minor impact on system maintainability.
 

### 2019-08-20 sections/conclusion.tex
Conclusion

@@
 
-We defined three aspects as part of the context of a clone: relation, location and contents.
-Regarding relations, we found that 37\% of clones are found in the same class.
+To determine which refactoring techniques are most suitable to refactor most clones, we analyzed their context.
+We measured the \textbf{relation} through inheritance of clone instances in a clone class.
+In our corpus, we found that 37\% of clones are found in the same class.
 24\% of clones are in the same inheritance hierarchy.
@@
 The final 7\% of clones have the same interface.
-Regarding where a clone is found, 78\% of clones is found at method-level of which 77\% is found in the body of a method or constructor.
+We also looked at the \textbf{location} of clones: 78\% of clones is found at method-level of which 77\% is found in the body of a method or constructor.
 Because of this, the ``Extract Method'' refactoring method is most suitable to refactor most clones.
@@
 We built a tool that can automatically apply refactorings to 28\% of clones in our corpus using the ``Extract Method'' refactoring technique.
-The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, for instance when code outside a method is part of a clone.
+The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, for instance when code outside the method body is part of a clone.
 
-We measured the effect of clone refactoring on the volume, cyclomatic complexity, duplication and method parameters metrics of the codebase.
+We measured the effect of clone refactoring on the volume, cyclomatic complexity, number of parameters and duplication metrics of the codebase.
 We measured these metrics before- and after each clone class that was refactored to determine the impact of each refactoring on system maintainability.

### 2019-08-20 sections/conclusion.tex
Introduction

@@
 In this study we presented evidence regarding the value of applying automated refactoring to analyze the before- and after state of source code and refactored source code.
-Analyzing these states we were able to analyze the improvement in maintainability after applying certain refactorings.
+Analyzing these states we were able to analyze the improvement in maintainability after refactoring duplicated code.
 This allows us to better assess thresholds by which maintainability issues in source code are identified.
@@
 When multiple parameters are used together in a method, there is an implicit dependency between these parameters: the dependency of being required by that method.
-\textit{If a lot of data hangs around really tight together, they should be made into their own object} \cite{fowler1999refactoring, visser2016building}.
+\textit{If a lot of data hangs around really tight together, they should be made into their own object} \cite{fowler1999refactoring}.
 Guidelines describe to limit the number of parameters per method to at most 4 \cite{visser2016building}.
@@
 
-We recommend to extend our tool, CloneRefactor, to allow for such capabilities.
-CloneRefactor already contains a component that calculates the Cyclomatic Complexity of a given method.
-Using our automated refactored model, identified problems can relatively easily be refactored.
-
 \subsubsection{Method size}
@@
 
-When programming, there are often trade-offs between technical debt and velocity.
-When a deadline comes near, often software quality in sacrificed to gain velocity \cite{costello1984software, austin2001effects, shah2014global}.
-Apart from that, a low programmer aptitude can result in low quality code \cite{cheney1984effects}.
-This is because often forming appropriate abstractions requires time, effort and critical thinking.
-By introducing these abstractions automatically, this negative impact can (partly) be mitigated.
 %When programming, many developers must take decisions between velocity

### 2019-08-20 sections/introduction.tex
Introduction

@@
 % TODO: Sander - What is refactoring? Hier zeg je meteen waarvoor het gebruikt wordt
-Refactoring is used to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
+Refactoring is the process of restructuring code to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
 There are many methods that have been introduced to help with the process of refactoring \cite{fowler2018refactoring, wake2004refactoring}.
@@
 Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, or does not happen at all \cite{mens2003refactoring}.
-For a large part, refactoring requires domain knowledge to do it right.
+%For a large part, refactoring requires domain knowledge to do it right.
 However, there are also refactoring opportunities that are rather trivial and repetitive to execute.
 % De zien hierna staat ook al in laatste alineas, past minder goed binnen intro imo
-In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
+%In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
 The main goal is to improve maintainability of the refactored code.
@@
 Duplication in source code is often seen as one of the most harmful types of technical debt.
-\textit{``Clones are problematic for the maintainability of a program, because if the clone is altered at one location to correct an erroneous behaviour, you cannot be sure that this correction is applied to all the cloned code as well.
-Additionally, the code base size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work''} \cite{ostberg2014automatically}.
-Bruntink et al.~\cite{bruntink2005use} show that code clones can contribute up to 25\% of the code size.
-% TODO: Sander - why is it bad to increase code size (i know ;) but reader might not)
+If the clone is altered at one location to correct an erroneous behaviour, you cannot be sure that this correction is applied to all the cloned code as well \cite{ostberg2014automatically}.
+Additionally, the code base size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work, as code clones can contribute up to 25\% of the code size \cite{bruntink2005use}.
 
@@
 We use software maintainability metrics to measure the impact of refactoring clones.
-This way we can determine better definitions of clones.
 We also look into what variability we can allow between code fragments to still consider them clones, while still improving maintainability when refactoring these clones.
@@
 \begin{itemize}
-	\item Find refactoring candidates, either tool-assisted or manually. % TODO: Sander - is tool assisted niet ook beetje manual? lijkt meer tool-assisted vs fully manual of iets
-	\item Refactor identified candidates, either tool-assisted or manually.
+	\item Find refactoring candidates, either tool-assisted or fully manually. % TODO: Sander - is tool assisted niet ook beetje manual? lijkt meer tool-assisted vs fully manual of iets
+	\item Refactor identified candidates, either tool-assisted or fully manually.
 \end{itemize}

### 2019-08-20 sections/discussion.tex
Conclusion
2R and 3R thresholds discussion

@@
 In this chapter, we discuss the results of our research and experiments.
-% TODO: Sander - ik mis ergens in chapter nog interpretatie van je resultaten van H6, of heb ik iets gemist?
 
@@
 In this section, we discuss the differences between clone types 1-3 and 1R-3R.
+
+\subsubsection{Found nodes}
 In Figure \ref{fig:typeres} we see that the difference between T1R and T1 is relatively small (11\% more cloned nodes found for T1).
@@
 
+\subsubsection{Performance}
 Regarding performance (Figure~\ref{fig:performance}, there is a notable difference between the refactoring-oriented clone types and the literature clone types.
@@
 The main reason for this is type resolution: finding the fully qualified identifiers of type-, variable- and method-references.
+
+\subsubsection{Type 2R Variability}
+In Figure~\ref{fig:t2rgraph} we show the increase of cloned nodes for a higher variability between clone instances.
+This graph is logaritmic: as the variability increases, the increase in nodes decreases.
+This implies that semantical equality increases the chances that tokens are equal.
+
+\subsubsection{Type 3R Gap Size}
+In Figure~\ref{fig:t3rgraph} we show the decrease in clone classes and the increase in cloned nodes when we increase the type 3R gap size threshold.
+We measure this threshold from a gap size of 0-200\%.
+In the graph, we see that both lines are rather linearly with minor jumps at certain thresholds.
+The jumps are at 33\%, 50\%, 100\%, 150\% and 200\%.
+The jump at 50\% is the largest.
+This makes sense regarding the nature of the threshold.
+At 50\%, all clone instances of 2 nodes with a gap of one node will merge into type 3R clones.
+
+The line denoting the number of clone classes seems a bit exponential whereas the line denoting cloned nodes is mostly linear.
+This also makes sense regarding the nature of the threshold.
+As we get into higher gap size percentages, fewer clones merge (thus the decrease in amount of clone classes merging).
+However, at these higher gap size percentages the gaps contains more nodes (thus the amount of cloned nodes being linear).
 

### 2019-08-20 sections/results.tex
PRI
Threats to validity
2R and 3R thresholds discussion

@@
 \subsection{Type 2R Variability Threshold}
-To determine the influence of the type 2R variability threshold on the amount of found nodes, we ran CloneRefactor for all variability percentages (0\% meaning no variance in expressions, 100\% meaning any variance in expression).
+To determine the influence of the type 2R variability threshold on the amount of found nodes, we ran CloneRefactor for all variability percentages (0\% meaning no variance in expressions, 100\% meaning any variance in expressions).
 Figure \ref{fig:t2rgraph} shows the results.
@@
 Table~\ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability.
-We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance.
+We mark rows based on less than 100 refactorings red, as their result does not have statistical significance.
 
@@
 \begin{figure}[H]
+  \centering
   \includegraphics[width=0.8\columnwidth]{img/arguments}

### 2019-08-20 icse/paper.tex
Conclusion
Ana

@@
 \begin{abstract}
-Duplication in source code is often seen as one of the most harmful types of technical debt because it increases the size of the codebase and creates implicit dependencies between fragments of code.
+Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code.
 To remove such anti-patterns, the codebase should be refactored.
-Many tools aid in the detection process of such duplication problems, but failed to determine whether a duplicate fragment would improve the maintainability of the codebase when refactored.
+Many tools aid in the detection process of such duplication problems, but fail to determine whether refactoring a duplicate fragment would improve the maintainability.
 
-We perform an exploratory study into the data that can be gathered from comparing before- and after snapshots of an automatically refactored system.
-We propose a tool to detect clones, analyze their context and automatically refactor a subset of them.
-We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the system.
-On the basis of these results, we decide which clones improve system design and thus should be refactored.
-%We identified a set of four factors that influence the maintainability impact of clones.
+We address this shortcoming by first analyzing what data should be gathered from an automatically refactored system.
+We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them.
+We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system.
+Based on these results, one could decide which clones improve system design and thus should be refactored.
+We evaluate our approach over a large corpus of open source Java projects.
+
+We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use.
+we find that the size of a clone is the biggest influencing factor: the majority of duplicates spanning 29 or more tokens improve maintainability when refactored.
+The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the refactored method should not have more than 2 arguments.
+%The relation  %We identified a set of four factors that influence the maintainability impact of clones.
 The first is the size of the clone.
@@
 By using these four factors, we can suggest only clones that will improve maintainability when refactored and prioritize them accordingly.
-Given these maintainability influencing factors and their effect on the source code, we measure their impact over a large corpus of open source Java projects.
+%Given these maintainability influencing factors and their effect on the source code, we measure their impact over a large corpus of open source Java projects.
 %This results in a set of thresholds by which clones can be found that should be refactored to improve system maintainability.
 
-We have identified that the size of the duplication problem is the biggest influencing factor on system maintainability.
-We found that the majority of duplicates spanning 29 or more tokens improve maintainability when refactored.
-Another maintainability influencing factor is the amount of data that needs to be passed to the merged location of the duplicate.
 \end{abstract}
@@
 
-In this study, we define a technique to detect clones such that they can be refactored.
-We evaluate the context of clones to determine which refactoring techniques are required to refactor clones in a specific context.
-We propose a tool for the automated refactoring of a subset of the detected clones, by extracting a new method out of duplicated code.
+In this study, we define a technique to detect clones such that they can be automatically refactored.
+We evaluate the relation and location of clones to determine which refactoring techniques are best suited.
+We introduce a tool that automatically refactors clones by extracting new methods out of duplicated code.
 
-We use automated refactoring to compare the maintainability of the before- and after snapshots of a codebase for each duplication problem that is refactored.
+%TODO: Hint about results. Hint about methodology.
+We evaluate our approach by comparing the maintainability of before- and after snapshots of a codebase for each duplication problem that is refactored.
 This gives us insight into whether clones detected by certain thresholds should be refactored to improve the maintainability of the codebase.
@@
 \section{Background}
-This study researches an intersection of code clone and refactoring research. In this background section, we will explain the required background knowledge for terms used throughout this study.
-
-\subsection{Code clone terminology}
-In this study we use two concepts used to argue about code clones \cite{roy2007survey}:
+Our study lies intersection of code clone and refactoring research. %In this background section, we explain the required background knowledge for terms used throughout this study.
+We use two concepts to argue about code clones \cite{roy2007survey}:
 \\ \textbf{Clone instance}: A single cloned fragment.
@@
 
-\subsection{Refactoring techniques}
-In this section, we describe refactoring techniques that are relevant to refactoring code clones.
-
-\subsubsection{Extract Method}
-The most used technique to refactor duplicate code is ``Extract Method'' \cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
-Several studies have already concluded that most duplication in source code is found in the body of methods \cite{lozano2007evaluating, white2016deep, bergman2004ethnographic}.
-The ``Extract Method'' technique moves functionality in method bodies to a new method.
-To reduce duplication, we extract the contents of a single clone instance to a new method and replace all clone instances by a call to this method.
-
-\subsubsection{Move Method}
-Often, ``Extract Method'' alone is not enough to refactor clones.
+%\subsection{Refactoring techniques}
+%In this section, we describe refactoring techniques that are relevant to refactoring code clones.
+There are several refactoring techniques that are relevant to refactoring duplicated code:
+\\ \textbf{Extract Method}: A common technique to refactor duplicate code is ``Extract Method'' \cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
+This technique moves functionality in method bodies to a new method.
+To reduce duplication, we extract the contents of a single clone instance to a new method and replace all clone instances in a clone class by a call to this method.
+\\ \textbf{Move Method}: Often, ``Extract Method'' alone is not enough to refactor clones.
 This is because the extracted method has to be moved to a location that is accessible by all clone instances.
@@
 \section{Conclusion}
-We defined refactorable clones and created a tool to detect and refactor them.
+We defined automatically refactorable clones and created a tool to detect and refactor them.
 We measured statistical data with this tool over a large corpus of open-source Java software systems to get more information about the context of clones and how refactoring them influences system maintainability.

### 2019-08-20 icse/paper.tex
ANA II

@@
 In this study, we define a technique to detect clones such that they can be automatically refactored.
+We list a set of criteria that can obtruct refactoring opportunities.
 We evaluate the relation and location of clones to determine which refactoring techniques are best suited.
@@
 %In this section, we describe refactoring techniques that are relevant to refactoring code clones.
-There are several refactoring techniques that are relevant to refactoring duplicated code:
-\\ \textbf{Extract Method}: A common technique to refactor duplicate code is ``Extract Method'' \cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
+The most common technique for refactoring clones is ``Extract Method'' \cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
 This technique moves functionality in method bodies to a new method.
-To reduce duplication, we extract the contents of a single clone instance to a new method and replace all clone instances in a clone class by a call to this method.
-\\ \textbf{Move Method}: Often, ``Extract Method'' alone is not enough to refactor clones.
-This is because the extracted method has to be moved to a location that is accessible by all clone instances.
-To do this, we apply the ``Move Method'' refactoring technique \cite{fowler2018refactoring}.
-In object-oriented programming languages, we often move methods up in the inheritance structure of classes, also called ``Pull Up Method'' \cite{fowler2018refactoring}.
+This technique extracts the contents of a single clone instance to a new method and replace all clone instances in a clone class by a call to this method.
+
+%TODO: Maybe explain something about ASTs, declarations, types, etc.?
 
@@
 In literature, several clone type definitions have been used to argue about duplication in source code \cite{roy2007survey}.
-In this section, we discuss how we can define clones such that they can be refactored without side effects on the source code.
+We discuss how we can define clones such that they can be automatically refactored without side effects on the source code.
 
@@
 % Explain type 1, why it is not always refactorable, solution
-Most modern clone detection tools detect clones by comparing the code textually together with the omission of certain tokens \cite{roy2009comparison, svajlenko2014evaluating}.
+Most modern clone detection tools detect duplication by comparing the code textually together with the omission of certain tokens \cite{roy2009comparison, svajlenko2014evaluating}.
 Clones detected by such means may not always be suitable for refactoring, because textual comparison fails to take into account the context of certain symbols in the code.
@@
 
-To detect clones that can be refactored, we propose to:
+To detect clones that can be automatically refactored, we propose to:
 \begin{itemize}
-  \item Compare variable references not only by their name but also by their type.
+  \item Compare variable references not only by their name, but also by their type.
   \item Compare referenced types by their fully qualified identifier (FQI). The FQI of a type reference describes the full path to where it is declared.
@@
 Often, duplication fragments in source code do not match exactly \cite{kodhai2013method}.
-Often when developers duplicate fragments of code, they modify the duplicated block to fit its new location and purpose.
-To detect duplicate fragments with minor variance, we look into in what expressions we can allow variability while still being refactorable.
+When developers duplicate fragments of code, they modify the duplicated block to fit its new location and purpose.
+To detect duplicate fragments with minor variance, we look into what expressions we can allow variability in, while still being refactorable.
 
@@
 
-\section{CloneRefactor}
+\section{The CloneRefactor tool}
 % NEED TO EXPLAIN WHY DO CURRENT DETECTION TOOLS NOT SUFFICE
@@
 To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques \cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
-We created a set of control projects to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
-None of the surveyed tools \cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we decided to implement our own tool.
+We created a set of control projects\footnote{Control projects for assessing clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
 
-To automate the process of refactoring clones, we propose a tool named CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
-This tool goes through a 3-step process to refactor clones.
-This process is displayed in Fig.~\ref{fig:clonerefactorflow}.
+None of the surveyed tools \cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we decided to implement our own tool: \url{https://github.com/SimonBaars/CloneRefactor}}.
+This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
+In the following sections, we explain these steps.
 \begin{figure}[H]
@@
 \end{figure}
-In this section, we explain each of these steps.
 
@@
 After clones are detected, we map the context of these clones.
-We have identified three properties of clones as their context: relation and contents.
+We have identified three properties of clones as their context: relation and location.
 We identify categories for each of these properties, to get a detailed insight into the context of clones.
@@
 % The rationale for our categories regarding clone relations.
-Clone instances in a clone class can have a relation with each other through inheritance.
+Clone instances in a clone class may have a relation with each other through inheritance.
 This relation has a big impact on how the clone should be refactored \cite{fontana2015duplicated}.
 We define the following categories to map the relation between clone instances in a clone class.
-These categories do not map external classes (classes outside the project, for instance, belonging to a library) unless explicitly stated:
+These categories do not map external classes (classes outside the project, e.g.
+belonging to a library) unless explicitly stated:
 \begin{itemize}
@@
 
-Based on these relations, we determine where to place the cloned code when refactored.
+Based on these relations, CloneRefactor determines where to place the cloned code when refactored.
 The code of clones that have a \textit{Common Class} relation can be refactored by placing the cloned code in this same class.
@@
 
-\subsubsection{Contents}\label{sec:contents}
-% The rationale for our categories regarding clone contents.
-The contents of a clone instance determine what refactoring techniques can be applied to refactor such clones. We define the following categories by which we analyze the contents of clones:
+\subsubsection{Location}\label{sec:location}
+% The rationale for our categories regarding clone locations.
+The location of a clone instance determine what refactoring techniques can be applied to refactor such clones. We define the following categories by which we analyze the location of clones:
 \begin{enumerate}
   \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
-  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method/constructor.
+  \item \textbf{Partial Method/Constructor Body:} A clone that spans (a part of) the body of a method/constructor.
   \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods.
@@
     \item \textbf{Spans Part Of A Block}: This clone spans a part of a block statement.
-    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Sec.~\ref{sec:contents}, the ``Extract Method'' refactoring technique cannot be applied.
+    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Sec.~\ref{sec:location}, the ``Extract Method'' refactoring technique cannot be applied.
     \item \textbf{Returns Multiple Values}: If a clone modifies or declares multiple pieces of data that it should return.
@@
 
-\subsubsection{Contents}
-Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Sec.~\ref{sec:contents}).
+\subsubsection{Location}
+Table~\ref{tab:location} displays the number of clone classes found for the entire corpus for different locations (see Sec.~\ref{sec:location}).
 
@@
 \toprule
-\textit{\textbf{Category}} & \textit{\textbf{Contents}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
+\textit{\textbf{Category}} & \textit{\textbf{Location}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
 \multirow{2}{*}{Partial} & Partial Method & 219,540 & \multirow{2}{*}{229,521} \\ \cmidrule(lr){2-3}
@@
 \end{tabular}
-\caption{Number of clone instances for clone contents categories}
-\label{tab:contents}
+\caption{Number of clone instances for clone location categories}
+\label{tab:location}
 \end{table}
@@
 
-Regarding clone contents, 74\% of clones span part of a method body (77\% if we include constructors).
+Regarding clone locations, 74\% of clones span part of a method body (77\% if we include constructors).
 8\% of clones span several methods, which often require refactorings on a more architectural level.
@@
 
-We defined two aspects as part of the context of a clone: relation and contents.
+We defined two aspects as part of the context of a clone: relation and location.
 Regarding relations, we found that most clones are found in the same class, over 37\%.
@@
 The final 7\% of clones have the same interface.
-Regarding contents, over 74\% of clones span part of a method.
+Regarding location, over 74\% of clones span part of a method.
 About 8\% span several methods.

### 2019-08-20 sections/experimentalsetup.tex
Experimental setup

@@
 In this study, we use four metrics to determine maintainability (see Section~\ref{sec:metrics}).
-For our experiments, we aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
+For our experiments, we aggregate the deltas obtained for these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
 We base our aggregation on the following assumptions:
@@
   \item Higher values for the metrics imply lower maintainability.
-  \item The obtained increase of the metric divided by the average distance from zero over our corpus weights the metric equally against the other metrics.
+  \item Normalizing each obtained metric delta over all deltas obtained a metric in our dataset results in equally weighted scores.
 \end{itemize}
@@
 
-By dividing the obtained metric scores by the average distance from zero of all obtained values for a specific metric, we ensure that each metric is weighted equally towards the final maintainability score.
-We calculate this average distance as follows:
+We normalize each obtained metric delta using the ``Standard score'', which is as follows:
 \begin{equation}\label{eq:scoredev}
-A = \frac{\sum_{x \in M} abs(x)}{|M|}
+N_{metric} = \frac {\delta X-\mu}{\sigma}
 \end{equation}
-Where \textit{M} is the multiset of all metric increase/decrease values for all refactorings applied to a certain metric over our corpus.
-\textit{|M|} is the cardinality of this multiset.
+Where $\delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metrics.
+This method works well for normalization of our data, because as we divide by the standard deviation, outliers do not influence the resulting scores much.
+
 We then calculate the maintainability for a specific refactoring as follows:
 \begin{equation}\label{eq:scoreref}
-A_M = \frac{dup}{A_{dup}} + \frac{com}{A_{com}} + \frac{par}{A_{par}} + \frac{vol}{A_{vol}}
+N_{duplication} + N_{complexity} + N_{volume} + N_{parameters}
 \end{equation}
-Where \textit{dup} is the decrease in duplication, \textit{com} is the decrease in complexity, \textit{par} is the decrease is method parameters and \textit{vol} is the decrease in system volume after the refactoring is applied.
-When comparing the maintainability of a set of refactorings we divide the sum of the maintainability score by the amount of clone instances of all refactored clones in the set.

### 2019-08-20 icse/paper.tex
Fixed stuff

@@
 
-None of the surveyed tools \cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we decided to implement our own tool: \url{https://github.com/SimonBaars/CloneRefactor}}.
+None of the surveyed tools \cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we decided to implement our own tool: CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
 This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
@@
 In this study, we use four metrics to determine maintainability (see Sec.~\ref{sec:metrics}).
-For our experiments, we aggregate the scores obtained by these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
+For our experiments, we aggregate the deltas obtained for these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
 We base our aggregation on the following assumptions:
@@
 
-By dividing the obtained metric scores by the average distance from zero of all obtained values for a specific metric, we ensure that each metric is weighted equally towards the final maintainability score.
-We calculate this average distance as follows:
+We normalize each obtained metric delta using the ``Standard score'', which is as follows:
 \begin{equation}\label{eq:scoredev}
-A = \frac{\sum_{x \in M} abs(x)}{|M|}
+N_{metric} = \frac {\Delta X-\mu}{\sigma}
 \end{equation}
-Where \textit{M} is the multiset of all change in a certain metric for all refactorings over all systems in  obtained for a certain metric over our corpus and \textit{|M|} is the cardinality of this set.
+Where $\Delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metrics.
+This method works well for normalization of our data, because as we divide by the standard deviation, outliers do not influence the resulting scores much.
+
 We then calculate the maintainability for a specific refactoring as follows:
 \begin{equation}\label{eq:scoreref}
-A_M = \frac{dup}{A_{dup}} + \frac{com}{A_{com}} + \frac{par}{A_{par}} + \frac{vol}{A_{vol}}
+N_{duplication} + N_{complexity} + N_{volume} + N_{parameters}
 \end{equation}
-Where \textit{dup} is the decrease in duplication, \textit{com} is the decrease in complexity, \textit{par} is the decrease is method parameters and \textit{vol} is the decrease in system volume after the refactoring is applied.
-When comparing the maintainability of a set of refactorings we divide the sum of the maintainability score by the amount of clone instances of all refactored clones in the set.
 

### 2019-08-20 sections/experimentalsetup.tex
Fixed stuff

@@
 
-\section{The corpus}\label{chap:corpus}
+\section{Tool Validation}
+\todo{TODO}
+
+\section{The Corpus}\label{chap:corpus}
 For our experiments we use a large corpus of open source projects \cite{githubCorpus2013}.
@@
 
-We normalize each obtained metric delta using the ``Standard score'', which is as follows:
+We normalize each obtained metric delta using the ``Standard score'', which is calculated as follows:
 \begin{equation}\label{eq:scoredev}
-N_{metric} = \frac {\delta X-\mu}{\sigma}
+N_{metric} = \frac {\Delta X-\mu}{\sigma}
 \end{equation}
-Where $\delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metrics.
+Where $\Delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metrics.
 This method works well for normalization of our data, because as we divide by the standard deviation, outliers do not influence the resulting scores much.

### 2019-08-21 icse/paper.tex
Updated the abstract and such

@@
 We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use.
-we find that the size of a clone is the biggest influencing factor: the majority of duplicates spanning 29 or more tokens improve maintainability when refactored.
+We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a volume 68 or more tokens improve maintainability when refactored.
 The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the refactored method should not have more than 2 arguments.

### 2019-08-21 sections/abstract.tex
Updated the abstract and such

--- 2019-04-11 sections/abstract.tex
@@
 \chapter*{Abstract}
-\todo[inline,color=blue!10]{This should be done when most of the rest of the document is finished. Be concise, introduce context, problem, known approaches, your solution, your findings.}
+%\todo[inline,color=blue!10]{This should be done when most of the rest of the document is finished. Be concise, introduce context, problem, known approaches, your solution, your findings.}
+Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code.
+To remove such anti-patterns, the codebase should be refactored.
+Many tools aid in the detection process of such duplication problems, but fail to determine whether refactoring a duplicate fragment would improve the maintainability.
+
+We address this shortcoming by first analyzing what data should be gathered from an automatically refactored system.
+We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them.
+We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system.
+Based on these results, one could decide which clones improve system design and thus should be refactored.
+We evaluate our approach over a large corpus of open source Java projects.
+
+We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use.
+We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a volume 68 or more tokens improve maintainability when refactored.
+The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the refactored method should not have more than 2 arguments.

### 2019-08-21 sections/results.tex
Updated the abstract and such

@@
 \subsection{Clone Token Volume}
-Figure \ref{fig:duplication} shows the obtained results when plotting the clone size (in tokens) vs the maintainability increase/decrease.
+Figure \ref{fig:duplication} shows the obtained results when plotting the clone size vs the maintainability increase/decrease.
+We define clone size as the size of a single clone instance of the clone before refactoring.
 On the secondary axis the amount of refactorings that have refactored a clone with the specified amount of tokens is displayed (e.g.
@@
   \includegraphics[width=1\textwidth]{img/duplication}
-  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability. Maintainability on the primary axis and amount of refactorings on the secondary axis.}
+  \caption{A graph that shows how the token size affects the maintainability score of the refactored clone}
   \label{fig:duplication}
+\end{figure}
+
+This graph does not take into account the number of clone instances.
+Because of that, we plot a graph that shows the clone volume vs the number of refactorings.
+We define the clone volume as the sum of the number of tokens in each clone instance.
+The resulting chart is displayed in Figure~\ref{fig:tokenvolume}.
+
+\begin{figure}[H]
+  \includegraphics[width=1\textwidth]{img/Tokenvolume}
+  \caption{A graph that shows how the token volume affects the maintainability score of the refactored clone}
+  \label{fig:tokenvolume}
 \end{figure}

### 2019-08-21 sections/abstract.tex
Introduction

@@
 To remove such anti-patterns, the codebase should be refactored.
-Many tools aid in the detection process of such duplication problems, but fail to determine whether refactoring a duplicate fragment would improve the maintainability.
+Many tools aid in the detection process of such duplication problems but fail to determine whether refactoring a duplicate fragment would improve the maintainability.
 

### 2019-08-21 sections/introduction.tex
Introduction

@@
 \label{ch:introduction}
-% TODO: Sander - What is refactoring? Hier zeg je meteen waarvoor het gebruikt wordt
 Refactoring is the process of restructuring code to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
@@
 However, there are also refactoring opportunities that are rather trivial and repetitive to execute.
-% De zien hierna staat ook al in laatste alineas, past minder goed binnen intro imo
-%In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
+In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
 The main goal is to improve maintainability of the refactored code.
@@
 Additionally, the code base size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work, as code clones can contribute up to 25\% of the code size \cite{bruntink2005use}.
+
+\todo{A paragraph aboout current clone types being ill-defined for automated refactoring}
 
@@
 The maintainability of a codebase has a large impact on the time and effort spent on building the desired software system \cite{bakota2012cost, munson1978software}.
-The maintainability of software is one of the factors to be kept under control in order to avoid major delays and unexpected costs as a result of a software project \cite{fowler2018refactoring}.
+The maintainability of software is one of the factors to be kept under control in order to avoid major delays and unexpected costs as the outcome of a software project \cite{fowler2018refactoring}.
 One factor that has a major impact on the maintainability of a software system is the amount of duplicate code present in a codebase \cite{heitlager2007practical, fowler1999refactoring}.
 
-The process of improving maintainability through the refactoring of duplicate code is time consuming and error-prone. This process mainly consists of these two aspects:
+The process of improving maintainability through the refactoring of duplicate code is time consuming and error-prone. This process mainly consists of two aspects:
 \begin{itemize}
-	\item Find refactoring candidates, either tool-assisted or fully manually. % TODO: Sander - is tool assisted niet ook beetje manual? lijkt meer tool-assisted vs fully manual of iets
+	\item Find refactoring candidates, either tool-assisted or fully manually.
 	\item Refactor identified candidates, either tool-assisted or fully manually.
@@
 Many false negatives are due to the thresholds that are used.
-Many clone detection tools \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval} only consider clones that have a minimum of 6 lines.
-Using such an approach is bound to result in many false negatives, but using a lower threshold is shown to increase the number of false-positives.
-%TODO cite threshold paper
+Clone detection tools are configured using a predefined amount of lines or tokens that two duplicate fragments should minimally have for them to be considered clones \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval}.
+Often, such thresholds are intuitively chosen \cite{li2006cp, roy2009mutation}, leading to a potentially non-optimal selection of clones that are presented to developer.
 
@@
 \cite{bavota2012does} shows that the process of refactoring often leaves side effects in the code.
-This study reports that refactorings involving hierarchies (e.g., pull up method) % TODO: Sander -unsure of pull up method bekende term is, miss "creating a new method in a superclass"
-, tend to induce faults very frequently. \textit{This suggests more accurate code inspection or testing activities % TODO: Sander - .. are needed?
-when such specific refactorings are performed.} Such specific refactorings often have to be used when dealing with duplication in software \cite{fowler2018refactoring, fontana2015duplicated}.
+This study reports that refactorings moving components in the inheritance hierarchy of object-oriented software tend to induce faults very frequently.
+This suggests that more accurate code inspection or testing activities are needed when such refactoring techniques are performed.
+Those refactoring techniques often have to be used when dealing with duplication in software \cite{fowler2018refactoring, fontana2015duplicated}.
 Because of that, refactoring code clones has been empirically proven to cause bugs or other side effects in code.
@@
 \section{Scope}
-% TODO: Sander - iets over OOP hier?
 In this study, we perform research efforts to be able to detect refactorable clones.
@@
 
+\subsection{Java}
+This research is limited to object-oriented programming languages.
+We relate our research to the most popular object-oriented programming languages (Python, Java, C\#).
+Our experiments and results have been conducted in the Java programming language, because many refactoring practises are language-specific.
+
+\subsection{Measuring Maintainability}
 There is a lot of study on how what metrics to consider to measure maintainability.
@@
 
-Applying refactoring often entails creating new method declarations, class declarations, etc.
+\subsection{Naming Declarations}
+By our automated refactoring model new method declarations, class declarations and interfaces are created.
 Each of these declarations needs to have a name.
-Because the quality of the name is not included in the maintainability metrics we use, finding appropriate names for automatically refactored code fragments is out of the scope for this study.
+Because the quality of the name will not have an impact on the maintainability metrics we use, finding appropriate names for automatically refactored code fragments is out of the scope for this study.
 For our automated refactoring efforts, we will use generated names for these declarations.
+%This may decrease the usefulness of the results of this research for refactoring-assistance.
 
+\subsection{Testcode}
 It is very disputable whether unit tests apply to the same maintainability metrics that applies to the functional code.
@@
 The findings of this research may be applicable to those classes, but we will not argue the validity.
+Furthermore, any other code than the production code of the system will not be taken into account.
+In Section~\ref{chap:corpus} we describe what classes we perform our experiments on.
 
@@
 In Chapter~\ref{ch:background} we describe the background of this thesis.
-In Chapter~\ref{chap:clonetypes} we list shortcomings with clone definitions from literature and propose a set of clone type definitions which can be automatically refactored.
-% TODO: Sander - Nu zeg je dat de definities automatisch gerefactored kunnen worden
+In Chapter~\ref{chap:clonetypes} we list shortcomings with established clone definitions which make them less suitable for automated refactoring.
+We also propose a set of clone type definitions that strive to solve these shortcomings.
 In Chapter \ref{ch:clonerefactor} we propose a tool to detect, analyze and automatically refactor such clones that can be refactored.
-Using this tool we perform a set of experiments, of which the results are shown in Chapter~\ref{ch:results} and discussed in Chapter~\ref{ch:discussion}.
+Using this tool we perform a set of experiments, of which the setup is explained in Chapter~\ref{ch:experimentalsetup}.
+The results of the experiments are in shown in Chapter~\ref{ch:results} and discussed in Chapter~\ref{ch:discussion}.
 Chapter~\ref{ch:related_work} contains the work related to this thesis.

### 2019-08-21 sections/introduction.tex
Introduction again
Ah sh** here we go again

@@
 \chapter{Introduction}
-%\todo[inline,color=blue!10]{Context: what is the bigger scope of the problem you are trying to solve? Try to connect to societal/economical challenges.
+%\todo[inline,color=blue!10]{Context: what is the bigger scope of the problem you are trying to solve? Try to connect to societal/economic challenges.
 %Problem Analysis: Here you present your analysis of the problem situation that your research will address.
-%How does this problem manifest itself at your host organisation?
+%How does this problem manifest itself at your host organization?
 %Also summarises existing scientific insight into the problem.}
 \label{ch:introduction}
-Refactoring is the process of restructuring code to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
-There are many methods that have been introduced to help with the process of refactoring \cite{fowler2018refactoring, wake2004refactoring}.
-However, most of these methods still require manual assessment of where and when to apply them.
+Refactoring is the process of restructuring code to improve quality-related attributes of a codebase (maintainability, performance, etc.) without changing the functionality.
+Many methods have been introduced to help with the process of refactoring \cite{fowler2018refactoring, wake2004refactoring}.
+However, most of these methods still require a manual assessment of where and when to apply them.
 Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, or does not happen at all \cite{mens2003refactoring}.
@@
 In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''.
-The main goal is to improve maintainability of the refactored code.
+The main goal is to improve the maintainability of the refactored code.
 
 Duplication in source code is often seen as one of the most harmful types of technical debt.
-If the clone is altered at one location to correct an erroneous behaviour, you cannot be sure that this correction is applied to all the cloned code as well \cite{ostberg2014automatically}.
-Additionally, the code base size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work, as code clones can contribute up to 25\% of the code size \cite{bruntink2005use}.
+If the clone is altered at one location to correct an erroneous behavior, you cannot be sure that this correction is applied to all the cloned code as well \cite{ostberg2014automatically}.
+Additionally, the codebase size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work, as code clones can contribute up to 25\% of the code size \cite{bruntink2005use}.
 
-\todo{A paragraph aboout current clone types being ill-defined for automated refactoring}
+\todo{A paragraph about current clone types being ill-defined for automated refactoring}
 
@@
 We also look into what variability we can allow between code fragments to still consider them clones, while still improving maintainability when refactoring these clones.
-Futhermore, we look into the thresholds that should be used while detecting clones to find clones that should be refactored.
+Furthermore, we look into the thresholds that should be used while detecting clones to find clones that should be refactored.
 
-We perform several quantitative experiments on a large corpus of open source software to collect statistical data.
-With these experiments we map the context of clones: where they reside in the codebase and what the relation is between duplicate fragments.
+We perform several quantitative experiments on a large corpus of open-source software to collect statistical data.
+With these experiments, we map the context of clones: where they reside in the codebase and what the relation is between duplicate fragments.
 We use the results to find appropriate refactoring opportunities for specific clones.
@@
 \section{Problem statement}
-In this section we describe the problem we address in this study and the research questions that we answer in order to contribute to solving the problem.
+In this section, we describe the problem we address in this study and the research questions that we answer to contribute to solving the problem.
 
@@
 The maintainability of a codebase has a large impact on the time and effort spent on building the desired software system \cite{bakota2012cost, munson1978software}.
-The maintainability of software is one of the factors to be kept under control in order to avoid major delays and unexpected costs as the outcome of a software project \cite{fowler2018refactoring}.
+The maintainability of software is one of the factors to be kept under control to avoid major delays and unexpected costs as the outcome of a software project \cite{fowler2018refactoring}.
 One factor that has a major impact on the maintainability of a software system is the amount of duplicate code present in a codebase \cite{heitlager2007practical, fowler1999refactoring}.
 
-The process of improving maintainability through the refactoring of duplicate code is time consuming and error-prone. This process mainly consists of two aspects:
+The process of improving maintainability through the refactoring of duplicate code is time-consuming and error-prone. This process mainly consists of two aspects:
 \begin{itemize}
@@
 \end{itemize}
-There are tools that assist in the process of finding duplicate code, but none of these tools identify all duplication problems.
-Often, these clone detection tools result in false-positives and false negatives \cite{roy2007survey}.
-We define false negatives as clones that can and should be refactored but are not found due to the configuration by which they are detected.
-We define false-positives as clones that do not improve the system maintainability when refactored.
-Many false negatives are due to the thresholds that are used.
-Clone detection tools are configured using a predefined amount of lines or tokens that two duplicate fragments should minimally have for them to be considered clones \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval}.
-Often, such thresholds are intuitively chosen \cite{li2006cp, roy2009mutation}, leading to a potentially non-optimal selection of clones that are presented to developer.
+Clone detection tools are configured using a predefined amount of lines or tokens that two duplicate fragments should minimally span for them to be considered clones \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval}.
+Often, such thresholds are intuitively chosen \cite{li2006cp, roy2009mutation}, leading to a potentially non-optimal selection of clones that are presented to the developer.
 
@@
 However, there is no research yet that looks into how these definitions align with refactoring opportunities.
-We will align clone type definitions as used in literature \cite{roy2007survey} with their corresponding refactoring methods \cite{fowler2018refactoring}.
-For this, we answer the following research question:
+We align clone type definitions as used in literature \cite{roy2007survey} with their corresponding refactoring methods \cite{fowler2018refactoring} and address the shortcomings of these definitions regarding automated refactoring.
+This results in the following research question:
 \begin{displayquote}
@@
 \end{displayquote}
-As a result, we expect to formulate clone type definitions that can be refactored.
-On the basis of this results we can perform analyses on the context of clones by these definitions.
-The context of a clone (location, relation between clones, etc.) has a big impact on how a clone should be refactored.
-We will create categories by which we map the context of clones and perform a statistical analysis on this.
+As a result, we formulate clone type definitions that can be refactored.
+Based on these results we perform analyses on the context of clones by these definitions.
+The context of a clone (the relation between cloned fragments, location of cloned fragments, etc.) has a big impact on how a clone should be refactored.
+We create categories by which we map the context of clones and perform statistical analyses on them.
 This results in the following research question:
@@
 \end{displayquote}
-We expect this research question to result in a priorization of refactoring opportunities: \textit{with what refactoring method can what percentage of clones be refactored?} As a result of these first two research questions we expect to have clone type definitions that can be refactored together with a prioritization of the refactoring methods that can be used.
-On the basis of this we expect to be able to build a script that can automatically refactor the highest prioritized clones.
-With this script, we expect to be able to answer our final research question:
+This research question results in a prioritization of refactoring opportunities: \textit{with what refactoring method can what percentage of clones be refactored?} As a result of these first two research questions, we have clone type definitions that can be refactored together with a prioritization of the refactoring methods that can be used.
+Based on this prioritization, we build a tool that automatically refactors a subset of the detected clones.
+
+Not in all cases will refactoring duplicated code result in a more maintainable codebase.
+Because of that, we compare the refactored code to the original code and measure the difference in maintainability.
+To do this, we use a practical model consisting of metrics to measure maintainability \cite{heitlager2007practical}.
+Based on this, we look into what \textit{thresholds} result in better maintainable code when refactored.
+This results in our final research question:
 \begin{displayquote}
@@
 \end{displayquote}
-Not in all cases will refactoring duplicated code result in a more maintainable codebase.
-Because of that, we compare the refactored code to the original code and measure the difference in maintainability.
-To do this, we will use a practical model consisting of metrics to measure maintainability \cite{heitlager2007practical}.
-Based on this, we can look into what \textit{thresholds} result in better maintainable code when refactored.
-These thresholds consist of the size of clones and the variability we can allow between cloned fragments to still consider them clones.
 
@@
 We also develop a tool to detect, analyze and refactor such clones.
-Using this tool, we perform \textbf{quantitative} experiments in which we statistically collect information about duplication in open source software.
-In these experiments we control several variables to see their impact on the results.
-During this process we explore concepts and develop understanding, because of which decisions in the study design are based upon the results of the experiments.
+Using this tool, we perform \textbf{quantitative} experiments in which we statistically collect information about duplication in open-source software.
+In these experiments, we control several variables to see their impact on the results.
+During this process, we explore concepts and develop understanding, because of which decisions in the study design are based on the results of the experiments.
 
@@
 With some code clones, the refactored alternative is less maintainable than keeping the duplication \cite{kapser2006cloning, aversano2007clones, hotta2010duplicate, kim2005empirical, krinke2007study, saha2010evaluating}.
-In this study, we analyze the maintainability of refactored code clones, in order to improve the suggestion of code clones that should be refactored.
+In this study, we analyze the maintainability of refactored code clones to improve the suggestion of code clones that should be refactored.
 This assists with both the identification and refactoring of code clones.
@@
 assisting in the refactoring process.
-The problem is that these tools have no limited % TODO: Sander -of limited of no, niet beide ;)
-insight on the impact of refactoring such clones on the design of the software.
+The problem is that these tools have no insight in the impact of refactoring such clones on the maintainability of the software.
 In this study, we can analyze a before- and after-refactoring snapshot of the code to determine the impact.
-A higher maintainability after refactoring increases the support for the clone being a true-positive.
+If the maintainability increases after refactoring, this gives a strong indication that the clone should be refactored.
 This way the results of our study can support the clone identification process.
@@
 \subsection{Refactoring}
-The tool that results from this research can aid in the process of applying refactorings to clones.
+The tool that results from this research can assist in the process of applying refactorings to clones.
 The tool will only apply a refactoring if the clone is refactorable and the maintainability of the source code increases as a result of applying the refactoring.
@@
 We relate our research to the most popular object-oriented programming languages (Python, Java, C\#).
-Our experiments and results have been conducted in the Java programming language, because many refactoring practises are language-specific.
+Our experiments and results have been conducted in the Java programming language because many refactoring practices are language-specific.
 
 \subsection{Measuring Maintainability}
-There is a lot of study on how what metrics to consider to measure maintainability.
+There is a lot of study on what metrics to consider to measure maintainability.
 In this study, we focus solely on the practical maintainability model by Heitlager et al.
 \cite{heitlager2007practical}.
-We consider the maintainability scores described in that paper as an sufficiently accurate indication of maintainability.
+We consider the maintainability scores described in that paper as a sufficiently accurate indication of maintainability.
 This will be used to quantitatively determine the impact on maintainability when applying refactoring techniques to code clones.
@@
 \subsection{Naming Declarations}
-By our automated refactoring model new method declarations, class declarations and interfaces are created.
+Our automated refactoring model can create new methods, classes and interfaces when refactoring clones.
 Each of these declarations needs to have a name.
@@
 \subsection{Testcode}
-It is very disputable whether unit tests apply to the same maintainability metrics that applies to the functional code.
+It is very disputable whether unit tests are subject to the same maintainability metrics that apply to the functional code.
 Because of that, for this research, unit tests are not taken into scope.
-The findings of this research may be applicable to those classes, but we will not argue the validity.
+The findings of this research may apply to test classes, but we will not argue the validity.
 Furthermore, any other code than the production code of the system will not be taken into account.
@@
 We also propose a set of clone type definitions that strive to solve these shortcomings.
-In Chapter \ref{ch:clonerefactor} we propose a tool to detect, analyze and automatically refactor such clones that can be refactored.
+In Chapter~\ref{ch:clonerefactor} we propose a tool to detect, analyze and automatically refactor such clones that can be refactored.
 Using this tool we perform a set of experiments, of which the setup is explained in Chapter~\ref{ch:experimentalsetup}.

### 2019-08-21 sections/introduction.tex
Okay this was the last of the introduction
#introduction #waytoomuchtimespent #yolo #thisisgonnagetmeintrouble #deadlinetomorrow #stress #help

@@
 However, most of these methods still require a manual assessment of where and when to apply them.
-Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, or does not happen at all \cite{mens2003refactoring}.
+Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, does not happen at all \cite{mens2003refactoring}, or leaves unintentional side-effects in the code \cite{bavota2012does}.
 %For a large part, refactoring requires domain knowledge to do it right.
@@
 
-Duplication in source code is often seen as one of the most harmful types of technical debt.
+Duplication in source code, also known as ``code clones'', is often seen as one of the most harmful types of technical debt.
 If the clone is altered at one location to correct an erroneous behavior, you cannot be sure that this correction is applied to all the cloned code as well \cite{ostberg2014automatically}.
@@
 
-\todo{A paragraph about current clone types being ill-defined for automated refactoring}
+Automating the refactoring process of code clones can help to deal with duplication problems.
+It can also assist in the evaluating whether refactoring a specific clone would improve the codebase, by using established metrics \cite{heitlager2007practical} to determine whether the code after applying the refactoring has improved.
+Howeverm clones detected on basis of established clone definitions \cite{roy2007survey} may not always be suitable for automated refactoring.
 
-In this study, we use refactoring techniques to automatically reduce duplication in software systems.
+In this study, we define clones such that they can be automatically refactored and build a tool to automatically refactor such clones.
 This allows us to obtain before- and after-refactoring snapshots of software systems.
-We use software maintainability metrics to measure the impact of refactoring clones.
+We use software maintainability metrics to measure the impact of these refactorings.
 We also look into what variability we can allow between code fragments to still consider them clones, while still improving maintainability when refactoring these clones.
@@
 Clone detection tools are configured using a predefined amount of lines or tokens that two duplicate fragments should minimally span for them to be considered clones \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval}.
-Often, such thresholds are intuitively chosen \cite{li2006cp, roy2009mutation}, leading to a potentially non-optimal selection of clones that are presented to the developer.
+Often, such thresholds are intuitively chosen \cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data \ref{alves2010deriving}.
+These methods do not always accurately reflect the effect of refactoring the system, leading to a potentially non-optimal selection of clones that are presented to the developer.
 

### 2019-08-21 sections/background.tex
Background

@@
 We created a summary of these concepts, which can be found in Table~\ref{tab:clone-terminology}.
+The terms displayed in this table show how tokens in code map to clones.
 
@@
 T & Token & - & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code.
-\\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range (R):} The range this token\\spans.\\ \textbf{Category (C):} Identifier, Keyword,\\Literal, Separator, Operator,\\ Comment or Whitespace.\end{tabular} \\
+\\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Category (C):} Identifier, Keyword,\\Literal, Separator, Operator,\\ Comment or Whitespace.\end{tabular} \\
 \rowcolor[HTML]{FFFFFF}
 N & Node \cite{jiang2007deckard} & Set of tokens.
-& \begin{tabular}[c]{@{}l@{}}A statement or declaration node\\in the AST of a codebase.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range (R):} The range this node\\spans.\end{tabular} \\
+& \begin{tabular}[c]{@{}l@{}}A statement or declaration node\\in the AST of a codebase.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range (R):} Begin line/column and end\\line/column of this node.\end{tabular} \\
 \rowcolor[HTML]{EFEFEF}
@@
 
-A \textbf{range} denotes the line and column at which a code fragment starts and ends. In this study, we use the symbols given in this table in our formulas.
-
-\subsection{Example}
-This section gives an example to make the terminology of Table~\ref{tab:clone-terminology} more concrete.
-The code fragment in Figure~\ref{fig:cloneclasses} shows two clone classes.
+As an example, consider the code fragments in Figure~\ref{fig:cloneclasses}.
+In this example, two clone classes are displayed.
 One of the clone classes consists of two clone instances and has three nodes per instance.
@@
 
-This example can be represented as a tree structure using the concepts from Table~\ref{tab:clone-terminology}. This tree structure is displayed in Figure~\ref{fig:terminologyexample}.
+This example can be represented as a tree structure using the concepts from Table~\ref{tab:clone-terminology} in Figure~\ref{fig:terminologyexample}.
 
@@
 \textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
-\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
-\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
+\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.
 \end{displayquote}
@@
 
-\subsection{Type 4 clones}
-For this study we have chosen to take type 4 clones out of the scope, because they are both hard to detect and hard to refactor. % TODO: Sander - why is this the case?
-A study by Kodhai et al \cite{kodhai2013method} looks into the distribution of the different types of clones in several open source systems (see table 6 of his study).
+%\subsection{Type 4 clones}
+%For this study we have chosen to take type 4 clones out of the scope, because they are both hard to detect and hard to refactor. % TODO: Sander - why is this the case?
+%A study by Kodhai et al \cite{kodhai2013method} looks into the distribution of the different types of clones in several open source systems (see table 6 of his study).
 It becomes apparent that type 4 clones exist way less in source code than all of the other types of clones.
@@
 
-\subsection{Clone refactoring in relationship to its context}
+%\subsection{Clone refactoring in relationship to its context}
 % TODO: Sander - Deze subsectie lijkt hier niet helemaal op zn plek
-How to refactor clones is highly dependent on their context.
+%How to refactor clones is highly dependent on their context.
 Method-level clones can be extracted to a method \cite{kodhai2013method} if all occurrences of the clone reside in the same class.
@@
 \section{(Object-Oriented) Programming Languages}
-% TODO: Sander - leg ook nog even in 1 zin uit wat een lezer aan al deze info heeft
-In this section we describe the relevant parts of the programming languages we research and experiment on.
+This section explains concepts, terminology and jargon of (object-oriented) programming languages that we use in this study.
 

### 2019-08-21 sections/research.tex
Research

@@
 \chapter{Defining refactoring-oriented clone types}\label{chap:clonetypes}
-In Section~\ref{chap:backgroundclonetypes} we introduced the four clone types as defined in literature. These simple % TODO: Sander - why are they simple, might just remove that word
-definitions are suitable for analysis of a codebase. Their detection results in simple to understand numbers to argue about a codebase. % TODO: Sander -this seems like an opinion
-However, these clone types have a few flaws which makes it hard to argue to what extend two fragments of code can and should be refactored.
+Clone type 1-3 (see Section~\ref{chap:backgroundclonetypes}) can (and should) not always be automatically refactored.
+we introduced clone types as defined in literature.
 For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings to increase the chance that we can refactor the clone while improving the design.
 
-We also look into clone detection tools for their suitability to support the proposed clone type definitions. We selected a few criteria % TODO: Sander -...?
-Most clone detection tools support these definitions of clone types.
+%We also look into clone detection tools for their suitability to support the proposed clone type definitions. We selected a few criteria % TODO: Sander -...?
+%Most clone detection tools support these definitions of clone types.
 However, many of these tools use a vastly different approach.
@@
 
-\section{Shortcomings of clone types}
-Clone types 1-3 (further explained in Section~\ref{chap:backgroundclonetypes}) allow reasoning about the duplication in a software system.
+\section{Problems with clone types for automated refactoring}
+%Clone types 1-3 (further explained in Section~\ref{chap:backgroundclonetypes}) allow reasoning about the duplication in a software system.
 Clones by these definitions can relatively easily and efficiently be detected.
 % TODO: Sander - compared to?
-This has allowed for large scale analyses of duplication~\cite{livieri2007very}.
+%This has allowed for large scale analyses of duplication~\cite{livieri2007very}.
 However, these clone type definitions have shortcomings which makes the clones detected in correspondence with these definitions less valuable for (automated) refactoring purposes.
 
-In this section, we discuss the shortcomings of the different clone type definitions.
+In this section, we discuss the shortcomings of clone type 1-3 \cite{roy2007survey}.
 Because of these shortcomings, clones found by these definitions are often found to require additional judgment whether they should and can be refactored.
@@
 \section{Suitability of existing Clone Detection Tools for detecting these clones}
-\todo{Is this still up to date?}
 \label{ch:tool-overview}
 We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities.
-The results of our survey are displayed in table~\ref{table:dettools}.
 We chose a set of tools that are open source and can analyze a popular object-oriented programming language.
@@
 \begin{enumerate}
-    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method level clones.
+    \item \textbf{Should find clones in any context}: Some tools only find clones in specific contexts, such as only method level clones.
 We want to perform an analysis of all clones in projects to get a complete overview.
-\item \textbf{Finds clone classes in control projects.} We assembled a number of control projects to assess the validity of clone detection tools.
-\item \textbf{Can analyze resolved symbols.} When detecting the types proposed in section~\ref{sec:rtypes}, it is important that we can analyze resolved symbols (for instance a type reference).
+\item \textbf{Finds clone classes in control projects\footnote{Control projects for assessing clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}}}: We assembled a number of control projects to assess the validity of clone detection tools.
+\item \textbf{Can analyze resolved symbols}: When detecting the types proposed in section~\ref{sec:rtypes}, it is important that we can analyze resolved symbols (for instance a type reference).
 The rationale for this is further explained in~\ref{chap:challenge}.
-\item \textbf{Extensive detection configuration.} Detecting our clone definitions, as proposed in section~\ref{sec:rtypes}, require to have some understanding about the meaning of tokens in the source code (whether a certain token is a type, variable, etc.).
+\item \textbf{Extensive detection configuration}: Detecting our clone definitions, as proposed in section~\ref{sec:rtypes}, require to have some understanding about the meaning of tokens in the source code (whether a certain token is a type, variable, etc.).
 The tool should recognize such structures, in order for us to configure our clone type definitions in the tool.
 \end{enumerate}
+The results of our survey are displayed in Table~\ref{table:dettools}.
 
-\begin{table}[H]
- \begin{center}
-  \caption{Our survey on clone detection tools.} \label{table:dettools}
-  \medskip
-\begin{tabular}{|l|l|l|l|l|l|}
-\hline
-\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
-Siamese~\cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
-NiCAD~\cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
-CPD~\cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
-\begin{tabular}[c]{@{}l@{}}CCFinder~\cite{kamiya2002ccfinder}\\ D-CCFinder~\cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
-CCFinderSW~\cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
-\begin{tabular}[c]{@{}l@{}}SourcererCC~\cite{sajnani2016sourcerercc}\\ Oreo~\cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
-BigCloneEval~\cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
-Deckard~\cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
-Scorpio~\cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
+\begin{table}[]
+\centering
+\begin{tabular}{@{}lcccc@{}}
+\toprule
+\textit{\textbf{Clone Detection Tool}} & \textit{\textbf{(1)}} & \textit{\textbf{(2)}} & \textit{\textbf{(3)}} & \textit{\textbf{(4)}} \\ \midrule
+Siamese~\cite{ragkhitwetsagul2019siamese} &  &  &  & \checkmark \\
+NiCAD~\cite{roy2008nicad, cordy2011nicad} & \checkmark & \checkmark &  &  \\
+CPD~\cite{roy2009comparison} & \checkmark & \checkmark &  &  \\
+\begin{tabular}[c]{@{}l@{}}CCFinder~\cite{kamiya2002ccfinder}\end{tabular} & \checkmark & \checkmark &  &  \\
+CCFinderSW~\cite{semura2017ccfindersw} & \checkmark &  &  & \checkmark \\
+\begin{tabular}[c]{@{}l@{}}SourcererCC/Oreo~\cite{sajnani2016sourcerercc, saini2018oreo}\end{tabular} & \checkmark &  &  & \checkmark \\
+BigCloneEval~\cite{svajlenko2016bigcloneeval} & \checkmark & \checkmark &  &  \\
+Deckard~\cite{jiang2007deckard} & \checkmark &  & \checkmark &  \\
+Scorpio~\cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark &  & \checkmark & \checkmark \\ \bottomrule
 \end{tabular}
-\end{center}
+\caption{Modern clone detection tools and the criteria they satisfy.}
+\label{tab:dettools}
 \end{table}

### 2019-08-21 sections/experimentalsetup.tex
Introduction again
Ah sh** here we go again
Tool validation

@@
-\chapter{Experimental Setup}
+\chapter{Experimental Setup}\label{ch:experimentalsetup}
 In this chapter we explain the setup of our experiments.
@@
 We then explain the way in which we calculate the impact of refactorings on the software maintainability.
-
-\section{Tool Validation}
-\todo{TODO}
 
@@
 In this section, we explain the steps we took to prepare the corpus\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} and the rationale behind those steps.
+
+\section{Tool Validation}
+We have validated the correctness of CloneRefactor through unit tests and empirical validation.
+First, we created a set of 57 control projects to verify the correctness in many (edge) cases.
+These projects contain clones for each identified relation, location, contents and refactorability category (see Section \ref{chap:contextsetup} and \ref{sec:refactorabilitysetup}), to see whether they get correctly identified.
+Next, we run the tool over the corpus and manually verify samples of the acquired results.
+This way, we check both the correctness of the identified clones, their context and their proposed refactoring.
+
+We also test the correctness of the resulting code after refactoring.
+For this, we use a GitHub project named JFreeChart.
+JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor.
 

### 2019-08-21 icse/paper.tex
:)

@@
 
+\subsection{Tool Validation}
+We have validated the correctness of CloneRefactor through unit tests and empirical validation.
+First, we created a set of 57 control projects to verify the correctness in many (edge) cases.
+These projects contain clones for each identified relation, location and refactorability category to see whether they get correctly identified.
+Next, we run the tool over the corpus and manually verify samples of the acquired results.
+This way, we check both the correctness of the identified clones, their context and their proposed refactoring.
+
+We also test the correctness of the resulting code after refactoring.
+For this, we use a GitHub project named JFreeChart.
+JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor.
+
 \subsection{Minimum clone size}

### 2019-08-21 sections/background.tex
:)

@@
 \section{Refactoring methods}
-Martin Fowler recently released the second edition of his Refactoring book \cite{fowler2018refactoring}.
-In this book he exclaims that \textit{``if you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them''} \cite{fowler1999refactoring, fowler2018refactoring}.
+In Martin Fowler's popular ``Refactoring'' book \cite{fowler2018refactoring}, he exclaims that \textit{``if you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them''}.
 He describes several methods to deal with duplication, dependent on the context of the clone.
@@
 \subsection{Extract Method}
-The main method for dealing with duplication in source code, as described by Martin Fowler, is to extract the duplication to a common place.
-This refactoring method is called ``Extract Method''.
-Several studies have already concluded that most duplication in source code is found in the body of methods \cite{lozano2007evaluating, white2016deep, bergman2004ethnographic}.
-Method extraction can move matching functionality in method bodies to a common place, namely a new method.
+Current clone refactoring research shows that the ``Extract Method'' refactoring technique can refactor most duplication problems \cite{fontana2015duplicated, tsantalis2015assessing, white2016deep}.
+Method extraction moves matching functionality in method bodies to a common place, namely a new method \cite{fowler2018refactoring}.
 An example of this procedure is displayed in figure \cite{fig:extractmethod}.

### 2019-08-22 sections/background.tex
Background Ana

@@
 \label{ch:background}
-This chapter will present the necessary background information for this thesis. Here, we define some basic terminology that will be used throughout this thesis.
+In this chapter we define some basic terminology that is used throughout this thesis.
 
@@
 \cite{jiang2007deckard}.
-We created a summary of these concepts, which can be found in Table~\ref{tab:clone-terminology}.
+A summary of these concepts can be found in Table~\ref{tab:clone-terminology}.
 The terms displayed in this table show how tokens in code map to clones.
@@
 
-This example can be represented as a tree structure using the concepts from Table~\ref{tab:clone-terminology} in Figure~\ref{fig:terminologyexample}.
+This example can be represented as a tree structure, as shown in Figure~\ref{fig:terminologyexample}.
 
@@
 
-\section{Refactoring methods}
+\section{Refactoring techniques}
 In Martin Fowler's popular ``Refactoring'' book \cite{fowler2018refactoring}, he exclaims that \textit{``if you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them''}.
-He describes several methods to deal with duplication, dependent on the context of the clone.
-In this section we describe the methods which we use in this study.
+He describes several techniques to deal with duplication, dependent on the context of the clone.
+In this section we describe the methods that we use in this study.
 
@@
 Current clone refactoring research shows that the ``Extract Method'' refactoring technique can refactor most duplication problems \cite{fontana2015duplicated, tsantalis2015assessing, white2016deep}.
-Method extraction moves matching functionality in method bodies to a common place, namely a new method \cite{fowler2018refactoring}.
-An example of this procedure is displayed in figure \cite{fig:extractmethod}.
+``Extract Method'' moves matching functionality in method bodies to a common place, namely a new method \cite{fowler2018refactoring}.
+An example of this procedure is displayed in figure \ref{fig:extractmethod}.
 
@@
 Based on the relation between clone instances, the extracted method must be moved to be accessible by all locations of the clone instances.
-This might require different techniques.
+This can require different techniques.
 
@@
 This way its possible to refactor both fully cloned methods (by just pulling up the method) and partially cloned methods (by first performing method extraction and then pulling up the refactored method).
+Anexample of this refactoring method is shown in Figure~\ref{fig:pullupmethod}.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+class Vehicle{
+  void start(){
+|\highlightYellow|    putKeyIn();
+|\highlightYellow|    turnKey();
+    drive();
+  }
+}
+
+class Car extends Vehicle{
+  void startEngine(){
+|\highlightYellow|    putKeyIn();
+|\highlightYellow|    turnKey();
+  }
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+class Vehicle{
+  void start(){
+|\highlightYellow|    startEngine();
+    drive();
+  }
+
+  void startEngine(){
+|\highlightYellow|    putKeyIn();
+|\highlightYellow|    turnKey();
+  }
+}
+
+class Car extends Vehicle{
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring a clone class using ``Pull Up Method''.}
+\label{fig:pullupmethod}
+\end{figure}
 
@@
 Duplication in source code is an implicit relation between fragments of source code.
-If two classes have many of these implicit relations, then the implementation should be refactored to make this relation explicit.
+If two classes have many of these implicit relations, then the implementation should be refactored to make this relation explicit \cite{fowler2018refactoring}.
 If the classes do not yet have a parent/super class, a parent class can be created and the common functionality can be placed in this newly created class.
@@
 
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+class Truck{
+  void startEngine(){
+|\highlightYellow|    putKeyIn();
+|\highlightYellow|    turnKey();
+  }
+}
+
+class Car{
+  void startEngine(){
+|\highlightYellow|    putKeyIn();
+|\highlightYellow|    turnKey();
+  }
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+class Vehicle{
+  void startEngine(){
+|\highlightYellow|    putKeyIn();
+|\highlightYellow|    turnKey();
+  }
+}
+
+class Truck extends Vehicle{
+}
+
+class Car extends Vehicle{
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring a clone class using ``Create class abstraction''.}
+\label{fig:createclassabstraction}
+\end{figure}
+
 \subsubsection{Providing default implementations for common functionality}
-Looking specifically at the Java programming language, recent versions of Java introduce a new method of reducing duplication through refactoring.
-Java has the concept of \textit{interfaces} as an abstract type that is used to specify a behavior that classes must implement.
-Since Java version 8, Java also supports default implementations to be provided in interfaces \cite{mohnen2002interfaces}.
+In Java, C\#, Python and possibly other object-oriented languages, the programmer can create interfaces of which a class can implement any number.
+Such interfaces can (in Java, C\# and Python) provide default implementations for common functionality \cite{mohnen2002interfaces}.
 This gives an opportunity to make the relation between classes explicit and reduce duplication.
 It can be used in instances where creating a new parent class for duplicated classes is undesirable.
+An example of this is shown in Figure~\ref{fig:createinterfaceabstraction}, in which two unrelated types (Human and Radio) share a common property (making sound).
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+class Human implements MakesSound{
+  void broadcastNews(){
+|\highlightYellow|    sayNews();
+|\highlightYellow|    sayWeather();
+  }
+}
+
+class Radio implements MakesSound{
+  void broadcastNews(){
+|\highlightYellow|    sayNews();
+|\highlightYellow|    sayWeather();
+  }
+}
+
+interface MakesSound{
+  void sayNews();
+  void sayWeather();
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+class Human implements MakesSound{
+}
+
+class Radio implements MakesSound{
+}
+
+interface MakesSound{
+  default void broadcastNews(){
+|\highlightYellow|    sayNews();
+|\highlightYellow|    sayWeather();
+  }
+
+  void sayNews();
+  void sayWeather();
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring a clone class creating a default implementation for common functionality.}
+\label{fig:createinterfaceabstraction}
+\end{figure}
 
@@
 
-\textit{External classes} are classes that a software system uses, but do not belong to this specific software system.
-Typically, the source code of external classes are not included in the source code of the project.
+\textit{External classes} are classes that a software system uses but do not belong to this specific software system (but to an external dependency).
 Most often these external dependencies are referenced in a file that its build automation system uses to fetch a projects' dependencies.
@@
 This can sometimes be a burden, when an external dependency does not use proper abstractions that are required by a software system.
-Because of that, in this study, we differentiate between internal and external classes to see what impact they have on the refactoring process.\todo{you don't consider external right?}
+In this study we take external classes into consideration when choosing a refactoring technique, to be sure not to modify them.
 
@@
 As these external dependencies are most often not included in a software systems' source code, we must first use the projects' build automation system to gather the dependencies.
-To limit the scope of this process, we decided to focus on only the \textit{Maven} build automation system.
+To limit the scope of this process, we decided to focus on only the \textit{Maven}\footnote{Apache Maven is a build automation system mainly used for Java: \url{https://maven.apache.org/}} build automation system.
 

### 2019-08-22 sections/research.tex
Fixed a display issue
Research Ana

@@
 Clone type 1-3 (see Section~\ref{chap:backgroundclonetypes}) can (and should) not always be automatically refactored.
-we introduced clone types as defined in literature.
+In Section~\ref{sec:literaturetypeproblems} we list shortcomings of each clone type that invalidate refactoring opportunities.
+In Section~\ref{sec:rtypes} we propose new clone type definitions that address these shortcomings.
+%we introduced clone types as defined in literature.
 For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings to increase the chance that we can refactor the clone while improving the design.
@@
 
-\section{Problems with clone types for automated refactoring}
+\section{Problems with clone types for automated refactoring}\label{sec:literaturetypeproblems}
 %Clone types 1-3 (further explained in Section~\ref{chap:backgroundclonetypes}) allow reasoning about the duplication in a software system.
@@
 In this section, we discuss the shortcomings of clone type 1-3 \cite{roy2007survey}.
-Because of these shortcomings, clones found by these definitions are often found to require additional judgment whether they should and can be refactored.
+Because of these shortcomings, clones found by these definitions are often found to require additional judgment whether they can and should be refactored.
 
@@
 This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
-When aiming to automatically refactor clones, applying refactorings to type 1 clones is bound to be error prone and can result in an uncompilable project or a difference in functionality.
+%When aiming to automatically refactor clones, applying refactorings to type 1 clones is bound to be error prone and can result in an uncompilable project or a difference in functionality.
 
@@
 
-In the example in Figure~\ref{fig:type1}, we see a type 1 clone displaying two clone classes.
+Figure~\ref{fig:type1} shows a type 1 clone with two clone classes.
 Defining an automatic way to refactor these clone classes is nearly impossible, as both cloned fragments describe different functional concepts.
@@
 
-The method call variability property of type 2R clones imply that type 2R clones are not a subset of type 2 clones.
+The method call variability property of type 2R clones implies that type 2R clones are not a subset of type 2 clones.
 Because methods calls can have a different structure, type 2R clones can be structurally slightly different.
@@
 \begin{javacode}
-|\highlightYellow|int a = getA(); // |\textcolor{pgreen}{$N_{1-1}$}|
-|\highlightBlue|doC(a); // |\textcolor{pgreen}{$N_{1-2}$}|
+|\highlightYellow|int a = getA(); // |\textcolor{pgreen}{$N_{1}$}|
+|\highlightBlue|doC(a); // |\textcolor{pgreen}{$N_{2}$}|
 \end{javacode}}
@@
 \begin{javacode}
-|\highlightYellow|int a = getA(); // |\textcolor{pgreen}{$N_{2-1}$}|
-a *= 5; // |\textcolor{pgreen}{$N_{2-2}$}|
-|\highlightBlue|doC(a); // |\textcolor{pgreen}{$N_{2-3}$}|
+|\highlightYellow|int a = getA(); // |\textcolor{pgreen}{$N_{3}$}|
+a *= 5; // |\textcolor{pgreen}{$N_{4}$}|
+|\highlightBlue|doC(a); // |\textcolor{pgreen}{$N_{5}$}|
 \end{javacode}}
@@
 \begin{equation}\label{eq:type3r}
-\text{T3R Gap Size}=\frac{|\{N_{2-2}\}|}{|\{N_{2-1}\}| + |\{N_{2-3}\}|}*100 = \frac{1}{2}*100 = 50\%
+\text{T3R Gap Size}=\frac{|\{N_{4}\}|}{|\{N_{3}, N_{5}\}|}*100 = \frac{1}{2}*100 = 50\%
 \end{equation}
+
+Where \textit{\{...\}} is the notation for sets and \textit{|A|} is the cardinality of set A.
 
@@
 Apart from this threshold, the gap in between clones may not span over different blocks.
-Look at Figure~\ref{fig:type3invalid} for an example of this.
+Figure~\ref{fig:type3invalid} illustrates this.
 We cannot refactor both statements into a single conditional block.
@@
 \begin{equation}\label{eq:typerelation}
-Cloned nodes T1R \subseteq Cloned nodes T2R \subseteq T3R
+clones(T1R) \subseteq clones(T2R) \subseteq clones(T3R)
 \end{equation}
@@
 \begin{equation}\label{eq:typerelation2}
-\text{Cloned nodes} = T1R \subseteq T1 \text{, but } T2R	\nsubseteq T2 \text{ and } T3R \nsubseteq T3
+clones(T1R) \subseteq clones(T1) \text{, but } clones(T2R) \nsubseteq clones(T2) \text{ and } clones(T3R) \nsubseteq clones(T3)
 \end{equation}
@@
 \label{ch:tool-overview}
-We conducted a short survey on (recent) clone detection tools that we could use to analyze refactoring possibilities.
-We chose a set of tools that are open source and can analyze a popular object-oriented programming language.
+We conduct a short survey on (recent) clone detection tools that we can use to analyze refactorable clones.
+We choose a set of tools from three modern clone detection tool surveys \cite{roy2009comparison, svajlenko2014evaluating, sheneamer2016survey}.
+We choose only tools that are open source, to be able to extend the tool to be able to detect refactoring-oriented clone detection types.
+Furthermore, the tool must be able to analyze a popular object-oriented programming language.
 Next, we formulate the following four criteria by which we analyze these tools:
 \begin{enumerate}
-    \item \textbf{Should find clones in any context}: Some tools only find clones in specific contexts, such as only method level clones.
+    \item \textbf{Finds clones in any context}: Some tools only find clones in specific contexts, such as only method level clones.
 We want to perform an analysis of all clones in projects to get a complete overview.
 \item \textbf{Finds clone classes in control projects\footnote{Control projects for assessing clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}}}: We assembled a number of control projects to assess the validity of clone detection tools.
-\item \textbf{Can analyze resolved symbols}: When detecting the types proposed in section~\ref{sec:rtypes}, it is important that we can analyze resolved symbols (for instance a type reference).
+\item \textbf{Analyzes resolved symbols}: When detecting the types proposed in section~\ref{sec:rtypes}, it is important that we can analyze resolved symbols (for instance a type reference).
 The rationale for this is further explained in~\ref{chap:challenge}.
@@
 \end{enumerate}
-The results of our survey are displayed in Table~\ref{table:dettools}.
+The results of our survey are displayed in Table~\ref{tab:dettools}.
 
-\begin{table}[]
+\begin{table}[H]
 \centering
@@
 \toprule
+\rowcolor[HTML]{FFFFFF}
 \textit{\textbf{Clone Detection Tool}} & \textit{\textbf{(1)}} & \textit{\textbf{(2)}} & \textit{\textbf{(3)}} & \textit{\textbf{(4)}} \\ \midrule
@@
 
-None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool, which is further described in the next chapter.
+None of the state-of-the-art tools we identified implement all our criteria. Because of that, we implement our own clone detection tool: CloneRefactor.

### 2019-08-22 sections/research.tex
More concise formulas

@@
 
-\begin{equation}\label{eq:typerelation}
-clones(T1R) \subseteq clones(T2R) \subseteq clones(T3R)
-\end{equation}
+\begin{align*}\label{eq:typerelation}
+%N_{1R} = \{n | n = a node found using the T1R set of rules\}
+%N_{2R} = \{n | n = a node found using the T2R set of rules\}
+%N_{3R} = \{n | n = a node found using the T3R set of rules\}
+\centerline{\text{$N_{T1R} \subseteq N_{T2R} \subseteq N_{T3R}}$} \\
+\text{where}~N_{T1R} &= \text{\{n | n = a node found using the T1R set of rules\}} \\
+  N_{T2R} &= \text{\{n | n = a node found using the T2R set of rules\}} \\
+	N_{T3R} &= \text{\{n | n = a node found using the T3R set of rules\}}
+\end{align*}
 
@@
 \begin{equation}\label{eq:typerelation2}
-clones(T1R) \subseteq clones(T1) \text{, but } clones(T2R) \nsubseteq clones(T2) \text{ and } clones(T3R) \nsubseteq clones(T3)
+N_{T1R} \subseteq N_{T1} \text{, but } N_{T2R} \nsubseteq N_{T2} \text{ and } N_{T3R} \nsubseteq N_{T3}
+\text{where}~N_{T1} &= \text{\{n | n = a node found using the T1 set of rules\}} \\
+  N_{T2} &= \text{\{n | n = a node found using the T2 set of rules\}} \\
+	N_{T3} &= \text{\{n | n = a node found using the T3 set of rules\}}
 \end{equation}

### 2019-08-22 sections/research.tex
Good enough

@@
 
-\begin{align*}\label{eq:typerelation}
+\begin{equation}\label{eq:typerelation}
 %N_{1R} = \{n | n = a node found using the T1R set of rules\}
@@
 %N_{3R} = \{n | n = a node found using the T3R set of rules\}
-\centerline{\text{$N_{T1R} \subseteq N_{T2R} \subseteq N_{T3R}}$} \\
-\text{where}~N_{T1R} &= \text{\{n | n = a node found using the T1R set of rules\}} \\
-  N_{T2R} &= \text{\{n | n = a node found using the T2R set of rules\}} \\
-	N_{T3R} &= \text{\{n | n = a node found using the T3R set of rules\}}
-\end{align*}
+N_{T1R} \subseteq N_{T2R} \subseteq N_{T3R}
+\end{equation}
 
+Where $N_{\text{clone type}}$ is the set of cloned nodes found by the rules of the specified clone type.
 Comparing these clone type definitions to the ones used in literature, type 1R clones are a subset of type 1 clones.
@@
 N_{T1R} \subseteq N_{T1} \text{, but } N_{T2R} \nsubseteq N_{T2} \text{ and } N_{T3R} \nsubseteq N_{T3}
-\text{where}~N_{T1} &= \text{\{n | n = a node found using the T1 set of rules\}} \\
-  N_{T2} &= \text{\{n | n = a node found using the T2 set of rules\}} \\
-	N_{T3} &= \text{\{n | n = a node found using the T3 set of rules\}}
 \end{equation}
+
+Where $N_{\text{clone type}}$ is the set of cloned nodes found by the rules of the specified clone type.
 

### 2019-08-22 sections/clonerefactor.tex
CloneRefactor

@@
 \chapter{CloneRefactor} \label{ch:clonerefactor}
-% We bridged a gap between clone detection and refactoring .. by designing a tool
 We bridged a gap between clone detection and refactoring by designing a tool that can detect clones by our refactoring-oriented clone types (chapter \ref{chap:clonetypes}).
@@
 The way in which CloneRefactor was designed does not allow for several clone types to be detected simultaneously.
-
 The overall process regarding clone detection is displayed in Figure~\ref{fig:clonedetection}.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{img/CloneDetection}
+  \caption{CloneRefactor clone detection process.}
+  \label{fig:clonedetection}
+\end{figure}
+
 First of all, we use JavaParser to read a project from disk and build an AST, one class file at a time.
@@
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/CloneDetection}
-  \caption{CloneRefactor clone detection process.}
-  \label{fig:clonedetection}
-\end{figure}
+\subsection{Clone Classes vs Clone Pairs}
+Regarding clone detection, there is variance in literature whether clone pairs or clone classes should be considered for detection.
+We decided to focus on clone classes, because of their advantages for refactoring.
+Clone pairs do not provide a general overview of all entities containing the clones, with all their related issues and characteristics~\cite{fontana2012duplicated}.
+Although clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered.
+Another issue that results from grouping clones by pairs: the amount of clone references increases according to the binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), which causes a heavy information redundancy~\cite{fontana2012duplicated}.
 

### 2019-08-22 sections/background.tex
I think this works better

@@
 \end{figure}
+
+\subsection{Clone Classes vs Clone Pairs}\label{sec:classesvspairs}
+In Table~\ref{tab:clone-terminology} we introduced the concept of clone classes.
+Clone classes consist of any number of clone instances.
+Some clone detection tools detect ``clone pairs'' instead, which consider each pair of clone instances separately.
+There are different reasons in literature whether clone pairs or clone classes should be considered for detection.
+
+We decided to focus on \textit{clone classes} for our study, because of their advantages for refactoring.
+Clone pairs do not provide a general overview of all entities containing the clones, with all their related issues and characteristics~\cite{fontana2012duplicated}.
+Although clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered.
+Another issue that results from grouping clones by pairs: the amount of clone references increases according to the binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), which causes a heavy information redundancy~\cite{fontana2012duplicated}.
 

### 2019-08-22 sections/clonerefactor.tex
I think this works better

--- 2019-08-19 sections/clonerefactor.tex
@@
 The way in which CloneRefactor was designed does not allow for several clone types to be detected simultaneously.
-
 The overall process regarding clone detection is displayed in Figure~\ref{fig:clonedetection}.
-First of all, we use JavaParser to read a project from disk and build an AST, one class file at a time.
-Each AST is then converted to a directed graph that maps relations between statements, further explained in Section~\ref{sec:clonegraph}.
-On the basis of this graph, we detect clone classes and verify them using three thresholds (in order of importance):
-\begin{itemize}
-  \item Amount of tokens.
-  \item Amount of statements.
-  \item Amount of lines.
-\end{itemize}
-If the detection was configured to detect either type 2R, 3 or 3R clones we perform some type specific transformations on the resulting set of clones.
 
@@
 \end{figure}
+
+First of all, we use JavaParser to read a project from disk and build an AST, one class file at a time.
+Each AST is then converted to a directed graph that maps relations between statements, further explained in Section~\ref{sec:clonegraph}.
+On the basis of this graph, we detect clone classes and verify them using three thresholds (in order of importance):
+\begin{itemize}
+  \item Amount of tokens.
+  \item Amount of statements.
+  \item Amount of lines.
+\end{itemize}
+If the detection was configured to detect either type 2R, 3 or 3R clones we perform some type specific transformations on the resulting set of clones.
 
@@
 \subsection{Detecting Clones} \label{sec:detectingclones}
-After building the clone clone graph, we use it to detect clones.
-We decided to focus on the detection of clone classes rather than clone pairs because clone pairs do not provide a general overview of all entities containing the clones, with all their related issues and characteristics \cite{fontana2012duplicated}.
-Although clone classes are harder to manage, they provide all information needed to plan a suitable refactoring strategy, since this way all instances of a clone are considered.
-Another issue that results from grouping clones by pairs: clone reference amount increases according to the binomial coefficient formula (two clones form a pair, three clones form three pairs, four clones form six pairs, and so on), which causes a heavy information redundancy \cite{fontana2012duplicated}.
-
-As stated in the previous section, nodes in the graph link to \textit{preceding} cloned statement.
-This implies that the first node that is cloned does not have any clone relation, as there are no clones preceding it (only following it).
+After building the clone clone graph, we use it to detect clone classes.
+Because nodes in the clone graph link to \textit{preceding} cloned statement, the first cloned node does not have any clone relation, as there are no clones preceding it (only following it).
 Because of this, we start our clone detection process at the final location encountered while building the graph.

### 2019-08-22 sections/results.tex
Fixed a display issue
Okay here come the results

--- 2019-08-20 sections/results.tex
@@
 These thresholds range from minimum clone size, variability, and gap size.
-In our corpus, CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Section~\ref{sec:metrics}).
+In our corpus, CloneRefactor has refactored 12,710 clone classes and measured the change in indicated metrics (see Section~\ref{sec:metrics}).
 Using the presented formulas (see Section~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Section~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
@@
 \subsection{Clone Token Volume}
-Figure \ref{fig:duplication} shows the obtained results when plotting the clone size (in tokens) vs the maintainability increase/decrease.
-On the secondary axis the amount of refactorings that have refactored a clone with the specified amount of tokens is displayed (e.g.
+Figure \ref{fig:tokenvolume} shows the obtained results when plotting the clone volume vs the maintainability increase/decrease.
+We define the clone volume as the combined number of tokens in all clone instances in a refactored clone class.
+On the secondary axis (blue line) we plot the amount of times a clone class with the specified amount of tokens is refactored (e.g.
 the amount of data points the data is based on).
@@
 \begin{figure}[H]
-  \includegraphics[width=1\textwidth]{img/duplication}
-  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability. Maintainability on the primary axis and amount of refactorings on the secondary axis.}
-  \label{fig:duplication}
+  \includegraphics[width=1\textwidth]{img/Tokenvolume}
+  \caption{A graph that shows how the token volume affects the maintainability score of the refactored clone}
+  \label{fig:tokenvolume}
 \end{figure}
+
+The tokens volume of the clone is equal to the decrease of duplicated tokens.
+Because of that, what we see in Figure~\ref{fig:tokenvolume} could largely be caused by this metric.
+Because of that, we also plot graphs in which each metric is considered singularly.
+In Figure~\ref{fig:}
 

### 2019-08-22 sections/related_work.tex

@@
 Mapping these to relations between clones, this results in Table \ref{tab:relationrefactoring}.
+% Sander: deze zin loop niet, bedoel je niet: "Mapping these to relations between clones results in Table \ref{tab:relationrefactoring}."
 
@@
 
-The author then proposes a tool named ``SUPREMO''.
-This tool determines the relations between clone instances, computes the impact of the clones and proposes refactorings.
+The author then proposes a tool named ``SUPREMO''. This tool determines the relations between clone instances, computes the impact % Sander: impact on what?
+of the clones and proposes refactorings.
 Their tool features visualizations to show how clones are related in the inheritance structure.
 This tool is written for the Smalltalk programming language.
+% Sander: Drie keep achter elkaar this/their tool, niet per se fout maar leest ook niet heel lekker, kijk maar of je tijd hebt ;)
 The authors verify their approach by presenting several cases in which their tool analyses source code and outputs a refactoring suggestion.
+% Sander: Ik mis beetje hoe dit zich verhoudt tot jouw werk, is ook wel bij andere research beetje ding, zou miss even kijken of je overal 1 of 2 zinnen bij kan zetten over hoe het zich verhoudt tot jouw werk, al is het opzich niet echt erg dus andere dingen gaan miss voor
 
@@
 A study by Higo et al.~\cite{higo2004aries, higo2008metric} looks into to what extent clones can be refactored.
-They show code examples and to what entent they can be cloned.
+They show code examples and to what extent they can be cloned.
 For instance, they look into what parts of a clone can be extracted to a new method.
 They define that partially cloned blocks obstruct method extraction.
-They propose t make the clone smaller to find a part of the clone that can be refactored.
+They propose to make the clone smaller to find a part of the clone that can be refactored.
 This is similar to our ``partial block'' category of Section~\ref{sec:refactorabilitysetup} and our discussion in Section~\ref{sec:partialblockdiscussion}.
@@
 In this figure, the clone spans a part of a different block so it cannot be refactored.
-However, they propose to ommit both ``else if'' lines from the merged fragment so that it can be refactored (in our study we would have flagged these clones as ``partial block'' and thus unsuitable for refactoring).
+However, they propose to omit both ``else if'' lines from the merged fragment so that it can be refactored (in our study we would have flagged these clones as ``partial block'' and thus unsuitable for refactoring).
 They also allow variability in literals and variables and replace them with method parameters.
@@
 This tool only proposes refactoring opportunities and does not provide help in the process of applying the refactoring.
+% Sander:..
+which our work does..
+is denk ik nice toevoeging
 
@@
 
-The second study, ``Unification and Refactoring of Clones'' by Krishnan et al.~\cite{krishnan2014unification}, the authors address the problem of the modifications made to copied fragments and their impact on the refactoring process.
+The second study, ``Unification and Refactoring of Clones'' by Krishnan et % Sander: In the second study? of iig iets waardoor zin klopt
+al.~\cite{krishnan2014unification}, the authors address the problem of the modifications made to copied fragments and their impact on the refactoring process.
 They identify a list of expressions in which they have found variability, which is displayed in Table~\ref{tab:krishnanvariability}.
@@
 If all branches return, the fragment can still be refactored even though there is a conditional return statement.
-
+% Sander:Als je tijd hebt, miss even overzicht in tabel van elke preconditie en hoe je die aanpakt zou het overzichtelijker maken
 After all these studies that determine what preconditions apply to be able to refactor modified clones, the authors propose a tool named JDeodorant that helps in the process of refactoring such clones~\cite{mazinanian2016jdeodorant}.
-This tool takes the output of many popular clone detection tools \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, NiCAD} and proposes refactoring opportunities.
+This tool takes the output of many popular clone detection tools \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, NiCAD} % Sander: Klopt het dat deze laatste citatie gewoon NiCAD is?
+ziet er beetje gek uit
+and proposes refactoring opportunities.
 The tool is integrated in the Eclipse IDE, making it easier to directly apply the refactoring.
@@
 A thesis by AlWaqfi~\cite{alwaqfi2017refactoring} propose a method for assessing refactorability of clone classes (whereas the previous tools only focus on clone pairs).
+% Sander: Deel tussen haakjes is juist mooie zin, zou hem uit haakjes halen en gewoon met komma ertussen achter de zin plaatsen
 The author surveys a set of clone detection tools \cite{kamiya2002ccfinder, baxter1999clonedr, jiang2007deckard, cordy2011nicad} and uses a publicly available dataset \cite{tsantalis2015assessing} to measure the amount of clones found by these tools.
@@
 To determine whether a clone is refactorable, the author uses the set of eight preconditions proposed by Tsantalis et al.~\ref{tsantalis2015assessing}.
+% Sander:Deze ref komt als ??
+in tekst
 
 \subsection{Pattern‐based clone Refactoring Inspection (PRI)}
-A study by Chen et al.~\ref{chen2018clone} addresses the problem that developers cannot easily determine which clones can be refactored or how they should be maintained scattered
+A study by Chen et al.~\ref{chen2018clone} % Sander: Deze ref komt als ?? in tekst
+addresses the problem that developers cannot easily determine which clones can be refactored or how they should be maintained scattered
 throughout a large code base in evolving systems.
@@
 In this section, we shortly introduce recent studies about refactoring code clones.
-
+% Sander: Waar ging de vorige sectie dan over?
 \subsection{Impact of Clone Refactoring on External Quality Attributes}
@@
 To collect this data, they used two systems that have been clone refactored.
-They conclude that there is a strong and positive correlation between clone refactoring and the reduction of the size of unit test cases.
-They also show that code quality attributes that are related to testability are significantly improved.
+% Sander: ik weet niet of 'clone refactored' een bestaand werkwoord is;) miss is; that had their clones refactored ofzo
+They conclude that there is a strong and positive % Sander: is strong, positive niet beter?
+correlation between clone refactoring and the reduction of the size of unit test cases. They also show that code quality attributes that are related to testability are significantly improved.

### 2019-08-22 sections/results.tex
Separate Metric Results

--- 2019-08-20 sections/results.tex
@@
 \subsection{Clone Token Volume}
-Figure \ref{fig:duplication} shows the obtained results when plotting the clone size (in tokens) vs the maintainability increase/decrease.
-On the secondary axis the amount of refactorings that have refactored a clone with the specified amount of tokens is displayed (e.g.
-the amount of data points the data is based on).
-As the amount of data points decreases, the datapoints gain less statistical significance.
+Figure \ref{fig:maintainabilityscore} shows the obtained results when plotting the clone volume vs the maintainability increase/decrease.
+We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class.
+The maintainability score, as shown in Figure \ref{fig:maintainabilityscore}, is the average delta maintainability score of all clone classes with the specified token volume that are refactored.
+As the amount of data points decreases, the datapoints gain less statistical significance, because of which we represent the x-axis as a logaritmic scale.
+The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.
 
 \begin{figure}[H]
-  \includegraphics[width=1\textwidth]{img/duplication}
-  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability. Maintainability on the primary axis and amount of refactorings on the secondary axis.}
-  \label{fig:duplication}
+  \includegraphics[width=1\textwidth]{img/maintainabilityscore}
+  \caption{The effect of token volume on the delta maintainability score of the refactored system}
+  \label{fig:maintainabilityscore}
+\end{figure}
+
+The token volume of the clone is equal to the decrease of duplicated tokens, which is part of the maintainability score.
+Because of that, what we see in Figure~\ref{fig:maintainabilityscore} could largely be caused by this metric.
+Do determine the effect of clone token volume on each metric, we also plot graphs in which each metric is considered singularly.
+In Figure~\ref{fig:volume} the average delta volume is shown when clones with the specified token volume are refactored.
+The trendline intersects the ``zero'' line (average delta volume does not increase nor decrease) at 60 tokens.
+A higher average delta volume implies a lower maintainability.
+
+\begin{figure}[H]
+  \includegraphics[width=1\textwidth]{img/volume}
+  \caption{The effect of token volume on the delta volume of the refactored system}
+  \label{fig:volume}
+\end{figure}
+
+In Figure~\ref{fig:numberofparameters} we show the average delta number of parameters when clones with the specified token volume are refactored.
+This metric can only increase by the refactoring, because CloneRefactor only applies ``Extract Method'' refactorings that create a method with a certain number of parameters (according to the data needed by the extracted method).
+
+\begin{figure}[H]
+  \includegraphics[width=1\textwidth]{img/numberofparameters}
+  \caption{The effect of token volume on the number of parameters of the refactored system}
+  \label{fig:numberofparameters}
+\end{figure}
+
+In Figure~\ref{fig:complexity} we show the average delta complexity when clones with the specified token volume are refactored.
+
+\begin{figure}[H]
+  \includegraphics[width=1\textwidth]{img/complexity}
+  \caption{The effect of token volume on the complexity of the refactored system}
+  \label{fig:complexity}
 \end{figure}

### 2019-08-22 sections/results.tex
Finished up results

@@
   \includegraphics[width=1\textwidth]{img/maintainabilityscore}
-  \caption{The effect of token volume on the delta maintainability score of the refactored system}
+  \caption{The effect of token volume on the delta maintainability score of the refactored clones}
   \label{fig:maintainabilityscore}
@@
   \includegraphics[width=1\textwidth]{img/volume}
-  \caption{The effect of token volume on the delta volume of the refactored system}
+  \caption{The effect of token volume on the delta volume of the refactored clones}
   \label{fig:volume}
@@
   \includegraphics[width=1\textwidth]{img/numberofparameters}
-  \caption{The effect of token volume on the number of parameters of the refactored system}
+  \caption{The effect of token volume on the number of parameters of the refactored clones}
   \label{fig:numberofparameters}
@@
 In Figure~\ref{fig:complexity} we show the average delta complexity when clones with the specified token volume are refactored.
+We did not add a trendline, as there does not seem to be a clear trend.
+The maximum delta complexity is 1, because the extracted method itself has a complexity of 1.
+For each branching point in the cloned fragment, the complexity of the system will decrease when such a clone is refactored.
 
@@
   \includegraphics[width=1\textwidth]{img/complexity}
-  \caption{The effect of token volume on the complexity of the refactored system}
+  \caption{The effect of token volume on the complexity of the refactored clones}
   \label{fig:complexity}
@@
 The volume of the clone is the dominating factor regarding the maintainability increase/decrease of cloned code.
-Because of that, for our further experiments, we filter out all refactorings with a token size smaller than 18 because otherwise the small clones dominate the results and turn all results towards unmaintainable.
+Because of that, in our further experiments we filter out all refactorings with a token size smaller than 18 because otherwise the small clones dominate the results and turn all results towards unmaintainable.
 

### 2019-08-22 sections/results.tex
New relations table

@@
 
-The volume of the clone is the dominating factor regarding the maintainability increase/decrease of cloned code.
+%The volume of the clone is the dominating factor regarding the maintainability increase/decrease of cloned code.
 Because of that, in our further experiments we filter out all refactorings with a token size smaller than 18 because otherwise the small clones dominate the results and turn all results towards unmaintainable.
@@
 \textit{\textbf{Relation}} & \textit{\textbf{Maintainability Score}} & \textit{\textbf{Number of Refactorings}} \\ \midrule
-\textbf{Common Hierarchy} & \textbf{0.51} & \textbf{792} \\ \midrule
-\hspace{10pt} Sibling & 0.57 & 637 \\
+\textbf{Common Hierarchy} & \textbf{0.23} & \textbf{2,202} \\ \midrule
+\hspace{10pt} Superclass & 0.42 & 229 \\
+\hspace{10pt} Sibling & 0.23 & 1,722 \\
 \rowcolor[HTML]{FFCCC9}
-\hspace{10pt} Same Hierarchy & 0.55 & 22 \\
+\hspace{10pt} Same Hierarchy & 0.10 & 87 \\
+\hspace{10pt} First Cousin & 0.02 & 144 \\
 \rowcolor[HTML]{FFCCC9}
-\hspace{10pt} Superclass & 0.20 & 74 \\
-\rowcolor[HTML]{FFCCC9}
-\hspace{10pt} First Cousin & -0.02 & 53 \\
-\rowcolor[HTML]{FFCCC9}
-\hspace{10pt} Ancestor & -0.65 & 6 \\ \midrule
-\textbf{Common Class} & \textbf{0.01} & \textbf{2,025}\\ \midrule
-\hspace{10pt} Same Method & 0.01 & 762  \\
-\hspace{10pt} Same Class & 0.01 & 1,263 \\ \midrule
-\textbf{Unrelated} & \textbf{-0.02} & \textbf{688}\\ \midrule
-\hspace{10pt} No Direct Superclass & 0.08 & 289 \\
-\hspace{10pt} External Superclass & -0.02 & 225  \\
-\rowcolor[HTML]{FFCCC9}
-\hspace{10pt} No Indirect Superclass & -0.04 & 30  \\
-\hspace{10pt} External Ancestor & -0.26 & 144  \\ \midrule
-\textbf{Common Interface} & \textbf{-0.11} & \textbf{283} \\ \midrule
-\hspace{10pt} Same Direct Interface & 0.02 & 160 \\
-\hspace{10pt} Same Indirect Interface & -0.31 & 123
+\hspace{10pt} Ancestor & -0.03 & 20 \\ \midrule
+\textbf{Common Interface} & \textbf{-0.02} & \textbf{1,044} \\ \midrule
+\hspace{10pt} Same Indirect Interface & -0.01 & 487 \\
+\hspace{10pt} Same Direct Interface & -0.02 & 557 \\ \midrule
+\textbf{Common Class} & \textbf{-0.02} & \textbf{7,239}\\ \midrule
+\hspace{10pt} Same Class & 0.04  & 4,874 \\
+\hspace{10pt} Same Method & -0.15 & 2,365  \\ \midrule
+\textbf{Unrelated} & \textbf{-0.15} & \textbf{2,198}\\ \midrule
+\hspace{10pt} No Direct Superclass & -0.06 & 811 \\
+\hspace{10pt} External Superclass & -0.17 & 697  \\
+\hspace{10pt} External Ancestor & -0.21 & 586  \\
+\hspace{10pt} No Indirect Superclass & -0.30 & 104  \\ \midrule
 \end{tabular}

### 2019-08-22 sections/results.tex
New return value table

@@
 \subsection{Return Value}
-Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.
+Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system (categories are explained in Section~\ref{sec:refreturn}).
 
@@
 \textit{\textbf{Return Value}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
-Return & 0.20 & 421 \\
-Void & 0.19 & 2052 \\
-Declare & 0.03 & 1318 \\
+Return & 0.19 & 1,571 \\
+Declare & 0.15 & 5,177 \\
 \rowcolor[HTML]{FFCCC9}
-Assign & -1.29 & 3 \\ \bottomrule
+Assign & 0.12 & 14 \\
+Void & -0.18 & 5,921 \\
+\bottomrule
 \end{tabular}
-\caption{Maintainability scores for different return values}
+\caption{Maintainability scores for different methods of handling returned data from the call to the extracted method.}
 \label{tab:return}

### 2019-08-23 sections/clonerefactor.tex
Okay here come the results
Xander

@@
   \centering
-  \includegraphics[width=0.8\columnwidth]{img/CloneRefactorOverall}
+  \includegraphics[width=0.8\columnwidth]{img/flow}
   \caption{CloneRefactor overall process.}
@@
 
-Because of the requirement of symbol resolution, the refactoring-oriented clone types are less suitable for large scale clone analysis.
+%Because of the requirement of symbol resolution, the refactoring-oriented clone types are less suitable for large scale clone analysis.
 
@@
 \begin{itemize}
-  \item \textbf{Minimum Amount of Nodes}: The minimum amount of nodes that should be in each instance of cloned fragements for them to be considered a clone class.
-  \item \textbf{Minimum Amount of Tokens}: The minimum amount of tokens that should be in each instance of cloned fragements for them to be considered a clone class.
-  \item \textbf{Minimum Amount of Lines}: The minimum amount of lines that should be in each instance of cloned fragements for them to be considered a clone class.
+  \item \textbf{Minimum Number of Nodes}: The minimum amount of nodes that should be in each instance of cloned fragements for them to be considered a clone class.
+  \item \textbf{Minimum Number of Tokens}: The minimum amount of tokens that should be in each instance of cloned fragements for them to be considered a clone class.
+  \item \textbf{Minimum Number of Lines}: The minimum amount of lines that should be in each instance of cloned fragements for them to be considered a clone class.
 \end{itemize}
@@
 To detect clones, CloneRefactor parses the AST aqcuired from JavaParser to an unweighted graph structure.
-On the basis of this graph structure, clones are detection.
+On the basis of this graph structure, clones are detected.
 Dependent on the type of clones being detected, transformations may be applied.
@@
 Each AST is then converted to a directed graph that maps relations between statements, further explained in Section~\ref{sec:clonegraph}.
-On the basis of this graph, we detect clone classes and verify them using three thresholds (in order of importance):
-\begin{itemize}
-  \item Amount of tokens.
-  \item Amount of statements.
-  \item Amount of lines.
-\end{itemize}
+On the basis of this graph, we detect clone classes and verify them the configured thresholds.
 If the detection was configured to detect either type 2R, 3 or 3R clones we perform some type specific transformations on the resulting set of clones.
+%\begin{itemize}
+%  \item Amount of tokens.
+%  \item Amount of statements.
+%  \item Amount of lines.
+%\end{itemize}
 
@@
 
-Additionally, we exclude package declarations and import statements. These are omitted by most clone detection tools, as clones in import statements hold limited valuable information.
+Additionally, we exclude package declarations and import statements. These are omitted by most clone detection tools, as import statements are most often generated by the IDE.
 
@@
 
-We refer to the declarations and statements in this graph as \textit{nodes}.
 The relations \textit{next} and \textit{previous} in this graph are represented as an twodirectional arrow.
@@
 In short, this process detects clones allowing for any variability between expressions.
-This postprocessing step then determines which (parts of) these clones are valid by the configure variability threshold.
+This postprocessing step then determines which (parts of) these clones are valid by the configured variability threshold.
 
@@
 %Two nodes are considered clones of each other if the size of their equality array is equal and all negative numbers in the equality array are equal.
-
 When a found clone class does not adhere to the global thresholds as explained in the previous section, we need to determine whether it contains any valid subclones.
@@
 
-\subsubsection{Example}
+\subsubsection{Type 3R Example}
 In this section we show an example of the identification of a type 3R clone.

### 2019-08-23 sections/experimentalsetup.tex
:)
Sander

@@
 \section{The Corpus}\label{chap:corpus}
-For our experiments we use a large corpus of open source projects \cite{githubCorpus2013}.
+For our experiments we use a large corpus of open source projects \cite{githubCorpus2013}. %Sander: Miss wil je hier zeggen dat het gemaakt is door Allamanis et al ofziets
 This corpus contains a set of Java projects from GitHub, selected by number of forks.
-The projects in this corpus were then de-duplicated manually.
+The projects in this corpus were de-duplicated manually.
+% Sander: Wat werd er ge-de-dupliceerd?
+de files?
+de projects?
+% Sander: Kan ik de corpus ergens vinden?
 This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
+% Sander:huh wat je zegt nu eerst dat hij useful is, en daarmee meteen dat we hem hebben veranderd. waarom hebben we die controlled set nodig?
 
-For our purposes, we have further filtered this corpus to get a controlled set of projects for our experiments.
-In this section, we explain the steps we took to prepare the corpus\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} and the rationale behind those steps.
+For our purposes, we have further filtered this corpus to get a controlled set of projects for our experiments. In this section,
+we explain the steps we took to prepare the corpus\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} and the rationale behind those steps.
 
-\section{Tool Validation}
+\subsection{Tool Validation}
+% Sander: deze eerst zin is heel plotseling, en relateerd niet meteen heel duidelijk aan de rest eromheen
+% Sander: Eigenlijk past deze hele subsectie niet echt in het corpus gedeelte
 We have validated the correctness of CloneRefactor through unit tests and empirical validation.
 First, we created a set of 57 control projects to verify the correctness in many (edge) cases.
-These projects contain clones for each identified relation, location, contents and refactorability category (see Section \ref{chap:contextsetup} and \ref{sec:refactorabilitysetup}), to see whether they get correctly identified.
+These projects contain clones for each identified relation, location, contents and refactorability category (see Section \ref{chap:contextsetup} and \ref{sec:refactorabilitysetup}), % Sander: weet je zeker dat contain goede woord is in die zin?
+to see whether they get correctly identified.
 Next, we run the tool over the corpus and manually verify samples of the acquired results.
@@
 
-Because we cloned the projects (and do not use the sources provided in the corpus), they still included generated source code.
+Because we cloned the projects (and do not use the sources provided in the corpus) % Sander:Het is hier niet duidelijk wat je nog met corpus bedoelt. Jouw corpus? die van allamanis?
+, they still included generated source code.
 Because we do not want to analyze generated Java files, we decided to further filter the corpus to only include projects with a conventional structure.
@@
 We omitted Maven projects that do not adhere to this convention.
+% Sander: weten we nu zeker dat er geen generated files meer in staan?
 
@@
 Maven uses the following command to automate this process: \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib}.
-This process can fail if external dependencies are no longer available.
-We removed such projects for which we could not obtain all dependencies.
+This process can % Sander: can fail of will fail?
+fail if external dependencies are no longer available. We removed such projects for which we could not obtain all dependencies.
 
@@
 A very small set of projects had syntactical errors, which we removed from the corpus.
+% Sander:examples of syntactical error?
+why did we remove those -> they crash the javaparser
 
 \subsection{Inspecting outliers}
-We ran CloneRefactor over every project in the corpus and inspected the output for each project.
-Some projects gave unusual high numbers of projects of a certain size, which we manually inspected.
-Often these projects contained generated source files.
-We removed these projects from the corpus.
+We ran CloneRefactor over every project in the corpus and inspected the output for each project. Some projects gave unusual high numbers of projects % Sander: clones?
+of a certain size, which we manually inspected. Often these projects contained generated source files. We removed these projects from the corpus.
 
@@
 The largest project in the corpus is \textit{VisAD} with 502,052 lines over 1,527.
+% Sander:files?
 
 \section{Minimum clone size}
-In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored.
-However, when clones are very small, they may never be able to improve maintainability.
-The detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication.
+In this study, we want to find out what thresholds will improve maintainability if clones by those thresholds are refactored.
+For example, when clones are very small, refactoring them might not improve maintainability since the detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication.
 Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones cannot improve maintainability when refactored.
+% Sander: Hoe ben je hier achter gekomen?
 
@@
   \item All metrics are equal in terms of weight towards system maintenance effort.
-  \item Higher values for the metrics imply lower maintainability.
-  \item Normalizing each obtained metric delta over all deltas obtained a metric in our dataset results in equally weighted scores.
+  \item Higher values for the metrics imply lower maintainability. % Sander: Dit is niet echt assumptie toch
+  \item Normalizing each obtained metric delta over all deltas obtained a metric in our dataset results in equally weighted scores. % Sander: zin klopt niet (en snap hem ook niet)
 \end{itemize}
@@
 Because of that, in our experiments we focus mainly on significant differences in maintainability to draw a conclusion.
+% Sander: miss wil je deze laatste twee zin weghalen om jezelf niet in je voet te schieten, als je het maar kan beantwoorden tijdens je defense
 
@@
 \end{equation}
-Where $\Delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metrics.
+Where $\Delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metric.
 This method works well for normalization of our data, because as we divide by the standard deviation, outliers do not influence the resulting scores much.
@@
 \end{equation}
+% Sander: miss mooier met Maintainability = ....

### 2019-08-23 sections/results.tex
Added context
Sander

@@
 \section{Clone types}\label{sec:clonetypeexperiments}
-In this section, we look into the differences between the different clone types that were introduced in Chapter \ref{chap:clonetypes}.
+In this section, we look into the differences between the clone types that were introduced in Chapter \ref{chap:clonetypes}.
 
 \subsection{Found nodes}
-In this section, we display our results regarding the differences in found nodes between clone type 1-3~\cite{roy2007survey} and type 1R-3R.
+In this section, we display our results regarding the differences in found nodes between clone type % Sander:waar komt nodes ineens vandaan? ik ga uit van AST nodes maar is niet duidelijk denk ik
+1-3~\cite{roy2007survey} and type 1R-3R.
 Figure~\ref{fig:typeres} shows the number of cloned nodes found over the entire corpus for the different clone types (the word ``Type'' is abbreviated as ``T'').
-For type 2R clones, we set the variability threshold (see Section~\ref{sec:variabilitythreshold}) to 10\%, meaning that no more than 10\% of expressions may differ between cloned fragments.
+For type 2R clones, we set the variability threshold (see Section~\ref{sec:variabilitythreshold}) to 10\%, meaning that no more than 10\% of expressions may differ between fragments to be considered clones.
 For type 3 and 3R clones, we allow a gap of 20\% the clones surrounding it.
@@
 \end{figure}
+% Sander: korte uitleg over wat we zien in de figures hier? (geld voor alle experimenten)
 
@@
 We ran these performance tests on the compute nodes of the DAS4 supercomputer \cite{bal2016medium}, which do not have many background processes severely affecting the results.
+% Sander: zou zin na de komma (which..results) weglaten.
 The durations are of course dependent on our implementation of the clone types.
+% Sander: deze zin voegt ook niet zoveel toe
 
@@
 Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Section~\ref{sec:setuprelation}).
+% Sander: is dat plaatje met overzicht van relaties van clone classen weg of ergens anders? hij is hier ook wel handig
 
@@
 \end{tabular}
-\caption{Amount of clone instances with a certain location}
+\caption{Amount of clone instances with a certain location} % Sander: miss: Amount of clone instances per location category ofzoiets
 \label{tab:location}
@@
 The third column shows our measurements when restricting our search to method bodies.
+% Sander: waarom willen we dat weten?
 The amount that can be extracted increases because, when restricting our search to method bodies, we do not exclude declarations that can obstruct the possibility of method extraction (for instance a cloned method signature).
-
+% Sander: die laatste zin snap ik niet
 \begin{table}[H]
@@
 In our corpus, CloneRefactor has refactored 12,710 clone classes and measured the change in indicated metrics (see Section~\ref{sec:metrics}).
-Using the presented formulas (see Section~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Section~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
+Using the presented formulas (see Section~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Section~\ref{sec:characteristics}) % Sander: Ref geeft ???
+influence the maintainability of the resulting codebase after refactoring.
 In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.
@@
 The maintainability score, as shown in Figure \ref{fig:maintainabilityscore}, is the average delta maintainability score of all clone classes with the specified token volume that are refactored.
-As the amount of data points decreases, the datapoints gain less statistical significance, because of which we represent the x-axis as a logaritmic scale.
+As the amount of data points decreases, the datapoints gain less statistical significance, because of which we represent the x-axis as a logaritmic scale.% Sander: weet niet zeker of dit logaritmische schaal heet
 The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.

### 2019-08-23 sections/clonerefactor.tex
CloneRef

@@
 This paper defines a set of metrics to measure the maintainability of a system.
-For each of these metrics, risk profiles are proposed to determine the maintainability impact on the system of a whole.
+For each of these metrics, risk profiles are proposed to determine the maintainability impact on the system as a whole.
 
@@
 
-\subsection{Saving refactored code}
-CloneRefactor features several ``Refactoring Strategies'', that indicate how and where refactored code will be saved. These are as follows:
-\begin{itemize}
-  \item \textbf{Do not refactor}: CloneRefactor does not apply refactorings at all, it only reports found clones.
-  \item \textbf{Simulate}: CloneRefactor only applies the refactorings to its internal AST structure and calculates the results of applying these refactorings.
+%\subsection{Saving refactored code}
+%CloneRefactor features several ``Refactoring Strategies'', that indicate how and where refactored code will be saved. These are as follows:
+%\begin{itemize}
+%  \item \textbf{Do not refactor}: CloneRefactor does not apply refactorings at all, it only reports found clones.
+%  \item \textbf{Simulate}: CloneRefactor only applies the refactorings to its internal AST structure and calculates the results of applying these refactorings.
 It does not modify/copy the codebase on disk.
-  \item \textbf{Replace}: CloneRefactor replaces the source code with the refactored source code.
-  \item \textbf{Copy Only Changes}: CloneRefactor writes only the changed files to a new location.
-  \item \textbf{Copy All}: CloneRefactor copies the entire project to a new location and applies the refactorings there.
+%  \item \textbf{Replace}: CloneRefactor replaces the source code with the refactored source code.
+%  \item \textbf{Copy Only Changes}: CloneRefactor writes only the changed files to a new location.
+%  \item \textbf{Copy All}: CloneRefactor copies the entire project to a new location and applies the refactorings there.
 This makes sure the original project stays unmodified, while also having a snapshot of the refactored project.
-  \item \textbf{Git Replace}: CloneRefactor creates a branch on the git VCS, or initializes a git repository if it is not available.
+%  \item \textbf{Git Replace}: CloneRefactor creates a branch on the git VCS, or initializes a git repository if it is not available.
 For every clone class refactored, CloneRefactor creates a commit in the git repository.
-  \item \textbf{Git Copy}: CloneRefactor copies the entire project to a new location.
+%  \item \textbf{Git Copy}: CloneRefactor copies the entire project to a new location.
 CloneRefactor then performs the same procedure as for ``Git Replace'', except now at the new location so the original project remains unmodified.
-\end{itemize}
-These ``Refactoring Strategies'' can be used to get more data regarding the transformations applied by CloneRefactor. In our experiments, we only make use of the ``Simulate'' ``Refactoring Strategy''.
+%\end{itemize}
+%These ``Refactoring Strategies'' can be used to get more data regarding the transformations applied by CloneRefactor.
+In our experiments, we only make use of the ``Simulate'' ``Refactoring Strategy''.

### 2019-08-23 sections/results.tex
Better outlining of tables
Commit before I make big changes
Moved some appendix stuff into the results

@@
 \centering
-\begin{tabular}{@{}llllll@{}}
+\begin{tabular}{@{}llrrrr@{}}
 \toprule
@@
 \centering
-\begin{tabular}{@{}lll@{}}
+\begin{tabular}{@{}lrr@{}}
 \toprule
@@
 \centering
-\begin{tabular}{@{}lllll@{}}
+\begin{tabular}{@{}lrrrr@{}}
 \toprule
@@
 
-\section{Refactoring}
+\section{Refactoring} \label{sec:refactoringexperiments}
 %I think the ultimate goal with this thesis is to do experiments with different clone thresholds.
@@
 In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.
+We use the following keywords as headers of the columns of our tables:
+\begin{itemize}
+  \item \textbf{Complexity}: The average delta complexity for all refactored clone classes in the specified category.
+  \item \textbf{Parameters}: The average delta number of parameters for all refactored clone classes in the specified category.
+  \item \textbf{Volume}: The average delta number of tokens for all refactored clone classes in the specified category.
+  \item \textbf{Duplication}: The average delta number of duplicate tokens for all refactored clone classes in the specified category.
+  \item \textbf{\#}: The number of times the specified category is refactored (and thus the number of datapoints we have for this category).
+  \item \textbf{Score}: The average delta maintainability score (see Section~\ref{sec:metricformula} for the formula by which this score is calculated) for all refactored clone classes in the specified category.
+\end{itemize}
+In this context, the \textit{delta} denotes the change in this metric between the before- and after-refactoring snapshot of the system, for each separate clone class that was refactored.
 
@@
 \subsection{Relation}
-Table~\ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability.
+Table~\ref{tab:full-relation} shows our data regarding how different relations influence maintainability.
 We mark rows based on less than 100 refactorings red, as their result does not have statistical significance.
+The \textbf{Relation} column refers to the relations introduced in Section~\ref{sec:setuprelation}.
+Relations are mutually exclusive so all percentages add up to 100\%.
 
@@
 \centering
-\begin{tabular}{@{}lll@{}}
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lrrrrrr@{}}
 \toprule
-\textit{\textbf{Relation}} & \textit{\textbf{Maintainability Score}} & \textit{\textbf{Number of Refactorings}} \\ \midrule
-\textbf{Common Hierarchy} & \textbf{0.23} & \textbf{2,202} \\ \midrule
-\hspace{10pt} Superclass & 0.42 & 229 \\
-\hspace{10pt} Sibling & 0.23 & 1,722 \\
-\rowcolor[HTML]{FFCCC9}
-\hspace{10pt} Same Hierarchy & 0.10 & 87 \\
-\hspace{10pt} First Cousin & 0.02 & 144 \\
-\rowcolor[HTML]{FFCCC9}
-\hspace{10pt} Ancestor & -0.03 & 20 \\ \midrule
-\textbf{Common Interface} & \textbf{-0.02} & \textbf{1,044} \\ \midrule
-\hspace{10pt} Same Indirect Interface & -0.01 & 487 \\
-\hspace{10pt} Same Direct Interface & -0.02 & 557 \\ \midrule
-\textbf{Common Class} & \textbf{-0.02} & \textbf{7,239}\\ \midrule
-\hspace{10pt} Same Class & 0.04  & 4,874 \\
-\hspace{10pt} Same Method & -0.15 & 2,365  \\ \midrule
-\textbf{Unrelated} & \textbf{-0.15} & \textbf{2,198}\\ \midrule
-\hspace{10pt} No Direct Superclass & -0.06 & 811 \\
-\hspace{10pt} External Superclass & -0.17 & 697  \\
-\hspace{10pt} External Ancestor & -0.21 & 586  \\
-\hspace{10pt} No Indirect Superclass & -0.30 & 104  \\ \midrule
-\end{tabular}
-\caption{Influence on maintainability of refactoring clones by certain relations.}
-\label{tab:relation_refactor}
+\textit{\textbf{Relation}} & \textit{\textbf{Duplication}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Volume}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
+\textbf{Common Hierarchy} & \textbf{-66.33} & \textbf{0.73} & \textbf{1.20} & \textbf{-8.85} & \textbf{2,202} & \textbf{0.23} \\ \midrule
+\hspace{10pt} Superclass & -64.48 & 0.79 & 0.94 & -7.22 & 229 & 0.42 \\
+\hspace{10pt} Sibling & -70.07 & 0.69 & 1.28 & -10.97 & 1,722 & 0.23 \\
+\hspace{10pt} Same Hierarchy & -44.18 & 0.95 & 0.89 & 1.54 & 87 & 0.10 \\
+\hspace{10pt} First Cousin & -42.69 & 0.89 & 0.93 & 4.86 & 144 & 0.02 \\
+\hspace{10pt} Ancestor & -32.75 & 1.00 & 0.75 & 11.00 & 20 & -0.03 \\ \midrule
+\textbf{Common Interface} & \textbf{-47.06} & \textbf{0.83} & \textbf{1.04} & \textbf{4.50} & \textbf{1,044} & \textbf{-0.02} \\ \midrule
+\hspace{10pt} Same Indirect Interface & -37.08 & 0.93 & 0.82 & 9.96 & 487 & -0.01 \\
+\hspace{10pt} Same Direct Interface & -55.79 & 0.75 & 1.24 & -0.28 & 557 & -0.02 \\ \midrule
+\textbf{Common Class} & \textbf{-52.42} & \textbf{0.87} & \textbf{1.13} & \textbf{1.47} & \textbf{7,239} & \textbf{-0.02} \\ \midrule
+\hspace{10pt} Same Class & -51.85 & 0.86 & 1.03 & 3.36 & 4,874 & 0.04 \\
+\hspace{10pt} Same Method & -53.60 & 0.90 & 1.32 & -2.44 & 2,365 & -0.15 \\ \midrule
+\textbf{Unrelated} & \textbf{-45.86} & \textbf{0.88} & \textbf{1.08} & \textbf{9.56} & \textbf{2,198} & \textbf{-0.15} \\ \midrule
+\hspace{10pt} No Direct Superclass & -52.24 & 0.84 & 1.12 & 6.04 & 811 & -0.06 \\
+\hspace{10pt} External Superclass & -47.09 & 0.87 & 1.13 & 8.77 & 697 & -0.17 \\
+\hspace{10pt} External Ancestor & -35.73 & 0.93 & 0.95 & 14.58 & 586 & -0.21 \\
+\hspace{10pt} No Indirect Superclass & -44.89 & 0.84 & 1.18 & 14.08 & 104 & -0.30 \\ \midrule
+\textbf{Grand Total} & \textbf{-53.26} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
+\end{tabular}%
+}
+\caption{Average metric values for refactorings of clone classes with the specified relations}
+\label{tab:full-relation}
 \end{table}
 
-\subsection{Return Value}
-Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system (categories are explained in Section~\ref{sec:refreturn}).
+\subsection{Return Category}
+Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.
+The \textbf{Return Category} column refers to the categories introduced in Section~\ref{sec:refreturn}.
 
@@
 \centering
-\begin{tabular}{@{}lll@{}}
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lrrrrrr@{}}
 \toprule
-\textit{\textbf{Return Value}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
-Return & 0.19 & 1,571 \\
-Declare & 0.15 & 5,177 \\
-\rowcolor[HTML]{FFCCC9}
-Assign & 0.12 & 14 \\
-Void & -0.18 & 5,921 \\
-\bottomrule
-\end{tabular}
-\caption{Maintainability scores for different methods of handling returned data from the call to the extracted method.}
-\label{tab:return}
+\textit{\textbf{Return Category}} & \textit{\textbf{Complexity}} & \textit{\textbf{Interface Size}} & \textit{\textbf{Size}} & \textit{\textbf{Duplication}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
+Return & 0.85 & 1.02 & -3.84 & -55.00 & 1,571 & 0.19 \\
+Declare & 0.94 & 0.74 & 11.11 & -49.19 & 5,177 & 0.15 \\
+Assign & 0.79 & 1.07 & 0.43 & -56.29 & 14 & 0.12 \\
+Void & 0.76 & 1.49 & -5.85 & -56.35 & 5,921 & -0.18 \\ \midrule
+\textbf{Grand Total} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{-53.26} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
+\end{tabular}%
+}
+\caption{Average metric values for refactorings of clone classes with the specified return category}
+\label{tab:full-return}
 \end{table}

### 2019-08-23 sections/results.tex
Link appendix

@@
 \toprule
-Category & Clone instances & \% \\ \midrule
+\textit{\textbf{Category}} & \textit{\textbf{Clone instances}} & \textit{\textbf{\%}} \\ \midrule
 Method Level & 232,545 & 78.43\% \\
@@
 The y-axis shows the number of parameters.
+The table containing all underlying data and separate metrics is displayed in Appendix~\ref{sec:parameterstable}.
 

### 2019-08-23 sections/discussion.tex
Working on discussion and results

--- 2019-08-19 sections/discussion.tex
@@
 In this section, we discuss the differences between clone types 1-3 and 1R-3R.
-In Figure \ref{fig:typeres} we see that the difference between T1R and T1 is relatively small (11\% more cloned nodes found for T1).
-Often textually equal code is also functionally equal.
-The difference between T2R and T2 is bigger (34.7\% more cloned nodes for T2).
-The main reason for this is that T2R does not allow any variability in types, wheareas T2 allows any variability in types.
-T3R and T3 only a little bit higher than T2R and T2.
+We see that the difference between T1R and T1 in terms of found clones is small (11\%).
+This implies that most often textually equal code is also functionally equal.
+The difference between T2R and T2 is bigger (35\%).
+Upon manual inspection we found that the main reason for this is that T2R does not allow any variability in types, wheareas T2 allows any variability in types.
 
@@
 The main reason for this is type resolution: finding the fully qualified identifiers of type-, variable- and method-references.
+
+In Figure~\ref{fig:t2rgraph} we show the increase of cloned nodes for a higher variability between clone instances.
+This graph is logaritmic: as the variability increases, the increase in nodes decreases.
+This implies that semantical equality increases the chances that tokens are equal.
+
+In Figure~\ref{fig:t3rgraph} we show the increase of cloned nodes for higher type 3R gap sizes.
+The line denoting the number of clone classes seems a bit exponential whereas the line denoting cloned nodes is mostly linear.
+This makes sense regarding the nature of the threshold.
+As we get into higher gap size percentages, fewer clones merge (thus the decrease in amount of clone classes merging).
+However, at these higher gap size percentages the gaps contains more nodes (thus the amount of cloned nodes being linear).
 

### 2019-08-23 sections/results.tex
Working on discussion and results

@@
 \subsection{Found nodes}
-In this section, we display our results regarding the differences in found nodes between clone type % Sander:waar komt nodes ineens vandaan? ik ga uit van AST nodes maar is niet duidelijk denk ik
-1-3~\cite{roy2007survey} and type 1R-3R.
+In this section, we display our results regarding the differences in the number of cloned nodes (see Section~\ref{sec:terminology} for our terminology) between clone type 1-3~\cite{roy2007survey} and type 1R-3R.
 Figure~\ref{fig:typeres} shows the number of cloned nodes found over the entire corpus for the different clone types (the word ``Type'' is abbreviated as ``T'').
 For type 2R clones, we set the variability threshold (see Section~\ref{sec:variabilitythreshold}) to 10\%, meaning that no more than 10\% of expressions may differ between fragments to be considered clones.
-For type 3 and 3R clones, we allow a gap of 20\% the clones surrounding it.
+For type 3 and 3R clones, we allow a gap size of 20\% the clones surrounding it (see Section~\ref{sec:t3rthreshold}).
 
@@
 \end{figure}
-% Sander: korte uitleg over wat we zien in de figures hier? (geld voor alle experimenten)
+
+In Figure \ref{fig:typeres} we see that the difference between T1R and T1 is relatively small (11\% more cloned nodes found for T1).
+The difference between T2R and T2 is bigger (35\% more cloned nodes for T2).
+The number of cloned nodes of T3R and T3 are only a little bit higher than T2R and T2.
 
@@
 This figure shows the average duration of running CloneRefactor 10 times for a certain clone type.
-We ran these performance tests on the compute nodes of the DAS4 supercomputer \cite{bal2016medium}, which do not have many background processes severely affecting the results.
+We ran these performance tests on the compute nodes of the DAS4 supercomputer \cite{bal2016medium}, which allow for higher accuracy performance measurements as they do have limited background processes affecting the results.
 % Sander: zou zin na de komma (which..results) weglaten.
-The durations are of course dependent on our implementation of the clone types.
-% Sander: deze zin voegt ook niet zoveel toe
+%The durations are of course dependent on our implementation of the clone types.
 
@@
 
+In this graph, we see that the amount of clones increases as the amount of variability allowed increases. The graph is logaritmic: as the variability increases, the increase in nodes decreases.
+
 \subsection{Type 3R Gap Size Thresholds}
@@
 \end{figure}
+
+In this graph, we see a decrease in clone classes and an increase in cloned nodes when we increase the type 3R gap size threshold.
+We measure this threshold for a gap size of 0-200\%.
+In the graph, we see that both lines are rather linearly with minor jumps at certain thresholds.
+The jumps are at 33\%, 50\%, 100\%, 150\% and 200\%.
+The jump at 50\% is the largest.
+This makes sense regarding the nature of the threshold.
+At 50\%, all clone instances of 2 nodes with a gap of one node will merge into type 3R clones.
 
@@
 \end{tabular}
-\caption{Number of clone classes per clone relation}
+\caption{Number of clone classes per clone relation.}
 \label{tab:relation}
 \end{table}
+
+Our results show that most clones (37\%) are in a common class. 24\% of clones are in a common hierarchy. Another 24\% of clones are unrelated. 15\% of clones are in an interface.
 
@@
 \end{tabular}
-\caption{Amount of clone instances with a certain location} % Sander: miss: Amount of clone instances per location category ofzoiets
+\caption{Amount of clone instances with a per location category.}
 \label{tab:location}
 \end{table}
+
+We can see from these results that most clones are found at method level.
 
@@
 
+From these results we see that 74\% of clones span part of a method body (77\% if we include constructors).
+8\% of clones span several methods.
+6\% of clones span only global variables.
+Only 4\% of clones span a full declaration (method, class, constructor, etc.).
+
 \section{Extract Method}
@@
 The second column shows our measurements for the complete systems (just like the former experiments).
-The third column shows our measurements when restricting our search to method bodies.
-% Sander: waarom willen we dat weten?
-The amount that can be extracted increases because, when restricting our search to method bodies, we do not exclude declarations that can obstruct the possibility of method extraction (for instance a cloned method signature).
-% Sander: die laatste zin snap ik niet
 \begin{table}[H]
 \centering
-\begin{tabular}{@{}lrrrr@{}}
+\begin{tabular}{@{}lrr@{}}
 \toprule
-\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{\% (All)}} & \textit{\textbf{Method Body}} & \textit{\textbf{\% (Method Body)}} \\ \midrule
-Can Be Extracted & 24,157 & 28.2\% & 26,109 & 50.4\% \\
-Is Not A Partial Method & 21,625 & 25.3\% & 0 & 0.0\% \\
-Top-level AST-Node is not a Statement & 19,887 & 23.2\% & 4,607 & 8.9\% \\
-Spans Part of a Block & 12,964 & 15.2\% & 13,460 & 26.1\% \\
-Multiple Return Values & 5,622 & 6.6\% & 6,131 & 11.9\% \\
-Complex Control Flow & 1,106 & 1.3\% & 1,216 & 2.4\% \\
-Overlap In Clone Class & 147 & 0.2\% & 147 & 0.3\% \\
-Not In Class Or Interface & 70 & 0.1\% & 93 & 0.2\% \\
+\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{\% (All)}} \\ \midrule
+Can Be Extracted & 24,157 & 28.2\%  \\
+Is Not A Partial Method & 21,625 & 25.3\% \\
+Top-level AST-Node is not a Statement & 19,887 & 23.2\% \\
+Spans Part of a Block & 12,964 & 15.2\%  \\
+Multiple Return Values & 5,622 & 6.6\%  \\
+Complex Control Flow & 1,106 & 1.3\% \\
+Overlap In Clone Class & 147 & 0.2\% \\
+Not In Class Or Interface & 70 & 0.1\% \\
 \bottomrule

### 2019-08-23 sections/clonerefactor.tex
Fixed many various issues

@@
 This means we won't be able to find when a single expression matches another expression, or even a single token matching another token.
-This is in most cases not a problem, as expressions are often small and do not span the minimal size to be considered a clone in the first place (more about this in Section~\ref{sec:thresholds}).
+This is in most cases not a problem, as expressions are often small and do not span the minimal size to be considered a clone in the first place.
 
@@
   \caption{Graph representation of the code example displayed in Figure~\ref{fig:2rvariabilityhigh4}.}
-  \label{fig:clonerefactorprocess}
+  \label{fig:t2rgraphexample}
 \end{figure}
@@
 
-\begin{equation}\label{eq:t3rexample}
+\begin{equation}\label{eq:t3rexample2}
 \text{gap}(C_1\text{ }I_2, C_2\text{ }I_2) = \frac{|\emptyset|}{|\{n_2, n_3\}| + |\{n_4, n_5\}|} * 100 = \frac{0}{4} = 0\%
@@
 
-\subsubsection{Characteristics of the extracted method}
+\subsubsection{Characteristics of the extracted method} \label{sec:characteristics}
 We define the following characteristics that have an impact on the refactoring of the clone class:

### 2019-08-23 sections/conclusion.tex
2R and 3R thresholds discussion
Fixed many various issues

@@
 We noticed that the inheritance relation of the clone and the return value of the extracted method has only a minor impact on system maintainability.
+
+% We recommend to extend our tool, CloneRefactor, to allow for such capabilities.
+CloneRefactor already contains a component that calculates the Cyclomatic Complexity of a given method.
+Using our automated refactored model, identified problems can relatively easily be refactored.
 
@@
 To assess an automated refactoring opportunity for complex methods, we should assess which parts of methods can be split to end up with parts of similar complexity.
-For this, our research can be used to assess whether a given piece of code can be extracted to a new method (see Section~\ref{sec:refactorability}).
+For this, our research can be used to assess whether a given piece of code can be extracted to a new method (see Section~\ref{sec:refactorabilitysetup}).
 
@@
 This way, it is possible to work towards an model of automated refactoring that reduces manual refactoring efforts significantly.
+
+% When programming, there are often trade-offs between technical debt and velocity.
+When a deadline comes near, often software quality in sacrificed to gain velocity \cite{costello1984software, austin2001effects, shah2014global}.
+Apart from that, a low programmer aptitude can result in low quality code \cite{cheney1984effects}.
+This is because often forming appropriate abstractions requires time, effort and critical thinking.
+By introducing these abstractions automatically, this negative impact can (partly) be mitigated.
 

### 2019-08-23 sections/discussion.tex
Fixed many various issues

@@
 \subsection{Refactoring}
-In Fig.~\ref{fig:duplication} we see an increase in maintainability for refactoring larger clone classes.
-The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie around 28 tokens.
+In Fig.~\ref{fig:maintainabilityscore} we see an increase in maintainability for refactoring larger clone classes.
+The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie at a token volume of 63 tokens.
 There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.
 
-In Table~\ref{tab:relation_refactor} we see the results regarding refactorings that are applied to clones with diverse relations.
+In Table~\ref{tab:relationref} we see the results regarding refactorings that are applied to clones with diverse relations.
 We see that most refactored clones are in a common class, over 54\%.
@@
 
-The maintainability scores displayed in Table~\ref{tab:relation_refactor} show that the most favorable clones to refactor are clones with a sibling relation.
+The maintainability scores displayed in Table~\ref{tab:relationref} show that the most favorable clones to refactor are clones with a sibling relation.
 The most unfavorable is to refactor clones to interfaces.

### 2019-08-23 sections/introduction.tex
Xander
Fixed many various issues

@@
 Clone detection tools are configured using a predefined amount of lines or tokens that two duplicate fragments should minimally span for them to be considered clones \cite{sajnani2016sourcerercc, svajlenko2016bigcloneeval}.
-Often, such thresholds are intuitively chosen \cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data \ref{alves2010deriving}.
+Often, such thresholds are intuitively chosen \cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data \cite{alves2010deriving}.
 These methods do not always accurately reflect the effect of refactoring the system, leading to a potentially non-optimal selection of clones that are presented to the developer.
@@
 Those refactoring techniques often have to be used when dealing with duplication in software \cite{fowler2018refactoring, fontana2015duplicated}.
-Because of that, refactoring code clones has been empirically proven to cause bugs or other side effects in code.
+Because of that, refactoring code clones has been empirically shown to cause bugs or other side effects in code.
 

### 2019-08-23 sections/related_work.tex
Fixed many various issues

@@
 After all these studies that determine what preconditions apply to be able to refactor modified clones, the authors propose a tool named JDeodorant that helps in the process of refactoring such clones~\cite{mazinanian2016jdeodorant}.
-This tool takes the output of many popular clone detection tools \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, NiCAD} % Sander: Klopt het dat deze laatste citatie gewoon NiCAD is?
-ziet er beetje gek uit
-and proposes refactoring opportunities.
+This tool takes the output of many popular clone detection tools \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, cordy2011nicad} and proposes refactoring opportunities.
 The tool is integrated in the Eclipse IDE, making it easier to directly apply the refactoring.
@@
 \subsection{Refactoring Technique for Large Groups of Software Clones}
-A thesis by AlWaqfi~\cite{alwaqfi2017refactoring} propose a method for assessing refactorability of clone classes (whereas the previous tools only focus on clone pairs).
-% Sander: Deel tussen haakjes is juist mooie zin, zou hem uit haakjes halen en gewoon met komma ertussen achter de zin plaatsen
+A thesis by AlWaqfi~\cite{alwaqfi2017refactoring} propose a method for assessing refactorability of clone classes , whereas the previous tools only focus on clone pairs.
 The author surveys a set of clone detection tools \cite{kamiya2002ccfinder, baxter1999clonedr, jiang2007deckard, cordy2011nicad} and uses a publicly available dataset \cite{tsantalis2015assessing} to measure the amount of clones found by these tools.
@@
 They find that about 29-54\% of clones are refactorable in the set of projects they inspect (Table 6.13 of \cite{alwaqfi2017refactoring}).
-To determine whether a clone is refactorable, the author uses the set of eight preconditions proposed by Tsantalis et al.~\ref{tsantalis2015assessing}.
-% Sander:Deze ref komt als ??
-in tekst
+To determine whether a clone is refactorable, the author uses the set of eight preconditions proposed by Tsantalis et al.~\cite{tsantalis2015assessing}.
 
 \subsection{Pattern‐based clone Refactoring Inspection (PRI)}
-A study by Chen et al.~\ref{chen2018clone} % Sander: Deze ref komt als ?? in tekst
-addresses the problem that developers cannot easily determine which clones can be refactored or how they should be maintained scattered
-throughout a large code base in evolving systems.
+A study by Chen et al.~\cite{chen2018clone} addresses the problem that developers cannot easily determine which clones can be refactored or how they should be maintained scattered throughout a large code base in evolving systems.
 They propose PRI, a technique for managing refactorings for clones with a Sibling relation.
@@
 
-\section{Clone refatoring}
+\section{Clone refactoring}
 In this section, we shortly introduce recent studies about refactoring code clones.

### 2019-08-23 sections/research.tex
Working on discussion and results
Fixed many various issues

@@
 Because of that, we require an extra argument.
-Because of this, this variability falls under the threshold described in section \label{sec:variabilitythreshold}, whereas the example in Figure~\ref{fig:type2variablerefactoringnotradeoff} does not.
+Because of this, this variability falls under the threshold described in section \ref{sec:variabilitythreshold}, whereas the example in Figure~\ref{fig:type2variablerefactoringnotradeoff} does not.
 
@@
 
-\subsubsection{Gap threshold}
+\subsubsection{Gap threshold} \label{sec:t3rthreshold}
 For type 3R, the size of the gap between two clones is bounded by a threshold. This threshold is calculated by the following formula:
@@
 
-\begin{equation}\label{eq:type3r}
+\begin{equation}\label{eq:type3rclones}
 \text{Number of nodes in clones}=|I_{before}| + |I_{after}|.
@@
 
-\begin{equation}\label{eq:type3r}
+\begin{equation}\label{eq:type3rexample}
 \text{T3R Gap Size}=\frac{|\{N_{4}\}|}{|\{N_{3}, N_{5}\}|}*100 = \frac{1}{2}*100 = 50\%

### 2019-08-23 sections/results.tex
Fixed many various issues

@@
 In our corpus, CloneRefactor has refactored 12,710 clone classes and measured the change in indicated metrics (see Section~\ref{sec:metrics}).
-Using the presented formulas (see Section~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Section~\ref{sec:characteristics}) % Sander: Ref geeft ???
-influence the maintainability of the resulting codebase after refactoring.
+Using the presented formulas (see Section~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Section~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
 In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.
@@
 \subsection{Relation}
-Table~\ref{tab:full-relation} shows our data regarding how different relations influence maintainability.
+Table~\ref{tab:relationref} shows our data regarding how different relations influence maintainability.
 We mark rows based on less than 100 refactorings red, as their result does not have statistical significance.
@@
 \caption{Average metric values for refactorings of clone classes with the specified relations}
-\label{tab:full-relation}
+\label{tab:relationref}
 \end{table}
@@
 \caption{Average metric values for refactorings of clone classes with the specified return category}
-\label{tab:full-return}
+\label{tab:return}
 \end{table}

### 2019-08-23 sections/results.tex
Explaining the results a bit

@@
 The maintainability score, as shown in Figure \ref{fig:maintainabilityscore}, is the average delta maintainability score of all clone classes with the specified token volume that are refactored.
-As the amount of data points decreases, the datapoints gain less statistical significance, because of which we represent the x-axis as a logaritmic scale.% Sander: weet niet zeker of dit logaritmische schaal heet
+As the amount of data points decreases, the datapoints gain less statistical significance, because of which we represent the x-axis as a logaritmic scale.
 The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.
@@
 Because of that, what we see in Figure~\ref{fig:maintainabilityscore} could largely be caused by this metric.
-Do determine the effect of clone token volume on each metric, we also plot graphs in which each metric is considered singularly.
+To determine the effect of clone token volume on each metric, we also plot graphs in which each metric is considered singularly.
 In Figure~\ref{fig:volume} the average delta volume is shown when clones with the specified token volume are refactored.
@@
 Table~\ref{tab:relationref} shows our data regarding how different relations influence maintainability.
-We mark rows based on less than 100 refactorings red, as their result does not have statistical significance.
+We mark rows based on less than 100 refactorings red, as their result might not have statistical significance.
 The \textbf{Relation} column refers to the relations introduced in Section~\ref{sec:setuprelation}.
@@
 \hspace{10pt} Sibling & -70.07 & 0.69 & 1.28 & -10.97 & 1,722 & 0.23 \\
+\rowcolor[HTML]{FFCCC9}
 \hspace{10pt} Same Hierarchy & -44.18 & 0.95 & 0.89 & 1.54 & 87 & 0.10 \\
 \hspace{10pt} First Cousin & -42.69 & 0.89 & 0.93 & 4.86 & 144 & 0.02 \\
+\rowcolor[HTML]{FFCCC9}
 \hspace{10pt} Ancestor & -32.75 & 1.00 & 0.75 & 11.00 & 20 & -0.03 \\ \midrule
@@
 
+The displayed relations are ordered by their scores.
+Overall, the scores do not deviate much (-0.15 to 0.23), indicating that the relation between clones has a minor impact on maintainability.
+Overall, we see that common hierarchy clones have the highest maintainability, whereas unrelated clones have the lowest maintainability.
+
 \subsection{Return Category}
@@
 \toprule
-\textit{\textbf{Return Category}} & \textit{\textbf{Complexity}} & \textit{\textbf{Interface Size}} & \textit{\textbf{Size}} & \textit{\textbf{Duplication}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
+\textit{\textbf{Return Category}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Size}} & \textit{\textbf{Duplication}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
 Return & 0.85 & 1.02 & -3.84 & -55.00 & 1,571 & 0.19 \\
 Declare & 0.94 & 0.74 & 11.11 & -49.19 & 5,177 & 0.15 \\
+\rowcolor[HTML]{FFCCC9}
 Assign & 0.79 & 1.07 & 0.43 & -56.29 & 14 & 0.12 \\
@@
 \end{table}
+
+The displayed return categories are ordered by their scores.
+Overall, the scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability.
+When the result of the call to the extracted method is directly returns, the maintainability score is the highest.
+When no value is returned, the maintainability score is the lowest.
+The main reason that no return value ends up lowest, is that it is linked to a higher number of parameters.
 

### 2019-08-23 sections/conclusion.tex
Moved discussion part to conclusion

@@
 Because of that, there is a threat to validity in the source code in the corpus, as it potentially includes sources that do not reflect human-maintained production code.
+
+%\subsection{Java Corpus}
+%In our experiments we chose to use a GitHub based software corpus.
+This corpus contains a diversity of projects of many different sizes.
+We noticed that there is a lot of difference in the quality of these software systems: some systems had a lot of duplication and some did not have any duplication.
+Furthermore, it took an extensive filtering process to remove all files not suitable for application in this research (like generated files).
+
+We think that there is value in running our experiments with different corpuses.
+We would, for instance, be interested in the results for industrial projects instead of open source software systems.
+We are curious to see whether the distributions are comparable, or whether they show large differences.
+
+Furthermore, we think that there is value in running our experiments with a set of larger sized and more professionally developed open-source systems.
+We noticed that in our corpus there were a lot of projects that have only few commits and contributors.
+We think it would be valuable to, for instance, perform our experiments with a set of larger open source systems, like the systems in the Apache ecosystem.
+
+\subsection{Survey}
+To limit the scope of this research, we chose not to include human subjects in this study.
+However, we think that the results of this study could be strengthened by performing a survey on software engineering practisioners.
+We have determined a set of refactoring opportunities only based on literature input and quantitive analysis.
+It would be valuable to have a control group rate the refactorings performed by CloneRefactor, as an extra form of input regarding the quality of the code transformation that CloneRefactor performs.
 

### 2019-08-23 sections/discussion.tex
Moved discussion part to conclusion

@@
 
-\section{Experimental setup}% TODO: Sander - deze sectie is gek, soort combinatie van opzet en threats to validity, het kan wel maar loopt niet super lekker met het geheel
-In this section we discuss the setup of our experiments. We discuss alternative setups that could lead to other perspectives on the problem addressed.
-
-\subsection{Java Corpus}
-In our experiments we chose to use a GitHub based software corpus.
-This corpus contains a diversity of projects of many different sizes.
-We noticed that there is a lot of difference in the quality of these software systems: some systems had a lot of duplication and some did not have any duplication.
-Furthermore, it took an extensive filtering process to remove all files not suitable for application in this research (like generated files).
-
-We think that there is value in running our experiments with different corpuses.
-We would, for instance, be interested in the results for industrial projects instead of open source software systems.
-We are curious to see whether the distributions are comparable, or whether they show large differences.
-
-Furthermore, we think that there is value in running our experiments with a set of larger sized and more professionally developed open source systems.
-We noticed that in our corpus there were a lot of projects that have only few commits and contributors.
-We think it would be valuable to, for instance, perform our experiments with a set of larger open source systems, like the systems in the Apache ecosystem.
-
-\subsection{Survey}
-To limit the scope of this research, we chose not to include human subjects in this study.
-However, we think that the results of this study could be strengthened by performing a survey on software engineering practisioners.
-We have determined a set of refactoring opportunities only based on literature input and quantitive analysis.
-It would be valuable to have a control group rate the refactorings performed by CloneRefactor, as an extra form of input regarding the quality of the code transformation that CloneRefactor performs.
-
 \section{Results}

### 2019-08-23 sections/discussion.tex
Sander feedback

@@
 \section{Clone Type Definitions}
-In this study, we proposed a set of clone type definitions for which a refactoring opportunity is known.
-% TODO: Sander - is known is beetje gek
-% TODO: Sander - zou ook uitleggen waarom we nieuwe definities nodig hadden
+In this study, we proposed a set of clone type definitions that can be automatically refactored.
 We based these clone type definitions on the clone type definitions that are commonly used in literature.
@@
 An example of this is displayed in Figure~\ref{fig:samereturn}.
-The only thing to watch out for is method that has side effects.
+The only thing to watch out for is methods that have side effects.
 Because methods may be executed in another point during execution, this might affect the functionality of the code.
-% TODO: Sander - how would you try to solve this?
+Because of that, before applying such a refactoring it should be verified that the called method has to side effects.
 

### 2019-08-23 sections/conclusion.tex
Sander

--- 2019-08-23 sections/conclusion.tex
@@
 \chapter{Conclusion} \label{ch:conclusion}
-We defined automatically refactorable clones and created a tool to detect and refactor them.
+In this work we defined automatically refactorable clones and created a tool to detect and refactor them.
 We measured statistical data with this tool over a large corpus of open-source Java software systems to get more information about the context of clones and how refactoring them influences system maintainability.
@@
 To assess an automated refactoring opportunity for complex methods, we should assess which parts of methods can be split to end up with parts of similar complexity.
-For this, our research can be used to assess whether a given piece of code can be extracted to a new method (see Section~\ref{sec:refactorabilitysetup}).
+For this, our research can be used to assess whether a given piece of code can be extracted to a new method (see Section~\ref{sec:refactorability}).
 

### 2019-08-23 sections/experimentalsetup.tex
Experimental setup Sander feedback

--- 2019-08-21 sections/experimentalsetup.tex
@@
 \section{The Corpus}\label{chap:corpus}
-For our experiments we use a large corpus of open source projects \cite{githubCorpus2013}.
+For our experiments we use a large corpus of open-source projects assembled by Allamanis et al.~\cite{githubCorpus2013}\footnote{The corpus can be downloaded at: \url{http://groups.inf.ed.ac.uk/cup/javaGithub/}}.
 This corpus contains a set of Java projects from GitHub, selected by number of forks.
-The projects in this corpus were then de-duplicated manually.
+The projects and files in this corpus were de-duplicated manually.
 This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
 
-For our purposes, we have further filtered this corpus to get a controlled set of projects for our experiments.
-In this section, we explain the steps we took to prepare the corpus\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} and the rationale behind those steps.
-
-\section{Tool Validation}
-We have validated the correctness of CloneRefactor through unit tests and empirical validation.
-First, we created a set of 57 control projects to verify the correctness in many (edge) cases.
-These projects contain clones for each identified relation, location, contents and refactorability category (see Section \ref{chap:contextsetup} and \ref{sec:refactorabilitysetup}), to see whether they get correctly identified.
-Next, we run the tool over the corpus and manually verify samples of the acquired results.
-This way, we check both the correctness of the identified clones, their context and their proposed refactoring.
-
-We also test the correctness of the resulting code after refactoring.
-For this, we use a GitHub project named JFreeChart.
-JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor.
+Because CloneRefactor requires all dependencies for the projects it analyses, we created a set of scripts\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} to filter the corpus for all projects for which we can obtain all dependencies using Maven.
+In this section, we explain the actions performed by the scripts and the rationale behind those actions.
 
@@
 As explained in Section~\ref{chap:challenge}, CloneRefactor requires all the libraries a software project is dependent on in order to perform its clone analysis.
-As these are not included in the used corpus \cite{githubCorpus2013}, we decided to limit our scope to a single build automation system.
+As these are not included in the corpus by Allamanis \cite{githubCorpus2013}, we created a script to gather these dependencies.
+As Java projects manage their dependencies in many different ways, we decided to limit our scope to a single build automation system.
 We chose Maven, as it is one of the most used build automation systems for Java projects.
 Maven uses a file, named \texttt{pom.xml}, to describe a projects' dependencies.
-As no \texttt{pom.xml} files are included in the corpus, we cloned the latest version of each project in the corpus.
-We then removed each project that has no \texttt{pom.xml} file (which indicates that those do not use the Maven build automation system).
+Our script clones the latest version of each project in the corpus.
+It then removes each project that has no \texttt{pom.xml} file (which indicates that those do not use the Maven build automation system).
 
-Because we cloned the projects (and do not use the sources provided in the corpus), they still included generated source code.
-Because we do not want to analyze generated Java files, we decided to further filter the corpus to only include projects with a conventional structure.
+We then continued to filter all testcases and generated files.
+As many projects store these files in many different places, we decided to further filter the corpus to only include projects with a conventional structure.
 For Maven, projects are recommended to put their production code in the folder structure \texttt{src/main/java}.
 We omitted Maven projects that do not adhere to this convention.
+We instruct CloneRefactor only to use the sources in the \texttt{src/main/java} folder.
+This decreases the chance of generated files and testcode being considered for clone detection.
 
@@
 Maven uses the following command to automate this process: \texttt{mvn dependency:copy-dependencies -DoutputDirectory=lib}.
-This process can fail if external dependencies are no longer available.
-We removed such projects for which we could not obtain all dependencies.
+This process fails if the project requires external dependencies that are no longer available.
+Our scripts remove such projects for which it cannot obtain all dependencies.
 
 \subsection{Building an AST of all Java files}
-To verify the correctness of all Java files in the projects, we used JavaParser \cite{tomassetti2017javaparser} to create an AST of every Java file in the \texttt{src/main/java} folder of the software projects.
+To verify the syntactical correctness of all Java files in the projects, we used JavaParser \cite{tomassetti2017javaparser} to create an AST of every Java file in the \texttt{src/main/java} folder of the software projects.
 A very small set of projects had syntactical errors, which we removed from the corpus.
+For instance, some projects had code that was still in development on their \textit{master} branch, which did not compile.
+We remove them because CloneRefactor cannot parse them into an AST.
 
@@
 We ran CloneRefactor over every project in the corpus and inspected the output for each project.
-Some projects gave unusual high numbers of projects of a certain size, which we manually inspected.
+Some projects gave unusual high numbers of clones of a certain size, which we manually inspected.
 Often these projects contained generated source files.
@@
 This is an average of 6,268 lines over an average of 44 files per project, 141 lines on average per file.
-The largest project in the corpus is \textit{VisAD} with 502,052 lines over 1,527.
+The largest project in the corpus is \textit{VisAD} with 502,052 lines over 1,527 files.
+
+\section{Tool Validation}
+We have validated the correctness of CloneRefactor through unit tests and empirical validation.
+First, we created a set of 57 control projects\footnote{Control projects for testing CloneRefactor: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to verify the correctness in many (edge) cases.
+These projects test each identified relation, location, contents and refactorability category (see Section \ref{chap:contextsetup} and \ref{sec:refactorabilitysetup}), to see whether they are correctly identified.
+Next, we run the tool over the corpus and manually verify samples of the acquired results.
+This way, we check the correctness of the identified clones, their context and their proposed refactoring.
+
+We also test the correctness of the resulting code after refactoring.
+For this, we use a GitHub project named JFreeChart.
+JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor.
+We run CloneRefactor manually over the JFreeChart project, run its testcases and check the correctness of the proposed refactorings.
 
 \section{Minimum clone size}
-In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored.
-However, when clones are very small, they may never be able to improve maintainability.
-The detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication.
+In this study, we want to find out what thresholds will improve maintainability if clones by those thresholds are refactored.
+For example, when clones are very small, refactoring them might not improve maintainability since the detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication.
 Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones cannot improve maintainability when refactored.
+
+The reason for this is that when applying the ``Extract Method'' refactoring technique, we create a new method.
+An empty method in Java consists of 7 tokens.
+We also need calls to the extracted method, which is 4 tokens per call if no arguments are required.
+Consider the smallest possible clone: 2 clone instances of 1 token.
+Such a refactoring will never improve maintainability.
+We reduce duplication by 2 tokens, while increasing volume by 7+4+4+1=16 tokens.
+This holds true for clones up to 9 tokens (reduce duplication by 18 tokens, increase volume by 7+4+4+9=24 tokens).
+Empirically, we found all clones below 10 tokens in size, are very unlikely to affect maintainability positively.
+To avoid such clones polluting our data, we do not consider clones smaller than 10 tokens.
 
@@
 In this study, we use four metrics to determine maintainability (see Section~\ref{sec:metrics}).
-For our experiments, we aggregate the deltas obtained for these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
+For each of these metrics, we collect their increase/decrease (delta) after each applied refactoring.
+We aggregate these delta metric values to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
 We base our aggregation on the following assumptions:
@@
   \item All metrics are equal in terms of weight towards system maintenance effort.
-  \item Higher values for the metrics imply lower maintainability.
-  \item Normalizing each obtained metric delta over all deltas obtained a metric in our dataset results in equally weighted scores.
+  \item Higher values for the metrics imply lower maintainability. % Sander: Dit is niet echt assumptie toch
+  \item Normalizing each obtained metric delta over all deltas obtained for a metric in our dataset results in equally weighted scores.
 \end{itemize}
-We derived these assumptions partly from Heitlager et al~\cite{heitlager2007practical} and our own expert intuition.
-The validity of these metrics influences the validity of the conclusions we can draw from our data.
-Because of that, in our experiments we focus mainly on significant differences in maintainability to draw a conclusion.
+We derived these assumptions from supporting evidence shown by Heitlager et al~\cite{heitlager2007practical} and Alves et al.~\cite{alves2010deriving}.
+Using the resulting aggregated maintainability score, we can argue for each refactoring whether it increases or decreases the maintainability of the system.
 
@@
 \begin{equation}\label{eq:scoreref}
-N_{duplication} + N_{complexity} + N_{volume} + N_{parameters}
+\text{Maintainability Score} = N_{duplication} + N_{complexity} + N_{volume} + N_{parameters}
 \end{equation}

### 2019-08-24 icse/paper.tex
Calculating maintainability score

@@
 In this study, we use four metrics to determine maintainability (see Sec.~\ref{sec:metrics}).
+For each of these metrics, we determine their value before and after each refactored clone class, resulting in a delta metric score.
 For our experiments, we aggregate the deltas obtained for these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
@@
   \item Higher values for the metrics imply lower maintainability.
-  \item Normalizing each obtained metric delta over all deltas obtained a metric in our dataset results in equally weighted scores.
+  \item Normalizing each obtained metric delta over all deltas obtained for a metric in our dataset results in equally weighted scores.
 \end{itemize}
-We derived these assumptions partly from Heitlager et al~\cite{heitlager2007practical} and our own expert intuition.
-The validity of these metrics influences the validity of the conclusions we can draw from our data.
-Because of that, in our experiments we focus mainly on significant differences in maintainability to draw a conclusion.
+We derived these assumptions from supporting evidence shown by Heitlager et al~\cite{heitlager2007practical} and Alves et al.~\cite{alves2010deriving}.
+Using the resulting aggregated maintainability score, we can argue for each refactoring whether it increases or decreases the maintainability of the system.
 
-We normalize each obtained metric delta using the ``Standard score'', which is as follows:
+We normalize each obtained metric delta using the ``Standard score'', which is calculated as follows:
 \begin{equation}\label{eq:scoredev}
@@
 \end{equation}
-Where $\Delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metrics.
-This method works well for normalization of our data, because as we divide by the standard deviation, outliers do not influence the resulting scores much.
+Where $\Delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metric.
+This method works well for normalization of our data, because as we divide by the standard deviation, outliers do not influence the resulting scores negatively.
 
@@
 \end{table}
+
+Our results show that most clones (37\%) are in a common class. 24\% of clones are in a common hierarchy. Another 24\% of clones are unrelated. 15\% of clones are in an interface.
 

### 2019-08-24 icse/paper.tex
Updating results

@@
 \centering
-\begin{tabular}{@{}llll@{}}
+\begin{tabular}{@{}llrr@{}}
 \toprule
@@
 
+From these results we see that 74\% of clones span part of a method body (77\% if we include constructors).
+8\% of clones span several methods.
+6\% of clones span only global variables.
+Only 4\% of clones span a full declaration (method, class, constructor, etc.).
+
 \subsection{Extract Method}
@@
 \centering
-\begin{tabular}{@{}lll@{}}
+\begin{tabular}{@{}lrr@{}}
 \toprule
-\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{Method Body}} \\ \midrule
-Can Be Extracted & 24,157 & 26,109 \\
-Is Not A Partial Method & 21,625 & 0 \\
-Top-level AST-Node is not a Statement & 19,887 & 4,607 \\
-Spans Part of a Block & 13,181 & 13,700 \\
-Multiple Return Values & 5,622 & 6,131 \\
-Complex Control Flow & 1,106 & 1,216 \\ \bottomrule
+\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{\%}} \\ \midrule
+Can Be Extracted & 24,157 & 28.2\%  \\
+Is Not A Partial Method & 21,625 & 25.3\% \\
+Top-level AST-Node is not a Statement & 19,887 & 23.2\% \\
+Spans Part of a Block & 12,964 & 15.2\%  \\
+Multiple Return Values & 5,622 & 6.6\%  \\
+Complex Control Flow & 1,106 & 1.3\% \\
+Overlap In Clone Class & 147 & 0.2\% \\
+Not In Class Or Interface & 70 & 0.1\% \\
 \end{tabular}

### 2019-08-24 icse/paper.tex
Some stuff

@@
 Based on these relations, CloneRefactor determines where to place the cloned code when refactored.
+These categories are mutually exclusive: a clone class will be flagged as the first relation in above list that it applies to.
 The code of clones that have a \textit{Common Class} relation can be refactored by placing the cloned code in this same class.
@@
 %To what extent can found clones be refactored through method extraction, without requiring additional transformations.
-Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique.
-The second column shows our measurements for the complete systems (just like the former experiments).
-The third column shows our measurements when restricting our search to method bodies.
+Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique (see ).
+%The second column shows our measurements for the complete systems (just like the former experiments).
+%The third column shows our measurements when restricting our search to method bodies.
 The amount that can be extracted increases because, when restricting our search to method bodies, we do not exclude declarations that can obstruct the possibility of method extraction (for instance a cloned method signature).
@@
 Top-level AST-Node is not a Statement & 19,887 & 23.2\% \\
-Spans Part of a Block & 12,964 & 15.2\%  \\
+Spans Part of a Block & 13,181 & 15.5\%  \\
 Multiple Return Values & 5,622 & 6.6\%  \\
 Complex Control Flow & 1,106 & 1.3\% \\
-Overlap In Clone Class & 147 & 0.2\% \\
-Not In Class Or Interface & 70 & 0.1\% \\
 \end{tabular}
-\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique}
+\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique.}
 \label{tab:refactorability}
@@
 \end{figure*}
-
-The volume of the clone is the dominating factor regarding the maintainability increase/decrease of cloned code.
-Because of that, for our further experiments, we filter out all refactorings with a token size smaller than 18 because otherwise the small clones dominate the results and turn all results towards unmaintainable.
 

### 2019-08-24 icse/paper.tex
ICSE Results

@@
 \subsubsection{Clone Token Volume}
-Figure \ref{fig:duplication} shows the obtained results when plotting the clone size (in tokens) vs the maintainability increase/decrease.
-On the secondary axis the amount of refactorings that have refactored a clone with the specified amount of tokens is displayed (e.g.
-the amount of data points the data is based on).
-As the amount of data points decreases, the datapoints gain less statistical significance.
+Figure \ref{fig:maintainabilityscore} shows the obtained results when plotting the clone volume vs the average delta maintainability score.
+We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class.
+For higher token volume numbers we have less refactorings that refactor such clones, because of which we represent the x-axis as a logaritmic scale.
+The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.
 
 \begin{figure*}
-  \includegraphics[width=1\textwidth]{img/duplication}
-  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability. Maintainability on the primary axis and amount of refactorings on the secondary axis.}
-  \label{fig:duplication}
+  \includegraphics[width=1\textwidth]{img/tokenvolume}
+  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability.}
+  \label{fig:maintainabilityscore}
 \end{figure*}
@@
 
-\begin{table}[]
+\begin{table*}[htb]
 \centering
-\begin{tabular}{@{}lll@{}}
+%\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lrrrrrr@{}}
 \toprule
-\textit{\textbf{Relation}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Maintainability\\ Score\end{tabular}}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Number of\\ Refactorings\end{tabular}}} \\ \midrule
-\textbf{Common Hierarchy} & \textbf{0.51} & \textbf{792} \\ \midrule
-\hspace{10pt} Sibling & 0.57 & 637 \\
+\textit{\textbf{Relation}} & \textit{\textbf{Duplication}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Volume}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
+\textbf{Common Hierarchy} & \textbf{-66.33} & \textbf{0.73} & \textbf{1.20} & \textbf{-8.85} & \textbf{2,202} & \textbf{0.23} \\ \midrule
+\hspace{10pt} Superclass & -64.48 & 0.79 & 0.94 & -7.22 & 229 & 0.42 \\
+\hspace{10pt} Sibling & -70.07 & 0.69 & 1.28 & -10.97 & 1,722 & 0.23 \\
 \rowcolor[HTML]{FFCCC9}
-\hspace{10pt} Same Hierarchy & 0.55 & 22 \\
+\hspace{10pt} Same Hierarchy & -44.18 & 0.95 & 0.89 & 1.54 & 87 & 0.10 \\
+\hspace{10pt} First Cousin & -42.69 & 0.89 & 0.93 & 4.86 & 144 & 0.02 \\
 \rowcolor[HTML]{FFCCC9}
-\hspace{10pt} Superclass & 0.20 & 74 \\
-\rowcolor[HTML]{FFCCC9}
-\hspace{10pt} First Cousin & -0.02 & 53 \\
-\rowcolor[HTML]{FFCCC9}
-\hspace{10pt} Ancestor & -0.65 & 6 \\ \midrule
-\textbf{Common Class} & \textbf{0.01} & \textbf{2,025}\\ \midrule
-\hspace{10pt} Same Method & 0.01 & 762  \\
-\hspace{10pt} Same Class & 0.01 & 1,263 \\ \midrule
-\textbf{Unrelated} & \textbf{-0.02} & \textbf{688}\\ \midrule
-\hspace{10pt} No Direct Superclass & 0.08 & 289 \\
-\hspace{10pt} External Superclass & -0.02 & 225  \\
-\rowcolor[HTML]{FFCCC9}
-\hspace{10pt} No Indirect Superclass & -0.04 & 30  \\
-\hspace{10pt} External Ancestor & -0.26 & 144  \\ \midrule
-\textbf{Common Interface} & \textbf{-0.11} & \textbf{283} \\ \midrule
-\hspace{10pt} Same Direct Interface & 0.02 & 160 \\
-\hspace{10pt} Same Indirect Interface & -0.31 & 123
-\end{tabular}
-\caption{Influence on maintainability of refactoring clones by certain relations.}
+\hspace{10pt} Ancestor & -32.75 & 1.00 & 0.75 & 11.00 & 20 & -0.03 \\ \midrule
+\textbf{Common Interface} & \textbf{-47.06} & \textbf{0.83} & \textbf{1.04} & \textbf{4.50} & \textbf{1,044} & \textbf{-0.02} \\ \midrule
+\hspace{10pt} Same Indirect Interface & -37.08 & 0.93 & 0.82 & 9.96 & 487 & -0.01 \\
+\hspace{10pt} Same Direct Interface & -55.79 & 0.75 & 1.24 & -0.28 & 557 & -0.02 \\ \midrule
+\textbf{Common Class} & \textbf{-52.42} & \textbf{0.87} & \textbf{1.13} & \textbf{1.47} & \textbf{7,239} & \textbf{-0.02} \\ \midrule
+\hspace{10pt} Same Class & -51.85 & 0.86 & 1.03 & 3.36 & 4,874 & 0.04 \\
+\hspace{10pt} Same Method & -53.60 & 0.90 & 1.32 & -2.44 & 2,365 & -0.15 \\ \midrule
+\textbf{Unrelated} & \textbf{-45.86} & \textbf{0.88} & \textbf{1.08} & \textbf{9.56} & \textbf{2,198} & \textbf{-0.15} \\ \midrule
+\hspace{10pt} No Direct Superclass & -52.24 & 0.84 & 1.12 & 6.04 & 811 & -0.06 \\
+\hspace{10pt} External Superclass & -47.09 & 0.87 & 1.13 & 8.77 & 697 & -0.17 \\
+\hspace{10pt} External Ancestor & -35.73 & 0.93 & 0.95 & 14.58 & 586 & -0.21 \\
+\hspace{10pt} No Indirect Superclass & -44.89 & 0.84 & 1.18 & 14.08 & 104 & -0.30 \\ \midrule
+\textbf{Grand Total} & \textbf{-53.26} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
+\end{tabular}%
+%}
+\caption{Influence on maintainability of refactoring clones with the specified relation categories.}
 \label{tab:relation_refactor}
-\end{table}
+\end{table*}
+
+The displayed relations are ordered by their scores.
+Overall, the scores do not deviate much (-0.15 to 0.23), indicating that the relation between clones has a minor impact on maintainability.
+Overall, we see that common hierarchy clones have the highest maintainability, whereas unrelated clones have the lowest maintainability.
 
@@
 \subsection{Refactoring}
-In Fig.~\ref{fig:duplication} we see an increase in maintainability for refactoring larger clone classes.
+In Fig.~\ref{fig:maintainabilityscore} we see an increase in maintainability for refactoring larger clone classes.
 The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie around 28 tokens.

### 2019-08-24 icse/paper.tex
New return value table

@@
 \subsubsection{Relation}
-Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Sec.~\ref{sec:relation}).
+Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for the identified relations between clone instances (see Sec.~\ref{sec:relation}).
 
@@
 
-\begin{table}[H]
+\begin{table*}
 \centering
-\begin{tabular}{@{}lll@{}}
+%\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lrrrrrr@{}}
 \toprule
-\textit{\textbf{Return Value}} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Maintainability}}\\\textit{\textbf{Score}}\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textit{\textbf{Number of}}\\\textit{\textbf{Refactorings}}\end{tabular} \\ \midrule
-Return & 0.20 & 421 \\
-Void & 0.19 & 2052 \\
-Declare & 0.03 & 1318 \\
+\textit{\textbf{Return Category}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Size}} & \textit{\textbf{Duplication}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
+Return & 0.85 & 1.02 & -3.84 & -55.00 & 1,571 & 0.19 \\
+Declare & 0.94 & 0.74 & 11.11 & -49.19 & 5,177 & 0.15 \\
 \rowcolor[HTML]{FFCCC9}
-Assign & -1.29 & 3 \\ \bottomrule
-\end{tabular}
-\caption{Maintainability scores for different return values}
+Assign & 0.79 & 1.07 & 0.43 & -56.29 & 14 & 0.12 \\
+Void & 0.76 & 1.49 & -5.85 & -56.35 & 5,921 & -0.18 \\ \midrule
+\textbf{Grand Total} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{-53.26} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
+\end{tabular}%
+%}
+\caption{Average metric values for refactorings of clone classes with the specified return category}
 \label{tab:return}
-\end{table}
+\end{table*}
+
+The displayed return categories are ordered by their scores.
+Overall, the scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability.
+When the result of the call to the extracted method is directly returns, the maintainability score is the highest.
+When no value is returned, the maintainability score is the lowest.
+The main reason that no return value ends up lowest, is that it is linked to a higher number of parameters required for the extracted method.
 

### 2019-08-24 icse/paper.tex
Replaced all results
Aaah I don't know what to do with this thresholds thing

@@
 
-\subsubsection{Extract Method}
+\subsubsection{Extract Method} \label{sec:refactorability}
 % Show my categories to show what clones can be dealt with by method extraction.
@@
 The detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication.
-Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones cannot improve maintainability when refactored.
+Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones are very unlikely to improve maintainability when refactored.
+
+\subsection{Thresholds}
+Most clone detection tools can be configured using thresholds.
+These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones.
+Often, such thresholds are intuitively chosen \cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data \cite{alves2010deriving}.
+Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
+
+%In our experiments, we compare the maintainability scores for different thresholds.
+We use the \textit{standard error} to determine the correlation between the used threshold metric and the maintainability score.
+A low standard error shows that the threshold metric has a high influence on the maintainability score.
+This makes it more suitable to use as a threshold.
+By plotting the maintainability scores for different thresholds, we can determine which thresholds should be used to positively influence maintainability.
+
+%We define the following volume-based thresholds for clones, ordered by how often clone detection tools support such thresholds:
+%\begin{itemize}
+%\item \textbf{Number of lines}: The number of lines a single instance of the clone class spans.
+%\item \textbf{Tokens}: The number of tokens a single instance of the clone class spans.
+%\item \textbf{Number of statements}: The number of statements a single clone instance.
+Often closely reflects the number of lines, but is not dependent on coding style (number of newlines used by the programmer in statements).
+%\item \textbf{Token Volume}: The number of tokens in all clone instances in a clone class combined.
+%\end{itemize}
 
@@
 \end{equation}
+
+%% RESULTS TABLES (MOVED UP SO LATEX PLACES THEM IN THE RIGHT PLACE)
+
+\begin{table*}
+\centering
+%\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lrrrrrr@{}}
+\toprule
+\textit{\textbf{Relation}} & \textit{\textbf{Duplication}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Volume}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
+\textbf{Common Hierarchy} & \textbf{-66.33} & \textbf{0.73} & \textbf{1.20} & \textbf{-8.85} & \textbf{2,202} & \textbf{0.23} \\ \midrule
+\hspace{10pt} Superclass & -64.48 & 0.79 & 0.94 & -7.22 & 229 & 0.42 \\
+\hspace{10pt} Sibling & -70.07 & 0.69 & 1.28 & -10.97 & 1,722 & 0.23 \\
+\rowcolor[HTML]{FFCCC9}
+\hspace{10pt} Same Hierarchy & -44.18 & 0.95 & 0.89 & 1.54 & 87 & 0.10 \\
+\hspace{10pt} First Cousin & -42.69 & 0.89 & 0.93 & 4.86 & 144 & 0.02 \\
+\rowcolor[HTML]{FFCCC9}
+\hspace{10pt} Ancestor & -32.75 & 1.00 & 0.75 & 11.00 & 20 & -0.03 \\ \midrule
+\textbf{Common Interface} & \textbf{-47.06} & \textbf{0.83} & \textbf{1.04} & \textbf{4.50} & \textbf{1,044} & \textbf{-0.02} \\ \midrule
+\hspace{10pt} Same Indirect Interface & -37.08 & 0.93 & 0.82 & 9.96 & 487 & -0.01 \\
+\hspace{10pt} Same Direct Interface & -55.79 & 0.75 & 1.24 & -0.28 & 557 & -0.02 \\ \midrule
+\textbf{Common Class} & \textbf{-52.42} & \textbf{0.87} & \textbf{1.13} & \textbf{1.47} & \textbf{7,239} & \textbf{-0.02} \\ \midrule
+\hspace{10pt} Same Class & -51.85 & 0.86 & 1.03 & 3.36 & 4,874 & 0.04 \\
+\hspace{10pt} Same Method & -53.60 & 0.90 & 1.32 & -2.44 & 2,365 & -0.15 \\ \midrule
+\textbf{Unrelated} & \textbf{-45.86} & \textbf{0.88} & \textbf{1.08} & \textbf{9.56} & \textbf{2,198} & \textbf{-0.15} \\ \midrule
+\hspace{10pt} No Direct Superclass & -52.24 & 0.84 & 1.12 & 6.04 & 811 & -0.06 \\
+\hspace{10pt} External Superclass & -47.09 & 0.87 & 1.13 & 8.77 & 697 & -0.17 \\
+\hspace{10pt} External Ancestor & -35.73 & 0.93 & 0.95 & 14.58 & 586 & -0.21 \\
+\hspace{10pt} No Indirect Superclass & -44.89 & 0.84 & 1.18 & 14.08 & 104 & -0.30 \\ \midrule
+\textbf{Grand Total} & \textbf{-53.26} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
+\end{tabular}%
+%}
+\caption{Influence on maintainability of refactoring clones with the specified relation categories.}
+\label{tab:relation_refactor}
+\end{table*}
+
+%% END TABLES
 
@@
 
-\subsection{Extract Method}
+\subsection{Refactorability}
 %To what extent can found clones be refactored through method extraction, without requiring additional transformations.
-Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique (see ).
+Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique (see Sec.~\ref{sec:refactorability}).
 %The second column shows our measurements for the complete systems (just like the former experiments).
@@
 
-\subsection{Refactoring}
+These results indicate that, given our refactorability criteria, 28\% of clones can be automatically refactored.
+Clones in other categories may require other refactoring techniques or further transformations to be automatically refactorable.
+
+\subsection{Thresholds}
 %I think the ultimate goal with this thesis is to do experiments with different clone thresholds.
@@
 In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.
+Using this data, we find supporting evidence regarding which thresholds are most likely to find clones that should be refactored to improve maintainability.
 
@@
 We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance.
-
-\begin{table*}[htb]
-\centering
-%\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lrrrrrr@{}}
-\toprule
-\textit{\textbf{Relation}} & \textit{\textbf{Duplication}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Volume}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
-\textbf{Common Hierarchy} & \textbf{-66.33} & \textbf{0.73} & \textbf{1.20} & \textbf{-8.85} & \textbf{2,202} & \textbf{0.23} \\ \midrule
-\hspace{10pt} Superclass & -64.48 & 0.79 & 0.94 & -7.22 & 229 & 0.42 \\
-\hspace{10pt} Sibling & -70.07 & 0.69 & 1.28 & -10.97 & 1,722 & 0.23 \\
-\rowcolor[HTML]{FFCCC9}
-\hspace{10pt} Same Hierarchy & -44.18 & 0.95 & 0.89 & 1.54 & 87 & 0.10 \\
-\hspace{10pt} First Cousin & -42.69 & 0.89 & 0.93 & 4.86 & 144 & 0.02 \\
-\rowcolor[HTML]{FFCCC9}
-\hspace{10pt} Ancestor & -32.75 & 1.00 & 0.75 & 11.00 & 20 & -0.03 \\ \midrule
-\textbf{Common Interface} & \textbf{-47.06} & \textbf{0.83} & \textbf{1.04} & \textbf{4.50} & \textbf{1,044} & \textbf{-0.02} \\ \midrule
-\hspace{10pt} Same Indirect Interface & -37.08 & 0.93 & 0.82 & 9.96 & 487 & -0.01 \\
-\hspace{10pt} Same Direct Interface & -55.79 & 0.75 & 1.24 & -0.28 & 557 & -0.02 \\ \midrule
-\textbf{Common Class} & \textbf{-52.42} & \textbf{0.87} & \textbf{1.13} & \textbf{1.47} & \textbf{7,239} & \textbf{-0.02} \\ \midrule
-\hspace{10pt} Same Class & -51.85 & 0.86 & 1.03 & 3.36 & 4,874 & 0.04 \\
-\hspace{10pt} Same Method & -53.60 & 0.90 & 1.32 & -2.44 & 2,365 & -0.15 \\ \midrule
-\textbf{Unrelated} & \textbf{-45.86} & \textbf{0.88} & \textbf{1.08} & \textbf{9.56} & \textbf{2,198} & \textbf{-0.15} \\ \midrule
-\hspace{10pt} No Direct Superclass & -52.24 & 0.84 & 1.12 & 6.04 & 811 & -0.06 \\
-\hspace{10pt} External Superclass & -47.09 & 0.87 & 1.13 & 8.77 & 697 & -0.17 \\
-\hspace{10pt} External Ancestor & -35.73 & 0.93 & 0.95 & 14.58 & 586 & -0.21 \\
-\hspace{10pt} No Indirect Superclass & -44.89 & 0.84 & 1.18 & 14.08 & 104 & -0.30 \\ \midrule
-\textbf{Grand Total} & \textbf{-53.26} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
-\end{tabular}%
-%}
-\caption{Influence on maintainability of refactoring clones with the specified relation categories.}
-\label{tab:relation_refactor}
-\end{table*}
 

### 2019-08-24 icse/paper.tex
Remove comments

@@
 We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use.
-We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a volume 68 or more tokens improve maintainability when refactored.
+We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored.
 The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the refactored method should not have more than 2 arguments.
-%The relation  %We identified a set of four factors that influence the maintainability impact of clones.
-The first is the size of the clone.
-The second is the relation between the code fragments in a clone.
-The third is whether the clone fragments create, modify or return data.
-The fourth is the amount of data that cloned fragments use.
-By using these four factors, we can suggest only clones that will improve maintainability when refactored and prioritize them accordingly.
-%Given these maintainability influencing factors and their effect on the source code, we measure their impact over a large corpus of open source Java projects.
-%This results in a set of thresholds by which clones can be found that should be refactored to improve system maintainability.
 
@@
 
-%TODO: Hint about results. Hint about methodology.
 We evaluate our approach by comparing the maintainability of before- and after snapshots of a codebase for each duplication problem that is refactored.
@@
 \section{Background}
-Our study lies intersection of code clone and refactoring research. %In this background section, we explain the required background knowledge for terms used throughout this study.
-We use two concepts to argue about code clones \cite{roy2007survey}:
+Our study lies intersection of code clone and refactoring research. We use two concepts to argue about code clones \cite{roy2007survey}:
 \\ \textbf{Clone instance}: A single cloned fragment.
@@
 
-%\subsection{Code clone definitions} Optional -> may do this if it adds something to the story
-%Quick overview of clone type definitions
-
-%\subsection{Refactoring techniques}
-%In this section, we describe refactoring techniques that are relevant to refactoring code clones.
 The most common technique for refactoring clones is ``Extract Method'' \cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
@@
 
-%TODO: Maybe explain something about ASTs, declarations, types, etc.?
-
 \section{Defining refactorable clones}
-% Instead of defining clone types, I just define how we can ensure that clones can be refactored.
-I do not plan to differentiate between T1R, T2R, and T3R here, because I think it makes the paper confusing.
-% To be honest, I'm not even sure how relevant it is to name the literature clone types.
-Maybe not focus on their shortcomings, but just start from the core (source code) and define how we can get to refactorable clones.
 In literature, several clone type definitions have been used to argue about duplication in source code \cite{roy2007survey}.
@@
 \subsection{Ensuring Equality}\label{sec:t1r}
-% Explain type 1, why it is not always refactorable, solution
 Most modern clone detection tools detect duplication by comparing the code textually together with the omission of certain tokens \cite{roy2009comparison, svajlenko2014evaluating}.
@@
 
-% Do we want an example here?
-
 \subsection{Allowing variability in a controlled set of expressions} \label{sec:t2r}
-%Explain type 2, why it is not always refactorable, solution
 Often, duplication fragments in source code do not match exactly \cite{kodhai2013method}.
@@
 \subsection{Gapped clones} \label{sec:t3r}
-%Explain type 3, why it is not always refactorable, solution
 Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context \cite{roy2007survey}.
@@
 \section{The CloneRefactor tool}
-% NEED TO EXPLAIN WHY DO CURRENT DETECTION TOOLS NOT SUFFICE
-% The tool: Detect Clones, Map Context, Refactor.
 To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques \cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
@@
 \subsection{Clone Detection}
-% Detecting refactorable clones, (clone graph?? do I want to explain my exact methods?)
 We use an AST-based method to detect clones.
@@
 \subsubsection{Relation}\label{sec:relation}
-% The rationale for our categories regarding clone relations.
 Clone instances in a clone class may have a relation with each other through inheritance.
@@
 \subsubsection{Location}\label{sec:location}
-% The rationale for our categories regarding clone locations.
 The location of a clone instance determine what refactoring techniques can be applied to refactor such clones. We define the following categories by which we analyze the location of clones:
@@
 \subsubsection{Extract Method} \label{sec:refactorability}
-% Show my categories to show what clones can be dealt with by method extraction.
 Several influencing factors may obstruct the possibility to extract code to a new method:
@@
 \subsubsection{AST Transformation}
-% Explain what AST transformations I do to apply the refactorings.
 CloneRefactor uses JavaParser \cite{tomassetti2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
@@
 \subsection{Clone context}
-% How many clones are there in certain contexts? Experiments for relation, location, and context.
 To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones (see Sec.~\ref{sec:context}).
@@
 \subsection{Refactorability}
-%To what extent can found clones be refactored through method extraction, without requiring additional transformations.
 Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique (see Sec.~\ref{sec:refactorability}).
-%The second column shows our measurements for the complete systems (just like the former experiments).
-%The third column shows our measurements when restricting our search to method bodies.
-The amount that can be extracted increases because, when restricting our search to method bodies, we do not exclude declarations that can obstruct the possibility of method extraction (for instance a cloned method signature).
 
@@
 \subsection{Thresholds}
-%I think the ultimate goal with this thesis is to do experiments with different clone thresholds.
-Which thresholds give clones that we should refactor?
-For this, we will measure the maintainability of the refactored source code over different thresholds.
-These thresholds range from minimum clone size, variability, and gap size.
 In our corpus, CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Sec.~\ref{sec:metrics}).
@@
 \centering
-%\resizebox{\textwidth}{!}{%
 \begin{tabular}{@{}lrrrrrr@{}}
@@
 \textbf{Grand Total} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{-53.26} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
-\end{tabular}%
-%}
+\end{tabular}
 \caption{Average metric values for refactorings of clone classes with the specified return category}

### 2019-08-24 sections/results.tex
Small thesis chnages

@@
 The maintainability score, as shown in Figure \ref{fig:maintainabilityscore}, is the average delta maintainability score of all clone classes with the specified token volume that are refactored.
-As the amount of data points decreases, the datapoints gain less statistical significance, because of which we represent the x-axis as a logaritmic scale.
+For higher token volume numbers we have less refactorings that refactor such clones, because of which we represent the x-axis as a logaritmic scale.
 The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.
@@
 When no value is returned, the maintainability score is the lowest.
-The main reason that no return value ends up lowest, is that it is linked to a higher number of parameters.
+The main reason that no return value ends up lowest, is that it is linked to a higher number of parameters required for the extracted method.
 

### 2019-08-24 icse/paper.tex
Cite

@@
 
-\acmConference[ICSE 2020]{Technical Papers}{May
-23--29}{Seoul, North Korea}
+\acmConference[ICSE 2020]{Technical Papers}{May 23--29}{Seoul, North Korea}
 
@@
 \section{Introduction}
-Duplicate fragments in source code (also named ``code clones'') are often seen as one of the most harmful types of technical debt \cite{fowler2018refactoring}.
-Duplicate fragments create implicit dependencies that make the code harder to maintain as the resolution of erroneous behaviour in one location may have to be applied to all the cloned code as well \cite{ostberg2014automatically}.
+Duplicate fragments in source code (also named ``code clones'') are often seen as one of the most harmful types of technical debt~\cite{fowler2018refactoring}.
+Duplicate fragments create implicit dependencies that make the code harder to maintain as the resolution of erroneous behaviour in one location may have to be applied to all the cloned code as well~\cite{ostberg2014automatically}.
 Apart from that, code clones can contribute up to 25\% of the code size~\cite{bruntink2005use}.
@@
 In this study, we define a technique to detect clones such that they can be automatically refactored.
-We list a set of criteria that can obtruct refactoring opportunities.
+We list a set of criteria that can obstruct refactoring opportunities.
 We evaluate the relation and location of clones to determine which refactoring techniques are best suited.
@@
 \section{Background}
-Our study lies intersection of code clone and refactoring research. We use two concepts to argue about code clones \cite{roy2007survey}:
+Our study lies intersection of code clone and refactoring research. We use two concepts to argue about code clones~\cite{roy2007survey}:
 \\ \textbf{Clone instance}: A single cloned fragment.
@@
 
-The most common technique for refactoring clones is ``Extract Method'' \cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
+The most common technique for refactoring clones is ``Extract Method''~\cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
 This technique moves functionality in method bodies to a new method.
@@
 \section{Defining refactorable clones}
-In literature, several clone type definitions have been used to argue about duplication in source code \cite{roy2007survey}.
+In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}.
 We discuss how we can define clones such that they can be automatically refactored without side effects on the source code.
@@
 \subsection{Ensuring Equality}\label{sec:t1r}
-Most modern clone detection tools detect duplication by comparing the code textually together with the omission of certain tokens \cite{roy2009comparison, svajlenko2014evaluating}.
+Most modern clone detection tools detect duplication by comparing the code textually together with the omission of certain tokens~\cite{roy2009comparison, svajlenko2014evaluating}.
 Clones detected by such means may not always be suitable for refactoring, because textual comparison fails to take into account the context of certain symbols in the code.
@@
 \subsection{Allowing variability in a controlled set of expressions} \label{sec:t2r}
-Often, duplication fragments in source code do not match exactly \cite{kodhai2013method}.
+Often, duplication fragments in source code do not match exactly~\cite{kodhai2013method}.
 When developers duplicate fragments of code, they modify the duplicated block to fit its new location and purpose.
@@
 \end{itemize}
-Often when allowing such variance, trade-offs come into play \cite{krishnan2013refactoring, krishnan2014unification}.
+Often when allowing such variance, trade-offs come into play~\cite{krishnan2013refactoring, krishnan2014unification}.
 For instance, variance in literals may require the introduction of a parameter to an extracted method if the ``Extract Method'' refactoring method is used, increasing the required effort to comprehend the code.
@@
 \subsection{Gapped clones} \label{sec:t3r}
-Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context \cite{roy2007survey}.
-When dealing with such a situation, there are several opportunities to refactor so-called ``gapped clones'' \cite{ueda2002detection, zhao2018automatic}.
+Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context~\cite{roy2007survey}.
+When dealing with such a situation, there are several opportunities to refactor so-called ``gapped clones''~\cite{ueda2002detection, zhao2018automatic}.
 ``Gapped clones'' are two clone instances separated by a ``gap'' of non-cloned statement(s).
@@
   \item We wrap the difference in statements in a conditionally executed block, one path for each different (group of) statement(s).
-  \item We use a lambda function to pass the difference in statements from each location of the clone \cite{tsantalis2017clone}.
+  \item We use a lambda function to pass the difference in statements from each location of the clone~\cite{tsantalis2017clone}.
 \end{itemize}
@@
 \section{The CloneRefactor tool}
-To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques \cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
+To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
 We created a set of control projects\footnote{Control projects for assessing clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
 
-None of the surveyed tools \cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we decided to implement our own tool: CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
+None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we decided to implement our own tool: CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
 This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
@@
 Clone instances in a clone class may have a relation with each other through inheritance.
-This relation has a big impact on how the clone should be refactored \cite{fontana2015duplicated}.
+This relation has a big impact on how the clone should be refactored~\cite{fontana2015duplicated}.
 We define the following categories to map the relation between clone instances in a clone class.
@@
 \subsubsection{AST Transformation}
-CloneRefactor uses JavaParser \cite{tomassetti2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
+CloneRefactor uses JavaParser~\cite{tomassetti2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
 To refactor clones, CloneRefactor creates a new method declaration and moves all statements from a clone instance in the clone class to the new method.
@@
 CloneRefactor measures the impact on maintainability metrics of the refactored source code for each clone class that is refactored.
-These metrics are derived from Heitlager et al.
-\cite{heitlager2007practical}.
+These metrics are derived from Heitlager et al.~\cite{heitlager2007practical}.
 This paper defines a set of metrics to measure the maintainability of a system.
@@
 To determine whether the maintainability improves when refactoring a single clone, we need to measure the impact of small-grained changes.
-Because of that, we measure only a subset of the metrics \cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
+Because of that, we measure only a subset of the metrics~\cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
 The subset of metrics we decided to focus on are all metrics that are measured on method level (as the other metrics show a lesser impact on the maintainability for these small changes).
@@
 \begin{itemize}
-\item \textbf{Duplication}: In Heitlager et al.
-\cite{heitlager2007practical} this metric is measured by taking the amount of duplicated lines.
+\item \textbf{Duplication}: In Heitlager et al.~\cite{heitlager2007practical} this metric is measured by taking the amount of duplicated lines.
 We decided to use the amount of duplicated tokens part of a clone class instead, to have a stronger reflection of the impact of the refactoring by measuring a more fine-grained system property.
 \item \textbf{Volume}: The more code a system has, the more code has to be maintained.
-The paper \cite{heitlager2007practical} measures volume as lines of code.
+The paper~\cite{heitlager2007practical} measures volume as lines of code.
 As with duplication, we use the number of tokens instead.
-\item \textbf{Complexity}: Heitlager et al.
-use MCCabe complexity \cite{mccabe1976complexity} to calculate their complexity metric.
+\item \textbf{Complexity}: Heitlager et al.~\cite{heitlager2007practical} use MCCabe complexity~\cite{mccabe1976complexity} to calculate their complexity metric.
 The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.
 \item \textbf{Method Interface Size}: The number of parameters that a method has.
-If a method has many parameters, the code may become harder to understand and it is an indication that data is not encapsulated adequately in objects \cite{fowler2018refactoring}.
+If a method has many parameters, the code may become harder to understand and it is an indication that data is not encapsulated adequately in objects~\cite{fowler2018refactoring}.
 \end{itemize}
@@
 We ran all our experiments using CloneRefactor on a corpus of open source Java projects.
-This corpus is derived from the corpus of a study that uses machine learning to determine the suitability of Java projects on GitHub for data analysis purposes \cite{githubCorpus2013}.
+This corpus is derived from the corpus of a study that uses machine learning to determine the suitability of Java projects on GitHub for data analysis purposes~\cite{githubCorpus2013}.
 
@@
 These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones.
-Often, such thresholds are intuitively chosen \cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data \cite{alves2010deriving}.
+Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}.
 Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.

### 2019-08-24 icse/paper.tex
Related work

@@
 This technique extracts the contents of a single clone instance to a new method and replace all clone instances in a clone class by a call to this method.
+
+\section{Related Work}
+The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
+The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems.
+This tool is based on several studies that look into different aspects of code clone refactoring.
+In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how does variability between cloned fragments influence the refactoring techniques required and their implications on system design.
+Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability.
+This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.
+In a recent study Tsantalis et al.~\cite{tsantalis2017clone} look into how lambda's can provide help in the clone refactoring process.
+
+In their work, the main focus is to find out which clones \textbf{can} be refactored.
+We extend this work by looking at what clones we \textbf{should} refactor.
+We propose definitions for refactorable clones together with thresholds to be able to limit their impact negative on system design.
+We measure which clones improve maintainability when refactored.
+This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
 

### 2019-08-24 icse/paper.tex
A bit of introduction

@@
 We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored.
-The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the refactored method should not have more than 2 arguments.
+The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones with more than requiring more than one external parameter decreases maintainability.
 
@@
 We evaluate our approach by comparing the maintainability of before- and after snapshots of a codebase for each duplication problem that is refactored.
-This gives us insight into whether clones detected by certain thresholds should be refactored to improve the maintainability of the codebase.
+We define which factors have the greatest influence on whether a clone improves maintainability when refactored.
+We find a set of thresholds by which clones can be detected that are more likely to improve maintainability when refactored.
 This allows for more accurate suggestion of code clones for refactoring and can provide assistance in the refactoring process.

### 2019-08-24 icse/paper.tex
Spelling

@@
 Duplicate fragments in source code (also named ``code clones'') are often seen as one of the most harmful types of technical debt~\cite{fowler2018refactoring}.
-Duplicate fragments create implicit dependencies that make the code harder to maintain as the resolution of erroneous behaviour in one location may have to be applied to all the cloned code as well~\cite{ostberg2014automatically}.
+Duplicate fragments create implicit dependencies that make the code harder to maintain as the resolution of erroneous behavior in one location may have to be applied to all the cloned code as well~\cite{ostberg2014automatically}.
 Apart from that, code clones can contribute up to 25\% of the code size~\cite{bruntink2005use}.
@@
 We find a set of thresholds by which clones can be detected that are more likely to improve maintainability when refactored.
-This allows for more accurate suggestion of code clones for refactoring and can provide assistance in the refactoring process.
+This allows for more a accurate suggestion of code clones for refactoring and can assist in the refactoring process.
 
 \section{Background}
-Our study lies intersection of code clone and refactoring research. We use two concepts to argue about code clones~\cite{roy2007survey}:
+Our study lies at the intersection of code clone and refactoring research. We use two concepts to argue about code clones~\cite{roy2007survey}:
 \\ \textbf{Clone instance}: A single cloned fragment.
@@
 The most common technique for refactoring clones is ``Extract Method''~\cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
-This technique moves functionality in method bodies to a new method.
-This technique extracts the contents of a single clone instance to a new method and replace all clone instances in a clone class by a call to this method.
+Applying this technique entails moving functionality in the body of a method to a new method.
+To reduce duplication with this technique, we extract the contents of a single clone instance to a new method and replace all clone instances in a clone class by a call to this method.
 
@@
 This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.
-In a recent study Tsantalis et al.~\cite{tsantalis2017clone} look into how lambda's can provide help in the clone refactoring process.
+In a recent study, Tsantalis et al.~\cite{tsantalis2017clone} look into how lambda's can provide help in the clone refactoring process.
 
@@
 \end{itemize}
-For both refactoring techniques a trade-off is at play, as these solutions increase the complexity and volume of the source code in favor of removing a clone.
+For both refactoring techniques, a trade-off is at play. This is because these solutions increase the complexity and volume of the source code in favor of removing a clone.
 
@@
 
-None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we decided to implement our own tool: CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
+None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we decided to implement a tool: CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
 This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
@@
     \begin{itemize}
-        \item \textbf{Same Direct Interface}: All clone instances are in a class that have the same interface.
+        \item \textbf{Same Direct Interface}: All clone instances are in classes that have the same interface.
         \item \textbf{Same Class}: All clone instances are in an inheritance hierarchy that contains the same interface.
@@
     \begin{itemize}
-        \item \textbf{No Direct Superclass}: All clone instances are in classes that have the Object class as parent.
-        \item \textbf{No Indirect Superclass}: All clone instances are in a hierarchy that contains a class that has the Object class as parent.
-        \item \textbf{External Superclass}: All clone instances are in classes the same external class as parent.
-        \item \textbf{Indirect External Ancestor}: All clone instances are in a hierarchy that contains a class that has an external class as parent.
+        \item \textbf{No Direct Superclass}: All clone instances are in classes that have the Object class as their parent.
+        \item \textbf{No Indirect Superclass}: All clone instances are in a hierarchy that contains a class that has the Object class as their parent.
+        \item \textbf{External Superclass}: All clone instances are in classes the same external class as their parent.
+        \item \textbf{Indirect External Ancestor}: All clone instances are in a hierarchy that contains a class that has an external class as their parent.
     \end{itemize}
@@
 Based on these relations, CloneRefactor determines where to place the cloned code when refactored.
-These categories are mutually exclusive: a clone class will be flagged as the first relation in above list that it applies to.
+These categories are mutually exclusive: a clone class will be flagged as the first relation in the above list that it applies to.
 The code of clones that have a \textit{Common Class} relation can be refactored by placing the cloned code in this same class.
@@
 \subsubsection{Location}\label{sec:location}
-The location of a clone instance determine what refactoring techniques can be applied to refactor such clones. We define the following categories by which we analyze the location of clones:
+The location of a clone instance determines what refactoring techniques can be applied to refactor such clones. We define the following categories by which we analyze the location of clones:
 \begin{enumerate}
@@
 First, we created a set of 57 control projects to verify the correctness in many (edge) cases.
-These projects contain clones for each identified relation, location and refactorability category to see whether they get correctly identified.
+These projects contain clones for each identified relation, location, and refactorability category to see whether they get correctly identified.
 Next, we run the tool over the corpus and manually verify samples of the acquired results.
-This way, we check both the correctness of the identified clones, their context and their proposed refactoring.
+This way, we check both the correctness of the identified clones, their context, and their proposed refactoring.
 
@@
   \item Higher values for the metrics imply lower maintainability.
-  \item Normalizing each obtained metric delta over all deltas obtained for a metric in our dataset results in equally weighted scores.
+  \item Normalizing each obtained metric delta over all deltas obtained for that metric in our dataset results in equally weighted scores.
 \end{itemize}
@@
 Where $\Delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metric.
-This method works well for normalization of our data, because as we divide by the standard deviation, outliers do not influence the resulting scores negatively.
+This method works well for normalization of our data because as we divide by the standard deviation, outliers do not influence the resulting scores negatively.
 
@@
 
-From these results we see that 74\% of clones span part of a method body (77\% if we include constructors).
+From these results, we see that 74\% of clones span part of a method body (77\% if we include constructors).
 8\% of clones span several methods.
@@
 We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class.
-For higher token volume numbers we have less refactorings that refactor such clones, because of which we represent the x-axis as a logaritmic scale.
+For higher token volume numbers we have fewer refactorings that refactor such clones, because of which we represent the x-axis as a logarithmic scale.
 The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.
@@
 Overall, the scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability.
-When the result of the call to the extracted method is directly returns, the maintainability score is the highest.
+When the result of the call to the extracted method is directly returned, the maintainability score is the highest.
 When no value is returned, the maintainability score is the lowest.
@@
 Many clones (23\%) do not have a statement as top-level AST-Node.
-Upon manual inspection, we noticed that the main reason for this is clones in anonymous functions or anonymous classes.
+Upon manual inspection, we noticed that the main reason for this is when clones are found in lambda functions or anonymous classes.
 About 15\% of clones span only part of an AST-Node.
@@
 Not only the number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
-Because of that, we see that trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.
+Because of that, we see that the trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.
 

### 2019-08-24 icse/paper.tex
Updates from Overleaf
JavaParser diff ref

@@
 The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones with more than requiring more than one external parameter decreases maintainability.
-
 \end{abstract}
@@
 \subsubsection{AST Transformation}
-CloneRefactor uses JavaParser~\cite{tomassetti2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
+CloneRefactor uses JavaParser~\cite{smith2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
 To refactor clones, CloneRefactor creates a new method declaration and moves all statements from a clone instance in the clone class to the new method.

### 2019-08-24 icse/paper.tex
Ana

--- 2019-08-24 icse/paper.tex
@@
 In their work, the main focus is to find out which clones \textbf{can} be refactored.
-We extend this work by looking at what clones we \textbf{should} refactor.
-We propose definitions for refactorable clones together with thresholds to be able to limit their impact negative on system design.
+We extend this work by looking into which clones \textbf{should} be refactored.
+We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design.
 We measure which clones improve maintainability when refactored.
@@
 \section{Discussion}
-In this section, we discuss the results of our experiments.
+%In this section, we discuss the results of our experiments.
 
@@
 We defined two aspects as part of the context of a clone: relation and location.
-Regarding relations, we found that most clones are found in the same class, over 37\%.
+Regarding relations, over 37\% of clones are found in the same class.
 About 24\% of clones are in the same inheritance hierarchy.
 Another 24\% of clones are unrelated.
-The final 7\% of clones have the same interface.
+The final 15\% of clones have the same interface.
 Regarding location, over 74\% of clones span part of a method.
@@
 
-We built a tool that can automatically apply refactorings to 28\% of clones in our corpus using the ``Extract Method'' refactoring technique.
-The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, for instance when code outside a method is part of a clone.
+We built a tool that can automatically apply refactorings to 28\% of the clones in our corpus using the ``Extract Method'' refactoring technique.
+The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, e.g., when code outside a method is part of a clone.
 

### 2019-08-24 icse/paper.tex
Code example

--- 2019-08-24 icse/paper.tex
@@
 \usepackage{multirow}
+\usepackage{parcolumns}
+
+\definecolor{pblue}{rgb}{0.13,0.13,1}
+\definecolor{pgreen}{rgb}{0,0.5,0}
+\definecolor{pred}{rgb}{0.9,0,0}
+\definecolor{pgrey}{rgb}{0.46,0.45,0.48}
+
+\usepackage{listings}
+\lstset{language=Java,
+  showspaces=false,
+  showtabs=false,
+  breaklines=true,
+  showstringspaces=false,
+  breakatwhitespace=true,
+  commentstyle=\color{pgreen},
+  keywordstyle=\color{pblue},
+  numbers = left,
+  stringstyle=\color{pred},
+  basicstyle=\ttfamily,
+  moredelim=[il][\textcolor{pgrey}]{$$},
+  moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%}
+}
+
+\definecolor{lightyellow}{HTML}{fffdcc}
+\definecolor{doublelightyellow}{HTML}{fffa9c}
+\definecolor{lightgreen}{HTML}{dcffd4}
+\definecolor{lightblue}{HTML}{e0ffff}
+\definecolor{lightred}{HTML}{ffe0e0}
+\definecolor{lightpink}{HTML}{ffe0ff}
+\definecolor{lightorange}{HTML}{ffede0}
+\definecolor{lightpurple}{HTML}{f0e0ff}
+\newcommand{\highlightYellow}{\makebox[0pt][l]{\color{lightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightGreen}{\makebox[0pt][l]{\color{lightgreen}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightBlue}{\makebox[0pt][l]{\color{lightblue}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightRed}{\makebox[0pt][l]{\color{lightred}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightPink}{\makebox[0pt][l]{\color{lightpink}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightOrange}{\makebox[0pt][l]{\color{lightorange}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightPurple}{\makebox[0pt][l]{\color{lightpurple}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightDarkyellow}{\makebox[0pt][l]{\color{doublelightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
+
+\lstnewenvironment{javacode}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small,#1}}{}
 
@@
 
+\begin{figure*}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+package com.sb.game;
+
+import java.util.List;
+
+public class GameScene
+{
+|\highlightYellow|	public void addToList(List l) {
+|\highlightYellow|		l.add(getClass().getName());
+|\highlightYellow|	}
+
+	public void addTen(int x) {
+|\highlightYellow|		x = x + 10; // Addition
+|\highlightYellow|		Notifier.notifyChanged(x);
+|\highlightYellow|		return x;
+	}
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+package com.sb.fruitgame;
+
+import java.awt.List; // Different type
+
+public class LoseScene
+{
+|\highlightYellow|	public void addToList(List l) {
+|\highlightYellow|		l.add(getClass().getName());
+|\highlightYellow|	}
+
+	public void concatTen(String x) {
+|\highlightYellow|		x = x + 10; // String concat
+|\highlightYellow|		Notifier.notifyChanged(x);
+|\highlightYellow|		return x;
+	}
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Example of textually equal code fragments that differ in functionality.}
+\label{fig:type1}
+\end{figure*}
+
 \subsection{Ensuring Equality}\label{sec:t1r}
@@
 Information that gets lost in textual comparison is the referenced declaration for type, variable and method references.
-Equally named type, variable and method references may refer to different declarations with a different implementation.
+Equally named type, variable and method references may refer to different declarations with a different implementation (Fig~\ref{fig:type1} shows an example of this).
 Such clones can be harder to refactor, if beneficial at all.
@@
 In case of a return value, CloneRefactor either assigns the call result, declares it or returns it accordingly.
-
-We verified the correctness of the resulting refactorings manually. We ran the tool over a large software project and verified over 1.000 applied refactorings.
 

### 2019-08-24 icse/paper.tex
Oops
Ana

@@
 
-\acmConference[ICSE 2020]{Technical Papers}{May 23--29}{Seoul, North Korea}
+\acmConference[ICSE 2020]{Technical Papers}{May 23--29}{Seoul, South Korea}
 
@@
 \affiliation{\institution{University of Amsterdam}}
-\email{ana.oprescu@uva.nl}
+\email{a.m.oprescu@uva.nl}
 
@@
 We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system.
-Based on these results, one could decide which clones improve system design and thus should be refactored.
+Based on these results, one could decide which clones improve system design when refactored.
 We evaluate our approach over a large corpus of open source Java projects.

### 2019-08-24 icse/paper.tex
Ana

@@
 
-\acmConference[ICSE 2020]{Technical Papers}{May 23--29}{Seoul, South Korea}
+\acmConference[ICSE 2020]{Technical Papers}{}{}
 
@@
 
-\author{Simon Baars}
-\affiliation{\institution{University of Amsterdam}}
-\email{simon.mailadres@gmail.com}
+%\author{Simon Baars}
+%\affiliation{\institution{University of Amsterdam}}
+%\email{simon.mailadres@gmail.com}
 
-\author{Ana Oprescu}
-\affiliation{\institution{University of Amsterdam}}
-\email{a.m.oprescu@uva.nl}
+%\author{Ana Oprescu}
+%\affiliation{\institution{University of Amsterdam}}
+%\email{a.m.oprescu@uva.nl}
 
@@
 We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system.
-Based on these results, one could decide which clones improve system design when refactored.
+Based on these results, one could decide which clones would improve system design if refactored.
 We evaluate our approach over a large corpus of open source Java projects.
@@
 This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.
-In a recent study, Tsantalis et al.~\cite{tsantalis2017clone} look into how lambda's can provide help in the clone refactoring process.
 
-In their work, the main focus is to find out which clones \textbf{can} be refactored.
+A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process.
+The main focus is to find out which clones \textbf{can} be refactored.
 We extend this work by looking into which clones \textbf{should} be refactored.
@@
 
-To detect clones that can be automatically refactored, we propose to:
+To detect automatically refactorable clones, we propose to:
 \begin{itemize}

### 2019-08-24 icse/paper.tex
Stuff

@@
 This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.
+In a recent study, Tsantalis et al.~\cite{tsantalis2017clone} look into how lambda's can provide help in the clone refactoring process.
 
-A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process.
-The main focus is to find out which clones \textbf{can} be refactored.
+In their work, the main focus is to find out which clones \textbf{can} be refactored.
 We extend this work by looking into which clones \textbf{should} be refactored.
@@
 \end{figure*}
+
+\section{Related Work}
+The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
+The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems.
+This tool is based on several studies that look into different aspects of code clone refactoring.
+In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how does variability between cloned fragments influence the refactoring techniques required and their implications on system design.
+Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability.
+This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.
+In a recent study, Tsantalis et al.~\cite{tsantalis2017clone} look into how lambda's can provide help in the clone refactoring process.
+
+In their work, the main focus is to find out which clones \textbf{can} be refactored.
+We extend this work by looking into which clones \textbf{should} be refactored.
+We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design.
+We measure which clones improve maintainability when refactored.
+This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
+
+\section{Defining refactorable clones}
+In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}.
+We discuss how we can define clones such that they can be automatically refactored without side effects on the source code.
 
@@
 
+\begin{figure*}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+|\highlightYellow|int a = getA();
+|\highlightYellow|while(a<1000) {
+|\highlightYellow|  a *= 5;
+  doC();
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+|\highlightYellow|int a = getA();
+|\highlightYellow|while(a<1000) {
+|\highlightYellow|  a *= 5;
+  doB(a);
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{A clone that spans a block partially.}
+\label{fig:refactorabilitypartialblock}
+\end{figure*}
+
 \subsection{Context Mapping} \label{sec:context}
@@
     \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
-    \item \textbf{Spans Part Of A Block}: This clone spans a part of a block statement.
+    \item \textbf{Spans Part Of A Block}: This clone spans a part of a block statement. An example of this is shown in Fig.~\ref{fig:refactorabilitypartialblock}.
     \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Sec.~\ref{sec:location}, the ``Extract Method'' refactoring technique cannot be applied.

### 2019-08-24 icse/paper.tex
Fixed merge problems

@@
 
-\section{Related Work}
-The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
-The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems.
-This tool is based on several studies that look into different aspects of code clone refactoring.
-In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how does variability between cloned fragments influence the refactoring techniques required and their implications on system design.
-Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability.
-This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.
-In a recent study, Tsantalis et al.~\cite{tsantalis2017clone} look into how lambda's can provide help in the clone refactoring process.
-
-In their work, the main focus is to find out which clones \textbf{can} be refactored.
-We extend this work by looking into which clones \textbf{should} be refactored.
-We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design.
-We measure which clones improve maintainability when refactored.
-This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
-
-\section{Defining refactorable clones}
-In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}.
-We discuss how we can define clones such that they can be automatically refactored without side effects on the source code.
-
 \begin{figure*}

### 2019-08-24 icse/paper.tex
I like this tho
Uh oops

@@
   basicstyle=\ttfamily,
-  moredelim=[il][\textcolor{pgrey}]{$$},
+  moredelim=[il][\textcolor{pgrey}]{\$\$},
   moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%}
@@
 
-\acmConference[ICSE 2020]{Technical Papers}{}{}
+\acmConference[ICSE 2020]{Technical Papers}{May 23--29}{Seoul, South Korea}
 
@@
 In Fig.~\ref{fig:maintainabilityscore} we see an increase in maintainability for refactoring larger clone classes.
-The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie around 28 tokens.
+The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie around a token volume of 63 tokens.
 There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.

### 2019-08-24 icse/paper.tex
Working on CloneRefactor part

@@
 
-None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we decided to implement a tool: CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
+None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
 This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.

### 2019-08-24 sections/clonerefactor.tex
Working on CloneRefactor part

@@
 This tool, named CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}, performs a comprehensive context analysis on the detected clones.
-Based on this this context, CloneRefactor can automatically refactor a subset of the detected clones by applying transformations to the source code of the analyzed software project(s).
-
-In this section we describe our approach and rationale for the design decisions regarding this tool.
+Based on this context, CloneRefactor can automatically refactor a subset of the detected clones by applying transformations to the source code of the analyzed software project(s).
+In this section, we describe our approach and rationale for the design decisions regarding this tool.
 
@@
 Figure \ref{fig:clonerefactorprocess} shows the overall process used by CloneRefactor.
-First, we detect clones on the basis of a Java codebase, given a Java project from disk and a configuration.
+First, we detect clones based on a Java codebase, given a Java project from disk and a configuration.
 The clone detection process is further explained in Section~\ref{sec:clonedetection}.
-After all clones are found, CloneRefactor maps the context of the clones.
-On the basis of this context, CloneRefactor applies transformations to the source code for clones for which we have configured a refactoring.
+When all clones are found, CloneRefactor maps the context of the clones.
+Based on this context, CloneRefactor applies transformations to the source code for clones that are found to be refactorable.
 
@@
 An important design decision for CloneRefactor is the usage of a library named JavaParser \cite{tomassetti2017javaparser}.
-JavaParser is a Java library which allows to parse Java source files to an abstract syntax tree (AST\footnote{An AST is a tree-representation of a source code file.}).
+JavaParser is a Java library which allows parsing Java source files to an abstract syntax tree (AST\footnote{An AST is a tree representation of a source code file.}).
 JavaParser allows to modify this AST and write the result back to Java source code.
@@
 
-Integrated in JavaParser is a library named SymbolSolver.
+Integrated into JavaParser is a library named SymbolSolver.
 This library allows for the resolution of symbols using JavaParser.
@@
 
-In order to be able to trace referenced identifiers SymbolSolver requires access to not only the analyzed Java projects, but also all its dependencies.
+To be able to trace referenced identifiers, SymbolSolver requires access to not only the analyzed Java project but also all its dependencies.
 This requires us to include all dependencies with the project.
@@
 \begin{itemize}
-  \item \textbf{Minimum Number of Nodes}: The minimum amount of nodes that should be in each instance of cloned fragements for them to be considered a clone class.
-  \item \textbf{Minimum Number of Tokens}: The minimum amount of tokens that should be in each instance of cloned fragements for them to be considered a clone class.
-  \item \textbf{Minimum Number of Lines}: The minimum amount of lines that should be in each instance of cloned fragements for them to be considered a clone class.
+  \item \textbf{Minimum Number of Nodes}: The minimum amount of nodes that should be in each instance of cloned fragments for them to be considered a clone class.
+  \item \textbf{Minimum Number of Tokens}: The minimum amount of tokens that should be in each instance of cloned fragments for them to be considered a clone class.
+  \item \textbf{Minimum Number of Lines}: The minimum amount of lines that should be in each instance of cloned fragments for them to be considered a clone class.
 \end{itemize}
@@
 \section{Clone Detection}\label{sec:clonedetection}
-To detect clones, CloneRefactor parses the AST aqcuired from JavaParser to an unweighted graph structure.
-On the basis of this graph structure, clones are detected.
+To detect clones, CloneRefactor parses the AST acquired from JavaParser to an unweighted graph structure.
+Based on this graph structure, clones are detected.
 Dependent on the type of clones being detected, transformations may be applied.
-The way in which CloneRefactor was designed does not allow for several clone types to be detected simultaneously.
+How CloneRefactor was designed does not allow for several clone types to be detected simultaneously.
 The overall process regarding clone detection is displayed in Figure~\ref{fig:clonedetection}.
@@
 Each AST is then converted to a directed graph that maps relations between statements, further explained in Section~\ref{sec:clonegraph}.
-On the basis of this graph, we detect clone classes and verify them the configured thresholds.
-If the detection was configured to detect either type 2R, 3 or 3R clones we perform some type specific transformations on the resulting set of clones.
+Based on this graph, we detect clone classes and verify them the configured thresholds.
+If the detection was configured to detect either type 2R, 3 or 3R clones we perform some type-specific transformations on the resulting set of clones.
 %\begin{itemize}
@@
 
-The relations \textit{next} and \textit{previous} in this graph are represented as an twodirectional arrow.
+The relations \textit{next} and \textit{previous} in this graph are represented as a bidirectional arrow.
 The relations representing duplication are directed.
@@
 \subsubsection{Comparing Statements/Declarations} \label{sec:comparingstuff}
-In the previous section we described a ``duplicate'' relation between nodes in the clone graph built by CloneRefactor.
+In the previous section, we described a ``duplicate'' relation between nodes in the clone graph built by CloneRefactor.
 Whether two nodes in this graph are duplicates of each other is dependent on the clone type.
@@
 
-CloneRefactor detects six different types of clones: T1, T2, T3, T1R, T2R and T3R.
+CloneRefactor detects six different types of clones: T1, T2, T3, T1R, T2R, and T3R.
 These types are further explained in chapter \ref{chap:clonetypes}.
-For \textbf{type 1} clones, CloneRefactor filters the tokens of a node to exclude its comments, whitespace and end of line (EOL) characters and then compares these tokens.
+For \textbf{type 1} clones, CloneRefactor filters the tokens of a node to exclude its comments, whitespace, and end of line (EOL) characters and then compares these tokens.
 For \textbf{type 2} clones, the tokens are further filtered to omit all identifiers and literals.
@@
 If the variable type is a primitive we can directly use it for comparison.
-If it is a referenced type, we have to trace this type first in order to collect their fully qualified identifier for comparison.
-
-\textbf{Type 2R} clones allow any variation in literals, variables and method calls at this stage in the clone detection process.
-However, for \textit{literals} we do resolve their type in order to verify that they are of the same type.
+If it is a referenced type, we have to trace this type first to collect their fully qualified identifier for comparison.
+
+\textbf{Type 2R} clones allow any variation in literals, variables, and method calls at this stage in the clone detection process.
+However, for \textit{literals} we do resolve their type to verify that they are of the same type.
 For \textit{variables} we also only verify that their types are the same (but not their names).
@@
 \subsubsection{Mapping graph nodes to code}
-The clone graph, as explained in Section~\ref{sec:buildingclonegraph}, contains all declarations and statements in a source code.
+The clone graph, as explained in Section~\ref{sec:buildingclonegraph}, contains all declarations and statements of a software project.
 However, declarations and statements may themselves have child declarations and statements.
@@
 
-In line 24-25 of the code fragment, we see a \texttt{MethodDeclaration}.
+On line 24-25 of the code fragment, we see a \texttt{MethodDeclaration}.
 The node corresponding with this MethodDeclaration denotes all tokens found on these two lines, line 24 and 25.
@@
 \subsection{Detecting Clones} \label{sec:detectingclones}
-After building the clone clone graph, we use it to detect clone classes.
-Because nodes in the clone graph link to \textit{preceding} cloned statement, the first cloned node does not have any clone relation, as there are no clones preceding it (only following it).
+After building the clone graph, we use it to detect clone classes.
+Because nodes in the clone graph link to \textit{preceding} cloned statement, the first cloned node does not have any clone relation, as no clones are preceding it (only following it).
 Because of this, we start our clone detection process at the final location encountered while building the graph.
@@
 When we are at that point, we will find only one cloned node for (2), namely (3).
-However, after we check this clone against the thresholds, we check whether it is a subset of any exisiting clone.
+However, after we check this clone against the thresholds, we check whether it is a subset of any existing clone.
 If this is the case (which it is for this example), we discard the clone.
@@
 \subsection{Validating the type 2R variability threshold}
-In the definition of type 2R clones (see Section~\ref{sec:type2r}) we described how type 2R clones work on the basis of a variability threshold.
+In the definition of type 2R clones (see Section~\ref{sec:type2r}) we described how type 2R clones work based on a variability threshold.
 This threshold is checked by CloneRefactor to assess the validity of found clone classes.
 Implementing such a threshold involves some important design decisions and has a lot of complexity.
-In this section we explain how CloneRefactor detects type 2R clones on the basis of this variability threshold.
+In this section, we explain how CloneRefactor detects type 2R clones based on this variability threshold.
 This process is done as a postprocessing step after clone detection.
@@
 \subsubsection{Create equality array}
-To determine the difference in literals, method calls and variables, we convert the code to an equality array.
-This equality array converts each (group of) token(s) to a number unique to that (group of) tokens.
-Each literal, method call or variable becomes a positive number, whereas each other token becomes a negative number.
+To determine the difference in literals, method calls, and variables, we convert the code to an equality array.
+This equality array converts each expression to a number unique to that expression.
+Each literal, method call or variable becomes a positive number, whereas each other expression becomes a negative number.
 An example of two code fragments converted to equality arrays is displayed in Figure~\ref{fig:equalityarrays}.
@@
 
-The first line of the cloned fragment shown in Figure~\ref{fig:2rvariabilityhigh1} has a high variability with its cloned fragement.
+The first line of the cloned fragment shown in Figure~\ref{fig:2rvariabilityhigh1} has a high variability with its cloned fragment.
 However, the rest of this method does not have any variability.
@@
 \subsubsection{Convert Equality Array to Graph}
-After the global threshold check has failed, we build a clone graph on the basis of the equality arrays.
+After the global threshold check has failed, we build a clone graph based on the equality arrays.
 The process used for building this graph is the same as the process described in \ref{sec:buildingclonegraph}.
@@
 \subsubsection{Detect Clones on Graph}
-Similar to the clone detection process, we detect clones on the basis of the graph described in the previous section.
+Similar to the clone detection process, we detect clones based on the graph described in the previous section.
 The only difference is that, in this step, we do not remove clones that do not meet the thresholds (as explained in Section~\ref{sec:clonerefactorthresholds}).
@@
 In this example, we see the four clones found on the graph of Figure~\ref{fig:clonerefactorprocess}.
-Three of these clone classes have a two clone instances, each consisting of a single nodes.
+Three of these clone classes have two clone instances, each consisting of a single node.
 The other clone class has three clone instances, each consisting of two nodes.
@@
 
-As an example, consider the clone fragment in Figure~\ref{fig:trytoexpand}.
+As an example, consider the cloned fragments in Figure~\ref{fig:trytoexpand}.
 In this example, we have 2 clone classes.
-In the ``Try To Expand'' step, we will check whether we can create a clone class with larger clone instances on the basis of the clones found in the previous step.
+In the ``Try To Expand'' step, we will check whether we can create a clone class with larger clone instances based on the clones found in the previous step.
 We start with the largest clone class, measured in clone volume.
-We measure clone volume as the product of the amount of clone instances in a clone class and the amount of nodes in any of its instances.
+We measure clone volume as the product of the number of clone instances in a clone class and the number of nodes in any of its instances.
 
@@
 
-\subsubsection{Type 3R Example}
-In this section we show an example of the identification of a type 3R clone.
+\subsubsection{Type 3R Indentification Example}
+In this section, we show an example of the identification of a type 3R clone.
 
@@
   \item \textbf{Same Class}: All instances of the clone class are in the same class.
-  \item \textbf{Superclass}: All instances of the clone class are in a class that is child or parent of each other.
+  \item \textbf{Superclass}: All instances of the clone class are in a class that are child or parent of each other.
   \item \textbf{Sibling Class}: All instances of the clone class have the same parent class.
@@
 
-Figure \ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
-The relation of clones through inheritance is measured on clone class level: it involves all child clone instances.
-The location and contents of clones is measured on clone instance level.
-A clone's location involves the file it resides in and the range it spans (for example: line 6 col 2 - line 7 col 50).
-A clone instance contents consists of a list of all statements and declarations it spans.
-
 \begin{figure}[H]
@@
 
-Every clone class only has a single relation, which is the first relation from above list that the clone class applies to.
+Every clone class only has a single relation, which is the first relation from the above list that the clone class applies to.
 For instance: all ``Superclass'' clones also apply to ``Same Hierarchy'', but because ``Superclass'' is earlier in above list they will get the ``Superclass'' relation.
@@
 \colchunk[2]{
-\begin{javacode}
 \begin{javacode}

### 2019-08-24 main.tex
Experimental setup
Stuff
T3R. CloneRefactor + Image
Various improvements

@@
 \usepackage{longtable}
-\usepackage[backend=bibtex, style=ieee,citestyle=numeric-comp]{biblatex}
+\usepackage[style=ieee,citestyle=numeric-comp]{biblatex}
 \usepackage[colorinlistoftodos, prependcaption]{todonotes}
@@
 \usepackage{titlesec}
-\usepackage{listings}
 \usepackage{parcolumns}
@@
 \usepackage{inconsolata}
+\usepackage{longtable}
 
@@
 
-\setcounter{secnumdepth}{4}
+\setcounter{secnumdepth}{3}
 
@@
 	\begin{center}
-		{\Huge\bfseries Towards Automatic Improvement of Software Maintainability through Automated Refactoring of Code Clones \par}
+		{\Huge\bfseries Improving Software Maintainability through Automated Refactoring of Code Clones \par}
 		% Earlier versions:
 		% Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages
+    % Towards Automated Improvement of Software Maintainability through Automated Refactoring of Code Clones
 		\vspace{44pt}
@@
 \input{sections/clonerefactor}
+\input{sections/experimentalsetup}
 \input{sections/results}

### 2019-08-24 sections/clonerefactor.tex

@@
 Every clone class only has a single relation, which is the first relation from the above list that the clone class applies to.
-For instance: all ``Superclass'' clones also apply to ``Same Hierarchy'', but because ``Superclass'' is earlier in above list they will get the ``Superclass'' relation.
+For instance: all ``Superclass'' clones also apply to ``Same Hierarchy'', but because ``Superclass'' is earlier in the list they will get the ``Superclass'' relation.
 This is because the items earlier in the list denote a more favorable refactoring.
 
-To check a the relation for a given clone class, we compare each node in a clone instance with the respective nodes in each other clone instance within a clone class.
+To determine the relation for a given clone class, we compare each node in a clone instance with the respective nodes in each other clone instance within a clone class.
 So for a clone class with x clone instances and each clone instance has y nodes, we perform:
@@
 Cloned nodes are flagged as \textit{Same method} if these nodes are found in the same method.
-We define the method as the first method declaration that is encountered when following the parent nodes in the ast for a given cloned node.
+We define the method as the first method declaration that is encountered when following the parent nodes in the AST for a given cloned node.
 Please note that a clone instance may not always be in a method, for which this predicate will fail.
@@
 Cloned nodes are flagged as \textit{Same class} if these nodes are found in the same class.
-We define the class as the first class declaration that is encountered when following the parent nodes in the ast for a given cloned node.
+We define the class as the first class declaration that is encountered when following the parent nodes in the AST for a given cloned node.
 
@@
 The greatest downside on system design of putting functionality in interfaces is that interfaces are per definition part of a classes' public contract.
-That is, all functionality that is shared between classes via an interface cannot be hidden by setting a stricter visibility.
+That is, all functionality that is shared between classes via an interface cannot be hidden by stricter visibility.
 Because of that, we favor all ``Common Hierarchy'' refactoring opportunities over ``Common Interface''.
@@
 Clones are unrelated if they share no common class or interface in their inheritance structure.
-These clones are least favorable when looking at refactoring, because their refactoring will almost always have a major impact on system design.
+These clones are least favorable for refactoring, because their refactoring will almost always have a major impact on system design.
 We formulated four categories of unrelated clones to look into their refactoring opportunities.
@@
 This marks the opportunity for creating a superclass abstraction and placing the extracted method there.
-Cloned nodes are flagged \textit{No Indirect Superclass} if any of their ancestors does not have a parent.
+Cloned nodes are flagged \textit{No Indirect Superclass} if any of their ancestors do not have a parent.
 In such a case, it would be possible to create such an abstraction for the ancestor that does not have a parent.
@@
 We check the location of each clone instance for each of its nodes.
-If any node reports a different location from the others, we choose the location that is lowest in above list.
+If any node reports a different location from the others, we choose the location that is lowest in the above list.
 So for instance, if a clone instance has 15 nodes that denote a \textit{Method Level} location but 3 nodes are \textit{Class Level}, the clone instance becomes \textit{Class Level}.
@@
 \subsubsection{Method/Constructor Level Clones} \label{sec:methodlevelcr}
-Method/Constructor Level clones denote clones that span are found in either a method or contructor.
+Method/Constructor Level clones denote clones that are found in either a method or constructor.
 A constructor is a special method that is called when an object is instantiated.
@@
 \textit{ancestors(n)} denotes all of ancestor nodes of a node.
-The ancestor nodes are recursively all the parents of a given node in the AST.
+The ancestor nodes are all recursive parents of a given node in the AST.
 Apart from this, we check that the MethodDeclaration ancestor of each clone instance is the same, to be sure the clone only spans a \textit{single} method.
@@
 It can also be a clone instance that exceeds the boundaries of a single method.
-These clone instances can contain a fields, (abstract) methods, inner classes, enumeration fields, etc.
+These clone instances can contain fields, (abstract) methods, inner classes, enumeration fields, etc.
 These types of clones require various refactoring techniques to refactor.
-For instance, we might have to move fields in a inheritance hierarchy.
+For instance, we might have to move fields in an inheritance hierarchy.
 Or, we might have to perform a refactoring on more of an architectural level, if a large set of methods is cloned.
@@
 Finally, we looked at what nodes individual clone instances span.
-We selected a set of catagories on the basis of empirical evaluation of a set of clones in our dataset.
+We selected a set of categories based on empirical evaluation of a set of clones in our dataset.
 We selected the following categories to be relevant for refactoring:
@@
 These clones can often be refactored by extracting a new method out of the cloned code.
-We detect such clones by checking that each node in the clone instance has a ancestor node that is a MethodDeclaration, but none of the nodes is a method declaration.
+We detect such clones by checking that each node in the clone instance has an ancestor node that is a MethodDeclaration, but none of the nodes is a method declaration.
 We describe the procedure by with we recursively seek the parent nodes of a node in Section~\ref{sec:methodlevelcr}.
@@
 The ``Other'' category denotes all configurations of clone contents that do not fall into above categories.
-Often, these are combinations of above states concepts.
-For instance, a combination of constructors and methods is clones, or a combination of fields and methods.
+Often, these are combinations of the above stated concepts.
+For instance, a combination of constructors and methods or a combination of fields and methods is cloned.
 Such clones indicate, like the ``Several Methods'', the requirement of performing a more architectural-level refactoring.
@@
 \subsection{Method extraction opportunities}\label{sec:refactorabilitysetup}
-The most used technique to refactor clones is ``Extract Method'' (creating a new method on the basis of the contents of clones).
+The most used technique to refactor clones is ``Extract Method'' (creating a new method based on the contents of clones).
 However, method extraction cannot be applied in all cases.
 In some instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.
-CloneRefactor maps to what extend this refactoring method can be used to refactor the found clones automatically.
+CloneRefactor maps to what extent this refactoring method can be used to refactor the found clones automatically.
 
@@
 We mapped the contents of clones in Section~\ref{sec:setuplocation}.
-Here we defined the ``Partial Method'' catagory as \textit{a clone that spans (a part of) the body of a method.
-The declaration itself is not included.} If the clone does not fall within this category, ``Extract Method'' is likely not to be correct technique for refactoring such clones.
+Here we defined the ``Partial Method'' category as \textit{a clone that spans (a part of) the body of a method.
+The declaration itself is not included.} If the clone does not fall within this category, ``Extract Method'' is likely not to be the correct technique for refactoring such clones.
 
@@
 We cannot put declarations in a method.
-However, there are possibilities where a clone consists of something else than a statement as top level node.
-The most prominent example is when a clause is cloned (see Section~\ref{sec:astbackground} for examples of such concepts).
-For instance, we cannot extract only the catch-clause of a try-statement to a new method.
-In such a case, we should either extract the complete try-statement, or only the contents of the catch clause.
+However, there are possibilities where a clone consists of something else than a statement as a top-level node.
+Upon manual inspection, we noticed that most clones falling into this category are clones that span part of a lambda or anonymous class.
 
@@
 That is because such clones may require other techniques to refactor them.
-We consider analyzing such refactoring methods future work.
 An example refactoring of clone instances that overlap within their clone class is displayed in Figure~\ref{fig:overlaprefactoring}.
@@
 \subsubsection{Can be extracted}
-All clones that do not adhere to any of above-stated categories, are considered suitable for automated method extraction.
+All clones that do not adhere to any of above-stated categories are considered suitable for automated method extraction.
 
@@
 The refactoring techniques that we use depend on the relation and contents of the clone.
-In this section, we explain the transformations we apply to the program AST in order to refactor clones.
-
-First, we create a new method and give it an uniquely generated name.
+In this section, we explain the transformations we apply to the program AST to refactor clones.
+
+First, we create a new method and give it a uniquely generated name.
 We replace all nodes from the clone instances of the clone to method calls of the newly created method.
-We place a copy the nodes that were removed from a single clone instance in the new method.
+We place a copy of the nodes that were removed from a single clone instance in the new method.
 
@@
 If all clone instances in a clone class are in different classes that do not yet have a superclass, or their ancestors have no superclass, we create a superclass abstraction for them.
-This way we make the implicit dependency between both clone fragments explicit, while provisioning a common place for common functionality.
+This way we make the implicit dependency between both clone fragments explicit while provisioning a common place for common functionality.
 We give the method a \texttt{protected} visibility, which indicates that the method can only be used within its hierarchy.
@@
 Most current code clone refactoring support tools use utility classes to refactor unrelated code clones \cite{mazinanian2016jdeodorant, yoshida2005refactoring, gode2010clone}.
-For this study we refrain from doing this, because the introduction of many static methods can make a codebase hard to comprehend \cite{xing2003pseudo}.
+For this study, we refrain from doing this because the introduction of many static methods can make a codebase hard to comprehend \cite{xing2003pseudo}.
 Additionally, we can use the created abstractions for further refactorings.
@@
 We determine which variables and methods that are used in the method body are not accessible anymore at the location where the extracted method is placed.
-For each of these variables and called methods we add a parameter to the extracted method.
+For each of these variables and called methods, we add a parameter to the extracted method.
 We then pass the appropriate data to each method call.
@@
 \paragraph{Return value}\label{sec:refreturn}
-The exracted method has a return value if one of these three conditions is met:
+The extracted method has a return value if one of these three conditions is met:
 \begin{itemize}
-\item \textbf{There is a return statement in the extracted fragment}: If the extracted code fragment ends in a return statement, we set the type of the returned variable as the type of the extracted method.
+\item \textbf{There is a return statement in the extracted fragment}: If the extracted code fragment ends in a return statement, we change the type of the returned extracted method to the type of the returned variable.
 We turn all method calls of the extracted method into return statements followed by the method call.
@@
 We also analyze all called methods to find out whether they throw exceptions.
-For each of these exception, we check whether they are caught in the extracted method.
-Any exception that is that is not a \texttt{RuntimeException} and that is not being caught is added to the thrown exceptions of the extracted method.
+For each of these exceptions, we check whether they are caught in the extracted method.
+Any exception that is not a \texttt{RuntimeException} and that is not being caught is added to the thrown exceptions of the extracted method.
 
@@
 
-In this case we are dealing with single refactorings and we want to measure the maintainability impact of such a small change.
+In this case, we are dealing with single refactorings and we want to measure the maintainability impact of such a small change.
 Because of that, we measure only a subset of the metrics \cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
@@
 The paper \cite{heitlager2007practical} measures volume as lines of code.
-As with duplication, we use the amount of tokens instead.
+As with duplication, we use the number of tokens instead.
 \item \textbf{Complexity}: Heitlager et al.
 use MCCabe complexity \cite{mccabe1976complexity} to calculate their complexity metric.
-The MCCabe complexity is a quantative measure of the number of linearly independent paths through a method.
-\item \textbf{Method Interface Size}: The amount of parameters that a method has.
+The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.
+\item \textbf{Method Interface Size}: The number of parameters that a method has.
 If a method has many parameters, the code may become harder to understand and it is an indication that data is not encapsulated adequately in objects \cite{fowler2018refactoring}.
@@
 \item \textbf{Volume}: The volume can both decrease and increase as a result of the refactoring.
-The reduction of volume is equal to the reduction of duplication.
-The volume is increased by the amount of tokens in each method call to the extracted method, plus optionally the return, assignment or declaration of the extracted method.
+The reduction of the volume is equal to the reduction of duplication.
+The volume is increased by the number of tokens in each method call to the extracted method, plus optionally the return, assignment or declaration of the extracted method.
 We also add the size in tokens of the extracted method itself to the volume.
-If the extracted method is moved to a newly created class or interface, we use volume of that declaration instead (because it in turn contains the extracted method).
+If the extracted method is moved to a newly created class or interface, we use the volume of that declaration instead (because it contains the extracted method).
 The added volume minus the reduced volume results in the change in volume.
@@
 The added volume complexity the reduced complexity results in the change in complexity.
-\item \textbf{Method Interface Size}: The duplication can only increase as a result of the refactoring. The method interface size increases by the amount of parameters in the extracted method.
+\item \textbf{Method Interface Size}: The duplication can only increase as a result of the refactoring. The method interface size increases by the number of parameters in the extracted method.
 \end{itemize}

### 2019-08-24 sections/discussion.tex

@@
 \subsubsection{Refactorability} \label{sec:discussrefactorability}
-In Section~\ref{sec:refactorability} we introduced catagories to determine the refactorability of clones through method extraction.
+In Section~\ref{sec:refactorabilitysetup} we introduced catagories to determine the refactorability of clones through method extraction.
 We excluded categories that could not not be directly refactored through method extraction.

### 2019-08-24 sections/related_work.tex

@@
 \subsection{JDeodorant} \label{sec:jdeodorant}
-The most used tool used to help in the process of refactoring clones is JDeodorant \cite{mazinanian2016jdeodorant}.
+The most used clone refactoring tool is JDeodorant \cite{mazinanian2016jdeodorant}.
 This tool is based on a set of studies, that look into several aspects of the clone refactoring process.
@@
 
-The second study, ``Unification and Refactoring of Clones'' by Krishnan et % Sander: In the second study? of iig iets waardoor zin klopt
-al.~\cite{krishnan2014unification}, the authors address the problem of the modifications made to copied fragments and their impact on the refactoring process.
+In the second study, ``Unification and Refactoring of Clones'' by Krishnan et al.~\cite{krishnan2014unification}, the authors address the problem of the modifications made to copied fragments and their impact on the refactoring process.
 They identify a list of expressions in which they have found variability, which is displayed in Table~\ref{tab:krishnanvariability}.

### 2019-08-24 sections/research.tex

@@
 In Section~\ref{sec:rtypes} we propose new clone type definitions that address these shortcomings.
-%we introduced clone types as defined in literature.
-For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings to increase the chance that we can refactor the clone while improving the design.
-
-%We also look into clone detection tools for their suitability to support the proposed clone type definitions. We selected a few criteria % TODO: Sander -...?
-%Most clone detection tools support these definitions of clone types.
-However, many of these tools use a vastly different approach.
-A study by Saini et al \cite{saini2018towards} outlines different clone detection tools and compares their results for each of type 1-3 clones.
-Even though they operate on the same type definitions, the tools used in this study yield different results.
-% TODO: Sander - hier mist nog conclusie van dit stukje
 
 \section{Problems with clone types for automated refactoring}\label{sec:literaturetypeproblems}
-%Clone types 1-3 (further explained in Section~\ref{chap:backgroundclonetypes}) allow reasoning about the duplication in a software system.
-Clones by these definitions can relatively easily and efficiently be detected.
-% TODO: Sander - compared to?
-%This has allowed for large scale analyses of duplication~\cite{livieri2007very}.
-However, these clone type definitions have shortcomings which makes the clones detected in correspondence with these definitions less valuable for (automated) refactoring purposes.
-
 In this section, we discuss the shortcomings of clone type 1-3 \cite{roy2007survey}.
-Because of these shortcomings, clones found by these definitions are often found to require additional judgment whether they can and should be refactored.
+Because of these shortcomings, clones found by these definitions are often found to require additional judgment whether they can and should be (automatically) refactored.
 
@@
 This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
-%When aiming to automatically refactor clones, applying refactorings to type 1 clones is bound to be error prone and can result in an uncompilable project or a difference in functionality.
+%When aiming to automatically refactor clones, applying refactorings to type 1 clones is bound to be error-prone and can result in an uncompilable project or a difference in functionality.
 
@@
 The cloned fragment on the left adds a specific amount to an integer.
-The cloned fragement on the right concatenates a number to a String.
+The cloned fragment on the right concatenates a number to a String.
 
 This shows that not all type 1 clones can easily be automatically refactored.
-In section \label{chap:type1rclones} we describe an alternate approach towards detecting type 1 clones, which results in only clones that can be refactored.
+In section \label{chap:type1rclones} we describe an alternative approach towards detecting type 1 clones, which results in only clones that can be refactored.
 
@@
 Detection of clones by this definition can be hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed.
-Because of this, most clone detection implementations of type 3 clones work on the basis of a similarity threshold~\cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
+Because of this, most clone detection implementations of type 3 clones work based on a similarity threshold~\cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
 This similarity threshold has been implemented in different ways: textual similarity (for instance using Levenshtein distance)~\cite{lavoie2011automated}, token-level similarity~\cite{sajnani2016sourcerercc} or statement-level similarity~\cite{kamalpriya2017enhancing}.
@@
 To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types directed at detecting clones that can and should be refactored.
-We have named these clones type 1R, 2R and 3R clones.
-These definitions address problems of the corresponding literature definitions.
+We have named these clones type 1R, 2R, and 3R clones.
+These definitions address the outlined shortcomings of the corresponding literature definitions.
 The ``R'' stands for refactoring-oriented.
@@
 \subsubsection{Referenced Types}
-Many object-oriented programming languages (like Java, Python and C\#) require the programmer to import a type (or the class in which it is declared) before it can be used.
+Many object-oriented programming languages (like Java, Python, and C\#) require the programmer to import a type (or the class in which it is declared) before it can be used.
 Based on what is imported, the meaning of the name of a type can differ.
-For instance, if we import \texttt{java.util.List}, we get the interface which is implemented by all list datastructures in Java.
+For instance, if we import \texttt{java.util.List}, we get the interface which is implemented by all list data structures in Java.
 However, importing \texttt{java.awt.List}, we get a listbox GUI component for the Java Abstract Window Toolkit (AWT).
+These are entirely different functional concepts.
 To be sure we compare between equal types, type 1R clones compare the FQI for all referenced types.
@@
 The implementation of these methods might differ.
-When we call two methods with an identical name, we can in fact call different methods.
-This is another reason that textually identical code fragments can differ functionally.
+When two code fragments call methods with an identical name or signature, they can call different methods.
+Because of this, textually identical code fragments can differ functionally.
 
-Because of this, for type 1R clones, we compare the fully qualified method signature for all method references.
+For type 1R clones, we compare the fully qualified method signature for all method references.
 A fully qualified method signature consists of the fully qualified name of the method, the fully qualified type of the method plus the fully qualified type of each of its arguments.
@@
 When we reference a variable, we only use its name.
-If, in different code fragments, we use variables with the same name but different types, the code can be functionally unequal but still textually equal.
+If we use variables with the same name but different types in different code fragments, the code can be functionally unequal but still textually equal.
 As an example, see the code in Figure~\ref{fig:type2variables}.
@@
 
-The body of both methods in Figure~\ref{fig:type2variables} is equal. However, their functionality is not. The first method adds two numbers together and the other concatenates an integer to a String.
+The body of both methods in Figure~\ref{fig:type2variables} is equal.
+However, their functionality is not.
+The first method adds two numbers together and the other concatenates an integer and a String.
 
@@
 \subsection{Type 2R clones} \label{sec:type2r}
-Type 2R clones are modelled after type 2 clones, which allow any change in identifiers, literals, types, layout, and comments.
+Type 2R clones are modeled after type 2 clones, which allow any change in identifiers, literals, types, layout, and comments.
 For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore.
@@
 When refactored, some identifiers have no detrimental effect on the design if they vary between cloned instances.
-This section explains several patterns of variability that we can allow between cloned fragements without changing the method by which the fragments can be refactored.
+This section explains several patterns of variability that we can allow between cloned fragments without changing the method by which the fragments can be refactored.
 
@@
 Both clone instances in this example use different variables, but in the same places and with the same type.
-Because these variables are locally defined, the extraced method requires an extra argument for the variable anyways.
+Because these variables are locally defined, the extracted method requires an extra argument for the variable anyways.
 If the second clone instances would be completely equal, so also use the same variable, the refactoring would be very similar (it would only differ by a single character).
@@
 The same variables are used, but they are not used in the same places in cloned fragments.
-In one fragment we use only one variable, in the other we use both.
+In one fragment we use only one variable, in the other, we use both.
 Because of that, we require an extra argument.
@@
 \paragraph{Literal and variable variability}\label{sec:t2rliteralandvariable}
-We allow only variability in the value of literals and variables, but not in their types.
+Type 2R allows variability in the value of literals and variables, but not in their types.
 This is because a difference in literal/variable type may have a big impact on the refactorability of the cloned fragment.
 When we refactor different literals/variables that have both the same type, in case of an ``Extract Method'' refactoring, we have to create a parameter for this literal and pass the corresponding literal/variable from cloned locations.
-However, if two literals have different types, this might not be possible (or will have a negative effect on the design of the system).
+However, if two literals have different types, this might not be possible (or will harm the design of the system).
 This is because a lot of variability in literals will result in more parameters required in the extracted method, which is detrimental for the design of the system.
@@
 \paragraph{Method call variability}
-Most modern programming languages (like Java, Python and C\#) allow to pass method references as a parameter to a method.
+Most modern programming languages (like Java, Python, and C\#) allow passing method references as a parameter to a method.
 This helps reducing duplication, as it is possible to refactor two code fragments which differ only by a method call.
@@
 Because methods calls can have a different structure, type 2R clones can be structurally slightly different.
-The example as shown in Figure~\ref{fig:type2method} can be a type 2R clone (dependent on the thresholds used), but is not a type 2 clone.
+The example as shown in Figure~\ref{fig:type2method} can be a type 2R clone (dependent on the thresholds used) but is not a type 2 clone.
 
@@
 In this formula, the ``Number of nodes in gap'' concerns the amount of non-cloned nodes that are in between both clone instances.
-The ``Number of nodes in clones'' is the amount of nodes that are in the clone instances surrounding the gap:
+The ``Number of nodes in clones'' is the number of nodes that are in the clone instances surrounding the gap:
 
@@
 We cannot refactor both statements into a single conditional block.
-We could however use two conditional blocks, but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for type 3R clones.
+We could use two conditional blocks, but due to the detrimental effect on the design of the code (as each conditional block adds a certain complexity), we decided not to allow this for type 3R clones.
 
@@
 \subsection{Clone types summarized}
-The given clone definitions (types 1R, 2R and 3R) are refactoring-oriented in the sense that they were designed after the literature type definitions but with a concrete refactoring opportunity in mind.
+The given clone definitions (types 1R, 2R, and 3R) are refactoring-oriented in the sense that they were designed after the literature type definitions but with a concrete refactoring opportunity in mind.
 Summarized, these types can be explained as follows:
@@
 \subsection{The challenge of detecting these clones}\label{chap:challenge}
-To detect each type of clone, we need to parse the fully qualified identifier of all types, method calls and variables.
+To detect each type of clone, we need to parse the fully qualified identifier of all types, method calls, and variables.
 This comes with serious challenges, regarding both performance and implementation.
-Also, to be able to parse all fully qualified identifiers, and trace the declarations of variables, we might need to follow cross file references.
+Also, to be able to parse all fully qualified identifiers, and trace the declarations of variables, we might need to follow cross-file references.
 The referenced types/variables/methods might even not be part of the project, but rather of an external library or the standard libraries of the programming language.
-All these factors need to be considered for the referenced entity to be found, on the basis of which a fully qualified identifier can be created.
+All these factors need to be considered for the referenced entity to be found, based on which a fully qualified identifier can be created.
 
-\section{Suitability of existing Clone Detection Tools for detecting these clones}
-\label{ch:tool-overview}
+\section{Suitability of existing Clone Detection Tools for detecting these clones} \label{ch:tool-overview}
 We conduct a short survey on (recent) clone detection tools that we can use to analyze refactorable clones.
@@
 We want to perform an analysis of all clones in projects to get a complete overview.
-\item \textbf{Finds clone classes in control projects\footnote{Control projects for assessing clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}}}: We assembled a number of control projects to assess the validity of clone detection tools.
+\item \textbf{Finds clone classes in control projects}: We assembled several control projects\footnote{Control projects for assessing clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to assess the validity of clone detection tools.
 \item \textbf{Analyzes resolved symbols}: When detecting the types proposed in section~\ref{sec:rtypes}, it is important that we can analyze resolved symbols (for instance a type reference).
@@
 \item \textbf{Extensive detection configuration}: Detecting our clone definitions, as proposed in section~\ref{sec:rtypes}, require to have some understanding about the meaning of tokens in the source code (whether a certain token is a type, variable, etc.).
-The tool should recognize such structures, in order for us to configure our clone type definitions in the tool.
+The tool should recognize such structures, for us to configure our clone type definitions in the tool.
 \end{enumerate}
@@
 
-None of the state-of-the-art tools we identified implement all our criteria. Because of that, we implement our own clone detection tool: CloneRefactor.
+None of the state-of-the-art tools we identified implement all our criteria. Because of that, we propose CloneRefactor (see Chapter~\ref{ch:clonerefactor}).

### 2019-08-24 sections/conclusion.tex
Experimental setup Sander feedback
Conclusion and future work

--- 2019-08-23 sections/conclusion.tex
@@
 \chapter{Conclusion} \label{ch:conclusion}
-We defined automatically refactorable clones and created a tool to detect and refactor them.
+In this work, we defined automatically refactorable clones and created a tool to detect and refactor them.
 We measured statistical data with this tool over a large corpus of open-source Java software systems to get more information about the context of clones and how refactoring them influences system maintainability.
@@
 Another 24\% of clones are unrelated.
-The final 7\% of clones have the same interface.
+The final 15\% of clones have the same interface.
 We also looked at the \textbf{location} of clones: 78\% of clones is found at method-level of which 77\% is found in the body of a method or constructor.
-Because of this, the ``Extract Method'' refactoring method is most suitable to refactor most clones.
+Because of this, the ``Extract Method'' refactoring technique is most suitable to refactor most clones.
 
@@
 We found that the most prominent factor influencing maintainability is the size of the clone.
-For our dataset, at a clone volume of 29 tokens per clone instance the average clone refactoring improved system maintainability.
+For our dataset, at a token volume of 63 tokens per clone instance the average clone refactoring improved system maintainability.
+We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class.
+
 Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data.
-We noticed that the inheritance relation of the clone and the return value of the extracted method has only a minor impact on system maintainability.
+Most refactored clones for which extracted methods with more than one parameter were created decreased maintainability.
+We found that the inheritance relation of the clone and the return value of the extracted method has only a minor impact on system maintainability.
 
@@
 \subsubsection{Long parameter list}
-When multiple parameters are used together in a method, there is an implicit dependency between these parameters: the dependency of being required by that method.
+%When multiple parameters are used together in a method, there is an implicit dependency between these parameters: the dependency of being required by that method.
 \textit{If a lot of data hangs around really tight together, they should be made into their own object} \cite{fowler1999refactoring}.
@@
 We must then trace all places in which they are used together and replace the variables by the newly created abstractions.
+If long parameter lists can be automatically refactored, automated clone refactoring can be improved by automatically grouping data into objects if they are used in unison.
 
 \subsubsection{Method complexity}
-Method complexity refers to the complexity of the logic in a method body.
+%Method complexity refers to the complexity of the logic in a method body.
 There are several methods to compute method complexity.
@@
 
-Dealing with method complexity can largely be done by method extraction.
+%Dealing with method complexity can largely be done by method extraction.
 We extract a part of a complex method to a new method.
@@
 
-Refactoring complex methods can largely be done automatically.
+Refactoring complex methods can largely be done automatically by applying ``Extract Method'' to large methods.
 Also, many of the results of this study can be reused.
@@
 
-\subsubsection{Method size}
-Method size has a strong relation, in terms of refactoring, with Cyclomatic Complexity.
+%\subsubsection{Method size}
+%Method size has a strong relation, in terms of refactoring, with Cyclomatic Complexity.
 Although method size is often related to Cyclomatic Complexity, a study by Landman et al.
@@
 
-\subsubsection{Combining the metrics}
-Combining the automated refactoring models for each of these metrics can result in a model that ultimately provides significant improvement in the ease of writing well-maintainable source code.
+%\subsubsection{Combining the metrics}
+%Combining the automated refactoring models for each of these metrics can result in a model that ultimately provides significant improvement in the ease of writing well-maintainable source code.
 In this study, we presented a few tradeoffs that are the result of refactoring code clones.
@@
 \subsection{Type 4 clones}
-In Section~\ref{chap:backgroundclonetypes} we introduced the clone types that are used in literature.
-Of these clone types, we considered type 1, 2 and 3 for refactoring.
-We chose not to consider type 4 clones because they appear far less in source code and are more difficult to detect and refactor.
-However, that does not mean that these clones should not be refactored.
-
+Type 4 clones are defined as \textit{two or more code fragments that perform the same computation, but implemented through different syntactic variants.} \cite{roy2007survey}.
 We think that there are relevant research opportunities in refactoring type 4 clones.
@@
 
-\subsubsection{Proposing new clone type definitions}
-We think that current definitions of clone types still lack in the identification of all duplication issues that a developer should invest his/her refactoring efforts in.
+%\subsubsection{Proposing new clone type definitions}
+%We think that current definitions of clone types still lack in the identification of all duplication issues that a developer should invest his/her refactoring efforts in.
 Current clone detection techniques still result in many false positives and false negatives.
@@
 
-Applying our experiments with other programming languages than just Java might result in valuable results.
+Applying our experiments with other programming languages than just Java might yield valuable results.
 Refactoring opportunities are greatly dependent on coding conventions, which differ per language.
 Other languages might result in different results, which might result in different insights regarding the resolution of duplication problems found.
-We prioritized refactoring efforts based on Java, which might differ from the prioritization that can result from running our experiments with other programming languages.
+We prioritized our refactoring efforts based on Java, which might differ from the prioritization that can result from running our experiments with other programming languages.
 
@@
 For instance, it might be valuable to look into the opportunities to reduce duplication in the functional domain.
-Dealing with code clones in the functional paradigm is pretty much an unexplored field and might hold valuable results.
+Dealing with code clones in the functional paradigm is largely an unexplored field and might hold valuable results.
 
@@
 There are definite automated refactoring opportunities here, automatically switching to the library implementation if available.
-
-This doesn't have to be limited to just the Java standard library.
-Although using a new library for a single cloned library, we can also search the libraries the project are already uses.
-CloneRefactor is an excellent tool to expand for finding such clones with external libraries and refactoring the source code to use the library implementation if available.
-This is because CloneRefactor has scripts to gather all dependent libraries for Maven projects.
-It loads these libraries in order to be able to resolve symbols.
-If this would be expanded not only to resolve symbols but also to consider the clones between the analyzed project and its dependencies, we could find such refactoring opportunities.
+This doesn't have to be limited to just the Java standard library., it is also possible to search the external libraries the project uses.

### 2019-08-24 sections/discussion.tex
Discussion

@@
-\chapter{Discussion}
-\label{ch:discussion}
-%Interpretations: what do the results mean?
-%Implications: why do the results matter?
-%Limitations: what can’t the results tell us?
-%Recommendations: what practical actions or scientific studies should follow?
+\chapter{Discussion} \label{ch:discussion}
 
@@
 In this study, we proposed a set of clone type definitions that can be automatically refactored.
-We based these clone type definitions on the clone type definitions that are commonly used in literature.
+We based these clone type definitions on the clone type definitions that are commonly used in literature \cite{roy2007survey}.
 The design of these clone type definitions entails some decisions that have a large impact on the clones we considered for refactoring in this study.
@@
 
-\section{Clone Context Analysis}
-In Section~\ref{chap:contextsetup} we introduced the categories we defined for mapping the context of clones. In this section, we discuss this together with the related experiments.
+%\section{Clone Context Analysis}
+%In Section~\ref{chap:contextsetup} we defined categories for mapping the context of clones. In this section, we discuss this together with the related experiments.
 
@@
 In this study we identified categories for three properties of clones: relation, location and contents.
-%Mapping the location and contents was mainly to find out what the best method of refactoring is to refactor most clones.
 We chose a set of relations that indicate different refactoring opportunities.
@@
 In this section, we discuss the differences between clone types 1-3 and 1R-3R.
-We see that the difference between T1R and T1 in terms of found clones is small (11\%).
+We see that the difference between T1R and T1 in terms of found clones is small (11\% more nodes found as cloned for T1).
 This implies that most often textually equal code is also functionally equal.
-The difference between T2R and T2 is bigger (35\%).
-Upon manual inspection we found that the main reason for this is that T2R does not allow any variability in types, wheareas T2 allows any variability in types.
+The difference between T2R and T2 is bigger (35\% more nodes found as cloned).
+Upon manual inspection, we found that the main reason for this is that T2R does not allow any variability in types, wheareas T2 allows any variability in types.
 
 Regarding performance (Figure~\ref{fig:performance}, there is a notable difference between the refactoring-oriented clone types and the literature clone types.
-Type 1R-3R take about 6 times longer to detect than type 1-3.
-The main reason for this is type resolution: finding the fully qualified identifiers of type-, variable- and method-references.
+Type 1R-3R take on average approximately 6 times longer to detect than type 1-3.
+The main reason for this is type resolution: finding the fully qualified identifiers of type-, variable-, and method-references.
 
@@
 This makes sense regarding the nature of the threshold.
-As we get into higher gap size percentages, fewer clones merge (thus the decrease in amount of clone classes merging).
-However, at these higher gap size percentages the gaps contains more nodes (thus the amount of cloned nodes being linear).
+Type 3R clones are formed by merging two gapped clone classes into a type 3R clone class.
+As we get into higher gap size percentages, fewer clone classes merge.
+However, at these higher gap size percentages the gaps contains more nodes , because of which the increase of the number of cloned nodes is linear.
 
@@
 \subsection{Extract Method}
-28\% of clones can be refactored using the ``Extract Method'' refactoring technique (50\% if we limit our searching scope to method bodies).
+28\% of clones can be refactored using the ``Extract Method'' refactoring technique.
 About 25\% of clones do not span part of a method, because of which they cannot be refactored.
-Many clones (23\%) do not have a statement as top-level AST-Node.
-Upon manual inspection, we noticed that the main reason for this is clones in anonymous functions or anonymous classes.
+23\% of the clones do not have a statement as top-level AST-Node.
+Upon manual inspection, we noticed that the main reason for this is when clones reside in anonymous functions or anonymous classes.
 About 15\% of clones span only part of an AST-Node.
@@
 \subsection{Refactoring}
-In Fig.~\ref{fig:maintainabilityscore} we see an increase in maintainability for refactoring larger clone classes.
-The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie at a token volume of 63 tokens.
-There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.
 
-In Table~\ref{tab:relationref} we see the results regarding refactorings that are applied to clones with diverse relations.
-We see that most refactored clones are in a common class, over 54\%.
+\subsubsection{Token Volume}
+In Fig.~\ref{fig:maintainabilityscore} we see an increase in the \textbf{maintainability score} for refactoring larger clone classes.
+The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, lies at a token volume of 63 tokens.
+There are fewer large clones than small clones (exponential decrease), resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.
+
+When looking at the relation between maintainability and the \textbf{volume} metric, we see that the volume increases if the average clone volume is less than 60 tokens, but decreases above 60 tokens.
+When token volume increases, the \textbf{number of parameters} of the extracted method rises very slowly.
+Overall, on average, extracted methods have only one parameter.
+When the token volume of clones becomes larger than 160 tokens, we also see that there are more outliers in terms of number of parameters.
+For the \textbf{complexity} we see that most clones do not have any complexity, because for most refactorings the complexity increases by one.
+This complexity is the added complexity of the extracted method, and implies that the removed clones did not have any complexity.
+There is also no clear trend regarding the complexity.
+
+\subsubsection{Relation}
+In Table~\ref{tab:relationref} we see the results regarding refactorings that are applied to clones with the specified relation category.
+We see that 57\% of the refactored clones are in a common class.
 This is significantly more than the percentage of clones in the common class relation as reported in Table~\ref{tab:relation}.
-Meanwhile, the number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% -> 18\%).
+Meanwhile, the number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% -> 17\%).
 The main reason for this is that refactoring unrelated clones can change the relation of other clones in the same system.
-If we create a superclass abstraction to refactor an unrelated clone, other clones in those classes that were previously unrelated might become related.
+If we create a superclass abstraction to refactor an unrelated clone, other clones in those classes that were previously unrelated become related.
 
-The maintainability scores displayed in Table~\ref{tab:relationref} show that the most favorable clones to refactor are clones with a sibling relation.
-The most unfavorable is to refactor clones to interfaces.
-However, the differences in maintainability in this table are generally small; according to our data relations have a minor impact on the maintainability of clones.
+The maintainability scores displayed in Table~\ref{tab:relationref} show that the most favorable clones to refactor are clones with a superclass relation.
+The most unfavorable is to refactor unrelated clones.
+The main reason for this difference in maintainability is that on average unrelated clones have a higher volume.
 
-Regarding the return type of refactored clones, we see in Table~\ref{tab:return} that this has no major impact on maintainability.
-A method call to the extracted method that is directly returned and no return type extracted methods are slightly more favorable than the others.
-We think the main reason that the ``Return'' category is on top is that when a variable is declared at the end of the cloned fragment, CloneRefactor directly returns its value and removes the declaration.
-This decreases the volume slightly.
+The differences in maintainability of relation are, compared to the differences in maintainability of different token volumes, very small.
+Common hierarchy (which has the highest score) has a maintainability score of 0.23 whereas unrelated clones (which has the lowest score) have a maintainability score of -0.15.
+This is a very small difference, which implies that according to our data relations have a minor impact on the maintainability of clones.
 
-A higher number of parameters directly influences the corresponding metric.
-Because of this, we see in Fig.~\ref{fig:arguments} that more parameters negatively influence maintainability.
-Not only the number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
-Because of that, we see that trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.
+\subsubsection{Return Category}
+Regarding the return category of refactored clones, we see in Table~\ref{tab:return} that this has no major impact on maintainability: the differences between the maintainability scores of the categories are very small.
+The worst maintainable return category is when methods do not return anything (void), mainly because it is related with a higher number of parameters in the extracted method.
+
+\subsubsection{Number of Parameters}
+We see in Figure~\ref{fig:arguments} that the average extracted method that requires more than one parameter decreases maintainability.
+This is because a higher number of parameters does not only increase the ``number of parameters'' metric, but also the volume for the extracted method and each of the calls to it.
+Because of that, we see that trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly and that the number of parameters in the extracted method has a major influence on maintainability.

### 2019-08-24 sections/results.tex
Discussion

@@
 \chapter{Results}\label{ch:results}
-In this chapter, we present the results of our experiments. We perform exploratory experiments to map the differences between clone types, contexts and refactoring opportunities.
+In this chapter, we present the results of our experiments\footnote{The underlying datasheets for all our results can be found on GitHub: \url{https://github.com/SimonBaars/Master-Thesis-Simon-Baars/tree/master/results}}.
+We perform exploratory experiments to map the differences between clone types, contexts and refactoring opportunities.
 
@@
 \subsection{Clone Token Volume}
-Figure \ref{fig:maintainabilityscore} shows the obtained results when plotting the clone volume vs the maintainability increase/decrease.
+Figure \ref{fig:maintainabilityscore} shows the obtained results when plotting the clone volume against the maintainability increase/decrease.
 We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class.
@@
 \centering
-\resizebox{\textwidth}{!}{%
+%\resizebox{\textwidth}{!}{%
 \begin{tabular}{@{}lrrrrrr@{}}
@@
 \end{tabular}%
-}
+%}
 \caption{Average metric values for refactorings of clone classes with the specified return category}

### 2019-08-24 sections/experimentalsetup.tex
ICSE Results
Experimental setup

@@
 \chapter{Experimental Setup}\label{ch:experimentalsetup}
-In this chapter we explain the setup of our experiments.
 All our experiments are quantitative experiments, measured over a corpus using CloneRefactor.
 In this chapter, we first explain the corpus we use.
-We then explain the way in which we calculate the impact of refactorings on the software maintainability.
+We then explain how we calculate the impact of refactorings on the software maintainability.
 
@@
 For our experiments we use a large corpus of open-source projects assembled by Allamanis et al.~\cite{githubCorpus2013}\footnote{The corpus can be downloaded at: \url{http://groups.inf.ed.ac.uk/cup/javaGithub/}}.
-This corpus contains a set of Java projects from GitHub, selected by number of forks.
+This corpus contains a set of Java projects from GitHub, selected by the number of forks.
 The projects and files in this corpus were de-duplicated manually.
-This results in a variety of Java projects that reflect the quality of average open source Java systems and are useful to perform measurements on.
+This results in a variety of Java projects that reflect the quality of average open-source Java systems and are useful to perform measurements on.
 
@@
 \subsection{Filtering Maven projects}
-As explained in Section~\ref{chap:challenge}, CloneRefactor requires all the libraries a software project is dependent on in order to perform its clone analysis.
+As explained in Section~\ref{chap:challenge}, CloneRefactor requires all the libraries a software project is dependent on to perform its clone analysis.
 As these are not included in the corpus by Allamanis \cite{githubCorpus2013}, we created a script to gather these dependencies.
@@
 
-We then continued to filter all testcases and generated files.
+We then continued to filter all test cases and generated files.
 As many projects store these files in many different places, we decided to further filter the corpus to only include projects with a conventional structure.
@@
 We instruct CloneRefactor only to use the sources in the \texttt{src/main/java} folder.
-This decreases the chance of generated files and testcode being considered for clone detection.
+This decreases the chance of generated files and test code being considered for clone detection.
 
@@
 Next, we run the tool over the corpus and manually verify samples of the acquired results.
-This way, we check the correctness of the identified clones, their context and their proposed refactoring.
+This way, we check the correctness of the identified clones, their context, and their proposed refactoring.
 
@@
 For this, we use a GitHub project named JFreeChart.
-JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor.
-We run CloneRefactor manually over the JFreeChart project, run its testcases and check the correctness of the proposed refactorings.
+JFreeChart has high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor.
+We run CloneRefactor manually over the JFreeChart project, run its test cases and check the correctness of the proposed refactorings.
 
@@
 We also need calls to the extracted method, which is 4 tokens per call if no arguments are required.
-Consider the smallest possible clone: 2 clone instances of 1 token.
-Such a refactoring will never improve maintainability.
-We reduce duplication by 2 tokens, while increasing volume by 7+4+4+1=16 tokens.
-This holds true for clones up to 9 tokens (reduce duplication by 18 tokens, increase volume by 7+4+4+9=24 tokens).
 Empirically, we found all clones below 10 tokens in size, are very unlikely to affect maintainability positively.
@@
   \item All metrics are equal in terms of weight towards system maintenance effort.
-  \item Higher values for the metrics imply lower maintainability. % Sander: Dit is niet echt assumptie toch
-  \item Normalizing each obtained metric delta over all deltas obtained for a metric in our dataset results in equally weighted scores.
+  \item Higher values for the metrics imply lower maintainability.
+  \item Normalizing each obtained metric delta over all deltas obtained for that metric in our dataset results in equally weighted scores.
 \end{itemize}
@@
 Where $\Delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metric.
-This method works well for normalization of our data, because as we divide by the standard deviation, outliers do not influence the resulting scores much.
+This method works well for normalization of our data because it is resilient against outliers.
+We divide by the standard deviation so outliers do not influence the resulting scores much.
 
-We then calculate the maintainability for a specific refactoring as follows:
+We then calculate the maintainability score for a specific refactoring as follows:
 \begin{equation}\label{eq:scoreref}

### 2019-08-24 sections/results.tex
Results

@@
 We ran these performance tests on the compute nodes of the DAS4 supercomputer \cite{bal2016medium}, which allow for higher accuracy performance measurements as they do have limited background processes affecting the results.
-% Sander: zou zin na de komma (which..results) weglaten.
-%The durations are of course dependent on our implementation of the clone types.
 
@@
 
-In this graph, we see that the amount of clones increases as the amount of variability allowed increases. The graph is logaritmic: as the variability increases, the increase in nodes decreases.
+In this graph, we see that the amount of clones increases as the amount of variability allowed increases. The graph is logarithmic: as the variability increases, the increase in nodes decreases.
 
@@
   \item \textbf{Duplication}: The average delta number of duplicate tokens for all refactored clone classes in the specified category.
-  \item \textbf{\#}: The number of times the specified category is refactored (and thus the number of datapoints we have for this category).
+  \item \textbf{\#}: The number of times the specified category is refactored (and thus the number of data points we have for this category).
   \item \textbf{Score}: The average delta maintainability score (see Section~\ref{sec:metricformula} for the formula by which this score is calculated) for all refactored clone classes in the specified category.
@@
 The maintainability score, as shown in Figure \ref{fig:maintainabilityscore}, is the average delta maintainability score of all clone classes with the specified token volume that are refactored.
-For higher token volume numbers we have less refactorings that refactor such clones, because of which we represent the x-axis as a logaritmic scale.
+For larger token volumes we have fewer refactorings that refactor such clones, because of which we represent the x-axis as a logarithmic scale.
 The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.
@@
 The trendline intersects the ``zero'' line (average delta volume does not increase nor decrease) at 60 tokens.
-A higher average delta volume implies a lower maintainability.
+A higher average delta volume implies lower maintainability.
 
@@
 In Figure~\ref{fig:numberofparameters} we show the average delta number of parameters when clones with the specified token volume are refactored.
-This metric can only increase by the refactoring, because CloneRefactor only applies ``Extract Method'' refactorings that create a method with a certain number of parameters (according to the data needed by the extracted method).
+This metric can only increase by the refactoring because CloneRefactor only applies ``Extract Method'' refactorings that create a method with a certain number of parameters (according to the data needed by the extracted method).
 
@@
 We did not add a trendline, as there does not seem to be a clear trend.
-The maximum delta complexity is 1, because the extracted method itself has a complexity of 1.
+The maximum delta complexity is one because the extracted method itself has a complexity of one.
 For each branching point in the cloned fragment, the complexity of the system will decrease when such a clone is refactored.
@@
 \end{figure}
-
-%The volume of the clone is the dominating factor regarding the maintainability increase/decrease of cloned code.
-Because of that, in our further experiments we filter out all refactorings with a token size smaller than 18 because otherwise the small clones dominate the results and turn all results towards unmaintainable.
 

### 2019-08-24 sections/discussion.tex
Discussion

@@
 The design of these clone type definitions entails some decisions that have a large impact on the clones we considered for refactoring in this study.
-In this section we discuss our clone type definitions as proposed in Section~\ref{sec:rtypes}.
+In this section, we discuss our clone type definitions as proposed in Section~\ref{sec:rtypes}.
 
@@
 \end{itemize}
-By building a graph that maps relations between nodes in the AST, we can find clones in an efficient manner, allowing to perform a comprehensive analysis of large systems.
+By building a graph that maps relations between nodes in the AST, we can efficiently find clones, allowing to perform a comprehensive analysis of large systems.
 This method has worked well for our purposes.
@@
 For our corpus, there were no larger systems, so this was not a big issue.
-However, for industry projects our tool might require optimization.
+However, for industry projects, our tool might require optimization.
 
 \subsection{Context Analysis}
-In this study we identified categories for three properties of clones: relation, location and contents.
+In this study, we identified categories for three properties of clones: relation, location, and contents.
 We chose a set of relations that indicate different refactoring opportunities.
-However, as our CloneRefactor tool only analyses Java source code, we we biased towards categories that are often found in Java source code.
+However, as our CloneRefactor tool only analyses Java source code, we are biased towards categories that are often found in Java source code.
 For other languages, other categories might be valuable to analyze to find suitable categories for that programming language.
@@
 \subsubsection{Refactorability} \label{sec:discussrefactorability}
-In Section~\ref{sec:refactorabilitysetup} we introduced catagories to determine the refactorability of clones through method extraction.
-We excluded categories that could not not be directly refactored through method extraction.
-However, with a few transformations or further considerations it might be possible to make these clones refactorable.
-In this section we will highlight a few of these categories which we believe to be refactorable through method extraction with more effort.
+In Section~\ref{sec:refactorabilitysetup} we introduced categories to determine the refactorability of clones through method extraction.
+We excluded categories that cannot be directly refactored through method extraction.
+However, with a few transformations or further considerations, it might be possible to make these clones refactorable.
+In this section, we will highlight a few of these categories which we believe to be refactorable through method extraction with more effort.
 
@@
 \subsubsection{Metrics}
-For this study we chose to focus on a set of four metrics to measure maintainability: method size, duplication, method parameters and cyclomatic complexity.
-These metrics give an indication of the impact of the refactoring, but do not give a complete overview.
+For this study, we chose to focus on a set of four metrics to measure maintainability: method size, duplication, method parameters, and cyclomatic complexity.
+These metrics indicate the impact of the refactoring, but do not give a complete overview.
 There are many more metrics that could be considered to measure the maintainability impact on the system.
-An example of such a metric is ``coupling'', which focuses on the amount of incoming calls into a method or class and what modules these calls come from.
-This metric is also influenced by the transformations we applied and might deliver valuable insights in the quality of the refactoring.
+An example of such a metric is ``coupling'', which focuses on the number of incoming calls into a method or class and what modules these calls come from.
+This metric is also influenced by the transformations we applied and might deliver valuable insights into the quality of the refactoring.
 
@@
 The difference between T2R and T2 is bigger (35\% more nodes found as cloned).
-Upon manual inspection, we found that the main reason for this is that T2R does not allow any variability in types, wheareas T2 allows any variability in types.
+Upon manual inspection, we found that the main reason for this is that T2R does not allow any variability in types, whereas T2 allows any variability in types.
 
@@
 In Figure~\ref{fig:t2rgraph} we show the increase of cloned nodes for a higher variability between clone instances.
-This graph is logaritmic: as the variability increases, the increase in nodes decreases.
+This graph is logarithmic: as the variability increases, the increase in nodes decreases.
 This implies that semantical equality increases the chances that tokens are equal.
@@
 As we get into higher gap size percentages, fewer clone classes merge.
-However, at these higher gap size percentages the gaps contains more nodes , because of which the increase of the number of cloned nodes is linear.
+However, at these higher gap size percentages, the gaps contain more nodes.
+Because of this, the increase of the number of cloned nodes is linear.
 
@@
 Overall, on average, extracted methods have only one parameter.
-When the token volume of clones becomes larger than 160 tokens, we also see that there are more outliers in terms of number of parameters.
+When the token volume of clones becomes larger than 160 tokens, we also see that there are more outliers in terms of the number of parameters.
 For the \textbf{complexity} we see that most clones do not have any complexity, because for most refactorings the complexity increases by one.
-This complexity is the added complexity of the extracted method, and implies that the removed clones did not have any complexity.
-There is also no clear trend regarding the complexity.
+This complexity is the added complexity of the extracted method and implies that the removed clones did not have any complexity.
+There is also no clear trend regarding the complexity metric against the token volume.
 
@@
 Regarding the return category of refactored clones, we see in Table~\ref{tab:return} that this has no major impact on maintainability: the differences between the maintainability scores of the categories are very small.
-The worst maintainable return category is when methods do not return anything (void), mainly because it is related with a higher number of parameters in the extracted method.
+The worst maintainable return category is when methods do not return anything (void), mainly because it is related to a higher number of parameters in the extracted method.
 
@@
 This is because a higher number of parameters does not only increase the ``number of parameters'' metric, but also the volume for the extracted method and each of the calls to it.
-Because of that, we see that trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly and that the number of parameters in the extracted method has a major influence on maintainability.
+Because of that, we see that the trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly and that the number of parameters in the extracted method has a major influence on maintainability.

### 2019-08-24 sections/conclusion.tex

@@
 It would be valuable to have a control group rate the refactorings performed by CloneRefactor, as an extra form of input regarding the quality of the code transformation that CloneRefactor performs.
+
+\subsection{Aggregated Maintainability Score}
+In Section~\ref{sec:metricformula} we proposed an aggregation to measure a maintainability score on small grained changes.
+The assumptions stated in this section influence the validity of the maintainability scores shown in our results.
+We noticed that the maintainability scores shown in Table~\ref{tab:relationref} and Table~\ref{tab:return} were mostly influenced by the differences in the ``number of parameters'' metric.
+This is because for the scores, we normalized the metrics over all values obtained by these metrics.
+As our data regarding ``number of parameters'' has a very low standard deviation, small changes in this metric will influence the maintainability score a lot.
 

### 2019-08-24 sections/acknowledgements.tex
Conclusion

@@
 \chapter*{Acknowledgements}
-Throughout the writing of this dissertation I have received a great deal of support and assistance.
+Throughout the writing of this dissertation, I have received a great deal of support and assistance.
 I would first like to thank my supervisor, Dr.
@@
 Next, we would like to thank my peer student Sander Meester for always being there when I was stuck.
-Whenever I needed to test some ideas you would always provide realistic insights.
+Whenever I needed to test some ideas you would always provide valuable insights.
 The long conversations about the problems I have been dealing with in my thesis would not have been solved in the same way if it wasn't for you.

### 2019-08-24 sections/conclusion.tex
Conclusion

--- 2019-08-24 sections/conclusion.tex
@@
 %For cloned fragments to be refactorable, we propose that fully qualified identifiers of method call signatures and type references should be considered instead of their plain text representation, to be sure that they refer to the same implementations.
-, we propose that one should define thresholds for variability in variables, literals and method calls, in order to limit the number of parameters that the merged unit shall have.
+, we propose that one should define thresholds for variability in variables, literals, and method calls, to limit the number of parameters that the merged unit shall have.
 
@@
 The final 15\% of clones have the same interface.
-We also looked at the \textbf{location} of clones: 78\% of clones is found at method-level of which 77\% is found in the body of a method or constructor.
+We also looked at the \textbf{location} of clones: 78\% of clones are found at method-level of which 77\% is found in the body of a method or constructor.
 Because of this, the ``Extract Method'' refactoring technique is most suitable to refactor most clones.
@@
 
-% We recommend to extend our tool, CloneRefactor, to allow for such capabilities.
-CloneRefactor already contains a component that calculates the Cyclomatic Complexity of a given method.
-Using our automated refactored model, identified problems can relatively easily be refactored.
-
 \section{Threats to validity}\label{chap:threatstovalidity}
-In this section we share some factors that can influence the validity of the obtained results.
 
@@
 This is done through a series of AST transformations as described in Section \ref{sec:applyingrefactorings}.
-Currently, these refactoring methods do not yet allow for variability (type 2R and 3R), as allowing variability quickly increases the complexity of the refactoring problem and the amount of edge cases to consider \cite{tsantalis2015assessing}.
+Currently, these refactoring methods do not yet allow for variability (type 2R and 3R), as allowing variability quickly increases the complexity of the refactoring problem and the number of edge cases to consider \cite{tsantalis2015assessing}.
 Because of this, CloneRefactor does not yet realistically emulate human refactoring efforts, as humans would take variability between code fragments into account.
@@
 
-We think that there is value in running our experiments with different corpuses.
-We would, for instance, be interested in the results for industrial projects instead of open source software systems.
+We think that there is value in running our experiments with different corpora.
+We would, for instance, be interested in the results for industrial projects instead of open-source software systems.
 We are curious to see whether the distributions are comparable, or whether they show large differences.
@@
 Furthermore, we think that there is value in running our experiments with a set of larger sized and more professionally developed open-source systems.
-We noticed that in our corpus there were a lot of projects that have only few commits and contributors.
+We noticed that in our corpus there were a lot of projects that have only a few commits and contributors.
 We think it would be valuable to, for instance, perform our experiments with a set of larger open source systems, like the systems in the Apache ecosystem.
@@
 To limit the scope of this research, we chose not to include human subjects in this study.
-However, we think that the results of this study could be strengthened by performing a survey on software engineering practisioners.
+However, we think that the results of this study could be strengthened by performing a survey on software engineering practitioners.
 We have determined a set of refactoring opportunities only based on literature input and quantitive analysis.
@@
 
+\subsection{Aggregated Maintainability Score}
+In Section~\ref{sec:metricformula} we proposed an aggregation to measure a maintainability score on small-grained changes.
+The assumptions stated in this section influence the validity of the maintainability scores shown in our results.
+We noticed that the maintainability scores displayed in Table~\ref{tab:relationref} and Table~\ref{tab:return} were mostly influenced by the differences in the ``number of parameters'' metric.
+This is because, for the scores, we normalized the metrics over all values obtained by these metrics.
+As our data regarding ``number of parameters'' has a very low standard deviation, small changes in this metric will influence the maintainability score a lot.
+
 \section{Future work} \label{sec:future_work}
-This study presents a foundation for research in a largely unexplored field of studies: analyzing maintainability through automated refactoring.
+%This study presents a foundation for research in a largely unexplored field of studies: analyzing maintainability through automated refactoring.
 However, we scratched just the tip of the iceberg regarding all research opportunities in this field.
-In this section we describe possible extensions to this research, as well as other research opportunities in this field of studies.
+In this section, we describe possible extensions to this research, as well as other research opportunities in this field of studies.
 
 \subsection{Automated Refactoring for more metrics}
-In this study we presented evidence regarding the value of applying automated refactoring to analyze the before- and after state of source code and refactored source code.
+In this study, we presented evidence regarding the value of applying automated refactoring to analyze the before- and after state of refactored source code.
 Analyzing these states we were able to analyze the improvement in maintainability after refactoring duplicated code.
 This allows us to better assess thresholds by which maintainability issues in source code are identified.
-We also get better insights in the costs and values of applying certain refactoring efforts.
+We also get better insights into the costs and values of applying certain refactoring efforts.
 
-For this study we chose to focus only on the automated refactoring of duplication in source code.
+For this study, we chose to focus only on the automated refactoring of duplication in source code.
 However, software maintainability depends on more factors and can be measured by more metrics.
@@
 Many of these metrics have automated refactoring opportunities.
-In this section we will focus on several of these metrics to outline their opportunities for automated refactoring.
+In this section, we will focus on several of these metrics to outline their opportunities for automated refactoring.
 
@@
 If this threshold exceeds a certain amount, we can group them into an object.
-We must then trace all places in which they are used together and replace the variables by the newly created abstractions.
+We must then trace all the places in which they are used together and replace the variables by the newly created abstractions.
 If long parameter lists can be automatically refactored, automated clone refactoring can be improved by automatically grouping data into objects if they are used in unison.
 
-\subsubsection{Method complexity}
+\subsubsection{Method complexity/size}
 %Method complexity refers to the complexity of the logic in a method body.
@@
 
-Refactoring complex methods can largely be done automatically by applying ``Extract Method'' to large methods.
+Refactoring complex/large methods can largely be done automatically by applying ``Extract Method'' to large methods.
 Also, many of the results of this study can be reused.
@@
 \subsection{Type 4 clones}
-Type 4 clones are defined as \textit{two or more code fragments that perform the same computation, but implemented through different syntactic variants.} \cite{roy2007survey}.
+Type 4 clones are defined as \textit{two or more code fragments that perform the same computation but implemented through different syntactic variants.} \cite{roy2007survey}.
 We think that there are relevant research opportunities in refactoring type 4 clones.
@@
 \subsection{Naming of refactored methods/classes/etc.}
-In this study, we took naming of refactored entities out of the scope.
-We applied automated refactoring to duplication, and gave all generated methods, classes and interfaces generated names.
+In this study, we took the naming of refactored entities out of the scope.
+We applied automated refactoring to duplication and gave all generated methods, classes and interfaces generated names.
 For our purposes that was not much of an issue, because of the validation methods used.
@@
 
-When using our work with the purpose of refactoring assistance, these names will have to be manually provided.
+When using our work for refactoring assistance, these names will have to be manually provided.
 However, recent studies allow assistance in this process by generating a name that matches the body of a declaration.
-If this can be done in a reliable way, we can apply refactorings without any manual steps required.
+If this can be done reliably, we can apply refactorings without any manual steps required.
 
@@
 \cite{allamanis2015suggesting} proposes a machine learning model that can suggest accurate method and class names.
-This study shows promising results towards generating method and class names on the basis of their body and context.
-However, the source code of this study in not available, making it harder to apply their findings to generate class and method names for any software project.
+This study shows promising results towards generating method and class names based on their body and context.
+However, the source code of this study is not available, making it harder to apply their findings to generate class and method names for any software project.
 
@@
 Although this model is still far from perfect, combining it with our research could already greatly reduce the manual refactoring effort required.
-The main deficiency of this model lies in that its limited to the method body and does currently not consider anything else in a method body.
-This method is flawed, because the meaning of method bodies depends heavily on their context.
+The main deficiency of this model lies in that it's limited to the method body and does currently not consider anything else in a method body.
+This method is flawed because the meaning of method bodies depends heavily on their context.
 For instance, the body of the method \texttt{get()} in \texttt{ArrayList} does not make any sense in relation to its name without considering its context (class, inheritance hierarchy, etc.).
@@
 \subsection{Looking into other languages/paradigms}
-In this study we describe duplicate code refactoring opportunities for object-oriented languages. We built a tool to refactor code clones in Java and used it to run our experiments.
+In this study, we describe duplicate code refactoring opportunities for object-oriented languages. We built a tool to refactor code clones in Java and used it to run our experiments.
 
@@
 
-In this study we focused only on the object-oriented paradigm because of the shared concepts.
+In this study, we focused only on the object-oriented paradigm because of the shared concepts.
 However, the problems that come with duplication in source code also appears in different programming languages.
 Because of that, more insights could be obtained when looking into automated refactoring opportunities for other paradigms.
-For instance, it might be valuable to look into the opportunities to reduce duplication in the functional domain.
+For instance, it might be valuable to look into opportunities to reduce duplication in the functional domain.
 Dealing with code clones in the functional paradigm is largely an unexplored field and might hold valuable results.

### 2019-08-25 sections/abstract.tex
Abstract

@@
 
-We address this shortcoming by first analyzing what data should be gathered from an automatically refactored system.
-We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them.
+We address this shortcoming by combining automated refactoring and maintainability metrics to measure the impact of refactoring code clones.
+We propose definitions of clones that can be automatically refactored.
+We then propose a tool to detect such clones, analyze their context and automatically refactor a subset of them.
 We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system.
@@
 We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use.
-We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a volume 68 or more tokens improve maintainability when refactored.
-The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the refactored method should not have more than 2 arguments.
+We find that the size of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total volume of 68 or more tokens improve maintainability when refactored.
+The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the refactored method should not have more than 1 parameter.

### 2019-08-25 sections/introduction.tex
Introduction

@@
 
-Duplication in source code, also known as ``code clones'', is often seen as one of the most harmful types of technical debt.
+Duplication in source code, also known as ``code clones'', is often seen as one of the most harmful types of technical debt \cite{fowler1999refactoring}.
 If the clone is altered at one location to correct an erroneous behavior, you cannot be sure that this correction is applied to all the cloned code as well \cite{ostberg2014automatically}.
-Additionally, the codebase size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work, as code clones can contribute up to 25\% of the code size \cite{bruntink2005use}.
+Additionally, the size of the codebase increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work, as code clones can contribute up to 25\% of the code size \cite{bruntink2005use}.
 
 Automating the refactoring process of code clones can help to deal with duplication problems.
-It can also assist in the evaluating whether refactoring a specific clone would improve the codebase, by using established metrics \cite{heitlager2007practical} to determine whether the code after applying the refactoring has improved.
-Howeverm clones detected on basis of established clone definitions \cite{roy2007survey} may not always be suitable for automated refactoring.
+It can also assist in the evaluation whether refactoring a specific clone would improve the codebase, by using established metrics \cite{heitlager2007practical} to determine whether the code after applying the refactoring has improved.
+However, clones detected on the basis of established clone definitions \cite{roy2007survey} may not always be suitable for automated refactoring.
 
@@
 We use software maintainability metrics to measure the impact of these refactorings.
-We also look into what variability we can allow between code fragments to still consider them clones, while still improving maintainability when refactoring these clones.
+We also look into what variability we can allow between code fragments while still improving maintainability when refactoring these clones.
 Furthermore, we look into the thresholds that should be used while detecting clones to find clones that should be refactored.
@@
 With these experiments, we map the context of clones: where they reside in the codebase and what the relation is between duplicate fragments.
-We use the results to find appropriate refactoring opportunities for specific clones.
-We then automate the process of applying such refactorings, to be able to measure the impact on maintainability when refactoring clones found by certain definitions and thresholds.
+We use the results to find appropriate refactoring opportunities for clones in a specific context.
+We then automate the process of applying such refactorings, to measure the impact on maintainability when refactoring clones found by certain definitions and thresholds.
 
@@
 \cite{bavota2012does} shows that the process of refactoring often leaves side effects in the code.
-This study reports that refactorings moving components in the inheritance hierarchy of object-oriented software tend to induce faults very frequently.
+This study reports that refactoring techniques to remove duplicate code tend to cause faults very frequently.
 This suggests that more accurate code inspection or testing activities are needed when such refactoring techniques are performed.
-Those refactoring techniques often have to be used when dealing with duplication in software \cite{fowler2018refactoring, fontana2015duplicated}.
 Because of that, refactoring code clones has been empirically shown to cause bugs or other side effects in code.
@@
 To do this, we use a practical model consisting of metrics to measure maintainability \cite{heitlager2007practical}.
-Based on this, we look into what \textit{thresholds} result in better maintainable code when refactored.
+Based on this, we look into what \textit{thresholds} to use to find clones that result in better maintainable code when refactored.
 This results in our final research question:
@@
 assisting in the refactoring process.
-The problem is that these tools have no insight in the impact of refactoring such clones on the maintainability of the software.
+The problem is that these tools have no insight into the impact of refactoring such clones on the maintainability of the software.
 In this study, we can analyze a before- and after-refactoring snapshot of the code to determine the impact.
@@
 \subsection{Naming Declarations}
-Our automated refactoring model can create new methods, classes and interfaces when refactoring clones.
+Our automated refactoring tool can create new methods, classes, and interfaces when refactoring clones.
 Each of these declarations needs to have a name.

### 2019-08-25 sections/introduction.tex
Introduction again

@@
 To do this, we combine knowledge from literature with our own experience to develop definitions for refactorable clones.
-We also develop a tool to detect, analyze and refactor such clones.
-Using this tool, we perform \textbf{quantitative} experiments in which we statistically collect information about duplication in open-source software.
+We also develop a tool to detect, analyze, and refactor such clones.
+Using this tool, we perform \textbf{quantitative} experiments in which we collect statistical information about duplication in open-source software.
 In these experiments, we control several variables to see their impact on the results.
@@
 Many studies report that code clones negatively affect maintainability \cite{heitlager2007practical, monden2002software, juergens2009code, chatterji2013effects}.
-However, no studies yet show in what cases code clones can reduce maintainability in source code.
-Refactoring often includes tradeoffs between design alternatives.
-With some code clones, the refactored alternative is less maintainable than keeping the duplication \cite{kapser2006cloning, aversano2007clones, hotta2010duplicate, kim2005empirical, krinke2007study, saha2010evaluating}.
-In this study, we analyze the maintainability of refactored code clones to improve the suggestion of code clones that should be refactored.
-This assists with both the identification and refactoring of code clones.
+However, no studies yet show in what cases clones can reduce maintainability in source code.
+Refactoring often includes trade-offs between design alternatives.
+With some clones, the refactored alternative is less maintainable than keeping the duplication \cite{kapser2006cloning, aversano2007clones, hotta2010duplicate, kim2005empirical, krinke2007study, saha2010evaluating}.
+In this study, we analyze the maintainability of refactored clones to improve the suggestion of clones that should be refactored.
+This assists with both the identification and refactoring of clones.
 
@@
 The problem is that these tools have no insight into the impact of refactoring such clones on the maintainability of the software.
-In this study, we can analyze a before- and after-refactoring snapshot of the code to determine the impact.
+In this study, we analyze a before- and after-refactoring snapshot of the code to determine the impact of a refactoring.
 If the maintainability increases after refactoring, this gives a strong indication that the clone should be refactored.
@@
 The tool that results from this research can assist in the process of applying refactorings to clones.
-The tool will only apply a refactoring if the clone is refactorable and the maintainability of the source code increases as a result of applying the refactoring.
-The tool applies only refactorings that do not, in any way, influence the functional correctness of the program.
-Because of this, potential bugs as a result of refactoring can be avoided \cite{bavota2012does}.
+The tool only applies a refactoring if the clone is refactorable and the maintainability of the source code increases as a result of applying the refactoring.
+Furthermore, the tool applies only refactorings that do not influence the functional correctness of the program.
+Because of this, potential bugs as a result of manual refactoring can be avoided \cite{bavota2012does}.
 
@@
 In this study, we perform research efforts to be able to detect refactorable clones.
-We will apply refactoring techniques to a subset of these clones and analyze the maintainability of the resulting source code.
+We apply refactoring techniques to a subset of these clones and analyze the maintainability of the resulting source code.
 
@@
 We consider the maintainability scores described in that paper as a sufficiently accurate indication of maintainability.
-This will be used to quantitatively determine the impact on maintainability when applying refactoring techniques to code clones.
+We use this to quantitatively determine the impact on maintainability when applying refactoring techniques to code clones.
 
@@
 Because the quality of the name will not have an impact on the maintainability metrics we use, finding appropriate names for automatically refactored code fragments is out of the scope for this study.
-For our automated refactoring efforts, we will use generated names for these declarations.
-%This may decrease the usefulness of the results of this research for refactoring-assistance.
+For our automated refactoring efforts, we use generated names for these declarations.
 
@@
 The findings of this research may apply to test classes, but we will not argue the validity.
-Furthermore, any other code than the production code of the system will not be taken into account.
+Furthermore, any other code than the production code of the system will not be taken into account in our experiments.
 In Section~\ref{chap:corpus} we describe what classes we perform our experiments on.
@@
 We also propose a set of clone type definitions that strive to solve these shortcomings.
-In Chapter~\ref{ch:clonerefactor} we propose a tool to detect, analyze and automatically refactor such clones that can be refactored.
+In Chapter~\ref{ch:clonerefactor} we propose a tool to detect, analyze, and automatically refactor such clones that can be refactored.
 Using this tool we perform a set of experiments, of which the setup is explained in Chapter~\ref{ch:experimentalsetup}.

### 2019-08-25 sections/background.tex
Small thesis chnages
Background

@@
 For this study, we mainly use the definitions from Bruntink et al.
-\cite{bruntink2005use}, Roy et al.
-\cite{roy2007survey} and Jiang et al.
+\cite{bruntink2005use} and Jiang et al.
 \cite{jiang2007deckard}.
@@
 The terms displayed in this table show how tokens in code map to clones.
+When detecting clones of a software system, we end up with a clone class collection.
+Each clone class denotes a set of duplicate fragments.
+We call these duplicate fragments clone instances.
+Each clone instance spans a number of statements/declarations.
+We refer to these statements and declarations as ``nodes''.
+Each node consists of a set of tokens.
 
@@
 \centering
-\resizebox{\textwidth}{!}{%
+%\resizebox{\textwidth}{!}{%
 \begin{tabular}{@{}lllll@{}}
@@
 \rowcolor[HTML]{FFFFFF}
-\textbf{Symbol} & \textbf{Meaning} & \textbf{Definition} & \textbf{Description} & \textbf{Properties} \\ \midrule
+\textbf{Symbol} & \textbf{Meaning} & \textbf{Definition} & \textbf{Description} \\ \midrule
 \rowcolor[HTML]{EFEFEF}
-T & Token & - & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code.
-\\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Category (C):} Identifier, Keyword,\\Literal, Separator, Operator,\\ Comment or Whitespace.\end{tabular} \\
+T & Token & - & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code. \\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} \\
 \rowcolor[HTML]{FFFFFF}
-N & Node \cite{jiang2007deckard} & Set of tokens.
-& \begin{tabular}[c]{@{}l@{}}A statement or declaration node\\in the AST of a codebase.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range (R):} Begin line/column and end\\line/column of this node.\end{tabular} \\
+N & Node \cite{jiang2007deckard} & Set of tokens. & \begin{tabular}[c]{@{}l@{}}A statement or declaration node\\in the AST of a codebase.\end{tabular}  \\
 \rowcolor[HTML]{EFEFEF}
-I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use, roy2007survey}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\nodes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{File (F):} The file in which this\\clone instance is found.\end{tabular} \\
+I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\nodes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} \\
 \rowcolor[HTML]{FFFFFF}
-C & Clone class \cite{bruntink2005use, roy2007survey}& \begin{tabular}[c]{@{}l@{}}Set of clone\\instances.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations.
-Each of these\\code fragments is called a\\``clone instance''.\end{tabular} & - \\
+C & Clone class \cite{bruntink2005use}& \begin{tabular}[c]{@{}l@{}}Set of clone\\instances.\end{tabular} & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations.
+Each of these\\code fragments is called a\\``clone instance''.\end{tabular} \\
 \rowcolor[HTML]{EFEFEF}
-S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\classes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} & - \\
+S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection \cite{bruntink2005use}\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\classes.\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} \\
 \rowcolor[HTML]{FFFFFF}
@@
 \end{tabular}%
-}
+%}
 \caption{Clone related terminology and how it maps to the source code.}
@@
 The other clone instance has three clone instances and consists of two nodes per instance.
+
+This example can be represented as a tree structure, as shown in Figure~\ref{fig:terminologyexample}.
+This example uses the terminology introduced in Table~\ref{tab:clone-terminology}, together with some properties of clone instances and nodes.
+Each clone instance has a \textbf{range}, which denotes the line and column at which a code fragment starts and ends.
+Each clone instance is found in a certain \textbf{file}.
 
@@
 \end{parcolumns}
-\caption{Two clone classes: One clone class with three clone instances and one with two clone instances.}
+\caption{Example of two clone classes.}
 \label{fig:cloneclasses}
@@
 
-This example can be represented as a tree structure, as shown in Figure~\ref{fig:terminologyexample}.
-
 \begin{figure}[H]
   \includegraphics[width=1\columnwidth]{img/TerminologyExample}
-  \caption{Representation of Figure~\ref{fig:cloneclasses} using the terminology introduced in Table~\ref{tab:clone-terminology}}
+  \caption{Tree representation of Figure~\ref{fig:cloneclasses} using the terminology of Table~\ref{tab:clone-terminology}}
   \label{fig:terminologyexample}
@@
 He describes several techniques to deal with duplication, dependent on the context of the clone.
-In this section we describe the methods that we use in this study.
+In this section we describe the techniques that we use in this study.
 
@@
 This way its possible to refactor both fully cloned methods (by just pulling up the method) and partially cloned methods (by first performing method extraction and then pulling up the refactored method).
-Anexample of this refactoring method is shown in Figure~\ref{fig:pullupmethod}.
+An example of this refactoring technique is shown in Figure~\ref{fig:pullupmethod}.
 
@@
 \subsubsection{Providing default implementations for common functionality}
-In Java, C\#, Python and possibly other object-oriented languages, the programmer can create interfaces of which a class can implement any number.
+In Java, C\#, Python, and possibly other object-oriented languages, the programmer can create interfaces of which a class can implement any number.
 Such interfaces can (in Java, C\# and Python) provide default implementations for common functionality \cite{mohnen2002interfaces}.
@@
 %\subsection{Clone refactoring in relationship to its context}
-% TODO: Sander - Deze subsectie lijkt hier niet helemaal op zn plek
 %How to refactor clones is highly dependent on their context.
@@
 \subsection{Maven}
-For this study we perform a shallow analysis on external dependencies, in order to derive more context for internally used concepts.
+For this study we perform an analysis on external dependencies, to derive more context for internally used concepts.
 As these external dependencies are most often not included in a software systems' source code, we must first use the projects' build automation system to gather the dependencies.

### 2019-08-25 sections/background.tex
Background again

@@
 \label{ch:background}
-In this chapter we define some basic terminology that is used throughout this thesis.
+In this chapter, we define some basic terminology that is used throughout this thesis.
 
@@
 A summary of these concepts can be found in Table~\ref{tab:clone-terminology}.
-The terms displayed in this table show how tokens in code map to clones.
+The terminology displayed in this table shows how tokens in code map to clones.
 When detecting clones of a software system, we end up with a clone class collection.
@@
 We call these duplicate fragments clone instances.
-Each clone instance spans a number of statements/declarations.
+Each clone instance spans several statements/declarations.
 We refer to these statements and declarations as ``nodes''.
@@
 Some clone detection tools detect ``clone pairs'' instead, which consider each pair of clone instances separately.
-There are different reasons in literature whether clone pairs or clone classes should be considered for detection.
+There are different arguments in the literature whether clone pairs or clone classes should be considered for detection.
 
@@
 \begin{displayquote}
-\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
-\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
-\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.
+\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout), and comments.\\
+\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout, and comments.\\
+\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.
 \end{displayquote}
-A higher type of clone means that it's harder to detect and refactor.
-There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
-
-%\subsection{Type 4 clones}
-%For this study we have chosen to take type 4 clones out of the scope, because they are both hard to detect and hard to refactor. % TODO: Sander - why is this the case?
-%A study by Kodhai et al \cite{kodhai2013method} looks into the distribution of the different types of clones in several open source systems (see table 6 of his study).
-It becomes apparent that type 4 clones exist way less in source code than all of the other types of clones.
-For instance, for the J2sdk-swing system he finds 8115 type 1 clones, 8205 type 2 clones, 11209 type 3 clones and only 30 type 4 clones.
-Because of that, we can conclude that type 4 clones are relatively less relevant to study.
-% TODO: Sander - Deze subsectie wil ik wel even over hebben, loopt niet helemaal lekker maar niet zo makkelijk uit te leggen
+A higher type of clone means that it is harder to detect and refactor.
+Many studies adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
 
@@
 He describes several techniques to deal with duplication, dependent on the context of the clone.
-In this section we describe the techniques that we use in this study.
+In this section, we describe the techniques that we use in this study.
 
@@
 This way, if cloned methods are related in any way through inheritance, they can be called by both classes by placing the method in a class they both have in common.
-This way its possible to refactor both fully cloned methods (by just pulling up the method) and partially cloned methods (by first performing method extraction and then pulling up the refactored method).
+This way it is possible to refactor both fully cloned methods (by just pulling up the method) and partially cloned methods (by first performing method extraction and then pulling up the refactored method).
 An example of this refactoring technique is shown in Figure~\ref{fig:pullupmethod}.
@@
 If two classes have many of these implicit relations, then the implementation should be refactored to make this relation explicit \cite{fowler2018refactoring}.
-If the classes do not yet have a parent/super class, a parent class can be created and the common functionality can be placed in this newly created class.
-This makes the relation between these classes explicit and reduces duplication.
+If the classes do not yet have a parent/superclass, a parent class can be created and the common functionality can be placed in this newly created class.
+This makes the relationship between these classes explicit and reduces duplication.
 
@@
 In Java, C\#, Python, and possibly other object-oriented languages, the programmer can create interfaces of which a class can implement any number.
-Such interfaces can (in Java, C\# and Python) provide default implementations for common functionality \cite{mohnen2002interfaces}.
-This gives an opportunity to make the relation between classes explicit and reduce duplication.
+Such interfaces can (in Java, C\#, and Python) provide default implementations for common functionality \cite{mohnen2002interfaces}.
+This allows making the relation between classes explicit and reduce duplication.
 It can be used in instances where creating a new parent class for duplicated classes is undesirable.
-An example of this is shown in Figure~\ref{fig:createinterfaceabstraction}, in which two unrelated types (Human and Radio) share a common property (making sound).
+An example of this is shown in Figure~\ref{fig:createinterfaceabstraction}, in which two unrelated types (Human and Radio) share a common property (making a sound).
 
@@
 
-%\subsection{Clone refactoring in relationship to its context}
-%How to refactor clones is highly dependent on their context.
-Method-level clones can be extracted to a method \cite{kodhai2013method} if all occurrences of the clone reside in the same class.
-If a method level clone is duplicated among classes in the same inheritance structure, we might need to pull-up a method in the inheritance structure.
-If instances of a method level clone are not in the same inheritance structure, we might need to either make a static method or create an inheritance structure ourselves.
-So not only a single instance of a clone has a context, but also the relationship between individual instances in a clone class.
-This is highly relevant to the way in which the clone has to be refactored.
-
 \section{Internal and external classes}
@@
 Regarding refactoring, a software system can often not change the source code of its dependencies.
-This can sometimes be a burden, when an external dependency does not use proper abstractions that are required by a software system.
-In this study we take external classes into consideration when choosing a refactoring technique, to be sure not to modify them.
+This can be a burden when an external dependency does not use proper abstractions that are required by a software system.
+In this study we consider external classes when choosing a refactoring technique, to be sure not to modify them.
 
 \subsection{Maven}
-For this study we perform an analysis on external dependencies, to derive more context for internally used concepts.
+For this study we perform an analysis of external dependencies, to derive more context for internally used concepts.
 As these external dependencies are most often not included in a software systems' source code, we must first use the projects' build automation system to gather the dependencies.
@@
 \section{(Object-Oriented) Programming Languages}
-This section explains concepts, terminology and jargon of (object-oriented) programming languages that we use in this study.
+This section explains concepts, terminology, and jargon of (object-oriented) programming languages that we use in this study.
 
 \subsection{AST} \label{sec:astbackground}
-An Abstract Syntax Tree (AST) is a tree consisting of an hierarchical representation of the source code of a program.
+An Abstract Syntax Tree (AST) is a tree consisting of a hierarchical representation of the source code of a program.
 Detecting code clones on the AST of a program allows for a deeper understanding of the concepts that are being analyzed.
@@
 The use of inheritance to group common functionality and data is called ``Abstraction''.
-Duplication in source code can be a result of an inadequate use of abstraction.
+Duplication in source code can be a result of inadequate use of abstraction.
 Because of that, refactoring code clones might require to create such abstractions of common functionality.
@@
 Different programming languages have different ways to measure code quality.
-For object-oriented programming languages this largely comes in the form of code smells (patterns that should be avoided) and design patterns (patterns which may improve code design and comprehensibility when used correctly).
+For object-oriented programming languages, this largely comes in the form of code smells (patterns that should be avoided) and design patterns (patterns which may improve code design and comprehensibility when used correctly).
 
 \subsubsection{Code Smells}
-Code smells are patterns in code that should be avoided, because they have a negative effect on system design.
+Code smells are patterns in code that should be avoided because they harm system design.
 Duplicate code is, among many others, one example of a code smell.
-Having many code smells present in source code can significantly increase maintainence costs of the source code or even render a software system unmaintainable.
+Having many code smells present in source code can significantly increase the maintenance costs of the source code or even render a software system unmaintainable.
 This increases technical debt: a debt present in the system the will have to be repaid at a later point of time.
-Such technical debt often comes at the expense of developing new features, fixing bugs and other aspects surrounding a programs functional behaviour.
+Such technical debt often comes at the expense of developing new features, fixing bugs and other aspects surrounding the functional behavior of a program.
 
@@
 \cite{heitlager2007practical} propose a maintainability model that categorize the results of metrics into different ``score'' categories.
-For instance, with duplication, if 0-3\% of the project is duplicated, the project will get the highest score on a scale of 1 to 5 (only integers, no floating point numbers).
+For instance, with duplication, if 0-3\% of the project is duplicated, the project will get the highest score on a scale of 1 to 5 (only integers, no floating-point numbers).
 Such a maintainability model is intuitive for measuring the quality of a software system, especially large software systems with a lot of source code to base the metrics on.
@@
 Often, methods don't need an entire object, but just use a few properties of it.
-Because of that, Java recommends to program to an interface rather than an implementation.
+Because of that, Java recommends programming to an interface rather than an implementation.
 This means that we should use abstractions of expected functionality rather than complete implementations of functionality.
@@
 
-Often, duplication is the result of an inappropriate use of abstractions.
-Two methods might describe operations on types following the same contract, but because of a lack of abstraction the programmer may choose to clone such methods.
+Often, duplication is the result of inappropriate use of abstractions.
+Two methods might describe operations on types following the same contract, but because of a lack of abstraction, the programmer may choose to clone such methods.
 This will result in duplicated methods with minor modifications to match a different implementation.
@@
 For instance, all UI logic in an application might go into the ``ui'' package.
-The ``ui'' package can have a subpackage named ``keyhandling'' for all keyhandling operations.
+The ``ui'' package can have a subpackage named ``keyhandling'' for all keyboard input related operations.
 These packages contain package-level declarations, like classes and interfaces.
 Names of class-level declarations must be unique within the package.
-However, duplicate declaration names may exists in subpackages and parent packages.
+%However, duplicate declaration names may exist in subpackages and parent packages.
 
@@
 Importing a declaration from outside the current package goes by the fully qualified identifier (FQI) of the declaration.
-The FQI of a declaration gives an unique identifier for a symbol in a codebase.
+The FQI of a declaration gives a unique identifier for a symbol in a codebase.
 For instance, if our ``keyhandling'' package would contain a ``KeyHandler'' class, its fully qualified identifier would be ``ui.keyhandling.KeyHandler''.

### 2019-08-25 sections/background.tex
Background again again

@@
 Classes are the components of a software system that contain its functionality.
-When analyzing a software system, \textit{Internal classes} are classes that belong to this software system specifically, and its source code is included in the project.
+When analyzing a software system, \textit{Internal classes} are classes that belong to this software system specifically, and their source code is included in the project.
 
 \textit{External classes} are classes that a software system uses but do not belong to this specific software system (but to an external dependency).
-Most often these external dependencies are referenced in a file that its build automation system uses to fetch a projects' dependencies.
+Most often these external dependencies are referenced in a file that its build automation system uses to fetch these external libraries.
 
@@
 This can be a burden when an external dependency does not use proper abstractions that are required by a software system.
-In this study we consider external classes when choosing a refactoring technique, to be sure not to modify them.
+In this study, we consider external classes when choosing a refactoring technique, to be sure not to modify them.
 
 \subsection{Maven}
-For this study we perform an analysis of external dependencies, to derive more context for internally used concepts.
+In this study, we perform an analysis of external dependencies, to derive more context for internally used concepts.
 As these external dependencies are most often not included in a software systems' source code, we must first use the projects' build automation system to gather the dependencies.
@@
 Maven has a simple ecosystem to configure and fetch the binaries and source code of all software projects a given codebase is dependent on.
-Maven can also be used to run tests for the systems and to package the project as an executable file.
+Maven can also be used to run unit tests and to package a project as an executable file.
 
@@
 
-The AST consists of nodes of the following types (examples are for Java):
+The AST consists of nodes of the following types \cite{tomassetti2017javaparser}:
 \begin{itemize}
@@
 Duplicate code is, among many others, one example of a code smell.
-Having many code smells present in source code can significantly increase the maintenance costs of the source code or even render a software system unmaintainable.
-This increases technical debt: a debt present in the system the will have to be repaid at a later point of time.
-Such technical debt often comes at the expense of developing new features, fixing bugs and other aspects surrounding the functional behavior of a program.
+Having many code smells present in source code can significantly increase the maintenance costs of the source code or even render a software system unmaintainable \cite{heitlager2007practical}.
+This increases technical debt: a debt present in the system the will have to be repaid at a later point of time \cite{tom2013exploration}.
+Such technical debt often comes at the expense of developing new features, fixing bugs and other aspects surrounding the functional behavior of a program \cite{kruchten2012technical}.
 
@@
 Maintainability metrics are features of source code by which an indication of the maintainability of the source code can be measured.
-Heitlager at al.
-\cite{heitlager2007practical} propose a maintainability model that categorize the results of metrics into different ``score'' categories.
-For instance, with duplication, if 0-3\% of the project is duplicated, the project will get the highest score on a scale of 1 to 5 (only integers, no floating-point numbers).
+Heitlager et al.~\cite{heitlager2007practical} propose a maintainability model that categorize the results of metrics into different risk profiles.
+For instance, with duplication, if 0-3\% of the project is duplicated, the project will get the highest score on a scale of 1 to 5.
 Such a maintainability model is intuitive for measuring the quality of a software system, especially large software systems with a lot of source code to base the metrics on.
-However, this maintainability model \cite{heitlager2007practical} lacks in measuring fine-grained changes: most small changes will not fall into a different category.
+However, this maintainability model~\cite{heitlager2007practical} lacks in measuring fine-grained changes: most small changes will not fall into a different category.
 Because of that, this model is less suitable for measuring the impact of single refactorings.
@@
 These are explained in this section.
-Many of these concepts also exist in other programming languages, but often not in all.
+Many of these concepts also exist in other programming languages.
 
@@
 Java uses the concept of interfaces to loosely couple a specification and its implementation.
-Interfaces are specifications about what a (group of) objects do.
+Interfaces are specifications of what a (group of) objects do.
 Often, methods don't need an entire object, but just use a few properties of it.
@@
 Two methods might describe operations on types following the same contract, but because of a lack of abstraction, the programmer may choose to clone such methods.
-This will result in duplicated methods with minor modifications to match a different implementation.
+This will result in duplicated methods with minor modifications to fit a different context.
 Such duplicates can be mitigated by using proper abstractions, of which one option is to program methods against interfaces (contracts of expected functionality) rather than their full implementations.
@@
 \subsubsection{Packages}
-Packages (sometimes called ``modules'' in other programming languages) are hierarchical groupings of related concepts.
+Packages (called ``modules'' in some other programming languages) are hierarchical groupings of related concepts.
 For instance, all UI logic in an application might go into the ``ui'' package.
 The ``ui'' package can have a subpackage named ``keyhandling'' for all keyboard input related operations.
-These packages contain package-level declarations, like classes and interfaces.
-Names of class-level declarations must be unique within the package.
+These packages contain type declarations, like classes and interfaces.
+The names of these type declarations must be unique within the package.
 %However, duplicate declaration names may exist in subpackages and parent packages.
@@
 Importing a declaration from outside the current package goes by the fully qualified identifier (FQI) of the declaration.
-The FQI of a declaration gives a unique identifier for a symbol in a codebase.
-For instance, if our ``keyhandling'' package would contain a ``KeyHandler'' class, its fully qualified identifier would be ``ui.keyhandling.KeyHandler''.
+The FQI of a declaration is the unique identifier of a type declaration in a codebase.
+For instance, if the ``keyhandling'' package would contain a ``KeyHandler'' class, its fully qualified identifier would be ``ui.keyhandling.KeyHandler''.
 
 \subsubsection{Visibility}
-In Java, we can protect declarations from being used in scopes in which they are supposed to be used.
+In Java, we can protect declarations from being used in scopes in which they are not supposed to be used.
 If a method should only be used within the class itself, we can give it a ``private'' visibility.
@@
 If a method is supposed to be part of the public contract of an object, we can set it to ``public'' visibility.
-Alternatively, there is ``package'' visibility, for declarations that should only be referenced within the same package.
+If a method should be accessible to all types in its package, we can give it a ``package'' visibility.
 This allows control over what parts of an application should be able to access what declarations.

### 2019-08-25 sections/research.tex
Research

@@
 \chapter{Defining refactoring-oriented clone types}\label{chap:clonetypes}
-Clone type 1-3 (see Section~\ref{chap:backgroundclonetypes}) can (and should) not always be automatically refactored.
-In Section~\ref{sec:literaturetypeproblems} we list shortcomings of each clone type that invalidate refactoring opportunities.
+Clone type 1-3 (see Section~\ref{chap:backgroundclonetypes}) cannot always be automatically refactored.
+In Section~\ref{sec:literaturetypeproblems} we list shortcomings of each clone type that invalidate automated refactoring opportunities.
 In Section~\ref{sec:rtypes} we propose new clone type definitions that address these shortcomings.
@@
 This allows for the detection of clones that are the result of copying and pasting existing code, along with other reasons why duplicates might get into a codebase.
-
-Type 1 clones are implemented as textual equality between code fragments (except for whitespace and comments) by most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating}.
-Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type.
-In such cases, refactoring opportunities could be invalidated.
-This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
-%When aiming to automatically refactor clones, applying refactorings to type 1 clones is bound to be error-prone and can result in an uncompilable project or a difference in functionality.
 
@@
 \end{figure}
+
+Type 1 clones are implemented as textual equality between code fragments (except for whitespace and comments) by most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating}.
+Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type.
+In such cases, refactoring opportunities could be invalidated.
+This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
 

### 2019-08-25 sections/research.tex
Research again

@@
 	public void addTen(int x) {
-|\highlightYellow|		x = x + 10;
+|\highlightYellow|		x = x + 10; // add number
 |\highlightYellow|		Notifier.notifyChanged(x);
@@
 	public void concatTen(String x) {
-|\highlightYellow|		x = x + 10;
+|\highlightYellow|		x = x + 10; // concat string
 |\highlightYellow|		Notifier.notifyChanged(x);
@@
 
-Type 1 clones are implemented as textual equality between code fragments (except for whitespace and comments) by most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating}.
-Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type.
+Most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating} detect type 1 clones by textually comparing code fragments (except for whitespace and comments).
+Although textually equal, method, type and variable references can still refer to different declarations.
 In such cases, refactoring opportunities could be invalidated.
@@
 Figure~\ref{fig:type1} shows a type 1 clone with two clone classes.
-Defining an automatic way to refactor these clone classes is nearly impossible, as both cloned fragments describe different functional concepts.
+Defining an automatic way to refactor these clone classes is nearly impossible, as both cloned fragments describe different functional behavior.
 The first cloned fragment is a method that adds something to a \texttt{List}.
@@
 
-The second cloned fragment shows how equally named variables can have different types and thus yield different functional concepts.
+The second cloned fragment shows how equally named variables can have different types and thus perform different functional concepts.
 The cloned fragment on the left adds a specific amount to an integer.
@@
 Type 3 clones are \textit{copied fragments with further modification (with added, removed or changed statements)}~\cite{roy2007survey}.
-Detection of clones by this definition can be hard, as it may be hard to detect whether a fragment was copied in the first place if it was severely changed.
+Detection of clones by this definition can be hard, as it may be hard to statically detect whether a fragment was copied in the first place if it was severely changed.
 Because of this, most clone detection implementations of type 3 clones work based on a similarity threshold~\cite{roy2008nicad,ragkhitwetsagul2019siamese,jiang2007deckard,semura2017ccfindersw}.
@@
 \section{Refactoring-oriented clone types}\label{sec:rtypes}
-To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types directed at detecting clones that can and should be refactored.
-We have named these clones type 1R, 2R, and 3R clones.
+To resolve the shortcomings of clone types as outlined in the previous section, we propose alternative definitions for clone types directed at detecting clones that can be automatically refactored.
+We name these clones type 1R, 2R, and 3R clones.
 These definitions address the outlined shortcomings of the corresponding literature definitions.
@@
 The implementation of these methods might differ.
-When two code fragments call methods with an identical name or signature, they can call different methods.
+When two code fragments call methods with an identical name or signature, they can still call different methods.
 Because of this, textually identical code fragments can differ functionally.
@@
 
-For type 1R clones variable references should be compared by both type and name.
+For type 1R, cloned variable references are compared by both their name and the FQI of their type.
 
@@
 \begin{itemize}
-  \item We allow a difference in identifiers between cloned fragments if it has no impact on the refactoring process.
-  \item We allow a difference in expressions between cloned fragments if the expression can be extracted to a method argument when applying the ``Extract Method'' refactoring.
+  \item We allow a difference in identifiers between cloned fragments if it does not introduce a trade-off in the refactoring process of the clone.
+  \item We allow a difference in expressions between cloned fragments if the expression can be extracted to a method parameter when applying the ``Extract Method'' refactoring.
 \end{itemize}
 
-Allowing variability between expressions includes a tradeoff.
-When many expressions vary between cloned the refactored method might require many additional arguments.
+Allowing variability between expressions introduces a design trade-off.
+When many expressions vary between cloned fragments, the refactored method might require many additional parameters, which is detrimental for system design \cite{heitlager2007practical}.
 Because of that, we constrain this variability by a threshold, which is explained in more detail in Section~\ref{sec:variabilitythreshold}.%to limit the negative effect on system design of variability in these expressions after refactoring.
@@
 When refactored, some identifiers have no detrimental effect on the design if they vary between cloned instances.
-This section explains several patterns of variability that we can allow between cloned fragments without changing the method by which the fragments can be refactored.
+This section explains several patterns of variability that we can allow between cloned fragments without changing the design trade-off introduced by refactoring a certain clone.
 
@@
 \begin{itemize}
-  \item The cloned variables are locally defined or the refactoring method used requires extraction to method argument anyways.
+%  \item The cloned variables are locally defined or the refactoring method used requires extraction to method argument anyways.
   \item The cloned variables have the same type.
@@
 Because these variables are locally defined, the extracted method requires an extra argument for the variable anyways.
-If the second clone instances would be completely equal, so also use the same variable, the refactoring would be very similar (it would only differ by a single character).
+%If the second clone instance would be completely equal, so also use the same variable, the refactoring would be very similar (it would only differ by a single character).
 
@@
 Based on this threshold, we decide whether a clone should be considered for refactoring.
-A concrete example of applying this formula to calculate a threshold is given in \ref{sec:t2rcheckglobalthres}.
+A concrete example of applying this formula to calculate a threshold is given in Section~\ref{sec:t2rcheckglobalthres}.
 
@@
 Type 2R allows variability in the value of literals and variables, but not in their types.
-This is because a difference in literal/variable type may have a big impact on the refactorability of the cloned fragment.
-When we refactor different literals/variables that have both the same type, in case of an ``Extract Method'' refactoring, we have to create a parameter for this literal and pass the corresponding literal/variable from cloned locations.
+This is because a difference in literal/variable types may have a big impact on the refactorability of the cloned fragment.
+When we refactor different literals/variables that have the same type using the ``Extract Method'' technique, we have to create a parameter for this literal/variable and pass the corresponding literal/variable from cloned locations.
 However, if two literals have different types, this might not be possible (or will harm the design of the system).
-This is because a lot of variability in literals will result in more parameters required in the extracted method, which is detrimental for the design of the system.
+%This is because a lot of variability in literals will result in more parameters required in the extracted method, which is detrimental for the design of the system.
 
@@
 void doDEF(){
-	doThis(s, "def");
+	doThis("def");
 }
@@
 This helps reducing duplication, as it is possible to refactor two code fragments which differ only by a method call.
-However, a method call does often not consist of a single token (like variables and literals).
-For instance, a method call \texttt{System.out.println()} consists of several segments: a type reference to the \texttt{System} type, a reference to the static \texttt{out} field and a call of the \texttt{println()} method.
-
 Type 2R clones allow called methods to vary as long as they have the same argument types and return type.
@@
 
-The method call variability property of type 2R clones implies that type 2R clones are not a subset of type 2 clones.
-Because methods calls can have a different structure, type 2R clones can be structurally slightly different.
-The example as shown in Figure~\ref{fig:type2method} can be a type 2R clone (dependent on the thresholds used) but is not a type 2 clone.
+%However, a method call does often not consist of a single token (like variables and literals).
+For instance, a method call \texttt{System.out.println()} consists of several segments: a type reference to the \texttt{System} type, a reference to the static \texttt{out} field and a call of the \texttt{println()} method.
 
@@
 \end{figure}
+
+The method call variability property of type 2R clones implies that type 2R clones are not a subset of type 2 clones.
+Because methods calls can have a different structure, type 2R clones can be structurally slightly different (which is not allowed by type 2 clones).
+The example as shown in Figure~\ref{fig:type2method} can be a type 2R clone (dependent on the thresholds used) but is not a type 2 clone.
 
@@
 This statement is found in between cloned lines.
-There is a \textit{gap} of non-cloned lines in between two clone classes.
+There is a \textit{gap} of non-cloned lines in between two clone classes \cite{ueda2002detection}.
 The following rules apply to this gap:
@@
 
+Where $I_{before}$ is the clone instance preceding the gap, $I_{after}$ is the clone instance following the gap and \textit{|$I$|} is the number of nodes in the clone instance (the cardinality).
 As an example, consider the code fragment in Figure~\ref{fig:gappedclones}.
@@
 \begin{itemize}
-\item \textbf{Type 1R:} Allows no difference between cloned fragments (both functionally and textually), making it possible to refactor both fragments to a method call that contains the code of both locations.
-\\
+\item \textbf{Type 1R:} Allows no difference between cloned fragments (both functionally and textually), making it possible to automatically refactor the cloned code. \\
 \item \textbf{Type 2R:} Allows difference between cloned fragments in a controlled set of expressions.
@@
 
-Where $N_{\text{clone type}}$ is the set of cloned nodes found by the rules of the specified clone type.
-Comparing these clone type definitions to the ones used in literature, type 1R clones are a subset of type 1 clones.
-However, this subset relation does not exist for type 2R and 3R clones.
-This is because these definitions allow variability in multi-token method calls, which type 2 and type 3 do not allow.
-Because of that, the following is true for these clone types:
+Where $N_{\text{clone type}}$ is the set of cloned nodes found by the rules of the specified clone type. All cloned clones found for type 1R will also be found for type 2R and type 3R.
+
+Comparing these clone type definitions to the ones used in literature, we have the following subset relations:
 
@@
 Where $N_{\text{clone type}}$ is the set of cloned nodes found by the rules of the specified clone type.
+The reason that type 2R and type 3R are not subsets of type 2 and 3, is that type 2R and type 3R allow variability in method calls which can differ in structure.
+Type 2 and 3 do not allow such differences.
 
@@
 This comes with serious challenges, regarding both performance and implementation.
-Also, to be able to parse all fully qualified identifiers, and trace the declarations of variables, we might need to follow cross-file references.
+To be able to parse all fully qualified identifiers, and trace the declarations of variables, we might need to follow cross-file references.
 The referenced types/variables/methods might even not be part of the project, but rather of an external library or the standard libraries of the programming language.
@@
 \section{Suitability of existing Clone Detection Tools for detecting these clones} \label{ch:tool-overview}
-We conduct a short survey on (recent) clone detection tools that we can use to analyze refactorable clones.
-We choose a set of tools from three modern clone detection tool surveys \cite{roy2009comparison, svajlenko2014evaluating, sheneamer2016survey}.
-We choose only tools that are open source, to be able to extend the tool to be able to detect refactoring-oriented clone detection types.
-Furthermore, the tool must be able to analyze a popular object-oriented programming language.
-Next, we formulate the following four criteria by which we analyze these tools:
+We conduct a short survey on (recent) clone detection tools.
+We select a set of open-source tools from three modern clone detection tool surveys \cite{roy2009comparison, svajlenko2014evaluating, sheneamer2016survey}, to determine which tool is suitable for the detection of our refactoring-oriented clone types.
+We formulate the following four criteria by which we analyze these tools:
 \begin{enumerate}

### 2019-08-25 sections/clonerefactor.tex
CloneRefactor

@@
 
-Figure \ref{fig:clonerefactorprocess} shows the overall process used by CloneRefactor.
-First, we detect clones based on a Java codebase, given a Java project from disk and a configuration.
+Figure \ref{fig:clonerefactorprocess} shows the overall process used by CloneRefactor (CR).
+First, CloneRefactor detects clones based on a Java codebase, given a Java project from disk and a configuration.
 The clone detection process is further explained in Section~\ref{sec:clonedetection}.
@@
 An important design decision for CloneRefactor is the usage of a library named JavaParser \cite{tomassetti2017javaparser}.
-JavaParser is a Java library which allows parsing Java source files to an abstract syntax tree (AST\footnote{An AST is a tree representation of a source code file.}).
+JavaParser is a Java library which allows parsing Java source files to an abstract syntax tree (AST).
 JavaParser allows to modify this AST and write the result back to Java source code.
@@
 For instance, we can use it to trace references (methods, variables, types, etc) to their declarations (these referenced identifiers are also called ``symbols'').
-This is very useful for the detection of our refactoring-oriented clone types, as they make use of the fully qualified identifiers of symbols.
+This is useful for the detection of our refactoring-oriented clone types, as they make use of the fully qualified identifiers of symbols.
 
@@
 \begin{itemize}
-  \item \textbf{Minimum Number of Nodes}: The minimum amount of nodes that should be in each instance of cloned fragments for them to be considered a clone class.
-  \item \textbf{Minimum Number of Tokens}: The minimum amount of tokens that should be in each instance of cloned fragments for them to be considered a clone class.
-  \item \textbf{Minimum Number of Lines}: The minimum amount of lines that should be in each instance of cloned fragments for them to be considered a clone class.
+  \item \textbf{Minimum Number of Nodes}: The minimum amount of nodes that should be in each instance of cloned fragments for them to be considered clones.
+  \item \textbf{Minimum Number of Tokens}: The minimum amount of tokens that should be in each instance of cloned fragments for them to be considered a clones.
+  \item \textbf{Minimum Number of Lines}: The minimum amount of lines that should be in each instance of cloned fragments for them to be considered a clones.
 \end{itemize}
@@
 \section{Clone Detection}\label{sec:clonedetection}
-To detect clones, CloneRefactor parses the AST acquired from JavaParser to an unweighted graph structure.
+To detect clones, CloneRefactor parses the AST acquired from JavaParser to a graph structure.
 Based on this graph structure, clones are detected.
@@
 
-First of all, we use JavaParser to read a project from disk and build an AST, one class file at a time.
+First of all, CloneRefactor uses JavaParser to read a project from disk and build an AST, one class file at a time.
 Each AST is then converted to a directed graph that maps relations between statements, further explained in Section~\ref{sec:clonegraph}.
-Based on this graph, we detect clone classes and verify them the configured thresholds.
-If the detection was configured to detect either type 2R, 3 or 3R clones we perform some type-specific transformations on the resulting set of clones.
+Based on this graph, CloneRefactor detects clone classes and verifies them using the configured thresholds.
+If the detection was configured to detect either type 2R, 3, or 3R clones, CloneRefactor perform some type-specific transformations on the resulting set of clones.
 %\begin{itemize}
@@
 \subsection{Generating the clone graph}\label{sec:clonegraph}
-First of all, we parse the AST obtained from JavaParser into a directed graph structure.
+First of all, CloneRefactor parses the AST obtained from JavaParser into a directed graph structure.
 We have chosen to base our clone detection around statements as the smallest unit of comparison.
@@
 As a first step towards building the clone graph, we preprocess the AST to decide which AST nodes should become part of the clone graph.
-We have decided to consider declarations and statements as the smallest compared entities.
-The main reasoning for this is because considering smaller AST constructs, like expressions, significantly increases the complexity and CPU usage of our clone detection and refactoring efforts.
-
-Additionally, we exclude package declarations and import statements. These are omitted by most clone detection tools, as import statements are most often generated by the IDE.
+We exclude package declarations and import statements from this graph.
+These are omitted by most clone detection tools, as package declarations and import statements are most often generated by the IDE.
 
@@
   \item The declaration/statement preceding it.
-  \item The declaration/statement following.
+  \item The declaration/statement following it.
   \item The last \textbf{preceding} declaration/statement with which it is cloned.
@@
 The relations representing duplication are directed.
-This is a restriction we've chosen as it creates an important constraint for the clone detection process.
+%This is a restriction we've chosen as it creates an important constraint for the clone detection process.
 This process is explained in Section~\ref{sec:detectingclones}.
@@
 
-For \textbf{type 1R} clones, this comparison is a lot more advanced.
-For \textit{method calls} we trace their declaration and use its fully qualified method signature for comparison with other nodes.
-For all \textit{referenced types} we trace their declarations and use assemble their fully qualified identifier for comparison with other nodes.
-For \textit{variables} we trace their declaration and their types.
-If the variable type is a primitive we can directly use it for comparison.
-If it is a referenced type, we have to trace this type first to collect their fully qualified identifier for comparison.
+For \textbf{type 1R} clones this comparison is more advanced.
+For \textit{method calls} we determine their fully qualified method signature for comparison with other nodes.
+For all \textit{referenced types} we use their fully qualified identifier (FQI) for comparison with other nodes.
+For \textit{variables} we compare their fully qualified type in addition to their name.
 
 \textbf{Type 2R} clones allow any variation in literals, variables, and method calls at this stage in the clone detection process.
-However, for \textit{literals} we do resolve their type to verify that they are of the same type.
-For \textit{variables} we also only verify that their types are the same (but not their names).
-For \textit{method calls}, we trace their declaration but only compare the fully qualified identifier for its return type and each of its arguments' types.
-Apart from that, we do not compare the names of method, class, interface and enum declarations.
-
-In this stage, \textbf{type 3R} clones have the same compare rules as type 2R clones.
+We compare \textit{variables} by the FQI of their types but not their names.
+For \textit{method calls}, we compare the FQI of their return type and the type of each of their parameters.
+Apart from that, we do not compare the names of type declarations.
+\textbf{Type 3R} clones have the same compare rules as type 2R clones.
 

### 2019-08-25 sections/clonerefactor.tex
More CloneRefactor

@@
 After building the clone graph, we use it to detect clone classes.
-Because nodes in the clone graph link to \textit{preceding} cloned statement, the first cloned node does not have any clone relation, as no clones are preceding it (only following it).
-Because of this, we start our clone detection process at the final location encountered while building the graph.
-For this node, we collect all nodes it is cloned with.
-Even though the final node only links to the preceding node it is cloned with, we can collect all clones.
-This is because the preceding clone also has a preceding clone (if applicable) and we can follow this trail to collect all clones of a single node.
+We start our clone detection process at the final location encountered while building the graph.
 As an example, we convert the code example shown in Figure~\ref{fig:clonegraph} to a clone graph as displayed in Figure~\ref{fig:clonegraph2}.
@@
 Suppose we are finding clones for two files and the final node of the second file is a variable declarator.
-This final node is represented in the example figure by the purple box (1).
+This node is represented in the example figure by the purple box (1).
 We then follow all ``duplicate'' relations until we have found all clones of this node (2 and 3).
-We now have a single statement clone class of three clone instances (1, 2 and 3).
-
-Next, we move to the previous line (4).
+We now have a clone class of three clone instances each with a single node (1, 2 and 3).
+
+Next, we move to the \textit{previous} line (4).
 Here again, we collect all duplicates of this node (4 and 5).
@@
 In this case, this node does not have any clones.
-This means we check the (2 and 5, 1 and 4) clone class against the thresholds, and if it adheres, consider it a clone.
+This means we check the (2 and 5, 1 and 4) clone class against the thresholds, and, if it adheres, consider it a clone.
 Dependent on the thresholds, this example can result in a total of two clone classes.
@@
 If this is the case (which it is for this example), we discard the clone.
-
-\todo{Explain the complexity of the algorithm: O(n)?}
 
@@
 
-Where \textit{$S_{before}$} is the clone class collection containing all clones that are found up in until this point and \textit{$C_{new}$} is the clone class that was just found.
-\textit{$S_{after}$} is the clone class collection after
+Where \textit{$S_{before}$} is the clone class collection containing all clones that are found up in until this point, \textit{$C_{new}$} is the clone class that was just found and \textit{$S_{after}$} is the clone class collection after removing all subsets of the added clone.
 
@@
 \begin{equation}\label{eq:removeexisting}
-\{C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S\} = \emptyset \Rightarrow S_{after} = S \cup C_{new}
-\end{equation}
-
-If the newly added clone is a subset of an existing clone, we do not add it to the set of clone classes. This way we avoid redundant clone classes being detected by CloneRefactor.
-\todo{Think about an example}
+\{C_{new} \subseteq C_{existing}\text{ }|\text{ }C_{existing} \in S\} = \emptyset \Rightarrow S_{after} = S \cup C_{new}
+\end{equation}
+
+Where \textit{$S_{before}$} is the clone class collection containing all clones that are found up in until this point, \textit{$C_{new}$} is the clone class that was just found and \textit{$S_{after}$} is the clone class collection after optionally adding the newly found clone.
+If the newly added clone is a subset of an existing clone, we do not add it to the set of clone classes.
+This way we avoid redundant clone classes being detected by CloneRefactor.
 
 \subsection{Validating the type 2R variability threshold}
-In the definition of type 2R clones (see Section~\ref{sec:type2r}) we described how type 2R clones work based on a variability threshold.
+In the definition of type 2R clones (see Section~\ref{sec:type2r}), we described how type 2R clones work based on a variability threshold.
 This threshold is checked by CloneRefactor to assess the validity of found clone classes.
@@
 This equality array converts each expression to a number unique to that expression.
-Each literal, method call or variable becomes a positive number, whereas each other expression becomes a negative number.
+Each literal, method call or variable becomes a positive number, whereas each other expression/token becomes a negative number.
 An example of two code fragments converted to equality arrays is displayed in Figure~\ref{fig:equalityarrays}.
+The equality array for each of the lines in this example is shown in Table~\ref{table:equalityarrays}.
 
@@
 
-The equality array for each of the lines in this example is shown in Table~\ref{table:equalityarrays}.
-
 \begin{table}[H]
 \begin{center}
- \caption{The equality arrays in our example Figure~\ref{fig:equalityarrays}.} \label{table:equalityarrays}
- \medskip
 \begin{tabular}{|l|l|l|}
@@
 \end{tabular}
+\caption{The equality arrays in our example Figure~\ref{fig:equalityarrays}.} \label{table:equalityarrays}
 \end{center}
@@
 Using the equality arrays explained in the previous section, we can determine the variability threshold of any clone class.
-We calculate the variability of the example given in Table~\ref{table:equalityarrays} as follows:
-
-\todo{This is not correct set theory. Sets have duplicates and have an order.}
+We calculate the variability of the example given in Table~\ref{table:equalityarrays} as follows (equality arrays are represented as total order sets):
+
 \begin{equation}\label{eq:variabilityclonerefactor}
@@
 
-\todo{Usage of the word adheres is questionable here...}
 So for the example given in Figure~\ref{fig:equalityarrays} we have a variability of 75\%.
 In CloneRefactor, the maximum variability percentage is a threshold that is entered in a configuration file.
-If a clone adheres to this threshold, it will stay in the set of found clones.
-However, if it does not adhere to the thresholds, a problem arises.
-Because a clone does not adhere to the thresholds, it does not yet mean it has to be discarded.
+If a clone satisfies this threshold, it will stay in the set of found clones.
+However, if it does not, a problem arises.
+Because a clone does not satisfy the thresholds, it does not yet mean it has to be discarded.
 This is because an invalid clone class can still contain valid clones that are a subset of the invalid clone (our definition of subsets of clones is given in Section~\ref{sec:conceptualremovingredundant}).
-
-%Two nodes are considered clones of each other if the size of their equality array is equal and all negative numbers in the equality array are equal.
-When a found clone class does not adhere to the global thresholds as explained in the previous section, we need to determine whether it contains any valid subclones.
+To detect these, CloneRefactor determines whether it contains any valid subclones.
 Below, we explain a few cases of valid subclones that may exist within an invalid clone class.
@@
 However, the rest of this method does not have any variability.
-The global thresholds could indicate a too high variability and thus render this clone invalid.
+%The global thresholds could indicate a too high variability and thus render this clone invalid.
 However, in this case, it might still have a valid subclone.
@@
 This requires an extensive search for such clones.
-This problem is very related to the problem of clone detection, except now it is within the boundaries of a single clone class except for an entire codebase.
+This problem is very related to the problem of clone detection, except now it is within the boundaries of a single clone class instead of an entire codebase.
 Because of that, just like the clone detection process, we build a clone graph and detect clones on it.
@@
 
-In Figure~\ref{fig:2rvariabilityhigh4} we display clone classes and their (simplified) equality arrays.
-We can convert this to a graph, using a similar process as the graph creation process used for clone detection.
-In this case, duplicate relations represent nodes of which their equality arrays are within the variability threshold.
-In Figure~\ref{fig:2rvariabilityhigh4} all relations are between equal equality arrays, but this does not always have to be the case.
-Large equality arrays, denoting statements that consist of many tokens, may have some variability and still be considered duplicates in this graph.
-
 \begin{figure}[H]
@@
 
-In this graph, the duplicate relations (green arrows) do not necessarily denote an exact match.
+In Figure~\ref{fig:2rvariabilityhigh4} we display clone classes and their (simplified) equality arrays.
+We can convert this to a graph, using a similar process as the graph creation process used for clone detection.
+In this case, duplicate relations represent nodes of which their equality arrays are within the variability threshold.
+%In Figure~\ref{fig:2rvariabilityhigh4} all relations are between equal equality arrays, but this does not always have to be the case.
+Large equality arrays, denoting statements that consist of many tokens, may have some variability and still be considered duplicates in this graph.
+
+%In this graph, the duplicate relations (green arrows) do not necessarily denote an exact match.
 The duplicate relations allow for variability in the equality arrays as long as it falls under the variability threshold.
@@
 This is because negative numbers are the tokens/expressions that we do not allow variability in because they cannot be refactored as easily:
-\begin{equation}\label{eq:t2rcloneequality}
-E_1\text{ can only be cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1, y \in E_2)\text{ }x<0 \lor y<0 \Rightarrow x=y
-\end{equation}
+%\begin{equation}\label{eq:t2rcloneequality}
+%E_1\text{ can only be cloned with }E_2\text{ iff }|E_1|=|E_2| \land \forall (x \in E_1, y \in E_2)\text{ }x<0 \lor y<0 \Rightarrow x=y
+%\end{equation}
 
@@
 The only difference is that, in this step, we do not remove clones that do not meet the thresholds (as explained in Section~\ref{sec:clonerefactorthresholds}).
-This is because the next step, explained in the next section, could potentially expand the found clones and thus make clones that would currently invalid by the thresholds valid.
+This is because the next step, explained in the next section, could potentially expand the found clones.
 
@@
 \subsubsection{Try to Expand}
-The problem with the graph clone detection technique is that only single nodes that are within the variability threshold are considered duplicates of each other.
-However, single nodes that are not within this threshold could still be part of a clone class if the other cloned nodes are more towards the lower bound of the threshold.
+The problem with the graph clone detection technique is that only single nodes that are within the variability threshold of each other are considered duplicates of each other.
+However, nodes that are not within this threshold could still be part of a clone class if the other cloned nodes are more towards the lower bound of the threshold.
 
@@
 We start with the largest clone class, measured in clone volume.
-We measure clone volume as the product of the number of clone instances in a clone class and the number of nodes in any of its instances.
-
-In the example in Figure~\ref{fig:trytoexpand} the largest instance has a volume of:
-
-\begin{equation}\label{eq:clonevolume}
-3 \text{ nodes} * 2 \text{ clone instances} = 6
-\end{equation}
+We define \textit{clone volume} as the combined volume of all clone instances in a clone class.
+
+%In the example in Figure~\ref{fig:trytoexpand} the largest instance has a volume of:
+
+%\begin{equation}\label{eq:clonevolume}
+%3 \text{ nodes} * 2 \text{ clone instances} = 6
+%\end{equation}
 
 Starting from this clone, we will try to expand it.
+We refer to the nodes in Figure~\ref{fig:trytoexpand} as $N_x$ where \textit{x} is the line number.
 We will include the previous node in the clone class and verify its variability threshold (node $N_2$).
@@
 \textit{gap\_threshold} is the defined threshold percentage of the maximum gap size between two clone instances.
-$\text{gap}(I_1, I_2)$ is the function that calculates the gap between two clone instances.
-This gap is calculated by dividing the amount of statements in the gap by the amount of statements that both clone instances span together:
+$\text{gap}(i_1, i_2)$ is the function that calculates the gap between two clone instances.
+This gap is calculated by dividing the amount of statements in the gap by the amount of nodes that both clone instances span together:
 
@@
 Fig.~\ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
-The relation of clones through inheritance is measured for each clone class.
-The location and contents of clones are measured for each clone instance.
+The relation of clones through inheritance is determined for each clone class.
+The location and contents of clones are determined for each clone instance.
 

### 2019-08-25 sections/clonerefactor.tex
Relations

@@
 \begin{enumerate}
-\item \textbf{Same Interface}: All instances of the clone class are in a class or interface that have a common interface anywhere in their inheritance hierarchy.
+\item \textbf{Same Direct Interface}: All instances of the clone class are in a class or interface implement the same interface.
+\item \textbf{Same Indirect Interface}: All instances of the clone class are in a class or interface that have a common interface anywhere in their inheritance hierarchy.
 \item \textbf{No Direct Superclass}: All instances of the clone class are in a class that does not have any superclass.
@@
   \item \textbf{Common Hierarchy}: \textit{Superclass}, \textit{Sibling Class}, \textit{Ancestor Class}, \textit{First Cousin}, \textit{Same Hierarchy}
-  \item \textbf{Common Interface}: \textit{Same Interface}
+  \item \textbf{Common Interface}: \textit{Same Direct Interface}, \textit{Same Indirect Interface}
   \item \textbf{Unrelated}: \textit{No Direct Superclass}, \textit{No Indirect Superclass}, \textit{External Superclass}, \textit{External Ancestor}
@@
 However, many programming languages nowadays support default implementations in interfaces.
-Since Java 7 and C\#8, these programming languages allow for functionality to be defined in interfaces.
+Since Java 7 and C\# 8, these programming languages allow for functionality to be defined in interfaces.
 Many other object-oriented languages like Python allow this by nature, as they do not have a true notion of interfaces.
@@
 
-To check whether two cloned nodes have common interfaces, we recursively walk all types the class or interface of the cloned nodes implement and extend.
+To check whether two cloned nodes have a \textit{Same Direct Interface} relation, we check that the classes to which these nodes belong both implement the same interface type.
+To check whether two cloned nodes have a \textit{Same Indirect Interface} relation, we recursively walk all types the class or interface of the cloned nodes implement and extend.
 The common interface that is closest to the cloned node in terms of depth of recursion will be flagged as the refactoring candidate.

### 2019-08-25 sections/clonerefactor.tex
Revamp Relation

@@
 Every clone class only has a single relation, which is the first relation from the above list that the clone class applies to.
-For instance: all ``Superclass'' clones also apply to ``Same Hierarchy'', but because ``Superclass'' is earlier in the list they will get the ``Superclass'' relation.
-This is because the items earlier in the list denote a more favorable refactoring.
-
-To determine the relation for a given clone class, we compare each node in a clone instance with the respective nodes in each other clone instance within a clone class.
-So for a clone class with x clone instances and each clone instance has y nodes, we perform:
-
-\begin{equation}\label{eq:sameclass}
-\frac{x * (x + 1)}{2} * y
-\end{equation}
-
-comparisons to determine the relation.
+For instance: all ``Superclass'' clones also apply to ``Same Hierarchy'', but because ``Superclass'' is earlier in the above list they will get the ``Superclass'' relation.
+This is because the items earlier in the above list denote a more favorable refactoring.
+
+When CloneRefactor applies automated refactorings, it uses this inheritance relation to see where it must place the refactored code.
+We explain this for each relation category over the following sections.
+
+%To determine the relation for a given clone class, we compare each node in a clone instance with the respective nodes in each other clone instance within a clone class.
+%So for a clone class with x clone instances and each clone instance has y nodes, we perform:
+
+%\begin{equation}\label{eq:sameclass}
+%\frac{x * (x + 1)}{2} * y
+%\end{equation}
+
+%comparisons to determine the relation.
 Each of these checks will result in one of the relations from the list above.
@@
 
-Cloned nodes are flagged as \textit{Same method} if these nodes are found in the same method.
-We define the method as the first method declaration that is encountered when following the parent nodes in the AST for a given cloned node.
-Please note that a clone instance may not always be in a method, for which this predicate will fail.
-
-Cloned nodes are flagged as \textit{Same class} if these nodes are found in the same class.
-We define the class as the first class declaration that is encountered when following the parent nodes in the AST for a given cloned node.
+ %We define the method as the first method declaration that is encountered when following the parent nodes in the AST for a given cloned node.
+%Please note that a clone instance may not always be in a method, for which this predicate will fail.
+
+%Clone classes are flagged as \textit{Same method} if all their clone instances are found in the same method.
+Cloned classes are flagged as \textit{Same class} if all their clone instances are found in the same class.
+%We define the class as the first class declaration that is encountered when following the parent nodes in the AST for a given cloned node.
 
@@
 This is because putting a lot of functionality in classes higher up in an inheritance structure can result in the ``God Object'' anti-pattern.
-A god object is an object that knows too much or does too much.
-
-Cloned nodes are flagged as \textit{Superclass} if the classes in which these nodes are found are parent and child class of each other.
-Cloned nodes are flagged as \textit{Siblings} if the classes in which these nodes are found all share the same parent and this parent class is not external.
-Cloned nodes are flagged as \textit{First Cousin} if the classes in which these nodes are found all share the same grandparent and this grandparent class is not external.
-
-Cloned nodes are flagged as \textit{Ancestor} if the classes in which these nodes are found are recursively the parent of an antecedent.
+A god object is an object that knows too much or does too much \cite{fowler2018refactoring}.
+
+%Clone classes are flagged as \textit{Superclass} if the classes in which the clone instances are found are parent and child class of each other.
+Clone classes are flagged as \textit{Siblings} if the classes in which their clone instances are found all share the same parent and this parent class is not external.
+Clone classes are flagged as \textit{First Cousin} if the classes in which their clone instances are found all share the same grandparent and this grandparent class is not external.
+
+%Clone classes nodes are flagged as \textit{Ancestor} if the classes in which their clone instances are found are recursively the parent of an antecedent.
 Cloned nodes are flagged as \textit{Same Hierarchy} if the classes in which these nodes are found are all in the same inheritance hierarchy and not linked by any external classes.
@@
 
-To check whether two cloned nodes have a \textit{Same Direct Interface} relation, we check that the classes to which these nodes belong both implement the same interface type.
+%To check whether two cloned nodes have a \textit{Same Direct Interface} relation, we check that the classes to which these nodes belong both implement the same interface type.
 To check whether two cloned nodes have a \textit{Same Indirect Interface} relation, we recursively walk all types the class or interface of the cloned nodes implement and extend.
@@
 
-Cloned nodes are flagged \textit{No Direct Superclass} if they are in classes that do currently not have a parent.
+Cloned classes with a \textit{No Direct Superclass} relation mark the opportunity for creating a superclass abstraction and placing the extracted method there.
+For clone classes with a \textit{No Indirect Superclass} relation, CloneRefactor creates such an abstraction for the ancestor that does not have a parent.
+Clone classes with a \textit{External Superclass} or \textit{External Ancestor} relation obstruct the possibility of creating a superclass abstraction.
+In such a case, CloneRefactor creates an interface abstraction to make their relation explicit.
+
+%Cloned nodes are flagged \textit{No Direct Superclass} if they are in classes that do currently not have a parent.
 This marks the opportunity for creating a superclass abstraction and placing the extracted method there.
@@
 
-Cloned nodes are flagged \textit{External Superclass} if they are in a class which has an external parent.
+%Cloned nodes are flagged \textit{External Superclass} if they are in a class which has an external parent.
 Cloned nodes are flagged \textit{External Ancestor} if one of their ancestors has an external parent.

### 2019-08-25 sections/clonerefactor.tex
Cutting quite some content from the context sections

@@
 A constructor is a special method that is called when an object is instantiated.
-Current clone refactoring studies only focus on clones at method level \cite{choi2011extracting, yue2018automatic, kodhai2013method, arcelli2013software, lin2014clonepedia, mandal2014automatic, balazinska2000advanced, yongting2018detection, bouktif2006novel, fanqi2014using, devi2016study}.
+Most modern clone refactoring studies only focus on clones at method level \cite{choi2011extracting, yue2018automatic, kodhai2013method, arcelli2013software, lin2014clonepedia, mandal2014automatic, balazinska2000advanced, yongting2018detection, bouktif2006novel, fanqi2014using, devi2016study}.
 This is because most clones reside at those places \cite{lozano2007evaluating, fontana2015duplicated} and most of those clones can be refactored with a relatively simple set of refactoring techniques \cite{kodhai2013method, fontana2015duplicated}.
 
-To detect whether a given clone instance is at Method Level, we check for each node in the clone instance whether it has an ancestor node that is a method declaration.
+%To detect whether a given clone instance is at Method Level, we check for each node in the clone instance whether it has an ancestor node that is a method declaration.
 A clone instance is considered ``Method Level'' if:
 
-\begin{equation}\label{eq:samemethod}
-\forall (n \in I)\text{ } Tn = \text{MethodDeclaration} \lor \exists (p \in ancestors(n)) \text{ } Tp = \text{MethodDeclaration}
-\end{equation}
-
-Where \textit{T} is the type of a node.
+%\begin{equation}\label{eq:samemethod}
+%\forall (n \in I)\text{ } Tn = \text{MethodDeclaration} \lor \exists (p \in ancestors(n)) \text{ } Tp = \text{MethodDeclaration}
+%\end{equation}
+
+%Where \textit{T} is the type of a node.
 \textit{ancestors(n)} denotes all of ancestor nodes of a node.
@@
 
-\begin{figure}[H]
-\begin{parcolumns}{2}
-\colchunk[1]{
-\begin{javacode}
-public class Class1 { // |\textcolor{pgreen}{$p_3$}|
-  public void doA() { // |\textcolor{pgreen}{$p_2$}|
-    if(isA()) // |\textcolor{pgreen}{$p_1$}|
-|\highlightYellow|      doB(); // |\textcolor{pgreen}{$n_1$}|
-  }
-}
-\end{javacode}}
-\colchunk[2]{
-\begin{javacode}
-public class Class2 { // |\textcolor{pgreen}{$p_3$}|
-  public void doB() { // |\textcolor{pgreen}{$p_2$}|
-    if(isB()) // |\textcolor{pgreen}{$p_1$}|
-|\highlightYellow|      doB(); // |\textcolor{pgreen}{$n_2$}|
-  }
-}
-\end{javacode}}
-\end{parcolumns}
-\caption{Example of a method level clone and its parents.}
-\label{fig:methodlevelclone}
-\end{figure}
+%\begin{figure}[H]
+%\begin{parcolumns}{2}
+%\colchunk[1]{
+%\begin{javacode}
+%  public void doA() { // |\textcolor{pgreen}{$p_2$}|
+%    public class Class1 { // |\textcolor{pgreen}{$p_3$}|
+%    if(isA()) // |\textcolor{pgreen}{$p_1$}|
+%|\highlightYellow|      doB(); // |\textcolor{pgreen}{$n_1$}|
+%  }
+%}
+%\end{javacode}}
+%\colchunk[2]{
+%\begin{javacode}
+%public class Class2 { // |\textcolor{pgreen}{$p_3$}|
+%  public void doB() { // |\textcolor{pgreen}{$p_2$}|
+%    if(isB()) // |\textcolor{pgreen}{$p_1$}|
+%|\highlightYellow|      doB(); // |\textcolor{pgreen}{$n_2$}|
+%  }
+%}
+%\end{javacode}}
+%\end{parcolumns}
+%\caption{Example of a method level clone and its parents.}
+%\label{fig:methodlevelclone}
+%\end{figure}
 
@@
 
-We detect these clones in the same way we detect method level clones: we walk up the AST until we find the first node that indicates one of these categories.
+%We detect these clones in the same way we detect method level clones: we walk up the AST until we find the first node that indicates one of these categories.
 
@@
 All usages of the removed declaration should be redirected to the clone instance that was not removed.
-We check for clones in this category by checking that the first node in a clone instance is a declaration and the last node in the clone instance is the last node in the body of that declaration.
+Sometimes, the declaration should be moved to a location that is accessible by all usages.
+%We check for clones in this category by checking that the first node in a clone instance is a declaration and the last node in the clone instance is the last node in the body of that declaration.
 
@@
 These clones can often be refactored by extracting a new method out of the cloned code.
-We detect such clones by checking that each node in the clone instance has an ancestor node that is a MethodDeclaration, but none of the nodes is a method declaration.
+%We detect such clones by checking that each node in the clone instance has an ancestor node that is a MethodDeclaration, but none of the nodes is a method declaration.
 We describe the procedure by with we recursively seek the parent nodes of a node in Section~\ref{sec:methodlevelcr}.
@@
 This increases the chance that these classes are missing some form of abstraction, or their abstraction is used inadequately.
-We detect such clones by checking that each cloned node has a parent node that is a MethodDeclaration.
+%We detect such clones by checking that each cloned node has a parent node that is a MethodDeclaration.
 This is the same process as described in equation \ref{eq:samemethod}.
@@
 \subsubsection{Only Fields}
-This category denotes that the clone spans over only global variables, fields that are declared outside of a method.
-This is to indicate data redundancy: pieces of data have an implicit dependency.
+This category denotes that the clone spans over only global variables/fields that are declared outside of a method.
+This indicates data redundancy: pieces of data have an implicit dependency.
 In such cases, these fields may have to be encapsulated in a new object.
 Or, the fields should be somewhere in the inheritance structure where all objects containing the clone can access them.
-We check for this category by validating that all nodes in the clone instance are a VariableDeclarator.
+%We check for this category by validating that all nodes in the clone instance are a VariableDeclarator.
 Because VariableDeclarators in methods would already fall into the ``Partial Method'' category, this includes only globally defined fields.
@@
 Such clones indicate, like the ``Several Methods'', the requirement of performing a more architectural-level refactoring.
-These are often more complicated, especially when aiming to automate this process.
+These are often more complicated to refactor, especially when aiming to automate this process.
 
 \section{Automated Refactoring}
-After clone detection and context analysis, CloneRefactor applies refactorings to a subset of type 1R clones.
-This section describes what clone classes are included in the refactoring and the refactoring methods CloneRefactor supports.
+After clone detection and context analysis, CloneRefactor applies refactorings to a subset of type 1R clones. This section describes what clone classes are refactored and which techniques are used.
 
 \subsection{Method extraction opportunities}\label{sec:refactorabilitysetup}
-The most used technique to refactor clones is ``Extract Method'' (creating a new method based on the contents of clones).
+The most used technique to refactor clones is ``Extract Method''~\cite{fowler2018refactoring} (creating a new method based on the contents of clones).
 However, method extraction cannot be applied in all cases.

### 2019-08-25 sections/clonerefactor.tex
Refactoring CloneRefactor

@@
 \section{JavaParser}
-An important design decision for CloneRefactor is the usage of a library named JavaParser \cite{tomassetti2017javaparser}.
+An important design decision for CloneRefactor is the usage of a library named JavaParser~\cite{tomassetti2017javaparser}.
 JavaParser is a Java library which allows parsing Java source files to an abstract syntax tree (AST).
@@
 This is because putting a lot of functionality in classes higher up in an inheritance structure can result in the ``God Object'' anti-pattern.
-A god object is an object that knows too much or does too much \cite{fowler2018refactoring}.
+A god object is an object that knows too much or does too much~\cite{fowler2018refactoring}.
 
@@
 \subsection{Location}\label{sec:setuplocation}
-A paper by Lozano et al.
-\cite{lozano2007evaluating} discusses the harmfulness of cloning.
+A paper by Lozano et al.~\cite{lozano2007evaluating} discusses the harmfulness of cloning.
 The authors argue that 98\% are produced at method-level.
@@
 A constructor is a special method that is called when an object is instantiated.
-Most modern clone refactoring studies only focus on clones at method level \cite{choi2011extracting, yue2018automatic, kodhai2013method, arcelli2013software, lin2014clonepedia, mandal2014automatic, balazinska2000advanced, yongting2018detection, bouktif2006novel, fanqi2014using, devi2016study}.
-This is because most clones reside at those places \cite{lozano2007evaluating, fontana2015duplicated} and most of those clones can be refactored with a relatively simple set of refactoring techniques \cite{kodhai2013method, fontana2015duplicated}.
+Most modern clone refactoring studies only focus on clones at method level~\cite{choi2011extracting, yue2018automatic, kodhai2013method, arcelli2013software, lin2014clonepedia, mandal2014automatic, balazinska2000advanced, yongting2018detection, bouktif2006novel, fanqi2014using, devi2016study}.
+This is because most clones reside at those places~\cite{lozano2007evaluating, fontana2015duplicated} and most of those clones can be refactored with a relatively simple set of refactoring techniques~\cite{kodhai2013method, fontana2015duplicated}.
 
@@
 In some instances, more conditions may apply to be able to conduct a refactoring, if beneficial at all.
-CloneRefactor maps to what extent this refactoring method can be used to refactor the found clones automatically.
-
-Because of this, we defined a set of categories of things that can obstruct a refactoring opportunity using the ``Extract Method'' technique.
-These categories are party derived from the clone refactoring preconditions defined by Tsantalis et al.~\cite{tsantalis2015assessing} (see Section \ref{sec:jdeodorant}).
+CloneRefactor maps to what extent this refactoring method can be used to automatically refactor clones.
+
+We defined a set of categories that can obstruct a refactoring opportunity using the ``Extract Method'' technique.
+These categories are party derived from the clone refactoring preconditions defined by Tsantalis et al.~\cite{tsantalis2015assessing} (see Section~\ref{sec:jdeodorant}).
 These categories are as follows:
@@
     \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
-    \item \textbf{Spans Part Of A Block}: This clone spans a part of a statement.
+    \item \textbf{Spans Part Of A Block}: This clone spans a part of a block.
     \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Section~\ref{sec:setupcontents}, the ``extract method'' refactoring technique cannot be applied.
@@
 \begin{itemize}
-  \item The clone class has at least one \texttt{return} statements, but not all paths through the clone class return.
+  \item The clone class has at least one \texttt{return} statement, but not all paths through the cloned fragment return.
   \item There are \texttt{break} and/or \texttt{continue} statements in the clone class, but the corresponding loop/switch is not included.
@@
 If this statement is included in the clone class, then the \texttt{break} and/or \texttt{continue} will be no problem for refactoring.
-However, if it isn't, then we mark it ``Complex Control Flow''.
+However, if it isn't, then we flag the clone class ``Complex Control Flow''.
 
 \subsubsection{Spans Part Of A Block}
-When applying an ``Abstract Method'' refactoring, we author a new method declaration.
+When applying an ``Extract Method'' refactoring, CloneRefactor creates a new method declaration.
 The body of this method declaration consists of a set of statements.
 However, if a single statement is only partially cloned, this might give issues with refactoring.
-An example of this is shown in Figure~\ref{fig:refactorabilitypartialblock}
+An example of this is shown in Figure~\ref{fig:refactorabilitypartialblock}.
 
@@
 The ``Extract Method'' refactoring can only refactor code in the body of a method.
-We mapped the contents of clones in Section~\ref{sec:setuplocation}.
-Here we defined the ``Partial Method'' category as \textit{a clone that spans (a part of) the body of a method.
+In Section~\ref{sec:setuplocation} we describe the ``Partial Method'' category as \textit{a clone that spans (a part of) the body of a method.
 The declaration itself is not included.} If the clone does not fall within this category, ``Extract Method'' is likely not to be the correct technique for refactoring such clones.
@@
 A method body can only consist of statements.
-We cannot put declarations in a method.
 However, there are possibilities where a clone consists of something else than a statement as a top-level node.
@@
 First, we create a new method and give it a uniquely generated name.
-We replace all nodes from the clone instances of the clone to method calls of the newly created method.
-We place a copy of the nodes that were removed from a single clone instance in the new method.
+We replace all nodes from the clone instances to method calls to the newly created method.
+We place a copy of the nodes that were removed from one of the clone instances in the new method.
 
 \subsubsection{Relation}
-For each of the identified clone relations (Section~\ref{sec:setuprelation}) we define a method of automatically refactoring clones in these categories.
-The relation determines the location at which we place the newly created method.
+For each of the identified clone relations (see Section~\ref{sec:setuprelation}) we define a location and a visibility for the extracted method.
 
@@
 \paragraph{Common Hierarchy}
-We place the extracted method in the class which all clone instances share as a superclass.
+We place the extracted method in the class which all clone instances share as an ancestor.
 We give the method a \texttt{protected} visibility, which indicates that the method can only be used within its hierarchy.
@@
 We place the extracted method in the interface all clone instances have in common.
-We give the method a \texttt{public} visibility (because interfaces do not allow for \texttt{protected} visibility) and turn it into a default implementation using the \texttt{default} keyword.
+We give the method a \texttt{public} visibility (because interfaces do not allow for \texttt{protected} visibility) and turn the extracted method into a default implementation using the \texttt{default} keyword.
 
@@
 Because for unrelated clone instances we create new abstractions, we could change the relation of other clones.
-When we introduce a new superclass abstraction, other clones might turn from ``unrelated'' into ``common hierarchy''.
+When we introduce a new superclass abstraction, other clones might turn from ``unrelated'' into ``common hierarchy'' or ``common interface''.
 Because of this, creating a single abstraction could favor multiple refactoring opportunities.
@@
 For unrelated clones, we always create a new abstraction instead of introducing a ``utility class''.
-Most current code clone refactoring support tools use utility classes to refactor unrelated code clones \cite{mazinanian2016jdeodorant, yoshida2005refactoring, gode2010clone}.
-For this study, we refrain from doing this because the introduction of many static methods can make a codebase hard to comprehend \cite{xing2003pseudo}.
+Most current code clone refactoring support tools use utility classes to refactor unrelated code clones~\cite{mazinanian2016jdeodorant, yoshida2005refactoring, gode2010clone}.
+For this study, we refrain from doing this because the introduction of many static methods can make a codebase hard to comprehend~\cite{xing2003pseudo}.
 Additionally, we can use the created abstractions for further refactorings.
@@
 \subsubsection{Populate method}
-After placing the newly abstracted method at an appropriate location, we analyze the method content to determine whether we need to add parameters, a return value or a \texttt{throws} clause to the method declaration.
+After placing the newly abstracted method at an appropriate location, CloneRefactor analyzes the method content to determine whether it needs to add parameters, a return value or a \texttt{throws} clause to the method declaration.
 
 \paragraph{Method parameters}
-We determine which variables and methods that are used in the method body are not accessible anymore at the location where the extracted method is placed.
-For each of these variables and called methods, we add a parameter to the extracted method.
-We then pass the appropriate data to each method call.
+CloneRefactor determines which variables and methods that are used in the method body are not accessible anymore at the location where the extracted method is placed.
+For each of these variables and called methods, it adds a parameter to the extracted method.
+It then passes the appropriate data to each method call.
 
@@
 If a method in Java throws an exception that is not a \texttt{RuntimeException}, it must be denoted in the method declaration.
-Because of this, we analyze the extracted method for \texttt{throw} statements, which denote an exception being thrown.
-We also analyze all called methods to find out whether they throw exceptions.
-For each of these exceptions, we check whether they are caught in the extracted method.
-Any exception that is not a \texttt{RuntimeException} and that is not being caught is added to the thrown exceptions of the extracted method.
+Because of this, CloneRefactor analyzes the extracted method for \texttt{throw} statements, which denote an exception being thrown.
+It also analyzes all called methods to find out whether they throw exceptions.
+For each of these exceptions, it checks whether they are caught in the extracted method.
+Any exception that is not a \texttt{RuntimeException} and that is not caught is added to the thrown exceptions of the extracted method.
 
 \subsection{Collecting data}
-To find out whether clones should be refactored (RQ3) we collect data about the applied refactorings.
+To find out whether clones should be refactored (RQ3) CloneRefactor collects data about the applied refactorings.
 We use this data to find out whether a specific refactoring succeeds in improving the maintainability of the system.
-For each refactored clone class, we map the characteristics of the extracted method to the impact of the refactoring on the maintainability of the system/
+For each refactored clone class, we map the characteristics of the extracted method to determine the impact of the refactoring on the maintainability of the system.
 
@@
 \item \textbf{Nodes}: The number of nodes that \textit{each clone instance of the clone class} spans. This concerns the size of a single clone instance before it was refactored.
-\item \textbf{Tokens}: The number of tokens that the \textit{each clone instance of the clone class} spans. This concerns the size of a single clone instance before it was refactored.
+\item \textbf{Tokens}: The number of tokens that \textit{each clone instance of the clone class} spans. This concerns the size of a single clone instance before it was refactored.
 \item \textbf{Relation}: The relation category (Section~\ref{sec:setuprelation}) that this clone class belongs to.
@@
 \subsubsection{Impact on maintainability metrics} \label{sec:metrics}
-We measure the impact on maintainability metrics of the refactored source code for each clone class that is refactored.
-These metrics are derived from Heitlager et al.
-\cite{heitlager2007practical}.
+For each clone class that is refactored, CloneRefactor determines how this influences a set of maintainability metrics.
+These metrics are derived from Heitlager et al.~\cite{heitlager2007practical}.
 This paper defines a set of metrics to measure the maintainability of a system.
@@
 In this case, we are dealing with single refactorings and we want to measure the maintainability impact of such a small change.
-Because of that, we measure only a subset of the metrics \cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
-The subset of metrics we decided to focus on are all metrics that are measured on method level (as the other metrics show a lesser impact on the maintainability for these small changes).
-These metrics are
+Because of that, we measure only a subset of the metrics~\cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
+The subset of metrics we decided to focus on are all metrics that are measured on method level (as the other metrics show a lesser impact on the maintainability for the small-grained changes introduced by CloneRefactor).
+These metrics are:
 \begin{itemize}
-\item \textbf{Duplication}: In Heitlager et al.
-\cite{heitlager2007practical} this metric is measured by taking the amount of duplicated lines.
+\item \textbf{Duplication}: In Heitlager et al.~\cite{heitlager2007practical} this metric is measured by taking the amount of duplicated lines.
 We decided to use the amount of duplicated tokens part of a clone class instead, to have a stronger reflection of the impact of the refactoring by measuring a more fine-grained system property.
 \item \textbf{Volume}: The more code a system has, the more code has to be maintained.
-The paper \cite{heitlager2007practical} measures volume as lines of code.
-As with duplication, we use the number of tokens instead.
+Heitlager et al.~\cite{heitlager2007practical} measure volume in lines of code.
+We use the amount of tokens, to have a stronger reflection of the impact of the refactoring by measuring a more fine-grained system property.
 \item \textbf{Complexity}: Heitlager et al.
-use MCCabe complexity \cite{mccabe1976complexity} to calculate their complexity metric.
+use MCCabe complexity~\cite{mccabe1976complexity} to calculate their complexity metric.
 The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.
-\item \textbf{Method Interface Size}: The number of parameters that a method has.
-If a method has many parameters, the code may become harder to understand and it is an indication that data is not encapsulated adequately in objects \cite{fowler2018refactoring}.
+\item \textbf{Number of Parameters}: The number of parameters that a method has.
+If a method has many parameters, the code may become harder to understand and it is an indication that data is not encapsulated adequately in objects~\cite{fowler2018refactoring}.
 \end{itemize}
 
-We can determine the change of the values of these metrics by considering the transformations that are done by the refactoring. We calculate these metrics as follows:
+We can determine the increase/decrease of these metrics (delta) by considering the transformations that are done by the refactoring. We calculate these metrics as follows:
 
 \begin{itemize}
-\item \textbf{Duplication}: The duplication can only decrease as a result of the refactoring.
-We calculate the reduction of duplication as the product of the number of tokens in the body of the extracted and the number of clone instances in the clone class.
-\item \textbf{Volume}: The volume can both decrease and increase as a result of the refactoring.
+\item \textbf{$\Delta$ Duplication}: The duplication can only decrease as a result of the refactoring. We calculate the reduction of duplication as the combined size of all removed clone instances.
+\item \textbf{$\Delta$ Volume}: The volume can both decrease and increase as a result of the refactoring.
 The reduction of the volume is equal to the reduction of duplication.
-The volume is increased by the number of tokens in each method call to the extracted method, plus optionally the return, assignment or declaration of the extracted method.
-We also add the size in tokens of the extracted method itself to the volume.
+The volume is increased by the number of tokens in each method call to the extracted method plus the size in tokens of the extracted method itself to the volume.
 If the extracted method is moved to a newly created class or interface, we use the volume of that declaration instead (because it contains the extracted method).
-The added volume minus the reduced volume results in the change in volume.
-\item \textbf{Complexity}: The complexity can both decrease and increase as a result of the refactoring.
+Optionally, each method call may include an assignment, declaration or return (based on the return category).
+The added volume minus the reduced volume results in the delta volume.
+\item \textbf{$\Delta$ Complexity}: The complexity can both decrease and increase as a result of the refactoring.
 To calculate the reduction of complexity, we take the sum of all branching statements in all clone instances.
 The increase in complexity is the complexity of the extracted method (the number of branches plus one).
-The added volume complexity the reduced complexity results in the change in complexity.
-\item \textbf{Method Interface Size}: The duplication can only increase as a result of the refactoring. The method interface size increases by the number of parameters in the extracted method.
+The added complexity minus the reduced complexity results in the delta complexity.
+\item \textbf{$\Delta$ Number of Parameters}: The number of parameters can only increase as a result of the refactoring. This metric increases by the number of parameters in the extracted method.
 \end{itemize}

### 2019-08-25 sections/experimentalsetup.tex
Experimental Setup

@@
 Our script clones the latest version of each project in the corpus.
-It then removes each project that has no \texttt{pom.xml} file (which indicates that those do not use the Maven build automation system).
+It then removes each project that has no \texttt{pom.xml} file (which indicates that those projects do not use the Maven build automation system).
 
-We then continued to filter all test cases and generated files.
+We then continued to filter all test code and generated files.
 As many projects store these files in many different places, we decided to further filter the corpus to only include projects with a conventional structure.
-For Maven, projects are recommended to put their production code in the folder structure \texttt{src/main/java}.
+When using Maven, projects are recommended to put their production code in the folder structure \texttt{src/main/java}.
 We omitted Maven projects that do not adhere to this convention.
@@
 \subsection{Resulting corpus}
-This procedure results in 2,267 Java projects including all their dependencies.
+This procedure results in 2,267 Java projects including all their dependencies\footnote{The full list of projects is in the following file in our GitHub repository: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts/blob/master/filtered_projects.txt}}.
 The projects vary in size and quality.
@@
 We also test the correctness of the resulting code after refactoring.
-For this, we use a GitHub project named JFreeChart.
+For this, we use a project named JFreeChart\footnote{JFreeChart is available on GitHub: \url{https://github.com/jfree/jfreechart}}.
 JFreeChart has high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor.
@@
 For example, when clones are very small, refactoring them might not improve maintainability since the detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication.
-Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones cannot improve maintainability when refactored.
+Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones almost never improve maintainability when refactored.
 
@@
 An empty method in Java consists of 7 tokens.
-We also need calls to the extracted method, which is 4 tokens per call if no arguments are required.
+We also need calls to the extracted method, which is 4 tokens per call if no parameters/arguments are required.
 Empirically, we found all clones below 10 tokens in size, are very unlikely to affect maintainability positively.

### 2019-08-25 sections/results.tex
Results
Working on results

@@
 For type 2R clones, we set the variability threshold (see Section~\ref{sec:variabilitythreshold}) to 10\%, meaning that no more than 10\% of expressions may differ between fragments to be considered clones.
-For type 3 and 3R clones, we allow a gap size of 20\% the clones surrounding it (see Section~\ref{sec:t3rthreshold}).
+For type 3 and 3R clones, we allow a gap size of 20\% (see Section~\ref{sec:t3rthreshold}).
 
@@
 This figure shows the average duration of running CloneRefactor 10 times for a certain clone type.
-We ran these performance tests on the compute nodes of the DAS4 supercomputer \cite{bal2016medium}, which allow for higher accuracy performance measurements as they do have limited background processes affecting the results.
+We ran these performance tests on the compute nodes of the DAS4 supercomputer \cite{bal2016medium}, which allow for higher accuracy performance measurements as they have limited background processes affecting the results.
 
 \subsection{Type 2R Variability Threshold}
-To determine the influence of the type 2R variability threshold on the amount of found nodes, we ran CloneRefactor for all variability percentages (0\% meaning no variance in expressions, 100\% meaning any variance in expressions).
+To determine the influence of the type 2R variability threshold on the amount of cloned nodes, we ran CloneRefactor for all variability percentages (0\% meaning no variance in expressions, 100\% meaning any variance in expressions).
 Figure \ref{fig:t2rgraph} shows the results.
@@
 
-In this graph, we see that the amount of clones increases as the amount of variability allowed increases. The graph is logarithmic: as the variability increases, the increase in nodes decreases.
+In this graph, we see that the amount of clones increases when we allow more variability between cloned fragments.
+The graph is logarithmic: as the variability increases, the increase in nodes decreases.
 
@@
 In this graph, we see a decrease in clone classes and an increase in cloned nodes when we increase the type 3R gap size threshold.
-We measure this threshold for a gap size of 0-200\%.
-In the graph, we see that both lines are rather linearly with minor jumps at certain thresholds.
+In the graph, we see that both lines are mostly linear with minor jumps at certain percentages.
 The jumps are at 33\%, 50\%, 100\%, 150\% and 200\%.
@@
 \subsection{Location}
-Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different locations (see Section~\ref{sec:setuplocation}).
+Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different location categories (see Section~\ref{sec:setuplocation}).
 \begin{table}[H]
@@
 \subsection{Contents}
-Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different contents (see Section~\ref{sec:setupcontents}).
+Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different content categories (see Section~\ref{sec:setupcontents}).
 
@@
  & Partial Constructor & 9,981 & 3.37\% & & \\ \midrule
+\multirow{3}{*}{Other} & Several Methods & 22,749 & 7.67\% & \multirow{3}{*}{53,773} & \multirow{3}{*}{18.14\%} \\ \cmidrule(lr){2-4}
+ & Only Fields & 17,700 & 5.97\% & & \\ \cmidrule(lr){2-4}
+ & Other & 13,324 & 4.49\% & & \\ \midrule
  \multirow{5}{*}{Full} & Full Method & 12,990 & 4.38\% & \multirow{5}{*}{13,173}& \multirow{5}{*}{4,44\%} \\ \cmidrule(lr){2-4}
@@
   & Full Class & 37 & 0.01\% & & \\ \cmidrule(lr){2-4}
- & Full Enum & 24 & 0.01\% & & \\ \midrule
-\multirow{3}{*}{Other} & Several Methods & 22,749 & 7.67\% & \multirow{3}{*}{53,773} & \multirow{3}{*}{18.14\%} \\ \cmidrule(lr){2-4}
- & Only Fields & 17,700 & 5.97\% & & \\ \cmidrule(lr){2-4}
- & Other & 13,324 & 4.49\% & & \\ \bottomrule
+  & Full Enum & 24 & 0.01\% & & \\ \bottomrule
 \end{tabular}
@@
 
-\section{Extract Method}
+\section{Refactorability}
 %To what extent can found clones be refactored through method extraction, without requiring additional transformations.
 Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique.
-The second column shows our measurements for the complete systems (just like the former experiments).
-\begin{table}[H]
+From these results we see that approximately 28\% of clones in our corpus can be automatically refactored.
+The main reason clones cannot be automatically refactored is because they are not flagged as ``Partial Method'' in Table~\ref{tab:contents}.
+Another reason is that top level AST-nodes are not a statement.
+
+\begin{table}[]
 \centering
@@
 
-\section{Refactoring} \label{sec:refactoringexperiments}
+\section{Thresholds} \label{sec:refactoringexperiments}
 %I think the ultimate goal with this thesis is to do experiments with different clone thresholds.
@@
 In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.
+Using this data, we find supporting evidence regarding which thresholds are most likely to find clones that should be refactored to improve maintainability.
+
 We use the following keywords as headers of the columns of our tables:
@@
 
-\begin{figure}[H]
+\begin{figure}[]
   \includegraphics[width=1\textwidth]{img/maintainabilityscore}
@@
 To determine the effect of clone token volume on each metric, we also plot graphs in which each metric is considered singularly.
+
 In Figure~\ref{fig:volume} the average delta volume is shown when clones with the specified token volume are refactored.
@@
 
-\begin{figure}[H]
+\begin{figure}[]
   \includegraphics[width=1\textwidth]{img/volume}
@@
 
-\begin{figure}[H]
+\begin{figure}[]
   \includegraphics[width=1\textwidth]{img/numberofparameters}

### 2019-08-25 sections/results.tex
Resulttts

@@
 
-We use the following keywords as headers of the columns of our tables:
-\begin{itemize}
-  \item \textbf{Complexity}: The average delta complexity for all refactored clone classes in the specified category.
-  \item \textbf{Parameters}: The average delta number of parameters for all refactored clone classes in the specified category.
-  \item \textbf{Volume}: The average delta number of tokens for all refactored clone classes in the specified category.
-  \item \textbf{Duplication}: The average delta number of duplicate tokens for all refactored clone classes in the specified category.
-  \item \textbf{\#}: The number of times the specified category is refactored (and thus the number of data points we have for this category).
-  \item \textbf{Score}: The average delta maintainability score (see Section~\ref{sec:metricformula} for the formula by which this score is calculated) for all refactored clone classes in the specified category.
-\end{itemize}
-In this context, the \textit{delta} denotes the change in this metric between the before- and after-refactoring snapshot of the system, for each separate clone class that was refactored.
-
 \subsection{Clone Token Volume}
@@
 
-\begin{figure}[]
+\begin{figure}[H]
   \includegraphics[width=1\textwidth]{img/maintainabilityscore}
@@
 
-In Figure~\ref{fig:complexity} we show the average delta complexity when clones with the specified token volume are refactored.
-We did not add a trendline, as there does not seem to be a clear trend.
-The maximum delta complexity is one because the extracted method itself has a complexity of one.
-For each branching point in the cloned fragment, the complexity of the system will decrease when such a clone is refactored.
-
-\begin{figure}[H]
+\begin{figure}[]
   \includegraphics[width=1\textwidth]{img/complexity}
@@
 
+In Figure~\ref{fig:complexity} we show the average delta complexity when clones with the specified token volume are refactored.
+We did not add a trendline, as there does not seem to be a clear trend.
+The maximum delta complexity is 1 because the extracted method itself has a complexity of 1.
+For each branching point in the cloned fragment, the complexity of the system will decrease when such a clone is refactored.
+
 \subsection{Relation}
 Table~\ref{tab:relationref} shows our data regarding how different relations influence maintainability.
-We mark rows based on less than 100 refactorings red, as their result might not have statistical significance.
+We mark rows based on less than 100 refactorings red, as their result is less likely to have statistical significance.
 The \textbf{Relation} column refers to the relations introduced in Section~\ref{sec:setuprelation}.
 Relations are mutually exclusive so all percentages add up to 100\%.
+We use the following keywords as headers of the columns of our tables:
+\begin{itemize}
+  \item \textbf{Complexity}: The average delta complexity for all refactored clone classes in the specified category.
+  \item \textbf{Parameters}: The average delta number of parameters for all refactored clone classes in the specified category.
+  \item \textbf{Volume}: The average delta number of tokens for all refactored clone classes in the specified category.
+  \item \textbf{Duplication}: The average delta number of duplicate tokens for all refactored clone classes in the specified category.
+  \item \textbf{\#}: The number of times the specified category is refactored (and thus the number of data points we have for this category).
+  \item \textbf{Score}: The average delta maintainability score (see Section~\ref{sec:metricformula} for the formula by which this score is calculated) for all refactored clone classes in the specified category.
+\end{itemize}
+In this context, the \textit{delta} denotes the change in this metric between the before- and after-refactoring snapshot of the system, for each separate clone class that was refactored.
 
@@
 \subsection{Return Category}
-Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.
+Table~\ref{tab:return} shows how the return category of the extracted method influences the maintainability of the resulting system.
 The \textbf{Return Category} column refers to the categories introduced in Section~\ref{sec:refreturn}.

### 2019-08-25 sections/discussion.tex
Cutting a lot of content from my thesis

@@
 \chapter{Discussion} \label{ch:discussion}
-
 In this chapter, we discuss the results of our research and experiments.
 
-\section{Clone Type Definitions}
-In this study, we proposed a set of clone type definitions that can be automatically refactored.
-We based these clone type definitions on the clone type definitions that are commonly used in literature \cite{roy2007survey}.
-The design of these clone type definitions entails some decisions that have a large impact on the clones we considered for refactoring in this study.
-In this section, we discuss our clone type definitions as proposed in Section~\ref{sec:rtypes}.
+\section{Type 2R Clones}
+In this study, we propose a set of clone type definitions that can be automatically refactored. In this section, we discuss our type 2R definition as proposed in Section~\ref{sec:type2r}.
 
-\subsection{Type 2R clones}
-With type 2R clones we allow variability in some identifiers and literals such that the code can and should still be refactored.
+With type 2R clones we allow variability in some expressions such that the code can still be refactored.
 For type 2R clones we chose a set of expressions in which we allow variability and proposed a recommended refactoring strategy.
-We think however that type 2R could still use a lot of improvement to find more duplication patterns that can be refactored.
+We think that type 2R could be improved to find more duplication patterns that can be refactored.
 
@@
 
-\section{CloneRefactor}
-In this section we discuss our decisions for the design of our CloneRefactor tool.
+%\section{CloneRefactor}
+%In this section we discuss decisions made in the design of our CloneRefactor tool.
 
-\subsection{Clone Detection}
-For CloneRefactor we chose to design a novel method of detecting clones, rather than using an existing clone detection technique or tool. Our rationale is as follows:
-\begin{itemize}
-  \item We perform comprehensive analysis on the source code which requires us to use an AST-based clone detection method.
-  \item We perform dependency graph analysis, which requires us to resolve symbols in the source code.
-  \item None of the existing clone detection methods implement all criteria required to build such a system.
-\end{itemize}
-By building a graph that maps relations between nodes in the AST, we can efficiently find clones, allowing to perform a comprehensive analysis of large systems.
+%\subsection{Clone Detection}
+%For CloneRefactor we chose to design a novel method of detecting clones, rather than using an existing clone detection technique or tool. Our rationale is as follows:
+%\begin{itemize}
+%  \item We perform comprehensive analysis on the source code which requires us to use an AST-based clone detection method.
+%  \item We perform dependency graph analysis, which requires us to resolve symbols in the source code.
+%  \item None of the existing clone detection methods implement all criteria required to build such a system.
+%\end{itemize}
+%By building a graph that maps relations between nodes in the AST, we can efficiently find clones, allowing to perform a comprehensive analysis of large systems.
 This method has worked well for our purposes.
 
-The main limitation we encountered is the memory required to build the clone graph.
+%The main limitation we encountered is the memory required to build the clone graph.
 As we load the entire graph into memory before starting the clone detection procedure, this can cause issues on systems with low available memory.
@@
 For our corpus, there were no larger systems, so this was not a big issue.
-However, for industry projects, our tool might require optimization.
+However, for larger systems, our tool might require optimization.
 
-\subsection{Context Analysis}
-In this study, we identified categories for three properties of clones: relation, location, and contents.
+%\subsection{Context Analysis}
+%In this study, we identified categories for three properties of clones: relation, location, and contents.
 We chose a set of relations that indicate different refactoring opportunities.
@@
 
-\subsection{Refactoring}
+\section{Automated Refactoring}
 In this section, we discuss our implementation decisions to refactor source code using CloneRefactor and measure its impact.
 
-\subsubsection{Refactorability} \label{sec:discussrefactorability}
+\subsection{Refactorability} \label{sec:discussrefactorability}
 In Section~\ref{sec:refactorabilitysetup} we introduced categories to determine the refactorability of clones through method extraction.
@@
 
-\subsubsection{Partial block} \label{sec:partialblockdiscussion}
+\subsection{Partial block} \label{sec:partialblockdiscussion}
 We did not consider clones for refactoring that span a part of a block.
@@
 
-\subsubsection{Complex control flow}
+\subsection{Complex control flow}
 Break, continue and return statements can obstruct the possibility of performing method extraction.
@@
 
-\subsubsection{Metrics}
+\subsection{Metrics}
 For this study, we chose to focus on a set of four metrics to measure maintainability: method size, duplication, method parameters, and cyclomatic complexity.

### 2019-08-25 sections/discussion.tex
Discussion

@@
 \section{Automated Refactoring}
-In this section, we discuss our implementation decisions to refactor source code using CloneRefactor and measure its impact.
+In this section, we discuss our implementation decisions regarding the automated refactoring of source code using CloneRefactor.
 
@@
 \subsection{Complex control flow}
-Break, continue and return statements can obstruct the possibility of performing method extraction.
+\texttt{break}, \texttt{continue} and \texttt{return} statements can obstruct the possibility of performing method extraction.
 However, with some extra transformations, method extraction will still be possible in such cases.
@@
 In this section, we discuss the differences between clone types 1-3 and 1R-3R.
+
+\subsubsection{Cloned Nodes}
 We see that the difference between T1R and T1 in terms of found clones is small (11\% more nodes found as cloned for T1).
@@
 
-Regarding performance (Figure~\ref{fig:performance}, there is a notable difference between the refactoring-oriented clone types and the literature clone types.
+\subsubsection{Performance}
+Regarding performance (Figure~\ref{fig:performance}), there is a notable difference between the refactoring-oriented clone types and the literature clone types.
 Type 1R-3R take on average approximately 6 times longer to detect than type 1-3.
@@
 
+\subsubsection{Type 2R Variability}
 In Figure~\ref{fig:t2rgraph} we show the increase of cloned nodes for a higher variability between clone instances.
@@
 
+\subsubsection{Type 3R Gap Size}
 In Figure~\ref{fig:t3rgraph} we show the increase of cloned nodes for higher type 3R gap sizes.
@@
 However, at these higher gap size percentages, the gaps contain more nodes.
-Because of this, the increase of the number of cloned nodes is linear.
+Because of this, the increase of the number of cloned nodes is more linear.
 
@@
 The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, lies at a token volume of 63 tokens.
-There are fewer large clones than small clones (exponential decrease), resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.
+There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.
 
-When looking at the relation between maintainability and the \textbf{volume} metric, we see that the volume increases if the average clone volume is less than 60 tokens, but decreases above 60 tokens.
+When looking at the relation between maintainability and the \textbf{volume} metric, we see that on average the delta volume increases if the average clone volume is less than 60 tokens, but decreases above 60 tokens.
 When token volume increases, the \textbf{number of parameters} of the extracted method rises very slowly.
-Overall, on average, extracted methods have only one parameter.
+Overall, on average, most extracted methods have only one parameter.
 When the token volume of clones becomes larger than 160 tokens, we also see that there are more outliers in terms of the number of parameters.
@@
 
-The maintainability scores displayed in Table~\ref{tab:relationref} show that the most favorable clones to refactor are clones with a superclass relation.
-The most unfavorable is to refactor unrelated clones.
+The maintainability scores displayed in Table~\ref{tab:relationref} show that the most favorable clones to refactor are clones with a \textit{superclass} relation.
+The most unfavorable is to refactor \textit{unrelated} clones.
 The main reason for this difference in maintainability is that on average unrelated clones have a higher volume.
@@
 The differences in maintainability of relation are, compared to the differences in maintainability of different token volumes, very small.
-Common hierarchy (which has the highest score) has a maintainability score of 0.23 whereas unrelated clones (which has the lowest score) have a maintainability score of -0.15.
+\textit{Common hierarchy} (which has the highest score) has a maintainability score of 0.23 whereas \textit{unrelated} clones (which has the lowest score) have a maintainability score of -0.15.
 This is a very small difference, which implies that according to our data relations have a minor impact on the maintainability of clones.

### 2019-08-25 sections/related_work.tex
Restructuring related work

@@
 \chapter{Related work} \label{ch:related_work}
-In this chapter we present the work related to this study.
+In this chapter, we present studies in the field of code clone refactoring. The sections are ordered chronologically, because many of these studies use findings of preceding studies.
 
-\section{Code clone refactoring suggestion tools}
-We are novel in the introduction of a fully automated refactoring tool.
-However, several tools have already been proposed for refactoring suggestion.
-In this section we discuss these tools.
-The tools are ordered on basis of the year in which they were proposed.
-
-\subsection{SUPREMO}
+\section{SUPREMO}
 A thesis by Golomingi~\cite{koni2001scenario} is the first to explore mapping the relation between clone instances to refactoring methods.
 The author analyses the refactoring methods described by Martin Fowler \cite{fowler1999refactoring}.
-Mapping these to relations between clones, this results in Table \ref{tab:relationrefactoring}.
-% Sander: deze zin loop niet, bedoel je niet: "Mapping these to relations between clones results in Table \ref{tab:relationrefactoring}."
+Mapping these to relations between clones results in Table \ref{tab:relationrefactoring}.
 
@@
 
-The author then proposes a tool named ``SUPREMO''. This tool determines the relations between clone instances, computes the impact % Sander: impact on what?
-of the clones and proposes refactorings.
-Their tool features visualizations to show how clones are related in the inheritance structure.
-This tool is written for the Smalltalk programming language.
-% Sander: Drie keep achter elkaar this/their tool, niet per se fout maar leest ook niet heel lekker, kijk maar of je tijd hebt ;)
+The author then proposes a tool named ``SUPREMO''.
+This tool determines the relations between clone instances, computes the impact of the clones on system design and proposes refactorings.
+It also features visualizations to show how clones are related in the inheritance structure.
+SUPREMO is written for the Smalltalk programming language.
 The authors verify their approach by presenting several cases in which their tool analyses source code and outputs a refactoring suggestion.
-% Sander: Ik mis beetje hoe dit zich verhoudt tot jouw werk, is ook wel bij andere research beetje ding, zou miss even kijken of je overal 1 of 2 zinnen bij kan zetten over hoe het zich verhoudt tot jouw werk, al is het opzich niet echt erg dus andere dingen gaan miss voor
+In our work, we use these same relations and refactoring techniques.
 
-\subsection{Aries}
+\section{Aries}
 A study by Higo et al.~\cite{higo2004aries, higo2008metric} looks into to what extent clones can be refactored.
-They show code examples and to what extent they can be cloned.
-For instance, they look into what parts of a clone can be extracted to a new method.
+The authors look into what parts of a clone can be extracted to a new method.
 They define that partially cloned blocks obstruct method extraction.
@@
 In this figure, the clone spans a part of a different block so it cannot be refactored.
-However, they propose to omit both ``else if'' lines from the merged fragment so that it can be refactored (in our study we would have flagged these clones as ``partial block'' and thus unsuitable for refactoring).
+They propose to omit both ``else if'' lines from the merged fragment so that it can be refactored (in our study we would have flagged these clones as ``partial block'' and thus unsuitable for refactoring).
 They also allow variability in literals and variables and replace them with method parameters.
@@
 They focus entirely on whether a clone \textbf{can} be refactored and not whether it \textbf{should} be refactored.
-This tool only proposes refactoring opportunities and does not provide help in the process of applying the refactoring.
-% Sander:..
-which our work does..
-is denk ik nice toevoeging
+This tool only proposes refactoring opportunities and does not provide help in the process of applying the refactoring, which our work does.
 
-\subsection{Duplicated Code Refactoring Advisor (DCRA)}
-Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} combine the research by Golomingi~\cite{koni2001scenario} with clone types \cite{roy2007survey}.
-They use a large corpus~\cite{tempero2010qualitas} on which they perform statistical analysis of clone relations together with clone types.
+\section{Duplicated Code Refactoring Advisor (DCRA)}
+Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} combine the research by Golomingi~\cite{koni2001scenario} with clone types 1 and 3 \cite{roy2007survey}.
+They use a large corpus~\cite{tempero2010qualitas} on which they perform statistical analyses of clone relations together with clone types.
 Table \ref{tab:dcra-relation} displays the result of this analysis.
-We added percentages and ordering to this table for easier comparison with the results of our studies (see \ref{sec:relationresults}).
+We added percentages and ordering to this table for easier comparison with the results of our work (see \ref{sec:relationresults}).
+We also added the percentages of our work to this table.
 
@@
 \centering
-\begin{tabular}{@{}lllll@{}}
+\begin{tabular}{@{}lrrrrr@{}}
 \toprule
-                         & Type 1 & Percentage & Type 3 & Percentage \\ \midrule
-Same Class               & 5,645  & 32.1\%     & 51,308 & 28.7\%     \\
-Same External Superclass & 4,384  & 25.0\%     & 66,391 & 37.1\%     \\
-Unrelated Class          & 2,758  & 15.7\%     & 35,035 & 19.6\%     \\
-Sibling Class            & 2,721  & 15.5\%     & 13,868 & 7.8\%      \\
-Common Hierarchy Class   & 970    & 5.5\%      & 3,152  & 1.8\%      \\
-Same Method              & 569    & 3.2\%      & 4,901  & 2.7\%      \\
-First Cousin Class       & 416    & 2.4\%      & 2,980  & 1.7\%      \\
-Superclass               & 91     & 0.5\%      & 981    & 0.5\%      \\
-Ancestor Class           & 13     & 0.1\%      & 281    & 0.2\%      \\ \bottomrule
+                         & Type 1 & Percentage & Type 3 & Percentage & Type 1R (Our Work) \\ \midrule
+Same Class               & 5,645  & 32.1\%     & 51,308 & 28.7\% & 26.8\%    \\
+Same External Superclass & 4,384  & 25.0\%     & 66,391 & 37.1\% & 20.6\%   \\
+Unrelated Class          & 2,758  & 15.7\%     & 35,035 & 19.6\% & 18.4\%    \\
+Sibling Class            & 2,721  & 15.5\%     & 13,868 & 7.8\%  & 18.2\%    \\
+Common Hierarchy Class   & 970    & 5.5\%      & 3,152  & 1.8\%  & 0.8\%    \\
+Same Method              & 569    & 3.2\%      & 4,901  & 2.7\%  & 10.5\%    \\
+First Cousin Class       & 416    & 2.4\%      & 2,980  & 1.7\%  & 1.4\%    \\
+Superclass               & 91     & 0.5\%      & 981    & 0.5\%  & 3.1\%    \\
+Ancestor Class           & 13     & 0.1\%      & 281    & 0.2\%  & 0.2\%    \\ \bottomrule
 \end{tabular}
@@
 
+Some of our results differ quite a lot from their results. We think this is mostly accounted due to two differences in their setup:
+\begin{itemize}
+\item The used clone type definitions differ (type 1 vs type 1R).
+\item Fontana et al. use a corpus consisting of large higher-quality open-source software systems \cite{tempero2010qualitas} where we use a more varied corpus \cite{githubCorpus2013}.
+\item Fontana et al. use clone pairs while we use clone classes.
+\end{itemize}
+
 Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} propose DCRA, a tool to suggest refactorings for the clones found by the NiCAD tool \cite{roy2008nicad, cordy2011nicad}.
@@
 
-\subsection{JDeodorant} \label{sec:jdeodorant}
+\section{JDeodorant} \label{sec:jdeodorant}
 The most used clone refactoring tool is JDeodorant \cite{mazinanian2016jdeodorant}.
@@
 If all branches return, the fragment can still be refactored even though there is a conditional return statement.
-% Sander:Als je tijd hebt, miss even overzicht in tabel van elke preconditie en hoe je die aanpakt zou het overzichtelijker maken
+
 After all these studies that determine what preconditions apply to be able to refactor modified clones, the authors propose a tool named JDeodorant that helps in the process of refactoring such clones~\cite{mazinanian2016jdeodorant}.
@@
 
-\subsection{Refactoring Technique for Large Groups of Software Clones}
+\section{Refactoring Technique for Large Groups of Software Clones}
 A thesis by AlWaqfi~\cite{alwaqfi2017refactoring} propose a method for assessing refactorability of clone classes , whereas the previous tools only focus on clone pairs.
@@
 
-\subsection{Pattern‐based clone Refactoring Inspection (PRI)}
+\section{Pattern‐based clone Refactoring Inspection (PRI)}
 A study by Chen et al.~\cite{chen2018clone} addresses the problem that developers cannot easily determine which clones can be refactored or how they should be maintained scattered throughout a large code base in evolving systems.
@@
 
-\section{Clone refactoring}
-In this section, we shortly introduce recent studies about refactoring code clones.
-% Sander: Waar ging de vorige sectie dan over?
-\subsection{Impact of Clone Refactoring on External Quality Attributes}
+\section{Impact of Clone Refactoring on External Quality Attributes}
 A study by Vashisht et al.~\cite{vashisht2018impact} determines the impact of clone refactoring on several quality attributes.
@@
 
-\subsection{Clone Recommendation System for Extract Method Refactoring}
+\section{Clone Recommendation System for Extract Method Refactoring}
 Yoshida et al.~\cite{yoshida2019proactive} propose a plugin for the Eclipse IDE that recommends clone refactoring candidates on basis of keystroke tracking.
@@
 
-\subsection{Effect of clone refactoring on the size of unit test cases}
+\section{Effect of clone refactoring on the size of unit test cases}
 Badri et al.~\cite{badri2019measuring} measure the impact on clone refactoring on metrics that affect the testability of software.
 The metrics they measure are size, cyclomatic complexity and coupling.
-To collect this data, they used two systems that have been clone refactored.
-% Sander: ik weet niet of 'clone refactored' een bestaand werkwoord is;) miss is; that had their clones refactored ofzo
-They conclude that there is a strong and positive % Sander: is strong, positive niet beter?
-correlation between clone refactoring and the reduction of the size of unit test cases. They also show that code quality attributes that are related to testability are significantly improved.
+To collect this data, they used two systems that have been de-duplicated manually.
+They conclude that there is a strong, positive correlation between clone refactoring and the reduction of the size of unit test cases.
+They also show that code quality attributes that are related to testability are significantly improved.

### 2019-08-25 sections/conclusion.tex
Background again
Conclusion

@@
 However, we think that the results of this study could be strengthened by performing a survey on software engineering practitioners.
-We have determined a set of refactoring opportunities only based on literature input and quantitive analysis.
-It would be valuable to have a control group rate the refactorings performed by CloneRefactor, as an extra form of input regarding the quality of the code transformation that CloneRefactor performs.
+We have determined maintainability scores only based on literature input and statistical analysis.
+It would be valuable to have a control group rate the refactorings performed by CloneRefactor, as an extra form of input regarding the quality of the code transformations that CloneRefactor performs.
 
@@
 \subsection{Automated Refactoring for more metrics}
-In this study, we presented evidence regarding the value of applying automated refactoring to analyze the before- and after state of refactored source code.
-Analyzing these states we were able to analyze the improvement in maintainability after refactoring duplicated code.
-This allows us to better assess thresholds by which maintainability issues in source code are identified.
-We also get better insights into the costs and values of applying certain refactoring efforts.
+In this study, we apply automated refactoring to analyze the before- and after state of refactored source code.
+This allows us to better determine which thresholds identify problems that should be refactored.
 
@@
 
-If a method has many parameters, we can group strongly related parameters into an object. This can be done automatically, but two things must be considered:
+To refactor a method with many parameters, one should group strongly related parameters into an object. This can be done automatically, but two things must be considered:
 \begin{itemize}
@@
 We must then trace all the places in which they are used together and replace the variables by the newly created abstractions.
-If long parameter lists can be automatically refactored, automated clone refactoring can be improved by automatically grouping data into objects if they are used in unison.
+If long parameter lists can be automatically refactored, automated clone refactoring can be improved by automatically grouping data if the extracted method requires many parameters.
 
@@
 Refactoring complex/large methods can largely be done automatically by applying ``Extract Method'' to large methods.
-Also, many of the results of this study can be reused.
+Many of the results of this study can be reused.
 To assess an automated refactoring opportunity for complex methods, we should assess which parts of methods can be split to end up with parts of similar complexity.
@@
 We think that there are relevant research opportunities in refactoring type 4 clones.
-Type 4 clones are functionally equal pieces of code that are implemented through different implementations.
-Although functionally equal, type 4 clones might still differ in other aspects.
-For instance, for type 4 clones, one alternative might be easier to maintain.
-Also, they can differ in performance.
-
+Although type 4 clone instances perform the same computation, they may still differ in other aspects.
+For instance, one alternative might be easier to maintain or have a better performance.
 There are interesting research opportunities in automatically choosing the better alternative among type 4 clone instances.
@@
 \subsection{Naming of refactored methods/classes/etc.}
-In this study, we took the naming of refactored entities out of the scope.
-We applied automated refactoring to duplication and gave all generated methods, classes and interfaces generated names.
-For our purposes that was not much of an issue, because of the validation methods used.
-We validated our approach using the SIG Maintainability model, which does not take naming quality into account.
-Because of that, the results of our experiments are in no way dependent on the names we give the generated methods, classes and interfaces.
+In this study, we applied automated refactoring to duplication and gave all generated methods, classes and interfaces generated names.
+For our purposes that was not much of an issue, because we used a maintainability model \cite{heitlager2007practical} that does not take naming quality into account.
+Because of that, the results of our experiments are not dependent on the names we give the generated declarations.
 
@@
 However, recent studies allow assistance in this process by generating a name that matches the body of a declaration.
-If this can be done reliably, we can apply refactorings without any manual steps required.
+If this can be done reliably, it is possible to apply automated refactorings without any manual steps required.
 
@@
 This study shows promising results towards generating method and class names based on their body and context.
-However, the source code of this study is not available, making it harder to apply their findings to generate class and method names for any software project.
+However, the source code of this study is not available, making it harder to apply their findings.
 
 In a recent study by Alon et al.
-\cite{alon2018code2seq} they propose code2seq.
+\cite{alon2018code2seq} the authors propose code2seq.
 Code2seq is a machine learning model that guesses the name of a method given a method body.
@@
 Although this model is still far from perfect, combining it with our research could already greatly reduce the manual refactoring effort required.
-The main deficiency of this model lies in that it's limited to the method body and does currently not consider anything else in a method body.
-This method is flawed because the meaning of method bodies depends heavily on their context.
+The main deficiency of this model lies in that it only guesses the name on basis of the body of the method and not its context.
+%This method is flawed because the meaning of method bodies depends heavily on their context.
 For instance, the body of the method \texttt{get()} in \texttt{ArrayList} does not make any sense in relation to its name without considering its context (class, inheritance hierarchy, etc.).
 
-\subsection{Looking into other languages/paradigms}
+\subsection{Looking into other languages}
 In this study, we describe duplicate code refactoring opportunities for object-oriented languages. We built a tool to refactor code clones in Java and used it to run our experiments.
@@
 
-In this study, we focused only on the object-oriented paradigm because of the shared concepts.
-However, the problems that come with duplication in source code also appears in different programming languages.
-Because of that, more insights could be obtained when looking into automated refactoring opportunities for other paradigms.
-For instance, it might be valuable to look into opportunities to reduce duplication in the functional domain.
-Dealing with code clones in the functional paradigm is largely an unexplored field and might hold valuable results.
-
-\subsection{Automatically refactoring code that is duplicated with a library}
-One of the clone detection tools we analyzed in this study is Sisyphus \cite{eremondi2017sisyphus}.
+%\subsection{Automatically refactoring code that is duplicated with a library}
+%One of the clone detection tools we analyzed in this study is Sisyphus \cite{eremondi2017sisyphus}.
 This clone detection tool searches a codebase for methods that are part of the Java standard libraries.
 There are definite automated refactoring opportunities here, automatically switching to the library implementation if available.
-This doesn't have to be limited to just the Java standard library., it is also possible to search the external libraries the project uses.
+This doesn't have to be limited to just the Java standard library, it is also possible to search the external libraries the project uses.

### 2019-08-25 sections/acknowledgements.tex
Acknowledgements

@@
 Oprescu , whose expertise was invaluable in the academic writing and mathematical aspects of this thesis.
-I would like to thank you for your patience whilst reading my texts, as my words often required quite some editing to concisely deliver the message I try to deliver.
+Thank you for helping me concisely deliver the message I try to deliver.
 
 Next, we would like to thank my peer student Sander Meester for always being there when I was stuck.
-Whenever I needed to test some ideas you would always provide valuable insights.
-The long conversations about the problems I have been dealing with in my thesis would not have been solved in the same way if it wasn't for you.
-Your proofreading efforts helped take my writing to the next level.
+Whenever I needed to test some ideas, you would always provide valuable insights.
+Your proofreading efforts helped me a lot to write this thesis.
 

### 2019-08-25 sections/related_work.tex
Related work

@@
 The authors describe clones that are refactored by extracting their functionality to a single method.
-They also describe that variability between identifiers and literals have to become parameters in the extracted method.
+They describe that variability between identifiers and literals have to become parameters in the extracted method.
 They identify the optimization problem where the variability between cloned fragments should be limited, to avoid limiting the reusability of methods because of too many method parameters.
@@
 We address precondition 6 by allowing modified statements as return values (and turning the calls to the extracted method into variable assignments).
-If more than 1 variable is assigned or other return values would be present, we flag the cloned fragments as ``not refactorable''.
-We address precondition 7 by using lambda expressions, which do allow void type methods to be used as parameters.
+If more than 1 variable is assigned or other return values would be present, we flag the cloned fragments as ``multiple return values'' (see Section~\ref{sec:refactorabilitysetup}).
+We address precondition 7 by using lambda expressions, which allow methods without return value to be used as parameters (using the \texttt{Runnable} interface).
 We address precondition 8 by analyzing all branches in the code.
@@
 
-After all these studies that determine what preconditions apply to be able to refactor modified clones, the authors propose a tool named JDeodorant that helps in the process of refactoring such clones~\cite{mazinanian2016jdeodorant}.
+After these studies that determine what preconditions apply to be able to refactor modified clones, the authors propose a tool named JDeodorant that helps in the process of refactoring such clones~\cite{mazinanian2016jdeodorant}.
 This tool takes the output of many popular clone detection tools \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, cordy2011nicad} and proposes refactoring opportunities.
@@
 They do this in order to mitigate some of the earlier established preconditions.
-Working with lambda's makes it possible to refactor statement gaps and expression differences.
+Working with lambda expressions makes it possible to refactor statement gaps and expression differences.
 They find that lambda expressions are very suitable to refactor clones with variability.
-The authors do not discuss the impact of such refactorings on system maintainability costs, their main focus is to positively influence the refactorability of clone classes.
+The authors do not discuss the impact of such refactorings on system maintainability, their main focus is to positively influence the refactorability of clone classes.
 

### 2019-08-25 sections/related_work.tex
Related work

@@
 \section{Refactoring Technique for Large Groups of Software Clones}
-A thesis by AlWaqfi~\cite{alwaqfi2017refactoring} propose a method for assessing refactorability of clone classes , whereas the previous tools only focus on clone pairs.
+In a thesis by AlWaqfi~\cite{alwaqfi2017refactoring} the author proposes a method for assessing refactorability of clone classes, whereas most of the previous tools only focus on clone pairs.
 The author surveys a set of clone detection tools \cite{kamiya2002ccfinder, baxter1999clonedr, jiang2007deckard, cordy2011nicad} and uses a publicly available dataset \cite{tsantalis2015assessing} to measure the amount of clones found by these tools.
-The resulting data shows that significant portions of source code of the measured systems are cloned.
-The data also shows that there are large differences between different tools in the amount of clones found.
-The author also measures of how many clone instances clone classes consist.
+The resulting data shows that there is a lot of variability in the amount of detected clones between different clone detection tools.
+The author measures of how many clone instances there are in clone classes.
 According to these experiments, about 68\% of clone classes consist of 2 clone instances, 13\% have 3 clone instances, 7\% have 4 clone instances and about 12\% is even larger.
@@
 They calculate the metrics of the system before refactoring, detect clones using CCFinder \cite{kamiya2002ccfinder}, use JDeodorant to refactor a subset of the detected clones \cite{mazinanian2016jdeodorant} and measure the metrics again after refactoring to assess the impact of the refactoring process on quality attributes.
-They conclude that some metrics affect some quality attributes positively and some negatively.
+They conclude that clone refactoring affects some quality attributes positively and some negatively.
 
-In this study, the authors only compare before and after snapshots of refactoring the entire system. This makes it hard to determine why some metrics are negatively influenced.
+In this study, the authors only compare before- and after-snapshots of refactoring the entire system.
+This makes it hard to determine why some metrics are negatively influenced.
+In our study, we consider each separate refactoring, which yields more precise results.
 
@@
 On average, it took participants 1,043 seconds to refactor 2.75 clones.
-They indicate that this is 35\% faster than when working with a popular clone detection tool (GemX).
+They report that this is 35\% faster than when working with a popular clone detection tool (GemX).
 
@@
 The metrics they measure are size, cyclomatic complexity and coupling.
-To collect this data, they used two systems that have been de-duplicated manually.
-They conclude that there is a strong, positive correlation between clone refactoring and the reduction of the size of unit test cases.
+To collect this data, they use two systems that have been de-duplicated manually.
+They conclude that there is a strong, positive correlation between clone refactoring and the reduction of the size of unit tests.
 They also show that code quality attributes that are related to testability are significantly improved.

### 2019-08-25 sections/results.tex
Appendix
Various improvements

@@
 Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different location categories (see Section~\ref{sec:setuplocation}).
+We can see from these results that nearly 80\% of clones are found at method level.
+17\% of clones are found at class level, meaning they exceed the boundaries of a single method (or do not span methods at all).
+Constructors account for approximately 3\% of clones.
+In interfaces, only 1\% of clones is found.
+
 \begin{table}[H]
@@
 \end{table}
-
-We can see from these results that most clones are found at method level.
 
@@
 
-\subsection{Relation}
+\subsection{Relation} \label{sec:resultsrelation}
 Table~\ref{tab:relationref} shows our data regarding how different relations influence maintainability.

### 2019-08-27 code_examples/AdditionUtils.java
Examples

@@ -1,0 +1,17 @@
+package com.sb.cryo.util;
+
+import java.util.List;
+import com.notificationlib.*;
+
+public class AdditionUtils
+{
+	public void addToList(List l) {
+		l.add(getClass().getName());
+	}
+
+	public int addTen(int x) {
+		x = x + 10; // add number
+		Notifier.notifyChanged(x);
+		return x;
+	}
+}

### 2019-08-27 code_examples/GameOverScene.java

@@ -8,9 +8,10 @@ public class LoseScene extends Scene
 		apple.setStatus(this);
 	}
 
-	public void concatTen(String x) {
+	public String concatTen(String x) {
 		x = x + 10;
 		notifyChanged(x);
 		return x;
 	}
 }
+

### 2019-08-27 code_examples/GameWinningContext.java

@@ -1,0 +1,17 @@
+package com.sb.fruitgame;
+
+import com.sb.fruitgame.Apple;
+
+public class GameScene extends com.sb.fruitgame.Scene
+{
+	public void collect(com.sb.fruitgame.Apple apple) {
+		((com.sb.fruitgame.Apple)apple).(com.sb.fruitgame.Scene.setStatus)((com.sb.fruitgame.Scene)this);
+	}
+
+	public int addTen(int x) {
+		(int)x = (int)x + 10;
+		com.sb.fruitgame.Scene.notifyChanged((int)x);
+		return (int)x;
+	}
+}
+

### 2019-08-27 code_examples/GameWinningScene.java

@@ -8,9 +8,10 @@ public class GameScene extends Scene
 		apple.setStatus(this);
 	}
 
-	public void addTen(int x) {
+	public int addTen(int x) {
 		x = x + 10;
 		notifyChanged(x);
 		return x;
 	}
 }
+

### 2019-08-27 code_examples/StringUtils.java

@@ -1,0 +1,16 @@
+package com.sb.cryo.util;
+
+import java.awt.List;
+
+public class StringUtils
+{
+	public void addToList(List l) {
+		l.add(getClass().getName());
+	}
+
+	public String concatTen(String x) {
+		x = x + 10; // concat number
+		Notifier.notifyChanged(x);
+		return x;
+	}
+}

### 2019-08-27 code_examples/AdditionUtils.java
pres

@@ -1,7 +1,7 @@
-package com.sb.cryo.util;
+package com.sb.cryo.addition;
 
-import java.util.List;
 import com.notificationlib.*;
+import java.util.List;
 
 public class AdditionUtils
 {

### 2019-08-27 sections/results.tex
Fixed some naming

@@
 17\% of clones are found at class level, meaning they exceed the boundaries of a single method (or do not span methods at all).
-Constructors account for approximately 3\% of clones.
+Constructors account for approximatelyTop- 3\% of clones.
 In interfaces, only 1\% of clones is found.
@@
 \textit{\textbf{Category}} & \textit{\textbf{Contents}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
-\multirow{2}{*}{Partial} & Partial Method & 219,540 & 74.05\% & \multirow{2}{*}{229,521}& \multirow{2}{*}{77.42\%} \\ \cmidrule(lr){2-4}
- & Partial Constructor & 9,981 & 3.37\% & & \\ \midrule
+\multirow{2}{*}{Partial} & Method Body & 219,540 & 74.05\% & \multirow{2}{*}{229,521}& \multirow{2}{*}{77.42\%} \\ \cmidrule(lr){2-4}
+ & Constructor Body & 9,981 & 3.37\% & & \\ \midrule
 \multirow{3}{*}{Other} & Several Methods & 22,749 & 7.67\% & \multirow{3}{*}{53,773} & \multirow{3}{*}{18.14\%} \\ \cmidrule(lr){2-4}
@@
 \textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{\% (All)}} \\ \midrule
-Can Be Extracted & 24,157 & 28.2\%  \\
-Is Not A Partial Method & 21,625 & 25.3\% \\
+Can be Extracted & 24,157 & 28.2\%  \\
+Is not in a Method Body & 21,625 & 25.3\% \\
 Top-level AST-Node is not a Statement & 19,887 & 23.2\% \\
@@
 Complex Control Flow & 1,106 & 1.3\% \\
-Overlap In Clone Class & 147 & 0.2\% \\
-Not In Class Or Interface & 70 & 0.1\% \\
+Overlap in Clone Class & 147 & 0.2\% \\
+Not in Class or Interface & 70 & 0.1\% \\
 \bottomrule

### 2019-08-29 main.tex
Related work
Corrected the date
Fixed some stuff

@@
 \usepackage{longtable}
-\usepackage[style=ieee,citestyle=numeric-comp]{biblatex}
+\usepackage[style=ieee,citestyle=numeric-comp,dashed=false]{biblatex}
 \usepackage[colorinlistoftodos, prependcaption]{todonotes}
@@
 			&\textsc{\Large University of Amsterdam}\\
-			&\textsc{Faculty of Physics, Mathematics and Informatics}\\
+			&\textsc{Faculty of Informatics}\\
 			&\textsc{Master Software Engineering}\\
@@
 		\vspace{11pt}
-		30 June 2019, \pageref{LastPage} pages
+		\today, \pageref{LastPage} pages
 	\end{center}
@@
 	\begin{tabular}{ll}
-		\textbf{Research supervisor:} Dr. Ana Oprescu, \email{ana.oprescu@uva.nl} \\
-		\textbf{Host/Daily supervisor:} Xander Schrijen Msc., \email{x.schrijen@sig.eu}\\
-		\textbf{Host organisation/Research group:} Software Improvement Group (SIG), \url{http://sig.eu/}
+		\textbf{Academic supervisor:} Dr. Ana Oprescu, \email{ana.oprescu@uva.nl} \\
+		\textbf{Host supervisor:} Xander Schrijen MSc., \email{x.schrijen@sig.eu}\\
+		\textbf{Host organisation:} Software Improvement Group (SIG), \url{http://sig.eu/}
 	\end{tabular}

### 2019-09-09 date/conference_041818.tex
Added date conference stuff

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes,
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins,
column widths, line spaces, and text fonts are prescribed; please do not
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement
and others are deliberate, using specifications that anticipate your paper
as one part of the entire proceedings, and not as an independent document.
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a
separate text file. Complete all content and organizational editing before
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been
formatted and styled. Do not number text heads---{\LaTeX} will do that
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text,
even after they have been defined in the abstract. Abbreviations such as
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your
equations more compact, you may use the solidus (~/~), the exp function, or
appropriate exponents. Italicize Roman symbols for quantities and variables,
but not Greek symbols. Use a long dash rather than a hyphen for a minus
sign. Punctuate equations with commas or periods when they are part of a
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the
symbols in your equation have been defined before or immediately following
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A
minimum of one author is required for all conference articles. Author names
should be listed starting from left to right and then moving down to the
next line. This is the author sequence that will be used in future citations
and by indexing services. Names should not be listed in columns nor group by
affiliation. Please keep your affiliations as succinct as possible (for
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not
topically subordinate to each other. Examples include Acknowledgments and
References and, for these, the correct style to use is ``Heading 5''. Use
``figure caption'' for your Figure captions, and ``table head'' for your
table title. Run-in heads, such as ``Abstract'', will require you to apply a
style (in this case, italic) in addition to the style provided by the drop
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For
example, the paper title is the primary text head because all subsequent
material relates and elaborates on this one topic. If there are two or more
sub-topics, the next level head (uppercase Roman numerals) should be used
and, conversely, if there are not at least two sub-topics, then no subheads
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and
bottom of columns. Avoid placing them in the middle of columns. Large
figures and tables may span across both columns. Figure captions should be
below the figures; table heads should appear above the tables. Insert
figures and tables after they are cited in the text. Use the abbreviation
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4}
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words
rather than symbols or abbreviations when writing Figure axis labels to
avoid confusing the reader. As an example, write the quantity
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including
units in the label, present them within parentheses. Do not label axes only
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of
quantities and units. For example, write ``Temperature (K)'', not
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B.
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at
the bottom of the column in which it was cited. Do not put footnotes in the
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use
``et al.''. Papers that have not been published, even if they have been
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers
that have been accepted for publication should be cited as ``in press'' \cite{b5}.
Capitalize only the first word in a paper title, except for proper nouns and
element symbols.

For papers published in translation journals, please give the English
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2019-09-09 date/paper.tex
blind paper
Put in stuff from icse paper

--- 2019-09-09 date/conference_041818.tex
@@
 
-\title{Paper Title*\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
-\thanks{Identify applicable funding agency here. If none, delete this.}
-}
-
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-}
+\title{Improving Software Maintainability through Automated Refactoring of Code Clones}
 
@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes,
-or Math in Paper Title or Abstract.
+Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code.
+To remove such anti-patterns, the codebase should be refactored.
+Many tools aid in the detection process of such duplication problems but fail to determine whether refactoring a duplicate fragment would improve the maintainability.
+
+We address this shortcoming by first analyzing what data should be gathered from an automatically refactored system.
+We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them.
+We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system.
+Based on these results, one could decide which clones would improve system design if refactored.
+We evaluate our approach over a large corpus of open source Java projects.
+
+We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use.
+We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored.
+The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones with more than requiring more than one external parameter decreases maintainability.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+code clones, refactoring, static code analysis, object-oriented programming
 \end{IEEEkeywords}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+Duplicate fragments in source code (also named ``code clones'') are often seen as one of the most harmful types of technical debt~\cite{fowler2018refactoring}.
+Duplicate fragments create implicit dependencies that make the code harder to maintain as the resolution of erroneous behavior in one location may have to be applied to all the cloned code as well~\cite{ostberg2014automatically}.
+Apart from that, code clones can contribute up to 25\% of the code size~\cite{bruntink2005use}.
 
-\section{Ease of Use}
+Current code clone detection techniques base their thresholds and prioritization on a limited set of metrics.
+Often, clone detection techniques are limited to measuring the size of clones to determine whether they should be considered.
+Because of this, the output of clone detection tools is often of limited assistance to the developer in the refactoring process.
 
-\subsection{Maintaining the Integrity of the Specifications}
+In this study, we define a technique to detect clones such that they can be automatically refactored.
+We list a set of criteria that can obstruct refactoring opportunities.
+We evaluate the relation and location of clones to determine which refactoring techniques are best suited.
+We introduce a tool that automatically refactors clones by extracting new methods out of duplicated code.
 
-The IEEEtran class file is used to format your paper and style the text. All margins,
-column widths, line spaces, and text fonts are prescribed; please do not
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement
-and others are deliberate, using specifications that anticipate your paper
-as one part of the entire proceedings, and not as an independent document.
-Please do not revise any of the current designations.
+We evaluate our approach by comparing the maintainability of before- and after snapshots of a codebase for each duplication problem that is refactored.
+We define which factors have the greatest influence on whether a clone improves maintainability when refactored.
+We find a set of thresholds by which clones can be detected that are more likely to improve maintainability when refactored.
+This allows for more a accurate suggestion of code clones for refactoring and can assist in the refactoring process.
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a
-separate text file. Complete all content and organizational editing before
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on
-proofreading, spelling and grammar.
+\section{Background}
+Our study lies at the intersection of code clone and refactoring research. We use two concepts to argue about code clones~\cite{roy2007survey}:
+\\ \textbf{Clone instance}: A single cloned fragment.
+\\ \textbf{Clone class}: A set of similar clone instances.
 
-Keep your text and graphic files separate until after the text has been
-formatted and styled. Do not number text heads---{\LaTeX} will do that
-for you.
+The most common technique for refactoring clones is ``Extract Method''~\cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
+Applying this technique entails moving functionality in the body of a method to a new method.
+To reduce duplication with this technique, we extract the contents of a single clone instance to a new method and replace all clone instances in a clone class by a call to this method.
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text,
-even after they have been defined in the abstract. Abbreviations such as
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use
-abbreviations in the title or heads unless they are unavoidable.
+\begin{figure*}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+package com.sb.game;
 
-\subsection{Units}
+import java.util.List;
+
+public class GameScene
+{
+|\highlightYellow|	public void addToList(List l) {
+|\highlightYellow|		l.add(getClass().getName());
+|\highlightYellow|	}
+
+	public void addTen(int x) {
+|\highlightYellow|		x = x + 10; // Addition
+|\highlightYellow|		Notifier.notifyChanged(x);
+|\highlightYellow|		return x;
+	}
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+package com.sb.fruitgame;
+
+import java.awt.List; // Different type
+
+public class LoseScene
+{
+|\highlightYellow|	public void addToList(List l) {
+|\highlightYellow|		l.add(getClass().getName());
+|\highlightYellow|	}
+
+	public void concatTen(String x) {
+|\highlightYellow|		x = x + 10; // String concat
+|\highlightYellow|		Notifier.notifyChanged(x);
+|\highlightYellow|		return x;
+	}
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Example of textually equal code fragments that differ in functionality.}
+\label{fig:type1}
+\end{figure*}
+
+\section{Related Work}
+The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
+The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems.
+This tool is based on several studies that look into different aspects of code clone refactoring.
+In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how does variability between cloned fragments influence the refactoring techniques required and their implications on system design.
+Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability.
+This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.
+
+A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process.
+The main focus is to find out which clones \textbf{can} be refactored.
+We extend this work by looking into which clones \textbf{should} be refactored.
+We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design.
+We measure which clones improve maintainability when refactored.
+This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
+
+\section{Defining refactorable clones}
+In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}.
+We discuss how we can define clones such that they can be automatically refactored without side effects on the source code.
+
+\subsection{Ensuring Equality}\label{sec:t1r}
+Most modern clone detection tools detect duplication by comparing the code textually together with the omission of certain tokens~\cite{roy2009comparison, svajlenko2014evaluating}.
+Clones detected by such means may not always be suitable for refactoring, because textual comparison fails to take into account the context of certain symbols in the code.
+Information that gets lost in textual comparison is the referenced declaration for type, variable and method references.
+Equally named type, variable and method references may refer to different declarations with a different implementation (Fig~\ref{fig:type1} shows an example of this).
+Such clones can be harder to refactor, if beneficial at all.
+
+To detect automatically refactorable clones, we propose to:
 \begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
+  \item Compare variable references not only by their name but also by their type.
+  \item Compare referenced types by their fully qualified identifier (FQI). The FQI of a type reference describes the full path to where it is declared.
+  \item Compare method references by their fully qualified signature (FQS). The FQS of a method reference describes the full path to where it is declared, plus the FQI of each of its parameters.
 \end{itemize}
 
-\subsection{Equations}
-Number equations consecutively. To make your
-equations more compact, you may use the solidus (~/~), the exp function, or
-appropriate exponents. Italicize Roman symbols for quantities and variables,
-but not Greek symbols. Use a long dash rather than a hyphen for a minus
-sign. Punctuate equations with commas or periods when they are part of a
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
+\subsection{Allowing variability in a controlled set of expressions} \label{sec:t2r}
+Often, duplication fragments in source code do not match exactly~\cite{kodhai2013method}.
+When developers duplicate fragments of code, they modify the duplicated block to fit its new location and purpose.
+To detect duplicate fragments with minor variance, we look into what expressions we can allow variability in, while still being refactorable.
+
+We define the following expressions as refactorable when varied:
+\begin{itemize}
+  \item \textbf{Literals}: Only if all varying literals in a clone class have the same type.
+  \item \textbf{Variables}: Only if all varying variables in a clone class have the same type.
+  \item \textbf{Method references}: Only if the return value of referenced methods match (or are not used).
+\end{itemize}
+Often when allowing such variance, trade-offs come into play~\cite{krishnan2013refactoring, krishnan2014unification}.
+For instance, variance in literals may require the introduction of a parameter to an extracted method if the ``Extract Method'' refactoring method is used, increasing the required effort to comprehend the code.
+
+\subsection{Gapped clones} \label{sec:t3r}
+Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context~\cite{roy2007survey}.
+When dealing with such a situation, there are several opportunities to refactor so-called ``gapped clones''~\cite{ueda2002detection, zhao2018automatic}.
+``Gapped clones'' are two clone instances separated by a ``gap'' of non-cloned statement(s).
+We define the following methods to refactor such clones:
+\begin{itemize}
+  \item We wrap the difference in statements in a conditionally executed block, one path for each different (group of) statement(s).
+  \item We use a lambda function to pass the difference in statements from each location of the clone~\cite{tsantalis2017clone}.
+\end{itemize}
+For both refactoring techniques, a trade-off is at play. This is because these solutions increase the complexity and volume of the source code in favor of removing a clone.
+
+\section{The CloneRefactor tool}
+To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
+We created a set of control projects\footnote{Control projects for assessing clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
+
+None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
+This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
+In the following sections, we explain these steps.
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/flow}
+  \caption{Simple flow diagram of CloneRefactor.}
+  \label{fig:clonerefactorflow}
+\end{figure}
+
+\subsection{Clone Detection}
+We use an AST-based method to detect clones.
+Clones are detected on a statement level: only full statements are considered as clones.
+In this process, we limit the variability between indicated expressions (see Sec.~\ref{sec:t2r}) by a threshold.
+This threshold is the percentage of different expressions against the total number of expressions in the source code:
+\begin{equation}\label{eq:type2r}
+\text{Variability}=\frac{\text{Different expressions}}{\text{Total expressions}}*100
 \end{equation}
 
-Be sure that the
-symbols in your equation have been defined before or immediately following
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
+After all clones have been detected, CloneRefactor determines whether clone classes can be merged into gapped clones (see Sec.~\ref{sec:t3r}).
+The maximum size of the gap is limited by a threshold.
+This threshold is the percentage of (not-cloned) statements in the gap against the sum of statements in both clones surrounding it.
+Unlike the expression variability threshold, this threshold can exceed 100\%:
+\begin{equation}\label{eq:type3r}
+\text{Gap Size}=\frac{\text{Statements in gap}}{\text{Statements in clones}}*100
+\end{equation}
 
-\subsection{\LaTeX-Specific Advice}
+To verify the correctness of all detected clones, we ran the tool over a large project and manually checked the output.
+We also created a set of control projects to test the correctness for many edge cases.
 
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
+\begin{figure*}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+|\highlightYellow|int a = getA();
+|\highlightYellow|while(a<1000) {
+|\highlightYellow|  a *= 5;
+  doC();
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+|\highlightYellow|int a = getA();
+|\highlightYellow|while(a<1000) {
+|\highlightYellow|  a *= 5;
+  doB(a);
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{A clone that spans a block partially.}
+\label{fig:refactorabilitypartialblock}
+\end{figure*}
 
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
+\subsection{Context Mapping} \label{sec:context}
+After clones are detected, we map the context of these clones.
+We have identified three properties of clones as their context: relation and location.
+We identify categories for each of these properties, to get a detailed insight into the context of clones.
 
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
+\subsubsection{Relation}\label{sec:relation}
+Clone instances in a clone class may have a relation with each other through inheritance.
+This relation has a big impact on how the clone should be refactored~\cite{fontana2015duplicated}.
+We define the following categories to map the relation between clone instances in a clone class.
+These categories do not map external classes (classes outside the project, e.g.
+belonging to a library) unless explicitly stated:
+\begin{itemize}
+    \item \textbf{Common Class}: All clone instances are in the same class.
+    \begin{itemize}
+        \item \textbf{Same Method}: All clone instances are in the same method.
+        \item \textbf{Same Class}: All clone instances are in the same class.
+    \end{itemize}
+    \item \textbf{Common Hierarchy}: All clone instances are in the same inheritance hierarchy.
+    \begin{itemize}
+        \item \textbf{Superclass}: Clone instances reside in a class or its parent class.
+        \item \textbf{Sibling Class}: All clone instances reside in classes with the same parent class.
+        \item \textbf{Ancestor Class}: All clone instances reside in a class, or any of its recursive parents.
+        \item \textbf{First Cousin}: All clone instances reside in classes with the same grandparent class.
+        \item \textbf{Same Hierarchy}: All clone instances are part of the same inheritance hierarchy.
+    \end{itemize}
+    \item \textbf{Common Interface}: All clone instances are in classes that have the same interface.
+    \begin{itemize}
+        \item \textbf{Same Direct Interface}: All clone instances are in classes that have the same interface.
+        \item \textbf{Same Class}: All clone instances are in an inheritance hierarchy that contains the same interface.
+    \end{itemize}
+    \item \textbf{Unrelated}: All clone instances are in classes that have the same interface.
+    \begin{itemize}
+        \item \textbf{No Direct Superclass}: All clone instances are in classes that have the Object class as their parent.
+        \item \textbf{No Indirect Superclass}: All clone instances are in a hierarchy that contains a class that has the Object class as their parent.
+        \item \textbf{External Superclass}: All clone instances are in classes the same external class as their parent.
+        \item \textbf{Indirect External Ancestor}: All clone instances are in a hierarchy that contains a class that has an external class as their parent.
+    \end{itemize}
+\end{itemize}
 
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
+Based on these relations, CloneRefactor determines where to place the cloned code when refactored.
+These categories are mutually exclusive: a clone class will be flagged as the first relation in the above list that it applies to.
+The code of clones that have a \textit{Common Class} relation can be refactored by placing the cloned code in this same class.
+The code of clones with a \textit{Common Hierarchy} relation can be placed in the intersecting class in the hierarchy (the class all clone instances have in common as an ancestor).
+The code of clones with a \textit{Common Interface} relation can be placed in the intersecting interface, but in the process has to become part of the classes' public contract.
+The code of clones that are \textit{Unrelated} can be placed in a newly created place: either a utility class, a new superclass abstraction or an interface.
 
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
+\subsubsection{Location}\label{sec:location}
+The location of a clone instance determines what refactoring techniques can be applied to refactor such clones. We define the following categories by which we analyze the location of clones:
+\begin{enumerate}
+  \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
+  \item \textbf{Partial Method/Constructor Body:} A clone that spans (a part of) the body of a method/constructor.
+  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods.
+  \item \textbf{Only Fields:} A clone that spans only global variables.
+  \item \textbf{Other:} Anything that does not match with above-stated categories.
+\end{enumerate}
 
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
+\subsubsection{Full Method/Constructor/Class/Interface/Enumeration}
+The categories denote that a full declaration (method, class, etc.) often denote redundancy and are often easy to refactor: one of both declarations is redundant and should be removed.
+Clones in the ``Partial Method/Constructor'' category can often be refactored using the ``Extract Method'' refactoring technique.
+Clones consisting of \textit{Several Methods} give a strong indication that cloned classes are missing some form of abstraction, or their abstraction is used inadequately.
+Clones consisting of \textit{Only Fields} often indicate data redundancy: different classes use the same data.
 
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
+\subsection{Refactoring}
+CloneRefactor can refactor clones using the ``Extract Method'' refactoring technique. In this section, we show which clones we refactor and how we apply these transformations.
 
-\subsection{Some Common Mistakes}\label{SCM}
+\subsubsection{Extract Method} \label{sec:refactorability}
+Several influencing factors may obstruct the possibility to extract code to a new method:
 \begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
+    \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
+    \item \textbf{Spans Part Of A Block}: This clone spans a part of a block statement. An example of this is shown in Fig.~\ref{fig:refactorabilitypartialblock}.
+    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Sec.~\ref{sec:location}, the ``Extract Method'' refactoring technique cannot be applied.
+    \item \textbf{Returns Multiple Values}: If a clone modifies or declares multiple pieces of data that it should return.
+    \item \textbf{Top-Level Non-Statement}: If one of the top-level AST nodes of the clone is not a statement. For instance, if a (part of) an anonymous class is cloned.
+    \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method.
+Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
 \end{itemize}
-An excellent style manual for science writers is \cite{b7}.
+Clones that do not fall in the \textit{Can Be Extracted} category may require additional transformations or other techniques to refactor.
+CloneRefactor only refactors the clones that \textit{Can Be Extracted}.
 
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A
-minimum of one author is required for all conference articles. Author names
-should be listed starting from left to right and then moving down to the
-next line. This is the author sequence that will be used in future citations
-and by indexing services. Names should not be listed in columns nor group by
-affiliation. Please keep your affiliations as succinct as possible (for
-example, do not differentiate among departments of the same organization).
+\subsubsection{AST Transformation}
+CloneRefactor uses JavaParser~\cite{smith2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
+To refactor clones, CloneRefactor creates a new method declaration and moves all statements from a clone instance in the clone class to the new method.
+This method is placed according to the relation between the clone instances (see Sec.~\ref{sec:relation}).
+CloneRefactor analyzes the source code of the extracted method and populates it with the following properties:
+\begin{itemize}
+  \item \textbf{Parameters}: For each variable used that is not accessible from the scope of the extracted method.
+  \item \textbf{A return value}: If the method modifies or declares local data that is needed outside of its scope, or if the cloned fragments already returned data.
+  \item \textbf{Thrown exception}: If the method throws an uncaught exception that is not a \texttt{RuntimeException}.
+\end{itemize}
+CloneRefactor then removes all cloned code and replaces it with a method call to the newly created method.
+In case of a return value, CloneRefactor either assigns the call result, declares it or returns it accordingly.
 
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through
-your paper. There are two types: component heads and text heads.
+\subsubsection{Characteristics of the extracted method}\label{sec:characteristics}
+We define the following characteristics of the extracted method and/or the call:
+\begin{itemize}
+\item \textbf{Tokens}: The number of tokens in the body of the method.
+\item \textbf{Relation}: The relation category (Sec.~\ref{sec:relation}) by which this methods' location was determined.
+\item \textbf{Returns}: Whether the method calls return, declare, assign or don't use any data from the extracted method.
+\item \textbf{Parameters}: The number of parameters the extracted method has.
+\end{itemize}
+We hypothesize that these characteristics are the main factors influencing the impact on the maintainability of the system as a result of refactoring the clone.
 
-Component heads identify the different components of your paper and are not
-topically subordinate to each other. Examples include Acknowledgments and
-References and, for these, the correct style to use is ``Heading 5''. Use
-``figure caption'' for your Figure captions, and ``table head'' for your
-table title. Run-in heads, such as ``Abstract'', will require you to apply a
-style (in this case, italic) in addition to the style provided by the drop
-down menu to differentiate the head from the text.
+\subsubsection{Impact on maintainability metrics} \label{sec:metrics}
+CloneRefactor measures the impact on maintainability metrics of the refactored source code for each clone class that is refactored.
+These metrics are derived from Heitlager et al.~\cite{heitlager2007practical}.
+This paper defines a set of metrics to measure the maintainability of a system.
+For each of these metrics, risk profiles are proposed to determine the maintainability impact on the system of a whole.
 
-Text heads organize the topics on a relational, hierarchical basis. For
-example, the paper title is the primary text head because all subsequent
-material relates and elaborates on this one topic. If there are two or more
-sub-topics, the next level head (uppercase Roman numerals) should be used
-and, conversely, if there are not at least two sub-topics, then no subheads
-should be introduced.
+To determine whether the maintainability improves when refactoring a single clone, we need to measure the impact of small-grained changes.
+Because of that, we measure only a subset of the metrics~\cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
+The subset of metrics we decided to focus on are all metrics that are measured on method level (as the other metrics show a lesser impact on the maintainability for these small changes).
+These metrics are:
+\begin{itemize}
+\item \textbf{Duplication}: In Heitlager et al.~\cite{heitlager2007practical} this metric is measured by taking the amount of duplicated lines.
+We decided to use the amount of duplicated tokens part of a clone class instead, to have a stronger reflection of the impact of the refactoring by measuring a more fine-grained system property.
+\item \textbf{Volume}: The more code a system has, the more code has to be maintained.
+The paper~\cite{heitlager2007practical} measures volume as lines of code.
+As with duplication, we use the number of tokens instead.
+\item \textbf{Complexity}: Heitlager et al.~\cite{heitlager2007practical} use MCCabe complexity~\cite{mccabe1976complexity} to calculate their complexity metric.
+The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.
+\item \textbf{Method Interface Size}: The number of parameters that a method has.
+If a method has many parameters, the code may become harder to understand and it is an indication that data is not encapsulated adequately in objects~\cite{fowler2018refactoring}.
+\end{itemize}
 
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and
-bottom of columns. Avoid placing them in the middle of columns. Large
-figures and tables may span across both columns. Figure captions should be
-below the figures; table heads should appear above the tables. Insert
-figures and tables after they are cited in the text. Use the abbreviation
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
+\section{Experimental setup}
+In this section, we describe the setup of our experiments.
 
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4}
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+\subsection{Corpus}
+We ran all our experiments using CloneRefactor on a corpus of open source Java projects.
+This corpus is derived from the corpus of a study that uses machine learning to determine the suitability of Java projects on GitHub for data analysis purposes~\cite{githubCorpus2013}.
+
+CloneRefactor requires all libraries of the projects it analyses, to find the full paths of all referenced symbols in the source code (see Sec.~\ref{sec:t1r}).
+Because of that requirement, we decided to filter the corpus to only projects using the Maven build automation system.
+We created a set of scripts\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} to prepare such a corpus with all dependencies included.
+
+This procedure results in 2.267 Java projects including all their dependencies.
+The projects vary in size and quality.
+The total size of all projects is 14.2M lines (11.3M when excluding whitespace) over a total of 100K Java files.
+This is an average of 6.3K lines over 44 files per project.
+The largest project in the corpus is \textit{VisAD} with 502K lines.
+
+\subsection{Tool Validation}
+We have validated the correctness of CloneRefactor through unit tests and empirical validation.
+First, we created a set of 57 control projects to verify the correctness in many (edge) cases.
+These projects contain clones for each identified relation, location, and refactorability category to see whether they get correctly identified.
+Next, we run the tool over the corpus and manually verify samples of the acquired results.
+This way, we check both the correctness of the identified clones, their context, and their proposed refactoring.
+
+We also test the correctness of the resulting code after refactoring.
+For this, we use a GitHub project named JFreeChart.
+JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor.
+
+\subsection{Minimum clone size}
+In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored.
+However, when clones are very small, they may never be able to improve maintainability.
+The detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication.
+Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones are very unlikely to improve maintainability when refactored.
+
+\subsection{Thresholds}
+Most clone detection tools can be configured using thresholds.
+These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones.
+Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}.
+Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
+
+%In our experiments, we compare the maintainability scores for different thresholds.
+We use the \textit{standard error} to determine the correlation between the used threshold metric and the maintainability score.
+A low standard error shows that the threshold metric has a high influence on the maintainability score.
+This makes it more suitable to use as a threshold.
+By plotting the maintainability scores for different thresholds, we can determine which thresholds should be used to positively influence maintainability.
+
+%We define the following volume-based thresholds for clones, ordered by how often clone detection tools support such thresholds:
+%\begin{itemize}
+%\item \textbf{Number of lines}: The number of lines a single instance of the clone class spans.
+%\item \textbf{Tokens}: The number of tokens a single instance of the clone class spans.
+%\item \textbf{Number of statements}: The number of statements a single clone instance.
+Often closely reflects the number of lines, but is not dependent on coding style (number of newlines used by the programmer in statements).
+%\item \textbf{Token Volume}: The number of tokens in all clone instances in a clone class combined.
+%\end{itemize}
+
+\subsection{Calculating a maintainability score}\label{sec:metricformula}
+In this study, we use four metrics to determine maintainability (see Sec.~\ref{sec:metrics}).
+For each of these metrics, we determine their value before and after each refactored clone class, resulting in a delta metric score.
+For our experiments, we aggregate the deltas obtained for these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
+We base our aggregation on the following assumptions:
+\begin{itemize}
+  \item All metrics are equal in terms of weight towards system maintenance effort.
+  \item Higher values for the metrics imply lower maintainability.
+  \item Normalizing each obtained metric delta over all deltas obtained for that metric in our dataset results in equally weighted scores.
+\end{itemize}
+We derived these assumptions from supporting evidence shown by Heitlager et al~\cite{heitlager2007practical} and Alves et al.~\cite{alves2010deriving}.
+Using the resulting aggregated maintainability score, we can argue for each refactoring whether it increases or decreases the maintainability of the system.
+
+We normalize each obtained metric delta using the ``Standard score'', which is calculated as follows:
+\begin{equation}\label{eq:scoredev}
+N_{metric} = \frac {\Delta X-\mu}{\sigma}
+\end{equation}
+Where $\Delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metric.
+This method works well for normalization of our data because as we divide by the standard deviation, outliers do not influence the resulting scores negatively.
+
+We then calculate the maintainability for a specific refactoring as follows:
+\begin{equation}\label{eq:scoreref}
+N_{duplication} + N_{complexity} + N_{volume} + N_{parameters}
+\end{equation}
+
+%% RESULTS TABLES (MOVED UP SO LATEX PLACES THEM IN THE RIGHT PLACE)
+
+\begin{table*}
+\centering
+%\resizebox{\textwidth}{!}{%
+\begin{tabular}{@{}lrrrrrr@{}}
+\toprule
+\textit{\textbf{Relation}} & \textit{\textbf{Duplication}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Volume}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
+\textbf{Common Hierarchy} & \textbf{-66.33} & \textbf{0.73} & \textbf{1.20} & \textbf{-8.85} & \textbf{2,202} & \textbf{0.23} \\ \midrule
+\hspace{10pt} Superclass & -64.48 & 0.79 & 0.94 & -7.22 & 229 & 0.42 \\
+\hspace{10pt} Sibling & -70.07 & 0.69 & 1.28 & -10.97 & 1,722 & 0.23 \\
+\rowcolor[HTML]{FFCCC9}
+\hspace{10pt} Same Hierarchy & -44.18 & 0.95 & 0.89 & 1.54 & 87 & 0.10 \\
+\hspace{10pt} First Cousin & -42.69 & 0.89 & 0.93 & 4.86 & 144 & 0.02 \\
+\rowcolor[HTML]{FFCCC9}
+\hspace{10pt} Ancestor & -32.75 & 1.00 & 0.75 & 11.00 & 20 & -0.03 \\ \midrule
+\textbf{Common Interface} & \textbf{-47.06} & \textbf{0.83} & \textbf{1.04} & \textbf{4.50} & \textbf{1,044} & \textbf{-0.02} \\ \midrule
+\hspace{10pt} Same Indirect Interface & -37.08 & 0.93 & 0.82 & 9.96 & 487 & -0.01 \\
+\hspace{10pt} Same Direct Interface & -55.79 & 0.75 & 1.24 & -0.28 & 557 & -0.02 \\ \midrule
+\textbf{Common Class} & \textbf{-52.42} & \textbf{0.87} & \textbf{1.13} & \textbf{1.47} & \textbf{7,239} & \textbf{-0.02} \\ \midrule
+\hspace{10pt} Same Class & -51.85 & 0.86 & 1.03 & 3.36 & 4,874 & 0.04 \\
+\hspace{10pt} Same Method & -53.60 & 0.90 & 1.32 & -2.44 & 2,365 & -0.15 \\ \midrule
+\textbf{Unrelated} & \textbf{-45.86} & \textbf{0.88} & \textbf{1.08} & \textbf{9.56} & \textbf{2,198} & \textbf{-0.15} \\ \midrule
+\hspace{10pt} No Direct Superclass & -52.24 & 0.84 & 1.12 & 6.04 & 811 & -0.06 \\
+\hspace{10pt} External Superclass & -47.09 & 0.87 & 1.13 & 8.77 & 697 & -0.17 \\
+\hspace{10pt} External Ancestor & -35.73 & 0.93 & 0.95 & 14.58 & 586 & -0.21 \\
+\hspace{10pt} No Indirect Superclass & -44.89 & 0.84 & 1.18 & 14.08 & 104 & -0.30 \\ \midrule
+\textbf{Grand Total} & \textbf{-53.26} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
+\end{tabular}%
+%}
+\caption{Influence on maintainability of refactoring clones with the specified relation categories.}
+\label{tab:relation_refactor}
+\end{table*}
+
+%% END TABLES
+
+\section{Results}
+In this section, we share the results of our experiments.
+
+\subsection{Clone context}
+To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones (see Sec.~\ref{sec:context}).
+
+\subsubsection{Relation}
+Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for the identified relations between clone instances (see Sec.~\ref{sec:relation}).
+
+\begin{table}[H]
+\centering
+\begin{tabular}{@{}llrr@{}}
+\toprule
+\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} \\ \midrule
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
+ & Same Method & 8,955 &  \\ \midrule
+\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342} \\ \cmidrule(lr){2-3}
+ & Superclass & 2,616 &  \\ \cmidrule(lr){2-3}
+ & First Cousin & 1,219 &  \\ \cmidrule(lr){2-3}
+ & Common Hierarchy & 720 &  \\ \cmidrule(lr){2-3}
+ & Ancestor & 199 &  \\ \midrule
+\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314} \\ \cmidrule(lr){2-3}
+ & External Superclass & 4,525 &  \\ \cmidrule(lr){2-3}
+ & External Ancestor & 3,347 &  \\ \cmidrule(lr){2-3}
+ & No Indirect Superclass & 1,765 &  \\ \midrule
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} \\ \cmidrule(lr){2-3}
+ & Same Indirect Interface & 5,552 &  \\ \bottomrule
 \end{tabular}
-\label{tab1}
-\end{center}
+\caption{Number of clone classes per clone relation}
+\label{tab:relation}
 \end{table}
 
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words
-rather than symbols or abbreviations when writing Figure axis labels to
-avoid confusing the reader. As an example, write the quantity
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including
-units in the label, present them within parentheses. Do not label axes only
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of
-quantities and units. For example, write ``Temperature (K)'', not
-``Temperature/K''.
+Our results show that most clones (37\%) are in a common class. 24\% of clones are in a common hierarchy. Another 24\% of clones are unrelated. 15\% of clones are in an interface.
 
-\section*{Acknowledgment}
+\subsubsection{Location}
+Table~\ref{tab:location} displays the number of clone classes found for the entire corpus for different locations (see Sec.~\ref{sec:location}).
 
-The preferred spelling of the word ``acknowledgment'' in America is without
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B.
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor
-acknowledgments in the unnumbered footnote on the first page.
+\begin{table}[H]
+\centering
+\begin{tabular}{@{}llrr@{}}
+\toprule
+\textit{\textbf{Category}} & \textit{\textbf{Location}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
+\multirow{2}{*}{Partial} & Partial Method & 219,540 & \multirow{2}{*}{229,521} \\ \cmidrule(lr){2-3}
+ & Partial Constructor & 9,981 &  \\ \midrule
+\multirow{5}{*}{Full} & Full Method & 12,990 & \multirow{5}{*}{13,173} \\ \cmidrule(lr){2-3}
+ & Full Interface & 64 &  \\ \cmidrule(lr){2-3}
+ & Full Constructor & 58 &  \\ \cmidrule(lr){2-3}
+ & Full Class & 37 &  \\ \cmidrule(lr){2-3}
+ & Full Enum & 24 &  \\ \midrule
+\multirow{3}{*}{Other} & Several Methods & 22,749 & \multirow{3}{*}{53,773} \\ \cmidrule(lr){2-3}
+ & Only Fields & 17,700 &  \\ \cmidrule(lr){2-3}
+ & Other & 13,324 &  \\ \bottomrule
+\end{tabular}
+\caption{Number of clone instances for clone location categories}
+\label{tab:location}
+\end{table}
 
-\section*{References}
+From these results, we see that 74\% of clones span part of a method body (77\% if we include constructors).
+8\% of clones span several methods.
+6\% of clones span only global variables.
+Only 4\% of clones span a full declaration (method, class, constructor, etc.).
 
-Please number citations consecutively within brackets \cite{b1}. The
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
+\subsection{Refactorability}
+Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique (see Sec.~\ref{sec:refactorability}).
 
-Number footnotes separately in superscripts. Place the actual footnote at
-the bottom of the column in which it was cited. Do not put footnotes in the
-abstract or reference list. Use letters for table footnotes.
+\begin{table}[H]
+\centering
+\begin{tabular}{@{}lrr@{}}
+\toprule
+\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{\%}} \\ \midrule
+Can Be Extracted & 24,157 & 28.2\%  \\
+Is Not A Partial Method & 21,625 & 25.3\% \\
+Top-level AST-Node is not a Statement & 19,887 & 23.2\% \\
+Spans Part of a Block & 13,181 & 15.5\%  \\
+Multiple Return Values & 5,622 & 6.6\%  \\
+Complex Control Flow & 1,106 & 1.3\% \\
+\end{tabular}
+\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique.}
+\label{tab:refactorability}
+\end{table}
 
-Unless there are six authors or more give all authors' names; do not use
-``et al.''. Papers that have not been published, even if they have been
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers
-that have been accepted for publication should be cited as ``in press'' \cite{b5}.
-Capitalize only the first word in a paper title, except for proper nouns and
-element symbols.
+These results indicate that, given our refactorability criteria, 28\% of clones can be automatically refactored.
+Clones in other categories may require other refactoring techniques or further transformations to be automatically refactorable.
 
-For papers published in translation journals, please give the English
-citation first, followed by the original foreign-language citation \cite{b6}.
+\subsection{Thresholds}
+In our corpus, CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Sec.~\ref{sec:metrics}).
+Using the presented formulas (see Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
+In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.
+Using this data, we find supporting evidence regarding which thresholds are most likely to find clones that should be refactored to improve maintainability.
+
+\subsubsection{Clone Token Volume}
+Figure \ref{fig:maintainabilityscore} shows the obtained results when plotting the clone volume vs the average delta maintainability score.
+We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class.
+For higher token volume numbers we have fewer refactorings that refactor such clones, because of which we represent the x-axis as a logarithmic scale.
+The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.
+
+\begin{figure*}
+  \includegraphics[width=1\textwidth]{img/tokenvolume}
+  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability.}
+  \label{fig:maintainabilityscore}
+\end{figure*}
+
+\subsubsection{Relation}
+Table~\ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability.
+We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance.
+
+The displayed relations are ordered by their scores.
+Overall, the scores do not deviate much (-0.15 to 0.23), indicating that the relation between clones has a minor impact on maintainability.
+Overall, we see that common hierarchy clones have the highest maintainability, whereas unrelated clones have the lowest maintainability.
+
+\subsubsection{Return Value}
+Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.
+
+\begin{table*}
+\centering
+\begin{tabular}{@{}lrrrrrr@{}}
+\toprule
+\textit{\textbf{Return Category}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Size}} & \textit{\textbf{Duplication}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
+Return & 0.85 & 1.02 & -3.84 & -55.00 & 1,571 & 0.19 \\
+Declare & 0.94 & 0.74 & 11.11 & -49.19 & 5,177 & 0.15 \\
+\rowcolor[HTML]{FFCCC9}
+Assign & 0.79 & 1.07 & 0.43 & -56.29 & 14 & 0.12 \\
+Void & 0.76 & 1.49 & -5.85 & -56.35 & 5,921 & -0.18 \\ \midrule
+\textbf{Grand Total} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{-53.26} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
+\end{tabular}
+\caption{Average metric values for refactorings of clone classes with the specified return category}
+\label{tab:return}
+\end{table*}
+
+The displayed return categories are ordered by their scores.
+Overall, the scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability.
+When the result of the call to the extracted method is directly returned, the maintainability score is the highest.
+When no value is returned, the maintainability score is the lowest.
+The main reason that no return value ends up lowest, is that it is linked to a higher number of parameters required for the extracted method.
+
+\subsubsection{Parameters}
+Fig.~\ref{fig:arguments} shows how an increase in parameters lowers the maintainability of the refactored code.
+On the primary x-axis, the maintainability is displayed.
+The secondary x-axis shows the number of refactorings.
+The y-axis shows the number of parameters.
+
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/arguments}
+  \caption{Influence of number of method parameters on system maintainability.}
+  \label{fig:arguments}
+\end{figure}
+
+\section{Discussion}
+%In this section, we discuss the results of our experiments.
+
+\subsection{Clone Context}
+Regarding clone context, our results indicate that most clones (37\%) are in a common class.
+This is favorable for refactoring because the extracted method does not have to be moved after extraction.
+24\% of clones are in a common hierarchy.
+These refactorings are also often favorable.
+Another 24\% of clones are unrelated, which is often unfavorable because it often requires a more comprehensive refactoring.
+15\% of clones are in an interface.
+
+Regarding clone locations, 74\% of clones span part of a method body (77\% if we include constructors).
+8\% of clones span several methods, which often require refactorings on a more architectural level.
+6\% of clones span only global variables, requiring an abstraction to encapsulate these data declarations.
+Only 4\% of clones span a full declaration (method, class, constructor, etc.).
+
+\subsection{Extract Method}
+28\% of clones can be refactored using the ``Extract Method'' refactoring technique (50\% if we limit our searching scope to method bodies).
+About 25\% of clones do not span part of a method, because of which they cannot be refactored.
+Many clones (23\%) do not have a statement as top-level AST-Node.
+Upon manual inspection, we noticed that the main reason for this is when clones are found in lambda functions or anonymous classes.
+About 15\% of clones span only part of an AST-Node.
+
+\subsection{Refactoring}
+In Fig.~\ref{fig:maintainabilityscore} we see an increase in maintainability for refactoring larger clone classes.
+The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie around a token volume of 63 tokens.
+There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.
+
+In Table~\ref{tab:relation_refactor} we see the results regarding refactorings that are applied to clones with diverse relations.
+We see that most refactored clones are in a common class, over 54\%.
+This is significantly more than the percentage of clones in the common class relation as reported in Table~\ref{tab:relation}.
+Meanwhile, the number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% -> 18\%).
+The main reason for this is that refactoring unrelated clones can change the relation of other clones in the same system.
+If we create a superclass abstraction to refactor an unrelated clone, other clones in those classes that were previously unrelated might become related.
+
+The maintainability scores displayed in Table~\ref{tab:relation_refactor} show that the most favorable clones to refactor are clones with a Sibling relation.
+The most unfavorable is to refactor clones to interfaces.
+However, the differences in maintainability in this table are generally small; according to our data relations have only a minor impact on the maintainability of clones.
+
+Regarding the return type of refactored clones, we see in Table~\ref{tab:return} that this has no major impact on maintainability.
+A method call to the extracted method that is directly returned and no return type extracted methods are slightly more favorable than the others.
+We think the main reason that the ``Return'' category is on top is that when a variable is declared at the end of the cloned fragment, CloneRefactor directly returns its value and removes the declaration.
+This decreases the volume slightly.
+
+A higher number of parameters directly influences the corresponding metric.
+Because of this, we see in Fig.~\ref{fig:arguments} that more parameters negatively influence maintainability.
+Not only the number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
+Because of that, we see that the trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.
+
+\section{Conclusion}
+We defined automatically refactorable clones and created a tool to detect and refactor them.
+We measured statistical data with this tool over a large corpus of open-source Java software systems to get more information about the context of clones and how refactoring them influences system maintainability.
+
+We defined two aspects as part of the context of a clone: relation and location.
+Regarding relations, over 37\% of clones are found in the same class.
+About 24\% of clones are in the same inheritance hierarchy.
+Another 24\% of clones are unrelated.
+The final 15\% of clones have the same interface.
+Regarding location, over 74\% of clones span part of a method.
+About 8\% span several methods.
+Only 4\% of clones span a declaration (method, class, etc.) fully.
+
+We built a tool that can automatically apply refactorings to 28\% of the clones in our corpus using the ``Extract Method'' refactoring technique.
+The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, e.g., when code outside a method is part of a clone.
+
+We measured four maintainability metrics before- and after applying each refactoring to determine the impact of each refactoring on system maintainability.
+We found that the most prominent factor influencing maintainability is the size of the clone.
+We found that the threshold lies at a clone volume of 29 tokens per clone instance for system maintainability to increase after refactoring the clone.
+Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data.
+We noticed that the inheritance relation of the clone and the return value of the extracted method has only a minor impact on system maintainability.
 

### 2019-09-09 date/paper.tex
Refined template

@@
 To reduce duplication with this technique, we extract the contents of a single clone instance to a new method and replace all clone instances in a clone class by a call to this method.
-
-\begin{figure*}
-\begin{parcolumns}{2}
-\colchunk[1]{
-\begin{javacode}
-package com.sb.game;
-
-import java.util.List;
-
-public class GameScene
-{
-|\highlightYellow|	public void addToList(List l) {
-|\highlightYellow|		l.add(getClass().getName());
-|\highlightYellow|	}
-
-	public void addTen(int x) {
-|\highlightYellow|		x = x + 10; // Addition
-|\highlightYellow|		Notifier.notifyChanged(x);
-|\highlightYellow|		return x;
-	}
-}
-\end{javacode}}
-\colchunk[2]{
-\begin{javacode}
-package com.sb.fruitgame;
-
-import java.awt.List; // Different type
-
-public class LoseScene
-{
-|\highlightYellow|	public void addToList(List l) {
-|\highlightYellow|		l.add(getClass().getName());
-|\highlightYellow|	}
-
-	public void concatTen(String x) {
-|\highlightYellow|		x = x + 10; // String concat
-|\highlightYellow|		Notifier.notifyChanged(x);
-|\highlightYellow|		return x;
-	}
-}
-\end{javacode}}
-\end{parcolumns}
-\caption{Example of textually equal code fragments that differ in functionality.}
-\label{fig:type1}
-\end{figure*}
 
@@
 We also created a set of control projects to test the correctness for many edge cases.
-
-\begin{figure*}
-\begin{parcolumns}{2}
-\colchunk[1]{
-\begin{javacode}
-|\highlightYellow|int a = getA();
-|\highlightYellow|while(a<1000) {
-|\highlightYellow|  a *= 5;
-  doC();
-}
-\end{javacode}}
-\colchunk[2]{
-\begin{javacode}
-|\highlightYellow|int a = getA();
-|\highlightYellow|while(a<1000) {
-|\highlightYellow|  a *= 5;
-  doB(a);
-}
-\end{javacode}}
-\end{parcolumns}
-\caption{A clone that spans a block partially.}
-\label{fig:refactorabilitypartialblock}
-\end{figure*}
 
@@
 
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
+\bibliography{references}
 

### 2019-09-09 date/paper.tex
Blinded even further

@@
 \usepackage{xcolor}
+\usepackage{float}
+\usepackage{booktabs}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
-We created a set of control projects\footnote{Control projects for assessing clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
+We created a set of control projects to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
 
-None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
+None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CloneRefactor.
 This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
@@
 Because of that requirement, we decided to filter the corpus to only projects using the Maven build automation system.
-We created a set of scripts\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} to prepare such a corpus with all dependencies included.
+We created a set of scripts to prepare such a corpus with all dependencies included.
 

### 2019-09-09 date/paper.tex
Fixing some package issues
Fixed document and references
Cut return value partly

@@
-\documentclass[conference]{IEEEtran}
+\documentclass[]{IEEEtran}
 \IEEEoverridecommandlockouts
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
+\usepackage{amsmath}
+\usepackage[table]{xcolor}
 \usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{xcolor}
 \usepackage{float}
 \usepackage{booktabs}
+\usepackage{multirow}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use.
+We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or returns data and the amount of external data that cloned fragments use.
 We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored.
@@
 \item \textbf{Relation}: The relation category (Sec.~\ref{sec:relation}) by which this methods' location was determined.
-\item \textbf{Returns}: Whether the method calls return, declare, assign or don't use any data from the extracted method.
+\item \textbf{Returns}: Whether the method calls return, declare, assign or doesn't use any data from the extracted method.
 \item \textbf{Parameters}: The number of parameters the extracted method has.
@@
 
-\subsubsection{Return Value}
-Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.
-
-\begin{table*}
-\centering
-\begin{tabular}{@{}lrrrrrr@{}}
-\toprule
-\textit{\textbf{Return Category}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Size}} & \textit{\textbf{Duplication}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
-Return & 0.85 & 1.02 & -3.84 & -55.00 & 1,571 & 0.19 \\
-Declare & 0.94 & 0.74 & 11.11 & -49.19 & 5,177 & 0.15 \\
-\rowcolor[HTML]{FFCCC9}
-Assign & 0.79 & 1.07 & 0.43 & -56.29 & 14 & 0.12 \\
-Void & 0.76 & 1.49 & -5.85 & -56.35 & 5,921 & -0.18 \\ \midrule
-\textbf{Grand Total} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{-53.26} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
-\end{tabular}
-\caption{Average metric values for refactorings of clone classes with the specified return category}
-\label{tab:return}
-\end{table*}
-
-The displayed return categories are ordered by their scores.
-Overall, the scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability.
-When the result of the call to the extracted method is directly returned, the maintainability score is the highest.
-When no value is returned, the maintainability score is the lowest.
-The main reason that no return value ends up lowest, is that it is linked to a higher number of parameters required for the extracted method.
-
 \subsubsection{Parameters}
@@
 
+\bibliographystyle{IEEEtran}
 \bibliography{references}

### 2019-09-09 date/paper.tex
Cut relation partly

@@
 \subsubsection{Relation}
-Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for the identified relations between clone instances (see Sec.~\ref{sec:relation}).
-
-\begin{table}[H]
-\centering
-\begin{tabular}{@{}llrr@{}}
-\toprule
-\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} \\ \midrule
-\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
- & Same Method & 8,955 &  \\ \midrule
-\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342} \\ \cmidrule(lr){2-3}
- & Superclass & 2,616 &  \\ \cmidrule(lr){2-3}
- & First Cousin & 1,219 &  \\ \cmidrule(lr){2-3}
- & Common Hierarchy & 720 &  \\ \cmidrule(lr){2-3}
- & Ancestor & 199 &  \\ \midrule
-\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314} \\ \cmidrule(lr){2-3}
- & External Superclass & 4,525 &  \\ \cmidrule(lr){2-3}
- & External Ancestor & 3,347 &  \\ \cmidrule(lr){2-3}
- & No Indirect Superclass & 1,765 &  \\ \midrule
-\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} \\ \cmidrule(lr){2-3}
- & Same Indirect Interface & 5,552 &  \\ \bottomrule
-\end{tabular}
-\caption{Number of clone classes per clone relation}
-\label{tab:relation}
-\end{table}
+We tested to what extent the relation between clone instances in a clone class (see Sec.~\ref{sec:relation}) has an influence on the maintainability of refactored clones.
 

### 2019-09-09 date/paper.tex
Cut characteristics section

@@
 
-\subsubsection{Characteristics of the extracted method}\label{sec:characteristics}
-We define the following characteristics of the extracted method and/or the call:
-\begin{itemize}
-\item \textbf{Tokens}: The number of tokens in the body of the method.
-\item \textbf{Relation}: The relation category (Sec.~\ref{sec:relation}) by which this methods' location was determined.
-\item \textbf{Returns}: Whether the method calls return, declare, assign or doesn't use any data from the extracted method.
-\item \textbf{Parameters}: The number of parameters the extracted method has.
-\end{itemize}
-We hypothesize that these characteristics are the main factors influencing the impact on the maintainability of the system as a result of refactoring the clone.
-
 \subsubsection{Impact on maintainability metrics} \label{sec:metrics}
@@
 In our corpus, CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Sec.~\ref{sec:metrics}).
-Using the presented formulas (see Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
+Using the presented formulas (see Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method influence the maintainability of the resulting codebase after refactoring.
 In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.

### 2019-09-09 date/paper.tex
Removed token size graph

@@
 \subsubsection{Clone Token Volume}
-Figure \ref{fig:maintainabilityscore} shows the obtained results when plotting the clone volume vs the average delta maintainability score.
+TODO shows the obtained results when plotting the clone volume vs the average delta maintainability score.
 We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class.
@@
 The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.
-
-\begin{figure*}
-  \includegraphics[width=1\textwidth]{img/tokenvolume}
-  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability.}
-  \label{fig:maintainabilityscore}
-\end{figure*}
 

### 2019-09-18 date/paper.tex
Updates from Overleaf

--- 2019-09-09 date/paper.tex
@@
-\documentclass[]{IEEEtran}
+\documentclass[conference]{IEEEtran}
 \IEEEoverridecommandlockouts
@@
 
-We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or returns data and the amount of external data that cloned fragments use.
+We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use.
 We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored.
@@
 \item \textbf{Relation}: The relation category (Sec.~\ref{sec:relation}) by which this methods' location was determined.
-\item \textbf{Returns}: Whether the method calls return, declare, assign or doesn't use any data from the extracted method.
+\item \textbf{Returns}: Whether the method calls return, declare, assign or don't use any data from the extracted method.
 \item \textbf{Parameters}: The number of parameters the extracted method has.
@@
 \subsubsection{Relation}
-We tested to what extent the relation between clone instances in a clone class (see Sec.~\ref{sec:relation}) has an influence on the maintainability of refactored clones.
+Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for the identified relations between clone instances (see Sec.~\ref{sec:relation}).
+
+\begin{table}[H]
+\centering
+\begin{tabular}{@{}llrr@{}}
+\toprule
+\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} \\ \midrule
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
+ & Same Method & 8,955 &  \\ \midrule
+\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342} \\ \cmidrule(lr){2-3}
+ & Superclass & 2,616 &  \\ \cmidrule(lr){2-3}
+ & First Cousin & 1,219 &  \\ \cmidrule(lr){2-3}
+ & Common Hierarchy & 720 &  \\ \cmidrule(lr){2-3}
+ & Ancestor & 199 &  \\ \midrule
+\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314} \\ \cmidrule(lr){2-3}
+ & External Superclass & 4,525 &  \\ \cmidrule(lr){2-3}
+ & External Ancestor & 3,347 &  \\ \cmidrule(lr){2-3}
+ & No Indirect Superclass & 1,765 &  \\ \midrule
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} \\ \cmidrule(lr){2-3}
+ & Same Indirect Interface & 5,552 &  \\ \bottomrule
+\end{tabular}
+\caption{Number of clone classes per clone relation}
+\label{tab:relation}
+\end{table}
 
@@
 Overall, we see that common hierarchy clones have the highest maintainability, whereas unrelated clones have the lowest maintainability.
+
+\subsubsection{Return Value}
+Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.
+
+\begin{table*}
+\centering
+\begin{tabular}{@{}lrrrrrr@{}}
+\toprule
+\textit{\textbf{Return Category}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Size}} & \textit{\textbf{Duplication}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
+Return & 0.85 & 1.02 & -3.84 & -55.00 & 1,571 & 0.19 \\
+Declare & 0.94 & 0.74 & 11.11 & -49.19 & 5,177 & 0.15 \\
+\rowcolor[HTML]{FFCCC9}
+Assign & 0.79 & 1.07 & 0.43 & -56.29 & 14 & 0.12 \\
+Void & 0.76 & 1.49 & -5.85 & -56.35 & 5,921 & -0.18 \\ \midrule
+\textbf{Grand Total} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{-53.26} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
+\end{tabular}
+\caption{Average metric values for refactorings of clone classes with the specified return category}
+\label{tab:return}
+\end{table*}
+
+The displayed return categories are ordered by their scores.
+Overall, the scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability.
+When the result of the call to the extracted method is directly returned, the maintainability score is the highest.
+When no value is returned, the maintainability score is the lowest.
+The main reason that no return value ends up lowest, is that it is linked to a higher number of parameters required for the extracted method.
 
@@
 
-\bibliographystyle{IEEEtran}
 \bibliography{references}

### 2019-09-18 date/paper.tex

--- 2019-09-09 date/paper.tex
@@
 \subsubsection{Parameters}
-Fig.~\ref{fig:arguments} shows how an increase in parameters lowers the maintainability of the refactored code.
+TODO shows how an increase in parameters lowers the maintainability of the refactored code.
 On the primary x-axis, the maintainability is displayed.
@@
 The y-axis shows the number of parameters.
-
-\begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/arguments}
-  \caption{Influence of number of method parameters on system maintainability.}
-  \label{fig:arguments}
-\end{figure}
 

### 2019-09-19 sattose/paper.tex
Updates from Overleaf

@@
 
-\title{Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -}
+\title{Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages}
 
@@
                 Amsterdam, Netherlands \\
-                AM.Oprescu@uva.nl
+                A.M.Oprescu@uva.nl
 }
@@
 \section{Conclusion and next steps}\label{chap:conclusion}
-In the research we have conducted so far we have made three novel contributions:
+In this research we made three novel contributions:
 \begin{itemize}
@@
     \item We mapped the context of clones in a large corpus of open source systems.
-    \item We mapped the opportunities to perform method extraction on clones this corpus.
+    \item We mapped the opportunities to perform the ``Extract Method'' refactoring technique on clones this corpus.
 \end{itemize}
@@
 
-The research that we have conducted so far analyzes the context of different kinds of clones and prioritizes their refactoring.
+We analyzed the context of different kinds of clones and prioritized their refactoring.
 Firstly, we looked at the inheritance relation of clone instances in a clone class.
-We have found that a little more than a third of all clone classes are flagged unrelated, which means that they have at least one instance that has no relation through inheritance with the other instances.
-About a third of the clone classes all of its instances are in the same class.
+We found that a little more than a third of all clone classes are flagged unrelated, which means that they have at least one instance that has no relation through inheritance with the other instances.
+For about a third of the clone classes all of their instances are in the same class.
 

### 2019-09-27 saner/paper.tex
Updates from Overleaf

--- 2019-09-18 date/paper.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{amsmath}
-\usepackage[table]{xcolor}
+\documentclass[sigconf,review, table]{acmart}
+
+\usepackage{xcolor}
 \usepackage{graphicx}
 \usepackage{float}
+
 \usepackage{booktabs}
 \usepackage{multirow}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\usepackage{parcolumns}
+
+\definecolor{pblue}{rgb}{0.13,0.13,1}
+\definecolor{pgreen}{rgb}{0,0.5,0}
+\definecolor{pred}{rgb}{0.9,0,0}
+\definecolor{pgrey}{rgb}{0.46,0.45,0.48}
+
+\usepackage{listings}
+\lstset{language=Java,
+  showspaces=false,
+  showtabs=false,
+  breaklines=true,
+  showstringspaces=false,
+  breakatwhitespace=true,
+  commentstyle=\color{pgreen},
+  keywordstyle=\color{pblue},
+  numbers = left,
+  stringstyle=\color{pred},
+  basicstyle=\ttfamily,
+  moredelim=[il][\textcolor{pgrey}]{\$\$},
+  moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%}
+}
+
+\definecolor{lightyellow}{HTML}{fffdcc}
+\definecolor{doublelightyellow}{HTML}{fffa9c}
+\definecolor{lightgreen}{HTML}{dcffd4}
+\definecolor{lightblue}{HTML}{e0ffff}
+\definecolor{lightred}{HTML}{ffe0e0}
+\definecolor{lightpink}{HTML}{ffe0ff}
+\definecolor{lightorange}{HTML}{ffede0}
+\definecolor{lightpurple}{HTML}{f0e0ff}
+\newcommand{\highlightYellow}{\makebox[0pt][l]{\color{lightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightGreen}{\makebox[0pt][l]{\color{lightgreen}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightBlue}{\makebox[0pt][l]{\color{lightblue}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightRed}{\makebox[0pt][l]{\color{lightred}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightPink}{\makebox[0pt][l]{\color{lightpink}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightOrange}{\makebox[0pt][l]{\color{lightorange}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightPurple}{\makebox[0pt][l]{\color{lightpurple}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightDarkyellow}{\makebox[0pt][l]{\color{doublelightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
+
+\lstnewenvironment{javacode}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small,#1}}{}
+
+\setcopyright{acmcopyright}
+\copyrightyear{2019}
+\acmYear{2019}
+\acmDOI{10.1145/1122445.1122456}
+\acmMonth{8}
+
+\acmConference[ICSE 2020]{Technical Papers}{May 23--29}{Seoul, South Korea}
+
 \begin{document}
@@
 
-\maketitle
+%\author{Simon Baars}
+%\affiliation{\institution{University of Amsterdam}}
+%\email{simon.mailadres@gmail.com}
+
+%\author{Ana Oprescu}
+%\affiliation{\institution{University of Amsterdam}}
+%\email{a.m.oprescu@uva.nl}
 
@@
 To reduce duplication with this technique, we extract the contents of a single clone instance to a new method and replace all clone instances in a clone class by a call to this method.
+
+\begin{figure*}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+package com.sb.game;
+
+import java.util.List;
+
+public class GameScene
+{
+|\highlightYellow|	public void addToList(List l) {
+|\highlightYellow|		l.add(getClass().getName());
+|\highlightYellow|	}
+
+	public void addTen(int x) {
+|\highlightYellow|		x = x + 10; // Addition
+|\highlightYellow|		Notifier.notifyChanged(x);
+|\highlightYellow|		return x;
+	}
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+package com.sb.fruitgame;
+
+import java.awt.List; // Different type
+
+public class LoseScene
+{
+|\highlightYellow|	public void addToList(List l) {
+|\highlightYellow|		l.add(getClass().getName());
+|\highlightYellow|	}
+
+	public void concatTen(String x) {
+|\highlightYellow|		x = x + 10; // String concat
+|\highlightYellow|		Notifier.notifyChanged(x);
+|\highlightYellow|		return x;
+	}
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Example of textually equal code fragments that differ in functionality.}
+\label{fig:type1}
+\end{figure*}
 
@@
 To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
-We created a set of control projects to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
+We created a set of control projects\footnote{Control projects for assessing clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
 
-None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CloneRefactor.
+None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
 This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
@@
 We also created a set of control projects to test the correctness for many edge cases.
+
+\begin{figure*}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+|\highlightYellow|int a = getA();
+|\highlightYellow|while(a<1000) {
+|\highlightYellow|  a *= 5;
+  doC();
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+|\highlightYellow|int a = getA();
+|\highlightYellow|while(a<1000) {
+|\highlightYellow|  a *= 5;
+  doB(a);
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{A clone that spans a block partially.}
+\label{fig:refactorabilitypartialblock}
+\end{figure*}
 
@@
 Because of that requirement, we decided to filter the corpus to only projects using the Maven build automation system.
-We created a set of scripts to prepare such a corpus with all dependencies included.
+We created a set of scripts\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} to prepare such a corpus with all dependencies included.
 
@@
 \subsection{Tool Validation}
-We have validated the correctness of CloneRefactor through unit tests and empirical validation.
-First, we created a set of 57 control projects to verify the correctness in many (edge) cases.
+We have verified the correctness of CloneRefactor through unit tests and empirical verification.\todo{With unit test you are testing the properties which is verification.
+With projects you are validating as you are checking whether its finding what is it supposed to be finding.} First, we created a set of 57 control projects to verify the correctness in many (edge) cases.
 These projects contain clones for each identified relation, location, and refactorability category to see whether they get correctly identified.
@@
 
+\section*{Acknowledgments}
+We would like to thank the Software Improvement Group for their continuous support in this project.
+In particular, we would like to thank Xander Schrijen for his invaluable input in this research.
+Furthermore, we would like to thank Sander Meester for his proofreading efforts and feedback.
+
+\bibliographystyle{ACM-Reference-Format}
 \bibliography{references}

### 2019-09-27 saner/paper.tex
Updates from Overleaf

@@
-\documentclass[sigconf,review, table]{acmart}
+\documentclass[10pt,conference]{IEEEtran}
 
@@
 
-\setcopyright{acmcopyright}
-\copyrightyear{2019}
-\acmYear{2019}
-\acmDOI{10.1145/1122445.1122456}
-\acmMonth{8}
-
-\acmConference[ICSE 2020]{Technical Papers}{May 23--29}{Seoul, South Korea}
-
 \begin{document}
@@
 \title{Improving Software Maintainability through Automated Refactoring of Code Clones}
+
+\maketitle
 
@@
 
-\keywords{code clones, refactoring, static code analysis, object-oriented programming}
+\begin{IEEEkeywords}
+code clones, refactoring, static code analysis, object-oriented programming
+\end{IEEEkeywords}
 
@@
 To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
-We created a set of control projects\footnote{Control projects for assessing clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
+We created a set of control projects to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
 
-None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
+None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CloneRefactor.
 This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
 In the following sections, we explain these steps.
+
 \begin{figure}[H]
@@
 \subsection{Tool Validation}
-We have verified the correctness of CloneRefactor through unit tests and empirical verification.\todo{With unit test you are testing the properties which is verification.
-With projects you are validating as you are checking whether its finding what is it supposed to be finding.} First, we created a set of 57 control projects to verify the correctness in many (edge) cases.
+We have validated the correctness of CloneRefactor through unit tests and empirical validation.
+First, we created a set of 57 control projects to verify the correctness in many (edge) cases.
 These projects contain clones for each identified relation, location, and refactorability category to see whether they get correctly identified.
@@
 
-\section*{Acknowledgments}
-We would like to thank the Software Improvement Group for their continuous support in this project.
-In particular, we would like to thank Xander Schrijen for his invaluable input in this research.
-Furthermore, we would like to thank Sander Meester for his proofreading efforts and feedback.
-
 \bibliographystyle{ACM-Reference-Format}

### 2019-09-27 saner/paper.tex
Updates from Overleaf

@@
 
-We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or returns data and the amount of external data that cloned fragments use.
+We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use.
 We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored.
-The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones with more than requiring more than one external parameter decreases maintainability.
+The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones requiring more than one external parameter decrease maintainability.
 \end{abstract}
@@
 In this study, we define a technique to detect clones such that they can be automatically refactored.
-We list a set of criteria that can obstruct refactoring opportunities.
+We list criteria that obstruct refactoring opportunities.
 We evaluate the relation and location of clones to determine which refactoring techniques are best suited.
@@
 	public void concatTen(String x) {
-|\highlightYellow|		x = x + 10; // String concat
+|\highlightYellow|		x = x + 10; // String concatenation
 |\highlightYellow|		Notifier.notifyChanged(x);
@@
 This tool is based on several studies that look into different aspects of code clone refactoring.
-In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how does variability between cloned fragments influence the refactoring techniques required and their implications on system design.
+In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design.
 Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability.
@@
 
+\todo{Add more related work?}
+
 \section{Defining refactorable clones}
 In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}.
-We discuss how we can define clones such that they can be automatically refactored without side effects on the source code.
+We discuss how we can define clones such that they can be automatically refactored while avoiding changing the functional behavior and other negative side effects on the source code.
 
@@
 \section{Experimental setup}
+\todo{This doesn't say anything: explain how the section is organized}
 In this section, we describe the setup of our experiments.
@@
 
+\todo{color package}
 \begin{table}[H]
@@
 
+\todo{Redo plot, explain axes units}
 \begin{figure*}
@@
 
+\todo{Redo plot, explain axes units}
 \begin{figure}[H]
@@
 
-\bibliographystyle{ACM-Reference-Format}
+\bibliographystyle{plain}
 \bibliography{references}

### 2019-09-27 saner/paper.tex
Fixed + paper

@@
 
-\usepackage{xcolor}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage[table]{xcolor}
 \usepackage{graphicx}
@@
 \usepackage{parcolumns}
+
+\usepackage{todo}
+\usepackage{amsmath}
 
@@
 \maketitle
+\thispagestyle{plain} % This is for page numbers, remove before submit
+\pagestyle{plain}
 
@@
 We decided to use the amount of duplicated tokens part of a clone class instead, to have a stronger reflection of the impact of the refactoring by measuring a more fine-grained system property.
-\item \textbf{Volume}: The more code a system has, the more code has to be maintained.
+%\item \textbf{Volume}: The more code a system has, the more code has to be maintained.
 The paper~\cite{heitlager2007practical} measures volume as lines of code.
 As with duplication, we use the number of tokens instead.
-\item \textbf{Complexity}: Heitlager et al.~\cite{heitlager2007practical} use MCCabe complexity~\cite{mccabe1976complexity} to calculate their complexity metric.
+\item \textbf{Method Complexity}: Heitlager et al.~\cite{heitlager2007practical} use MCCabe complexity~\cite{mccabe1976complexity} to calculate their complexity metric.
 The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.
@@
 If a method has many parameters, the code may become harder to understand and it is an indication that data is not encapsulated adequately in objects~\cite{fowler2018refactoring}.
+\item \textbf{Method size}: The longer a method is, the harder it becomes to comprehend and maintain \cite{heitlager2007practical}.
+The ``extract method'' refactoring technique is often used to split up long methods \cite{charalampidou2018structural}.
+When refactoring duplicated code fragments in the body of a method, this could improve maintainability of the methods from which the duplication was removed because of their reduced size.
 \end{itemize}

### 2019-09-27 saner/paper.tex
Added some stuff to the paper

@@
 \begin{itemize}
-  \item Compare variable references not only by their name but also by their type.
-  \item Compare referenced types by their fully qualified identifier (FQI). The FQI of a type reference describes the full path to where it is declared.
-  \item Compare method references by their fully qualified signature (FQS). The FQS of a method reference describes the full path to where it is declared, plus the FQI of each of its parameters.
+  \item Compare types by their fully qualified identifier (FQI). The FQI of a type reference describes the full path to where it is declared.
+  \item Compare variable references not only by their name but also by their type (FQI).
+  \item Compare method references by their fully qualified signature (FQS).
+The FQS of a method reference describes the full path to where it is declared, plus the FQI of the type of each of its parameters.
 \end{itemize}

### 2019-10-21 saner/paper.tex
Updates from Overleaf

@@
 
-\usepackage{todo}
+\usepackage{todonotes}
 \usepackage{amsmath}
@@
 \title{Improving Software Maintainability through Automated Refactoring of Code Clones}
-
+\author{}
 \maketitle
@@
 To remove such anti-patterns, the codebase should be refactored.
-Many tools aid in the detection process of such duplication problems but fail to determine whether refactoring a duplicate fragment would improve the maintainability.
+Many tools aid in the detection process of such duplication problems but do not determine whether refactoring a duplicate fragment would improve the maintainability.
 
-We address this shortcoming by first analyzing what data should be gathered from an automatically refactored system.
+We address this shortcoming by first analyzing what factors influence the maintainability of clones when refactored.
 We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them.
@@
 
-\todo{color package}
 \begin{table}[H]

### 2019-10-21 saner/paper.tex
Updates from Overleaf

@@
 To remove such anti-patterns, the codebase should be refactored.
-Many tools aid in the detection process of such duplication problems but do not determine whether refactoring a duplicate fragment would improve the maintainability.
+Many tools aid in the detection process of such duplication problems but do not determine whether refactoring an identified clone would improve the maintainability.
 

### 2019-10-22 saner/paper.tex
Updates from Overleaf
Abstract & Introduction

@@
 
-We address this shortcoming by first analyzing what factors influence the maintainability of clones when refactored.
+We address this shortcoming by first analyzing what preconditions apply to be able to refactor clones.
 We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them.
@@
 Based on these results, one could decide which clones would improve system design if refactored.
-We evaluate our approach over a large corpus of open source Java projects.
+We evaluate our approach over a large corpus of open-source Java projects.
 
-We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use.
-We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored.
-The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones requiring more than one external parameter decrease maintainability.
+We identify the factors of interest characterizing the impact on maintainability of automatically applied refactorings.
+We find that the biggest influencing factor is token volume.
+We define token volume as the combined number of tokens in all clone instances in a clone class.
+The majority of duplicates with a token volume of 63 or more tokens improve maintainability when refactored.
+The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones requiring more than two external parameters decrease maintainability.
 \end{abstract}
@@
 
-Current code clone detection techniques base their thresholds and prioritization on a limited set of metrics.
-Often, clone detection techniques are limited to measuring the size of clones to determine whether they should be considered.
+%Clone detection tools often use thresholds to determine which clones should be considered.
+Most clone detection tools use the number of lines \cite{kamiya2002ccfinder, svajlenko2016bigcloneeval}, statements \cite{higo2013revisiting, kamalpriya2017enhancing} and/or tokens \cite{ragkhitwetsagul2019siamese, jiang2007deckard} as thresholds to determine whether clones should be considered.
+We outline the shortcomings of these thresholds to find clones such that the maintainability of the source code is improved when refactored, and propose new thresholds to control this characteristic.
+% Current clone detection techniques are limited to measuring the size of clones to determine whether they should be considered.
 Because of this, the output of clone detection tools is often of limited assistance to the developer in the refactoring process.
+To reduce duplication of a codebase, there are several refactoring techniques that can be applied.
+The most used refactoring technique to deal with code clones is ``Extract Method'' \cite{fowler2018refactoring}.
+This technique entails that the duplicated code is moved to a new method, which is then called from all locations where the duplicated code was used.
+To be able to execute such a refactoring, several preconditions apply \cite{tsantalis2015assessing}.
 
-In this study, we define a technique to detect clones such that they can be automatically refactored.
-We list criteria that obstruct refactoring opportunities.
-We evaluate the relation and location of clones to determine which refactoring techniques are best suited.
-We introduce a tool that automatically refactors clones by extracting new methods out of duplicated code.
+In this study, we analyze which preconditions apply to determine whether a clone can be automatically refactored.
+We list criteria that influence the maintainability of clones when refactored.
+We evaluate the context of clones to determine which refactoring techniques are best suited.
+We define the context of clones as the inheritance relation between clone instances in a clone class and the location of clone instances in the codebase.
+We showcase the proposed technique as a tool that automatically refactors clones by extracting new methods out of duplicated code.
 
-We evaluate our approach by comparing the maintainability of before- and after snapshots of a codebase for each duplication problem that is refactored.
+We measure several maintainability metrics before and after refactoring to determine the impact on system maintainability of applying the refactoring.
+These metrics are volume, method parameters, duplication and complexity.
+Using this setup, we gain empirical data about the maintainability improvement of clones on a large set of data in a controlled environment.
+We use this data to define which characteristics of clones have the biggest influence of system maintainability when such a clone is refactored.
+This allows for more a accurate suggestion of code clones for refactoring and can assist in the refactoring process.
+
+%We evaluate our approach by comparing the maintainability of before- and after snapshots of a codebase for each duplication problem that is refactored.
 We define which factors have the greatest influence on whether a clone improves maintainability when refactored.

### 2019-10-22 saner/paper.tex
Introduction

@@
 
+Over a corpus of 2.267 Java project our tool refactored 12.710 clone classes.
+We found that the main influencing factor on maintainability when refactored is token volume.
+We define token volume as the combined number of tokens in all clone instances in a clone class.
+When refactoring clones with a very small token volume, we found that the maintainability decreases when such clones are refactored.
+The average clone with a clone volume of 65 or larger improves maintainability when refactored.
+The other factor with a major influence on maintainability is the number of parameters that are required for the extracted method.
+We found that if a clone requires more than 2 parameters in the extracted method, it is more likely to decrease maintainability.
+
+This paper is organized as follows.
+In Sec.~\ref{sec:background} we introduce important terminilogy in the field of clone refactoring.
+In Sec.~\ref{sec:relatedwork} we introduce the state-of-the-art in automated clone refactoring research.
+In Sec.~\ref{sec:research} we propose a definition for clones such that they can and should be automatically refactored.
+In Sec.~\ref{sec:clonerefactor} we introduce our clone refactoring tool.
+In Sec.~\ref{sec:experimentalsetup} we explain the setup of our experiments, of which the results are shown in Sec.\ref{sec:results} and discussed in \ref{sec:discussion}.
 %We evaluate our approach by comparing the maintainability of before- and after snapshots of a codebase for each duplication problem that is refactored.
@@
 
-\section{Background}
+\section{Background}\label{sec:background}
 Our study lies at the intersection of code clone and refactoring research. We use two concepts to argue about code clones~\cite{roy2007survey}:
@@
 
-\section{Related Work}
+\section{Related Work}\label{sec:relatedwork}
 The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
@@
 
-\section{Defining refactorable clones}
+\section{Defining refactorable clones}\label{sec:research}
 In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}.
@@
 
-\section{The CloneRefactor tool}
+\section{The CloneRefactor tool}\label{sec:clonerefactor}
 To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
@@
 
-\section{Experimental setup}
+\section{Experimental setup} \label{sec:experimentalsetup}
 \todo{This doesn't say anything: explain how the section is organized}
@@
 
-\section{Results}
+\section{Results} \label{sec:results}
 In this section, we share the results of our experiments.
@@
 
-\section{Discussion}
+\section{Discussion} \label{sec:discussion}
 %In this section, we discuss the results of our experiments.
@@
 
-\section{Conclusion}
+\section{Conclusion} \label{sec:conclusion}
 We defined automatically refactorable clones and created a tool to detect and refactor them.

### 2019-10-22 saner/paper.tex
Background & related work

@@
 
+\subsection{Clone Types}
+Duplication in code is found in many different forms.
+Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}.
+Sometimes this code is then adapted to fit the new context.
+To reason about these modifications, several clone types have been proposed.
+These clone types are described in Roy et al \cite{roy2007survey}:
+\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout), and comments.\\
+\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout, and comments.\\
+\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.
+A higher type of clone means that it is harder to detect and refactor.
+Many studies adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
+
+\subsection{Refactoring}
 The most common technique for refactoring clones is ``Extract Method''~\cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
-Applying this technique entails moving functionality in the body of a method to a new method.
-To reduce duplication with this technique, we extract the contents of a single clone instance to a new method and replace all clone instances in a clone class by a call to this method.
+Applying this technique entails moving functionality from the body of a method to a new method.
+To reduce duplication with this technique, the contents of a single clone instance are extracted to a new method and all further locations of the clone are replaced by a call to the new method.
 
@@
 \section{Related Work}\label{sec:relatedwork}
+\subsection{Clone Context analysis}
+A study by Golomingi~\cite{koni2001scenario} explores mapping the relation between clone instances to refactoring methods.
+The author analyses the refactoring methods described by Martin Fowler \cite{fowler1999refactoring} and analyzes what refactoring methods can be used to refactor clones with what inheritance relations.
+The identified clone relations are: Ancestor, Common Hierarchy, First Cousin, Same Method, Sibling, Single Class, Superclass and Unrelated.
+
+Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} combine the research by Golomingi~\cite{koni2001scenario} with clone types 1 and 3 \cite{roy2007survey}.
+They use a large corpus~\cite{tempero2010qualitas} on which they perform statistical analyses of clone relations together with clone types.
+We repeat this research with a vastly different setup: we use the clone definition from Sec.~\ref{sec:research} and the relation categories outlined in Sec.~\ref{sec:relation}.
+
+\subsection{JDeodorant}
 The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
@@
 This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
-
-\todo{Add more related work?}
 

### 2019-10-22 saner/paper.tex
Hello cheap and easy content!

@@
 
-\subsection{Refactoring}
+\subsection{Clone Refactoring}
+\subsubsection{Refactoring techniques}
 The most common technique for refactoring clones is ``Extract Method''~\cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
@@
 To reduce duplication with this technique, the contents of a single clone instance are extracted to a new method and all further locations of the clone are replaced by a call to the new method.
+
+\subsubsection{Preconditions}
+Clones detected by current detection techniques \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, cordy2011nicad} are subject to a set of preconditions to determine whether they can be refactored \ref{tsantalis2015assessing}:
+\begin{enumerate}
+  \item The parameterization of differences between the matched statements should not break existing data-, anti-, and output-dependences.
+  \item The unmatched statements should be movable before or after the matched statements without breaking existing data-, anti-, and output-dependences.
+  \item The duplicated code fragments should return at most one variable of the same type.
+  \item Matched branching (\texttt{break}, \texttt{continue}) statements should be accompanied with corresponding matched loop statements.
+  \item Matched variables having different subclass types should call only methods that are declared in the common superclass or are being overridden in the respective subclasses.
+  \item The parameterization of fields belonging to differences between the mapped statements is possible only if they are not modified.
+  \item The parameterization of method calls belonging to differences between the mapped statements is possible only if they do not return a void type.
+  \item The mapped statements within the clone fragments should not contain any conditional return statements.
+\end{enumerate}
 
@@
 \section{Related Work}\label{sec:relatedwork}
-\subsection{Clone Context analysis}
+\subsection{Clone context analysis}
 A study by Golomingi~\cite{koni2001scenario} explores mapping the relation between clone instances to refactoring methods.
@@
 
-\subsection{JDeodorant}
+\subsection{Clone refactoring}
 The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
@@
 In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}.
-We discuss how we can define clones such that they can be automatically refactored while avoiding changing the functional behavior and other negative side effects on the source code.
+We discuss how we can define clones such that they can be automatically refactored while avoiding changing the functional behavior and other negative side effects on the source code such as decreasing the maintainability of the code.
 
-\subsection{Ensuring Equality}\label{sec:t1r}
+\subsection{Ensuring equality}\label{sec:t1r}
 Most modern clone detection tools detect duplication by comparing the code textually together with the omission of certain tokens~\cite{roy2009comparison, svajlenko2014evaluating}.
@@
 
-\subsection{Clone Detection}
+\subsection{Clone detection}
 We use an AST-based method to detect clones.
@@
 
-\subsection{Context Mapping} \label{sec:context}
+\subsection{Context mapping} \label{sec:context}
 After clones are detected, we map the context of these clones.
@@
 
-\subsubsection{Full Method/Constructor/Class/Interface/Enumeration}
+\subsubsection{Full method/constructor/class/interface/enumeration}
 The categories denote that a full declaration (method, class, etc.) often denote redundancy and are often easy to refactor: one of both declarations is redundant and should be removed.

### 2019-10-23 saner/paper.tex
Related work

@@
 \subsubsection{Preconditions}
-Clones detected by current detection techniques \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, cordy2011nicad} are subject to a set of preconditions to determine whether they can be refactored \ref{tsantalis2015assessing}:
+Clones detected by current detection techniques \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, cordy2011nicad} are subject to a set of preconditions to determine whether they can be refactored \cite{tsantalis2015assessing}:
 \begin{enumerate}
@@
 \subsection{Clone refactoring}
-The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
+In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design.
+The main focus of this study is to find out which clones \textbf{can} be refactored.
+We extend this work by looking into which clones \textbf{should} be refactored.
+We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design.
+We measure which clones improve maintainability when refactored.
+This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
+%The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
 The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems.
@@
 
-A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process.
-The main focus is to find out which clones \textbf{can} be refactored.
-We extend this work by looking into which clones \textbf{should} be refactored.
-We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design.
-We measure which clones improve maintainability when refactored.
-This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
+%A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process.
 

### 2019-10-23 saner/paper.tex
Stuff

@@
 Using this setup, we gain empirical data about the maintainability improvement of clones on a large set of data in a controlled environment.
+Because the refactoring is done automatically, we also consider micro-clones, which are shown to be important for refactoring consideration \cite{mondai2018micro}.
 We use this data to define which characteristics of clones have the biggest influence of system maintainability when such a clone is refactored.
@@
 When developers duplicate fragments of code, they modify the duplicated block to fit its new location and purpose.
-To detect duplicate fragments with minor variance, we look into what expressions we can allow variability in, while still being refactorable.
+To detect duplicate fragments with minor variance, we look into what expressions we can allow variability in, while still being automatically refactorable.
 
-We define the following expressions as refactorable when varied:
+We define the following expressions as automatically refactorable when varied:
 \begin{itemize}
@@
 Often when allowing such variance, trade-offs come into play~\cite{krishnan2013refactoring, krishnan2014unification}.
-For instance, variance in literals may require the introduction of a parameter to an extracted method if the ``Extract Method'' refactoring method is used, increasing the required effort to comprehend the code.
+For instance, variance in literals may require the introduction of a parameter to an extracted method if the ``Extract Method'' refactoring method is used, increasing the required effort to comprehend the code \cite{heitlager2007practical}.
 
@@
 Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context~\cite{roy2007survey}.
-When dealing with such a situation, there are several opportunities to refactor so-called ``gapped clones''~\cite{ueda2002detection, zhao2018automatic}.
+When dealing with such situations, there are several opportunities to refactor so-called ``gapped clones''~\cite{ueda2002detection, zhao2018automatic}.
 ``Gapped clones'' are two clone instances separated by a ``gap'' of non-cloned statement(s).
-We define the following methods to refactor such clones:
+We define the following methods to refactor such clones, based on research by Tsantalis et al~\cite{tsantalis2015assessing}:
 \begin{itemize}
-  \item We wrap the difference in statements in a conditionally executed block, one path for each different (group of) statement(s).
-  \item We use a lambda function to pass the difference in statements from each location of the clone~\cite{tsantalis2017clone}.
+  \item Wrap the difference in statements in a conditionally executed block, one path for each different (group of) statement(s).
+  \item Use a lambda function to pass the difference in statements from each location of the clone~\cite{tsantalis2017clone}.
 \end{itemize}
-For both refactoring techniques, a trade-off is at play. This is because these solutions increase the complexity and volume of the source code in favor of removing a clone.
+For both of these techniques, a trade-off is at play. This is because these solutions increase the complexity and volume of the source code in favor of removing a clone.
 
-\section{The CloneRefactor tool}\label{sec:clonerefactor}
+\section{A tool for automatic clone refactoring}\label{sec:clonerefactor}
 To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.

### 2019-10-23 saner/paper.tex
CR = CloneRefactor

@@
 To remove such anti-patterns, the codebase should be refactored.
-Many tools aid in the detection process of such duplication problems but do not determine whether refactoring an identified clone would improve the maintainability.
+Many tools aid in the de©tection process of such duplication problems but do not determine whether refactoring an identified clone would improve the maintainability.
 
@@
 In Sec.~\ref{sec:clonerefactor} we introduce our clone refactoring tool.
-In Sec.~\ref{sec:experimentalsetup} we explain the setup of our experiments, of which the results are shown in Sec.\ref{sec:results} and discussed in \ref{sec:discussion}.
+In Sec.~\ref{sec:experimentalsetup} we explain the setup of our experiments, of which the results are shown in Sec.~\ref{sec:results} and discussed in Sec.~\ref{sec:discussion}.
 %We evaluate our approach by comparing the maintainability of before- and after snapshots of a codebase for each duplication problem that is refactored.
@@
 \section{A tool for automatic clone refactoring}\label{sec:clonerefactor}
-To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
-We created a set of control projects to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
+To detect clones that can be automatically refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
+We created a set of control projects to determine the suitability of these tools to detect automatically refactorable clones, either through configuration or postprocessing of their output.
 
-None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CloneRefactor.
+None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CR\footnote{Name anonymized for the blind review, camera-ready paper will include a link to the GitHub repo of the tool.}.
 This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
@@
   \includegraphics[width=1\columnwidth]{img/flow}
-  \caption{Simple flow diagram of CloneRefactor.}
+  \caption{Simple flow diagram of CR.}
   \label{fig:clonerefactorflow}
@@
 
-After all clones have been detected, CloneRefactor determines whether clone classes can be merged into gapped clones (see Sec.~\ref{sec:t3r}).
+After all clones have been detected, CR determines whether clone classes can be merged into gapped clones (see Sec.~\ref{sec:t3r}).
 The maximum size of the gap is limited by a threshold.
@@
 
-Based on these relations, CloneRefactor determines where to place the cloned code when refactored.
+Based on these relations, CR determines where to place the cloned code when refactored.
 These categories are mutually exclusive: a clone class will be flagged as the first relation in the above list that it applies to.
@@
 \subsection{Refactoring}
-CloneRefactor can refactor clones using the ``Extract Method'' refactoring technique. In this section, we show which clones we refactor and how we apply these transformations.
+CR can refactor clones using the ``Extract Method'' refactoring technique. In this section, we show which clones we refactor and how we apply these transformations.
 
@@
 \end{itemize}
-Clones that do not fall in the \textit{Can Be Extracted} category may require additional transformations or other techniques to refactor.
-CloneRefactor only refactors the clones that \textit{Can Be Extracted}.
+Clones that do not fall in the \textit{Can Be Extracted} category may require additional transformations or other techniques to refactor. CR only refactors the clones that \textit{Can Be Extracted}.
 
 \subsubsection{AST Transformation}
-CloneRefactor uses JavaParser~\cite{smith2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
-To refactor clones, CloneRefactor creates a new method declaration and moves all statements from a clone instance in the clone class to the new method.
+CR uses JavaParser~\cite{smith2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
+To refactor clones, CR creates a new method declaration and moves all statements from a clone instance in the clone class to the new method.
 This method is placed according to the relation between the clone instances (see Sec.~\ref{sec:relation}).
-CloneRefactor analyzes the source code of the extracted method and populates it with the following properties:
+CR analyzes the source code of the extracted method and populates it with the following properties:
 \begin{itemize}
@@
 \end{itemize}
-CloneRefactor then removes all cloned code and replaces it with a method call to the newly created method.
-In case of a return value, CloneRefactor either assigns the call result, declares it or returns it accordingly.
+CR then removes all cloned code and replaces it with a method call to the newly created method. In case of a return value, CR either assigns the call result, declares it or returns it accordingly.
 
@@
 \subsubsection{Impact on maintainability metrics} \label{sec:metrics}
-CloneRefactor measures the impact on maintainability metrics of the refactored source code for each clone class that is refactored.
+CR measures the impact on maintainability metrics of the refactored source code for each clone class that is refactored.
 These metrics are derived from Heitlager et al.~\cite{heitlager2007practical}.
@@
 \subsection{Corpus}
-We ran all our experiments using CloneRefactor on a corpus of open source Java projects.
+We ran all our experiments using CR on a corpus of open source Java projects.
 This corpus is derived from the corpus of a study that uses machine learning to determine the suitability of Java projects on GitHub for data analysis purposes~\cite{githubCorpus2013}.
 
-CloneRefactor requires all libraries of the projects it analyses, to find the full paths of all referenced symbols in the source code (see Sec.~\ref{sec:t1r}).
+CR requires all libraries of the projects it analyses, to find the full paths of all referenced symbols in the source code (see Sec.~\ref{sec:t1r}).
 Because of that requirement, we decided to filter the corpus to only projects using the Maven build automation system.
@@
 \subsection{Tool Validation}
-We have validated the correctness of CloneRefactor through unit tests and empirical validation.
+We have validated the correctness of CR through unit tests and empirical validation.
 First, we created a set of 57 control projects to verify the correctness in many (edge) cases.
@@
 For this, we use a GitHub project named JFreeChart.
-JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor.
+JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CR.
 
@@
 \subsection{Thresholds}
-In our corpus, CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Sec.~\ref{sec:metrics}).
+In our corpus, CR has refactored 12.710 clone classes and measured the change in indicated metrics (see Sec.~\ref{sec:metrics}).
 Using the presented formulas (see Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
@@
 A method call to the extracted method that is directly returned and no return type extracted methods are slightly more favorable than the others.
-We think the main reason that the ``Return'' category is on top is that when a variable is declared at the end of the cloned fragment, CloneRefactor directly returns its value and removes the declaration.
+We think the main reason that the ``Return'' category is on top is that when a variable is declared at the end of the cloned fragment, CR directly returns its value and removes the declaration.
 This decreases the volume slightly.

### 2019-10-25 saner/paper.tex
remark
Updates from Overleaf

@@
 This paper is organized as follows.
-In Sec.~\ref{sec:background} we introduce important terminilogy in the field of clone refactoring.
-In Sec.~\ref{sec:relatedwork} we introduce the state-of-the-art in automated clone refactoring research.
-In Sec.~\ref{sec:research} we propose a definition for clones such that they can and should be automatically refactored.
+In Sec.~\ref{sec:background} we revisit key clone refactoring background.
+Sec.~\ref{sec:relatedwork} discusses state-of-the-art in automated clone refactoring research.
+In Sec.~\ref{sec:research} we propose a definition for clones such that they could and should be automatically refactored.
 In Sec.~\ref{sec:clonerefactor} we introduce our clone refactoring tool.
@@
 \section{Background}\label{sec:background}
-Our study lies at the intersection of code clone and refactoring research. We use two concepts to argue about code clones~\cite{roy2007survey}:
+In this section, we describe relevant code clone and clone refactoring research.
+
+\subsection{Code clones}
+We use two concepts to argue about code clones~\cite{roy2007survey}:
 \\ \textbf{Clone instance}: A single cloned fragment.
@@
 
-\subsection{Clone Types}
+%\subsection{Clone Types}
 Duplication in code is found in many different forms.
@@
 Sometimes this code is then adapted to fit the new context.
-To reason about these modifications, several clone types have been proposed.
-These clone types are described in Roy et al \cite{roy2007survey}:
+To reason about these modifications, several clone types have been proposed%.
+These clone types are described in Roy et al
+~\cite{roy2007survey}:\\
 \textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout), and comments.\\
-\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout, and comments.\\
-\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.
+\textbf{Type II:} Structurally/syntactically identical fragments except variations in identifiers, literals, types, layout, and comments.\\
+\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed next to variations in identifiers, literals, types, layout, and comments.
 A higher type of clone means that it is harder to detect and refactor.
@@
 \section{Related Work}\label{sec:relatedwork}
+We outline relevant research to clone refactoring. A significant aspect is the context of clones.
+
 \subsection{Clone context analysis}
-A study by Golomingi~\cite{koni2001scenario} explores mapping the relation between clone instances to refactoring methods.
+Golomingi~\cite{koni2001scenario} explores mapping the relation between clone instances to refactoring methods.
 The author analyses the refactoring methods described by Martin Fowler \cite{fowler1999refactoring} and analyzes what refactoring methods can be used to refactor clones with what inheritance relations.
 The identified clone relations are: Ancestor, Common Hierarchy, First Cousin, Same Method, Sibling, Single Class, Superclass and Unrelated.
+We extend this list with several more fine-grained relations, suitable for automatic refactoring (see Sec.~\ref{sec:relation}).
 
@@
 \subsection{Clone refactoring}
-In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design.
+Krishnan et al.~\cite{krishnan2013refactoring} approach clone refactoring as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design.
 The main focus of this study is to find out which clones \textbf{can} be refactored.
@@
 \section{Defining refactorable clones}\label{sec:research}
-In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}.
-We discuss how we can define clones such that they can be automatically refactored while avoiding changing the functional behavior and other negative side effects on the source code such as decreasing the maintainability of the code.
+%In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}.
+We discuss how we can define clones such that they can be automatically refactored while avoiding changing the functional behavior and other negative side effects on the source code, such as decreasing the maintainability of the code.
 
@@
 
-None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CR\footnote{Name anonymized for the blind review, camera-ready paper will include a link to the GitHub repo of the tool.}.
+None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CR\footnote{Name anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.}.
 This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
@@
   \includegraphics[width=1\columnwidth]{img/flow}
-  \caption{Simple flow diagram of CR.}
+  \caption{Abstract flow diagram of CR.}
   \label{fig:clonerefactorflow}
@@
 After clones are detected, we map the context of these clones.
-We have identified three properties of clones as their context: relation and location.
+We have identified two properties of clones as their context: relation and location.
 We identify categories for each of these properties, to get a detailed insight into the context of clones.

### 2019-10-25 saner/paper.tex
Updates from Overleaf

@@
 \usepackage{amsmath}
+
+\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
 
@@
 In Sec.~\ref{sec:clonerefactor} we introduce our clone refactoring tool.
-In Sec.~\ref{sec:experimentalsetup} we explain the setup of our experiments, of which the results are shown in Sec.~\ref{sec:results} and discussed in Sec.~\ref{sec:discussion}.
+In Sec.~\ref{sec:experimentalsetup} we explain the setup of our experiments; we show the results in Sec.~\ref{sec:results} and discuss them in Sec.~\ref{sec:discussion}.
 %We evaluate our approach by comparing the maintainability of before- and after snapshots of a codebase for each duplication problem that is refactored.
@@
 \section{A tool for automatic clone refactoring}\label{sec:clonerefactor}
-To detect clones that can be automatically refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
+%To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability. 
+To investigate the impact of the definitions introduced in Sec.~\ref{sec:research}, we need a tool to detect refactorable clones according to these definitions.
+We attempt to reuse an existing tool, thus we search for candidates.
+None are found, thus we build a new tool.
+
+\subsection{Survey existing clone detection tools}
+We conducted a short survey on (recent) clone detection tools to detect such clones that can be refactored.
+The results of our survey are displayed in table~\ref{table:dettools}.
+We chose a set of tools that are open source and can analyze a popular object-oriented programming language.
+Next, we formulate the following four criteria by which we analyze these tools:
+\begin{enumerate}
+    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method level clones.
+We want to perform an analysis of all clones in projects to get a complete overview.
+\item \textbf{Can be extended to the definitions of refactorable clones.} We assembled a number of control projects to assess the validity of clone detection tools.
+\item \textbf{Can analyze resolved symbols.} When detecting the types proposed in Sec.~\ref{sec:rtypes}, it is important that we can analyze resolved symbols (for instance a type reference).
+The rationale for this is further explained in~\ref{chap:challenge}.
+\item \textbf{Extensive detection configuration.} Detecting our clone definitions, as proposed in Sec.~\ref{sec:rtypes}, require to have some understanding about the meaning of tokens in the source code (whether a certain token is a type, variable, etc.).
+The tool should recognize such structures, in order for us to configure our clone type definitions in the tool.
+\end{enumerate}
+
+\begin{table}[H]
+ \begin{center}
+  \caption{Our survey on clone detection tools.} \label{table:dettools}
+  \medskip
+\begin{tabular}{|l|l|l|l|l|l|}
+\hline
+\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
+Siamese~\cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
+NiCAD~\cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
+CPD~\cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
+\begin{tabular}[c]{@{}l@{}}CCFinder~\cite{kamiya2002ccfinder}\\ D-CCFinder~\cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
+CCFinderSW~\cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
+\begin{tabular}[c]{@{}l@{}}SourcererCC~\cite{sajnani2016sourcerercc}\\ Oreo~\cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
+BigCloneEval~\cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
+Deckard~\cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
+Scorpio~\cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+Apart from these criteria, we found that the output of these clone detection tools cannot be post-processed to find the clone types proposed in Sec.
+\ref{sec:rtypes}.
+This is mainly because the clones of T2R are not a subset of type 2 clones and will thus require an analysis of the entire system.
+
+%To detect clones that can be automatically refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
 We created a set of control projects to determine the suitability of these tools to detect automatically refactorable clones, either through configuration or postprocessing of their output.
 
-None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CR\footnote{Name anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.}.
+%None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable for our definitions of refactorable clones, because of which we propose CR\footnote{Name anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.}.
 This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.

### 2019-10-25 saner/paper.tex
Updates from Overleaf

@@
 
-\section{A tool for automatic clone refactoring}\label{sec:clonerefactor}
+\section{Survey existing clone detection tools}\label{sec:survey}
 %To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability. 
 To investigate the impact of the definitions introduced in Sec.~\ref{sec:research}, we need a tool to detect refactorable clones according to these definitions.
-We attempt to reuse an existing tool, thus we search for candidates.
-None are found, thus we build a new tool.
-
-\subsection{Survey existing clone detection tools}
 We conducted a short survey on (recent) clone detection tools to detect such clones that can be refactored.
@@
 We want to perform an analysis of all clones in projects to get a complete overview.
-\item \textbf{Can be extended to the definitions of refactorable clones.} We assembled a number of control projects to assess the validity of clone detection tools.
+\item \textbf{Correctly identifies .} In order to detect such clones that can be refactored, we need to be able to extend the corresponding tool accordingly.
 \item \textbf{Can analyze resolved symbols.} When detecting the types proposed in Sec.~\ref{sec:rtypes}, it is important that we can analyze resolved symbols (for instance a type reference).
@@
 
-Apart from these criteria, we found that the output of these clone detection tools cannot be post-processed to find the clone types proposed in Sec.
-\ref{sec:rtypes}.
+Apart from these criteria, we found that the output of these clone detection tools cannot be post-processed to find the clone types proposed in Sec.~\ref{sec:rtypes}.
 This is mainly because the clones of T2R are not a subset of type 2 clones and will thus require an analysis of the entire system.
+% TODO
 
@@
 
-%None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable for our definitions of refactorable clones, because of which we propose CR\footnote{Name anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.}.
+%None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable for our definitions of refactorable clones, because of which we propose CR.
 This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
 In the following sections, we explain these steps.
+
+\section{A tool for automatic clone refactoring}\label{sec:clonerefactor}
+None of the surveyed tools were suitable for our definitions of refactorable clones.
+Therefore, we built a new tool, CR\footnote{Name anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.} This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
+In Sec.~\ref{sec:detection} we describe how CR detects refactorable clones.
+In Sec.~\ref{sec:context} we describe how CR maps the context of clones as input for the refactoring process described in Sec.~\ref{sec:refactoring}.
 
@@
 
-\subsection{Clone detection}
+\subsection{Clone detection}\label{sec:detection}
 We use an AST-based method to detect clones.
 Clones are detected on a statement level: only full statements are considered as clones.
-In this process, we limit the variability between indicated expressions (see Sec.~\ref{sec:t2r}) by a threshold.
+We limit the variability between indicated expressions (see Sec.~\ref{sec:t2r}) by a threshold.
 This threshold is the percentage of different expressions against the total number of expressions in the source code:
@@
 
-\subsection{Refactoring}
+\subsection{Refactoring}\label{sec:refactoring}
 CR can refactor clones using the ``Extract Method'' refactoring technique. In this section, we show which clones we refactor and how we apply these transformations.

### 2019-10-25 saner/paper.tex
Updates from Overleaf

@@
 \begin{enumerate}
-  \item The parameterization of differences between the matched statements should not break existing data-, anti-, and output-dependences.
-  \item The unmatched statements should be movable before or after the matched statements without breaking existing data-, anti-, and output-dependences.
+  \item The parameterization of differences between the matched statements should not break existing data-, anti-, and output-dependencies.
+  \item The unmatched statements should be movable before or after the matched statements without breaking existing data-, anti-, and output-dependencies.
   \item The duplicated code fragments should return at most one variable of the same type.
@@
 
-\subsection{Clone context analysis}
+\subsection{Clone context analysis}\label{sec:rw:contextanalysis}
 Golomingi~\cite{koni2001scenario} explores mapping the relation between clone instances to refactoring methods.
@@
 
-Apart from these criteria, we found that the output of these clone detection tools cannot be post-processed to find the clone types proposed in Sec.~\ref{sec:rtypes}.
-This is mainly because the clones of T2R are not a subset of type 2 clones and will thus require an analysis of the entire system.
-% TODO
+Apart from these criteria, we found that the output of these clone detection tools cannot be post-processed to find the clone definition proposed in Sec.~\ref{sec:research}.
+This is mainly because these clones are not necessarily a subset of clones detected by these tools and will thus require an analysis of the entire system.
 
@@
 Clones are detected on a statement level: only full statements are considered as clones.
-We limit the variability between indicated expressions (see Sec.~\ref{sec:t2r}) by a threshold.
+In Sec.~\ref{sec:t2r} we described that we limit the variability between variable, literal and method reference expressions by a threshold.
 This threshold is the percentage of different expressions against the total number of expressions in the source code:
@@
 The maximum size of the gap is limited by a threshold.
-This threshold is the percentage of (not-cloned) statements in the gap against the sum of statements in both clones surrounding it.
-Unlike the expression variability threshold, this threshold can exceed 100\%:
+This threshold is the percentage of (not-cloned) statements in the gap against the sum of statements in both clones surrounding it:
 \begin{equation}\label{eq:type3r}
@@
 
-To verify the correctness of all detected clones, we ran the tool over a large project and manually checked the output.
+Note that unlike the expression variability threshold, this threshold can exceed 100\%. This is because, in theory, the gap can be larger than the clones surrounding it.
+
+% To verify the correctness of all detected clones, we ran the tool over a large project and manually checked the output.
 We also created a set of control projects to test the correctness for many edge cases.
@@
 After clones are detected, we map the context of these clones.
-We have identified two properties of clones as their context: relation and location.
+We identify two properties of clones as their context: relation~\cite{fontana2012duplicated} and location~\cite{tairas2011representing}.
 We identify categories for each of these properties, to get a detailed insight into the context of clones.
@@
 This relation has a big impact on how the clone should be refactored~\cite{fontana2015duplicated}.
-We define the following categories to map the relation between clone instances in a clone class.
+We define the following categories to map the relation between clone instances in a clone class, partly derived from Fontana et al~\cite{fontana2015duplicated} (see Sec~\ref{sec:rw:contextanalysis}).
 These categories do not map external classes (classes outside the project, e.g.
@@
     \begin{itemize}
-        \item \textbf{Same Method}: All clone instances are in the same method.
+        \item[$\square$] \textbf{Same Method}: All clone instances are in the same method.
         \item \textbf{Same Class}: All clone instances are in the same class.
@@
 \subsubsection{Location}\label{sec:location}
-The location of a clone instance determines what refactoring techniques can be applied to refactor such clones. We define the following categories by which we analyze the location of clones:
+The location of a clone instance helps determine what refactoring techniques can be applied to refactor such clones. We define the following categories by which we analyze the location of clones:
 \begin{enumerate}
@@
 
-\subsection{Tool Validation}
-We have validated the correctness of CR through unit tests and empirical validation.
-First, we created a set of 57 control projects to verify the correctness in many (edge) cases.
+\subsection{Tool Evaluation}
+We assess the correctness of CR through unit tests and empirical validation.
+First, we create a set of 57 control projects to verify the correctness in many (edge) cases.
 These projects contain clones for each identified relation, location, and refactorability category to see whether they get correctly identified.

### 2019-10-25 saner/paper.tex
Updates from Overleaf

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 
@@
     \begin{itemize}
-        \item[$\square$] \textbf{Same Method}: All clone instances are in the same method.
+        \item \textbf{Same Method}: All clone instances are in the same method.
         \item \textbf{Same Class}: All clone instances are in the same class.
@@
 
-Based on these relations, CR determines where to place the cloned code when refactored.
-These categories are mutually exclusive: a clone class will be flagged as the first relation in the above list that it applies to.
-The code of clones that have a \textit{Common Class} relation can be refactored by placing the cloned code in this same class.
-The code of clones with a \textit{Common Hierarchy} relation can be placed in the intersecting class in the hierarchy (the class all clone instances have in common as an ancestor).
-The code of clones with a \textit{Common Interface} relation can be placed in the intersecting interface, but in the process has to become part of the classes' public contract.
-The code of clones that are \textit{Unrelated} can be placed in a newly created place: either a utility class, a new superclass abstraction or an interface.
+Based on these relations, CR determines where to place the cloned fragment when extracted to a new method.
+These categories are mutually exclusive: a clone class is flagged as the first relation in the above list that it applies to.
+The code of clones that have a \textit{Common Class} relation can be refactored by placing the cloned code in this same class~\cite{fowler2018refactoring}.
+The code of clones with a \textit{Common Hierarchy} relation can be placed in the intersecting class in the hierarchy (the class all clone instances have in common as an ancestor)~\cite{fowler2018refactoring}.
+The code of clones with a \textit{Common Interface} relation can be placed in the intersecting interface~\cite{mohnen2002interfaces}, but in the process has to become part of the classes' public contract.
+The code of clones that are \textit{Unrelated} can be placed in a newly created place.
+The state-of-the-art uses a utility class~\cite{mazinanian2016jdeodorant}, whereas CR creates a new superclass or interface abstraction.
+% TODO: Elaborate on the superclass abstraction and interface (this is my contribution) --> in refactoring section
 
 \subsubsection{Location}\label{sec:location}
-The location of a clone instance helps determine what refactoring techniques can be applied to refactor such clones. We define the following categories by which we analyze the location of clones:
+The location of a clone instance helps determine what refactoring techniques can be applied to it. We define the following categories of clones based on their location:
 \begin{enumerate}
@@
 \end{enumerate}
+%TODO: Link to table IV to explain how this table created our scoping for this research, and we only refactor partial method.
 
@@
 
+% TODO: Explain about the coupling metric.
+Discussion: it is not too relevant to the results because most refactorings are SAME CLASS which do not impact on the coupling metric.
+(maybe more about architectural refactorings because COUPLING, BALANCE, COHESION?)
+
 \subsection{Clone Context}

### 2019-10-25 saner/paper.tex
Updates from Overleaf

@@
 \end{enumerate}
-%TODO: Link to table IV to explain how this table created our scoping for this research, and we only refactor partial method.
-
-\subsubsection{Full method/constructor/class/interface/enumeration}
 The categories denote that a full declaration (method, class, etc.) often denote redundancy and are often easy to refactor: one of both declarations is redundant and should be removed.
-Clones in the ``Partial Method/Constructor'' category can often be refactored using the ``Extract Method'' refactoring technique.
+Clones in the ``Partial Method/Constructor'' category can often be refactored using the ``Extract Method'' refactoring technique~\cite{mazinanian2016jdeodorant}.
 Clones consisting of \textit{Several Methods} give a strong indication that cloned classes are missing some form of abstraction, or their abstraction is used inadequately.
@@
 \subsection{Refactoring}\label{sec:refactoring}
-CR can refactor clones using the ``Extract Method'' refactoring technique. In this section, we show which clones we refactor and how we apply these transformations.
+Table~\ref{tab:location} shows that most clones are found in method bodies.
+Therefore, we focus on refactoring such clones which entails using the ``Extract Method'' refactoring technique.
+We show which clones CR refactors and how it applies these transformations.
 
-\subsubsection{Extract Method} \label{sec:refactorability}
-Several influencing factors may obstruct the possibility to extract code to a new method:
+\subsubsection{Refactorability} \label{sec:refactorability}
+Several factors may obstruct the possibility to extract code to a new method~\cite{tsantalis2015assessing}:
 \begin{itemize}
@@
 
-\subsubsection{AST Transformation}
-CR uses JavaParser~\cite{smith2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
+\subsubsection{AST Transformation} % TODO: Big todo --> Find literature, introduce proper reasoning why I need to do this.
+rtCR uses JavaParser~\cite{smith20e17javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
 To refactor clones, CR creates a new method declaration and moves all statements from a clone instance in the clone class to the new method.

### 2019-10-26 saner/paper.tex
Stuff

@@
 This allows for more a accurate suggestion of code clones for refactoring and can assist in the refactoring process.
+
+Most clone detection tools can be configured using thresholds.
+These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones.
+Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}.
+Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
+%TODO: Check whether this really fits here
 
@@
 We want to perform an analysis of all clones in projects to get a complete overview.
-\item \textbf{Correctly identifies .} In order to detect such clones that can be refactored, we need to be able to extend the corresponding tool accordingly.
+\item \textbf{Finds clone classes in control projects.} We assembled a number of control projects to assess the validity of the surveyed clone detection tools.
 \item \textbf{Can analyze resolved symbols.} When detecting the types proposed in Sec.~\ref{sec:rtypes}, it is important that we can analyze resolved symbols (for instance a type reference).
@@
 The state-of-the-art uses a utility class~\cite{mazinanian2016jdeodorant}, whereas CR creates a new superclass or interface abstraction.
+The reason CR creates a superclass or interface rather than a utility class is that it makes the relation explicit and allows previously unrelated clones to become related.
 % TODO: Elaborate on the superclass abstraction and interface (this is my contribution) --> in refactoring section
@@
 \end{enumerate}
-The categories denote that a full declaration (method, class, etc.) often denote redundancy and are often easy to refactor: one of both declarations is redundant and should be removed.
+The categories denote that a full declaration (method, class, etc.) often denotes redundancy and are often easy to refactor: one of the declarations is redundant and should be removed.
 Clones in the ``Partial Method/Constructor'' category can often be refactored using the ``Extract Method'' refactoring technique~\cite{mazinanian2016jdeodorant}.
@@
 \todo{This doesn't say anything: explain how the section is organized}
-In this section, we describe the setup of our experiments.
+We explain the corpus used for our experiments in Sec.~\ref{}
 
-\subsection{Corpus}
+\subsection{Corpus}\label{sec:corpus}
 We ran all our experiments using CR on a corpus of open source Java projects.
@@
 
-\subsection{Tool Evaluation}
+\subsection{Tool Evaluation}\label{sec:evaluation}
 We assess the correctness of CR through unit tests and empirical validation.
@@
 
-\subsection{Minimum clone size}
+\subsection{Minimum clone size}\label{sec:thresholds}
 In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored.
@@
 Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones are very unlikely to improve maintainability when refactored.
-
-\subsection{Thresholds}
-Most clone detection tools can be configured using thresholds.
-These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones.
-Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}.
-Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
 

### 2019-10-26 saner/paper.tex
Updates from Overleaf

--- 2019-10-25 saner/paper.tex
@@
 To be able to execute such a refactoring, several preconditions apply \cite{tsantalis2015assessing}.
-
-In this study, we analyze which preconditions apply to determine whether a clone can be automatically refactored.
+\todo[inline]{still missing link on how current solutions do not help improving maintainability - our message from monday night is not crystal clear yet}
+In this study, we analyze which preconditions apply to determine whether a clone could and should be automatically refactored.
 We list criteria that influence the maintainability of clones when refactored.
@@
 \section{Background}\label{sec:background}
-In this section, we describe relevant code clone and clone refactoring research.
+We briefly describe relevant code clone and clone refactoring research.
 
@@
     \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method.
-Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
+Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance \todo{be consistent: ``Extract Method" or ``extract method"} ``pull up method'' for clones in sibling classes).
 \end{itemize}
@@
 \subsubsection{AST Transformation} % TODO: Big todo --> Find literature, introduce proper reasoning why I need to do this.
-rtCR uses JavaParser~\cite{smith20e17javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
+CR uses JavaParser~\cite{smith20e17javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
 To refactor clones, CR creates a new method declaration and moves all statements from a clone instance in the clone class to the new method.
@@
 \end{itemize}
-CR then removes all cloned code and replaces it with a method call to the newly created method. In case of a return value, CR either assigns the call result, declares it or returns it accordingly.
+CR then removes all cloned code and replaces it with a call to the newly created method. In case of a return value, CR either assigns the call result, declares it or returns it accordingly.
 
 \subsubsection{Characteristics of the extracted method}\label{sec:characteristics}
-We define the following characteristics of the extracted method and/or the call:
+We define the following characteristics of the extracted method and/or the call: \todo{why these?}
 \begin{itemize}
@@
 \end{itemize}
-We hypothesize that these characteristics are the main factors influencing the impact on the maintainability of the system as a result of refactoring the clone.
+We hypothesize that these characteristics are the main factors influencing the impact on the maintainability of the system as a result of refactoring the clone. \todo{why?}
 
 \subsubsection{Impact on maintainability metrics} \label{sec:metrics}
-CR measures the impact on maintainability metrics of the refactored source code for each clone class that is refactored.
-These metrics are derived from Heitlager et al.~\cite{heitlager2007practical}.
+\todo[inline]{rephrase this text for clarity: this paper -- which paper? }
+CR measures the impact on maintainability metrics of refactoring source code for each clone class that is refactored.
+These metrics are derived \todo{how did you change them?} from Heitlager et al.~\cite{heitlager2007practical}.
 This paper defines a set of metrics to measure the maintainability of a system.
@@
 
-To determine whether the maintainability improves when refactoring a single clone, we need to measure the impact of small-grained changes.
-Because of that, we measure only a subset of the metrics~\cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
-The subset of metrics we decided to focus on are all metrics that are measured on method level (as the other metrics show a lesser impact on the maintainability for these small changes).
+To determine whether the maintainability improves when refactoring a given clone, we need to measure the impact of fine-grained changes.
+Therefore, we measure only a subset of the metrics~\cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
+The subset of metrics we choose to focus on are all measured on method level (as the other metrics show a lesser impact on the maintainability for these small changes).
 These metrics are:
 \begin{itemize}
-\item \textbf{Duplication}: In Heitlager et al.~\cite{heitlager2007practical} this metric is measured by taking the amount of duplicated lines.
+\item \textbf{Duplication}: Originally~\cite{heitlager2007practical} measured by taking the amount of duplicated lines.
 We decided to use the amount of duplicated tokens part of a clone class instead, to have a stronger reflection of the impact of the refactoring by measuring a more fine-grained system property.
@@
 As with duplication, we use the number of tokens instead.
-\item \textbf{Method Complexity}: Heitlager et al.~\cite{heitlager2007practical} use MCCabe complexity~\cite{mccabe1976complexity} to calculate their complexity metric.
-The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.
+\item \textbf{Method Complexity}:  Originally ~\cite{heitlager2007practical} computed using MCCabe complexity~\cite{mccabe1976complexity}.
+The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.\todo{why is the original way ok for us?}
 \item \textbf{Method Interface Size}: The number of parameters that a method has.
@@
 The ``extract method'' refactoring technique is often used to split up long methods \cite{charalampidou2018structural}.
-When refactoring duplicated code fragments in the body of a method, this could improve maintainability of the methods from which the duplication was removed because of their reduced size.
+When refactoring duplicated code fragments in the body of a method, this could improve maintainability of the refactored (reduced size).
 \end{itemize}
@@
 \todo{This doesn't say anything: explain how the section is organized}
-In this section, we describe the setup of our experiments.
+%In this section, we describe the setup of our experiments.
+Our goal is analysing whether automated refactoring of code clones leads to an improved maintainability.
+We first validate our automated refactoring tool, CR.
+Next, we run our tool on a reference corpus and measure the change in the maintainability score.
+
+\subsection{Tool Evaluation}
+We assess the correctness of CR through unit tests and empirical validation.
+First, we create a set of 57 control projects to verify the correctness in many (edge) cases.
+These projects contain clones for each relation, location, and refactorability category.
+%to see whether they get correctly identified. 
+Next, we run the tool over the corpus and manually verify samples \todo{how many?
+why not all?} of the acquired results.
+This way, we check both the correctness of the identified clones, their context, and their proposed refactoring.
+
+We also test the correctness of the refactored code using the JFreeChart project~\cite{jfreechart}.
+JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CR.
 
 \subsection{Corpus}
-We ran all our experiments using CR on a corpus of open source Java projects.
-This corpus is derived from the corpus of a study that uses machine learning to determine the suitability of Java projects on GitHub for data analysis purposes~\cite{githubCorpus2013}.
+Our corpus, consisting of open source Java projects, is derived from the corpus of a study that uses machine learning to determine the suitability of GitHub Java projects for data analysis purposes~\cite{githubCorpus2013}.
+\todo[inline]{why did you choose this corpus?}
 
-CR requires all libraries of the projects it analyses, to find the full paths of all referenced symbols in the source code (see Sec.~\ref{sec:t1r}).
-Because of that requirement, we decided to filter the corpus to only projects using the Maven build automation system.
-We created a set of scripts to prepare such a corpus with all dependencies included.
+CR requires all libraries of the analyzed projects
+%it analyses, to find the full paths of all referenced symbols in the source code 
+(see Sec.~\ref{sec:t1r}).
+Therefore, we decided to filter the corpus to contain only projects using the Maven build automation system.
+The filtering scripts are publicly availble \footnotesize{The camera-ready version would include the GitHub repo url}.
+%We created a set of scripts to prepare such a corpus with all dependencies included.
 
-This procedure results in 2.267 Java projects including all their dependencies.
+This procedure results in 2.267 Java projects including all their dependencies \todo{this is confusing, how many original projects are there?
+were the dependencies in the original corpus?}.
 The projects vary in size and quality.
@@
 The largest project in the corpus is \textit{VisAD} with 502K lines.
-
-\subsection{Tool Evaluation}
-We assess the correctness of CR through unit tests and empirical validation.
-First, we create a set of 57 control projects to verify the correctness in many (edge) cases.
-These projects contain clones for each identified relation, location, and refactorability category to see whether they get correctly identified.
-Next, we run the tool over the corpus and manually verify samples of the acquired results.
-This way, we check both the correctness of the identified clones, their context, and their proposed refactoring.
-
-We also test the correctness of the resulting code after refactoring.
-For this, we use a GitHub project named JFreeChart.
-JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CR.
+\todo[inline]{figure with the distribution of project sizes?}
 
 \subsection{Minimum clone size}
-In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored.
-However, when clones are very small, they may never be able to improve maintainability.
+% In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored. However, 
+When clones are very small, they may never be able to improve maintainability.
 The detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication.
-Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones are very unlikely to improve maintainability when refactored.
+We perform all our experiments with a minimum clone size of 10 tokens, as smaller clones are very unlikely\todo{any ref?} to improve maintainability when refactored.
 
@@
 These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones.
-Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}.
-Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
+Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile \todo{quartile or quantile?} distribution of empirical data~\cite{alves2010deriving}.
+\todo{paragraph commented below seems more suitable for the discussion part. otherwise it should be rephrased.}
+% Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
 
@@
 \subsection{Calculating a maintainability score}\label{sec:metricformula}
-In this study, we use four metrics to determine maintainability (see Sec.~\ref{sec:metrics}).
-For each of these metrics, we determine their value before and after each refactored clone class, resulting in a delta metric score.
-For our experiments, we aggregate the deltas obtained for these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
-We base our aggregation on the following assumptions:
+We use four metrics to determine maintainability (see Sec.~\ref{sec:metrics}).
+We determine the value of each metric before and after for each refactored clone class, resulting in a delta metric score.
+We aggregate the deltas obtained for these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
+We base our aggregation on the following assumptions derived from supporting evidence~\cite{heitlager2007practical},~\cite{alves2010deriving}:
 \begin{itemize}
@@
   \item Higher values for the metrics imply lower maintainability.
-  \item Normalizing each obtained metric delta over all deltas obtained for that metric in our dataset results in equally weighted scores.
+  \item Normalizing each metric delta over all deltas obtained for that metric in our dataset results in equally weighted
+  scores.\todo{confusing}
+  \item \todo{isn't this also an assumption?} all considered metrics do not interfere with the out-of-scope metrics
 \end{itemize}
-We derived these assumptions from supporting evidence shown by Heitlager et al~\cite{heitlager2007practical} and Alves et al.~\cite{alves2010deriving}.
-Using the resulting aggregated maintainability score, we can argue for each refactoring whether it increases or decreases the maintainability of the system.
 
-We normalize each obtained metric delta using the ``Standard score'', which is calculated as follows:
+We use the resulting aggregated maintainability score to analyze  for each refactoring whether it increases or decreases the maintainability of the system.
+
+We normalize each obtained metric delta using the ``Standard score''\todo{this name is confusing, is it established?
+then cite ref, otherwise I don't understand the quotes}, which is calculated as follows \todo{first give the intuition, then the math!}:
 \begin{equation}\label{eq:scoredev}
@@
 Where $\Delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metric.
-This method works well for normalization of our data because as we divide by the standard deviation, outliers do not influence the resulting scores negatively.
+This method works well for normalization of our data because as we divide by the standard deviation, outliers do not influence the resulting scores negatively \todo{backup by citing relevant reference}.
 
-We then calculate the maintainability for a specific refactoring as follows:
+We calculate the maintainability of a refactoring as:
 \begin{equation}\label{eq:scoreref}
@@
 \section{Results} \label{sec:results}
-In this section, we share the results of our experiments.
+We first report the context results, then the refactorability results.
 
@@
 \subsubsection{Relation}
-Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for the identified relations between clone instances (see Sec.~\ref{sec:relation}).
+Table~\ref{tab:relation} shows the number of clone classes found for the entire corpus for each type of relations between clone instances (see Sec.~\ref{sec:relation}).
 
@@
 \subsubsection{Location}
-Table~\ref{tab:location} displays the number of clone classes found for the entire corpus for different locations (see Sec.~\ref{sec:location}).
+Table~\ref{tab:location} shows the number of clone classes found for the entire corpus for different locations (see Sec.~\ref{sec:location}).
 
@@
 
-From these results, we see that 74\% of clones span part of a method body (77\% if we include constructors).
+The results show that 74\% of clones span part of a method body (77\% if we include constructors).
 8\% of clones span several methods.
@@
 
-These results indicate that, given our refactorability criteria, 28\% of clones can be automatically refactored.
+\todo[inline]{the paragraph below belongs to discussion}
+The results indicate that, given our refactorability criteria, 28\% of clones can be automatically refactored.
 Clones in other categories may require other refactoring techniques or further transformations to be automatically refactorable.
@@
 \subsection{Thresholds}
-In our corpus, CR has refactored 12.710 clone classes and measured the change in indicated metrics (see Sec.~\ref{sec:metrics}).
-Using the presented formulas (see Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
-In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.
+ CR has refactored 12.710 clone classes and measured the change in the selected metrics (Sec.~\ref{sec:metrics}).
+\todo{use the formulas labels to refer here} Using the presented formulas (Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
+We explore the data obtained by comparing the before- and after snapshots of the system for each separate refactoring.
 Using this data, we find supporting evidence regarding which thresholds are most likely to find clones that should be refactored to improve maintainability.
@@
 \subsubsection{Clone Token Volume}
-Figure \ref{fig:maintainabilityscore} shows the obtained results when plotting the clone volume vs the average delta maintainability score.
+Figure \ref{fig:maintainabilityscore} shows the results by plotting the clone volume vs the average delta maintainability score.
 We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class.
-For higher token volume numbers we have fewer refactorings that refactor such clones, because of which we represent the x-axis as a logarithmic scale.
+For higher token volume numbers we have fewer refactorings that refactor such clones, therefore we represent the x-axis as a logarithmic scale.
 The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.
@@
 Table~\ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability.
-We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance.
-
-The displayed relations are ordered by their scores.
-Overall, the scores do not deviate much (-0.15 to 0.23), indicating that the relation between clones has a minor impact on maintainability.
-Overall, we see that common hierarchy clones have the highest maintainability, whereas unrelated clones have the lowest maintainability.
+We have marked rows based on less than 100 refactorings red\todo{not color-agnostic, if printed bw might be a problem --> just make it grey }, as their result does not have statistical significance.
+Relations are ordered by their scores.
+\todo{this sentence about relation impact seems more suitable for discussion}Scores do not deviate much (-0.15 to 0.23), indicating that the relation between clones has a minor impact on maintainability.
+Overall, common hierarchy clones have the highest maintainability, whereas unrelated clones have the lowest maintainability.
 
@@
 Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.
+The return categories are ordered by their scores.
+\todo{this sentence about relation impact seems more suitable for discussion}Scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability.
+When the result of the call to the extracted method is directly returned, the maintainability score is the highest.
+When no value is returned, the maintainability score is the lowest.
+\todo{this sentence about relation impact seems more suitable for discussion}The main reason that no return value is lowest, is that it is linked to a higher number of parameters required for the extracted method.
 
@@
 \end{table*}
-
-The displayed return categories are ordered by their scores.
-Overall, the scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability.
-When the result of the call to the extracted method is directly returned, the maintainability score is the highest.
-When no value is returned, the maintainability score is the lowest.
-The main reason that no return value ends up lowest, is that it is linked to a higher number of parameters required for the extracted method.
 
@@
 Regarding clone context, our results indicate that most clones (37\%) are in a common class.
-This is favorable for refactoring because the extracted method does not have to be moved after extraction.
+This is favorable for \todo{automated?} refactoring because the extracted method does not have to be moved after extraction.
 24\% of clones are in a common hierarchy.
@@
 Another 24\% of clones are unrelated, which is often unfavorable because it often requires a more comprehensive refactoring.
-15\% of clones are in an interface.
+15\% of clones are in an interface \todo{which ...}.
 
@@
 28\% of clones can be refactored using the ``Extract Method'' refactoring technique (50\% if we limit our searching scope to method bodies).
-About 25\% of clones do not span part of a method, because of which they cannot be refactored.
+About 25\% of clones do not span part of a method, therefore they cannot be refactored.
 Many clones (23\%) do not have a statement as top-level AST-Node.
-Upon manual inspection, we noticed that the main reason for this is when clones are found in lambda functions or anonymous classes.
-About 15\% of clones span only part of an AST-Node.
+Upon manual inspection, we noticed that the main reason is clones in lambda functions or in anonymous classes.
+About 15\% of clones span only part of an AST-Node \todo{and?}.
 
 \subsection{Refactoring}
-In Fig.~\ref{fig:maintainabilityscore} we see an increase in maintainability for refactoring larger clone classes.
-The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie around a token volume of 63 tokens.
-There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.
+Fig.~\ref{fig:maintainabilityscore} shows an increase in maintainability for refactoring larger clone classes.
+The tipping point, between a better and a worse maintainable refactoring, seems to lie around a token volume of 63 tokens.
+There are fewer large clones than small clones, resulting in a very limited \todo{how limited?
+give the p-value} statistical significance on our corpus when considering clones larger than 100 tokens.
 
-In Table~\ref{tab:relation_refactor} we see the results regarding refactorings that are applied to clones with diverse relations.
-We see that most refactored clones are in a common class, over 54\%.
-This is significantly more than the percentage of clones in the common class relation as reported in Table~\ref{tab:relation}.
-Meanwhile, the number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% -> 18\%).
+Table~\ref{tab:relation_refactor} shows the results regarding refactorings that are applied to clones with diverse relations.
+More than 54\% of the refactored clones are in a common class.
+This is significantly more than the percentage of clones in the common class relation reported in Table~\ref{tab:relation}.
+The number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% -> 18\%).
 The main reason for this is that refactoring unrelated clones can change the relation of other clones in the same system.
@@
 
-The maintainability scores displayed in Table~\ref{tab:relation_refactor} show that the most favorable clones to refactor are clones with a Sibling relation.
-The most unfavorable is to refactor clones to interfaces.
-However, the differences in maintainability in this table are generally small; according to our data relations have only a minor impact on the maintainability of clones.
+The maintainability scores in Table~\ref{tab:relation_refactor} show that the most favorable clones to refactor are clones with a Sibling relation.
+The most unfavorable is refactoring clones to interfaces.
+However, the differences in maintainability in this table are generally small \todo{and?}; according to our data relations have only a minor impact on the maintainability of clones.
 
-Regarding the return type of refactored clones, we see in Table~\ref{tab:return} that this has no major impact on maintainability.
+Regarding the return type of refactored clones, Table~\ref{tab:return} shows that this has no major impact on maintainability.
 A method call to the extracted method that is directly returned and no return type extracted methods are slightly more favorable than the others.
@@
 
-A higher number of parameters directly influences the corresponding metric.
-Because of this, we see in Fig.~\ref{fig:arguments} that more parameters negatively influence maintainability.
-Not only the number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
+% A higher number of parameters directly influences the corresponding metric. 
+Fig.~\ref{fig:arguments} shows that more parameters negatively influence maintainability.
+Not only the \todo{wasn't this a characteristic?
+this paragraph is somewhat confusing} number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
 Because of that, we see that the trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.
 
+\todo[inline]{one paragraph with a general remark on this discussion, summarizing our findings}
 \section{Conclusion} \label{sec:conclusion}
+\todo[inline]{one paragraph summarizing the context of our research}
 We defined automatically refactorable clones and created a tool to detect and refactor them.
@@
 We built a tool that can automatically apply refactorings to 28\% of the clones in our corpus using the ``Extract Method'' refactoring technique. 
-The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, e.g., when code outside a method is part of a clone.
+% The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, e.g., when code outside a method is part of a clone.
 
-We measured four maintainability metrics before- and after applying each refactoring to determine the impact of each refactoring on system maintainability.
+We measured the change in four maintainability metrics
+%before- and after applying each refactoring 
+to determine the impact of each refactoring on system maintainability.
 We found that the most prominent factor influencing maintainability is the size of the clone.
-We found that the threshold lies at a clone volume of 29 tokens per clone instance for system maintainability to increase after refactoring the clone.
+We found that the threshold lies at a clone volume of 29 \todo{wasn't this 63?} tokens per clone instance for system maintainability to increase after refactoring the clone.
 Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data.

### 2019-10-26 saner/paper.tex
Updates from Overleaf

@@
 
-\title{Improving Software Maintainability through Automated Refactoring of Code Clones}
+\title{Improving Software Maintainability through automatic refactoring of Code Clones}
 \author{}
@@
 
-\subsubsection{Characteristics of the extracted method}\label{sec:characteristics}
-We define the following characteristics of the extracted method and/or the call: \todo{why these?}
-\begin{itemize}
-\item \textbf{Tokens}: The number of tokens in the body of the method.
-\item \textbf{Relation}: The relation category (Sec.~\ref{sec:relation}) by which this methods' location was determined.
-\item \textbf{Returns}: Whether the method calls return, declare, assign or don't use any data from the extracted method.
-\item \textbf{Parameters}: The number of parameters the extracted method has.
-\end{itemize}
-We hypothesize that these characteristics are the main factors influencing the impact on the maintainability of the system as a result of refactoring the clone. \todo{why?}
+\subsection{Maintainability Metrics}
+After applying the refactorings, CR measures the impact of the refactoring on maintainability metrics.
+We first state the metrics that we measure and then define the characteristics of the applied refactoring that influence the metrics.
 
-\subsubsection{Impact on maintainability metrics} \label{sec:metrics}
+\subsubsection{Maintainability metrics} \label{sec:metrics}
 \todo[inline]{rephrase this text for clarity: this paper -- which paper? }
@@
 
+\subsubsection{Characteristics of the extracted method}\label{sec:characteristics}
+To assess the impact of an applied refactoring, we selected the four characteristics that have the highest impact on the resulting maintainability scores:
+\begin{itemize}
+\item \textbf{Size (in tokens)}: The number of tokens in the body of the method.
+A larger number of tokens means that more duplicate code can be removed, and thus has a positive impact on maintainability.
+\item \textbf{Relation}: The relation category (Sec.~\ref{sec:relation}) by which this methods' location was determined. Some relations are less favorable for maintainability than others.
+\item \textbf{Returns}: Whether the method calls return, declare, assign or don't use any data from the extracted method.
+This affects maintainability because the data must be returned from the extracted method, and assigned at each method call.
+This increases the volume of the refactoring.
+\item \textbf{Parameters}: The number of parameters the extracted method has.
+If the extracted method uses data that is not available where it is located, the data must be passed using method parameters.
+If a method has many parameters, it becomes less reusable and harder to comprehend, thus harder to maintain \cite{heitlager2007practical}.
+Additionally, this increases the volume, because each call to the extracted method must pass all required data.
+\end{itemize}
+We hypothesize that these characteristics are the main factors influencing the impact on the maintainability of the system as a result of refactoring the clone.
+This is because there are no further transformations that are applied that influence the maintainability metrics.
+
 \section{Experimental setup} \label{sec:experimentalsetup}
@@
 %In this section, we describe the setup of our experiments.
-Our goal is analysing whether automated refactoring of code clones leads to an improved maintainability.
-We first validate our automated refactoring tool, CR.
+Our goal is analysing whether automatic refactoring of code clones leads to an improved maintainability.
+We first validate our automatic refactoring tool, CR.
 Next, we run our tool on a reference corpus and measure the change in the maintainability score.

### 2019-10-26 saner/paper.tex

@@
 Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
-%TODO: Check whether this really fits here
+\todo{Check whether this really fits here}
 
@@
 \item \textbf{Finds clone classes in control projects.} We assembled a number of control projects to assess the validity of the surveyed clone detection tools.
-\item \textbf{Can analyze resolved symbols.} When detecting the types proposed in Sec.~\ref{sec:rtypes}, it is important that we can analyze resolved symbols (for instance a type reference).
-The rationale for this is further explained in~\ref{chap:challenge}.
-\item \textbf{Extensive detection configuration.} Detecting our clone definitions, as proposed in Sec.~\ref{sec:rtypes}, require to have some understanding about the meaning of tokens in the source code (whether a certain token is a type, variable, etc.).
+\item \textbf{Can analyze resolved symbols.} When detecting the clones proposed in Sec.~\ref{sec:research}, it is important that we can analyze resolved symbols (for instance a type reference).
+\item \textbf{Extensive detection configuration.} Detecting our clone definitions, as proposed in Sec.~\ref{sec:research}, require to have some understanding about the meaning of tokens in the source code (whether a certain token is a type, variable, etc.).
 The tool should recognize such structures, in order for us to configure our clone type definitions in the tool.
@@
 The reason CR creates a superclass or interface rather than a utility class is that it makes the relation explicit and allows previously unrelated clones to become related.
-% TODO: Elaborate on the superclass abstraction and interface (this is my contribution) --> in refactoring section
 
@@
     \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method.
-Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance \todo{be consistent: ``Extract Method" or ``extract method"} ``pull up method'' for clones in sibling classes).
+Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``Pull Up Method'' for clones in sibling classes).
 \end{itemize}
@@
 
-\subsubsection{AST Transformation} % TODO: Big todo --> Find literature, introduce proper reasoning why I need to do this.
-CR uses JavaParser~\cite{smith20e17javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
+\subsubsection{AST Transformation}
+\todo{Big todo --> Find literature, introduce proper reasoning why I need to do this.}
+CR uses JavaParser~\cite{smith2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
 To refactor clones, CR creates a new method declaration and moves all statements from a clone instance in the clone class to the new method.
@@
 
-We also test the correctness of the refactored code using the JFreeChart project~\cite{jfreechart}.
+We also test the correctness of the refactored code using the JFreeChart project~\cite{gilbert2002jfreechart}.
 JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CR.
@@
 
-% TODO: Explain about the coupling metric.
+\todo{Explain about the coupling metric.
 Discussion: it is not too relevant to the results because most refactorings are SAME CLASS which do not impact on the coupling metric.
-(maybe more about architectural refactorings because COUPLING, BALANCE, COHESION?)
+(maybe more about architectural refactorings because COUPLING, BALANCE, COHESION?)}
 

### 2019-10-26 saner/paper.tex
Updates from Overleaf

@@
 \subsubsection{Maintainability metrics} \label{sec:metrics}
-\todo[inline]{rephrase this text for clarity: this paper -- which paper? }
 CR measures the impact on maintainability metrics of refactoring source code for each clone class that is refactored.
-These metrics are derived \todo{how did you change them?} from Heitlager et al.~\cite{heitlager2007practical}.
-This paper defines a set of metrics to measure the maintainability of a system.
+These metrics are from Heitlager et al.~\cite{heitlager2007practical}.
 For each of these metrics, risk profiles are proposed to determine the maintainability impact on the system of a whole.
@@
 \item \textbf{Method Complexity}:  Originally ~\cite{heitlager2007practical} computed using MCCabe complexity~\cite{mccabe1976complexity}.
-The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.\todo{why is the original way ok for us?}
+The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.%\todo{why is the original way ok for us?}
 \item \textbf{Method Interface Size}: The number of parameters that a method has.
@@
 \section{Experimental setup} \label{sec:experimentalsetup}
-\todo{This doesn't say anything: explain how the section is organized}
 %In this section, we describe the setup of our experiments.
-Our goal is analysing whether automatic refactoring of code clones leads to an improved maintainability.
+We describe how we evaluated CR and the corpus on which we ran CR. We then describe the configuration of our experiments. Finally, we describe how we calculated our results.
+%Our goal is analysing whether automatic refactoring of code clones leads to an improved maintainability.
 We first validate our automatic refactoring tool, CR.
@@
 %to see whether they get correctly identified. 
-Next, we run the tool over the corpus and manually verify samples \todo{how many?
-why not all?} of the acquired results.
+Next, we run the tool over the corpus and manually verify samples of the acquired results.
+We verified at least 5 clones of each relation, location and refactoring.
 This way, we check both the correctness of the identified clones, their context, and their proposed refactoring.
@@
 Our corpus, consisting of open source Java projects, is derived from the corpus of a study that uses machine learning to determine the suitability of GitHub Java projects for data analysis purposes~\cite{githubCorpus2013}.
-\todo[inline]{why did you choose this corpus?}
+We chose this corpus because it has a variety of projects of different size and quality, which accurately reflects the target group for the results of our research.
 
@@
 
-This procedure results in 2.267 Java projects including all their dependencies \todo{this is confusing, how many original projects are there?
-were the dependencies in the original corpus?}.
+This procedure results in 2.267 Java projects including all their dependencies%\todo{this is confusing, how many original projects are there? were the dependencies in the original corpus?}
+.
 The projects vary in size and quality.
@@
 The largest project in the corpus is \textit{VisAD} with 502K lines.
-\todo[inline]{figure with the distribution of project sizes?}
+The distribution of project sizes is displayed in Fig.~\ref{fig:dist}.
+
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/dist2}
+  \caption{Distribution of project sizes in corpus on a logaritmic scale.}
+  \label{fig:dist}
+\end{figure}
 

### 2019-10-26 saner/paper.tex
Updates from Overleaf

@@
 The detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication.
-We perform all our experiments with a minimum clone size of 10 tokens, as smaller clones are very unlikely\todo{any ref?} to improve maintainability when refactored.
+We perform all our experiments with a minimum clone size of 10 tokens, as smaller clones are very unlikely to improve maintainability when refactored (see our results in Sec.~\ref{sec:clonetokenvolume}).
 
-\subsection{Thresholds}
-Most clone detection tools can be configured using thresholds.
+%\subsection{Thresholds}
+%Most clone detection tools can be configured using thresholds.
 These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones.
-Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile \todo{quartile or quantile?} distribution of empirical data~\cite{alves2010deriving}.
-\todo{paragraph commented below seems more suitable for the discussion part. otherwise it should be rephrased.}
+Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quantile distribution of empirical data~\cite{alves2010deriving}.
+%\todo{paragraph commented below seems more suitable for the discussion part. otherwise it should be rephrased.}
 % Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
@@
   \item Normalizing each metric delta over all deltas obtained for that metric in our dataset results in equally weighted
-  scores.\todo{confusing}
-  \item \todo{isn't this also an assumption?} all considered metrics do not interfere with the out-of-scope metrics
+  scores.%\todo{confusing}
+  \item All considered metrics do not interfere with the out-of-scope metrics
 \end{itemize}
@@
 
-We normalize each obtained metric delta using the ``Standard score''\todo{this name is confusing, is it established?
-then cite ref, otherwise I don't understand the quotes}, which is calculated as follows \todo{first give the intuition, then the math!}:
+We normalize each obtained metric delta using the standard score, because our data contains many outliers and the standard score is not much affected by those.
+The standard score is calculated as follows:
 \begin{equation}\label{eq:scoredev}
@@
 Where $\Delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metric.
-This method works well for normalization of our data because as we divide by the standard deviation, outliers do not influence the resulting scores negatively \todo{backup by citing relevant reference}.
+This method works well for normalization of our data because as we divide by the standard deviation, outliers do not influence the resulting scores negatively.% \todo{backup by citing relevant reference}.
 
@@
 
-\todo[inline]{the paragraph below belongs to discussion}
-The results indicate that, given our refactorability criteria, 28\% of clones can be automatically refactored.
+The results show that, given our refactorability criteria, 28\% of clones can be automatically refactored.
 Clones in other categories may require other refactoring techniques or further transformations to be automatically refactorable.
@@
 
-\subsubsection{Clone Token Volume}
+\subsubsection{Clone Token Volume} \label{sec:clonetokenvolume}
 Figure \ref{fig:maintainabilityscore} shows the results by plotting the clone volume vs the average delta maintainability score.

### 2019-10-26 saner/paper.tex
Updates from Overleaf

@@
 To be able to execute such a refactoring, several preconditions apply \cite{tsantalis2015assessing}.
-\todo[inline]{still missing link on how current solutions do not help improving maintainability - our message from monday night is not crystal clear yet}
+%\todo[inline]{still missing link on how current solutions do not help improving maintainability - our message from monday night is not crystal clear yet}
 In this study, we analyze which preconditions apply to determine whether a clone could and should be automatically refactored.
@@
 Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}.
-Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
-\todo{Check whether this really fits here}
+Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.% \todo{Check whether this really fits here}
 
@@
 \subsubsection{AST Transformation}
-\todo{Big todo --> Find literature, introduce proper reasoning why I need to do this.}
+%\todo{Big todo --> Find literature, introduce proper reasoning why I need to do this.}
 CR uses JavaParser~\cite{smith2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
@@
 \hspace{10pt} Sibling & -70.07 & 0.69 & 1.28 & -10.97 & 1,722 & 0.23 \\
-\rowcolor[HTML]{FFCCC9}
+\rowcolor[HTML]{D0D0D0}
 \hspace{10pt} Same Hierarchy & -44.18 & 0.95 & 0.89 & 1.54 & 87 & 0.10 \\
 \hspace{10pt} First Cousin & -42.69 & 0.89 & 0.93 & 4.86 & 144 & 0.02 \\
-\rowcolor[HTML]{FFCCC9}
+\rowcolor[HTML]{D0D0D0}
 \hspace{10pt} Ancestor & -32.75 & 1.00 & 0.75 & 11.00 & 20 & -0.03 \\ \midrule
@@
 \subsection{Thresholds}
-CR has refactored 12.710 clone classes and measured the change in the selected metrics (Sec.~\ref{sec:metrics}).
-\todo{use the formulas labels to refer here} Using the presented formulas (Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
+CR has refactored 12.710 clone classes and measured the change in the selected metrics (Sec.~\ref{sec:metrics}). %\todo{use the formulas labels to refer here.
+Using the presented formulas (Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
 We explore the data obtained by comparing the before- and after snapshots of the system for each separate refactoring.
@@
 
-\todo{Redo plot, explain axes units}
+%\todo{Redo plot, explain axes units}
 \begin{figure*}
@@
 Table~\ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability.
-We have marked rows based on less than 100 refactorings red\todo{not color-agnostic, if printed bw might be a problem --> just make it grey }, as their result does not have statistical significance.
+We mark rows grey if they are based on less than 100 refactorings, as their result does not have statistical significance.
 Relations are ordered by their scores.
-\todo{this sentence about relation impact seems more suitable for discussion}Scores do not deviate much (-0.15 to 0.23), indicating that the relation between clones has a minor impact on maintainability.
+%\todo{this sentence about relation impact seems more suitable for discussion}
+Scores do not deviate much (-0.15 to 0.23), indicating that the relation between clones has a minor impact on maintainability.
 Overall, common hierarchy clones have the highest maintainability, whereas unrelated clones have the lowest maintainability.
@@
 The return categories are ordered by their scores.
-\todo{this sentence about relation impact seems more suitable for discussion}Scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability.
+%\todo{this sentence about relation impact seems more suitable for discussion}
+Scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability.
 When the result of the call to the extracted method is directly returned, the maintainability score is the highest.
 When no value is returned, the maintainability score is the lowest.
-\todo{this sentence about relation impact seems more suitable for discussion}The main reason that no return value is lowest, is that it is linked to a higher number of parameters required for the extracted method.
+%\todo{this sentence about relation impact seems more suitable for discussion}
+The main reason that no return value is lowest, is that it is linked to a higher number of parameters required for the extracted method.
 
@@
 Declare & 0.94 & 0.74 & 11.11 & -49.19 & 5,177 & 0.15 \\
-\rowcolor[HTML]{FFCCC9}
+\rowcolor[HTML]{D0D0D0}
 Assign & 0.79 & 1.07 & 0.43 & -56.29 & 14 & 0.12 \\
@@
 
-\todo{Redo plot, explain axes units}
+%\todo{Redo plot, explain axes units}
 \begin{figure}[H]
@@
 
-\todo{Explain about the coupling metric.
+%\todo{Explain about the coupling metric.
 Discussion: it is not too relevant to the results because most refactorings are SAME CLASS which do not impact on the coupling metric.
@@
 Regarding clone context, our results indicate that most clones (37\%) are in a common class.
-This is favorable for \todo{automated?} refactoring because the extracted method does not have to be moved after extraction.
+This is favorable for automatic refactoring because the extracted method does not have to be moved after extraction.
 24\% of clones are in a common hierarchy.
@@
 Another 24\% of clones are unrelated, which is often unfavorable because it often requires a more comprehensive refactoring.
-15\% of clones are in an interface \todo{which ...}.
+15\% of clones are in an interface.
+%\todo{which ...}.
 
@@
 Upon manual inspection, we noticed that the main reason is clones in lambda functions or in anonymous classes.
-About 15\% of clones span only part of an AST-Node \todo{and?}.
+About 15\% of clones span only part of an AST-Node.% \todo{and?}.
 
@@
 The tipping point, between a better and a worse maintainable refactoring, seems to lie around a token volume of 63 tokens.
-There are fewer large clones than small clones, resulting in a very limited \todo{how limited?
-give the p-value} statistical significance on our corpus when considering clones larger than 100 tokens.
+There are fewer large clones than small clones, resulting in a very limited %\todo{how limited?
+give the p-value}
+statistical significance on our corpus when considering clones larger than 100 tokens.
 
@@
 The most unfavorable is refactoring clones to interfaces.
-However, the differences in maintainability in this table are generally small \todo{and?}; according to our data relations have only a minor impact on the maintainability of clones.
+However, the differences in maintainability in this table are generally small %\todo{and?}
+; according to our data relations have only a minor impact on the maintainability of clones.
 
@@
 % A higher number of parameters directly influences the corresponding metric. 
-Fig.~\ref{fig:arguments} shows that more parameters negatively influence maintainability.
-Not only the \todo{wasn't this a characteristic?
-this paragraph is somewhat confusing} number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
+Fig.~\ref{fig:arguments} shows that more parameters negatively influence maintainability. Not only the %\todo{wasn't this a characteristic? this paragraph is somewhat confusing}
+number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
 Because of that, we see that the trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.
 
-\todo[inline]{one paragraph with a general remark on this discussion, summarizing our findings}
+%\todo[inline]{one paragraph with a general remark on this discussion, summarizing our findings}
 \section{Conclusion} \label{sec:conclusion}
-\todo[inline]{one paragraph summarizing the context of our research}
+%\todo[inline]{one paragraph summarizing the context of our research}
 We defined automatically refactorable clones and created a tool to detect and refactor them.
@@
 We found that the most prominent factor influencing maintainability is the size of the clone.
-We found that the threshold lies at a clone volume of 29 \todo{wasn't this 63?} tokens per clone instance for system maintainability to increase after refactoring the clone.
+We found that the threshold lies at a clone volume of 63  %\todo{wasn't this 63?}
+tokens for all clone instances combined for system maintainability to increase after refactoring the clone.
 Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data.

### 2019-11-06 saner/paper.tex
Updates from Overleaf

@@
 To remove such anti-patterns, the codebase should be refactored.
-Many tools aid in the de©tection process of such duplication problems but do not determine whether refactoring an identified clone would improve the maintainability.
+Many tools aid in the detection process of such duplication problems but do not determine whether refactoring an identified clone would improve the maintainability.
+Moreover, manual code clone refactoring is often tedious and could benefit from an automated tool.
 
-We address this shortcoming by first analyzing what preconditions apply to be able to refactor clones.
+We address this shortcoming by first analyzing what preconditions apply to be able to automatically refactor clones.
 We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them.
@@
 
-We identify the factors of interest characterizing the impact on maintainability of automatically applied refactorings.
+We identify the factors of interest characterizing the impact on the maintainability of automatically applied refactorings.
 We find that the biggest influencing factor is token volume.
@@
 Apart from that, code clones can contribute up to 25\% of the code size~\cite{bruntink2005use}.
+However, manual code clone refactoring is often tedious and could benefit from an automated tool~\cite{mazinanian2016jdeodorant}.
 
@@
 Because of this, the output of clone detection tools is often of limited assistance to the developer in the refactoring process.
-To reduce duplication of a codebase, there are several refactoring techniques that can be applied.
+To reduce duplication of a codebase, there are several refactoring techniques that can be applied in an automated manner.
 The most used refactoring technique to deal with code clones is ``Extract Method'' \cite{fowler2018refactoring}.
@@
 These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones.
-Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}.
+Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quantile distribution of empirical data~\cite{alves2010deriving}.
 Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.% \todo{Check whether this really fits here}
@@
 In Sec.~\ref{sec:background} we revisit key clone refactoring background.
-Sec.~\ref{sec:relatedwork} discusses state-of-the-art in automated clone refactoring research.
+Sec.~\ref{sec:relatedwork} discusses state-of-the-art in automatic clone refactoring research.
 In Sec.~\ref{sec:research} we propose a definition for clones such that they could and should be automatically refactored.
@@
 CR has refactored 12.710 clone classes and measured the change in the selected metrics (Sec.~\ref{sec:metrics}). %\todo{use the formulas labels to refer here.
-Using the presented formulas (Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
+Using the formulas in Eq.~\ref{eq:scoredev} and~\ref{eq:scoreref}
+(Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
 We explore the data obtained by comparing the before- and after snapshots of the system for each separate refactoring.
@@
 %\todo{this sentence about relation impact seems more suitable for discussion}
-The main reason that no return value is lowest, is that it is linked to a higher number of parameters required for the extracted method.
+The main reason that "Void" is lowest, is that it is linked to a higher number of parameters required for the extracted method.
 
@@
 %\todo{Redo plot, explain axes units}
-\begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/arguments}
+\begin{figure*}
+  \includegraphics[width=1\textwidth]{img/argu}
   \caption{Influence of number of method parameters on system maintainability.}
   \label{fig:arguments}
-\end{figure}
+\end{figure*}
 
@@
 tokens for all clone instances combined for system maintainability to increase after refactoring the clone.
-Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data.
+Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data: when a clone is refactored to a method that requires more than 2 parameters it is more likely to decrease maintainability than to increase it.
 We noticed that the inheritance relation of the clone and the return value of the extracted method has only a minor impact on system maintainability.

### 2019-11-06 benevol/introduction.tex
Added benevol stuff

--- 2019-09-18 date/paper.tex
@@
-\documentclass[]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{amsmath}
-\usepackage[table]{xcolor}
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage{booktabs}
-\usepackage{multirow}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\begin{document}
+\section{Introduction}
 
-\title{Improving Software Maintainability through Automated Refactoring of Code Clones}
-
-\maketitle
-
-\begin{abstract}
-Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code.
-To remove such anti-patterns, the codebase should be refactored.
-Many tools aid in the detection process of such duplication problems but fail to determine whether refactoring a duplicate fragment would improve the maintainability.
-
-We address this shortcoming by first analyzing what data should be gathered from an automatically refactored system.
-We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them.
-We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system.
-Based on these results, one could decide which clones would improve system design if refactored.
-We evaluate our approach over a large corpus of open source Java projects.
-
-We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or returns data and the amount of external data that cloned fragments use.
-We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored.
-The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones with more than requiring more than one external parameter decreases maintainability.
-\end{abstract}
-
-\begin{IEEEkeywords}
-code clones, refactoring, static code analysis, object-oriented programming
-\end{IEEEkeywords}
-
-\section{Introduction}
-Duplicate fragments in source code (also named ``code clones'') are often seen as one of the most harmful types of technical debt~\cite{fowler2018refactoring}.
-Duplicate fragments create implicit dependencies that make the code harder to maintain as the resolution of erroneous behavior in one location may have to be applied to all the cloned code as well~\cite{ostberg2014automatically}.
-Apart from that, code clones can contribute up to 25\% of the code size~\cite{bruntink2005use}.
-
-Current code clone detection techniques base their thresholds and prioritization on a limited set of metrics.
-Often, clone detection techniques are limited to measuring the size of clones to determine whether they should be considered.
-Because of this, the output of clone detection tools is often of limited assistance to the developer in the refactoring process.
-
-In this study, we define a technique to detect clones such that they can be automatically refactored.
-We list a set of criteria that can obstruct refactoring opportunities.
-We evaluate the relation and location of clones to determine which refactoring techniques are best suited.
-We introduce a tool that automatically refactors clones by extracting new methods out of duplicated code.
-
-We evaluate our approach by comparing the maintainability of before- and after snapshots of a codebase for each duplication problem that is refactored.
-We define which factors have the greatest influence on whether a clone improves maintainability when refactored.
-We find a set of thresholds by which clones can be detected that are more likely to improve maintainability when refactored.
-This allows for more a accurate suggestion of code clones for refactoring and can assist in the refactoring process.
-
-\section{Background}
-Our study lies at the intersection of code clone and refactoring research. We use two concepts to argue about code clones~\cite{roy2007survey}:
-\\ \textbf{Clone instance}: A single cloned fragment.
-\\ \textbf{Clone class}: A set of similar clone instances.
-
-The most common technique for refactoring clones is ``Extract Method''~\cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
-Applying this technique entails moving functionality in the body of a method to a new method.
-To reduce duplication with this technique, we extract the contents of a single clone instance to a new method and replace all clone instances in a clone class by a call to this method.
-
-\section{Related Work}
-The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
-The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems.
-This tool is based on several studies that look into different aspects of code clone refactoring.
-In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how does variability between cloned fragments influence the refactoring techniques required and their implications on system design.
-Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability.
-This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.
-
-A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process.
-The main focus is to find out which clones \textbf{can} be refactored.
-We extend this work by looking into which clones \textbf{should} be refactored.
-We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design.
-We measure which clones improve maintainability when refactored.
-This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
-
-\section{Defining refactorable clones}
-In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}.
-We discuss how we can define clones such that they can be automatically refactored without side effects on the source code.
-
-\subsection{Ensuring Equality}\label{sec:t1r}
-Most modern clone detection tools detect duplication by comparing the code textually together with the omission of certain tokens~\cite{roy2009comparison, svajlenko2014evaluating}.
-Clones detected by such means may not always be suitable for refactoring, because textual comparison fails to take into account the context of certain symbols in the code.
-Information that gets lost in textual comparison is the referenced declaration for type, variable and method references.
-Equally named type, variable and method references may refer to different declarations with a different implementation (Fig~\ref{fig:type1} shows an example of this).
-Such clones can be harder to refactor, if beneficial at all.
-
-To detect automatically refactorable clones, we propose to:
-\begin{itemize}
-  \item Compare variable references not only by their name but also by their type.
-  \item Compare referenced types by their fully qualified identifier (FQI). The FQI of a type reference describes the full path to where it is declared.
-  \item Compare method references by their fully qualified signature (FQS). The FQS of a method reference describes the full path to where it is declared, plus the FQI of each of its parameters.
-\end{itemize}
-
-\subsection{Allowing variability in a controlled set of expressions} \label{sec:t2r}
-Often, duplication fragments in source code do not match exactly~\cite{kodhai2013method}.
-When developers duplicate fragments of code, they modify the duplicated block to fit its new location and purpose.
-To detect duplicate fragments with minor variance, we look into what expressions we can allow variability in, while still being refactorable.
-
-We define the following expressions as refactorable when varied:
-\begin{itemize}
-  \item \textbf{Literals}: Only if all varying literals in a clone class have the same type.
-  \item \textbf{Variables}: Only if all varying variables in a clone class have the same type.
-  \item \textbf{Method references}: Only if the return value of referenced methods match (or are not used).
-\end{itemize}
-Often when allowing such variance, trade-offs come into play~\cite{krishnan2013refactoring, krishnan2014unification}.
-For instance, variance in literals may require the introduction of a parameter to an extracted method if the ``Extract Method'' refactoring method is used, increasing the required effort to comprehend the code.
-
-\subsection{Gapped clones} \label{sec:t3r}
-Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context~\cite{roy2007survey}.
-When dealing with such a situation, there are several opportunities to refactor so-called ``gapped clones''~\cite{ueda2002detection, zhao2018automatic}.
-``Gapped clones'' are two clone instances separated by a ``gap'' of non-cloned statement(s).
-We define the following methods to refactor such clones:
-\begin{itemize}
-  \item We wrap the difference in statements in a conditionally executed block, one path for each different (group of) statement(s).
-  \item We use a lambda function to pass the difference in statements from each location of the clone~\cite{tsantalis2017clone}.
-\end{itemize}
-For both refactoring techniques, a trade-off is at play. This is because these solutions increase the complexity and volume of the source code in favor of removing a clone.
-
-\section{The CloneRefactor tool}
-To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
-We created a set of control projects to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
-
-None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CloneRefactor.
-This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
-In the following sections, we explain these steps.
-\begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/flow}
-  \caption{Simple flow diagram of CloneRefactor.}
-  \label{fig:clonerefactorflow}
-\end{figure}
-
-\subsection{Clone Detection}
-We use an AST-based method to detect clones.
-Clones are detected on a statement level: only full statements are considered as clones.
-In this process, we limit the variability between indicated expressions (see Sec.~\ref{sec:t2r}) by a threshold.
-This threshold is the percentage of different expressions against the total number of expressions in the source code:
-\begin{equation}\label{eq:type2r}
-\text{Variability}=\frac{\text{Different expressions}}{\text{Total expressions}}*100
-\end{equation}
-
-After all clones have been detected, CloneRefactor determines whether clone classes can be merged into gapped clones (see Sec.~\ref{sec:t3r}).
-The maximum size of the gap is limited by a threshold.
-This threshold is the percentage of (not-cloned) statements in the gap against the sum of statements in both clones surrounding it.
-Unlike the expression variability threshold, this threshold can exceed 100\%:
-\begin{equation}\label{eq:type3r}
-\text{Gap Size}=\frac{\text{Statements in gap}}{\text{Statements in clones}}*100
-\end{equation}
-
-To verify the correctness of all detected clones, we ran the tool over a large project and manually checked the output.
-We also created a set of control projects to test the correctness for many edge cases.
-
-\subsection{Context Mapping} \label{sec:context}
-After clones are detected, we map the context of these clones.
-We have identified three properties of clones as their context: relation and location.
-We identify categories for each of these properties, to get a detailed insight into the context of clones.
-
-\subsubsection{Relation}\label{sec:relation}
-Clone instances in a clone class may have a relation with each other through inheritance.
-This relation has a big impact on how the clone should be refactored~\cite{fontana2015duplicated}.
-We define the following categories to map the relation between clone instances in a clone class.
-These categories do not map external classes (classes outside the project, e.g.
-belonging to a library) unless explicitly stated:
-\begin{itemize}
-    \item \textbf{Common Class}: All clone instances are in the same class.
-    \begin{itemize}
-        \item \textbf{Same Method}: All clone instances are in the same method.
-        \item \textbf{Same Class}: All clone instances are in the same class.
-    \end{itemize}
-    \item \textbf{Common Hierarchy}: All clone instances are in the same inheritance hierarchy.
-    \begin{itemize}
-        \item \textbf{Superclass}: Clone instances reside in a class or its parent class.
-        \item \textbf{Sibling Class}: All clone instances reside in classes with the same parent class.
-        \item \textbf{Ancestor Class}: All clone instances reside in a class, or any of its recursive parents.
-        \item \textbf{First Cousin}: All clone instances reside in classes with the same grandparent class.
-        \item \textbf{Same Hierarchy}: All clone instances are part of the same inheritance hierarchy.
-    \end{itemize}
-    \item \textbf{Common Interface}: All clone instances are in classes that have the same interface.
-    \begin{itemize}
-        \item \textbf{Same Direct Interface}: All clone instances are in classes that have the same interface.
-        \item \textbf{Same Class}: All clone instances are in an inheritance hierarchy that contains the same interface.
-    \end{itemize}
-    \item \textbf{Unrelated}: All clone instances are in classes that have the same interface.
-    \begin{itemize}
-        \item \textbf{No Direct Superclass}: All clone instances are in classes that have the Object class as their parent.
-        \item \textbf{No Indirect Superclass}: All clone instances are in a hierarchy that contains a class that has the Object class as their parent.
-        \item \textbf{External Superclass}: All clone instances are in classes the same external class as their parent.
-        \item \textbf{Indirect External Ancestor}: All clone instances are in a hierarchy that contains a class that has an external class as their parent.
-    \end{itemize}
-\end{itemize}
-
-Based on these relations, CloneRefactor determines where to place the cloned code when refactored.
-These categories are mutually exclusive: a clone class will be flagged as the first relation in the above list that it applies to.
-The code of clones that have a \textit{Common Class} relation can be refactored by placing the cloned code in this same class.
-The code of clones with a \textit{Common Hierarchy} relation can be placed in the intersecting class in the hierarchy (the class all clone instances have in common as an ancestor).
-The code of clones with a \textit{Common Interface} relation can be placed in the intersecting interface, but in the process has to become part of the classes' public contract.
-The code of clones that are \textit{Unrelated} can be placed in a newly created place: either a utility class, a new superclass abstraction or an interface.
-
-\subsubsection{Location}\label{sec:location}
-The location of a clone instance determines what refactoring techniques can be applied to refactor such clones. We define the following categories by which we analyze the location of clones:
-\begin{enumerate}
-  \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
-  \item \textbf{Partial Method/Constructor Body:} A clone that spans (a part of) the body of a method/constructor.
-  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods.
-  \item \textbf{Only Fields:} A clone that spans only global variables.
-  \item \textbf{Other:} Anything that does not match with above-stated categories.
-\end{enumerate}
-
-\subsubsection{Full Method/Constructor/Class/Interface/Enumeration}
-The categories denote that a full declaration (method, class, etc.) often denote redundancy and are often easy to refactor: one of both declarations is redundant and should be removed.
-Clones in the ``Partial Method/Constructor'' category can often be refactored using the ``Extract Method'' refactoring technique.
-Clones consisting of \textit{Several Methods} give a strong indication that cloned classes are missing some form of abstraction, or their abstraction is used inadequately.
-Clones consisting of \textit{Only Fields} often indicate data redundancy: different classes use the same data.
-
-\subsection{Refactoring}
-CloneRefactor can refactor clones using the ``Extract Method'' refactoring technique. In this section, we show which clones we refactor and how we apply these transformations.
-
-\subsubsection{Extract Method} \label{sec:refactorability}
-Several influencing factors may obstruct the possibility to extract code to a new method:
-\begin{itemize}
-    \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
-    \item \textbf{Spans Part Of A Block}: This clone spans a part of a block statement. An example of this is shown in Fig.~\ref{fig:refactorabilitypartialblock}.
-    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Sec.~\ref{sec:location}, the ``Extract Method'' refactoring technique cannot be applied.
-    \item \textbf{Returns Multiple Values}: If a clone modifies or declares multiple pieces of data that it should return.
-    \item \textbf{Top-Level Non-Statement}: If one of the top-level AST nodes of the clone is not a statement. For instance, if a (part of) an anonymous class is cloned.
-    \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method.
-Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
-\end{itemize}
-Clones that do not fall in the \textit{Can Be Extracted} category may require additional transformations or other techniques to refactor.
-CloneRefactor only refactors the clones that \textit{Can Be Extracted}.
-
-\subsubsection{AST Transformation}
-CloneRefactor uses JavaParser~\cite{smith2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
-To refactor clones, CloneRefactor creates a new method declaration and moves all statements from a clone instance in the clone class to the new method.
-This method is placed according to the relation between the clone instances (see Sec.~\ref{sec:relation}).
-CloneRefactor analyzes the source code of the extracted method and populates it with the following properties:
-\begin{itemize}
-  \item \textbf{Parameters}: For each variable used that is not accessible from the scope of the extracted method.
-  \item \textbf{A return value}: If the method modifies or declares local data that is needed outside of its scope, or if the cloned fragments already returned data.
-  \item \textbf{Thrown exception}: If the method throws an uncaught exception that is not a \texttt{RuntimeException}.
-\end{itemize}
-CloneRefactor then removes all cloned code and replaces it with a method call to the newly created method.
-In case of a return value, CloneRefactor either assigns the call result, declares it or returns it accordingly.
-
-\subsubsection{Impact on maintainability metrics} \label{sec:metrics}
-CloneRefactor measures the impact on maintainability metrics of the refactored source code for each clone class that is refactored.
-These metrics are derived from Heitlager et al.~\cite{heitlager2007practical}.
-This paper defines a set of metrics to measure the maintainability of a system.
-For each of these metrics, risk profiles are proposed to determine the maintainability impact on the system of a whole.
-
-To determine whether the maintainability improves when refactoring a single clone, we need to measure the impact of small-grained changes.
-Because of that, we measure only a subset of the metrics~\cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
-The subset of metrics we decided to focus on are all metrics that are measured on method level (as the other metrics show a lesser impact on the maintainability for these small changes).
-These metrics are:
-\begin{itemize}
-\item \textbf{Duplication}: In Heitlager et al.~\cite{heitlager2007practical} this metric is measured by taking the amount of duplicated lines.
-We decided to use the amount of duplicated tokens part of a clone class instead, to have a stronger reflection of the impact of the refactoring by measuring a more fine-grained system property.
-\item \textbf{Volume}: The more code a system has, the more code has to be maintained.
-The paper~\cite{heitlager2007practical} measures volume as lines of code.
-As with duplication, we use the number of tokens instead.
-\item \textbf{Complexity}: Heitlager et al.~\cite{heitlager2007practical} use MCCabe complexity~\cite{mccabe1976complexity} to calculate their complexity metric.
-The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.
-\item \textbf{Method Interface Size}: The number of parameters that a method has.
-If a method has many parameters, the code may become harder to understand and it is an indication that data is not encapsulated adequately in objects~\cite{fowler2018refactoring}.
-\end{itemize}
-
-\section{Experimental setup}
-In this section, we describe the setup of our experiments.
-
-\subsection{Corpus}
-We ran all our experiments using CloneRefactor on a corpus of open source Java projects.
-This corpus is derived from the corpus of a study that uses machine learning to determine the suitability of Java projects on GitHub for data analysis purposes~\cite{githubCorpus2013}.
-
-CloneRefactor requires all libraries of the projects it analyses, to find the full paths of all referenced symbols in the source code (see Sec.~\ref{sec:t1r}).
-Because of that requirement, we decided to filter the corpus to only projects using the Maven build automation system.
-We created a set of scripts to prepare such a corpus with all dependencies included.
-
-This procedure results in 2.267 Java projects including all their dependencies.
-The projects vary in size and quality.
-The total size of all projects is 14.2M lines (11.3M when excluding whitespace) over a total of 100K Java files.
-This is an average of 6.3K lines over 44 files per project.
-The largest project in the corpus is \textit{VisAD} with 502K lines.
-
-\subsection{Tool Validation}
-We have validated the correctness of CloneRefactor through unit tests and empirical validation.
-First, we created a set of 57 control projects to verify the correctness in many (edge) cases.
-These projects contain clones for each identified relation, location, and refactorability category to see whether they get correctly identified.
-Next, we run the tool over the corpus and manually verify samples of the acquired results.
-This way, we check both the correctness of the identified clones, their context, and their proposed refactoring.
-
-We also test the correctness of the resulting code after refactoring.
-For this, we use a GitHub project named JFreeChart.
-JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor.
-
-\subsection{Minimum clone size}
-In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored.
-However, when clones are very small, they may never be able to improve maintainability.
-The detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication.
-Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones are very unlikely to improve maintainability when refactored.
-
-\subsection{Thresholds}
 Most clone detection tools can be configured using thresholds.
@@
 Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
-
-%In our experiments, we compare the maintainability scores for different thresholds.
-We use the \textit{standard error} to determine the correlation between the used threshold metric and the maintainability score.
-A low standard error shows that the threshold metric has a high influence on the maintainability score.
-This makes it more suitable to use as a threshold.
-By plotting the maintainability scores for different thresholds, we can determine which thresholds should be used to positively influence maintainability.
-
-%We define the following volume-based thresholds for clones, ordered by how often clone detection tools support such thresholds:
-%\begin{itemize}
-%\item \textbf{Number of lines}: The number of lines a single instance of the clone class spans.
-%\item \textbf{Tokens}: The number of tokens a single instance of the clone class spans.
-%\item \textbf{Number of statements}: The number of statements a single clone instance.
-Often closely reflects the number of lines, but is not dependent on coding style (number of newlines used by the programmer in statements).
-%\item \textbf{Token Volume}: The number of tokens in all clone instances in a clone class combined.
-%\end{itemize}
-
-\subsection{Calculating a maintainability score}\label{sec:metricformula}
-In this study, we use four metrics to determine maintainability (see Sec.~\ref{sec:metrics}).
-For each of these metrics, we determine their value before and after each refactored clone class, resulting in a delta metric score.
-For our experiments, we aggregate the deltas obtained for these metrics to draw a conclusion about the maintainability increase or decrease after applying a refactoring.
-We base our aggregation on the following assumptions:
-\begin{itemize}
-  \item All metrics are equal in terms of weight towards system maintenance effort.
-  \item Higher values for the metrics imply lower maintainability.
-  \item Normalizing each obtained metric delta over all deltas obtained for that metric in our dataset results in equally weighted scores.
-\end{itemize}
-We derived these assumptions from supporting evidence shown by Heitlager et al~\cite{heitlager2007practical} and Alves et al.~\cite{alves2010deriving}.
-Using the resulting aggregated maintainability score, we can argue for each refactoring whether it increases or decreases the maintainability of the system.
-
-We normalize each obtained metric delta using the ``Standard score'', which is calculated as follows:
-\begin{equation}\label{eq:scoredev}
-N_{metric} = \frac {\Delta X-\mu}{\sigma}
-\end{equation}
-Where $\Delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metric.
-This method works well for normalization of our data because as we divide by the standard deviation, outliers do not influence the resulting scores negatively.
-
-We then calculate the maintainability for a specific refactoring as follows:
-\begin{equation}\label{eq:scoreref}
-N_{duplication} + N_{complexity} + N_{volume} + N_{parameters}
-\end{equation}
-
-%% RESULTS TABLES (MOVED UP SO LATEX PLACES THEM IN THE RIGHT PLACE)
-
-\begin{table*}
-\centering
-%\resizebox{\textwidth}{!}{%
-\begin{tabular}{@{}lrrrrrr@{}}
-\toprule
-\textit{\textbf{Relation}} & \textit{\textbf{Duplication}} & \textit{\textbf{Complexity}} & \textit{\textbf{Parameters}} & \textit{\textbf{Volume}} & \textit{\textbf{\#}} & \textit{\textbf{Score}} \\ \midrule
-\textbf{Common Hierarchy} & \textbf{-66.33} & \textbf{0.73} & \textbf{1.20} & \textbf{-8.85} & \textbf{2,202} & \textbf{0.23} \\ \midrule
-\hspace{10pt} Superclass & -64.48 & 0.79 & 0.94 & -7.22 & 229 & 0.42 \\
-\hspace{10pt} Sibling & -70.07 & 0.69 & 1.28 & -10.97 & 1,722 & 0.23 \\
-\rowcolor[HTML]{FFCCC9}
-\hspace{10pt} Same Hierarchy & -44.18 & 0.95 & 0.89 & 1.54 & 87 & 0.10 \\
-\hspace{10pt} First Cousin & -42.69 & 0.89 & 0.93 & 4.86 & 144 & 0.02 \\
-\rowcolor[HTML]{FFCCC9}
-\hspace{10pt} Ancestor & -32.75 & 1.00 & 0.75 & 11.00 & 20 & -0.03 \\ \midrule
-\textbf{Common Interface} & \textbf{-47.06} & \textbf{0.83} & \textbf{1.04} & \textbf{4.50} & \textbf{1,044} & \textbf{-0.02} \\ \midrule
-\hspace{10pt} Same Indirect Interface & -37.08 & 0.93 & 0.82 & 9.96 & 487 & -0.01 \\
-\hspace{10pt} Same Direct Interface & -55.79 & 0.75 & 1.24 & -0.28 & 557 & -0.02 \\ \midrule
-\textbf{Common Class} & \textbf{-52.42} & \textbf{0.87} & \textbf{1.13} & \textbf{1.47} & \textbf{7,239} & \textbf{-0.02} \\ \midrule
-\hspace{10pt} Same Class & -51.85 & 0.86 & 1.03 & 3.36 & 4,874 & 0.04 \\
-\hspace{10pt} Same Method & -53.60 & 0.90 & 1.32 & -2.44 & 2,365 & -0.15 \\ \midrule
-\textbf{Unrelated} & \textbf{-45.86} & \textbf{0.88} & \textbf{1.08} & \textbf{9.56} & \textbf{2,198} & \textbf{-0.15} \\ \midrule
-\hspace{10pt} No Direct Superclass & -52.24 & 0.84 & 1.12 & 6.04 & 811 & -0.06 \\
-\hspace{10pt} External Superclass & -47.09 & 0.87 & 1.13 & 8.77 & 697 & -0.17 \\
-\hspace{10pt} External Ancestor & -35.73 & 0.93 & 0.95 & 14.58 & 586 & -0.21 \\
-\hspace{10pt} No Indirect Superclass & -44.89 & 0.84 & 1.18 & 14.08 & 104 & -0.30 \\ \midrule
-\textbf{Grand Total} & \textbf{-53.26} & \textbf{0.84} & \textbf{1.12} & \textbf{1.33} & \textbf{12,683} & \textbf{0.00} \\ \bottomrule
-\end{tabular}%
-%}
-\caption{Influence on maintainability of refactoring clones with the specified relation categories.}
-\label{tab:relation_refactor}
-\end{table*}
-
-%% END TABLES
-
-\section{Results}
-In this section, we share the results of our experiments.
-
-\subsection{Clone context}
-To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones (see Sec.~\ref{sec:context}).
-
-\subsubsection{Relation}
-We tested to what extent the relation between clone instances in a clone class (see Sec.~\ref{sec:relation}) has an influence on the maintainability of refactored clones.
-
-Our results show that most clones (37\%) are in a common class. 24\% of clones are in a common hierarchy. Another 24\% of clones are unrelated. 15\% of clones are in an interface.
-
-\subsubsection{Location}
-Table~\ref{tab:location} displays the number of clone classes found for the entire corpus for different locations (see Sec.~\ref{sec:location}).
-
-\begin{table}[H]
-\centering
-\begin{tabular}{@{}llrr@{}}
-\toprule
-\textit{\textbf{Category}} & \textit{\textbf{Location}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
-\multirow{2}{*}{Partial} & Partial Method & 219,540 & \multirow{2}{*}{229,521} \\ \cmidrule(lr){2-3}
- & Partial Constructor & 9,981 &  \\ \midrule
-\multirow{5}{*}{Full} & Full Method & 12,990 & \multirow{5}{*}{13,173} \\ \cmidrule(lr){2-3}
- & Full Interface & 64 &  \\ \cmidrule(lr){2-3}
- & Full Constructor & 58 &  \\ \cmidrule(lr){2-3}
- & Full Class & 37 &  \\ \cmidrule(lr){2-3}
- & Full Enum & 24 &  \\ \midrule
-\multirow{3}{*}{Other} & Several Methods & 22,749 & \multirow{3}{*}{53,773} \\ \cmidrule(lr){2-3}
- & Only Fields & 17,700 &  \\ \cmidrule(lr){2-3}
- & Other & 13,324 &  \\ \bottomrule
-\end{tabular}
-\caption{Number of clone instances for clone location categories}
-\label{tab:location}
-\end{table}
-
-From these results, we see that 74\% of clones span part of a method body (77\% if we include constructors).
-8\% of clones span several methods.
-6\% of clones span only global variables.
-Only 4\% of clones span a full declaration (method, class, constructor, etc.).
-
-\subsection{Refactorability}
-Table~\ref{tab:refactorability} shows to what extent clone classes can be refactored by using the ``Extract Method'' refactoring technique (see Sec.~\ref{sec:refactorability}).
-
-\begin{table}[H]
-\centering
-\begin{tabular}{@{}lrr@{}}
-\toprule
-\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{\%}} \\ \midrule
-Can Be Extracted & 24,157 & 28.2\%  \\
-Is Not A Partial Method & 21,625 & 25.3\% \\
-Top-level AST-Node is not a Statement & 19,887 & 23.2\% \\
-Spans Part of a Block & 13,181 & 15.5\%  \\
-Multiple Return Values & 5,622 & 6.6\%  \\
-Complex Control Flow & 1,106 & 1.3\% \\
-\end{tabular}
-\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique.}
-\label{tab:refactorability}
-\end{table}
-
-These results indicate that, given our refactorability criteria, 28\% of clones can be automatically refactored.
-Clones in other categories may require other refactoring techniques or further transformations to be automatically refactorable.
-
-\subsection{Thresholds}
-In our corpus, CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Sec.~\ref{sec:metrics}).
-Using the presented formulas (see Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method influence the maintainability of the resulting codebase after refactoring.
-In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.
-Using this data, we find supporting evidence regarding which thresholds are most likely to find clones that should be refactored to improve maintainability.
-
-\subsubsection{Clone Token Volume}
-TODO shows the obtained results when plotting the clone volume vs the average delta maintainability score.
-We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class.
-For higher token volume numbers we have fewer refactorings that refactor such clones, because of which we represent the x-axis as a logarithmic scale.
-The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.
-
-\subsubsection{Relation}
-Table~\ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability.
-We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance.
-
-The displayed relations are ordered by their scores.
-Overall, the scores do not deviate much (-0.15 to 0.23), indicating that the relation between clones has a minor impact on maintainability.
-Overall, we see that common hierarchy clones have the highest maintainability, whereas unrelated clones have the lowest maintainability.
-
-\subsubsection{Parameters}
-TODO shows how an increase in parameters lowers the maintainability of the refactored code.
-On the primary x-axis, the maintainability is displayed.
-The secondary x-axis shows the number of refactorings.
-The y-axis shows the number of parameters.
-
-\section{Discussion}
-%In this section, we discuss the results of our experiments.
-
-\subsection{Clone Context}
-Regarding clone context, our results indicate that most clones (37\%) are in a common class.
-This is favorable for refactoring because the extracted method does not have to be moved after extraction.
-24\% of clones are in a common hierarchy.
-These refactorings are also often favorable.
-Another 24\% of clones are unrelated, which is often unfavorable because it often requires a more comprehensive refactoring.
-15\% of clones are in an interface.
-
-Regarding clone locations, 74\% of clones span part of a method body (77\% if we include constructors).
-8\% of clones span several methods, which often require refactorings on a more architectural level.
-6\% of clones span only global variables, requiring an abstraction to encapsulate these data declarations.
-Only 4\% of clones span a full declaration (method, class, constructor, etc.).
-
-\subsection{Extract Method}
-28\% of clones can be refactored using the ``Extract Method'' refactoring technique (50\% if we limit our searching scope to method bodies).
-About 25\% of clones do not span part of a method, because of which they cannot be refactored.
-Many clones (23\%) do not have a statement as top-level AST-Node.
-Upon manual inspection, we noticed that the main reason for this is when clones are found in lambda functions or anonymous classes.
-About 15\% of clones span only part of an AST-Node.
-
-\subsection{Refactoring}
-In Fig.~\ref{fig:maintainabilityscore} we see an increase in maintainability for refactoring larger clone classes.
-The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie around a token volume of 63 tokens.
-There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.
-
-In Table~\ref{tab:relation_refactor} we see the results regarding refactorings that are applied to clones with diverse relations.
-We see that most refactored clones are in a common class, over 54\%.
-This is significantly more than the percentage of clones in the common class relation as reported in Table~\ref{tab:relation}.
-Meanwhile, the number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% -> 18\%).
-The main reason for this is that refactoring unrelated clones can change the relation of other clones in the same system.
-If we create a superclass abstraction to refactor an unrelated clone, other clones in those classes that were previously unrelated might become related.
-
-The maintainability scores displayed in Table~\ref{tab:relation_refactor} show that the most favorable clones to refactor are clones with a Sibling relation.
-The most unfavorable is to refactor clones to interfaces.
-However, the differences in maintainability in this table are generally small; according to our data relations have only a minor impact on the maintainability of clones.
-
-Regarding the return type of refactored clones, we see in Table~\ref{tab:return} that this has no major impact on maintainability.
-A method call to the extracted method that is directly returned and no return type extracted methods are slightly more favorable than the others.
-We think the main reason that the ``Return'' category is on top is that when a variable is declared at the end of the cloned fragment, CloneRefactor directly returns its value and removes the declaration.
-This decreases the volume slightly.
-
-A higher number of parameters directly influences the corresponding metric.
-Because of this, we see in Fig.~\ref{fig:arguments} that more parameters negatively influence maintainability.
-Not only the number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
-Because of that, we see that the trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.
-
-\section{Conclusion}
-We defined automatically refactorable clones and created a tool to detect and refactor them.
-We measured statistical data with this tool over a large corpus of open-source Java software systems to get more information about the context of clones and how refactoring them influences system maintainability.
-
-We defined two aspects as part of the context of a clone: relation and location.
-Regarding relations, over 37\% of clones are found in the same class.
-About 24\% of clones are in the same inheritance hierarchy.
-Another 24\% of clones are unrelated.
-The final 15\% of clones have the same interface.
-Regarding location, over 74\% of clones span part of a method.
-About 8\% span several methods.
-Only 4\% of clones span a declaration (method, class, etc.) fully.
-
-We built a tool that can automatically apply refactorings to 28\% of the clones in our corpus using the ``Extract Method'' refactoring technique.
-The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, e.g., when code outside a method is part of a clone.
-
-We measured four maintainability metrics before- and after applying each refactoring to determine the impact of each refactoring on system maintainability.
-We found that the most prominent factor influencing maintainability is the size of the clone.
-We found that the threshold lies at a clone volume of 29 tokens per clone instance for system maintainability to increase after refactoring the clone.
-Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data.
-We noticed that the inheritance relation of the clone and the return value of the extracted method has only a minor impact on system maintainability.
-
-\bibliographystyle{IEEEtran}
-\bibliography{references}
-
-\end{document}

### 2019-11-06 benevol/main.tex
Added benevol stuff

\documentclass[twocolumn,showpacs,%
  nofootinbib,aps,superscriptaddress,%
  eqsecnum,prd,notitlepage,showkeys,10pt]{article}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{hyperref}
\usepackage{float}

\begin{document}

\title{Statement-level AST-based Clone Detection in Java using Resolved Symbols}
\author{Simon Baars, Ana Oprescu}
%\affiliation{University of Amsterdam}

\maketitle

\begin{abstract}
Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code. Detecting such problems can provide valuable insight into the quality of systems and help to improve the source code. To correctly identify cloned code, contextual information should be considered, such as the type of variables and called methods.

Comparing code fragments including their contextual information introduces an optimization problem, as contextual information may be hard to retrieve. It can be ambiguous where contextual information resides and tracking it down may require to follow cross-file references. For large codebases, this can require a lot of time due to the sheer number of referenced symbols.

We propose a method to efficiently detect clones taking into account contextual information. To do this, we propose a tool that uses an AST-parsing library named JavaParser to detect clones a retrieve contextual information. Our method first parses the AST retrieved from JavaParser into a graph structure, which is then used to find clones. This graph maps the following relations for each statement in the codebase: the next statement, the previous statement, and the previous cloned statement.
\end{abstract}

\maketitle

\input{introduction}

\input{case}

\input{approaches}

\input{comparison}

\input{analysis}

\input{conclusion}

\bibliographystyle{plain}
\bibliography{references}

\end{document}

### 2019-11-06 benevol/main.tex
Updates from Overleaf

@@
 \author{Simon Baars, Ana Oprescu}
-%\affiliation{University of Amsterdam}
+\affiliation{University of Amsterdam}
 
@@
 
-\input{introduction}
+\section{Introduction}
+Most clone detection tools can be configured using thresholds.
+These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones.
+Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}.
+Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
 
-\input{case}
-
-\input{approaches}
-
-\input{comparison}
-
-\input{analysis}
-
-\input{conclusion}
+\section{Conclusion}
 

### 2019-11-06 benevol/main.tex
Updates from Overleaf

--- 2019-11-06 benevol/main.tex
@@
 
-\input{introduction}
+\section{Introduction}
+%Most clone detection tools can be configured using thresholds.
+These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones.
+Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}.
+Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
+Duplicate code fragments are often considered as symptoms of bad design~\cite{fowler2018refactoring}.
+They create implicit dependencies, thus increasing maintenance efforts or causing bugs in evolving software.
+Changing one occurrence of such a duplicated fragment may require other occurrences to be changed as well~\cite{ostberg2014automatically}.
+Also, duplicated code has been shown to add up to 25\% of total system volume~\cite{bruntink2005use}, which entails more code to be maintained.
 
-\input{case}
+A lot of tools have been proposed to detect such duplication issues \cite{roy2009comparison, svajlenko2014evaluating, sheneamer2016survey}.
+These tools can find matching fragments of code, but do not take into account contextual information of code.
+An example of such contextual information is the name of used variables: many different methods with the same name can exist in a codebase.
+This can obstruct refactoring opportunities.
 
-\input{approaches}
+We describe a method to detect clones while taking into account such contextual information. Our experiments show us that
 
-\input{comparison}
+\section{JavaParser}
+An important design decision for CloneRefactor is the usage of a library named JavaParser~\cite{tomassetti2017javaparser}.
+JavaParser is a Java library which allows parsing Java source files to an abstract syntax tree (AST).
+JavaParser allows to modify this AST and write the result back to Java source code.
+This allows us to apply refactorings to the detected problems in the source code.
 
-\input{analysis}
+Integrated into JavaParser is a library named SymbolSolver.
+This library allows for the resolution of symbols using JavaParser.
+For instance, we can use it to trace references (methods, variables, types, etc) to their declarations (these referenced identifiers are also called ``symbols'').
+This is useful for the detection of our refactoring-oriented clone types, as they make use of the fully qualified identifiers of symbols.
 
-\input{conclusion}
+To be able to trace referenced identifiers, SymbolSolver requires access to not only the analyzed Java project but also all its dependencies.
+This requires us to include all dependencies with the project.
+Along with this, SymbolSolver solves symbols in the JRE System Library (the standard libraries coming with every installation of Java) using the active Java Virtual Machine (JVM).
+This has a big impact on performance efficiency.
+This is visible in our results, as displayed in Section~\ref{sec:clonetypeexperiments}.
+
+\section{Conclusion}
 

### 2019-11-06 benevol/paper.tex
stuff
Set format

--- 2019-11-06 benevol/main.tex
@@
-\documentclass[twocolumn,showpacs,%
-  nofootinbib,aps,superscriptaddress,%
-  eqsecnum,prd,notitlepage,showkeys,10pt]{article}
+\documentclass[conference]{IEEEtran}
 
@@
 \title{Statement-level AST-based Clone Detection in Java using Resolved Symbols}
-\author{Simon Baars, Ana Oprescu}
-\affiliation{University of Amsterdam}
+\author{\IEEEauthorblockN{1\textsuperscript{st} Simon Baars}
+\IEEEauthorblockA{\textit{University of Amsterdam}\\
+Amsterdam, the Netherlands \\
+simon.mailadres@gmail.com}
+%\affiliation{University of Amsterdam}
 
@@
 
-\maketitle
+\begin{IEEEkeywords}
+clone detection, context, java, parsing, static code analysis
+\end{IEEEkeywords}
 
@@
 Along with this, SymbolSolver solves symbols in the JRE System Library (the standard libraries coming with every installation of Java) using the active Java Virtual Machine (JVM).
-This has a big impact on performance efficiency.
+%This has a big impact on performance efficiency.
 This is visible in our results, as displayed in Section~\ref{sec:clonetypeexperiments}.
@@
 
-\bibliographystyle{plain}
+%\bibliographystyle{plain}
 \bibliography{references}

### 2019-11-06 benevol/paper.tex
Fixed it
It's Frankensteins monster

@@
 \usepackage{dcolumn}
+
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage[table]{xcolor}
+
+\usepackage{booktabs}
+\usepackage{multirow}
+\usepackage{parcolumns}
+
+\usepackage{todonotes}
+
 \usepackage{hyperref}
 \usepackage{float}
+\usepackage{parcolumns}
+
+\usepackage{listings}
+\lstset{language=Java,
+  showspaces=false,
+  showtabs=false,
+  breaklines=true,
+  showstringspaces=false,
+  breakatwhitespace=true,
+  commentstyle=\color{pgreen},
+  keywordstyle=\color{pblue},
+  numbers = left,
+  stringstyle=\color{pred},
+  basicstyle=\ttfamily,
+%  moredelim=[il][\textcolor{pgrey}]{$$}
+  moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%}
+}
+
+\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
+
+\definecolor{pblue}{rgb}{0.13,0.13,1}
+\definecolor{pgreen}{rgb}{0,0.5,0}
+\definecolor{pred}{rgb}{0.9,0,0}
+\definecolor{pgrey}{rgb}{0.46,0.45,0.48}
+
+\definecolor{lightyellow}{HTML}{fffdcc}
+\definecolor{doublelightyellow}{HTML}{fffa9c}
+\definecolor{lightgreen}{HTML}{dcffd4}
+\definecolor{lightblue}{HTML}{e0ffff}
+\definecolor{lightred}{HTML}{ffe0e0}
+\definecolor{lightpink}{HTML}{ffe0ff}
+\definecolor{lightorange}{HTML}{ffede0}
+\definecolor{lightpurple}{HTML}{f0e0ff}
+\newcommand{\highlightYellow}{\makebox[0pt][l]{\color{lightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightGreen}{\makebox[0pt][l]{\color{lightgreen}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightBlue}{\makebox[0pt][l]{\color{lightblue}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightRed}{\makebox[0pt][l]{\color{lightred}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightPink}{\makebox[0pt][l]{\color{lightpink}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightOrange}{\makebox[0pt][l]{\color{lightorange}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightPurple}{\makebox[0pt][l]{\color{lightpurple}\rule[-4pt]{1\linewidth}{14pt}}}
+\newcommand{\highlightDarkyellow}{\makebox[0pt][l]{\color{doublelightyellow}\rule[-4pt]{1\linewidth}{14pt}}}
+
+\lstnewenvironment{javacode}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small,#1}}{}
 
@@
 simon.mailadres@gmail.com}
+}
 %\affiliation{University of Amsterdam}
@@
 \maketitle
+
+\thispagestyle{plain}
+\pagestyle{plain}
 
@@
 
-We describe a method to detect clones while taking into account such contextual information. Our experiments show us that
+We describe a method to detect clones while taking into account such contextual information and propose a tool to detect clones taking into account this contextual information.
+Run this tool over a corpus of 2,267 Java projects.
+We find that taking into account contextual information results in 11\% less clones than found when not taking this information into account.
+Manually inspecting a sample the difference, we find that all clones with different contextual information in our sample are less relevant for refactoring.
+
+\section{Background}
+We use two concepts to argue about code clones~\cite{roy2007survey}:
+\\ \textbf{Clone instance}: A single cloned fragment.
+\\ \textbf{Clone class}: A set of similar clone instances.
+
+%\subsection{Clone Types}
+Duplication in code is found in many different forms.
+Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}.
+Sometimes this code is then adapted to fit the new context.
+To reason about these modifications, several clone types have been proposed%.
+These clone types are described in Roy et al
+~\cite{roy2007survey}:\\
+\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout), and comments.\\
+\textbf{Type II:} Structurally/syntactically identical fragments except variations in identifiers, literals, types, layout, and comments.\\
+\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed next to variations in identifiers, literals, types, layout, and comments.
+A higher type of clone means that it is harder to detect and refactor.
+Many studies adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
+
+\section{Motivating example}
+\begin{figure*}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+package com.sb.game;
+
+import java.util.List;
+
+public class GameScene
+{
+|\highlightYellow|	public void addToList(List l) {
+|\highlightYellow|		l.add(getClass().getName());
+|\highlightYellow|	}
+
+	public void addTen(int x) {
+|\highlightYellow|		x = x + 10; // add number
+|\highlightYellow|		Notifier.notifyChanged(x);
+|\highlightYellow|		return x;
+	}
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+package com.sb.fruitgame;
+
+import java.awt.List;
+
+public class LoseScene
+{
+|\highlightYellow|	public void addToList(List l) {
+|\highlightYellow|		l.add(getClass().getName());
+|\highlightYellow|	}
+
+	public void concatTen(String x) {
+|\highlightYellow|		x = x + 10; // concat string
+|\highlightYellow|		Notifier.notifyChanged(x);
+|\highlightYellow|		return x;
+	}
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Example of a type 1 clone that is functionally different.}
+\label{fig:type1}
+\end{figure*}
+
+Most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating} detect type 1 clones by textually comparing code fragments (except for whitespace and comments).
+Although textually equal, method, type and variable references can still refer to different declarations.
+In such cases, refactoring opportunities could be invalidated.
+This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
+
+Figure~\ref{fig:type1} shows a type 1 clone with two clone classes.
+Defining an automatic way to refactor these clone classes is nearly impossible, as both cloned fragments describe different functional behavior.
+The first cloned fragment is a method that adds something to a \texttt{List}.
+However, the \texttt{List} objects to which something is added are different.
+Looking at the \texttt{import} statement above the class, one fragment uses the \texttt{java.util.List} and the other uses the \texttt{java.awt.List}.
+Both happen to have an \texttt{add} method, but apart from that their implementation is completely different.
+
+The second cloned fragment shows how equally named variables can have different types and thus perform different functional concepts.
+The cloned fragment on the left adds a specific amount to an integer.
+The cloned fragment on the right concatenates a number to a String.
+
+This shows that not all type 1 clones can easily be automatically refactored.
+In section \label{chap:type1rclones} we describe an alternative approach towards detecting type 1 clones, which results in only clones that can be refactored.
 
@@
 
-%\bibliographystyle{plain}
+\bibliographystyle{plain}
 \bibliography{references}

### 2019-11-06 benevol/paper.tex
Stuff again

@@
 \end{parcolumns}
-\caption{Example of a type 1 clone that is functionally different.}
+\caption{Example of a clone that, although textually equal, is contextually different.}
 \label{fig:type1}
@@
 
-Most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating} detect type 1 clones by textually comparing code fragments (except for whitespace and comments).
+Most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating} detect clones by textually comparing code fragments (except for whitespace and comments).
 Although textually equal, method, type and variable references can still refer to different declarations.
 In such cases, refactoring opportunities could be invalidated.
-This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
+This can make clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
 
-Figure~\ref{fig:type1} shows a type 1 clone with two clone classes.
-Defining an automatic way to refactor these clone classes is nearly impossible, as both cloned fragments describe different functional behavior.
+Figure~\ref{fig:type1} shows two clone classes.
+Merging these clone classes is very hard (and likely not desirable), as both cloned fragments describe different functional behavior.
 The first cloned fragment is a method that adds something to a \texttt{List}.
@@
 
-This shows that not all type 1 clones can easily be automatically refactored.
-In section \label{chap:type1rclones} we describe an alternative approach towards detecting type 1 clones, which results in only clones that can be refactored.
+This shows that not all textually equal clones can easily be refactored.
+
+\section{CloneRefactor}
+We develop a tool named CloneRefactor\footnote{CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}} that detects clones that can (relatively) easily be refactored.
+This tool uses JavaParser~\cite{tomassetti2017javaparser} to
 

### 2019-11-06 benevol/paper.tex
Updates from Overleaf

@@
 We develop a tool named CloneRefactor\footnote{CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}} that detects clones that can (relatively) easily be refactored.
-This tool uses JavaParser~\cite{tomassetti2017javaparser} to
+This tool uses JavaParser~\cite{tomassetti2017javaparser} to build an AST and to find contextual information (e.g.
+resolve symbols).
+We then propose a novel clone detection technique to detect clones using JavaParser.
 
 \section{JavaParser}
-An important design decision for CloneRefactor is the usage of a library named JavaParser~\cite{tomassetti2017javaparser}.
-JavaParser is a Java library which allows parsing Java source files to an abstract syntax tree (AST).
+JavaParser~\cite{tomassetti2017javaparser} is a Java library which allows parsing Java source files to an abstract syntax tree (AST).
 JavaParser allows to modify this AST and write the result back to Java source code.
-This allows us to apply refactorings to the detected problems in the source code.
+The ultimate goal is to use this to be able to apply automated refactorings.
 
@@
 For instance, we can use it to trace references (methods, variables, types, etc) to their declarations (these referenced identifiers are also called ``symbols'').
-This is useful for the detection of our refactoring-oriented clone types, as they make use of the fully qualified identifiers of symbols.
+Using this, we can find the required contextual information.
 
@@
 
+\section{Clone Detection}\label{sec:clonedetection}
+To detect clones, CloneRefactor parses the AST acquired from JavaParser to a graph structure.
+Based on this graph structure, clones are detected.
+Dependent on the type of clones being detected, transformations may be applied.
+How CloneRefactor was designed does not allow for several clone types to be detected simultaneously.
+The overall process regarding clone detection is displayed in Figure~\ref{fig:clonedetection}.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{img/CloneDetection}
+  \caption{CloneRefactor clone detection process.}
+  \label{fig:clonedetection}
+\end{figure}
+
+First of all, CloneRefactor uses JavaParser to read a project from disk and build an AST, one class file at a time.
+Each AST is then converted to a directed graph that maps relations between statements, further explained in Section~\ref{sec:clonegraph}.
+Based on this graph, CloneRefactor detects clone classes and verifies them using the configured thresholds.
+If the detection was configured to detect either type 2R, 3, or 3R clones, CloneRefactor perform some type-specific transformations on the resulting set of clones.
+%\begin{itemize}
+%  \item Amount of tokens.
+%  \item Amount of statements.
+%  \item Amount of lines.
+%\end{itemize}
+
+\subsection{Generating the clone graph}\label{sec:clonegraph}
+First of all, CloneRefactor parses the AST obtained from JavaParser into a directed graph structure.
+We have chosen to base our clone detection around statements as the smallest unit of comparison.
+This means that a single statement cloned with another single statement is the smallest clone we can find.
+The rationale for this lies in both simplicity and performance efficiency.
+This means we won't be able to find when a single expression matches another expression, or even a single token matching another token.
+This is in most cases not a problem, as expressions are often small and do not span the minimal size to be considered a clone in the first place.
+
+\subsubsection{Filtering the AST}
+As a first step towards building the clone graph, we preprocess the AST to decide which AST nodes should become part of the clone graph.
+We exclude package declarations and import statements from this graph.
+These are omitted by most clone detection tools, as package declarations and import statements are most often generated by the IDE.
+
+\subsubsection{Building the clone graph}\label{sec:buildingclonegraph}
+Building the clone graph consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
+\begin{itemize}
+  \item The declaration/statement preceding it.
+  \item The declaration/statement following it.
+  \item The last \textbf{preceding} declaration/statement with which it is cloned.
+\end{itemize}
+We do not create a separate graph for each class file, so the statement/declaration preceding or following could be in a different file.
+While mapping these relations, we maintain a hashed map containing the last occurrence of each unique statement.
+This map is used to efficiently find out whether a statement is cloned with another.
+An example of such a graph is displayed in Figure~\ref{fig:clonegraphsimple}.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{img/CodeGraph2}
+  \caption{Abstract example of a part of a possible clone graph as built by CloneRefactor.}
+  \label{fig:clonegraphsimple}
+\end{figure}
+
+The relations \textit{next} and \textit{previous} in this graph are represented as a bidirectional arrow.
+The relations representing duplication are directed.
+%This is a restriction we've chosen as it creates an important constraint for the clone detection process.
+This process is explained in Section~\ref{sec:detectingclones}.
+
+\subsubsection{Comparing Statements/Declarations} \label{sec:comparingstuff}
+In the previous section, we described a ``duplicate'' relation between nodes in the clone graph built by CloneRefactor.
+Whether two nodes in this graph are duplicates of each other is dependent on the clone type.
+In this section, we will describe for each type how we compare statements and declarations to assess whether they are clones of each other.
+
+CloneRefactor detects six different types of clones: T1, T2, T3, T1R, T2R, and T3R.
+These types are further explained in chapter \ref{chap:clonetypes}.
+For \textbf{type 1} clones, CloneRefactor filters the tokens of a node to exclude its comments, whitespace, and end of line (EOL) characters and then compares these tokens.
+For \textbf{type 2} clones, the tokens are further filtered to omit all identifiers and literals.
+\textbf{Type 3} clones do the same duplication comparison as type 2 clones.
+
+For \textbf{type 1R} clones this comparison is more advanced.
+For \textit{method calls} we determine their fully qualified method signature for comparison with other nodes.
+For all \textit{referenced types} we use their fully qualified identifier (FQI) for comparison with other nodes.
+For \textit{variables} we compare their fully qualified type in addition to their name.
+
+\textbf{Type 2R} clones allow any variation in literals, variables, and method calls at this stage in the clone detection process.
+We compare \textit{variables} by the FQI of their types but not their names.
+For \textit{method calls}, we compare the FQI of their return type and the type of each of their parameters.
+Apart from that, we do not compare the names of type declarations.
+\textbf{Type 3R} clones have the same compare rules as type 2R clones.
+
+\subsubsection{Mapping graph nodes to code}
+The clone graph, as explained in Section~\ref{sec:buildingclonegraph}, contains all declarations and statements of a software project.
+However, declarations and statements may themselves have child declarations and statements.
+To avoid redundant duplication checks, we exclude the body of each node.
+Look at Figure~\ref{fig:clonegraph} for an example of how source code maps to AST nodes.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{img/CloneGraphCode}
+  \caption{CloneRefactor extracts statements and declarations from source code.}
+  \label{fig:clonegraph}
+\end{figure}
+
+On line 24-25 of the code fragment, we see a \texttt{MethodDeclaration}.
+The node corresponding with this MethodDeclaration denotes all tokens found on these two lines, line 24 and 25.
+Although the statements following this method declaration (those that are part of its body) officially belong to the method declaration, they are not included in its graph node.
+Because of that, in this example, the \texttt{MethodDeclaration} on line 24-25 will be considered a clone of the \texttt{MethodDeclaration} on line 205 even though their bodies might differ.
+Even the range (the line and column that this node spans) does not include its child statements and declarations.
+
+\subsection{Detecting Clones} \label{sec:detectingclones}
+After building the clone graph, we use it to detect clone classes.
+We start our clone detection process at the final location encountered while building the graph.
+As an example, we convert the code example shown in Figure~\ref{fig:clonegraph} to a clone graph as displayed in Figure~\ref{fig:clonegraph2}.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{img/CodeGraphExample}
+  \caption{Example of a clone graph built by CloneRefactor.}
+  \label{fig:clonegraph2}
+\end{figure}
+
+Using the example shown in Figure~\ref{fig:clonegraph} and \ref{fig:clonegraph2} we can explain how we detect clones on the basis of this graph.
+Suppose we are finding clones for two files and the final node of the second file is a variable declarator.
+This node is represented in the example figure by the purple box (1).
+We then follow all ``duplicate'' relations until we have found all clones of this node (2 and 3).
+We now have a clone class of three clone instances each with a single node (1, 2 and 3).
+
+Next, we move to the \textit{previous} line (4).
+Here again, we collect all duplicates of this node (4 and 5).
+For each of these duplicates, we check whether the node following it is already in the clone class we collected in the previous iteration.
+In this case, (2) follows (5) and (1) follows (4).
+This means that node (3) does not form a `chain' with other cloned statements.
+Because of this, the clone class of (1, 2 and 3) comes to an end.
+It will be checked against the thresholds, and if adhering to the thresholds, considered a clone.
+
+We then go further to the previous node (6).
+In this case, this node does not have any clones.
+This means we check the (2 and 5, 1 and 4) clone class against the thresholds, and, if it adheres, consider it a clone.
+Dependent on the thresholds, this example can result in a total of two clone classes.
+
+Eventually, following only the ``previous node'' relations, we can get from (6) to (2).
+When we are at that point, we will find only one cloned node for (2), namely (3).
+However, after we check this clone against the thresholds, we check whether it is a subset of any existing clone.
+If this is the case (which it is for this example), we discard the clone.
+
+\subsubsection{Removing redundant clone classes}\label{sec:conceptualremovingredundant}
+The clone detection method used by CloneRefactor can, for various reasons, result in redundant clone classes.
+After the insertion of each newly detected clone, we check whether it is redundant and/or any of the existent clones has become redundant by adding this clone.
+A clone is redundant if it is a subset of another clone.
+We define the subset relation between clones as follows:
+
+\begin{equation}\label{eq:subset}
+C_1 \subseteq C_2 := \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
+\end{equation} % Right symbol for definition
+
+Where \textit{C} refers to a clone class (a set of clone instances), \textit{i} refers to a clone instance, \textit{F} is the file in which a clone instance is located and \textit{R} is the range of tokens that a clone instance spans.
+For each clone found, we remove all existing clones that are a subset of the found clone:
+
+\begin{equation}\label{eq:removeall}
+S_{after} = S_{before} \setminus \{C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S_{before}\}
+\end{equation}
+
+Where \textit{$S_{before}$} is the clone class collection containing all clones that are found up in until this point, \textit{$C_{new}$} is the clone class that was just found and \textit{$S_{after}$} is the clone class collection after removing all subsets of the added clone.
+
+We should not add the new clone to our list of clones if its a subset of an existing clone.
+Because of that, we check for each clone added whether there exists a clone class of which the found clone class is a subset:
+
+\begin{equation}\label{eq:removeexisting}
+\{C_{new} \subseteq C_{existing}\text{ }|\text{ }C_{existing} \in S\} = \emptyset \Rightarrow S_{after} = S \cup C_{new}
+\end{equation}
+
+Where \textit{$S_{before}$} is the clone class collection containing all clones that are found up in until this point, \textit{$C_{new}$} is the clone class that was just found and \textit{$S_{after}$} is the clone class collection after optionally adding the newly found clone.
+If the newly added clone is a subset of an existing clone, we do not add it to the set of clone classes.
+This way we avoid redundant clone classes being detected by CloneRefactor.
+
 \section{Conclusion}

### 2019-11-06 benevol/paper.tex
Updates from Overleaf

@@
 
+\definecolor{pblue}{rgb}{0.13,0.13,1}
+\definecolor{pgreen}{rgb}{0,0.5,0}
+\definecolor{pred}{rgb}{0.9,0,0}
+\definecolor{pgrey}{rgb}{0.46,0.45,0.48}
+
 \usepackage{listings}
@@
 \def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
-
-\definecolor{pblue}{rgb}{0.13,0.13,1}
-\definecolor{pgreen}{rgb}{0,0.5,0}
-\definecolor{pred}{rgb}{0.9,0,0}
-\definecolor{pgrey}{rgb}{0.46,0.45,0.48}
 
@@
 
-\section{Motivating example}
+\section{Motivating example} \label{sec:type1}
 \begin{figure*}
@@
 
-Most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating} detect clones by textually comparing code fragments (except for whitespace and comments).
+Most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating} detect type 1 clones by textually comparing code fragments (except for whitespace and comments).
 Although textually equal, method, type and variable references can still refer to different declarations.
@@
 This shows that not all textually equal clones can easily be refactored.
+
+\section{Contextual information}
+To solve the issues identified in Section~\ref{sec:type1}, we expand clone detection by taking into account contextual information: cloned fragments have to be both textually \textit{and} contextually equal.
+We check contextual equality of two fragments by validating the equality of the fully qualified identifier (FQI) for referenced types, methods and variables.
+If an identifier is fully qualified, it means we specify the full location of its declaration (e.g.
+\texttt{com.sb.fruit.Apple} for an \texttt{Apple} object).
+
+\subsection{Referenced Types}
+Many object-oriented programming languages (like Java, Python, and C\#) require the programmer to import a type (or the class in which it is declared) before it can be used.
+Based on what is imported, the meaning of the name of a type can differ.
+For instance, if we import \texttt{java.util.List}, we get the interface which is implemented by all list data structures in Java.
+However, importing \texttt{java.awt.List}, we get a listbox GUI component for the Java Abstract Window Toolkit (AWT).
+These are entirely different functional concepts.
+To be sure we compare between equal types, we compare the FQI for all referenced types.
+
+\subsubsection{Called methods}
+A codebase can have several methods with the same name.
+The implementation of these methods might differ.
+When two code fragments call methods with an identical name or signature, they can still call different methods.
+Because of this, textually identical code fragments can differ functionally.
+
+We compare the fully qualified method signature for all method references.
+A fully qualified method signature consists of the fully qualified name of the method, the fully qualified type of the method plus the fully qualified type of each of its arguments.
+For instance, an \texttt{eat} method could become \texttt{com.sb.AppleCore com.sb.fruitgame.Apple.eat(com.sb.fruitgame.Tool)}.
+
+\subsubsection{Variables}
+In typed programming languages, each variable declaration should declare a name and a type.
+When we reference a variable, we only use its name.
+If we use variables with the same name but different types in different code fragments, the code can be functionally unequal but still textually equal.
+
+The body of both methods in Figure~\ref{fig:type1} is equal.
+However, their functionality is not.
+The first method adds two numbers together and the other concatenates an integer and a String.
+Because of this, we compare cloned variable references by both their name and the FQI of their type.
 
@@
 Dependent on the type of clones being detected, transformations may be applied.
-How CloneRefactor was designed does not allow for several clone types to be detected simultaneously.
-The overall process regarding clone detection is displayed in Figure~\ref{fig:clonedetection}.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/CloneDetection}
-  \caption{CloneRefactor clone detection process.}
-  \label{fig:clonedetection}
-\end{figure}
 
 First of all, CloneRefactor uses JavaParser to read a project from disk and build an AST, one class file at a time.
-Each AST is then converted to a directed graph that maps relations between statements, further explained in Section~\ref{sec:clonegraph}.
+Each AST is then converted to a directed graph that maps relations between statements.
 Based on this graph, CloneRefactor detects clone classes and verifies them using the configured thresholds.
-If the detection was configured to detect either type 2R, 3, or 3R clones, CloneRefactor perform some type-specific transformations on the resulting set of clones.
+This process is explained in further detail over the following sections.
 %\begin{itemize}
@@
 \subsection{Generating the clone graph}\label{sec:clonegraph}
-First of all, CloneRefactor parses the AST obtained from JavaParser into a directed graph structure.
+CloneRefactor parses the AST obtained from JavaParser into a directed graph structure.
 We have chosen to base our clone detection around statements as the smallest unit of comparison.
@@
 
-\subsubsection{Filtering the AST}
+\subsection{Filtering the AST}
 As a first step towards building the clone graph, we preprocess the AST to decide which AST nodes should become part of the clone graph.
@@
 
-\subsubsection{Building the clone graph}\label{sec:buildingclonegraph}
+\subsection{Building the clone graph}\label{sec:buildingclonegraph}
 Building the clone graph consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
@@
 This map is used to efficiently find out whether a statement is cloned with another.
-An example of such a graph is displayed in Figure~\ref{fig:clonegraphsimple}.
+%An example of such a graph is displayed in Figure~\ref{fig:clonegraphsimple}.
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/CodeGraph2}
-  \caption{Abstract example of a part of a possible clone graph as built by CloneRefactor.}
-  \label{fig:clonegraphsimple}
-\end{figure}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=1\textwidth]{img/CodeGraph2}
+%   \caption{Abstract example of a part of a possible clone graph as built by CloneRefactor.}
+%   \label{fig:clonegraphsimple}
+% \end{figure*}
 
@@
 
-\subsubsection{Comparing Statements/Declarations} \label{sec:comparingstuff}
+\subsection{Comparing Statements/Declarations} \label{sec:comparingstuff}
 In the previous section, we described a ``duplicate'' relation between nodes in the clone graph built by CloneRefactor.
-Whether two nodes in this graph are duplicates of each other is dependent on the clone type.
-In this section, we will describe for each type how we compare statements and declarations to assess whether they are clones of each other.
-
-CloneRefactor detects six different types of clones: T1, T2, T3, T1R, T2R, and T3R.
-These types are further explained in chapter \ref{chap:clonetypes}.
-For \textbf{type 1} clones, CloneRefactor filters the tokens of a node to exclude its comments, whitespace, and end of line (EOL) characters and then compares these tokens.
-For \textbf{type 2} clones, the tokens are further filtered to omit all identifiers and literals.
-\textbf{Type 3} clones do the same duplication comparison as type 2 clones.
-
-For \textbf{type 1R} clones this comparison is more advanced.
+Whether this duplicate relation exists between two nodes is determined by taking into account the contextual information.
 For \textit{method calls} we determine their fully qualified method signature for comparison with other nodes.
@@
 
-\textbf{Type 2R} clones allow any variation in literals, variables, and method calls at this stage in the clone detection process.
-We compare \textit{variables} by the FQI of their types but not their names.
-For \textit{method calls}, we compare the FQI of their return type and the type of each of their parameters.
-Apart from that, we do not compare the names of type declarations.
-\textbf{Type 3R} clones have the same compare rules as type 2R clones.
-
-\subsubsection{Mapping graph nodes to code}
+\subsection{Mapping graph nodes to code}
 The clone graph, as explained in Section~\ref{sec:buildingclonegraph}, contains all declarations and statements of a software project.

### 2019-11-06 benevol/paper.tex
Updates from Overleaf

@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=1\textwidth]{img/CodeGraphExample}
+  \caption{Example of a clone graph built by CloneRefactor.}
+  \label{fig:clonegraph2}
+\end{figure*}
+
 \subsubsection{Variables}
@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=1\textwidth]{img/CloneGraphCode}
+  \caption{CloneRefactor extracts statements and declarations from source code.}
+  \label{fig:clonegraph}
+\end{figure*}
+
 \subsection{Filtering the AST}
@@
 This map is used to efficiently find out whether a statement is cloned with another.
-%An example of such a graph is displayed in Figure~\ref{fig:clonegraphsimple}.
+An example of such a graph is displayed in Figure~\ref{fig:clonegraph2}.
 
@@
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/CloneGraphCode}
-  \caption{CloneRefactor extracts statements and declarations from source code.}
-  \label{fig:clonegraph}
-\end{figure}
-
 On line 24-25 of the code fragment, we see a \texttt{MethodDeclaration}.
@@
 As an example, we convert the code example shown in Figure~\ref{fig:clonegraph} to a clone graph as displayed in Figure~\ref{fig:clonegraph2}.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{img/CodeGraphExample}
-  \caption{Example of a clone graph built by CloneRefactor.}
-  \label{fig:clonegraph2}
-\end{figure}
 
@@
 
-\subsubsection{Removing redundant clone classes}\label{sec:conceptualremovingredundant}
-The clone detection method used by CloneRefactor can, for various reasons, result in redundant clone classes.
-After the insertion of each newly detected clone, we check whether it is redundant and/or any of the existent clones has become redundant by adding this clone.
-A clone is redundant if it is a subset of another clone.
-We define the subset relation between clones as follows:
-
-\begin{equation}\label{eq:subset}
-C_1 \subseteq C_2 := \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
-\end{equation} % Right symbol for definition
-
-Where \textit{C} refers to a clone class (a set of clone instances), \textit{i} refers to a clone instance, \textit{F} is the file in which a clone instance is located and \textit{R} is the range of tokens that a clone instance spans.
-For each clone found, we remove all existing clones that are a subset of the found clone:
-
-\begin{equation}\label{eq:removeall}
-S_{after} = S_{before} \setminus \{C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S_{before}\}
-\end{equation}
-
-Where \textit{$S_{before}$} is the clone class collection containing all clones that are found up in until this point, \textit{$C_{new}$} is the clone class that was just found and \textit{$S_{after}$} is the clone class collection after removing all subsets of the added clone.
-
-We should not add the new clone to our list of clones if its a subset of an existing clone.
-Because of that, we check for each clone added whether there exists a clone class of which the found clone class is a subset:
-
-\begin{equation}\label{eq:removeexisting}
-\{C_{new} \subseteq C_{existing}\text{ }|\text{ }C_{existing} \in S\} = \emptyset \Rightarrow S_{after} = S \cup C_{new}
-\end{equation}
-
-Where \textit{$S_{before}$} is the clone class collection containing all clones that are found up in until this point, \textit{$C_{new}$} is the clone class that was just found and \textit{$S_{after}$} is the clone class collection after optionally adding the newly found clone.
-If the newly added clone is a subset of an existing clone, we do not add it to the set of clone classes.
-This way we avoid redundant clone classes being detected by CloneRefactor.
+\section{Results}
+To compare the difference in detected clones when contextual information is considered, we
 

### 2019-11-06 benevol/paper.tex
Updates from Overleaf

@@
 
-Comparing code fragments including their contextual information introduces an optimization problem, as contextual information may be hard to retrieve.
+Comparing code fragments including their contextual information introduces an optimization problem, as this information may be hard to retrieve.
 It can be ambiguous where contextual information resides and tracking it down may require to follow cross-file references.
-For large codebases, this can require a lot of time due to the sheer number of referenced symbols.
+For large codebases, it could become time-consuming due to the sheer number of referenced symbols.
 
 We propose a method to efficiently detect clones taking into account contextual information.
-To do this, we propose a tool that uses an AST-parsing library named JavaParser to detect clones a retrieve contextual information.
-Our method first parses the AST retrieved from JavaParser into a graph structure, which is then used to find clones.
+We introduce a tool that uses an AST-parsing library named JavaParser to detect clones and retrieve contextual information.
+Our method parses the Abstract Syntax Tree retrieved from JavaParser into a graph structure, which is used to find clones.
 This graph maps the following relations for each statement in the codebase: the next statement, the previous statement, and the previous cloned statement.
@@
 They create implicit dependencies, thus increasing maintenance efforts or causing bugs in evolving software.
-Changing one occurrence of such a duplicated fragment may require other occurrences to be changed as well~\cite{ostberg2014automatically}.
+Changing one occurrence of a duplicated fragment may require other occurrences to be changed as well~\cite{ostberg2014automatically}.
 Also, duplicated code has been shown to add up to 25\% of total system volume~\cite{bruntink2005use}, which entails more code to be maintained.
@@
 \section{Background}
+\subsection{Code clones}
 We use two concepts to argue about code clones~\cite{roy2007survey}:
@@
 Many studies adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
+
+\section{JavaParser}
+JavaParser~\cite{tomassetti2017javaparser} is a Java library which allows parsing Java source files to an abstract syntax tree (AST).
+Integrated into JavaParser is a library named SymbolSolver.
+This library allows for the resolution of symbols using JavaParser.
+For instance, we can use it to trace references (methods, variables, types, etc) to their declarations (these referenced identifiers are also called ``symbols'').
+Using this, we can find the required contextual information.
+
+To be able to trace referenced identifiers, SymbolSolver requires access to not only the analyzed Java project but also all its dependencies.
+This requires us to include all dependencies with the project.
+Along with this, SymbolSolver solves symbols in the JRE System Library (the standard libraries coming with every installation of Java) using the active Java Virtual Machine (JVM).
+%This has a big impact on performance efficiency.
+This is visible in our results, as displayed in Section~\ref{sec:clonetypeexperiments}.
 
@@
 
-\section{CloneRefactor}
+\section{Clone Detection}\label{sec:clonedetection}
 We develop a tool named CloneRefactor\footnote{CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}} that detects clones that can (relatively) easily be refactored.
@@
 
-\section{JavaParser}
-JavaParser~\cite{tomassetti2017javaparser} is a Java library which allows parsing Java source files to an abstract syntax tree (AST).
-JavaParser allows to modify this AST and write the result back to Java source code.
-The ultimate goal is to use this to be able to apply automated refactorings.
-
-Integrated into JavaParser is a library named SymbolSolver.
-This library allows for the resolution of symbols using JavaParser.
-For instance, we can use it to trace references (methods, variables, types, etc) to their declarations (these referenced identifiers are also called ``symbols'').
-Using this, we can find the required contextual information.
-
-To be able to trace referenced identifiers, SymbolSolver requires access to not only the analyzed Java project but also all its dependencies.
-This requires us to include all dependencies with the project.
-Along with this, SymbolSolver solves symbols in the JRE System Library (the standard libraries coming with every installation of Java) using the active Java Virtual Machine (JVM).
-%This has a big impact on performance efficiency.
-This is visible in our results, as displayed in Section~\ref{sec:clonetypeexperiments}.
-
-\section{Clone Detection}\label{sec:clonedetection}
 To detect clones, CloneRefactor parses the AST acquired from JavaParser to a graph structure.
@@
 \section{Results}
-To compare the difference in detected clones when contextual information is considered, we
+To compare the difference in detected clones when contextual information is considered, we compared the number of clones found when considering contextual information with when it is not considered.
+For this, we use a corpus of 2.
 

### 2019-11-06 benevol/paper.tex
Updates from Overleaf

@@
 They create implicit dependencies, thus increasing maintenance efforts or causing bugs in evolving software.
-Changing one occurrence of a duplicated fragment may require other occurrences to be changed as well~\cite{ostberg2014automatically}.
-Also, duplicated code has been shown to add up to 25\% of total system volume~\cite{bruntink2005use}, which entails more code to be maintained.
+Changing one occurrence of a duplicated fragment may require changes in other occurrences ~\cite{ostberg2014automatically}.
+Also, duplicated code was shown to add up to 25\% of total system volume~\cite{bruntink2005use}, which entails more code to be maintained.
 

### 2019-11-07 benevol/paper.tex
Updates from Overleaf

@@
 This graph maps the following relations for each statement in the codebase: the next statement, the previous statement, and the previous cloned statement.
+
+We find that, when taking into account contextual information in our clone detection, we find 11\% fewer clones.
+Manually inspecting the difference, we find that they are less relevant for refactoring.
 \end{abstract}
@@
 Changing one occurrence of a duplicated fragment may require changes in other occurrences ~\cite{ostberg2014automatically}.
-Also, duplicated code was shown to add up to 25\% of total system volume~\cite{bruntink2005use}, which entails more code to be maintained.
+Also, duplicated code was shown to account for 25\% of total system volume~\cite{bruntink2005use}, entailing more code to be maintained.
 
-A lot of tools have been proposed to detect such duplication issues \cite{roy2009comparison, svajlenko2014evaluating, sheneamer2016survey}.
-These tools can find matching fragments of code, but do not take into account contextual information of code.
+Several tools have been proposed to detect duplication issues \cite{roy2009comparison, svajlenko2014evaluating, sheneamer2016survey}.
+These tools can find matching fragments of code, however do not take into account contextual information of code.
 An example of such contextual information is the name of used variables: many different methods with the same name can exist in a codebase.
@@
 
-We describe a method to detect clones while taking into account such contextual information and propose a tool to detect clones taking into account this contextual information.
-Run this tool over a corpus of 2,267 Java projects.
+We describe a method to detect clones while taking into account the contextual information and introduce a tool to detect clones taking into account this contextual information.
+We run the tool over a corpus of 2,267 Java projects.
 We find that taking into account contextual information results in 11\% less clones than found when not taking this information into account.
@@
 
-\section{Background}
-\subsection{Code clones}
-We use two concepts to argue about code clones~\cite{roy2007survey}:
-\\ \textbf{Clone instance}: A single cloned fragment.
-\\ \textbf{Clone class}: A set of similar clone instances.
-
-%\subsection{Clone Types}
-Duplication in code is found in many different forms.
-Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}.
-Sometimes this code is then adapted to fit the new context.
-To reason about these modifications, several clone types have been proposed%.
-These clone types are described in Roy et al
-~\cite{roy2007survey}:\\
-\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout), and comments.\\
-\textbf{Type II:} Structurally/syntactically identical fragments except variations in identifiers, literals, types, layout, and comments.\\
-\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed next to variations in identifiers, literals, types, layout, and comments.
-A higher type of clone means that it is harder to detect and refactor.
-Many studies adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
-
-\section{JavaParser}
-JavaParser~\cite{tomassetti2017javaparser} is a Java library which allows parsing Java source files to an abstract syntax tree (AST).
-Integrated into JavaParser is a library named SymbolSolver.
-This library allows for the resolution of symbols using JavaParser.
-For instance, we can use it to trace references (methods, variables, types, etc) to their declarations (these referenced identifiers are also called ``symbols'').
-Using this, we can find the required contextual information.
-
-To be able to trace referenced identifiers, SymbolSolver requires access to not only the analyzed Java project but also all its dependencies.
-This requires us to include all dependencies with the project.
-Along with this, SymbolSolver solves symbols in the JRE System Library (the standard libraries coming with every installation of Java) using the active Java Virtual Machine (JVM).
-%This has a big impact on performance efficiency.
-This is visible in our results, as displayed in Section~\ref{sec:clonetypeexperiments}.
-
-\section{Motivating example} \label{sec:type1}
 \begin{figure*}
@@
 
+\section{Background}
+We first explain relevant code clone terminology and definitions. Next, we describe the JavaParser tool, used to retrieve contextual information of source code.
+
+\subsection{Code clones}
+We use two concepts to argue about code clones~\cite{roy2007survey}:
+\\ \textbf{Clone instance}: A single cloned fragment.
+\\ \textbf{Clone class}: A set of similar clone instances.
+
+%\subsection{Clone Types}
+Duplication in code is found in many different forms.
+Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}.
+Sometimes this code is then adapted to fit the new context.
+To reason about these modifications, several clone types have been proposed%.
+These clone types are described in Roy et al
+~\cite{roy2007survey}:\\
+\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout), and comments.\\
+\textbf{Type II:} Structurally/syntactically identical fragments except variations in identifiers, literals, types, layout, and comments.\\
+\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed next to variations in identifiers, literals, types, layout, and comments.
+A higher type of clone means that it is harder to detect and refactor.
+Many studies adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
+
+\subsection{JavaParser}
+JavaParser~\cite{tomassetti2017javaparser} is a Java library which allows parsing Java source files to an abstract syntax tree (AST).
+Integrated into JavaParser is a library named SymbolSolver.
+This library allows for the resolution of symbols using JavaParser.
+For instance, we can use it to trace references (methods, variables, types, etc) to their declarations (these referenced identifiers are also called ``symbols'').
+Using this, we can find the required contextual information.
+
+To be able to trace referenced identifiers, SymbolSolver requires access to not only the analyzed Java project but also all its dependencies.
+This requires us to include all dependencies with the project.
+Along with this, SymbolSolver solves symbols in the JRE System Library (the standard libraries coming with every installation of Java) using the active Java Virtual Machine (JVM).
+%This has a big impact on performance efficiency.
+This is visible in our results, as displayed in Section~\ref{sec:clonetypeexperiments}.
+
+\section{Motivating example} \label{sec:type1}
 Most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating} detect type 1 clones by textually comparing code fragments (except for whitespace and comments).
@@
 Looking at the \texttt{import} statement above the class, one fragment uses the \texttt{java.util.List} and the other uses the \texttt{java.awt.List}.
-Both happen to have an \texttt{add} method, but apart from that their implementation is completely different.
+Both happen to have an \texttt{add} method, however their implementation is completely different.
 
@@
 
-This shows that not all textually equal clones can easily be refactored.
+This shows that not all textually equal clones can be easily refactored.
 
@@
 A fully qualified method signature consists of the fully qualified name of the method, the fully qualified type of the method plus the fully qualified type of each of its arguments.
-For instance, an \texttt{eat} method could become \texttt{com.sb.AppleCore com.sb.fruitgame.Apple.eat(com.sb.fruitgame.Tool)}.
+For instance, an \texttt{eat} method could become
+%\footnotesize{
+\texttt{com.sb.Apple.eat(com.sb.Tool)}.
+%}.
 
@@
 
-\section{Results}
+\section{Experiments and Results}
 To compare the difference in detected clones when contextual information is considered, we compared the number of clones found when considering contextual information with when it is not considered.
-For this, we use a corpus of 2.
+For this, we use a corpus of 2,267 Java projects including their dependencies \cite{baars2019towards}.
+
+We find that 167,913 clones are found when contextual information is not considered, whereas 149,569 clones are found when it is considered.
+We manually analyse a sample of 50 clones that are not found when considering contextual information.
+We found that these clones are indeed hard to refactor because they describe different functional operations and can thus not be extracted to a new method.
+Also, most often they were not relevant because, based on our judgement, refactoring would not improve the code design.
+Often, different methods were called or variables of different types were used.
+
+We also look into the difference in performance when taking into account contextual information.
+Detecting the clones in all 2,267 projects took 20.83 minutes when considering contextual information.
+When contextual information was not considered, it took 1.58 minutes.
 
 \section{Conclusion}
+We propose a method to detect clones taking into account contextual information of source code.
+Contextual information is important because different functional concepts may turn up as clones because they are textually identical.
+
+We define three aspects of source code as the contextual information:
+\begin{itemize}
+    \item The type of variable references.
+    \item The location of method references.
+    \item The location of type references.
+\end{itemize}
+When these references have the same name but point to different locations, clones may not be easily refactorable.
+Our results show that most such clones are not relevant for refactoring.
+This accounts for about 11\% of clones.
+This comes however with a performance trade-off: detecting clones with contextual information took 13 times longer than when not taking contextual information into account (1.6min vs 20.8min).
 

### 2019-11-07 benevol/paper.tex
Updates from Overleaf

@@
 We manually analyse a sample of 50 clones that are not found when considering contextual information.
-We found that these clones are indeed hard to refactor because they describe different functional operations and can thus not be extracted to a new method.
+We find that these clones are indeed hard to refactor because they describe different functional operations and can thus not be extracted to a new method.
 Also, most often they were not relevant because, based on our judgement, refactoring would not improve the code design.
@@
 
-We define three aspects of source code as the contextual information:
-\begin{itemize}
-    \item The type of variable references.
-    \item The location of method references.
-    \item The location of type references.
-\end{itemize}
+We define three aspects of source code as the contextual information:  a) the type of variable references; b) the location of method references; and c) the location of type references.
 When these references have the same name but point to different locations, clones may not be easily refactorable.

### 2019-11-07 benevol/paper.tex
Introduction and abstract

@@
 
-We find that, when taking into account contextual information in our clone detection, we find 11\% fewer clones.
-Manually inspecting the difference, we find that they are less relevant for refactoring.
+We find that, when taking into account contextual information in our clone detection, 11\% fewer clones are found.
+Manually inspecting a sample of the difference, we find that they are less relevant for refactoring.
 \end{abstract}
@@
 Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
-Duplicate code fragments are often considered as symptoms of bad design~\cite{fowler2018refactoring}.
-They create implicit dependencies, thus increasing maintenance efforts or causing bugs in evolving software.
-Changing one occurrence of a duplicated fragment may require changes in other occurrences ~\cite{ostberg2014automatically}.
-Also, duplicated code was shown to account for 25\% of total system volume~\cite{bruntink2005use}, entailing more code to be maintained.
+Duplicate code fragments are often considered as bad design~\cite{fowler2018refactoring}.
+They increasing maintenance efforts or causing bugs in evolving software~\cite{heitlager2007practical}.
+Changing one occurrence of a duplicated fragment may require changes in other occurrences~\cite{ostberg2014automatically}.
+Furthermore, duplicated code was shown to account for up to 25\% of total system volume~\cite{bruntink2005use}, entailing more code to be maintained.
 
@@
 
-We describe a method to detect clones while taking into account the contextual information and introduce a tool to detect clones taking into account this contextual information.
+We describe a method to detect clones while taking into account the contextual information and introduce a tool to detect clones taking into account such contextual information.
 We run the tool over a corpus of 2,267 Java projects.

### 2019-11-07 benevol/paper.tex
Updates from Overleaf

@@
 \textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed next to variations in identifiers, literals, types, layout, and comments.
-A higher type of clone means that it is harder to detect and refactor.
 Many studies adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
+In this study, we mainly focus expanding type 1 clone detection to take into account contextual information.
 
@@
 In such cases, refactoring opportunities could be invalidated.
-This can make clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
+This can make the detected clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone.
 
@@
 
-To detect clones, CloneRefactor parses the AST acquired from JavaParser to a graph structure.
+%To detect clones, CloneRefactor parses the AST acquired from JavaParser to a graph structure.
 Based on this graph structure, clones are detected.
@@
 
-First of all, CloneRefactor uses JavaParser to read a project from disk and build an AST, one class file at a time.
+CloneRefactor uses JavaParser to read a project from disk and build an AST. %, one class file at a time. 
 Each AST is then converted to a directed graph that maps relations between statements.
@@
 \subsection{Filtering the AST}
-As a first step towards building the clone graph, we preprocess the AST to decide which AST nodes should become part of the clone graph.
-We exclude package declarations and import statements from this graph.
-These are omitted by most clone detection tools, as package declarations and import statements are most often generated by the IDE.
+As a first step towards building the clone graph, we preprocess the AST to decide which AST nodes should become part of the clone graph: we exclude package declarations and import statements.
+These are omitted by most clone detection tools, as package declarations and import statements are most often generated by the IDE and not relevant for refactoring purposes.
 
@@
 To avoid redundant duplication checks, we exclude the body of each node.
-Look at Figure~\ref{fig:clonegraph} for an example of how source code maps to AST nodes.
 
-On line 24-25 of the code fragment, we see a \texttt{MethodDeclaration}.
+Figure~\ref{fig:clonegraph} shows an example of how source code maps to AST nodes.
+On line 24-25 of the code fragment is a \texttt{MethodDeclaration}.
 The node corresponding with this MethodDeclaration denotes all tokens found on these two lines, line 24 and 25.
@@
 
-Using the example shown in Figure~\ref{fig:clonegraph} and \ref{fig:clonegraph2} we can explain how we detect clones on the basis of this graph.
+Using the example shown in Figure~\ref{fig:clonegraph2} and~\ref{fig:clonegraph} we can explain how we detect clones on the basis of this graph.
 Suppose we are finding clones for two files and the final node of the second file is a variable declarator.
@@
 When contextual information was not considered, it took 1.58 minutes.
+This is mainly because contextual information may be hard to retrieve, because the location of the contextual information may not be explicit.
+To find contextual information it may also be required to follow cross-file references.
+%The location of contextual information may also be implicit, which may require to seek through several files.
 

### 2019-11-20 pldi/paper.tex

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[sigplan,10pt,review,anonymous]{acmart}
\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[sigplan]{acmart}\settopmatter{}

%% Conference information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmConference[PL'18]{ACM SIGPLAN Conference on Programming Languages}{January 01--03, 2018}{New York, NY, USA}
\acmYear{2018}
\acmISBN{} % \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission;
%% use 'none' for review submission.
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2018}           %% If different from \acmYear

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
%% Citation style
%\citestyle{acmauthoryear}  %% For author/year citations
%\citestyle{acmnumeric}     %% For numeric citations
%\setcitestyle{nosort}      %% With 'acmnumeric', to disable automatic
                            %% sorting of references within a single citation;
                            %% e.g., \cite{Smith99,Carpenter05,Baker12}
                            %% rendered as [14,5,2] rather than [2,5,14].
%\setcitesyle{nocompress}   %% With 'acmnumeric', to disable automatic
                            %% compression of sequential references within a
                            %% single citation;
                            %% e.g., \cite{Baker12,Baker14,Baker16}
                            %% rendered as [2,3,4] rather than [2-4].

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Note: Authors migrating a paper from traditional SIGPLAN
%% proceedings format to PACMPL format must update the
%% '\documentclass' and topmatter commands above; see
%% 'acmart-pacmpl-template.tex'.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption

\usepackage{todonotes}

\begin{document}

%% Title information
\title%[Short Title]
{A Code Clone Detection DSL for Java}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

%% Author with single affiliation.
\author{Simon Baars}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Research Assistant}
  \department{Systems and Network Engineering Research Group}              %% \department is recommended
  \institution{University of Amsterdam}            %% \institution is required
  %\streetaddress{Street1 Address1}
  %\city{City1}
  %\state{State1}
  %\postcode{Post-Code1}
  \country{Amsterdam}                    %% \country is recommended
}
\email{simon.j.baars@gmail.com}          %% \email is recommended

%% Author with two affiliations and emails.
%\author{First2 Last2}
%\authornote{with author2 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
%\affiliation{
%  \position{Position2a}
%  \department{Department2a}             %% %%\department is recommended
 % \institution{Institution2a}           %% \institution is required
%  \streetaddress{Street2a Address2a}
%  \city{City2a}
%  \state{State2a}
%  \postcode{Post-Code2a}
%  \country{Country2a}                   %% \country is recommended
%}
% %\email{first2.last2@inst2a.com}         %% \email is recommended
% \affiliation{
%   \position{Position2b}
%   \department{Department2b}             %% \department is recommended
%   \institution{Institution2b}           %% \institution is required
%   \streetaddress{Street3b Address2b}
%   \city{City2b}
%   \state{State2b}
%   \postcode{Post-Code2b}
%   \country{Country2b}                   %% \country is recommended
% }
% \email{first2.last2@inst2b.org}         %% \email is recommended

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
Duplication in source code is generally considered an undesirable pattern, because it unnecessarily increases system volume and is prone to cause bugs. Many studies propose definitions and techniques to detect such duplication issues. The clones detected by these definitions and techniques differ greatly. This is because there is a trade-off between completeness and number of false-positives. Additionally, clone detection may have different purposes, which may require different clone detection techniques.

We propose a DSL for clone detection, that allows for the specification of clone definitions. Using this DSL, code clone definitions can be easily expressed, whilst not having to worry about the actual clone detection algorithm and its optimization. Our DSL allows to exclude expressions, statements and declarations from clone matching. Our DSL supports line-based and AST-based clone detection approaches. The DSL can also take into account context information of expressions.

We use the DSL to express type 1, 2 and 3 clone definitions. We then use these definitions to validate the DSL over a corpus of open-source Java projects. We compare these results with established clone detection tools. We find that our DSL matches the output of the control tools, while allowing for a much wider spectrum of configurations. 
\end{abstract}

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008</concept_id>
<concept_desc>Software and its engineering~General programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003456.10003457.10003521.10003525</concept_id>
<concept_desc>Social and professional topics~History of programming languages</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~General programming languages}
\ccsdesc[300]{Social and professional topics~History of programming languages}
%% End of generated code

%% Keywords
%% comma separated list
\keywords{clone detection, domain specific language, language engineering, meta-programming}  %% \keywords are mandatory in final camera-ready submission

%% \maketitle
%% Note: \maketitle command must come after title commands, author
%% commands, abstract environment, Computing Classification System
%% environment and commands, and keywords command.
\maketitle

\section{Introduction}
An abundant number of clone detection tools have been proposed in the literature due to the many applications and benefits of clone detection.

% %% Acknowledgments
% \begin{acks}                            %% acks environment is optional
%                                         %% contents suppressed with 'anonymous'
%   %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
%   %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
%   %% acknowledge financial support and will be used by metadata
%   %% extraction tools.
%   This material is based upon work supported by the
%   \grantsponsor{GS100000001}{National Science
%     Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
%   No.~\grantnum{GS100000001}{nnnnnnn} and Grant
%   No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
%   conclusions or recommendations expressed in this material are those
%   of the author and do not necessarily reflect the views of the
%   National Science Foundation.
% \end{acks}

%% Bibliography
%\bibliography{bibfile}

%% Appendix
\appendix
\section{Appendix}

Text of appendix \ldots

\end{document}

### 2019-11-20 sattose/paper.tex

@@
 \subsection{CloneRefactor}
-None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
+None of the state-of-the-art tools we identified implement all our criteria, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
 In this tool, we implemented both the literature clone types~\cite{roy2007survey} and our refactoring-oriented clone types as described in Sec.~\ref{sec:rtypes}.

### 2019-11-21 pldi/paper.tex
Introduction PLDI paper

@@
 \section{Introduction}
-An abundant number of clone detection tools have been proposed in the literature due to the many applications and benefits of clone detection.
+Code clones argue about the duplicate code present in the source code of software systems.
+An abundant number of clone detection tools and techniques have been proposed in the literature due to the many applications and benefits of clone detection \cite{svajlenko2019mutation}.
+Clones are most often the result of code reuse by copying and pasting existing code, among other reasons \cite{roy2007survey}.
+Clones are often seen as harmful \cite{roy2007survey, ostberg2014automatically, juergens2009code}, but can also have positive effects on system maintainability \cite{roy2007survey, kapser2006cloning, aversano2007clones}.
+
+Clone detection is applied in various domains.
+This includes (automated) refactoring, education (plagiarism detection) \cite{wahler2004clone}, (legacy code) modernization \cite{meng2013refactoring} and maintainability analysis \cite{heitlager2007practical}.
+For these varying purposes, many clone detection tools have been proposed: a 2013 survey by Rattan et al.
+\cite{rattan2013software} surveyed more than 70 clone detection tools.
+Comparisons show large differences in recall and precisions of these tools \cite{svajlenko2014evaluating}.
+
+To allow easy experimentation with code clone defitions and methods, we propose a DSL to configure clone detection.
+
+\section{Language Design}
+
+\section{Results}
+
+\section{Discussion}
+
+\section{Conclusion}
+
+\subsection{Threats to validity}
 
@@
 %% Appendix
-\appendix
-\section{Appendix}
-
-Text of appendix \ldots
+% \appendix
+% \section{Appendix}
+%
+% Text of appendix \ldots
 

### 2019-11-22 pldi/paper.tex
Working on PLDI paper

@@
 \usepackage{todonotes}
+
+\usepackage{xcolor}
+\usepackage{float}
+
+\usepackage{graphicx}
 
@@
 
+\section{Background}
+We describe code clone definitions and techniques that are commonly used in code clone detection.
+
+\subsection{Clone type definitions}
+Most modern clone detection tools detect clones by the following clone type definitions \cite{svajlenko2014evaluating}:
+\textbf{Type 1:} Code fragments that are syntactically identical, except for differences in white space, layout and comments.
+\textbf{Type 2:} Code fragments that are syntactically identical, except for differences in identifier names, literal values, white space, layout and comments.
+\textbf{Type 3:} Code fragments that are syntactically similar with differences at the statement level. The fragments may differ by the addition, removal or modification of statements.
+
+\subsection{Clone detection techniques}
+
+\section{Clone Detection Techniques Survey}
+As an initial step towards creating a clone detection DSL, we surveyed clone detection techniques and tools to extract common functionalities.
+
 \section{Language Design}
+We propose Clone Detection DSL (CDD)\footnote{Link to the GitHub repository is omitted to adhere to the double-blind review rules.
+Link to full source code of the DSL will be included in the camera-ready version.}, a DSL that allows to build a clone detection script to analyze Java systems.
+
+\subsection{Clone Size}
+An important feature of many clone detection tools, to be able to find clones that have a high relevance, is to be able to configure what characteristics clones should have for them to be considered.
+Some clone detection tools use a threshold that specifies the minimum number of lines \cite{juergens2009clonedetective, ducasse1999language, cordy2011nicad, uddin2013simcad}.
+Other clone detection tools specify the minimum number of tokens \cite{kamiya2002ccfinder, toomey2012ctcompare, jiang2007deckard}.
+Some AST-based clone detectors use the minimum number of statements \cite{higo2009enhancing}.
+
+Based on such thresholds, clones that are too small are filtered.
+How these thresholds are configured has a big impact on the results and their relevance \cite{roy2007survey}.
+Our DSL allows for any combination of metric values to configure the minimum size of a clone.
+For this, we introduce the \textbf{Size} keyword.
+This is an example of how the \textbf{Size} keyword can be configured:
+\\
+\textbf{\textcolor[HTML]{7F0055}{Size}} (\textcolor[HTML]{7D7D7D}{4} \textbf{\textcolor[HTML]{7F0055}{lines}} $\&$  \textcolor[HTML]{7D7D7D}{50} \textbf{\textcolor[HTML]{7F0055}{tokens}}) $ \vert $  (\textcolor[HTML]{7D7D7D}{6} \textbf{\textcolor[HTML]{7F0055}{lines}} $\&$  \textcolor[HTML]{7D7D7D}{40} \textbf{\textcolor[HTML]{7F0055}{tokens}})
+\\
+
+\subsection{Match Granularity}
+
+\subsection{Exclusions}
+
+\subsection{Compare Rules}
+
+\section{Example scripts}
 
@@
 % Text of appendix \ldots
+\bibliography{references}
 

### 2019-11-22 pldi/paper.tex
Terminology and techniques

@@
 \section{Background}
-We describe code clone definitions and techniques that are commonly used in code clone detection.
+We describe terminology, definitions and techniques that are commonly used in code clone detection.
+
+\subsection{Code clone terminology}
+To argue about code clones, we use the following terminology:
+\\ \textbf{Code fragment} \cite{svajlenko2019mutation}: A continuous region of source code.
+Specified by the triple $(l,s,e)$, including the source file \textit{l}, the start line and column \textit{s}, and the end line and column \textit{e}.
+\\ \textbf{Clone class} \cite{roy2007survey}: A set of similar code fragments. The definition of similarity depends on the desired granularity of clones.
+\\ \textbf{Clone instance} \cite{roy2007survey}: A cloned code fragment that is part of a clone class.
 
@@
 Most modern clone detection tools detect clones by the following clone type definitions \cite{svajlenko2014evaluating}:
-\textbf{Type 1:} Code fragments that are syntactically identical, except for differences in white space, layout and comments.
-\textbf{Type 2:} Code fragments that are syntactically identical, except for differences in identifier names, literal values, white space, layout and comments.
-\textbf{Type 3:} Code fragments that are syntactically similar with differences at the statement level. The fragments may differ by the addition, removal or modification of statements.
+\\ \textbf{Type 1}: Code fragments that are syntactically identical, except for differences in white space, layout and comments.
+\\ \textbf{Type 2}: Code fragments that are syntactically identical, except for differences in identifier names, literal values, white space, layout and comments.
+\\ \textbf{Type 3}: Code fragments that are syntactically similar with differences at the statement level. The fragments may differ by the addition, removal or modification of statements.
 
 \subsection{Clone detection techniques}
+Different clone detection techniques have been proposed in literature \cite{sheneamer2016survey}:
+\textbf{Textual}: Code lines are textually compared.
+Advantages are that textual approaches are often simpler, easier to implement and are independent of language.
+Disadvantages are that it is harder to exclude certain constructs from matching.
+\\ \textbf{Lexical (Token)}: Lexical approaches first tokenize the source code, so certain groups of tokens can be excluded from matching \cite{svajlenko2014evaluating}.
+The disadvantage is that tokens must be specified for each language.
+\\ \textbf{Syntactic (Tree)}: AST-based approaches first parse the source code into an AST. This allows for subtree based comparison and mapping context of clones \cite{fontana2015duplicated}.
+\\ \textbf{Syntactic (Metric)}: In metric-based clone detection techniques, a number of metrics are computed for each fragment of code to find similar fragments by comparing metric vectors instead of comparing code or ASTs directly.
+\\ \textbf{Semantic (Graph)}: A graph-based clone detection technique uses a graph to represent the data and control flow of a program.
+\\ \textbf{Semantic (Hybrid)}: Hybrid approaches use a combination of before-mentioned techniques to speed up detection of clones and find clones with a variety of characteristics.
 
 \section{Clone Detection Techniques Survey}
-As an initial step towards creating a clone detection DSL, we surveyed clone detection techniques and tools to extract common functionalities.
+As an initial step towards creating a clone detection DSL, we survey clone detection techniques and tools to extract common functionalities. \todo{Write this section}
 
@@
 This is an example of how the \textbf{Size} keyword can be configured:
-\\
-\textbf{\textcolor[HTML]{7F0055}{Size}} (\textcolor[HTML]{7D7D7D}{4} \textbf{\textcolor[HTML]{7F0055}{lines}} $\&$  \textcolor[HTML]{7D7D7D}{50} \textbf{\textcolor[HTML]{7F0055}{tokens}}) $ \vert $  (\textcolor[HTML]{7D7D7D}{6} \textbf{\textcolor[HTML]{7F0055}{lines}} $\&$  \textcolor[HTML]{7D7D7D}{40} \textbf{\textcolor[HTML]{7F0055}{tokens}})
-\\
+
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+\textbf{\textcolor[HTML]{7F0055}{Size}} (\textcolor[HTML]{7D7D7D}{4} \textbf{\textcolor[HTML]{7F0055}{lines}} $\&$  \textcolor[HTML]{7D7D7D}{50} \textbf{\textcolor[HTML]{7F0055}{tokens}}) $ \vert $  (\textcolor[HTML]{7D7D7D}{6} \textbf{\textcolor[HTML]{7F0055}{lines}} $\&$  \textcolor[HTML]{7D7D7D}{40} \textbf{\textcolor[HTML]{7F0055}{tokens}})\\
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+
+In this example, we seek clones that either have many tokens but fewer lines, or many lines but fewer tokens.
+We allow the following keywords to be used in the condition of the \textbf{Size} threshold:
+\begin{itemize}
+  \item \textit{lines}: Number of lines found in each clone instance
+\end{itemize}
 

### 2019-11-22 pldi/paper.tex
Clone size

@@
 \section{Language Design}
-We propose Clone Detection DSL (CDD)\footnote{Link to the GitHub repository is omitted to adhere to the double-blind review rules.
-Link to full source code of the DSL will be included in the camera-ready version.}, a DSL that allows to build a clone detection script to analyze Java systems.
+We propose the Clone Detection DSL (CDD)\footnote{Link to the GitHub repository is omitted to adhere to the double-blind review rules.
+Link to full source code of the DSL would be included in the camera-ready version.}, a DSL that allows to build a clone detection script to analyze Java systems.
 
@@
 \begin{itemize}
-  \item \textit{lines}: Number of lines found in each clone instance
+  \item \textit{lines}: Number of lines in clone instance
+  \item \textit{tokens}: Number of tokens in clone instance
+  \item \textit{statements}: Number of statements in clone instance
+  \item \textit{declarations}: Number of declarations in clone instance
+  \item \textit{complexity}: The cyclomatic complexity \cite{mccabe1976complexity} found in a clone instance.
 \end{itemize}
+Normally, these keywords denote the value of the metric of each clone instance.
+However, when prepended by \textit{``class\_''}, they denote the value of the metric for all clone instances in a clone class combined.
+This means that \textit{lines} specifies the minimum number of lines in each clone instance, and \textit{class\_lines} specifies the minimum number of lines in all clone instances of a clone class combined.
+
+This allows for easy experiments of combinations of metrics to determine whether a clone should be considered.
 

### 2019-11-22 pldi/paper.tex
LLOC stuff

@@
 \title%[Short Title]
-{A Code Clone Detection DSL for Java}         %% [Short Title] is optional;
+{CDD: A Code Clone Detection DSL for Java}         %% [Short Title] is optional;
                                         %% when present, will be used in
@@
 
-\section{Clone Detection Techniques Survey}
-As an initial step towards creating a clone detection DSL, we survey clone detection techniques and tools to extract common functionalities. \todo{Write this section}
+%\section{Clone Detection Techniques Survey} TODO
+%As an initial step towards creating a clone detection DSL, we survey clone detection techniques and tools to extract common functionalities. \todo{Write this section}
 
@@
 \subsection{Match Granularity}
+The \textbf{Match} keyword describes on what granularity clones will be matched.
+CDD can find clones that span physical lines of code, logical lines of code and in subtrees of the AST of a program.% certain physical CDD supports three granularities:
+\begin{itemize}
+  \item \textbf{PLOC}: These are physical lines of code, excluding whitespace and comments.
+Comparison is done between the tokens found on the lines.
+The smallest clone that can be found using this approach is a single line clone.
+  \item \textbf{LLOC}: These are logical lines of code, where each statement and some declarations are counted as a logical line of code \cite{nguyen2007sloc}.
+We compare these logical lines of code to find duplicates.
+The smallest clone that can be found using this approach is are clones that span a single logical line.
+  \item \textbf{Subtree}: This method compares subtrees in the AST of the program.
+\end{itemize}
 

### 2019-11-22 pldi/paper.tex
Playing a bit around

@@
 CDD can find clones that span physical lines of code, logical lines of code and in subtrees of the AST of a program.% certain physical CDD supports three granularities:
-\begin{itemize}
-  \item \textbf{PLOC}: These are physical lines of code, excluding whitespace and comments.
-Comparison is done between the tokens found on the lines.
-The smallest clone that can be found using this approach is a single line clone.
-  \item \textbf{LLOC}: These are logical lines of code, where each statement and some declarations are counted as a logical line of code \cite{nguyen2007sloc}.
-We compare these logical lines of code to find duplicates.
-The smallest clone that can be found using this approach is are clones that span a single logical line.
-  \item \textbf{Subtree}: This method compares subtrees in the AST of the program.
-\end{itemize}
+
+\subsubsection{Physical Lines of Code (LoC)}
+Physical lines of code are the lines of code as displayed in the editor of a program, excluding whitespace and comments.
+Code lines are compared by comparing tokens on one line with another.
+The main advantage of LOC is that, if statements are relatively equally distributed over lines, each line
+
+The main disadvantage of LOC is that its granularity depends on the coding style used by the programmer of the source code.
+A programmer that adheres to a maximum line length might break up statements more often than those who do not \cite{nguyen2007sloc}.
+Because of that, using LOC might give different results based on the design of the code.
+
+Another disadvantage is that changing the style of the code between fragments might result in duplicate code not being considered a clone.
+For instance, if in one fragment a statement is on a single line and in another the same statement is distributed over two lines, it will not be detected as a clone.
+
+\subsubsection{Logical Lines of Code (LLoC)}
+These are logical lines of code, where each statement and some declarations are counted as a logical line of code.
+In the study ``A SLOC Counting Standard'' \cite{nguyen2007sloc}, Nguyen et al.
+discuss which declarations and statements should be considered as a logical line of code.
+
+The main advantage of LLoC over LoC is that it is less dependent on coding style.
+If two statements are equal, independent of how they are distributed over physical lines, they will be considered clones.
+Some also argue that LLoC gives a more accurate indication of volume \cite{nguyen2007sloc}.
+
+\subsubsection{Subtree}
+A third approach to compare blocks of code is to compare subtrees of the AST of the source code.
+
+\subsection{Search Root}
 
@@
 \section{Example scripts}
+Hello :)
+
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+\noindent type1.cdd\par
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+\noindent\textbf{\textcolor[HTML]{7F0055}{Project}} \textcolor[HTML]{2A00FF}{"/path/to/java/project"} \par
+\noindent\textbf{\textcolor[HTML]{7F0055}{Size}} \textcolor[HTML]{7D7D7D}{6} \textbf{\textcolor[HTML]{7F0055}{lines}}  \par
+\noindent\textbf{\textcolor[HTML]{7F0055}{Match}} \textbf{\textcolor[HTML]{7F0055}{SLOC}}  \par
+\noindent\textbf{\textcolor[HTML]{7F0055}{Exclude}} PackageDeclaration, ImportDeclaration \\
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+\noindent type2.cdd\par
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+\noindent\textbf{\textcolor[HTML]{7F0055}{Project}} \textcolor[HTML]{2A00FF}{"/Users/sbaars/Documents/Kim/jhotdraw"}\par
+\noindent\textbf{\textcolor[HTML]{7F0055}{Size}} \textcolor[HTML]{7D7D7D}{6 \textbf{lines}}\par
+\noindent\textbf{\textcolor[HTML]{7F0055}{Match}} \textbf{\textcolor[HTML]{7F0055}{SLOC}}\par
+\noindent\textbf{\textcolor[HTML]{7F0055}{Exclude}} PackageDeclaration, ImportDeclaration\par
+\noindent\textbf{\textcolor[HTML]{7F0055}{DoNotCompare}} SimpleName, LiteralExpr\par
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
 

### 2019-11-22 pldi/paper.tex
This document needs more code :)

@@
 \noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
-\noindent\textbf{\textcolor[HTML]{7F0055}{Project}} \textcolor[HTML]{2A00FF}{"/Users/sbaars/Documents/Kim/jhotdraw"}\par
-\noindent\textbf{\textcolor[HTML]{7F0055}{Size}} \textcolor[HTML]{7D7D7D}{6 \textbf{lines}}\par
+\noindent\textbf{\textcolor[HTML]{7F0055}{Project}} \textcolor[HTML]{2A00FF}{"/path/to/java/project"}\par
+\noindent\textbf{\textcolor[HTML]{7F0055}{Size}} \textcolor[HTML]{7D7D7D}{6} \textbf{\textcolor[HTML]{7F0055}{lines}}\par
 \noindent\textbf{\textcolor[HTML]{7F0055}{Match}} \textbf{\textcolor[HTML]{7F0055}{SLOC}}\par
@@
 \noindent\textbf{\textcolor[HTML]{7F0055}{DoNotCompare}} SimpleName, LiteralExpr\par
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+\noindent type3.cdd\par
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+\noindent \textbf{\textcolor[HTML]{7F0055}{Project}} \textcolor[HTML]{2A00FF}{"/path/to/java/project"}\par
+\noindent \textbf{\textcolor[HTML]{7F0055}{Size}} \textcolor[HTML]{7D7D7D}{6} \textbf{\textcolor[HTML]{7F0055}{nodes}}\par
+\noindent \textbf{\textcolor[HTML]{7F0055}{Match}} \textbf{\textcolor[HTML]{7F0055}{Subtree}}\par
+\noindent \textbf{\textcolor[HTML]{7F0055}{Exclude}} PackageDeclaration, ImportDeclaration\par
+\noindent \textbf{\textcolor[HTML]{7F0055}{DoNotCompare}} SimpleName, LiteralExpr\par
+\noindent\textbf{\textcolor[HTML]{7F0055}{Compare}} $\ast$  \textbf{\textcolor[HTML]{7F0055}{Subnodes}} Statement \textcolor[HTML]{7D7D7D}{10$\%$}  \textcolor[HTML]{3F7F5F}{/$\ast$  We allow 10$\%$  variance in Statements $\ast$ /}\par
 \noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}

### 2019-11-22 pldi/paper.tex
Explain the examples a bit

@@
 \section{Example scripts}
-Hello :)
+To experiment with the CDD language, we convert current clone type definitions to CDD code.
+The only required keywords in the CDD language are \textbf{Project}, \textbf{Size} and \textbf{Match}.
+For the minimum size of type 1 clones many studies use \textit{6 lines} \cite{heitlager2007practical, bruntink2004evaluation, sajnani2016sourcerercc}.
+We choose to compare \textbf{LoC}, but the other options would also be valid (the definition of type 1 clones is ambiguous in this aspect).
+We exclude package and import declarations, as clones found in those declarations are often not useful \cite{koschke2012large}.
+The CDD code for this is as follows:
 
@@
 \noindent\textbf{\textcolor[HTML]{7F0055}{Size}} \textcolor[HTML]{7D7D7D}{6} \textbf{\textcolor[HTML]{7F0055}{lines}}  \par
-\noindent\textbf{\textcolor[HTML]{7F0055}{Match}} \textbf{\textcolor[HTML]{7F0055}{SLOC}}  \par
+\noindent\textbf{\textcolor[HTML]{7F0055}{Match}} \textbf{\textcolor[HTML]{7F0055}{LoC}}  \par
 \noindent\textbf{\textcolor[HTML]{7F0055}{Exclude}} PackageDeclaration, ImportDeclaration \\
 \noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+
+For type 2, we allow variance in identifiers and literals.
+For this, we can use the \textbf{DoNotCompare} keyword: all subnodes of these nodes are not compared between lines when comparing lines to determine whether they are similar.
+The CDD code for type 2 is as follows:
 
@@
 \noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+
+For type 3, we allow statements to differ. To implement this, we specify a percentage of variance that we allow statements to differ (in this case 10\%). This results in the following code:
 

### 2019-11-22 pldi/paper.tex
Apples are cool

@@
 \usepackage{graphicx}
+\usepackage{multirow}
+\usepackage{parcolumns}
+
+\definecolor{pblue}{rgb}{0.13,0.13,1}
+\definecolor{pgreen}{rgb}{0,0.5,0}
+\definecolor{pred}{rgb}{0.9,0,0}
+\definecolor{pgrey}{rgb}{0.46,0.45,0.48}
+\usepackage{listings}
+\lstset{language=Java,
+  showspaces=false,
+  showtabs=false,
+  breaklines=true,
+  showstringspaces=false,
+  breakatwhitespace=true,
+  commentstyle=\color{pgreen},
+  keywordstyle=\color{pblue},
+  numbers = left,
+  stringstyle=\color{pred},
+  basicstyle=\ttfamily,
+  moredelim=[il][\textcolor{pgrey}]{\$\$},
+  moredelim=[is][\textcolor{pgrey}]{\%\%}{\%\%}
+}
+
+\definecolor{lightgrey}{HTML}{ebebe0}
+\newcommand{\highlightGrey}{\makebox[0pt][l]{\color{lightgrey}\rule[-4pt]{1\linewidth}{14pt}}}
+
+\lstnewenvironment{javacode}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small,#1}}{}
 
@@
 A third approach to compare blocks of code is to compare subtrees of the AST of the source code.
+The advantage of this is that the result may be more useful for refactoring, as clones that are found are often easier to refactor.
+The disadvantage is that some clones may not be found.
+An example of this is shown in Fig.~\ref{fig:subtreecomparison}.
+
+\begin{figure*}
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+|\highlightGrey|for(int i = 0; i<apples.length; i++){
+|\highlightGrey|  Apple thisApple = apple[i];
+|\highlightGrey|  if(thisApple.isEdible()){
+|\highlightGrey|    thisApple.eat();
+    Logger.log("Apple eaten");
+  }
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+|\highlightGrey|for(int i = 0; i<apples.length; i++){
+|\highlightGrey|  Apple thisApple = apple[i];
+|\highlightGrey|  if(thisApple.isEdible()){
+|\highlightGrey|    thisApple.eat();
+  }
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Example of clone that may not be detected when comparing subtrees.}
+\label{fig:subtreecomparison}
+\end{figure*}
 

### 2019-11-22 pldi/paper.tex
Bla

@@
 
-To allow easy experimentation with code clone defitions and methods, we propose a DSL to configure clone detection.
+To allow easy experimentation with code clone defitions and methods, we propose a DSL to configure clone detection. \todo{finish this}
 
@@
 An example of this is shown in Fig.~\ref{fig:subtreecomparison}.
+In this figure, both the for-loop and the if-statement do not match completely between the two fragments.
+Because of that, when comparing subtrees, both would not indicate a match.
 
@@
 \subsection{Search Root}
+Some clone detection tools only search for clones inside of method bodies \cite{ragkhitwetsagul2019siamese}.
+To allow for such targeted analyses, we introduce the \textbf{SearchRoot} keyword into CDD.
+This keyword determines where the script will start looking for clones.
+For instance, if we want to limit our analysis to methods and constructors, we can specify the following:
+
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+\noindent\textbf{\textcolor[HTML]{7F0055}{SearchRoot}} MethodDeclaration, ConstructorDeclaration \\
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+
+The \textit{SearchRoot} keyword takes as an argument a comma separated list of nodes.
+The names that are being used here, \textit{MethodDeclaration} and \textit{ConstructorDeclaration}, are the names of the method and constructor declaration nodes.
+The names of these nodes can be the name of any node specified in the JavaParser library \cite{tomassetti2017javaparser}.
+This is because CDD uses JavaParser under the hood to parse an AST and perform clone detection.
 
 \subsection{Exclusions}
+Type 2 clones allow variance in identifiers and literals.
+To allow to exclude nodes in CDD, there is the \textbf{DoNotCompare} keyword.
+This keyword allows to specify a list of nodes that should be excluded from matching.
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+\noindent \textbf{\textcolor[HTML]{7F0055}{DoNotCompare}} SimpleName, LiteralExpr \\
+\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
+This keyword is different from the \textit{Exclude} keyword in that the \textit{Exclude} keyword specifies nodes that will not be included in clones, whereas \textit{DoNotCompare} nodes will be included in clones but do not have to match for them to be considered a clone.
 
 \subsection{Compare Rules}
+Finally, CDD allows to specify any number of compare rules. The syntax for these rules is simple but powerful. \todo{explain}
 

### 2019-11-22 pldi/paper.tex
Refactoring oriented clone types

@@
 
-\section{Results}
+\section{Improving Existing Clone Types with CDD}
+Bla bla refactoring oriented clone types bla bla
+
+\vspace{\baselineskip}
+type1r.cdd\par
+
+\textbf{\textcolor[HTML]{7F0055}{Project}} \textcolor[HTML]{2A00FF}{"/Users/sbaars/Documents/Kim/jhotdraw"}\par
+
+\textbf{\textcolor[HTML]{7F0055}{Size}} (\textcolor[HTML]{7D7D7D}{6 \textbf{nodes} $\&$  20 \textbf{tokens}) $ \vert $  (5 \textbf{nodes} $\&$  25 \textbf{tokens}) $ \vert $  (4 \textbf{nodes} $\&$  30 \textbf{tokens}) $ \vert $  (3 \textbf{nodes} $\&$  35 \textbf{tokens}) $ \vert $  (2 \textbf{nodes} $\&$  40 \textbf{tokens}) $ \vert $  (1 \textbf{nodes} $\&$  50 \textbf{tokens})}\par
+
+\textbf{\textcolor[HTML]{7F0055}{Match}} \textbf{\textcolor[HTML]{7F0055}{LLOC}}\par
+
+\textbf{\textcolor[HTML]{7F0055}{Exclude}} PackageDeclaration, ImportDeclaration\par
+
+\textbf{\textcolor[HTML]{7F0055}{Compare}} ReferenceType, LiteralExpr, MethodCallExpr \textbf{\textcolor[HTML]{7F0055}{FQI}}\par
+
+\vspace{\baselineskip}
+type2r.cdd\par
+
+\textbf{\textcolor[HTML]{7F0055}{Project}} \textcolor[HTML]{2A00FF}{"/Users/sbaars/Documents/Kim/jhotdraw"}\par
+
+\textbf{\textcolor[HTML]{7F0055}{Size}} (\textcolor[HTML]{7D7D7D}{6 \textbf{nodes} $\&$  20 \textbf{tokens}) $ \vert $  (5 \textbf{nodes} $\&$  25 \textbf{tokens}) $ \vert $  (4 \textbf{nodes} $\&$  30 \textbf{tokens}) $ \vert $  (3 \textbf{nodes} $\&$  35 \textbf{tokens}) $ \vert $  (2 \textbf{nodes} $\&$  40 \textbf{tokens}) $ \vert $  (1 \textbf{nodes} $\&$  50 \textbf{tokens})}\par
+
+\textbf{\textcolor[HTML]{7F0055}{Match}} \textbf{\textcolor[HTML]{7F0055}{LLOC}}\par
+
+\textbf{\textcolor[HTML]{7F0055}{Exclude}} PackageDeclaration, ImportDeclaration\par
+
+\textbf{\textcolor[HTML]{7F0055}{Compare}} ReferenceType \textcolor[HTML]{3F7F5F}{/$\ast$  Reference Types $\ast$ /, LiteralExpr /$\ast$  Literals $\ast$ /, MethodCallExpr /$\ast$  Method Calls $\ast$ / \textbf{FQI}}\par
+
+\textbf{\textcolor[HTML]{7F0055}{Compare}} LiteralExpr \textcolor[HTML]{3F7F5F}{/$\ast$  Literals $\ast$ / \textbf{StringMatch} 10$\%$ }\par
+
+\textbf{\textcolor[HTML]{7F0055}{Compare}} NameExpr \textcolor[HTML]{3F7F5F}{/$\ast$  Variables $\ast$ /, MethodCallExpr /$\ast$  Method Calls $\ast$ / \textbf{CompleteMatch} 10$\%$ }\par
+
+\vspace{\baselineskip}
+type3r.cdd\par
+
+\textbf{\textcolor[HTML]{7F0055}{Project}} \textcolor[HTML]{2A00FF}{"/Users/sbaars/Documents/Kim/jhotdraw"}\par
+
+\textbf{\textcolor[HTML]{7F0055}{Size}} (\textcolor[HTML]{7D7D7D}{6 \textbf{nodes} $\&$  20 \textbf{tokens}) $ \vert $  (5 \textbf{nodes} $\&$  25 \textbf{tokens}) $ \vert $  (4 \textbf{nodes} $\&$  30 \textbf{tokens}) $ \vert $  (3 \textbf{nodes} $\&$  35 \textbf{tokens}) $ \vert $  (2 \textbf{nodes} $\&$  40 \textbf{tokens}) $ \vert $  (1 \textbf{nodes} $\&$  50 \textbf{tokens})}\par
+
+\textbf{\textcolor[HTML]{7F0055}{Match}} \textbf{\textcolor[HTML]{7F0055}{LLOC}}\par
+
+\textbf{\textcolor[HTML]{7F0055}{Exclude}} PackageDeclaration, ImportDeclaration\par
+
+\textbf{\textcolor[HTML]{7F0055}{Compare}} ReferenceType \textcolor[HTML]{3F7F5F}{/$\ast$  Reference Types $\ast$ /, LiteralExpr /$\ast$  Literals $\ast$ /, MethodCallExpr /$\ast$  Method Calls $\ast$ / \textbf{FQI}}\par
+
+\textbf{\textcolor[HTML]{7F0055}{Compare}} LiteralExpr \textcolor[HTML]{3F7F5F}{/$\ast$  Literals $\ast$ / \textbf{StringMatch} 10$\%$ }\par
+
+\textbf{\textcolor[HTML]{7F0055}{Compare}} NameExpr \textcolor[HTML]{3F7F5F}{/$\ast$  Variables $\ast$ /, MethodCallExpr /$\ast$  Method Calls $\ast$ / \textbf{CompleteMatch} 10$\%$ }\par
+
+\textbf{\textcolor[HTML]{7F0055}{Compare}} $\ast$  \textbf{\textcolor[HTML]{7F0055}{Subnodes}} Statement \textcolor[HTML]{7D7D7D}{10$\%$  /$\ast$  We allow 10$\%$  variance in Statements $\ast$ /}\par
+
+%\section{Results}
 

### 2019-11-26 pldi/paper.tex
Fixed line break

@@
 Different clone detection techniques have been proposed in literature \cite{sheneamer2016survey}:
-\textbf{Textual}: Code lines are textually compared.
+\\ \textbf{Textual}: Code lines are textually compared.
 Advantages are that textual approaches are often simpler, easier to implement and are independent of language.
@@
 \section{Improving Existing Clone Types with CDD}
-Bla bla refactoring oriented clone types bla bla
+Bla bla refactoring oriented clone types bla bla HOI
 

### 2019-11-29 cefp/paper.tex
General Setup

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Mining Software Repositories for Contextual Information of Code Clones}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Simon Baars\inst{1,2}\orcidID{0000-0001-7905-1027} \and
Ana Oprescu\inst{1,3}\orcidID{0000-0001-6376-0750}}
%
%\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Amsterdam \and
\email{simon.j.baars@gmail.com} \and
\email{A.M.Oprescu@uva.nl}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{First Section}

\bibliographystyle{splncs04}
\bibliography{references}

\end{document}

### 2019-11-29 cefp/paper.tex
Ported context info

@@
 \usepackage{graphicx}
+\usepackage{float}
 % Used for displaying a sample figure. If possible, figure files should
@@
 
-\keywords{First keyword  \and Second keyword \and Another keyword.}
+\keywords{Code Clones \and MSR \and Clone Relation \and Inheritance \and Object-Oriented Programming.}
 \end{abstract}
@@
 %
-\section{First Section}
+\section{Context Analysis of Clones}\label{chap:contextsetup}
+To be able to refactor code clones, CloneRefactor first maps the context of code clones. We define the following aspects of the clone as its context:
+\begin{enumerate}
+  \item \textbf{Relation:} The relation of clone instances among each other through inheritance.
+  \item \textbf{Location:} Where a clone instance occurs in the code.
+  \item \textbf{Contents:} The statements/declarations of a clone instance.
+\end{enumerate}
+We define categories for each of these aspects and enable CloneRefactor to determine the categories of clones.
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.8\columnwidth]{img/context}
+    \caption{Abstract representation of clone classes and clone instances.}
+  \label{fig:clonecontext}
+\end{figure}
+
+Fig.~\ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
+The relation of clones through inheritance is determined for each clone class.
+The location and contents of clones are determined for each clone instance.
+
+\subsection{Relation}\label{sec:setuprelation}
+When merging code clones in object-oriented languages, it is important to consider the inheritance relation between clone instances. This relation has a big impact on how a clone should be refactored.
+
+Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other.
+To do this, they first define several categories for the relation between clone instances in object-oriented languages.
+These categories are as follows:
+\begin{enumerate}
+  \item \textbf{Same Method}: All instances of the clone class are in the same method.
+  \item \textbf{Same Class}: All instances of the clone class are in the same class.
+  \item \textbf{Superclass}: All instances of the clone class are in a class that are child or parent of each other.
+  \item \textbf{Sibling Class}: All instances of the clone class have the same parent class.
+    \item \textbf{Ancestor Class}: All instances of the clone class are superclasses except for the direct superclass.
+  \item \textbf{First Cousin Class}: All instances of the clone class have the same grandparent class.
+\item \textbf{Same Hierarchy Class}: All instances of the clone class belong to the same inheritance hierarchy, but do not belong to any of the other categories.
+\item \textbf{Same External Superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
+\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
+\end{enumerate}
+
+We added the following categories, to gain more information about clones and reduce the number of unrelated clones:
+
+\begin{enumerate}
+\item \textbf{Same Direct Interface}: All instances of the clone class are in a class or interface implement the same interface.
+\item \textbf{Same Indirect Interface}: All instances of the clone class are in a class or interface that have a common interface anywhere in their inheritance hierarchy.
+\item \textbf{No Direct Superclass}: All instances of the clone class are in a class that does not have any superclass.
+\item \textbf{No Indirect Superclass}: All instances of the clone class are in a class that does not have any external classes in its inheritance hierarchy.
+\item \textbf{External Ancestor}: All instances of the clone class are in a class that does not have any external classes in its inheritance hierarchy.
+\end{enumerate}
+
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.6\columnwidth]{img/Relation}
+      \caption{Abstract figure displaying relations of clone classes. Arrows represent superclass relations.}
+  \label{fig:clonerelation}
+\end{figure}
+
+We separate these relations into the following categories, because of their related refactoring opportunities:
+\begin{itemize}
+  \item \textbf{Common Class}: \textit{Same Method}, \textit{Same Class}
+  \item \textbf{Common Hierarchy}: \textit{Superclass}, \textit{Sibling Class}, \textit{Ancestor Class}, \textit{First Cousin}, \textit{Same Hierarchy}
+  \item \textbf{Common Interface}: \textit{Same Direct Interface}, \textit{Same Indirect Interface}
+  \item \textbf{Unrelated}: \textit{No Direct Superclass}, \textit{No Indirect Superclass}, \textit{External Superclass}, \textit{External Ancestor}
+\end{itemize}
+
+Every clone class only has a single relation, which is the first relation from the above list that the clone class applies to.
+For instance: all ``Superclass'' clones also apply to ``Same Hierarchy'', but because ``Superclass'' is earlier in the above list they will get the ``Superclass'' relation.
+This is because the items earlier in the above list denote a more favorable refactoring.
+
+When CloneRefactor applies automated refactorings, it uses this inheritance relation to see where it must place the refactored code.
+We explain this for each relation category over the following sections.
+
+%To determine the relation for a given clone class, we compare each node in a clone instance with the respective nodes in each other clone instance within a clone class.
+%So for a clone class with x clone instances and each clone instance has y nodes, we perform:
+
+%\begin{equation}\label{eq:sameclass}
+%\frac{x * (x + 1)}{2} * y
+%\end{equation}
+
+%comparisons to determine the relation.
+Each of these checks will result in one of the relations from the list above.
+Of these relations, the item lowest in the list is going to be the relation of the clone class.
+So for instance, if a clone class has 15 nodes that denote a \textit{Superclass} relation but 3 nodes are \textit{Unrelated}, the clone class becomes \textit{Unrelated}.
+
+\subsubsection{Common Class}
+The \textit{Same method} and \textit{Same class} relations share a common refactoring opportunity.
+Clones of both these categories, when extracted to a new method, can be placed in the same class.
+Both of these relations are most favorable for refactoring, as they require a minimal design tradeoff.
+Furthermore, global variables that are used in the class can be used without having to create method parameters.
+
+ %We define the method as the first method declaration that is encountered when following the parent nodes in the AST for a given cloned node.
+%Please note that a clone instance may not always be in a method, for which this predicate will fail.
+
+%Clone classes are flagged as \textit{Same method} if all their clone instances are found in the same method.
+Cloned classes are flagged as \textit{Same class} if all their clone instances are found in the same class.
+%We define the class as the first class declaration that is encountered when following the parent nodes in the AST for a given cloned node.
+
+\subsubsection{Common Hierarchy}
+Clones that are in a common hierarchy can be refactored by using the ``Extract Method'' refactoring method followed by ``Pull Up Method'' until the method reaches a location that is accessible by all clone instances.
+However, the more often ``Pull Up Method'' has to be used, the more detrimental the effect is on system design.
+This is because putting a lot of functionality in classes higher up in an inheritance structure can result in the ``God Object'' anti-pattern.
+A god object is an object that knows too much or does too much~\cite{fowler2018refactoring}.
+
+%Clone classes are flagged as \textit{Superclass} if the classes in which the clone instances are found are parent and child class of each other.
+Clone classes are flagged as \textit{Siblings} if the classes in which their clone instances are found all share the same parent and this parent class is not external.
+Clone classes are flagged as \textit{First Cousin} if the classes in which their clone instances are found all share the same grandparent and this grandparent class is not external.
+
+%Clone classes nodes are flagged as \textit{Ancestor} if the classes in which their clone instances are found are recursively the parent of an antecedent.
+Cloned nodes are flagged as \textit{Same Hierarchy} if the classes in which these nodes are found are all in the same inheritance hierarchy and not linked by any external classes.
+
+\subsubsection{Common Interface}
+Many object-oriented languages know the concept of ``interfaces'', which are used to specify a behavior that classes must implement.
+As code clones describe functionality and interfaces originally did not allow for functionality, interfaces did not open up refactoring opportunities for duplicated code.
+However, many programming languages nowadays support default implementations in interfaces.
+Since Java 7 and C\# 8, these programming languages allow for functionality to be defined in interfaces.
+Many other object-oriented languages like Python allow this by nature, as they do not have a true notion of interfaces.
+
+The greatest downside on system design of putting functionality in interfaces is that interfaces are per definition part of a classes' public contract.
+That is, all functionality that is shared between classes via an interface cannot be hidden by stricter visibility.
+Because of that, we favor all ``Common Hierarchy'' refactoring opportunities over ``Common Interface''.
+
+%To check whether two cloned nodes have a \textit{Same Direct Interface} relation, we check that the classes to which these nodes belong both implement the same interface type.
+To check whether two cloned nodes have a \textit{Same Indirect Interface} relation, we recursively walk all types the class or interface of the cloned nodes implement and extend.
+The common interface that is closest to the cloned node in terms of depth of recursion will be flagged as the refactoring candidate.
+
+\subsubsection{Unrelated}
+Clones are unrelated if they share no common class or interface in their inheritance structure.
+These clones are least favorable for refactoring, because their refactoring will almost always have a major impact on system design.
+We formulated four categories of unrelated clones to look into their refactoring opportunities.
+
+Cloned classes with a \textit{No Direct Superclass} relation mark the opportunity for creating a superclass abstraction and placing the extracted method there.
+For clone classes with a \textit{No Indirect Superclass} relation, CloneRefactor creates such an abstraction for the ancestor that does not have a parent.
+Clone classes with a \textit{External Superclass} or \textit{External Ancestor} relation obstruct the possibility of creating a superclass abstraction.
+In such a case, CloneRefactor creates an interface abstraction to make their relation explicit.
+
+%Cloned nodes are flagged \textit{No Direct Superclass} if they are in classes that do currently not have a parent.
+This marks the opportunity for creating a superclass abstraction and placing the extracted method there.
+Cloned nodes are flagged \textit{No Indirect Superclass} if any of their ancestors do not have a parent.
+In such a case, it would be possible to create such an abstraction for the ancestor that does not have a parent.
+
+%Cloned nodes are flagged \textit{External Superclass} if they are in a class which has an external parent.
+Cloned nodes are flagged \textit{External Ancestor} if one of their ancestors has an external parent.
+Both of these relations obstruct the possibility of creating a superclass abstraction.
+In such a case, an interface abstraction could be created to make their relation explicit.
+
+\subsection{Location}\label{sec:setuplocation}
+A paper by Lozano et al.~\cite{lozano2007evaluating} discusses the harmfulness of cloning.
+The authors argue that 98\% are produced at method-level.
+However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
+We decided to measure the locations of clones through static analysis on our dataset.
+We chose the following categories:
+\begin{enumerate}
+  \item \textbf{Method/Constructor Level:} A clone instance that does not exceed the boundaries of a single method or constructor (optionally including the declaration of the method or constructor itself).
+  \item \textbf{Class Level:} A clone instance in a class, that exceeds the boundaries of a single method or contains something else in the class (like field declarations, other methods, etc.).
+  \item \textbf{Interface/Enumeration Level:} A clone that is (a part of) an interface or enumeration.
+\end{enumerate}
+We check the location of each clone instance for each of its nodes.
+If any node reports a different location from the others, we choose the location that is lowest in the above list.
+So for instance, if a clone instance has 15 nodes that denote a \textit{Method Level} location but 3 nodes are \textit{Class Level}, the clone instance becomes \textit{Class Level}.
+
+\subsubsection{Method/Constructor Level Clones} \label{sec:methodlevelcr}
+Method/Constructor Level clones denote clones that are found in either a method or constructor.
+A constructor is a special method that is called when an object is instantiated.
+Most modern clone refactoring studies only focus on clones at method level~\cite{choi2011extracting, yue2018automatic, kodhai2013method, arcelli2013software, lin2014clonepedia, mandal2014automatic, balazinska2000advanced, yongting2018detection, bouktif2006novel, fanqi2014using, devi2016study}.
+This is because most clones reside at those places~\cite{lozano2007evaluating, fontana2015duplicated} and most of those clones can be refactored with a relatively simple set of refactoring techniques~\cite{kodhai2013method, fontana2015duplicated}.
+
+%To detect whether a given clone instance is at Method Level, we check for each node in the clone instance whether it has an ancestor node that is a method declaration.
+A clone instance is considered ``Method Level'' if:
+
+%\begin{equation}\label{eq:samemethod}
+%\forall (n \in I)\text{ } Tn = \text{MethodDeclaration} \lor \exists (p \in ancestors(n)) \text{ } Tp = \text{MethodDeclaration}
+%\end{equation}
+
+%Where \textit{T} is the type of a node.
+\textit{ancestors(n)} denotes all of ancestor nodes of a node.
+The ancestor nodes are all recursive parents of a given node in the AST.
+Apart from this, we check that the MethodDeclaration ancestor of each clone instance is the same, to be sure the clone only spans a \textit{single} method.
+Figure \ref{fig:methodlevelclone} shows an example of a method level clone and its recursive parents.
+
+%\begin{figure}[H]
+%\begin{parcolumns}{2}
+%\colchunk[1]{
+%\begin{javacode}
+%  public void doA() { // |\textcolor{pgreen}{$p_2$}|
+%    public class Class1 { // |\textcolor{pgreen}{$p_3$}|
+%    if(isA()) // |\textcolor{pgreen}{$p_1$}|
+%|\highlightYellow|      doB(); // |\textcolor{pgreen}{$n_1$}|
+%  }
+%}
+%\end{javacode}}
+%\colchunk[2]{
+%\begin{javacode}
+%public class Class2 { // |\textcolor{pgreen}{$p_3$}|
+%  public void doB() { // |\textcolor{pgreen}{$p_2$}|
+%    if(isB()) // |\textcolor{pgreen}{$p_1$}|
+%|\highlightYellow|      doB(); // |\textcolor{pgreen}{$n_2$}|
+%  }
+%}
+%\end{javacode}}
+%\end{parcolumns}
+%\caption{Example of a method level clone and its parents.}
+%\label{fig:methodlevelclone}
+%\end{figure}
+
+\subsubsection{Class/Interface/Enumeration Level Clones}
+Class/Interface/Enumeration Level clone instances are found inside the body of one of these declarations and optionally include the declaration itself.
+It can also be a clone instance that exceeds the boundaries of a single method.
+These clone instances can contain fields, (abstract) methods, inner classes, enumeration fields, etc.
+These types of clones require various refactoring techniques to refactor.
+For instance, we might have to move fields in an inheritance hierarchy.
+Or, we might have to perform a refactoring on more of an architectural level, if a large set of methods is cloned.
+
+%We detect these clones in the same way we detect method level clones: we walk up the AST until we find the first node that indicates one of these categories.
+
+\subsection{Contents}\label{sec:setupcontents}
+Finally, we looked at what nodes individual clone instances span.
+We selected a set of categories based on empirical evaluation of a set of clones in our dataset.
+We selected the following categories to be relevant for refactoring:
+\begin{enumerate}
+  \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
+  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method/constructor. The declaration itself is not included.
+  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
+  \item \textbf{Only Fields:} A clone that spans only global variables.
+  \item \textbf{Other:} Anything that does not match with above-stated categories.
+\end{enumerate}
+
+\subsubsection{Full Method/Constructor/Class/Interface/Enumeration}
+These categories denote that a full declaration, including its body, is cloned with another declaration.
+These categories often denote redundancy and are often easy to refactor: one of both declarations is redundant and should be removed.
+All usages of the removed declaration should be redirected to the clone instance that was not removed.
+Sometimes, the declaration should be moved to a location that is accessible by all usages.
+%We check for clones in this category by checking that the first node in a clone instance is a declaration and the last node in the clone instance is the last node in the body of that declaration.
+
+\subsubsection{Partial Method/Constructor}
+These categories describe clone instances which are found in the body of a method or constructor.
+These clones can often be refactored by extracting a new method out of the cloned code.
+%We detect such clones by checking that each node in the clone instance has an ancestor node that is a MethodDeclaration, but none of the nodes is a method declaration.
+We describe the procedure by with we recursively seek the parent nodes of a node in Section~\ref{sec:methodlevelcr}.
+
+\subsubsection{Several Methods}
+Several methods cloned in a single class is a strong indication of implicit dependencies between two classes.
+This increases the chance that these classes are missing some form of abstraction, or their abstraction is used inadequately.
+%We detect such clones by checking that each cloned node has a parent node that is a MethodDeclaration.
+This is the same process as described in equation \ref{eq:samemethod}.
+Additionally, we check that the MethodDeclaration ancestor of the first node in the clone instance differs from the last, to be sure that the clone instance spans over at least two methods.
+
+\subsubsection{Only Fields}
+This category denotes that the clone spans over only global variables/fields that are declared outside of a method.
+This indicates data redundancy: pieces of data have an implicit dependency.
+In such cases, these fields may have to be encapsulated in a new object.
+Or, the fields should be somewhere in the inheritance structure where all objects containing the clone can access them.
+%We check for this category by validating that all nodes in the clone instance are a VariableDeclarator.
+Because VariableDeclarators in methods would already fall into the ``Partial Method'' category, this includes only globally defined fields.
+
+\subsubsection{Other}
+The ``Other'' category denotes all configurations of clone contents that do not fall into above categories.
+Often, these are combinations of the above stated concepts.
+For instance, a combination of constructors and methods or a combination of fields and methods is cloned.
+Such clones indicate, like the ``Several Methods'', the requirement of performing a more architectural-level refactoring.
+These are often more complicated to refactor, especially when aiming to automate this process.
 

### 2019-11-29 cefp/paper.tex
Experimental setup

@@
 \usepackage{float}
+\usepackage{hyperref}
 % Used for displaying a sample figure. If possible, figure files should
@@
 
+\section{Experimental Setup}
+All our experiments are quantitative experiments, measured over a corpus using CloneRefactor.
+In this chapter, we first explain the corpus we use.
+We then explain how we calculate the impact of refactorings on the software maintainability.
+
+\subsection{The Corpus}\label{chap:corpus}
+For our experiments we use a large corpus of open-source projects assembled by Allamanis et al.~\cite{githubCorpus2013}\footnote{The corpus can be downloaded at: \url{http://groups.inf.ed.ac.uk/cup/javaGithub/}}.
+This corpus contains a set of Java projects from GitHub, selected by the number of forks.
+The projects and files in this corpus were de-duplicated manually.
+This results in a variety of Java projects that reflect the quality of average open-source Java systems and are useful to perform measurements on.
+
+Because CloneRefactor requires all dependencies for the projects it analyses, we created a set of scripts\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} to filter the corpus for all projects for which we can obtain all dependencies using Maven.
+
+\subsection{Resulting corpus}
+This procedure results in 2,267 Java projects including all their dependencies\footnote{The full list of projects is in the following file in our GitHub repository: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts/blob/master/filtered_projects.txt}}.
+The projects vary in size and quality.
+The total size of all projects is 14.210.357 lines (11,315,484 when excluding whitespace) over a total of 99,586 Java files.
+This is an average of 6,268 lines over an average of 44 files per project, 141 lines on average per file.
+The largest project in the corpus is \textit{VisAD} with 502,052 lines over 1,527 files.
+
+\subsection{Tool Validation}
+We have validated the correctness of CloneRefactor through unit tests and empirical validation.
+First, we created a set of 57 control projects\footnote{Control projects for testing CloneRefactor: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to verify the correctness in many (edge) cases.
+These projects test each identified relation, location, contents and refactorability category (see Section \ref{chap:contextsetup} and \ref{sec:refactorabilitysetup}), to see whether they are correctly identified.
+Next, we run the tool over the corpus and manually verify samples of the acquired results.
+This way, we check the correctness of the identified clones, their context, and their proposed refactoring.
+
+We also test the correctness of the resulting code after refactoring.
+For this, we use a project named JFreeChart\footnote{JFreeChart is available on GitHub: \url{https://github.com/jfree/jfreechart}}.
+JFreeChart has high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor.
+We run CloneRefactor manually over the JFreeChart project, run its test cases and check the correctness of the proposed refactorings.
+
+\section{Results}
+
+\section{Conclusion}
+
 \bibliographystyle{splncs04}

### 2019-11-29 cefp/paper.tex
Updates from Overleaf

@@
 %
+\section{Introduction}
+
 \section{Context Analysis of Clones}\label{chap:contextsetup}
@@
   \centering
-    \includegraphics[width=0.8\columnwidth]{img/context}
+    \includegraphics[width=1\columnwidth]{img/context}
     \caption{Abstract representation of clone classes and clone instances.}
@@
   \centering
-    \includegraphics[width=0.6\columnwidth]{img/Relation}
+    \includegraphics[width=0.7\columnwidth]{img/Relation}
       \caption{Abstract figure displaying relations of clone classes. Arrows represent superclass relations.}
@@
 First, we created a set of 57 control projects\footnote{Control projects for testing CloneRefactor: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to verify the correctness in many (edge) cases.
-These projects test each identified relation, location, contents and refactorability category (see Section \ref{chap:contextsetup} and \ref{sec:refactorabilitysetup}), to see whether they are correctly identified.
+These projects test each identified relation, location, contents and refactorability category (see Section \ref{chap:contextsetup}), to see whether they are correctly identified.
 Next, we run the tool over the corpus and manually verify samples of the acquired results.

### 2019-11-29 cefp/paper.tex
Added some results

--- 2019-11-29 cefp/paper.tex
@@
 \usepackage{hyperref}
+\usepackage[style=ieee,citestyle=numeric-comp,dashed=false]{biblatex}
+\usepackage{booktabs}
+\usepackage{multirow}
+\addbibresource{refs.bib}
 % Used for displaying a sample figure. If possible, figure files should
@@
 \section{Results}
+To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones (see Section~\ref{chap:contextsetup}).
+
+\subsection{Relation} \label{sec:relationresults}
+Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Section~\ref{sec:setuprelation}).
+% Sander: is dat plaatje met overzicht van relaties van clone classen weg of ergens anders? hij is hier ook wel handig
+
+\begin{table}[H]
+\centering
+\begin{tabular}{@{}llrrrr@{}}
+\toprule
+\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{\%}} & \textit{\textbf{Total}} & \textit{\textbf{\%}} \\ \midrule
+\multirow{2}{*}{Common Class} & Same Class & 22,893 & 26.8\% & \multirow{2}{*}{31,848} & \multirow{2}{*}{37.2\%} \\ \cmidrule(lr){2-4}
+ & Same Method & 8,955 & 10.5\% & & \\ \midrule
+\multirow{5}{*}{Common Hierarchy} & Sibling & 15,588 & 18.2\% & \multirow{5}{*}{20,342}& \multirow{5}{*}{23.8\%} \\ \cmidrule(lr){2-4}
+ & Superclass & 2,616 & 3.1\% & & \\ \cmidrule(lr){2-4}
+ & First Cousin & 1,219 & 1.4\% & & \\ \cmidrule(lr){2-4}
+ & Common Hierarchy & 720 & 0.8\% & & \\ \cmidrule(lr){2-4}
+ & Ancestor & 199 & 0.2\% & & \\ \midrule
+\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & 12.5\% & \multirow{4}{*}{20,314}& \multirow{4}{*}{23.7\%} \\ \cmidrule(lr){2-4}
+ & External Superclass & 4,525 & 5.3\% & & \\ \cmidrule(lr){2-4}
+ & External Ancestor & 3,347 & 3.9\% & & \\ \cmidrule(lr){2-4}
+ & No Indirect Superclass & 1,765 & 2.1\% & & \\ \midrule
+\multirow{2}{*}{Common Interface} & Same Direct Interface & 7,522 & 8.8\% & \multirow{2}{*}{13,074} & \multirow{2}{*}{15.3\%} \\ \cmidrule(lr){2-4}
+ & Same Indirect Interface & 5,552 & 6.5\% & & \\ \bottomrule
+\end{tabular}
+\caption{Number of clone classes per clone relation.}
+\label{tab:relation}
+\end{table}
+
+Our results show that most clones (37\%) are in a common class. 24\% of clones are in a common hierarchy. Another 24\% of clones are unrelated. 15\% of clones are in an interface.
+
+\subsection{Location}
+Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different location categories (see Section~\ref{sec:setuplocation}).
+We can see from these results that nearly 80\% of clones are found at method level.
+17\% of clones are found at class level, meaning they exceed the boundaries of a single method (or do not span methods at all).
+Constructors account for approximatelyTop- 3\% of clones.
+In interfaces, only 1\% of clones is found.
+
+\begin{table}[H]
+\centering
+\begin{tabular}{@{}lrr@{}}
+\toprule
+\textit{\textbf{Category}} & \textit{\textbf{Clone instances}} & \textit{\textbf{\%}} \\ \midrule
+Method Level & 232,545 & 78.43\% \\
+Class Level & 50,402 & 17.00\% \\
+Constructor Level & 10,039 & 3.39\% \\
+Interface Level & 2,693 & 0.91\% \\
+Enum Level & 788 & 0.27\% \\
+\end{tabular}
+\caption{Amount of clone instances with a per location category.}
+\label{tab:location}
+\end{table}
+
+\subsection{Contents}
+Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different content categories (see Section~\ref{sec:setupcontents}).
+
+\begin{table}[H]
+\centering
+\begin{tabular}{@{}llrrrr@{}}
+\toprule
+\textit{\textbf{Category}} & \textit{\textbf{Contents}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
+\multirow{2}{*}{Partial} & Method Body & 219,540 & 74.05\% & \multirow{2}{*}{229,521}& \multirow{2}{*}{77.42\%} \\ \cmidrule(lr){2-4}
+ & Constructor Body & 9,981 & 3.37\% & & \\ \midrule
+\multirow{3}{*}{Other} & Several Methods & 22,749 & 7.67\% & \multirow{3}{*}{53,773} & \multirow{3}{*}{18.14\%} \\ \cmidrule(lr){2-4}
+ & Only Fields & 17,700 & 5.97\% & & \\ \cmidrule(lr){2-4}
+ & Other & 13,324 & 4.49\% & & \\ \midrule
+ \multirow{5}{*}{Full} & Full Method & 12,990 & 4.38\% & \multirow{5}{*}{13,173}& \multirow{5}{*}{4,44\%} \\ \cmidrule(lr){2-4}
+  & Full Interface & 64 & 0.02\% & & \\ \cmidrule(lr){2-4}
+  & Full Constructor & 58 & 0.02\% & & \\ \cmidrule(lr){2-4}
+  & Full Class & 37 & 0.01\% & & \\ \cmidrule(lr){2-4}
+  & Full Enum & 24 & 0.01\% & & \\ \bottomrule
+\end{tabular}
+\caption{Number of clone instances for clone contents categories}
+\label{tab:contents}
+\end{table}
+
+From these results, we see that 74\% of clones span part of a method body (77\% if we include constructors).
+8\% of clones span several methods.
+6\% of clones span only global variables.
+Only 4\% of clones span a full declaration (method, class, constructor, etc.).
+
+\section{Discussion}
+Regarding clone context, our results indicate that most clones (37\%) are in a common class.
+This is favorable for refactoring because the extracted method does not have to be moved after extraction.
+24\% of clones are in a common hierarchy.
+These refactorings are also often favorable.
+Another 24\% of clones are unrelated, which is often unfavorable because it often requires a more comprehensive refactoring.
+15\% of clones are in an interface.
+
+Regarding clone contents, 74\% of clones span part of a method body (77\% if we include constructors).
+8\% of clones span several methods, which often require refactorings on a more architectural level.
+6\% of clones span only global variables, requiring an abstraction to encapsulate these data declarations.
+Only 4\% of clones span a full declaration (method, class, constructor, etc.).
 
@@
 
-\bibliographystyle{splncs04}
-\bibliography{references}
+%\bibliographystyle{splncs04}
+\printbibliography
 

### 2019-11-29 cefp/paper.tex
Conclusion and new title

@@
 %
-\title{Mining Software Repositories for Contextual Information of Code Clones}
+\title{Determining Most-Suitable Refactoring Techniques for Refactoring Code Clones}
 %
@@
 \section{Introduction}
+
+\section{Background}
 
@@
 \section{Conclusion}
+To determine which refactoring techniques are most suitable to refactor most clones, we analyzed their context.
+We measured the \textbf{relation} through inheritance of clone instances in a clone class.
+In our corpus, we found that 37\% of clones are found in the same class.
+24\% of clones are in the same inheritance hierarchy.
+Another 24\% of clones are unrelated.
+The final 15\% of clones have the same interface.
+We also looked at the \textbf{location} of clones: 78\% of clones are found at method-level of which 77\% is found in the body of a method or constructor.
+
+From this, we conclude that the ``Extract Method'' refactoring technique is most suitable to refactor most clones.
 

### 2019-12-02 cefp/paper.tex
Abstract

@@
 %
-\title{Determining Most-Suitable Refactoring Techniques for Refactoring Code Clones}
+\title{Finding the Most Suitable Code Clone Refactoring Techniques by Mapping Clone Context}
 %
@@
 \begin{abstract}
-The abstract should briefly summarize the contents of the paper in
-15--250 words.
+One of the most important purposes of code clone analyses is as input for refactoring.
+Which refactoring technique to use depends on where a clone is found and what the relation between clone instances in a clone class is.
+We define three influencing factors on how a clone should be refactored: Relation, Location and Contents.
+The Relation describes the inheritance relation among the clone instances in a clone class.
+The Location describes where a clone instance is found in the source code.
+The Contents describe what a clone instance spans.
+
+We find that most clones (77\%) are in the body of methods or constructors and thus the ``Extract Method'' refactoring technique applies.
+What further techniques are requires for the refactoring depends on the relation among the clone instances of a clone.
+We define four relations that require different further refactoring techniques: Common Class, Common Hierarchy, Common Interface, Unrelated.
+For each of these, we define subcategories to facilitate further understanding in what relations clones are found in the codebase.
+
+% What further techniques apply when refactoring a clone using the ``Extract Method'' technique depends on the relation among its clone instances.
+If clone instances share a common class, no further refactoring techniques are required.
+If they are in the same inheritance hierarchy, ``Pull-Up Method'' can be used till the extracted method is in a location accessible by all instances.
 
@@
 \section{Introduction}
+Duplicate code fragments are often considered as bad design~\cite{fowler2018refactoring}.
+They increasing maintenance efforts or causing bugs in evolving software~\cite{heitlager2007practical}.
+Changing one occurrence of a duplicated fragment may require changes in other occurrences~\cite{ostberg2014automatically}.
+Furthermore, duplicated code was shown to account for up to 25\% of total system volume~\cite{bruntink2005use}, entailing more code to be maintained.
+
+Several refactoring techniques can be used to reduce duplication in source code.
+Which refactoring technique to apply depends on where a clone is located and what the relation is between similar code fragments \cite{koni2001scenario}.
+Subsequent studies have performed statistical measurements on how many clones fall into these location and relation categories \cite{fontana2012duplicated, fontana2015duplicated}.
+
+We extend the state-of-the-art \cite{fontana2015duplicated} by defining location, relation and contents categories for clones to determine how they should be refactored.
+The extra categories we propose help to propose a refactoring opportunity that can automatically be applied, rather than merely suggesting the technique that has to be used \cite{fontana2015duplicated}.
+
+We perform statistical measurements on a large corpus of open-source software systems to determine which relation, location and contents category has the most clones.
+We find that 77\% of clones is found in the bodies of constructors and methods, which indicate clones that can be refactored by applying the ``Extract Method'' refactoring technique.
+Clones were found in very diverse relations, which indicates that in
 
 \section{Background}
+We use two definitions to argue about code clones~\cite{roy2007survey}:
+\\ \textbf{Clone instance}: A single cloned fragment.
+\\ \textbf{Clone class}: A set of similar clone instances.
+
+To argue about the similarity relation between clone instances in a clone class, several clone type definitions have been proposed~\cite{roy2007survey}:
+\\\\
+\textbf{Type 1:} Identical code fragments except for variations in whitespace (may also be variations in layout) and comments.\\
+\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
+\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\
+
+A higher type of clone means that it is harder to detect.
+It also makes the clone harder to refactor, as more transformations would be required.
+Higher clone types also become more disputable whether they actually indicate a harmful anti-pattern (as not every clone is harmful~\cite{jarzabek2010clones, kapser2008cloning}).
 
@@
 \section{Experimental Setup}
-All our experiments are quantitative experiments, measured over a corpus using CloneRefactor.
-In this chapter, we first explain the corpus we use.
+To find out in which location, relation and contents category most clones are found, we performed statistical measurements on a large corpus of diverse open-source projects.
+We use the tool CloneRefactor\footnote{CloneRefactor is a code clone detection and refactoring tool: \url{https://github.com/SimonBaars/CloneRefactor}} which automatically determines these context aspects of code clones.
+In this section, we first explain the corpus we use.
 We then explain how we calculate the impact of refactorings on the software maintainability.

### 2019-12-02 cefp/paper.tex
Introduction

@@
 
+%We perform statistical measurements on a large corpus of open-source software systems to determine which relation, location and contents category has the most clones.
+We find that 77\% of clones is found in the bodies of constructors and methods, which indicate clones that can be refactored by applying the ``Extract Method'' refactoring technique.
+Clones were found in very diverse relations, which indicates that in
 We perform statistical measurements on a large corpus of open-source software systems to determine which relation, location and contents category has the most clones.
 We find that 77\% of clones is found in the bodies of constructors and methods, which indicate clones that can be refactored by applying the ``Extract Method'' refactoring technique.
-Clones were found in very diverse relations, which indicates that in
+What further techniques apply when refactoring a clone using the ``Extract Method'' technique depends on the relation among its clone instances.
+
+If clone instances share a common class, no further refactoring techniques are required.
+If they are in the same inheritance hierarchy, ``Pull-Up Method'' can be used till the extracted method is in a location accessible by all instances.
+If the instances share a common interface, some languages allow to move the extracted method there.
+Otherwise, if the clone instances are not related, we either have to create a superclass/interface abstaction or create an utility class to put the common functionality.
 

### 2019-12-03 cefp/paper.tex
Working on conclusion

@@
 If the instances share a common interface, some languages allow to move the extracted method there.
-Otherwise, if the clone instances are not related, we either have to create a superclass/interface abstaction or create an utility class to put the common functionality.
+Otherwise, if the clone instances are not related, we either have to create a superclass/interface abstraction or create a utility class to put the common functionality.
 
@@
 \section{Conclusion}
+We defined categories to argue about the contextual information of code clones. These categories are:
+\begin{itemize}
+  \item \textbf{Clone Relation}: The relation between clone instances among each other in a clone class.
+  \item \textbf{Clone Location}: The location of clone instances in the codebase.
+  \item \textbf{Clone Contents}: The contents of clone instances in the codebase.
+\end{itemize}
+For each category we propose subcategories,
+
 To determine which refactoring techniques are most suitable to refactor most clones, we analyzed their context.

### 2019-12-04 cefp/paper.tex
Conclusion

@@
 \end{itemize}
-For each category we propose subcategories,
+For each category we propose subcategories to get more insight into the number of transformations required for the refactoring and their impact on the maintainability of the software.
+We measure the distribution of clones over these categories on a corpus of 2,267 open-source systems to determine in which contexts most clones are found.
 
-To determine which refactoring techniques are most suitable to refactor most clones, we analyzed their context.
-We measured the \textbf{relation} through inheritance of clone instances in a clone class.
-In our corpus, we found that 37\% of clones are found in the same class.
+We looked at the \textbf{location} of clones: 78\% of clones are found at method-level of which 77\% is found in the body of a method or constructor.
+From this, we conclude that the ``Extract Method'' refactoring technique is most suitable to refactor most clones.
+
+We also looked at the \textbf{relation} of clones.
+We found that 37\% of clones are found in the same class.
 24\% of clones are in the same inheritance hierarchy.
@@
 The final 15\% of clones have the same interface.
-We also looked at the \textbf{location} of clones: 78\% of clones are found at method-level of which 77\% is found in the body of a method or constructor.
-
-From this, we conclude that the ``Extract Method'' refactoring technique is most suitable to refactor most clones.
+This implies that most clone refactorings require more transformations than only method extraction to ensure that the extracted method is accessible by all clone instances.
 

### 2019-12-06 cefp/paper.tex
Updates from Overleaf

--- 2019-12-02 cefp/paper.tex
@@
 \usepackage{hyperref}
-\usepackage[style=ieee,citestyle=numeric-comp,dashed=false]{biblatex}
-\usepackage{booktabs}
-\usepackage{multirow}
-\addbibresource{refs.bib}
 % Used for displaying a sample figure. If possible, figure files should
@@
 %
-\title{Finding the Most Suitable Code Clone Refactoring Techniques by Mapping Clone Context}
+\title{Mining Software Repositories for Contextual Information of Code Clones}
 %
@@
 \begin{abstract}
-One of the most important purposes of code clone analyses is as input for refactoring.
-Which refactoring technique to use depends on where a clone is found and what the relation between clone instances in a clone class is.
-We define three influencing factors on how a clone should be refactored: Relation, Location and Contents.
-The Relation describes the inheritance relation among the clone instances in a clone class.
-The Location describes where a clone instance is found in the source code.
-The Contents describe what a clone instance spans.
-
-We find that most clones (77\%) are in the body of methods or constructors and thus the ``Extract Method'' refactoring technique applies.
-What further techniques are requires for the refactoring depends on the relation among the clone instances of a clone.
-We define four relations that require different further refactoring techniques: Common Class, Common Hierarchy, Common Interface, Unrelated.
-For each of these, we define subcategories to facilitate further understanding in what relations clones are found in the codebase.
-
-% What further techniques apply when refactoring a clone using the ``Extract Method'' technique depends on the relation among its clone instances.
-If clone instances share a common class, no further refactoring techniques are required.
-If they are in the same inheritance hierarchy, ``Pull-Up Method'' can be used till the extracted method is in a location accessible by all instances.
+The abstract should briefly summarize the contents of the paper in
+15--250 words.
 
@@
 \section{Introduction}
-Duplicate code fragments are often considered as bad design~\cite{fowler2018refactoring}.
-They increasing maintenance efforts or causing bugs in evolving software~\cite{heitlager2007practical}.
-Changing one occurrence of a duplicated fragment may require changes in other occurrences~\cite{ostberg2014automatically}.
-Furthermore, duplicated code was shown to account for up to 25\% of total system volume~\cite{bruntink2005use}, entailing more code to be maintained.
-
-Several refactoring techniques can be used to reduce duplication in source code.
-Which refactoring technique to apply depends on where a clone is located and what the relation is between similar code fragments \cite{koni2001scenario}.
-Subsequent studies have performed statistical measurements on how many clones fall into these location and relation categories \cite{fontana2012duplicated, fontana2015duplicated}.
-
-We extend the state-of-the-art \cite{fontana2015duplicated} by defining location, relation and contents categories for clones to determine how they should be refactored.
-The extra categories we propose help to propose a refactoring opportunity that can automatically be applied, rather than merely suggesting the technique that has to be used \cite{fontana2015duplicated}.
-
-%We perform statistical measurements on a large corpus of open-source software systems to determine which relation, location and contents category has the most clones.
-We find that 77\% of clones is found in the bodies of constructors and methods, which indicate clones that can be refactored by applying the ``Extract Method'' refactoring technique.
-Clones were found in very diverse relations, which indicates that in
-We perform statistical measurements on a large corpus of open-source software systems to determine which relation, location and contents category has the most clones.
-We find that 77\% of clones is found in the bodies of constructors and methods, which indicate clones that can be refactored by applying the ``Extract Method'' refactoring technique.
-What further techniques apply when refactoring a clone using the ``Extract Method'' technique depends on the relation among its clone instances.
-
-If clone instances share a common class, no further refactoring techniques are required.
-If they are in the same inheritance hierarchy, ``Pull-Up Method'' can be used till the extracted method is in a location accessible by all instances.
-If the instances share a common interface, some languages allow to move the extracted method there.
-Otherwise, if the clone instances are not related, we either have to create a superclass/interface abstaction or create an utility class to put the common functionality.
-
-\section{Background}
-We use two definitions to argue about code clones~\cite{roy2007survey}:
-\\ \textbf{Clone instance}: A single cloned fragment.
-\\ \textbf{Clone class}: A set of similar clone instances.
-
-To argue about the similarity relation between clone instances in a clone class, several clone type definitions have been proposed~\cite{roy2007survey}:
-\\\\
-\textbf{Type 1:} Identical code fragments except for variations in whitespace (may also be variations in layout) and comments.\\
-\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
-\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\
-
-A higher type of clone means that it is harder to detect.
-It also makes the clone harder to refactor, as more transformations would be required.
-Higher clone types also become more disputable whether they actually indicate a harmful anti-pattern (as not every clone is harmful~\cite{jarzabek2010clones, kapser2008cloning}).
 
@@
 \section{Experimental Setup}
-To find out in which location, relation and contents category most clones are found, we performed statistical measurements on a large corpus of diverse open-source projects.
-We use the tool CloneRefactor\footnote{CloneRefactor is a code clone detection and refactoring tool: \url{https://github.com/SimonBaars/CloneRefactor}} which automatically determines these context aspects of code clones.
-In this section, we first explain the corpus we use.
+All our experiments are quantitative experiments, measured over a corpus using CloneRefactor.
+In this chapter, we first explain the corpus we use.
 We then explain how we calculate the impact of refactorings on the software maintainability.
@@
 \section{Results}
-To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones (see Section~\ref{chap:contextsetup}).
-
-\subsection{Relation} \label{sec:relationresults}
-Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Section~\ref{sec:setuprelation}).
-% Sander: is dat plaatje met overzicht van relaties van clone classen weg of ergens anders? hij is hier ook wel handig
-
-\begin{table}[H]
-\centering
-\begin{tabular}{@{}llrrrr@{}}
-\toprule
-\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{\%}} & \textit{\textbf{Total}} & \textit{\textbf{\%}} \\ \midrule
-\multirow{2}{*}{Common Class} & Same Class & 22,893 & 26.8\% & \multirow{2}{*}{31,848} & \multirow{2}{*}{37.2\%} \\ \cmidrule(lr){2-4}
- & Same Method & 8,955 & 10.5\% & & \\ \midrule
-\multirow{5}{*}{Common Hierarchy} & Sibling & 15,588 & 18.2\% & \multirow{5}{*}{20,342}& \multirow{5}{*}{23.8\%} \\ \cmidrule(lr){2-4}
- & Superclass & 2,616 & 3.1\% & & \\ \cmidrule(lr){2-4}
- & First Cousin & 1,219 & 1.4\% & & \\ \cmidrule(lr){2-4}
- & Common Hierarchy & 720 & 0.8\% & & \\ \cmidrule(lr){2-4}
- & Ancestor & 199 & 0.2\% & & \\ \midrule
-\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & 12.5\% & \multirow{4}{*}{20,314}& \multirow{4}{*}{23.7\%} \\ \cmidrule(lr){2-4}
- & External Superclass & 4,525 & 5.3\% & & \\ \cmidrule(lr){2-4}
- & External Ancestor & 3,347 & 3.9\% & & \\ \cmidrule(lr){2-4}
- & No Indirect Superclass & 1,765 & 2.1\% & & \\ \midrule
-\multirow{2}{*}{Common Interface} & Same Direct Interface & 7,522 & 8.8\% & \multirow{2}{*}{13,074} & \multirow{2}{*}{15.3\%} \\ \cmidrule(lr){2-4}
- & Same Indirect Interface & 5,552 & 6.5\% & & \\ \bottomrule
-\end{tabular}
-\caption{Number of clone classes per clone relation.}
-\label{tab:relation}
-\end{table}
-
-Our results show that most clones (37\%) are in a common class. 24\% of clones are in a common hierarchy. Another 24\% of clones are unrelated. 15\% of clones are in an interface.
-
-\subsection{Location}
-Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different location categories (see Section~\ref{sec:setuplocation}).
-We can see from these results that nearly 80\% of clones are found at method level.
-17\% of clones are found at class level, meaning they exceed the boundaries of a single method (or do not span methods at all).
-Constructors account for approximatelyTop- 3\% of clones.
-In interfaces, only 1\% of clones is found.
-
-\begin{table}[H]
-\centering
-\begin{tabular}{@{}lrr@{}}
-\toprule
-\textit{\textbf{Category}} & \textit{\textbf{Clone instances}} & \textit{\textbf{\%}} \\ \midrule
-Method Level & 232,545 & 78.43\% \\
-Class Level & 50,402 & 17.00\% \\
-Constructor Level & 10,039 & 3.39\% \\
-Interface Level & 2,693 & 0.91\% \\
-Enum Level & 788 & 0.27\% \\
-\end{tabular}
-\caption{Amount of clone instances with a per location category.}
-\label{tab:location}
-\end{table}
-
-\subsection{Contents}
-Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different content categories (see Section~\ref{sec:setupcontents}).
-
-\begin{table}[H]
-\centering
-\begin{tabular}{@{}llrrrr@{}}
-\toprule
-\textit{\textbf{Category}} & \textit{\textbf{Contents}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
-\multirow{2}{*}{Partial} & Method Body & 219,540 & 74.05\% & \multirow{2}{*}{229,521}& \multirow{2}{*}{77.42\%} \\ \cmidrule(lr){2-4}
- & Constructor Body & 9,981 & 3.37\% & & \\ \midrule
-\multirow{3}{*}{Other} & Several Methods & 22,749 & 7.67\% & \multirow{3}{*}{53,773} & \multirow{3}{*}{18.14\%} \\ \cmidrule(lr){2-4}
- & Only Fields & 17,700 & 5.97\% & & \\ \cmidrule(lr){2-4}
- & Other & 13,324 & 4.49\% & & \\ \midrule
- \multirow{5}{*}{Full} & Full Method & 12,990 & 4.38\% & \multirow{5}{*}{13,173}& \multirow{5}{*}{4,44\%} \\ \cmidrule(lr){2-4}
-  & Full Interface & 64 & 0.02\% & & \\ \cmidrule(lr){2-4}
-  & Full Constructor & 58 & 0.02\% & & \\ \cmidrule(lr){2-4}
-  & Full Class & 37 & 0.01\% & & \\ \cmidrule(lr){2-4}
-  & Full Enum & 24 & 0.01\% & & \\ \bottomrule
-\end{tabular}
-\caption{Number of clone instances for clone contents categories}
-\label{tab:contents}
-\end{table}
-
-From these results, we see that 74\% of clones span part of a method body (77\% if we include constructors).
-8\% of clones span several methods.
-6\% of clones span only global variables.
-Only 4\% of clones span a full declaration (method, class, constructor, etc.).
-
-\section{Discussion}
-Regarding clone context, our results indicate that most clones (37\%) are in a common class.
-This is favorable for refactoring because the extracted method does not have to be moved after extraction.
-24\% of clones are in a common hierarchy.
-These refactorings are also often favorable.
-Another 24\% of clones are unrelated, which is often unfavorable because it often requires a more comprehensive refactoring.
-15\% of clones are in an interface.
-
-Regarding clone contents, 74\% of clones span part of a method body (77\% if we include constructors).
-8\% of clones span several methods, which often require refactorings on a more architectural level.
-6\% of clones span only global variables, requiring an abstraction to encapsulate these data declarations.
-Only 4\% of clones span a full declaration (method, class, constructor, etc.).
 
 \section{Conclusion}
-To determine which refactoring techniques are most suitable to refactor most clones, we analyzed their context.
-We measured the \textbf{relation} through inheritance of clone instances in a clone class.
-In our corpus, we found that 37\% of clones are found in the same class.
-24\% of clones are in the same inheritance hierarchy.
-Another 24\% of clones are unrelated.
-The final 15\% of clones have the same interface.
-We also looked at the \textbf{location} of clones: 78\% of clones are found at method-level of which 77\% is found in the body of a method or constructor.
 
-From this, we conclude that the ``Extract Method'' refactoring technique is most suitable to refactor most clones.
-
-%\bibliographystyle{splncs04}
-\printbibliography
+\bibliographystyle{plain}
+\bibliography{references}
 

### 2019-12-06 cefp/paper.tex
Abstract

--- 2019-12-04 cefp/paper.tex
@@
 
-We find that most clones (77\%) are in the body of methods or constructors and thus the ``Extract Method'' refactoring technique applies.
-What further techniques are requires for the refactoring depends on the relation among the clone instances of a clone.
-We define four relations that require different further refactoring techniques: Common Class, Common Hierarchy, Common Interface, Unrelated.
-For each of these, we define subcategories to facilitate further understanding in what relations clones are found in the codebase.
+Based on experiments on corpus of open-source Java projects we find that most clones (77\%) are in the body of methods or constructors and thus the ``Extract Method'' refactoring technique applies.
+What further techniques are required for the refactoring depends on the relation among the clone instances of a clone.
+We define four relations that require different further refactoring techniques: Common Class, Common Hierarchy, Common Interface and Unrelated.
+% (ordered by how favorable their refactoring is).
+When clones are in the same class, no further techniques than ``Extract Method'' have to be applied.
+If they are not, further techniques have to be applied that create a trade-off on system maintainability.
+The closer classes are related, the more favorable refactoring clones by such relations becomes.
+37\% of clones are in the same class, 24\% share an inheritance hierarchy, 24\% are unrelated and 15\% have a common interface.% For each of these, we define subcategories to facilitate further understanding in what relations clones are found in the codebase.
 

### 2019-12-06 cefp/paper.tex
Introduction and background

@@
 
-Several refactoring techniques can be used to reduce duplication in source code.
+Several refactoring techniques can be used to reduce duplication in source code~\cite{fowler2018refactoring}.
 Which refactoring technique to apply depends on where a clone is located and what the relation is between similar code fragments \cite{koni2001scenario}.
@@
 We perform statistical measurements on a large corpus of open-source software systems to determine which relation, location and contents category has the most clones.
-We find that 77\% of clones is found in the bodies of constructors and methods, which indicate clones that can be refactored by applying the ``Extract Method'' refactoring technique.
-What further techniques apply when refactoring a clone using the ``Extract Method'' technique depends on the relation among its clone instances.
+We find that a significant portion of clones is found in the bodies of constructors and methods, which indicate clones that can be refactored by applying the ``Extract Method'' refactoring technique.
+What further techniques apply when refactoring such a clone depends on the relation among its clone instances.
 
@@
 We use two definitions to argue about code clones~\cite{roy2007survey}:
-\\ \textbf{Clone instance}: A single cloned fragment.
-\\ \textbf{Clone class}: A set of similar clone instances.
+\\ \textbf{Clone instance}: A single code fragment of which a similar/identical copy exists elsewhere in the codebase.
+\\ \textbf{Clone class}: A set of similar/identical clone instances.
 
@@
 \section{Context Analysis of Clones}\label{chap:contextsetup}
-To be able to refactor code clones, CloneRefactor first maps the context of code clones. We define the following aspects of the clone as its context:
+We define the following aspects of the clone as its context:
 \begin{enumerate}
-  \item \textbf{Relation:} The relation of clone instances among each other through inheritance.
+  \item \textbf{Relation:} The relation of clone instances in a clone class among each other through inheritance.
   \item \textbf{Location:} Where a clone instance occurs in the code.

### 2019-12-06 cefp/paper.tex
Clone relation

@@
 \section{Context Analysis of Clones}\label{chap:contextsetup}
-We define the following aspects of the clone as its context:
+The context of a clone determines how it should be refactored~\cite{fowler2018refactoring}.
+Based on current literature \cite{fontana2012duplicated, fontana2015duplicated}, we define the following aspects of a clone as its context:
 \begin{enumerate}
@@
 \end{enumerate}
-We define categories for each of these aspects and enable CloneRefactor to determine the categories of clones.
+
+This is shown schematically in Figure~\ref{fig:clonecontext}.
+%We define categories for each of these aspects and determine the categories of clones.
 
@@
 
-Fig.~\ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
+%Fig.~\ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
 The relation of clones through inheritance is determined for each clone class.
@@
 
-Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other.
-To do this, they first define several categories for the relation between clone instances in object-oriented languages.
+Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation between clone instances in a clone class.
+To do this, they first define several categories to argue about such relations.
 These categories are as follows:
@@
 
-We added the following categories, to gain more information about clones and reduce the number of unrelated clones:
+We added the following categories, to gain more information about clones and be able to suggest a more fine-grained refactoring opportunity:
 
@@
     \includegraphics[width=0.6\columnwidth]{img/Relation}
-      \caption{Abstract figure displaying relations of clone classes. Arrows represent superclass relations.}
+      \caption{Abstract figure displaying some relations of clone classes. Arrows represent superclass relations.}
   \label{fig:clonerelation}
@@
 
-When CloneRefactor applies automated refactorings, it uses this inheritance relation to see where it must place the refactored code.
+%When CloneRefactor applies automated refactorings, it uses this inheritance relation to see where it must place the refactored code.
 We explain this for each relation category over the following sections.
@@
 Cloned classes with a \textit{No Direct Superclass} relation mark the opportunity for creating a superclass abstraction and placing the extracted method there.
-For clone classes with a \textit{No Indirect Superclass} relation, CloneRefactor creates such an abstraction for the ancestor that does not have a parent.
+For clone classes with a \textit{No Indirect Superclass} relation, it is possible to create such an abstraction for the ancestor that does not have a parent.
 Clone classes with a \textit{External Superclass} or \textit{External Ancestor} relation obstruct the possibility of creating a superclass abstraction.
-In such a case, CloneRefactor creates an interface abstraction to make their relation explicit.
+In such a case, it is possible to create an interface abstraction to make their relation explicit.
 

### 2019-12-09 cefp/paper.tex
Updates from Overleaf

@@
 %
-\title{Finding the Most Suitable Code Clone Refactoring Techniques by Mapping Clone Context}
+\title{Finding Code Clone Refactoring Techniques by Mapping Clone Context}
 %
@@
 We use the tool CloneRefactor\footnote{CloneRefactor is a code clone detection and refactoring tool: \url{https://github.com/SimonBaars/CloneRefactor}} which automatically determines these context aspects of code clones.
-In this section, we first explain the corpus we use.
-We then explain how we calculate the impact of refactorings on the software maintainability.
 
@@
 
-Because CloneRefactor requires all dependencies for the projects it analyses, we created a set of scripts\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} to filter the corpus for all projects for which we can obtain all dependencies using Maven.
+Because CloneRefactor requires all dependencies for the projects it analyses, we created a set of scripts\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} to filter the corpus for all projects for which we can obtain all dependencies using Maven\footnote{Maven is a build automation system, mainly used for Java programs: \url{https://maven.apache.org/}}.
 
-\subsection{Resulting corpus}
 This procedure results in 2,267 Java projects including all their dependencies\footnote{The full list of projects is in the following file in our GitHub repository: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts/blob/master/filtered_projects.txt}}.
@@
 First, we created a set of 57 control projects\footnote{Control projects for testing CloneRefactor: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to verify the correctness in many (edge) cases.
-These projects test each identified relation, location, contents and refactorability category (see Section \ref{chap:contextsetup} and \ref{sec:refactorabilitysetup}), to see whether they are correctly identified.
+These projects test each identified relation, location and contents category (see Section \ref{chap:contextsetup}), to see whether they are correctly identified.
 Next, we run the tool over the corpus and manually verify samples of the acquired results.
-This way, we check the correctness of the identified clones, their context, and their proposed refactoring.
-
-We also test the correctness of the resulting code after refactoring.
-For this, we use a project named JFreeChart\footnote{JFreeChart is available on GitHub: \url{https://github.com/jfree/jfreechart}}.
-JFreeChart has high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor.
-We run CloneRefactor manually over the JFreeChart project, run its test cases and check the correctness of the proposed refactorings.
+This way, we check the correctness of the identified clones and their context.
 
 \section{Results}
-To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones (see Section~\ref{chap:contextsetup}).
+To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones.
 
@@
 Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different location categories (see Section~\ref{sec:setuplocation}).
-We can see from these results that nearly 80\% of clones are found at method level.
-17\% of clones are found at class level, meaning they exceed the boundaries of a single method (or do not span methods at all).
-Constructors account for approximatelyTop- 3\% of clones.
-In interfaces, only 1\% of clones is found.
 
@@
 \end{table}
+
+We can see from these results that nearly 80\% of clones are found at method level.
+17\% of clones are found at class level, meaning they exceed the boundaries of a single method (or do not span methods at all).
+Constructors account for approximately 3\% of clones.
+In interfaces, only 1\% of clones is found.
 
@@
 \begin{itemize}
-  \item \textbf{Clone Relation}: The relation between clone instances among each other in a clone class.
+  \item \textbf{Clone Relation}: The inheritance relation between clone instances among each other in a clone class.
   \item \textbf{Clone Location}: The location of clone instances in the codebase.

### 2019-12-10 benevol/paper.tex
Updated results
Updates from Overleaf

@@
 Amsterdam, the Netherlands \\
-simon.mailadres@gmail.com}
+simon.j.baars@gmail.com}
 }
@@
 Duplicate code fragments are often considered as bad design~\cite{fowler2018refactoring}.
-They increasing maintenance efforts or causing bugs in evolving software~\cite{heitlager2007practical}.
+They increase maintenance efforts or cause bugs in evolving software~\cite{heitlager2007practical}.
 Changing one occurrence of a duplicated fragment may require changes in other occurrences~\cite{ostberg2014automatically}.
-Furthermore, duplicated code was shown to account for up to 25\% of total system volume~\cite{bruntink2005use}, entailing more code to be maintained.
+Furthermore, duplicated code often significantly increases total system volume~\cite{svajlenko2019mutation}, entailing more code to be maintained.
 
 Several tools have been proposed to detect duplication issues \cite{roy2009comparison, svajlenko2014evaluating, sheneamer2016survey}.
-These tools can find matching fragments of code, however do not take into account contextual information of code.
+These tools can find matching fragments of code, however they do not take into account contextual information of code.
 An example of such contextual information is the name of used variables: many different methods with the same name can exist in a codebase.
@@
 We describe a method to detect clones while taking into account the contextual information and introduce a tool to detect clones taking into account such contextual information.
-We run the tool over a corpus of 2,267 Java projects.
-We find that taking into account contextual information results in 11\% less clones than found when not taking this information into account.
-Manually inspecting a sample the difference, we find that all clones with different contextual information in our sample are less relevant for refactoring.
+Next, we collect and discuss statistical information regarding the difference in output when contextual information is considered and when it is not.
 
@@
 Many studies adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
-In this study, we mainly focus expanding type 1 clone detection to take into account contextual information.
+To limit the scope of this study, we mainly focus on expanding type 1 clone detection to take into account contextual information.
 
@@
 We find that 167,913 clones are found when contextual information is not considered, whereas 149,569 clones are found when it is considered.
-We manually analyse a sample of 50 clones that are not found when considering contextual information.
+We manually analyse a random sample of 50 clones that are not found when considering contextual information.
 We find that these clones are indeed hard to refactor because they describe different functional operations and can thus not be extracted to a new method.
-Also, most often they were not relevant because, based on our judgement, refactoring would not improve the code design.
+Also, most often they were not relevant because, based on our expert intuition, refactoring would not improve the code design.
 Often, different methods were called or variables of different types were used.

### 2019-12-10 benevol/paper.tex
Working on copyright
Updates from Overleaf

@@
-\documentclass[conference]{IEEEtran}
+\documentclass[journal]{IEEEtran}
 
@@
 
+% \makeatletter
+% \def\ps@IEEEtitlepagestyle{%
+%   \def\@oddfoot{\mycopyrightnotice}%
+%   \def\@evenfoot{}%
+% }
+% \def\mycopyrightnotice{%
+%   {\hfill \footnotesize 978-1-4673-9563-2/15/\$31.00 \copyright 2015 IEEE\hfill}
+% }
+% \makeatother
+
 \begin{document}
@@
 
+%\copyright{Copyright 2019 for this paper by its authors. Use permitted under Creative Commons License Attribution 4.0 International (CC BY 4.0).}
+
+% \IEEEoverridecommandlockouts
+% \IEEEpubid{\makebox[\columnwidth]{978-1-5386-5541-2/18/\$31.00~\copyright2018 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ bla bla}}
+
+\newcommand\blfootnote[1]{%
+  \begingroup
+  \renewcommand\thefootnote{}\footnote{#1}%
+  \addtocounter{footnote}{-1}%
+  \endgroup
+}
+
 \maketitle
+
+% \IEEEpubid{\begin{minipage}{\textwidth}\ \\[12pt] \centering
+%   1551-3203 \copyright 2015 IEEE. Personal use is permitted, but republication/redistribution requires IEEE permission.\\
+%   See http://www.ieee.org/publications standards/publications/rights/index.html for more information.
+% \end{minipage}}
+
+% \IEEEpubidadjcol
 
@@
 We find that, when taking into account contextual information in our clone detection, 11\% fewer clones are found.
-Manually inspecting a sample of the difference, we find that they are less relevant for refactoring.
+Manually inspecting a sample of the difference, we find that they are less relevant for refactoring.\blfootnote{Copyright 2019 for this paper by its authors.
+Use permitted under Creative Commons License Attribution 4.0 International (CC BY 4.0).}
 \end{abstract}

### 2020-01-09 ecoop/paper.tex
ECOOP

--- 2019-08-24 icse/paper.tex
@@
-\documentclass[sigconf,review, table]{acmart}
+\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate,authorcolumns]{lipics-v2019}
 
@@
 
-\setcopyright{acmcopyright}
-\copyrightyear{2019}
-\acmYear{2019}
-\acmDOI{10.1145/1122445.1122456}
-\acmMonth{8}
+\title{Improving Software Maintainability through Automated Refactoring of Code Clones}
 
-\acmConference[ICSE 2020]{Technical Papers}{May 23--29}{Seoul, South Korea}
+\keywords{code clones, refactoring, static code analysis, object-oriented programming}
+
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10011007.10011074.10011111.10011696</concept_id>
+<concept_desc>Software and its engineering~Maintaining software</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10011007.10011074.10011111.10011113</concept_id>
+<concept_desc>Software and its engineering~Software evolution</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10011007.10011074.10011092.10011093</concept_id>
+<concept_desc>Software and its engineering~Object oriented development</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Software and its engineering~Maintaining software}
+\ccsdesc[500]{Software and its engineering~Software evolution}
+\ccsdesc[300]{Software and its engineering~Object oriented development}
+
+\author{}
+\authorrunning{}
 
 \begin{document}
-
-\title{Improving Software Maintainability through Automated Refactoring of Code Clones}
 
@@
 \end{abstract}
-
-\keywords{code clones, refactoring, static code analysis, object-oriented programming}
 

### 2020-01-09 ecoop/paper.tex
Updates from Overleaf

@@
 
-\begin{figure*}
-\begin{parcolumns}{2}
-\colchunk[1]{
-\begin{javacode}
+%\begin{figure}
+% \begin{parcolumns}{2}
+% \colchunk[1]{
+\begin{lstlisting}[language=Java,escapechar=|,label=list:8-6,captionpos=t,float,abovecaptionskip=-\medskipamount,tabsize=2, basicstyle=\small, linewidth=6cm]
 package com.sb.game;
@@
 }
-\end{javacode}}
-\colchunk[2]{
-\begin{javacode}
+\end{lstlisting}% }
+%\colchunk[2]{
+\begin{lstlisting}[language=Java,escapechar=|,label=list:8-6,captionpos=t,float,abovecaptionskip=-\medskipamount,tabsize=2, basicstyle=\small, linewidth=6cm]
 package com.sb.fruitgame;
@@
 }
-\end{javacode}}
-\end{parcolumns}
-\caption{Example of textually equal code fragments that differ in functionality.}
-\label{fig:type1}
-\end{figure*}
+\end{lstlisting} %}
+%\end{parcolumns}
+%\caption{Example of textually equal code fragments that differ in functionality.}
+%\label{fig:type1}
+%\end{figure}
+
+\begin{lstlisting}[caption={Useless code},label=list:8-6,captionpos=t,float,abovecaptionskip=-\medskipamount]
+for i:=maxint to 0 do 
+begin 
+    j:=square(root(i));
+end;
+\end{lstlisting}
 
@@
 
-\begin{figure*}
+\begin{figure}
 \begin{parcolumns}{2}
@@
 \label{fig:refactorabilitypartialblock}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{table*}
+\begin{table}
 \centering
@@
 \label{tab:relation_refactor}
-\end{table*}
+\end{table}
 
@@
 
-\begin{figure*}
+\begin{figure}
   \includegraphics[width=1\textwidth]{img/tokenvolume}
@@
   \label{fig:maintainabilityscore}
-\end{figure*}
+\end{figure}
 
@@
 \label{tab:return}
-\end{table*}
+\end{table}
 

### 2020-01-09 ecoop/paper.tex
Updates from Overleaf

--- 2020-01-09 ecoop/paper.tex
@@
 Apart from that, code clones can contribute up to 25\% of the code size~\cite{bruntink2005use}.
+However, manual code clone refactoring is often tedious and could benefit from an automated tool~\cite{mazinanian2016jdeodorant}.
 
-Current code clone detection techniques base their thresholds and prioritization on a limited set of metrics.
-Often, clone detection techniques are limited to measuring the size of clones to determine whether they should be considered.
+%Clone detection tools often use thresholds to determine which clones should be considered.
+Most clone detection tools use the number of lines \cite{kamiya2002ccfinder, svajlenko2016bigcloneeval}, statements \cite{higo2013revisiting, kamalpriya2017enhancing} and/or tokens \cite{ragkhitwetsagul2019siamese, jiang2007deckard} as thresholds to determine whether clones should be considered.
+We outline the shortcomings of these thresholds to find clones such that the maintainability of the source code is improved when refactored, and propose new thresholds to control this characteristic.
+% Current clone detection techniques are limited to measuring the size of clones to determine whether they should be considered.
 Because of this, the output of clone detection tools is often of limited assistance to the developer in the refactoring process.
+To reduce duplication of a codebase, there are several refactoring techniques that can be applied in an automated manner.
+The most used refactoring technique to deal with code clones is ``Extract Method'' \cite{fowler2018refactoring}.
+This technique entails that the duplicated code is moved to a new method, which is then called from all locations where the duplicated code was used.
+To be able to execute such a refactoring, several preconditions apply \cite{tsantalis2015assessing}.
+%\todo[inline]{still missing link on how current solutions do not help improving maintainability - our message from monday night is not crystal clear yet}
+In this study, we analyze which preconditions apply to determine whether a clone could and should be automatically refactored.
+We list criteria that influence the maintainability of clones when refactored.
+We evaluate the context of clones to determine which refactoring techniques are best suited.
+We define the context of clones as the inheritance relation between clone instances in a clone class and the location of clone instances in the codebase.
+We showcase the proposed technique as a tool that automatically refactors clones by extracting new methods out of duplicated code.
 
-In this study, we define a technique to detect clones such that they can be automatically refactored.
-We list a set of criteria that can obstruct refactoring opportunities.
-We evaluate the relation and location of clones to determine which refactoring techniques are best suited.
-We introduce a tool that automatically refactors clones by extracting new methods out of duplicated code.
+We measure several maintainability metrics before and after refactoring to determine the impact on system maintainability of applying the refactoring.
+These metrics are volume, method parameters, duplication and complexity.
+Using this setup, we gain empirical data about the maintainability improvement of clones on a large set of data in a controlled environment.
+Because the refactoring is done automatically, we also consider micro-clones, which are shown to be important for refactoring consideration \cite{mondai2018micro}.
+We use this data to define which characteristics of clones have the biggest influence of system maintainability when such a clone is refactored.
+This allows for more a accurate suggestion of code clones for refactoring and can assist in the refactoring process.
 
-We evaluate our approach by comparing the maintainability of before- and after snapshots of a codebase for each duplication problem that is refactored.
+Most clone detection tools can be configured using thresholds.
+These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones.
+Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quantile distribution of empirical data~\cite{alves2010deriving}.
+Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.% \todo{Check whether this really fits here}
+
+Over a corpus of 2.267 Java project our tool refactored 12.710 clone classes.
+We found that the main influencing factor on maintainability when refactored is token volume.
+We define token volume as the combined number of tokens in all clone instances in a clone class.
+When refactoring clones with a very small token volume, we found that the maintainability decreases when such clones are refactored.
+The average clone with a clone volume of 65 or larger improves maintainability when refactored.
+The other factor with a major influence on maintainability is the number of parameters that are required for the extracted method.
+We found that if a clone requires more than 2 parameters in the extracted method, it is more likely to decrease maintainability.
+
+This paper is organized as follows.
+In Sec.~\ref{sec:background} we revisit key clone refactoring background.
+Sec.~\ref{sec:relatedwork} discusses state-of-the-art in automatic clone refactoring research.
+In Sec.~\ref{sec:research} we propose a definition for clones such that they could and should be automatically refactored.
+In Sec.~\ref{sec:clonerefactor} we introduce our clone refactoring tool.
+In Sec.~\ref{sec:experimentalsetup} we explain the setup of our experiments; we show the results in Sec.~\ref{sec:results} and discuss them in Sec.~\ref{sec:discussion}.
+%We evaluate our approach by comparing the maintainability of before- and after snapshots of a codebase for each duplication problem that is refactored.
 We define which factors have the greatest influence on whether a clone improves maintainability when refactored.
@@
 
-\section{Background}
-Our study lies at the intersection of code clone and refactoring research. We use two concepts to argue about code clones~\cite{roy2007survey}:
+\section{Background}\label{sec:background}
+We briefly describe relevant code clone and clone refactoring research.
+
+\subsection{Code clones}
+We use two concepts to argue about code clones~\cite{roy2007survey}:
 \\ \textbf{Clone instance}: A single cloned fragment.
@@
 
+%\subsection{Clone Types}
+Duplication in code is found in many different forms.
+Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}.
+Sometimes this code is then adapted to fit the new context.
+To reason about these modifications, several clone types have been proposed%.
+These clone types are described in Roy et al
+~\cite{roy2007survey}:\\
+\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout), and comments.\\
+\textbf{Type II:} Structurally/syntactically identical fragments except variations in identifiers, literals, types, layout, and comments.\\
+\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed next to variations in identifiers, literals, types, layout, and comments.
+A higher type of clone means that it is harder to detect and refactor.
+Many studies adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
+
+\subsection{Clone Refactoring}
+\subsubsection{Refactoring techniques}
 The most common technique for refactoring clones is ``Extract Method''~\cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
-Applying this technique entails moving functionality in the body of a method to a new method.
-To reduce duplication with this technique, we extract the contents of a single clone instance to a new method and replace all clone instances in a clone class by a call to this method.
+Applying this technique entails moving functionality from the body of a method to a new method.
+To reduce duplication with this technique, the contents of a single clone instance are extracted to a new method and all further locations of the clone are replaced by a call to the new method.
+
+\subsubsection{Preconditions}
+Clones detected by current detection techniques \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, cordy2011nicad} are subject to a set of preconditions to determine whether they can be refactored \cite{tsantalis2015assessing}:
+\begin{enumerate}
+  \item The parameterization of differences between the matched statements should not break existing data-, anti-, and output-dependencies.
+  \item The unmatched statements should be movable before or after the matched statements without breaking existing data-, anti-, and output-dependencies.
+  \item The duplicated code fragments should return at most one variable of the same type.
+  \item Matched branching (\texttt{break}, \texttt{continue}) statements should be accompanied with corresponding matched loop statements.
+  \item Matched variables having different subclass types should call only methods that are declared in the common superclass or are being overridden in the respective subclasses.
+  \item The parameterization of fields belonging to differences between the mapped statements is possible only if they are not modified.
+  \item The parameterization of method calls belonging to differences between the mapped statements is possible only if they do not return a void type.
+  \item The mapped statements within the clone fragments should not contain any conditional return statements.
+\end{enumerate}
 
@@
 
-\section{Related Work}
-The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
-The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems.
-This tool is based on several studies that look into different aspects of code clone refactoring.
-In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how does variability between cloned fragments influence the refactoring techniques required and their implications on system design.
-Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability.
-This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.
+\section{Related Work}\label{sec:relatedwork}
+We outline relevant research to clone refactoring. A significant aspect is the context of clones.
 
-A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process.
-The main focus is to find out which clones \textbf{can} be refactored.
+\subsection{Clone context analysis}\label{sec:rw:contextanalysis}
+Golomingi~\cite{koni2001scenario} explores mapping the relation between clone instances to refactoring methods.
+The author analyses the refactoring methods described by Martin Fowler \cite{fowler1999refactoring} and analyzes what refactoring methods can be used to refactor clones with what inheritance relations.
+The identified clone relations are: Ancestor, Common Hierarchy, First Cousin, Same Method, Sibling, Single Class, Superclass and Unrelated.
+We extend this list with several more fine-grained relations, suitable for automatic refactoring (see Sec.~\ref{sec:relation}).
+
+Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} combine the research by Golomingi~\cite{koni2001scenario} with clone types 1 and 3 \cite{roy2007survey}.
+They use a large corpus~\cite{tempero2010qualitas} on which they perform statistical analyses of clone relations together with clone types.
+We repeat this research with a vastly different setup: we use the clone definition from Sec.~\ref{sec:research} and the relation categories outlined in Sec.~\ref{sec:relation}.
+
+\subsection{Clone refactoring}
+Krishnan et al.~\cite{krishnan2013refactoring} approach clone refactoring as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design.
+The main focus of this study is to find out which clones \textbf{can} be refactored.
 We extend this work by looking into which clones \textbf{should} be refactored.
@@
 This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
+%The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
+The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems.
+This tool is based on several studies that look into different aspects of code clone refactoring.
+In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design.
+Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability.
+This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.
 
-\section{Defining refactorable clones}
-In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}.
-We discuss how we can define clones such that they can be automatically refactored without side effects on the source code.
+%A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process.
 
-\subsection{Ensuring Equality}\label{sec:t1r}
+\section{Defining refactorable clones}\label{sec:research}
+%In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}.
+We discuss how we can define clones such that they can be automatically refactored while avoiding changing the functional behavior and other negative side effects on the source code, such as decreasing the maintainability of the code.
+
+\subsection{Ensuring equality}\label{sec:t1r}
 Most modern clone detection tools detect duplication by comparing the code textually together with the omission of certain tokens~\cite{roy2009comparison, svajlenko2014evaluating}.
@@
 Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context~\cite{roy2007survey}.
-When dealing with such a situation, there are several opportunities to refactor so-called ``gapped clones''~\cite{ueda2002detection, zhao2018automatic}.
+When dealing with such situations, there are several opportunities to refactor so-called ``gapped clones''~\cite{ueda2002detection, zhao2018automatic}.
 ``Gapped clones'' are two clone instances separated by a ``gap'' of non-cloned statement(s).
-We define the following methods to refactor such clones:
+We define the following methods to refactor such clones, based on research by Tsantalis et al~\cite{tsantalis2015assessing}:
 \begin{itemize}
-  \item We wrap the difference in statements in a conditionally executed block, one path for each different (group of) statement(s).
-  \item We use a lambda function to pass the difference in statements from each location of the clone~\cite{tsantalis2017clone}.
+  \item Wrap the difference in statements in a conditionally executed block, one path for each different (group of) statement(s).
+  \item Use a lambda function to pass the difference in statements from each location of the clone~\cite{tsantalis2017clone}.
 \end{itemize}
-For both refactoring techniques, a trade-off is at play. This is because these solutions increase the complexity and volume of the source code in favor of removing a clone.
+For both of these techniques, a trade-off is at play. This is because these solutions increase the complexity and volume of the source code in favor of removing a clone.
 
-\section{The CloneRefactor tool}
-To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
-We created a set of control projects\footnote{Control projects for assessing clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
+\section{Survey existing clone detection tools}\label{sec:survey}
+%To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability.
+To investigate the impact of the definitions introduced in Sec.~\ref{sec:research}, we need a tool to detect refactorable clones according to these definitions.
+We conducted a short survey on (recent) clone detection tools to detect such clones that can be refactored.
+The results of our survey are displayed in table~\ref{table:dettools}.
+We chose a set of tools that are open source and can analyze a popular object-oriented programming language.
+Next, we formulate the following four criteria by which we analyze these tools:
+\begin{enumerate}
+    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method level clones.
+We want to perform an analysis of all clones in projects to get a complete overview.
+\item \textbf{Finds clone classes in control projects.} We assembled a number of control projects to assess the validity of the surveyed clone detection tools.
+\item \textbf{Can analyze resolved symbols.} When detecting the clones proposed in Sec.~\ref{sec:research}, it is important that we can analyze resolved symbols (for instance a type reference).
+\item \textbf{Extensive detection configuration.} Detecting our clone definitions, as proposed in Sec.~\ref{sec:research}, require to have some understanding about the meaning of tokens in the source code (whether a certain token is a type, variable, etc.).
+The tool should recognize such structures, in order for us to configure our clone type definitions in the tool.
+\end{enumerate}
 
-None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
+\begin{table}[H]
+ \begin{center}
+  \caption{Our survey on clone detection tools.} \label{table:dettools}
+  \medskip
+\begin{tabular}{|l|l|l|l|l|l|}
+\hline
+\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
+Siamese~\cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
+NiCAD~\cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
+CPD~\cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
+\begin{tabular}[c]{@{}l@{}}CCFinder~\cite{kamiya2002ccfinder}\\ D-CCFinder~\cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
+CCFinderSW~\cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
+\begin{tabular}[c]{@{}l@{}}SourcererCC~\cite{sajnani2016sourcerercc}\\ Oreo~\cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
+BigCloneEval~\cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
+Deckard~\cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
+Scorpio~\cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+Apart from these criteria, we found that the output of these clone detection tools cannot be post-processed to find the clone definition proposed in Sec.~\ref{sec:research}.
+This is mainly because these clones are not necessarily a subset of clones detected by these tools and will thus require an analysis of the entire system.
+
+%To detect clones that can be automatically refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
+We created a set of control projects to determine the suitability of these tools to detect automatically refactorable clones, either through configuration or postprocessing of their output.
+
+%None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable for our definitions of refactorable clones, because of which we propose CR.
 This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
 In the following sections, we explain these steps.
+
+\section{A tool for automatic clone refactoring}\label{sec:clonerefactor}
+None of the surveyed tools were suitable for our definitions of refactorable clones.
+Therefore, we built a new tool, CR\footnote{Name anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.} This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
+In Sec.~\ref{sec:detection} we describe how CR detects refactorable clones.
+In Sec.~\ref{sec:context} we describe how CR maps the context of clones as input for the refactoring process described in Sec.~\ref{sec:refactoring}.
+
 \begin{figure}[H]
   \includegraphics[width=1\columnwidth]{img/flow}
-  \caption{Simple flow diagram of CloneRefactor.}
+  \caption{Abstract flow diagram of CR.}
   \label{fig:clonerefactorflow}
@@
 
-\subsection{Clone Detection}
+\subsection{Clone detection}\label{sec:detection}
 We use an AST-based method to detect clones.
 Clones are detected on a statement level: only full statements are considered as clones.
-In this process, we limit the variability between indicated expressions (see Sec.~\ref{sec:t2r}) by a threshold.
+In Sec.~\ref{sec:t2r} we described that we limit the variability between variable, literal and method reference expressions by a threshold.
 This threshold is the percentage of different expressions against the total number of expressions in the source code:
@@
 
-After all clones have been detected, CloneRefactor determines whether clone classes can be merged into gapped clones (see Sec.~\ref{sec:t3r}).
+After all clones have been detected, CR determines whether clone classes can be merged into gapped clones (see Sec.~\ref{sec:t3r}).
 The maximum size of the gap is limited by a threshold.
-This threshold is the percentage of (not-cloned) statements in the gap against the sum of statements in both clones surrounding it.
-Unlike the expression variability threshold, this threshold can exceed 100\%:
+This threshold is the percentage of (not-cloned) statements in the gap against the sum of statements in both clones surrounding it:
 \begin{equation}\label{eq:type3r}
@@
 
-\subsection{Context Mapping} \label{sec:context}
+\subsection{Context mapping} \label{sec:context}
 After clones are detected, we map the context of these clones.
-We have identified three properties of clones as their context: relation and location.
+We identify two properties of clones as their context: relation~\cite{fontana2012duplicated} and location~\cite{tairas2011representing}.
 We identify categories for each of these properties, to get a detailed insight into the context of clones.
@@
 
-Based on these relations, CloneRefactor determines where to place the cloned code when refactored.
-These categories are mutually exclusive: a clone class will be flagged as the first relation in the above list that it applies to.
-The code of clones that have a \textit{Common Class} relation can be refactored by placing the cloned code in this same class.
-The code of clones with a \textit{Common Hierarchy} relation can be placed in the intersecting class in the hierarchy (the class all clone instances have in common as an ancestor).
-The code of clones with a \textit{Common Interface} relation can be placed in the intersecting interface, but in the process has to become part of the classes' public contract.
-The code of clones that are \textit{Unrelated} can be placed in a newly created place: either a utility class, a new superclass abstraction or an interface.
+Based on these relations, CR determines where to place the cloned fragment when extracted to a new method.
+These categories are mutually exclusive: a clone class is flagged as the first relation in the above list that it applies to.
+The code of clones that have a \textit{Common Class} relation can be refactored by placing the cloned code in this same class~\cite{fowler2018refactoring}.
+The code of clones with a \textit{Common Hierarchy} relation can be placed in the intersecting class in the hierarchy (the class all clone instances have in common as an ancestor)~\cite{fowler2018refactoring}.
+The code of clones with a \textit{Common Interface} relation can be placed in the intersecting interface~\cite{mohnen2002interfaces}, but in the process has to become part of the classes' public contract.
+The code of clones that are \textit{Unrelated} can be placed in a newly created place.
+The state-of-the-art uses a utility class~\cite{mazinanian2016jdeodorant}, whereas CR creates a new superclass or interface abstraction.
+The reason CR creates a superclass or interface rather than a utility class is that it makes the relation explicit and allows previously unrelated clones to become related.
 
 \subsubsection{Location}\label{sec:location}
-The location of a clone instance determines what refactoring techniques can be applied to refactor such clones. We define the following categories by which we analyze the location of clones:
+The location of a clone instance helps determine what refactoring techniques can be applied to it. We define the following categories of clones based on their location:
 \begin{enumerate}
@@
 \end{enumerate}
-
-\subsubsection{Full Method/Constructor/Class/Interface/Enumeration}
-The categories denote that a full declaration (method, class, etc.) often denote redundancy and are often easy to refactor: one of both declarations is redundant and should be removed.
-Clones in the ``Partial Method/Constructor'' category can often be refactored using the ``Extract Method'' refactoring technique.
+The categories denote that a full declaration (method, class, etc.) often denotes redundancy and are often easy to refactor: one of the declarations is redundant and should be removed.
+Clones in the ``Partial Method/Constructor'' category can often be refactored using the ``Extract Method'' refactoring technique~\cite{mazinanian2016jdeodorant}.
 Clones consisting of \textit{Several Methods} give a strong indication that cloned classes are missing some form of abstraction, or their abstraction is used inadequately.
@@
 
-\subsection{Refactoring}
-CloneRefactor can refactor clones using the ``Extract Method'' refactoring technique. In this section, we show which clones we refactor and how we apply these transformations.
+\subsection{Refactoring}\label{sec:refactoring}
+Table~\ref{tab:location} shows that most clones are found in method bodies.
+Therefore, we focus on refactoring such clones which entails using the ``Extract Method'' refactoring technique.
+We show which clones CR refactors and how it applies these transformations.
 
-\subsubsection{Extract Method} \label{sec:refactorability}
-Several influencing factors may obstruct the possibility to extract code to a new method:
+\subsubsection{Refactorability} \label{sec:refactorability}
+Several factors may obstruct the possibility to extract code to a new method~\cite{tsantalis2015assessing}:
 \begin{itemize}
@@
     \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method.
-Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
+Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``Pull Up Method'' for clones in sibling classes).
 \end{itemize}
-Clones that do not fall in the \textit{Can Be Extracted} category may require additional transformations or other techniques to refactor.
-CloneRefactor only refactors the clones that \textit{Can Be Extracted}.
+Clones that do not fall in the \textit{Can Be Extracted} category may require additional transformations or other techniques to refactor. CR only refactors the clones that \textit{Can Be Extracted}.
 
 \subsubsection{AST Transformation}
-CloneRefactor uses JavaParser~\cite{smith2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
-To refactor clones, CloneRefactor creates a new method declaration and moves all statements from a clone instance in the clone class to the new method.
+%\todo{Big todo --> Find literature, introduce proper reasoning why I need to do this.}
+CR uses JavaParser~\cite{smith2017javaparser}: an AST-parsing library that allows to modify the AST and write it back to source code.
+To refactor clones, CR creates a new method declaration and moves all statements from a clone instance in the clone class to the new method.
 This method is placed according to the relation between the clone instances (see Sec.~\ref{sec:relation}).
-CloneRefactor analyzes the source code of the extracted method and populates it with the following properties:
+CR analyzes the source code of the extracted method and populates it with the following properties:
 \begin{itemize}
@@
 \end{itemize}
-CloneRefactor then removes all cloned code and replaces it with a method call to the newly created method.
-In case of a return value, CloneRefactor either assigns the call result, declares it or returns it accordingly.
+CR then removes all cloned code and replaces it with a call to the newly created method. In case of a return value, CR either assigns the call result, declares it or returns it accordingly.
+
+\subsection{Maintainability Metrics}
+After applying the refactorings, CR measures the impact of the refactoring on maintainability metrics.
+We first state the metrics that we measure and then define the characteristics of the applied refactoring that influence the metrics.
+
+\subsubsection{Maintainability metrics} \label{sec:metrics}
+CR measures the impact on maintainability metrics of refactoring source code for each clone class that is refactored.
+These metrics are from Heitlager et al.~\cite{heitlager2007practical}.
+For each of these metrics, risk profiles are proposed to determine the maintainability impact on the system of a whole.
+
+To determine whether the maintainability improves when refactoring a given clone, we need to measure the impact of fine-grained changes.
+Therefore, we measure only a subset of the metrics~\cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
+The subset of metrics we choose to focus on are all measured on method level (as the other metrics show a lesser impact on the maintainability for these small changes).
+These metrics are:
+\begin{itemize}
+\item \textbf{Duplication}: Originally~\cite{heitlager2007practical} measured by taking the amount of duplicated lines.
+We decided to use the amount of duplicated tokens part of a clone class instead, to have a stronger reflection of the impact of the refactoring by measuring a more fine-grained system property.
+%\item \textbf{Volume}: The more code a system has, the more code has to be maintained.
+The paper~\cite{heitlager2007practical} measures volume as lines of code.
+As with duplication, we use the number of tokens instead.
+\item \textbf{Method Complexity}:  Originally ~\cite{heitlager2007practical} computed using MCCabe complexity~\cite{mccabe1976complexity}.
+The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.%\todo{why is the original way ok for us?}
+\item \textbf{Method Interface Size}: The number of parameters that a method has.
+If a method has many parameters, the code may become harder to understand and it is an indication that data is not encapsulated adequately in objects~\cite{fowler2018refactoring}.
+\item \textbf{Method size}: The longer a method is, the harder it becomes to comprehend and maintain \cite{heitlager2007practical}.
+The ``extract method'' refactoring technique is often used to split up long methods \cite{charalampidou2018structural}.
+When refactoring duplicated code fragments in the body of a method, this could improve maintainability of the refactored (reduced size).
+\end{itemize}
 
 \subsubsection{Characteristics of the extracted method}\label{sec:characteristics}
-We define the following characteristics of the extracted method and/or the call:
+To assess the impact of an applied refactoring, we selected the four characteristics that have the highest impact on the resulting maintainability scores:
 \begin{itemize}
-\item \textbf{Tokens}: The number of tokens in the body of the method.
-\item \textbf{Relation}: The relation category (Sec.~\ref{sec:relation}) by which this methods' location was determined.
+\item \textbf{Size (in tokens)}: The number of tokens in the body of the method.
+A larger number of tokens means that more duplicate code can be removed, and thus has a positive impact on maintainability.
+\item \textbf{Relation}: The relation category (Sec.~\ref{sec:relation}) by which this methods' location was determined. Some relations are less favorable for maintainability than others.
 \item \textbf{Returns}: Whether the method calls return, declare, assign or don't use any data from the extracted method.
+This affects maintainability because the data must be returned from the extracted method, and assigned at each method call.
+This increases the volume of the refactoring.
 \item \textbf{Parameters}: The number of parameters the extracted method has.
+If the extracted method uses data that is not available where it is located, the data must be passed using method parameters.
+If a method has many parameters, it becomes less reusable and harder to comprehend, thus harder to maintain \cite{heitlager2007practical}.
+Additionally, this increases the volume, because each call to the extracted method must pass all required data.
 \end{itemize}
 We hypothesize that these characteristics are the main factors influencing the impact on the maintainability of the system as a result of refactoring the clone.
+This is because there are no further transformations that are applied that influence the maintainability metrics.
 
-\subsubsection{Impact on maintainability metrics} \label{sec:metrics}
-CloneRefactor measures the impact on maintainability metrics of the refactored source code for each clone class that is refactored.
-These metrics are derived from Heitlager et al.~\cite{heitlager2007practical}.
-This paper defines a set of metrics to measure the maintainability of a system.
-For each of these metrics, risk profiles are proposed to determine the maintainability impact on the system of a whole.
+\section{Experimental setup} \label{sec:experimentalsetup}
+%In this section, we describe the setup of our experiments.
+We describe how we evaluated CR and the corpus on which we ran CR. We then describe the configuration of our experiments. Finally, we describe how we calculated our results.
+%Our goal is analysing whether automatic refactoring of code clones leads to an improved maintainability.
+We first validate our automatic refactoring tool, CR.
+Next, we run our tool on a reference corpus and measure the change in the maintainability score.
 
-To determine whether the maintainability improves when refactoring a single clone, we need to measure the impact of small-grained changes.
-Because of that, we measure only a subset of the metrics~\cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
-The subset of metrics we decided to focus on are all metrics that are measured on method level (as the other metrics show a lesser impact on the maintainability for these small changes).
-These metrics are:
-\begin{itemize}
-\item \textbf{Duplication}: In Heitlager et al.~\cite{heitlager2007practical} this metric is measured by taking the amount of duplicated lines.
-We decided to use the amount of duplicated tokens part of a clone class instead, to have a stronger reflection of the impact of the refactoring by measuring a more fine-grained system property.
-\item \textbf{Volume}: The more code a system has, the more code has to be maintained.
-The paper~\cite{heitlager2007practical} measures volume as lines of code.
-As with duplication, we use the number of tokens instead.
-\item \textbf{Complexity}: Heitlager et al.~\cite{heitlager2007practical} use MCCabe complexity~\cite{mccabe1976complexity} to calculate their complexity metric.
-The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.
-\item \textbf{Method Interface Size}: The number of parameters that a method has.
-If a method has many parameters, the code may become harder to understand and it is an indication that data is not encapsulated adequately in objects~\cite{fowler2018refactoring}.
-\end{itemize}
+\subsection{Tool Evaluation}
+We assess the correctness of CR through unit tests and empirical validation.
+First, we create a set of 57 control projects to verify the correctness in many (edge) cases.
+These projects contain clones for each relation, location, and refactorability category.
+%to see whether they get correctly identified. 
+Next, we run the tool over the corpus and manually verify samples of the acquired results.
+We verified at least 5 clones of each relation, location and refactoring.
+This way, we check both the correctness of the identified clones, their context, and their proposed refactoring.
 
-\section{Experimental setup}
-In this section, we describe the setup of our experiments.
+We also test the correctness of the refactored code using the JFreeChart project~\cite{gilbert2002jfreechart}.
+JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CR.
 
 \subsection{Corpus}
-We ran all our experiments using CloneRefactor on a corpus of open source Java projects.
-This corpus is derived from the corpus of a study that uses machine learning to determine the suitability of Java projects on GitHub for data analysis purposes~\cite{githubCorpus2013}.
+Our corpus, consisting of open source Java projects, is derived from the corpus of a study that uses machine learning to determine the suitability of GitHub Java projects for data analysis purposes~\cite{githubCorpus2013}.
+We chose this corpus because it has a variety of projects of different size and quality, which accurately reflects the target group for the results of our research.
 
-CloneRefactor requires all libraries of the projects it analyses, to find the full paths of all referenced symbols in the source code (see Sec.~\ref{sec:t1r}).
-Because of that requirement, we decided to filter the corpus to only projects using the Maven build automation system.
-We created a set of scripts\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} to prepare such a corpus with all dependencies included.
+CR requires all libraries of the analyzed projects
+%it analyses, to find the full paths of all referenced symbols in the source code 
+(see Sec.~\ref{sec:t1r}).
+Therefore, we decided to filter the corpus to contain only projects using the Maven build automation system.
+The filtering scripts are publicly availble \footnotesize{The camera-ready version would include the GitHub repo url}.
+%We created a set of scripts to prepare such a corpus with all dependencies included.
 
-This procedure results in 2.267 Java projects including all their dependencies.
+This procedure results in 2.267 Java projects including all their dependencies%\todo{this is confusing, how many original projects are there? were the dependencies in the original corpus?}
+.
 The projects vary in size and quality.
@@
 The largest project in the corpus is \textit{VisAD} with 502K lines.
+The distribution of project sizes is displayed in Fig.~\ref{fig:dist}.
 
-\subsection{Tool Validation}
-We have verified the correctness of CloneRefactor through unit tests and empirical verification.\todo{With unit test you are testing the properties which is verification.
-With projects you are validating as you are checking whether its finding what is it supposed to be finding.} First, we created a set of 57 control projects to verify the correctness in many (edge) cases.
-These projects contain clones for each identified relation, location, and refactorability category to see whether they get correctly identified.
-Next, we run the tool over the corpus and manually verify samples of the acquired results.
-This way, we check both the correctness of the identified clones, their context, and their proposed refactoring.
-
-We also test the correctness of the resulting code after refactoring.
-For this, we use a GitHub project named JFreeChart.
-JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor.
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/dist2}
+  \caption{Distribution of project sizes in corpus on a logaritmic scale.}
+  \label{fig:dist}
+\end{figure}
 
 \subsection{Minimum clone size}
-In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored.
-However, when clones are very small, they may never be able to improve maintainability.
+% In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored. However, 
+When clones are very small, they may never be able to improve maintainability.
 The detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication.
-Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones are very unlikely to improve maintainability when refactored.
+We perform all our experiments with a minimum clone size of 10 tokens, as smaller clones are very unlikely to improve maintainability when refactored (see our results in Sec.~\ref{sec:clonetokenvolume}).
 
-\subsection{Thresholds}
-Most clone detection tools can be configured using thresholds.
+%\subsection{Thresholds}
+%Most clone detection tools can be configured using thresholds.
 These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones.
-Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}.
-Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
+Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quantile distribution of empirical data~\cite{alves2010deriving}.
+%\todo{paragraph commented below seems more suitable for the discussion part. otherwise it should be rephrased.}
+% Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
 
@@
   \item Higher values for the metrics imply lower maintainability.
-  \item Normalizing each obtained metric delta over all deltas obtained for that metric in our dataset results in equally weighted scores.
+  \item Normalizing each metric delta over all deltas obtained for that metric in our dataset results in equally weighted
+  scores.%\todo{confusing}
+  \item All considered metrics do not interfere with the out-of-scope metrics
 \end{itemize}
-We derived these assumptions from supporting evidence shown by Heitlager et al~\cite{heitlager2007practical} and Alves et al.~\cite{alves2010deriving}.
-Using the resulting aggregated maintainability score, we can argue for each refactoring whether it increases or decreases the maintainability of the system.
 
-We normalize each obtained metric delta using the ``Standard score'', which is calculated as follows:
+We use the resulting aggregated maintainability score to analyze  for each refactoring whether it increases or decreases the maintainability of the system.
+
+We normalize each obtained metric delta using the standard score, because our data contains many outliers and the standard score is not much affected by those.
+The standard score is calculated as follows:
 \begin{equation}\label{eq:scoredev}
@@
 Where $\Delta X$ is a metric delta, $\mu$ is the mean of all deltas for this metric and $\sigma$ is the standard deviation of all deltas for this metric.
-This method works well for normalization of our data because as we divide by the standard deviation, outliers do not influence the resulting scores negatively.
+This method works well for normalization of our data because as we divide by the standard deviation, outliers do not influence the resulting scores negatively.% \todo{backup by citing relevant reference}.
 
-We then calculate the maintainability for a specific refactoring as follows:
+We calculate the maintainability of a refactoring as:
 \begin{equation}\label{eq:scoreref}
@@
 
-\section{Results}
-In this section, we share the results of our experiments.
+\section{Results} \label{sec:results}
+We first report the context results, then the refactorability results.
 
@@
 
-These results indicate that, given our refactorability criteria, 28\% of clones can be automatically refactored.
+The results show that, given our refactorability criteria, 28\% of clones can be automatically refactored.
 Clones in other categories may require other refactoring techniques or further transformations to be automatically refactorable.
@@
 \subsection{Thresholds}
-In our corpus, CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Sec.~\ref{sec:metrics}).
-Using the presented formulas (see Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
-In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.
+CR has refactored 12.710 clone classes and measured the change in the selected metrics (Sec.~\ref{sec:metrics}). %\todo{use the formulas labels to refer here.
+Using the formulas in Eq.~\ref{eq:scoredev} and~\ref{eq:scoreref}
+(Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
+We explore the data obtained by comparing the before- and after snapshots of the system for each separate refactoring.
 Using this data, we find supporting evidence regarding which thresholds are most likely to find clones that should be refactored to improve maintainability.
 
-\subsubsection{Clone Token Volume}
-Figure \ref{fig:maintainabilityscore} shows the obtained results when plotting the clone volume vs the average delta maintainability score.
+\subsubsection{Clone Token Volume} \label{sec:clonetokenvolume}
+Figure \ref{fig:maintainabilityscore} shows the results by plotting the clone volume vs the average delta maintainability score.
 We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class.
-For higher token volume numbers we have fewer refactorings that refactor such clones, because of which we represent the x-axis as a logarithmic scale.
+For higher token volume numbers we have fewer refactorings that refactor such clones, therefore we represent the x-axis as a logarithmic scale.
 The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.
 
+%\todo{Redo plot, explain axes units}
 \begin{figure*}
@@
 Table~\ref{tab:relation_refactor} shows our data regarding how different relations influence maintainability.
-We have marked rows based on less than 100 refactorings red, as their result does not have statistical significance.
-
-The displayed relations are ordered by their scores.
-Overall, the scores do not deviate much (-0.15 to 0.23), indicating that the relation between clones has a minor impact on maintainability.
-Overall, we see that common hierarchy clones have the highest maintainability, whereas unrelated clones have the lowest maintainability.
+We mark rows grey if they are based on less than 100 refactorings, as their result does not have statistical significance.
+Relations are ordered by their scores.
+%\todo{this sentence about relation impact seems more suitable for discussion}
+Scores do not deviate much (-0.15 to 0.23), indicating that the relation between clones has a minor impact on maintainability.
+Overall, common hierarchy clones have the highest maintainability, whereas unrelated clones have the lowest maintainability.
 
@@
 Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.
+The return categories are ordered by their scores.
+%\todo{this sentence about relation impact seems more suitable for discussion}
+Scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability.
+When the result of the call to the extracted method is directly returned, the maintainability score is the highest.
+When no value is returned, the maintainability score is the lowest.
+%\todo{this sentence about relation impact seems more suitable for discussion}
+The main reason that "Void" is lowest, is that it is linked to a higher number of parameters required for the extracted method.
 
@@
 
-The displayed return categories are ordered by their scores.
-Overall, the scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability.
-When the result of the call to the extracted method is directly returned, the maintainability score is the highest.
-When no value is returned, the maintainability score is the lowest.
-The main reason that no return value ends up lowest, is that it is linked to a higher number of parameters required for the extracted method.
-
 \subsubsection{Parameters}
@@
 
-\begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/arguments}
+%\todo{Redo plot, explain axes units}
+\begin{figure*}
+  \includegraphics[width=1\textwidth]{img/argu}
   \caption{Influence of number of method parameters on system maintainability.}
   \label{fig:arguments}
-\end{figure}
+\end{figure*}
 
-\section{Discussion}
+\section{Discussion} \label{sec:discussion}
 %In this section, we discuss the results of our experiments.
+
+%\todo{Explain about the coupling metric.
+Discussion: it is not too relevant to the results because most refactorings are SAME CLASS which do not impact on the coupling metric.
+(maybe more about architectural refactorings because COUPLING, BALANCE, COHESION?)}
 
@@
 Regarding clone context, our results indicate that most clones (37\%) are in a common class.
-This is favorable for refactoring because the extracted method does not have to be moved after extraction.
+This is favorable for automatic refactoring because the extracted method does not have to be moved after extraction.
 24\% of clones are in a common hierarchy.
@@
 15\% of clones are in an interface.
+%\todo{which ...}.
 
@@
 28\% of clones can be refactored using the ``Extract Method'' refactoring technique (50\% if we limit our searching scope to method bodies).
-About 25\% of clones do not span part of a method, because of which they cannot be refactored.
+About 25\% of clones do not span part of a method, therefore they cannot be refactored.
 Many clones (23\%) do not have a statement as top-level AST-Node.
-Upon manual inspection, we noticed that the main reason for this is when clones are found in lambda functions or anonymous classes.
-About 15\% of clones span only part of an AST-Node.
+Upon manual inspection, we noticed that the main reason is clones in lambda functions or in anonymous classes.
+About 15\% of clones span only part of an AST-Node.% \todo{and?}.
 
 \subsection{Refactoring}
-In Fig.~\ref{fig:maintainabilityscore} we see an increase in maintainability for refactoring larger clone classes.
-The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie around a token volume of 63 tokens.
-There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.
+Fig.~\ref{fig:maintainabilityscore} shows an increase in maintainability for refactoring larger clone classes.
+The tipping point, between a better and a worse maintainable refactoring, seems to lie around a token volume of 63 tokens.
+There are fewer large clones than small clones, resulting in a very limited %\todo{how limited?
+give the p-value}
+statistical significance on our corpus when considering clones larger than 100 tokens.
 
-In Table~\ref{tab:relation_refactor} we see the results regarding refactorings that are applied to clones with diverse relations.
-We see that most refactored clones are in a common class, over 54\%.
-This is significantly more than the percentage of clones in the common class relation as reported in Table~\ref{tab:relation}.
-Meanwhile, the number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% -> 18\%).
+Table~\ref{tab:relation_refactor} shows the results regarding refactorings that are applied to clones with diverse relations.
+More than 54\% of the refactored clones are in a common class.
+This is significantly more than the percentage of clones in the common class relation reported in Table~\ref{tab:relation}.
+The number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% -> 18\%).
 The main reason for this is that refactoring unrelated clones can change the relation of other clones in the same system.
@@
 
-The maintainability scores displayed in Table~\ref{tab:relation_refactor} show that the most favorable clones to refactor are clones with a Sibling relation.
-The most unfavorable is to refactor clones to interfaces.
-However, the differences in maintainability in this table are generally small; according to our data relations have only a minor impact on the maintainability of clones.
+The maintainability scores in Table~\ref{tab:relation_refactor} show that the most favorable clones to refactor are clones with a Sibling relation.
+The most unfavorable is refactoring clones to interfaces.
+However, the differences in maintainability in this table are generally small %\todo{and?}
+; according to our data relations have only a minor impact on the maintainability of clones.
 
-Regarding the return type of refactored clones, we see in Table~\ref{tab:return} that this has no major impact on maintainability.
+Regarding the return type of refactored clones, Table~\ref{tab:return} shows that this has no major impact on maintainability.
 A method call to the extracted method that is directly returned and no return type extracted methods are slightly more favorable than the others.
-We think the main reason that the ``Return'' category is on top is that when a variable is declared at the end of the cloned fragment, CloneRefactor directly returns its value and removes the declaration.
+We think the main reason that the ``Return'' category is on top is that when a variable is declared at the end of the cloned fragment, CR directly returns its value and removes the declaration.
 This decreases the volume slightly.
 
-A higher number of parameters directly influences the corresponding metric.
-Because of this, we see in Fig.~\ref{fig:arguments} that more parameters negatively influence maintainability.
-Not only the number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
+% A higher number of parameters directly influences the corresponding metric. 
+Fig.~\ref{fig:arguments} shows that more parameters negatively influence maintainability. Not only the %\todo{wasn't this a characteristic? this paragraph is somewhat confusing}
+number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
 Because of that, we see that the trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.
 
-\section{Conclusion}
+%\todo[inline]{one paragraph with a general remark on this discussion, summarizing our findings}
+\section{Conclusion} \label{sec:conclusion}
+%\todo[inline]{one paragraph summarizing the context of our research}
 We defined automatically refactorable clones and created a tool to detect and refactor them.
@@
 We built a tool that can automatically apply refactorings to 28\% of the clones in our corpus using the ``Extract Method'' refactoring technique. 
-The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, e.g., when code outside a method is part of a clone.
+% The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, e.g., when code outside a method is part of a clone.
 
-We measured four maintainability metrics before- and after applying each refactoring to determine the impact of each refactoring on system maintainability.
+We measured the change in four maintainability metrics
+%before- and after applying each refactoring 
+to determine the impact of each refactoring on system maintainability.
 We found that the most prominent factor influencing maintainability is the size of the clone.
-We found that the threshold lies at a clone volume of 29 tokens per clone instance for system maintainability to increase after refactoring the clone.
-Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data.
+We found that the threshold lies at a clone volume of 63  %\todo{wasn't this 63?}
+tokens for all clone instances combined for system maintainability to increase after refactoring the clone.
+Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data: when a clone is refactored to a method that requires more than 2 parameters it is more likely to decrease maintainability than to increase it.
 We noticed that the inheritance relation of the clone and the return value of the extracted method has only a minor impact on system maintainability.
 
-\section*{Acknowledgments}
-We would like to thank the Software Improvement Group for their continuous support in this project.
-In particular, we would like to thank Xander Schrijen for his invaluable input in this research.
-Furthermore, we would like to thank Sander Meester for his proofreading efforts and feedback.
-
-\bibliographystyle{ACM-Reference-Format}
+\bibliographystyle{plain}
 \bibliography{references}

### 2020-01-09 ecoop/paper.tex
Updates from Overleaf

@@
 \usepackage{parcolumns}
+
+\usepackage{chngpage}
+
+\usepackage{courier}
 
@@
 
-\lstnewenvironment{javacode}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small,#1}}{}
+\lstnewenvironment{javacode}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small}}{}
 
@@
 To remove such anti-patterns, the codebase should be refactored.
-Many tools aid in the detection process of such duplication problems but fail to determine whether refactoring a duplicate fragment would improve the maintainability.
+Many tools aid in the detection process of such duplication problems but do not determine whether refactoring an identified clone would improve the maintainability.
+Moreover, manual code clone refactoring is often tedious and could benefit from an automated tool.
 
-We address this shortcoming by first analyzing what data should be gathered from an automatically refactored system.
+We address this shortcoming by first analyzing what preconditions apply to be able to automatically refactor clones.
 We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them.
@@
 Based on these results, one could decide which clones would improve system design if refactored.
-We evaluate our approach over a large corpus of open source Java projects.
+We evaluate our approach over a large corpus of open-source Java projects.
 
-We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use.
-We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored.
-The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones with more than requiring more than one external parameter decreases maintainability.
+We identify the factors of interest characterizing the impact on the maintainability of automatically applied refactorings.
+We find that the biggest influencing factor is token volume.
+We define token volume as the combined number of tokens in all clone instances in a clone class.
+The majority of duplicates with a token volume of 63 or more tokens improve maintainability when refactored.
+The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones requiring more than two external parameters decrease maintainability.
 \end{abstract}
@@
 
-\begin{figure*}
+\begin{adjustwidth}{-0.8in}{-0.8in}% adjust the L and R margins by 1 inch
+\begin{minipage}{\linewidth}
 \begin{parcolumns}{2}
@@
 
-	public void addTen(int x) {
+	public int addTen(int x) {
 |\highlightYellow|		x = x + 10; // Addition
@@
 
-	public void concatTen(String x) {
+	public String concatTen(String x) {
 |\highlightYellow|		x = x + 10; // String concatenation
@@
 \end{parcolumns}
-\caption{Example of textually equal code fragments that differ in functionality.}
-\label{fig:type1}
-\end{figure*}
+%\caption{Example of textually equal code fragments that differ in functionality.}
+%\label{fig:type1}
+%\end{figure*}
+\end{minipage}
+\end{adjustwidth}
+
+\begin{lstlisting}[language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small]
+for i:=maxint to 0 do 
+begin 
+    j:=square(root(i));
+end;
+\end{lstlisting}
 

### 2020-01-10 ecoop/paper.tex
Updates from Overleaf

@@
 
-\lstnewenvironment{javacode}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small}}{}
+\lstnewenvironment{javacode}[1][]{\lstset{language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small,basicstyle=\ttfamily\footnotesize,
+    backgroundcolor=\color{white}}}{}
 
@@
 \author{}
-\authorrunning{}
+\authorrunning{Siimon :)}
 
@@
 
-\begin{adjustwidth}{-0.8in}{-0.8in}% adjust the L and R margins by 1 inch
+\begin{adjustwidth}{-0.5in}{-0.5in}% adjust the L and R margins by 1 inch
 \begin{minipage}{\linewidth}
@@
 \end{adjustwidth}
-
-\begin{lstlisting}[language=Java,escapechar=|,tabsize=2, breaklines=true, xleftmargin=.25in, keywordstyle=\color{pblue},basicstyle=\small]
-for i:=maxint to 0 do 
-begin 
-    j:=square(root(i));
-end;
-\end{lstlisting}
 
@@
  \begin{center}
-  \caption{Our survey on clone detection tools.} \label{table:dettools}
   \medskip
@@
 \end{tabular}
+\caption{Our survey on clone detection tools.} \label{table:dettools}
 \end{center}
@@
         \item \textbf{No Direct Superclass}: All clone instances are in classes that have the Object class as their parent.
-        \item \textbf{No Indirect Superclass}: All clone instances are in a hierarchy that contains a class that has the Object class as their parent.
-        \item \textbf{External Superclass}: All clone instances are in classes the same external class as their parent.
-        \item \textbf{Indirect External Ancestor}: All clone instances are in a hierarchy that contains a class that has an external class as their parent.
+        \item \textbf{No Indirect Superclass}: All clone instances have a non-external ancestor that extends the Object class as their parent.
+        \item \textbf{External Superclass}: All clone instances are in classes that have the same external class as their parent.
+        \item \textbf{Indirect External Ancestor}: If the clone does not adhere to all above-mentioned categories, it has an indirect external ancestor.
     \end{itemize}
@@
   \item \textbf{A return value}: If the method modifies or declares local data that is needed outside of its scope, or if the cloned fragments already returned data.
-  \item \textbf{Thrown exception}: If the method throws an uncaught exception that is not a \texttt{RuntimeException}.
+  \item \textbf{Thrown exception}: If the method throws an uncaught exception that is not a \\ \texttt{RuntimeException}.
 \end{itemize}
@@
 Therefore, we decided to filter the corpus to contain only projects using the Maven build automation system.
-The filtering scripts are publicly availble \footnotesize{The camera-ready version would include the GitHub repo url}.
+%The filtering scripts are publicly availble \footnotesize{The camera-ready version would include the GitHub repo url}.
 %We created a set of scripts to prepare such a corpus with all dependencies included.
@@
 CR has refactored 12.710 clone classes and measured the change in the selected metrics (Sec.~\ref{sec:metrics}). %\todo{use the formulas labels to refer here.
-Using the formulas in Eq.~\ref{eq:scoredev} and~\ref{eq:scoreref}
-(Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
+Using the formulas in Eq.~\ref{eq:scoredev} and~\ref{eq:scoreref} (Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
 We explore the data obtained by comparing the before- and after snapshots of the system for each separate refactoring.

### 2020-01-10 ecoop/paper.tex
Updates from Overleaf

@@
 
-\subsubsection{Maintainability metrics} \label{sec:metrics}
+\subsubsection{Selected metrics} \label{sec:metrics}
 CR measures the impact on maintainability metrics of refactoring source code for each clone class that is refactored.

### 2020-01-10 ecoop/paper.tex
Updates from Overleaf

@@
 \usepackage{courier}
+
+\usepackage{etoolbox}
+\AtBeginEnvironment{quote}{\singlespacing\footnotesize\ttfamily}
+
+\bibliographystyle{plainurl}
 
@@
 
-\author{}
-\authorrunning{Siimon :)}
+%\author{Anonymous Author}
+%\authorrunning{Anonymous Author}
+\author{Anonymous Author(s)}{-}{-}{-}{-}
+
+\authorrunning{Anonymous Author(s)}
+
+\Copyright{Anonymous Author(s)}
 
 \begin{document}
-
-%\author{Simon Baars}
-%\affiliation{\institution{University of Amsterdam}}
-%\email{simon.mailadres@gmail.com}
-
-%\author{Ana Oprescu}
-%\affiliation{\institution{University of Amsterdam}}
-%\email{a.m.oprescu@uva.nl}
 
@@
 This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
+
+For refactoring clones, we took naming the extracted method outside of the scope of the study.
+To have this not influence the results, the metrics that determine the maintainability of an applied refactoring do not measure the quality of the name of the extracted method.
 %The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
@@
 \begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/flow}
+  \includegraphics[width=0.7\columnwidth]{img/flow}
   \caption{Abstract flow diagram of CR.}
@@
 
+\subsection{Refactoring evaluation}
+To evaluate the refactorings applied by CR and their impact, we expanded CR to create a git-commit for each applied transformation.
+We then use the ``Github Desktop''\footnote{GitHub Desktop is a git client: \url{https://desktop.github.com/}} to visualize each change made by CR (see Fig.~\ref{fig:cr_refactoring}).
+We then checked samples of the applied refactorings and the calculated metrics.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1\columnwidth]{img/cr.png}
+    \caption{Automatically applied refactoring by CR shown in the GitHub Desktop client.
+CR automatically authors a git commit for each applied transformation and specifies the impact of the change in the commit message.}
+    \label{fig:cr_refactoring}
+\end{figure}
+
+The full commit message for the refactoring example displayed in Fig.~\ref{fig:cr_refactoring} is as follows:
+\begin{quote}
+CloneRefactor refactored a clone class with 2 clone instances.
+For the common code we created a new method and named this method “cloneRefactor0".
+These clone instances have a Same Method relation with each other.
+The newly created method has been placed in ISODateTimeFormat.
+Each duplicated fragment has been replaced with a call to this method.
+\\ \\
+== System Quality Metrics == \\
+Total Cyclomatic Complexity increased by 1 from 6,994 to 6,995.\\
+Total Unit Interface Size increased by 1 from 3,715 to 3,716.\\
+Total Unit Line Size increased by 1 from 23,024 to 23,025.\\
+Total Unit Token Size decreased by 2 from 153,190 to 153,188.\\
+Total Nodes decreased by 1 from 18,866 to 18,865.\\
+\\
+Duplicated Nodes decreased by 6 from 502 to 496.\\
+Duplicated Tokens decreased by 42 from 5,064 to 5,022.\\
+Duplicated Lines decreased by 6 from 504 to 498.\\
+\\
+== Risk Profiles ==\\
+Unit Complexity\\
+Created a new method with a low risk Unit Complexity of 1.\\
+Removing duplicate blocks changed 1 method.\\
+The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 8 to 8 Unit Complexity. This did not influence the risk category of this method, it is still low risk.\\
+\\
+Line Volume\\
+Created a new method with a low risk Line Volume of 5.\\
+Removing duplicate blocks changed 1 method.\\
+The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 47 to 39 Line Volume. This did not influence the risk category of this method, it is still high risk.\\
+\\
+Token Volume\\
+Created a new method with a low risk Token Volume of 30.\\
+Removing duplicate blocks changed 1 method.\\
+The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 303 to 271 Token Volume. This increased the risk category of this method from high to moderate.\\
+\\
+The new method has a low risk Unit Interface Size of 1.\\
+\\
+Duplication went from 2.66\% to 2.63\%. This did not influence the risk category of the duplication in this codebase, it is still low risk.
+\end{quote}
+
 \section{Experimental setup} \label{sec:experimentalsetup}
@@
 
-\begin{table}[H]
+\begin{table}
 \centering
@@
 
+\subsection{Future Work}
+
 \bibliographystyle{plain}

### 2020-01-10 ecoop/paper.tex
Updates from Overleaf
Abstract

@@
 
-\title{Improving Software Maintainability through Automated Refactoring of Code Clones}
+\title{Improving Software Maintainability through Automated Refactoring of Duplicate Code}
 
@@
 We address this shortcoming by first analyzing what preconditions apply to be able to automatically refactor clones.
-We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them.
+We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them using the ``Extract Method'' refactoring technique.
 We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system.
@@
 We identify the factors of interest characterizing the impact on the maintainability of automatically applied refactorings.
-We find that the biggest influencing factor is token volume.
-We define token volume as the combined number of tokens in all clone instances in a clone class.
-The majority of duplicates with a token volume of 63 or more tokens improve maintainability when refactored.
-The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones requiring more than two external parameters decrease maintainability.
+We find that the biggest influencing factor is the size of the clone.
+The majority of duplicates larger than 63 tokens improve maintainability when refactored.
+The amount of external data that needs to be passed to the extracted method is the other important factor: the majority of extracted methods requiring more than two parameters decrease maintainability.
 \end{abstract}

### 2020-01-11 ecoop/paper.tex
Future work

@@
 We find that the biggest influencing factor is the size of the clone.
-The majority of duplicates larger than 63 tokens improve maintainability when refactored.
+The majority of duplicates with 63 or more tokens improve maintainability when refactored.
 The amount of external data that needs to be passed to the extracted method is the other important factor: the majority of extracted methods requiring more than two parameters decrease maintainability.
@@
 
-We measure several maintainability metrics before and after refactoring to determine the impact on system maintainability of applying the refactoring.
-These metrics are volume, method parameters, duplication and complexity.
-Using this setup, we gain empirical data about the maintainability improvement of clones on a large set of data in a controlled environment.
-Because the refactoring is done automatically, we also consider micro-clones, which are shown to be important for refactoring consideration \cite{mondai2018micro}.
-We use this data to define which characteristics of clones have the biggest influence of system maintainability when such a clone is refactored.
+We measure several maintainability metrics \cite{heitlager2007practical} before and after refactoring each clone to determine its impact on system maintainability.
+These metrics are volume, number of parameters, duplication and complexity.
+Using this setup, we gain empirical data about the maintainability improvement of clones on a large set of projects in a controlled environment.
+We use this data to define which characteristics of clones have the biggest influence on system maintainability when such a clone is refactored.
 This allows for more a accurate suggestion of code clones for refactoring and can assist in the refactoring process.
@@
 Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quantile distribution of empirical data~\cite{alves2010deriving}.
-Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.% \todo{Check whether this really fits here}
-
-Over a corpus of 2.267 Java project our tool refactored 12.710 clone classes.
+Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
+Because of this, we minimize limiting the size of clones we find to measure the maintainability impact of all clones, including micro-clones \cite{mondai2018micro}.
+
+Over a corpus of 2,267 Java project our tool refactored 12,710 clone classes.
 We found that the main influencing factor on maintainability when refactored is token volume.
 We define token volume as the combined number of tokens in all clone instances in a clone class.
-When refactoring clones with a very small token volume, we found that the maintainability decreases when such clones are refactored.
-The average clone with a clone volume of 65 or larger improves maintainability when refactored.
+%When refactoring clones with a very small token volume, we found that the maintainability decreases when such clones are refactored.
+The average clone with a token volume of 63 or larger improves maintainability when refactored.
 The other factor with a major influence on maintainability is the number of parameters that are required for the extracted method.
@@
 \\ \textbf{Clone class}: A set of similar clone instances.
+
+Fig.~\ref{fig:cloneclasses} shows an example of two clone classes. The first clone class spans the first two lines of all three files. The second clone class spans all lines of the first two files.
+
+\begin{figure}[H]
+\begin{parcolumns}{3}
+\colchunk[1]{
+\begin{javacode}
+// File1.java
+|\highlightDarkyellow|doA();
+|\highlightDarkyellow|doB();
+|\highlightYellow|doC();
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// File2.java
+|\highlightDarkyellow|doA();
+|\highlightDarkyellow|doB();
+|\highlightYellow|doC();
+\end{javacode}}
+\colchunk[3]{
+\begin{javacode}
+// File3.java
+|\highlightYellow|doA();
+|\highlightYellow|doB();
+doD();
+\end{javacode}}
+\end{parcolumns}
+\caption{Example of two clone classes.}
+\label{fig:cloneclasses}
+\end{figure}
 
@@
 \subsection{Future Work}
+In this study, we limited our scope by taking the naming of generated declarations outside of the scope.
+When using our work for refactoring assistance, these names will have to be manually provided.
+Recent studies aim at solving this problem by generating a name that matches the body of a declaration \cite{allamanis2015suggesting, alon2018code2seq}.
+We will investigate the possibility to combine such approaches with CR, to make it more usable in the refactoring process.
+
+We also limited our scope by choosing a set of four metrics.
+However, software maintainability depends on more factors and can be measured by more metrics.
+By taking more metrics into account, we can give a better indication whether the maintainability improves after refactoring.
+For instance, we think that module coupling \cite{heitlager2007practical} is an important metric to be considered when refactoring clones.
+In out future work we will investigate other metrics and map their impact on the results.
 

### 2020-01-11 ecoop/paper.tex
Threats to validity

@@
 
-\usepackage{xcolor}
+\usepackage[table]{xcolor}
 \usepackage{graphicx}
@@
 \usepackage{chngpage}
-
 \usepackage{courier}
-
 \usepackage{etoolbox}
-\AtBeginEnvironment{quote}{\singlespacing\footnotesize\ttfamily}
+\AtBeginEnvironment{quote}{\footnotesize\ttfamily}
 
@@
 
+\begin{figure*}
 \begin{adjustwidth}{-0.5in}{-0.5in}% adjust the L and R margins by 1 inch
@@
 \end{parcolumns}
-%\caption{Example of textually equal code fragments that differ in functionality.}
-%\label{fig:type1}
-%\end{figure*}
 \end{minipage}
 \end{adjustwidth}
+\caption{Example of textually equal code fragments that differ in functionality.}
+\label{fig:type1}
+\end{figure*}
 
@@
 \begin{quote}
-CloneRefactor refactored a clone class with 2 clone instances.
-For the common code we created a new method and named this method “cloneRefactor0".
+CR refactored a clone class with 2 clone instances.
+For the common code we created a new method and named this method “refactoredClone0".
 These clone instances have a Same Method relation with each other.
@@
 
+\subsection{Threats to Validity}
+To limit the scope of this research, we chose not to include human subjects in this study.
+However, we think that the results of this study could be strengthened by performing a survey on software engineering practitioners.
+We have determined maintainability scores only based on literature input and statistical analysis.
+It would be valuable to have a control group rate the refactorings performed by CR, as an extra form of input regarding the quality of the code transformations that CR performs.
+
+In Section~\ref{sec:metricformula} we proposed an aggregation to measure a maintainability score on small-grained changes.
+The assumptions stated in this section influence the validity of the maintainability scores shown in our results.
+We noticed that the maintainability scores displayed in Table~\ref{tab:relation_refactor} and Table~\ref{tab:return} were mostly influenced by the differences in the ``number of parameters'' metric.
+This is because, for the scores, we normalized the metrics over all values obtained by these metrics.
+As our data regarding ``number of parameters'' has a very low standard deviation, small changes in this metric will influence the maintainability score a lot.
+
 \subsection{Future Work}

### 2020-01-11 ecoop/paper.tex
Updates from Overleaf

@@
 \textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed next to variations in identifiers, literals, types, layout, and comments.
+
 A higher type of clone means that it is harder to detect and refactor.
@@
 To reduce duplication with this technique, the contents of a single clone instance are extracted to a new method and all further locations of the clone are replaced by a call to the new method.
+An example of this is shown in Fig.~\ref{fig:extractmethod}.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+public void doStuff(){
+|\highlightYellow|  doA();
+|\highlightYellow|  doB();
+  doC();
+|\highlightYellow|  doA();
+|\highlightYellow|  doB();
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+public void doStuff(){
+|\highlightYellow|  doAandB();
+  doC();
+|\highlightYellow|  doAandB();
+}
+
+public void doAandB(){
+  doA();
+  doB();
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring a clone class through method extraction.}
+\label{fig:extractmethod}
+\end{figure}
 
@@
 \end{enumerate}
+
+\section{Related Work}\label{sec:relatedwork}
+We outline relevant research to clone refactoring. A significant aspect is the context of clones.
+
+\subsection{Clone context analysis}\label{sec:rw:contextanalysis}
+Golomingi~\cite{koni2001scenario} explores mapping the relation between clone instances to refactoring methods.
+The author analyses the refactoring methods described by Martin Fowler \cite{fowler1999refactoring} and analyzes what refactoring methods can be used to refactor clones with what inheritance relations.
+The identified clone relations are: Ancestor, Common Hierarchy, First Cousin, Same Method, Sibling, Single Class, Superclass and Unrelated.
+We extend this list with several more fine-grained relations, suitable for automatic refactoring (see Sec.~\ref{sec:relation}).
+
+Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} combine the research by Golomingi~\cite{koni2001scenario} with clone types 1 and 3 \cite{roy2007survey}.
+They use a large corpus~\cite{tempero2010qualitas} on which they perform statistical analyses of clone relations together with clone types.
+We repeat this research with a vastly different setup: we use the clone definition from Sec.~\ref{sec:research} and the relation categories outlined in Sec.~\ref{sec:relation}.
+
+\subsection{Clone refactoring}
+Krishnan et al.~\cite{krishnan2013refactoring} approach clone refactoring as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design.
+The main focus of this study is to find out which clones \textbf{can} be refactored.
+We extend this work by looking into which clones \textbf{should} be refactored.
+We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design.
+We measure which clones improve maintainability when refactored.
+This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
+
+For refactoring clones, we took naming the extracted method outside of the scope of the study.
+To have this not influence the results, the metrics that determine the maintainability of an applied refactoring do not measure the quality of the name of the extracted method.
+%The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
+The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems.
+This tool is based on several studies that look into different aspects of code clone refactoring.
+In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design.
+Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability.
+This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.
+
+%A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process.
 
@@
 
-\section{Related Work}\label{sec:relatedwork}
-We outline relevant research to clone refactoring. A significant aspect is the context of clones.
-
-\subsection{Clone context analysis}\label{sec:rw:contextanalysis}
-Golomingi~\cite{koni2001scenario} explores mapping the relation between clone instances to refactoring methods.
-The author analyses the refactoring methods described by Martin Fowler \cite{fowler1999refactoring} and analyzes what refactoring methods can be used to refactor clones with what inheritance relations.
-The identified clone relations are: Ancestor, Common Hierarchy, First Cousin, Same Method, Sibling, Single Class, Superclass and Unrelated.
-We extend this list with several more fine-grained relations, suitable for automatic refactoring (see Sec.~\ref{sec:relation}).
-
-Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} combine the research by Golomingi~\cite{koni2001scenario} with clone types 1 and 3 \cite{roy2007survey}.
-They use a large corpus~\cite{tempero2010qualitas} on which they perform statistical analyses of clone relations together with clone types.
-We repeat this research with a vastly different setup: we use the clone definition from Sec.~\ref{sec:research} and the relation categories outlined in Sec.~\ref{sec:relation}.
-
-\subsection{Clone refactoring}
-Krishnan et al.~\cite{krishnan2013refactoring} approach clone refactoring as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design.
-The main focus of this study is to find out which clones \textbf{can} be refactored.
-We extend this work by looking into which clones \textbf{should} be refactored.
-We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design.
-We measure which clones improve maintainability when refactored.
-This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
-
-For refactoring clones, we took naming the extracted method outside of the scope of the study.
-To have this not influence the results, the metrics that determine the maintainability of an applied refactoring do not measure the quality of the name of the extracted method.
-%The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
-The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems.
-This tool is based on several studies that look into different aspects of code clone refactoring.
-In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design.
-Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability.
-This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.
-
-%A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process.
-
 \section{Defining refactorable clones}\label{sec:research}
@@
 
-\section{Survey existing clone detection tools}\label{sec:survey}
+\section{Survey of existing clone detection tools}\label{sec:survey}
 %To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability.
@@
 
-\begin{figure}[H]
+\begin{figure}
     \centering
@@
 We chose this corpus because it has a variety of projects of different size and quality, which accurately reflects the target group for the results of our research.
+The entire corpus contains a total of 14,765 Java projects.
 
@@
 Therefore, we decided to filter the corpus to contain only projects using the Maven build automation system.
+We further discarded projects with build errors or unavailable dependencies.
 %The filtering scripts are publicly availble \footnotesize{The camera-ready version would include the GitHub repo url}.
@@
 
-This procedure results in 2.267 Java projects including all their dependencies%\todo{this is confusing, how many original projects are there? were the dependencies in the original corpus?}
+This procedure results in 2,267 Java projects including all their dependencies%\todo{this is confusing, how many original projects are there? were the dependencies in the original corpus?}
 .
@@
   \includegraphics[width=1\columnwidth]{img/dist2}
-  \caption{Distribution of project sizes in corpus on a logaritmic scale.}
+  \caption{Distribution of project sizes in corpus on a logarithmic scale.}
   \label{fig:dist}
@@
 
-\begin{table*}
+\begin{table}
 \centering
-%\resizebox{\textwidth}{!}{%
+\resizebox{\textwidth}{!}{%
 \begin{tabular}{@{}lrrrrrr@{}}
@@
 \end{tabular}%
-%}
+}
 \caption{Influence on maintainability of refactoring clones with the specified relation categories.}
 \label{tab:relation_refactor}
-\end{table*}
+\end{table}
 
@@
 This is significantly more than the percentage of clones in the common class relation reported in Table~\ref{tab:relation}.
-The number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% -> 18\%).
+The number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% vs 18\%).
 The main reason for this is that refactoring unrelated clones can change the relation of other clones in the same system.

### 2020-01-30 summary.tex
Updates from Overleaf

To be able to deliver high-quality software without major delays, it is important to control the maintainability of the software. Low maintainability means that developers spend too much time on maintaining and fixing old code. Research shows that maintaining source code takes at least twice as long when maintainability is measured as below average, compared to when maintainability is above average. Lack of maintainability is to a large extent caused by simple issues that occur over and over again. Consequently, the most efficient and effective way to improve maintainability is to address these simple issues.

One of these issues is duplication. Duplication in source code, also called ``code clones'', is the result of a developer reusing code by copying it to another place in the codebase. The often more desired alternative is to, instead of copying code, introduce abstractions to call the same code from different places. Failing to do so needlessly increases the size of the system (up to 25\% volume overhead). It also makes the system more error-prone, because making a change in a cloned code fragment may have to be applied to the other instances as well. Failing to do so can result in unintended behavior.

To solve such duplication issues several refactoring techniques can be used. Refactoring is the process of restructuring code to improve its quality attributes, without changing its functionality. Manual refactoring efforts to reduce duplication take time, require expertise and are prone to cause bugs. To mitigate these issues, we look into to what extent duplication can automatically be refactored.

We first look into how to define clones such that they can be refactored. We look into existing clone type definitions, which argue about the variance that is allowed between code fragments to still consider them clones. The problem towards our goals is that these definitions cannot be be automatically refactored. We propose new clone type definitions that allow for automated refactoring, and propose a method with which to detect clones by these definitions.

To determine what refactoring method to use to refactor clones, we consider their context. We define the context of clones as their relation, location and contents attributes. The relation argues about how each similar fragment in a clone is related to one another, which is important to determine where to place the merged code fragment. The location argues about in what type of place the clone is located in the code: this is used to determine the refactorability of the clone (not every location can be refactored). The contents argue about what code the clone spans: based on this different refactoring techniques may be required.

We then perform statistical measurements on these context categories, to understand which refactoring methods can be used to refactor most clones.

% After 15 years of consulting about software quality, we at the Software Improvement
% Group (SIG) have learned a thing or two about maintainability.
% First, insufficient maintainability is a real problem in the practice of software development. Low maintainability means that developers spend too much time on main‐
% taining and fixing old code. That leaves less time available for the most rewarding
% part of software development: writing new code. Our experience, as well as the data
% we have collected, shows that maintaining source code takes at least twice as long
% when maintainability is measured as below average, compared to when maintainabil‐
% ity is above average. See Appendix A to learn how we measure maintainability.
% Second, lack of maintainability is to a large extent caused by simple issues that occur
% over and over again. Consequently, the most efficient and effective way to improve
% maintainability is to address these simple issues. Improving maintainability does not
% require magic or rocket science. A combination of relatively simple skills and knowl‐
% edge, plus the discipline and environment to apply them, leads to the largest improve‐
% ment in maintainability.
% At SIG, we have seen systems that are essentially unmaintainable. In these systems,
% bugs are not fixed, and functionality is not changed or extended because it is consid‐
% ered too time-consuming and risky. Unfortunately, this is all too common in today’s
% IT industry, but it does not have to be like that.

% Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code. To remove such anti-patterns, the codebase should be refactored. Many tools aid in the detection process of such duplication problems but fail to determine whether refactoring a duplicate fragment would improve the maintainability.

% We address this shortcoming by combining automated refactoring and maintainability metrics to measure the impact of refactoring code clones. We propose definitions of clones that can be automatically refactored. We then propose a tool to detect such clones, analyze their context and automatically refactor a subset of them. We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system. Based on these results, one could decide which clones improve system design and thus should be refactored. We evaluate our approach over a large corpus of open source Java projects.

% We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use. We find that the size of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total volume of 68 or more tokens improve maintainability when refactored. The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the refactored method should not have more than 1 parameter.

### 2020-01-30 summary.tex
Updates from Overleaf

@@
 We then perform statistical measurements on these context categories, to understand which refactoring methods can be used to refactor most clones.
+We find that most clones can be refactored by moving common code to a new method and placing that method in a location that is accessible by all places the duplicated code was used, then replacing each of these fragments by a call to the new method.
+This technique is called ``Extract Method''.
+We apply this technique to automatically refactor clones in a large corpus of open-source Java projects and use it to automatically refactor 28\% of the present duplication.
+
+We then look at which characteristics of the refactored clones have the biggest impact on the maintainability of the system.
+We find that the size of the clone, measured in number of tokens (a token is the smallest element of a program that is meaningful to the compiler), has the biggest impact on the maintainability of the system.
+A second factor with a large impact is the amount of data used in both code fragments that are declared outside the scope of the fragment.
+The latter is currently not used to determine whether a clone should be refactored, however our results show that it is relevant to be considered.
 

### 2020-04-25 ase/paper.tex
Updates from Overleaf

--- 2019-08-24 icse/paper.tex
@@
-\documentclass[sigconf,review, table]{acmart}
+\documentclass[sigconf,review,anonymous]{acmart}
 
@@
 
-%\author{Simon Baars}
-%\affiliation{\institution{University of Amsterdam}}
-%\email{simon.mailadres@gmail.com}
+\author{Simon Baars}
+\affiliation{\institution{University of Amsterdam}}
+\email{simon.mailadres@gmail.com}
 
-%\author{Ana Oprescu}
-%\affiliation{\institution{University of Amsterdam}}
-%\email{a.m.oprescu@uva.nl}
+\author{Ana Oprescu}
+\affiliation{\institution{University of Amsterdam}}
+\email{a.m.oprescu@uva.nl}
 
@@
 To remove such anti-patterns, the codebase should be refactored.
-Many tools aid in the detection process of such duplication problems but fail to determine whether refactoring a duplicate fragment would improve the maintainability.
+Many tools aid in the detection process of such duplication problems but do not determine whether refactoring an identified clone would improve the maintainability.
+Moreover, manual code clone refactoring is often tedious and could benefit from an automated tool.
 
-We address this shortcoming by first analyzing what data should be gathered from an automatically refactored system.
-We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them.
+We address this shortcoming by first analyzing what preconditions apply to be able to automatically refactor clones.
+We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them using the ``Extract Method'' refactoring technique.
 We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system.
 Based on these results, one could decide which clones would improve system design if refactored.
-We evaluate our approach over a large corpus of open source Java projects.
+We evaluate our approach over a large corpus of open-source Java projects.
 
-We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use.
-We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored.
-The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones with more than requiring more than one external parameter decreases maintainability.
+We identify the factors of interest characterizing the impact on the maintainability of automatically applied refactorings.
+We find that the biggest influencing factor is the size of the clone.
+The majority of duplicates with 63 or more tokens improve maintainability when refactored.
+The amount of external data that needs to be passed to the extracted method is the other important factor: the majority of extracted methods requiring more than two parameters decrease maintainability.
 \end{abstract}

### 2020-04-26 ase/paper.tex
Updates from Overleaf

@@
 Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code.
-To remove such anti-patterns, the codebase should be refactored.
+Several studies show however, that not all duplication should be refactored.
+When some duplication is refactored, other system attributes are negatively affected thus resulting in a negative impact on the codebase when all system attributes are considered.
+% To remove such anti-patterns, the codebase should be refactored.
 Many tools aid in the detection process of such duplication problems but do not determine whether refactoring an identified clone would improve the maintainability.
@@
 
-We address this shortcoming by first analyzing what preconditions apply to be able to automatically refactor clones.
+We use software maintainabilty metrics to determine the impact of refactoring 
+We consider the ``duplicate code'' code smell from a maintainability perspective. We analyze 
+%We address this shortcoming by first analyzing what preconditions apply to be able to automatically refactor clones.
 We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them using the ``Extract Method'' refactoring technique.

### 2020-04-26 ase/paper.tex
Updates from Overleaf

@@
 When some duplication is refactored, other system attributes are negatively affected thus resulting in a negative impact on the codebase when all system attributes are considered.
-% To remove such anti-patterns, the codebase should be refactored.
-Many tools aid in the detection process of such duplication problems but do not determine whether refactoring an identified clone would improve the maintainability.
-Moreover, manual code clone refactoring is often tedious and could benefit from an automated tool.
+We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code.
+For a given refactoring we aggregate several maintainability metrics (duplication, complexity, unit size, code volume) to determine whether it improves the code.
+To simulate such refactorings in a controlled environment, we propose a tool that can automatically refactor a subset of duplication problems in Java source code.
+Our tool refactors 13k clones over 2k open source Java projects and measures the delta maintainability scores of the refactoring.
 
-We use software maintainabilty metrics to determine the impact of refactoring 
-We consider the ``duplicate code'' code smell from a maintainability perspective. We analyze 
-%We address this shortcoming by first analyzing what preconditions apply to be able to automatically refactor clones.
-We then propose a tool to detect clones, analyze their context and automatically refactor a subset of them using the ``Extract Method'' refactoring technique.
-We use a set of established metrics to determine the impact of the applied refactorings on the maintainability of the system.
-Based on these results, one could decide which clones would improve system design if refactored.
-We evaluate our approach over a large corpus of open-source Java projects.
-
-We identify the factors of interest characterizing the impact on the maintainability of automatically applied refactorings.
-We find that the biggest influencing factor is the size of the clone.
-The majority of duplicates with 63 or more tokens improve maintainability when refactored.
-The amount of external data that needs to be passed to the extracted method is the other important factor: the majority of extracted methods requiring more than two parameters decrease maintainability.
+We correlate the delta maintainability score with the factors that influence this score (clone volume, clone complexity, externally declared data used).
+We find that the biggest influencing factor is the volume of the clone.
+Our data shows that clones consisting of 63 or fewer tokens most often shouldn't be refactored.
+The other important factor is externally declared data that is used in the clone, clones with more than two externally declared variables most often do not improve maintainability when refactored.
 \end{abstract}
@@
 
+\section{Threats to validity}
+This research relies on the assumption that the maintainability model proposed by Heitlager et al.~\cite{heitlager2007practical} gives a good indication of the actual maintainabilty of a system.
+Furthermore, we rely on that the scores of different metrics have an equal weight relative to each other, as for our aggregation of the scores.
+
 \section{Conclusion}

### 2020-05-03 ase/paper.tex
Updates from Overleaf

@@
 
-\title{Improving Software Maintainability through Automated Refactoring of Code Clones}
+\title{Code Clones: To refactor or not to refactor?}
 
@@
 \begin{abstract}
+% Problem
 Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code.
-Several studies show however, that not all duplication should be refactored.
-When some duplication is refactored, other system attributes are negatively affected thus resulting in a negative impact on the codebase when all system attributes are considered.
+Several studies show that not all duplication should be refactored.
+When duplication is refactored, other system attributes may be negatively affected thus resulting in a negative impact on the codebase when all system attributes are considered.
+
+% How we fix the problem that we introduced in the first paragraph
 We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code.
 For a given refactoring we aggregate several maintainability metrics (duplication, complexity, unit size, code volume) to determine whether it improves the code.
+
+% Experimental setup: how we validated that we fixed the problem
 To simulate such refactorings in a controlled environment, we propose a tool that can automatically refactor a subset of duplication problems in Java source code.
-Our tool refactors 13k clones over 2k open source Java projects and measures the delta maintainability scores of the refactoring.
+Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.
 
+% results: what have we learned by fixing the problem
 We correlate the delta maintainability score with the factors that influence this score (clone volume, clone complexity, externally declared data used).
 We find that the biggest influencing factor is the volume of the clone.
-Our data shows that clones consisting of 63 or fewer tokens most often shouldn't be refactored.
+Our data shows that clones consisting of 63 or fewer tokens most often \textit{should not} be refactored.
 The other important factor is externally declared data that is used in the clone, clones with more than two externally declared variables most often do not improve maintainability when refactored.
+
+% What we want to achieve: provide support for a developer to decide whether a given clone is likely to improve the codebase when refactoring.
+Intersect clones with maintainability metrics to answer the "which clones should be considered harmful" question that can be found throughout literature.
+% Output: A checklist for developers.
+% The quantitative study with the tool is about validating the checklist.
+% Check whether it is doable to create an automated tool for predicting (mathematically whether a given clone improves the code), otherwise we have to continue on with the checklist.
 \end{abstract}

### 2020-05-03 ase/paper.tex
Updates from Overleaf

@@
 Apart from that, code clones can contribute up to 25\% of the code size~\cite{bruntink2005use}.
+However, manual code clone refactoring is often tedious and could benefit from an automated tool~\cite{mazinanian2016jdeodorant}.
 
-Current code clone detection techniques base their thresholds and prioritization on a limited set of metrics.
-Often, clone detection techniques are limited to measuring the size of clones to determine whether they should be considered.
+%Clone detection tools often use thresholds to determine which clones should be considered.
+Most clone detection tools use the number of lines \cite{kamiya2002ccfinder, svajlenko2016bigcloneeval}, statements \cite{higo2013revisiting, kamalpriya2017enhancing} and/or tokens \cite{ragkhitwetsagul2019siamese, jiang2007deckard} as thresholds to determine whether clones should be considered.
+We outline the shortcomings of these thresholds to find clones such that the maintainability of the source code is improved when refactored, and propose new thresholds to control this characteristic.
+% Current clone detection techniques are limited to measuring the size of clones to determine whether they should be considered.
 Because of this, the output of clone detection tools is often of limited assistance to the developer in the refactoring process.
+To reduce duplication of a codebase, there are several refactoring techniques that can be applied in an automated manner.
+The most used refactoring technique to deal with code clones is ``Extract Method'' \cite{fowler2018refactoring}.
+This technique entails that the duplicated code is moved to a new method, which is then called from all locations where the duplicated code was used.
+To be able to execute such a refactoring, several preconditions apply \cite{tsantalis2015assessing}.
+%\todo[inline]{still missing link on how current solutions do not help improving maintainability - our message from monday night is not crystal clear yet}
+In this study, we analyze which preconditions apply to determine whether a clone could and should be automatically refactored.
+We list criteria that influence the maintainability of clones when refactored.
+We evaluate the context of clones to determine which refactoring techniques are best suited.
+We define the context of clones as the inheritance relation between clone instances in a clone class and the location of clone instances in the codebase.
+We showcase the proposed technique as a tool that automatically refactors clones by extracting new methods out of duplicated code.
 
-In this study, we define a technique to detect clones such that they can be automatically refactored.
-We list a set of criteria that can obstruct refactoring opportunities.
-We evaluate the relation and location of clones to determine which refactoring techniques are best suited.
-We introduce a tool that automatically refactors clones by extracting new methods out of duplicated code.
+We measure several maintainability metrics \cite{heitlager2007practical} before and after refactoring each clone to determine its impact on system maintainability.
+These metrics are volume, number of parameters, duplication and complexity.
+Using this setup, we gain empirical data about the maintainability improvement of clones on a large set of projects in a controlled environment.
+We use this data to define which characteristics of clones have the biggest influence on system maintainability when such a clone is refactored.
+This allows for more a accurate suggestion of code clones for refactoring and can assist in the refactoring process.
 
-We evaluate our approach by comparing the maintainability of before- and after snapshots of a codebase for each duplication problem that is refactored.
+Most clone detection tools can be configured using thresholds.
+These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones.
+Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quantile distribution of empirical data~\cite{alves2010deriving}.
+Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
+Because of this, we minimize limiting the size of clones we find to measure the maintainability impact of all clones, including micro-clones \cite{mondai2018micro}.
+
+Over a corpus of 2,267 Java project our tool refactored 12,710 clone classes.
+We found that the main influencing factor on maintainability when refactored is token volume.
+We define token volume as the combined number of tokens in all clone instances in a clone class.
+%When refactoring clones with a very small token volume, we found that the maintainability decreases when such clones are refactored.
+The average clone with a token volume of 63 or larger improves maintainability when refactored.
+The other factor with a major influence on maintainability is the number of parameters that are required for the extracted method.
+We found that if a clone requires more than 2 parameters in the extracted method, it is more likely to decrease maintainability.
+
+This paper is organized as follows.
+In Sec.~\ref{sec:background} we revisit key clone refactoring background.
+Sec.~\ref{sec:relatedwork} discusses state-of-the-art in automatic clone refactoring research.
+In Sec.~\ref{sec:research} we propose a definition for clones such that they could and should be automatically refactored.
+In Sec.~\ref{sec:clonerefactor} we introduce our clone refactoring tool.
+In Sec.~\ref{sec:experimentalsetup} we explain the setup of our experiments; we show the results in Sec.~\ref{sec:results} and discuss them in Sec.~\ref{sec:discussion}.
+%We evaluate our approach by comparing the maintainability of before- and after snapshots of a codebase for each duplication problem that is refactored.
 We define which factors have the greatest influence on whether a clone improves maintainability when refactored.
@@
 
+Fig.~\ref{fig:cloneclasses} shows an example of two clone classes. The first clone class spans the first two lines of all three files. The second clone class spans all lines of the first two files.
+
+\begin{figure}[H]
+\begin{parcolumns}{3}
+\colchunk[1]{
+\begin{javacode}
+// File1.java
+|\highlightDarkyellow|doA();
+|\highlightDarkyellow|doB();
+|\highlightYellow|doC();
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// File2.java
+|\highlightDarkyellow|doA();
+|\highlightDarkyellow|doB();
+|\highlightYellow|doC();
+\end{javacode}}
+\colchunk[3]{
+\begin{javacode}
+// File3.java
+|\highlightYellow|doA();
+|\highlightYellow|doB();
+doD();
+\end{javacode}}
+\end{parcolumns}
+\caption{Example of two clone classes.}
+\label{fig:cloneclasses}
+\end{figure}
+
+%\subsection{Clone Types}
+Duplication in code is found in many different forms.
+Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}.
+Sometimes this code is then adapted to fit the new context.
+To reason about these modifications, several clone types have been proposed%.
+These clone types are described in Roy et al
+~\cite{roy2007survey}:\\
+\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout), and comments.\\
+\textbf{Type II:} Structurally/syntactically identical fragments except variations in identifiers, literals, types, layout, and comments.\\
+\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed next to variations in identifiers, literals, types, layout, and comments.
+
+A higher type of clone means that it is harder to detect and refactor.
+Many studies adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
+
+\subsection{Clone Refactoring}
+\subsubsection{Refactoring techniques}
 The most common technique for refactoring clones is ``Extract Method''~\cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
-Applying this technique entails moving functionality in the body of a method to a new method.
-To reduce duplication with this technique, we extract the contents of a single clone instance to a new method and replace all clone instances in a clone class by a call to this method.
+Applying this technique entails moving functionality from the body of a method to a new method.
+To reduce duplication with this technique, the contents of a single clone instance are extracted to a new method and all further locations of the clone are replaced by a call to the new method.
+An example of this is shown in Fig.~\ref{fig:extractmethod}.
+
+\begin{figure}[H]
+\begin{parcolumns}{2}
+\colchunk[1]{
+\begin{javacode}
+// Original
+public void doStuff(){
+|\highlightYellow|  doA();
+|\highlightYellow|  doB();
+  doC();
+|\highlightYellow|  doA();
+|\highlightYellow|  doB();
+}
+\end{javacode}}
+\colchunk[2]{
+\begin{javacode}
+// Refactored
+public void doStuff(){
+|\highlightYellow|  doAandB();
+  doC();
+|\highlightYellow|  doAandB();
+}
+
+public void doAandB(){
+  doA();
+  doB();
+}
+\end{javacode}}
+\end{parcolumns}
+\caption{Refactoring a clone class through method extraction.}
+\label{fig:extractmethod}
+\end{figure}
+
+\subsubsection{Preconditions}
+Clones detected by current detection techniques \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, cordy2011nicad} are subject to a set of preconditions to determine whether they can be refactored \cite{tsantalis2015assessing}:
+\begin{enumerate}
+  \item The parameterization of differences between the matched statements should not break existing data-, anti-, and output-dependencies.
+  \item The unmatched statements should be movable before or after the matched statements without breaking existing data-, anti-, and output-dependencies.
+  \item The duplicated code fragments should return at most one variable of the same type.
+  \item Matched branching (\texttt{break}, \texttt{continue}) statements should be accompanied with corresponding matched loop statements.
+  \item Matched variables having different subclass types should call only methods that are declared in the common superclass or are being overridden in the respective subclasses.
+  \item The parameterization of fields belonging to differences between the mapped statements is possible only if they are not modified.
+  \item The parameterization of method calls belonging to differences between the mapped statements is possible only if they do not return a void type.
+  \item The mapped statements within the clone fragments should not contain any conditional return statements.
+\end{enumerate}
+
+\section{Related Work}\label{sec:relatedwork}
+We outline relevant research to clone refactoring. A significant aspect is the context of clones.
+
+\subsection{Clone context analysis}\label{sec:rw:contextanalysis}
+Golomingi~\cite{koni2001scenario} explores mapping the relation between clone instances to refactoring methods.
+The author analyses the refactoring methods described by Martin Fowler \cite{fowler1999refactoring} and analyzes what refactoring methods can be used to refactor clones with what inheritance relations.
+The identified clone relations are: Ancestor, Common Hierarchy, First Cousin, Same Method, Sibling, Single Class, Superclass and Unrelated.
+We extend this list with several more fine-grained relations, suitable for automatic refactoring (see Sec.~\ref{sec:relation}).
+
+Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} combine the research by Golomingi~\cite{koni2001scenario} with clone types 1 and 3 \cite{roy2007survey}.
+They use a large corpus~\cite{tempero2010qualitas} on which they perform statistical analyses of clone relations together with clone types.
+We repeat this research with a vastly different setup: we use the clone definition from Sec.~\ref{sec:research} and the relation categories outlined in Sec.~\ref{sec:relation}.
+
+\subsection{Clone refactoring}
+Krishnan et al.~\cite{krishnan2013refactoring} approach clone refactoring as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design.
+The main focus of this study is to find out which clones \textbf{can} be refactored.
+We extend this work by looking into which clones \textbf{should} be refactored.
+We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design.
+We measure which clones improve maintainability when refactored.
+This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
+
+For refactoring clones, we took naming the extracted method outside of the scope of the study.
+To have this not influence the results, the metrics that determine the maintainability of an applied refactoring do not measure the quality of the name of the extracted method.
+%The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
+The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems.
+This tool is based on several studies that look into different aspects of code clone refactoring.
+In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design.
+Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability.
+This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.
+
+%A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process.
 
 \begin{figure*}
+\begin{adjustwidth}{-0.5in}{-0.5in}% adjust the L and R margins by 1 inch
+\begin{minipage}{\linewidth}
 \begin{parcolumns}{2}
@@
 
-	public void concatTen(String x) {
-|\highlightYellow|		x = x + 10; // String concat
+	public String concatTen(String x) {
+|\highlightYellow|		x = x + 10; // String concatenation
 |\highlightYellow|		Notifier.notifyChanged(x);
@@
 \end{parcolumns}
+\end{minipage}
+\end{adjustwidth}
 \caption{Example of textually equal code fragments that differ in functionality.}
@@
 
-\section{Related Work}
-The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
-The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems.
-This tool is based on several studies that look into different aspects of code clone refactoring.
-In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how does variability between cloned fragments influence the refactoring techniques required and their implications on system design.
-Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability.
-This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.
+\section{Defining refactorable clones}\label{sec:research}
+%In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}.
+We discuss how we can define clones such that they can be automatically refactored while avoiding changing the functional behavior and other negative side effects on the source code, such as decreasing the maintainability of the code.
 
-A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process.
-The main focus is to find out which clones \textbf{can} be refactored.
-We extend this work by looking into which clones \textbf{should} be refactored.
-We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design.
-We measure which clones improve maintainability when refactored.
-This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
-
-\section{Defining refactorable clones}
-In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}.
-We discuss how we can define clones such that they can be automatically refactored without side effects on the source code.
-
-\subsection{Ensuring Equality}\label{sec:t1r}
+\subsection{Ensuring equality}\label{sec:t1r}
 Most modern clone detection tools detect duplication by comparing the code textually together with the omission of certain tokens~\cite{roy2009comparison, svajlenko2014evaluating}.
@@
 Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context~\cite{roy2007survey}.
-When dealing with such a situation, there are several opportunities to refactor so-called ``gapped clones''~\cite{ueda2002detection, zhao2018automatic}.
+When dealing with such situations, there are several opportunities to refactor so-called ``gapped clones''~\cite{ueda2002detection, zhao2018automatic}.
 ``Gapped clones'' are two clone instances separated by a ``gap'' of non-cloned statement(s).
-We define the following methods to refactor such clones:
+We define the following methods to refactor such clones, based on research by Tsantalis et al~\cite{tsantalis2015assessing}:
 \begin{itemize}
-  \item We wrap the difference in statements in a conditionally executed block, one path for each different (group of) statement(s).
-  \item We use a lambda function to pass the difference in statements from each location of the clone~\cite{tsantalis2017clone}.
+  \item Wrap the difference in statements in a conditionally executed block, one path for each different (group of) statement(s).
+  \item Use a lambda function to pass the difference in statements from each location of the clone~\cite{tsantalis2017clone}.
 \end{itemize}
-For both refactoring techniques, a trade-off is at play. This is because these solutions increase the complexity and volume of the source code in favor of removing a clone.
+For both of these techniques, a trade-off is at play. This is because these solutions increase the complexity and volume of the source code in favor of removing a clone.
 
-\section{The CloneRefactor tool}
-To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
-We created a set of control projects\footnote{Control projects for assessing clone detection tools: \url{https://github.com/SimonBaars/CloneRefactor/tree/master/src/test/resources}} to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output.
+\section{Survey of existing clone detection tools}\label{sec:survey}
+%To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability.
+To investigate the impact of the definitions introduced in Sec.~\ref{sec:research}, we need a tool to detect refactorable clones according to these definitions.
+We conducted a short survey on (recent) clone detection tools to detect such clones that can be refactored.
+The results of our survey are displayed in table~\ref{table:dettools}.
+We chose a set of tools that are open source and can analyze a popular object-oriented programming language.
+Next, we formulate the following four criteria by which we analyze these tools:
+\begin{enumerate}
+    \item \textbf{Should find clones in any context.} Some tools only find clones in specific contexts, such as only method level clones.
+We want to perform an analysis of all clones in projects to get a complete overview.
+\item \textbf{Finds clone classes in control projects.} We assembled a number of control projects to assess the validity of the surveyed clone detection tools.
+\item \textbf{Can analyze resolved symbols.} When detecting the clones proposed in Sec.~\ref{sec:research}, it is important that we can analyze resolved symbols (for instance a type reference).
+\item \textbf{Extensive detection configuration.} Detecting our clone definitions, as proposed in Sec.~\ref{sec:research}, require to have some understanding about the meaning of tokens in the source code (whether a certain token is a type, variable, etc.).
+The tool should recognize such structures, in order for us to configure our clone type definitions in the tool.
+\end{enumerate}
 
-None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we propose CloneRefactor\footnote{The source code of CloneRefactor is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
+\begin{table}[H]
+ \begin{center}
+  \medskip
+\begin{tabular}{|l|l|l|l|l|l|}
+\hline
+\textbf{Clone Detection Tool} & \textbf{(1)} & \textbf{(2)} & \textbf{(3)} & \textbf{(4)} \\ \hline
+Siamese~\cite{ragkhitwetsagul2019siamese} &  &             &             & \checkmark            \\ \hline
+NiCAD~\cite{roy2008nicad, cordy2011nicad} & \checkmark                             & \checkmark            &             &             \\ \hline
+CPD~\cite{roy2009comparison} & \checkmark & \checkmark            &             &             \\ \hline
+\begin{tabular}[c]{@{}l@{}}CCFinder~\cite{kamiya2002ccfinder}\\ D-CCFinder~\cite{livieri2007very}\end{tabular} & \checkmark  & \checkmark   &    &   \\ \hline
+CCFinderSW~\cite{semura2017ccfindersw}   & \checkmark     &             &             & \checkmark            \\ \hline
+\begin{tabular}[c]{@{}l@{}}SourcererCC~\cite{sajnani2016sourcerercc}\\ Oreo~\cite{saini2018oreo}\end{tabular} & \checkmark    &             &             & \checkmark            \\ \hline
+BigCloneEval~\cite{svajlenko2016bigcloneeval}  & \checkmark  & \checkmark   &             &             \\ \hline
+Deckard~\cite{jiang2007deckard} & \checkmark   &             & \checkmark            &             \\ \hline
+Scorpio~\cite{higo2013revisiting, kamalpriya2017enhancing} & \checkmark   &     & \checkmark  & \checkmark   \\ \hline
+\end{tabular}
+\caption{Our survey on clone detection tools.} \label{table:dettools}
+\end{center}
+\end{table}
+
+Apart from these criteria, we found that the output of these clone detection tools cannot be post-processed to find the clone definition proposed in Sec.~\ref{sec:research}.
+This is mainly because these clones are not necessarily a subset of clones detected by these tools and will thus require an analysis of the entire system.
+
+%To detect clones that can be automatically refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
+We created a set of control projects to determine the suitability of these tools to detect automatically refactorable clones, either through configuration or postprocessing of their output.
+
+%None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable for our definitions of refactorable clones, because of which we propose CR.
 This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
 In the following sections, we explain these steps.
+
+\section{A tool for automatic clone refactoring}\label{sec:clonerefactor}
+None of the surveyed tools were suitable for our definitions of refactorable clones.
+Therefore, we built a new tool, CR\footnote{Name anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.} This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
+In Sec.~\ref{sec:detection} we describe how CR detects refactorable clones.
+In Sec.~\ref{sec:context} we describe how CR maps the context of clones as input for the refactoring process described in Sec.~\ref{sec:refactoring}.
+
 \begin{figure}[H]
-  \includegraphics[width=1\columnwidth]{img/flow}
-  \caption{Simple flow diagram of CloneRefactor.}
+  \includegraphics[width=0.7\columnwidth]{img/flow}
+  \caption{Abstract flow diagram of CR.}
   \label{fig:clonerefactorflow}
@@
   \item \textbf{A return value}: If the method modifies or declares local data that is needed outside of its scope, or if the cloned fragments already returned data.
-  \item \textbf{Thrown exception}: If the method throws an uncaught exception that is not a \texttt{RuntimeException}.
+  \item \textbf{Thrown exception}: If the method throws an uncaught exception that is not a \\ \texttt{RuntimeException}.
 \end{itemize}
-CloneRefactor then removes all cloned code and replaces it with a method call to the newly created method.
-In case of a return value, CloneRefactor either assigns the call result, declares it or returns it accordingly.
+CR then removes all cloned code and replaces it with a call to the newly created method. In case of a return value, CR either assigns the call result, declares it or returns it accordingly.
+
+\subsection{Maintainability Metrics}
+After applying the refactorings, CR measures the impact of the refactoring on maintainability metrics.
+We first state the metrics that we measure and then define the characteristics of the applied refactoring that influence the metrics.
+
+\subsubsection{Selected metrics} \label{sec:metrics}
+CR measures the impact on maintainability metrics of refactoring source code for each clone class that is refactored.
+These metrics are from Heitlager et al.~\cite{heitlager2007practical}.
+For each of these metrics, risk profiles are proposed to determine the maintainability impact on the system of a whole.
+
+To determine whether the maintainability improves when refactoring a given clone, we need to measure the impact of fine-grained changes.
+Therefore, we measure only a subset of the metrics~\cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
+The subset of metrics we choose to focus on are all measured on method level (as the other metrics show a lesser impact on the maintainability for these small changes).
+These metrics are:
+\begin{itemize}
+\item \textbf{Duplication}: Originally~\cite{heitlager2007practical} measured by taking the amount of duplicated lines.
+We decided to use the amount of duplicated tokens part of a clone class instead, to have a stronger reflection of the impact of the refactoring by measuring a more fine-grained system property.
+%\item \textbf{Volume}: The more code a system has, the more code has to be maintained.
+The paper~\cite{heitlager2007practical} measures volume as lines of code.
+As with duplication, we use the number of tokens instead.
+\item \textbf{Method Complexity}:  Originally ~\cite{heitlager2007practical} computed using MCCabe complexity~\cite{mccabe1976complexity}.
+The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.%\todo{why is the original way ok for us?}
+\item \textbf{Method Interface Size}: The number of parameters that a method has.
+If a method has many parameters, the code may become harder to understand and it is an indication that data is not encapsulated adequately in objects~\cite{fowler2018refactoring}.
+\item \textbf{Method size}: The longer a method is, the harder it becomes to comprehend and maintain \cite{heitlager2007practical}.
+The ``extract method'' refactoring technique is often used to split up long methods \cite{charalampidou2018structural}.
+When refactoring duplicated code fragments in the body of a method, this could improve maintainability of the refactored (reduced size).
+\end{itemize}
 
 \subsubsection{Characteristics of the extracted method}\label{sec:characteristics}
-We define the following characteristics of the extracted method and/or the call:
+To assess the impact of an applied refactoring, we selected the four characteristics that have the highest impact on the resulting maintainability scores:
 \begin{itemize}
-\item \textbf{Tokens}: The number of tokens in the body of the method.
-\item \textbf{Relation}: The relation category (Sec.~\ref{sec:relation}) by which this methods' location was determined.
+\item \textbf{Size (in tokens)}: The number of tokens in the body of the method.
+A larger number of tokens means that more duplicate code can be removed, and thus has a positive impact on maintainability.
+\item \textbf{Relation}: The relation category (Sec.~\ref{sec:relation}) by which this methods' location was determined. Some relations are less favorable for maintainability than others.
 \item \textbf{Returns}: Whether the method calls return, declare, assign or don't use any data from the extracted method.
+This affects maintainability because the data must be returned from the extracted method, and assigned at each method call.
+This increases the volume of the refactoring.
 \item \textbf{Parameters}: The number of parameters the extracted method has.
+If the extracted method uses data that is not available where it is located, the data must be passed using method parameters.
+If a method has many parameters, it becomes less reusable and harder to comprehend, thus harder to maintain \cite{heitlager2007practical}.
+Additionally, this increases the volume, because each call to the extracted method must pass all required data.
 \end{itemize}
 We hypothesize that these characteristics are the main factors influencing the impact on the maintainability of the system as a result of refactoring the clone.
+This is because there are no further transformations that are applied that influence the maintainability metrics.
 
-\subsubsection{Impact on maintainability metrics} \label{sec:metrics}
-CloneRefactor measures the impact on maintainability metrics of the refactored source code for each clone class that is refactored.
-These metrics are derived from Heitlager et al.~\cite{heitlager2007practical}.
-This paper defines a set of metrics to measure the maintainability of a system.
-For each of these metrics, risk profiles are proposed to determine the maintainability impact on the system of a whole.
+\subsection{Refactoring evaluation}
+To evaluate the refactorings applied by CR and their impact, we expanded CR to create a git-commit for each applied transformation.
+We then use the ``Github Desktop''\footnote{GitHub Desktop is a git client: \url{https://desktop.github.com/}} to visualize each change made by CR (see Fig.~\ref{fig:cr_refactoring}).
+We then checked samples of the applied refactorings and the calculated metrics.
 
-To determine whether the maintainability improves when refactoring a single clone, we need to measure the impact of small-grained changes.
-Because of that, we measure only a subset of the metrics~\cite{heitlager2007practical} and focus on the absolute metric changes (instead of the risk profiles).
-The subset of metrics we decided to focus on are all metrics that are measured on method level (as the other metrics show a lesser impact on the maintainability for these small changes).
-These metrics are:
-\begin{itemize}
-\item \textbf{Duplication}: In Heitlager et al.~\cite{heitlager2007practical} this metric is measured by taking the amount of duplicated lines.
-We decided to use the amount of duplicated tokens part of a clone class instead, to have a stronger reflection of the impact of the refactoring by measuring a more fine-grained system property.
-\item \textbf{Volume}: The more code a system has, the more code has to be maintained.
-The paper~\cite{heitlager2007practical} measures volume as lines of code.
-As with duplication, we use the number of tokens instead.
-\item \textbf{Complexity}: Heitlager et al.~\cite{heitlager2007practical} use MCCabe complexity~\cite{mccabe1976complexity} to calculate their complexity metric.
-The MCCabe complexity is a quantitative measure of the number of linearly independent paths through a method.
-\item \textbf{Method Interface Size}: The number of parameters that a method has.
-If a method has many parameters, the code may become harder to understand and it is an indication that data is not encapsulated adequately in objects~\cite{fowler2018refactoring}.
-\end{itemize}
+\begin{figure}
+    \centering
+    \includegraphics[width=1\columnwidth]{img/cr.png}
+    \caption{Automatically applied refactoring by CR shown in the GitHub Desktop client.
+CR automatically authors a git commit for each applied transformation and specifies the impact of the change in the commit message.}
+    \label{fig:cr_refactoring}
+\end{figure}
 
-\section{Experimental setup}
-In this section, we describe the setup of our experiments.
+The full commit message for the refactoring example displayed in Fig.~\ref{fig:cr_refactoring} is as follows:
+\begin{quote}
+CR refactored a clone class with 2 clone instances.
+For the common code we created a new method and named this method “refactoredClone0".
+These clone instances have a Same Method relation with each other.
+The newly created method has been placed in ISODateTimeFormat.
+Each duplicated fragment has been replaced with a call to this method.
+\\ \\
+== System Quality Metrics == \\
+Total Cyclomatic Complexity increased by 1 from 6,994 to 6,995.\\
+Total Unit Interface Size increased by 1 from 3,715 to 3,716.\\
+Total Unit Line Size increased by 1 from 23,024 to 23,025.\\
+Total Unit Token Size decreased by 2 from 153,190 to 153,188.\\
+Total Nodes decreased by 1 from 18,866 to 18,865.\\
+\\
+Duplicated Nodes decreased by 6 from 502 to 496.\\
+Duplicated Tokens decreased by 42 from 5,064 to 5,022.\\
+Duplicated Lines decreased by 6 from 504 to 498.\\
+\\
+== Risk Profiles ==\\
+Unit Complexity\\
+Created a new method with a low risk Unit Complexity of 1.\\
+Removing duplicate blocks changed 1 method.\\
+The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 8 to 8 Unit Complexity. This did not influence the risk category of this method, it is still low risk.\\
+\\
+Line Volume\\
+Created a new method with a low risk Line Volume of 5.\\
+Removing duplicate blocks changed 1 method.\\
+The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 47 to 39 Line Volume. This did not influence the risk category of this method, it is still high risk.\\
+\\
+Token Volume\\
+Created a new method with a low risk Token Volume of 30.\\
+Removing duplicate blocks changed 1 method.\\
+The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 303 to 271 Token Volume. This increased the risk category of this method from high to moderate.\\
+\\
+The new method has a low risk Unit Interface Size of 1.\\
+\\
+Duplication went from 2.66\% to 2.63\%. This did not influence the risk category of the duplication in this codebase, it is still low risk.
+\end{quote}
+Inspecting these
+
+\section{Experimental setup} \label{sec:experimentalsetup}
+%In this section, we describe the setup of our experiments.
+We describe how we evaluated CR and the corpus on which we ran CR. We then describe the configuration of our experiments. Finally, we describe how we calculated our results.
+%Our goal is analysing whether automatic refactoring of code clones leads to an improved maintainability.
+We first validate our automatic refactoring tool, CR.
+Next, we run our tool on a reference corpus and measure the change in the maintainability score.
+
+\subsection{Tool Evaluation}
+We assess the correctness of CR through unit tests and empirical validation.
+First, we create a set of 57 control projects to verify the correctness in many (edge) cases.
+These projects contain clones for each relation, location, and refactorability category.
+%to see whether they get correctly identified. 
+Next, we run the tool over the corpus and manually verify samples of the acquired results.
+We verified at least 5 clones of each relation, location and refactoring.
+This way, we check both the correctness of the identified clones, their context, and their proposed refactoring.
+
+We also test the correctness of the refactored code using the JFreeChart project~\cite{gilbert2002jfreechart}.
+JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CR.
 
 \subsection{Corpus}
-We ran all our experiments using CloneRefactor on a corpus of open source Java projects.
-This corpus is derived from the corpus of a study that uses machine learning to determine the suitability of Java projects on GitHub for data analysis purposes~\cite{githubCorpus2013}.
+Our corpus, consisting of open source Java projects, is derived from the corpus of a study that uses machine learning to determine the suitability of GitHub Java projects for data analysis purposes~\cite{githubCorpus2013}.
+We chose this corpus because it has a variety of projects of different size and quality, which accurately reflects the target group for the results of our research.
+The entire corpus contains a total of 14,765 Java projects.
 
-CloneRefactor requires all libraries of the projects it analyses, to find the full paths of all referenced symbols in the source code (see Sec.~\ref{sec:t1r}).
-Because of that requirement, we decided to filter the corpus to only projects using the Maven build automation system.
-We created a set of scripts\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} to prepare such a corpus with all dependencies included.
+CR requires all libraries of the analyzed projects
+%it analyses, to find the full paths of all referenced symbols in the source code 
+(see Sec.~\ref{sec:t1r}).
+Therefore, we decided to filter the corpus to contain only projects using the Maven build automation system.
+We further discarded projects with build errors or unavailable dependencies.
+%The filtering scripts are publicly availble \footnotesize{The camera-ready version would include the GitHub repo url}.
+%We created a set of scripts to prepare such a corpus with all dependencies included.
 
-This procedure results in 2.267 Java projects including all their dependencies.
+This procedure results in 2,267 Java projects including all their dependencies%\todo{this is confusing, how many original projects are there? were the dependencies in the original corpus?}
+.
 The projects vary in size and quality.
@@
 The largest project in the corpus is \textit{VisAD} with 502K lines.
+The distribution of project sizes is displayed in Fig.~\ref{fig:dist}.
 
-\subsection{Tool Validation}
-We have verified the correctness of CloneRefactor through unit tests and empirical verification.\todo{With unit test you are testing the properties which is verification.
-With projects you are validating as you are checking whether its finding what is it supposed to be finding.} First, we created a set of 57 control projects to verify the correctness in many (edge) cases.
-These projects contain clones for each identified relation, location, and refactorability category to see whether they get correctly identified.
-Next, we run the tool over the corpus and manually verify samples of the acquired results.
-This way, we check both the correctness of the identified clones, their context, and their proposed refactoring.
-
-We also test the correctness of the resulting code after refactoring.
-For this, we use a GitHub project named JFreeChart.
-JFreeChart has a high test coverage and working tests, which allows us to test the correctness of the program after running CloneRefactor.
+\begin{figure}[H]
+  \includegraphics[width=1\columnwidth]{img/dist2}
+  \caption{Distribution of project sizes in corpus on a logarithmic scale.}
+  \label{fig:dist}
+\end{figure}
 
 \subsection{Minimum clone size}
-In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored.
-However, when clones are very small, they may never be able to improve maintainability.
+% In this study, we want to find out what thresholds to use to improve maintainability if clones by those thresholds are refactored. However, 
+When clones are very small, they may never be able to improve maintainability.
 The detrimental effect of the added volume of the newly created method exceeds the positive effect of removing duplication.
-Because of that, we perform all our experiments with a minimum clone size of 10 tokens, because smaller clones are very unlikely to improve maintainability when refactored.
+We perform all our experiments with a minimum clone size of 10 tokens, as smaller clones are very unlikely to improve maintainability when refactored (see our results in Sec.~\ref{sec:clonetokenvolume}).
 
-\subsection{Thresholds}
-Most clone detection tools can be configured using thresholds.
+%\subsection{Thresholds}
+%Most clone detection tools can be configured using thresholds.
 These thresholds indicate the minimum number of lines, tokens and/or statements that must be spanned for duplicate fragments to be considered clones.
-Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quartile distribution of empirical data~\cite{alves2010deriving}.
-Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
+Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quantile distribution of empirical data~\cite{alves2010deriving}.
+%\todo{paragraph commented below seems more suitable for the discussion part. otherwise it should be rephrased.}
+% Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
 
@@
 \subsubsection{Relation}
-Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for the identified relations between clone instances (see Sec.~\ref{sec:relation}).
+Table~\ref{tab:relation} shows the number of clone classes found for the entire corpus for each type of relations between clone instances (see Sec.~\ref{sec:relation}).
 
-\begin{table}[H]
+\begin{table}
 \centering
@@
 \subsubsection{Location}
-Table~\ref{tab:location} displays the number of clone classes found for the entire corpus for different locations (see Sec.~\ref{sec:location}).
+Table~\ref{tab:location} shows the number of clone classes found for the entire corpus for different locations (see Sec.~\ref{sec:location}).
 
-\begin{table}[H]
+\begin{table}
 \centering
@@
 \subsection{Thresholds}
-In our corpus, CloneRefactor has refactored 12.710 clone classes and measured the change in indicated metrics (see Sec.~\ref{sec:metrics}).
-Using the presented formulas (see Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
-In this section, we explore the data received by comparing the before- and after snapshots of the system for each separate refactoring.
+CR has refactored 12.710 clone classes and measured the change in the selected metrics (Sec.~\ref{sec:metrics}). %\todo{use the formulas labels to refer here.
+Using the formulas in Eq.~\ref{eq:scoredev} and~\ref{eq:scoreref} (Sec.~\ref{sec:metricformula}) we determine how the characteristics of the extracted method (see Sec.~\ref{sec:characteristics}) influence the maintainability of the resulting codebase after refactoring.
+We explore the data obtained by comparing the before- and after snapshots of the system for each separate refactoring.
 Using this data, we find supporting evidence regarding which thresholds are most likely to find clones that should be refactored to improve maintainability.
 
-\subsubsection{Clone Token Volume}
-Figure \ref{fig:maintainabilityscore} shows the obtained results when plotting the clone volume vs the average delta maintainability score.
+\subsubsection{Clone Token Volume} \label{sec:clonetokenvolume}
+Figure \ref{fig:maintainabilityscore} shows the results by plotting the clone volume vs the average delta maintainability score.
 We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class.
-For higher token volume numbers we have fewer refactorings that refactor such clones, because of which we represent the x-axis as a logarithmic scale.
+For higher token volume numbers we have fewer refactorings that refactor such clones, therefore we represent the x-axis as a logarithmic scale.
 The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.
 
+%\todo{Redo plot, explain axes units}
 \begin{figure*}
@@
 28\% of clones can be refactored using the ``Extract Method'' refactoring technique (50\% if we limit our searching scope to method bodies).
-About 25\% of clones do not span part of a method, because of which they cannot be refactored.
+About 25\% of clones do not span part of a method, therefore they cannot be refactored.
 Many clones (23\%) do not have a statement as top-level AST-Node.
-Upon manual inspection, we noticed that the main reason for this is when clones are found in lambda functions or anonymous classes.
-About 15\% of clones span only part of an AST-Node.
+Upon manual inspection, we noticed that the main reason is clones in lambda functions or in anonymous classes.
+About 15\% of clones span only part of an AST-Node.% \todo{and?}.
 
 \subsection{Refactoring}
-In Fig.~\ref{fig:maintainabilityscore} we see an increase in maintainability for refactoring larger clone classes.
-The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie around a token volume of 63 tokens.
-There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.
+Fig.~\ref{fig:maintainabilityscore} shows an increase in maintainability for refactoring larger clone classes.
+The tipping point, between a better and a worse maintainable refactoring, seems to lie around a token volume of 63 tokens.
+There are fewer large clones than small clones, resulting in a very limited %\todo{how limited?
+give the p-value}
+statistical significance on our corpus when considering clones larger than 100 tokens.
 
-In Table~\ref{tab:relation_refactor} we see the results regarding refactorings that are applied to clones with diverse relations.
-We see that most refactored clones are in a common class, over 54\%.
-This is significantly more than the percentage of clones in the common class relation as reported in Table~\ref{tab:relation}.
-Meanwhile, the number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% -> 18\%).
+Table~\ref{tab:relation_refactor} shows the results regarding refactorings that are applied to clones with diverse relations.
+More than 54\% of the refactored clones are in a common class.
+This is significantly more than the percentage of clones in the common class relation reported in Table~\ref{tab:relation}.
+The number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% vs 18\%).
 The main reason for this is that refactoring unrelated clones can change the relation of other clones in the same system.
@@
 
-The maintainability scores displayed in Table~\ref{tab:relation_refactor} show that the most favorable clones to refactor are clones with a Sibling relation.
-The most unfavorable is to refactor clones to interfaces.
-However, the differences in maintainability in this table are generally small; according to our data relations have only a minor impact on the maintainability of clones.
+The maintainability scores in Table~\ref{tab:relation_refactor} show that the most favorable clones to refactor are clones with a Sibling relation.
+The most unfavorable is refactoring clones to interfaces.
+However, the differences in maintainability in this table are generally small %\todo{and?}
+; according to our data relations have only a minor impact on the maintainability of clones.
 
-Regarding the return type of refactored clones, we see in Table~\ref{tab:return} that this has no major impact on maintainability.
+Regarding the return type of refactored clones, Table~\ref{tab:return} shows that this has no major impact on maintainability.
 A method call to the extracted method that is directly returned and no return type extracted methods are slightly more favorable than the others.
-We think the main reason that the ``Return'' category is on top is that when a variable is declared at the end of the cloned fragment, CloneRefactor directly returns its value and removes the declaration.
+We think the main reason that the ``Return'' category is on top is that when a variable is declared at the end of the cloned fragment, CR directly returns its value and removes the declaration.
 This decreases the volume slightly.
 
-A higher number of parameters directly influences the corresponding metric.
-Because of this, we see in Fig.~\ref{fig:arguments} that more parameters negatively influence maintainability.
-Not only the number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
+% A higher number of parameters directly influences the corresponding metric. 
+Fig.~\ref{fig:arguments} shows that more parameters negatively influence maintainability. Not only the %\todo{wasn't this a characteristic? this paragraph is somewhat confusing}
+number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
 Because of that, we see that the trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.
 
-\section{Threats to validity}
-This research relies on the assumption that the maintainability model proposed by Heitlager et al.~\cite{heitlager2007practical} gives a good indication of the actual maintainabilty of a system.
-Furthermore, we rely on that the scores of different metrics have an equal weight relative to each other, as for our aggregation of the scores.
-
-\section{Conclusion}
+%\todo[inline]{one paragraph with a general remark on this discussion, summarizing our findings}
+\section{Conclusion} \label{sec:conclusion}
+%\todo[inline]{one paragraph summarizing the context of our research}
 We defined automatically refactorable clones and created a tool to detect and refactor them.
@@
 We built a tool that can automatically apply refactorings to 28\% of the clones in our corpus using the ``Extract Method'' refactoring technique. 
-The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, e.g., when code outside a method is part of a clone.
+% The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, e.g., when code outside a method is part of a clone.
 
-We measured four maintainability metrics before- and after applying each refactoring to determine the impact of each refactoring on system maintainability.
+We measured the change in four maintainability metrics
+%before- and after applying each refactoring 
+to determine the impact of each refactoring on system maintainability.
 We found that the most prominent factor influencing maintainability is the size of the clone.
-We found that the threshold lies at a clone volume of 29 tokens per clone instance for system maintainability to increase after refactoring the clone.
-Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data.
+We found that the threshold lies at a clone volume of 63  %\todo{wasn't this 63?}
+tokens for all clone instances combined for system maintainability to increase after refactoring the clone.
+Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data: when a clone is refactored to a method that requires more than 2 parameters it is more likely to decrease maintainability than to increase it.
 We noticed that the inheritance relation of the clone and the return value of the extracted method has only a minor impact on system maintainability.
 
-\section*{Acknowledgments}
-We would like to thank the Software Improvement Group for their continuous support in this project.
-In particular, we would like to thank Xander Schrijen for his invaluable input in this research.
-Furthermore, we would like to thank Sander Meester for his proofreading efforts and feedback.
+\subsection{Threats to Validity}
+To limit the scope of this research, we chose not to include human subjects in this study.
+However, we think that the results of this study could be strengthened by performing a survey on software engineering practitioners.
+We have determined maintainability scores only based on literature input and statistical analysis.
+It would be valuable to have a control group rate the refactorings performed by CR, as an extra form of input regarding the quality of the code transformations that CR performs.
+
+In Section~\ref{sec:metricformula} we proposed an aggregation to measure a maintainability score on small-grained changes.
+The assumptions stated in this section influence the validity of the maintainability scores shown in our results.
+We noticed that the maintainability scores displayed in Table~\ref{tab:relation_refactor} and Table~\ref{tab:return} were mostly influenced by the differences in the ``number of parameters'' metric.
+This is because, for the scores, we normalized the metrics over all values obtained by these metrics.
+As our data regarding ``number of parameters'' has a very low standard deviation, small changes in this metric will influence the maintainability score a lot.
+
+\subsection{Future Work}
+In this study, we limited our scope by taking the naming of generated declarations outside of the scope.
+When using our work for refactoring assistance, these names will have to be manually provided.
+Recent studies aim at solving this problem by generating a name that matches the body of a declaration \cite{allamanis2015suggesting, alon2018code2seq}.
+We will investigate the possibility to combine such approaches with CR, to make it more usable in the refactoring process.
+
+We also limited our scope by choosing a set of four metrics.
+However, software maintainability depends on more factors and can be measured by more metrics.
+By taking more metrics into account, we can give a better indication whether the maintainability improves after refactoring.
+For instance, we think that module coupling \cite{heitlager2007practical} is an important metric to be considered when refactoring clones.
+In out future work we will investigate other metrics and map their impact on the results.
 

### 2020-05-03 ase/paper.tex
Updates from Overleaf

@@
 
+\settopmatter{printfolios=true} % TODO: Remove before final version
 \maketitle
@@
 Duplicate fragments in source code (also named ``code clones'') are often seen as one of the most harmful types of technical debt~\cite{fowler2018refactoring}.
-Duplicate fragments create implicit dependencies that make the code harder to maintain as the resolution of erroneous behavior in one location may have to be applied to all the cloned code as well~\cite{ostberg2014automatically}.
+Duplicate fragments create implicit dependencies that make the code harder to maintain as the resolution of erroneous behavior in one location may have to be applied to all the cloned code as well~\cite{ostberg2014automatically, chatterji2013effects}.
 Apart from that, code clones can contribute up to 25\% of the code size~\cite{bruntink2005use}.
-However, manual code clone refactoring is often tedious and could benefit from an automated tool~\cite{mazinanian2016jdeodorant}.
+
+However, several studies show that not all clones should be refactored~\cite{jarzabek2010clones, kapser2008cloning}.
+This can be due to variance between cloned fragments~\cite{roy2007survey} or parts of the codebase that have a low coupling and evolve separately~\cite{jarzabek2010clones}.
+There are many tools to detect clones \cite{roy2007survey, sheneamer2016survey, svajlenko2014evaluating, gautam2016various} that can find similar pieces of code, but none show which clones are relevant refactoring candidates.
 
@@
 Because of this, the output of clone detection tools is often of limited assistance to the developer in the refactoring process.
-To reduce duplication of a codebase, there are several refactoring techniques that can be applied in an automated manner.
+To reduce duplication of a codebase, there are several refactoring techniques that can be used. %applied in an automated manner. 
 The most used refactoring technique to deal with code clones is ``Extract Method'' \cite{fowler2018refactoring}.
 This technique entails that the duplicated code is moved to a new method, which is then called from all locations where the duplicated code was used.
-To be able to execute such a refactoring, several preconditions apply \cite{tsantalis2015assessing}.
+To be able to execute such a refactoring, several preconditions apply \cite{tsantalis2015assessing}.% By automatically identifying refactori
 %\todo[inline]{still missing link on how current solutions do not help improving maintainability - our message from monday night is not crystal clear yet}

### 2020-05-04 ase/paper.tex
Updates from Overleaf

@@
 This technique entails that the duplicated code is moved to a new method, which is then called from all locations where the duplicated code was used.
-To be able to execute such a refactoring, several preconditions apply \cite{tsantalis2015assessing}.% By automatically identifying refactori
+Using this refactoring method may have both positive and negative implications for the maintainability of the codebase.
+Positive implications include reduction of complexity, volume and implicit dependencies.
+Negative implications include an increase of parameters, volume and coupling.
+% To be able to execute such a refactoring, several preconditions apply \cite{tsantalis2015assessing}.% By automatically identifying refactori
 %\todo[inline]{still missing link on how current solutions do not help improving maintainability - our message from monday night is not crystal clear yet}
-In this study, we analyze which preconditions apply to determine whether a clone could and should be automatically refactored.
+In this study, we analyze the effect of clone refactoring on maintainability.
+% we analyze which preconditions apply to determine whether a clone could and should be automatically refactored.
 We list criteria that influence the maintainability of clones when refactored.

### 2020-05-04 ase/paper.tex
Updates from Overleaf

@@
 
-%Clone detection tools often use thresholds to determine which clones should be considered.
-Most clone detection tools use the number of lines \cite{kamiya2002ccfinder, svajlenko2016bigcloneeval}, statements \cite{higo2013revisiting, kamalpriya2017enhancing} and/or tokens \cite{ragkhitwetsagul2019siamese, jiang2007deckard} as thresholds to determine whether clones should be considered.
-We outline the shortcomings of these thresholds to find clones such that the maintainability of the source code is improved when refactored, and propose new thresholds to control this characteristic.
-% Current clone detection techniques are limited to measuring the size of clones to determine whether they should be considered.
-Because of this, the output of clone detection tools is often of limited assistance to the developer in the refactoring process.
-To reduce duplication of a codebase, there are several refactoring techniques that can be used. %applied in an automated manner. 
+To reduce duplication of a codebase, there are several refactoring techniques that can be used.
 The most used refactoring technique to deal with code clones is ``Extract Method'' \cite{fowler2018refactoring}.
@@
 Negative implications include an increase of parameters, volume and coupling.
-% To be able to execute such a refactoring, several preconditions apply \cite{tsantalis2015assessing}.% By automatically identifying refactori
-%\todo[inline]{still missing link on how current solutions do not help improving maintainability - our message from monday night is not crystal clear yet}
+
 In this study, we analyze the effect of clone refactoring on maintainability.
-% we analyze which preconditions apply to determine whether a clone could and should be automatically refactored.
-We list criteria that influence the maintainability of clones when refactored.
-We evaluate the context of clones to determine which refactoring techniques are best suited.
-We define the context of clones as the inheritance relation between clone instances in a clone class and the location of clone instances in the codebase.
-We showcase the proposed technique as a tool that automatically refactors clones by extracting new methods out of duplicated code.
-
+We create a tool that automatically applies ``Extract Method'' refactorings to a subset of detected clones.
 We measure several maintainability metrics \cite{heitlager2007practical} before and after refactoring each clone to determine its impact on system maintainability.
@@
 Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
-Because of this, we minimize limiting the size of clones we find to measure the maintainability impact of all clones, including micro-clones \cite{mondai2018micro}.
 
 Over a corpus of 2,267 Java project our tool refactored 12,710 clone classes.
-We found that the main influencing factor on maintainability when refactored is token volume.
-We define token volume as the combined number of tokens in all clone instances in a clone class.
+We found that the main influencing factor on maintainability when refactored is clone volume.
+%We define token volume as the combined number of tokens in all clone instances in a clone class.
 %When refactoring clones with a very small token volume, we found that the maintainability decreases when such clones are refactored.
-The average clone with a token volume of 63 or larger improves maintainability when refactored.
+The average clone with a volume of 63 or more tokens improves maintainability when refactored.
 The other factor with a major influence on maintainability is the number of parameters that are required for the extracted method.
@@
 \subsection{Clone Refactoring}
-\subsubsection{Refactoring techniques}
 The most common technique for refactoring clones is ``Extract Method''~\cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
@@
 To reduce duplication with this technique, the contents of a single clone instance are extracted to a new method and all further locations of the clone are replaced by a call to the new method.
-An example of this is shown in Fig.~\ref{fig:extractmethod}.
-
-\begin{figure}[H]
-\begin{parcolumns}{2}
-\colchunk[1]{
-\begin{javacode}
-// Original
-public void doStuff(){
-|\highlightYellow|  doA();
-|\highlightYellow|  doB();
-  doC();
-|\highlightYellow|  doA();
-|\highlightYellow|  doB();
-}
-\end{javacode}}
-\colchunk[2]{
-\begin{javacode}
-// Refactored
-public void doStuff(){
-|\highlightYellow|  doAandB();
-  doC();
-|\highlightYellow|  doAandB();
-}
-
-public void doAandB(){
-  doA();
-  doB();
-}
-\end{javacode}}
-\end{parcolumns}
-\caption{Refactoring a clone class through method extraction.}
-\label{fig:extractmethod}
-\end{figure}
-
-\subsubsection{Preconditions}
-Clones detected by current detection techniques \cite{kamiya2002ccfinder, deissenboeck2010flexible, jiang2007deckard, cordy2011nicad} are subject to a set of preconditions to determine whether they can be refactored \cite{tsantalis2015assessing}:
-\begin{enumerate}
-  \item The parameterization of differences between the matched statements should not break existing data-, anti-, and output-dependencies.
-  \item The unmatched statements should be movable before or after the matched statements without breaking existing data-, anti-, and output-dependencies.
-  \item The duplicated code fragments should return at most one variable of the same type.
-  \item Matched branching (\texttt{break}, \texttt{continue}) statements should be accompanied with corresponding matched loop statements.
-  \item Matched variables having different subclass types should call only methods that are declared in the common superclass or are being overridden in the respective subclasses.
-  \item The parameterization of fields belonging to differences between the mapped statements is possible only if they are not modified.
-  \item The parameterization of method calls belonging to differences between the mapped statements is possible only if they do not return a void type.
-  \item The mapped statements within the clone fragments should not contain any conditional return statements.
-\end{enumerate}
 

### 2020-05-04 ase/paper.tex
Updates from Overleaf

@@
 
-\subsection{Code clones}
+\subsection{Definition of code clones}
 We use two concepts to argue about code clones~\cite{roy2007survey}:
@@
 
-Fig.~\ref{fig:cloneclasses} shows an example of two clone classes. The first clone class spans the first two lines of all three files. The second clone class spans all lines of the first two files.
-
-\begin{figure}[H]
-\begin{parcolumns}{3}
-\colchunk[1]{
-\begin{javacode}
-// File1.java
-|\highlightDarkyellow|doA();
-|\highlightDarkyellow|doB();
-|\highlightYellow|doC();
-\end{javacode}}
-\colchunk[2]{
-\begin{javacode}
-// File2.java
-|\highlightDarkyellow|doA();
-|\highlightDarkyellow|doB();
-|\highlightYellow|doC();
-\end{javacode}}
-\colchunk[3]{
-\begin{javacode}
-// File3.java
-|\highlightYellow|doA();
-|\highlightYellow|doB();
-doD();
-\end{javacode}}
-\end{parcolumns}
-\caption{Example of two clone classes.}
-\label{fig:cloneclasses}
-\end{figure}
-
-%\subsection{Clone Types}
 Duplication in code is found in many different forms.
@@
 Sometimes this code is then adapted to fit the new context.
-To reason about these modifications, several clone types have been proposed%.
-These clone types are described in Roy et al
-~\cite{roy2007survey}:\\
+To reason about these modifications, several clone types have been proposed~\cite{roy2007survey}:\\
 \textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout), and comments.\\
@@
 
-\subsection{Clone Refactoring}
+\subsection{Clone harmfulness}
+
+\subsection{Clone refactoring}
 The most common technique for refactoring clones is ``Extract Method''~\cite{fowler2018refactoring}, which can be applied on code inside the body of a method.
@@
 
-\section{Related Work}\label{sec:relatedwork}
+\section{Related work}\label{sec:relatedwork}
 We outline relevant research to clone refactoring. A significant aspect is the context of clones.

### 2020-05-04 ase/paper.tex
zucht

@@
 
-\subsection{Refactoring evaluation}
-To evaluate the refactorings applied by CR and their impact, we expanded CR to create a git-commit for each applied transformation.
-We then use the ``Github Desktop''\footnote{GitHub Desktop is a git client: \url{https://desktop.github.com/}} to visualize each change made by CR (see Fig.~\ref{fig:cr_refactoring}).
-We then checked samples of the applied refactorings and the calculated metrics.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=1\columnwidth]{img/cr.png}
-    \caption{Automatically applied refactoring by CR shown in the GitHub Desktop client.
-CR automatically authors a git commit for each applied transformation and specifies the impact of the change in the commit message.}
-    \label{fig:cr_refactoring}
-\end{figure}
-
-The full commit message for the refactoring example displayed in Fig.~\ref{fig:cr_refactoring} is as follows:
-\begin{quote}
-CR refactored a clone class with 2 clone instances.
-For the common code we created a new method and named this method “refactoredClone0".
-These clone instances have a Same Method relation with each other.
-The newly created method has been placed in ISODateTimeFormat.
-Each duplicated fragment has been replaced with a call to this method.
-\\ \\
-== System Quality Metrics == \\
-Total Cyclomatic Complexity increased by 1 from 6,994 to 6,995.\\
-Total Unit Interface Size increased by 1 from 3,715 to 3,716.\\
-Total Unit Line Size increased by 1 from 23,024 to 23,025.\\
-Total Unit Token Size decreased by 2 from 153,190 to 153,188.\\
-Total Nodes decreased by 1 from 18,866 to 18,865.\\
-\\
-Duplicated Nodes decreased by 6 from 502 to 496.\\
-Duplicated Tokens decreased by 42 from 5,064 to 5,022.\\
-Duplicated Lines decreased by 6 from 504 to 498.\\
-\\
-== Risk Profiles ==\\
-Unit Complexity\\
-Created a new method with a low risk Unit Complexity of 1.\\
-Removing duplicate blocks changed 1 method.\\
-The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 8 to 8 Unit Complexity. This did not influence the risk category of this method, it is still low risk.\\
-\\
-Line Volume\\
-Created a new method with a low risk Line Volume of 5.\\
-Removing duplicate blocks changed 1 method.\\
-The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 47 to 39 Line Volume. This did not influence the risk category of this method, it is still high risk.\\
-\\
-Token Volume\\
-Created a new method with a low risk Token Volume of 30.\\
-Removing duplicate blocks changed 1 method.\\
-The method "dateByWeek(DateTimeFormatterBuilder, Collection, boolean, boolean)" went from 303 to 271 Token Volume. This increased the risk category of this method from high to moderate.\\
-\\
-The new method has a low risk Unit Interface Size of 1.\\
-\\
-Duplication went from 2.66\% to 2.63\%. This did not influence the risk category of the duplication in this codebase, it is still low risk.
-\end{quote}
-Inspecting these
-
 \section{Experimental setup} \label{sec:experimentalsetup}
@@
 
-\begin{table}
+\begin{table*}
 \centering
@@
 \label{tab:relation_refactor}
-\end{table}
+\end{table*}
 

### 2020-05-05 ase/paper.tex
Updates from Overleaf

@@
 
-\usepackage{xcolor}
+\usepackage{amsmath}
+\usepackage[table]{xcolor}
 \usepackage{graphicx}
 \usepackage{float}
-
 \usepackage{booktabs}
 \usepackage{multirow}
-\usepackage{parcolumns}
 
@@
 
-\acmConference[ICSE 2020]{Technical Papers}{May 23--29}{Seoul, South Korea}
+\acmConference[ASE 2020]{Technical Papers}{September 21--25}{Melbourne, Australia}
 
@@
 For a given refactoring we aggregate several maintainability metrics (duplication, complexity, unit size, code volume) to determine whether it improves the code.
+This score provides support for a developer to decide whether a given clone is likely to improve the codebase when refactoring.
 
@@
 \hspace{10pt} Sibling & -70.07 & 0.69 & 1.28 & -10.97 & 1,722 & 0.23 \\
-\rowcolor[HTML]{D0D0D0}
 \hspace{10pt} Same Hierarchy & -44.18 & 0.95 & 0.89 & 1.54 & 87 & 0.10 \\
 \hspace{10pt} First Cousin & -42.69 & 0.89 & 0.93 & 4.86 & 144 & 0.02 \\
-\rowcolor[HTML]{D0D0D0}
 \hspace{10pt} Ancestor & -32.75 & 1.00 & 0.75 & 11.00 & 20 & -0.03 \\ \midrule
@@
 Declare & 0.94 & 0.74 & 11.11 & -49.19 & 5,177 & 0.15 \\
-\rowcolor[HTML]{D0D0D0}
 Assign & 0.79 & 1.07 & 0.43 & -56.29 & 14 & 0.12 \\

### 2020-05-05 ase/paper.tex
Updates from Overleaf

@@
 To have this not influence the results, the metrics that determine the maintainability of an applied refactoring do not measure the quality of the name of the extracted method.
-%The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}.
-The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems.
-This tool is based on several studies that look into different aspects of code clone refactoring.
-In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design.
-Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability.
-This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.
-
-%A recent study~\cite{tsantalis2017clone} looks into how lambdas can assist the clone refactoring process.
-
-\begin{figure*}
-\begin{adjustwidth}{-0.5in}{-0.5in}% adjust the L and R margins by 1 inch
-\begin{minipage}{\linewidth}
-\begin{parcolumns}{2}
-\colchunk[1]{
-\begin{javacode}
-package com.sb.game;
-
-import java.util.List;
-
-public class GameScene
-{
-|\highlightYellow|	public void addToList(List l) {
-|\highlightYellow|		l.add(getClass().getName());
-|\highlightYellow|	}
-
-	public int addTen(int x) {
-|\highlightYellow|		x = x + 10; // Addition
-|\highlightYellow|		Notifier.notifyChanged(x);
-|\highlightYellow|		return x;
-	}
-}
-\end{javacode}}
-\colchunk[2]{
-\begin{javacode}
-package com.sb.fruitgame;
-
-import java.awt.List; // Different type
-
-public class LoseScene
-{
-|\highlightYellow|	public void addToList(List l) {
-|\highlightYellow|		l.add(getClass().getName());
-|\highlightYellow|	}
-
-	public String concatTen(String x) {
-|\highlightYellow|		x = x + 10; // String concatenation
-|\highlightYellow|		Notifier.notifyChanged(x);
-|\highlightYellow|		return x;
-	}
-}
-\end{javacode}}
-\end{parcolumns}
-\end{minipage}
-\end{adjustwidth}
-\caption{Example of textually equal code fragments that differ in functionality.}
-\label{fig:type1}
-\end{figure*}
 
@@
 Information that gets lost in textual comparison is the referenced declaration for type, variable and method references.
-Equally named type, variable and method references may refer to different declarations with a different implementation (Fig~\ref{fig:type1} shows an example of this).
+Equally named type, variable and method references may refer to different declarations with a different implementation.
 Such clones can be harder to refactor, if beneficial at all.
@@
 
-% To verify the correctness of all detected clones, we ran the tool over a large project and manually checked the output.
-We also created a set of control projects to test the correctness for many edge cases.
-
-\begin{figure*}
-\begin{parcolumns}{2}
-\colchunk[1]{
-\begin{javacode}
-|\highlightYellow|int a = getA();
-|\highlightYellow|while(a<1000) {
-|\highlightYellow|  a *= 5;
-  doC();
-}
-\end{javacode}}
-\colchunk[2]{
-\begin{javacode}
-|\highlightYellow|int a = getA();
-|\highlightYellow|while(a<1000) {
-|\highlightYellow|  a *= 5;
-  doB(a);
-}
-\end{javacode}}
-\end{parcolumns}
-\caption{A clone that spans a block partially.}
-\label{fig:refactorabilitypartialblock}
-\end{figure*}
-
 \subsection{Context mapping} \label{sec:context}
@@
     \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
-    \item \textbf{Spans Part Of A Block}: This clone spans a part of a block statement. An example of this is shown in Fig.~\ref{fig:refactorabilitypartialblock}.
+    \item \textbf{Spans Part Of A Block}: This clone spans a part of a block statement.
     \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Sec.~\ref{sec:location}, the ``Extract Method'' refactoring technique cannot be applied.
@@
 
-\begin{figure}[H]
+\begin{figure}
   \includegraphics[width=1\columnwidth]{img/dist2}
@@
 \centering
-\resizebox{\textwidth}{!}{%
 \begin{tabular}{@{}lrrrrrr@{}}
@@
 \end{tabular}%
-}
 \caption{Influence on maintainability of refactoring clones with the specified relation categories.}

### 2020-05-08 ase/paper.tex
Updates from Overleaf

@@
 We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code.
-For a given refactoring we aggregate several maintainability metrics (duplication, complexity, unit size, code volume) to determine whether it improves the code.
+For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) that are calculated on unit level.
 This score provides support for a developer to decide whether a given clone is likely to improve the codebase when refactoring.

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 \usepackage{multirow}
+
+\usepackage{todonotes}
 
@@
 % Experimental setup: how we validated that we fixed the problem
-To simulate such refactorings in a controlled environment, we propose a tool that can automatically refactor a subset of duplication problems in Java source code.
+To simulate such refactorings in a controlled environment, we create a tool that can automatically refactor a subset of duplication problems in Java source code.
 Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.
@@
 This can be due to variance between cloned fragments~\cite{roy2007survey} or parts of the codebase that have a low coupling and evolve separately~\cite{jarzabek2010clones}.
-There are many tools to detect clones \cite{roy2007survey, sheneamer2016survey, svajlenko2014evaluating, gautam2016various} that can find similar pieces of code, but none show which clones are relevant refactoring candidates.
+There are many tools to detect clones \cite{roy2007survey, sheneamer2016survey, svajlenko2014evaluating, gautam2016various} that can find similar pieces of code, but none show to which extent these are relevant refactoring candidates.
 
@@
 Using this setup, we gain empirical data about the maintainability improvement of clones on a large set of projects in a controlled environment.
-We use this data to define which characteristics of clones have the biggest influence on system maintainability when such a clone is refactored.
+We use this data to understand which characteristics of clones have the biggest influence on system maintainability when refactoring.
 This allows for more a accurate suggestion of code clones for refactoring and can assist in the refactoring process.
@@
 Over a corpus of 2,267 Java project our tool refactored 12,710 clone classes.
-We found that the main influencing factor on maintainability when refactored is clone volume.
+We find that the main influencing factor on maintainability when refactored is clone volume.
 %We define token volume as the combined number of tokens in all clone instances in a clone class.
@@
 The other factor with a major influence on maintainability is the number of parameters that are required for the extracted method.
-We found that if a clone requires more than 2 parameters in the extracted method, it is more likely to decrease maintainability.
+We find that if a clone requires more than 2 parameters in the extracted method, it is more likely to decrease maintainability.
 
@@
 \subsection{Clone harmfulness}
+\todo{incomplete}
 

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 
-In this study, we analyze the effect of clone refactoring on maintainability.
+In this study, we analyze which factors influence the impact of refactoring a clone on maintainability.
 We create a tool that automatically applies ``Extract Method'' refactorings to a subset of detected clones.
@@
 Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quantile distribution of empirical data~\cite{alves2010deriving}.
-Using the maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
+Using the delta maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
 
@@
 Sec.~\ref{sec:relatedwork} discusses state-of-the-art in automatic clone refactoring research.
-In Sec.~\ref{sec:research} we propose a definition for clones such that they could and should be automatically refactored.
+In Sec.~\ref{sec:research} we propose preconditions for a subset of clones such that they can be automatically refactored.
 In Sec.~\ref{sec:clonerefactor} we introduce our clone refactoring tool.
@@
 A higher type of clone means that it is harder to detect and refactor.
-Many studies adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
+Many studies adopt these clone types, analyzing them further and writing detection techniques for them~\cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.
 
 \subsection{Clone harmfulness}
-\todo{incomplete}
+In literature, clones are generally considered anti-patterns that should be avoided~\cite{fowler2018refactoring, ostberg2014automatically, chatterji2013effects}.
+However, removing some clones can leave the system in a less-desirable state~\cite{jarzabek2010clones, kapser2008cloning}.
+Jarzabek et al.~\cite{jarzabek2010clones} describe that mainly clones located in semantically unrelated parts of the codebase hinder maintenance.
+Clones in semantically unrelated parts of the codebase are merely a manifestation of the design choices.
+Therefore, elimination of clones is only beneficial if it also reduces
+the semantic dependency among parts of the system.
 
@@
 Golomingi~\cite{koni2001scenario} explores mapping the relation between clone instances to refactoring methods.
-The author analyses the refactoring methods described by Martin Fowler \cite{fowler1999refactoring} and analyzes what refactoring methods can be used to refactor clones with what inheritance relations.
+The author analyses the refactoring methods described by Martin Fowler~\cite{fowler1999refactoring} and analyzes what refactoring methods can be used to refactor clones with what inheritance relations.
 The identified clone relations are: Ancestor, Common Hierarchy, First Cousin, Same Method, Sibling, Single Class, Superclass and Unrelated.
@@
 
-\section{Defining refactorable clones}\label{sec:research}
+\section{Defining automatically refactorable clones}\label{sec:research}
 %In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}.

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code.
-For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) that are calculated on unit level.
-This score provides support for a developer to decide whether a given clone is likely to improve the codebase when refactoring.
+For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) that are calculated on unit level, which we call the delta maintainability score.
+%This score provides support for a developer to decide whether a given clone is likely to improve the codebase when refactoring.
+Based on this score, we extract common factors between clones for a developer to filter their clone output based on the factors and the derived thresholds for them.
 
@@
 To simulate such refactorings in a controlled environment, we create a tool that can automatically refactor a subset of duplication problems in Java source code.
+This subset is based on adapted clone definitions, that are optimized towards automated refactoring.
+Using these definitions we can extract a sufficiently large dataset of refactored clones to perform our analyses.
 Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.
@@
 
-\section{Survey of existing clone detection tools}\label{sec:survey}
+\section{A tool for automatic clone refactoring}\label{sec:clonerefactor}
+None of the surveyed tools were suitable for our definitions of refactorable clones.
+Therefore, we built a new tool, CR\footnote{Name anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.} This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
+In Sec.~\ref{sec:detection} we describe how CR detects refactorable clones.
+In Sec.~\ref{sec:context} we describe how CR maps the context of clones as input for the refactoring process described in Sec.~\ref{sec:refactoring}.
+
+\begin{figure}[H]
+  \includegraphics[width=0.7\columnwidth]{img/flow}
+  \caption{Abstract flow diagram of CR.}
+  \label{fig:clonerefactorflow}
+\end{figure}
+
+\subsection{Survey of existing clone detection tools}\label{sec:survey}
 %To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability.
@@
 In the following sections, we explain these steps.
-
-\section{A tool for automatic clone refactoring}\label{sec:clonerefactor}
-None of the surveyed tools were suitable for our definitions of refactorable clones.
-Therefore, we built a new tool, CR\footnote{Name anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.} This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
-In Sec.~\ref{sec:detection} we describe how CR detects refactorable clones.
-In Sec.~\ref{sec:context} we describe how CR maps the context of clones as input for the refactoring process described in Sec.~\ref{sec:refactoring}.
-
-\begin{figure}[H]
-  \includegraphics[width=0.7\columnwidth]{img/flow}
-  \caption{Abstract flow diagram of CR.}
-  \label{fig:clonerefactorflow}
-\end{figure}
 

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 \section{A tool for automatic clone refactoring}\label{sec:clonerefactor}
-None of the surveyed tools were suitable for our definitions of refactorable clones.
-Therefore, we built a new tool, CR\footnote{Name anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.} This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
-In Sec.~\ref{sec:detection} we describe how CR detects refactorable clones.
-In Sec.~\ref{sec:context} we describe how CR maps the context of clones as input for the refactoring process described in Sec.~\ref{sec:refactoring}.
 
-\begin{figure}[H]
-  \includegraphics[width=0.7\columnwidth]{img/flow}
-  \caption{Abstract flow diagram of CR.}
-  \label{fig:clonerefactorflow}
-\end{figure}
-
-\subsection{Survey of existing clone detection tools}\label{sec:survey}
-%To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability.
-To investigate the impact of the definitions introduced in Sec.~\ref{sec:research}, we need a tool to detect refactorable clones according to these definitions.
-We conducted a short survey on (recent) clone detection tools to detect such clones that can be refactored.
-The results of our survey are displayed in table~\ref{table:dettools}.
-We chose a set of tools that are open source and can analyze a popular object-oriented programming language.
-Next, we formulate the following four criteria by which we analyze these tools:
+To automatically refactor a large set of clones, we first need tool able to detect refactorable clones, as defined in Sec.~\ref{sec:research}.  We formulate the following four c required by such :
 \begin{enumerate}
@@
 \end{enumerate}
+
+\begin{figure}[H]
+  \includegraphics[width=0.7\columnwidth]{img/flow}
+  \caption{Abstract flow diagram of CR.}
+  \label{fig:clonerefactorflow}
+\end{figure}
+
+None of the surveyed tools were suitable for our definitions of refactorable clones.
+Therefore, we built a new tool, CR\footnote{Name anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.} This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
+In Sec.~\ref{sec:detection} we describe how CR detects refactorable clones.
+In Sec.~\ref{sec:context} we describe how CR maps the context of clones as input for the refactoring process described in Sec.~\ref{sec:refactoring}.
+
+% \subsection{Survey of existing clone detection tools}\label{sec:survey}
+%To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability.
 

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 To simulate such refactorings in a controlled environment, we create a tool that can automatically refactor a subset of duplication problems in Java source code.
+This subset is selected because not all clones can easily be automatically refactored, so we identify and define those that can.
 This subset is based on adapted clone definitions, that are optimized towards automated refactoring.
@@
 
-To automatically refactor a large set of clones, we first need tool able to detect refactorable clones, as defined in Sec.~\ref{sec:research}.  We formulate the following four c required by such :
+To automatically refactor a large set of clones, we first need tool able to detect refactorable clones, as defined in Sec.~\ref{sec:research}.
+We formulate the following four characteristics required by such a tool:
 \begin{enumerate}
@@
 
-\begin{figure}[H]
-  \includegraphics[width=0.7\columnwidth]{img/flow}
-  \caption{Abstract flow diagram of CR.}
-  \label{fig:clonerefactorflow}
-\end{figure}
-
-None of the surveyed tools were suitable for our definitions of refactorable clones.
-Therefore, we built a new tool, CR\footnote{Name anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.} This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
-In Sec.~\ref{sec:detection} we describe how CR detects refactorable clones.
-In Sec.~\ref{sec:context} we describe how CR maps the context of clones as input for the refactoring process described in Sec.~\ref{sec:refactoring}.
-
-% \subsection{Survey of existing clone detection tools}\label{sec:survey}
-%To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability.
+We conducted a short survey on (recent) clone detection tools based on the above characteristics.
+We chose a set of tools that are open source and can analyze a popular object-oriented programming language.
+The results of our survey are shown in Table~\ref{table:dettools}.
 
@@
 
+None of the surveyed tools had all desired characteristics.
 Apart from these criteria, we found that the output of these clone detection tools cannot be post-processed to find the clone definition proposed in Sec.~\ref{sec:research}.
 This is mainly because these clones are not necessarily a subset of clones detected by these tools and will thus require an analysis of the entire system.
+
+anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.}, which goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
+In Sec.~\ref{sec:detection} we describe how CR detects refactorable clones.
+In Sec.~\ref{sec:context} we describe how CR maps the context of clones as input for the refactoring process described in Sec.~\ref{sec:refactoring}.
+
+\begin{figure}[H]
+  \includegraphics[width=0.7\columnwidth]{img/flow}
+  \caption{Abstract flow diagram of CR.}
+  \label{fig:clonerefactorflow}
+\end{figure}
+
+% \subsection{Survey of existing clone detection tools}\label{sec:survey}
+%To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability.
 

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 This subset is selected because not all clones can easily be automatically refactored, so we identify and define those that can.
-This subset is based on adapted clone definitions, that are optimized towards automated refactoring.
+%This subset is based on adapted clone definitions, that are optimized towards automated refactoring.
 Using these definitions we can extract a sufficiently large dataset of refactored clones to perform our analyses.
@@
 
-None of the surveyed tools had all desired characteristics.
-Apart from these criteria, we found that the output of these clone detection tools cannot be post-processed to find the clone definition proposed in Sec.~\ref{sec:research}.
-This is mainly because these clones are not necessarily a subset of clones detected by these tools and will thus require an analysis of the entire system.
+None of the surveyed tools had all the desired characteristics.
+Also, the output of these clone detection tools cannot be post-processed to match the clone definition proposed in Sec.~\ref{sec:research}.
+This is mainly because the automatically refactorable clones are not necessarily a subset of clones detected by these tools and will thus require an analysis of the entire system.
 
-anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.}, which goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
+Therefore, we created a tool, CR\footnote{anonymized for the blind review, camera-ready paper would include a link to the GitHub repo of the tool.}, which goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
 In Sec.~\ref{sec:detection} we describe how CR detects refactorable clones.

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 However, several studies show that not all clones should be refactored~\cite{jarzabek2010clones, kapser2008cloning}.
-This can be due to variance between cloned fragments~\cite{roy2007survey} or parts of the codebase that have a low coupling and evolve separately~\cite{jarzabek2010clones}.
+This can be due to semantical variance between cloned fragments~\cite{roy2007survey} or parts of the codebase that have a low coupling and evolve separately~\cite{jarzabek2010clones}.
 There are many tools to detect clones \cite{roy2007survey, sheneamer2016survey, svajlenko2014evaluating, gautam2016various} that can find similar pieces of code, but none show to which extent these are relevant refactoring candidates.
@@
 Often, such thresholds are intuitively chosen~\cite{li2006cp, roy2009mutation} or based on a quantile distribution of empirical data~\cite{alves2010deriving}.
-Using the delta maintainability score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
+Using the delta score we can find support for which thresholds should be chosen to increase the chance to find clones that improve maintainability when refactored.
 
-Over a corpus of 2,267 Java project our tool refactored 12,710 clone classes.
+Over a corpus of 2,267 Java project our tool refactors 12,710 clone classes.
 We find that the main influencing factor on maintainability when refactored is clone volume.
@@
 For instance, we think that module coupling \cite{heitlager2007practical} is an important metric to be considered when refactoring clones.
-In out future work we will investigate other metrics and map their impact on the results.
+In future work we will investigate other groups of maintainability metrics to broaden the understanding of factors influencing the desirability of a refactoring.
 

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) that are calculated on unit level, which we call the delta maintainability score.
-%This score provides support for a developer to decide whether a given clone is likely to improve the codebase when refactoring.
 Based on this score, we extract common factors between clones for a developer to filter their clone output based on the factors and the derived thresholds for them.
@@
 This subset is selected because not all clones can easily be automatically refactored, so we identify and define those that can.
-%This subset is based on adapted clone definitions, that are optimized towards automated refactoring.
 Using these definitions we can extract a sufficiently large dataset of refactored clones to perform our analyses.
@@
 
-\settopmatter{printfolios=true} % TODO: Remove before final version
+%\settopmatter{printfolios=true} % TODO: Remove before final version
 \maketitle
@@
 We use this data to understand which characteristics of clones have the biggest influence on system maintainability when refactoring.
-This allows for more a accurate suggestion of code clones for refactoring and can assist in the refactoring process.
+This allows to suggest more relevant clones for refactoring and can thus assist in the refactoring process.
 
@@
 Clones in semantically unrelated parts of the codebase are merely a manifestation of the design choices.
-Therefore, elimination of clones is only beneficial if it also reduces
-the semantic dependency among parts of the system.
+Therefore, elimination of clones is only beneficial if it also reduces the semantic dependency among parts of the system.
 
@@
 By taking more metrics into account, we can give a better indication whether the maintainability improves after refactoring.
-For instance, we think that module coupling \cite{heitlager2007practical} is an important metric to be considered when refactoring clones.
+For instance, we think that module coupling \cite{briand1999unified,heitlager2007practical} is an important metric to be considered when refactoring clones.
 In future work we will investigate other groups of maintainability metrics to broaden the understanding of factors influencing the desirability of a refactoring.

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 % Experimental setup: how we validated that we fixed the problem
-To simulate such refactorings in a controlled environment, we create a tool that can automatically refactor a subset of duplication problems in Java source code.
-This subset is selected because not all clones can easily be automatically refactored, so we identify and define those that can.
+To conduct such refactorings in a controlled environment, we create a tool that can automatically refactor a set of duplication problems in Java source code.
+This set is selected because not all clones can easily be automatically refactored, so we identify and define those that can.
 Using these definitions we can extract a sufficiently large dataset of refactored clones to perform our analyses.
@@
 
-Over a corpus of 2,267 Java project our tool refactors 12,710 clone classes.
+Over a corpus of 2,267 Java projects our tool refactors 12,710 clone classes.
 We find that the main influencing factor on maintainability when refactored is clone volume.

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 To conduct such refactorings in a controlled environment, we create a tool that can automatically refactor a set of duplication problems in Java source code.
-This set is selected because not all clones can easily be automatically refactored, so we identify and define those that can.
+This set is selected because not all clones can easily be automatically refactored, so we define those that can.
 Using these definitions we can extract a sufficiently large dataset of refactored clones to perform our analyses.
@@
 Sec.~\ref{sec:relatedwork} discusses state-of-the-art in automatic clone refactoring research.
-In Sec.~\ref{sec:research} we propose preconditions for a subset of clones such that they can be automatically refactored.
+In Sec.~\ref{sec:research} we propose preconditions for a set of clones such that they can be automatically refactored.
 In Sec.~\ref{sec:clonerefactor} we introduce our clone refactoring tool.
@@
 \subsection{Ensuring equality}\label{sec:t1r}
-Most modern clone detection tools detect duplication by comparing the code textually together with the omission of certain tokens~\cite{roy2009comparison, svajlenko2014evaluating}.
+Most modern clone detection tools detect duplication by comparing the code textually together with the omission of certain tokens~\cite{roy2009comparison, svajlenko2014evaluating} (type 1 clones \cite{roy2007survey}).
 Clones detected by such means may not always be suitable for refactoring, because textual comparison fails to take into account the context of certain symbols in the code.
@@
 \subsection{Allowing variability in a controlled set of expressions} \label{sec:t2r}
-Often, duplication fragments in source code do not match exactly~\cite{kodhai2013method}.
+Often, duplication fragments in source code do not match exactly~\cite{kodhai2013method} (type 2 clones \cite{roy2007survey}).
 When developers duplicate fragments of code, they modify the duplicated block to fit its new location and purpose.
@@
 \end{itemize}
+
 Often when allowing such variance, trade-offs come into play~\cite{krishnan2013refactoring, krishnan2014unification}.
@@
 \subsection{Gapped clones} \label{sec:t3r}
-Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context~\cite{roy2007survey}.
+Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context~\cite{roy2007survey} (type 3 clones).
 When dealing with such situations, there are several opportunities to refactor so-called ``gapped clones''~\cite{ueda2002detection, zhao2018automatic}.
@@
 For both of these techniques, a trade-off is at play. This is because these solutions increase the complexity and volume of the source code in favor of removing a clone.
+
+\subsection{Difference from literature clone types}
+These proposed definitions slightly differ from type 1, 2 and 3 clones as defined in literature \cite{roy2007survey}.
+To compare them, we refer to the literature types as T1, T2 and T3 and towards our as T1R (contextually equal clones), T2R (allowing variability) and T3R (gapped clones).
+Like the literature types, these clone type definitions are subsets of each other:
+
+\begin{equation}\label{eq:typerelation}
+%N_{1R} = \{n | n = a node found using the T1R set of rules\}
+%N_{2R} = \{n | n = a node found using the T2R set of rules\}
+%N_{3R} = \{n | n = a node found using the T3R set of rules\}
+L_{T1R} \subseteq L_{T2R} \subseteq L_{T3R}
+\end{equation}
+
+Where $N_{\text{clone type}}$ is the set of cloned lines found by the rules of the specified clone type. All clones found for type 1R will also be found for type 2R and type 3R.
+
+Comparing these clone type definitions to the ones used in literature, we have the following subset relations:
+
+\begin{equation}\label{eq:typerelation2}
+N_{T1R} \subseteq N_{T1} \text{, but } N_{T2R} \nsubseteq N_{T2} \text{ and } N_{T3R} \nsubseteq N_{T3}
+\end{equation}
+
+Where $N_{\text{clone type}}$ is the set of cloned nodes found by the rules of the specified clone type.
+The reason that type 2R and type 3R are not subsets of type 2 and 3, is that type 2R and type 3R allow variability in method calls which can differ in structure.
+Type 2 and 3 do not allow such differences.
 

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 These proposed definitions slightly differ from type 1, 2 and 3 clones as defined in literature \cite{roy2007survey}.
-To compare them, we refer to the literature types as T1, T2 and T3 and towards our as T1R (contextually equal clones), T2R (allowing variability) and T3R (gapped clones).
-Like the literature types, these clone type definitions are subsets of each other:
+To compare them, we refer to the literature types as T1, T2 and T3 and to our set as T1R (contextually equal clones), T2R (allowing variability) and T3R (gapped clones).
+Mirroring the literature types, our clone type definitions are subsets of each other:
 
 \begin{equation}\label{eq:typerelation}
-%N_{1R} = \{n | n = a node found using the T1R set of rules\}
-%N_{2R} = \{n | n = a node found using the T2R set of rules\}
-%N_{3R} = \{n | n = a node found using the T3R set of rules\}
 L_{T1R} \subseteq L_{T2R} \subseteq L_{T3R}
@@
 
-Where $N_{\text{clone type}}$ is the set of cloned lines found by the rules of the specified clone type. All clones found for type 1R will also be found for type 2R and type 3R.
+Where $L_{\text{clone type}}$ is the set of cloned lines found by the rules of the specified clone type.
 
@@
 \begin{equation}\label{eq:typerelation2}
-N_{T1R} \subseteq N_{T1} \text{, but } N_{T2R} \nsubseteq N_{T2} \text{ and } N_{T3R} \nsubseteq N_{T3}
+L_{T1R} \subseteq L_{T1} \text{, but } L_{T2R} \nsubseteq L_{T2} \text{ and } L_{T3R} \nsubseteq L_{T3}
 \end{equation}
 
-Where $N_{\text{clone type}}$ is the set of cloned nodes found by the rules of the specified clone type.
-The reason that type 2R and type 3R are not subsets of type 2 and 3, is that type 2R and type 3R allow variability in method calls which can differ in structure.
-Type 2 and 3 do not allow such differences.
+Where $L_{\text{clone type}}$ is the set of cloned lines found by the rules of the specified clone type.
+The reason that T2R and T3R are not subsets of T2 and T3, is that T2R and T3R allow variability in method calls which can differ in structure.
+T2 and T3 do not allow such differences.
 
 \section{A tool for automatic clone refactoring}\label{sec:clonerefactor}
-
 To automatically refactor a large set of clones, we first need tool able to detect refactorable clones, as defined in Sec.~\ref{sec:research}.

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 \begin{equation}\label{eq:typerelation}
-L_{T1R} \subseteq L_{T2R} \subseteq L_{T3R}
+L_{T1R} \subseteq L_{T2R} \subseteq L_{T3R},
 \end{equation}
 
-Where $L_{\text{clone type}}$ is the set of cloned lines found by the rules of the specified clone type.
+where $L_{\text{clone type}}$ is the set of cloned lines according to the rules of the respective $\text{clone type}$.
 
@@
 
-Where $L_{\text{clone type}}$ is the set of cloned lines found by the rules of the specified clone type.
-The reason that T2R and T3R are not subsets of T2 and T3, is that T2R and T3R allow variability in method calls which can differ in structure.
-T2 and T3 do not allow such differences.
+ The reason that T2R and T3R are not subsets of T2 and T3, is that T2R and T3R allow variability in method calls which can differ in structure. T2 and T3 do not allow such differences.
 
@@
 Also, the output of these clone detection tools cannot be post-processed to match the clone definition proposed in Sec.~\ref{sec:research}.
-This is mainly because the automatically refactorable clones are not necessarily a subset of clones detected by these tools and will thus require an analysis of the entire system.
+This is mainly because the automatically refactorable clones are not necessarily a subset of the clones detected by these tools (see Sec.~\ref{sec:} and will thus require an analysis of the entire system.
 

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 % Problem
-Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and creates implicit dependencies between fragments of code.
+Duplication in source code is often seen as one of the most harmful types of technical debt as it increases the size of the codebase and it creates implicit dependencies between fragments of code.
 Several studies show that not all duplication should be refactored.
@@
 We use software maintainability metrics to determine the impact of a refactoring applied to duplicate code.
-For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) that are calculated on unit level, which we call the delta maintainability score.
-Based on this score, we extract common factors between clones for a developer to filter their clone output based on the factors and the derived thresholds for them.
+For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) calculated on unit level, which we call the delta maintainability score.
+Based on this score, we extract common factors between clones and the derived thresholds for them, based on which a developer could filter their clone output.
 
@@
 
-\subsection{Difference from literature clone types}
+\subsection{Difference from literature clone types}\label{sec:different-types}
 These proposed definitions slightly differ from type 1, 2 and 3 clones as defined in literature \cite{roy2007survey}.
@@
 Also, the output of these clone detection tools cannot be post-processed to match the clone definition proposed in Sec.~\ref{sec:research}.
-This is mainly because the automatically refactorable clones are not necessarily a subset of the clones detected by these tools (see Sec.~\ref{sec:} and will thus require an analysis of the entire system.
+This is mainly because the automatically refactorable clones are not necessarily a subset of the clones detected by these tools (see Sec.~\ref{sec:different-types}) and will thus require an analysis of the entire system.
 

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 To conduct such refactorings in a controlled environment, we create a tool that can automatically refactor a set of duplication problems in Java source code.
-This set is selected because not all clones can easily be automatically refactored, so we define those that can.
-Using these definitions we can extract a sufficiently large dataset of refactored clones to perform our analyses.
+Because not all clones can easily be automatically refactored, we define those that can.
+Using these definitions we can extract a sufficiently large set of refactored clones to perform our analyses.
 Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.
@@
 Also, the output of these clone detection tools cannot be post-processed to match the clone definition proposed in Sec.~\ref{sec:research}.
-This is mainly because the automatically refactorable clones are not necessarily a subset of the clones detected by these tools (see Sec.~\ref{sec:different-types}) and will thus require an analysis of the entire system.
+This is because the automatically refactorable clones are not necessarily a subset of the clones detected by these tools (see Sec.~\ref{sec:different-types}) and will thus require an analysis of the entire system.
 
@@
 \end{figure}
-
-% \subsection{Survey of existing clone detection tools}\label{sec:survey}
-%To detect refactorable clones according to the definitions introduced in Sec.~\ref{sec:research}, we survey existing clone detection tools for their suitability.
-
-%To detect clones that can be automatically refactored, we surveyed a set of modern clone detection tools and techniques~\cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}.
-We created a set of control projects to determine the suitability of these tools to detect automatically refactorable clones, either through configuration or postprocessing of their output.
-
-%None of the surveyed tools~\cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable for our definitions of refactorable clones, because of which we propose CR.
-This tool goes through a 3-step process to automatically refactor clones as shown in Fig.~\ref{fig:clonerefactorflow}.
-In the following sections, we explain these steps.
 

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 Using these definitions we can extract a sufficiently large set of refactored clones to perform our analyses.
-Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.
+Our tool refactors 13k clones over 2k open-source Java projects and computes the delta maintainability scores.
 
 % results: what have we learned by fixing the problem
-We correlate the delta maintainability score with the factors that influence this score (clone volume, clone complexity, externally declared data used).
+We correlate the delta maintainability scores with the factors that influence this score (clone volume, clone complexity, externally declared data used).
 We find that the biggest influencing factor is the volume of the clone.

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 For a given refactoring we aggregate a set maintainability metrics (duplication, complexity, unit size, code volume) calculated on unit level, which we call the delta maintainability score.
-Based on this score, we extract common factors between clones and the derived thresholds for them, based on which a developer could filter their clone output.
+Based on this score, we extract common factors between clones and derive thresholds for them, based on which a developer could filter their clone output.
 
 % Experimental setup: how we validated that we fixed the problem
-To conduct such refactorings in a controlled environment, we create a tool that can automatically refactor a set of duplication problems in Java source code.
+To analyse such refactorings in a controlled environment, we create a tool that can automatically refactor a set of duplication problems in Java source code.
 Because not all clones can easily be automatically refactored, we define those that can.

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 %\todo[inline]{one paragraph summarizing the context of our research}
-We defined automatically refactorable clones and created a tool to detect and refactor them.
+We define automatically refactorable clones and create a tool to detect and refactor them.
 We measured statistical data with this tool over a large corpus of open-source Java software systems to get more information about the context of clones and how refactoring them influences system maintainability.
+Based on this information, we extract characteristics of clones that influence system maintainability when they are refactored.
 
-We defined two aspects as part of the context of a clone: relation and location.
+We define two aspects as part of the context of a clone: relation and location.
 Regarding relations, over 37\% of clones are found in the same class.
@@
 
-We built a tool that can automatically apply refactorings to 28\% of the clones in our corpus using the ``Extract Method'' refactoring technique. 
 % The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, e.g., when code outside a method is part of a clone.
 
-We measured the change in four maintainability metrics
-%before- and after applying each refactoring 
-to determine the impact of each refactoring on system maintainability.
+We built a tool that can automatically apply refactorings to 28\% of the clones in our corpus using the ``Extract Method'' refactoring technique.
+It measured the change in four maintainability metrics to determine the impact of each refactoring on system maintainability.
 We found that the most prominent factor influencing maintainability is the size of the clone.
-We found that the threshold lies at a clone volume of 63  %\todo{wasn't this 63?}
-tokens for all clone instances combined for system maintainability to increase after refactoring the clone.
+We found that the threshold lies at a clone volume of 63 tokens for all clone instances combined for system maintainability to increase after refactoring the clone.
+
 Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data: when a clone is refactored to a method that requires more than 2 parameters it is more likely to decrease maintainability than to increase it.
@@
 
-\subsection{Threats to Validity}
+\subsection{Threats to validity}
 To limit the scope of this research, we chose not to include human subjects in this study.
@@
 
-\subsection{Future Work}
+\subsection{Future work}
 In this study, we limited our scope by taking the naming of generated declarations outside of the scope.

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 
-\subsubsection{AST Transformation}
+\subsubsection{AST transformation}
 %\todo{Big todo --> Find literature, introduce proper reasoning why I need to do this.}
@@
 
-\subsection{Maintainability Metrics}
+\subsection{Maintainability metrics}
 After applying the refactorings, CR measures the impact of the refactoring on maintainability metrics.
@@
 
-\subsection{Tool Evaluation}
+\subsection{Tool evaluation}
 We assess the correctness of CR through unit tests and empirical validation.
@@
 
-\subsubsection{Clone Token Volume} \label{sec:clonetokenvolume}
+\subsubsection{Clone token volume} \label{sec:clonetokenvolume}
 Figure \ref{fig:maintainabilityscore} shows the results by plotting the clone volume vs the average delta maintainability score.
@@
 
-\subsubsection{Return Value}
+\subsubsection{Return value}
 Table~\ref{tab:return} shows how the return value of the extracted method influences the maintainability of the resulting system.
@@
 
-\subsection{Clone Context}
+\subsection{Clone context}
 Regarding clone context, our results indicate that most clones (37\%) are in a common class.
@@
 
-\subsection{Extract Method}
+\subsection{Extract method}
 28\% of clones can be refactored using the ``Extract Method'' refactoring technique (50\% if we limit our searching scope to method bodies).

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 Upon manual inspection, we noticed that the main reason is clones in lambda functions or in anonymous classes.
-About 15\% of clones span only part of an AST-Node.% \todo{and?}.
+About 15\% of clones span only part of an AST-Node.
 
@@
 The tipping point, between a better and a worse maintainable refactoring, seems to lie around a token volume of 63 tokens.
-There are fewer large clones than small clones, resulting in a very limited %\todo{how limited?
-give the p-value}
-statistical significance on our corpus when considering clones larger than 100 tokens.
+There are fewer large clones than small clones, resulting in a limited statistical significance on our corpus when considering clones larger than 100 tokens.
 
@@
 The most unfavorable is refactoring clones to interfaces.
-However, the differences in maintainability in this table are generally small %\todo{and?}
-; according to our data relations have only a minor impact on the maintainability of clones.
+However, the differences in maintainability in this table are generally small; according to our data relations have only a minor impact on the maintainability of clones.
 
@@
 
-% A higher number of parameters directly influences the corresponding metric. 
-Fig.~\ref{fig:arguments} shows that more parameters negatively influence maintainability. Not only the %\todo{wasn't this a characteristic? this paragraph is somewhat confusing}
-number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
+Fig.~\ref{fig:arguments} shows that more parameters negatively influence maintainability.
+Not only the number of parameters metric is negatively influenced, but more method parameters also increase volume for the extracted method and each of the calls to it.
 Because of that, we see that the trend of the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.
 
-%\todo[inline]{one paragraph with a general remark on this discussion, summarizing our findings}
+\subsection{Threats to validity}
+To limit the scope of this research, we chose not to include human subjects in this study.
+However, we think that the results of this study could be strengthened by performing a survey on software engineering practitioners.
+We have determined maintainability scores only based on literature input and statistical analysis.
+It would be valuable to have a control group rate the refactorings performed by CR, as an extra form of input regarding the quality of the code transformations that CR performs.
+
+In Sec.~\ref{sec:metricformula} we proposed an aggregation to measure a maintainability score on small-grained changes.
+The assumptions stated in this section influence the validity of the maintainability scores shown in our results.
+We noticed that the maintainability scores displayed in Table~\ref{tab:relation_refactor} and Table~\ref{tab:return} were mostly influenced by the differences in the ``number of parameters'' metric.
+This is because, for the scores, we normalized the metrics over all values obtained by these metrics.
+As our data regarding ``number of parameters'' has a very low standard deviation, small changes in this metric will influence the maintainability score a lot.
+
 \section{Conclusion} \label{sec:conclusion}
-%\todo[inline]{one paragraph summarizing the context of our research}
 We define automatically refactorable clones and create a tool to detect and refactor them.
@@
 
-\subsection{Threats to validity}
-To limit the scope of this research, we chose not to include human subjects in this study.
-However, we think that the results of this study could be strengthened by performing a survey on software engineering practitioners.
-We have determined maintainability scores only based on literature input and statistical analysis.
-It would be valuable to have a control group rate the refactorings performed by CR, as an extra form of input regarding the quality of the code transformations that CR performs.
-
-In Section~\ref{sec:metricformula} we proposed an aggregation to measure a maintainability score on small-grained changes.
-The assumptions stated in this section influence the validity of the maintainability scores shown in our results.
-We noticed that the maintainability scores displayed in Table~\ref{tab:relation_refactor} and Table~\ref{tab:return} were mostly influenced by the differences in the ``number of parameters'' metric.
-This is because, for the scores, we normalized the metrics over all values obtained by these metrics.
-As our data regarding ``number of parameters'' has a very low standard deviation, small changes in this metric will influence the maintainability score a lot.
-
 \subsection{Future work}

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@
 We built a tool that can automatically apply refactorings to 28\% of the clones in our corpus using the ``Extract Method'' refactoring technique.
-It measured the change in four maintainability metrics to determine the impact of each refactoring on system maintainability.
+We measured the change in four maintainability metrics to determine the impact of each refactoring on system maintainability.
 We found that the most prominent factor influencing maintainability is the size of the clone.
@@
 
-We also limited our scope by choosing a set of four metrics.
+Our scope is currently limited to a set of four metrics.
 However, software maintainability depends on more factors and can be measured by more metrics.

### 2021-11-08 cefp/paper.tex
Updates from Overleaf
Grammar CEFP

@@
 \begin{abstract}
-One of the most important purposes of code clone analyses is as input for refactoring.
+Reducing clones in source code is one of the techniques to improve the maintainability of a software system.
 Which refactoring technique to use depends on where a clone is found and what the relation between clone instances in a clone class is.
@@
 Duplicate code fragments are often considered as bad design~\cite{fowler2018refactoring}.
-They increasing maintenance efforts or causing bugs in evolving software~\cite{heitlager2007practical}.
+They increase maintenance efforts or cause bugs in evolving software~\cite{heitlager2007practical}.
 Changing one occurrence of a duplicated fragment may require changes in other occurrences~\cite{ostberg2014automatically}.
@@
 We extend the state-of-the-art \cite{fontana2015duplicated} by defining location, relation and contents categories for clones to determine how they should be refactored.
-The extra categories we propose help to propose a refactoring opportunity that can automatically be applied, rather than merely suggesting the technique that has to be used \cite{fontana2015duplicated}.
+The extra categories we provide help to propose a refactoring opportunity that can automatically be applied, rather than merely suggesting the technique that has to be used \cite{fontana2015duplicated}.
 
@@
 If clone instances share a common class, no further refactoring techniques are required.
-If they are in the same inheritance hierarchy, ``Pull-Up Method'' can be used till the extracted method is in a location accessible by all instances.
+If they are in the same inheritance hierarchy, the ``Pull-Up Method'' can be used till the extracted method is in a location accessible by all instances.
 If the instances share a common interface, some languages allow to move the extracted method there.
@@
 \begin{enumerate}
-  \item \textbf{Relation:} The relation of clone instances in a clone class among each other through inheritance.
+  \item \textbf{Relation:} The relation of clone instances in a clone class through inheritance.
   \item \textbf{Location:} Where a clone instance occurs in the code.
@@
 \item \textbf{Same External Superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
-\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
+\item \textbf{Unrelated class}: There is at least one instance of the clone class that is not in the same hierarchy.
 \end{enumerate}
@@
 For clone classes with a \textit{No Indirect Superclass} relation, it is possible to create such an abstraction for the ancestor that does not have a parent.
-Clone classes with a \textit{External Superclass} or \textit{External Ancestor} relation obstruct the possibility of creating a superclass abstraction.
+Clone classes with an \textit{External Superclass} or \textit{External Ancestor} relation obstruct the possibility of creating a superclass abstraction.
 In such a case, it is possible to create an interface abstraction to make their relation explicit.
@@
 However, this claim is based on a small dataset and based on human copy-paste behavior rather than static code analysis.
-We decided to measure the locations of clones through static analysis on our dataset.
+We decided to measure the locations of clones through static analysis in our dataset.
 We chose the following categories:
@@
 For instance, we might have to move fields in an inheritance hierarchy.
-Or, we might have to perform a refactoring on more of an architectural level, if a large set of methods is cloned.
+Or, we might have to perform refactoring on an architectural level, if a large set of methods is cloned.
 
@@
 Constructors account for approximately 3\% of clones.
-In interfaces, only 1\% of clones is found.
+In interfaces, only 1\% of clones are found.
 
@@
 These refactorings are also often favorable.
-Another 24\% of clones are unrelated, which is often unfavorable because it often requires a more comprehensive refactoring.
+Another 24\% of clones are unrelated, which is often unfavorable because they often require more comprehensive refactoring.
 15\% of clones are in an interface.
@@
 \begin{itemize}
-  \item \textbf{Clone Relation}: The inheritance relation between clone instances among each other in a clone class.
+  \item \textbf{Clone Relation}: The inheritance relation between clone instances in a clone class.
   \item \textbf{Clone Location}: The location of clone instances in the codebase.
@@
 
-We looked at the \textbf{location} of clones: 78\% of clones are found at method-level of which 77\% is found in the body of a method or constructor.
+Regarding the \textbf{location} of clones: 78\% of clones are found at method-level of which 77\% is found in the body of a method or constructor.
 From this, we conclude that the ``Extract Method'' refactoring technique is most suitable to refactor most clones.
@@
 
-%\bibliographystyle{splncs04}
 \printbibliography

### 2021-11-10 cefp/paper.tex
Updates from Overleaf

@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
 \documentclass[runningheads]{llncs}
-%
 \usepackage{graphicx}
@@
 \addbibresource{refs.bib}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
 
 \begin{document}
-%
 \title{Finding Code Clone Refactoring Techniques by Mapping Clone Context}
-%
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
+
 \author{Simon Baars\inst{1,2}\orcidID{0000-0001-7905-1027} \and
 Ana Oprescu\inst{1,3}\orcidID{0000-0001-6376-0750}}
-%
-%\authorrunning{F. Author et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
+
 \institute{University of Amsterdam \and
@@
 \email{A.M.Oprescu@uva.nl}}
-%
-\maketitle              % typeset the header of the contribution
-%
+\maketitle
+
 \begin{abstract}
@@
 We define four relations that require different further refactoring techniques: Common Class, Common Hierarchy, Common Interface and Unrelated.
-% (ordered by how favorable their refactoring is).
-When clones are in the same class, no further techniques than ``Extract Method'' have to be applied.
-If they are not, further techniques have to be applied that create a trade-off on system maintainability.
 The closer classes are related, the more favorable refactoring clones by such relations becomes.
-37\% of clones are in the same class, 24\% share an inheritance hierarchy, 24\% are unrelated and 15\% have a common interface.% For each of these, we define subcategories to facilitate further understanding in what relations clones are found in the codebase.
-
-% What further techniques apply when refactoring a clone using the ``Extract Method'' technique depends on the relation among its clone instances.
-If clone instances share a common class, no further refactoring techniques are required.
-If they are in the same inheritance hierarchy, ``Pull-Up Method'' can be used till the extracted method is in a location accessible by all instances.
+37\% of clones are in the same class, 24\% share an inheritance hierarchy, 24\% are unrelated and 15\% have a common interface.
 
@@
 \end{abstract}
-%
-%
-%
+
 \section{Introduction}
@@
 
-%We perform statistical measurements on a large corpus of open-source software systems to determine which relation, location and contents category has the most clones.
-We find that 77\% of clones is found in the bodies of constructors and methods, which indicate clones that can be refactored by applying the ``Extract Method'' refactoring technique.
-Clones were found in very diverse relations, which indicates that in
 We perform statistical measurements on a large corpus of open-source software systems to determine which relation, location and contents category has the most clones.
@@
 This is shown schematically in Figure~\ref{fig:clonecontext}.
-%We define categories for each of these aspects and determine the categories of clones.
 
@@
 \end{figure}
-
-%Fig.~\ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances.
-The relation of clones through inheritance is determined for each clone class.
-The location and contents of clones are determined for each clone instance.
 
@@
 
-%When CloneRefactor applies automated refactorings, it uses this inheritance relation to see where it must place the refactored code.
-We explain this for each relation category over the following sections.
-
-%To determine the relation for a given clone class, we compare each node in a clone instance with the respective nodes in each other clone instance within a clone class.
-%So for a clone class with x clone instances and each clone instance has y nodes, we perform:
-
-%\begin{equation}\label{eq:sameclass}
-%\frac{x * (x + 1)}{2} * y
-%\end{equation}
-
-%comparisons to determine the relation.
-Each of these checks will result in one of the relations from the list above.
-Of these relations, the item lowest in the list is going to be the relation of the clone class.
-So for instance, if a clone class has 15 nodes that denote a \textit{Superclass} relation but 3 nodes are \textit{Unrelated}, the clone class becomes \textit{Unrelated}.
-
 \subsubsection{Common Class}
@@
 
- %We define the method as the first method declaration that is encountered when following the parent nodes in the AST for a given cloned node.
-%Please note that a clone instance may not always be in a method, for which this predicate will fail.
-
-%Clone classes are flagged as \textit{Same method} if all their clone instances are found in the same method.
-Cloned classes are flagged as \textit{Same class} if all their clone instances are found in the same class.
-%We define the class as the first class declaration that is encountered when following the parent nodes in the AST for a given cloned node.
-
 \subsubsection{Common Hierarchy}
@@
 A god object is an object that knows too much or does too much~\cite{fowler2018refactoring}.
-
-%Clone classes are flagged as \textit{Superclass} if the classes in which the clone instances are found are parent and child class of each other.
-Clone classes are flagged as \textit{Siblings} if the classes in which their clone instances are found all share the same parent and this parent class is not external.
-Clone classes are flagged as \textit{First Cousin} if the classes in which their clone instances are found all share the same grandparent and this grandparent class is not external.
-
-%Clone classes nodes are flagged as \textit{Ancestor} if the classes in which their clone instances are found are recursively the parent of an antecedent.
-Cloned nodes are flagged as \textit{Same Hierarchy} if the classes in which these nodes are found are all in the same inheritance hierarchy and not linked by any external classes.
 
@@
 
-%To check whether two cloned nodes have a \textit{Same Direct Interface} relation, we check that the classes to which these nodes belong both implement the same interface type.
-To check whether two cloned nodes have a \textit{Same Indirect Interface} relation, we recursively walk all types the class or interface of the cloned nodes implement and extend.
-The common interface that is closest to the cloned node in terms of depth of recursion will be flagged as the refactoring candidate.
-
 \subsubsection{Unrelated}
@@
 In such a case, it is possible to create an interface abstraction to make their relation explicit.
-
-%Cloned nodes are flagged \textit{No Direct Superclass} if they are in classes that do currently not have a parent.
-This marks the opportunity for creating a superclass abstraction and placing the extracted method there.
-Cloned nodes are flagged \textit{No Indirect Superclass} if any of their ancestors do not have a parent.
-In such a case, it would be possible to create such an abstraction for the ancestor that does not have a parent.
-
-%Cloned nodes are flagged \textit{External Superclass} if they are in a class which has an external parent.
-Cloned nodes are flagged \textit{External Ancestor} if one of their ancestors has an external parent.
-Both of these relations obstruct the possibility of creating a superclass abstraction.
-In such a case, an interface abstraction could be created to make their relation explicit.
 
@@
 
-%To detect whether a given clone instance is at Method Level, we check for each node in the clone instance whether it has an ancestor node that is a method declaration.
-A clone instance is considered ``Method Level'' if:
-
-%\begin{equation}\label{eq:samemethod}
-%\forall (n \in I)\text{ } Tn = \text{MethodDeclaration} \lor \exists (p \in ancestors(n)) \text{ } Tp = \text{MethodDeclaration}
-%\end{equation}
-
-%Where \textit{T} is the type of a node.
-\textit{ancestors(n)} denotes all of ancestor nodes of a node.
-The ancestor nodes are all recursive parents of a given node in the AST.
-Apart from this, we check that the MethodDeclaration ancestor of each clone instance is the same, to be sure the clone only spans a \textit{single} method.
-Figure \ref{fig:methodlevelclone} shows an example of a method level clone and its recursive parents.
-
-%\begin{figure}[H]
-%\begin{parcolumns}{2}
-%\colchunk[1]{
-%\begin{javacode}
-%  public void doA() { // |\textcolor{pgreen}{$p_2$}|
-%    public class Class1 { // |\textcolor{pgreen}{$p_3$}|
-%    if(isA()) // |\textcolor{pgreen}{$p_1$}|
-%|\highlightYellow|      doB(); // |\textcolor{pgreen}{$n_1$}|
-%  }
-%}
-%\end{javacode}}
-%\colchunk[2]{
-%\begin{javacode}
-%public class Class2 { // |\textcolor{pgreen}{$p_3$}|
-%  public void doB() { // |\textcolor{pgreen}{$p_2$}|
-%    if(isB()) // |\textcolor{pgreen}{$p_1$}|
-%|\highlightYellow|      doB(); // |\textcolor{pgreen}{$n_2$}|
-%  }
-%}
-%\end{javacode}}
-%\end{parcolumns}
-%\caption{Example of a method level clone and its parents.}
-%\label{fig:methodlevelclone}
-%\end{figure}
-
 \subsubsection{Class/Interface/Enumeration Level Clones}
@@
 Or, we might have to perform refactoring on an architectural level, if a large set of methods is cloned.
-
-%We detect these clones in the same way we detect method level clones: we walk up the AST until we find the first node that indicates one of these categories.
 
@@
 Sometimes, the declaration should be moved to a location that is accessible by all usages.
-%We check for clones in this category by checking that the first node in a clone instance is a declaration and the last node in the clone instance is the last node in the body of that declaration.
 
 \subsubsection{Partial Method/Constructor}
-These categories describe clone instances which are found in the body of a method or constructor.
-These clones can often be refactored by extracting a new method out of the cloned code.
-%We detect such clones by checking that each node in the clone instance has an ancestor node that is a MethodDeclaration, but none of the nodes is a method declaration.
-We describe the procedure by with we recursively seek the parent nodes of a node in Section~\ref{sec:methodlevelcr}.
+These categories describe clone instances which are found in the body of a method or constructor. These clones can often be refactored by extracting a new method out of the cloned code.
 
@@
 This increases the chance that these classes are missing some form of abstraction, or their abstraction is used inadequately.
-%We detect such clones by checking that each cloned node has a parent node that is a MethodDeclaration.
-This is the same process as described in equation \ref{eq:samemethod}.
-Additionally, we check that the MethodDeclaration ancestor of the first node in the clone instance differs from the last, to be sure that the clone instance spans over at least two methods.
 
@@
 Or, the fields should be somewhere in the inheritance structure where all objects containing the clone can access them.
-%We check for this category by validating that all nodes in the clone instance are a VariableDeclarator.
-Because VariableDeclarators in methods would already fall into the ``Partial Method'' category, this includes only globally defined fields.
 
@@
 Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for different relations (see Section~\ref{sec:setuprelation}).
-% Sander: is dat plaatje met overzicht van relaties van clone classen weg of ergens anders? hij is hier ook wel handig
 

### 2021-11-10 cefp/paper.tex
Updates from Overleaf

@@
 Which refactoring technique to use depends on where a clone is found and what the relation between clone instances in a clone class is.
-We define three influencing factors on how a clone should be refactored: Relation, Location and Contents.
-The Relation describes the inheritance relation among the clone instances in a clone class.
-The Location describes where a clone instance is found in the source code.
-The Contents describe what a clone instance spans.
+We define three influencing factors on how a clone should be refactored: relation, location and contents.
+The relation describes the inheritance relation among the clone instances in a clone class.
+The location describes where a clone instance is found in the source code.
+The contents describe what a clone instance spans.
 
@@
 
-We perform statistical measurements on a large corpus of open-source software systems to determine which relation, location and contents category has the most clones.
+We study a large corpus of open-source software systems to determine which relation, location and contents category has the most clones.
 We find that a significant portion of clones is found in the bodies of constructors and methods, which indicate clones that can be refactored by applying the ``Extract Method'' refactoring technique.
@@
 We use two definitions to argue about code clones~\cite{roy2007survey}:
-\\ \textbf{Clone instance}: A single code fragment of which a similar/identical copy exists elsewhere in the codebase.
-\\ \textbf{Clone class}: A set of similar/identical clone instances.
+\begin{itemize}
+    \item \textbf{Clone instance}: A single code fragment of which a similar/identical copy exists elsewhere in the codebase.
+    \item \textbf{Clone class}: A set of similar/identical clone instances.
+\end{itemize}
 
 To argue about the similarity relation between clone instances in a clone class, several clone type definitions have been proposed~\cite{roy2007survey}:
-\\\\
-\textbf{Type 1:} Identical code fragments except for variations in whitespace (may also be variations in layout) and comments.\\
-\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
-\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\
+\begin{itemize}
+    \item \textbf{Type 1:} Identical code fragments except for variations in whitespace (may also be variations in layout) and comments.
+    \item \textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.
+    \item \textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.
+\end{itemize}
 
@@
 \subsection{Relation}\label{sec:setuprelation}
-When merging code clones in object-oriented languages, it is important to consider the inheritance relation between clone instances. This relation has a big impact on how a clone should be refactored.
+When merging code clones in object-oriented languages, it is important to consider the relation between clone instances. This relation has a big impact on how a clone should be refactored.
 
@@
 
+\section{CloneRefactor}
+\todo[inline]{add text from other paper}
+
 \section{Experimental Setup}
-To find out in which location, relation and contents category most clones are found, we performed statistical measurements on a large corpus of diverse open-source projects.
+To find out in which location, relation and contents category most clones are found, we performed measurements on a large corpus of diverse open-source projects.
 We use the tool CloneRefactor\footnote{CloneRefactor is a code clone detection and refactoring tool: \url{https://github.com/SimonBaars/CloneRefactor}} which automatically determines these context aspects of code clones.
@@
 The projects and files in this corpus were de-duplicated manually.
-This results in a variety of Java projects that reflect the quality of average open-source Java systems and are useful to perform measurements on.
+This results in a variety of Java projects that reflect the quality of average open-source Java systems and are thus relevant to study.
 
@@
 \section{Results}
-To determine the refactoring method(s) that can be used to refactor most clones, we perform statistical analysis on the context of clones.
+To determine the refactoring method(s) that can be used to refactor most clones, we perform analysis on the context of clones.
 
@@
 
+\todo[inline]{add more details here, especially about comparison with previous studies.}
 \section{Conclusion}

### 2021-11-10 cefp/paper.tex
Updates from Overleaf

@@
 \usepackage{multirow}
+\usepackage{todonotes}
 \addbibresource{refs.bib}
@@
 
-\keywords{Code Clones \and MSR \and Clone Relation \and Inheritance \and Object-Oriented Programming.}
+\keywords{Code Clones \and Mining Software Repositories \and Clone Relation \and Inheritance \and Object-Oriented Programming.}
 \end{abstract}
@@
 
-\section{Background}
+\section{Background and Related Work}
 We use two definitions to argue about code clones~\cite{roy2007survey}:
@@
 It also makes the clone harder to refactor, as more transformations would be required.
-Higher clone types also become more disputable whether they actually indicate a harmful anti-pattern (as not every clone is harmful~\cite{jarzabek2010clones, kapser2008cloning}).
+Higher clone types also become more disputable whether they actually indicate a harmful anti-pattern as not every clone is harmful~\cite{jarzabek2010clones, kapser2008cloning}.
+
+Next, we outline relevant research to clone refactoring. A significant aspect is the context of clones.
+
+\subsection{Clone context analysis}\label{sec:rw:contextanalysis}
+Golomingi~\cite{koni2001scenario} explores mapping the relation between clone instances to refactoring methods.
+The author analyses the refactoring methods described by Martin Fowler~\cite{fowler1999refactoring} and analyzes what refactoring methods can be used to refactor clones with what inheritance relations.
+The identified clone relations are: Ancestor, Common Hierarchy, First Cousin, Same Method, Sibling, Single Class, Superclass and Unrelated.
+We extend this list with several more fine-grained relations, suitable for automatic refactoring.
+
+Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated} combine the research by Golomingi~\cite{koni2001scenario} with clone types 1 and 3 \cite{roy2007survey}.
+They use a large corpus~\cite{tempero2010qualitas} on which they perform statistical analysis of clone relations together with clone types.
+We repeat this research with a different setup, namely we elaborate further in the categories analysed, and thus get results with a finer granularity, and we use a larger dataset, namely the GitHub set of repositories~\cite{githubCorpus2013}.
+
+\subsection{Clone refactoring}
+Krishnan et al.~\cite{krishnan2013refactoring} approach clone refactoring as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design.
+The main focus of this study is to find out which clones \textbf{can} be refactored.
+We extend this work by looking into which clones \textbf{should} be refactored.
+We propose definitions for refactorable clones together with thresholds to be able to limit their negative impact on system design.
+We measure which clones improve maintainability when refactored.
+This results in a set of thresholds that can be used to detect and refactor clones that should be refactored.
+
+For refactoring clones, we took naming the extracted method outside of the scope of the study.
+To have this not influence the results, the metrics that determine the maintainability of an applied refactoring do not measure the quality of the name of the extracted method.
 
@@
 Based on current literature \cite{fontana2012duplicated, fontana2015duplicated}, we define the following aspects of a clone as its context:
-\begin{enumerate}
+\begin{itemize}
   \item \textbf{Relation:} The relation of clone instances in a clone class through inheritance.
@@
   \item \textbf{Contents:} The statements/declarations of a clone instance.
-\end{enumerate}
+\end{itemize}
 
@@
 
+\todo{Redo figure to show the clone context as a composite of relation, location and contents}
 \begin{figure}[H]
@@
 These categories are as follows:
-\begin{enumerate}
+\begin{itemize}
   \item \textbf{Same Method}: All instances of the clone class are in the same method.
@@
 \item \textbf{Unrelated class}: There is at least one instance of the clone class that is not in the same hierarchy.
-\end{enumerate}
+\end{itemize}
 
@@
 
-\begin{enumerate}
+\begin{itemize}
 \item \textbf{Same Direct Interface}: All instances of the clone class are in a class or interface implement the same interface.
@@
 \item \textbf{External Ancestor}: All instances of the clone class are in a class that does not have any external classes in its inheritance hierarchy.
-\end{enumerate}
+\end{itemize}
 
@@
 We chose the following categories:
-\begin{enumerate}
+\begin{itemize}
   \item \textbf{Method/Constructor Level:} A clone instance that does not exceed the boundaries of a single method or constructor (optionally including the declaration of the method or constructor itself).
@@
   \item \textbf{Interface/Enumeration Level:} A clone that is (a part of) an interface or enumeration.
-\end{enumerate}
+\end{itemize}
 We check the location of each clone instance for each of its nodes.
@@
 We selected the following categories to be relevant for refactoring:
-\begin{enumerate}
+\begin{itemize}
   \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
@@
   \item \textbf{Other:} Anything that does not match with above-stated categories.
-\end{enumerate}
+\end{itemize}
 
@@
 \centering
-\begin{tabular}{@{}llrrrr@{}}
+\begin{tabular}{@{}l|l|rr|rr@{}}
 \toprule
@@
 \centering
-\begin{tabular}{@{}llrrrr@{}}
+\begin{tabular}{@{}l|l|rr|rr@{}}
 \toprule
-\textit{\textbf{Category}} & \textit{\textbf{Contents}} & \textit{\textbf{Clone instances}} & \textit{\textbf{Total}} \\ \midrule
+\textit{\textbf{Category}} & \textit{\textbf{Contents}} & \textit{\textbf{Clone instances}} & \textit{\textbf{\%}} & \textit{\textbf{Total}} & \textit{\textbf{\%}} \\ \midrule
 \multirow{2}{*}{Partial} & Method Body & 219,540 & 74.05\% & \multirow{2}{*}{229,521}& \multirow{2}{*}{77.42\%} \\ \cmidrule(lr){2-4}

### 2021-11-12 cefp/paper.tex
Updates from Overleaf

@@
 A constructor is a special method that is called when an object is instantiated.
-Most modern clone refactoring studies only focus on clones at method level~\cite{choi2011extracting, yue2018automatic, kodhai2013method, arcelli2013software, lin2014clonepedia, mandal2014automatic, balazinska2000advanced, yongting2018detection, bouktif2006novel, fanqi2014using, devi2016study}.
+Most modern clone refactoring studies only focus on clones at method level~\cite{yue2018automatic, yongting2018detection}.
 This is because most clones reside at those places~\cite{lozano2007evaluating, fontana2015duplicated} and most of those clones can be refactored with a relatively simple set of refactoring techniques~\cite{kodhai2013method, fontana2015duplicated}.
@@
 \subsection{Location}
-Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different location categories (see Section~\ref{sec:setuplocation}).
+Table~\ref{tab:location} displays the number of clone instances found for the entire corpus for different location categories (see Section~\ref{sec:setuplocation}).
 
@@
 \subsection{Contents}
-Table~\ref{tab:contents} displays the number of clone classes found for the entire corpus for different content categories (see Section~\ref{sec:setupcontents}).
+Table~\ref{tab:contents} displays the number of clone instances found for the entire corpus for different content categories (see Section~\ref{sec:setupcontents}).
 

### 2021-11-20 cefp/paper.tex
Updates from Overleaf

@@
 
-This is shown schematically in Figure~\ref{fig:clonecontext}.
-
-\todo{Redo figure to show the clone context as a composite of relation, location and contents}
-\begin{figure}[H]
-  \centering
-    \includegraphics[width=0.8\columnwidth]{img/context}
-    \caption{Abstract representation of clone classes and clone instances.}
-  \label{fig:clonecontext}
-\end{figure}
-
 \subsection{Relation}\label{sec:setuprelation}
@@
 
-\begin{figure}[H]
+\begin{figure}
   \centering
@@
 \section{CloneRefactor}
-\todo[inline]{add text from other paper}
+To determine the context of clones, we use the tool CloneRefactor\footnote{CloneRefactor is a code clone detection and refactoring tool: \url{https://github.com/SimonBaars/CloneRefactor}}.
+CloneRefactor uses JavaParser~\cite{tomassetti2017javaparser} to parse the Abstract Syntax Tree (AST) of Java source code.
+We then find cloned nodes in the syntax tree, of which we map the relation, location, and contents.
+
+CloneRefactor uses this information to propose refactorings for the detected clones.
+Where clone instances are located in the code has a large impact on how it can be refactored, and what the impact on the design of the code is.
+In that way, the categorizations that CloneRefactor proposes helps determine which clones are most suitable for refactoring, as opposed to traditional clone detection approaches that do not take clone context into account.
 
@@
 To find out in which location, relation and contents category most clones are found, we performed measurements on a large corpus of diverse open-source projects.
-We use the tool CloneRefactor\footnote{CloneRefactor is a code clone detection and refactoring tool: \url{https://github.com/SimonBaars/CloneRefactor}} which automatically determines these context aspects of code clones.
 

### 2021-11-20 cefp/paper.tex
Updates from Overleaf

@@
 \addbibresource{refs.bib}
+\usepackage{makecell}
 
@@
 
-\todo[inline]{add more details here, especially about comparison with previous studies.}
+Comparing our results for the relation categories to the similar study of Fontana et al.~\cite{fontana2012duplicated, fontana2015duplicated}, we get the percentages stated in.
+They use a large corpus~\cite{tempero2010qualitas} on which they perform statistical analyses of clone relations together with clone types.
+Table \ref{tab:dcra-relation} displays the result of this analysis.
+We added percentages and ordering to this table for easier comparison with the results of our work (see \ref{sec:relationresults}).
+We also added the percentages of our work to this table.
+
+\begin{table}[H]
+\centering
+\begin{tabular}{@{}lrrrrr@{}}
+\toprule
+                         & \makecell{# clones\\(Fontana et al.)} & \makecell{Percentage\\(Fontana et al.)} & \makecell{Percentage\\(Our Work)} \\ \midrule
+Same Class               & 5,645  & 32.1\%     & 26.8\%    \\
+Same External Superclass & 4,384  & 25.0\%     & 20.6\%   \\
+Unrelated Class          & 2,758  & 15.7\%     & 18.4\%    \\
+Sibling Class            & 2,721  & 15.5\%     & 18.2\%    \\
+Common Hierarchy Class   & 970    & 5.5\%      & 0.8\%    \\
+Same Method              & 569    & 3.2\%      & 10.5\%    \\
+First Cousin Class       & 416    & 2.4\%      & 1.4\%    \\
+Superclass               & 91     & 0.5\%      & 3.1\%    \\
+Ancestor Class           & 13     & 0.1\%      & 0.2\%    \\ \bottomrule
+\end{tabular}
+\caption{Clone relation analysis by Fontana et al. \cite{fontana2012duplicated} measured over the Qualitas Corpus \cite{tempero2010qualitas}.}
+\label{tab:dcra-relation}
+\end{table}
+
+Some of our results differ quite a lot from their results. We think this is mostly accounted due to two differences in their setup:
+\begin{itemize}
+\item Fontana et al. use a corpus consisting of large higher-quality open-source software systems \cite{tempero2010qualitas} where we use a more varied corpus \cite{githubCorpus2013}.
+\item Fontana et al. use clone pairs while we use clone classes.
+\end{itemize}
+
 \section{Conclusion}

### 2021-11-20 cefp/paper.tex
Updates from Overleaf

@@
 \usepackage{multirow}
-\usepackage{todonotes}
 \addbibresource{refs.bib}
@@
 \centering
+\caption{Number of clone classes per clone relation.}
 \begin{tabular}{@{}l|l|rr|rr@{}}
@@
 \end{tabular}
-\caption{Number of clone classes per clone relation.}
 \label{tab:relation}
@@
 \centering
+\caption{Amount of clone instances with a per location category.}
 \begin{tabular}{@{}lrr@{}}
@@
 \end{tabular}
-\caption{Amount of clone instances with a per location category.}
 \label{tab:location}
@@
 \centering
+\caption{Number of clone instances for clone contents categories}
 \begin{tabular}{@{}l|l|rr|rr@{}}
@@
 \end{tabular}
-\caption{Number of clone instances for clone contents categories}
 \label{tab:contents}
@@
 \centering
+\caption{Clone relation analysis by Fontana et al. \cite{fontana2012duplicated} measured over the Qualitas Corpus \cite{tempero2010qualitas}.}
 \begin{tabular}{@{}lrrrrr@{}}
 \toprule
-                         & \makecell{# clones\\(Fontana et al.)} & \makecell{Percentage\\(Fontana et al.)} & \makecell{Percentage\\(Our Work)} \\ \midrule
+                         & \makecell{Nr. of clones\\(Fontana et al.)} & \makecell{Percentage\\(Fontana et al.)} & \makecell{Percentage\\(Our Work)} \\ \midrule
 Same Class               & 5,645  & 32.1\%     & 26.8\%    \\
@@
 \end{tabular}
-\caption{Clone relation analysis by Fontana et al. \cite{fontana2012duplicated} measured over the Qualitas Corpus \cite{tempero2010qualitas}.}
+
 \label{tab:dcra-relation}

### 2021-11-20 cefp/paper.tex
Updates from Overleaf

@@
 \section{CloneRefactor}
-To determine the context of clones, we use the tool CloneRefactor\footnote{CloneRefactor is a code clone detection and refactoring tool: \url{https://github.com/SimonBaars/CloneRefactor}}.
+To determine the context of clones, we use the tool CloneRefactor\cite{simonbaarsclonerefactor}.
 CloneRefactor uses JavaParser~\cite{tomassetti2017javaparser} to parse the Abstract Syntax Tree (AST) of Java source code.
@@
 \subsection{The Corpus}\label{chap:corpus}
-For our experiments we use a large corpus of open-source projects assembled by Allamanis et al.~\cite{githubCorpus2013}\footnote{The corpus can be downloaded at: \url{http://groups.inf.ed.ac.uk/cup/javaGithub/}}.
+For our experiments we use a large corpus of open-source projects assembled by Allamanis et al.~\cite{githubCorpus2013}.
 This corpus contains a set of Java projects from GitHub, selected by the number of forks.
@@
 
-Because CloneRefactor requires all dependencies for the projects it analyses, we created a set of scripts\footnote{All scripts to prepare the corpus are available on GitHub: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts}} to filter the corpus for all projects for which we can obtain all dependencies using Maven\footnote{Maven is a build automation system, mainly used for Java programs: \url{https://maven.apache.org/}}.
+Because CloneRefactor requires all dependencies for the projects it analyses, we created a set of scripts\cite{simonbaarscorpusscripts} to filter the corpus for all projects for which we can obtain all dependencies using Maven.
 
-This procedure results in 2,267 Java projects including all their dependencies\footnote{The full list of projects is in the following file in our GitHub repository: \url{https://github.com/SimonBaars/GitHub-Java-Corpus-Scripts/blob/master/filtered_projects.txt}}.
+This procedure results in 2,267 Java projects including all their dependencies\footnote{The full list of projects is in the \texttt{SimonBaars/GitHub-Java-Corpus-Scripts} GitHub repository as \texttt{filtered\_projects.txt}}.
 The projects vary in size and quality.
-The total size of all projects is 14.210.357 lines (11,315,484 when excluding whitespace) over a total of 99,586 Java files.
+The total size of all projects is 14,210,357 lines (11,315,484 when excluding whitespace) over a total of 99,586 Java files.
 This is an average of 6,268 lines over an average of 44 files per project, 141 lines on average per file.
@@
 \section{Results}
-To determine the refactoring method(s) that can be used to refactor most clones, we perform analysis on the context of clones.
+To determine the refactoring methods that can be used to refactor most clones, we perform analysis on the context of clones.
 

### 2021-11-20 cefp/paper.tex
Updates from Overleaf

@@
 Which refactoring technique to use depends on where a clone is found and what the relation between clone instances in a clone class is.
-We define three influencing factors on how a clone should be refactored: relation, location and contents.
+We define three influencing factors on how a clone should be refactored: relation, location, and contents.
 The relation describes the inheritance relation among the clone instances in a clone class.
@@
 
-Based on experiments on corpus of open-source Java projects we find that most clones (77\%) are in the body of methods or constructors and thus the ``Extract Method'' refactoring technique applies.
+Based on experiments on a corpus of open-source Java projects we find that most clones (77\%) are in the body of methods or constructors and thus the ``Extract Method'' refactoring technique applies.
 What further techniques are required for the refactoring depends on the relation among the clone instances of a clone.
-We define four relations that require different further refactoring techniques: Common Class, Common Hierarchy, Common Interface and Unrelated.
+We define four relations that require different further refactoring techniques: Common Class, Common Hierarchy, Common Interface, and Unrelated.
 The closer classes are related, the more favorable refactoring clones by such relations becomes.
@@
 For instance, a combination of constructors and methods or a combination of fields and methods is cloned.
-Such clones indicate, like the ``Several Methods'', the requirement of performing a more architectural-level refactoring.
+Clones in this category, similarly to ``Several Methods'', require more architectural-level refactorings.
 These are often more complicated to refactor, especially when aiming to automate this process.
